### 2019-06-18 1905 Mungbean_PM_preliminary_analysis.Rmd
Reserected deleted RMD file from (2019) Powdery_mildew_Mungbean repo, which was accidently deleted during bookdown compilations

---
title: "PM Mungbean meta-analysis"
author: "P. Melloy"
date: "30 April 2019"
output: html_document
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

## Studies considered in meta-analysis

* 2001  
   + Bongeen #1  
   + Bongeen #2

* 2002
   + Hermitage #1  
   + Hermitage #2  
   + Kingaroy

* 2004
   + Redvale

* 2010  
   + Hermitage  
   + Kingaroy

* 2011  
   + Hermitage  
   + Kingaroy

* 2012  
   + Gatton  
   + Kingaroy

* 2013
   + Premer; no raw data
   + Milmerran; no raw data
   + Mt Mary; no raw data
   + Goolhi; no raw data

* 2015  
   + Hermitage  
   + Dalby - Site abandoned due it insuficient/late disease infection  
   + Emerald

* 2016  
   + Hermitage  
   + Kingaroy  
   + Emerald

* 2017  
   + Fogerty  
   + Hermitage

* 2018
   + Wellcamp

* 2019
   + Hermitage

### 2001 - 2004 trials

Trial data were obtained from a non-published manuscript.
Ratings for powdery Mildew were on a 1-5 rating scale and can be read in the file "Powdery mildew paper#1.doc".  
Comparing Trials which have not used the same rating scale wil be done using a percentage change.

### 2013 Field trials
Fungicide treatments were described in reports in Two letter acronyms. The following is the assumed usage.

```{r}
knitr::kable(
   cbind(Acronym = c("SF", "Ti", "AX", "Ca"),
         Expected_Fungicide = c("Sulphur", "Tilt", "Amistar Xtra", "Carbendazim"),
         Active_Ingredient = c("Sulphur", "Propiconazole", "Amistar", "Carbendazim")
   )
)
```

## Research questions

What is the length of a Mungbean season and how has it varied in this trial

How has the first sign of powdery mildew changed over the seasons and between experimental sites.

When is the optimum time to spray fungicide to limit the impact of powdery mildew on mungbean yeilds.

When would the ideal planting time be to make use of powdery mildew defoliation in the final growth of the crop.

Do infections that occur before flowering increase the probable yield loss?

## Powdery Mildew analysis 2011 - 2017
### Summary of data

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(openxlsx)
source("Cleaning historical data.R", echo = FALSE, print.eval = FALSE)
# ___ Datasets available ___
# data   Herm_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2017, Hermitage and Fogerty
# data   King_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2016, Hermitage and Kingaroy
# data   Fogerty_17.1   - Full disease ratings and yeild data from Fogerty field trial in 2017
# data   Herm_17.1      - Full disease ratings and yeild data from Hermitage field trial in 2017
# data   PM_MB_17       - Full disease ratings and yeild data from Hermitage and Fogerty in 2017
# data   PM_MB_16       - End of season powdery mildew rating and Yield data from two field trials in 2016, Hermitage and Kingaroy
# data   PM_MB_means    - Mean disease rating and yeild data, from trial reports
PM.dat <- read.xlsx("C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/1902 powdery mildew-Mungbean - Collated means.xlsx",
                    sheet = "Sheet1", startRow = 1, colNames = TRUE, detectDates = TRUE)
knitr::kable(
PM.dat %>%
   group_by(Trial_ref, Year, Location, trial_design, Replicates, planting_date, emergence_date, first_sign_disease) %>%
   summarise(Treatments = length(E_treatment))
)
PM.dat$Trial_ref <- factor(PM.dat$Trial_ref)
PM.dat$Location <- factor(PM.dat$Location)
PM.dat$Year <- factor(PM.dat$Year)
PM.dat$host_genotype <- factor(PM.dat$host_genotype)
PM.dat$Fungicide <- factor(PM.dat$Fungicide)
PM.dat$Trade_name <- factor(PM.dat$Trade_name)
#glimpse(PM.dat)
#str(PM.dat)
first1 <- PM.dat %>%
   group_by(Trial_ref, Location) %>%
   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
   filter(Location == "Kingaroy")

King_first <- subset(first1, Location == "Kingaroy")$First_sign
```

### Plotting weather data

The mungbean DSS determines the need to spray on:  
   1. The presence of the disease  
   2. The forecasted maximum temperatures in the next seven days  
   3. The number of days over the next seven days with rainfall

Below I am plotting the mean maximum temperures over 7 days during the growing season at each Mungbean trial site. The vertical lines indicate when powdery mildew was first observed in that season. Variation may exist in the sowing date of each trial.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Need weather data between 2011 and 2017
library(ggplot2)
# function to extract date from the year
# format should be Universal time format
year.day <- function(date){
   if(is.na(date) == TRUE){ 
      print(NA)
      } else {
as.numeric(as.Date(date) - as.Date(paste0(substr(date, start = 1, stop = 4),"-01-01")))
      }
   }
# Function to generate some of the ggplot grouping colours
gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}
cols1 <- gg_color_hue(4)
silo_war_Tmax <- getPPD2(station_id = 041525,start = 20110101,end = 20160630, silo.apikey = silo.API, variables = "max_temp,min_temp,daily_rain")
# retrieve the maximum temperatures from the six yearsd between 2011 and 2017 at weather station 041525 (Hermitage)
silo_king_Tmax <- getPPD2(lat = -26.58, long = 151.83, start = 20110101, end = 20160630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
silo_gatton_Tmax <- getPPD2(lat = -27.56, long = 152.32, start = 20110101, end = 20170630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
silo_emerald_Tmax <- getPPD2(lat = -23.54, long = 148.19, start = 20110101, end = 20170630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
experiment_sites <- data.frame(
   location = c("Hermitage", "Kingaroy research station","Gatton", "Emerald Agricultural College"),
   lat = c(-28.215 ,-26.58,-27.56,-23.54),
   lon = c(152.1003,151.83,152.32,148.19)
)
# leaflet() %>%
#    addProviderTiles("Esri.WorldTopoMap") %>%
#    addMarkers(lng = experiment_sites$lon, lat = experiment_sites$lat)
# head(silo_gatton_Tmax)
# ______  Kingaroy_______
max_T <- vector()
min_T <- vector()
for(i in 1:length(silo_king_Tmax[,1])){
   max_T <- c(max_T,mean(silo_king_Tmax$max_temp[i:(i+7)]))
   min_T <- c(min_T,mean(silo_king_Tmax$min_temp[i:(i+7)]))
}
king_Tm_aver <- data.frame(location = "Kingaroy", date = as.Date(silo_king_Tmax$date), max_T, min_T, daily_rain = silo_king_Tmax$daily_rain)
# Add columns for Year and date to data
king_Tm_aver <- king_Tm_aver %>%
   mutate(Year = substr(king_Tm_aver$date, start = 1, stop = 4),
          Day = year.day(king_Tm_aver$date)) 
# Create data subset of Powdery mildew data means for the first sign of the disease by location
King_FS <- PM.dat %>%
   group_by(Trial_ref, Location, Year) %>%
   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
   filter(Location == "Kingaroy") %>%
   mutate(Day = year.day(First_sign))
ggplot(subset(king_Tm_aver, Year == levels(factor(King_FS$Year))),
              aes(Day))+
   geom_line(aes(y = max_T, colour = Year))+
   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
   geom_line(aes(y = min_T, colour=Year))+
   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
   title = "Maximum and minimum daily temperatures in Kingaroy")+
   scale_y_continuous(limits = c(0,40))+
   scale_x_continuous(limits = c(0,200), 
                      labels = c(subset(king_Tm_aver, Year == 2016)$date[c(1,50,100,150,200)]),
                      breaks = c(1,50,100,150,200))+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   geom_vline(xintercept = King_FS$Day[1], size =1, colour = cols1[1], linetype = "dotted")+
   geom_vline(xintercept = King_FS$Day[2], size =1.5, colour = cols1[2], linetype = "dotted")+
   geom_vline(xintercept = King_FS$Day[3], size =1, colour = cols1[3], linetype = "dashed")+
   geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
   scale_x_continuous(limits = c(1,180),
                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
                      labels = c("2012-Jan-01","2012-Feb-01","2012-Mar-01","2012-Apr-01","2012-May-01","2012-Jun-01","2012-Jul-01"))
# ______  Hermitage  _______
max_T <- vector()
min_T <- vector()
for(i in 1:length(silo_war_Tmax[,1])){
   max_T <- c(max_T,mean(silo_war_Tmax$max_temp[i:(i+7)]))
   min_T <- c(min_T,mean(silo_war_Tmax$min_temp[i:(i+7)]))
}
war_Tm_aver <- data.frame(location = "Hermitage", date = as.Date(silo_war_Tmax$date), max_T, min_T, daily_rain = silo_war_Tmax$daily_rain)
# Add columns for Year and date to data
war_Tm_aver <- war_Tm_aver %>%
   mutate(Year = substr(war_Tm_aver$date, start = 1, stop = 4),
          Day = year.day(war_Tm_aver$date)) 
# Create data subset of Powdery mildew data means for the first sign of the disease by location
Herm_FS <- PM.dat %>%
   group_by(Trial_ref, Location, Year) %>%
   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
   filter(Location == "Hermitage") %>%
   mutate(Day = year.day(First_sign))
ggplot(subset(war_Tm_aver, Year == levels(factor(Herm_FS$Year))),
              aes(Day))+
   geom_line(aes(y = max_T, colour = Year))+
   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
   geom_line(aes(y = min_T, color = Year))+
   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
   title = "Maximum and minimum daily temperatures in Hermitage")+
   scale_y_continuous(limits = c(0,40))+
   scale_x_continuous(limits = c(0,200), 
                      labels = c(subset(war_Tm_aver, Year == 2016)$date[c(1,50,100,150,200)]),
                      breaks = c(1,50,100,150,200))+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   geom_vline(xintercept = Herm_FS$Day[1], size =1, colour = cols1[1], linetype = "dotted")+
   geom_vline(xintercept = Herm_FS$Day[2], size =1.5, colour = cols1[2], linetype = "dotted")+
   geom_vline(xintercept = Herm_FS$Day[3], size =1, colour = cols1[3], linetype = "dashed")+
      geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
   scale_x_continuous(limits = c(1,180),
                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
                      labels = c("Jan-01","Feb-01","Mar-01","Apr-01","May-01","Jun-01","Jul-01"))
# ______  Gatton  _______
max_T <- vector()
min_T <- vector()
for(i in 1:length(silo_gatton_Tmax[,1])){
   max_T <- c(max_T,mean(silo_gatton_Tmax$max_temp[i:(i+7)]))
   min_T <- c(min_T,mean(silo_gatton_Tmax$min_temp[i:(i+7)]))
}
# put maximum, minimum temperatures into a dataframe corresponding with thier corresponding date
Gat_Tm_aver <- data.frame(location = "Gatton", date = as.Date(silo_gatton_Tmax$date), max_T, min_T, daily_rain = silo_gatton_Tmax$daily_rain)
# Add columns for Year and date to data
Gat_Tm_aver <- Gat_Tm_aver %>%
   mutate(Year = substr(Gat_Tm_aver$date, start = 1, stop = 4),
          Day = year.day(Gat_Tm_aver$date)) 
# Create data subset of Powdery mildew data means for the first sign of the disease by location
Gatton_FS <- PM.dat %>%
   group_by(Trial_ref, Location) %>%
   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
   filter(Location == "Gatton") %>%
   mutate(Year = factor(substr(First_sign,1,4)),
          Day = year.day(First_sign))
ggplot(subset(Gat_Tm_aver, Year == levels(Gatton_FS$Year)),
               aes(Day))+
   geom_line(aes(y = max_T, colour = Year))+
   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
   geom_line(aes(y = min_T, colour = Year))+
   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
   title = "Maximum and minimum daily temperatures in Gatton")+
   scale_y_continuous(limits = c(0,40))+
   scale_x_continuous(limits = c(0,200), 
                      labels = c(subset(Gat_Tm_aver, Year == levels(Gatton_FS$Year))$date[c(1,50,100,150,200)]),
                      breaks = c(1,50,100,150,200))+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   geom_vline(xintercept = Gatton_FS$Day, colour = "green", size =1)+
      geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
   scale_x_continuous(limits = c(1,180),
                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
                      labels = c("2012-Jan-01","2012-Feb-01","2012-Mar-01","2012-Apr-01","2012-May-01","2012-Jun-01","2012-Jul-01"))
#   scale_x_continuous(limits = as.Date(c("2012-01-01","2012-06-01")))

# line 259
vec1 <- year.day(Herm_FS$First_sign)
```

### Yield saved from fungicide applications

The data plotted below are from the past field trials (2011 - 2017) described in the aforementioned table. All data are a list of mean values from each treatment applied in each experiment. Various factors have been studied in the previous experiments which may influence the following results. The following variables were disregarded in the plots below.

   1) Fungicide type
   2) Fungicide dose
   3) row spacing
   4) Host cultivars
   5) Experiment location
   6) Final disease rating

```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
library(lme4)
# What row spacing leads to the highest yield penalty
head(PM_MB_17)
class(PM_MB_17$Incidence_assessment_date)
class(PM_MB_17$Incidence)
# `2017-05-11` # last assessment Fogerty
subset(PM_MB_17, location == "Hermitage")
ggplot(subset(PM_MB_17, Treatment.No == "T1"||"1"), 
       aes(y = Incidence, x = Incidence_assessment_date, colour = location))+
   geom_point()+
   geom_smooth()+
   scale_y_continuous(limits = c(-5,15))
# PM_MB_means <- subset(PM_MB_means, Fungicide != "control")   
# PM_MB_means$Fungicide <- factor(PM_MB_means$Fungicide, levels = c("Sulphur", "Amistar", "propiconazole", "Tebeconazole"))
PM_MB_means$Fungicide <- factor(PM_MB_means$Fungicide, levels = c("control", "Sulphur", "Amistar", "propiconazole", "Tebeconazole"))
yield_lmer1 <- lmer(`yield_gain` ~ factor(total_Fungicide) + Fungicide + factor(Year) + (factor(Year)|Location), 
                    data = PM_MB_means, na.action = na.omit, REML = F)
# removed the Year interaction with location
yield_lmer2 <- lmer(`yield_gain` ~ factor(total_Fungicide) + Fungicide + factor(Year) + (1|Location), 
                    data = PM_MB_means, na.action = na.omit, REML = F)
# Removing Fungicide as different fungicides were sprayed a different number of times
yield_lmer3 <- lmer(`yield_gain` ~ factor(total_Fungicide)  + factor(Year) + (1|Location), 
                    data = PM_MB_means, na.action = na.omit, REML = F)
# Removing Fungicide as different fungicides were sprayed a different number of times
yield_lmer4 <- lmer(`yield_gain` ~ factor(total_Fungicide)  + factor(Year) + (1|Location) + (1|Fungicide), 
                    data = PM_MB_means, na.action = na.omit, REML = T)
ranef(yield_lmer4)
anova(yield_lmer1, yield_lmer2) # P = 0.8943  # removed random intercept 'Year' for each random slope 'Location' # Keep simpler model 
anova(yield_lmer2, yield_lmer3) # P = 0.8005  # Removed (FE) Fungicide     #     Fungicide showed not to be significant in protecting yield
anova(yield_lmer3, yield_lmer4) # P = 1       # Added Fungicide as a random effect #     Fungicide showed not to contribute to variation and 
yield_lmer <- lmer(`yield_gain` ~ factor(total_Fungicide) + factor(Year) + (1|Location), 
                    data = PM_MB_means, na.action = na.omit)
summary(yield_lmer)
ranef(yield_lmer)
```

#### Yield saved 
##### Number of fungicide applications
The following density plots show mean yield saved in relation to how many sprays were applied.

```{r warning=FALSE, echo=FALSE}
library(ggplot2)
PM_MB_means <- read.xlsx("C:/Users/U8011054/Documents/GitHub/Mungbean_PM/data/1902 powdery mildew-Mungbean - Collated means.xlsx", detectDates = TRUE)
# Making a table of showing the upper and lower percentiles (95%)
quant_PMy <- PM_MB_means %>%
   filter(Fungicide != "control") %>%
   group_by(total_Fungicide) %>%
   summarise(lower = quantile(yield_gain, na.rm = T, c(0.025)),
             upper = quantile(yield_gain, na.rm = T, c(0.975)))
# Density plot of Number of fungicide applications and the resulting yeild saved (as a proportion)
ggplot(subset(PM_MB_means,Fungicide != "control"), aes(yield_gain))+
   geom_density(aes(group = factor(total_Fungicide), fill = factor(total_Fungicide)), alpha = 0.6)+
   geom_vline(xintercept = 0, size =1)+
   labs(x = "Grain yeild saved (t/ha)",
   title = "Density plot of grain yield saved from differing numbers of fungicide applications")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   geom_vline(data = quant_PMy, aes(xintercept = lower, 
               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
   geom_vline(data = quant_PMy, aes(xintercept = upper, 
               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
   guides(colour = guide_legend(title="Upper (97.5%) and \nLower (2.5%) percentiles"),
          fill=guide_legend(title="Number of \nFungicide applications"))+
   scale_x_continuous(limits = c(-0.3,0.8))

names(quant_PMy) <- c("Number of sprays", "2.5 percentile", "97.5 percentile")
knitr::kable(quant_PMy)
#             col.names = c("Number of sprays", "2.5 percentile", "97.5 percentile"))
#            caption = "The 'upper' and 'lower' percentiles for yeild saved (t/Ha) against the number of Fungicide sprays in a season. Data from 2011-2017 mungbean experimental means. Data ignores factors such as fungicide, dose, season or location of experiment")
# Making a table of showing the upper and lower percentiles (95%)
quant_PM <- PM_MB_means %>%
   filter(Fungicide != "control") %>%
   group_by(total_Fungicide) %>%
   summarise(lower = quantile(prop_YG, na.rm = T, c(0.025)),
             upper = quantile(prop_YG, na.rm = T, c(0.975)))
# Density plot of proportion of yield saved
ggplot(subset(PM_MB_means,Fungicide != "control"), aes(prop_YG))+
   geom_density(aes(group = factor(total_Fungicide), fill = factor(total_Fungicide)), alpha = 0.6)+
   geom_vline(xintercept = 0, size =1)+
   labs(x = "Proportion of grain yeild saved",
   title = "Density plot of the grain yield proportion saved \n by the number of fungicide applications")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   geom_vline(data = quant_PM, aes(xintercept = lower, 
               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
   geom_vline(data = quant_PM, aes(xintercept = upper, 
               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
   guides(colour = guide_legend(title="Upper (97.5%) and \nLower (2.5%) percentiles"),
          fill=guide_legend(title="Number of \nFungicide applications"))+
   scale_x_continuous(limits = c(-0.3,0.55))
names(quant_PM) <- c("Number of sprays", "2.5 percentile", "97.5 percentile")
knitr::kable(quant_PM)   
#knitr::kable(quant_PM, 
#             col.names = c("Number of sprays", "2.5 percentile", "97.5 percentile"))
             #caption = "The 'upper' and 'lower' percentiles for proportion of yeild saved against the number of Fungicide sprays in a season. Data from 2011-2017 mungbean experimental means. Data ignores factors such as fungicide, dose, season or location of experiment")
```

\n\n\n\n\n\n\n

#### Timing of Fungicide application
The following density plots show mean yield saved (t/Ha) or proportion yield saved in relation to when the first fungicide spray was applied in relation to when powdery mildew was first seen in the mungbean crop.

```{r echo = FALSE, message=FALSE, warning=FALSE}
# removing 2017 and control data
# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
PM_MB_means1 <- PM_MB_means %>%
   filter(Fungicide != "control") %>%
   filter(Year != 2017) %>%
#   filter(total_Fungicide ==1) %>%
   mutate(days_from_1st = as.numeric(as.Date(Fungicide_application_1) - first_sign_disease))
colnames(PM_MB_means)
days_from_fungicid <- function(FSD,F1,F2,F3){
   dF1 <- as.numeric(as.Date(F1) - as.Date(FSD))
   dF2 <- as.numeric(as.Date(F2) - as.Date(FSD))
   dF3 <- as.numeric(as.Date(F3) - as.Date(FSD))
   if(is.na(dF1)){
      return(NA)} else{
   if(between(dF1,lower = -1, upper = 1000)){
      return(dF1)}else{
   if(is.na(dF2)){
      return(dF1)}else{
      if(between(dF2,lower = dF1, upper = -0.1)){
            return(dF2)} else{
               return(dF3)}}
            }}
}
vec1<- vector()
for(i in 1:dim(PM_MB_means1)[1]){
   dF1 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_1)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
   dF2 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_2)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
   dF3 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_3)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
   if(is.na(dF1)){
      vec1 <- c(vec1,dF1)} else{
         if(between(as.numeric(dF1),-1, 1000)){
            vec1 <- c(vec1,dF1)}else{
               if(is.na(dF2)){
                  vec1 <- c(vec1,dF1)}else{
                     if(between(as.numeric(dF2),as.numeric(dF1), -1.1)){
            vec1 <- c(vec1,dF2)} else{
               if(as.numeric(dF3)>=0){
                  vec1 <- c(vec1,dF2)} else{
                     vec1 <- c(vec1,dF3)}}}
            }}
}
PM_MB_means1$spray_diff <- vec1 # gives the 
PM_MB_means1$days_from_1st
#summary(factor(PM_MB_means1$days_from_1st))
# Density plot of proportion of yield saved
ggplot(PM_MB_means1, aes(prop_YG))+
   geom_density(aes(group = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20)), 
                    fill = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20))), alpha = 0.3)+
   geom_vline(xintercept = 0, size =1)+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="First spray window\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.3,0.55))
###########################################3
unique(PM_MB_means1$days_from_1st)
ggplot(PM_MB_means1, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))~., factor(PM_MB_means1$Fungicide))+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.2,0.55))
unique(PM_MB_means1$spray_diff)
ggplot(PM_MB_means1, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means1$spray_diff, c(-29,-20,-15,-12,-0.5,1.5,7,10,12,20))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means1$spray_diff, c(-29,-20,-15,-12,-0.5,1.5,7,10,12,20))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.2,0.55))
# Making a table of showing the upper and lower percentiles (95%)
quant_PM_prop <- PM_MB_means1 %>%
   mutate(cut_daysfrom1st = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20))) %>%
   group_by(cut_daysfrom1st) %>%
   summarise(lower = quantile(prop_YG, na.rm = T, c(0.025)),
             upper = quantile(prop_YG, na.rm = T, c(0.975)))
names(quant_PM_prop) <- c("Days relative to\nfirst incidence", "2.5 percentile", "97.5 percentile")
cat("Lower (2.5) and Upper (97.5) quantiles for the proportion of yield gained, when the first fungicide applied relative to when powdery mildew is first seen")
knitr::kable(quant_PM_prop)   
ggplot(PM_MB_means1, aes(yield_gain))+
   geom_density(aes(fill = cut(PM_MB_means1$days_from_1st, c(-29,-15,-6,-0.5,0.5,2,10,20))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means1$days_from_1st, c(-29,-15,-6,-0.5,0.5,2,10,20))~.)+
   scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Grain yield (t/Ha) saved",
   title = "Grain yield (t/Ha) saved, grouped by when the\nfirst fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.4,1.2))
# Making a table of showing the upper and lower percentiles (95%)
quant_PM_prop <- PM_MB_means1 %>%
   mutate(cut_daysfrom1st = cut(PM_MB_means1$days_from_1st, c(-29,-20,-15,-6,-0.5,0.5,2,10,20))) %>%
   group_by(cut_daysfrom1st) %>%
   summarise(lower = quantile(yield_gain, na.rm = T, c(0.025)),
             upper = quantile(yield_gain, na.rm = T, c(0.975)))
names(quant_PM_prop) <- c("Days relative to\nfirst incidence", "2.5 percentile", "97.5 percentile")
print("Yield gain quantiles when the first fungicide applied relative to when powdery mildew is first seen, Lower (2.5) and Upper (97.5) quantiles of yeild ")
knitr::kable(quant_PM_prop)  
```

```{r}
PM_MB_means2 <- PM_MB_means1 %>%
   filter(Fungicide == "Tebeconazole")
unique(PM_MB_means2$spray_diff)
ggplot(PM_MB_means2, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-1,2,7,10,12,20))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means2$spray_diff, c(1,2,7,10,12,20))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.2,0.55))
#__________________________________________________________________________________________________________
levels(factor(PM_MB_means$Fungicide))
PM_MB_means2 <- PM_MB_means1 %>%
   filter(Fungicide == "Sulphur" |
             Fungicide == "Sulphur (SC)" |
             Fungicide == "Sulphur (Ultra SC)" |
             Fungicide == "Sulphur (WP)")
unique(PM_MB_means2$spray_diff)
ggplot(PM_MB_means2, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.3,0.6))
Chemical <- c("Amistar","Carbendazim","Tebeconazole", "propiconazole")
levels(factor(PM_MB_means$Fungicide))
for(Chem in Chemical){
PM_MB_means2 <- PM_MB_means1 %>%
   filter(Fungicide == Chem)
cat(Chem)
cat(unique(PM_MB_means2$spray_diff))
p1 <- ggplot(PM_MB_means2, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title=paste(Chem,"Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease")))+
   scale_x_continuous(limits = c(-0.3,0.6))
print(p1)
Sys.sleep(10)
}
```

### 2019-06-19 index.Rmd
Initialising Bookdown files

---
title: "Powdery Milder yield loss mitigation strategies in Mungbean a Meta-analysis"
author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
date: "19/06/2019"
output:
  bookdown::html_book:
    theme: united
---

### 2019-06-19 01_Meta-analysis_experiments.Rmd
Served _book Updated ReadMe breaking up 1905_Mungbean_PM_preliminary_analysis into seperate files. Created index.Rmd Created 1_Meta-analysis_experiments

--- 2019-06-18 1905 Mungbean_PM_preliminary_analysis.Rmd
@@
----
-title: "PM Mungbean meta-analysis"
-author: "P. Melloy"
-date: "30 April 2019"
-output: html_document
----
-
-```{r include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-library(dplyr)
-```
-
-## Studies considered in meta-analysis
+# Studies considered in meta-analysis
 
@@
 
-### 2001 - 2004 trials
-
+**2001 - 2004 trials**  
 Trial data were obtained from a non-published manuscript.  
@@
 
-### 2013 Field trials
+**2013 Field trials**  
 Fungicide treatments were described in reports in Two letter acronyms. The following is the assumed usage.
@@
 ```
-
-## Research questions
-
-What is the length of a Mungbean season and how has it varied in this trial
-
-How has the first sign of powdery mildew changed over the seasons and between experimental sites.
-
-When is the optimum time to spray fungicide to limit the impact of powdery mildew on mungbean yeilds.
-
-When would the ideal planting time be to make use of powdery mildew defoliation in the final growth of the crop.
-
-Do infections that occur before flowering increase the probable yield loss?
-
-## Powdery Mildew analysis 2011 - 2017
-### Summary of data
-
-```{r echo=FALSE, message=FALSE, warning=FALSE}
-library(openxlsx)
-source("Cleaning historical data.R", echo = FALSE, print.eval = FALSE)
-# ___ Datasets available ___
-# data   Herm_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2017, Hermitage and Fogerty
-# data   King_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2016, Hermitage and Kingaroy
-# data   Fogerty_17.1   - Full disease ratings and yeild data from Fogerty field trial in 2017
-# data   Herm_17.1      - Full disease ratings and yeild data from Hermitage field trial in 2017
-# data   PM_MB_17       - Full disease ratings and yeild data from Hermitage and Fogerty in 2017
-# data   PM_MB_16       - End of season powdery mildew rating and Yield data from two field trials in 2016, Hermitage and Kingaroy
-# data   PM_MB_means    - Mean disease rating and yeild data, from trial reports
-PM.dat <- read.xlsx("C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/1902 powdery mildew-Mungbean - Collated means.xlsx",
-                    sheet = "Sheet1", startRow = 1, colNames = TRUE, detectDates = TRUE)
-knitr::kable(
-PM.dat %>%
-   group_by(Trial_ref, Year, Location, trial_design, Replicates, planting_date, emergence_date, first_sign_disease) %>%
-   summarise(Treatments = length(E_treatment))
-)
-PM.dat$Trial_ref <- factor(PM.dat$Trial_ref)
-PM.dat$Location <- factor(PM.dat$Location)
-PM.dat$Year <- factor(PM.dat$Year)
-PM.dat$host_genotype <- factor(PM.dat$host_genotype)
-PM.dat$Fungicide <- factor(PM.dat$Fungicide)
-PM.dat$Trade_name <- factor(PM.dat$Trade_name)
-#glimpse(PM.dat)
-#str(PM.dat)
-first1 <- PM.dat %>%
-   group_by(Trial_ref, Location) %>%
-   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
-   filter(Location == "Kingaroy")
-
-King_first <- subset(first1, Location == "Kingaroy")$First_sign
-```
-
-### Plotting weather data
-
-The mungbean DSS determines the need to spray on:  
-   1. The presence of the disease  
-   2. The forecasted maximum temperatures in the next seven days  
-   3. The number of days over the next seven days with rainfall
-
-Below I am plotting the mean maximum temperures over 7 days during the growing season at each Mungbean trial site.
-The vertical lines indicate when powdery mildew was first observed in that season.
-Variation may exist in the sowing date of each trial.
-
-```{r echo=FALSE, message=FALSE, warning=FALSE}
-# Need weather data between 2011 and 2017
-library(ggplot2)
-# function to extract date from the year
-# format should be Universal time format
-year.day <- function(date){
-   if(is.na(date) == TRUE){ 
-      print(NA)
-      } else {
-as.numeric(as.Date(date) - as.Date(paste0(substr(date, start = 1, stop = 4),"-01-01")))
-      }
-   }
-# Function to generate some of the ggplot grouping colours
-gg_color_hue <- function(n) {
-  hues = seq(15, 375, length = n + 1)
-  hcl(h = hues, l = 65, c = 100)[1:n]
-}
-cols1 <- gg_color_hue(4)
-silo_war_Tmax <- getPPD2(station_id = 041525,start = 20110101,end = 20160630, silo.apikey = silo.API, variables = "max_temp,min_temp,daily_rain")
-# retrieve the maximum temperatures from the six yearsd between 2011 and 2017 at weather station 041525 (Hermitage)
-silo_king_Tmax <- getPPD2(lat = -26.58, long = 151.83, start = 20110101, end = 20160630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
-silo_gatton_Tmax <- getPPD2(lat = -27.56, long = 152.32, start = 20110101, end = 20170630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
-silo_emerald_Tmax <- getPPD2(lat = -23.54, long = 148.19, start = 20110101, end = 20170630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
-experiment_sites <- data.frame(
-   location = c("Hermitage", "Kingaroy research station","Gatton", "Emerald Agricultural College"),
-   lat = c(-28.215 ,-26.58,-27.56,-23.54),
-   lon = c(152.1003,151.83,152.32,148.19)
-)
-# leaflet() %>%
-#    addProviderTiles("Esri.WorldTopoMap") %>%
-#    addMarkers(lng = experiment_sites$lon, lat = experiment_sites$lat)
-# head(silo_gatton_Tmax)
-# ______  Kingaroy_______
-max_T <- vector()
-min_T <- vector()
-for(i in 1:length(silo_king_Tmax[,1])){
-   max_T <- c(max_T,mean(silo_king_Tmax$max_temp[i:(i+7)]))
-   min_T <- c(min_T,mean(silo_king_Tmax$min_temp[i:(i+7)]))
-}
-king_Tm_aver <- data.frame(location = "Kingaroy", date = as.Date(silo_king_Tmax$date), max_T, min_T, daily_rain = silo_king_Tmax$daily_rain)
-# Add columns for Year and date to data
-king_Tm_aver <- king_Tm_aver %>%
-   mutate(Year = substr(king_Tm_aver$date, start = 1, stop = 4),
-          Day = year.day(king_Tm_aver$date)) 
-# Create data subset of Powdery mildew data means for the first sign of the disease by location
-King_FS <- PM.dat %>%
-   group_by(Trial_ref, Location, Year) %>%
-   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
-   filter(Location == "Kingaroy") %>%
-   mutate(Day = year.day(First_sign))
-ggplot(subset(king_Tm_aver, Year == levels(factor(King_FS$Year))),
-              aes(Day))+
-   geom_line(aes(y = max_T, colour = Year))+
-   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
-   geom_line(aes(y = min_T, colour=Year))+
-   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
-   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
-   title = "Maximum and minimum daily temperatures in Kingaroy")+
-   scale_y_continuous(limits = c(0,40))+
-   scale_x_continuous(limits = c(0,200), 
-                      labels = c(subset(king_Tm_aver, Year == 2016)$date[c(1,50,100,150,200)]),
-                      breaks = c(1,50,100,150,200))+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(xintercept = King_FS$Day[1], size =1, colour = cols1[1], linetype = "dotted")+
-   geom_vline(xintercept = King_FS$Day[2], size =1.5, colour = cols1[2], linetype = "dotted")+
-   geom_vline(xintercept = King_FS$Day[3], size =1, colour = cols1[3], linetype = "dashed")+
-   geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
-   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
-   scale_x_continuous(limits = c(1,180),
-                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
-                      labels = c("2012-Jan-01","2012-Feb-01","2012-Mar-01","2012-Apr-01","2012-May-01","2012-Jun-01","2012-Jul-01"))
-# ______  Hermitage  _______
-max_T <- vector()
-min_T <- vector()
-for(i in 1:length(silo_war_Tmax[,1])){
-   max_T <- c(max_T,mean(silo_war_Tmax$max_temp[i:(i+7)]))
-   min_T <- c(min_T,mean(silo_war_Tmax$min_temp[i:(i+7)]))
-}
-war_Tm_aver <- data.frame(location = "Hermitage", date = as.Date(silo_war_Tmax$date), max_T, min_T, daily_rain = silo_war_Tmax$daily_rain)
-# Add columns for Year and date to data
-war_Tm_aver <- war_Tm_aver %>%
-   mutate(Year = substr(war_Tm_aver$date, start = 1, stop = 4),
-          Day = year.day(war_Tm_aver$date)) 
-# Create data subset of Powdery mildew data means for the first sign of the disease by location
-Herm_FS <- PM.dat %>%
-   group_by(Trial_ref, Location, Year) %>%
-   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
-   filter(Location == "Hermitage") %>%
-   mutate(Day = year.day(First_sign))
-ggplot(subset(war_Tm_aver, Year == levels(factor(Herm_FS$Year))),
-              aes(Day))+
-   geom_line(aes(y = max_T, colour = Year))+
-   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
-   geom_line(aes(y = min_T, color = Year))+
-   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
-   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
-   title = "Maximum and minimum daily temperatures in Hermitage")+
-   scale_y_continuous(limits = c(0,40))+
-   scale_x_continuous(limits = c(0,200), 
-                      labels = c(subset(war_Tm_aver, Year == 2016)$date[c(1,50,100,150,200)]),
-                      breaks = c(1,50,100,150,200))+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(xintercept = Herm_FS$Day[1], size =1, colour = cols1[1], linetype = "dotted")+
-   geom_vline(xintercept = Herm_FS$Day[2], size =1.5, colour = cols1[2], linetype = "dotted")+
-   geom_vline(xintercept = Herm_FS$Day[3], size =1, colour = cols1[3], linetype = "dashed")+
-      geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
-   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
-   scale_x_continuous(limits = c(1,180),
-                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
-                      labels = c("Jan-01","Feb-01","Mar-01","Apr-01","May-01","Jun-01","Jul-01"))
-# ______  Gatton  _______
-max_T <- vector()
-min_T <- vector()
-for(i in 1:length(silo_gatton_Tmax[,1])){
-   max_T <- c(max_T,mean(silo_gatton_Tmax$max_temp[i:(i+7)]))
-   min_T <- c(min_T,mean(silo_gatton_Tmax$min_temp[i:(i+7)]))
-}
-# put maximum, minimum temperatures into a dataframe corresponding with thier corresponding date
-Gat_Tm_aver <- data.frame(location = "Gatton", date = as.Date(silo_gatton_Tmax$date), max_T, min_T, daily_rain = silo_gatton_Tmax$daily_rain)
-# Add columns for Year and date to data
-Gat_Tm_aver <- Gat_Tm_aver %>%
-   mutate(Year = substr(Gat_Tm_aver$date, start = 1, stop = 4),
-          Day = year.day(Gat_Tm_aver$date)) 
-# Create data subset of Powdery mildew data means for the first sign of the disease by location
-Gatton_FS <- PM.dat %>%
-   group_by(Trial_ref, Location) %>%
-   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
-   filter(Location == "Gatton") %>%
-   mutate(Year = factor(substr(First_sign,1,4)),
-          Day = year.day(First_sign))
-ggplot(subset(Gat_Tm_aver, Year == levels(Gatton_FS$Year)),
-               aes(Day))+
-   geom_line(aes(y = max_T, colour = Year))+
-   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
-   geom_line(aes(y = min_T, colour = Year))+
-   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
-   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
-   title = "Maximum and minimum daily temperatures in Gatton")+
-   scale_y_continuous(limits = c(0,40))+
-   scale_x_continuous(limits = c(0,200), 
-                      labels = c(subset(Gat_Tm_aver, Year == levels(Gatton_FS$Year))$date[c(1,50,100,150,200)]),
-                      breaks = c(1,50,100,150,200))+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(xintercept = Gatton_FS$Day, colour = "green", size =1)+
-      geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
-   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
-   scale_x_continuous(limits = c(1,180),
-                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
-                      labels = c("2012-Jan-01","2012-Feb-01","2012-Mar-01","2012-Apr-01","2012-May-01","2012-Jun-01","2012-Jul-01"))
-#   scale_x_continuous(limits = as.Date(c("2012-01-01","2012-06-01")))
-
-# line 259
-vec1 <- year.day(Herm_FS$First_sign)
-```
-
-### Yield saved from fungicide applications
-
-The data plotted below are from the past field trials (2011 - 2017) described in the aforementioned table.
-All data are a list of mean values from each treatment applied in each experiment.
-Various factors have been studied in the previous experiments which may influence the following results.
-The following variables were disregarded in the plots below.
-
-   1) Fungicide type
-   2) Fungicide dose
-   3) row spacing
-   4) Host cultivars
-   5) Experiment location
-   6) Final disease rating
-
-```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
-library(lme4)
-# What row spacing leads to the highest yield penalty
-head(PM_MB_17)
-class(PM_MB_17$Incidence_assessment_date)
-class(PM_MB_17$Incidence)
-# `2017-05-11` # last assessment Fogerty
-subset(PM_MB_17, location == "Hermitage")
-ggplot(subset(PM_MB_17, Treatment.No == "T1"||"1"), 
-       aes(y = Incidence, x = Incidence_assessment_date, colour = location))+
-   geom_point()+
-   geom_smooth()+
-   scale_y_continuous(limits = c(-5,15))
-# PM_MB_means <- subset(PM_MB_means, Fungicide != "control")   
-# PM_MB_means$Fungicide <- factor(PM_MB_means$Fungicide, levels = c("Sulphur", "Amistar", "propiconazole", "Tebeconazole"))
-PM_MB_means$Fungicide <- factor(PM_MB_means$Fungicide, levels = c("control", "Sulphur", "Amistar", "propiconazole", "Tebeconazole"))
-yield_lmer1 <- lmer(`yield_gain` ~ factor(total_Fungicide) + Fungicide + factor(Year) + (factor(Year)|Location), 
-                    data = PM_MB_means, na.action = na.omit, REML = F)
-# removed the Year interaction with location
-yield_lmer2 <- lmer(`yield_gain` ~ factor(total_Fungicide) + Fungicide + factor(Year) + (1|Location), 
-                    data = PM_MB_means, na.action = na.omit, REML = F)
-# Removing Fungicide as different fungicides were sprayed a different number of times
-yield_lmer3 <- lmer(`yield_gain` ~ factor(total_Fungicide)  + factor(Year) + (1|Location), 
-                    data = PM_MB_means, na.action = na.omit, REML = F)
-# Removing Fungicide as different fungicides were sprayed a different number of times
-yield_lmer4 <- lmer(`yield_gain` ~ factor(total_Fungicide)  + factor(Year) + (1|Location) + (1|Fungicide), 
-                    data = PM_MB_means, na.action = na.omit, REML = T)
-ranef(yield_lmer4)
-anova(yield_lmer1, yield_lmer2) # P = 0.8943  # removed random intercept 'Year' for each random slope 'Location' # Keep simpler model 
-anova(yield_lmer2, yield_lmer3) # P = 0.8005  # Removed (FE) Fungicide     #     Fungicide showed not to be significant in protecting yield
-anova(yield_lmer3, yield_lmer4) # P = 1       # Added Fungicide as a random effect #     Fungicide showed not to contribute to variation and 
-yield_lmer <- lmer(`yield_gain` ~ factor(total_Fungicide) + factor(Year) + (1|Location), 
-                    data = PM_MB_means, na.action = na.omit)
-summary(yield_lmer)
-ranef(yield_lmer)
-```
-
-#### Yield saved 
-##### Number of fungicide applications
-The following density plots show mean yield saved in relation to how many sprays were applied.
-
-```{r warning=FALSE, echo=FALSE}
-library(ggplot2)
-PM_MB_means <- read.xlsx("C:/Users/U8011054/Documents/GitHub/Mungbean_PM/data/1902 powdery mildew-Mungbean - Collated means.xlsx", detectDates = TRUE)
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PMy <- PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-   group_by(total_Fungicide) %>%
-   summarise(lower = quantile(yield_gain, na.rm = T, c(0.025)),
-             upper = quantile(yield_gain, na.rm = T, c(0.975)))
-# Density plot of Number of fungicide applications and the resulting yeild saved (as a proportion)
-ggplot(subset(PM_MB_means,Fungicide != "control"), aes(yield_gain))+
-   geom_density(aes(group = factor(total_Fungicide), fill = factor(total_Fungicide)), alpha = 0.6)+
-   geom_vline(xintercept = 0, size =1)+
-   labs(x = "Grain yeild saved (t/ha)",
-   title = "Density plot of grain yield saved from differing numbers of fungicide applications")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(data = quant_PMy, aes(xintercept = lower, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   geom_vline(data = quant_PMy, aes(xintercept = upper, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   guides(colour = guide_legend(title="Upper (97.5%) and \nLower (2.5%) percentiles"),
-          fill=guide_legend(title="Number of \nFungicide applications"))+
-   scale_x_continuous(limits = c(-0.3,0.8))
-
-names(quant_PMy) <- c("Number of sprays", "2.5 percentile", "97.5 percentile")
-knitr::kable(quant_PMy)
-#             col.names = c("Number of sprays", "2.5 percentile", "97.5 percentile"))
-#            caption = "The 'upper' and 'lower' percentiles for yeild saved (t/Ha) against the number of Fungicide sprays in a season.
-Data from 2011-2017 mungbean experimental means.
-Data ignores factors such as fungicide, dose, season or location of experiment")
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PM <- PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-   group_by(total_Fungicide) %>%
-   summarise(lower = quantile(prop_YG, na.rm = T, c(0.025)),
-             upper = quantile(prop_YG, na.rm = T, c(0.975)))
-# Density plot of proportion of yield saved
-ggplot(subset(PM_MB_means,Fungicide != "control"), aes(prop_YG))+
-   geom_density(aes(group = factor(total_Fungicide), fill = factor(total_Fungicide)), alpha = 0.6)+
-   geom_vline(xintercept = 0, size =1)+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Density plot of the grain yield proportion saved \n by the number of fungicide applications")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(data = quant_PM, aes(xintercept = lower, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   geom_vline(data = quant_PM, aes(xintercept = upper, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   guides(colour = guide_legend(title="Upper (97.5%) and \nLower (2.5%) percentiles"),
-          fill=guide_legend(title="Number of \nFungicide applications"))+
-   scale_x_continuous(limits = c(-0.3,0.55))
-names(quant_PM) <- c("Number of sprays", "2.5 percentile", "97.5 percentile")
-knitr::kable(quant_PM)   
-#knitr::kable(quant_PM, 
-#             col.names = c("Number of sprays", "2.5 percentile", "97.5 percentile"))
-             #caption = "The 'upper' and 'lower' percentiles for proportion of yeild saved against the number of Fungicide sprays in a season.
-Data from 2011-2017 mungbean experimental means.
-Data ignores factors such as fungicide, dose, season or location of experiment")
-```
-
-\n\n\n\n\n\n\n
-
-#### Timing of Fungicide application
-The following density plots show mean yield saved (t/Ha) or proportion yield saved in relation to when the first fungicide spray was applied in relation to when powdery mildew was first seen in the mungbean crop.
-
-```{r echo = FALSE, message=FALSE, warning=FALSE}
-# removing 2017 and control data
-# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
-PM_MB_means1 <- PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-   filter(Year != 2017) %>%
-#   filter(total_Fungicide ==1) %>%
-   mutate(days_from_1st = as.numeric(as.Date(Fungicide_application_1) - first_sign_disease))
-colnames(PM_MB_means)
-days_from_fungicid <- function(FSD,F1,F2,F3){
-   dF1 <- as.numeric(as.Date(F1) - as.Date(FSD))
-   dF2 <- as.numeric(as.Date(F2) - as.Date(FSD))
-   dF3 <- as.numeric(as.Date(F3) - as.Date(FSD))
-   if(is.na(dF1)){
-      return(NA)} else{
-   if(between(dF1,lower = -1, upper = 1000)){
-      return(dF1)}else{
-   if(is.na(dF2)){
-      return(dF1)}else{
-      if(between(dF2,lower = dF1, upper = -0.1)){
-            return(dF2)} else{
-               return(dF3)}}
-            }}
-}
-vec1<- vector()
-for(i in 1:dim(PM_MB_means1)[1]){
-   dF1 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_1)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
-   dF2 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_2)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
-   dF3 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_3)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
-   if(is.na(dF1)){
-      vec1 <- c(vec1,dF1)} else{
-         if(between(as.numeric(dF1),-1, 1000)){
-            vec1 <- c(vec1,dF1)}else{
-               if(is.na(dF2)){
-                  vec1 <- c(vec1,dF1)}else{
-                     if(between(as.numeric(dF2),as.numeric(dF1), -1.1)){
-            vec1 <- c(vec1,dF2)} else{
-               if(as.numeric(dF3)>=0){
-                  vec1 <- c(vec1,dF2)} else{
-                     vec1 <- c(vec1,dF3)}}}
-            }}
-}
-PM_MB_means1$spray_diff <- vec1 # gives the 
-PM_MB_means1$days_from_1st
-#summary(factor(PM_MB_means1$days_from_1st))
-# Density plot of proportion of yield saved
-ggplot(PM_MB_means1, aes(prop_YG))+
-   geom_density(aes(group = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20)), 
-                    fill = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20))), alpha = 0.3)+
-   geom_vline(xintercept = 0, size =1)+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="First spray window\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.3,0.55))
-###########################################3
-unique(PM_MB_means1$days_from_1st)
-ggplot(PM_MB_means1, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))~., factor(PM_MB_means1$Fungicide))+
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.2,0.55))
-unique(PM_MB_means1$spray_diff)
-ggplot(PM_MB_means1, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means1$spray_diff, c(-29,-20,-15,-12,-0.5,1.5,7,10,12,20))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means1$spray_diff, c(-29,-20,-15,-12,-0.5,1.5,7,10,12,20))~.)+
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.2,0.55))
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PM_prop <- PM_MB_means1 %>%
-   mutate(cut_daysfrom1st = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20))) %>%
-   group_by(cut_daysfrom1st) %>%
-   summarise(lower = quantile(prop_YG, na.rm = T, c(0.025)),
-             upper = quantile(prop_YG, na.rm = T, c(0.975)))
-names(quant_PM_prop) <- c("Days relative to\nfirst incidence", "2.5 percentile", "97.5 percentile")
-cat("Lower (2.5) and Upper (97.5) quantiles for the proportion of yield gained, when the first fungicide applied relative to when powdery mildew is first seen")
-knitr::kable(quant_PM_prop)   
-ggplot(PM_MB_means1, aes(yield_gain))+
-   geom_density(aes(fill = cut(PM_MB_means1$days_from_1st, c(-29,-15,-6,-0.5,0.5,2,10,20))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means1$days_from_1st, c(-29,-15,-6,-0.5,0.5,2,10,20))~.)+
-   scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Grain yield (t/Ha) saved",
-   title = "Grain yield (t/Ha) saved, grouped by when the\nfirst fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.4,1.2))
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PM_prop <- PM_MB_means1 %>%
-   mutate(cut_daysfrom1st = cut(PM_MB_means1$days_from_1st, c(-29,-20,-15,-6,-0.5,0.5,2,10,20))) %>%
-   group_by(cut_daysfrom1st) %>%
-   summarise(lower = quantile(yield_gain, na.rm = T, c(0.025)),
-             upper = quantile(yield_gain, na.rm = T, c(0.975)))
-names(quant_PM_prop) <- c("Days relative to\nfirst incidence", "2.5 percentile", "97.5 percentile")
-print("Yield gain quantiles when the first fungicide applied relative to when powdery mildew is first seen, Lower (2.5) and Upper (97.5) quantiles of yeild ")
-knitr::kable(quant_PM_prop)  
-```
-
-```{r}
-PM_MB_means2 <- PM_MB_means1 %>%
-   filter(Fungicide == "Tebeconazole")
-unique(PM_MB_means2$spray_diff)
-ggplot(PM_MB_means2, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-1,2,7,10,12,20))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means2$spray_diff, c(1,2,7,10,12,20))~.)+
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.2,0.55))
-#__________________________________________________________________________________________________________
-levels(factor(PM_MB_means$Fungicide))
-PM_MB_means2 <- PM_MB_means1 %>%
-   filter(Fungicide == "Sulphur" |
-             Fungicide == "Sulphur (SC)" |
-             Fungicide == "Sulphur (Ultra SC)" |
-             Fungicide == "Sulphur (WP)")
-unique(PM_MB_means2$spray_diff)
-ggplot(PM_MB_means2, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))~.)+
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.3,0.6))
-Chemical <- c("Amistar","Carbendazim","Tebeconazole", "propiconazole")
-levels(factor(PM_MB_means$Fungicide))
-for(Chem in Chemical){
-PM_MB_means2 <- PM_MB_means1 %>%
-   filter(Fungicide == Chem)
-cat(Chem)
-cat(unique(PM_MB_means2$spray_diff))
-p1 <- ggplot(PM_MB_means2, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))~.)+
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title=paste(Chem,"Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease")))+
-   scale_x_continuous(limits = c(-0.3,0.6))
-print(p1)
-Sys.sleep(10)
-}
-```

### 2019-06-19 index.Rmd
Served _book Updated ReadMe breaking up 1905_Mungbean_PM_preliminary_analysis into seperate files. Created index.Rmd Created 1_Meta-analysis_experiments

@@
 ---
+
+# Research questions
+
+What is the length of a Mungbean season and how has it varied in this trial
+
+How has the first sign of powdery mildew changed over the seasons and between experimental sites.
+
+When is the optimum time to spray fungicide to limit the impact of powdery mildew on mungbean yeilds.
+
+When would the ideal planting time be to make use of powdery mildew defoliation in the final growth of the crop.
+
+Do infections that occur before flowering increase the probable yield loss?

### 2019-06-19 02_Preliminary_analysis.Rmd
Rename preliminary analysis into Book

--- 2019-06-18 1905 Mungbean_PM_preliminary_analysis.Rmd
@@
 ```
-
-## Studies considered in meta-analysis
-
-* 2001  
-   + Bongeen #1  
-   + Bongeen #2
-
-* 2002
-   + Hermitage #1  
-   + Hermitage #2  
-   + Kingaroy
-
-* 2004
-   + Redvale
-
-* 2010  
-   + Hermitage  
-   + Kingaroy
-
-* 2011  
-   + Hermitage  
-   + Kingaroy
-
-* 2012  
-   + Gatton  
-   + Kingaroy
-
-* 2013
-   + Premer; no raw data
-   + Milmerran; no raw data
-   + Mt Mary; no raw data
-   + Goolhi; no raw data
-
-* 2015  
-   + Hermitage  
-   + Dalby - Site abandoned due it insuficient/late disease infection  
-   + Emerald
-
-* 2016  
-   + Hermitage  
-   + Kingaroy  
-   + Emerald
-
-* 2017  
-   + Fogerty  
-   + Hermitage
-
-* 2018
-   + Wellcamp
-
-* 2019
-   + Hermitage
-
-### 2001 - 2004 trials
-
-Trial data were obtained from a non-published manuscript.
-Ratings for powdery Mildew were on a 1-5 rating scale and can be read in the file "Powdery mildew paper#1.doc".  
-Comparing Trials which have not used the same rating scale wil be done using a percentage change.
-
-### 2013 Field trials
-Fungicide treatments were described in reports in Two letter acronyms. The following is the assumed usage.
-
-```{r}
-knitr::kable(
-   cbind(Acronym = c("SF", "Ti", "AX", "Ca"),
-         Expected_Fungicide = c("Sulphur", "Tilt", "Amistar Xtra", "Carbendazim"),
-         Active_Ingredient = c("Sulphur", "Propiconazole", "Amistar", "Carbendazim")
-   )
-)
-```
-
-## Research questions
-
-What is the length of a Mungbean season and how has it varied in this trial
-
-How has the first sign of powdery mildew changed over the seasons and between experimental sites.
-
-When is the optimum time to spray fungicide to limit the impact of powdery mildew on mungbean yeilds.
-
-When would the ideal planting time be to make use of powdery mildew defoliation in the final growth of the crop.
-
-Do infections that occur before flowering increase the probable yield loss?
 

### 2019-06-19 02_Preliminary_analysis.Rmd
Cleaning up 02_Preliminary data Chunck data_summary

@@
----
-title: "PM Mungbean meta-analysis"
-author: "P. Melloy"
-date: "30 April 2019"
-output: html_document
----
+# Preliminary Analysis
 
-```{r include=FALSE}
+```{r PA_Libraries, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
 library(dplyr)
+library(openxlsx)
+library(kableExtra)
+library(ggplot2)
+
 ```
 
-## Powdery Mildew analysis 2011 - 2017
-### Summary of data
+## Summary of data
 
-```{r echo=FALSE, message=FALSE, warning=FALSE}
-library(openxlsx)
+```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}
+
 source("Cleaning historical data.R", echo = FALSE, print.eval = FALSE)
@@
 # data   PM_MB_means    - Mean disease rating and yeild data, from trial reports
-PM.dat <- read.xlsx("C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/1902 powdery mildew-Mungbean - Collated means.xlsx",
-                    sheet = "Sheet1", startRow = 1, colNames = TRUE, detectDates = TRUE)
-knitr::kable(
-PM.dat %>%
+
+PM.dat <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
+
+glimpse(PM.dat)
+
+kable(PM.dat %>%
    group_by(Trial_ref, Year, Location, trial_design, Replicates, planting_date, emergence_date, first_sign_disease) %>%
-   summarise(Treatments = length(E_treatment))
-)
+   summarise(Treatments = length(E_treatment)),
+   caption = "Description of Experiments") %>%
+   kable_styling(fixed_thead = T, full_width = T) %>%
+   scroll_box(width = "900px", height = "500px")
+
 PM.dat$Trial_ref <- factor(PM.dat$Trial_ref)
@@
 PM.dat$Trade_name <- factor(PM.dat$Trade_name)
-#glimpse(PM.dat)
-#str(PM.dat)
-first1 <- PM.dat %>%
-   group_by(Trial_ref, Location) %>%
-   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
-   filter(Location == "Kingaroy")
 
-King_first <- subset(first1, Location == "Kingaroy")$First_sign
 ```
 
-### Plotting weather data
+## Weather data
 
@@
 # Need weather data between 2011 and 2017
-library(ggplot2)
+
 # function to extract date from the year

### 2019-06-19 Cleaning historical data.R

@@ -1,0 +1,534 @@
+# This script is dedicated to 
+# importing and cleaning previous powdery Mildew experimental field trial data.
+
+# install.packages("openxlsx")
+# install.packages("readxl")
+# install.packages("tidyr")
+
+library(openxlsx)
+library(readxl)
+library(tidyr)
+library(dplyr)
+library(data.table)
+
+# Year #  Trial location  #  Sowing date
+
+
+# ____________________________________________________________
+# _____________            Hermitage  2010        ____________
+
+Herm_10 <- read_xls("C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/Past Trials/2010/2010 PMmung Herm/2010 PMmung hermitage RAW field book.xls", 
+                        sheet = "For analysis")
+
+Herm_10_m <- Herm_10 %>%
+   group_by(`Cultivar!`, `Treat!`, `Description!`) %>%
+   summarise_all(list(~mean(.,na.rm = TRUE),~sd(.,na.rm=TRUE)))
+   
+write.csv(as.data.frame(Herm_10_m ), "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/2010 PMmung Hermitage means.csv")
+
+
+# ____________________________________________________________
+# _____________            Hermitage  2011        ____________
+
+Herm_11 <- read_xls("C:/Users/U8011054/OneDrive - USQ//Cloudstor/Mungbean/Past trials/2011/2011 PMmung Herm/pmhermratings2011.xls", 
+                    sheet = "Analyses factor")
+
+
+new_cols <- as.data.table(tstrsplit(Herm_11$'Treatment!'," "))
+colnames(new_cols) <- c("spray_n", "spray", "fungicide")
+Herm_11 <- cbind(new_cols, as.data.table(Herm_11)[, 'Treatment!' := NULL])
+#Herm_11$`Yld Kg ha` <- as.numeric(Herm_11$`Yld Kg ha`)
+head(Herm_11)
+
+Herm_11_m <- Herm_11 %>%
+   group_by(`Cultivar!`, `Tr`, `fungicide`, `spray_n`) %>%
+   summarise_all(list(~mean(.,na.rm = TRUE),~sd(.,na.rm=TRUE)))
+
+Herm_11_m <- data.table(Herm_11_m)[,c(1:4,8:12,16:20)]
+colnames(Herm_11_m)
+
[…]

### 2019-06-19 02_Preliminary_analysis.Rmd
Replaced non-functioning get_ppd() function with csv weather data files of some experimental locations

@@
 
-```{r PA_Libraries, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+```{r PA_Libraries}
 library(dplyr)
@@
 library(ggplot2)
+library(devtools)
+#source("./getPPD2.R")
 
@@
 
-```{r echo=FALSE, message=FALSE, warning=FALSE}
+```{r weather1, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
+# This chunk has been removed as the get_PPD2 function has stopped working and needs fixing
+# Update: I have included data files instead of seeking the data from the web. 
+# issue has something to do with website certificates not being appropriete.
+
 # Need weather data between 2011 and 2017
@@
    if(is.na(date) == TRUE){ 
-      print(NA)
+      return(NA)
       } else {
-as.numeric(as.Date(date) - as.Date(paste0(substr(date, start = 1, stop = 4),"-01-01")))
+return(as.numeric(as.Date(date) - as.Date(paste0(substr(date, start = 1, stop = 4),"-01-01"))))
       }
 }
+
 # Function to generate some of the ggplot grouping colours
@@
 cols1 <- gg_color_hue(4)
-silo_war_Tmax <- getPPD2(station_id = 041525,start = 20110101,end = 20160630, silo.apikey = silo.API, variables = "max_temp,min_temp,daily_rain")
-# retrieve the maximum temperatures from the six yearsd between 2011 and 2017 at weather station 041525 (Hermitage)
-silo_king_Tmax <- getPPD2(lat = -26.58, long = 151.83, start = 20110101, end = 20160630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
-silo_gatton_Tmax <- getPPD2(lat = -27.56, long = 152.32, start = 20110101, end = 20170630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
-silo_emerald_Tmax <- getPPD2(lat = -23.54, long = 148.19, start = 20110101, end = 20170630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
+
+# silo.API <- "YeTZsWlFNC8hvbQLllv8KtbRQWsje4qxic5QQ7mL"
+# # retrieve the maximum temperatures from the six yearsd between 2011 and 2017 at weather station 041525 (Hermitage)
+# silo_war_Tmax <- getPPD2(station_id = 041525,start = 20110101,end = 20160630, silo.apikey = silo.API, variables = "max_temp,min_temp,daily_rain")
+# # retrieve the maximum temperatures from the six yearsd between 2011 and 2017 by location
+# silo_king_Tmax <- getPPD2(lat = -26.58, long = 151.83, start = 20110101, end = 20160630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
+# silo_gatton_Tmax <- getPPD2(lat = -27.56, long = 152.32, start = 20110101, end = 20170630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
+# silo_emerald_Tmax <- getPPD2(lat = -23.54, long = 148.19, start = 20110101, end = 20170630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
+
+silo_war_Tmax <- read.csv("./data/silo_war_Tmax.csv")
+silo_king_Tmax <- read.csv("./data/silo_king_Tmax.csv")
+silo_gatton_Tmax <- read.csv("./data/silo_gatton_Tmax.csv")
+silo_emerald_Tmax <- read.csv("./data/silo_emerald_Tmax.csv")
+
 experiment_sites <- data.frame(
@@
 )
-# leaflet() %>%
-#    addProviderTiles("Esri.WorldTopoMap") %>%
-#    addMarkers(lng = experiment_sites$lon, lat = experiment_sites$lat)
+
+ leaflet() %>%
+    addProviderTiles("Esri.WorldTopoMap") %>%
+    addMarkers(lng = experiment_sites$lon, lat = experiment_sites$lat)
 # head(silo_gatton_Tmax)
 # ______  Kingaroy_______
+
+```
+
+### Kingaroy historical weather
+```{r Kingaroy_weather, include=FALSE}
+
+# Smoothing temperatures by taking a rolling7 day average
 max_T <- vector()
@@
 }
+
 king_Tm_aver <- data.frame(location = "Kingaroy", date = as.Date(silo_king_Tmax$date), max_T, min_T, daily_rain = silo_king_Tmax$daily_rain)
+
 # Add columns for Year and date to data
@@
           Day = year.day(king_Tm_aver$date))
+
 # Create data subset of Powdery mildew data means for the first sign of the disease by location
@@
    group_by(Trial_ref, Location, Year) %>%
-   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
+   summarise(First_sign = mean(as.Date(first_sign_disease), na.rm = T)) %>%
    filter(Location == "Kingaroy") %>%
    mutate(Day = year.day(First_sign))
+str(king_Tm_aver)
+str(King_FS)
 ggplot(subset(king_Tm_aver, Year == levels(factor(King_FS$Year))),
@@
    #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
-   geom_line(aes(y = min_T, colour=Year))+
+   geom_line(aes(y = min_T, colour = Year))+
    #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
@@
    geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
-   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
-   scale_x_continuous(limits = c(1,180),
-                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
-                      labels = c("2012-Jan-01","2012-Feb-01","2012-Mar-01","2012-Apr-01","2012-May-01","2012-Jun-01","2012-Jul-01"))
+   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))
+#   scale_x_continuous(limits = c(1,180),
+#                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
+#                      labels = c("2012-Jan-01","2012-Feb-01","2012-Mar-01","2012-Apr-01","2012-May-01","2012-Jun-01","2012-Jul-01"))
+
+```
+
+### Hermitage historical weather
+```{r Hermitage_weather, include=FALSE}
+
 # ______  Hermitage  _______
@@
 }
+
 war_Tm_aver <- data.frame(location = "Hermitage", date = as.Date(silo_war_Tmax$date), max_T, min_T, daily_rain = silo_war_Tmax$daily_rain)
+
 # Add columns for Year and date to data
@@
           Day = year.day(war_Tm_aver$date))
+
 # Create data subset of Powdery mildew data means for the first sign of the disease by location
@@
    group_by(Trial_ref, Location, Year) %>%
-   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
+   summarise(First_sign = mean(as.Date(first_sign_disease), na.rm = T)) %>%
    filter(Location == "Hermitage") %>%
    mutate(Day = year.day(First_sign))
+
 ggplot(subset(war_Tm_aver, Year == levels(factor(Herm_FS$Year))),
@@
                       labels = c("Jan-01","Feb-01","Mar-01","Apr-01","May-01","Jun-01","Jul-01"))
+
+```
+
+### Gatton historical weather
+```{r Gatton_weather, include=FALSE}
+
 # ______  Gatton  _______
@@
 library(lme4)
-# What row spacing leads to the highest yield penalty
-head(PM_MB_17)
-class(PM_MB_17$Incidence_assessment_date)
-class(PM_MB_17$Incidence)
+
+# Which row spacing leads to the highest yield penalty
+
 # `2017-05-11` # last assessment Fogerty
@@
 library(ggplot2)
-PM_MB_means <- read.xlsx("C:/Users/U8011054/Documents/GitHub/Mungbean_PM/data/1902 powdery mildew-Mungbean - Collated means.xlsx", detectDates = TRUE)
+PM_MB_means <- read.csv("./data/1902 powdery mildew-Mungbean - Collated means.csv")
+
 # Making a table of showing the upper and lower percentiles (95%)

### 2019-06-20 01_Meta-analysis_experiments.Rmd
Moved code chunck to experiment description chapter

@@
 ```
+
+## Experimental locations
+```{r Experiment_locations}
+
+experiment_sites <- data.frame(
+   location = c("Hermitage", "Kingaroy research station","Gatton", "Emerald Agricultural College"),
+   lat = c(-28.215 ,-26.58,-27.56,-23.54),
+   lon = c(152.1003,151.83,152.32,148.19)
+)
+
+ leaflet() %>%
+    addProviderTiles("Esri.WorldTopoMap") %>%
+    addMarkers(lng = experiment_sites$lon, lat = experiment_sites$lat)
+# head(silo_gatton_Tmax)
+
+```

### 2019-06-20 02_Weather.Rmd
Moving weather data to it's own chapter

--- 2019-06-19 02_Preliminary_analysis.Rmd
@@
-# Preliminary Analysis
-
-```{r PA_Libraries}
-library(dplyr)
-library(openxlsx)
-library(kableExtra)
-library(ggplot2)
-library(devtools)
-#source("./getPPD2.R")
-
-```
-
-## Summary of data
-
-```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}
-
-source("Cleaning historical data.R", echo = FALSE, print.eval = FALSE)
-# ___ Datasets available ___
-# data   Herm_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2017, Hermitage and Fogerty
-# data   King_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2016, Hermitage and Kingaroy
-# data   Fogerty_17.1   - Full disease ratings and yeild data from Fogerty field trial in 2017
-# data   Herm_17.1      - Full disease ratings and yeild data from Hermitage field trial in 2017
-# data   PM_MB_17       - Full disease ratings and yeild data from Hermitage and Fogerty in 2017
-# data   PM_MB_16       - End of season powdery mildew rating and Yield data from two field trials in 2016, Hermitage and Kingaroy
-# data   PM_MB_means    - Mean disease rating and yeild data, from trial reports
-
-PM.dat <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
-
-glimpse(PM.dat)
-
-kable(PM.dat %>%
-   group_by(Trial_ref, Year, Location, trial_design, Replicates, planting_date, emergence_date, first_sign_disease) %>%
-   summarise(Treatments = length(E_treatment)),
-   caption = "Description of Experiments") %>%
-   kable_styling(fixed_thead = T, full_width = T) %>%
-   scroll_box(width = "900px", height = "500px")
-
-PM.dat$Trial_ref <- factor(PM.dat$Trial_ref)
-PM.dat$Location <- factor(PM.dat$Location)
-PM.dat$Year <- factor(PM.dat$Year)
-PM.dat$host_genotype <- factor(PM.dat$host_genotype)
-PM.dat$Fungicide <- factor(PM.dat$Fungicide)
-PM.dat$Trade_name <- factor(PM.dat$Trade_name)
-
-```
-
-## Weather data
+# Weather data
 
@@
 silo_emerald_Tmax <- read.csv("./data/silo_emerald_Tmax.csv")
-
-experiment_sites <- data.frame(
-   location = c("Hermitage", "Kingaroy research station","Gatton", "Emerald Agricultural College"),
-   lat = c(-28.215 ,-26.58,-27.56,-23.54),
-   lon = c(152.1003,151.83,152.32,148.19)
-)
-
- leaflet() %>%
-    addProviderTiles("Esri.WorldTopoMap") %>%
-    addMarkers(lng = experiment_sites$lon, lat = experiment_sites$lat)
-# head(silo_gatton_Tmax)
-# ______  Kingaroy_______
 
@@
    title = "Maximum and minimum daily temperatures in Hermitage")+
-   scale_y_continuous(limits = c(0,40))+
+   scale_y_continuous(limits = c(0,45))+
    scale_x_continuous(limits = c(0,200), 
@@
 }
+
 # put maximum, minimum temperatures into a dataframe corresponding with thier corresponding date
 Gat_Tm_aver <- data.frame(location = "Gatton", date = as.Date(silo_gatton_Tmax$date), max_T, min_T, daily_rain = silo_gatton_Tmax$daily_rain)
+
 # Add columns for Year and date to data
@@
           Day = year.day(Gat_Tm_aver$date))
+
 # Create data subset of Powdery mildew data means for the first sign of the disease by location
@@
    group_by(Trial_ref, Location) %>%
-   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
+   summarise(First_sign = mean(as.Date(first_sign_disease), na.rm = T)) %>%
    filter(Location == "Gatton") %>%
@@
           Day = year.day(First_sign))
-ggplot(subset(Gat_Tm_aver, Year == levels(Gatton_FS$Year)),
+
+ggplot(subset(Gat_Tm_aver, Year == 2012),
                aes(Day))+
@@
 
-# line 259
-vec1 <- year.day(Herm_FS$First_sign)
 ```
-
-### Yield saved from fungicide applications
-
-The data plotted below are from the past field trials (2011 - 2017) described in the aforementioned table.
-All data are a list of mean values from each treatment applied in each experiment.
-Various factors have been studied in the previous experiments which may influence the following results.
-The following variables were disregarded in the plots below.
-
-   1) Fungicide type
-   2) Fungicide dose
-   3) row spacing
-   4) Host cultivars
-   5) Experiment location
-   6) Final disease rating
-
-```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
-library(lme4)
-
-# Which row spacing leads to the highest yield penalty
-
-# `2017-05-11` # last assessment Fogerty
-subset(PM_MB_17, location == "Hermitage")
-ggplot(subset(PM_MB_17, Treatment.No == "T1"||"1"), 
-       aes(y = Incidence, x = Incidence_assessment_date, colour = location))+
-   geom_point()+
-   geom_smooth()+
-   scale_y_continuous(limits = c(-5,15))
-# PM_MB_means <- subset(PM_MB_means, Fungicide != "control")   
-# PM_MB_means$Fungicide <- factor(PM_MB_means$Fungicide, levels = c("Sulphur", "Amistar", "propiconazole", "Tebeconazole"))
-PM_MB_means$Fungicide <- factor(PM_MB_means$Fungicide, levels = c("control", "Sulphur", "Amistar", "propiconazole", "Tebeconazole"))
-yield_lmer1 <- lmer(`yield_gain` ~ factor(total_Fungicide) + Fungicide + factor(Year) + (factor(Year)|Location), 
-                    data = PM_MB_means, na.action = na.omit, REML = F)
-# removed the Year interaction with location
-yield_lmer2 <- lmer(`yield_gain` ~ factor(total_Fungicide) + Fungicide + factor(Year) + (1|Location), 
-                    data = PM_MB_means, na.action = na.omit, REML = F)
-# Removing Fungicide as different fungicides were sprayed a different number of times
-yield_lmer3 <- lmer(`yield_gain` ~ factor(total_Fungicide)  + factor(Year) + (1|Location), 
-                    data = PM_MB_means, na.action = na.omit, REML = F)
-# Removing Fungicide as different fungicides were sprayed a different number of times
-yield_lmer4 <- lmer(`yield_gain` ~ factor(total_Fungicide)  + factor(Year) + (1|Location) + (1|Fungicide), 
-                    data = PM_MB_means, na.action = na.omit, REML = T)
-ranef(yield_lmer4)
-anova(yield_lmer1, yield_lmer2) # P = 0.8943  # removed random intercept 'Year' for each random slope 'Location' # Keep simpler model 
-anova(yield_lmer2, yield_lmer3) # P = 0.8005  # Removed (FE) Fungicide     #     Fungicide showed not to be significant in protecting yield
-anova(yield_lmer3, yield_lmer4) # P = 1       # Added Fungicide as a random effect #     Fungicide showed not to contribute to variation and 
-yield_lmer <- lmer(`yield_gain` ~ factor(total_Fungicide) + factor(Year) + (1|Location), 
-                    data = PM_MB_means, na.action = na.omit)
-summary(yield_lmer)
-ranef(yield_lmer)
-```
-
-#### Yield saved 
-##### Number of fungicide applications
-The following density plots show mean yield saved in relation to how many sprays were applied.
-
-```{r warning=FALSE, echo=FALSE}
-library(ggplot2)
-PM_MB_means <- read.csv("./data/1902 powdery mildew-Mungbean - Collated means.csv")
-
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PMy <- PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-   group_by(total_Fungicide) %>%
-   summarise(lower = quantile(yield_gain, na.rm = T, c(0.025)),
-             upper = quantile(yield_gain, na.rm = T, c(0.975)))
-# Density plot of Number of fungicide applications and the resulting yeild saved (as a proportion)
-ggplot(subset(PM_MB_means,Fungicide != "control"), aes(yield_gain))+
-   geom_density(aes(group = factor(total_Fungicide), fill = factor(total_Fungicide)), alpha = 0.6)+
-   geom_vline(xintercept = 0, size =1)+
-   labs(x = "Grain yeild saved (t/ha)",
-   title = "Density plot of grain yield saved from differing numbers of fungicide applications")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(data = quant_PMy, aes(xintercept = lower, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   geom_vline(data = quant_PMy, aes(xintercept = upper, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   guides(colour = guide_legend(title="Upper (97.5%) and \nLower (2.5%) percentiles"),
-          fill=guide_legend(title="Number of \nFungicide applications"))+
-   scale_x_continuous(limits = c(-0.3,0.8))
-
-names(quant_PMy) <- c("Number of sprays", "2.5 percentile", "97.5 percentile")
-knitr::kable(quant_PMy)
-#             col.names = c("Number of sprays", "2.5 percentile", "97.5 percentile"))
-#            caption = "The 'upper' and 'lower' percentiles for yeild saved (t/Ha) against the number of Fungicide sprays in a season.
-Data from 2011-2017 mungbean experimental means.
-Data ignores factors such as fungicide, dose, season or location of experiment")
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PM <- PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-   group_by(total_Fungicide) %>%
-   summarise(lower = quantile(prop_YG, na.rm = T, c(0.025)),
-             upper = quantile(prop_YG, na.rm = T, c(0.975)))
-# Density plot of proportion of yield saved
-ggplot(subset(PM_MB_means,Fungicide != "control"), aes(prop_YG))+
-   geom_density(aes(group = factor(total_Fungicide), fill = factor(total_Fungicide)), alpha = 0.6)+
-   geom_vline(xintercept = 0, size =1)+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Density plot of the grain yield proportion saved \n by the number of fungicide applications")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(data = quant_PM, aes(xintercept = lower, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   geom_vline(data = quant_PM, aes(xintercept = upper, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   guides(colour = guide_legend(title="Upper (97.5%) and \nLower (2.5%) percentiles"),
-          fill=guide_legend(title="Number of \nFungicide applications"))+
-   scale_x_continuous(limits = c(-0.3,0.55))
-names(quant_PM) <- c("Number of sprays", "2.5 percentile", "97.5 percentile")
-knitr::kable(quant_PM)   
-#knitr::kable(quant_PM, 
-#             col.names = c("Number of sprays", "2.5 percentile", "97.5 percentile"))
-             #caption = "The 'upper' and 'lower' percentiles for proportion of yeild saved against the number of Fungicide sprays in a season.
-Data from 2011-2017 mungbean experimental means.
-Data ignores factors such as fungicide, dose, season or location of experiment")
-```
-
-\n\n\n\n\n\n\n
-
-#### Timing of Fungicide application
-The following density plots show mean yield saved (t/Ha) or proportion yield saved in relation to when the first fungicide spray was applied in relation to when powdery mildew was first seen in the mungbean crop.
-
-```{r echo = FALSE, message=FALSE, warning=FALSE}
-# removing 2017 and control data
-# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
-PM_MB_means1 <- PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-   filter(Year != 2017) %>%
-#   filter(total_Fungicide ==1) %>%
-   mutate(days_from_1st = as.numeric(as.Date(Fungicide_application_1) - first_sign_disease))
-colnames(PM_MB_means)
-days_from_fungicid <- function(FSD,F1,F2,F3){
-   dF1 <- as.numeric(as.Date(F1) - as.Date(FSD))
-   dF2 <- as.numeric(as.Date(F2) - as.Date(FSD))
-   dF3 <- as.numeric(as.Date(F3) - as.Date(FSD))
-   if(is.na(dF1)){
-      return(NA)} else{
-   if(between(dF1,lower = -1, upper = 1000)){
-      return(dF1)}else{
-   if(is.na(dF2)){
-      return(dF1)}else{
-      if(between(dF2,lower = dF1, upper = -0.1)){
-            return(dF2)} else{
-               return(dF3)}}
-            }}
-}
-vec1<- vector()
-for(i in 1:dim(PM_MB_means1)[1]){
-   dF1 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_1)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
-   dF2 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_2)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
-   dF3 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_3)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
-   if(is.na(dF1)){
-      vec1 <- c(vec1,dF1)} else{
-         if(between(as.numeric(dF1),-1, 1000)){
-            vec1 <- c(vec1,dF1)}else{
-               if(is.na(dF2)){
-                  vec1 <- c(vec1,dF1)}else{
-                     if(between(as.numeric(dF2),as.numeric(dF1), -1.1)){
-            vec1 <- c(vec1,dF2)} else{
-               if(as.numeric(dF3)>=0){
-                  vec1 <- c(vec1,dF2)} else{
-                     vec1 <- c(vec1,dF3)}}}
-            }}
-}
-PM_MB_means1$spray_diff <- vec1 # gives the 
-PM_MB_means1$days_from_1st
-#summary(factor(PM_MB_means1$days_from_1st))
-# Density plot of proportion of yield saved
-ggplot(PM_MB_means1, aes(prop_YG))+
-   geom_density(aes(group = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20)), 
-                    fill = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20))), alpha = 0.3)+
-   geom_vline(xintercept = 0, size =1)+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="First spray window\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.3,0.55))
-###########################################3
-unique(PM_MB_means1$days_from_1st)
-ggplot(PM_MB_means1, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))~., factor(PM_MB_means1$Fungicide))+
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.2,0.55))
-unique(PM_MB_means1$spray_diff)
-ggplot(PM_MB_means1, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means1$spray_diff, c(-29,-20,-15,-12,-0.5,1.5,7,10,12,20))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means1$spray_diff, c(-29,-20,-15,-12,-0.5,1.5,7,10,12,20))~.)+
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.2,0.55))
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PM_prop <- PM_MB_means1 %>%
-   mutate(cut_daysfrom1st = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20))) %>%
-   group_by(cut_daysfrom1st) %>%
-   summarise(lower = quantile(prop_YG, na.rm = T, c(0.025)),
-             upper = quantile(prop_YG, na.rm = T, c(0.975)))
-names(quant_PM_prop) <- c("Days relative to\nfirst incidence", "2.5 percentile", "97.5 percentile")
-cat("Lower (2.5) and Upper (97.5) quantiles for the proportion of yield gained, when the first fungicide applied relative to when powdery mildew is first seen")
-knitr::kable(quant_PM_prop)   
-ggplot(PM_MB_means1, aes(yield_gain))+
-   geom_density(aes(fill = cut(PM_MB_means1$days_from_1st, c(-29,-15,-6,-0.5,0.5,2,10,20))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means1$days_from_1st, c(-29,-15,-6,-0.5,0.5,2,10,20))~.)+
-   scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Grain yield (t/Ha) saved",
-   title = "Grain yield (t/Ha) saved, grouped by when the\nfirst fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.4,1.2))
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PM_prop <- PM_MB_means1 %>%
-   mutate(cut_daysfrom1st = cut(PM_MB_means1$days_from_1st, c(-29,-20,-15,-6,-0.5,0.5,2,10,20))) %>%
-   group_by(cut_daysfrom1st) %>%
-   summarise(lower = quantile(yield_gain, na.rm = T, c(0.025)),
-             upper = quantile(yield_gain, na.rm = T, c(0.975)))
-names(quant_PM_prop) <- c("Days relative to\nfirst incidence", "2.5 percentile", "97.5 percentile")
-print("Yield gain quantiles when the first fungicide applied relative to when powdery mildew is first seen, Lower (2.5) and Upper (97.5) quantiles of yeild ")
-knitr::kable(quant_PM_prop)  
-```
-
-```{r}
-PM_MB_means2 <- PM_MB_means1 %>%
-   filter(Fungicide == "Tebeconazole")
-unique(PM_MB_means2$spray_diff)
-ggplot(PM_MB_means2, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-1,2,7,10,12,20))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means2$spray_diff, c(1,2,7,10,12,20))~.)+
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.2,0.55))
-#__________________________________________________________________________________________________________
-levels(factor(PM_MB_means$Fungicide))
-PM_MB_means2 <- PM_MB_means1 %>%
-   filter(Fungicide == "Sulphur" |
-             Fungicide == "Sulphur (SC)" |
-             Fungicide == "Sulphur (Ultra SC)" |
-             Fungicide == "Sulphur (WP)")
-unique(PM_MB_means2$spray_diff)
-ggplot(PM_MB_means2, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))~.)+
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.3,0.6))
-Chemical <- c("Amistar","Carbendazim","Tebeconazole", "propiconazole")
-levels(factor(PM_MB_means$Fungicide))
-for(Chem in Chemical){
-PM_MB_means2 <- PM_MB_means1 %>%
-   filter(Fungicide == Chem)
-cat(Chem)
-cat(unique(PM_MB_means2$spray_diff))
-p1 <- ggplot(PM_MB_means2, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))~.)+
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title=paste(Chem,"Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease")))+
-   scale_x_continuous(limits = c(-0.3,0.6))
-print(p1)
-Sys.sleep(10)
-}
-```

### 2019-06-20 01_Meta-analysis_experiments.Rmd
Trial table moved to 01_summary data

@@
 
+## Summary of data
+
+```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}
+
+source("Cleaning historical data.R", echo = FALSE, print.eval = FALSE)
+# ___ Datasets available ___
+# data   Herm_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2017, Hermitage and Fogerty
+# data   King_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2016, Hermitage and Kingaroy
+# data   Fogerty_17.1   - Full disease ratings and yeild data from Fogerty field trial in 2017
+# data   Herm_17.1      - Full disease ratings and yeild data from Hermitage field trial in 2017
+# data   PM_MB_17       - Full disease ratings and yeild data from Hermitage and Fogerty in 2017
+# data   PM_MB_16       - End of season powdery mildew rating and Yield data from two field trials in 2016, Hermitage and Kingaroy
+# data   PM_MB_means    - Mean disease rating and yeild data, from trial reports
+
+PM.dat <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
+
+glimpse(PM.dat)
+
+kable(PM.dat %>%
+   group_by(Trial_ref, Year, Location, trial_design, Replicates, planting_date, emergence_date, first_sign_disease) %>%
+   summarise(Treatments = length(E_treatment)),
+   caption = "Description of Experiments") %>%
+   kable_styling(fixed_thead = T, full_width = T) %>%
+   scroll_box(width = "900px", height = "500px")
+
+PM.dat$Trial_ref <- factor(PM.dat$Trial_ref)
+PM.dat$Location <- factor(PM.dat$Location)
+PM.dat$Year <- factor(PM.dat$Year)
+PM.dat$host_genotype <- factor(PM.dat$host_genotype)
+PM.dat$Fungicide <- factor(PM.dat$Fungicide)
+PM.dat$Trade_name <- factor(PM.dat$Trade_name)
+
+```
+
 ## Experimental locations

### 2019-06-20 03_Preliminary_analysis.Rmd
rename chapter order

--- 2019-06-19 02_Preliminary_analysis.Rmd
@@
 
-```
-
-## Summary of data
-
-```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}
-
-source("Cleaning historical data.R", echo = FALSE, print.eval = FALSE)
-# ___ Datasets available ___
-# data   Herm_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2017, Hermitage and Fogerty
-# data   King_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2016, Hermitage and Kingaroy
-# data   Fogerty_17.1   - Full disease ratings and yeild data from Fogerty field trial in 2017
-# data   Herm_17.1      - Full disease ratings and yeild data from Hermitage field trial in 2017
-# data   PM_MB_17       - Full disease ratings and yeild data from Hermitage and Fogerty in 2017
-# data   PM_MB_16       - End of season powdery mildew rating and Yield data from two field trials in 2016, Hermitage and Kingaroy
-# data   PM_MB_means    - Mean disease rating and yeild data, from trial reports
-
-PM.dat <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
-
-glimpse(PM.dat)
-
-kable(PM.dat %>%
-   group_by(Trial_ref, Year, Location, trial_design, Replicates, planting_date, emergence_date, first_sign_disease) %>%
-   summarise(Treatments = length(E_treatment)),
-   caption = "Description of Experiments") %>%
-   kable_styling(fixed_thead = T, full_width = T) %>%
-   scroll_box(width = "900px", height = "500px")
-
-PM.dat$Trial_ref <- factor(PM.dat$Trial_ref)
-PM.dat$Location <- factor(PM.dat$Location)
-PM.dat$Year <- factor(PM.dat$Year)
-PM.dat$host_genotype <- factor(PM.dat$host_genotype)
-PM.dat$Fungicide <- factor(PM.dat$Fungicide)
-PM.dat$Trade_name <- factor(PM.dat$Trade_name)
-
-```
-
-## Weather data
-
-The mungbean DSS determines the need to spray on:  
-   1. The presence of the disease  
-   2. The forecasted maximum temperatures in the next seven days  
-   3. The number of days over the next seven days with rainfall
-
-Below I am plotting the mean maximum temperures over 7 days during the growing season at each Mungbean trial site.
-The vertical lines indicate when powdery mildew was first observed in that season.
-Variation may exist in the sowing date of each trial.
-
-```{r weather1, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
-# This chunk has been removed as the get_PPD2 function has stopped working and needs fixing
-# Update: I have included data files instead of seeking the data from the web. 
-# issue has something to do with website certificates not being appropriete.
-
-# Need weather data between 2011 and 2017
-
-# function to extract date from the year
-# format should be Universal time format
-year.day <- function(date){
-   if(is.na(date) == TRUE){ 
-      return(NA)
-      } else {
-return(as.numeric(as.Date(date) - as.Date(paste0(substr(date, start = 1, stop = 4),"-01-01"))))
-      }
-}
-
-# Function to generate some of the ggplot grouping colours
-gg_color_hue <- function(n) {
-  hues = seq(15, 375, length = n + 1)
-  hcl(h = hues, l = 65, c = 100)[1:n]
-}
-cols1 <- gg_color_hue(4)
-
-# silo.API <- "YeTZsWlFNC8hvbQLllv8KtbRQWsje4qxic5QQ7mL"
-# # retrieve the maximum temperatures from the six yearsd between 2011 and 2017 at weather station 041525 (Hermitage)
-# silo_war_Tmax <- getPPD2(station_id = 041525,start = 20110101,end = 20160630, silo.apikey = silo.API, variables = "max_temp,min_temp,daily_rain")
-# # retrieve the maximum temperatures from the six yearsd between 2011 and 2017 by location
-# silo_king_Tmax <- getPPD2(lat = -26.58, long = 151.83, start = 20110101, end = 20160630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
-# silo_gatton_Tmax <- getPPD2(lat = -27.56, long = 152.32, start = 20110101, end = 20170630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
-# silo_emerald_Tmax <- getPPD2(lat = -23.54, long = 148.19, start = 20110101, end = 20170630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
-
-silo_war_Tmax <- read.csv("./data/silo_war_Tmax.csv")
-silo_king_Tmax <- read.csv("./data/silo_king_Tmax.csv")
-silo_gatton_Tmax <- read.csv("./data/silo_gatton_Tmax.csv")
-silo_emerald_Tmax <- read.csv("./data/silo_emerald_Tmax.csv")
-
-experiment_sites <- data.frame(
-   location = c("Hermitage", "Kingaroy research station","Gatton", "Emerald Agricultural College"),
-   lat = c(-28.215 ,-26.58,-27.56,-23.54),
-   lon = c(152.1003,151.83,152.32,148.19)
-)
-
- leaflet() %>%
-    addProviderTiles("Esri.WorldTopoMap") %>%
-    addMarkers(lng = experiment_sites$lon, lat = experiment_sites$lat)
-# head(silo_gatton_Tmax)
-# ______  Kingaroy_______
-
-```
-
-### Kingaroy historical weather
-```{r Kingaroy_weather, include=FALSE}
-
-# Smoothing temperatures by taking a rolling7 day average
-max_T <- vector()
-min_T <- vector()
-for(i in 1:length(silo_king_Tmax[,1])){
-   max_T <- c(max_T,mean(silo_king_Tmax$max_temp[i:(i+7)]))
-   min_T <- c(min_T,mean(silo_king_Tmax$min_temp[i:(i+7)]))
-}
-
-king_Tm_aver <- data.frame(location = "Kingaroy", date = as.Date(silo_king_Tmax$date), max_T, min_T, daily_rain = silo_king_Tmax$daily_rain)
-
-# Add columns for Year and date to data
-king_Tm_aver <- king_Tm_aver %>%
-   mutate(Year = substr(king_Tm_aver$date, start = 1, stop = 4),
-          Day = year.day(king_Tm_aver$date))
-
-# Create data subset of Powdery mildew data means for the first sign of the disease by location
-King_FS <- PM.dat %>%
-   group_by(Trial_ref, Location, Year) %>%
-   summarise(First_sign = mean(as.Date(first_sign_disease), na.rm = T)) %>%
-   filter(Location == "Kingaroy") %>%
-   mutate(Day = year.day(First_sign))
-str(king_Tm_aver)
-str(King_FS)
-ggplot(subset(king_Tm_aver, Year == levels(factor(King_FS$Year))),
-              aes(Day))+
-   geom_line(aes(y = max_T, colour = Year))+
-   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
-   geom_line(aes(y = min_T, colour = Year))+
-   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
-   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
-   title = "Maximum and minimum daily temperatures in Kingaroy")+
-   scale_y_continuous(limits = c(0,40))+
-   scale_x_continuous(limits = c(0,200), 
-                      labels = c(subset(king_Tm_aver, Year == 2016)$date[c(1,50,100,150,200)]),
-                      breaks = c(1,50,100,150,200))+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(xintercept = King_FS$Day[1], size =1, colour = cols1[1], linetype = "dotted")+
-   geom_vline(xintercept = King_FS$Day[2], size =1.5, colour = cols1[2], linetype = "dotted")+
-   geom_vline(xintercept = King_FS$Day[3], size =1, colour = cols1[3], linetype = "dashed")+
-   geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
-   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))
-#   scale_x_continuous(limits = c(1,180),
-#                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
-#                      labels = c("2012-Jan-01","2012-Feb-01","2012-Mar-01","2012-Apr-01","2012-May-01","2012-Jun-01","2012-Jul-01"))
-
-```
-
-### Hermitage historical weather
-```{r Hermitage_weather, include=FALSE}
-
-# ______  Hermitage  _______
-max_T <- vector()
-min_T <- vector()
-for(i in 1:length(silo_war_Tmax[,1])){
-   max_T <- c(max_T,mean(silo_war_Tmax$max_temp[i:(i+7)]))
-   min_T <- c(min_T,mean(silo_war_Tmax$min_temp[i:(i+7)]))
-}
-
-war_Tm_aver <- data.frame(location = "Hermitage", date = as.Date(silo_war_Tmax$date), max_T, min_T, daily_rain = silo_war_Tmax$daily_rain)
-
-# Add columns for Year and date to data
-war_Tm_aver <- war_Tm_aver %>%
-   mutate(Year = substr(war_Tm_aver$date, start = 1, stop = 4),
-          Day = year.day(war_Tm_aver$date))
-
-# Create data subset of Powdery mildew data means for the first sign of the disease by location
-Herm_FS <- PM.dat %>%
-   group_by(Trial_ref, Location, Year) %>%
-   summarise(First_sign = mean(as.Date(first_sign_disease), na.rm = T)) %>%
-   filter(Location == "Hermitage") %>%
-   mutate(Day = year.day(First_sign))
-
-ggplot(subset(war_Tm_aver, Year == levels(factor(Herm_FS$Year))),
-              aes(Day))+
-   geom_line(aes(y = max_T, colour = Year))+
-   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
-   geom_line(aes(y = min_T, color = Year))+
-   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
-   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
-   title = "Maximum and minimum daily temperatures in Hermitage")+
-   scale_y_continuous(limits = c(0,40))+
-   scale_x_continuous(limits = c(0,200), 
-                      labels = c(subset(war_Tm_aver, Year == 2016)$date[c(1,50,100,150,200)]),
-                      breaks = c(1,50,100,150,200))+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(xintercept = Herm_FS$Day[1], size =1, colour = cols1[1], linetype = "dotted")+
-   geom_vline(xintercept = Herm_FS$Day[2], size =1.5, colour = cols1[2], linetype = "dotted")+
-   geom_vline(xintercept = Herm_FS$Day[3], size =1, colour = cols1[3], linetype = "dashed")+
-      geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
-   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
-   scale_x_continuous(limits = c(1,180),
-                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
-                      labels = c("Jan-01","Feb-01","Mar-01","Apr-01","May-01","Jun-01","Jul-01"))
-
-```
-
-### Gatton historical weather
-```{r Gatton_weather, include=FALSE}
-
-# ______  Gatton  _______
-max_T <- vector()
-min_T <- vector()
-for(i in 1:length(silo_gatton_Tmax[,1])){
-   max_T <- c(max_T,mean(silo_gatton_Tmax$max_temp[i:(i+7)]))
-   min_T <- c(min_T,mean(silo_gatton_Tmax$min_temp[i:(i+7)]))
-}
-# put maximum, minimum temperatures into a dataframe corresponding with thier corresponding date
-Gat_Tm_aver <- data.frame(location = "Gatton", date = as.Date(silo_gatton_Tmax$date), max_T, min_T, daily_rain = silo_gatton_Tmax$daily_rain)
-# Add columns for Year and date to data
-Gat_Tm_aver <- Gat_Tm_aver %>%
-   mutate(Year = substr(Gat_Tm_aver$date, start = 1, stop = 4),
-          Day = year.day(Gat_Tm_aver$date)) 
-# Create data subset of Powdery mildew data means for the first sign of the disease by location
-Gatton_FS <- PM.dat %>%
-   group_by(Trial_ref, Location) %>%
-   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
-   filter(Location == "Gatton") %>%
-   mutate(Year = factor(substr(First_sign,1,4)),
-          Day = year.day(First_sign))
-ggplot(subset(Gat_Tm_aver, Year == levels(Gatton_FS$Year)),
-               aes(Day))+
-   geom_line(aes(y = max_T, colour = Year))+
-   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
-   geom_line(aes(y = min_T, colour = Year))+
-   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
-   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
-   title = "Maximum and minimum daily temperatures in Gatton")+
-   scale_y_continuous(limits = c(0,40))+
-   scale_x_continuous(limits = c(0,200), 
-                      labels = c(subset(Gat_Tm_aver, Year == levels(Gatton_FS$Year))$date[c(1,50,100,150,200)]),
-                      breaks = c(1,50,100,150,200))+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(xintercept = Gatton_FS$Day, colour = "green", size =1)+
-      geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
-   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
-   scale_x_continuous(limits = c(1,180),
-                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
-                      labels = c("2012-Jan-01","2012-Feb-01","2012-Mar-01","2012-Apr-01","2012-May-01","2012-Jun-01","2012-Jul-01"))
-#   scale_x_continuous(limits = as.Date(c("2012-01-01","2012-06-01")))
-
-# line 259
-vec1 <- year.day(Herm_FS$First_sign)
 ```

### 2019-06-20 03_Preliminary_analysis.Rmd
remove old analysis

@@
 library(devtools)
+library(lme4)
+library(theme.usq)
 #source("./getPPD2.R")
@@
 ```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
-library(lme4)
+# Import data
+PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
 
-# Which row spacing leads to the highest yield penalty
-
-# `2017-05-11` # last assessment Fogerty
-subset(PM_MB_17, location == "Hermitage")
-ggplot(subset(PM_MB_17, Treatment.No == "T1"||"1"), 
-       aes(y = Incidence, x = Incidence_assessment_date, colour = location))+
+# Which row spacing leads to the higher disease severity
+PM_MB_means %>%
+   filter(Year >= 2017)%>%
+   filter(Fungicide == "control") %>%
+ggplot(aes(y = PM_final_severity, x = row_spacing, colour = Location))+
    geom_point()+
    geom_smooth()+
-   scale_y_continuous(limits = c(-5,15))
-# PM_MB_means <- subset(PM_MB_means, Fungicide != "control")   
-# PM_MB_means$Fungicide <- factor(PM_MB_means$Fungicide, levels = c("Sulphur", "Amistar", "propiconazole", "Tebeconazole"))
-PM_MB_means$Fungicide <- factor(PM_MB_means$Fungicide, levels = c("control", "Sulphur", "Amistar", "propiconazole", "Tebeconazole"))
-yield_lmer1 <- lmer(`yield_gain` ~ factor(total_Fungicide) + Fungicide + factor(Year) + (factor(Year)|Location), 
-                    data = PM_MB_means, na.action = na.omit, REML = F)
-# removed the Year interaction with location
-yield_lmer2 <- lmer(`yield_gain` ~ factor(total_Fungicide) + Fungicide + factor(Year) + (1|Location), 
-                    data = PM_MB_means, na.action = na.omit, REML = F)
-# Removing Fungicide as different fungicides were sprayed a different number of times
-yield_lmer3 <- lmer(`yield_gain` ~ factor(total_Fungicide)  + factor(Year) + (1|Location), 
-                    data = PM_MB_means, na.action = na.omit, REML = F)
-# Removing Fungicide as different fungicides were sprayed a different number of times
-yield_lmer4 <- lmer(`yield_gain` ~ factor(total_Fungicide)  + factor(Year) + (1|Location) + (1|Fungicide), 
-                    data = PM_MB_means, na.action = na.omit, REML = T)
-ranef(yield_lmer4)
-anova(yield_lmer1, yield_lmer2) # P = 0.8943  # removed random intercept 'Year' for each random slope 'Location' # Keep simpler model 
-anova(yield_lmer2, yield_lmer3) # P = 0.8005  # Removed (FE) Fungicide     #     Fungicide showed not to be significant in protecting yield
-anova(yield_lmer3, yield_lmer4) # P = 1       # Added Fungicide as a random effect #     Fungicide showed not to contribute to variation and 
-yield_lmer <- lmer(`yield_gain` ~ factor(total_Fungicide) + factor(Year) + (1|Location), 
-                    data = PM_MB_means, na.action = na.omit)
-summary(yield_lmer)
-ranef(yield_lmer)
+   scale_y_continuous(limits = c(-5,15))+
+   theme_usq()
+
+# Which row spacing leads to the higher yeild potential
+PM_MB_means %>%
+   filter(Year >= 2017)%>%
+#   filter(Fungicide == "control") %>%
+ggplot(aes(y = as.numeric(grain_yield.t.ha.), x = row_spacing, colour = Location))+
+   geom_jitter(width = 0.01)+
+   geom_smooth()+
+#   scale_y_continuous(limits = c(-5,15))+
+   theme_usq()
+
 ```

### 2019-06-20 03_Preliminary_analysis.Rmd
Fixing code and cleaning data, Deleted some code which makes $spray_diff a comparison to when the first application of fungicide was and when the disease first occured

@@
 PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
+colnames(PM_MB_means)
+PM_MB_means$Fungicide_application_1[as.character(PM_MB_means$Fungicide_application_1) == ""] <- NA
+PM_MB_means$Fungicide_application_2[as.character(PM_MB_means$Fungicide_application_2) == ""] <- NA
+PM_MB_means$Fungicide_application_3[as.character(PM_MB_means$Fungicide_application_3) == ""] <- NA
+PM_MB_means$Fungicide_application_4[as.character(PM_MB_means$Fungicide_application_4) == ""] <- NA
+PM_MB_means$Fungicide_application_5[as.character(PM_MB_means$Fungicide_application_5) == ""] <- NA
+PM_MB_means$Fungicide_application_6[as.character(PM_MB_means$Fungicide_application_6) == ""] <- NA
+PM_MB_means$Fungicide_application_7[as.character(PM_MB_means$Fungicide_application_7) == ""] <- NA
 
@@
 
-#### Yield saved 
-##### Number of fungicide applications
+### Yield saved 
+**Number of fungicide applications**
 The following density plots show mean yield saved in relation to how many sprays were applied.
 
-```{r warning=FALSE, echo=FALSE}
-library(ggplot2)
-PM_MB_means <- read.csv("./data/1902 powdery mildew-Mungbean - Collated means.csv")
+```{r PA_Yield, warning=FALSE, echo=FALSE}
 
@@
    group_by(total_Fungicide) %>%
-   summarise(lower = quantile(yield_gain, na.rm = T, c(0.025)),
-             upper = quantile(yield_gain, na.rm = T, c(0.975)))
+   summarise(n = length(yield_gain),
+             lower_2.5 = quantile(yield_gain, na.rm = T, c(0.025)),
+             median = median(yield_gain, na.rm = T),
+             mean = mean(yield_gain, na.rm = T),
+             upper_97.5 = quantile(yield_gain, na.rm = T, c(0.975)))
+
 # Density plot of Number of fungicide applications and the resulting yeild saved (as a proportion)
@@
          panel.background = element_rect(fill = NA))+
-   geom_vline(data = quant_PMy, aes(xintercept = lower, 
+   geom_vline(data = quant_PMy, aes(xintercept = lower_2.5, 
                colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   geom_vline(data = quant_PMy, aes(xintercept = upper, 
+   geom_vline(data = quant_PMy, aes(xintercept = upper_97.5, 
                colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
@@
 
-names(quant_PMy) <- c("Number of sprays", "2.5 percentile", "97.5 percentile")
-knitr::kable(quant_PMy)
-#             col.names = c("Number of sprays", "2.5 percentile", "97.5 percentile"))
-#            caption = "The 'upper' and 'lower' percentiles for yeild saved (t/Ha) against the number of Fungicide sprays in a season.
-Data from 2011-2017 mungbean experimental means.
-Data ignores factors such as fungicide, dose, season or location of experiment")
+kable(quant_PMy,
+   caption = "Yeild gain for each number of fungicide applications") %>%
+   kable_styling(fixed_thead = T, full_width = T)
+
 # Making a table of showing the upper and lower percentiles (95%)
@@
    group_by(total_Fungicide) %>%
-   summarise(lower = quantile(prop_YG, na.rm = T, c(0.025)),
-             upper = quantile(prop_YG, na.rm = T, c(0.975)))
+   summarise(lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
+             median = median(prop_YG, na.rm = T),
+             mean = mean(prop_YG, na.rm = T),
+             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975)))
+
 # Density plot of proportion of yield saved
@@
          panel.background = element_rect(fill = NA))+
-   geom_vline(data = quant_PM, aes(xintercept = lower, 
+   geom_vline(data = quant_PM, aes(xintercept = lower_2.5, 
                colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   geom_vline(data = quant_PM, aes(xintercept = upper, 
+   geom_vline(data = quant_PM, aes(xintercept = upper_97.5, 
                colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
@@
    scale_x_continuous(limits = c(-0.3,0.55))
-names(quant_PM) <- c("Number of sprays", "2.5 percentile", "97.5 percentile")
-knitr::kable(quant_PM)   
+
+kable(quant_PM,
+   caption = "Proportion of yeild gain for each number of fungicide applications") %>%
+   kable_styling(fixed_thead = T, full_width = T)   
 #knitr::kable(quant_PM, 
@@
    filter(Fungicide != "control") %>%
-   filter(Year != 2017) %>%
 #   filter(total_Fungicide ==1) %>%
-   mutate(days_from_1st = as.numeric(as.Date(Fungicide_application_1) - first_sign_disease))
-colnames(PM_MB_means)
-days_from_fungicid <- function(FSD,F1,F2,F3){
-   dF1 <- as.numeric(as.Date(F1) - as.Date(FSD))
-   dF2 <- as.numeric(as.Date(F2) - as.Date(FSD))
-   dF3 <- as.numeric(as.Date(F3) - as.Date(FSD))
-   if(is.na(dF1)){
-      return(NA)} else{
-   if(between(dF1,lower = -1, upper = 1000)){
-      return(dF1)}else{
-   if(is.na(dF2)){
-      return(dF1)}else{
-      if(between(dF2,lower = dF1, upper = -0.1)){
-            return(dF2)} else{
-               return(dF3)}}
-            }}
-}
-vec1<- vector()
-for(i in 1:dim(PM_MB_means1)[1]){
-   dF1 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_1)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
-   dF2 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_2)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
-   dF3 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_3)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
-   if(is.na(dF1)){
-      vec1 <- c(vec1,dF1)} else{
-         if(between(as.numeric(dF1),-1, 1000)){
-            vec1 <- c(vec1,dF1)}else{
-               if(is.na(dF2)){
-                  vec1 <- c(vec1,dF1)}else{
-                     if(between(as.numeric(dF2),as.numeric(dF1), -1.1)){
-            vec1 <- c(vec1,dF2)} else{
-               if(as.numeric(dF3)>=0){
-                  vec1 <- c(vec1,dF2)} else{
-                     vec1 <- c(vec1,dF3)}}}
-            }}
-}
-PM_MB_means1$spray_diff <- vec1 # gives the 
-PM_MB_means1$days_from_1st
-#summary(factor(PM_MB_means1$days_from_1st))
-# Density plot of proportion of yield saved
-ggplot(PM_MB_means1, aes(prop_YG))+
-   geom_density(aes(group = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20)), 
-                    fill = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20))), alpha = 0.3)+
-   geom_vline(xintercept = 0, size =1)+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="First spray window\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.3,0.55))
-###########################################3
+   mutate(days_from_1st = as.numeric(
+      as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") -
+         as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")))
+
+# What range of 
 unique(PM_MB_means1$days_from_1st)
+PM_MB_means1 %>%
+   group_by(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))) %>%
+   summarise(n = length(prop_YG),
+             lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
+             median = median(prop_YG, na.rm = T),
+             mean = mean(prop_YG, na.rm = T),
+             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
+   kable(caption = "Difference in days between first sign of disease and first fungicide application and the effect on proportion of yield gain") %>%
+   kable_styling(fixed_thead = T, full_width = T)
+
+summarise()
+levels(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20)))
+
 ggplot(PM_MB_means1, aes(prop_YG))+
@@
    geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))~., factor(PM_MB_means1$Fungicide))+
+   facet_grid(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))~.)+
    #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
@@
    scale_x_continuous(limits = c(-0.2,0.55))
-unique(PM_MB_means1$spray_diff)
-ggplot(PM_MB_means1, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means1$spray_diff, c(-29,-20,-15,-12,-0.5,1.5,7,10,12,20))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means1$spray_diff, c(-29,-20,-15,-12,-0.5,1.5,7,10,12,20))~.)+
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.2,0.55))
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PM_prop <- PM_MB_means1 %>%
-   mutate(cut_daysfrom1st = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20))) %>%
-   group_by(cut_daysfrom1st) %>%
-   summarise(lower = quantile(prop_YG, na.rm = T, c(0.025)),
-             upper = quantile(prop_YG, na.rm = T, c(0.975)))
-names(quant_PM_prop) <- c("Days relative to\nfirst incidence", "2.5 percentile", "97.5 percentile")
-cat("Lower (2.5) and Upper (97.5) quantiles for the proportion of yield gained, when the first fungicide applied relative to when powdery mildew is first seen")
-knitr::kable(quant_PM_prop)   
-ggplot(PM_MB_means1, aes(yield_gain))+
-   geom_density(aes(fill = cut(PM_MB_means1$days_from_1st, c(-29,-15,-6,-0.5,0.5,2,10,20))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means1$days_from_1st, c(-29,-15,-6,-0.5,0.5,2,10,20))~.)+
-   scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Grain yield (t/Ha) saved",
-   title = "Grain yield (t/Ha) saved, grouped by when the\nfirst fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.4,1.2))
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PM_prop <- PM_MB_means1 %>%
-   mutate(cut_daysfrom1st = cut(PM_MB_means1$days_from_1st, c(-29,-20,-15,-6,-0.5,0.5,2,10,20))) %>%
-   group_by(cut_daysfrom1st) %>%
-   summarise(lower = quantile(yield_gain, na.rm = T, c(0.025)),
-             upper = quantile(yield_gain, na.rm = T, c(0.975)))
-names(quant_PM_prop) <- c("Days relative to\nfirst incidence", "2.5 percentile", "97.5 percentile")
-print("Yield gain quantiles when the first fungicide applied relative to when powdery mildew is first seen, Lower (2.5) and Upper (97.5) quantiles of yeild ")
-knitr::kable(quant_PM_prop)  
 ```
 
+#### Effect of Fungicide on proportional yiTiming of fungicide application
 ```{r}

### 2019-06-20 03_Preliminary_analysis.Rmd
readding deleted chunk

@@
 
-#### Effect of Fungicide on proportional yiTiming of fungicide application
 ```{r}
-PM_MB_means2 <- PM_MB_means1 %>%
-   filter(Fungicide == "Tebeconazole")
-unique(PM_MB_means2$spray_diff)
-ggplot(PM_MB_means2, aes(prop_YG))+
+# removing 2017 and control data
+# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
+PM_MB_means1 <- PM_MB_means %>%
+   filter(Fungicide != "control") %>%
+   filter(Year != 2017) %>%
+#   filter(total_Fungicide ==1) %>%
+   mutate(days_from_1st = as.numeric(as.Date(Fungicide_application_1) - first_sign_disease))
+colnames(PM_MB_means)
+days_from_fungicid <- function(FSD,F1,F2,F3){
+   dF1 <- as.numeric(as.Date(F1) - as.Date(FSD))
+   dF2 <- as.numeric(as.Date(F2) - as.Date(FSD))
+   dF3 <- as.numeric(as.Date(F3) - as.Date(FSD))
+   if(is.na(dF1)){
+      return(NA)} else{
+   if(between(dF1,lower = -1, upper = 1000)){
+      return(dF1)}else{
+   if(is.na(dF2)){
+      return(dF1)}else{
+      if(between(dF2,lower = dF1, upper = -0.1)){
+            return(dF2)} else{
+               return(dF3)}}
+            }}
+}
+vec1<- vector()
+for(i in 1:dim(PM_MB_means1)[1]){
+   dF1 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_1)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
+   dF2 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_2)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
+   dF3 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_3)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
+   if(is.na(dF1)){
+      vec1 <- c(vec1,dF1)} else{
+         if(between(as.numeric(dF1),-1, 1000)){
+            vec1 <- c(vec1,dF1)}else{
+               if(is.na(dF2)){
+                  vec1 <- c(vec1,dF1)}else{
+                     if(between(as.numeric(dF2),as.numeric(dF1), -1.1)){
+            vec1 <- c(vec1,dF2)} else{
+               if(as.numeric(dF3)>=0){
+                  vec1 <- c(vec1,dF2)} else{
+                     vec1 <- c(vec1,dF3)}}}
+            }}
+}
+PM_MB_means1$spray_diff <- vec1 # gives the 
+PM_MB_means1$days_from_1st
+```
+
+#### Effect of Fungicide 
+**on proportional yield gain with repect to time of application**
+##### Tebeconazole
+```{r}
+PM_MB_means1 %>%
+   group_by(Fungicide) %>%
+   filter(n() >= 5) %>% # remove any fungicide groups with less than 5 observations
+   summarise(n = length(prop_YG),
+             lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
+             median = median(prop_YG, na.rm = T),
+             mean = mean(prop_YG, na.rm = T),
+             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
+   kable(caption = "Fungicide effect on proportion of yield gain") %>%
+   kable_styling(fixed_thead = T, full_width = T)
+
+unique(
+PM_MB_means1 %>%
+   group_by(Fungicide) %>%
+   filter(n() >= 5) %>%
+   select(days_from_1st))
+
+PM_MB_means1 %>%
+   group_by(Fungicide) %>%
+   filter(n() >= 5) %>%
+ggplot(aes(prop_YG))+
    geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-1,2,7,10,12,20))), alpha = 0.5)+

### 2019-06-21 03_Preliminary_analysis.Rmd
Updating parts of non-functional code to make functional

--- 2019-06-20 03_Preliminary_analysis.Rmd
@@
 
-#### Effect of Fungicide on proportional yiTiming of fungicide application
 ```{r}
-PM_MB_means2 <- PM_MB_means1 %>%
-   filter(Fungicide == "Tebeconazole")
-unique(PM_MB_means2$spray_diff)
-ggplot(PM_MB_means2, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-1,2,7,10,12,20))), alpha = 0.5)+
+# removing 2017 and control data
+# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
+PM_MB_means1 <- PM_MB_means %>%
+   filter(Fungicide != "control") %>%
+   filter(Year != 2017) %>%
+#   filter(total_Fungicide ==1) %>%
+   mutate(days_from_1st = as.numeric(as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") - 
+                                        as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")))
+
+days_from_fungicid <- function(FSD,F1,F2,F3){
+   dF1 <- as.numeric(as.Date(F1) - as.Date(FSD))
+   dF2 <- as.numeric(as.Date(F2) - as.Date(FSD))
+   dF3 <- as.numeric(as.Date(F3) - as.Date(FSD))
+   if(is.na(dF1)){
+      return(NA)} else{
+   if(between(dF1,lower = -1, upper = 1000)){
+      return(dF1)}else{
+   if(is.na(dF2)){
+      return(dF1)}else{
+      if(between(dF2,lower = dF1, upper = -0.1)){
+            return(dF2)} else{
+               return(dF3)}}
+            }}
+}
+vec1<- vector()
+for(i in 1:dim(PM_MB_means1)[1]){
+   dF1 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_1, format = "%d/%m/%Y")[i] -
+                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
+   dF2 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_2, format = "%d/%m/%Y")[i] -
+                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
+   dF3 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_3, format = "%d/%m/%Y")[i] -
+                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
+   if(is.na(dF1)){
+      vec1 <- c(vec1,dF1)} else{
+         if(between(as.numeric(dF1),-1, 1000)){
+            vec1 <- c(vec1,dF1)}else{
+               if(is.na(dF2)){
+                  vec1 <- c(vec1,dF1)}else{
+                     if(between(as.numeric(dF2),as.numeric(dF1), -1.1)){
+            vec1 <- c(vec1,dF2)} else{
+               if(is.na(dF3)){
+                  vec1 <- c(vec1,dF2)}else{
+               if(as.numeric(dF3)>=0){
+                  vec1 <- c(vec1,dF2)}else{
+                     vec1 <- c(vec1,dF3)}}}}
+            }}
+}
+PM_MB_means1$spray_diff <- vec1 # gives the closest fungicide application date to the first sign of disease
+#PM_MB_means1$days_from_1st
+
+```
+
+#### Effect of Fungicide 
+**on proportional yield gain with repect to time of application**
+##### Tebeconazole
+```{r}
+PM_MB_means1 %>%
+   group_by(Fungicide) %>%
+   filter(n() >= 5) %>% # remove any fungicide groups with less than 5 observations
+   summarise(n = length(prop_YG),
+             lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
+             median = median(prop_YG, na.rm = T),
+             mean = mean(prop_YG, na.rm = T),
+             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
+   kable(caption = "Fungicide effect on proportion of yield gain") %>%
+   kable_styling(fixed_thead = T, full_width = T)
+
+unique(
+PM_MB_means1 %>%
+   group_by(Fungicide) %>%
+   filter(n() >= 5) %>%
+   select(days_from_1st))
+
+PM_MB_means1 %>%
+   group_by(Fungicide) %>%
+   filter(n() >= 5) %>%
+ggplot(aes(prop_YG))+
+   geom_density(aes(fill = cut(spray_diff, c(-1,2,7,10,12,20))), alpha = 0.5)+
    geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means2$spray_diff, c(1,2,7,10,12,20))~.)+
+   facet_grid(cut(spray_diff, c(1,2,7,10,12,20))~.)+
    #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+

### 2019-06-21 03_Preliminary_analysis.Rmd
Corrected code to make loop of density plots, one for each fungicide work.

@@
 
-summarise()
-levels(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20)))
-
 ggplot(PM_MB_means1, aes(prop_YG))+
@@
 
-unique(
-PM_MB_means1 %>%
-   group_by(Fungicide) %>%
-   filter(n() >= 5) %>%
-   select(days_from_1st))
+# unique(
+# PM_MB_means1 %>%
+#    group_by(Fungicide) %>%
+#    filter(n() >= 5) %>%
+#    select(days_from_1st))
+# 
+# 
+# PM_MB_means1 %>%
+#    group_by(Fungicide) %>%
+#    filter(n() >= 5) %>%
+# ggplot(aes(prop_YG))+
+#    geom_density(aes(fill = cut(spray_diff, c(-1,2,7,10,12,20))), alpha = 0.5)+
+#    geom_vline(aes(xintercept = 0), size =0.5)+
+#    facet_grid(rows = vars(cut(spray_diff, c(1,2,7,10,12,20))), cols = vars(Fungicide))+
+#    #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
+#    labs(x = "Proportion of grain yeild saved",
+#    title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
+#    theme(panel.grid.major = element_line(colour = "grey80"),
+#          panel.grid.minor = element_line(colour = "grey50"),
+#          panel.background = element_rect(fill = NA))+
+#    guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
+#    scale_x_continuous(limits = c(-0.2,0.55))
+# 
+#
 
-PM_MB_means1 %>%
-   group_by(Fungicide) %>%
-   filter(n() >= 5) %>%
-ggplot(aes(prop_YG))+
-   geom_density(aes(fill = cut(spray_diff, c(-1,2,7,10,12,20))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(spray_diff, c(1,2,7,10,12,20))~.)+
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.2,0.55))
 #__________________________________________________________________________________________________________
-levels(factor(PM_MB_means$Fungicide))
+# levels(factor(PM_MB_means$Fungicide))
+
+# combine Sulphur treatments
 PM_MB_means2 <- PM_MB_means1 %>%
@@
              Fungicide == "Sulphur (WP)")
+
 unique(PM_MB_means2$spray_diff)
+
 ggplot(PM_MB_means2, aes(prop_YG))+
@@
    labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
+   title = "Grain yield proportion saved grouped by\nwhen the first Sulphur fungicide application was made\nrelative to when Powdery Mildew was first seen")+
    theme(panel.grid.major = element_line(colour = "grey80"),
@@
    scale_x_continuous(limits = c(-0.3,0.6))
+
+```
+This plot shows that there is not a good probability that Sulphur will help save yield, even when it is sprayed at the ideal time.
+
+```{r each_fungicide}
 Chemical <- c("Amistar","Carbendazim","Tebeconazole", "propiconazole")
 levels(factor(PM_MB_means$Fungicide))
+
+# Generates multiple plots for each type of fungicide tested
 for(Chem in Chemical){
@@
    filter(Fungicide == Chem)
+
 cat(Chem)
-cat(unique(PM_MB_means2$spray_diff))
+
+# the following code 'spray_group' sets the spray_diff groupings that are used in the plots
+spray_group <- c(min(unique(PM_MB_means2$spray_diff))-1,
+      -5, 5,
+      max(unique(PM_MB_means2$spray_diff))+1)
+
+spray_group < - c(sort(unique(PM_MB_means2$spray_diff)-1), max(unique(PM_MB_means2$spray_diff)))
+
+print(spray_group)
+
 p1 <- ggplot(PM_MB_means2, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))), alpha = 0.5)+
+   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, spray_group)), alpha = 0.5)+
    geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))~.)+
+   facet_grid(cut(PM_MB_means2$spray_diff, spray_group)~.)+
    #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
@@
    guides(fill=guide_legend(title=paste(Chem,"Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease")))+
-   scale_x_continuous(limits = c(-0.3,0.6))
+   scale_x_continuous(limits = c(-1,1))
+
 print(p1)
-Sys.sleep(10)
+
 }
 ```
+It seems the calculation of spray diff does not elucidate any differences between application dates.

### 2019-07-03 01_Meta-analysis_experiments.Rmd
clarifying information on experimental site details
update libraries
commenting out some lines

--- 2019-06-20 01_Meta-analysis_experiments.Rmd
@@
 # Studies considered in meta-analysis
+
+```{r MEsummary_Libraries}
+library(dplyr)
+library(openxlsx)
+library(kableExtra)
+library(ggplot2)
+library(leaflet)
+#source("./getPPD2.R")
+
+```
 
@@
 
+## Summary of data
+
+```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}
+
+# source("Cleaning historical data.R", echo = FALSE, print.eval = FALSE)
+# ___ Datasets available ___
+# data   Herm_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2017, Hermitage and Fogerty
+# data   King_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2016, Hermitage and Kingaroy
+# data   Fogerty_17.1   - Full disease ratings and yeild data from Fogerty field trial in 2017
+# data   Herm_17.1      - Full disease ratings and yeild data from Hermitage field trial in 2017
+# data   PM_MB_17       - Full disease ratings and yeild data from Hermitage and Fogerty in 2017
+# data   PM_MB_16       - End of season powdery mildew rating and Yield data from two field trials in 2016, Hermitage and Kingaroy
+# data   PM_MB_means    - Mean disease rating and yeild data, from trial reports
+
+PM.dat <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
+
+glimpse(PM.dat)
+
+kable(PM.dat %>%
+   group_by(Trial_ref, Year, Location, trial_design, Replicates, planting_date, emergence_date, first_sign_disease) %>%
+   summarise(Treatments = length(E_treatment)),
+   caption = "Description of Experiments") %>%
+   kable_styling(fixed_thead = T, full_width = T) %>%
+   scroll_box(width = "900px", height = "500px")
+
+PM.dat$Trial_ref <- factor(PM.dat$Trial_ref)
+PM.dat$Location <- factor(PM.dat$Location)
+PM.dat$Year <- factor(PM.dat$Year)
+PM.dat$host_genotype <- factor(PM.dat$host_genotype)
+PM.dat$Fungicide <- factor(PM.dat$Fungicide)
+PM.dat$Trade_name <- factor(PM.dat$Trade_name)
+
+```
+
 ## Experimental locations
+Experimental locations where data was sufficient to include in meta-analysis
 ```{r Experiment_locations}

### 2019-07-03 Cleaning historical data.R

@@ -82,7 +82,7 @@ write.csv(as.data.frame(King_11_m ), "C:/Users/U8011054/OneDrive - USQ/Cloudstor
 # _____________            Hermitage  2015        ____________
 
 # Yeild data from 2016 Hermitage trial with final disease severity
-Herm_15 <- read.xlsx("C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/Past Trials/2015/2015 PMmung Herm/Mugbean powdery mildew 2014-15 inc results v2.xlsx", 
+Herm_15 <- read.xlsx("C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/Past Trials/2015 PMmung Herm/Mugbean powdery mildew 2014-15 inc results v2.xlsx", 
                      sheet = "HRS yield data", startRow = 4, colNames = TRUE, detectDates = TRUE)[1:31,1:9]
 
 
@@ -91,7 +91,7 @@ Herm_15$Year <- 2015
 Herm_15$location <- "Hermitage"
 
 # Disease incidence assessments through the 2016 season
-Herm_15.DR  <- read.xlsx("C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/Past Trials/2015/2015 PMmung Herm/Mugbean powdery mildew 2014-15 inc results v2.xlsx", 
+Herm_15.DR  <- read.xlsx("C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/Past Trials/2015 PMmung Herm/Mugbean powdery mildew 2014-15 inc results v2.xlsx", 
                                     sheet = "HRS ratings & graphs", startRow = 5, colNames = TRUE)[1:31,1:8]
 
 Herm_15$Plot.Length <- as.numeric(Herm_15$Plot.Length)
@@ -248,7 +248,7 @@ write.csv(Herm_17_sum, "./data/2017_Hermitage_summary.csv")
 
 
 # Columns to keep
-Herm_17 <- Herm_17[,c(1,2,4,5,7,10,9,11,12,43,
+Herm_17 <- Herm_17[,c(1,2,4,5,7,10,9,11,12,13,
                       17,19,21,23,25,27,29,
 #                      18,20,22,24,26,28,30,
                       34,36,37,35)]
@@ -264,11 +264,11 @@ Herm_17.1 <- reshape(data = Herm_17, idvar = "Plot", direction = "long",
         timevar = "ass_date"
 )
 
[…]

### 2019-07-04 04_MetaAnalysis.Rmd
Commenced Meta-analysis chapter

---
title: "Meta-analysis"
author: "P. Melloy"
date: "04/07/2019"
output: html_document
---

# Meta-analysis

## Data-wrangling

```{r}
PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
str(PM_MB_means)
```

When investigating previous studies into Powdery Mildew Fungicide efficacy on Mungbean `r length(unique(PM_MB_means$Trial_ref))` trials were found, however only eleven Tebeconazol were used for the following meta-analysis, followed by the next common Fungicide Propiconazole. Sulphur was disregarded due to it's inconsistancy in efficacy.

```{r Fungicides}
unique(PM_MB_means$Fungicide)
PM_MB_means %>%
   group_by(Fungicide,Trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Trials = n) %>%
   kable()

```

### Fungicide Doses
All trials that used Tebeconazole used approimately the same dose. dose of the active ingredient ranged from 62.35 grams per hectare to 60 grams per hectare. 
```{r Tebe_dose}
PM_MB_means %>%
   filter(Fungicide == "Tebeconazole") %>%
   select(Trial_ref, Year, Location, first_sign_disease, Dose.ai.ha., total_Fungicide) %>%
   kable()
```

### Row spacing

Some experiments were designed to investigate the effect of row spacing and plant density on Powdery Mildew disease and crop yield. The results showed that shorter distances between rows increase crop yields and mitigated the yield impact of the disease.

```{r row_spacing}
PM_MB_means %>%
   filter(Fungicide == "Tebeconazole") %>%
   group_by(row_spacing,Trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Treatments = n) %>%
   kable()

```

### 2019-07-17 05_MetaAnalysis.Rmd
rename meta-analysis chapter

--- 2019-07-04 04_MetaAnalysis.Rmd
@@
 The results showed that shorter distances between rows increase crop yields and mitigated the yield impact of the disease.
+Seven trials used a row spacing of 0.75 meters.
 
@@
 ```
+
+### standardising the type of variance
+
+The type of variance needs to be standardised between trials and treatments for the meta-analysis.
+
+```{r variance}
+PM_MB_means %>%
+   filter(Fungicide == "Tebeconazole",
+          row_spacing == 0.75) %>%
+   group_by(Y_error.type) %>%
+   summarise(n = length(Y_error.type))
+
+```

### 2019-07-17 05_MetaAnalysis.Rmd
Added formula to calculate standard deviation from the LSD. Needs to be checked

@@
 
-```{r}
+```{r Meta_dataImport}
 PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
+
 str(PM_MB_means)
@@
 
+PM_MB_means %>%
+   filter(Fungicide == "Tebeconazole",
+          row_spacing == 0.75)
+
 ```
@@
 ```
+
+```{r LSD_2_SD}
+# Formula and modifications based off information found at https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/
+colnames(PM_MB_means)
+
+Tcrit <- 1.697  # 0.05 and DFw = 30 # T critical value for which there is significant difference between two groups
+DFw <- sum(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates) - 
+   length(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates) # degrees of freedom within groups
+n.A <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[1]
+n.B <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[1]
+LSD <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Yield_error[1]
+
+# SSwithin <- #unknown
+# MSW <- SSwithin / DFw # mean square within (SS within / DF within)
+
+#  LSD = (Tcrit) * sqrt(MSW * (1/n.A + 1/n.B))
+#  (LSD/Tcrit) = sqrt(MSW * (1/n.A + 1/n.B))
+#  (LSD/Tcrit)^2 = MSW * (1/n.A + 1/n.B)
+#  (LSD/Tcrit)^2/(1/n.A + 1/n.B) = MSW
+MSW <- (LSD/Tcrit)^2/(1/n.A + 1/n.B)
+
+SSquares <- MSW * DFw
+
+Stdev <- sqrt(
+   (1/(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[1] - 1)) * 
+      SSquares)
+
+```

### 2019-07-19 05_MetaAnalysis.Rmd
removed -1 As a random variable
replaced -1
addding sampling variance calculation for mung1112/02

--- 2019-07-17 05_MetaAnalysis.Rmd
@@
    summarise() %>%
-   count() %>%
+   count(sort = T) %>%
    rename(Trials = n) %>%
@@
 ```
+
+```{r LSD_2_MSE}
+# Formula and modifications based off information found at https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/
+colnames(PM_MB_means)
+
+Tcrit <- 1.697  # 0.05 and DFw = 30 # T critical value for which there is significant difference between two groups
+DFw <- sum(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates) - 
+   length(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates) # degrees of freedom within groups
+n.A <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[1]
+n.B <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[2]
+LSD <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Yield_error[1]
+
+# SSwithin <- #unknown
+# MSW <- SSwithin / DFw # mean square within (SS within / DF within)
+
+#  LSD = (Tcrit) * sqrt(MSW * (1/n.A + 1/n.B))
+#  (LSD/Tcrit) = sqrt(MSW * (1/n.A + 1/n.B))
+#  (LSD/Tcrit)^2 = MSW * (1/n.A + 1/n.B)
+#  (LSD/Tcrit)^2/(1/n.A + 1/n.B) = MSW
+MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B)
+
+```
+![calculating sampling variance from mean squared error Paul et. al. (2008)](Paul_etal_2008.PNG)
+
+```{r sampling_variance}
+for(j in seq_along(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates)){
+   if(j == 1){Sv <- vector(length = length(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates))}
+#  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[j] *
+#                   PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$grain_yield.t.ha.[j])
+# Balance equation 
+   Sv[j] = sqrt(MSE/(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[j] *
+                  as.numeric(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$grain_yield.t.ha.[j])))
+
+   }
+
+```

### 2019-07-22 05_MetaAnalysis.Rmd
Addition of standard deviation to sample Variance chunk

@@
 ```{r Meta_dataImport}
-PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
+PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv", stringsAsFactors = FALSE)
 
-str(PM_MB_means)
+#str(PM_MB_means)
 ```
@@
 
+The trial, `mung1112/02` uses Least squre differences to describe the variation within the experiment. The following code attempts to convert this to sampling variance as per the method in
+
 ```{r LSD_2_MSE}
@@
 MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B)
+MSE <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[1]*(LSD/Tcrit)^2/2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
 
@@
 
+# and replacing the values in the dataset
+
+PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Yield_error <- Sv
+PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Y_error.type <- "SamplingVariance"
+
 ```
+
+Now to estimate the variance from the standard deviation
+
+```{r stdev2SampVariance}
+# subset data by those which describe the Yield error with standard deviation
+Trials <- PM_MB_means %>%
+   filter(Fungicide == "Tebeconazole",
+          row_spacing == 0.75,
+          Y_error.type == "stdev")%>%
+   select(Trial_ref)%>%
+   distinct()
+
+# calculate the Sampling variance from the standard deviation
+# standard error of the mean equals the standard deviation divided by the square root of the number of samples
+# Sv <- sem^2 <- stdev/sqrt(n)
+# Sampling variance eqauls the square of the standard error.
+# Sv <- (stdev/sqrt(n))^2
+
+# Therefore
+
+for(j in seq_along(PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error)){
+# create empty vector at first iteration with length of j
+   if(j == 1){Sv <- vector(length = length(PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error))}
+
+# Equation to convert standard deviation to Sampling Variance 
+   Sv[j] = (PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error/
+               sqrt(PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Replicates))^2
+   }
+
+PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error <-
+
+   # and replacing the values in the dataset
+PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error <- Sv
+PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Y_error.type <- "SamplingVariance"
+
+```

### 2019-07-22 05_MetaAnalysis.Rmd
updating explainations and comments

@@
 
-The trial, `mung1112/02` uses Least squre differences to describe the variation within the experiment. The following code attempts to convert this to sampling variance as per the method in
+The trial, `mung1112/02` uses Least squre differences to describe the variation within the experiment.
+The following code attempts to convert this to sampling variance as per the method in [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
+Ideas for using a T-critical value of 1.697 came from reading a [statisics-how-to website](https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/).
+A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted where 30 degrees of freedom within expeiment was used to find the 'T-crit' value of 1.697.
 
@@
 # Formula and modifications based off information found at https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/
-colnames(PM_MB_means)
 
@@
 #  (LSD/Tcrit)^2/(1/n.A + 1/n.B) = MSW
-MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B)
+#  MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B) # This formula was abandon in favor for the formula in Nugugi et. at (2011)
 MSE <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[1]*(LSD/Tcrit)^2/2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
@@
 ```
-![calculating sampling variance from mean squared error Paul et. al. (2008)](Paul_etal_2008.PNG)
+![Calculating sampling variance from mean squared error Paul et. al. (2008)](Paul_etal_2008.PNG)
 
@@
 ```
+
+Now for the trickier part creating 'Sampling Variance from NAs.
+```{r}
+Trials <- PM_MB_means %>%
+   filter(Fungicide == "Tebeconazole",
+          row_spacing == 0.75,
+          Y_error.type == NA)%>%
+   select(Trial_ref)%>%
+   distinct()
+```

### 2019-07-23 05_MetaAnalysis.Rmd
updated LSD conversion to loop in the two trials instead of the one. Corrected Standard deviation loop

@@
 
+```{r LSD_trials}
+Trials <- PM_MB_means %>%
+   filter(Fungicide == "Tebeconazole",
+          row_spacing == 0.75,
+          Y_error.type == "lsd (P=0.05)")%>%
+   select(Trial_ref)%>%
+   distinct()
+
+```
+
 The trial, `mung1112/02` uses Least squre differences to describe the variation within the experiment.
@@
 
-```{r LSD_2_MSE}
+![Calculating sampling variance from mean squared error Paul et. al. (2008)](Paul_etal_2008.PNG)
+
+```{r LSD_2_Sampling Variance}
 # Formula and modifications based off information found at https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/
 
-Tcrit <- 1.697  # 0.05 and DFw = 30 # T critical value for which there is significant difference between two groups
-DFw <- sum(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates) - 
-   length(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates) # degrees of freedom within groups
-n.A <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[1]
-n.B <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[2]
-LSD <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Yield_error[1]
+for(Trial2012 in Trials$Trial_ref){
+
+Tcrit <- 1.697  # 0.05 and DFw = 30 # T critical value for which there is significant difference between two groups; This value is the same for both trials "mung1112/01" and "mung1112/02"
+DFw <- sum(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates) - 
+   length(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates) # degrees of freedom within groups
+# n.A <- PM_MB_means[PM_MB_means$Trial_ref == "Trial2012,]$Replicates[1]
+# n.B <- PM_MB_means[PM_MB_means$Trial_ref == "Trial2012,]$Replicates[2]
+LSD <- PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Yield_error[1]
 
@@
 #  MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B) # This formula was abandon in favor for the formula in Nugugi et. at (2011)
-MSE <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[1]*(LSD/Tcrit)^2/2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
+MSE <- PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates[1]*(LSD/Tcrit)^2/2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
 
-```
-![Calculating sampling variance from mean squared error Paul et. al. (2008)](Paul_etal_2008.PNG)
-
-```{r sampling_variance}
-for(j in seq_along(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates)){
-   if(j == 1){Sv <- vector(length = length(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates))}
-#  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[j] *
-#                   PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$grain_yield.t.ha.[j])
+for(j in seq_along(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates)){
+   if(j == 1){Sv <- vector(length = length(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates))}
+#  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates[j] *
+#                   PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$grain_yield.t.ha.[j])
 # Balance equation 
-   Sv[j] = sqrt(MSE/(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[j] *
-                  as.numeric(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$grain_yield.t.ha.[j])))
+   Sv[j] = sqrt(MSE/(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates[j] *
+                  as.numeric(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$grain_yield.t.ha.[j])))
 
@@
 
-PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Yield_error <- Sv
-PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Y_error.type <- "SamplingVariance"
+PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Yield_error <- Sv
+PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Y_error.type <- "SamplingVariance"
 
+}
 ```
@@
 # Equation to convert standard deviation to Sampling Variance 
-   Sv[j] = (PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error/
-               sqrt(PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Replicates))^2
+   Sv[j] = (PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error[j]/
+               sqrt(PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Replicates[j]))^2
    }
-
-PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error <-
 
@@
           row_spacing == 0.75,
-          Y_error.type == NA)%>%
-   select(Trial_ref)%>%
+          is.na(Y_error.type))
+
    distinct()

### 2019-07-23 05_MetaAnalysis.Rmd
Notes, host genotypes and trying to understand generating variance from log ratios... TBC

@@
 ```
+
+### Host genotypes
+Host genotype may have to be analysed to determine the effect.  
+```{r Host_genotype}
+PM_MB_means %>%
+   filter(Fungicide == "Tebeconazole",
+          row_spacing == 0.75) %>% 
+   group_by(host_genotype) %>%
+   summarise(n = length(host_genotype))
+
+```
+In general the mungbean varieties have the following resistance to powdery mildew.  
+   - Berken: Highly susceptible  
+   - Crystal: Susceptible  
+   - Jade: Moderatly susceptible
 
@@
 
-Now for the trickier part creating 'Sampling Variance from NAs.
+Now for the trickier part creating 'Sampling Variance' for treatments where only mean yeild is recorded.  
+The trial which does not report any type of variance also reports that there is no significant difference between the means.
 ```{r}
-Trials <- PM_MB_means %>%
+PM_MB_means %>%
    filter(Fungicide == "Tebeconazole",
           row_spacing == 0.75,
-          is.na(Y_error.type))
-
+          is.na(Y_error.type)) %>%
+   select(Trial_ref)%>%
    distinct()
 ```
+
+A single trial `mung1516/03` within the current scope od the meta-analysis fails to report a varience statistic.
+According to [Machado F.
+et.
+al (2017)](http://apsjournals.apsnet.org/doi/10.1094/PDIS-03-17-0340-RE) [Paul et.
+al.
+(2007)](https://apsjournals.apsnet.org/doi/pdfplus/10.1094/PHYTO-97-2-0211) uses linear regression model to estimate sampling variance.
+
+```{r na2Sampling_variance}
+
+for(i in PM_MB_means$Trial_ref){
+
+log(V)[i] = a + b * log(
+   mean(subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "control"),
+        subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "Tebeconazole")))
+# need to know what parameters a and b are here
+# I am guessing they represent prediction parameters for each "study" for each of the treatments, "control" and Tebeconazole"
+
+}
+
+```

### 2019-07-24 05_MetaAnalysis.Rmd
APPS abstract

@@
           row_spacing == 0.75) %>% 
-   group_by(host_genotype) %>%
-   summarise(n = length(host_genotype))
+   group_by(host_genotype, Trial_ref) %>%
+   summarise() %>%
+   count() %>%
+   rename(Treatments = n) %>%
+   kable()
+
+PM_MB_means %>%
+   filter(Fungicide == "Tebeconazole") %>%
+   group_by(row_spacing,Trial_ref) %>%
+   summarise() %>%
+   count() %>%
+   rename(Treatments = n) %>%
+   kable()
 

### 2019-07-24 Presentations/2019_APPS_Meta-PowderyMildewMungbean_Abstract.Rmd
APPS abstract

---
title: Meta-analysis of the fungicide application for management of Powdery Mildew
  in Mungbean.
author: "P. Melloy"
date: "24/07/2019"
output: word_document
---

Commercially available Mungbean varieties lack adequate powdery mildew resistance to protect crop yields. Growers, therefore, manage severe epidemics by applying fungicide and sowing early in the growing season to avoid the cooler temperatures which are associated with Powdery Mildew infestations. Since 2001 twenty-four field trials have assessed the timing and frequency of fungicide application on Powdery Mildew disease incidence and Mungbean yield. Results from these trials have advised the best practice for managing the disease through fungicide application at first sign of disease, and a second spray two weeks later if necessary. However, the outcomes of these trials sometimes lacked certainty when analysed in isolation. This meta-analysis aims to use the combined power of multiple studies to increase certainty for the ideal fungicide spray window for minimising yield loss due to powdery mildew and maximise disease control. This meta-analysis also associates environmental variables to the first sighting of disease and can be used to inform growers when to begin scouting their crop for powdery mildew. The outcomes of this research can be used to refine decision support system (DSS) tools to boost accuracy and add functionality such as disease alerts.

### 2019-07-24 Presentations/2019_APPS_Meta-PowderyMildewMungbean_Abstract.Rmd
Author updates
Update 2019_APPS_Meta-PowderyMildewMungbean_Abstract.Rmd

@@
 ---
-title: Meta-analysis of the fungicide application for management of Powdery Mildew
+title: Meta-analysis of Fungicide Application Trials for the Management of Powdery Mildew
   in Mungbean.
-author: "P. Melloy"
+author: "P. Melloy; E. M. Del Ponte; C. T. Gray; A. H. Sparks;"
 date: "24/07/2019"
@@
 
-Commercially available Mungbean varieties lack adequate powdery mildew resistance to protect crop yields.
-Growers, therefore, manage severe epidemics by applying fungicide and sowing early in the growing season to avoid the cooler temperatures which are associated with Powdery Mildew infestations.
-Since 2001 twenty-four field trials have assessed the timing and frequency of fungicide application on Powdery Mildew disease incidence and Mungbean yield.
-Results from these trials have advised the best practice for managing the disease through fungicide application at first sign of disease, and a second spray two weeks later if necessary.
-However, the outcomes of these trials sometimes lacked certainty when analysed in isolation.
+Current commercially available mungbean varieties lack adequate powdery mildew (_Podosphaera xanthii_) resistance to protect crop yields in the presence of high disease pressure.
+Growers therefore manage severe epidemics by applying fungicide and sowing early in the growing season to avoid the cooler temperatures, which are associated with powdery mildew infestations.
+Since 2001 twenty-four field trials have assessed the timing and frequency of fungicide application on powdery mildew disease incidence and mungbean yield in the northern grains region.
+Results from these trials have advised the best practice for managing the disease is through a fungicide application at first sign of disease followed by a second spray two weeks later if necessary.
+However, the outcomes of these trials have occasionally lacked certainty when analysed in isolation.
 This meta-analysis aims to use the combined power of multiple studies to increase certainty for the ideal fungicide spray window for minimising yield loss due to powdery mildew and maximise disease control.
-This meta-analysis also associates environmental variables to the first sighting of disease and can be used to inform growers when to begin scouting their crop for powdery mildew.
-The outcomes of this research can be used to refine decision support system (DSS) tools to boost accuracy and add functionality such as disease alerts.
+This meta-analysis also associates environmental variables to the first sighting of disease that can be used to inform agronomists and growers when to begin scouting their crop for the first signs of powdery mildew.
+The outcomes of this research can be used to refine decision support system (DSS) tools like PowderyMildewMBM to boost accuracy and add functionality such as disease alerts.

### 2019-07-24 Presentations/2019_APPS_Meta-PowderyMildewMungbean_Abstract.Rmd
Add affiliations, still need Charles's

@@
   in Mungbean.
-author: "P. Melloy; E. M. Del Ponte; C. T. Gray; A. H. Sparks;"
-date: "24/07/2019"
-output: word_document
+author:
+  - P. Melloy:
+      email: paul.melloy@usq.edu.au
+      institute: USQ
+      correspondence: true
+  - name: E. M. Del Ponte
+    institute: UFVR
+  - name: C. T. Gray
+    institute: LaTrobe
+  - name: A. H. Sparks
+    institute: USQ
+institute:
+  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland 4350, Australia
+  - LaTrobe: Charles's affiliation here
+  - UFVR: Universidade Federal de Viçosa, Viçosa, Brazil
+date: "`r format(Sys.time(), '%d %B, %Y')`"
+output: 
+  bookdown::word_document2:
+    toc: no
+    pandoc_args:
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
 ---

### 2019-07-25 Presentations/2019_APPS_Meta-PowderyMildewMungbean_Abstract.Rmd
Add Charle's affiliation

--- 2019-07-24 Presentations/2019_APPS_Meta-PowderyMildewMungbean_Abstract.Rmd
@@
   in Mungbean.
-author: "P. Melloy; E. M. Del Ponte; C. T. Gray; A. H. Sparks;"
-date: "24/07/2019"
-output: word_document
+author:
+  - P. Melloy:
+      email: paul.melloy@usq.edu.au
+      institute: USQ
+      correspondence: true
+  - name: E. M. Del Ponte
+    institute: UFVR
+  - name: C. T. Gray
+    institute: LaTrobe
+  - name: A. H. Sparks
+    institute: USQ
+institute:
+  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland 4350, Australia
+  - LaTrobe: La Trobe University, Melbourne, Victoria 3086, Australia
+  - UFVR: Universidade Federal de Viçosa, Viçosa, Brazil
+date: "`r format(Sys.time(), '%d %B, %Y')`"
+output: 
+  bookdown::word_document2:
+    toc: no
+    pandoc_args:
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
 ---

### 2019-07-26 05_MetaAnalysis.Rmd
predict missing NAs model is not strong..

@@
 ---
+
+```{r MEsummary_Libraries}
+library(dplyr)
+library(openxlsx)
+library(kableExtra)
+library(ggplot2)
+library(leaflet)
+#source("./getPPD2.R")
+
+```
 
@@
 
+library(dplyr)
 #str(PM_MB_means)
@@
 ### Host genotypes
-Host genotype may have to be analysed to determine the effect.  
+Host genotype may need to be analysed to determine the effect.  
 ```{r Host_genotype}
@@
 
-PM_MB_means %>%
-   filter(Fungicide == "Tebeconazole") %>%
-   group_by(row_spacing,Trial_ref) %>%
-   summarise() %>%
-   count() %>%
-   rename(Treatments = n) %>%
-   kable()
-
 ```
@@
    - Crystal: Susceptible  
-   - Jade: Moderatly susceptible
+   - Jade: Moderatley susceptible
 
@@
 # I am guessing they represent prediction parameters for each "study" for each of the treatments, "control" and Tebeconazole"
-
 }
 
+# method as described by Emerson
+levels(factor(PM_MB_means$Y_error.type))
+
+PM_MB_train <- PM_MB_means %>%
+   filter(Y_error.type == "SamplingVariance")
+
+PM_MB_train$Trial_ref <- as.factor(PM_MB_train$Trial_ref)
+
+plot(PM_MB_train$Yield_error, log(as.numeric(PM_MB_train$`grain_yield.t.ha.`)))
+
+library(lme4)
+
+PM_MB_trianLMER <- lmer(log(as.numeric(`grain_yield.t.ha.`)) ~ Yield_error + 
+         (1|Trial_ref), data = PM_MB_train)
+
+paramA <- (summary(PM_MB_trianLMER)$coef)[2,1]
+InterC <- (summary(PM_MB_trianLMER)$coef)[1,1]
+
+ggplot(PM_MB_train, aes(y = log(as.numeric(`grain_yield.t.ha.`)), x = Yield_error, colour = Trial_ref))+
+   geom_point()+
+   geom_abline(intercept = InterC, slope = paramA)
+
+exp((log(as.numeric(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`)) * paramA)+InterC)
+# PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$Yield_error
+hist(PM_MB_train$Yield_error)
+hist(as.numeric(PM_MB_train$`grain_yield.t.ha.`))
+hist(log(as.numeric(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`)))
+
 ```

### 2019-07-26 Presentations/2019_APPS_Meta-PowderyMildewMungbean_Abstract.Rmd

--- 2019-07-24 Presentations/2019_APPS_Meta-PowderyMildewMungbean_Abstract.Rmd
@@
   in Mungbean.
-author: "P. Melloy; E. M. Del Ponte; C. T. Gray; A. H. Sparks;"
-date: "24/07/2019"
-output: word_document
+author:
+  - P. Melloy:
+      email: paul.melloy@usq.edu.au
+      institute: USQ
+      correspondence: true
+  - name: E. M. Del Ponte
+    institute: UFV
+  - name: C. T. Gray
+    institute: LaTrobe
+  - name: A. H. Sparks
+    institute: USQ
+institute:
+  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland 4350, Australia
+  - LaTrobe: La Trobe University, Melbourne, Victoria 3086, Australia
+  - UFV: Universidade Federal de Viçosa, Viçosa, Brazil
+date: "`r format(Sys.time(), '%d %B, %Y')`"
+output: 
+  bookdown::word_document2:
+    toc: no
+    pandoc_args:
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
 ---

### 2019-07-26 05_MetaAnalysis.Rmd
Corrections made to raw data file updated the imputation of yield_error for trials lacking error

@@
 PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv", stringsAsFactors = FALSE)
-
+PM_MB_means$grain_yield.t.ha. <- as.numeric(PM_MB_means$grain_yield.t.ha.)
 library(dplyr)
@@
           row_spacing == 0.75) %>%
-   group_by(Y_error.type) %>%
-   summarise(n = length(Y_error.type))
-
+   group_by(Trial_ref, Y_error.type) %>%
+   summarise(Tebe_Treatments = length(Y_error.type))
 ```
@@
 
-plot(PM_MB_train$Yield_error, log(as.numeric(PM_MB_train$`grain_yield.t.ha.`)))
+plot(PM_MB_train$Yield_error, log(PM_MB_train$`grain_yield.t.ha.`))
 
@@
 
-PM_MB_trianLMER <- lmer(log(as.numeric(`grain_yield.t.ha.`)) ~ Yield_error + 
+# Run a linear model with Yield error as a fixed effect predictor and Trial as a random intercept
+PM_MB_trianLMER <- lmer(log(`grain_yield.t.ha.`) ~ Yield_error + 
          (1|Trial_ref), data = PM_MB_train)
 
-paramA <- (summary(PM_MB_trianLMER)$coef)[2,1]
-InterC <- (summary(PM_MB_trianLMER)$coef)[1,1]
+paramA <- (summary(PM_MB_trianLMER)$coef)[2,1] # Extract the Slope to predict Yield error
+InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the intercept to predict Yield error
 
-ggplot(PM_MB_train, aes(y = log(as.numeric(`grain_yield.t.ha.`)), x = Yield_error, colour = Trial_ref))+
-   geom_point()+
-   geom_abline(intercept = InterC, slope = paramA)
+lmer.coef <- coef(PM_MB_trianLMER)
 
-exp((log(as.numeric(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`)) * paramA)+InterC)
+# plot of the mixed effect model, Black line shows the mean lmer regression line
+ggplot(PM_MB_train)+
+   geom_point(aes(y = log(`grain_yield.t.ha.`), x = Yield_error, colour = Trial_ref))+
+   geom_abline(intercept = c(InterC,lmer.coef$Trial_ref[,1]), 
+               slope = c(paramA,lmer.coef$Trial_ref[,2]),
+               size = 1.5,
+               colour = c("Black",hue_pal()(6)))
+   geom_point(aes(y = log(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`),
+                  x = rep(0,length(log(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`)))
+                  ),colour = "Black")
+
+library(scales)
+
+Sv <- (log(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`) - InterC)/ paramA
+
 # PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$Yield_error
 hist(PM_MB_train$Yield_error)
-hist(as.numeric(PM_MB_train$`grain_yield.t.ha.`))
+hist(PM_MB_train$`grain_yield.t.ha.`)
 hist(log(as.numeric(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`)))
 
+PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$Yield_error <- Sv
+PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$Y_error.type <- "SamplingVariance"
+
 ```
+
+Just for kicks lets look at the linear regression model as a Random effects model where `Yield_error` is set as a random slope to the random intercept `Trial_ref`.  
+The model fits better as shown by an anova comparison. But now to determine how to impute from this model ....
+```{r random_slope_model}
+
+# Run a linear model with Yield error as a fixed effect predictor and Trial as a random intercept
+PM_MB_trianLMERx <- lmer(log(`grain_yield.t.ha.`) ~ 1 + 
+         (Yield_error|Trial_ref), data = PM_MB_train)
+
+anova(PM_MB_trianLMER,PM_MB_trianLMERx) # random slope model signigicantly better
+
+summary(PM_MB_trianLMERx)
+
+InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the intercept to predict Yield error
+
+lmer.coef <- coef(PM_MB_trianLMERx)
+
+# plot of the mixed effect model, Black line shows the mean lmer regression line
+ggplot(PM_MB_train)+
+   geom_point(aes(y = log(`grain_yield.t.ha.`), x = Yield_error, colour = Trial_ref))+
+   geom_abline(intercept = lmer.coef$Trial_ref[,2], 
+               slope = lmer.coef$Trial_ref[,1],
+               size = 1.5,
+               colour = hue_pal()(6))
+
+```

### 2019-07-26 05_MetaAnalysis.Rmd
Loop to imput for both trials missing Yield_errors

@@
 ```{r}
-PM_MB_means %>%
+NATrials <- PM_MB_means %>%
    filter(Fungicide == "Tebeconazole",
@@
                colour = c("Black",hue_pal()(6)))
-   geom_point(aes(y = log(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`),
-                  x = rep(0,length(log(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`)))
-                  ),colour = "Black")
 
@@
 
-Sv <- (log(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`) - InterC)/ paramA
+for(i in NATrials$Trial_ref){
+Sv <- (log(PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.`) - InterC)/ paramA
 
-# PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$Yield_error
-hist(PM_MB_train$Yield_error)
-hist(PM_MB_train$`grain_yield.t.ha.`)
-hist(log(as.numeric(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`)))
-
-PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$Yield_error <- Sv
-PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$Y_error.type <- "SamplingVariance"
-
+PM_MB_means[PM_MB_means$Trial_ref == i,]$Yield_error <- Sv
+PM_MB_means[PM_MB_means$Trial_ref == i,]$Y_error.type <- "SamplingVariance"
+}
 ```

### 2019-08-01 03_Preliminary_analysis.Rmd
nl
Update after meeting with Adam

@@
    3) row spacing
-   4) Host cultivars
+   4) Host cultivars (probably is a covariate with season due to changing cultivars over time)
    5) Experiment location

### 2019-08-01 05_MetaAnalysis.Rmd
Update after meeting with Adam

@@
 PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv", stringsAsFactors = FALSE)
-PM_MB_means$grain_yield.t.ha. <- as.numeric(PM_MB_means$grain_yield.t.ha.)
-library(dplyr)
+PM_MB_means$grain_yield.t.ha. <- as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data
+
 #str(PM_MB_means)
@@
 
+# How many trials do we have if Tebe and Propi are pooled?
+
 ```
+Tebeconazole and propiconazole might be able to be pooled as a 'Triazole' fungicide treatment.
+Amistar is a combination of Azoxistrobin and Cyproconazole.
+Perhaps Amistar and 200 g/l Tebuconazole + 120 g/l Azoxystrobin might be able to be pooled given they both contain strobins and triazole, however they contain differening dose ratio (inverted).
+
+Perhaps best way forward is to do an analysis of only the Triazoles. Then do another including Amistar as a comparison.
 
@@
    kable()
+# why are there zeros
 ```
@@
    count() %>%
-   rename(Treatments = n) %>%
+   rename(Trials = n) %>%
    kable()
@@
 ```
+Were there any statistical diference between all row spacing or only some?  
+Can we pool certain row spacings that have no significant difference?
 
@@
 
-for(i in PM_MB_means$Trial_ref){
-
-log(V)[i] = a + b * log(
-   mean(subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "control"),
-        subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "Tebeconazole")))
-# need to know what parameters a and b are here
-# I am guessing they represent prediction parameters for each "study" for each of the treatments, "control" and Tebeconazole"
-}
+# for(i in PM_MB_means$Trial_ref){
+# 
+# log(V)[i] = a + b * log(
+#    mean(subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "control"),
+#         subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "Tebeconazole")))
+# # need to know what parameters a and b are here
+# # I am guessing they represent prediction parameters for each "study" for each of the treatments, "control" and Tebeconazole"
+# }
 
@@
 library(lme4)
+library(scales)
+# Run a linear model with Yield error as a fixed effect predictor and Trial as a random intercept
+PM_MB_trianLMER <- lmer(log(Yield_error) ~ `grain_yield.t.ha.`+ 
+         (1|Trial_ref), data = PM_MB_train)
 
-# Run a linear model with Yield error as a fixed effect predictor and Trial as a random intercept
-PM_MB_trianLMER <- lmer(log(`grain_yield.t.ha.`) ~ Yield_error + 
-         (1|Trial_ref), data = PM_MB_train)
+summary(PM_MB_trianLMER)
 
@@
 
-library(scales)
-
 for(i in NATrials$Trial_ref){
@@
 PM_MB_means[PM_MB_means$Trial_ref == i,]$Y_error.type <- "SamplingVariance"
+print(Sv)
+
 }

### 2019-08-01 05_MetaAnalysis.Rmd
Corrected the yeild error prediction models to have yield error as the response. Also investigated a fully random model

@@
 library(scales)
-# Run a linear model with Yield error as a fixed effect predictor and Trial as a random intercept
-PM_MB_trianLMER <- lmer(log(Yield_error) ~ `grain_yield.t.ha.`+ 
+# Run a linear model with Grain_yield as a fixed effect predictor and Trial as a random intercept
+PM_MB_trianLMER <- lmer(Yield_error ~ `grain_yield.t.ha.`+ 
          (1|Trial_ref), data = PM_MB_train)
-
 summary(PM_MB_trianLMER)
 
-paramA <- (summary(PM_MB_trianLMER)$coef)[2,1] # Extract the Slope to predict Yield error
-InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the intercept to predict Yield error
+# grain yeild is a significant predictor for yeild error (t value = -2.757)
+# does log transformation improve the model
 
-lmer.coef <- coef(PM_MB_trianLMER)
+PM_MB_trianLMER.1 <- lmer(log(Yield_error) ~ `grain_yield.t.ha.`+ 
+         (1|Trial_ref), data = PM_MB_train)
+summary(PM_MB_trianLMER.1) # grain yeild is not a significant predictor of log(yeild error)
+anova(PM_MB_trianLMER, PM_MB_trianLMER.1) # no significant difference between the models
+
+PM_MB_trianLMER.2 <- lmer(Yield_error ~ log(`grain_yield.t.ha.`)+ 
+         (1|Trial_ref), data = PM_MB_train)
+summary(PM_MB_trianLMER.2) # log(grain yeild) is a significant predictor of yeild error
+anova(PM_MB_trianLMER, PM_MB_trianLMER.2) # no significant difference between the models
+
+#log transforming the response or predictor variables did not improve the model therefore I will leave it untransformed
+# I will be using the first model PM_MB_trianLMER for further analyses beyond this point
+
+paramA <- (summary(PM_MB_trianLMER)$coef)[2,1] # Extract the overall mean Slope to predict Yield error
+InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the overall mean intercept to predict Yield error
+
+lmer.coef <- coef(PM_MB_trianLMER) # extracting the mean random intercept for each of trial variables
 
@@
 ggplot(PM_MB_train)+
-   geom_point(aes(y = log(`grain_yield.t.ha.`), x = Yield_error, colour = Trial_ref))+
+   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
    geom_abline(intercept = c(InterC,lmer.coef$Trial_ref[,1]), 
@@
                size = 1.5,
-               colour = c("Black",hue_pal()(6)))
+               colour = c("Black",hue_pal()(6)))+
+   coord_cartesian(xlim = c(0.8, 1.2))
 
 for(i in NATrials$Trial_ref){
-Sv <- (log(PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.`) - InterC)/ paramA
+#Sv <- (log(PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped
+
+Sv <- (PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.` * paramA) + InterC
 
@@
 PM_MB_means[PM_MB_means$Trial_ref == i,]$Y_error.type <- "SamplingVariance"
-print(Sv)
 
@@
 
-Just for kicks lets look at the linear regression model as a Random effects model where `Yield_error` is set as a random slope to the random intercept `Trial_ref`.  
+Just for kicks lets look at the linear regression model as a Random effects model where `grain_yield.t.ha.` is set as a random slope to the random intercept `Trial_ref`.  
 The model fits better as shown by an anova comparison. But now to determine how to impute from this model ....
@@
 # Run a linear model with Yield error as a fixed effect predictor and Trial as a random intercept
-PM_MB_trianLMERx <- lmer(log(`grain_yield.t.ha.`) ~ 1 + 
-         (Yield_error|Trial_ref), data = PM_MB_train)
+PM_MB_trianLMERx <- lmer(Yield_error ~ 1 + 
+         (`grain_yield.t.ha.`|Trial_ref), data = PM_MB_train)
 
-anova(PM_MB_trianLMER,PM_MB_trianLMERx) # random slope model signigicantly better
+anova(PM_MB_trianLMER,PM_MB_trianLMERx) # random slope model significantly better # P = 0.00378
 
@@
 
-InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the intercept to predict Yield error
+InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the overall mean intercept
 
-lmer.coef <- coef(PM_MB_trianLMERx)
+lmer.coefx <- coef(PM_MB_trianLMERx)
 
@@
 ggplot(PM_MB_train)+
-   geom_point(aes(y = log(`grain_yield.t.ha.`), x = Yield_error, colour = Trial_ref))+
-   geom_abline(intercept = lmer.coef$Trial_ref[,2], 
-               slope = lmer.coef$Trial_ref[,1],
+   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
+   geom_abline(intercept = lmer.coefx$Trial_ref[,2], 
+               slope = lmer.coefx$Trial_ref[,1],
                size = 1.5,
-               colour = hue_pal()(6))
+               colour = hue_pal()(6))+
+   coord_cartesian(xlim = c(0, 3))
 
 ```
+
+What is interesting about this model is the slopes all converge and pass through a specific point.
+We can use this to predict the slope of the trials we don't know the specific slope for and get a better prediction of the errors.
+
+```{r imputing_from_randomModel}
+ggplot(PM_MB_train)+
+   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
+   geom_abline(intercept = lmer.coefx$Trial_ref[,2], 
+               slope = lmer.coefx$Trial_ref[,1],
+               size = 1.5,
+               colour = hue_pal()(6))+
+   coord_cartesian(xlim = c(2.85, 2.875), ylim = c(0.0048,0.0049))
+
+# let us find the value of this point
+# what are the slopes and intercepts for each random grouping factor (Trial_ref)
+randomS_coefs <- lmer.coefx$Trial_ref
+
+# lets write a funcion to generate a sequence of predicted Y (yield error) values
+slope_generator <- function(slope,intercept, x_minimum = 0.8, x_maximum = 1.2, increment = 0.00000001){
+   Xi <- seq(from = x_minimum, to = x_maximum, by = increment)
+   (Xi * slope) + intercept
+}
+
+# generate a vector of predicted values for each of the trial slopes, returned as a matrix
+tmp2 <- apply(randomS_coefs,1,FUN = function(x) {
+   slope_generator(slope = x[1], intercept = x[2],x_minimum = 2.86135, x_maximum = 2.8614)
+                      })
+head(tmp2)
+
+# find which X predictor gives the lowest variation between trials and therefore the closest to the point at which the slopes converge
+tmp3 <- apply(tmp2,1,sd)
+plot(tmp3)
+min(tmp3)
+x_3252 <- which(tmp3 == min(tmp3))
+
+# zooming in on the X predictor by increasing resolution
+seq(from = 2.85,to = 2.875, by =0.0001)[115]
+seq(from = 2.85,to = 2.875, by =0.00001)[1139]
+x_point <- seq(from = 2.86135,to = 2.8614, by =0.00000001)[x_3252]
+
+# predict the y (yeild error) at the x predictor (grain.yield) for each trial group
+tmp4 <- apply(randomS_coefs,1,FUN = function(x){
+   (x_point * x[1]) + x[2]
+})
+
+# they are all the same value but lets take the mean to be more precise
+y_point <- mean(tmp4)
+
+# here is my 'good-enough' prediction of the convergence point
+common_S_coordinate <- c(x_point, y_point)
+
+```

### 2019-08-05 03_Preliminary_analysis.Rmd
updating preliminary analysis. Removing multiple variations of sulphur treatments

@@
 
+# Rewrite all variations of sulphur treatments as just sulphur
+PM_MB_means$Fungicide[PM_MB_means$Fungicide == "Sulphur"| PM_MB_means$Fungicide == "Sulphur (SC)" | PM_MB_means$Fungicide == "Sulphur (Ultra SC)" | PM_MB_means$Fungicide == "Sulphur (WP)"] <- "Sulphur"
+```
+
+```{r row_spacing}
+
 # Which row spacing leads to the higher disease severity
@@
 
-### Yield saved 
-**Number of fungicide applications**
-The following density plots show mean yield saved in relation to how many sprays were applied.
-
-```{r PA_Yield, warning=FALSE, echo=FALSE}
-
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PMy <- PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-   group_by(total_Fungicide) %>%
-   summarise(n = length(yield_gain),
-             lower_2.5 = quantile(yield_gain, na.rm = T, c(0.025)),
-             median = median(yield_gain, na.rm = T),
-             mean = mean(yield_gain, na.rm = T),
-             upper_97.5 = quantile(yield_gain, na.rm = T, c(0.975)))
-
-# Density plot of Number of fungicide applications and the resulting yeild saved (as a proportion)
-ggplot(subset(PM_MB_means,Fungicide != "control"), aes(yield_gain))+
-   geom_density(aes(group = factor(total_Fungicide), fill = factor(total_Fungicide)), alpha = 0.6)+
-   geom_vline(xintercept = 0, size =1)+
-   labs(x = "Grain yeild saved (t/ha)",
-   title = "Density plot of grain yield saved from differing numbers of fungicide applications")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(data = quant_PMy, aes(xintercept = lower_2.5, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   geom_vline(data = quant_PMy, aes(xintercept = upper_97.5, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   guides(colour = guide_legend(title="Upper (97.5%) and \nLower (2.5%) percentiles"),
-          fill=guide_legend(title="Number of \nFungicide applications"))+
-   scale_x_continuous(limits = c(-0.3,0.8))
-
-kable(quant_PMy,
-   caption = "Yeild gain for each number of fungicide applications") %>%
-   kable_styling(fixed_thead = T, full_width = T)
-
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PM <- PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-   group_by(total_Fungicide) %>%
-   summarise(lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
-             median = median(prop_YG, na.rm = T),
-             mean = mean(prop_YG, na.rm = T),
-             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975)))
-
-# Density plot of proportion of yield saved
-ggplot(subset(PM_MB_means,Fungicide != "control"), aes(prop_YG))+
-   geom_density(aes(group = factor(total_Fungicide), fill = factor(total_Fungicide)), alpha = 0.6)+
-   geom_vline(xintercept = 0, size =1)+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Density plot of the grain yield proportion saved \n by the number of fungicide applications")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(data = quant_PM, aes(xintercept = lower_2.5, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   geom_vline(data = quant_PM, aes(xintercept = upper_97.5, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   guides(colour = guide_legend(title="Upper (97.5%) and \nLower (2.5%) percentiles"),
-          fill=guide_legend(title="Number of \nFungicide applications"))+
-   scale_x_continuous(limits = c(-0.3,0.55))
-
-kable(quant_PM,
-   caption = "Proportion of yeild gain for each number of fungicide applications") %>%
-   kable_styling(fixed_thead = T, full_width = T)   
-#knitr::kable(quant_PM, 
-#             col.names = c("Number of sprays", "2.5 percentile", "97.5 percentile"))
-             #caption = "The 'upper' and 'lower' percentiles for proportion of yeild saved against the number of Fungicide sprays in a season.
-Data from 2011-2017 mungbean experimental means.
-Data ignores factors such as fungicide, dose, season or location of experiment")
-```
-
-\n\n\n\n\n\n\n
-
-#### Timing of Fungicide application
-The following density plots show mean yield saved (t/Ha) or proportion yield saved in relation to when the first fungicide spray was applied in relation to when powdery mildew was first seen in the mungbean crop.
-
-```{r echo = FALSE, message=FALSE, warning=FALSE}
-# removing 2017 and control data
-# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
-PM_MB_means1 <- PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-#   filter(total_Fungicide ==1) %>%
-   mutate(days_from_1st = as.numeric(
-      as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") -
-         as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")))
-
-# What range of 
-unique(PM_MB_means1$days_from_1st)
-PM_MB_means1 %>%
-   group_by(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))) %>%
+#### Effect of Fungicide 
+**on proportional yield gain with repect to time of application**
+First lets look at the quantiles for each fungicide irrespective of other factors.
+We will focus on proportional yield gain, compared to no treatment control, as this should partially correct for some spatial and seasonal effects.  
+```{r}
+PM_MB_means %>%
+   group_by(Fungicide) %>%
    summarise(n = length(prop_YG),
@@
              upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
-   kable(caption = "Difference in days between first sign of disease and first fungicide application and the effect on proportion of yield gain") %>%
+   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
+   arrange(desc(median)) %>%
+   kable(caption = "Fungicide effect on proportion of yield gain") %>%
    kable_styling(fixed_thead = T, full_width = T)
 
-ggplot(PM_MB_means1, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))), alpha = 0.5)+
+# plot table as a density plot
+
+ggplot(PM_MB_means, aes(prop_YG))+
+   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))), alpha = 0.5)+
    geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))~.)+
+   facet_grid(cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))~.)+
    #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
    labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
+   title = "Grain yield proportion saved grouped by\nwhen the first Sulphur fungicide application was made\nrelative to when Powdery Mildew was first seen")+
    theme(panel.grid.major = element_line(colour = "grey80"),
@@
    guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.2,0.55))
+   scale_x_continuous(limits = c(-0.3,0.6))
+
 ```
@@
 ```{r}
-# removing 2017 and control data
-# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
-PM_MB_means1 <- PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-   filter(Year != 2017) %>%
-#   filter(total_Fungicide ==1) %>%
-   mutate(days_from_1st = as.numeric(as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") - 
-                                        as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")))
-
-days_from_fungicid <- function(FSD,F1,F2,F3){
-   dF1 <- as.numeric(as.Date(F1) - as.Date(FSD))
-   dF2 <- as.numeric(as.Date(F2) - as.Date(FSD))
-   dF3 <- as.numeric(as.Date(F3) - as.Date(FSD))
-   if(is.na(dF1)){
-      return(NA)} else{
-   if(between(dF1,lower = -1, upper = 1000)){
-      return(dF1)}else{
-   if(is.na(dF2)){
-      return(dF1)}else{
-      if(between(dF2,lower = dF1, upper = -0.1)){
-            return(dF2)} else{
-               return(dF3)}}
-            }}
-}
-vec1<- vector()
-for(i in 1:dim(PM_MB_means1)[1]){
-   dF1 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_1, format = "%d/%m/%Y")[i] -
-                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
-   dF2 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_2, format = "%d/%m/%Y")[i] -
-                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
-   dF3 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_3, format = "%d/%m/%Y")[i] -
-                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
-   if(is.na(dF1)){
-      vec1 <- c(vec1,dF1)} else{
-         if(between(as.numeric(dF1),-1, 1000)){
-            vec1 <- c(vec1,dF1)}else{
-               if(is.na(dF2)){
-                  vec1 <- c(vec1,dF1)}else{
-                     if(between(as.numeric(dF2),as.numeric(dF1), -1.1)){
-            vec1 <- c(vec1,dF2)} else{
-               if(is.na(dF3)){
-                  vec1 <- c(vec1,dF2)}else{
-               if(as.numeric(dF3)>=0){
-                  vec1 <- c(vec1,dF2)}else{
-                     vec1 <- c(vec1,dF3)}}}}
-            }}
-}
-PM_MB_means1$spray_diff <- vec1 # gives the closest fungicide application date to the first sign of disease
-#PM_MB_means1$days_from_1st
-
-```
-
-#### Effect of Fungicide 
-**on proportional yield gain with repect to time of application**
-##### Tebeconazole
-```{r}
-PM_MB_means1 %>%
-   group_by(Fungicide) %>%
-   filter(n() >= 5) %>% # remove any fungicide groups with less than 5 observations
-   summarise(n = length(prop_YG),
-             lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
-             median = median(prop_YG, na.rm = T),
-             mean = mean(prop_YG, na.rm = T),
-             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
-   kable(caption = "Fungicide effect on proportion of yield gain") %>%
-   kable_styling(fixed_thead = T, full_width = T)
 
@@
 It seems the calculation of spray diff does not elucidate any differences between application dates.
+
+### Yield saved 
+**Number of fungicide applications**
+The following density plots show mean yield saved in relation to how many sprays were applied.
+
+```{r PA_Yield, warning=FALSE, echo=FALSE}
+
+# Making a table of showing the upper and lower percentiles (95%)
+quant_PMy <- PM_MB_means %>%
+   filter(Fungicide != "control") %>%
+   group_by(total_Fungicide) %>%
+   summarise(n = length(yield_gain),
+             lower_2.5 = quantile(yield_gain, na.rm = T, c(0.025)),
+             median = median(yield_gain, na.rm = T),
+             mean = mean(yield_gain, na.rm = T),
+             upper_97.5 = quantile(yield_gain, na.rm = T, c(0.975)))
+
+# Density plot of Number of fungicide applications and the resulting yeild saved (as a proportion)
+ggplot(subset(PM_MB_means,Fungicide != "control"), aes(yield_gain))+
+   geom_density(aes(group = factor(total_Fungicide), fill = factor(total_Fungicide)), alpha = 0.6)+
+   geom_vline(xintercept = 0, size =1)+
+   labs(x = "Grain yeild saved (t/ha)",
+   title = "Density plot of grain yield saved from differing numbers of fungicide applications")+
+   theme(panel.grid.major = element_line(colour = "grey80"),
+         panel.grid.minor = element_line(colour = "grey50"),
+         panel.background = element_rect(fill = NA))+
+   geom_vline(data = quant_PMy, aes(xintercept = lower_2.5, 
+               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
+   geom_vline(data = quant_PMy, aes(xintercept = upper_97.5, 
+               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
+   guides(colour = guide_legend(title="Upper (97.5%) and \nLower (2.5%) percentiles"),
+          fill=guide_legend(title="Number of \nFungicide applications"))+
+   scale_x_continuous(limits = c(-0.3,0.8))
+
+kable(quant_PMy,
+   caption = "Yeild gain for each number of fungicide applications") %>%
+   kable_styling(fixed_thead = T, full_width = T)
+
+# Making a table of showing the upper and lower percentiles (95%)
+quant_PM <- PM_MB_means %>%
+   filter(Fungicide != "control") %>%
+   group_by(total_Fungicide) %>%
+   summarise(lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
+             median = median(prop_YG, na.rm = T),
+             mean = mean(prop_YG, na.rm = T),
+             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975)))
+
+# Density plot of proportion of yield saved
+ggplot(subset(PM_MB_means,Fungicide != "control"), aes(prop_YG))+
+   geom_density(aes(group = factor(total_Fungicide), fill = factor(total_Fungicide)), alpha = 0.6)+
+   geom_vline(xintercept = 0, size =1)+
+   labs(x = "Proportion of grain yeild saved",
+   title = "Density plot of the grain yield proportion saved \n by the number of fungicide applications")+
+   theme(panel.grid.major = element_line(colour = "grey80"),
+         panel.grid.minor = element_line(colour = "grey50"),
+         panel.background = element_rect(fill = NA))+
+   geom_vline(data = quant_PM, aes(xintercept = lower_2.5, 
+               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
+   geom_vline(data = quant_PM, aes(xintercept = upper_97.5, 
+               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
+   guides(colour = guide_legend(title="Upper (97.5%) and \nLower (2.5%) percentiles"),
+          fill=guide_legend(title="Number of \nFungicide applications"))+
+   scale_x_continuous(limits = c(-0.3,0.55))
+
+kable(quant_PM,
+   caption = "Proportion of yeild gain for each number of fungicide applications") %>%
+   kable_styling(fixed_thead = T, full_width = T)   
+#knitr::kable(quant_PM, 
+#             col.names = c("Number of sprays", "2.5 percentile", "97.5 percentile"))
+             #caption = "The 'upper' and 'lower' percentiles for proportion of yeild saved against the number of Fungicide sprays in a season.
+Data from 2011-2017 mungbean experimental means.
+Data ignores factors such as fungicide, dose, season or location of experiment")
+```
+
+\n\n\n\n\n\n\n
+
+#### Timing of Fungicide application
+The following density plots show mean yield saved (t/Ha) or proportion yield saved in relation to when the first fungicide spray was applied in relation to when powdery mildew was first seen in the mungbean crop.
+
+```{r echo = FALSE, message=FALSE, warning=FALSE}
+PM_MB_means %>%
+   filter(Fungicide != "control") %>%
+#   filter(total_Fungicide ==1) %>%
+   mutate(days_from_1st = as.numeric(
+      as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") -
+         as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")))
+
+# What range of 
+unique(PM_MB_means1$days_from_1st)
+PM_MB_means1 %>%
+   group_by(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))) %>%
+   summarise(n = length(prop_YG),
+             lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
+             median = median(prop_YG, na.rm = T),
+             mean = mean(prop_YG, na.rm = T),
+             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
+   kable(caption = "Difference in days between first sign of disease and first fungicide application and the effect on proportion of yield gain") %>%
+   kable_styling(fixed_thead = T, full_width = T)
+
+ggplot(PM_MB_means1, aes(prop_YG))+
+   geom_density(aes(fill = cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))), alpha = 0.5)+
+   geom_vline(aes(xintercept = 0), size =0.5)+
+   facet_grid(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))~.)+
+   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
+   labs(x = "Proportion of grain yeild saved",
+   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
+   theme(panel.grid.major = element_line(colour = "grey80"),
+         panel.grid.minor = element_line(colour = "grey50"),
+         panel.background = element_rect(fill = NA))+
+   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
+   scale_x_continuous(limits = c(-0.2,0.55))
+```
+
+```{r}
+# removing 2017 and control data
+# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
+PM_MB_means1 <- PM_MB_means %>%
+   filter(Fungicide != "control") %>%
+   filter(Year != 2017) %>%
+#   filter(total_Fungicide ==1) %>%
+   mutate(days_from_1st = as.numeric(as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") - 
+                                        as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")))
+
+days_from_fungicid <- function(FSD,F1,F2,F3){
+   dF1 <- as.numeric(as.Date(F1) - as.Date(FSD))
+   dF2 <- as.numeric(as.Date(F2) - as.Date(FSD))
+   dF3 <- as.numeric(as.Date(F3) - as.Date(FSD))
+   if(is.na(dF1)){
+      return(NA)} else{
+   if(between(dF1,lower = -1, upper = 1000)){
+      return(dF1)}else{
+   if(is.na(dF2)){
+      return(dF1)}else{
+      if(between(dF2,lower = dF1, upper = -0.1)){
+            return(dF2)} else{
+               return(dF3)}}
+            }}
+}
+vec1<- vector()
+for(i in 1:dim(PM_MB_means1)[1]){
+   dF1 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_1, format = "%d/%m/%Y")[i] -
+                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
+   dF2 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_2, format = "%d/%m/%Y")[i] -
+                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
+   dF3 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_3, format = "%d/%m/%Y")[i] -
+                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
+   if(is.na(dF1)){
+      vec1 <- c(vec1,dF1)} else{
+         if(between(as.numeric(dF1),-1, 1000)){
+            vec1 <- c(vec1,dF1)}else{
+               if(is.na(dF2)){
+                  vec1 <- c(vec1,dF1)}else{
+                     if(between(as.numeric(dF2),as.numeric(dF1), -1.1)){
+            vec1 <- c(vec1,dF2)} else{
+               if(is.na(dF3)){
+                  vec1 <- c(vec1,dF2)}else{
+               if(as.numeric(dF3)>=0){
+                  vec1 <- c(vec1,dF2)}else{
+                     vec1 <- c(vec1,dF3)}}}}
+            }}
+}
+PM_MB_means1$spray_diff <- vec1 # gives the closest fungicide application date to the first sign of disease
+#PM_MB_means1$days_from_1st
+
+```

### 2019-08-05 05_MetaAnalysis.Rmd
more tinkering

@@
                size = 1.5,
-               colour = c("Black",hue_pal()(6)))+
+               colour = c("Black",hue_pal()(5)))
    coord_cartesian(xlim = c(0.8, 1.2))
@@
                size = 1.5,
-               colour = hue_pal()(6))+
+               colour = hue_pal()(5))+
    coord_cartesian(xlim = c(0, 3))
@@
 What is interesting about this model is the slopes all converge and pass through a specific point.
-We can use this to predict the slope of the trials we don't know the specific slope for and get a better prediction of the errors.
+Perhaps can use this to predict the slope of the trials we don't know the specific slope for and get a better prediction of the errors.
 
@@
 ```
+After much deliberation I don't think this is possible to use the model with grain yield/ha as a random slope.
+Even though we know the grain yields and the mean in the grain yeilds we still can't predict the effect of the random intercept trial on the yield error.
+I also re-ran the model without including the trial which we used LSD to interprete the sampling variance and the model lost a lot of significance.

### 2019-08-06 Cleaning historical data.R
Added code used to generate 2019 means from raw data

@@ -507,6 +507,61 @@ write.csv(dat5,"C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/Past trials/
 
 
 
+# ________________________________________________________________
+# _____________         Hermitage 2019           ________________
+# ________________________________________________________________
+library(data.table)
+
+
+PM_MB_19 <- read.xlsx("C:/Users/U8011054/USQ/SCP - Documents/DAW1810/Mungbean/1901_Herm_PM/1901 Mungbean powdery mildew disease and yeild data.xlsx",
+                     startRow = 2,
+                     cols = c(1:21))
+
+PM_MB_19 <- subset(PM_MB_19, Harvest.Plot.Number != 5)
+PM_MB_19 <- subset(PM_MB_19, Harvest.Plot.Number != 6)
+
+
+
+PM19_means <- PM_MB_19 %>%
+   group_by(TOS.NUM, `T/ment.NUM`)%>%
+   summarise(Incidence190423 = mean(`23-4-19.Incedence`, na.rm = TRUE),
+             Inc.sd.190423 = sd(`23-4-19.Incedence`, na.rm = TRUE),
+             Inc.error.190423 = "Stdev",
+             Incidence190501 = mean(`1-5-19.Incedence`, na.rm = TRUE),
+             Inc.sd.190501 = sd(`1-5-19.Incedence`, na.rm = TRUE),
+             Inc.error.190501 = "Stdev",
+             Plot_length = mean(Plot.Lengths, na.rm = TRUE),
+             Yield = mean(Yeild, na.rm = TRUE),
+             Yield_error = sd(Yeild, na.rm = TRUE),
+             AUDPC = mean(AUDPC, na.rm = TRUE)
+   )
+
+library(agricolae)
+?audpc
+colnames(PM_MB_19)
+
+audpc(PM_MB_19[PM_MB_19$TOS.NUM == 2 ,c(5,7,9)],c(70,78,86))
+
+PM_MB_19$AUDPC <- NA
+PM_MB_19[PM_MB_19$TOS.NUM == 1 , "AUDPC"] <- audpc(PM_MB_19[PM_MB_19$TOS.NUM == 1 ,c(5,7)],c(70,78))
[…]

### 2019-08-06 03_Preliminary_analysis.Rmd
Added investigation into the role of fungicide on proportion of yield gain

@@
 We will focus on proportional yield gain, compared to no treatment control, as this should partially correct for some spatial and seasonal effects.  
-```{r}
+```{r fungicide_proportion_yield}
 PM_MB_means %>%
@@
 
-# plot table as a density plot
+# plot table as a box plot
 
-ggplot(PM_MB_means, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))~.)+
+ggplot(PM_MB_means, aes(y = prop_YG, x = Fungicide))+
+   geom_boxplot()+
+   geom_hline(aes(yintercept = 0), size =0.5)+
    #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
    labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first Sulphur fungicide application was made\nrelative to when Powdery Mildew was first seen")+
+   title = "Grain yield proportion saved grouped by\nFungicide type")+
    theme(panel.grid.major = element_line(colour = "grey80"),
@@
          panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.3,0.6))
+   guides(fill=guide_legend(title="Fungicide"))+
+   coord_cartesian()+
+   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))
+   #scale_x_continuous(limits = c(-0.3,0.6))
+
+```
+There was some hope groups of fungicide could be combined, ie Propiconazole and Tebeconazole, however it seems that they have different efficacies.
+Let us look to see if there is anything skewing the above.
+
+```{r Fungicide_x_nSprays}
+PM_MB_means %>%
+   group_by(Fungicide, total_Fungicide) %>%
+   summarise(n = length(prop_YG),
+             lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
+             median = median(prop_YG, na.rm = T),
+             mean = mean(prop_YG, na.rm = T),
+             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
+   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
+   arrange(desc(median)) %>%
+   kable(caption = "Fungicide effect on proportion of yield gain") %>%
+   kable_styling(fixed_thead = T, full_width = T)
+
+PM_MB_means %>%
+   filter(total_Fungicide ==1 |total_Fungicide ==2 ) %>%
+ggplot(aes(y = prop_YG, x = Fungicide))+
+   facet_grid(cols = vars(total_Fungicide))+
+   geom_boxplot(aes(fill = Fungicide, alpha = 0.5))+
+   geom_hline(aes(yintercept = 0), size =0.5)+
+   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
+   labs(x = "Proportion of grain yeild saved",
+   title = "Grain yield proportion saved grouped by\nFungicide type")+
+   theme(panel.grid.major = element_line(colour = "grey80"),
+         panel.grid.minor = element_line(colour = "grey50"),
+         panel.background = element_rect(fill = NA))+
+   guides(fill=guide_legend(title="Fungicide"))+
+   coord_cartesian()+
+   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))
+   #scale_x_continuous(limits = c(-0.3,0.6))
+
+```
+
+Lets run this by a quick linear mixed effect model
+```{r Fungicide_lmer}
+levels(PM_MB_means$Fungicide)
+
+PM_MB_means$Fungicide <- factor(PM_MB_means$Fungicide, levels = c("control","propiconazole","Tebeconazole",
+                                                        "Amistar",
+                                                        "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin", "Carbendazim",
+                                                        "Benomyl",  
+                                                         "Pyrazophos","Acibenzolar-S-Methyl",
+                                                        "Sulphur", "Sulphur (SC)","Sulphur (Ultra SC)","Sulphur (WP)"
+                                                        ))
+
+PM_MB_lmer.1 <- lmer(prop_YG ~ Fungicide + as.factor(total_Fungicide) + row_spacing + (1|Trial_ref), 
+     data = subset(PM_MB_means, total_Fungicide == 1 | total_Fungicide == 2))
+
+summary(PM_MB_lmer.1)
+
+```
+There is no significant difference between Fungicides, except for Sulphur which is significantly less effective than propiconazole.
+Propiconazole, on average, out performs other fungicides when mitigating yield loss.
+
+How many trials contain all of the most studied fungicides
+```{r}
+Tebe_trials <- unique(PM_MB_means[PM_MB_means$Fungicide == "Tebeconazole",]$Trial_ref)
+Propi_trials <- unique(PM_MB_means[PM_MB_means$Fungicide == "propiconazole",]$Trial_ref)
+Amistar_trials <- unique(PM_MB_means[PM_MB_means$Fungicide == "Amistar",]$Trial_ref)
+
+intersect(
+   intersect(Tebe_trials,Propi_trials)
+   ,Amistar_trials)
 

### 2019-08-07 05_MetaAnalysis.Rmd
corrected conversion equation for stdev to sample variance

@@
 # Equation to convert standard deviation to Sampling Variance 
-   Sv[j] = (PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error[j]/
-               sqrt(PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Replicates[j]))^2
+   Sv[j] = (PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error[j])^2
    }

### 2019-08-07 05_MetaAnalysis.Rmd
updated lmer analysis from changes stdev calculation

@@
 
-# grain yeild is a significant predictor for yeild error (t value = -2.757)
+# grain yeild is not a significant predictor for yeild error (t value = -1.613)
+#  And the variance decreases as the mean increases, counter to expectation
 # does log transformation improve the model
@@
 anova(PM_MB_trianLMER, PM_MB_trianLMER.2) # no significant difference between the models
+
+PM_MB_trianLMER.3 <- lmer(log(Yield_error) ~ log(`grain_yield.t.ha.`)+ 
+         (1|Trial_ref), data = PM_MB_train)
+summary(PM_MB_trianLMER.3) # log(grain yeild) is a significant predictor of log(yeild error)
+anova(PM_MB_trianLMER, PM_MB_trianLMER.3) # no significant difference between the models
 
@@
                slope = c(paramA,lmer.coef$Trial_ref[,2]),
-               size = 1.5,
-               colour = c("Black",hue_pal()(5)))
+               size = 1,
+               colour = c("Black",hue_pal()(6)))
    coord_cartesian(xlim = c(0.8, 1.2))
@@
 
-anova(PM_MB_trianLMER,PM_MB_trianLMERx) # random slope model significantly better # P = 0.00378
+anova(PM_MB_trianLMER,PM_MB_trianLMERx) # random slope model NOT significantly better # P = 0.6677
 
@@
                size = 1.5,
-               colour = hue_pal()(5))+
+               colour = hue_pal()(6))+
    coord_cartesian(xlim = c(0, 3))

### 2019-08-07 05_MetaAnalysis.Rmd
Change lmer analysis to predict errors to include all trials with standard deviation data Delete random slope imputing chunk

@@
 
+## Investigating data and the number of factors represented in each Trial
+
+### Fungicides
 When investigating previous studies into Powdery Mildew Fungicide efficacy on Mungbean `r length(unique(PM_MB_means$Trial_ref))` trials were found, however only eleven Tebeconazol were used for the following meta-analysis, followed by the next common Fungicide Propiconazole.
@@
 
-### standardising the type of variance
+## Standardising the type of variance
 
@@
 Trials <- PM_MB_means %>%
-   filter(Fungicide == "Tebeconazole",
-          row_spacing == 0.75,
+   filter(
+      #Fungicide == "Tebeconazole",
+       #   row_spacing == 0.75,
           Y_error.type == "lsd (P=0.05)")%>%
@@
 Trials <- PM_MB_means %>%
-   filter(Fungicide == "Tebeconazole",
-          row_spacing == 0.75,
+   filter(
+         #Fungicide == "Tebeconazole",
+         #row_spacing == 0.75,
           Y_error.type == "stdev")%>%
@@
 ```{r na2Sampling_variance}
+library(lme4)
+library(scales)
 
@@
 # method as described by Emerson
-levels(factor(PM_MB_means$Y_error.type))
-
 PM_MB_train <- PM_MB_means %>%
@@
 
-library(lme4)
-library(scales)
 # Run a linear model with Grain_yield as a fixed effect predictor and Trial as a random intercept
@@
 
+# Lets try with Fungicide as a fixed effect
+PM_MB_trianLMER.4 <- lmer(Yield_error ~ `grain_yield.t.ha.`+ as.factor(Fungicide) + 
+         (1|Trial_ref), data = PM_MB_train)
+summary(PM_MB_trianLMER.4)
+anova(PM_MB_trianLMER, PM_MB_trianLMER.4) # no significant difference between the models
+
 #log transforming the response or predictor variables did not improve the model therefore I will leave it untransformed
@@
 lmer.coef <- coef(PM_MB_trianLMER) # extracting the mean random intercept for each of trial variables
+dim(lmer.coef$Trial_ref)
 
@@
                size = 1,
-               colour = c("Black",hue_pal()(6)))
-   coord_cartesian(xlim = c(0.8, 1.2))
+               colour = c("Black",hue_pal()(11)))+
+   coord_cartesian(xlim = c(0, 3))
 
@@
                slope = lmer.coefx$Trial_ref[,1],
-               size = 1.5,
-               colour = hue_pal()(6))+
-   coord_cartesian(xlim = c(0, 3))
+               size = 1,
+               colour = hue_pal()(11))+
+   coord_cartesian(xlim = c(0, 3),
+                   ylim = c(0, 1))
 
@@
 
-What is interesting about this model is the slopes all converge and pass through a specific point.
-Perhaps can use this to predict the slope of the trials we don't know the specific slope for and get a better prediction of the errors.
-
-```{r imputing_from_randomModel}
-ggplot(PM_MB_train)+
-   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
-   geom_abline(intercept = lmer.coefx$Trial_ref[,2], 
-               slope = lmer.coefx$Trial_ref[,1],
-               size = 1.5,
-               colour = hue_pal()(6))+
-   coord_cartesian(xlim = c(2.85, 2.875), ylim = c(0.0048,0.0049))
-
-# let us find the value of this point
-# what are the slopes and intercepts for each random grouping factor (Trial_ref)
-randomS_coefs <- lmer.coefx$Trial_ref
-
-# lets write a funcion to generate a sequence of predicted Y (yield error) values
-slope_generator <- function(slope,intercept, x_minimum = 0.8, x_maximum = 1.2, increment = 0.00000001){
-   Xi <- seq(from = x_minimum, to = x_maximum, by = increment)
-   (Xi * slope) + intercept
-}
-
-# generate a vector of predicted values for each of the trial slopes, returned as a matrix
-tmp2 <- apply(randomS_coefs,1,FUN = function(x) {
-   slope_generator(slope = x[1], intercept = x[2],x_minimum = 2.86135, x_maximum = 2.8614)
-                      })
-head(tmp2)
-
-# find which X predictor gives the lowest variation between trials and therefore the closest to the point at which the slopes converge
-tmp3 <- apply(tmp2,1,sd)
-plot(tmp3)
-min(tmp3)
-x_3252 <- which(tmp3 == min(tmp3))
-
-# zooming in on the X predictor by increasing resolution
-seq(from = 2.85,to = 2.875, by =0.0001)[115]
-seq(from = 2.85,to = 2.875, by =0.00001)[1139]
-x_point <- seq(from = 2.86135,to = 2.8614, by =0.00000001)[x_3252]
-
-# predict the y (yeild error) at the x predictor (grain.yield) for each trial group
-tmp4 <- apply(randomS_coefs,1,FUN = function(x){
-   (x_point * x[1]) + x[2]
-})
-
-# they are all the same value but lets take the mean to be more precise
-y_point <- mean(tmp4)
-
-# here is my 'good-enough' prediction of the convergence point
-common_S_coordinate <- c(x_point, y_point)
-
-```
 After much deliberation I don't think this is possible to use the model with grain yield/ha as a random slope.

### 2019-08-07 05_MetaAnalysis.Rmd
added analysis after removing outlier trial.

@@
 
-# grain yeild is not a significant predictor for yeild error (t value = -1.613)
-#  And the variance decreases as the mean increases, counter to expectation
-# does log transformation improve the model
+# grain yeild (in this model) IS a significant predictor for yeild error (t value = 5.826)
+#  And the variance increases as the mean increases
+# does log transformation improve the model?
 
@@
          (1|Trial_ref), data = PM_MB_train)
-summary(PM_MB_trianLMER.1) # grain yeild is not a significant predictor of log(yeild error)
+summary(PM_MB_trianLMER.1) # grain yeild a significant predictor of log(yeild error)
 anova(PM_MB_trianLMER, PM_MB_trianLMER.1) # no significant difference between the models
@@
 
+# Extract the model cooeficients
 paramA <- (summary(PM_MB_trianLMER)$coef)[2,1] # Extract the overall mean Slope to predict Yield error
 InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the overall mean intercept to predict Yield error
-
 lmer.coef <- coef(PM_MB_trianLMER) # extracting the mean random intercept for each of trial variables
-dim(lmer.coef$Trial_ref)
 
@@
 
+```
+```{r na2Sv_formula}
+
 for(i in NATrials$Trial_ref){
@@
 PM_MB_means[PM_MB_means$Trial_ref == i,]$Y_error.type <- "SamplingVariance"
+}
 
-}
+```
+
+Lets look at the model without the trial mung1718/01, as it looks to be adding some skew.
+```{r lmer_remove_mung1718-01}
+# remove from mung1718/01 from training dataset
+PM_MB_train.2 <- PM_MB_train[PM_MB_train$Trial_ref != "mung1718/01",]
+
+# Rerun the model
+PM_MB_trianLMER.5 <- lmer(Yield_error ~ `grain_yield.t.ha.`+ 
+         (1|Trial_ref), data = PM_MB_train.2)
+summary(PM_MB_trianLMER.5) # no significant effect of mean grain yield on yeild error
+
+# Extract the cooeficients
+paramA <- (summary(PM_MB_trianLMER.5)$coef)[2,1] # Extract the overall mean Slope to predict Yield error
+InterC <- (summary(PM_MB_trianLMER.5)$coef)[1,1] # Extract the overall mean intercept to predict Yield error
+lmer.coef <- coef(PM_MB_trianLMER.5) # extracting the mean random intercept for each of trial variables
+
+# plot the data with the predicted slopes overlayed
+ggplot(PM_MB_train.2)+
+   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
+   geom_abline(intercept = c(InterC,lmer.coef$Trial_ref[,1]), 
+               slope = c(paramA,lmer.coef$Trial_ref[,2]),
+               size = 1,
+               colour = c("Black",hue_pal()(10)))+
+   coord_cartesian(ylim = c(0, 0.33))
+
 ```
@@
 Just for kicks lets look at the linear regression model as a Random effects model where `grain_yield.t.ha.` is set as a random slope to the random intercept `Trial_ref`.  
-The model fits better as shown by an anova comparison. But now to determine how to impute from this model ....
+The model fits better as shown by an anova comparison. But how to impute from this model if mean variance for a trial is unknown....
 ```{r random_slope_model}

### 2019-08-09 03_Preliminary_analysis.Rmd
Minor edits

@@
    geom_point()+
-   geom_smooth()+
+ #  geom_smooth()+
    scale_y_continuous(limits = c(-5,15))+
@@
 
+levels(as.factor(PM_MB_means$Fungicide))
 # plot table as a box plot
-
-ggplot(PM_MB_means, aes(y = prop_YG, x = Fungicide))+
+PM_MB_means %>%
+   filter(Fungicide == c("200 g/l  Tebuconazole + 120 g/l  Azoxystrobin" , "Amistar","Tebeconazole","propiconazole"))%>%
+ggplot(aes(y = prop_YG, x = Fungicide))+
    geom_boxplot()+
@@
    coord_cartesian()+
-   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))
+   theme(axis.text.x = element_text(angle = 30, hjust =.51, vjust = 0.3))
    #scale_x_continuous(limits = c(-0.3,0.6))
@@
 
-PM_MB_lmer.1 <- lmer(prop_YG ~ Fungicide + as.factor(total_Fungicide) + row_spacing + (1|Trial_ref), 
+PM_MB_lmer.1 <- lmer(prop_YG ~ Fungicide * as.factor(total_Fungicide) + row_spacing + (1|Trial_ref), 
      data = subset(PM_MB_means, total_Fungicide == 1 | total_Fungicide == 2))

### 2019-08-29 04_Prep_data.Rmd
Coded the calculation of yield gains and proportion of yield gain

# Place holder

```{r}
library(dplyr)
library(openxlsx)
library(kableExtra)
library(ggplot2)
library(leaflet)
#source("./getPPD2.R")

```

```{r Calculate_yield-gains}
PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv", stringsAsFactors = FALSE)
PM_MB_means$grain_yield.t.ha. <- as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data

for(i in levels(as.factor(PM_MB_means$Trial_ref))){
   dat1 <- PM_MB_means[PM_MB_means$Trial_ref == i,]

   if(any(is.na(unique(dat1$row_spacing)))){
      warning(paste(unique(dat1$Trial_ref), "at", unique(dat1$Location), "in year", unique(dat1$Year), "has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n") )
      next()}

   for(j in unique(dat1$row_spacing)){

      dat2 <- dat1[dat1$row_spacing == j,]
      controlY <- mean(dat2[dat2$Fungicide == "control","grain_yield.t.ha."])

      dat2$yield_gain <- dat2$grain_yield.t.ha. - controlY
      dat2$prop_YG <- dat2$yield_gain/controlY

      dat2[dat2$Fungicide == "control",c("yield_gain", "prop_YG")] <- NA

      dat1[dat1$row_spacing == j,] <- dat2
   }
   PM_MB_means[PM_MB_means$Trial_ref == i,] <- dat1
}

# caluculate yield gain and prop_yield gain for experiments with no row spacing data
dat1 <- PM_MB_means[PM_MB_means$Trial_ref == "AM1303",]
controlY <- mean(dat2[dat1$Fungicide == "control","grain_yield.t.ha."])
dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
dat1$prop_YG <- dat1$yield_gain/controlY
dat1[dat1$Fungicide == "control",c("yield_gain", "prop_YG")] <- NA
PM_MB_means[PM_MB_means$Trial_ref == "AM1303",] <- dat1

write.csv(PM_MB_means, "data/1902 powdery mildew-Mungbean - Collated means.csv")

```

### 2019-08-29 index.Rmd
Update after meeting with Adam
Reordered research questions

@@
 
-What is the length of a Mungbean season and how has it varied in this trial
+When is the optimum time to spray fungicide to limit the impact of powdery mildew on mungbean yeilds.
 
@@
 
-When is the optimum time to spray fungicide to limit the impact of powdery mildew on mungbean yeilds.
+How has the first sign of powdery mildew changed over the seasons and between experimental sites.
 
@@
 Do infections that occur before flowering increase the probable yield loss?
+
+What is the length of a Mungbean season and how has it varied in this trial.  
+   - This data has not been collected or is not accuarate enough to be useful to answer this question.
+
+## parts fof analysis that need checking
+
+Variability among host genotypes and probable influence of season given that over the years, the genotype studied changed from Berken, Crystal to Jade.

### 2019-09-01 03_Preliminary_analysis.Rmd
Tidy up chunks for knitting to function and make html document

@@
 
-```{r PA_Libraries}
+```{r PA_Libraries, include=FALSE}
 library(dplyr)
@@
 
-levels(as.factor(PM_MB_means$Fungicide))
 # plot table as a box plot
@@
 
-```{r Fungicide_x_nSprays}
+```{r Fungicide_x_nSprays, message=FALSE}
 PM_MB_means %>%
@@
 How many trials contain all of the most studied fungicides
-```{r}
+```{r Trials_with_top_three_Fungicides}
 Tebe_trials <- unique(PM_MB_means[PM_MB_means$Fungicide == "Tebeconazole",]$Trial_ref)
@@
 
-```{r}
+```{r Calculate_cuts, echo=FALSE}
+# removing 2017 and control data
+# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
+PM_MB_means1 <- PM_MB_means %>%
+   filter(Fungicide != "control") %>%
+#   filter(total_Fungicide ==1) %>%
+   mutate(days_from_1st = as.numeric(as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") - 
+                                        as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")))
+
+days_from_fungicid <- function(FSD,F1,F2,F3){
+   dF1 <- as.numeric(as.Date(F1) - as.Date(FSD))
+   dF2 <- as.numeric(as.Date(F2) - as.Date(FSD))
+   dF3 <- as.numeric(as.Date(F3) - as.Date(FSD))
+   if(is.na(dF1)){
+      return(NA)} else{
+   if(between(dF1,lower = -1, upper = 1000)){
+      return(dF1)}else{
+   if(is.na(dF2)){
+      return(dF1)}else{
+      if(between(dF2,lower = dF1, upper = -0.1)){
+            return(dF2)} else{
+               return(dF3)}}
+            }}
+}
+vec1<- vector()
+for(i in 1:dim(PM_MB_means1)[1]){
+   dF1 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_1, format = "%d/%m/%Y")[i] -
+                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
+   dF2 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_2, format = "%d/%m/%Y")[i] -
+                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
+   dF3 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_3, format = "%d/%m/%Y")[i] -
+                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
+   if(is.na(dF1)){
+      vec1 <- c(vec1,dF1)} else{
+         if(between(as.numeric(dF1),-1, 1000)){
+            vec1 <- c(vec1,dF1)}else{
+               if(is.na(dF2)){
+                  vec1 <- c(vec1,dF1)}else{
+                     if(between(as.numeric(dF2),as.numeric(dF1), -1.1)){
+            vec1 <- c(vec1,dF2)} else{
+               if(is.na(dF3)){
+                  vec1 <- c(vec1,dF2)}else{
+               if(as.numeric(dF3)>=0){
+                  vec1 <- c(vec1,dF2)}else{
+                     vec1 <- c(vec1,dF3)}}}}
+            }}
+}
+PM_MB_means1$spray_diff <- vec1 # gives the closest fungicide application date to the first sign of disease
+#PM_MB_means1$days_from_1st
+
+```
+
+```{r Sulphur_efficacy, echo=FALSE}
 
@@
 ```
-
-```{r}
-# removing 2017 and control data
-# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
-PM_MB_means1 <- PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-   filter(Year != 2017) %>%
-#   filter(total_Fungicide ==1) %>%
-   mutate(days_from_1st = as.numeric(as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") - 
-                                        as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")))
-
-days_from_fungicid <- function(FSD,F1,F2,F3){
-   dF1 <- as.numeric(as.Date(F1) - as.Date(FSD))
-   dF2 <- as.numeric(as.Date(F2) - as.Date(FSD))
-   dF3 <- as.numeric(as.Date(F3) - as.Date(FSD))
-   if(is.na(dF1)){
-      return(NA)} else{
-   if(between(dF1,lower = -1, upper = 1000)){
-      return(dF1)}else{
-   if(is.na(dF2)){
-      return(dF1)}else{
-      if(between(dF2,lower = dF1, upper = -0.1)){
-            return(dF2)} else{
-               return(dF3)}}
-            }}
-}
-vec1<- vector()
-for(i in 1:dim(PM_MB_means1)[1]){
-   dF1 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_1, format = "%d/%m/%Y")[i] -
-                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
-   dF2 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_2, format = "%d/%m/%Y")[i] -
-                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
-   dF3 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_3, format = "%d/%m/%Y")[i] -
-                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
-   if(is.na(dF1)){
-      vec1 <- c(vec1,dF1)} else{
-         if(between(as.numeric(dF1),-1, 1000)){
-            vec1 <- c(vec1,dF1)}else{
-               if(is.na(dF2)){
-                  vec1 <- c(vec1,dF1)}else{
-                     if(between(as.numeric(dF2),as.numeric(dF1), -1.1)){
-            vec1 <- c(vec1,dF2)} else{
-               if(is.na(dF3)){
-                  vec1 <- c(vec1,dF2)}else{
-               if(as.numeric(dF3)>=0){
-                  vec1 <- c(vec1,dF2)}else{
-                     vec1 <- c(vec1,dF3)}}}}
-            }}
-}
-PM_MB_means1$spray_diff <- vec1 # gives the closest fungicide application date to the first sign of disease
-#PM_MB_means1$days_from_1st
-
-```

### 2019-09-01 04_Prep_data.Rmd
Correction to code typo

@@
 dat1 <- PM_MB_means[PM_MB_means$Trial_ref == "AM1303",]
-controlY <- mean(dat2[dat1$Fungicide == "control","grain_yield.t.ha."])
+controlY <- mean(dat1[dat1$Fungicide == "control","grain_yield.t.ha."])
 dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY

### 2019-09-01 03_Preliminary_analysis.Rmd
Correct some graphs

@@
 ggplot(aes(y = as.numeric(grain_yield.t.ha.), x = row_spacing, colour = Location))+
+   geom_smooth(method = "gam")+
    geom_jitter(width = 0.01)+
-   geom_smooth()+
    #   scale_y_continuous(limits = c(-5,15))+
@@
    coord_cartesian()+
-   theme(axis.text.x = element_text(angle = 30, hjust =.51, vjust = 0.3))
+   coord_flip()
+   #theme(axis.text.x = element_text(angle = 30, hjust =.6, vjust = 0.83))
    #scale_x_continuous(limits = c(-0.3,0.6))
@@
 PM_MB_means %>%
-   filter(total_Fungicide ==1 |total_Fungicide ==2 ) %>%
+   filter(total_Fungicide ==1 |total_Fungicide ==2) %>% 
+   filter(Fungicide != "Pyrazophos" & Fungicide != "control" & Fungicide != "Benomyl" & Fungicide != "Acibenzolar-S-Methyl" & Fungicide != "200g/L azoxystrobin + 80 g/L cyproconazole + adj" ) %>%
 ggplot(aes(y = prop_YG, x = Fungicide))+
-   facet_grid(cols = vars(total_Fungicide))+
+   facet_grid(rows = vars(total_Fungicide))+
    geom_boxplot(aes(fill = Fungicide, alpha = 0.5))+
@@
    #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nFungicide type")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Fungicide"))+
+   labs(y = "Proportion of grain yeild saved",
+   title = "Grain yield proportion saved\ngrouped by Fungicide type")+
+   theme_usq()+
+   theme(legend.position="none")+
    coord_cartesian()+
-   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))
+   scale_x_discrete(limits = c("200 g/l  Tebuconazole + 120 g/l  Azoxystrobin","propiconazole", "Tebeconazole", "200g/L azoxystrobin + 80 g/L cyproconazole", "Sulphur", "Carbendazim", "Pyraclostrobin","Amistar"))+
+ #  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
+   coord_flip()
    #scale_x_continuous(limits = c(-0.3,0.6))
+
+levels(PM_MB_means$Fungicide)
 
@@
 
-```{r echo = FALSE, message=FALSE, warning=FALSE}
+```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
 PM_MB_means %>%
@@
 
+```
+
+```{r spray_timing&PropYield}
 # What range of 

### 2019-09-02 05_MetaAnalysis.Rmd
Exploring between trial variation with fungicide use .... However this does not find the means of each trial so it is not effectivley measureing the correct aggregated data. This is because it is taking the means of each fungicide treatment within trial, regardless of row.spacing or spray applications

@@
 ```{r Fungicides}
-unique(PM_MB_means$Fungicide)
+#unique(PM_MB_means$Fungicide)
 PM_MB_means %>%
@@
 
+Preliminary analysis of Fungicides show there is a difference the effect of Fungicide in proportion of yield gained
+
 ### Fungicide Doses
@@
    kable()
-# why are there zeros
+# why are there zeros - FIXED
 ```
@@
 PM_MB_means %>%
+   filter(Fungicide == "propiconazole") %>%
+   group_by(row_spacing,Trial_ref) %>%
+   summarise() %>%
+   count() %>%
+   rename(Trials = n) %>%
+   kable()
+
+PM_MB_means %>%
    filter(Fungicide == "Tebeconazole",
@@
 Can we pool certain row spacings that have no significant difference?
+From the preliminary analysis, graphs seem to imply that if there is a lower overall yeild there is no effect of row spacing on yield.
+However if the average yield is more than approximatley 0.6 - 1 T/Ha then smaller row spacing has the potenial to provide greater yield.
 
@@
           row_spacing == 0.75) %>%
-   group_by(Trial_ref, Y_error.type) %>%
+   group_by(Trial_ref, Location, Y_error.type) %>%
    summarise(Tebe_Treatments = length(Y_error.type))
+
+   PM_MB_means %>%
+   filter(Fungicide == "propiconazole",
+          row_spacing == 0.75) %>%
+   group_by(Trial_ref, Location, Y_error.type) %>%
+   summarise(Tebe_Treatments = length(Y_error.type))
+colnames(PM_MB_means)
+
 ```
@@
 
-The trial, `mung1112/02` uses Least squre differences to describe the variation within the experiment.
+The trial, `mung1112/02` uses Least square differences to describe the variation within the experiment.
 The following code attempts to convert this to sampling variance as per the method in [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
@@
 I also re-ran the model without including the trial which we used LSD to interprete the sampling variance and the model lost a lot of significance.
+
+Emerson proposed I look at the between trial variation
+```{r between_trial_variation}
+levels(factor(PM_MB_means$Y_error.type))
+
+PM_MB_means.SV <- PM_MB_means[PM_MB_means$Y_error.type == "SamplingVariance",]
+
+meta_mean.GY <- mean(PM_MB_means.SV$grain_yield.t.ha.,na.rm = TRUE)
+
+PM_MB_means_T <- PM_MB_means %>%
+   group_by(Trial_ref, Fungicide) %>%
+   summarise(trial_mean = mean(grain_yield.t.ha.,na.rm = TRUE),
+             BW_trial_variance = sd(grain_yield.t.ha.,na.rm = TRUE)^2)
+PM_MB_means_T
+
+summary(lm(BW_trial_variance ~ trial_mean  Fungicide, data = PM_MB_means_T))
+summary(lm(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "Tebeconazole")))
+summary(lm(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "propiconazole")))
+
+plot(BW_trial_variance ~ trial_mean, data = PM_MB_means_T)
+abline(-0.01356,0.03076)
+points(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "Tebeconazole"),col = "red", pch = 3)
+abline(-0.005162, 0.019892, col = "red")
+points(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "propiconazole"),col = "blue", pch = 3)
+abline(-0.03962, 0.05454, col = "blue")
+
+lm_within <- lm(BW_trial_variance ~ trial_mean * Trial_ref + Fungicide,
+                    data = PM_MB_means_T)
+summary(lm_within) # Not accurate in predicting TrialVariance from trial means
+
+lm_within2 <- lm(BW_trial_variance ~ trial_mean + Trial_ref + Fungicide,
+                    data = PM_MB_means_T)
+summary(lm_within2) # Not accurate in predicting TrialVariance from trial means
+
+lmer_within_1 <- lmer(BW_trial_variance ~ trial_mean + (1|Trial_ref/Fungicide),
+                    data = PM_MB_means_T)
+# unable to nest Fungicide under trial ref
+
+lmer_within_1 <- lmer(BW_trial_variance ~ trial_mean + Fungicide + (1|Trial_ref),
+                    data = PM_MB_means_T)
+# not accurate  for predicting TrialVariance
+
+summary(lmer_within_1)
+
+```

### 2019-09-02 05_MetaAnalysis.Rmd
Remove analysis with fungicide subset, it was incorrect

@@
 PM_MB_means_T <- PM_MB_means %>%
-   group_by(Trial_ref, Fungicide) %>%
+   group_by(Trial_ref) %>%
    summarise(trial_mean = mean(grain_yield.t.ha.,na.rm = TRUE),
@@
 
-summary(lm(BW_trial_variance ~ trial_mean  Fungicide, data = PM_MB_means_T))
+summary(lm(BW_trial_variance ~ trial_mean, data = PM_MB_means_T))
 summary(lm(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "Tebeconazole")))
@@
 
-lm_within <- lm(BW_trial_variance ~ trial_mean * Trial_ref + Fungicide,
-                    data = PM_MB_means_T)
-summary(lm_within) # Not accurate in predicting TrialVariance from trial means
-
-lm_within2 <- lm(BW_trial_variance ~ trial_mean + Trial_ref + Fungicide,
-                    data = PM_MB_means_T)
-summary(lm_within2) # Not accurate in predicting TrialVariance from trial means
-
-lmer_within_1 <- lmer(BW_trial_variance ~ trial_mean + (1|Trial_ref/Fungicide),
-                    data = PM_MB_means_T)
-# unable to nest Fungicide under trial ref
-
-lmer_within_1 <- lmer(BW_trial_variance ~ trial_mean + Fungicide + (1|Trial_ref),
-                    data = PM_MB_means_T)
-# not accurate  for predicting TrialVariance
-
-summary(lmer_within_1)
-
 ```

### 2019-09-02 05_MetaAnalysis.Rmd
between trial variance calculated

@@
 
+All_Trials <- unique(PM_MB_means$Trial_ref)
+PM_MB_means$TrialVariance <- NA
+
+for(i in All_Trials){
+   PM_MB_means[PM_MB_means$Trial_ref == i, "TrialVariance"] <- PM_MB_means_T[PM_MB_means_T$Trial_ref == i,"BW_trial_variance"]
+}
+
+PM_MB_means$TrialVariance
+
 summary(lm(BW_trial_variance ~ trial_mean, data = PM_MB_means_T))
@@
 abline(-0.01356,0.03076)
-points(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "Tebeconazole"),col = "red", pch = 3)
-abline(-0.005162, 0.019892, col = "red")
-points(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "propiconazole"),col = "blue", pch = 3)
-abline(-0.03962, 0.05454, col = "blue")
 

### 2019-09-14 01_Meta-analysis_experiments.Rmd
Spelling and grammar corrections, also fungicide AI

@@
    + Hermitage  
-   + Dalby - Site abandoned due it insuficient/late disease infection  
+   + Dalby - Site abandoned due to insufficient/late disease infection  
    + Emerald
@@
 * 2017  
-   + Fogerty  
+   + Missen Flats (Fogerty's farm)  
    + Hermitage
@@
 Trial data were obtained from a non-published manuscript. 
-Ratings for powdery Mildew were on a 1-5 rating scale and can be read in the file "Powdery mildew paper#1.doc".  
-Comparing Trials which have not used the same rating scale wil be done using a percentage change.
+Ratings for powdery mildew were on a 1-5 rating scale and can be read in the file "Powdery mildew paper#1.doc". 
+Comparing trials which have not used the same rating scale will be done using a percentage change.
 
 **2013 Field trials**  
-Fungicide treatments were described in reports in Two letter acronyms. The following is the assumed usage.
+Fungicide treatments were described in reports in two letter acronyms.
+The following is the assumed usage.
 
@@
          Expected_Fungicide = c("Sulphur", "Tilt", "Amistar Xtra", "Carbendazim"),
-         Active_Ingredient = c("Sulphur", "Propiconazole", "Amistar", "Carbendazim")
+         Active_Ingredient = c("Sulphur", "Propiconazole", "Azoxystrobin and Cyproconazole", "Carbendazim")
    )

### 2019-09-14 01_Meta-analysis_experiments.Rmd
Reformat R code chunks

@@
 ```{r}
-knitr::kable(
-   cbind(Acronym = c("SF", "Ti", "AX", "Ca"),
+knitr::kable(cbind(
+   Acronym = c("SF", "Ti", "AX", "Ca"),
    Expected_Fungicide = c("Sulphur", "Tilt", "Amistar Xtra", "Carbendazim"),
-         Active_Ingredient = c("Sulphur", "Propiconazole", "Azoxystrobin and Cyproconazole", "Carbendazim")
+   Active_Ingredient = c(
+      "Sulphur",
+      "Propiconazole",
+      "Azoxystrobin and Cyproconazole",
+      "Carbendazim"
    )
-)
+))
 ```
@@
 
-kable(PM.dat %>%
-   group_by(Trial_ref, Year, Location, trial_design, Replicates, planting_date, emergence_date, first_sign_disease) %>%
+kable(
+   PM.dat %>%
+      group_by(
+         Trial_ref,
+         Year,
+         Location,
+         trial_design,
+         Replicates,
+         planting_date,
+         emergence_date,
+         first_sign_disease
+      ) %>%
       summarise(Treatments = length(E_treatment)),
-   caption = "Description of Experiments") %>%
-   kable_styling(fixed_thead = T, full_width = T) %>%
+   caption = "Description of Experiments"
+) %>%
+   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
    scroll_box(width = "900px", height = "500px")
@@
 PM.dat$Trade_name <- factor(PM.dat$Trade_name)
-
 ```
@@
 ## Experimental locations
-Experimental locations where data was sufficient to include in meta-analysis
+
+Experimental locations where data was sufficient to include in meta-analysis.
+
 ```{r Experiment_locations}
-
 experiment_sites <- data.frame(
-   location = c("Hermitage", "Kingaroy research station","Gatton", "Emerald Agricultural College"),
-   lat = c(-28.215 ,-26.58,-27.56,-23.54),
-   lon = c(152.1003,151.83,152.32,148.19)
+   location = c(
+      "Hermitage",
+      "Kingaroy Research Station",
+      "Gatton",
+      "Emerald Agricultural College"
+   ),
+   lat = c(-28.215 , -26.58, -27.56, -23.54),
+   lon = c(152.1003, 151.83, 152.32, 148.19)
 )
@@
 # head(silo_gatton_Tmax)
-
 ```

### 2019-09-14 02_Weather.Rmd
formatting
Reformat R code and spellcheck

@@
 
-Below I am plotting the mean maximum temperures over 7 days during the growing season at each Mungbean trial site.
+Below I am plotting the mean maximum temperatures over 7 days during the growing season at each mungbean trial site.
 The vertical lines indicate when powdery mildew was first observed in that season.
@@
 # Update: I have included data files instead of seeking the data from the web. 
-# issue has something to do with website certificates not being appropriete.
+# issue has something to do with website certificates not being appropriate
+
+# Import dataset
+PM.dat <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
 
@@
 # format should be Universal time format
-year.day <- function(date){
-   if(is.na(date) == TRUE){ 
+year.day <- function(date) {
+   if (is.na(date) == TRUE) {
       return(NA)
    } else {
-return(as.numeric(as.Date(date) - as.Date(paste0(substr(date, start = 1, stop = 4),"-01-01"))))
+      return(as.numeric(as.Date(date) - as.Date(paste0(
+         substr(date, start = 1, stop = 4), "-01-01"
+      ))))
    }
@@
 silo_emerald_Tmax <- read.csv("./data/silo_emerald_Tmax.csv")
-
 ```
@@
 ```{r Kingaroy_weather, include=FALSE}
-
 # Smoothing temperatures by taking a rolling7 day average
@@
 min_T <- vector()
-for(i in 1:length(silo_king_Tmax[,1])){
-   max_T <- c(max_T,mean(silo_king_Tmax$max_temp[i:(i+7)]))
-   min_T <- c(min_T,mean(silo_king_Tmax$min_temp[i:(i+7)]))
+for (i in 1:length(silo_king_Tmax[, 1])) {
+   max_T <- c(max_T, mean(silo_king_Tmax$max_temp[i:(i + 7)]))
+   min_T <- c(min_T, mean(silo_king_Tmax$min_temp[i:(i + 7)]))
 }
 
-king_Tm_aver <- data.frame(location = "Kingaroy", date = as.Date(silo_king_Tmax$date), max_T, min_T, daily_rain = silo_king_Tmax$daily_rain)
+king_Tm_aver <-
+   data.frame(
+      location = "Kingaroy",
+      date = as.Date(silo_king_Tmax$date),
+      max_T,
+      min_T,
+      daily_rain = silo_king_Tmax$daily_rain
+   )
 
@@
 king_Tm_aver <- king_Tm_aver %>%
-   mutate(Year = substr(king_Tm_aver$date, start = 1, stop = 4),
-          Day = year.day(king_Tm_aver$date))
+   mutate(
+      Year = substr(king_Tm_aver$date, start = 1, stop = 4),
+      Day = year.day(king_Tm_aver$date)
+   )
 
-# Create data subset of Powdery mildew data means for the first sign of the disease by location
+# Create data subset of powdery mildew data means for the first sign of the disease by location
 King_FS <- PM.dat %>%
@@
 ggplot(subset(king_Tm_aver, Year == levels(factor(King_FS$Year))),
-              aes(Day))+
-   geom_line(aes(y = max_T, colour = Year))+
+       aes(Day)) +
+   geom_line(aes(y = max_T, colour = Year)) +
    #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
-   geom_line(aes(y = min_T, colour = Year))+
+   geom_line(aes(y = min_T, colour = Year)) +
    #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
    labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
-   title = "Maximum and minimum daily temperatures in Kingaroy")+
-   scale_y_continuous(limits = c(0,40))+
-   scale_x_continuous(limits = c(0,200), 
-                      labels = c(subset(king_Tm_aver, Year == 2016)$date[c(1,50,100,150,200)]),
-                      breaks = c(1,50,100,150,200))+
-   theme(panel.grid.major = element_line(colour = "grey80"),
+        title = "Maximum and minimum daily temperatures in Kingaroy") +
+   scale_y_continuous(limits = c(0, 40)) +
+   scale_x_continuous(
+      limits = c(0, 200),
+      labels = c(subset(king_Tm_aver, Year == 2016)$date[c(1, 50, 100, 150, 200)]),
+      breaks = c(1, 50, 100, 150, 200)
+   ) +
+   theme(
+      panel.grid.major = element_line(colour = "grey80"),
       panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(xintercept = King_FS$Day[1], size =1, colour = cols1[1], linetype = "dotted")+
-   geom_vline(xintercept = King_FS$Day[2], size =1.5, colour = cols1[2], linetype = "dotted")+
-   geom_vline(xintercept = King_FS$Day[3], size =1, colour = cols1[3], linetype = "dashed")+
-   geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
+      panel.background = element_rect(fill = NA)
+   ) +
+   geom_vline(
+      xintercept = King_FS$Day[1],
+      size = 1,
+      colour = cols1[1],
+      linetype = "dotted"
+   ) +
+   geom_vline(
+      xintercept = King_FS$Day[2],
+      size = 1.5,
+      colour = cols1[2],
+      linetype = "dotted"
+   ) +
+   geom_vline(
+      xintercept = King_FS$Day[3],
+      size = 1,
+      colour = cols1[3],
+      linetype = "dashed"
+   ) +
+   geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5) +
    scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))
@@
 #                      labels = c("2012-Jan-01","2012-Feb-01","2012-Mar-01","2012-Apr-01","2012-May-01","2012-Jun-01","2012-Jul-01"))
-
 ```
@@
 ```{r Hermitage_weather, include=FALSE}
-
 # ______  Hermitage  _______
@@
 min_T <- vector()
-for(i in 1:length(silo_war_Tmax[,1])){
-   max_T <- c(max_T,mean(silo_war_Tmax$max_temp[i:(i+7)]))
-   min_T <- c(min_T,mean(silo_war_Tmax$min_temp[i:(i+7)]))
+for (i in 1:length(silo_war_Tmax[, 1])) {
+   max_T <- c(max_T, mean(silo_war_Tmax$max_temp[i:(i + 7)]))
+   min_T <- c(min_T, mean(silo_war_Tmax$min_temp[i:(i + 7)]))
 }
 
-war_Tm_aver <- data.frame(location = "Hermitage", date = as.Date(silo_war_Tmax$date), max_T, min_T, daily_rain = silo_war_Tmax$daily_rain)
+war_Tm_aver <-
+   data.frame(
+      location = "Hermitage",
+      date = as.Date(silo_war_Tmax$date),
+      max_T,
+      min_T,
+      daily_rain = silo_war_Tmax$daily_rain
+   )
 
@@
 war_Tm_aver <- war_Tm_aver %>%
-   mutate(Year = substr(war_Tm_aver$date, start = 1, stop = 4),
-          Day = year.day(war_Tm_aver$date))
+   mutate(
+      Year = substr(war_Tm_aver$date, start = 1, stop = 4),
+      Day = year.day(war_Tm_aver$date)
+   )
 
-# Create data subset of Powdery mildew data means for the first sign of the disease by location
+# Create data subset of powdery mildew data means for the first sign of the disease by location
 Herm_FS <- PM.dat %>%
@@
 ggplot(subset(war_Tm_aver, Year == levels(factor(Herm_FS$Year))),
-              aes(Day))+
-   geom_line(aes(y = max_T, colour = Year))+
+       aes(Day)) +
+   geom_line(aes(y = max_T, colour = Year)) +
    #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
-   geom_line(aes(y = min_T, color = Year))+
+   geom_line(aes(y = min_T, color = Year)) +
    #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
    labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
-   title = "Maximum and minimum daily temperatures in Hermitage")+
-   scale_y_continuous(limits = c(0,45))+
-   scale_x_continuous(limits = c(0,200), 
-                      labels = c(subset(war_Tm_aver, Year == 2016)$date[c(1,50,100,150,200)]),
-                      breaks = c(1,50,100,150,200))+
-   theme(panel.grid.major = element_line(colour = "grey80"),
+        title = "Maximum and minimum daily temperatures in Hermitage") +
+   scale_y_continuous(limits = c(0, 45)) +
+   scale_x_continuous(
+      limits = c(0, 200),
+      labels = c(subset(war_Tm_aver, Year == 2016)$date[c(1, 50, 100, 150, 200)]),
+      breaks = c(1, 50, 100, 150, 200)
+   ) +
+   theme(
+      panel.grid.major = element_line(colour = "grey80"),
       panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(xintercept = Herm_FS$Day[1], size =1, colour = cols1[1], linetype = "dotted")+
-   geom_vline(xintercept = Herm_FS$Day[2], size =1.5, colour = cols1[2], linetype = "dotted")+
-   geom_vline(xintercept = Herm_FS$Day[3], size =1, colour = cols1[3], linetype = "dashed")+
-      geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
-   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
-   scale_x_continuous(limits = c(1,180),
-                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
-                      labels = c("Jan-01","Feb-01","Mar-01","Apr-01","May-01","Jun-01","Jul-01"))
+      panel.background = element_rect(fill = NA)
+   ) +
+   geom_vline(
+      xintercept = Herm_FS$Day[1],
+      size = 1,
+      colour = cols1[1],
+      linetype = "dotted"
+   ) +
+   geom_vline(
+      xintercept = Herm_FS$Day[2],
+      size = 1.5,
+      colour = cols1[2],
+      linetype = "dotted"
+   ) +
+   geom_vline(
+      xintercept = Herm_FS$Day[3],
+      size = 1,
+      colour = cols1[3],
+      linetype = "dashed"
+   ) +
+   geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5) +
+   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)")) +
+   scale_x_continuous(
+      limits = c(1, 180),
+      breaks = c(
+         1,
+         32,
+         (31 + 29),
+         (31 + 29 + 31),
+         (31 + 29 + 31 + 30),
+         (31 + 29 + 31 + 30 + 31),
+         (31 + 29 + 31 + 30 + 31 + 30)
+      ),
+      labels = c(
+         "Jan-01",
+         "Feb-01",
+         "Mar-01",
+         "Apr-01",
+         "May-01",
+         "Jun-01",
+         "Jul-01"
+      )
+   )
 
@@
 ```{r Gatton_weather, include=FALSE}
-
 # ______  Gatton  _______
@@
 min_T <- vector()
-for(i in 1:length(silo_gatton_Tmax[,1])){
-   max_T <- c(max_T,mean(silo_gatton_Tmax$max_temp[i:(i+7)]))
-   min_T <- c(min_T,mean(silo_gatton_Tmax$min_temp[i:(i+7)]))
+for (i in 1:length(silo_gatton_Tmax[, 1])) {
+   max_T <- c(max_T, mean(silo_gatton_Tmax$max_temp[i:(i + 7)]))
+   min_T <- c(min_T, mean(silo_gatton_Tmax$min_temp[i:(i + 7)]))
 }
 
-# put maximum, minimum temperatures into a dataframe corresponding with thier corresponding date
-Gat_Tm_aver <- data.frame(location = "Gatton", date = as.Date(silo_gatton_Tmax$date), max_T, min_T, daily_rain = silo_gatton_Tmax$daily_rain)
+# put maximum, minimum temperatures into a dataframe corresponding with their corresponding date
+Gat_Tm_aver <-
+   data.frame(
+      location = "Gatton",
+      date = as.Date(silo_gatton_Tmax$date),
+      max_T,
+      min_T,
+      daily_rain = silo_gatton_Tmax$daily_rain
+   )
 
@@
 Gat_Tm_aver <- Gat_Tm_aver %>%
-   mutate(Year = substr(Gat_Tm_aver$date, start = 1, stop = 4),
-          Day = year.day(Gat_Tm_aver$date))
+   mutate(
+      Year = substr(Gat_Tm_aver$date, start = 1, stop = 4),
+      Day = year.day(Gat_Tm_aver$date)
+   )
 
-# Create data subset of Powdery mildew data means for the first sign of the disease by location
+# Create data subset of powdery mildew data means for the first sign of the disease by location
 Gatton_FS <- PM.dat %>%
@@
    filter(Location == "Gatton") %>%
-   mutate(Year = factor(substr(First_sign,1,4)),
+   mutate(Year = factor(substr(First_sign, 1, 4)),
           Day = year.day(First_sign))
@@
 ggplot(subset(Gat_Tm_aver, Year == 2012),
-               aes(Day))+
-   geom_line(aes(y = max_T, colour = Year))+
+       aes(Day)) +
+   geom_line(aes(y = max_T, colour = Year)) +
    #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
-   geom_line(aes(y = min_T, colour = Year))+
+   geom_line(aes(y = min_T, colour = Year)) +
    #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
    labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
-   title = "Maximum and minimum daily temperatures in Gatton")+
-   scale_y_continuous(limits = c(0,40))+
-   scale_x_continuous(limits = c(0,200), 
-                      labels = c(subset(Gat_Tm_aver, Year == levels(Gatton_FS$Year))$date[c(1,50,100,150,200)]),
-                      breaks = c(1,50,100,150,200))+
-   theme(panel.grid.major = element_line(colour = "grey80"),
+        title = "Maximum and minimum daily temperatures in Gatton") +
+   scale_y_continuous(limits = c(0, 40)) +
+   scale_x_continuous(
+      limits = c(0, 200),
+      labels = c(subset(
+         Gat_Tm_aver, Year == levels(Gatton_FS$Year)
+      )$date[c(1, 50, 100, 150, 200)]),
+      breaks = c(1, 50, 100, 150, 200)
+   ) +
+   theme(
+      panel.grid.major = element_line(colour = "grey80"),
       panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(xintercept = Gatton_FS$Day, colour = "green", size =1)+
-      geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
-   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
-   scale_x_continuous(limits = c(1,180),
-                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
-                      labels = c("2012-Jan-01","2012-Feb-01","2012-Mar-01","2012-Apr-01","2012-May-01","2012-Jun-01","2012-Jul-01"))
+      panel.background = element_rect(fill = NA)
+   ) +
+   geom_vline(xintercept = Gatton_FS$Day,
+              colour = "green",
+              size = 1) +
+   geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5) +
+   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)")) +
+   scale_x_continuous(
+      limits = c(1, 180),
+      breaks = c(
+         1,
+         32,
+         (31 + 29),
+         (31 + 29 + 31),
+         (31 + 29 + 31 + 30),
+         (31 + 29 + 31 + 30 + 31),
+         (31 + 29 + 31 + 30 + 31 + 30)
+      ),
+      labels = c(
+         "2012-Jan-01",
+         "2012-Feb-01",
+         "2012-Mar-01",
+         "2012-Apr-01",
+         "2012-May-01",
+         "2012-Jun-01",
+         "2012-Jul-01"
+      )
+   )
 #   scale_x_continuous(limits = as.Date(c("2012-01-01","2012-06-01")))
-
 ```

### 2019-09-14 03_Preliminary_analysis.Rmd
Spellcheck and reformat R code

--- 2019-09-01 03_Preliminary_analysis.Rmd
@@
 #source("./getPPD2.R")
-
 ```
@@
 All data are a list of mean values from each treatment applied in each experiment.
-Various factors have been studied in the previous experiments which may influence the following results.
-The following variables were disregarded in the plots below.
+Various factors have been studied in the previous experiments which may influence the following results. The following variables were disregarded in the plots below.
 
@@
 # Import data
-PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
+PM_MB_means <-
+   read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
 colnames(PM_MB_means)
-PM_MB_means$Fungicide_application_1[as.character(PM_MB_means$Fungicide_application_1) == ""] <- NA
-PM_MB_means$Fungicide_application_2[as.character(PM_MB_means$Fungicide_application_2) == ""] <- NA
-PM_MB_means$Fungicide_application_3[as.character(PM_MB_means$Fungicide_application_3) == ""] <- NA
-PM_MB_means$Fungicide_application_4[as.character(PM_MB_means$Fungicide_application_4) == ""] <- NA
-PM_MB_means$Fungicide_application_5[as.character(PM_MB_means$Fungicide_application_5) == ""] <- NA
-PM_MB_means$Fungicide_application_6[as.character(PM_MB_means$Fungicide_application_6) == ""] <- NA
-PM_MB_means$Fungicide_application_7[as.character(PM_MB_means$Fungicide_application_7) == ""] <- NA
+PM_MB_means$Fungicide_application_1[as.character(PM_MB_means$Fungicide_application_1) == ""] <-
+   NA
+PM_MB_means$Fungicide_application_2[as.character(PM_MB_means$Fungicide_application_2) == ""] <-
+   NA
+PM_MB_means$Fungicide_application_3[as.character(PM_MB_means$Fungicide_application_3) == ""] <-
+   NA
+PM_MB_means$Fungicide_application_4[as.character(PM_MB_means$Fungicide_application_4) == ""] <-
+   NA
+PM_MB_means$Fungicide_application_5[as.character(PM_MB_means$Fungicide_application_5) == ""] <-
+   NA
+PM_MB_means$Fungicide_application_6[as.character(PM_MB_means$Fungicide_application_6) == ""] <-
+   NA
+PM_MB_means$Fungicide_application_7[as.character(PM_MB_means$Fungicide_application_7) == ""] <-
+   NA
 
 # Rewrite all variations of sulphur treatments as just sulphur
-PM_MB_means$Fungicide[PM_MB_means$Fungicide == "Sulphur"| PM_MB_means$Fungicide == "Sulphur (SC)" | PM_MB_means$Fungicide == "Sulphur (Ultra SC)" | PM_MB_means$Fungicide == "Sulphur (WP)"] <- "Sulphur"
+PM_MB_means$Fungicide[PM_MB_means$Fungicide == "Sulphur" |
+                         PM_MB_means$Fungicide == "Sulphur (SC)" |
+                         PM_MB_means$Fungicide == "Sulphur (Ultra SC)" |
+                         PM_MB_means$Fungicide == "Sulphur (WP)"] <- "Sulphur"
 ```
@@
 PM_MB_means %>%
-   filter(Year >= 2017)%>%
+   filter(Year >= 2017) %>%
    filter(Fungicide == "control") %>%
-ggplot(aes(y = PM_final_severity, x = row_spacing, colour = Location))+
-   geom_point()+
+   ggplot(aes(y = PM_final_severity, x = row_spacing, colour = Location)) +
+   geom_point() +
    #  geom_smooth()+
-   scale_y_continuous(limits = c(-5,15))+
+   scale_y_continuous(limits = c(-5, 15)) +
    theme_usq()
@@
 PM_MB_means %>%
-   filter(Year >= 2017)%>%
+   filter(Year >= 2017) %>%
    #   filter(Fungicide == "control") %>%
-ggplot(aes(y = as.numeric(grain_yield.t.ha.), x = row_spacing, colour = Location))+
-   geom_jitter(width = 0.01)+
-   geom_smooth()+
+   ggplot(aes(
+      y = as.numeric(grain_yield.t.ha.),
+      x = row_spacing,
+      colour = Location
+   )) +
+   geom_smooth(method = "gam") +
+   geom_jitter(width = 0.01) +
    #   scale_y_continuous(limits = c(-5,15))+
@@
 #### Effect of Fungicide 
-**on proportional yield gain with repect to time of application**
+**on proportional yield gain with respect to time of application**
 First lets look at the quantiles for each fungicide irrespective of other factors.
@@
    group_by(Fungicide) %>%
-   summarise(n = length(prop_YG),
+   summarise(
+      n = length(prop_YG),
       lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
@@
       mean = mean(prop_YG, na.rm = T),
-             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
+      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
+   ) %>%
    filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
@@
 PM_MB_means %>%
-   filter(Fungicide == c("200 g/l  Tebuconazole + 120 g/l  Azoxystrobin" , "Amistar","Tebeconazole","propiconazole"))%>%
-ggplot(aes(y = prop_YG, x = Fungicide))+
-   geom_boxplot()+
-   geom_hline(aes(yintercept = 0), size =0.5)+
+   filter(
+      Fungicide == c(
+         "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin" ,
+         "Azoxystrobin",
+         "Tebeconazole",
+         "Propiconoazole"
+      )
+   ) %>%
+   ggplot(aes(y = prop_YG, x = Fungicide)) +
+   geom_boxplot() +
+   geom_hline(aes(yintercept = 0), size = 0.5) +
    #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nFungicide type")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
+   labs(x = "Proportion of grain yield saved",
+        title = "Grain yield proportion saved grouped by\nFungicide type") +
+   theme(
+      panel.grid.major = element_line(colour = "grey80"),
       panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Fungicide"))+
-   coord_cartesian()+
-   theme(axis.text.x = element_text(angle = 30, hjust =.51, vjust = 0.3))
+      panel.background = element_rect(fill = NA)
+   ) +
+   guides(fill = guide_legend(title = "Fungicide")) +
+   coord_cartesian() +
+   coord_flip()
+#theme(axis.text.x = element_text(angle = 30, hjust =.6, vjust = 0.83))
 #scale_x_continuous(limits = c(-0.3,0.6))
@@
 ```
-There was some hope groups of fungicide could be combined, ie Propiconazole and Tebeconazole, however it seems that they have different efficacies.
+There was some hope groups of fungicide could be combined, _i.e._ Propiconazole and Tebeconazole, however it seems that they have different efficacies.
 Let us look to see if there is anything skewing the above.
@@
    group_by(Fungicide, total_Fungicide) %>%
-   summarise(n = length(prop_YG),
+   summarise(
+      n = length(prop_YG),
       lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
@@
 PM_MB_means %>%
-   filter(total_Fungicide ==1 |total_Fungicide ==2 ) %>%
-ggplot(aes(y = prop_YG, x = Fungicide))+
-   facet_grid(cols = vars(total_Fungicide))+
-   geom_boxplot(aes(fill = Fungicide, alpha = 0.5))+
-   geom_hline(aes(yintercept = 0), size =0.5)+
+   filter(total_Fungicide == 1 | total_Fungicide == 2) %>%
+   filter(
+      Fungicide != "Pyrazophos" &
+         Fungicide != "control" &
+         Fungicide != "Benomyl" &
+         Fungicide != "Acibenzolar-S-Methyl" &
+         Fungicide != "200g/L Azoxystrobin + 80 g/L Cyproconazole + adj"
+   ) %>%
+   ggplot(aes(y = prop_YG, x = Fungicide)) +
+   facet_grid(rows = vars(total_Fungicide)) +
+   geom_boxplot(aes(fill = Fungicide, alpha = 0.5)) +
+   geom_hline(aes(yintercept = 0), size = 0.5) +
    #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nFungicide type")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Fungicide"))+
-   coord_cartesian()+
-   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))
+   labs(y = "Proportion of grain yield saved",
+        title = "Grain yield proportion saved\ngrouped by Fungicide type") +
+   theme_usq() +
+   theme(legend.position = "none") +
+   coord_cartesian() +
+   scale_x_discrete(
+      limits = c(
+         "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin",
+         "Propiconazole",
+         "Tebeconazole",
+         "200g/L Azoxystrobin + 80 g/L Cyproconazole",
+         "Sulphur",
+         "Carbendazim",
+         "Pyraclostrobin",
+         "Azoxystrobin"
+      )
+   ) +
+   #  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
+   coord_flip()
 #scale_x_continuous(limits = c(-0.3,0.6))
+
+levels(PM_MB_means$Fungicide)
 
@@
 
-PM_MB_means$Fungicide <- factor(PM_MB_means$Fungicide, levels = c("control","propiconazole","Tebeconazole",
-                                                        "Amistar",
-                                                        "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin", "Carbendazim",
+PM_MB_means$Fungicide <-
+   factor(
+      PM_MB_means$Fungicide,
+      levels = c(
+         "control",
+         "Propiconazole",
+         "Tebeconazole",
+         "Azoxystrobin",
+         "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin",
+         "Carbendazim",
          "Benomyl",
-                                                         "Pyrazophos","Acibenzolar-S-Methyl",
-                                                        "Sulphur", "Sulphur (SC)","Sulphur (Ultra SC)","Sulphur (WP)"
-                                                        ))
+         "Pyrazophos",
+         "Acibenzolar-S-Methyl",
+         "Sulphur",
+         "Sulphur (SC)",
+         "Sulphur (Ultra SC)",
+         "Sulphur (WP)"
+      )
+   )
 
-PM_MB_lmer.1 <- lmer(prop_YG ~ Fungicide * as.factor(total_Fungicide) + row_spacing + (1|Trial_ref), 
-     data = subset(PM_MB_means, total_Fungicide == 1 | total_Fungicide == 2))
+PM_MB_lmer.1 <-
+   lmer(
+      prop_YG ~ Fungicide * as.factor(total_Fungicide) + row_spacing + (1 |
+                                                                           Trial_ref),
+      data = subset(PM_MB_means, total_Fungicide == 1 |
+                       total_Fungicide == 2)
+   )
 
@@
 ```
-There is no significant difference between Fungicides, except for Sulphur which is significantly less effective than propiconazole.
+There is no significant difference between Fungicides, except for Sulphur which is significantly less effective than Propiconazole.
 Propiconazole, on average, out performs other fungicides when mitigating yield loss.
@@
 ```{r Trials_with_top_three_Fungicides}
-Tebe_trials <- unique(PM_MB_means[PM_MB_means$Fungicide == "Tebeconazole",]$Trial_ref)
-Propi_trials <- unique(PM_MB_means[PM_MB_means$Fungicide == "propiconazole",]$Trial_ref)
-Amistar_trials <- unique(PM_MB_means[PM_MB_means$Fungicide == "Amistar",]$Trial_ref)
+Tebe_trials <-
+   unique(PM_MB_means[PM_MB_means$Fungicide == "Tebeconazole", ]$Trial_ref)
+Propi_trials <-
+   unique(PM_MB_means[PM_MB_means$Fungicide == "Propiconazole", ]$Trial_ref)
+Azoxystrobin_trials <-
+   unique(PM_MB_means[PM_MB_means$Fungicide == "Azoxystrobin", ]$Trial_ref)
 
-intersect(
-   intersect(Tebe_trials,Propi_trials)
-   ,Amistar_trials)
+intersect(intersect(Tebe_trials, Propi_trials)
+          , Azoxystrobin_trials)
 
@@
    #   filter(total_Fungicide ==1) %>%
-   mutate(days_from_1st = as.numeric(as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") - 
-                                        as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")))
+   mutate(days_from_1st = as.numeric(
+      as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") -
+         as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")
+   ))
 
-days_from_fungicid <- function(FSD,F1,F2,F3){
+days_from_fungicid <- function(FSD, F1, F2, F3) {
    dF1 <- as.numeric(as.Date(F1) - as.Date(FSD))
@@
    dF3 <- as.numeric(as.Date(F3) - as.Date(FSD))
-   if(is.na(dF1)){
-      return(NA)} else{
-   if(between(dF1,lower = -1, upper = 1000)){
-      return(dF1)}else{
-   if(is.na(dF2)){
-      return(dF1)}else{
-      if(between(dF2,lower = dF1, upper = -0.1)){
-            return(dF2)} else{
-               return(dF3)}}
-            }}
+   if (is.na(dF1)) {
+      return(NA)
+   } else{
+      if (between(dF1, lower = -1, upper = 1000)) {
+         return(dF1)
+      } else{
+         if (is.na(dF2)) {
+            return(dF1)
+         } else{
+            if (between(dF2, lower = dF1, upper = -0.1)) {
+               return(dF2)
+            } else{
+               return(dF3)
             }
-vec1<- vector()
-for(i in 1:dim(PM_MB_means1)[1]){
-   dF1 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_1, format = "%d/%m/%Y")[i] -
-                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
-   dF2 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_2, format = "%d/%m/%Y")[i] -
-                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
-   dF3 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_3, format = "%d/%m/%Y")[i] -
-                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
-   if(is.na(dF1)){
-      vec1 <- c(vec1,dF1)} else{
-         if(between(as.numeric(dF1),-1, 1000)){
-            vec1 <- c(vec1,dF1)}else{
-               if(is.na(dF2)){
-                  vec1 <- c(vec1,dF1)}else{
-                     if(between(as.numeric(dF2),as.numeric(dF1), -1.1)){
-            vec1 <- c(vec1,dF2)} else{
-               if(is.na(dF3)){
-                  vec1 <- c(vec1,dF2)}else{
-               if(as.numeric(dF3)>=0){
-                  vec1 <- c(vec1,dF2)}else{
-                     vec1 <- c(vec1,dF3)}}}}
-            }}
          }
-PM_MB_means1$spray_diff <- vec1 # gives the closest fungicide application date to the first sign of disease
+      }
+   }
+}
+vec1 <- vector()
+for (i in 1:dim(PM_MB_means1)[1]) {
+   dF1 <-
+      as.numeric(
+         as.Date(PM_MB_means1$Fungicide_application_1, format = "%d/%m/%Y")[i] -
+            as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i]
+      )
+   dF2 <-
+      as.numeric(
+         as.Date(PM_MB_means1$Fungicide_application_2, format = "%d/%m/%Y")[i] -
+            as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i]
+      )
+   dF3 <-
+      as.numeric(
+         as.Date(PM_MB_means1$Fungicide_application_3, format = "%d/%m/%Y")[i] -
+            as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i]
+      )
+   if (is.na(dF1)) {
+      vec1 <- c(vec1, dF1)
+   } else{
+      if (between(as.numeric(dF1), -1, 1000)) {
+         vec1 <- c(vec1, dF1)
+      } else{
+         if (is.na(dF2)) {
+            vec1 <- c(vec1, dF1)
+         } else{
+            if (between(as.numeric(dF2), as.numeric(dF1), -1.1)) {
+               vec1 <- c(vec1, dF2)
+            } else{
+               if (is.na(dF3)) {
+                  vec1 <- c(vec1, dF2)
+               } else{
+                  if (as.numeric(dF3) >= 0) {
+                     vec1 <- c(vec1, dF2)
+                  } else{
+                     vec1 <- c(vec1, dF3)
+                  }
+               }
+            }
+         }
+      }
+   }
+}
+PM_MB_means1$spray_diff <-
+   vec1 # gives the closest fungicide application date to the first sign of disease
 #PM_MB_means1$days_from_1st
@@
 PM_MB_means2 <- PM_MB_means1 %>%
-   filter(Fungicide == "Sulphur" |
+   filter(
+      Fungicide == "Sulphur" |
          Fungicide == "Sulphur (SC)" |
          Fungicide == "Sulphur (Ultra SC)" |
-             Fungicide == "Sulphur (WP)")
+         Fungicide == "Sulphur (WP)"
+   )
 
@@
 
-ggplot(PM_MB_means2, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))~.)+
+ggplot(PM_MB_means2, aes(prop_YG)) +
+   geom_density(aes(fill = cut(
+      PM_MB_means2$spray_diff, c(-30, -19, -15, -10, -1, 2, 7, 10, 12, 21)
+   )), alpha = 0.5) +
+   geom_vline(aes(xintercept = 0), size = 0.5) +
+   facet_grid(cut(PM_MB_means2$spray_diff, c(-30, -19, -15, -10, -1, 2, 7, 10, 12, 21)) ~
+                 .) +
    #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first Sulphur fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
+   labs(x = "Proportion of grain yield saved",
+        title = "Grain yield proportion saved grouped by\nwhen the first Sulphur fungicide application was made\nrelative to when Powdery Mildew was first seen") +
+   theme(
+      panel.grid.major = element_line(colour = "grey80"),
       panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.3,0.6))
+      panel.background = element_rect(fill = NA)
+   ) +
+   guides(
+      fill = guide_legend(title = "Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease")
+   ) +
+   scale_x_continuous(limits = c(-0.3, 0.6))
 
@@
 ```{r each_fungicide}
-Chemical <- c("Amistar","Carbendazim","Tebeconazole", "propiconazole")
+Chemical <-
+   c("Azoxystrobin", "Carbendazim", "Tebeconazole", "Propiconazole")
 levels(factor(PM_MB_means$Fungicide))
@@
 # Generates multiple plots for each type of fungicide tested
-for(Chem in Chemical){
+for (Chem in Chemical) {
    PM_MB_means2 <- PM_MB_means1 %>%
@@
    # the following code 'spray_group' sets the spray_diff groupings that are used in the plots
-spray_group <- c(min(unique(PM_MB_means2$spray_diff))-1,
+   spray_group <- c(min(unique(PM_MB_means2$spray_diff)) - 1,
                     -5, 5,
-      max(unique(PM_MB_means2$spray_diff))+1)
+                    max(unique(PM_MB_means2$spray_diff)) + 1)
 
-spray_group < - c(sort(unique(PM_MB_means2$spray_diff)-1), max(unique(PM_MB_means2$spray_diff)))
+   spray_group < -c(sort(unique(PM_MB_means2$spray_diff) - 1), max(unique(PM_MB_means2$spray_diff)))
 
@@
 
-p1 <- ggplot(PM_MB_means2, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, spray_group)), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means2$spray_diff, spray_group)~.)+
+   p1 <- ggplot(PM_MB_means2, aes(prop_YG)) +
+      geom_density(aes(fill = cut(PM_MB_means2$spray_diff, spray_group)), alpha = 0.5) +
+      geom_vline(aes(xintercept = 0), size = 0.5) +
+      facet_grid(cut(PM_MB_means2$spray_diff, spray_group) ~ .) +
       #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
+      labs(x = "Proportion of grain yield saved",
+           title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen") +
+      theme(
+         panel.grid.major = element_line(colour = "grey80"),
          panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title=paste(Chem,"Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease")))+
-   scale_x_continuous(limits = c(-1,1))
+         panel.background = element_rect(fill = NA)
+      ) +
+      guides(fill = guide_legend(
+         title = paste(
+            Chem,
+            "Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"
+         )
+      )) +
+      scale_x_continuous(limits = c(-1, 1))
 
@@
    group_by(total_Fungicide) %>%
-   summarise(n = length(yield_gain),
+   summarise(
+      n = length(yield_gain),
       lower_2.5 = quantile(yield_gain, na.rm = T, c(0.025)),
@@
       mean = mean(yield_gain, na.rm = T),
-             upper_97.5 = quantile(yield_gain, na.rm = T, c(0.975)))
+      upper_97.5 = quantile(yield_gain, na.rm = T, c(0.975))
+   )
 
 # Density plot of Number of fungicide applications and the resulting yeild saved (as a proportion)
-ggplot(subset(PM_MB_means,Fungicide != "control"), aes(yield_gain))+
-   geom_density(aes(group = factor(total_Fungicide), fill = factor(total_Fungicide)), alpha = 0.6)+
-   geom_vline(xintercept = 0, size =1)+
-   labs(x = "Grain yeild saved (t/ha)",
-   title = "Density plot of grain yield saved from differing numbers of fungicide applications")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
+ggplot(subset(PM_MB_means, Fungicide != "control"), aes(yield_gain)) +
+   geom_density(aes(
+      group = factor(total_Fungicide),
+      fill = factor(total_Fungicide)
+   ), alpha = 0.6) +
+   geom_vline(xintercept = 0, size = 1) +
+   labs(x = "Grain yield saved (t/ha)",
+        title = "Density plot of grain yield saved from differing numbers of fungicide applications") +
+   theme(
+      panel.grid.major = element_line(colour = "grey80"),
       panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(data = quant_PMy, aes(xintercept = lower_2.5, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   geom_vline(data = quant_PMy, aes(xintercept = upper_97.5, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   guides(colour = guide_legend(title="Upper (97.5%) and \nLower (2.5%) percentiles"),
-          fill=guide_legend(title="Number of \nFungicide applications"))+
-   scale_x_continuous(limits = c(-0.3,0.8))
+      panel.background = element_rect(fill = NA)
+   ) +
+   geom_vline(
+      data = quant_PMy,
+      aes(xintercept = lower_2.5,
+          colour = factor(total_Fungicide)),
+      size = 0.9,
+      linetype =  "dashed"
+   ) +
+   geom_vline(
+      data = quant_PMy,
+      aes(xintercept = upper_97.5,
+          colour = factor(total_Fungicide)),
+      size = 0.9,
+      linetype =  "dashed"
+   ) +
+   guides(
+      colour = guide_legend(title = "Upper (97.5%) and \nLower (2.5%) percentiles"),
+      fill = guide_legend(title = "Number of \nFungicide applications")
+   ) +
+   scale_x_continuous(limits = c(-0.3, 0.8))
 
 kable(quant_PMy,
-   caption = "Yeild gain for each number of fungicide applications") %>%
+      caption = "Yield gain for each number of fungicide applications") %>%
    kable_styling(fixed_thead = T, full_width = T)
@@
    group_by(total_Fungicide) %>%
-   summarise(lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
+   summarise(
+      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
       median = median(prop_YG, na.rm = T),
       mean = mean(prop_YG, na.rm = T),
-             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975)))
+      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
+   )
 
 # Density plot of proportion of yield saved
-ggplot(subset(PM_MB_means,Fungicide != "control"), aes(prop_YG))+
-   geom_density(aes(group = factor(total_Fungicide), fill = factor(total_Fungicide)), alpha = 0.6)+
-   geom_vline(xintercept = 0, size =1)+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Density plot of the grain yield proportion saved \n by the number of fungicide applications")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
+ggplot(subset(PM_MB_means, Fungicide != "control"), aes(prop_YG)) +
+   geom_density(aes(
+      group = factor(total_Fungicide),
+      fill = factor(total_Fungicide)
+   ), alpha = 0.6) +
+   geom_vline(xintercept = 0, size = 1) +
+   labs(x = "Proportion of grain yield saved",
+        title = "Density plot of the grain yield proportion saved \n by the number of fungicide applications") +
+   theme(
+      panel.grid.major = element_line(colour = "grey80"),
       panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(data = quant_PM, aes(xintercept = lower_2.5, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   geom_vline(data = quant_PM, aes(xintercept = upper_97.5, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   guides(colour = guide_legend(title="Upper (97.5%) and \nLower (2.5%) percentiles"),
-          fill=guide_legend(title="Number of \nFungicide applications"))+
-   scale_x_continuous(limits = c(-0.3,0.55))
+      panel.background = element_rect(fill = NA)
+   ) +
+   geom_vline(
+      data = quant_PM,
+      aes(xintercept = lower_2.5,
+          colour = factor(total_Fungicide)),
+      size = 0.9,
+      linetype =  "dashed"
+   ) +
+   geom_vline(
+      data = quant_PM,
+      aes(xintercept = upper_97.5,
+          colour = factor(total_Fungicide)),
+      size = 0.9,
+      linetype =  "dashed"
+   ) +
+   guides(
+      colour = guide_legend(title = "Upper (97.5%) and \nLower (2.5%) percentiles"),
+      fill = guide_legend(title = "Number of \nFungicide applications")
+   ) +
+   scale_x_continuous(limits = c(-0.3, 0.55))
 
 kable(quant_PM,
-   caption = "Proportion of yeild gain for each number of fungicide applications") %>%
+      caption = "Proportion of yield gain for each number of fungicide applications") %>%
    kable_styling(fixed_thead = T, full_width = T)
@@
 #### Timing of Fungicide application
-The following density plots show mean yield saved (t/Ha) or proportion yield saved in relation to when the first fungicide spray was applied in relation to when powdery mildew was first seen in the mungbean crop.
+The following density plots show mean yield saved (t / Ha) or proportion yield saved in relation to when the first fungicide spray was applied in relation to when powdery mildew was first seen in the mungbean crop.
 
-```{r echo = FALSE, message=FALSE, warning=FALSE}
+```{r eval = FALSE, message = FALSE, warning = FALSE, include = FALSE}
 PM_MB_means %>%
@@
       as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") -
-         as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")))
+         as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")
+   ))
 
+```
+
+```{r spray_timing&PropYield}
 # What range of
@@
 PM_MB_means1 %>%
-   group_by(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))) %>%
-   summarise(n = length(prop_YG),
+   group_by(cut(
+      PM_MB_means1$days_from_1st,
+      c(-41, -20, -15, -12, -0.5, 1.5, 7, 10, 12, 20)
+   )) %>%
+   summarise(
+      n = length(prop_YG),
       lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
@@
       mean = mean(prop_YG, na.rm = T),
-             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
+      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
+   ) %>%
    kable(caption = "Difference in days between first sign of disease and first fungicide application and the effect on proportion of yield gain") %>%
@@
 
-ggplot(PM_MB_means1, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))~.)+
+ggplot(PM_MB_means1, aes(prop_YG)) +
+   geom_density(aes(fill = cut(
+      PM_MB_means1$days_from_1st,
+      c(-41, -20, -15, -12, -0.5, 1.5, 7, 10, 12, 20)
+   )), alpha = 0.5) +
+   geom_vline(aes(xintercept = 0), size = 0.5) +
+   facet_grid(cut(
+      PM_MB_means1$days_from_1st,
+      c(-41, -20, -15, -12, -0.5, 1.5, 7, 10, 12, 20)
+   ) ~ .) +
    #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
+   labs(x = "Proportion of grain yield saved",
+        title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen") +
+   theme(
+      panel.grid.major = element_line(colour = "grey80"),
       panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.2,0.55))
+      panel.background = element_rect(fill = NA)
+   ) +
+   guides(
+      fill = guide_legend(title = "Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease")
+   ) +
+   scale_x_continuous(limits = c(-0.2, 0.55))
 ```

### 2019-09-14 04_Prep_data.Rmd
Reformat R code

@@
 ```{r Calculate_yield-gains}
-PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv", stringsAsFactors = FALSE)
-PM_MB_means$grain_yield.t.ha. <- as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data
+PM_MB_means <-
+   read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv",
+            stringsAsFactors = FALSE)
+PM_MB_means$grain_yield.t.ha. <-
+   as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data
 
-for(i in levels(as.factor(PM_MB_means$Trial_ref))){
-   dat1 <- PM_MB_means[PM_MB_means$Trial_ref == i,]
+for (i in levels(as.factor(PM_MB_means$Trial_ref))) {
+   dat1 <- PM_MB_means[PM_MB_means$Trial_ref == i, ]
 
-   if(any(is.na(unique(dat1$row_spacing)))){
-      warning(paste(unique(dat1$Trial_ref), "at", unique(dat1$Location), "in year", unique(dat1$Year), "has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n") )
-      next()}
+   if (any(is.na(unique(dat1$row_spacing)))) {
+      warning(
+         paste(
+            unique(dat1$Trial_ref),
+            "at",
+            unique(dat1$Location),
+            "in year",
+            unique(dat1$Year),
+            "has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n"
+         )
+      )
+      next()
+   }
 
-   for(j in unique(dat1$row_spacing)){
-
-      dat2 <- dat1[dat1$row_spacing == j,]
-      controlY <- mean(dat2[dat2$Fungicide == "control","grain_yield.t.ha."])
+   for (j in unique(dat1$row_spacing)) {
+      dat2 <- dat1[dat1$row_spacing == j, ]
+      controlY <-
+         mean(dat2[dat2$Fungicide == "control", "grain_yield.t.ha."])
 
       dat2$yield_gain <- dat2$grain_yield.t.ha. - controlY
-      dat2$prop_YG <- dat2$yield_gain/controlY
+      dat2$prop_YG <- dat2$yield_gain  /  controlY
 
-      dat2[dat2$Fungicide == "control",c("yield_gain", "prop_YG")] <- NA
+      dat2[dat2$Fungicide == "control", c("yield_gain", "prop_YG")] <-
+         NA
 
-      dat1[dat1$row_spacing == j,] <- dat2
+      dat1[dat1$row_spacing == j, ] <- dat2
    }
-   PM_MB_means[PM_MB_means$Trial_ref == i,] <- dat1
+   PM_MB_means[PM_MB_means$Trial_ref == i, ] <- dat1
 }
@@
 # caluculate yield gain and prop_yield gain for experiments with no row spacing data
-dat1 <- PM_MB_means[PM_MB_means$Trial_ref == "AM1303",]
-controlY <- mean(dat1[dat1$Fungicide == "control","grain_yield.t.ha."])
+dat1 <- PM_MB_means[PM_MB_means$Trial_ref == "AM1303", ]
+controlY <-
+   mean(dat1[dat1$Fungicide == "control", "grain_yield.t.ha."])
 dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
-dat1$prop_YG <- dat1$yield_gain/controlY
-dat1[dat1$Fungicide == "control",c("yield_gain", "prop_YG")] <- NA
-PM_MB_means[PM_MB_means$Trial_ref == "AM1303",] <- dat1
+dat1$prop_YG <- dat1$yield_gain / controlY
+dat1[dat1$Fungicide == "control", c("yield_gain", "prop_YG")] <- NA
+PM_MB_means[PM_MB_means$Trial_ref == "AM1303", ] <- dat1
 
-write.csv(PM_MB_means, "data/1902 powdery mildew-Mungbean - Collated means.csv")
-
+write.csv(PM_MB_means,
+          "data/1902 powdery mildew-Mungbean - Collated means.csv")
 ```

### 2019-09-14 Cleaning historical data.R
Format R code and spellcheck

@@ -1,5 +1,5 @@
-# This script is dedicated to 
-# importing and cleaning previous powdery Mildew experimental field trial data.
+# This script is dedicated to
+# importing and cleaning previous powdery mildew experimental field trial data.
 
 # install.packages("openxlsx")
 # install.packages("readxl")
@@ -13,41 +13,53 @@ library(data.table)
 
 # Year #  Trial location  #  Sowing date
 
-
 # ____________________________________________________________
 # _____________            Hermitage  2010        ____________
 
-Herm_10 <- read_xls("C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/Past Trials/2010/2010 PMmung Herm/2010 PMmung hermitage RAW field book.xls", 
-                        sheet = "For analysis")
+Herm_10 <-
+   read_xls(
+      "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/Past Trials/2010/2010 PMmung Herm/2010 PMmung hermitage RAW field book.xls",
+      sheet = "For analysis"
+   )
 
 Herm_10_m <- Herm_10 %>%
    group_by(`Cultivar!`, `Treat!`, `Description!`) %>%
-   summarise_all(list(~mean(.,na.rm = TRUE),~sd(.,na.rm=TRUE)))
-   
-write.csv(as.data.frame(Herm_10_m ), "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/2010 PMmung Hermitage means.csv")
+   summarise_all(list(~ mean(., na.rm = TRUE),  ~ sd(., na.rm = TRUE)))
+
+write.csv(
+   as.data.frame(Herm_10_m),
+   "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/2010 PMmung Hermitage means.csv"
+)
 
 
 # ____________________________________________________________
 # _____________            Hermitage  2011        ____________
 
[…]

### 2019-09-14 05_MetaAnalysis.Rmd
Start using cleaned means.csv file

@@
 ```{r MEsummary_Libraries}
-library(dplyr)
-library(openxlsx)
+library(tidyverse)
 library(kableExtra)
-library(ggplot2)
 library(leaflet)
-#source("./getPPD2.R")
-
 ```
@@
 
-```{r Meta_dataImport}
-PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv", stringsAsFactors = FALSE)
-PM_MB_means$grain_yield.t.ha. <- as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data
+```{r Meta_dataImport, message=FALSE}
+PM_MB_means <-
+   read_csv(
+      "data/1902 powdery mildew-Mungbean - Collated means.csv"
+   )
 
-#str(PM_MB_means)
+# convert coltypes
+
+PM_MB_means <- 
+   PM_MB_means %>% 
+   mutate(year = as.integer(year)) %>% 
+   mutate(replicates = as.integer(replicates)) %>% 
+   mutate(planting_date = as.Date(planting_date)) %>%
+   mutate(emergence_date = as.Date(emergence_date)) %>% 
+   mutate(flowering_date = as.Date(flowering_date)) %>% 
+   mutate(pod_final_date = as.Date(pod_final_date)) %>% 
+   mutate(mid_late_pod_final = as.Date(mid_late_pod_final)) %>% 
+   mutate(first_sign_disease = as.Date(first_sign_disease)) %>% 
+   mutate(fungicide_application_1 = as.Date(fungicide_application_1)) %>% 
+   mutate(fungicide_application_2 = as.Date(fungicide_application_2)) %>% 
+   mutate(fungicide_application_3 = as.Date(fungicide_application_3)) %>%
+   mutate(fungicide_application_4 = as.Date(fungicide_application_4)) %>% 
+   mutate(fungicide_application_5 = as.Date(fungicide_application_5)) %>%
+   mutate(fungicide_application_6 = as.Date(fungicide_application_6)) %>%
+   mutate(fungicide_application_7 = as.Date(fungicide_application_7)) %>% 
+   mutate(harvest_date = as.Date(harvest_date)) %>% 
+   mutate(final_assessment = as.Date(final_assessment))
+
 ```
 
-## Investigating data and the number of factors represented in each Trial
+## Investigating data and the number of factors represented in each trial
 
 ### Fungicides
-When investigating previous studies into Powdery Mildew Fungicide efficacy on Mungbean `r length(unique(PM_MB_means$Trial_ref))` trials were found, however only eleven Tebeconazol were used for the following meta-analysis, followed by the next common Fungicide Propiconazole.
-Sulphur was disregarded due to it's inconsistancy in efficacy.
+
+When investigating previous studies into powdery mildew fungicide efficacy on mungbean `r length(unique(PM_MB_means$trial_ref))` trials were found.
+However, only eleven tebuconazole were used for the following meta-analysis, followed by the next most common fungicide, propiconazole. Sulphur was disregarded due to its inconsistency in efficacy.
 
 ```{r Fungicides}
-#unique(PM_MB_means$Fungicide)
 PM_MB_means %>%
-   group_by(Fungicide,Trial_ref) %>%
+   group_by(fungicide_ai, trial_ref) %>%
    summarise() %>%
-   count(sort = T) %>%
+   count(sort = TRUE) %>%
    rename(Trials = n) %>%
@@
 ```
-Tebeconazole and propiconazole might be able to be pooled as a 'Triazole' fungicide treatment.
-Amistar is a combination of Azoxistrobin and Cyproconazole.
-Perhaps Amistar and 200 g/l Tebuconazole + 120 g/l Azoxystrobin might be able to be pooled given they both contain strobins and triazole, however they contain differening dose ratio (inverted).
 
-Perhaps best way forward is to do an analysis of only the Triazoles. Then do another including Amistar as a comparison.
+Tebuconazole and propiconazole might be able to be pooled as a 'triazole' fungicide treatment. 
+Amistar Xtra is a combination of azoxystrobin and cyproconazole.
+Perhaps Amistar Xtra and Custodia might be able to be pooled given they both contain strobilurin and triazole, however they contain differing dose ratio (inverted).
 
-Preliminary analysis of Fungicides show there is a difference the effect of Fungicide in proportion of yield gained
+Perhaps best way forward is to do an analysis of only the triazoles. Then do another including azoxystrobin as a comparison.
+
+Preliminary analysis of fungicides show there is a difference the effect of fungicide in proportion of yield gained
 
 ### Fungicide Doses
-All trials that used Tebeconazole used approimately the same dose. dose of the active ingredient ranged from 62.35 grams per hectare to 60 grams per hectare. 
+All trials that used tebuconazole used approximately the same dose.
+Dose of the active ingredient ranged from 62.35 grams per hectare to 60 grams per hectare.
+
 ```{r Tebe_dose}
 PM_MB_means %>%
-   filter(Fungicide == "Tebeconazole") %>%
-   select(Trial_ref, Year, Location, first_sign_disease, Dose.ai.ha., total_Fungicide) %>%
+   filter(fungicide_ai == "tebuconazole") %>%
+   select(trial_ref,
+          year,
+          location,
+          first_sign_disease,
+          dose_ai.ha,
+          total_fungicide) %>%
    kable()
-# why are there zeros - FIXED
 ```
@@
 
-Some experiments were designed to investigate the effect of row spacing and plant density on Powdery Mildew disease and crop yield.
-The results showed that shorter distances between rows increase crop yields and mitigated the yield impact of the disease.
+Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease and crop yield.
+The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows did increase yield significantly.
 Seven trials used a row spacing of 0.75 meters.
 
-```{r row_spacing}
+```{r row_spacing.m}
 PM_MB_means %>%
-   filter(Fungicide == "Tebeconazole") %>%
-   group_by(row_spacing,Trial_ref) %>%
+   filter(fungicide_ai == "tebuconazole") %>%
+   group_by(row_spacing.m, trial_ref) %>%
    summarise() %>%
@@
 PM_MB_means %>%
-   filter(Fungicide == "propiconazole") %>%
-   group_by(row_spacing,Trial_ref) %>%
+   filter(fungicide_ai == "propiconazole") %>%
+   group_by(row_spacing.m, trial_ref) %>%
    summarise() %>%
@@
 PM_MB_means %>%
-   filter(Fungicide == "Tebeconazole",
-          row_spacing == 0.75)
+   filter(fungicide_ai == "tebuconazole",
+         row_spacing.m == 0.75) 
+```
 
-```
-Were there any statistical diference between all row spacing or only some?  
+Were there any statistical difference between all row spacing or only some?  
 Can we pool certain row spacings that have no significant difference?
-From the preliminary analysis, graphs seem to imply that if there is a lower overall yeild there is no effect of row spacing on yield.
-However if the average yield is more than approximatley 0.6 - 1 T/Ha then smaller row spacing has the potenial to provide greater yield.
+From the preliminary analysis, the graphs seem to imply that if there is a lower overall yield there is no effect of row spacing on yield.
+However, if the average yield is more than approximately 0.6 - 1 t/ha then smaller row spacing has the potential to provide greater yield.
 
 ### Host genotypes
+
 Host genotype may need to be analysed to determine the effect.
+
 ```{r Host_genotype}
 PM_MB_means %>%
-   filter(Fungicide == "Tebeconazole",
-          row_spacing == 0.75) %>% 
-   group_by(host_genotype, Trial_ref) %>%
+   filter(fungicide_ai == "tebuconazole",
+         row_spacing.m == 0.75) %>%
+   group_by(host_genotype, trial_ref) %>%
    summarise() %>%
@@
    kable()
-
 ```
@@
    - Crystal: Susceptible  
-   - Jade: Moderatley susceptible
+   - Jade: Moderately susceptible
 
@@
 PM_MB_means %>%
-   filter(Fungicide == "Tebeconazole",
-          row_spacing == 0.75) %>%
-   group_by(Trial_ref, Location, Y_error.type) %>%
-   summarise(Tebe_Treatments = length(Y_error.type))
+   filter(fungicide_ai == "tebuconazole",
+         row_spacing.m == 0.75) %>%
+   group_by(trial_ref, location, y_error.type) %>%
+   summarise(tebu_treatments = length(y_error.type))
 
 PM_MB_means %>%
-   filter(Fungicide == "propiconazole",
-          row_spacing == 0.75) %>%
-   group_by(Trial_ref, Location, Y_error.type) %>%
-   summarise(Tebe_Treatments = length(Y_error.type))
+   filter(fungicide_ai == "propiconazole",
+          row_spacing.m == 0.75) %>%
+   group_by(trial_ref, location, y_error.type) %>%
+   summarise(Tebe_Treatments = length(y_error.type))
 colnames(PM_MB_means)
-
 ```
@@
 Trials <- PM_MB_means %>%
-   filter(
-      #Fungicide == "Tebeconazole",
-       #   row_spacing == 0.75,
-          Y_error.type == "lsd (P=0.05)")%>%
-   select(Trial_ref)%>%
+   filter(fungicide_ai == "tebuconazole",
+          row_spacing.m == 0.75,
+          y_error.type == "lsd (P=0.05)") %>%
+   select(trial_ref) %>%
    distinct()
-
 ```
@@
 Ideas for using a T-critical value of 1.697 came from reading a [statisics-how-to website](https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/).
-A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted where 30 degrees of freedom within expeiment was used to find the 'T-crit' value of 1.697.
+A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted where 30 degrees of freedom within experiment was used to find the 'T-crit' value of 1.697.
 
@@
 
-for(Trial2012 in Trials$Trial_ref){
-
-Tcrit <- 1.697  # 0.05 and DFw = 30 # T critical value for which there is significant difference between two groups; This value is the same for both trials "mung1112/01" and "mung1112/02"
-DFw <- sum(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates) - 
-   length(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates) # degrees of freedom within groups
-# n.A <- PM_MB_means[PM_MB_means$Trial_ref == "Trial2012,]$Replicates[1]
-# n.B <- PM_MB_means[PM_MB_means$Trial_ref == "Trial2012,]$Replicates[2]
-LSD <- PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Yield_error[1]
+for (Trial2012 in Trials$trial_ref) {
+   Tcrit <-
+      1.697  # 0.05 and DFw = 30 # T critical value for which there is significant difference between two groups; This value is the same for both trials "mung1112/01" and "mung1112/02"
+   DFw <-
+      sum(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Replicates) -
+      length(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Replicates) # degrees of freedom within groups
+   # n.A <- PM_MB_means[PM_MB_means$trial_ref == "Trial2012,]$Replicates[1]
+   # n.B <- PM_MB_means[PM_MB_means$trial_ref == "Trial2012,]$Replicates[2]
+   LSD <-
+      PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Yield_error[1]
 
@@
    #  MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B) # This formula was abandon in favor for the formula in Nugugi et. at (2011)
-MSE <- PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates[1]*(LSD/Tcrit)^2/2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
+   MSE <-
+      PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Replicates[1] * (LSD /
+                                                                           Tcrit) ^ 2 / 2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
 
-for(j in seq_along(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates)){
-   if(j == 1){Sv <- vector(length = length(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates))}
-#  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates[j] *
-#                   PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$grain_yield.t.ha.[j])
+   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Replicates)) {
+      if (j == 1) {
+         Sv <-
+            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Replicates))
+      }
+      #  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Replicates[j] *
+      #                   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$grain_yield.t.ha.[j])
       # Balance equation
-   Sv[j] = sqrt(MSE/(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates[j] *
-                  as.numeric(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$grain_yield.t.ha.[j])))
+      Sv[j] = sqrt(MSE / (
+         PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Replicates[j] *
+            as.numeric(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$grain_yield.t.ha.[j])
+      ))
 
@@
 
-PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Yield_error <- Sv
-PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Y_error.type <- "SamplingVariance"
+   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Yield_error <-
+      Sv
+   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$y_error.type <-
+      "SamplingVariance"
 
@@
 Trials <- PM_MB_means %>%
-   filter(
-         #Fungicide == "Tebeconazole",
-         #row_spacing == 0.75,
-          Y_error.type == "stdev")%>%
-   select(Trial_ref)%>%
+   filter(#fungicide_ai == "tebuconazole",
+      #row_spacing.m == 0.75,
+      y_error.type == "stdev") %>%
+   select(trial_ref) %>%
    distinct()
@@
 
-for(j in seq_along(PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error)){
+for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$Yield_error)) {
    # create empty vector at first iteration with length of j
-   if(j == 1){Sv <- vector(length = length(PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error))}
+   if (j == 1) {
+      Sv <-
+         vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$Yield_error))
+   }
 
    # Equation to convert standard deviation to Sampling Variance
-   Sv[j] = (PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error[j])^2
+   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$Yield_error[j]) ^
+      2
 }
@@
 # and replacing the values in the dataset
-PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error <- Sv
-PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Y_error.type <- "SamplingVariance"
+PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$Yield_error <-
+   Sv
+PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$y_error.type <-
+   "SamplingVariance"
 
@@
 
-Now for the trickier part creating 'Sampling Variance' for treatments where only mean yeild is recorded.  
+Now for the trickier part creating 'Sampling Variance' for treatments where only mean yield is recorded.  
 The trial which does not report any type of variance also reports that there is no significant difference between the means.
@@
 NATrials <- PM_MB_means %>%
-   filter(Fungicide == "Tebeconazole",
-          row_spacing == 0.75,
-          is.na(Y_error.type)) %>%
-   select(Trial_ref)%>%
+   filter(fungicide_ai == "tebuconazole",
+          row_spacing.m == 0.75,
+          is.na(y_error.type)) %>%
+   select(trial_ref) %>%
    distinct()
@@
 
-A single trial `mung1516/03` within the current scope od the meta-analysis fails to report a varience statistic.
+A single trial `mung1516/03` within the current scope of the meta-analysis fails to report a variance statistic.
 According to [Machado F.
@@
 
-# for(i in PM_MB_means$Trial_ref){
+# for(i in PM_MB_means$trial_ref){
 #
 # log(V)[i] = a + b * log(
-#    mean(subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "control"),
-#         subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "Tebeconazole")))
+#    mean(subset(PM_MB_means$grain_yield.t.ha.[i], fungicide_ai == "control"),
+#         subset(PM_MB_means$grain_yield.t.ha.[i], fungicide_ai == "tebuconazole")))
 # # need to know what parameters a and b are here
-# # I am guessing they represent prediction parameters for each "study" for each of the treatments, "control" and Tebeconazole"
+# # I am guessing they represent prediction parameters for each "study" for each of the treatments, "control" and tebuconazole"
 # }
@@
 PM_MB_train <- PM_MB_means %>%
-   filter(Y_error.type == "SamplingVariance")
+   filter(y_error.type == "SamplingVariance")
 
-PM_MB_train$Trial_ref <- as.factor(PM_MB_train$Trial_ref)
+PM_MB_train$trial_ref <- as.factor(PM_MB_train$trial_ref)
 
-plot(PM_MB_train$Yield_error, log(PM_MB_train$`grain_yield.t.ha.`))
+plot(PM_MB_train$Yield_error,
+     log(PM_MB_train$`grain_yield.t.ha.`))
 
 # Run a linear model with Grain_yield as a fixed effect predictor and Trial as a random intercept
-PM_MB_trianLMER <- lmer(Yield_error ~ `grain_yield.t.ha.`+ 
-         (1|Trial_ref), data = PM_MB_train)
+PM_MB_trianLMER <- lmer(Yield_error ~ `grain_yield.t.ha.` +
+                           (1 | trial_ref), data = PM_MB_train)
 summary(PM_MB_trianLMER)
@@
 
-PM_MB_trianLMER.1 <- lmer(log(Yield_error) ~ `grain_yield.t.ha.`+ 
-         (1|Trial_ref), data = PM_MB_train)
+PM_MB_trianLMER.1 <- lmer(log(Yield_error) ~ `grain_yield.t.ha.` +
+                             (1 | trial_ref), data = PM_MB_train)
 summary(PM_MB_trianLMER.1) # grain yeild a significant predictor of log(yeild error)
@@
 
-PM_MB_trianLMER.2 <- lmer(Yield_error ~ log(`grain_yield.t.ha.`)+ 
-         (1|Trial_ref), data = PM_MB_train)
+PM_MB_trianLMER.2 <- lmer(Yield_error ~ log(`grain_yield.t.ha.`) +
+                             (1 | trial_ref), data = PM_MB_train)
 summary(PM_MB_trianLMER.2) # log(grain yeild) is a significant predictor of yeild error
@@
 
-PM_MB_trianLMER.3 <- lmer(log(Yield_error) ~ log(`grain_yield.t.ha.`)+ 
-         (1|Trial_ref), data = PM_MB_train)
+PM_MB_trianLMER.3 <-
+   lmer(log(Yield_error) ~ log(`grain_yield.t.ha.`) +
+           (1 | trial_ref),
+        data = PM_MB_train)
 summary(PM_MB_trianLMER.3) # log(grain yeild) is a significant predictor of log(yeild error)
@@
 # Lets try with Fungicide as a fixed effect
-PM_MB_trianLMER.4 <- lmer(Yield_error ~ `grain_yield.t.ha.`+ as.factor(Fungicide) + 
-         (1|Trial_ref), data = PM_MB_train)
+PM_MB_trianLMER.4 <-
+   lmer(Yield_error ~ `grain_yield.t.ha.` + as.factor(Fungicide) +
+           (1 | trial_ref),
+        data = PM_MB_train)
 summary(PM_MB_trianLMER.4)
@@
 # Extract the model cooeficients
-paramA <- (summary(PM_MB_trianLMER)$coef)[2,1] # Extract the overall mean Slope to predict Yield error
-InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the overall mean intercept to predict Yield error
-lmer.coef <- coef(PM_MB_trianLMER) # extracting the mean random intercept for each of trial variables
+paramA <-
+   (summary(PM_MB_trianLMER)$coef)[2, 1] # Extract the overall mean Slope to predict Yield error
+InterC <-
+   (summary(PM_MB_trianLMER)$coef)[1, 1] # Extract the overall mean intercept to predict Yield error
+lmer.coef <-
+   coef(PM_MB_trianLMER) # extracting the mean random intercept for each of trial variables
 
 # plot of the mixed effect model, Black line shows the mean lmer regression line
-ggplot(PM_MB_train)+
-   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
-   geom_abline(intercept = c(InterC,lmer.coef$Trial_ref[,1]), 
-               slope = c(paramA,lmer.coef$Trial_ref[,2]),
+ggplot(PM_MB_train) +
+   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = trial_ref)) +
+   geom_abline(
+      intercept = c(InterC, lmer.coef$trial_ref[, 1]),
+      slope = c(paramA, lmer.coef$trial_ref[, 2]),
       size = 1,
-               colour = c("Black",hue_pal()(11)))+
+      colour = c("Black", hue_pal()(11))
+   ) +
    coord_cartesian(xlim = c(0, 3))
@@
 
-for(i in NATrials$Trial_ref){
-#Sv <- (log(PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped
+for (i in NATrials$trial_ref) {
+   #Sv <- (log(PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha.`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped
 
-Sv <- (PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.` * paramA) + InterC
+   Sv <-
+      (PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha.` * paramA) + InterC
 
-PM_MB_means[PM_MB_means$Trial_ref == i,]$Yield_error <- Sv
-PM_MB_means[PM_MB_means$Trial_ref == i,]$Y_error.type <- "SamplingVariance"
+   PM_MB_means[PM_MB_means$trial_ref == i,]$Yield_error <- Sv
+   PM_MB_means[PM_MB_means$trial_ref == i,]$y_error.type <-
+      "SamplingVariance"
 }
@@
 # remove from mung1718/01 from training dataset
-PM_MB_train.2 <- PM_MB_train[PM_MB_train$Trial_ref != "mung1718/01",]
+PM_MB_train.2 <-
+   PM_MB_train[PM_MB_train$trial_ref != "mung1718/01",]
 
 # Rerun the model
-PM_MB_trianLMER.5 <- lmer(Yield_error ~ `grain_yield.t.ha.`+ 
-         (1|Trial_ref), data = PM_MB_train.2)
+PM_MB_trianLMER.5 <- lmer(Yield_error ~ `grain_yield.t.ha.` +
+                             (1 | trial_ref), data = PM_MB_train.2)
 summary(PM_MB_trianLMER.5) # no significant effect of mean grain yield on yeild error
@@
 # Extract the cooeficients
-paramA <- (summary(PM_MB_trianLMER.5)$coef)[2,1] # Extract the overall mean Slope to predict Yield error
-InterC <- (summary(PM_MB_trianLMER.5)$coef)[1,1] # Extract the overall mean intercept to predict Yield error
-lmer.coef <- coef(PM_MB_trianLMER.5) # extracting the mean random intercept for each of trial variables
+paramA <-
+   (summary(PM_MB_trianLMER.5)$coef)[2, 1] # Extract the overall mean Slope to predict Yield error
+InterC <-
+   (summary(PM_MB_trianLMER.5)$coef)[1, 1] # Extract the overall mean intercept to predict Yield error
+lmer.coef <-
+   coef(PM_MB_trianLMER.5) # extracting the mean random intercept for each of trial variables
 
 # plot the data with the predicted slopes overlayed
-ggplot(PM_MB_train.2)+
-   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
-   geom_abline(intercept = c(InterC,lmer.coef$Trial_ref[,1]), 
-               slope = c(paramA,lmer.coef$Trial_ref[,2]),
+ggplot(PM_MB_train.2) +
+   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = trial_ref)) +
+   geom_abline(
+      intercept = c(InterC, lmer.coef$trial_ref[, 1]),
+      slope = c(paramA, lmer.coef$trial_ref[, 2]),
       size = 1,
-               colour = c("Black",hue_pal()(10)))+
+      colour = c("Black", hue_pal()(10))
+   ) +
    coord_cartesian(ylim = c(0, 0.33))
@@
 
-Just for kicks lets look at the linear regression model as a Random effects model where `grain_yield.t.ha.` is set as a random slope to the random intercept `Trial_ref`.  
-The model fits better as shown by an anova comparison. But how to impute from this model if mean variance for a trial is unknown....
+Just for kicks lets look at the linear regression model as a Random effects model where `grain_yield.t.ha.` is set as a random slope to the random intercept `trial_ref`.  
+The model fits better as shown by an ANOVA comparison. But how to impute from this model if mean variance for a trial is unknown....
 ```{r random_slope_model}
@@
 PM_MB_trianLMERx <- lmer(Yield_error ~ 1 +
-         (`grain_yield.t.ha.`|Trial_ref), data = PM_MB_train)
+                            (`grain_yield.t.ha.` | trial_ref), data = PM_MB_train)
 
-anova(PM_MB_trianLMER,PM_MB_trianLMERx) # random slope model NOT significantly better # P = 0.6677
+anova(PM_MB_trianLMER, PM_MB_trianLMERx) # random slope model NOT significantly better # P = 0.6677
 
@@
 
-InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the overall mean intercept
+InterC <-
+   (summary(PM_MB_trianLMER)$coef)[1, 1] # Extract the overall mean intercept
 
@@
 # plot of the mixed effect model, Black line shows the mean lmer regression line
-ggplot(PM_MB_train)+
-   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
-   geom_abline(intercept = lmer.coefx$Trial_ref[,2], 
-               slope = lmer.coefx$Trial_ref[,1],
+ggplot(PM_MB_train) +
+   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = trial_ref)) +
+   geom_abline(
+      intercept = lmer.coefx$trial_ref[, 2],
+      slope = lmer.coefx$trial_ref[, 1],
       size = 1,
-               colour = hue_pal()(11))+
+      colour = hue_pal()(11)
+   ) +
    coord_cartesian(xlim = c(0, 3),
                    ylim = c(0, 1))
-
 ```
@@
 After much deliberation I don't think this is possible to use the model with grain yield/ha as a random slope.
-Even though we know the grain yields and the mean in the grain yeilds we still can't predict the effect of the random intercept trial on the yield error.
-I also re-ran the model without including the trial which we used LSD to interprete the sampling variance and the model lost a lot of significance.
+Even though we know the grain yields and the mean in the grain yields we still can't predict the effect of the random intercept trial on the yield error.
+I also re-ran the model without including the trial which we used LSD to interpret the sampling variance and the model lost a lot of significance.
 
 Emerson proposed I look at the between trial variation
+
 ```{r between_trial_variation}
-levels(factor(PM_MB_means$Y_error.type))
+levels(factor(PM_MB_means$y_error.type))
 
-PM_MB_means.SV <- PM_MB_means[PM_MB_means$Y_error.type == "SamplingVariance",]
+PM_MB_means.SV <-
+   PM_MB_means[PM_MB_means$y_error.type == "SamplingVariance", ]
 
-meta_mean.GY <- mean(PM_MB_means.SV$grain_yield.t.ha.,na.rm = TRUE)
+meta_mean.GY <- mean(PM_MB_means.SV$grain_yield.t.ha., na.rm = TRUE)
 
 PM_MB_means_T <- PM_MB_means %>%
-   group_by(Trial_ref) %>%
-   summarise(trial_mean = mean(grain_yield.t.ha.,na.rm = TRUE),
-             BW_trial_variance = sd(grain_yield.t.ha.,na.rm = TRUE)^2)
+   group_by(trial_ref) %>%
+   summarise(
+      trial_mean = mean(grain_yield.t.ha., na.rm = TRUE),
+      BW_trial_variance = sd(grain_yield.t.ha., na.rm = TRUE) ^ 2
+   )
 PM_MB_means_T
 
-All_Trials <- unique(PM_MB_means$Trial_ref)
+All_Trials <- unique(PM_MB_means$trial_ref)
 PM_MB_means$TrialVariance <- NA
 
-for(i in All_Trials){
-   PM_MB_means[PM_MB_means$Trial_ref == i, "TrialVariance"] <- PM_MB_means_T[PM_MB_means_T$Trial_ref == i,"BW_trial_variance"]
+for (i in All_Trials) {
+   PM_MB_means[PM_MB_means$trial_ref == i, "TrialVariance"] <-
+      PM_MB_means_T[PM_MB_means_T$trial_ref == i, "BW_trial_variance"]
 }
@@
 summary(lm(BW_trial_variance ~ trial_mean, data = PM_MB_means_T))
-summary(lm(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "Tebeconazole")))
-summary(lm(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "propiconazole")))
+summary(lm(
+   BW_trial_variance ~ trial_mean,
+   data = subset(PM_MB_means_T, fungicide_ai == "tebuconazole")
+))
+summary(lm(
+   BW_trial_variance ~ trial_mean,
+   data = subset(PM_MB_means_T, fungicide_ai == "propiconazole")
+))
 
 plot(BW_trial_variance ~ trial_mean, data = PM_MB_means_T)
-abline(-0.01356,0.03076)
+abline(-0.01356, 0.03076)
 

### 2019-09-14 05_MetaAnalysis.Rmd
Fix date formats on import

@@
 # convert coltypes
-
 PM_MB_means <-
@@
    mutate(replicates = as.integer(replicates)) %>%
-   mutate(planting_date = as.Date(planting_date)) %>%
-   mutate(emergence_date = as.Date(emergence_date)) %>% 
-   mutate(flowering_date = as.Date(flowering_date)) %>% 
-   mutate(pod_final_date = as.Date(pod_final_date)) %>% 
-   mutate(mid_late_pod_final = as.Date(mid_late_pod_final)) %>% 
-   mutate(first_sign_disease = as.Date(first_sign_disease)) %>% 
-   mutate(fungicide_application_1 = as.Date(fungicide_application_1)) %>% 
-   mutate(fungicide_application_2 = as.Date(fungicide_application_2)) %>% 
-   mutate(fungicide_application_3 = as.Date(fungicide_application_3)) %>%
-   mutate(fungicide_application_4 = as.Date(fungicide_application_4)) %>% 
-   mutate(fungicide_application_5 = as.Date(fungicide_application_5)) %>%
-   mutate(fungicide_application_6 = as.Date(fungicide_application_6)) %>%
-   mutate(fungicide_application_7 = as.Date(fungicide_application_7)) %>% 
-   mutate(harvest_date = as.Date(harvest_date)) %>% 
-   mutate(final_assessment = as.Date(final_assessment))
-
+   mutate(planting_date = as.Date(planting_date, format = "%d/%m/%Y")) %>%
+   mutate(emergence_date = as.Date(emergence_date, format = "%d/%m/%Y")) %>%
+   mutate(flowering_date = as.Date(flowering_date, format = "%d/%m/%Y")) %>%
+   mutate(pod_final_date = as.Date(pod_final_date, format = "%d/%m/%Y")) %>%
+   mutate(mid_late_pod_final = as.Date(mid_late_pod_final, format = "%d/%m/%Y")) %>%
+   mutate(first_sign_disease = as.Date(first_sign_disease, format = "%d/%m/%Y")) %>%
+   mutate(fungicide_application_1 = as.Date(fungicide_application_1, format = "%d/%m/%Y")) %>%
+   mutate(fungicide_application_2 = as.Date(fungicide_application_2, format = "%d/%m/%Y")) %>%
+   mutate(fungicide_application_3 = as.Date(fungicide_application_3, format = "%d/%m/%Y")) %>%
+   mutate(fungicide_application_4 = as.Date(fungicide_application_4, format = "%d/%m/%Y")) %>%
+   mutate(fungicide_application_5 = as.Date(fungicide_application_5, format = "%d/%m/%Y")) %>%
+   mutate(fungicide_application_6 = as.Date(fungicide_application_6, format = "%d/%m/%Y")) %>%
+   mutate(fungicide_application_7 = as.Date(fungicide_application_7, format = "%d/%m/%Y")) %>%
+   mutate(harvest_date = as.Date(harvest_date, format = "%d/%m/%Y")) %>%
+   mutate(final_assessment = as.Date(final_assessment, format = "%d/%m/%Y"))
 ```
@@
    DFw <-
-      sum(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Replicates) -
-      length(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Replicates) # degrees of freedom within groups
-   # n.A <- PM_MB_means[PM_MB_means$trial_ref == "Trial2012,]$Replicates[1]
-   # n.B <- PM_MB_means[PM_MB_means$trial_ref == "Trial2012,]$Replicates[2]
+      sum(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates) -
+      length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates) # degrees of freedom within groups
+   # n.A <- PM_MB_means[PM_MB_means$trial_ref == "Trial2012,]$replicates[1]
+   # n.B <- PM_MB_means[PM_MB_means$trial_ref == "Trial2012,]$replicates[2]
    LSD <-
-      PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Yield_error[1]
+      PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error[1]
 
@@
    MSE <-
-      PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Replicates[1] * (LSD /
+      PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[1] * (LSD /
                                                                             Tcrit) ^ 2 / 2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
 
-   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Replicates)) {
+   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates)) {
       if (j == 1) {
          Sv <-
-            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Replicates))
+            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates))
       }
-      #  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Replicates[j] *
-      #                   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$grain_yield.t.ha.[j])
+      #  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates[j] *
+      #                   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$grain_yield.t.ha[j])
       # Balance equation
       Sv[j] = sqrt(MSE / (
-         PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Replicates[j] *
-            as.numeric(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$grain_yield.t.ha.[j])
+         PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j] *
+            as.numeric(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$grain_yield.t.ha[j])
       ))
@@
 
-   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Yield_error <-
+   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error <-
       Sv
-   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$y_error.type <-
+   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$y_error.type <-
       "SamplingVariance"
@@
 
-for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$Yield_error)) {
+for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error)) {
    # create empty vector at first iteration with length of j
@@
       Sv <-
-         vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$Yield_error))
+         vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error))
    }
@@
    # Equation to convert standard deviation to Sampling Variance
-   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$Yield_error[j]) ^
+   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error[j]) ^
       2
@@
 # and replacing the values in the dataset
-PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$Yield_error <-
+PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error <-
    Sv
-PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$y_error.type <-
+PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$y_error.type <-
    "SamplingVariance"
@@
 # log(V)[i] = a + b * log(
-#    mean(subset(PM_MB_means$grain_yield.t.ha.[i], fungicide_ai == "control"),
-#         subset(PM_MB_means$grain_yield.t.ha.[i], fungicide_ai == "tebuconazole")))
+#    mean(subset(PM_MB_means$grain_yield.t.ha[i], fungicide_ai == "control"),
+#         subset(PM_MB_means$grain_yield.t.ha[i], fungicide_ai == "tebuconazole")))
 # # need to know what parameters a and b are here
@@
 
-plot(PM_MB_train$Yield_error,
-     log(PM_MB_train$`grain_yield.t.ha.`))
+plot(PM_MB_train$yield_error,
+     log(PM_MB_train$grain_yield.t.ha))
 
-# Run a linear model with Grain_yield as a fixed effect predictor and Trial as a random intercept
-PM_MB_trianLMER <- lmer(Yield_error ~ `grain_yield.t.ha.` +
+# Run a linear model with grain_yield.t.ha as a fixed effect predictor and trial as a random intercept
+PM_MB_trianLMER <- lmer(yield_error ~ grain_yield.t.ha +
                            (1 | trial_ref), data = PM_MB_train)
@@
 
-PM_MB_trianLMER.1 <- lmer(log(Yield_error) ~ `grain_yield.t.ha.` +
+PM_MB_trianLMER.1 <- lmer(log(yield_error) ~ `grain_yield.t.ha` +
                              (1 | trial_ref), data = PM_MB_train)
@@
 
-PM_MB_trianLMER.2 <- lmer(Yield_error ~ log(`grain_yield.t.ha.`) +
+PM_MB_trianLMER.2 <- lmer(yield_error ~ log(`grain_yield.t.ha`) +
                              (1 | trial_ref), data = PM_MB_train)
@@
 PM_MB_trianLMER.3 <-
-   lmer(log(Yield_error) ~ log(`grain_yield.t.ha.`) +
+   lmer(log(yield_error) ~ log(`grain_yield.t.ha`) +
            (1 | trial_ref),
@@
 PM_MB_trianLMER.4 <-
-   lmer(Yield_error ~ `grain_yield.t.ha.` + as.factor(Fungicide) +
+   lmer(yield_error ~ `grain_yield.t.ha` + as.factor(fungicide_ai) +
            (1 | trial_ref),
@@
 ggplot(PM_MB_train) +
-   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = trial_ref)) +
+   geom_point(aes(y = yield_error, x = `grain_yield.t.ha`, colour = trial_ref)) +
    geom_abline(
@@
 for (i in NATrials$trial_ref) {
-   #Sv <- (log(PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha.`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped
+   #Sv <- (log(PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped
 
    Sv <-
-      (PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha.` * paramA) + InterC
+      (PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha` * paramA) + InterC
 
-   PM_MB_means[PM_MB_means$trial_ref == i,]$Yield_error <- Sv
+   PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <- Sv
    PM_MB_means[PM_MB_means$trial_ref == i,]$y_error.type <-
@@
 # Rerun the model
-PM_MB_trianLMER.5 <- lmer(Yield_error ~ `grain_yield.t.ha.` +
+PM_MB_trianLMER.5 <- lmer(yield_error ~ `grain_yield.t.ha` +
                              (1 | trial_ref), data = PM_MB_train.2)
@@
 ggplot(PM_MB_train.2) +
-   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = trial_ref)) +
+   geom_point(aes(y = yield_error, x = `grain_yield.t.ha`, colour = trial_ref)) +
    geom_abline(
@@
 
-Just for kicks lets look at the linear regression model as a Random effects model where `grain_yield.t.ha.` is set as a random slope to the random intercept `trial_ref`.  
+Just for kicks lets look at the linear regression model as a Random effects model where `grain_yield.t.ha` is set as a random slope to the random intercept `trial_ref`.  
 The model fits better as shown by an ANOVA comparison. But how to impute from this model if mean variance for a trial is unknown....
@@
 # Run a linear model with Yield error as a fixed effect predictor and Trial as a random intercept
-PM_MB_trianLMERx <- lmer(Yield_error ~ 1 +
-                            (`grain_yield.t.ha.` | trial_ref), data = PM_MB_train)
+PM_MB_trianLMERx <- lmer(yield_error ~ 1 +
+                            (`grain_yield.t.ha` | trial_ref), data = PM_MB_train)
 
@@
 
-meta_mean.GY <- mean(PM_MB_means.SV$grain_yield.t.ha., na.rm = TRUE)
+meta_mean.GY <- mean(PM_MB_means.SV$grain_yield.t.ha, na.rm = TRUE)
 
@@
    summarise(
-      trial_mean = mean(grain_yield.t.ha., na.rm = TRUE),
-      BW_trial_variance = sd(grain_yield.t.ha., na.rm = TRUE) ^ 2
+      trial_mean = mean(grain_yield.t.ha, na.rm = TRUE),
+      BW_trial_variance = sd(grain_yield.t.ha, na.rm = TRUE) ^ 2
    )

### 2019-09-14 05_MetaAnalysis.Rmd
Use barplot in place of table for dose/ha tebu ai

@@
 Amistar Xtra is a combination of azoxystrobin and cyproconazole.
-Perhaps Amistar Xtra and Custodia might be able to be pooled given they both contain strobilurin and triazole, however they contain differing dose ratio (inverted).
+Custodia is a combination of tebuconazole and azoxystrobin.
+Perhaps Amistar Xtra and Custodia might be able to be pooled given they both contain strobilurin and triazole, however they contain differing dose ratios (inverted).
 
@@
 
-Preliminary analysis of fungicides show there is a difference the effect of fungicide in proportion of yield gained
+Preliminary analysis of fungicides show there is a difference the effect of fungicide in proportion of yield saved.
 
 ### Fungicide Doses
+
 All trials that used tebuconazole used approximately the same dose.
-Dose of the active ingredient ranged from 62.35 grams per hectare to 60 grams per hectare.
+Dose of the active ingredient ranged from 62.35&nbsp;g per hectare to 60&nbsp;g per hectare.
 

### 2019-09-15 05_MetaAnalysis.Rmd
Update 05_MetaAnalysis.Rmd
This DOES knit, however it needs to be thorougly checked and validated against Paul's original work to be sure that we're getting what we want. Some models do fail to converge. Need to address that.

- Use graphs in place of tables

- Spelling corrections

- Import data and format cols correctly

- Put line breaks in text for easier Git commit tracking

@@
 author: "P. Melloy"
-date: "04/07/2019"
+date: "`r Sys.Date()`"
 output: html_document
@@
 
-```{r MEsummary_Libraries}
+```{r MEsummary_Libraries, message=FALSE}
 library(tidyverse)
-library(kableExtra)
-library(leaflet)
+library(theme.usq)
 ```
@@
 
-## Data-wrangling
-
-```{r Meta_dataImport, message=FALSE}
+```{r data_import, message=FALSE, echo=FALSE}
 PM_MB_means <-
@@
 
-## Investigating data and the number of factors represented in each trial
+## Visualise Data
+
+Visualise and inspect the number of factors represented in each trial.
 
@@
    rename(Trials = n) %>%
-   kable()
-
-# How many trials do we have if Tebe and Propi are pooled?
-
+   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
+   xlab("Fungicide active ingredient") +
+   ylab("N Trials") +
+   geom_col() +
+   scale_fill_usq() +
+   scale_colour_usq() +
+   theme_usq() +
+   coord_flip()
 ```
 
-Tebuconazole and propiconazole might be able to be pooled as a 'triazole' fungicide treatment. 
+Tebuconazole and propiconazole might be able to be pooled as a triazole fungicide treatment. 
 Amistar Xtra is a combination of azoxystrobin and cyproconazole.
 Custodia is a combination of tebuconazole and azoxystrobin.
-Perhaps Amistar Xtra and Custodia might be able to be pooled given they both contain strobilurin and triazole, however they contain differing dose ratios (inverted).
+Amistar Xtra and Custodia might be able to be pooled given they both contain strobilurin and triazole, however, they contain differing dose ratios (inverted).
 
@@
 
-```{r Tebe_dose}
+```{r tebu_dose}
 PM_MB_means %>%
@@
           first_sign_disease,
-          dose_ai.ha,
+          dose_ai_f1_g.ha,
           total_fungicide) %>%
-   kable()
+   ggplot(aes(x = as.factor(dose_ai_f1_g.ha))) +
+   xlab("Dose (g ai/ha)") +
+   geom_bar() +
+   scale_fill_usq() +
+   scale_colour_usq() +
+   theme_usq()
 ```
@@
 
-Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease and crop yield.
-The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows did increase yield significantly.
-Seven trials used a row spacing of 0.75 meters.
+Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease.
+The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows did increase yield significantly, which has been shown by Kerry McKenzie's work as well.
+Eight trials used a row spacing of 0.75&nbsp;meters and tebuconazole as an active ingredient (AI).
 
@@
 PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole") %>%
-   group_by(row_spacing.m, trial_ref) %>%
+   filter(fungicide_ai == "tebuconazole" | fungicide_ai == "propiconazole") %>%
+   group_by(fungicide_ai, row_spacing.m, trial_ref) %>%
    summarise() %>%
@@
    rename(Trials = n) %>%
-   kable()
-
-PM_MB_means %>%
-   filter(fungicide_ai == "propiconazole") %>%
-   group_by(row_spacing.m, trial_ref) %>%
-   summarise() %>%
-   count() %>%
-   rename(Trials = n) %>%
-   kable()
+   ggplot(aes(x = as.factor(row_spacing.m), y = Trials)) +
+   xlab("Row Spacing (m)") +
+   ylab("N Trials") +
+   ggtitle(label = "Trial row spacings using tebuconazole") +
+   geom_col(aes(fill = fungicide_ai),
+            position = "dodge") +
+   scale_fill_usq(name = "Fungicide AI") +
+   theme_usq()
 
@@
    filter(fungicide_ai == "tebuconazole",
-         row_spacing.m == 0.75) 
+         row_spacing.m == 0.75) %>% 
+   glimpse()
 ```
@@
    rename(Treatments = n) %>%
-   kable()
+   ggplot(aes(x = host_genotype, y = Treatments)) +
+   xlab("Cultivar") +
+   ylab("N Trials") +
+   ggtitle(label = "Cultivars used in tebuconazole trials with 0.75 m row spacing") +
+   geom_col() +
+   scale_fill_usq() +
+   scale_colour_usq() +
+   theme_usq()
 ```
+
 In general the mungbean varieties have the following resistance to powdery mildew.
+
    - Berken: Highly susceptible
+
    - Crystal: Susceptible
+
    - Jade: Moderately susceptible
@@
 ```{r variance}
+# Trials using tebuconazole
 PM_MB_means %>%
@@
    group_by(trial_ref, location, y_error.type) %>%
-   summarise(tebu_treatments = length(y_error.type))
+   summarise(tebuconazole_trts = length(y_error.type))
 
+# Trials using propiconazole
 PM_MB_means %>%
@@
    group_by(trial_ref, location, y_error.type) %>%
-   summarise(Tebe_Treatments = length(y_error.type))
-colnames(PM_MB_means)
+   summarise(propiconazole_trts = length(y_error.type))
 ```
@@
    distinct()
+Trials
 ```
 
-The trial, `mung1112/02` uses Least square differences to describe the variation within the experiment.
+The trial, `mung1112/02` uses Least Square Differences (LSD) to describe the variation within the experiment.
 The following code attempts to convert this to sampling variance as per the method in [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
@@
 
-![Calculating sampling variance from mean squared error Paul et. al. (2008)](Paul_etal_2008.PNG)
+![Calculating sampling variance from mean squared error Paul et al. (2008)](Paul_etal_2008.PNG)
 
@@
 # Sv <- sem^2 <- stdev/sqrt(n)
-# Sampling variance eqauls the square of the standard error.
+# Sampling variance equals the square of the standard error.
 # Sv <- (stdev/sqrt(n))^2
@@
 The trial which does not report any type of variance also reports that there is no significant difference between the means.
+
 ```{r}
@@
 et.
-al (2017)](http://apsjournals.apsnet.org/doi/10.1094/PDIS-03-17-0340-RE) [Paul et.
-al.
+al (2017)](http://apsjournals.apsnet.org/doi/10.1094/PDIS-03-17-0340-RE) [Paul et al.
 (2007)](https://apsjournals.apsnet.org/doi/pdfplus/10.1094/PHYTO-97-2-0211) uses linear regression model to estimate sampling variance.
 
-```{r na2Sampling_variance}
+```{r na2Sampling_variance, message=FALSE}
 library(lme4)
@@
 # Run a linear model with grain_yield.t.ha as a fixed effect predictor and trial as a random intercept
-PM_MB_trianLMER <- lmer(yield_error ~ grain_yield.t.ha +
+PM_MB_trainLMER <- lmer(yield_error ~ grain_yield.t.ha +
                            (1 | trial_ref), data = PM_MB_train)
-summary(PM_MB_trianLMER)
+summary(PM_MB_trainLMER)
 
-# grain yeild (in this model) IS a significant predictor for yeild error (t value = 5.826)
-#  And the variance increases as the mean increases
-# does log transformation improve the model?
+# grain yield (in this model) IS a significant predictor for yield error
+# (t value = 5.826)
+# And the variance increases as the mean increases does log transformation
+# improve the model?
 
-PM_MB_trianLMER.1 <- lmer(log(yield_error) ~ `grain_yield.t.ha` +
+PM_MB_trainLMER.1 <- lmer(log(yield_error) ~ `grain_yield.t.ha` +
                              (1 | trial_ref), data = PM_MB_train)
-summary(PM_MB_trianLMER.1) # grain yeild a significant predictor of log(yeild error)
-anova(PM_MB_trianLMER, PM_MB_trianLMER.1) # no significant difference between the models
+summary(PM_MB_trainLMER.1) # grain yield a significant predictor of log(yield error)
+anova(PM_MB_trainLMER, PM_MB_trainLMER.1) # no significant difference between the models
 
-PM_MB_trianLMER.2 <- lmer(yield_error ~ log(`grain_yield.t.ha`) +
+PM_MB_trainLMER.2 <- lmer(yield_error ~ log(`grain_yield.t.ha`) +
                              (1 | trial_ref), data = PM_MB_train)
-summary(PM_MB_trianLMER.2) # log(grain yeild) is a significant predictor of yeild error
-anova(PM_MB_trianLMER, PM_MB_trianLMER.2) # no significant difference between the models
+summary(PM_MB_trainLMER.2) # log(grain yeild) is a significant predictor of yield error
+anova(PM_MB_trainLMER, PM_MB_trainLMER.2) # no significant difference between the models
 
-PM_MB_trianLMER.3 <-
+PM_MB_trainLMER.3 <-
    lmer(log(yield_error) ~ log(`grain_yield.t.ha`) +
@@
         data = PM_MB_train)
-summary(PM_MB_trianLMER.3) # log(grain yeild) is a significant predictor of log(yeild error)
-anova(PM_MB_trianLMER, PM_MB_trianLMER.3) # no significant difference between the models
+summary(PM_MB_trainLMER.3) # log(grain yeild) is a significant predictor of log(yielderror)
+anova(PM_MB_trainLMER, PM_MB_trainLMER.3) # no significant difference between the models
 
 # Lets try with Fungicide as a fixed effect
-PM_MB_trianLMER.4 <-
+PM_MB_trainLMER.4 <-
    lmer(yield_error ~ `grain_yield.t.ha` + as.factor(fungicide_ai) +
@@
         data = PM_MB_train)
-summary(PM_MB_trianLMER.4)
-anova(PM_MB_trianLMER, PM_MB_trianLMER.4) # no significant difference between the models
+summary(PM_MB_trainLMER.4)
+anova(PM_MB_trainLMER, PM_MB_trainLMER.4) # no significant difference between the models
 
 #log transforming the response or predictor variables did not improve the model therefore I will leave it untransformed
-# I will be using the first model PM_MB_trianLMER for further analyses beyond this point
+# I will be using the first model PM_MB_trainLMER for further analyses beyond this point
 
-# Extract the model cooeficients
+# Extract the model coefficients
 paramA <-
-   (summary(PM_MB_trianLMER)$coef)[2, 1] # Extract the overall mean Slope to predict Yield error
+   (summary(PM_MB_trainLMER)$coef)[2, 1] # Extract the overall mean slope to predict Yield error
 InterC <-
-   (summary(PM_MB_trianLMER)$coef)[1, 1] # Extract the overall mean intercept to predict Yield error
+   (summary(PM_MB_trainLMER)$coef)[1, 1] # Extract the overall mean intercept to predict Yield error
 lmer.coef <-
-   coef(PM_MB_trianLMER) # extracting the mean random intercept for each of trial variables
+   coef(PM_MB_trainLMER) # extracting the mean random intercept for each of trial variables
 
@@
 ggplot(PM_MB_train) +
-   geom_point(aes(y = yield_error, x = `grain_yield.t.ha`, colour = trial_ref)) +
+   geom_point(aes(y = yield_error, x = grain_yield.t.ha, colour = trial_ref)) +
    geom_abline(
@@
       size = 1,
-      colour = c("Black", hue_pal()(11))
+      colour = c("Black", hue_pal()(16))
    ) +
-   coord_cartesian(xlim = c(0, 3))
+   coord_cartesian(xlim = c(0, 3)) +
+   theme_usq()
+```
 
-```
 ```{r na2Sv_formula}
-
 for (i in NATrials$trial_ref) {
@@
 }
-
 ```
 
-Lets look at the model without the trial mung1718/01, as it looks to be adding some skew.
+Let's look at the model without the trial mung1718/01, as it looks to be adding some skew.
+
 ```{r lmer_remove_mung1718-01}
@@
 # Rerun the model
-PM_MB_trianLMER.5 <- lmer(yield_error ~ `grain_yield.t.ha` +
+PM_MB_trainLMER.5 <- lmer(yield_error ~ `grain_yield.t.ha` +
                              (1 | trial_ref), data = PM_MB_train.2)
-summary(PM_MB_trianLMER.5) # no significant effect of mean grain yield on yeild error
+summary(PM_MB_trainLMER.5) # no significant effect of mean grain yield on yield error
 
@@
 paramA <-
-   (summary(PM_MB_trianLMER.5)$coef)[2, 1] # Extract the overall mean Slope to predict Yield error
+   (summary(PM_MB_trainLMER.5)$coef)[2, 1] # Extract the overall mean Slope to predict Yield error
 InterC <-
-   (summary(PM_MB_trianLMER.5)$coef)[1, 1] # Extract the overall mean intercept to predict Yield error
+   (summary(PM_MB_trainLMER.5)$coef)[1, 1] # Extract the overall mean intercept to predict Yield error
 lmer.coef <-
-   coef(PM_MB_trianLMER.5) # extracting the mean random intercept for each of trial variables
+   coef(PM_MB_trainLMER.5) # extracting the mean random intercept for each of trial variables
 
@@
 ggplot(PM_MB_train.2) +
-   geom_point(aes(y = yield_error, x = `grain_yield.t.ha`, colour = trial_ref)) +
+   geom_point(aes(y = yield_error, x = grain_yield.t.ha, colour = trial_ref)) +
    geom_abline(
@@
       size = 1,
-      colour = c("Black", hue_pal()(10))
+      colour = c("Black", hue_pal()(15))
    ) +
-   coord_cartesian(ylim = c(0, 0.33))
-
+   coord_cartesian(ylim = c(0, 0.33)) +
+   xlab("Grain Yield (t/ha)") +
+   ylab("Yield Error") +
+   scale_colour_discrete("Trial Reference") +
+   theme_usq()
 ```
 
-Just for kicks lets look at the linear regression model as a Random effects model where `grain_yield.t.ha` is set as a random slope to the random intercept `trial_ref`.  
-The model fits better as shown by an ANOVA comparison. But how to impute from this model if mean variance for a trial is unknown....
+Just for kicks lets look at the linear regression model as a random effects model where `grain_yield.t.ha` is set as a random slope to the random intercept `trial_ref`.
+
+The model fits better as shown by an ANOVA comparison. But how to impute from this model if mean variance for a trial is unknown...
+
 ```{r random_slope_model}
+# Run a linear model with yield error as a fixed effect predictor and trial as a random intercept
+PM_MB_trainLMERx <- lmer(yield_error ~ 1 +
+                            (grain_yield.t.ha |
+                                trial_ref), data = PM_MB_train)
 
-# Run a linear model with Yield error as a fixed effect predictor and Trial as a random intercept
-PM_MB_trianLMERx <- lmer(yield_error ~ 1 +
-                            (`grain_yield.t.ha` | trial_ref), data = PM_MB_train)
+anova(PM_MB_trainLMER, PM_MB_trainLMERx) # random slope model NOT significantly better # P = 0.6677
 
-anova(PM_MB_trianLMER, PM_MB_trianLMERx) # random slope model NOT significantly better # P = 0.6677
-
-summary(PM_MB_trianLMERx)
+summary(PM_MB_trainLMERx)
 
 InterC <-
-   (summary(PM_MB_trianLMER)$coef)[1, 1] # Extract the overall mean intercept
+   (summary(PM_MB_trainLMER)$coef)[1, 1] # Extract the overall mean intercept
 
-lmer.coefx <- coef(PM_MB_trianLMERx)
+lmer.coefx <- coef(PM_MB_trainLMERx)
 
@@
       size = 1,
-      colour = hue_pal()(11)
+      colour = hue_pal()(16)
    ) +
    coord_cartesian(xlim = c(0, 3),
-                   ylim = c(0, 1))
+                   ylim = c(0, 1)) +
+   xlab("Grain Yield (t/ha)") +
+   ylab("Yield Error") +
+   scale_colour_discrete("Trial Reference") +
+   theme_usq()
 ```
 
-After much deliberation I don't think this is possible to use the model with grain yield/ha as a random slope.
-Even though we know the grain yields and the mean in the grain yields we still can't predict the effect of the random intercept trial on the yield error.
-I also re-ran the model without including the trial which we used LSD to interpret the sampling variance and the model lost a lot of significance.
+After much deliberation I don't think this is possible to use the model with grain yield t/ha as a random slope.
+Even though we know the grain yields and the mean of the grain yields, we still can't predict the effect of the random intercept trial on the yield error.
 
-Emerson proposed I look at the between trial variation
+I also re-ran the model without including the trial in which we used LSD to interpret the sampling variance and the model lost a lot of significance.
+
+## Between trial variation
+
+Emerson proposed I look at the between trial variation.
 
@@
 PM_MB_means.SV <-
-   PM_MB_means[PM_MB_means$y_error.type == "SamplingVariance", ]
+   filter(PM_MB_means, y_error.type == "SamplingVariance")
 
@@
    )
-PM_MB_means_T
 
-All_Trials <- unique(PM_MB_means$trial_ref)
-PM_MB_means$TrialVariance <- NA
+PM_MB_means <- left_join(PM_MB_means, PM_MB_means_T, by = "trial_ref")
 
-for (i in All_Trials) {
-   PM_MB_means[PM_MB_means$trial_ref == i, "TrialVariance"] <-
-      PM_MB_means_T[PM_MB_means_T$trial_ref == i, "BW_trial_variance"]
-}
-
-PM_MB_means$TrialVariance
-
-summary(lm(BW_trial_variance ~ trial_mean, data = PM_MB_means_T))
+summary(lm(BW_trial_variance ~ trial_mean, data = PM_MB_means))
 summary(lm(
    BW_trial_variance ~ trial_mean,
-   data = subset(PM_MB_means_T, fungicide_ai == "tebuconazole")
+   data = subset(PM_MB_means, fungicide_ai == "tebuconazole")
 ))
@@
    BW_trial_variance ~ trial_mean,
-   data = subset(PM_MB_means_T, fungicide_ai == "propiconazole")
+   data = subset(PM_MB_means, fungicide_ai == "propiconazole")
 ))
 
-plot(BW_trial_variance ~ trial_mean, data = PM_MB_means_T)
+plot(BW_trial_variance ~ trial_mean, data = PM_MB_means)
 abline(-0.01356, 0.03076)

### 2019-09-15 05_MetaAnalysis.Rmd
Use sampling variance only studies on line 499

@@
    "SamplingVariance"
-
 ```
@@
 
-PM_MB_means_T <- PM_MB_means %>%
+PM_MB_means_T <- PM_MB_means.SV %>%
    group_by(trial_ref) %>%
@@
 abline(-0.01356, 0.03076)
-
 ```

### 2019-09-15 R/import_data.R
Add function to import data

@@ -1,0 +1,38 @@
+
+#' Import mungbean powdery mildew data
+#'
+#' Imports mungbean powdery mildew data and formats columns correctly.
+#'
+#' @return a Tibble of mungbean powdery mildew trial data
+#'
+#' @examples
+#'
+#' PM_MB_means <- import_data()
+#'
+import_data <- function() {
+   x <-
+      read_csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
+   x <- x %>%
+      mutate(trial_ref = as.factor(trial_ref)) %>%
+      mutate(location = as.factor(location)) %>%
+      mutate(host_genotype = as.factor(host_genotype)) %>%
+      mutate(fungicide_ai = as.factor(fungicide_ai)) %>%
+      mutate(trade_name = as.factor(trade_name)) %>%
+      mutate(year = as.factor(year)) %>%
+      mutate(replicates = as.factor(replicates)) %>%
+      mutate(planting_date = as.Date(planting_date, format = "%d/%m/%Y")) %>%
+      mutate(emergence_date = as.Date(emergence_date, format = "%d/%m/%Y")) %>%
+      mutate(flowering_date = as.Date(flowering_date, format = "%d/%m/%Y")) %>%
+      mutate(pod_final_date = as.Date(pod_final_date, format = "%d/%m/%Y")) %>%
+      mutate(mid_late_pod_final = as.Date(mid_late_pod_final, format = "%d/%m/%Y")) %>%
+      mutate(first_sign_disease = as.Date(first_sign_disease, format = "%d/%m/%Y")) %>%
+      mutate(fungicide_application_1 = as.Date(fungicide_application_1, format = "%d/%m/%Y")) %>%
+      mutate(fungicide_application_2 = as.Date(fungicide_application_2, format = "%d/%m/%Y")) %>%
+      mutate(fungicide_application_3 = as.Date(fungicide_application_3, format = "%d/%m/%Y")) %>%
+      mutate(fungicide_application_4 = as.Date(fungicide_application_4, format = "%d/%m/%Y")) %>%
+      mutate(fungicide_application_5 = as.Date(fungicide_application_5, format = "%d/%m/%Y")) %>%
+      mutate(fungicide_application_6 = as.Date(fungicide_application_6, format = "%d/%m/%Y")) %>%
+      mutate(fungicide_application_7 = as.Date(fungicide_application_7, format = "%d/%m/%Y")) %>%
[…]

### 2019-09-15 R/Cleaning historical data.R
Move R scripts to ./R

@@ -1,0 +1,1686 @@
+# This script is dedicated to
+# importing and cleaning previous powdery mildew experimental field trial data.
+
+# install.packages("openxlsx")
+# install.packages("readxl")
+# install.packages("tidyr")
+
+library(openxlsx)
+library(readxl)
+library(tidyr)
+library(dplyr)
+library(data.table)
+
+# Year #  Trial location  #  Sowing date
+
+# ____________________________________________________________
+# _____________            Hermitage  2010        ____________
+
+Herm_10 <-
+   read_xls(
+      "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/Past Trials/2010/2010 PMmung Herm/2010 PMmung hermitage RAW field book.xls",
+      sheet = "For analysis"
+   )
+
+Herm_10_m <- Herm_10 %>%
+   group_by(`Cultivar!`, `Treat!`, `Description!`) %>%
+   summarise_all(list(~ mean(., na.rm = TRUE),  ~ sd(., na.rm = TRUE)))
+
+write.csv(
+   as.data.frame(Herm_10_m),
+   "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/2010 PMmung Hermitage means.csv"
+)
+
+
+# ____________________________________________________________
+# _____________            Hermitage  2011        ____________
+
+Herm_11 <-
+   read_xls(
+      "C:/Users/U8011054/OneDrive - USQ//Cloudstor/Mungbean/Past trials/2011/2011 PMmung Herm/pmhermratings2011.xls",
+      sheet = "Analyses factor"
+   )
+
+
+new_cols <- as.data.table(tstrsplit(Herm_11$'Treatment!', " "))
+colnames(new_cols) <- c("spray_n", "spray", "fungicide")
+Herm_11 <-
+   cbind(new_cols, as.data.table(Herm_11)[, 'Treatment!' := NULL])
+#Herm_11$`Yld Kg ha` <- as.numeric(Herm_11$`Yld Kg ha`)
+head(Herm_11)
+
+Herm_11_m <- Herm_11 %>%
+   group_by(`Cultivar!`, `Tr`, `fungicide`, `spray_n`) %>%
[…]

### 2019-09-15 getPPD2.R
Delete getPPD2.R

@@ -1,64 +1,0 @@
-#' Download PPD data
-#' 
-#' Download PPD data for a station and return as a data frame
-#'
-#' @param id Weather station ID.
-#' @param start Start date (String YYYYmmdd).
-#' @param end End date (String YYYYmmdd).
-#' @param silo.apiKey SILO API key (available from https://silo.longpaddock.qld.gov.au/).
-#' @param variables Vector of weather variables (Full list available  at https://silo.longpaddock.qld.gov.au/climate-variables)
-#'
-#' @author Paul Melloy & Fiona Evans
-#' 
-#' @return Data frame containing daily weather data.
-#' @export
-
-
-getPPD2 <- function(station_id, lat, long, start, end, silo.apikey, variables) {
-if(missing(lat)|missing(long)){
-# 'If' statement for when user does not specify variables
-   if(missing(variables)){
-      variables <- paste("daily_rain", "max_temp", "min_temp", "rh_tmax", "rh_tmin","vp", "vp_deficit", "radiation",
-              sep = ",")
-   }
-
-   
-url <- "https://siloapi.longpaddock.qld.gov.au/pointdata?apikey="
-
-
-   print(paste0(url,silo.apikey , "&start=", start,  "&finish=", end,  "&station=", station_id,  "&format=csv", "&variables=", variables))
-read.csv(paste0(url,silo.apikey , "&start=", start,  "&finish=", end,  "&station=", station_id,  "&format=csv", "&variables=", variables))
-
-
-
-}else{ 
-   if(missing(station_id)) {
-   # 'If' statement for when user does not specify variables
-   if(missing(variables)){
-      variables <- paste("daily_rain", "max_temp", "min_temp", "rh_tmax", "rh_tmin","vp", "vp_deficit", "radiation",
-                         sep = ",")
-   }
-   
-   url <- "https://siloapi.longpaddock.qld.gov.au/pointdata?apikey="
-   
-   print(paste0(url,silo.apikey , "&start=", start,  "&finish=", end,  "&lat=", lat, "&lon=",long,  "&format=csv", "&variables=", variables))   
-read.csv(paste0(url,silo.apikey , "&start=", start,  "&finish=", end,  "&lat=", lat, "&lon=",long,  "&format=csv", "&variables=", variables))
-
-
-   
-   
-}
-   
-}
-   
-}
-
[…]

### 2019-09-15 Cleaning historical data.R
Delete Cleaning historical data.R

@@ -1,1686 +1,0 @@
-# This script is dedicated to
-# importing and cleaning previous powdery mildew experimental field trial data.
-
-# install.packages("openxlsx")
-# install.packages("readxl")
-# install.packages("tidyr")
-
-library(openxlsx)
-library(readxl)
-library(tidyr)
-library(dplyr)
-library(data.table)
-
-# Year #  Trial location  #  Sowing date
-
-# ____________________________________________________________
-# _____________            Hermitage  2010        ____________
-
-Herm_10 <-
-   read_xls(
-      "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/Past Trials/2010/2010 PMmung Herm/2010 PMmung hermitage RAW field book.xls",
-      sheet = "For analysis"
-   )
-
-Herm_10_m <- Herm_10 %>%
-   group_by(`Cultivar!`, `Treat!`, `Description!`) %>%
-   summarise_all(list(~ mean(., na.rm = TRUE),  ~ sd(., na.rm = TRUE)))
-
-write.csv(
-   as.data.frame(Herm_10_m),
-   "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/2010 PMmung Hermitage means.csv"
-)
-
-
-# ____________________________________________________________
-# _____________            Hermitage  2011        ____________
-
-Herm_11 <-
-   read_xls(
-      "C:/Users/U8011054/OneDrive - USQ//Cloudstor/Mungbean/Past trials/2011/2011 PMmung Herm/pmhermratings2011.xls",
-      sheet = "Analyses factor"
-   )
-
-
-new_cols <- as.data.table(tstrsplit(Herm_11$'Treatment!', " "))
-colnames(new_cols) <- c("spray_n", "spray", "fungicide")
-Herm_11 <-
-   cbind(new_cols, as.data.table(Herm_11)[, 'Treatment!' := NULL])
-#Herm_11$`Yld Kg ha` <- as.numeric(Herm_11$`Yld Kg ha`)
-head(Herm_11)
-
-Herm_11_m <- Herm_11 %>%
-   group_by(`Cultivar!`, `Tr`, `fungicide`, `spray_n`) %>%
[…]

### 2019-09-15 05_MetaAnalysis.Rmd
Use import_data() function

@@
 library(theme.usq)
+source("R/import_data.R")
 ```
@@
 ```{r data_import, message=FALSE, echo=FALSE}
-PM_MB_means <-
-   read_csv(
-      "data/1902 powdery mildew-Mungbean - Collated means.csv"
-   )
-
-# convert coltypes
-PM_MB_means <-
-   PM_MB_means %>%
-   mutate(year = as.integer(year)) %>%
-   mutate(replicates = as.integer(replicates)) %>%
-   mutate(planting_date = as.Date(planting_date, format = "%d/%m/%Y")) %>%
-   mutate(emergence_date = as.Date(emergence_date, format = "%d/%m/%Y")) %>%
-   mutate(flowering_date = as.Date(flowering_date, format = "%d/%m/%Y")) %>%
-   mutate(pod_final_date = as.Date(pod_final_date, format = "%d/%m/%Y")) %>%
-   mutate(mid_late_pod_final = as.Date(mid_late_pod_final, format = "%d/%m/%Y")) %>%
-   mutate(first_sign_disease = as.Date(first_sign_disease, format = "%d/%m/%Y")) %>%
-   mutate(fungicide_application_1 = as.Date(fungicide_application_1, format = "%d/%m/%Y")) %>%
-   mutate(fungicide_application_2 = as.Date(fungicide_application_2, format = "%d/%m/%Y")) %>%
-   mutate(fungicide_application_3 = as.Date(fungicide_application_3, format = "%d/%m/%Y")) %>%
-   mutate(fungicide_application_4 = as.Date(fungicide_application_4, format = "%d/%m/%Y")) %>%
-   mutate(fungicide_application_5 = as.Date(fungicide_application_5, format = "%d/%m/%Y")) %>%
-   mutate(fungicide_application_6 = as.Date(fungicide_application_6, format = "%d/%m/%Y")) %>%
-   mutate(fungicide_application_7 = as.Date(fungicide_application_7, format = "%d/%m/%Y")) %>%
-   mutate(harvest_date = as.Date(harvest_date, format = "%d/%m/%Y")) %>%
-   mutate(final_assessment = as.Date(final_assessment, format = "%d/%m/%Y"))
+PM_MB_means <- import_data()
 ```

### 2019-09-15 03_Preliminary_analysis.Rmd
Format Rmd

@@
 library(theme.usq)
+source("R/import_data.R")
 #source("./getPPD2.R")
@@
    1) Fungicide type
+
    2) Fungicide dose
-   3) row spacing
+
+   3) Row spacing
+
    4) Host cultivars (probably is a covariate with season due to changing cultivars over time)
+
    5) Experiment location
+
    6) Final disease rating
@@
 # Import data
-PM_MB_means <-
-   read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
+PM_MB_means <- import_data()
 colnames(PM_MB_means)
-PM_MB_means$Fungicide_application_1[as.character(PM_MB_means$Fungicide_application_1) == ""] <-
-   NA
-PM_MB_means$Fungicide_application_2[as.character(PM_MB_means$Fungicide_application_2) == ""] <-
-   NA
-PM_MB_means$Fungicide_application_3[as.character(PM_MB_means$Fungicide_application_3) == ""] <-
-   NA
-PM_MB_means$Fungicide_application_4[as.character(PM_MB_means$Fungicide_application_4) == ""] <-
-   NA
-PM_MB_means$Fungicide_application_5[as.character(PM_MB_means$Fungicide_application_5) == ""] <-
-   NA
-PM_MB_means$Fungicide_application_6[as.character(PM_MB_means$Fungicide_application_6) == ""] <-
-   NA
-PM_MB_means$Fungicide_application_7[as.character(PM_MB_means$Fungicide_application_7) == ""] <-
-   NA
-
-# Rewrite all variations of sulphur treatments as just sulphur
-PM_MB_means$Fungicide[PM_MB_means$Fungicide == "Sulphur" |
-                         PM_MB_means$Fungicide == "Sulphur (SC)" |
-                         PM_MB_means$Fungicide == "Sulphur (Ultra SC)" |
-                         PM_MB_means$Fungicide == "Sulphur (WP)"] <- "Sulphur"
 ```

### 2019-09-15 02_Weather.Rmd
Use custom import_data() function

@@
 # Import dataset
-PM.dat <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
+PM.dat <-
+   read_csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
+PM.dat <- PM.dat %>%
+   mutate(trial_ref = as.factor(trial_ref)) %>%
+   mutate(location = as.factor(location)) %>%
+   mutate(host_genotype = as.factor(host_genotype)) %>%
+   mutate(fungicide_ai = as.factor(fungicide_ai)) %>%
+   mutate(trade_name = as.factor(trade_name)) %>%
+   mutate(year = as.factor(year)) %>%
+   mutate(replicates = as.factor(replicates)) %>%
+   mutate(planting_date = as.Date(planting_date, format = "%d/%m/%Y")) %>%
+   mutate(emergence_date = as.Date(emergence_date, format = "%d/%m/%Y")) %>%
+   mutate(flowering_date = as.Date(flowering_date, format = "%d/%m/%Y")) %>%
+   mutate(pod_final_date = as.Date(pod_final_date, format = "%d/%m/%Y")) %>%
+   mutate(mid_late_pod_final = as.Date(mid_late_pod_final, format = "%d/%m/%Y")) %>%
+   mutate(first_sign_disease = as.Date(first_sign_disease, format = "%d/%m/%Y")) %>%
+   mutate(fungicide_application_1 = as.Date(fungicide_application_1, format = "%d/%m/%Y")) %>%
+   mutate(fungicide_application_2 = as.Date(fungicide_application_2, format = "%d/%m/%Y")) %>%
+   mutate(fungicide_application_3 = as.Date(fungicide_application_3, format = "%d/%m/%Y")) %>%
+   mutate(fungicide_application_4 = as.Date(fungicide_application_4, format = "%d/%m/%Y")) %>%
+   mutate(fungicide_application_5 = as.Date(fungicide_application_5, format = "%d/%m/%Y")) %>%
+   mutate(fungicide_application_6 = as.Date(fungicide_application_6, format = "%d/%m/%Y")) %>%
+   mutate(fungicide_application_7 = as.Date(fungicide_application_7, format = "%d/%m/%Y")) %>%
+   mutate(harvest_date = as.Date(harvest_date, format = "%d/%m/%Y")) %>%
+   mutate(final_assessment = as.Date(final_assessment, format = "%d/%m/%Y"))
 
@@
       Year = substr(king_Tm_aver$date, start = 1, stop = 4),
-      Day = year.day(king_Tm_aver$date)
+      Day = ymd(king_Tm_aver$date)
    )
@@
 King_FS <- PM.dat %>%
-   group_by(Trial_ref, Location, Year) %>%
-   summarise(First_sign = mean(as.Date(first_sign_disease), na.rm = T)) %>%
-   filter(Location == "Kingaroy") %>%
-   mutate(Day = year.day(First_sign))
+   group_by(trial_ref, location, year) %>%
+   summarise(first_sign = mean(as.Date(first_sign_disease), na.rm = T)) %>%
+   filter(location == "Kingaroy") %>%
+   mutate(day = ymd(first_sign))
 str(king_Tm_aver)
 str(King_FS)
-ggplot(subset(king_Tm_aver, Year == levels(factor(King_FS$Year))),
-       aes(Day)) +
-   geom_line(aes(y = max_T, colour = Year)) +
+ggplot(subset(king_Tm_aver, year == levels(factor(King_FS$year))),
+       aes(day)) +
+   geom_line(aes(y = max_T, colour = year)) +
    #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
@@
    geom_vline(
-      xintercept = King_FS$Day[1],
+      xintercept = King_FS$day[1],
       size = 1,
@@
    geom_vline(
-      xintercept = King_FS$Day[2],
+      xintercept = King_FS$day[2],
       size = 1.5,

### 2019-09-18 05_MetaAnalysis.Rmd
- Comment NA2SamplingVariance chunk - edited ggplot code to accept changes in number of trials in the colouring scheme - Corrected between_trial_variation chunk to look summarise linear model of trial variation

@@
 author: "P. Melloy"
-date: "`r Sys.Date()`"
+date: "04/07/2019"
 output: html_document
@@
 
-```{r MEsummary_Libraries, message=FALSE}
-library(tidyverse)
-library(theme.usq)
-source("R/import_data.R")
+```{r MEsummary_Libraries}
+library(dplyr)
+library(openxlsx)
+library(kableExtra)
+library(ggplot2)
+library(lme4)
+library(leaflet)
+#source("./getPPD2.R")
+
 ```
@@
 
-```{r data_import, message=FALSE, echo=FALSE}
-PM_MB_means <- import_data()
+## Data-wrangling
+
+```{r Meta_dataImport}
+PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv", stringsAsFactors = FALSE)
+PM_MB_means$grain_yield.t.ha. <- as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data
+
+#str(PM_MB_means)
 ```
 
-## Visualise Data
-
-Visualise and inspect the number of factors represented in each trial.
+## Investigating data and the number of factors represented in each Trial
 
 ### Fungicides
-
-When investigating previous studies into powdery mildew fungicide efficacy on mungbean `r length(unique(PM_MB_means$trial_ref))` trials were found.
-However, only eleven tebuconazole were used for the following meta-analysis, followed by the next most common fungicide, propiconazole. Sulphur was disregarded due to its inconsistency in efficacy.
+When investigating previous studies into Powdery Mildew Fungicide efficacy on Mungbean `r length(unique(PM_MB_means$Trial_ref))` trials were found, however only eleven Tebeconazol were used for the following meta-analysis, followed by the next common Fungicide Propiconazole.
+Sulphur was disregarded due to it's inconsistancy in efficacy.
 
 ```{r Fungicides}
+#unique(PM_MB_means$Fungicide)
 PM_MB_means %>%
-   group_by(fungicide_ai, trial_ref) %>%
+   group_by(Fungicide,Trial_ref) %>%
    summarise() %>%
-   count(sort = TRUE) %>%
+   count(sort = T) %>%
    rename(Trials = n) %>%
-   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
-   xlab("Fungicide active ingredient") +
-   ylab("N Trials") +
-   geom_col() +
-   scale_fill_usq() +
-   scale_colour_usq() +
-   theme_usq() +
-   coord_flip()
+   kable()
+
+# How many trials do we have if Tebe and Propi are pooled?
+
 ```
+Tebeconazole and propiconazole might be able to be pooled as a 'Triazole' fungicide treatment.
+Amistar is a combination of Azoxistrobin and Cyproconazole.
+Perhaps Amistar and 200 g/l Tebuconazole + 120 g/l Azoxystrobin might be able to be pooled given they both contain strobins and triazole, however they contain differening dose ratio (inverted).
 
-Tebuconazole and propiconazole might be able to be pooled as a triazole fungicide treatment. 
-Amistar Xtra is a combination of azoxystrobin and cyproconazole.
-Custodia is a combination of tebuconazole and azoxystrobin.
-Amistar Xtra and Custodia might be able to be pooled given they both contain strobilurin and triazole, however, they contain differing dose ratios (inverted).
+Perhaps best way forward is to do an analysis of only the Triazoles. Then do another including Amistar as a comparison.
 
-Perhaps best way forward is to do an analysis of only the triazoles. Then do another including azoxystrobin as a comparison.
-
-Preliminary analysis of fungicides show there is a difference the effect of fungicide in proportion of yield saved.
+Preliminary analysis of Fungicides show there is a difference the effect of Fungicide in proportion of yield gained
 
 ### Fungicide Doses
-
-All trials that used tebuconazole used approximately the same dose.
-Dose of the active ingredient ranged from 62.35&nbsp;g per hectare to 60&nbsp;g per hectare.
-
-```{r tebu_dose}
+All trials that used Tebeconazole used approimately the same dose. dose of the active ingredient ranged from 62.35 grams per hectare to 60 grams per hectare. 
+```{r Tebe_dose}
 PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole") %>%
-   select(trial_ref,
-          year,
-          location,
-          first_sign_disease,
-          dose_ai_f1_g.ha,
-          total_fungicide) %>%
-   ggplot(aes(x = as.factor(dose_ai_f1_g.ha))) +
-   xlab("Dose (g ai/ha)") +
-   geom_bar() +
-   scale_fill_usq() +
-   scale_colour_usq() +
-   theme_usq()
+   filter(Fungicide == "Tebeconazole") %>%
+   select(Trial_ref, Year, Location, first_sign_disease, Dose.ai.ha., total_Fungicide) %>%
+   kable()
+# why are there zeros - FIXED
 ```
@@
 
-Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease.
-The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows did increase yield significantly, which has been shown by Kerry McKenzie's work as well.
-Eight trials used a row spacing of 0.75&nbsp;meters and tebuconazole as an active ingredient (AI).
+Some experiments were designed to investigate the effect of row spacing and plant density on Powdery Mildew disease and crop yield.
+The results showed that shorter distances between rows increase crop yields and mitigated the yield impact of the disease.
+Seven trials used a row spacing of 0.75 meters.
 
-```{r row_spacing.m}
+```{r row_spacing}
 PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole" | fungicide_ai == "propiconazole") %>%
-   group_by(fungicide_ai, row_spacing.m, trial_ref) %>%
+   filter(Fungicide == "Tebeconazole") %>%
+   group_by(row_spacing,Trial_ref) %>%
    summarise() %>%
@@
    rename(Trials = n) %>%
-   ggplot(aes(x = as.factor(row_spacing.m), y = Trials)) +
-   xlab("Row Spacing (m)") +
-   ylab("N Trials") +
-   ggtitle(label = "Trial row spacings using tebuconazole") +
-   geom_col(aes(fill = fungicide_ai),
-            position = "dodge") +
-   scale_fill_usq(name = "Fungicide AI") +
-   theme_usq()
+   kable()
 
 PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole",
-         row_spacing.m == 0.75) %>% 
-   glimpse()
+   filter(Fungicide == "propiconazole") %>%
+   group_by(row_spacing,Trial_ref) %>%
+   summarise() %>%
+   count() %>%
+   rename(Trials = n) %>%
+   kable()
+
+PM_MB_means %>%
+   filter(Fungicide == "Tebeconazole",
+          row_spacing == 0.75)
+
 ```
-
-Were there any statistical difference between all row spacing or only some?
+Were there any statistical diference between all row spacing or only some?  
 Can we pool certain row spacings that have no significant difference?
-From the preliminary analysis, the graphs seem to imply that if there is a lower overall yield there is no effect of row spacing on yield.
-However, if the average yield is more than approximately 0.6 - 1 t/ha then smaller row spacing has the potential to provide greater yield.
+From the preliminary analysis, graphs seem to imply that if there is a lower overall yeild there is no effect of row spacing on yield.
+However if the average yield is more than approximatley 0.6 - 1 T/Ha then smaller row spacing has the potenial to provide greater yield.
 
 ### Host genotypes
-
 Host genotype may need to be analysed to determine the effect.  
-
 ```{r Host_genotype}
 PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole",
-         row_spacing.m == 0.75) %>%
-   group_by(host_genotype, trial_ref) %>%
+   filter(Fungicide == "Tebeconazole",
+          row_spacing == 0.75) %>% 
+   group_by(host_genotype, Trial_ref) %>%
    summarise() %>%
@@
    rename(Treatments = n) %>%
-   ggplot(aes(x = host_genotype, y = Treatments)) +
-   xlab("Cultivar") +
-   ylab("N Trials") +
-   ggtitle(label = "Cultivars used in tebuconazole trials with 0.75 m row spacing") +
-   geom_col() +
-   scale_fill_usq() +
-   scale_colour_usq() +
-   theme_usq()
+   kable()
+
 ```
-
 In general the mungbean varieties have the following resistance to powdery mildew.  
-
    - Berken: Highly susceptible  
-
    - Crystal: Susceptible  
-
-   - Jade: Moderately susceptible
+   - Jade: Moderatley susceptible
 
@@
 ```{r variance}
-# Trials using tebuconazole
    PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole",
-         row_spacing.m == 0.75) %>%
-   group_by(trial_ref, location, y_error.type) %>%
-   summarise(tebuconazole_trts = length(y_error.type))
+   filter(Fungicide == "Tebeconazole",
+          row_spacing == 0.75) %>%
+   group_by(Trial_ref, Location, Y_error.type) %>%
+   summarise(Tebe_Treatments = length(Y_error.type))
 
-# Trials using propiconazole
    PM_MB_means %>%
-   filter(fungicide_ai == "propiconazole",
-          row_spacing.m == 0.75) %>%
-   group_by(trial_ref, location, y_error.type) %>%
-   summarise(propiconazole_trts = length(y_error.type))
+   filter(Fungicide == "propiconazole",
+          row_spacing == 0.75) %>%
+   group_by(Trial_ref, Location, Y_error.type) %>%
+   summarise(Tebe_Treatments = length(Y_error.type))
+
 ```
@@
 Trials <- PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole",
-          row_spacing.m == 0.75,
-          y_error.type == "lsd (P=0.05)") %>%
-   select(trial_ref) %>%
+   filter(
+      #Fungicide == "Tebeconazole",
+       #   row_spacing == 0.75,
+          Y_error.type == "lsd (P=0.05)")%>%
+   select(Trial_ref)%>%
    distinct()
-Trials
+
 ```
 
-The trial, `mung1112/02` uses Least Square Differences (LSD) to describe the variation within the experiment.
+The trial, `mung1112/02` uses Least square differences to describe the variation within the experiment.
 The following code attempts to convert this to sampling variance as per the method in [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
 Ideas for using a T-critical value of 1.697 came from reading a [statisics-how-to website](https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/).
-A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted where 30 degrees of freedom within experiment was used to find the 'T-crit' value of 1.697.
+A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted where 30 degrees of freedom within expeiment was used to find the 'T-crit' value of 1.697.
 
-![Calculating sampling variance from mean squared error Paul et al. (2008)](Paul_etal_2008.PNG)
+![Calculating sampling variance from mean squared error Paul et. al. (2008)](Paul_etal_2008.PNG)
 
@@
 
-for (Trial2012 in Trials$trial_ref) {
-   Tcrit <-
-      1.697  # 0.05 and DFw = 30 # T critical value for which there is significant difference between two groups; This value is the same for both trials "mung1112/01" and "mung1112/02"
-   DFw <-
-      sum(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates) -
-      length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates) # degrees of freedom within groups
-   # n.A <- PM_MB_means[PM_MB_means$trial_ref == "Trial2012,]$replicates[1]
-   # n.B <- PM_MB_means[PM_MB_means$trial_ref == "Trial2012,]$replicates[2]
-   LSD <-
-      PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error[1]
+for(Trial2012 in Trials$Trial_ref){
+
+Tcrit <- 1.697  # 0.05 and DFw = 30 # T critical value for which there is significant difference between two groups; This value is the same for both trials "mung1112/01" and "mung1112/02"
+DFw <- sum(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates) - 
+   length(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates) # degrees of freedom within groups
+# n.A <- PM_MB_means[PM_MB_means$Trial_ref == "Trial2012,]$Replicates[1]
+# n.B <- PM_MB_means[PM_MB_means$Trial_ref == "Trial2012,]$Replicates[2]
+LSD <- PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Yield_error[1]
 
@@
 #  MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B) # This formula was abandon in favor for the formula in Nugugi et. at (2011)
-   MSE <-
-      PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[1] * (LSD /
-                                                                            Tcrit) ^ 2 / 2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
+MSE <- PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates[1]*(LSD/Tcrit)^2/2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
 
-   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates)) {
-      if (j == 1) {
-         Sv <-
-            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates))
-      }
-      #  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates[j] *
-      #                   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$grain_yield.t.ha[j])
+for(j in seq_along(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates)){
+   if(j == 1){Sv <- vector(length = length(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates))}
+#  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates[j] *
+#                   PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$grain_yield.t.ha.[j])
 # Balance equation 
-      Sv[j] = sqrt(MSE / (
-         PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j] *
-            as.numeric(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$grain_yield.t.ha[j])
-      ))
+   Sv[j] = sqrt(MSE/(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates[j] *
+                  as.numeric(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$grain_yield.t.ha.[j])))
 
@@
 
-   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error <-
-      Sv
-   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$y_error.type <-
-      "SamplingVariance"
+PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Yield_error <- Sv
+PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Y_error.type <- "SamplingVariance"
 
@@
 Trials <- PM_MB_means %>%
-   filter(#fungicide_ai == "tebuconazole",
-      #row_spacing.m == 0.75,
-      y_error.type == "stdev") %>%
-   select(trial_ref) %>%
+   filter(
+         #Fungicide == "Tebeconazole",
+         #row_spacing == 0.75,
+          Y_error.type == "stdev")%>%
+   select(Trial_ref)%>%
    distinct()
@@
 # Sv <- sem^2 <- stdev/sqrt(n)
-# Sampling variance equals the square of the standard error.
+# Sampling variance eqauls the square of the standard error.
 # Sv <- (stdev/sqrt(n))^2
@@
 
-for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error)) {
+for(j in seq_along(PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error)){
 # create empty vector at first iteration with length of j
-   if (j == 1) {
-      Sv <-
-         vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error))
-   }
+   if(j == 1){Sv <- vector(length = length(PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error))}
 
 # Equation to convert standard deviation to Sampling Variance 
-   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error[j]) ^
-      2
+   Sv[j] = (PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error[j])^2
    }
@@
    # and replacing the values in the dataset
-PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error <-
-   Sv
-PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$y_error.type <-
-   "SamplingVariance"
+PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error <- Sv
+PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Y_error.type <- "SamplingVariance"
+
 ```
 
-Now for the trickier part creating 'Sampling Variance' for treatments where only mean yield is recorded.  
+Now for the trickier part creating 'Sampling Variance' for treatments where only mean yeild is recorded.  
 The trial which does not report any type of variance also reports that there is no significant difference between the means.
-
 ```{r}
 NATrials <- PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole",
-          row_spacing.m == 0.75,
-          is.na(y_error.type)) %>%
-   select(trial_ref) %>%
+   filter(Fungicide == "Tebeconazole",
+          row_spacing == 0.75,
+          is.na(Y_error.type)) %>%
+   select(Trial_ref)%>%
    distinct()
@@
 
-A single trial `mung1516/03` within the current scope of the meta-analysis fails to report a variance statistic.
+A single trial `mung1516/03` within the current scope od the meta-analysis fails to report a varience statistic.
 According to [Machado F.
 et.
-al (2017)](http://apsjournals.apsnet.org/doi/10.1094/PDIS-03-17-0340-RE) [Paul et al.
+al (2017)](http://apsjournals.apsnet.org/doi/10.1094/PDIS-03-17-0340-RE) [Paul et.
+al.
 (2007)](https://apsjournals.apsnet.org/doi/pdfplus/10.1094/PHYTO-97-2-0211) uses linear regression model to estimate sampling variance.
 
-```{r na2Sampling_variance, message=FALSE}
+```{r na2Sampling_variance}
 library(lme4)
@@
 
-# for(i in PM_MB_means$trial_ref){
+# for(i in PM_MB_means$Trial_ref){
 # 
 # log(V)[i] = a + b * log(
-#    mean(subset(PM_MB_means$grain_yield.t.ha[i], fungicide_ai == "control"),
-#         subset(PM_MB_means$grain_yield.t.ha[i], fungicide_ai == "tebuconazole")))
+#    mean(subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "control"),
+#         subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "Tebeconazole")))
 # # need to know what parameters a and b are here
-# # I am guessing they represent prediction parameters for each "study" for each of the treatments, "control" and tebuconazole"
+# # I am guessing they represent prediction parameters for each "study" for each of the treatments, "control" and Tebeconazole"
 # }
@@
 PM_MB_train <- PM_MB_means %>%
-   filter(y_error.type == "SamplingVariance")
+   filter(Y_error.type == "SamplingVariance")
 
-PM_MB_train$trial_ref <- as.factor(PM_MB_train$trial_ref)
+PM_MB_train$Trial_ref <- as.factor(PM_MB_train$Trial_ref)
 
-plot(PM_MB_train$yield_error,
-     log(PM_MB_train$grain_yield.t.ha))
+plot(PM_MB_train$Yield_error, log(PM_MB_train$`grain_yield.t.ha.`))
 
-# Run a linear model with grain_yield.t.ha as a fixed effect predictor and trial as a random intercept
-PM_MB_trainLMER <- lmer(yield_error ~ grain_yield.t.ha +
-                           (1 | trial_ref), data = PM_MB_train)
-summary(PM_MB_trainLMER)
+length(unique(PM_MB_train$Trial_ref))
 
-# grain yield (in this model) IS a significant predictor for yield error
-# (t value = 5.826)
-# And the variance increases as the mean increases does log transformation
-# improve the model?
+# Run a linear model with Grain_yield as a fixed effect predictor and Trial as a random intercept
+PM_MB_trianLMER <- lmer(Yield_error ~ `grain_yield.t.ha.`+ 
+         (1|Trial_ref), data = PM_MB_train)
+summary(PM_MB_trianLMER)
 
-PM_MB_trainLMER.1 <- lmer(log(yield_error) ~ `grain_yield.t.ha` +
-                             (1 | trial_ref), data = PM_MB_train)
-summary(PM_MB_trainLMER.1) # grain yield a significant predictor of log(yield error)
-anova(PM_MB_trainLMER, PM_MB_trainLMER.1) # no significant difference between the models
+# grain yeild (in this model) IS a significant predictor for yeild error (t value = 5.826)
+#  And the variance increases as the mean increases
+# does log transformation improve the model?
 
-PM_MB_trainLMER.2 <- lmer(yield_error ~ log(`grain_yield.t.ha`) +
-                             (1 | trial_ref), data = PM_MB_train)
-summary(PM_MB_trainLMER.2) # log(grain yeild) is a significant predictor of yield error
-anova(PM_MB_trainLMER, PM_MB_trainLMER.2) # no significant difference between the models
+PM_MB_trianLMER.1 <- lmer(log(Yield_error) ~ `grain_yield.t.ha.`+ 
+         (1|Trial_ref), data = PM_MB_train)
+summary(PM_MB_trianLMER.1) # grain yeild a significant predictor of log(yeild error)
+anova(PM_MB_trianLMER, PM_MB_trianLMER.1) # no significant difference between the models
 
-PM_MB_trainLMER.3 <-
-   lmer(log(yield_error) ~ log(`grain_yield.t.ha`) +
-           (1 | trial_ref),
-        data = PM_MB_train)
-summary(PM_MB_trainLMER.3) # log(grain yeild) is a significant predictor of log(yielderror)
-anova(PM_MB_trainLMER, PM_MB_trainLMER.3) # no significant difference between the models
+PM_MB_trianLMER.2 <- lmer(Yield_error ~ log(`grain_yield.t.ha.`)+ 
+         (1|Trial_ref), data = PM_MB_train)
+summary(PM_MB_trianLMER.2) # log(grain yeild) is a significant predictor of yeild error
+anova(PM_MB_trianLMER, PM_MB_trianLMER.2) # no significant difference between the models
+
+PM_MB_trianLMER.3 <- lmer(log(Yield_error) ~ log(`grain_yield.t.ha.`)+ 
+         (1|Trial_ref), data = PM_MB_train)
+summary(PM_MB_trianLMER.3) # log(grain yeild) is a significant predictor of log(yeild error)
+anova(PM_MB_trianLMER, PM_MB_trianLMER.3) # no significant difference between the models
 
 # Lets try with Fungicide as a fixed effect
-PM_MB_trainLMER.4 <-
-   lmer(yield_error ~ `grain_yield.t.ha` + as.factor(fungicide_ai) +
-           (1 | trial_ref),
-        data = PM_MB_train)
-summary(PM_MB_trainLMER.4)
-anova(PM_MB_trainLMER, PM_MB_trainLMER.4) # no significant difference between the models
+PM_MB_trianLMER.4 <- lmer(Yield_error ~ `grain_yield.t.ha.`+ as.factor(Fungicide) + 
+         (1|Trial_ref), data = PM_MB_train)
+summary(PM_MB_trianLMER.4)
+anova(PM_MB_trianLMER, PM_MB_trianLMER.4) # no significant difference between the models
 
 #log transforming the response or predictor variables did not improve the model therefore I will leave it untransformed
-# I will be using the first model PM_MB_trainLMER for further analyses beyond this point
+# I will be using the first model PM_MB_trianLMER for further analyses beyond this point
 
-# Extract the model coefficients
-paramA <-
-   (summary(PM_MB_trainLMER)$coef)[2, 1] # Extract the overall mean slope to predict Yield error
-InterC <-
-   (summary(PM_MB_trainLMER)$coef)[1, 1] # Extract the overall mean intercept to predict Yield error
-lmer.coef <-
-   coef(PM_MB_trainLMER) # extracting the mean random intercept for each of trial variables
+# Extract the model cooeficients
+paramA <- (summary(PM_MB_trianLMER)$coef)[2,1] # Extract the overall mean Slope to predict Yield error
+InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the overall mean intercept to predict Yield error
+lmer.coef <- coef(PM_MB_trianLMER) # extracting the mean random intercept for each of trial variables
+
+# plot of the mixed effect model, Black line shows the mean lmer regression line
+ggplot(PM_MB_train)+
+   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
+   geom_abline(intercept = c(InterC,lmer.coef$Trial_ref[,1]), 
+               slope = c(paramA,lmer.coef$Trial_ref[,2]),
+               size = 1,
+               colour = c("Black",hue_pal()(length(unique(PM_MB_train$Trial_ref)))))+
+   coord_cartesian(xlim = c(0, 3))
+
+```
+```{r na2Sv_formula}
+
+# commented until a reliable model can be written
+
+# for(i in NATrials$Trial_ref){
+# #Sv <- (log(PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped
+# 
+# Sv <- (PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.` * paramA) + InterC
+# 
+# PM_MB_means[PM_MB_means$Trial_ref == i,]$Yield_error <- Sv
+# PM_MB_means[PM_MB_means$Trial_ref == i,]$Y_error.type <- "SamplingVariance"
+# }
+
+```
+
+Lets look at the model without the trial mung1718/01, as it looks to be adding some skew.
+```{r lmer_remove_mung1718-01}
+# remove from mung1718/01 from training dataset
+PM_MB_train.2 <- PM_MB_train[PM_MB_train$Trial_ref != "mung1718/01",]
+
+# Rerun the model
+PM_MB_trianLMER.5 <- lmer(Yield_error ~ `grain_yield.t.ha.`+ 
+         (1|Trial_ref), data = PM_MB_train.2)
+summary(PM_MB_trianLMER.5) # no significant effect of mean grain yield on yeild error
+
+# Extract the cooeficients
+paramA <- (summary(PM_MB_trianLMER.5)$coef)[2,1] # Extract the overall mean Slope to predict Yield error
+InterC <- (summary(PM_MB_trianLMER.5)$coef)[1,1] # Extract the overall mean intercept to predict Yield error
+lmer.coef <- coef(PM_MB_trianLMER.5) # extracting the mean random intercept for each of trial variables
+
+# plot the data with the predicted slopes overlayed
+ggplot(PM_MB_train.2)+
+   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
+   geom_abline(intercept = c(InterC,lmer.coef$Trial_ref[,1]), 
+               slope = c(paramA,lmer.coef$Trial_ref[,2]),
+               size = 1,
+               colour = c("Black",hue_pal()(length(unique(PM_MB_train.2$Trial_ref)))))+
+   coord_cartesian(ylim = c(0, 0.33))
+
+```
+
+Just for kicks lets look at the linear regression model as a Random effects model where `grain_yield.t.ha.` is set as a random slope to the random intercept `Trial_ref`.  
+The model fits better as shown by an anova comparison. But how to impute from this model if mean variance for a trial is unknown....
+```{r random_slope_model} 
+# This code chunk broke with the addition of new data, I will re-inspect the data and remodel.
+
+# Run a linear model with Yield error as a fixed effect predictor and Trial as a random intercept
+PM_MB_trianLMERx <- lmer(Yield_error ~ 1 + 
+         (`grain_yield.t.ha.`|Trial_ref), data = PM_MB_train)
+
+anova(PM_MB_trianLMER,PM_MB_trianLMERx) # random slope model NOT significantly better # P = 0.6677
+
+summary(PM_MB_trianLMERx)
+
+InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the overall mean intercept
+
+lmer.coefx <- coef(PM_MB_trianLMERx)
 
@@
 ggplot(PM_MB_train) +
-   geom_point(aes(y = yield_error, x = grain_yield.t.ha, colour = trial_ref)) +
-   geom_abline(
-      intercept = c(InterC, lmer.coef$trial_ref[, 1]),
-      slope = c(paramA, lmer.coef$trial_ref[, 2]),
+   geom_point(aes(y = Yield_error, x = `grain_yield.t.ha.`, colour = Trial_ref))+
+   geom_abline(intercept = lmer.coefx$Trial_ref[,2], 
+               slope = lmer.coefx$Trial_ref[,1],
                size = 1,
-      colour = c("Black", hue_pal()(16))
-   ) +
-   coord_cartesian(xlim = c(0, 3)) +
-   theme_usq()
+               colour = hue_pal()(length(unique(PM_MB_train$Trial_ref))))+
+   coord_cartesian(xlim = c(0, 3),
+                   ylim = c(0, 1))
+
 ```
 
-```{r na2Sv_formula}
-for (i in NATrials$trial_ref) {
-   #Sv <- (log(PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped
+After much deliberation I don't think this is possible to use the model with grain yield/ha as a random slope.
+Even though we know the grain yields and the mean in the grain yeilds we still can't predict the effect of the random intercept trial on the yield error.
+I also re-ran the model without including the trial which we used LSD to interprete the sampling variance and the model lost a lot of significance.
 
-   Sv <-
-      (PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha` * paramA) + InterC
+Emerson proposed I look at the between trial variation
+```{r between_trial_variation}
+levels(factor(PM_MB_means$Y_error.type))
 
-   PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <- Sv
-   PM_MB_means[PM_MB_means$trial_ref == i,]$y_error.type <-
-      "SamplingVariance"
+PM_MB_means.SV <- PM_MB_means[PM_MB_means$Y_error.type == "SamplingVariance",]
+meta_mean.GY <- mean(PM_MB_means.SV$grain_yield.t.ha.,na.rm = TRUE)
+
+# find the mean and variance of each trial
+PM_MB_means_T <- PM_MB_means %>%
+   filter(Y_error.type == "SamplingVariance") %>%
+   group_by(Trial_ref) %>%
+   summarise(trial_mean = mean(grain_yield.t.ha.,na.rm = TRUE),
+             Trial_variance = sd(grain_yield.t.ha.,na.rm = TRUE)^2)  # I am not sure I have calculated between trial variance or trial variance// Should I be using a denominator (N-1) or (N), sd by default uses (N-1)
+
+# update the main data set with Trial variance
+SV_Trials <- unique(PM_MB_means_T$Trial_ref)
+PM_MB_means$TrialVariance <- NA
+
+for(i in SV_Trials){
+   PM_MB_means[PM_MB_means$Trial_ref == i, "TrialVariance"] <- PM_MB_means_T[PM_MB_means_T$Trial_ref == i,"Trial_variance"]
 }
+PM_MB_means$TrialVariance
+
+SV_mod1 <- lm(Trial_variance ~ trial_mean, data = PM_MB_means_T)
+summary(SV_mod1)
+
+plot(Trial_variance ~ trial_mean, data = PM_MB_means_T)
+abline(SV_mod1)
+
 ```
-
-Let's look at the model without the trial mung1718/01, as it looks to be adding some skew.
-
-```{r lmer_remove_mung1718-01}
-# remove from mung1718/01 from training dataset
-PM_MB_train.2 <-
-   PM_MB_train[PM_MB_train$trial_ref != "mung1718/01",]
-
-# Rerun the model
-PM_MB_trainLMER.5 <- lmer(yield_error ~ `grain_yield.t.ha` +
-                             (1 | trial_ref), data = PM_MB_train.2)
-summary(PM_MB_trainLMER.5) # no significant effect of mean grain yield on yield error
-
-# Extract the cooeficients
-paramA <-
-   (summary(PM_MB_trainLMER.5)$coef)[2, 1] # Extract the overall mean Slope to predict Yield error
-InterC <-
-   (summary(PM_MB_trainLMER.5)$coef)[1, 1] # Extract the overall mean intercept to predict Yield error
-lmer.coef <-
-   coef(PM_MB_trainLMER.5) # extracting the mean random intercept for each of trial variables
-
-# plot the data with the predicted slopes overlayed
-ggplot(PM_MB_train.2) +
-   geom_point(aes(y = yield_error, x = grain_yield.t.ha, colour = trial_ref)) +
-   geom_abline(
-      intercept = c(InterC, lmer.coef$trial_ref[, 1]),
-      slope = c(paramA, lmer.coef$trial_ref[, 2]),
-      size = 1,
-      colour = c("Black", hue_pal()(15))
-   ) +
-   coord_cartesian(ylim = c(0, 0.33)) +
-   xlab("Grain Yield (t/ha)") +
-   ylab("Yield Error") +
-   scale_colour_discrete("Trial Reference") +
-   theme_usq()
-```
-
-Just for kicks lets look at the linear regression model as a random effects model where `grain_yield.t.ha` is set as a random slope to the random intercept `trial_ref`.
-
-The model fits better as shown by an ANOVA comparison. But how to impute from this model if mean variance for a trial is unknown...
-
-```{r random_slope_model}
-# Run a linear model with yield error as a fixed effect predictor and trial as a random intercept
-PM_MB_trainLMERx <- lmer(yield_error ~ 1 +
-                            (grain_yield.t.ha |
-                                trial_ref), data = PM_MB_train)
-
-anova(PM_MB_trainLMER, PM_MB_trainLMERx) # random slope model NOT significantly better # P = 0.6677
-
-summary(PM_MB_trainLMERx)
-
-InterC <-
-   (summary(PM_MB_trainLMER)$coef)[1, 1] # Extract the overall mean intercept
-
-lmer.coefx <- coef(PM_MB_trainLMERx)
-
-# plot of the mixed effect model, Black line shows the mean lmer regression line
-ggplot(PM_MB_train) +
-   geom_point(aes(y = yield_error, x = grain_yield.t.ha, colour = trial_ref)) +
-   geom_abline(
-      intercept = lmer.coefx$trial_ref[, 2],
-      slope = lmer.coefx$trial_ref[, 1],
-      size = 1,
-      colour = hue_pal()(16)
-   ) +
-   coord_cartesian(xlim = c(0, 3),
-                   ylim = c(0, 1)) +
-   xlab("Grain Yield (t/ha)") +
-   ylab("Yield Error") +
-   scale_colour_discrete("Trial Reference") +
-   theme_usq()
-```
-
-After much deliberation I don't think this is possible to use the model with grain yield t/ha as a random slope.
-Even though we know the grain yields and the mean of the grain yields, we still can't predict the effect of the random intercept trial on the yield error.
-
-I also re-ran the model without including the trial in which we used LSD to interpret the sampling variance and the model lost a lot of significance.
-
-## Between trial variation
-
-Emerson proposed I look at the between trial variation.
-
-```{r between_trial_variation}
-levels(factor(PM_MB_means$y_error.type))
-
-PM_MB_means.SV <-
-   filter(PM_MB_means, y_error.type == "SamplingVariance")
-
-meta_mean.GY <- mean(PM_MB_means.SV$grain_yield.t.ha, na.rm = TRUE)
-
-PM_MB_means_T <- PM_MB_means.SV %>%
-   group_by(trial_ref) %>%
-   summarise(
-      trial_mean = mean(grain_yield.t.ha, na.rm = TRUE),
-      BW_trial_variance = sd(grain_yield.t.ha, na.rm = TRUE) ^ 2
-   )
-
-PM_MB_means <- left_join(PM_MB_means, PM_MB_means_T, by = "trial_ref")
-
-summary(lm(BW_trial_variance ~ trial_mean, data = PM_MB_means))
-summary(lm(
-   BW_trial_variance ~ trial_mean,
-   data = subset(PM_MB_means, fungicide_ai == "tebuconazole")
-))
-summary(lm(
-   BW_trial_variance ~ trial_mean,
-   data = subset(PM_MB_means, fungicide_ai == "propiconazole")
-))
-
-plot(BW_trial_variance ~ trial_mean, data = PM_MB_means)
-abline(-0.01356, 0.03076)
-```

### 2019-09-19 05_MetaAnalysis.Rmd

--- 2019-09-15 05_MetaAnalysis.Rmd
@@
 ```{r variance}
+
 # Trials using tebuconazole
@@
 
+length(unique(PM_MB_train$Trial_ref))
+
 # Run a linear model with grain_yield.t.ha as a fixed effect predictor and trial as a random intercept
@@
 
+# for(i in NATrials$Trial_ref){
+# #Sv <- (log(PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped
+# 
+# Sv <- (PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.` * paramA) + InterC
+# 
+# PM_MB_means[PM_MB_means$Trial_ref == i,]$Yield_error <- Sv
+# PM_MB_means[PM_MB_means$Trial_ref == i,]$Y_error.type <- "SamplingVariance"
+# }
+
 # plot of the mixed effect model, Black line shows the mean lmer regression line
@@
       size = 1,
-      colour = c("Black", hue_pal()(16))
+      colour = c("Black", hue_pal()(length(unique(PM_MB_train$trial_ref))))
    ) +
@@
 ```{r na2Sv_formula}
-for (i in NATrials$trial_ref) {
-   #Sv <- (log(PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped
+# commented until a reliable model can be written
 
-   Sv <-
-      (PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha` * paramA) + InterC
+# for (i in NATrials$trial_ref) {
+#    #Sv <- (log(PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped
+#    
+#    Sv <-
+#       (PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha` * paramA) + InterC
+#    
+#    PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <- Sv
+#    PM_MB_means[PM_MB_means$trial_ref == i,]$y_error.type <-
+#       "SamplingVariance"
+# }
 
-   PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <- Sv
-   PM_MB_means[PM_MB_means$trial_ref == i,]$y_error.type <-
-      "SamplingVariance"
-}
 ```
@@
 # plot the data with the predicted slopes overlayed
+
 ggplot(PM_MB_train.2) +
@@
       size = 1,
-      colour = c("Black", hue_pal()(15))
+      colour = c("Black", hue_pal()(length(unique(PM_MB_train.2$Trial_ref))))
    ) +
@@
    theme_usq()
+
 ```
@@
 ```{r random_slope_model} 
+# This code chunk broke with the addition of new data, I will re-inspect the data and remodel.
+
 # Run a linear model with yield error as a fixed effect predictor and trial as a random intercept
@@
       size = 1,
-      colour = hue_pal()(16)
+      colour = hue_pal()(length(unique(PM_MB_train$Trial_ref)))
    ) +
@@
 ```
-
 After much deliberation I don't think this is possible to use the model with grain yield t/ha as a random slope.
@@
 
-Emerson proposed I look at the between trial variation.
+Emerson proposed I look at the between trial variation
+```{r between_trial_variation}
+levels(factor(PM_MB_means$Y_error.type))
 
-```{r between_trial_variation}
-levels(factor(PM_MB_means$y_error.type))
+PM_MB_means.SV <- PM_MB_means[PM_MB_means$Y_error.type == "SamplingVariance",]
+meta_mean.GY <- mean(PM_MB_means.SV$grain_yield.t.ha.,na.rm = TRUE)
 
-PM_MB_means.SV <-
-   filter(PM_MB_means, y_error.type == "SamplingVariance")
+# find the mean and variance of each trial
+PM_MB_means_T <- PM_MB_means %>%
+   filter(Y_error.type == "SamplingVariance") %>%
+   group_by(trial_ref) %>%
+   summarise(trial_mean = mean(grain_yield.t.ha, na.rm = TRUE),
+             BW_trial_variance = sd(grain_yield.t.ha, na.rm = TRUE) ^ 2
+             ) # I am not sure I have calculated between trial variance or trial variance// Should I be using a denominator (N-1) or (N), sd by default uses (N-1)
 
-meta_mean.GY <- mean(PM_MB_means.SV$grain_yield.t.ha, na.rm = TRUE)
+# update the main data set with Trial variance
+SV_Trials <- unique(PM_MB_means_T$Trial_ref)
+PM_MB_means$TrialVariance <- NA
 
-PM_MB_means_T <- PM_MB_means.SV %>%
-   group_by(trial_ref) %>%
-   summarise(
-      trial_mean = mean(grain_yield.t.ha, na.rm = TRUE),
-      BW_trial_variance = sd(grain_yield.t.ha, na.rm = TRUE) ^ 2
-   )
-
+for(i in SV_Trials){
+   PM_MB_means[PM_MB_means$Trial_ref == i, "TrialVariance"] <- PM_MB_means_T[PM_MB_means_T$Trial_ref == i,"Trial_variance"]
+}
+PM_MB_means$TrialVariance
+# OR ?
 PM_MB_means <- left_join(PM_MB_means, PM_MB_means_T, by = "trial_ref")
 
-summary(lm(BW_trial_variance ~ trial_mean, data = PM_MB_means))
-summary(lm(
-   BW_trial_variance ~ trial_mean,
-   data = subset(PM_MB_means, fungicide_ai == "tebuconazole")
-))
-summary(lm(
-   BW_trial_variance ~ trial_mean,
-   data = subset(PM_MB_means, fungicide_ai == "propiconazole")
-))
+SV_mod1 <- lm(Trial_variance ~ trial_mean, data = PM_MB_means_T)
+summary(SV_mod1)
 
-plot(BW_trial_variance ~ trial_mean, data = PM_MB_means)
-abline(-0.01356, 0.03076)
+plot(Trial_variance ~ trial_mean, data = PM_MB_means_T)
+abline(SV_mod1)
+
 ```

### 2019-09-19 01_Meta-analysis_experiments.Rmd
Edits reviewed and accepted

@@
 
-```{r MEsummary_Libraries}
+```{r MEsummary_Libraries, message=FALSE, echo=FALSE}
 library(dplyr)
-library(openxlsx)
+library(readr)
 library(kableExtra)
-library(ggplot2)
 library(leaflet)
-#source("./getPPD2.R")
-
+source("R/import_data.R")
 ```
@@
    Acronym = c("SF", "Ti", "AX", "Ca"),
-   Expected_Fungicide = c("Sulphur", "Tilt", "Amistar Xtra", "Carbendazim"),
-   Active_Ingredient = c(
+   `Expected Fungicide` = c("Sulphur", "Tilt", "Amistar Xtra", "Carbendazim"),
+   `Active Ingredient` = c(
       "Sulphur",
@@
 
-PM.dat <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
+PM.dat <- import_data()
 
@@
       group_by(
-         Trial_ref,
-         Year,
-         Location,
+         trial_ref,
+         year,
+         location,
          trial_design,
-         Replicates,
+         replicates,
          planting_date,
@@
       ) %>%
-      summarise(Treatments = length(E_treatment)),
+      summarise(treatments = length(e_treatment)),
    caption = "Description of Experiments"
@@
 
-PM.dat$Trial_ref <- factor(PM.dat$Trial_ref)
-PM.dat$Location <- factor(PM.dat$Location)
-PM.dat$Year <- factor(PM.dat$Year)
-PM.dat$host_genotype <- factor(PM.dat$host_genotype)
-PM.dat$Fungicide <- factor(PM.dat$Fungicide)
-PM.dat$Trade_name <- factor(PM.dat$Trade_name)
 ```
@@
    location = c(
-      "Hermitage",
+      "Hermitage Research Station",
       "Kingaroy Research Station",

### 2019-09-19 Cleaning historical data.R
files relocated

@@ -1,1479 +1,0 @@
-# This script is dedicated to 
-# importing and cleaning previous powdery Mildew experimental field trial data.
-
-# install.packages("openxlsx")
-# install.packages("readxl")
-# install.packages("tidyr")
-
-library(openxlsx)
-library(readxl)
-library(tidyr)
-library(dplyr)
-library(data.table)
-
-# Year #  Trial location  #  Sowing date
-
-
-# ____________________________________________________________
-# _____________            Hermitage  2010        ____________
-
-Herm_10 <- read_xls("C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/Past Trials/2010/2010 PMmung Herm/2010 PMmung hermitage RAW field book.xls", 
-                        sheet = "For analysis")
-
-Herm_10_m <- Herm_10 %>%
-   group_by(`Cultivar!`, `Treat!`, `Description!`) %>%
-   summarise_all(list(~mean(.,na.rm = TRUE),~sd(.,na.rm=TRUE)))
-   
-write.csv(as.data.frame(Herm_10_m ), "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/2010 PMmung Hermitage means.csv")
-
-
-# ____________________________________________________________
-# _____________            Hermitage  2011        ____________
-
-Herm_11 <- read_xls("C:/Users/U8011054/OneDrive - USQ//Cloudstor/Mungbean/Past trials/2011/2011 PMmung Herm/pmhermratings2011.xls", 
-                    sheet = "Analyses factor")
-
-
-new_cols <- as.data.table(tstrsplit(Herm_11$'Treatment!'," "))
-colnames(new_cols) <- c("spray_n", "spray", "fungicide")
-Herm_11 <- cbind(new_cols, as.data.table(Herm_11)[, 'Treatment!' := NULL])
-#Herm_11$`Yld Kg ha` <- as.numeric(Herm_11$`Yld Kg ha`)
-head(Herm_11)
-
-Herm_11_m <- Herm_11 %>%
-   group_by(`Cultivar!`, `Tr`, `fungicide`, `spray_n`) %>%
[…]

### 2019-09-19 index.Rmd
Edits reviewed and accepted

--- 2019-06-19 index.Rmd
@@
 title: "Powdery Milder yield loss mitigation strategies in Mungbean a Meta-analysis"
-author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
-date: "19/06/2019"
+author: "Paul Melloy, Emerson Del Ponte, Charles T. Gray and Adam H. Sparks"
+date: "`r Sys.Date()`"
 output:
@@
 ---
+
+# Research questions
+
+When is the optimum time to spray fungicide to limit the impact of powdery mildew on mungbean yields?
+
+How has the first sign of powdery mildew changed over the seasons and between experimental sites?
+
+How has the first sign of powdery mildew changed over the seasons and between experimental sites?
+
+When would the ideal planting time be to make use of powdery mildew defoliation in the final growth of the crop?
+
+Do infections that occur before flowering increase the probable yield loss?
+
+What is the length of a mungbean season and how has it varied in this trial?
+   - This data has not been collected or is not accurate enough to be useful to answer this question.
+
+## Parts of analysis that need checking
+
+Variability among host genotypes and probable influence of season given that over the years, the genotype studied changed from Berken, Crystal to Jade.

### 2019-09-19 R/getPPD2.R
Files relocated

@@ -1,0 +1,64 @@
+#' Download PPD data
+#' 
+#' Download PPD data for a station and return as a data frame
+#'
+#' @param id Weather station ID.
+#' @param start Start date (String YYYYmmdd).
+#' @param end End date (String YYYYmmdd).
+#' @param silo.apiKey SILO API key (available from https://silo.longpaddock.qld.gov.au/).
+#' @param variables Vector of weather variables (Full list available  at https://silo.longpaddock.qld.gov.au/climate-variables)
+#'
+#' @author Paul Melloy & Fiona Evans
+#' 
+#' @return Data frame containing daily weather data.
+#' @export
+
+
+getPPD2 <- function(station_id, lat, long, start, end, silo.apikey, variables) {
+if(missing(lat)|missing(long)){
+# 'If' statement for when user does not specify variables
+   if(missing(variables)){
+      variables <- paste("daily_rain", "max_temp", "min_temp", "rh_tmax", "rh_tmin","vp", "vp_deficit", "radiation",
+              sep = ",")
+   }
+
+   
+url <- "https://siloapi.longpaddock.qld.gov.au/pointdata?apikey="
+
+
+   print(paste0(url,silo.apikey , "&start=", start,  "&finish=", end,  "&station=", station_id,  "&format=csv", "&variables=", variables))
+read.csv(paste0(url,silo.apikey , "&start=", start,  "&finish=", end,  "&station=", station_id,  "&format=csv", "&variables=", variables))
+
+
+
+}else{ 
+   if(missing(station_id)) {
+   # 'If' statement for when user does not specify variables
+   if(missing(variables)){
+      variables <- paste("daily_rain", "max_temp", "min_temp", "rh_tmax", "rh_tmin","vp", "vp_deficit", "radiation",
+                         sep = ",")
+   }
+   
+   url <- "https://siloapi.longpaddock.qld.gov.au/pointdata?apikey="
+   
+   print(paste0(url,silo.apikey , "&start=", start,  "&finish=", end,  "&lat=", lat, "&lon=",long,  "&format=csv", "&variables=", variables))   
+read.csv(paste0(url,silo.apikey , "&start=", start,  "&finish=", end,  "&lat=", lat, "&lon=",long,  "&format=csv", "&variables=", variables))
+
+
+   
+   
+}
+   
+}
+   
+}
+
[…]

### 2019-09-20 01_Meta-analysis_experiments.Rmd
updated information on maps corrected some code Removed obsolete information

@@
 library(leaflet)
+library(htmltools)
 source("R/import_data.R")
@@
 * 2013  
-   + Premer; no raw data
-   + Milmerran; no raw data
-   + Mt Mary; no raw data
-   + Goolhi; no raw data
+   + Premer  
+   + Milmerran   
+   + Mt Mary   
+   + Goolhi
 
@@
 **2013 Field trials**  
-Fungicide treatments were described in reports in two letter acronyms.
-The following is the assumed usage.
-
-```{r}
-knitr::kable(cbind(
-   Acronym = c("SF", "Ti", "AX", "Ca"),
-   `Expected Fungicide` = c("Sulphur", "Tilt", "Amistar Xtra", "Carbendazim"),
-   `Active Ingredient` = c(
-      "Sulphur",
-      "Propiconazole",
-      "Azoxystrobin and Cyproconazole",
-      "Carbendazim"
-   )
-))
-```
+Trials were conducted by the National Growers Alliance (NGA).
+The raw data were obtained from Lawrie Price.
+NGA data were formatted to be compliant with existing data rating and scales in the R script `Cleaning historical data.R`.
 
@@
       ) %>%
-      summarise(treatments = length(e_treatment)),
+      summarise(treatments = length(n_treatment)),
    caption = "Description of Experiments"
-) %>%
-   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
-   scroll_box(width = "900px", height = "500px")
+ ) # %>%  #commented as was redering empty, needs a look in
+#    kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
+#    scroll_box(width = "900px", height = "500px")
 
@@
       "Hermitage Research Station",
-      "Kingaroy Research Station",
+      "Red Vale & Kingaroy Research Station",
       "Gatton",
-      "Emerald Agricultural College"
+      "Emerald Agricultural College",
+      "Bongeen 1 & 2",
+      "NGA - Premer",
+      "NGA - Millmerran",
+      "NGA - Marys Mount",
+      "NGA - Goolhi",
+      "Missen Flats",
+      "Wellcamp"
       ),
-   lat = c(-28.215 , -26.58, -27.56, -23.54),
-   lon = c(152.1003, 151.83, 152.32, 148.19)
+   lat = c(-28.215 , -26.58, -27.56, -23.54, -27.51666, -31.43449, -27.923674, -31.0142, -31.00246, -27.905313, -27.564277),
+   lon = c(152.1003, 151.83, 152.32, 148.19, 151.450,150.0052, 151.242706, 150.05018, 149.82507, 151.9772,151.867879)
 )
 
-leaflet() %>%
+leaflet(experiment_sites) %>%
    addProviderTiles("Esri.WorldTopoMap") %>%
-   addMarkers(lng = experiment_sites$lon, lat = experiment_sites$lat)
-# head(silo_gatton_Tmax)
+   setView(lat = -27.31, lng = 150.456,zoom = 5) %>%
+   addMarkers(lng = ~lon, lat = ~lat, popup = ~htmlEscape(location))
+#   addPopups(lng = experiment_sites$lon, lat = experiment_sites$lat, popup = experiment_sites$location)
+
 ```

### 2019-09-20 R/import_data.R
rewrote without the need for tidyverse corrected headers

@@ -11,28 +11,28 @@
 #'
 import_data <- function() {
    x <-
-      read_csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
-   x <- x %>%
-      mutate(trial_ref = as.factor(trial_ref)) %>%
-      mutate(location = as.factor(location)) %>%
-      mutate(host_genotype = as.factor(host_genotype)) %>%
-      mutate(fungicide_ai = as.factor(fungicide_ai)) %>%
-      mutate(trade_name = as.factor(trade_name)) %>%
-      mutate(year = as.factor(year)) %>%
-      mutate(replicates = as.factor(replicates)) %>%
-      mutate(planting_date = as.Date(planting_date, format = "%d/%m/%Y")) %>%
-      mutate(emergence_date = as.Date(emergence_date, format = "%d/%m/%Y")) %>%
-      mutate(flowering_date = as.Date(flowering_date, format = "%d/%m/%Y")) %>%
-      mutate(pod_final_date = as.Date(pod_final_date, format = "%d/%m/%Y")) %>%
-      mutate(mid_late_pod_final = as.Date(mid_late_pod_final, format = "%d/%m/%Y")) %>%
-      mutate(first_sign_disease = as.Date(first_sign_disease, format = "%d/%m/%Y")) %>%
-      mutate(fungicide_application_1 = as.Date(fungicide_application_1, format = "%d/%m/%Y")) %>%
-      mutate(fungicide_application_2 = as.Date(fungicide_application_2, format = "%d/%m/%Y")) %>%
-      mutate(fungicide_application_3 = as.Date(fungicide_application_3, format = "%d/%m/%Y")) %>%
-      mutate(fungicide_application_4 = as.Date(fungicide_application_4, format = "%d/%m/%Y")) %>%
-      mutate(fungicide_application_5 = as.Date(fungicide_application_5, format = "%d/%m/%Y")) %>%
-      mutate(fungicide_application_6 = as.Date(fungicide_application_6, format = "%d/%m/%Y")) %>%
-      mutate(fungicide_application_7 = as.Date(fungicide_application_7, format = "%d/%m/%Y")) %>%
-      mutate(harvest_date = as.Date(harvest_date, format = "%d/%m/%Y")) %>%
-      mutate(final_assessment = as.Date(final_assessment, format = "%d/%m/%Y"))
[…]

### 2019-10-15 05_MetaAnalysis.Rmd
Updated based on new data import method

@@
 PM_MB_means <- import_data()
+
 ```
@@
    scale_fill_usq() +
+   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
    scale_colour_usq() +
@@
           first_sign_disease,
-          dose_ai_f1_g.ha,
+          dose_ai.ha,
           total_fungicide) %>%
-   ggplot(aes(x = as.factor(dose_ai_f1_g.ha))) +
+   ggplot(aes(x = as.factor(dose_ai.ha))) +
    xlab("Dose (g ai/ha)") +
+   ggtitle(label = "Total number of treatments for each respective tebuconazole dose") +
    geom_bar() +
@@
 Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease.
-The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows did increase yield significantly, which has been shown by Kerry McKenzie's work as well.
+The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows in most cases increased yield significantly.
+This finding has also been shown by Kerry McKenzie's work as well.
 Eight trials used a row spacing of 0.75&nbsp;meters and tebuconazole as an active ingredient (AI).
@@
    filter(fungicide_ai == "tebuconazole" | fungicide_ai == "propiconazole") %>%
-   group_by(fungicide_ai, row_spacing.m, trial_ref) %>%
+   group_by(fungicide_ai, row_spacing, trial_ref) %>%
    summarise() %>%
@@
    rename(Trials = n) %>%
-   ggplot(aes(x = as.factor(row_spacing.m), y = Trials)) +
+   ggplot(aes(x = as.factor(row_spacing), y = Trials)) +
    xlab("Row Spacing (m)") +
@@
    filter(fungicide_ai == "tebuconazole",
-         row_spacing.m == 0.75) %>% 
+         row_spacing == 0.75) %>% 
    glimpse()
@@
    filter(fungicide_ai == "tebuconazole",
-         row_spacing.m == 0.75) %>%
+         row_spacing == 0.75) %>%
    group_by(host_genotype, trial_ref) %>%
@@
 ```{r variance}
-
+# PM_MB_means$Y_error_type <- forcats::fct_explicit_na(PM_MB_means$Y_error_type, na_level = NA)
 # Trials using tebuconazole
@@
    filter(fungicide_ai == "tebuconazole",
-         row_spacing.m == 0.75) %>%
-   group_by(trial_ref, location, y_error.type) %>%
-   summarise(tebuconazole_trts = length(y_error.type))
+         row_spacing == 0.75) %>%
+   group_by(trial_ref, location, Y_error_type) %>%
+   summarise(tebuconazole_trts = length(Y_error_type))
 
@@
    filter(fungicide_ai == "propiconazole",
-          row_spacing.m == 0.75) %>%
-   group_by(trial_ref, location, y_error.type) %>%
-   summarise(propiconazole_trts = length(y_error.type))
+          row_spacing == 0.75) %>%
+   group_by(trial_ref, location, Y_error_type) %>%
+   summarise(propiconazole_trts = length(Y_error_type))
 ```
@@
    filter(fungicide_ai == "tebuconazole",
-          row_spacing.m == 0.75,
-          y_error.type == "lsd (P=0.05)") %>%
+          row_spacing == 0.75,
+          Y_error_type == "lsd (P=0.05)") %>%
    select(trial_ref) %>%
@@
       Sv
-   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$y_error.type <-
+   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$Y_error_type <-
       "SamplingVariance"
@@
       #row_spacing.m == 0.75,
-      y_error.type == "stdev") %>%
+      Y_error_type == "stdev") %>%
    select(trial_ref) %>%
@@
    Sv
-PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$y_error.type <-
+PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$Y_error_type <-
    "SamplingVariance"
@@
           row_spacing.m == 0.75,
-          is.na(y_error.type)) %>%
+          is.na(Y_error_type)) %>%
    select(trial_ref) %>%
@@
 PM_MB_train <- PM_MB_means %>%
-   filter(y_error.type == "SamplingVariance")
+   filter(Y_error_type == "SamplingVariance")
 
@@
 #    PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <- Sv
-#    PM_MB_means[PM_MB_means$trial_ref == i,]$y_error.type <-
+#    PM_MB_means[PM_MB_means$trial_ref == i,]$Y_error_type <-
 #       "SamplingVariance"
@@
 ```{r between_trial_variation}
-levels(factor(PM_MB_means$Y_error.type))
+unique(PM_MB_means$Y_error_type)
 
-PM_MB_means.SV <- PM_MB_means[PM_MB_means$Y_error.type == "SamplingVariance",]
+PM_MB_means.SV <- PM_MB_means[PM_MB_means$Y_error_type == "SamplingVariance",]
 meta_mean.GY <- mean(PM_MB_means.SV$grain_yield.t.ha.,na.rm = TRUE)
@@
 PM_MB_means_T <- PM_MB_means %>%
-   filter(Y_error.type == "SamplingVariance") %>%
+   filter(Y_error_type == "SamplingVariance") %>%
    group_by(trial_ref) %>%
-   summarise(trial_mean = mean(grain_yield.t.ha, na.rm = TRUE),
-             BW_trial_variance = sd(grain_yield.t.ha, na.rm = TRUE) ^ 2
+   summarise(trial_mean = mean(grain_yield.t.ha., na.rm = TRUE),
+             BW_trial_variance = sd(grain_yield.t.ha., na.rm = TRUE) ^ 2
              ) # I am not sure I have calculated between trial variance or trial variance// Should I be using a denominator (N-1) or (N), sd by default uses (N-1)
+
+# by excluding the standard deviation of each treatment I have discarded much of the variance.
+Should I simulate a larger number of samples for each treatment to reflect the sample distribution of each treatment and then take the mean and standard deviation of the whole trial of the simulated data?
 
@@
 for(i in SV_Trials){
-   PM_MB_means[PM_MB_means$Trial_ref == i, "TrialVariance"] <- PM_MB_means_T[PM_MB_means_T$Trial_ref == i,"Trial_variance"]
+   PM_MB_means[PM_MB_means$Trial_ref == i, "TrialVariance"] <- PM_MB_means_T[PM_MB_means_T$Trial_ref == i,"BW_trial_variance"]
 }

### 2019-10-15 R/OD_DL_csv.R

@@ -15,6 +15,6 @@ OD_DL_csv <- function(sharedURL, file_name, save2wd = FALSE){
          to = "./")
    }
    
-   return(read.csv(paste0(tempdir(), "\\" ,file_name)))
+   return(read.csv(paste0(tempdir(), "\\" ,file_name), stringsAsFactors = FALSE ))
    
 }

### 2019-10-15 R/import_data.R

@@ -22,7 +22,7 @@ import_data <- function() {
    x$fungicide_ai <- as.factor(x$fungicide)
    x$trade_name <- as.factor(x$trade_name)
    x$year <- as.factor(x$year)
-   x$replicates <- as.factor(x$replicates)
+   x$replicates <- as.numeric(x$replicates)
    x$planting_date <- as.Date(x$planting_date, format = "%d/%m/%Y")
    x$emergence_date <- as.Date(x$emergence_date, format = "%d/%m/%Y")
    x$flowering_date <- as.Date(x$flowering_date, format = "%d/%m/%Y")
@@ -38,5 +38,6 @@ import_data <- function() {
    x$fungicide_application_7 <- as.Date(x$fungicide_application_7, format = "%d/%m/%Y")
    x$harvest_date <- as.Date(x$harvest_date, format = "%d/%m/%Y")
    x$final_assessment <- as.Date(x$final_assessment, format = "%d/%m/%Y")
+   x$Y_error_type <- as.character(x$Y_error_type)
    return(x)
 }

### 2019-10-18 05_MetaAnalysis.Rmd
Add section to look at genotype variability Add chunk to investigate the influence of rainfall on yeilds-  not complete

@@
    - Jade: Moderately susceptible
+
+#### Genotype yield variability
+
+Host genotype seems to contribute to the variation in yield. Berken shows higher yields compared to crystal and jade.
+```{r}
+source("R/yield_volatility.r") #function to investigate the volatility in yields
+
+yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
+yield_volatility(genotype_by_trial = FALSE, control_only = TRUE)
+yield_volatility(genotype_by_trial = FALSE, control_only = FALSE, location = "Hermitage")
+
+yield_volatility("Crystal",control_only = TRUE)
+yield_volatility("Crystal",control_only = FALSE)
+
+yield_volatility("Jade",control_only = TRUE)
+yield_volatility("Jade",control_only = FALSE, location = "Hermitage")
+
+```
+
+## Yield vs in-season rain
+
+```{r}
+experiment_sites <- read.csv("data/Mungbean_experiment_sites.csv", stringsAsFactors = FALSE)
+
+rain_dat <- PM_MB_means[!is.na(PM_MB_means$planting_date),] # Which locations don't have NA for planting date
+unique(as.character(rain_dat$location)) # locations with recorded planting date
+
+rain_dat_sum <- rain_dat %>%
+   group_by(trial_ref) %>%
+   summarise(location = unique(location),
+             planting_date = unique(as.character(planting_date))[1],
+             grain_yield = mean(grain_yield.t.ha., na.rm = TRUE))
+
+rain_dat_sum <- rain_dat_sum[order(rain_dat_sum$location),] # order them to make adding the lat long easier
+
+rain_dat_sum$lat <- NA
+rain_dat_sum$lon <- NA
+
+# 
+rain_dat_sum[rain_dat_sum$location == "Bongeen_1", c("lat","lon")] <- 
+   experiment_sites[experiment_sites$location == "Bongeen 1 & 2",c("lat","lon")]
+
+rain_dat_sum[rain_dat_sum$location == "Hermitage", c("lat","lon")] <- 
+   experiment_sites[experiment_sites$location == "Hermitage Research Station",c("lat","lon")]
+
+rain_dat_sum[rain_dat_sum$location == "Gatton", c("lat","lon")] <- 
+   experiment_sites[experiment_sites$location == "Gatton",c("lat","lon")]
+
+rain_dat_sum[rain_dat_sum$location == "Kingaroy", c("lat","lon")] <- 
+   experiment_sites[experiment_sites$location == "Red Vale & Kingaroy Research Station",c("lat","lon")]
+
+rain_dat_sum[rain_dat_sum$location == "Missen Flats", c("lat","lon")] <- 
+   experiment_sites[experiment_sites$location == "Missen Flats",c("lat","lon")]
+
+rain_dat_sum[rain_dat_sum$location == "Premer", c("lat","lon")] <- 
+   experiment_sites[experiment_sites$location == "NGA - Premer",c("lat","lon")]
+
+rain_dat_sum[rain_dat_sum$location == "Emerald", c("lat","lon")] <- 
+   experiment_sites[experiment_sites$location == "Emerald Agricultural College",c("lat","lon")]
+
+rain_dat_sum[rain_dat_sum$location == "Redvale", c("lat","lon")] <- 
+   experiment_sites[experiment_sites$location == "Red Vale & Kingaroy Research Station",c("lat","lon")]
+
+rain_dat_sum[rain_dat_sum$location == "Wellcamp", c("lat","lon")] <- 
+   experiment_sites[experiment_sites$location == "Wellcamp",c("lat","lon")]
+
+source("R/AUS_rainfall_function.r")
+
+# use Bomrang to find the quantaty of rain for the season and do a linear regression
+
+```
 

### 2019-10-18 R/AUS_rainfall_function.r
intiate writing a function to return the quantity of rainfall between two dates for a specific location

@@ -1,0 +1,27 @@
+AUS_rainfall <- function(StartDate = Sys.Date()-30,
+                         EndDate = Sys.Date(),
+                       StationID = "041525",
+                       latlong = NULL){
+   # This function should return the quantity of rainfall between the input dates
+   library(bomrang)
+   
+   
+   if(is.null(latlong)){
+      
+      rain <- as.data.frame(get_historical(stationid = StationID, type = c("rain")))   
+   }else{
+      rain <- as.data.frame(get_historical(latlon = latlong , type = c("rain")))   
+   }
+   
+   season <- EndDate - StartDate
+   
+   Date1 <- as.numeric(unlist(strsplit(as.character(StartDate),"-")))
+   Date2 <- as.numeric(unlist(strsplit(as.character(StartDate),"-")))
+   
+   x1 <- sum(rain[rain$year == Date1[1] &
+                     rain$year == Date2[1] &
+                     rain$month == Date[2] &
+                     rain$day >= Date[3] &
+                     rain$day < Date[3] + 7, ]$rainfall > 0, na.rm = TRUE)
+   return(x1)                                       
+}

### 2019-10-18 R/yield_volatility.R
Yield volatility function for the PM_MB_means dataset

@@ -1,0 +1,117 @@
+yield_volatility <- function(genotype, control_only = TRUE, genotype_by_trial = TRUE, location = NA){
+   
+   if(isTRUE(genotype_by_trial)){
+   
+   if(isTRUE(control_only)){
+      dat1 <- PM_MB_means[PM_MB_means$host_genotype == genotype &
+                             PM_MB_means$Y_error_type == "stdev" &
+                             PM_MB_means$trial_ref != "mung1718/01" &  # Outlier
+                             PM_MB_means$fungicide == "control", ]
+   }else{
+      dat1 <- PM_MB_means[PM_MB_means$host_genotype == genotype &
+                             PM_MB_means$trial_ref != "mung1718/01" & # Outlier
+                             PM_MB_means$Y_error_type == "stdev", ]    
+   }
+   
+   dat1 <- dat1[!is.na(dat1$trial_ref),]
+   
+   for(i in unique(dat1$trial_ref)){
+      
+      
+      dat2 <- dat1[dat1$trial_ref == i,]
+      for(j in seq_along(dat2$trial_ref)){
+         if(j == 1 & i == unique(dat1$trial_ref)[1]){
+            dat3 <-data.frame()
+         }
+         
+         
+         dat3 <- rbind(dat3, data.frame(trial = rep(i, times = 600),
+                                        values = rnorm(n = 600,
+                                                       mean = dat2$grain_yield.t.ha.[j], 
+                                                       sd = dat2$yield_error[j]))
+         )
+      }}
+   
+   seq_along(10)      
+   
+   Plot1 <- dat3 %>%
+      ggplot(aes(x = values))+
+      geom_density(aes(fill = trial), alpha = 0.4)
+   
+   mean_Y_volatility <- dat3 %>%
+      group_by(trial) %>%
+      summarise(volatility = sort(values)[0.975 * length(values)] - 
+                   sort(values)[0.025 * length(values)])
+   
+   
+   return(list(dat3,Plot1, mean_Y_volatility))
+   }
+   
+   
+   
+   
+   
+   if(isFALSE(genotype_by_trial)){
+      if(isTRUE(control_only)){
+         if(!is.na(location)){
+            dat1 <- PM_MB_means[PM_MB_means$Y_error_type == "stdev" &
+                                   PM_MB_means$location == location &
+                                   PM_MB_means$trial_ref != "mung1718/01" &  # Outlier
+                                   PM_MB_means$fungicide == "control", ]
+         }
+         if(is.na(location)){
[…]

### 2019-10-22 R/AUS_rainfall_function.r
Some edits to try and make the data Cache to speed up looping and applying

@@ -1,27 +1,106 @@
 AUS_rainfall <- function(StartDate = Sys.Date()-30,
                          EndDate = Sys.Date(),
-                       StationID = "041525",
-                       latlong = NULL){
+                         lat = NULL,
+                         long = NULL,
+                         StationID = "041525"
+                       ){
    # This function should return the quantity of rainfall between the input dates
-   library(bomrang)
+   #library(bomrang)
+   #lat <- experiment_sites[experiment_sites$location == "Emerald Agricultural College","lat"]
+   #long <- experiment_sites[experiment_sites$location == "Emerald Agricultural College","lon"]
    
+
+   StartDate <- as.Date(StartDate)
+   EndDate <- as.Date(EndDate)
    
-   if(is.null(latlong)){
+   if(is.null(lat) & is.null(long)){
       
-      rain <- as.data.frame(get_historical(stationid = StationID, type = c("rain")))   
+      temp_files <- list.files(tempdir())
+      if(sum(temp_files == paste0("IDCJAC0009_",StationID,"_1800_Data.csv"))>0){
+         rain <- read.csv(paste0(tempdir(),"\\IDCJAC0009_",StationID,"_1800_Data.csv"))
+      }else{
+      
+      rain <- as.data.frame(get_historical(stationid = StationID, type = c("rain")))
+      }
+      
+      
+      
    }else{
-      rain <- as.data.frame(get_historical(latlon = latlong , type = c("rain")))   
-   }
    
-   season <- EndDate - StartDate
+   
+   
+			
+      
+      if(sum(list.files(tempdir()) == "cache_rain.csv") > 0){
+         cache_rain <- read.csv(paste0(tempdir(),"\\cache_rain.csv"), stringsAsFactors = FALSE)
+         
+         if(length(cache_rain[cache_rain$latt == lat &
+                       cache_rain$lon == long,]$BOM.station.number) > 0){
+            StationID <- as.character(cache_rain[cache_rain$latt == lat &
+                                                    cache_rain$lon == long,]$BOM.station.number[1])
+            
+            if(nchar(StationID) == 5){
+               StationID <- paste0("0",StationID)
+            }
+            if(nchar(StationID) == 4){
+               StationID <- paste0("00",StationID)
+            }
+            
+            temp_files <- list.files(tempdir())
[…]

### 2019-10-22 05_MetaAnalysis.Rmd
Investigations for what contributes to yield volatility

@@
 library(theme.usq)
+library(bomrang)
 source("R/import_data.R")
@@
 Host genotype seems to contribute to the variation in yield. Berken shows higher yields compared to crystal and jade.
-```{r}
+```{r yield_vol}
 source("R/yield_volatility.r") #function to investigate the volatility in yields
@@
 
-```{r}
+```{r yield_from_rain}
 experiment_sites <- read.csv("data/Mungbean_experiment_sites.csv", stringsAsFactors = FALSE)
@@
 
+# sweep_for_stations(latlon = unlist(c(rain_dat_sum[rain_dat_sum$location == "Premer", c("lat","lon")])))[2,c("lon")]
+# closest weather to Premer does not have rain, recoding so it takes the next closest station
 rain_dat_sum[rain_dat_sum$location == "Premer", c("lat","lon")] <- 
-   experiment_sites[experiment_sites$location == "NGA - Premer",c("lat","lon")]
+   sweep_for_stations(latlon = unlist(c(rain_dat_sum[rain_dat_sum$location == "Premer", c("lat","lon")])))[2,c("lat","lon")]
 
@@
 
+rain_dat_sum[rain_dat_sum$location == "Dalby", c("lat","lon")] <- c(-27.168426, 151.264421)
+
+rain_dat_sum$rainfall_sum <- NA
+
 source("R/AUS_rainfall_function.r")
 
+# loop to download and save all the rainfall sum data
+
+for(j in -10:20){
+   if(j == -10){lm_data <- data.frame()}
+
+   for(i in seq_along(rain_dat_sum$trial_ref)){
+
+      #ERROR HANDLING
+     # possibleError <- tryCatch(
+         rain_dat_sum$rainfall_sum[i] <- 
+            AUS_rainfall(StartDate = as.Date(rain_dat_sum$planting_date)[i] + 10,
+                         EndDate = as.Date(rain_dat_sum$planting_date)[i] + 90,
+                         lat = rain_dat_sum$lat[i],
+                         long = rain_dat_sum$lon[i])
+         #error=function(e) e
+         #)
+
+      #if(inherits(possibleError, "error")) {print(possibleError)
+      #   next
+      }
+   }
+
+   lmod1 <- summary(lm(rainfall_sum ~ grain_yield, 
+                       data = rain_dat_sum[rain_dat_sum$location != "Hermitage",])) # remove hermitage which is irrigated
+
+   lm_data <- rbind(lm_data,
+                    data.frame(days_from_plant = 10,
+                               estimate = coef(lmod1)[2,1],
+                               P_value = coef(lmod1)[2,4],
+                               r_squared = lmod1$r.squared,
+                               adj_r_squared = lmod1$adj.r.squared,
+                               stringsAsFactors = FALSE)
+                    )
+
+}
+
+write.csv(lm_data, "data/rainfall_x_Gyield_lmod.csv")
+<- read.csv("data/rainfall_x_Gyield_lmod.csv", stringsAsFactors = FALSE)
+rain_dat_sum[rain_dat_sum$location != "Hermitage",] %>%
+   ggplot(aes(x = rainfall_sum, y = grain_yield )) + 
+   geom_point(aes(colour = location)) +
+   geom_smooth(method = "lm")
+
 # use Bomrang to find the quantaty of rain for the season and do a linear regression
+
+is.vector(unlist(c(rain_dat_sum[1,5],rain_dat_sum[1,6])))
+
+plot(P_value ~ days_from_plant, data = lm_data)
+plot(r_squared ~ days_from_plant, data = lm_data)
+plot(estimate ~ days_from_plant, data = lm_data)
+
+tmp1 <- read.csv("C:/Users/U8011054/AppData/Local/Temp/RtmpkbEvfL/IDCJAC0009_041359_1800_Data.csv", stringsAsFactors = FALSE)
+
+nchar(tmp1$Bureau.of.Meteorology.station.number[1])
+strsp
+
+head(tmp1)
+message()
 

### 2019-10-23 05_MetaAnalysis.Rmd
install packages Started work on First incidence graph

@@
 ```{r MEsummary_Libraries, message=FALSE}
+install.packages("tidyverse")
+install.packages("devtools")
+devtools::install_github("https://github.com/PaulMelloy/bomrang")
+devtools::install_github("https://github.com/adamhsparks/theme.usq")
+
 library(tidyverse)
@@
 message()
+
+```
+
+```{r first_incidence}
+# Here I want to build a plot of horizontal lines indicating the season length and
+# place a dot on the line to indicating the day of the year first sign was observed for that trial
+
+FS_dates <- data.frame(first_sign = as.Date(unique(PM_MB_means$first_sign_disease)),
+                       plant.date = as.Date(PM_MB_)
+)
+
+PM_MB_
+
+dat1 <- data.frame(First_sign = sort(format(FS_dates, "%b-%d"))[c(5:25,1:4)])
+
+dat1$First_sign <- as.Date(dat1$First_sign)
+
+ggplot(dat1, aes(x = First_sign))+
+   geom_dotplot()+
+   scale_x_date()+
+   coord_flip()
+
+as.character(format(FS_dates, "%b-%d"))
+
+as.Date()
 

### 2019-10-23 05_MetaAnalysis.Rmd
Remove Trycatch error handling

@@
 source("R/AUS_rainfall_function.r")
-
 # loop to download and save all the rainfall sum data
@@
 
-      #ERROR HANDLING
-     # possibleError <- tryCatch(
          rain_dat_sum$rainfall_sum[i] <- 
@@
                          long = rain_dat_sum$lon[i])
-         #error=function(e) e
-         #)
 
-      #if(inherits(possibleError, "error")) {print(possibleError)
-      #   next
       }
@@
 
-}
-
-write.csv(lm_data, "data/rainfall_x_Gyield_lmod.csv")
-<- read.csv("data/rainfall_x_Gyield_lmod.csv", stringsAsFactors = FALSE)
+#write.csv(lm_data, "data/rainfall_x_Gyield_lmod.csv")
+lm_data <- read.csv("data/rainfall_x_Gyield_lmod.csv", stringsAsFactors = FALSE)
 rain_dat_sum[rain_dat_sum$location != "Hermitage",] %>%

### 2019-10-23 05_MetaAnalysis.Rmd
Added chunks for start of season rainfall and end of season rainfall.
Edited rainfall lm plots

@@
 ```{r MEsummary_Libraries, message=FALSE}
-install.packages("tidyverse")
-install.packages("devtools")
-devtools::install_github("https://github.com/PaulMelloy/bomrang")
-devtools::install_github("https://github.com/adamhsparks/theme.usq")
+# install.packages("tidyverse")
+# install.packages("devtools")
+# devtools::install_github("https://github.com/PaulMelloy/bomrang")
+# devtools::install_github("https://github.com/adamhsparks/theme.usq")
+# install.packages("lme4")
 
@@
 
-```{r yield_from_rain}
+In crop rain could be a significant factor which contributes to the end of season grain yield.
+To investigate any relationship I will loop a linear model over time periods from 10 days prior to planting, to 100 days after planting.
+
+```{r yield_from_rain_DataRangle}
+# Import the information for each experimental site
 experiment_sites <- read.csv("data/Mungbean_experiment_sites.csv", stringsAsFactors = FALSE)
@@
 
+# Create data set for which we will input the sum in-crop rainfall
 rain_dat_sum <- rain_dat %>%
@@
 
+# add columns for lat and lon
 rain_dat_sum$lat <- NA
@@
 
-# 
+# Input lat and lon to dataframe for each experimental location
 rain_dat_sum[rain_dat_sum$location == "Bongeen_1", c("lat","lon")] <- 
@@
 rain_dat_sum[rain_dat_sum$location == "Dalby", c("lat","lon")] <- c(-27.168426, 151.264421)
+```
 
+Loop over the dates at the start of the season (to 90 days after planting) to find which date fits the best linear model for grain weight and in-crop rainfall.
+```{r rainfall_sum_Sstart}
+# add column for sum in-crop rainfall
 rain_dat_sum$rainfall_sum <- NA
 
+# source funtion that uses bomrang get_historical to return the sum rainfall between two dates
 source("R/AUS_rainfall_function.r")
 # loop to download and save all the rainfall sum data
+# this first loop Investigate when is the first day in the season for which in-crop rainfall is important
 
-for(j in -10:20){
-   if(j == -10){lm_data <- data.frame()}
+for(j in -20:20){
+   if(j == -20){lm_data <- data.frame()}
 
@@
          rain_dat_sum$rainfall_sum[i] <- 
-            AUS_rainfall(StartDate = as.Date(rain_dat_sum$planting_date)[i] + 10,
-                         EndDate = as.Date(rain_dat_sum$planting_date)[i] + 90,
+            AUS_rainfall(StartDate = (as.Date(rain_dat_sum$planting_date)[i] + j),
+                         EndDate = (as.Date(rain_dat_sum$planting_date)[i] + 90 ),
                          lat = rain_dat_sum$lat[i],
@@
 
-      }
    }
@@
       lm_data <- rbind(lm_data,
-                    data.frame(days_from_plant = 10,
+                    data.frame(days_from_plant = j,
                                estimate = coef(lmod1)[2,1],
@@
 
+   } # If it aborts with an error Error in row_start:(row_start + season) : argument of length 0, just re-run the code
+
+plot(log(P_value) ~ days_from_plant, data = lm_data)
+abline(v = lm_data[lm_data$P_value == min(lm_data$P_value),"days_from_plant"])
+plot(r_squared ~ days_from_plant, data = lm_data)
+abline(v = lm_data[lm_data$r_squared == max(lm_data$r_squared),"days_from_plant"])
+plot(estimate ~ days_from_plant, data = lm_data)
+abline(v = 14, h = lm_data[lm_data$r_squared == max(lm_data$r_squared),"estimate"], col = "grey")
+```
+
+```{r rainfall_sum_SEnd}
+
+# Loop to find the last day in the season for which in crop rainfall is important
+for(j in -20:20){
+   if(j == -10){lm_data <- data.frame()}
+
+   for(i in seq_along(rain_dat_sum$trial_ref)){
+
+         rain_dat_sum$rainfall_sum[i] <- 
+            AUS_rainfall(StartDate = (as.Date(rain_dat_sum$planting_date)[i] + 11),
+                         EndDate = (as.Date(rain_dat_sum$planting_date)[i] + 90 + j),
+                         lat = rain_dat_sum$lat[i],
+                         long = rain_dat_sum$lon[i])
+
+   }
+
+    lmod1 <- summary(lm(rainfall_sum ~ grain_yield, 
+                       data = rain_dat_sum[rain_dat_sum$location != "Hermitage",])) # remove hermitage which is irrigated
+
+      lm_data <- rbind(lm_data,
+                    data.frame(days_from_plant = j,
+                               estimate = coef(lmod1)[2,1],
+                               P_value = coef(lmod1)[2,4],
+                               r_squared = lmod1$r.squared,
+                               adj_r_squared = lmod1$adj.r.squared,
+                               stringsAsFactors = FALSE)
+                    )
+
+   }
+
+plot(P_value ~ days_from_plant, data = lm_data)
+abline(v = -3)
+abline(h = 0.00315, col = "grey")
+plot(r_squared ~ days_from_plant, data = lm_data)
+abline(v = -3)
+abline(h = 0.562, col = "grey")
+plot(estimate ~ days_from_plant, data = lm_data)
+abline(v = -3)
+
 #write.csv(lm_data, "data/rainfall_x_Gyield_lmod.csv")
+
 lm_data <- read.csv("data/rainfall_x_Gyield_lmod.csv", stringsAsFactors = FALSE)
@@
 
-is.vector(unlist(c(rain_dat_sum[1,5],rain_dat_sum[1,6])))
-
-plot(P_value ~ days_from_plant, data = lm_data)
-plot(r_squared ~ days_from_plant, data = lm_data)
-plot(estimate ~ days_from_plant, data = lm_data)
-
-tmp1 <- read.csv("C:/Users/U8011054/AppData/Local/Temp/RtmpkbEvfL/IDCJAC0009_041359_1800_Data.csv", stringsAsFactors = FALSE)
-
-nchar(tmp1$Bureau.of.Meteorology.station.number[1])
-strsp
-
-head(tmp1)
-message()
-
 ```
+The approximate period when in-crop rainfall impacts the most on the mean harvest is bettween 11 - 88 days after planting.
 
@@
 
-FS_dates <- data.frame(first_sign = as.Date(unique(PM_MB_means$first_sign_disease)),
-                       plant.date = as.Date(PM_MB_)
+season_dates <- PM_MB_means %>%
+   group_by(trial_ref)%>%
+   summarise(Planting_date = unique(planting_date),
+             Harvest_date = unique(harvest_date),
+             First_sign_PM = unique(first_sign_disease),
+             season_length = as.integer(as.Date(unique(harvest_date)) - as.Date(unique(planting_date)))
              )
 
-PM_MB_
+# function to extract date from the year
+# format should be Universal time format
+source("R/year2day.r")
+year.day(season_dates$Planting_date[5])
 
-dat1 <- data.frame(First_sign = sort(format(FS_dates, "%b-%d"))[c(5:25,1:4)])
+season_dates$Planting_day <- unlist(lapply(season_dates$Planting_date,year2day))
+season_dates$Disease_day <- unlist(lapply(season_dates$First_sign_PM,year2day))
+season_dates$Harvest_day <- season_dates$Planting_day + season_dates$season_length
 
-dat1$First_sign <- as.Date(dat1$First_sign)
+season_dates[1,"Planting_day"] <- year2day(as.Date("2012-02-28")-7) # planted in december and emerged in February, Assuming due to lack of rain or recording error.
+Using 7 days prior to emergence day as planting day
 
-ggplot(dat1, aes(x = First_sign))+
-   geom_dotplot()+
-   scale_x_date()+
-   coord_flip()
+first_day_month <- c(0, 31, 59, 90, 120, 151, 181, 211, 243, 273)
+axis_labels_date <- c(format(Sys.Date() - year2day(Sys.Date()) + first_day_month[1], "%b-%d"),  # Jan
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[2], "%b-%d"), # Feb
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[3], "%b-%d"), # March
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[4], "%b-%d"), # April
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[5], "%b-%d"), # May
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[6], "%b-%d"), # June
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[7], "%b-%d"), # July
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[8], "%b-%d"), # August
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[9], "%b-%d"), # Sept
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[10], "%b-%d") # October
+                         )
+
+# reorder the factors so they will appear in chronilogical order
+# I used First sign because all trials have recorded this
+season_dates$trial_ref <- factor(season_dates$trial_ref, levels = levels(season_dates$trial_ref)[rev(order(season_dates$First_sign_PM))])
+
+season_dates %>%
+   ggplot()+
+   geom_pointrange(aes(x = trial_ref, y = Disease_day, ymin = Planting_day, ymax = Harvest_day))+
+   scale_y_continuous(
+      limits = c(0, max(season_dates$Planting_day + 
+                           season_dates$season_length, 
+                        na.rm = TRUE)),
+      labels = axis_labels_date,
+      breaks = first_day_month
+   )+
+   geom_point(aes(x = trial_ref, y = Disease_day))+
+   coord_flip()+
+   ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
+
+    scale_x_continuous(
+      limits = c(0, 200),
+      labels = c(),
+      breaks = c(1, 50, 100, 150, 200)
+   )
 
@@
 as.Date()
+
+head(season_dates)
 

### 2019-10-23 R/AUS_rainfall_function.r
Function works well if data is downloaded. Still getting an error on first downloads where it can't compute the season length

@@ -6,8 +6,8 @@ AUS_rainfall <- function(StartDate = Sys.Date()-30,
                        ){
    # This function should return the quantity of rainfall between the input dates
    #library(bomrang)
-   #lat <- experiment_sites[experiment_sites$location == "Emerald Agricultural College","lat"]
-   #long <- experiment_sites[experiment_sites$location == "Emerald Agricultural College","lon"]
+   # lat <- experiment_sites[experiment_sites$location == "Missen Flats","lat"]
+   # long <- experiment_sites[experiment_sites$location == "Missen Flats","lon"]
    
 
    StartDate <- as.Date(StartDate)
@@ -47,16 +47,18 @@ AUS_rainfall <- function(StartDate = Sys.Date()-30,
             }
             
             temp_files <- list.files(tempdir())
-            if(sum(temp_files == paste0("IDCJAC0009_",StationID,"_1800_Data.csv"))>0){
+            if(sum(temp_files == paste0("IDCJAC0009_",StationID,"_1800_Data.csv")) > 0){
                rain <- read.csv(paste0(tempdir(),"\\IDCJAC0009_",StationID,"_1800_Data.csv"), stringsAsFactors = FALSE)
-               }else{
+               }
+            if(sum(temp_files == paste0("IDCJAC0009_",StationID,"_1800_Data.csv")) == 0){
                   rain <- as.data.frame(get_historical(latlon = unlist(c(lat,long)) , type = c("rain")))
                }
-            #rain <- as.data.frame(get_historical(latlon = unlist(c(lat,long)) , type = c("rain")))
+            
             }else{
                rain <- as.data.frame(get_historical(latlon = unlist(c(lat,long)) , type = c("rain")))
             }
-         }else{
+         }
+      if(sum(list.files(tempdir()) == "cache_rain.csv") == 0){
             cache_rain <- data.frame()
             rain <- as.data.frame(get_historical(latlon = unlist(c(lat,long)) , type = c("rain")))
          }
@@ -89,18 +91,19 @@ AUS_rainfall <- function(StartDate = Sys.Date()-30,
          cache_rain <- rbind(cache_rain,cache_rain_tmp)
          write.csv(cache_rain, paste0(tempdir(),"\\cache_rain.csv"), row.names = FALSE)
 
-   
+   #StartDate <- as.Date("2017-01-27")-10
+   #EndDate <- as.Date("2017-01-27")+90
    
    season <- as.numeric(as.Date(EndDate) - as.Date(StartDate))
    
[…]

### 2019-10-23 02_Weather.Rmd
Moved year.day function to it's own R file and referenced with source. I used this function in other chapters

@@
 # format should be Universal time format
-year.day <- function(date) {
-   if (is.na(date) == TRUE) {
-      return(NA)
-   } else {
-      return(as.numeric(as.Date(date) - as.Date(paste0(
-         substr(date, start = 1, stop = 4), "-01-01"
-      ))))
-   }
-}
+source("R/year2day.r")
 
@@
       Year = substr(war_Tm_aver$date, start = 1, stop = 4),
-      Day = year.day(war_Tm_aver$date)
+      Day = year2day(war_Tm_aver$date)
    )
@@
    filter(Location == "Hermitage") %>%
-   mutate(Day = year.day(First_sign))
+   mutate(Day = year2day(First_sign))
 
@@
       Year = substr(Gat_Tm_aver$date, start = 1, stop = 4),
-      Day = year.day(Gat_Tm_aver$date)
+      Day = year2day(Gat_Tm_aver$date)
    )
@@
    mutate(Year = factor(substr(First_sign, 1, 4)),
-          Day = year.day(First_sign))
+          Day = year2day(First_sign))
 

### 2019-10-29 05_MetaAnalysis.Rmd
Added a looped analysis to investigate the best incrop rainfall window to predict grain yield

@@
 
+# see Yield vs in-season rain section on the influence of rain and irrigation on grain yield
+PM_MB_means$irrigation <- NA
+PM_MB_means[PM_MB_means$location == "Hermitage", "irrigation"] <- TRUE
+PM_MB_means[PM_MB_means$location != "Hermitage", "irrigation"] <- FALSE
+
 ```
 
-## Visualise Data
+## Explore and visualise Data
 
@@
 
-## Yield vs in-season rain
+### Yield vs in-season rain
 
@@
 
+#### Best start day for in-crop rainfall
+
 Loop over the dates at the start of the season (to 90 days after planting) to find which date fits the best linear model for grain weight and in-crop rainfall.
+
 ```{r rainfall_sum_Sstart}
@@
 source("R/AUS_rainfall_function.r")
+
 # loop to download and save all the rainfall sum data
@@
 
+# use Bomrang to find the quantaty of rain for the season and do a linear regression
+for(k in -19:20){
+for(j in -9:30){
+
+   lm_rain <- data.frame(start_day = rep(-20:40, times = length(-30:30)),
+              end_day = rep(-30:30, each = length(-20:40)),
+              lm_pval = NA,
+              lm_rsquared = NA,
+              lm_adj_rsquared = NA
+   )
+   dim(lm_rain)
+
+# for using parRapply   
+#    cl8 <- makeCluster(getOption("cl.cores", 8))
+# clusterExport(cl8, list("rain_dat_sum", "AUS_rainfall", "lm_rain", "get_historical"))
+
+   testlist1 <- apply(lm_rain,1,function(x1){
+         for(i in seq_along(rain_dat_sum$trial_ref)){
+
+         rain_dat_sum$rainfall_sum <- AUS_rainfall(StartDate = as.Date(rain_dat_sum$planting_date)[i] + x1[1],
+                                                   EndDate = as.Date(rain_dat_sum$planting_date[i]) + 80 + x1[2],
+                                                   lat = rain_dat_sum$lat[i],
+                                                   long = rain_dat_sum$lon[i])
+         }
+         lmod1 <- summary(lm(rainfall_sum ~ grain_yield, 
+                       data = rain_dat_sum[rain_dat_sum$location != "Hermitage",])) # remove hermitage which is irrigated
+
+         pval <- coef(lmod1)[2,4]
+         rsqu <- lmod1$r.squared
+         ADrs <- lmod1$adj.r.squared
+         return(list(pval,rsqu,ADrs))
+
+         })
+
+head(testlist1)   
+lm_rain$lm_pval <- head(bind_rows(testlist1))
+   ?bind_rows
+
+for(i in seq_along(testlist1)){
+   lm_rain$lm_pval[i] <- testlist1[[i]][[1]]
+   lm_rain$lm_rsquared[i] <- testlist1[[i]][[2]]
+   lm_rain$lm_adj_rsquared[i] <- testlist1[[i]][[3]]
+}
+head(lm_rain)
+
+summary(lm_rain$lm_adj_rsquared)
+
+ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_pval))+
+   geom_contour()
+
+   if(k == -19 & j == -19){
+      lm_pval <- matrix(nrow = 40,
+                        ncol = 40)
+      colnames(lm_pval) <- as.character(-19:20) # End date
+      row.names(lm_pval) <- as.character(-9:30) # start date
+
+      lm_square <- matrix(nrow = 40,
+                          ncol = 40)
+      colnames(lm_square) <- as.character(-19:20) # End date
+      row.names(lm_square) <- as.character(-9:30) # start date
+      }
+
+   for(i in seq_along(rain_dat_sum$trial_ref)){
+
+         rain_dat_sum$rainfall_sum[i] <- 
+            AUS_rainfall(StartDate = (as.Date(rain_dat_sum$planting_date)[i] + j),
+                         EndDate = (as.Date(rain_dat_sum$planting_date)[i] + 80 + k ),
+                         lat = rain_dat_sum$lat[i],
+                         long = rain_dat_sum$lon[i])
+
+   }
+
+    lmod1 <- summary(lm(rainfall_sum ~ grain_yield, 
+                       data = rain_dat_sum[rain_dat_sum$location != "Hermitage",])) # remove hermitage which is irrigated
+
+      lm_pval[j,k] <- coef(lmod1)[2,4]
+      lm_square[j,k] <- lmod1$r.squared
+
+   }
+   }# If it aborts with an error Error in row_start:(row_start + season) : argument of length 0, just re-run the code
+
+image(1:ncol(lm_pval), 1:nrow(lm_pval), t(lm_pval), col = terrain.colors(60), axes = TRUE)
+
+image(1:ncol(lm_square), 1:nrow(lm_square), t(lm_square), col = terrain.colors(60), axes = TRUE)
+
+ggplot(lm_pval, aes(x = colnames(lm_pval), y = row.names(lm_pval), z = ))
+
+plot(log(P_value) ~ days_from_plant, data = lm_data)
+abline(v = lm_data[lm_data$P_value == min(lm_data$P_value),"days_from_plant"], col = "grey")
+text(x = lm_data[lm_data$P_value == min(lm_data$P_value),"days_from_plant"], 
+     y = log(max(lm_data$P_value))/0.95, 
+     labels = paste("pvalue =",round(min(lm_data$P_value),2)),
+     pos = 4)
+plot(r_squared ~ days_from_plant, data = lm_data)
+abline(v = lm_data[lm_data$r_squared == max(lm_data$r_squared),"days_from_plant"], col = "grey")
+text(x = lm_data[lm_data$r_squared == max(lm_data$r_squared),"days_from_plant"], 
+     y = max(lm_data$r_squared * 0.75), 
+     labels = paste("Rsquared =",round(max(lm_data$r_squared),4)),
+     pos = 2)
+
+plot(estimate ~ days_from_plant, data = lm_data)
+abline(v = 14, h = lm_data[lm_data$r_squared == max(lm_data$r_squared),"estimate"], col = "grey")
+```
+
+#### Best end day for in-crop rainfall
+
+```{r rainfall_sum_SEnd}
+
+# Loop to find the last day in the season for which in crop rainfall is important
 for(j in -20:20){
@@
          rain_dat_sum$rainfall_sum[i] <- 
-            AUS_rainfall(StartDate = (as.Date(rain_dat_sum$planting_date)[i] + j),
-                         EndDate = (as.Date(rain_dat_sum$planting_date)[i] + 90 ),
+            AUS_rainfall(StartDate = (as.Date(rain_dat_sum$planting_date)[i] + 14),
+                         EndDate = (as.Date(rain_dat_sum$planting_date)[i] + 80 + j),
                          lat = rain_dat_sum$lat[i],
@@
       lm_data <- rbind(lm_data,
-                    data.frame(days_from_plant = j,
-                               estimate = coef(lmod1)[2,1],
-                               P_value = coef(lmod1)[2,4],
-                               r_squared = lmod1$r.squared,
-                               adj_r_squared = lmod1$adj.r.squared,
-                               stringsAsFactors = FALSE)
-                    )
-
-   } # If it aborts with an error Error in row_start:(row_start + season) : argument of length 0, just re-run the code
-
-plot(log(P_value) ~ days_from_plant, data = lm_data)
-abline(v = lm_data[lm_data$P_value == min(lm_data$P_value),"days_from_plant"])
-plot(r_squared ~ days_from_plant, data = lm_data)
-abline(v = lm_data[lm_data$r_squared == max(lm_data$r_squared),"days_from_plant"])
-plot(estimate ~ days_from_plant, data = lm_data)
-abline(v = 14, h = lm_data[lm_data$r_squared == max(lm_data$r_squared),"estimate"], col = "grey")
-```
-
-```{r rainfall_sum_SEnd}
-
-# Loop to find the last day in the season for which in crop rainfall is important
-for(j in -20:20){
-   if(j == -10){lm_data <- data.frame()}
-
-   for(i in seq_along(rain_dat_sum$trial_ref)){
-
-         rain_dat_sum$rainfall_sum[i] <- 
-            AUS_rainfall(StartDate = (as.Date(rain_dat_sum$planting_date)[i] + 11),
-                         EndDate = (as.Date(rain_dat_sum$planting_date)[i] + 90 + j),
-                         lat = rain_dat_sum$lat[i],
-                         long = rain_dat_sum$lon[i])
-
-   }
-
-    lmod1 <- summary(lm(rainfall_sum ~ grain_yield, 
-                       data = rain_dat_sum[rain_dat_sum$location != "Hermitage",])) # remove hermitage which is irrigated
-
-      lm_data <- rbind(lm_data,
-                    data.frame(days_from_plant = j,
+                    data.frame(days_from_plant = j + 80,
                                estimate = coef(lmod1)[2,1],
@@
 
-plot(P_value ~ days_from_plant, data = lm_data)
-abline(v = -3)
-abline(h = 0.00315, col = "grey")
-plot(r_squared ~ days_from_plant, data = lm_data)
-abline(v = -3)
-abline(h = 0.562, col = "grey")
+plot(log(P_value) ~ days_from_plant, data = lm_data, xlab = "End of in-crop rain referenced to 90 days after planting")
+abline(v = lm_data[lm_data$P_value == min(lm_data$P_value),"days_from_plant"], col = "grey")
+text(x = lm_data[lm_data$P_value == min(lm_data$P_value),"days_from_plant"], 
+     y = max(log(lm_data$P_value * 0.75)), 
+     labels = paste("pvalue =",round(min(lm_data$P_value),4)),
+     pos = 4)
+
+plot(r_squared ~ days_from_plant, data = lm_data, xlab = "End of in-crop rain referenced to 90 days after planting")
+abline(v = lm_data[lm_data$r_squared == max(lm_data$r_squared),"days_from_plant"], col = "grey")
+text(x = lm_data[lm_data$r_squared == max(lm_data$r_squared),"days_from_plant"], 
+     y = max(lm_data$r_squared * 0.75), 
+     labels = paste("Rsquared =",round(max(lm_data$r_squared),4)),
+     pos = 2)
+
 plot(estimate ~ days_from_plant, data = lm_data)
-abline(v = -3)
+abline(v = -3 ,h = lm_data[lm_data$r_squared == max(lm_data$r_squared),"estimate"], col = "grey")
 
@@
 
-# use Bomrang to find the quantaty of rain for the season and do a linear regression
-
 ```
 The approximate period when in-crop rainfall impacts the most on the mean harvest is bettween 11 - 88 days after planting.
+
+### Season range and first incidence
 
@@
 source("R/year2day.r")
-year.day(season_dates$Planting_date[5])
 
@@
 
-    scale_x_continuous(
-      limits = c(0, 200),
-      labels = c(),
-      breaks = c(1, 50, 100, 150, 200)
-   )
-
-as.character(format(FS_dates, "%b-%d"))
-
-as.Date()
-
-head(season_dates)
-
 ```
 
-## Standardising the type of variance
+## Standardising sample variance
 
@@
 
-```{r LSD_trials}
+### Converting least-squares tp sample variance
+
+```{r all_LSD_trials}
 Trials <- PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole",
-          row_spacing == 0.75,
+   filter(
+      #fungicide_ai == "tebuconazole",
+      #    row_spacing == 0.75,
           Y_error_type == "lsd (P=0.05)") %>%
@@
 
+### Converting standard deviation to sample variance
 Now to estimate the variance from the standard deviation
@@
 
+### Estimating variance for trials without reported error
+
 Now for the trickier part creating 'Sampling Variance' for treatments where only mean yield is recorded.  
@@
    filter(fungicide_ai == "tebuconazole",
-          row_spacing.m == 0.75,
+          row_spacing == 0.75,
           is.na(Y_error_type)) %>%
@@
 (2007)](https://apsjournals.apsnet.org/doi/pdfplus/10.1094/PHYTO-97-2-0211) uses linear regression model to estimate sampling variance.
+
+#### Mixed effect model to estimate variance
 
@@
 
-length(unique(PM_MB_train$Trial_ref))
+length(unique(PM_MB_train$trial_ref))
 
 # Run a linear model with grain_yield.t.ha as a fixed effect predictor and trial as a random intercept
-PM_MB_trainLMER <- lmer(yield_error ~ grain_yield.t.ha +
+PM_MB_trainLMER <- lmer(yield_error ~ grain_yield.t.ha. +
                            (1 | trial_ref), data = PM_MB_train)
@@
 
+#### Random effects model to predict trial variance
 Just for kicks lets look at the linear regression model as a random effects model where `grain_yield.t.ha` is set as a random slope to the random intercept `trial_ref`.

### 2019-10-30 R/AUS_rainfall_function.r
Function formated to allow use by the apply family

@@ -1,7 +1,6 @@
 AUS_rainfall <- function(StartDate = Sys.Date()-30,
                          EndDate = Sys.Date(),
-                         lat = NULL,
-                         long = NULL,
+                         latlong = NULL,
                          StationID = "041525"
                        ){
    # This function should return the quantity of rainfall between the input dates
@@ -9,11 +8,12 @@ AUS_rainfall <- function(StartDate = Sys.Date()-30,
    # lat <- experiment_sites[experiment_sites$location == "Missen Flats","lat"]
    # long <- experiment_sites[experiment_sites$location == "Missen Flats","lon"]
    
-
+   
    StartDate <- as.Date(StartDate)
    EndDate <- as.Date(EndDate)
+   latlong <- as.numeric(latlong)
    
-   if(is.null(lat) & is.null(long)){
+   if(is.null(latlong)){
       
       temp_files <- list.files(tempdir())
       if(sum(temp_files == paste0("IDCJAC0009_",StationID,"_1800_Data.csv"))>0){
@@ -33,11 +33,11 @@ AUS_rainfall <- function(StartDate = Sys.Date()-30,
       
       if(sum(list.files(tempdir()) == "cache_rain.csv") > 0){
          cache_rain <- read.csv(paste0(tempdir(),"\\cache_rain.csv"), stringsAsFactors = FALSE)
-         
-         if(length(cache_rain[cache_rain$latt == lat &
-                       cache_rain$lon == long,]$BOM.station.number) > 0){
-            StationID <- as.character(cache_rain[cache_rain$latt == lat &
-                                                    cache_rain$lon == long,]$BOM.station.number[1])
+
+         if(length(cache_rain[cache_rain$latt == as.numeric(latlong[1]) &
+                       cache_rain$lon == as.numeric(latlong[2]),]$BOM.station.number) > 0){
+            StationID <- as.character(cache_rain[cache_rain$latt == as.numeric(latlong[1]) &
+                                                    cache_rain$lon == latlong[2],]$BOM.station.number[1])
             
             if(nchar(StationID) == 5){
                StationID <- paste0("0",StationID)
@@ -51,23 +51,23 @@ AUS_rainfall <- function(StartDate = Sys.Date()-30,
                rain <- read.csv(paste0(tempdir(),"\\IDCJAC0009_",StationID,"_1800_Data.csv"), stringsAsFactors = FALSE)
                }
             if(sum(temp_files == paste0("IDCJAC0009_",StationID,"_1800_Data.csv")) == 0){
[…]

### 2019-10-30 05_MetaAnalysis.Rmd
Cleaning up the grainyield x rainfall regression. moving code to a script file

@@
 ```{r rainfall_sum_Sstart}
-# add column for sum in-crop rainfall
-rain_dat_sum$rainfall_sum <- NA
+#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+#
+#       BEWARE THIS CODE REQUIRES MORE WORK AND TAKES ~10 HOURS TO RUN
+#
+# !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+# !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
 
-# source funtion that uses bomrang get_historical to return the sum rainfall between two dates
-source("R/AUS_rainfall_function.r")
-
-# loop to download and save all the rainfall sum data
-# this first loop Investigate when is the first day in the season for which in-crop rainfall is important
-
-# use Bomrang to find the quantaty of rain for the season and do a linear regression
-for(k in -19:20){
-for(j in -9:30){
-
-   lm_rain <- data.frame(start_day = rep(-20:40, times = length(-30:30)),
-              end_day = rep(-30:30, each = length(-20:40)),
-              lm_pval = NA,
-              lm_rsquared = NA,
-              lm_adj_rsquared = NA
-   )
-   dim(lm_rain)
-
-# for using parRapply   
-#    cl8 <- makeCluster(getOption("cl.cores", 8))
-# clusterExport(cl8, list("rain_dat_sum", "AUS_rainfall", "lm_rain", "get_historical"))
-
-   testlist1 <- apply(lm_rain,1,function(x1){
-         for(i in seq_along(rain_dat_sum$trial_ref)){
-
-         rain_dat_sum$rainfall_sum <- AUS_rainfall(StartDate = as.Date(rain_dat_sum$planting_date)[i] + x1[1],
-                                                   EndDate = as.Date(rain_dat_sum$planting_date[i]) + 80 + x1[2],
-                                                   lat = rain_dat_sum$lat[i],
-                                                   long = rain_dat_sum$lon[i])
-         }
-         lmod1 <- summary(lm(rainfall_sum ~ grain_yield, 
-                       data = rain_dat_sum[rain_dat_sum$location != "Hermitage",])) # remove hermitage which is irrigated
-
-         pval <- coef(lmod1)[2,4]
-         rsqu <- lmod1$r.squared
-         ADrs <- lmod1$adj.r.squared
-         return(list(pval,rsqu,ADrs))
-
-         })
-
-head(testlist1)   
-lm_rain$lm_pval <- head(bind_rows(testlist1))
-   ?bind_rows
-
-for(i in seq_along(testlist1)){
-   lm_rain$lm_pval[i] <- testlist1[[i]][[1]]
-   lm_rain$lm_rsquared[i] <- testlist1[[i]][[2]]
-   lm_rain$lm_adj_rsquared[i] <- testlist1[[i]][[3]]
-}
+source("R/Rainfall_x_cropYield.R")
 head(lm_rain)
+lm_rain <- read.csv("data/lmInSeasonRainfall.csv",stringsAsFactors = FALSE)
 
@@
    geom_contour()
-
-   if(k == -19 & j == -19){
-      lm_pval <- matrix(nrow = 40,
-                        ncol = 40)
-      colnames(lm_pval) <- as.character(-19:20) # End date
-      row.names(lm_pval) <- as.character(-9:30) # start date
-
-      lm_square <- matrix(nrow = 40,
-                          ncol = 40)
-      colnames(lm_square) <- as.character(-19:20) # End date
-      row.names(lm_square) <- as.character(-9:30) # start date
-      }
-
-   for(i in seq_along(rain_dat_sum$trial_ref)){
-
-         rain_dat_sum$rainfall_sum[i] <- 
-            AUS_rainfall(StartDate = (as.Date(rain_dat_sum$planting_date)[i] + j),
-                         EndDate = (as.Date(rain_dat_sum$planting_date)[i] + 80 + k ),
-                         lat = rain_dat_sum$lat[i],
-                         long = rain_dat_sum$lon[i])
-
-   }
-
-    lmod1 <- summary(lm(rainfall_sum ~ grain_yield, 
-                       data = rain_dat_sum[rain_dat_sum$location != "Hermitage",])) # remove hermitage which is irrigated
-
-      lm_pval[j,k] <- coef(lmod1)[2,4]
-      lm_square[j,k] <- lmod1$r.squared
-
-   }
-   }# If it aborts with an error Error in row_start:(row_start + season) : argument of length 0, just re-run the code
 

### 2019-10-30 Cluster Timing/MB_PM_data.Rmd
Add Rmd to cluster application timings

---
title: "Mungbean Powdery Mildew Spray Timing"
author: "Adam H. Sparks"
date: "30/10/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(skimr)
mb <- read_csv("data/slim-mungbean-powdery_mildew.csv")
```

# Clean data

The csv file included is already reduced in columns compared with the original file.
This next step converts the date columns to `Date` class, removes more cols, including the dates for spray applications after two (there are up to seven in some studies) and creates two columns of time differences.

The first column of time differences is for the time from first sign to first spray. The second is for time from first sign to second spray.

Any rows that are missing yield data are removed.

```{r mutate-filter}
mb <-
  mb %>%
  mutate(first_sign_disease = as.Date(first_sign_disease, format = "%d/%m/%Y")) %>%
  mutate_at(vars(starts_with("fungicide_application_")), dmy) %>%
  mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
  mutate(fungicide_timing_2 = fungicide_application_2 - first_sign_disease) %>%
  select(-c(fungicide_application_3:fungicide_application_7)) %>%
  filter(!is.na(grain_yield.t.ha.))
```

# Inspect the new data set

```{r skim}
skim(mb)
```

# Create Histograms of time differences to spray

## First spray

```{r first-spray-hist}
ggplot(filter(mb, !is.na(fungicide_timing_1)),
       aes(x = as.numeric(fungicide_timing_1))) +
  geom_histogram(bins = 50, fill = "grey") +
  geom_vline(linetype = 2,
             xintercept = 0,
             colour = "red") +
  xlab("Days from first sign") +
  ggtitle("First Application",
          subtitle = "Line at first sign") +
  theme_bw()
```

Suggest that any sprays prior to first sign are a group with another group from Day 0 to Day 3 and third group being >= Day 4.

## Second spray

```{r second-spray-hist}
ggplot(filter(mb, !is.na(fungicide_timing_2)),
       aes(x = as.numeric(fungicide_timing_2))) +
   geom_histogram(bins = 50, fill = "grey") +
   geom_vline(linetype = 2,
              xintercept = 14,
              colour = "red") +
   xlab("Days from first sign") +
   ggtitle("Second Application",
           subtitle = "Line at 14 days after first sign") +
   theme_bw()
```

Again, suggest any sprays that are prior to 14 days after first sign be first group, the second being 14 days to 17 days after first sign and the third being >= 18 days after first sign.

These groups would then have preventative (before), at first sign and then 14 days after and late applications.

```{r cluster}
mb <-
  mb %>%
  mutate(
    cluster_1 = case_when(
      fungicide_timing_1 < 0 ~ "Early",
      fungicide_timing_1 >= 0 &
        fungicide_timing_1 < 3 ~ "Recommended",
      TRUE ~ "Late"
    )
  ) %>%
  mutate(
    cluster_2 = case_when(
      fungicide_timing_2 < 13 ~ "Early",
      fungicide_timing_2 >= 13 &
        fungicide_timing_2 < 17 ~ "Recommended",
      TRUE ~ "Late"
    )
  )
```

# Histograms with Clusters

## First spray

```{r hist-clust1}
ggplot(filter(mb, !is.na(fungicide_timing_1)),
       aes(x = as.numeric(fungicide_timing_1))) +
  geom_histogram(bins = 50, aes(fill = cluster_1)) +
  scale_fill_viridis_d("Cluster") +
   geom_vline(linetype = 2,
              xintercept = 0,
              colour = "red") +
   xlab("Days from first sign") +
   ggtitle("First Application",
           subtitle = "Line at first sign") +
   theme_bw()
```

## Second spray

```{r hist-clust2}
ggplot(filter(mb, !is.na(fungicide_timing_2)),
       aes(x = as.numeric(fungicide_timing_2))) +
  geom_histogram(bins = 50, aes(fill = cluster_2)) +
  scale_fill_viridis_d("Cluster") +
  geom_vline(linetype = 2,
             xintercept = 14,
             colour = "red") +
  xlab("Days from first sign") +
  ggtitle("Second Application",
          subtitle = "Line at 14 days after first sign") +
  theme_bw()
```

Note that the cluster for the second spray "reccomended" is from Day 13, not Day 14.

### 2019-10-30 Cluster Timing/MB_PM_data.Rmd
Rearrange first step and spellcheck

@@
 library(skimr)
-mb <- read_csv("data/slim-mungbean-powdery_mildew.csv")
+mb <- read_csv("slim-mungbean-powdery_mildew.csv")
 ```
@@
   mb %>%
+  select(-c(fungicide_application_3:fungicide_application_7)) %>%
   mutate(first_sign_disease = as.Date(first_sign_disease, format = "%d/%m/%Y")) %>%
@@
   mutate(fungicide_timing_2 = fungicide_application_2 - first_sign_disease) %>%
-  select(-c(fungicide_application_3:fungicide_application_7)) %>%
   filter(!is.na(grain_yield.t.ha.))
@@
 
-Note that the cluster for the second spray "reccomended" is from Day 13, not Day 14.
+Note that the cluster for the second spray "recommended" is from Day 13, not Day 14.

### 2019-10-31 05_MetaAnalysis.Rmd
Improved rainfall x yield linear model plots and cleaner formatting

@@
 
+library(RColorBrewer)
 library(tidyverse)
@@
 In crop rain could be a significant factor which contributes to the end of season grain yield.
-To investigate any relationship I will loop a linear model over time periods from 10 days prior to planting, to 100 days after planting.
-
-```{r yield_from_rain_DataRangle}
-# Import the information for each experimental site
-experiment_sites <- read.csv("data/Mungbean_experiment_sites.csv", stringsAsFactors = FALSE)
-
-rain_dat <- PM_MB_means[!is.na(PM_MB_means$planting_date),] # Which locations don't have NA for planting date
-unique(as.character(rain_dat$location)) # locations with recorded planting date
-
-# Create data set for which we will input the sum in-crop rainfall
-rain_dat_sum <- rain_dat %>%
-   group_by(trial_ref) %>%
-   summarise(location = unique(location),
-             planting_date = unique(as.character(planting_date))[1],
-             grain_yield = mean(grain_yield.t.ha., na.rm = TRUE))
-
-rain_dat_sum <- rain_dat_sum[order(rain_dat_sum$location),] # order them to make adding the lat long easier
-
-# add columns for lat and lon
-rain_dat_sum$lat <- NA
-rain_dat_sum$lon <- NA
-
-# Input lat and lon to dataframe for each experimental location
-rain_dat_sum[rain_dat_sum$location == "Bongeen_1", c("lat","lon")] <- 
-   experiment_sites[experiment_sites$location == "Bongeen 1 & 2",c("lat","lon")]
-
-rain_dat_sum[rain_dat_sum$location == "Hermitage", c("lat","lon")] <- 
-   experiment_sites[experiment_sites$location == "Hermitage Research Station",c("lat","lon")]
-
-rain_dat_sum[rain_dat_sum$location == "Gatton", c("lat","lon")] <- 
-   experiment_sites[experiment_sites$location == "Gatton",c("lat","lon")]
-
-rain_dat_sum[rain_dat_sum$location == "Kingaroy", c("lat","lon")] <- 
-   experiment_sites[experiment_sites$location == "Red Vale & Kingaroy Research Station",c("lat","lon")]
-
-rain_dat_sum[rain_dat_sum$location == "Missen Flats", c("lat","lon")] <- 
-   experiment_sites[experiment_sites$location == "Missen Flats",c("lat","lon")]
-
-# sweep_for_stations(latlon = unlist(c(rain_dat_sum[rain_dat_sum$location == "Premer", c("lat","lon")])))[2,c("lon")]
-# closest weather to Premer does not have rain, recoding so it takes the next closest station
-rain_dat_sum[rain_dat_sum$location == "Premer", c("lat","lon")] <- 
-   sweep_for_stations(latlon = unlist(c(rain_dat_sum[rain_dat_sum$location == "Premer", c("lat","lon")])))[2,c("lat","lon")]
-
-rain_dat_sum[rain_dat_sum$location == "Emerald", c("lat","lon")] <- 
-   experiment_sites[experiment_sites$location == "Emerald Agricultural College",c("lat","lon")]
-
-rain_dat_sum[rain_dat_sum$location == "Redvale", c("lat","lon")] <- 
-   experiment_sites[experiment_sites$location == "Red Vale & Kingaroy Research Station",c("lat","lon")]
-
-rain_dat_sum[rain_dat_sum$location == "Wellcamp", c("lat","lon")] <- 
-   experiment_sites[experiment_sites$location == "Wellcamp",c("lat","lon")]
-
-rain_dat_sum[rain_dat_sum$location == "Dalby", c("lat","lon")] <- c(-27.168426, 151.264421)
-```
+To investigate any relationship I will loop a linear model over time periods from 20 days prior to planting, to 100 days after planting.
 
@@
 Loop over the dates at the start of the season (to 90 days after planting) to find which date fits the best linear model for grain weight and in-crop rainfall.
+The code for this process was moved to be contained within it's own script and can be run as a job as it can take a long time.
+The output of the script is saved with the prefix `lmInSeasonRainfall` followed by the time windows the model is run.
+For example `lmInSeasonRainfall_20.40_50.80.csv` holds the model results for start days between 20 and 40 days after planting to end window dates between 50 and 80 days after planting.
 
 ```{r rainfall_sum_Sstart}
-#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-#
-#       BEWARE THIS CODE REQUIRES MORE WORK AND TAKES ~10 HOURS TO RUN
-#
-# !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-# !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
 
 source("R/Rainfall_x_cropYield.R")
-head(lm_rain)
+
 lm_rain <- read.csv("data/lmInSeasonRainfall.csv",stringsAsFactors = FALSE)
 
-summary(lm_rain$lm_adj_rsquared)
+lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)),]
+lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),]
+lm_rain[which(lm_rain$lm_adj_rsquared == max(lm_rain$lm_adj_rsquared)),]
 
 ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_pval))+
-   geom_contour()
+   geom_raster(aes(fill = lm_pval), interpolate = TRUE)+
+   geom_contour(bins = 15, colour = "white")+
+   geom_abline(intercept = 0, slope = 1, colour = "red")+
+   geom_point(data = lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)),], aes(x = start_day, y = end_day), colour =" red")+
+   scale_fill_distiller(palette ="RdBu", direction = -1)
 
-image(1:ncol(lm_pval), 1:nrow(lm_pval), t(lm_pval), col = terrain.colors(60), axes = TRUE)
+ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_rsquared))+
+   geom_raster(aes(fill = lm_rsquared), interpolate = TRUE)+
+   geom_contour(bins = 15, colour = "white")+
+   geom_abline(intercept = 0, slope = 1, colour = "red")+
+   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),], aes(x = start_day, y = end_day), colour =" red")+
+   scale_fill_distiller(palette ="RdBu")
 
-image(1:ncol(lm_square), 1:nrow(lm_square), t(lm_square), col = terrain.colors(60), axes = TRUE)
-
-ggplot(lm_pval, aes(x = colnames(lm_pval), y = row.names(lm_pval), z = ))
+ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_adj_rsquared))+
+   geom_raster(aes(fill = lm_adj_rsquared), interpolate = TRUE)+
+   geom_contour(bins = 15, colour = "white")+
+   geom_abline(intercept = 0, slope = 1, colour = "red")+
+   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),], aes(x = start_day, y = end_day), colour =" red")+
+   scale_fill_distiller(palette ="RdBu")
 
@@
 
-#### Best end day for in-crop rainfall
-
-```{r rainfall_sum_SEnd}
-
-# Loop to find the last day in the season for which in crop rainfall is important
-for(j in -20:20){
-   if(j == -20){lm_data <- data.frame()}
-
-   for(i in seq_along(rain_dat_sum$trial_ref)){
-
-         rain_dat_sum$rainfall_sum[i] <- 
-            AUS_rainfall(StartDate = (as.Date(rain_dat_sum$planting_date)[i] + 14),
-                         EndDate = (as.Date(rain_dat_sum$planting_date)[i] + 80 + j),
-                         lat = rain_dat_sum$lat[i],
-                         long = rain_dat_sum$lon[i])
-
-   }
-
-    lmod1 <- summary(lm(rainfall_sum ~ grain_yield, 
-                       data = rain_dat_sum[rain_dat_sum$location != "Hermitage",])) # remove hermitage which is irrigated
-
-      lm_data <- rbind(lm_data,
-                    data.frame(days_from_plant = j + 80,
-                               estimate = coef(lmod1)[2,1],
-                               P_value = coef(lmod1)[2,4],
-                               r_squared = lmod1$r.squared,
-                               adj_r_squared = lmod1$adj.r.squared,
-                               stringsAsFactors = FALSE)
-                    )
-
-   }
-
-plot(log(P_value) ~ days_from_plant, data = lm_data, xlab = "End of in-crop rain referenced to 90 days after planting")
-abline(v = lm_data[lm_data$P_value == min(lm_data$P_value),"days_from_plant"], col = "grey")
-text(x = lm_data[lm_data$P_value == min(lm_data$P_value),"days_from_plant"], 
-     y = max(log(lm_data$P_value * 0.75)), 
-     labels = paste("pvalue =",round(min(lm_data$P_value),4)),
-     pos = 4)
-
-plot(r_squared ~ days_from_plant, data = lm_data, xlab = "End of in-crop rain referenced to 90 days after planting")
-abline(v = lm_data[lm_data$r_squared == max(lm_data$r_squared),"days_from_plant"], col = "grey")
-text(x = lm_data[lm_data$r_squared == max(lm_data$r_squared),"days_from_plant"], 
-     y = max(lm_data$r_squared * 0.75), 
-     labels = paste("Rsquared =",round(max(lm_data$r_squared),4)),
-     pos = 2)
-
-plot(estimate ~ days_from_plant, data = lm_data)
-abline(v = -3 ,h = lm_data[lm_data$r_squared == max(lm_data$r_squared),"estimate"], col = "grey")
-
-#write.csv(lm_data, "data/rainfall_x_Gyield_lmod.csv")
-
-lm_data <- read.csv("data/rainfall_x_Gyield_lmod.csv", stringsAsFactors = FALSE)
-rain_dat_sum[rain_dat_sum$location != "Hermitage",] %>%
-   ggplot(aes(x = rainfall_sum, y = grain_yield )) + 
-   geom_point(aes(colour = location)) +
-   geom_smooth(method = "lm")
-
-```
 The approximate period when in-crop rainfall impacts the most on the mean harvest is bettween 11 - 88 days after planting.

### 2019-10-31 R/AUS_rainfall_function.r
removed message about sum rainfall

@@ -107,7 +107,7 @@ AUS_rainfall <- function(StartDate = Sys.Date()-30,
    
    
    rainfall <- sum(rain[as.numeric(row_start):(as.numeric(row_start) + as.numeric(season)),"Rainfall.amount..millimetres."],na.rm = TRUE)
-   message(paste("rainfall:",rainfall))
+   
    message(paste0("Season days: ",season))
    return(rainfall)                                       
 }

### 2019-10-31 R/Rainfall_x_cropYield.R
editing start and end days on script

@@ -93,8 +93,8 @@ rain_dat_sum$rainfall_sum <- NA
 # this first loop Investigate when is the first day in the season for which in-crop rainfall is important
 
 # use Bomrang to find the quantaty of rain for the season and do a linear regression
-      lm_rain <- data.frame(start_day = rep(-20:40, times = length(-30:30)),
-                            end_day = rep(50:110, each = length(-20:40)),
+      lm_rain <- data.frame(start_day = rep(-10:20, times = length(50:110)),
+                            end_day = rep(50:110, each = length(-10:20)),
                             lm_pval = NA,
                             lm_rsquared = NA,
                             lm_adj_rsquared = NA
@@ -140,6 +140,9 @@ rain_dat_sum$rainfall_sum <- NA
       
       
       
+      
+      
+      
       for(i in seq_along(testlist1)){
          lm_rain$lm_pval[i] <- testlist1[[i]][[1]]
          lm_rain$lm_rsquared[i] <- testlist1[[i]][[2]]
@@ -149,3 +152,4 @@ rain_dat_sum$rainfall_sum <- NA
       write.csv(lm_rain, file = "data/lmInSeasonRainfall.csv", row.names = FALSE)
       
       message("Script completed running")
+      

### 2019-10-31 R/Rainfall_x_cropYield_s-10.20_e50.110.R
Initialiseing scripts for specific time windows

@@ -1,0 +1,164 @@
+# In crop rainfall lm loop to predict grainyield
+# See 05_MetaAnalysis.Rmd
+#  Code chunk rainfall_sum_Sstart
+# This file runs a linear model on grain yield and inseason rainfall
+# this is to find the best timeframe that contributes to grain yeild
+#
+# This file contains a start date of:
+#     between 10 days before planting and 20 days after planting
+# An end date between 
+#     50 days after planting and 110 days after planting.
+# 
+
+
+library(tidyverse)
+library(theme.usq)
+library(bomrang)
+library(parallel)
+source("R/import_data.R")
+
+
+# ___________
+# Import data
+PM_MB_means <- import_data()
+# see Yield vs in-season rain section on the influence of rain and irrigation on grain yield
+PM_MB_means$irrigation <- NA
+PM_MB_means[PM_MB_means$location == "Hermitage", "irrigation"] <- TRUE
+PM_MB_means[PM_MB_means$location != "Hermitage", "irrigation"] <- FALSE
+
+
+#_________
+# Prep data
+# Import the information for each experimental site
+experiment_sites <- read.csv("data/Mungbean_experiment_sites.csv", stringsAsFactors = FALSE)
+
+
+rain_dat <- PM_MB_means[!is.na(PM_MB_means$planting_date),] # Which locations don't have NA for planting date
+unique(as.character(rain_dat$location)) # locations with recorded planting date
+
+# Create data set for which we will input the sum in-crop rainfall
+rain_dat_sum <- rain_dat %>%
+   group_by(trial_ref) %>%
+   summarise(location = unique(location),
+             planting_date = unique(as.character(planting_date))[1],
+             grain_yield = mean(grain_yield.t.ha., na.rm = TRUE))
+
+rain_dat_sum <- rain_dat_sum[order(rain_dat_sum$location),] # order them to make adding the lat long easier
+
+# add columns for lat and lon
+rain_dat_sum$lat <- NA
+rain_dat_sum$lon <- NA
+
+
+# Input lat and lon to dataframe for each experimental location
+rain_dat_sum[rain_dat_sum$location == "Bongeen_1", c("lat","lon")] <- 
+   experiment_sites[experiment_sites$location == "Bongeen 1 & 2",c("lat","lon")]
+
+rain_dat_sum[rain_dat_sum$location == "Hermitage", c("lat","lon")] <- 
[…]

### 2019-10-31 R/Rainfall_x_cropYield_s20.40_e50.80.R

@@ -1,0 +1,169 @@
+# In crop rainfall lm loop to predict grainyield
+# See 05_MetaAnalysis.Rmd
+#  Code chunk rainfall_sum_Sstart
+# This file runs a linear model on grain yield and inseason rainfall
+# this is to find the best timeframe that contributes to grain yeild
+#
+# This file contains a start date of:
+#     between 20 days after planting and 40 days after planting
+# An end date between 
+#     50 days after planting and 80 days after planting.
+# 
+
+start1 <- 20
+start2 <- 40
+end1 <- 50
+end2 <- 80
+
+
+library(tidyverse)
+library(theme.usq)
+library(bomrang)
+library(parallel)
+source("R/import_data.R")
+
+
+# ___________
+# Import data
+PM_MB_means <- import_data()
+# see Yield vs in-season rain section on the influence of rain and irrigation on grain yield
+PM_MB_means$irrigation <- NA
+PM_MB_means[PM_MB_means$location == "Hermitage", "irrigation"] <- TRUE
+PM_MB_means[PM_MB_means$location != "Hermitage", "irrigation"] <- FALSE
+
+
+#_________
+# Prep data
+# Import the information for each experimental site
+experiment_sites <- read.csv("data/Mungbean_experiment_sites.csv", stringsAsFactors = FALSE)
+
+
+rain_dat <- PM_MB_means[!is.na(PM_MB_means$planting_date),] # Which locations don't have NA for planting date
+unique(as.character(rain_dat$location)) # locations with recorded planting date
+
+# Create data set for which we will input the sum in-crop rainfall
+rain_dat_sum <- rain_dat %>%
+   group_by(trial_ref) %>%
+   summarise(location = unique(location),
+             planting_date = unique(as.character(planting_date))[1],
+             grain_yield = mean(grain_yield.t.ha., na.rm = TRUE))
+
+rain_dat_sum <- rain_dat_sum[order(rain_dat_sum$location),] # order them to make adding the lat long easier
+
+# add columns for lat and lon
+rain_dat_sum$lat <- NA
+rain_dat_sum$lon <- NA
+
+
+# Input lat and lon to dataframe for each experimental location
+rain_dat_sum[rain_dat_sum$location == "Bongeen_1", c("lat","lon")] <- 
+   experiment_sites[experiment_sites$location == "Bongeen 1 & 2",c("lat","lon")]
+
[…]

### 2019-10-31 R/Rainfall_x_cropYield_s20.40_e80.110.R

@@ -1,0 +1,169 @@
+# In crop rainfall lm loop to predict grainyield
+# See 05_MetaAnalysis.Rmd
+#  Code chunk rainfall_sum_Sstart
+# This file runs a linear model on grain yield and inseason rainfall
+# this is to find the best timeframe that contributes to grain yeild
+#
+# This file contains a start date of:
+#     between 20 days after planting and 40 days after planting
+# An end date between 
+#     80 days after planting and 110 days after planting.
+# 
+
+start1 <- 20
+start2 <- 40
+end1 <- 80
+end2 <- 110
+
+
+library(tidyverse)
+library(theme.usq)
+library(bomrang)
+library(parallel)
+source("R/import_data.R")
+
+
+# ___________
+# Import data
+PM_MB_means <- import_data()
+# see Yield vs in-season rain section on the influence of rain and irrigation on grain yield
+PM_MB_means$irrigation <- NA
+PM_MB_means[PM_MB_means$location == "Hermitage", "irrigation"] <- TRUE
+PM_MB_means[PM_MB_means$location != "Hermitage", "irrigation"] <- FALSE
+
+
+#_________
+# Prep data
+# Import the information for each experimental site
+experiment_sites <- read.csv("data/Mungbean_experiment_sites.csv", stringsAsFactors = FALSE)
+
+
+rain_dat <- PM_MB_means[!is.na(PM_MB_means$planting_date),] # Which locations don't have NA for planting date
+unique(as.character(rain_dat$location)) # locations with recorded planting date
+
+# Create data set for which we will input the sum in-crop rainfall
+rain_dat_sum <- rain_dat %>%
+   group_by(trial_ref) %>%
+   summarise(location = unique(location),
+             planting_date = unique(as.character(planting_date))[1],
+             grain_yield = mean(grain_yield.t.ha., na.rm = TRUE))
+
+rain_dat_sum <- rain_dat_sum[order(rain_dat_sum$location),] # order them to make adding the lat long easier
+
+# add columns for lat and lon
+rain_dat_sum$lat <- NA
+rain_dat_sum$lon <- NA
+
+
+# Input lat and lon to dataframe for each experimental location
+rain_dat_sum[rain_dat_sum$location == "Bongeen_1", c("lat","lon")] <- 
+   experiment_sites[experiment_sites$location == "Bongeen 1 & 2",c("lat","lon")]
+
[…]

### 2019-10-31 05_MetaAnalysis.Rmd
Editing file names

@@
 
-lm_rain <- read.csv("data/lmInSeasonRainfall.csv",stringsAsFactors = FALSE)
+# lm_rain <- read.csv("data/lmInSeasonRainfall_-10.20_50.110.csv",stringsAsFactors = FALSE)
+# lm_rain <- read.csv("data/lmInSeasonRainfall_10.30_60.95.csv",stringsAsFactors = FALSE)
+# lm_rain <- read.csv("data/lmInSeasonRainfall_20.40_80.110.csv",stringsAsFactors = FALSE)
+# lm_rain <- read.csv("data/lmInSeasonRainfall_-10.30_50.80.csv",stringsAsFactors = FALSE)
 
@@
 
-plot(log(P_value) ~ days_from_plant, data = lm_data)
-abline(v = lm_data[lm_data$P_value == min(lm_data$P_value),"days_from_plant"], col = "grey")
-text(x = lm_data[lm_data$P_value == min(lm_data$P_value),"days_from_plant"], 
-     y = log(max(lm_data$P_value))/0.95, 
-     labels = paste("pvalue =",round(min(lm_data$P_value),2)),
-     pos = 4)
-plot(r_squared ~ days_from_plant, data = lm_data)
-abline(v = lm_data[lm_data$r_squared == max(lm_data$r_squared),"days_from_plant"], col = "grey")
-text(x = lm_data[lm_data$r_squared == max(lm_data$r_squared),"days_from_plant"], 
-     y = max(lm_data$r_squared * 0.75), 
-     labels = paste("Rsquared =",round(max(lm_data$r_squared),4)),
-     pos = 2)
-
-plot(estimate ~ days_from_plant, data = lm_data)
-abline(v = 14, h = lm_data[lm_data$r_squared == max(lm_data$r_squared),"estimate"], col = "grey")
 ```

### 2019-10-31 R/Rainfall_x_cropYield_s-10.30_e40.100.R
LM scripts and subsequent data

@@ -10,10 +10,10 @@
 #     60 days after planting and 95 days after planting.
 # 
 
-start1 <- 10
+start1 <- -10
 start2 <- 30
-end1 <- 60
-end2 <- 95
+end1 <- 50
+end2 <- 100
 
 
 library(tidyverse)
@@ -163,7 +163,7 @@ rain_dat_sum$rainfall_sum <- NA
          lm_rain$lm_adj_rsquared[i] <- testlist1[[i]][[3]]
       }
       
-      write.csv(lm_rain, file = "data/lmInSeasonRainfall_10.30_60.95.csv", row.names = FALSE)
+      write.csv(lm_rain, file = "data/lmInSeasonRainfall_-10.30_50.100.csv", row.names = FALSE)
       
       message("Script completed running")
       

### 2019-10-31 R/Cleaning historical data.R
Changed code with new file location and to consolidate the 2 no spray controls in Hermitage 2011

@@ -37,7 +37,7 @@ write.csv(
 
 Herm_11 <-
    read_xls(
-      "C:/Users/U8011054/OneDrive - USQ//Cloudstor/Mungbean/Past trials/2011/2011 PMmung Herm/pmhermratings2011.xls",
+      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2011/2011 PMmung Herm/pmhermratings2011.xls",
       sheet = "Analyses factor"
    )
 
@@ -50,15 +50,19 @@ Herm_11 <-
 head(Herm_11)
 
 Herm_11_m <- Herm_11 %>%
-   group_by(`Cultivar!`, `Tr`, `fungicide`, `spray_n`) %>%
+   group_by(`Cultivar!`, `fungicide`, `spray_n`) %>%
    summarise_all(list( ~ mean(., na.rm = TRUE),  ~ sd(., na.rm = TRUE)))
 
-Herm_11_m <- data.table(Herm_11_m)[, c(1:4, 8:12, 16:20)]
+head(data.frame(Herm_11_m))
+
+Herm_11_m <- data.frame(Herm_11_m[, c("Cultivar!","fungicide", "spray_n",
+                                      "P.M. 11  w.a.p._mean","P.M. 11  w.a.p._sd",
+                                      "Yld Kg/ha_mean", "Yld Kg/ha_sd")])
 colnames(Herm_11_m)
 
 write.csv(
    as.data.frame(Herm_11_m),
-   "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/2011 PMmung Herm means.csv"
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2011/2011 PMmung Herm/2011 PMmung Herm means.csv"
 )
 
 

### 2019-10-31 05_MetaAnalysis.Rmd
log the pvalue for plotting

@@
 
-ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_pval))+
-   geom_raster(aes(fill = lm_pval), interpolate = TRUE)+
+ggplot(lm_rain, aes(x = start_day, y = end_day, z = log(lm_pval)))+
+   geom_raster(aes(fill = log(lm_pval)), interpolate = TRUE)+
    geom_contour(bins = 15, colour = "white")+

### 2019-10-31 04_Prep_data.Rmd
Edits reviewed and accepted
Correct data source to OneDrive link

@@
 # Place holder
+
+Warning this markdown file needs corrections to variable names.
+Column headers for PM_MB_means were changed and the column names need to be corrected below accordingly
 
@@
 library(dplyr)
-library(openxlsx)
-library(kableExtra)
-library(ggplot2)
-library(leaflet)
-#source("./getPPD2.R")
-
+library(readr)
 ```
@@
 ```{r Calculate_yield-gains}
-PM_MB_means <-
-   read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv",
-            stringsAsFactors = FALSE)
+source("R/import_data.R")
+PM_MB_means <- import_data()
+
 PM_MB_means$grain_yield.t.ha. <-

### 2019-10-31 R/Rainfall_x_cropYield_s-10.09_e30.65.R
Finaling the yield x rainfall analysis

@@ -10,10 +10,10 @@
 #     60 days after planting and 95 days after planting.
 # 
 
-start1 <- 10
-start2 <- 30
-end1 <- 60
-end2 <- 95
+start1 <- -10
+start2 <- 9
+end1 <- 30
+end2 <- 64
 
 
 library(tidyverse)
@@ -163,7 +163,7 @@ rain_dat_sum$rainfall_sum <- NA
          lm_rain$lm_adj_rsquared[i] <- testlist1[[i]][[3]]
       }
       
-      write.csv(lm_rain, file = "data/lmInSeasonRainfall_10.30_60.95.csv", row.names = FALSE)
+      write.csv(lm_rain, file = "data/lmInSeasonRainfall_-10.09_30.64.csv", row.names = FALSE)
       
       message("Script completed running")
       

### 2019-10-31 R/Rainfall_x_cropYield_s-10.09_e65.100.R

@@ -5,15 +5,15 @@
 # this is to find the best timeframe that contributes to grain yeild
 #
 # This file contains a start date of:
-#     between 20 days after planting and 40 days after planting
+#     between 10 days after planting and 30 days after planting
 # An end date between 
-#     50 days after planting and 80 days after planting.
+#     60 days after planting and 95 days after planting.
 # 
 
-start1 <- 20
-start2 <- 40
-end1 <- 50
-end2 <- 80
+start1 <- -10
+start2 <- 9
+end1 <- 65
+end2 <- 100
 
 
 library(tidyverse)
@@ -163,7 +163,7 @@ rain_dat_sum$rainfall_sum <- NA
          lm_rain$lm_adj_rsquared[i] <- testlist1[[i]][[3]]
       }
       
-      write.csv(lm_rain, file = "data/lmInSeasonRainfall_20.40_50.80.csv", row.names = FALSE)
+      write.csv(lm_rain, file = "data/lmInSeasonRainfall_-10.09_65.100.csv", row.names = FALSE)
       
       message("Script completed running")
       

### 2019-10-31 R/Rainfall_x_cropYield_s-10.20_e50.110.R

@@ -1,164 +1,0 @@
-# In crop rainfall lm loop to predict grainyield
-# See 05_MetaAnalysis.Rmd
-#  Code chunk rainfall_sum_Sstart
-# This file runs a linear model on grain yield and inseason rainfall
-# this is to find the best timeframe that contributes to grain yeild
-#
-# This file contains a start date of:
-#     between 10 days before planting and 20 days after planting
-# An end date between 
-#     50 days after planting and 110 days after planting.
-# 
-
-
-library(tidyverse)
-library(theme.usq)
-library(bomrang)
-library(parallel)
-source("R/import_data.R")
-
-
-# ___________
-# Import data
-PM_MB_means <- import_data()
-# see Yield vs in-season rain section on the influence of rain and irrigation on grain yield
-PM_MB_means$irrigation <- NA
-PM_MB_means[PM_MB_means$location == "Hermitage", "irrigation"] <- TRUE
-PM_MB_means[PM_MB_means$location != "Hermitage", "irrigation"] <- FALSE
-
-
-#_________
-# Prep data
-# Import the information for each experimental site
-experiment_sites <- read.csv("data/Mungbean_experiment_sites.csv", stringsAsFactors = FALSE)
-
-
-rain_dat <- PM_MB_means[!is.na(PM_MB_means$planting_date),] # Which locations don't have NA for planting date
-unique(as.character(rain_dat$location)) # locations with recorded planting date
-
-# Create data set for which we will input the sum in-crop rainfall
-rain_dat_sum <- rain_dat %>%
-   group_by(trial_ref) %>%
-   summarise(location = unique(location),
-             planting_date = unique(as.character(planting_date))[1],
-             grain_yield = mean(grain_yield.t.ha., na.rm = TRUE))
-
-rain_dat_sum <- rain_dat_sum[order(rain_dat_sum$location),] # order them to make adding the lat long easier
-
-# add columns for lat and lon
-rain_dat_sum$lat <- NA
-rain_dat_sum$lon <- NA
-
-
-# Input lat and lon to dataframe for each experimental location
-rain_dat_sum[rain_dat_sum$location == "Bongeen_1", c("lat","lon")] <- 
-   experiment_sites[experiment_sites$location == "Bongeen 1 & 2",c("lat","lon")]
-
-rain_dat_sum[rain_dat_sum$location == "Hermitage", c("lat","lon")] <- 
[…]

### 2019-10-31 R/Rainfall_x_cropYield_s10.30_e30.65.R

@@ -5,15 +5,15 @@
 # this is to find the best timeframe that contributes to grain yeild
 #
 # This file contains a start date of:
-#     between 10 days after planting and 30 days after planting
+#     between 20 days after planting and 40 days after planting
 # An end date between 
-#     60 days after planting and 95 days after planting.
+#     50 days after planting and 80 days after planting.
 # 
 
-start1 <- -10
+start1 <- 10
 start2 <- 30
-end1 <- 50
-end2 <- 100
+end1 <- 30
+end2 <- 64
 
 
 library(tidyverse)
@@ -163,7 +163,7 @@ rain_dat_sum$rainfall_sum <- NA
          lm_rain$lm_adj_rsquared[i] <- testlist1[[i]][[3]]
       }
       
-      write.csv(lm_rain, file = "data/lmInSeasonRainfall_-10.30_50.100.csv", row.names = FALSE)
+      write.csv(lm_rain, file = "data/lmInSeasonRainfall_10.30_30.64.csv", row.names = FALSE)
       
       message("Script completed running")
       

### 2019-10-31 R/Rainfall_x_cropYield_s10.30_e65.10.R

@@ -10,10 +10,10 @@
 #     80 days after planting and 110 days after planting.
 # 
 
-start1 <- 20
-start2 <- 40
-end1 <- 80
-end2 <- 110
+start1 <- 10
+start2 <- 30
+end1 <- 65
+end2 <- 100
 
 
 library(tidyverse)
@@ -163,7 +163,7 @@ rain_dat_sum$rainfall_sum <- NA
          lm_rain$lm_adj_rsquared[i] <- testlist1[[i]][[3]]
       }
       
-      write.csv(lm_rain, file = "data/lmInSeasonRainfall_20.40_80.110.csv", row.names = FALSE)
+      write.csv(lm_rain, file = "data/lmInSeasonRainfall_10.30_65.100.csv", row.names = FALSE)
       
       message("Script completed running")
       

### 2019-10-31 05_MetaAnalysis.Rmd
Moving the import_data code to be above where it is used

@@
 library(bomrang)
-source("R/import_data.R")
+
 ```
@@
 ```{r data_import, message=FALSE, echo=FALSE}
+source("R/import_data.R")
 PM_MB_means <- import_data()
@@
 ```{r rainfall_sum_Sstart}
+# The four data files were created from four scripts run as four jobs in Rstudio
+# when the four jobs are finished they can be imported and combined into one data.frame
+# source(Rainfall_x_cropYield_s-10.09_e30.65.R)
+# source(Rainfall_x_cropYield_s-10.09_e65.100.R)
+# source(Rainfall_x_cropYield_s10.30_e30.65.R)
+# source(Rainfall_x_cropYield_s10.30_e65.10.R)
 
-source("R/Rainfall_x_cropYield.R")
+lm_rain1 <- read.csv("data/lmInSeasonRainfall_-10.09_30.64.csv",stringsAsFactors = FALSE)
+lm_rain2 <- read.csv("data/lmInSeasonRainfall_-10.09_65.100.csv",stringsAsFactors = FALSE)
+lm_rain3 <- read.csv("data/lmInSeasonRainfall_10.30_30.64.csv",stringsAsFactors = FALSE)
+lm_rain4 <- read.csv("data/lmInSeasonRainfall_10.30_65.100.csv",stringsAsFactors = FALSE)
 
-# lm_rain <- read.csv("data/lmInSeasonRainfall_-10.20_50.110.csv",stringsAsFactors = FALSE)
-# lm_rain <- read.csv("data/lmInSeasonRainfall_10.30_60.95.csv",stringsAsFactors = FALSE)
-# lm_rain <- read.csv("data/lmInSeasonRainfall_20.40_80.110.csv",stringsAsFactors = FALSE)
-# lm_rain <- read.csv("data/lmInSeasonRainfall_-10.30_50.80.csv",stringsAsFactors = FALSE)
+lm_rain <- rbind(lm_rain1,lm_rain2,lm_rain3,lm_rain4)
 

### 2019-11-01 04_Prep_data.Rmd
column names and variable formating updated. Output data file changed to `data/1902 PM_MB_means&Ygains.csv`

@@
 
-```{r}
+```{r load_libraries}
 library(dplyr)
@@
 
-```{r Calculate_yield-gains}
+```{r import_data}
 source("R/import_data.R")
 PM_MB_means <- import_data()
+```
 
+Data from `r length(PM_MB_means$trial_ref)` trials were collected and the means of each treatment calculated (`R/Cleaning historical data.R`).
+These data were combined into one file `1902 powdery mildew-Mungbean - Collated means.csv`.
+
+```{r Calculate_yield-gains}
 PM_MB_means$grain_yield.t.ha. <-
@@
 
-for (i in levels(as.factor(PM_MB_means$Trial_ref))) {
-   dat1 <- PM_MB_means[PM_MB_means$Trial_ref == i, ]
+for (i in unique(PM_MB_means$trial_ref)) {
+   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
 
@@
          paste(
-            unique(dat1$Trial_ref),
+            unique(dat1$trial_ref),
             "at",
-            unique(dat1$Location),
+            unique(dat1$location),
             "in year",
-            unique(dat1$Year),
+            unique(dat1$year),
             "has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n"
@@
       controlY <-
-         mean(dat2[dat2$Fungicide == "control", "grain_yield.t.ha."])
+         mean(dat2[dat2$fungicide == "control", "grain_yield.t.ha."])
 
@@
 
-      dat2[dat2$Fungicide == "control", c("yield_gain", "prop_YG")] <-
+      dat2[dat2$fungicide == "control", c("yield_gain", "prop_YG")] <-
          NA
@@
    }
-   PM_MB_means[PM_MB_means$Trial_ref == i, ] <- dat1
+   PM_MB_means[PM_MB_means$trial_ref == i, ] <- dat1
 }
 
-# caluculate yield gain and prop_yield gain for experiments with no row spacing data
-dat1 <- PM_MB_means[PM_MB_means$Trial_ref == "AM1303", ]
-controlY <-
-   mean(dat1[dat1$Fungicide == "control", "grain_yield.t.ha."])
-dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
-dat1$prop_YG <- dat1$yield_gain / controlY
-dat1[dat1$Fungicide == "control", c("yield_gain", "prop_YG")] <- NA
-PM_MB_means[PM_MB_means$Trial_ref == "AM1303", ] <- dat1
+# ____________________________________________
+# calculate yield gain and prop_yield gain for experiments with no row spacing data
+
+# dat1 <- PM_MB_means[PM_MB_means$trial_ref == "AM1303", ]
+# 
+# controlY <-
+#    mean(dat1[dat1$fungicide == "control", "grain_yield.t.ha."])
+# 
+# dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
+# dat1$prop_YG <- dat1$yield_gain / controlY
+# dat1[dat1$fungicide == "control", c("yield_gain", "prop_YG")] <- NA
+# PM_MB_means[PM_MB_means$trial_ref == "AM1303", ] <- dat1
 
 write.csv(PM_MB_means,
-          "data/1902 powdery mildew-Mungbean - Collated means.csv")
+          "data/1902 PM_MB_means&Ygains.csv")
 ```

### 2019-11-01 02_Weather.Rmd
Changed data import corrected some code from changed data files

@@
 
+```{r import_libraries_&_data}
+source("R/import_data.R")
+PM.dat <- import_data()  # importing means yield and disease severity for each treatment within each powdery mildew trial on mungbean
+source("R/year2day.r")
+
+```
+
 ```{r weather1, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
@@
 # Import dataset
-PM.dat <-
-   read_csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
-PM.dat <- PM.dat %>%
-   mutate(trial_ref = as.factor(trial_ref)) %>%
-   mutate(location = as.factor(location)) %>%
-   mutate(host_genotype = as.factor(host_genotype)) %>%
-   mutate(fungicide_ai = as.factor(fungicide_ai)) %>%
-   mutate(trade_name = as.factor(trade_name)) %>%
-   mutate(year = as.factor(year)) %>%
-   mutate(replicates = as.factor(replicates)) %>%
-   mutate(planting_date = as.Date(planting_date, format = "%d/%m/%Y")) %>%
-   mutate(emergence_date = as.Date(emergence_date, format = "%d/%m/%Y")) %>%
-   mutate(flowering_date = as.Date(flowering_date, format = "%d/%m/%Y")) %>%
-   mutate(pod_final_date = as.Date(pod_final_date, format = "%d/%m/%Y")) %>%
-   mutate(mid_late_pod_final = as.Date(mid_late_pod_final, format = "%d/%m/%Y")) %>%
-   mutate(first_sign_disease = as.Date(first_sign_disease, format = "%d/%m/%Y")) %>%
-   mutate(fungicide_application_1 = as.Date(fungicide_application_1, format = "%d/%m/%Y")) %>%
-   mutate(fungicide_application_2 = as.Date(fungicide_application_2, format = "%d/%m/%Y")) %>%
-   mutate(fungicide_application_3 = as.Date(fungicide_application_3, format = "%d/%m/%Y")) %>%
-   mutate(fungicide_application_4 = as.Date(fungicide_application_4, format = "%d/%m/%Y")) %>%
-   mutate(fungicide_application_5 = as.Date(fungicide_application_5, format = "%d/%m/%Y")) %>%
-   mutate(fungicide_application_6 = as.Date(fungicide_application_6, format = "%d/%m/%Y")) %>%
-   mutate(fungicide_application_7 = as.Date(fungicide_application_7, format = "%d/%m/%Y")) %>%
-   mutate(harvest_date = as.Date(harvest_date, format = "%d/%m/%Y")) %>%
-   mutate(final_assessment = as.Date(final_assessment, format = "%d/%m/%Y"))
 
@@
 cols1 <- gg_color_hue(4)
-
-# silo.API <- "YeTZsWlFNC8hvbQLllv8KtbRQWsje4qxic5QQ7mL"
-# # retrieve the maximum temperatures from the six yearsd between 2011 and 2017 at weather station 041525 (Hermitage)
-# silo_war_Tmax <- getPPD2(station_id = 041525,start = 20110101,end = 20160630, silo.apikey = silo.API, variables = "max_temp,min_temp,daily_rain")
-# # retrieve the maximum temperatures from the six yearsd between 2011 and 2017 by location
-# silo_king_Tmax <- getPPD2(lat = -26.58, long = 151.83, start = 20110101, end = 20160630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
-# silo_gatton_Tmax <- getPPD2(lat = -27.56, long = 152.32, start = 20110101, end = 20170630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
-# silo_emerald_Tmax <- getPPD2(lat = -23.54, long = 148.19, start = 20110101, end = 20170630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
 
@@
       Year = substr(king_Tm_aver$date, start = 1, stop = 4),
-      Day = ymd(king_Tm_aver$date)
+      Day = year2day(king_Tm_aver$date)
    )
@@
    filter(location == "Kingaroy") %>%
-   mutate(day = ymd(first_sign))
-str(king_Tm_aver)
-str(King_FS)
+   mutate(day = year2day(first_sign))
+
 ggplot(subset(king_Tm_aver, year == levels(factor(King_FS$year))),

### 2019-11-01 03_Preliminary_analysis.Rmd
small query
Edits reviewed and accepted
Corrected code based on changed data

@@
 colnames(PM_MB_means)
+class(PM_MB_means$year)
 ```
@@
 PM_MB_means %>%
-   filter(Year >= 2017) %>%
-   filter(Fungicide == "control") %>%
-   ggplot(aes(y = PM_final_severity, x = row_spacing, colour = Location)) +
+   filter(year == 2017 |
+             year == 2018) %>%
+   filter(fungicide == "control") %>%
+   ggplot(aes(y = PM_final_severity, x = row_spacing, colour = location)) +
    geom_point() +
@@
 PM_MB_means %>%
-   filter(Year >= 2017) %>%
+   filter(year == 2017|
+             year == 2018) %>%
    #   filter(Fungicide == "control") %>%
@@
       x = row_spacing,
-      colour = Location
+      colour = location
    )) +
@@
 PM_MB_means %>%
-   group_by(Fungicide) %>%
+   group_by(fungicide) %>%
    summarise(
@@
 
+unique(PM_MB_means$fungicide)
 # plot table as a box plot
@@
    filter(
-      Fungicide == c(
-         "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin" ,
-         "Azoxystrobin",
-         "Tebeconazole",
-         "Propiconoazole"
+      fungicide == c(
+         "200 g/L tebuconazole + 120 g/L azoxystrobin" ,
+         "200 g/L azoxystrobin + 80 g/L cyproconazole",
+         "tebuconazole",
+         "propiconazole"
       )
    ) %>%
-   ggplot(aes(y = prop_YG, x = Fungicide)) +
+   ggplot(aes(y = prop_YG, x = fungicide)) +
    geom_boxplot() +
@@
 PM_MB_means %>%
-   group_by(Fungicide, total_Fungicide) %>%
+   group_by(fungicide, total_fungicide) %>%
    summarise(
@@
 PM_MB_means %>%
-   filter(total_Fungicide == 1 | total_Fungicide == 2) %>%
+   filter(total_fungicide == 1 | total_fungicide == 2) %>%
    filter(
-      Fungicide != "Pyrazophos" &
-         Fungicide != "control" &
-         Fungicide != "Benomyl" &
-         Fungicide != "Acibenzolar-S-Methyl" &
-         Fungicide != "200g/L Azoxystrobin + 80 g/L Cyproconazole + adj"
+      fungicide != "pyrazophos" &
+         fungicide != "control" &
+         fungicide != "benomyl" &
+         fungicide != "Acibenzolar-S-methyl" &
+         fungicide != "200g/L azoxystrobin + 80 g/L cyproconazole + adj"
    ) %>%
-   ggplot(aes(y = prop_YG, x = Fungicide)) +
-   facet_grid(rows = vars(total_Fungicide)) +
-   geom_boxplot(aes(fill = Fungicide, alpha = 0.5)) +
+   ggplot(aes(y = prop_YG, x = fungicide)) +
+   facet_grid(rows = vars(total_fungicide)) +
+   geom_boxplot(aes(fill = fungicide, alpha = 0.5)) +
    geom_hline(aes(yintercept = 0), size = 0.5) +
@@
    theme(legend.position = "none") +
-   coord_cartesian() +
-   scale_x_discrete(
-      limits = c(
-         "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin",
-         "Propiconazole",
-         "Tebeconazole",
-         "200g/L Azoxystrobin + 80 g/L Cyproconazole",
-         "Sulphur",
-         "Carbendazim",
-         "Pyraclostrobin",
-         "Azoxystrobin"
-      )
-   ) +
+   # coord_cartesian() +
+   # scale_x_discrete(
+   #    limits = c(
+   #       "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin",
+   #       "Propiconazole",
+   #       "Tebeconazole",
+   #       "200g/L Azoxystrobin + 80 g/L Cyproconazole",
+   #       "Sulphur",
+   #       "Carbendazim",
+   #       "Pyraclostrobin",
+   #       "Azoxystrobin"
+   #    )
+   # ) +
    #  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
@@
 #scale_x_continuous(limits = c(-0.3,0.6))
-
-levels(PM_MB_means$Fungicide)
 

### 2019-11-01 05_MetaAnalysis.Rmd
spell check

@@
    ylab("N Trials") +
-   ggtitle(label = "Trial row spacings using tebuconazole") +
+   ggtitle(label = "Trial row spacing using tebuconazole") +
    geom_col(aes(fill = fungicide_ai),
@@
 Were there any statistical difference between all row spacing or only some?
-Can we pool certain row spacings that have no significant difference?
+Can we pool certain row spacing that have no significant difference?
 From the preliminary analysis, the graphs seem to imply that if there is a lower overall yield there is no effect of row spacing on yield.
@@
 
-The approximate period when in-crop rainfall impacts the most on the mean harvest is bettween 11 - 88 days after planting.
+The approximate period when in-crop rainfall impacts the most on the mean harvest is between 11 - 88 days after planting.
 
@@
 
-### Converting least-squares tp sample variance
+### Converting least-squares to sample variance
 

### 2019-11-01 03_Preliminary_analysis.Rmd
Moving preliminary analyses and plotting to chapter 3

@@
 
-### Yield saved from fungicide applications
+## Explore and visualise Data
 
-The data plotted below are from the past field trials (2011 - 2017) described in the aforementioned table.
-All data are a list of mean values from each treatment applied in each experiment.
-Various factors have been studied in the previous experiments which may influence the following results. The following variables were disregarded in the plots below.
+```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
+# Import data
+PM_MB_means <- import_data()
+
+```
+
+Various factors have been studied in the previous experiments which may influence the following results.
+However unless stated the following plots and analyses were made disregarding effects from other factors not mentioned.
 
@@
 
-```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
-# Import data
-PM_MB_means <- import_data()
-colnames(PM_MB_means)
-class(PM_MB_means$year)
+1. Type of Fungicide sprayed
+2. In-crop rainfall
+3. mungbean cultivar
+4. Fungicide dose (we don't expect this to influence as it was only changes slightly)
+5. Mean daily temperature in the weeks following spray application
+6. Row spacing
+7. Two pathogen species cause PM (new discovery)
+8. irrigated vs non-irrigated trials
+9. Number of fungicide sprays (edited)
+
+### Fungicides
+
+The data plotted below are from the past field trials (2011 - 2017) described in the aforementioned table.
+All data are a list of mean values from each treatment applied in each experiment.
+
+When investigating previous studies into powdery mildew fungicide efficacy on mungbean `r length(unique(PM_MB_means$trial_ref))` trials were found.
+However, only eleven tebuconazole were used for the following meta-analysis, followed by the next most common fungicide, propiconazole. Sulphur was disregarded due to its inconsistency in efficacy.
+
+```{r Fungicides}
+PM_MB_means %>%
+   group_by(fungicide_ai, trial_ref) %>%
+   summarise() %>%
+   count(sort = TRUE) %>%
+   rename(Trials = n) %>%
+   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
+   xlab("Fungicide active ingredient") +
+   ylab("N Trials") +
+   geom_col() +
+   scale_fill_usq() +
+   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
+   scale_colour_usq() +
+   theme_usq() +
+   coord_flip()
 ```
+
+Tebuconazole and propiconazole might be able to be pooled as a triazole fungicide treatment. 
+Amistar Xtra is a combination of azoxystrobin and cyproconazole.
+Custodia is a combination of tebuconazole and azoxystrobin.
+Amistar Xtra and Custodia might be able to be pooled given they both contain strobilurin and triazole, however, they contain differing dose ratios (inverted).
+
+Perhaps best way forward is to do an analysis of only the triazoles. Then do another including azoxystrobin as a comparison.
+
+Preliminary analysis of fungicides show there is a difference the effect of fungicide in proportion of yield saved.
+
+#### Fungicide Doses
+
+All trials that used tebuconazole used approximately the same dose.
+Dose of the active ingredient ranged from 62.35&nbsp;g per hectare to 60&nbsp;g per hectare.
+
+```{r tebu_dose}
+PM_MB_means %>%
+   filter(fungicide_ai == "tebuconazole") %>%
+   select(trial_ref,
+          year,
+          location,
+          first_sign_disease,
+          dose_ai.ha,
+          total_fungicide) %>%
+   ggplot(aes(x = as.factor(dose_ai.ha))) +
+   xlab("Dose (g ai/ha)") +
+   ggtitle(label = "Total number of treatments for each respective tebuconazole dose") +
+   geom_bar() +
+   scale_fill_usq() +
+   scale_colour_usq() +
+   theme_usq()
+```
+
+### Row spacing
+
+Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease.
+The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows in most cases increased yield significantly.
+This finding has also been shown by Kerry McKenzie's work as well.
+Eight trials used a row spacing of 0.75&nbsp;meters and tebuconazole as an active ingredient (AI).
+
+```{r row_spacing.m}
+PM_MB_means %>%
+   filter(fungicide_ai == "tebuconazole" | fungicide_ai == "propiconazole") %>%
+   group_by(fungicide_ai, row_spacing, trial_ref) %>%
+   summarise() %>%
+   count() %>%
+   rename(Trials = n) %>%
+   ggplot(aes(x = as.factor(row_spacing), y = Trials)) +
+   xlab("Row Spacing (m)") +
+   ylab("N Trials") +
+   ggtitle(label = "Trial row spacing using tebuconazole") +
+   geom_col(aes(fill = fungicide_ai),
+            position = "dodge") +
+   scale_fill_usq(name = "Fungicide AI") +
+   theme_usq()
+
+PM_MB_means %>%
+   filter(fungicide_ai == "tebuconazole",
+         row_spacing == 0.75) %>% 
+   glimpse()
+```
+
+Were there any statistical difference between all row spacing or only some?
+Can we pool certain row spacing that have no significant difference?
+From the preliminary analysis, the graphs seem to imply that if there is a lower overall yield there is no effect of row spacing on yield.
+However, if the average yield is more than approximately 0.6 - 1 t/ha then smaller row spacing has the potential to provide greater yield.
 
@@
    theme_usq()
+
+```
+
+### Host genotypes
+
+Host genotype may need to be analysed to determine the effect.
+
+```{r Host_genotype}
+PM_MB_means %>%
+   filter(fungicide_ai == "tebuconazole",
+         row_spacing == 0.75) %>%
+   group_by(host_genotype, trial_ref) %>%
+   summarise() %>%
+   count() %>%
+   rename(Treatments = n) %>%
+   ggplot(aes(x = host_genotype, y = Treatments)) +
+   xlab("Cultivar") +
+   ylab("N Trials") +
+   ggtitle(label = "Cultivars used in tebuconazole trials with 0.75 m row spacing") +
+   geom_col() +
+   scale_fill_usq() +
+   scale_colour_usq() +
+   theme_usq()
+```
+
+In general the mungbean varieties have the following resistance to powdery mildew.
+
+   - Berken: Highly susceptible
+
+   - Crystal: Susceptible
+
+   - Jade: Moderately susceptible
+
+#### Genotype yield variability
+
+Host genotype seems to contribute to the variation in yield. Berken shows higher yields compared to crystal and jade.
+```{r yield_vol}
+source("R/yield_volatility.r") #function to investigate the volatility in yields
+
+yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
+yield_volatility(genotype_by_trial = FALSE, control_only = TRUE)
+yield_volatility(genotype_by_trial = FALSE, control_only = FALSE, location = "Hermitage")
+
+yield_volatility("Crystal",control_only = TRUE)
+yield_volatility("Crystal",control_only = FALSE)
+
+yield_volatility("Jade",control_only = TRUE)
+yield_volatility("Jade",control_only = FALSE, location = "Hermitage")
+
+```
+
+### Yield vs in-season rain
+
+In crop rain could be a significant factor which contributes to the end of season grain yield.
+To investigate any relationship I will loop a linear model over time periods from 20 days prior to planting, to 100 days after planting.
+
+#### Best start day for in-crop rainfall
+
+Loop over the dates at the start of the season (to 90 days after planting) to find which date fits the best linear model for grain weight and in-crop rainfall.
+The code for this process was moved to be contained within it's own script and can be run as a job as it can take a long time.
+The output of the script is saved with the prefix `lmInSeasonRainfall` followed by the time windows the model is run.
+For example `lmInSeasonRainfall_20.40_50.80.csv` holds the model results for start days between 20 and 40 days after planting to end window dates between 50 and 80 days after planting.
+
+```{r rainfall_sum_Sstart}
+# The four data files were created from four scripts run as four jobs in Rstudio
+# when the four jobs are finished they can be imported and combined into one data.frame
+# source(Rainfall_x_cropYield_s-10.09_e30.65.R)
+# source(Rainfall_x_cropYield_s-10.09_e65.100.R)
+# source(Rainfall_x_cropYield_s10.30_e30.65.R)
+# source(Rainfall_x_cropYield_s10.30_e65.10.R)
+
+lm_rain1 <- read.csv("data/lmInSeasonRainfall_-10.09_30.64.csv",stringsAsFactors = FALSE)
+lm_rain2 <- read.csv("data/lmInSeasonRainfall_-10.09_65.100.csv",stringsAsFactors = FALSE)
+lm_rain3 <- read.csv("data/lmInSeasonRainfall_10.30_30.64.csv",stringsAsFactors = FALSE)
+lm_rain4 <- read.csv("data/lmInSeasonRainfall_10.30_65.100.csv",stringsAsFactors = FALSE)
+
+lm_rain <- rbind(lm_rain1,lm_rain2,lm_rain3,lm_rain4)
+
+lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)),]
+lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),]
+lm_rain[which(lm_rain$lm_adj_rsquared == max(lm_rain$lm_adj_rsquared)),]
+
+ggplot(lm_rain, aes(x = start_day, y = end_day, z = log(lm_pval)))+
+   geom_raster(aes(fill = log(lm_pval)), interpolate = TRUE)+
+   geom_contour(bins = 15, colour = "white")+
+   geom_abline(intercept = 0, slope = 1, colour = "red")+
+   geom_point(data = lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)),], aes(x = start_day, y = end_day), colour =" red")+
+   scale_fill_distiller(palette ="RdBu", direction = -1)
+
+ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_rsquared))+
+   geom_raster(aes(fill = lm_rsquared), interpolate = TRUE)+
+   geom_contour(bins = 15, colour = "white")+
+   geom_abline(intercept = 0, slope = 1, colour = "red")+
+   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),], aes(x = start_day, y = end_day), colour =" red")+
+   scale_fill_distiller(palette ="RdBu")
+
+ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_adj_rsquared))+
+   geom_raster(aes(fill = lm_adj_rsquared), interpolate = TRUE)+
+   geom_contour(bins = 15, colour = "white")+
+   geom_abline(intercept = 0, slope = 1, colour = "red")+
+   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),], aes(x = start_day, y = end_day), colour =" red")+
+   scale_fill_distiller(palette ="RdBu")
+
+```
+
+The approximate period when in-crop rainfall impacts the most on the mean harvest is between 11 - 88 days after planting.
+
+### Season range and first incidence
+
+```{r first_incidence}
+# Here I want to build a plot of horizontal lines indicating the season length and
+# place a dot on the line to indicating the day of the year first sign was observed for that trial
+
+season_dates <- PM_MB_means %>%
+   group_by(trial_ref)%>%
+   summarise(Planting_date = unique(planting_date),
+             Harvest_date = unique(harvest_date),
+             First_sign_PM = unique(first_sign_disease),
+             season_length = as.integer(as.Date(unique(harvest_date)) - as.Date(unique(planting_date)))
+             )
+
+# function to extract date from the year
+# format should be Universal time format
+source("R/year2day.r")
+
+season_dates$Planting_day <- unlist(lapply(season_dates$Planting_date,year2day))
+season_dates$Disease_day <- unlist(lapply(season_dates$First_sign_PM,year2day))
+season_dates$Harvest_day <- season_dates$Planting_day + season_dates$season_length
+
+season_dates[1,"Planting_day"] <- year2day(as.Date("2012-02-28")-7) # planted in december and emerged in February, Assuming due to lack of rain or recording error.
+Using 7 days prior to emergence day as planting day
+
+first_day_month <- c(0, 31, 59, 90, 120, 151, 181, 211, 243, 273)
+axis_labels_date <- c(format(Sys.Date() - year2day(Sys.Date()) + first_day_month[1], "%b-%d"),  # Jan
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[2], "%b-%d"), # Feb
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[3], "%b-%d"), # March
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[4], "%b-%d"), # April
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[5], "%b-%d"), # May
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[6], "%b-%d"), # June
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[7], "%b-%d"), # July
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[8], "%b-%d"), # August
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[9], "%b-%d"), # Sept
+                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[10], "%b-%d") # October
+                         )
+
+# reorder the factors so they will appear in chronilogical order
+# I used First sign because all trials have recorded this
+season_dates$trial_ref <- factor(season_dates$trial_ref, levels = levels(season_dates$trial_ref)[rev(order(season_dates$First_sign_PM))])
+
+season_dates %>%
+   ggplot()+
+   geom_pointrange(aes(x = trial_ref, y = Disease_day, ymin = Planting_day, ymax = Harvest_day))+
+   scale_y_continuous(
+      limits = c(0, max(season_dates$Planting_day + 
+                           season_dates$season_length, 
+                        na.rm = TRUE)),
+      labels = axis_labels_date,
+      breaks = first_day_month
+   )+
+   geom_point(aes(x = trial_ref, y = Disease_day))+
+   coord_flip()+
+   ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
 

### 2019-11-01 05_MetaAnalysis.Rmd
Moving preliminary analyses and plotting to chapter 3

@@
 PM_MB_means[PM_MB_means$location != "Hermitage", "irrigation"] <- FALSE
-
-```
-
-## Explore and visualise Data
-
-Visualise and inspect the number of factors represented in each trial.
-
-### Fungicides
-
-When investigating previous studies into powdery mildew fungicide efficacy on mungbean `r length(unique(PM_MB_means$trial_ref))` trials were found.
-However, only eleven tebuconazole were used for the following meta-analysis, followed by the next most common fungicide, propiconazole. Sulphur was disregarded due to its inconsistency in efficacy.
-
-```{r Fungicides}
-PM_MB_means %>%
-   group_by(fungicide_ai, trial_ref) %>%
-   summarise() %>%
-   count(sort = TRUE) %>%
-   rename(Trials = n) %>%
-   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
-   xlab("Fungicide active ingredient") +
-   ylab("N Trials") +
-   geom_col() +
-   scale_fill_usq() +
-   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
-   scale_colour_usq() +
-   theme_usq() +
-   coord_flip()
-```
-
-Tebuconazole and propiconazole might be able to be pooled as a triazole fungicide treatment. 
-Amistar Xtra is a combination of azoxystrobin and cyproconazole.
-Custodia is a combination of tebuconazole and azoxystrobin.
-Amistar Xtra and Custodia might be able to be pooled given they both contain strobilurin and triazole, however, they contain differing dose ratios (inverted).
-
-Perhaps best way forward is to do an analysis of only the triazoles. Then do another including azoxystrobin as a comparison.
-
-Preliminary analysis of fungicides show there is a difference the effect of fungicide in proportion of yield saved.
-
-### Fungicide Doses
-
-All trials that used tebuconazole used approximately the same dose.
-Dose of the active ingredient ranged from 62.35&nbsp;g per hectare to 60&nbsp;g per hectare.
-
-```{r tebu_dose}
-PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole") %>%
-   select(trial_ref,
-          year,
-          location,
-          first_sign_disease,
-          dose_ai.ha,
-          total_fungicide) %>%
-   ggplot(aes(x = as.factor(dose_ai.ha))) +
-   xlab("Dose (g ai/ha)") +
-   ggtitle(label = "Total number of treatments for each respective tebuconazole dose") +
-   geom_bar() +
-   scale_fill_usq() +
-   scale_colour_usq() +
-   theme_usq()
-```
-
-### Row spacing
-
-Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease.
-The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows in most cases increased yield significantly.
-This finding has also been shown by Kerry McKenzie's work as well.
-Eight trials used a row spacing of 0.75&nbsp;meters and tebuconazole as an active ingredient (AI).
-
-```{r row_spacing.m}
-PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole" | fungicide_ai == "propiconazole") %>%
-   group_by(fungicide_ai, row_spacing, trial_ref) %>%
-   summarise() %>%
-   count() %>%
-   rename(Trials = n) %>%
-   ggplot(aes(x = as.factor(row_spacing), y = Trials)) +
-   xlab("Row Spacing (m)") +
-   ylab("N Trials") +
-   ggtitle(label = "Trial row spacing using tebuconazole") +
-   geom_col(aes(fill = fungicide_ai),
-            position = "dodge") +
-   scale_fill_usq(name = "Fungicide AI") +
-   theme_usq()
-
-PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole",
-         row_spacing == 0.75) %>% 
-   glimpse()
-```
-
-Were there any statistical difference between all row spacing or only some?
-Can we pool certain row spacing that have no significant difference?
-From the preliminary analysis, the graphs seem to imply that if there is a lower overall yield there is no effect of row spacing on yield.
-However, if the average yield is more than approximately 0.6 - 1 t/ha then smaller row spacing has the potential to provide greater yield.
-
-### Host genotypes
-
-Host genotype may need to be analysed to determine the effect.
-
-```{r Host_genotype}
-PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole",
-         row_spacing == 0.75) %>%
-   group_by(host_genotype, trial_ref) %>%
-   summarise() %>%
-   count() %>%
-   rename(Treatments = n) %>%
-   ggplot(aes(x = host_genotype, y = Treatments)) +
-   xlab("Cultivar") +
-   ylab("N Trials") +
-   ggtitle(label = "Cultivars used in tebuconazole trials with 0.75 m row spacing") +
-   geom_col() +
-   scale_fill_usq() +
-   scale_colour_usq() +
-   theme_usq()
-```
-
-In general the mungbean varieties have the following resistance to powdery mildew.
-
-   - Berken: Highly susceptible
-
-   - Crystal: Susceptible
-
-   - Jade: Moderately susceptible
-
-#### Genotype yield variability
-
-Host genotype seems to contribute to the variation in yield. Berken shows higher yields compared to crystal and jade.
-```{r yield_vol}
-source("R/yield_volatility.r") #function to investigate the volatility in yields
-
-yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
-yield_volatility(genotype_by_trial = FALSE, control_only = TRUE)
-yield_volatility(genotype_by_trial = FALSE, control_only = FALSE, location = "Hermitage")
-
-yield_volatility("Crystal",control_only = TRUE)
-yield_volatility("Crystal",control_only = FALSE)
-
-yield_volatility("Jade",control_only = TRUE)
-yield_volatility("Jade",control_only = FALSE, location = "Hermitage")
-
-```
-
-### Yield vs in-season rain
-
-In crop rain could be a significant factor which contributes to the end of season grain yield.
-To investigate any relationship I will loop a linear model over time periods from 20 days prior to planting, to 100 days after planting.
-
-#### Best start day for in-crop rainfall
-
-Loop over the dates at the start of the season (to 90 days after planting) to find which date fits the best linear model for grain weight and in-crop rainfall.
-The code for this process was moved to be contained within it's own script and can be run as a job as it can take a long time.
-The output of the script is saved with the prefix `lmInSeasonRainfall` followed by the time windows the model is run.
-For example `lmInSeasonRainfall_20.40_50.80.csv` holds the model results for start days between 20 and 40 days after planting to end window dates between 50 and 80 days after planting.
-
-```{r rainfall_sum_Sstart}
-# The four data files were created from four scripts run as four jobs in Rstudio
-# when the four jobs are finished they can be imported and combined into one data.frame
-# source(Rainfall_x_cropYield_s-10.09_e30.65.R)
-# source(Rainfall_x_cropYield_s-10.09_e65.100.R)
-# source(Rainfall_x_cropYield_s10.30_e30.65.R)
-# source(Rainfall_x_cropYield_s10.30_e65.10.R)
-
-lm_rain1 <- read.csv("data/lmInSeasonRainfall_-10.09_30.64.csv",stringsAsFactors = FALSE)
-lm_rain2 <- read.csv("data/lmInSeasonRainfall_-10.09_65.100.csv",stringsAsFactors = FALSE)
-lm_rain3 <- read.csv("data/lmInSeasonRainfall_10.30_30.64.csv",stringsAsFactors = FALSE)
-lm_rain4 <- read.csv("data/lmInSeasonRainfall_10.30_65.100.csv",stringsAsFactors = FALSE)
-
-lm_rain <- rbind(lm_rain1,lm_rain2,lm_rain3,lm_rain4)
-
-lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)),]
-lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),]
-lm_rain[which(lm_rain$lm_adj_rsquared == max(lm_rain$lm_adj_rsquared)),]
-
-ggplot(lm_rain, aes(x = start_day, y = end_day, z = log(lm_pval)))+
-   geom_raster(aes(fill = log(lm_pval)), interpolate = TRUE)+
-   geom_contour(bins = 15, colour = "white")+
-   geom_abline(intercept = 0, slope = 1, colour = "red")+
-   geom_point(data = lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)),], aes(x = start_day, y = end_day), colour =" red")+
-   scale_fill_distiller(palette ="RdBu", direction = -1)
-
-ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_rsquared))+
-   geom_raster(aes(fill = lm_rsquared), interpolate = TRUE)+
-   geom_contour(bins = 15, colour = "white")+
-   geom_abline(intercept = 0, slope = 1, colour = "red")+
-   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),], aes(x = start_day, y = end_day), colour =" red")+
-   scale_fill_distiller(palette ="RdBu")
-
-ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_adj_rsquared))+
-   geom_raster(aes(fill = lm_adj_rsquared), interpolate = TRUE)+
-   geom_contour(bins = 15, colour = "white")+
-   geom_abline(intercept = 0, slope = 1, colour = "red")+
-   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),], aes(x = start_day, y = end_day), colour =" red")+
-   scale_fill_distiller(palette ="RdBu")
-
-```
-
-The approximate period when in-crop rainfall impacts the most on the mean harvest is between 11 - 88 days after planting.
-
-### Season range and first incidence
-
-```{r first_incidence}
-# Here I want to build a plot of horizontal lines indicating the season length and
-# place a dot on the line to indicating the day of the year first sign was observed for that trial
-
-season_dates <- PM_MB_means %>%
-   group_by(trial_ref)%>%
-   summarise(Planting_date = unique(planting_date),
-             Harvest_date = unique(harvest_date),
-             First_sign_PM = unique(first_sign_disease),
-             season_length = as.integer(as.Date(unique(harvest_date)) - as.Date(unique(planting_date)))
-             )
-
-# function to extract date from the year
-# format should be Universal time format
-source("R/year2day.r")
-
-season_dates$Planting_day <- unlist(lapply(season_dates$Planting_date,year2day))
-season_dates$Disease_day <- unlist(lapply(season_dates$First_sign_PM,year2day))
-season_dates$Harvest_day <- season_dates$Planting_day + season_dates$season_length
-
-season_dates[1,"Planting_day"] <- year2day(as.Date("2012-02-28")-7) # planted in december and emerged in February, Assuming due to lack of rain or recording error.
-Using 7 days prior to emergence day as planting day
-
-first_day_month <- c(0, 31, 59, 90, 120, 151, 181, 211, 243, 273)
-axis_labels_date <- c(format(Sys.Date() - year2day(Sys.Date()) + first_day_month[1], "%b-%d"),  # Jan
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[2], "%b-%d"), # Feb
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[3], "%b-%d"), # March
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[4], "%b-%d"), # April
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[5], "%b-%d"), # May
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[6], "%b-%d"), # June
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[7], "%b-%d"), # July
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[8], "%b-%d"), # August
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[9], "%b-%d"), # Sept
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[10], "%b-%d") # October
-                         )
-
-# reorder the factors so they will appear in chronilogical order
-# I used First sign because all trials have recorded this
-season_dates$trial_ref <- factor(season_dates$trial_ref, levels = levels(season_dates$trial_ref)[rev(order(season_dates$First_sign_PM))])
-
-season_dates %>%
-   ggplot()+
-   geom_pointrange(aes(x = trial_ref, y = Disease_day, ymin = Planting_day, ymax = Harvest_day))+
-   scale_y_continuous(
-      limits = c(0, max(season_dates$Planting_day + 
-                           season_dates$season_length, 
-                        na.rm = TRUE)),
-      labels = axis_labels_date,
-      breaks = first_day_month
-   )+
-   geom_point(aes(x = trial_ref, y = Disease_day))+
-   coord_flip()+
-   ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
 

### 2019-11-03 index.Rmd

@@
 ---
-title: "Powdery Milder yield loss mitigation strategies in Mungbean a Meta-analysis"
+title: "Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis."
 author: "Paul Melloy, Emerson Del Ponte, Charles T. Gray and Adam H. Sparks"
@@
 
-When is the optimum time to spray fungicide to limit the impact of powdery mildew on mungbean yields?
++ When is the optimum time to spray fungicide to limit the impact of powdery mildew on mungbean yields?
 
-How has the first sign of powdery mildew changed over the seasons and between experimental sites?
++ How has the first sign of powdery mildew changed over the seasons and between experimental sites?
 
-How has the first sign of powdery mildew changed over the seasons and between experimental sites?
++ Is there an ideal planting time, or fungicide management strategy, which could make use of powdery mildew defoliation during pod maturation resulting in an increased yield?
 
-When would the ideal planting time be to make use of powdery mildew defoliation in the final growth of the crop?
++ Do infections that occur before flowering increase the probable yield loss?
 
-Do infections that occur before flowering increase the probable yield loss?
-
-What is the length of a mungbean season and how has it varied in this trial?
++ What is the length of a mungbean season and how has it varied in this trial?  
    - This data has not been collected or is not accurate enough to be useful to answer this question.
@@
 
-Variability among host genotypes and probable influence of season given that over the years, the genotype studied changed from Berken, Crystal to Jade.
++ Variability among host genotypes.  
+   + The probable influence of season might be influenced by host genotype. This is because newer varieties were adopted into experimental trials as they were released.  
+   + Between 2001 and 2015 mungbean genotype changed from Green Diamond, Berken, Crystal to Jade. Jade was the only cultivar used between 2015 and 2019.
+
++ Estimations of plant maturity stages over each growing season. These estimations might able to be computed using APSIM.

### 2019-11-03 Cluster Timing/MB_PM_data.Rmd
Uses Paul's new csv file and adds third spray date clusters

@@
 library(skimr)
-mb <- read_csv("slim-mungbean-powdery_mildew.csv")
+mb <- read_csv("slim_PM_dat.csv")
 ```
@@
   mb %>%
-  select(-c(fungicide_application_3:fungicide_application_7)) %>%
-  mutate(first_sign_disease = as.Date(first_sign_disease, format = "%d/%m/%Y")) %>%
-  mutate_at(vars(starts_with("fungicide_application_")), dmy) %>%
   mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
-  mutate(fungicide_timing_2 = fungicide_application_2 - first_sign_disease) %>%
-  filter(!is.na(grain_yield.t.ha.))
+  mutate(fungicide_timing_2 = fungicide_application_2 - fungicide_application_1) %>%
+  mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2) %>%
+  filter(!is.na(grain_yield.t.ha)) %>% 
+  filter(!is.na(PM_final_severity))
 ```
@@
    ggtitle("Second Application",
-           subtitle = "Line at 14 days after first sign") +
+           subtitle = "Line at 14 days after first spray") +
    theme_bw()
@@
 These groups would then have preventative (before), at first sign and then 14 days after and late applications.
+
+## Third spray
+
+```{r third-spray-hist}
+ggplot(filter(mb, !is.na(fungicide_timing_3)),
+       aes(x = as.numeric(fungicide_timing_3))) +
+   geom_histogram(bins = 50, fill = "grey") +
+   geom_vline(linetype = 2,
+              xintercept = 14,
+              colour = "red") +
+   xlab("Days from first sign") +
+   ggtitle("Second Application",
+           subtitle = "Line at 14 days after second spray") +
+   theme_bw()
+```
 
@@
       fungicide_timing_1 >= 0 &
-        fungicide_timing_1 < 3 ~ "Recommended",
+        fungicide_timing_1 < 4 ~ "Recommended",
       TRUE ~ "Late"
@@
       TRUE ~ "Late"
+    )
+  ) %>% 
+  mutate(
+    cluster_3 = case_when(
+      fungicide_timing_3 < 14 ~ "Early",
+      TRUE ~ "Recommended"
     )
@@
 
+The APVMA permit allows for a second spray not sooner than 14 days after the first.
+
 ```{r hist-clust2}
@@
              colour = "red") +
-  xlab("Days from first sign") +
+  xlab("Days from first application") +
   ggtitle("Second Application",
-          subtitle = "Line at 14 days after first sign") +
+          subtitle = "Line at 14 days after first application") +
   theme_bw()
@@
 Note that the cluster for the second spray "recommended" is from Day 13, not Day 14.
+
+## Third spray
+
+The APVMA permit allows for a second spray not sooner than 14 days after the first.
+
+```{r hist-clust3}
+ggplot(filter(mb, !is.na(fungicide_timing_3)),
+       aes(x = as.numeric(fungicide_timing_3))) +
+  geom_histogram(bins = 50, aes(fill = cluster_3)) +
+  scale_fill_viridis_d("Cluster") +
+  geom_vline(linetype = 2,
+             xintercept = 14,
+             colour = "red") +
+  xlab("Days from second sign") +
+  ggtitle("Second Application",
+          subtitle = "Line at 14 days after second application") +
+  theme_bw()
+```

### 2019-11-04 03_Preliminary_analysis.Rmd
Improved formatting flow and correction of broken code

@@
 ```{r PA_Libraries, include=FALSE}
-library(dplyr)
+library(tidyverse)
 library(openxlsx)
@@
 
+#remove the variation in different sulphur formulations
+unique(PM_MB_means[
+   grep("sulphur",PM_MB_means$fungicide),
+   "fungicide"])
+PM_MB_means[grep("sulphur",PM_MB_means$fungicide),"fungicide"] <- "sulphur"
+
 ```
@@
 
-   2) Fungicide dose
+   2) Fungicide dose (varies only slightly within some fungicide types)
 
-   3) Row spacing
+   3) Number of fungicide sprays
 
-   4) Host cultivars (probably is a covariate with season due to changing cultivars over time)
+   4) Timing of fungicide spray/s relative to first sign of disease (ie. when pathogen is present)
 
-   5) Experiment location
+   5) Host cultivars (probably is a covariate with season due to changing cultivars over time)
 
-   6) Final disease rating
+   6) Experiment location
 
-1. Type of Fungicide sprayed
-2. In-crop rainfall
-3. mungbean cultivar
-4. Fungicide dose (we don't expect this to influence as it was only changes slightly)
-5. Mean daily temperature in the weeks following spray application
-6. Row spacing
-7. Two pathogen species cause PM (new discovery)
-8. irrigated vs non-irrigated trials
-9. Number of fungicide sprays (edited)
+   7) Row spacing
+
+   8) In-crop rainfall
+
+   9) irrigated vs non-irrigated trials
+
+   10) Mean daily temperature in the weeks following spray application
+
+   11) Final disease rating
+
+   12) Two pathogen species cause PM (new discovery)
 
 ### Fungicides
-
-The data plotted below are from the past field trials (2011 - 2017) described in the aforementioned table.
-All data are a list of mean values from each treatment applied in each experiment.
-
-When investigating previous studies into powdery mildew fungicide efficacy on mungbean `r length(unique(PM_MB_means$trial_ref))` trials were found.
-However, only eleven tebuconazole were used for the following meta-analysis, followed by the next most common fungicide, propiconazole. Sulphur was disregarded due to its inconsistency in efficacy.
-
+#### Fungicide type
+The data plotted below are from `r length(unique(PM_MB_means$trial_ref))` field trials between (`r first(levels(PM_MB_means$year))` - `r last(levels(PM_MB_means$year))`) of which the details are described in [Studies considered in meta-analysis section](#studies-considered-in-meta-analysis).
+All data explored below are a list of mean values from each treatment applied in each experiment.
+Some experiments have in-season observations of disease incidence and severity, however here we have summarised the data to show only the end of season observations.
 ```{r Fungicides}
@@
 
-Tebuconazole and propiconazole might be able to be pooled as a triazole fungicide treatment. 
-Amistar Xtra is a combination of azoxystrobin and cyproconazole.
-Custodia is a combination of tebuconazole and azoxystrobin.
-Amistar Xtra and Custodia might be able to be pooled given they both contain strobilurin and triazole, however, they contain differing dose ratios (inverted).
+   - Tebuconazole and propiconazole might be able to be pooled as a triazole fungicide treatment.
 
-Perhaps best way forward is to do an analysis of only the triazoles. Then do another including azoxystrobin as a comparison.
+   - Amistar Xtra and Custodia are both contain strobilurin and triazole, however, they because they contain differing dose ratios (inverted) pooling may not be appropriate.
 
-Preliminary analysis of fungicides show there is a difference the effect of fungicide in proportion of yield saved.
+   - Perhaps best way forward is to do an analysis of only the triazoles/demethylation inhibitors. Then do another including azoxystrobin as a comparison.
+
+The primary focus of this research is the effect of fungicide on mitigating yield loss to disease.
+To reduce the affect of location and seasonal influences we will investigate the proportion of grain yield saved, relative to the no spray controls.
+
+First lets investigate the difference in the effect of fungicide on proportion of yield saved?
+
+```{r Fungicide_x_nSprays, message=FALSE}
+PM_MB_means %>%
+   group_by(fungicide, total_fungicide) %>%
+   summarise(
+      n = length(prop_YG),
+      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
+      median = median(prop_YG, na.rm = T),
+      mean = mean(prop_YG, na.rm = T),
+      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
+   ) %>%
+   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
+   arrange(desc(median)) %>%
+   kable(caption = "Fungicide effect on proportion of yield gain.") %>%
+   kable_styling(fixed_thead = T, full_width = T) %>%
+   footnote(general = "Fungicides with less than five observations were omitted from this table")
+
+class(PM_MB_means$fungicide)
+
+PM_MB_means %>%
+   mutate(fungicide = as.factor(PM_MB_means$fungicide)) %>%
+   filter(total_fungicide == 1 | total_fungicide == 2) %>%
+   filter(
+      fungicide != "pyrazophos" &
+         fungicide != "control" &
+         fungicide != "benomyl" &
+         fungicide != "Acibenzolar-S-methyl"
+   ) %>%
+   mutate(fungicide = factor(fungicide, 
+                             levels = c("carbendazim", "pyraclostrobin",
+                                        "sulphur", "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                                        "tebuconazole", "propiconazole", 
+                                        "200 g/L tebuconazole + 120 g/L azoxystrobin"))) %>%
+   ggplot(aes(y = prop_YG, x = fungicide)) +
+   facet_grid(rows = vars(total_fungicide)) +
+   geom_boxplot(aes(fill = fungicide, alpha = 0.5)) +
+   geom_hline(aes(yintercept = 0), size = 0.5) +
+   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
+   labs(y = "Proportion of grain yield saved",
+        title = "Grain yield proportion saved\ngrouped by Fungicide type") +
+   theme_usq() +
+   theme(legend.position = "none") +
+   # coord_cartesian() +
+   # scale_x_discrete(
+   #    limits = c(
+   #       "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin",
+   #       "Propiconazole",
+   #       "Tebeconazole",
+   #       "200g/L Azoxystrobin + 80 g/L Cyproconazole",
+   #       "Sulphur",
+   #       "Carbendazim",
+   #       "Pyraclostrobin",
+   #       "Azoxystrobin"
+   #    )
+   # ) +
+   #  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
+   coord_flip()
+#scale_x_continuous(limits = c(-0.3,0.6))
+
+```
 
@@
    theme_usq()
+```
+
+#### Number of fungicide sprays
+
+#### Timing of fungicide sprays
+
+### Mungbean cultivars  
+Host genotype may need to be analysed to determine the effect.
+
+```{r Host_genotype}
+PM_MB_means %>%
+   filter(fungicide_ai == "tebuconazole",
+         row_spacing == 0.75) %>%
+   group_by(host_genotype, trial_ref) %>%
+   summarise() %>%
+   count() %>%
+   rename(Treatments = n) %>%
+   ggplot(aes(x = host_genotype, y = Treatments)) +
+   xlab("Cultivar") +
+   ylab("N Trials") +
+   ggtitle(label = "Cultivars used in tebuconazole trials with 0.75 m row spacing") +
+   geom_col() +
+   scale_fill_usq() +
+   scale_colour_usq() +
+   theme_usq()
+```
+
+In general the mungbean varieties have the following resistance to powdery mildew.
+
+   - Berken: Highly susceptible
+
+   - Crystal: Susceptible
+
+   - Jade: Moderately susceptible
+
+#### Genotype yield variability
+
+Host genotype seems to contribute to the variation in yield. Berken shows higher yields compared to crystal and jade.
+```{r yield_vol}
+# this could be converted into a shiny app as a chunk. Make each input for the function a shiny option
+# Outputs the table and graph
+source("R/yield_volatility.r") #function to investigate the volatility in yields
+# Volitility is the range between the upper and lower 97.5 and 2.5 % quartiles
+
+YV1 <- yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
+YV1[[2]]
+YV1[[3]]
+YV2 <- yield_volatility(genotype_by_trial = FALSE, control_only = TRUE)
+YV2[[2]]
+
+YV1_herm <- yield_volatility(genotype_by_trial = FALSE, control_only = FALSE, location = "Hermitage")
+YV1_herm[[2]]
+
+YV1_crystal <- yield_volatility("Crystal",control_only = FALSE)
+YV1_crystal[[2]]
+
+YV2_crystal <- yield_volatility("Crystal",control_only = TRUE)
+YV2_crystal[[2]]
+
+YV1_herm_jade <- yield_volatility("Jade",control_only = FALSE, location = "Hermitage")
+YV2_jade <- yield_volatility("Jade",control_only = TRUE)
+
 ```
@@
 Can we pool certain row spacing that have no significant difference?  
-From the preliminary analysis, the graphs seem to imply that if there is a lower overall yield there is no effect of row spacing on yield.
-However, if the average yield is more than approximately 0.6 - 1 t/ha then smaller row spacing has the potential to provide greater yield.
+From the preliminary analysis, the graphs seem to imply if there is a lower overall yield there is no effect of row spacing on yield.
+However, if the average yield is more than approximately 0.6 - 1 t/ha then smaller row spacing has the potential to provide greater yield per hectare.
 
@@
    filter(fungicide == "control") %>%
-   ggplot(aes(y = PM_final_severity, x = row_spacing, colour = location)) +
-   geom_point() +
+   ggplot(aes(y = PM_final_severity, x = factor(row_spacing))) +
+   geom_boxplot() +
    #  geom_smooth()+
    scale_y_continuous(limits = c(-5, 15)) +
-   theme_usq()
+   theme_usq()+
+   ggtitle("Powdery mildew variation between different row spacing")
 
@@
    #   scale_y_continuous(limits = c(-5,15))+
-   theme_usq()
-
-```
-
-### Host genotypes
-
-Host genotype may need to be analysed to determine the effect.
-
-```{r Host_genotype}
-PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole",
-         row_spacing == 0.75) %>%
-   group_by(host_genotype, trial_ref) %>%
-   summarise() %>%
-   count() %>%
-   rename(Treatments = n) %>%
-   ggplot(aes(x = host_genotype, y = Treatments)) +
-   xlab("Cultivar") +
-   ylab("N Trials") +
-   ggtitle(label = "Cultivars used in tebuconazole trials with 0.75 m row spacing") +
-   geom_col() +
-   scale_fill_usq() +
-   scale_colour_usq() +
-   theme_usq()
-```
-
-In general the mungbean varieties have the following resistance to powdery mildew.
-
-   - Berken: Highly susceptible
-
-   - Crystal: Susceptible
-
-   - Jade: Moderately susceptible
-
-#### Genotype yield variability
-
-Host genotype seems to contribute to the variation in yield. Berken shows higher yields compared to crystal and jade.
-```{r yield_vol}
-source("R/yield_volatility.r") #function to investigate the volatility in yields
-
-yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
-yield_volatility(genotype_by_trial = FALSE, control_only = TRUE)
-yield_volatility(genotype_by_trial = FALSE, control_only = FALSE, location = "Hermitage")
-
-yield_volatility("Crystal",control_only = TRUE)
-yield_volatility("Crystal",control_only = FALSE)
-
-yield_volatility("Jade",control_only = TRUE)
-yield_volatility("Jade",control_only = FALSE, location = "Hermitage")
+   theme_usq()+
+   ggtitle("Grain yield results for different row spacing at three locations")
 
@@
 
-#### Best start day for in-crop rainfall
-
 Loop over the dates at the start of the season (to 90 days after planting) to find which date fits the best linear model for grain weight and in-crop rainfall.
 The code for this process was moved to be contained within it's own script and can be run as a job as it can take a long time.
+To speed up the computation I split the script into four, ran the jobs and bound the data into one frame.
 The output of the script is saved with the prefix `lmInSeasonRainfall` followed by the time windows the model is run.
@@
 
+source("R/AUS_rainfall_function.r")
+source("R/rainfall_sum_dat.R")
+
+for(i in rain_dat_sum$trial_ref){
+dat_rain <- rain_dat_sum[rain_dat_sum$trial_ref == i,]
+
+   rain_dat_sum[which(rain_dat_sum$trial_ref == i), "rainfall_sum"] <- 
+      AUS_rainfall(StartDate = as.Date(dat_rain$planting_date) +
+                   lm_rain[which(lm_rain$lm_adj_rsquared == max(lm_rain$lm_adj_rsquared)), "start_day"],
+                EndDate = as.Date(dat_rain$planting_date) +
+                   lm_rain[which(lm_rain$lm_adj_rsquared == max(lm_rain$lm_adj_rsquared)), "end_day"],
+                latlong = as.vector(unlist(dat_rain[, 5:6])))
+}
+
+summary(lm(rainfall_sum ~ grain_yield, 
+                             data = rain_dat_sum[rain_dat_sum$location != "Hermitage",]))
+
+rain_dat_sum %>%
+   ggplot(aes(x = grain_yield, y = rainfall_sum, colour = location))+
+   geom_point() + 
+   geom_abline(intercept = -167.98, slope = 284.44, colour = "red")
+
 ```
 
-The approximate period when in-crop rainfall impacts the most on the mean harvest is between 11 - 88 days after planting.
+The approximate period when in-crop rainfall impacts the most on the mean harvest is between 14 - 67 days after planting.
 
@@
 Let us look to see if there is anything skewing the above.
-
-```{r Fungicide_x_nSprays, message=FALSE}
-PM_MB_means %>%
-   group_by(fungicide, total_fungicide) %>%
-   summarise(
-      n = length(prop_YG),
-      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
-      median = median(prop_YG, na.rm = T),
-      mean = mean(prop_YG, na.rm = T),
-      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
-   ) %>%
-   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
-   arrange(desc(median)) %>%
-   kable(caption = "Fungicide effect on proportion of yield gain") %>%
-   kable_styling(fixed_thead = T, full_width = T)
-
-PM_MB_means %>%
-   filter(total_fungicide == 1 | total_fungicide == 2) %>%
-   filter(
-      fungicide != "pyrazophos" &
-         fungicide != "control" &
-         fungicide != "benomyl" &
-         fungicide != "Acibenzolar-S-methyl" &
-         fungicide != "200g/L azoxystrobin + 80 g/L cyproconazole + adj"
-   ) %>%
-   ggplot(aes(y = prop_YG, x = fungicide)) +
-   facet_grid(rows = vars(total_fungicide)) +
-   geom_boxplot(aes(fill = fungicide, alpha = 0.5)) +
-   geom_hline(aes(yintercept = 0), size = 0.5) +
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(y = "Proportion of grain yield saved",
-        title = "Grain yield proportion saved\ngrouped by Fungicide type") +
-   theme_usq() +
-   theme(legend.position = "none") +
-   # coord_cartesian() +
-   # scale_x_discrete(
-   #    limits = c(
-   #       "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin",
-   #       "Propiconazole",
-   #       "Tebeconazole",
-   #       "200g/L Azoxystrobin + 80 g/L Cyproconazole",
-   #       "Sulphur",
-   #       "Carbendazim",
-   #       "Pyraclostrobin",
-   #       "Azoxystrobin"
-   #    )
-   # ) +
-   #  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
-   coord_flip()
-#scale_x_continuous(limits = c(-0.3,0.6))
-
-```
 
@@
 quant_PMy <- PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-   group_by(total_Fungicide) %>%
+   filter(fungicide != "control") %>%
+   group_by(total_fungicide) %>%
    summarise(
@@
 # Density plot of Number of fungicide applications and the resulting yeild saved (as a proportion)
-ggplot(subset(PM_MB_means, Fungicide != "control"), aes(yield_gain)) +
+ggplot(subset(PM_MB_means, fungicide != "control"), aes(yield_gain)) +
    geom_density(aes(
-      group = factor(total_Fungicide),
-      fill = factor(total_Fungicide)
+      group = factor(total_fungicide),
+      fill = factor(total_fungicide)
    ), alpha = 0.6) +
@@
       aes(xintercept = lower_2.5,
-          colour = factor(total_Fungicide)),
+          colour = factor(total_fungicide)),
       size = 0.9,
@@
       aes(xintercept = upper_97.5,
-          colour = factor(total_Fungicide)),
+          colour = factor(total_fungicide)),
       size = 0.9,

### 2019-11-04 04_Prep_data.Rmd
Added cluster grouping to the slim data

@@
 # Place holder
-
-Warning this markdown file needs corrections to variable names.
-Column headers for PM_MB_means were changed and the column names need to be corrected below accordingly
 
@@
 ```
+
+```{r clustered_fungicide_applications}
+source("R/slimming_PM_dat.R")
+head(slim_PM_dat)
+
+slim_PM_dat %<>%
+  mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
+  mutate(fungicide_timing_2 = fungicide_application_2 - fungicide_application_1) %>%
+  mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2) %>%
+  filter(!is.na(grain_yield.t.ha)) %>% 
+  filter(!is.na(PM_final_severity))
+
+```
+
+```{r cluster}
+
+slim_PM_dat %<>%
+  mutate(
+    cluster_1 = case_when(
+      fungicide_timing_1 < 0 ~ "Early",
+      fungicide_timing_1 >= 0 &
+        fungicide_timing_1 < 4 ~ "Recommended",
+      TRUE ~ "Late"
+    )
+  ) %>%
+  mutate(
+    cluster_2 = case_when(
+      fungicide_timing_2 < 13 ~ "Early",
+      fungicide_timing_2 >= 13 &
+        fungicide_timing_2 < 17 ~ "Recommended",
+      TRUE ~ "Late"
+    )
+  ) %>% 
+  mutate(
+    cluster_3 = case_when(
+      fungicide_timing_3 < 14 ~ "Early",
+      TRUE ~ "Recommended"
+    )
+  )
+
+slim_PM_dat[slim_PM_dat$fungicide_ai == "control", c("fungicide_timing_1", "fungicide_timing_2", "fungicide_timing_3",
+                                                     "cluster_1", "cluster_2","cluster_3")] <- "control"
+
+```

### 2019-11-04 R/AUS_rainfall_function.r
Running this as a job again updated output to include non-filtered linear models

@@ -67,7 +67,7 @@ AUS_rainfall <- function(StartDate = Sys.Date()-30,
       
          
     }
-	head(rain)
+	
 	rain$Bureau.of.Meteorology.station.number <- as.character(rain[,2])
 	
 	if(nchar(rain$Bureau.of.Meteorology.station.number[1]) == 5){
@@ -106,7 +106,10 @@ AUS_rainfall <- function(StartDate = Sys.Date()-30,
 
    
    
-   rainfall <- sum(rain[as.numeric(row_start):(as.numeric(row_start) + as.numeric(season)),"Rainfall.amount..millimetres."],na.rm = TRUE)
+   rainfall <- sum(
+      rain[as.numeric(row_start):(as.numeric(row_start) + 
+                                     as.numeric(season)),
+           6],na.rm = TRUE)
    
    message(paste0("Season days: ",season))
    return(rainfall)                                       

### 2019-11-04 R/Rainfall_x_cropYield_s-10.09_e30.65.R

@@ -101,7 +101,7 @@ rain_dat_sum[rain_dat_sum$location == "Dalby", c("lat","lon")] <- c(-27.168426, 
 rain_dat_sum$rainfall_sum <- NA
 
 # source funtion that uses bomrang get_historical to return the sum rainfall between two dates
-   source("R/AUS_rainfall_function.r")
+source("R/AUS_rainfall_function.r")
 
 # loop to download and save all the rainfall sum data
 # this first loop Investigate when is the first day in the season for which in-crop rainfall is important
@@ -142,11 +142,20 @@ rain_dat_sum$rainfall_sum <- NA
          
          lmod1 <- summary(lm(rainfall_sum ~ grain_yield, 
                              data = rain_dat_sum[rain_dat_sum$location != "Hermitage",])) # remove hermitage which is irrigated
-         
          pval <- coef(lmod1)[2,4]
          rsqu <- lmod1$r.squared
          ADrs <- lmod1$adj.r.squared
-         return(list(pval,rsqu,ADrs))
+         
+         
+         lmod2 <- summary(lm(rainfall_sum ~ grain_yield, 
+                             data = rain_dat_sum)) # remove hermitage which is irrigated
+         
+         pval2 <- coef(lmod2)[2,4]
+         rsqu2 <- lmod2$r.squared
+         ADrs2 <- lmod2$adj.r.squared
+         
+         
+         return(list(pval,rsqu,ADrs,pval2,rsqu2,ADrs2))
          
       })
       
@@ -164,6 +173,16 @@ rain_dat_sum$rainfall_sum <- NA
       }
       
       write.csv(lm_rain, file = "data/lmInSeasonRainfall_-10.09_30.64.csv", row.names = FALSE)
+      
+      
+      for(i in seq_along(testlist1)){
+         lm_rain$lm_pval[i] <- testlist1[[i]][[4]]
+         lm_rain$lm_rsquared[i] <- testlist1[[i]][[5]]
+         lm_rain$lm_adj_rsquared[i] <- testlist1[[i]][[6]]
+      }
+      
+      write.csv(lm_rain, file = "data/lmInSeasonRainfall_-10.09_30.64_HERM.csv", row.names = FALSE)
+      
       
       message("Script completed running")
       

### 2019-11-04 R/Rainfall_x_cropYield_s-10.09_e65.100.R

@@ -146,8 +146,17 @@ rain_dat_sum$rainfall_sum <- NA
          pval <- coef(lmod1)[2,4]
          rsqu <- lmod1$r.squared
          ADrs <- lmod1$adj.r.squared
-         return(list(pval,rsqu,ADrs))
          
+         
+         lmod2 <- summary(lm(rainfall_sum ~ grain_yield, 
+                             data = rain_dat_sum)) # remove hermitage which is irrigated
+         
+         pval2 <- coef(lmod2)[2,4]
+         rsqu2 <- lmod2$r.squared
+         ADrs2 <- lmod2$adj.r.squared
+         
+         
+         return(list(pval,rsqu,ADrs,pval2,rsqu2,ADrs2))
       })
       
       #stopCluster(cl8)
@@ -164,6 +173,14 @@ rain_dat_sum$rainfall_sum <- NA
       }
       
       write.csv(lm_rain, file = "data/lmInSeasonRainfall_-10.09_65.100.csv", row.names = FALSE)
+      
+      for(i in seq_along(testlist1)){
+         lm_rain$lm_pval[i] <- testlist1[[i]][[4]]
+         lm_rain$lm_rsquared[i] <- testlist1[[i]][[5]]
+         lm_rain$lm_adj_rsquared[i] <- testlist1[[i]][[6]]
+      }
+      
+      write.csv(lm_rain, file = "data/lmInSeasonRainfall_-10.09_65.100_HERM.csv", row.names = FALSE)
       
       message("Script completed running")
       

### 2019-11-04 R/Rainfall_x_cropYield_s10.30_e30.65.R

@@ -146,7 +146,17 @@ rain_dat_sum$rainfall_sum <- NA
          pval <- coef(lmod1)[2,4]
          rsqu <- lmod1$r.squared
          ADrs <- lmod1$adj.r.squared
-         return(list(pval,rsqu,ADrs))
+
+         
+         lmod2 <- summary(lm(rainfall_sum ~ grain_yield, 
+                             data = rain_dat_sum)) # remove hermitage which is irrigated
+         
+         pval2 <- coef(lmod2)[2,4]
+         rsqu2 <- lmod2$r.squared
+         ADrs2 <- lmod2$adj.r.squared
+         
+         
+         return(list(pval,rsqu,ADrs,pval2,rsqu2,ADrs2))
          
       })
       
@@ -164,6 +174,14 @@ rain_dat_sum$rainfall_sum <- NA
       }
       
       write.csv(lm_rain, file = "data/lmInSeasonRainfall_10.30_30.64.csv", row.names = FALSE)
+      
+      for(i in seq_along(testlist1)){
+         lm_rain$lm_pval[i] <- testlist1[[i]][[4]]
+         lm_rain$lm_rsquared[i] <- testlist1[[i]][[5]]
+         lm_rain$lm_adj_rsquared[i] <- testlist1[[i]][[6]]
+      }
+      
+      write.csv(lm_rain, file = "data/lmInSeasonRainfall_10.30_30.64_HERM.csv", row.names = FALSE)
       
       message("Script completed running")
       

### 2019-11-04 R/slimming_PM_dat.R
Extra code to remove trials without tebuconazole and propiconazole

@@ -28,6 +28,20 @@ slim_PM_dat <- slim_PM_dat[slim_PM_dat$fungicide_ai == "control" |
                               slim_PM_dat$fungicide_ai == "tebuconazole" |
                               slim_PM_dat$fungicide_ai == "propiconazole" ,
                            ]
+for(i in levels(slim_PM_dat$trial_ref)){
+   if(i == levels(slim_PM_dat$trial_ref)[1]){
+      rows_to_delete <- vector()
+   }
+   
+   if(any(slim_PM_dat[slim_PM_dat$trial_ref == i,"fungicide_ai"] == "tebuconazole" |
+                            slim_PM_dat[slim_PM_dat$trial_ref == i,"fungicide_ai"] == "propiconazole")){
+      next()
+   }else
+      rows_to_delete <- c(rows_to_delete, which(slim_PM_dat$trial_ref == i))
+}
+
+slim_PM_dat <- slim_PM_dat[-rows_to_delete,]
+
 
 write.csv(slim_PM_dat, file = "data/slim_PM_dat.csv", row.names = FALSE)
 

### 2019-11-04 R/yield_volatility.R
Formating improvements

@@ -1,4 +1,7 @@
-yield_volatility <- function(genotype, control_only = TRUE, genotype_by_trial = TRUE, location = NA){
+yield_volatility <- function(genotype, 
+                             control_only = TRUE, 
+                             genotype_by_trial = TRUE, 
+                             location = NA){
    
    if(isTRUE(genotype_by_trial)){
    
@@ -36,7 +39,8 @@ yield_volatility <- function(genotype, control_only = TRUE, genotype_by_trial = 
    
    Plot1 <- dat3 %>%
       ggplot(aes(x = values))+
-      geom_density(aes(fill = trial), alpha = 0.4)
+      geom_density(aes(fill = trial), alpha = 0.4)+
+      xlim(0.25,2.25)
    
    mean_Y_volatility <- dat3 %>%
       group_by(trial) %>%

### 2019-11-04 Cluster Timing/MB_PM_data.Rmd
Fixes control being assigned to "Late" clusters

@@
         fungicide_timing_1 < 4 ~ "Recommended",
-      TRUE ~ "Late"
+      fungicide_timing_1 > 4 ~ "Late"
     )
@@
         fungicide_timing_2 < 17 ~ "Recommended",
-      TRUE ~ "Late"
+      fungicide_timing_2 > 17 ~ "Late"
     )
@@
       fungicide_timing_3 < 14 ~ "Early",
-      TRUE ~ "Recommended"
+      fungicide_timing_3 == 14 ~ "Recommended"
     )
-  )
+  ) %>% 
+  View()
 ```

### 2019-11-04 Cluster Timing/MB_PM_data.Rmd
Remove View()

--- 2019-11-03 Cluster Timing/MB_PM_data.Rmd
@@
       fungicide_timing_3 < 14 ~ "Early",
-      TRUE ~ "Recommended"
+      fungicide_timing_3 == 14 ~ "Recommended"
     )

### 2019-11-05 04_Prep_data.Rmd
Updated to incorportate data wrangling from the means data set to a slim data with clustered spray categories

@@
 ```
+
+## Standardising sample variance
+
+The type of variance needs to be standardised between trials and treatments for the meta-analysis.
+
+```{r variance_types}
+# PM_MB_means$Y_error_type <- forcats::fct_explicit_na(PM_MB_means$Y_error_type, na_level = NA)
+# Trials using tebuconazole
+PM_MB_means %>%
+   filter(fungicide_ai == "tebuconazole",
+         row_spacing == 0.75) %>%
+   group_by(trial_ref, location, Y_error_type) %>%
+   summarise(tebuconazole_trts = length(Y_error_type))
+
+# Trials using propiconazole
+PM_MB_means %>%
+   filter(fungicide_ai == "propiconazole",
+          row_spacing == 0.75) %>%
+   group_by(trial_ref, location, Y_error_type) %>%
+   summarise(propiconazole_trts = length(Y_error_type))
+```
+
+The experiment summaries report either standard deviation, least square differences or no error term (`NA`). Below we will convert LSD and standard deviation to sample variance
+
+### Converting least-squares to sample variance
+
+```{r all_LSD_trials}
+Trials <- PM_MB_means %>%
+   filter(
+          Y_error_type == "lsd (P=0.05)") %>%
+   select(trial_ref) %>%
+   distinct()
+Trials
+```
+
+The trial, `mung1112/02` uses Least Square Differences (LSD) to describe the variation within the experiment.
+The following code attempts to convert this to sampling variance as per the method in [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
+Ideas for using a T-critical value of 1.697 came from reading a [statisics-how-to website](https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/).
+A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted where 30 degrees of freedom within experiment was used to find the 'T-crit' value of 1.697.
+
+![Calculating sampling variance from mean squared error Paul et al. (2008)](Paul_etal_2008.PNG)
+
+```{r LSD_2_Sampling Variance}
+# Formula and modifications based off information found at https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/
+
+for (Trial2012 in Trials$trial_ref) {
+   Tcrit <-
+      1.697  # 0.05 and DFw = 30 # T critical value for which there is significant difference between two groups; This value is the same for both trials "mung1112/01" and "mung1112/02"
+   DFw <-
+      sum(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates) -
+      length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates) # degrees of freedom within groups
+   # n.A <- PM_MB_means[PM_MB_means$trial_ref == "Trial2012,]$replicates[1]
+   # n.B <- PM_MB_means[PM_MB_means$trial_ref == "Trial2012,]$replicates[2]
+   LSD <-
+      PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error[1]
+
+   # SSwithin <- #unknown
+   # MSW <- SSwithin / DFw # mean square within (SS within / DF within)
+
+   #  LSD = (Tcrit) * sqrt(MSW * (1/n.A + 1/n.B))
+   #  (LSD/Tcrit) = sqrt(MSW * (1/n.A + 1/n.B))
+   #  (LSD/Tcrit)^2 = MSW * (1/n.A + 1/n.B)
+   #  (LSD/Tcrit)^2/(1/n.A + 1/n.B) = MSW
+   #  MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B) # This formula was abandon in favor for the formula in Nugugi et. at (2011)
+   MSE <-
+      PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[1] * (LSD /
+                                                                            Tcrit) ^ 2 / 2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
+
+   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates)) {
+      if (j == 1) {
+         Sv <-
+            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates))
+      }
+      #  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates[j] *
+      #                   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$grain_yield.t.ha[j])
+      # Balance equation
+      Sv[j] = sqrt(MSE / (
+         PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j] *
+            as.numeric(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$grain_yield.t.ha[j])
+      ))
+
+   }
+
+   # and replacing the values in the dataset
+
+   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error <-
+      Sv
+   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$Y_error_type <-
+      "SamplingVariance"
+
+}
+```
+
+### Converting standard deviation to sample variance
+Now to estimate the variance from the standard deviation
+
+```{r stdev2SampVariance}
+# subset data by those which describe the Yield error with standard deviation
+Trials <- PM_MB_means %>%
+   filter(#fungicide_ai == "tebuconazole",
+      #row_spacing.m == 0.75,
+      Y_error_type == "stdev") %>%
+   select(trial_ref) %>%
+   distinct()
+
+# calculate the Sampling variance from the standard deviation
+# standard error of the mean equals the standard deviation divided by the square root of the number of samples
+# Sv <- sem^2 <- stdev/sqrt(n)
+# Sampling variance equals the square of the standard error.
+# Sv <- (stdev/sqrt(n))^2
+
+# Therefore
+
+for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error)) {
+   # create empty vector at first iteration with length of j
+   if (j == 1) {
+      Sv <-
+         vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error))
+   }
+
+   # Equation to convert standard deviation to Sampling Variance
+   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error[j]) ^
+      2
+}
+
+# and replacing the values in the dataset
+PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error <-
+   Sv
+PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$Y_error_type <-
+   "SamplingVariance"
+```
+
+## Yield gains  
+Yield gains and yield gains proportional to the control.
 
@@
 
-# dat1 <- PM_MB_means[PM_MB_means$trial_ref == "AM1303", ]
-# 
-# controlY <-
-#    mean(dat1[dat1$fungicide == "control", "grain_yield.t.ha."])
-# 
-# dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
-# dat1$prop_YG <- dat1$yield_gain / controlY
-# dat1[dat1$fungicide == "control", c("yield_gain", "prop_YG")] <- NA
-# PM_MB_means[PM_MB_means$trial_ref == "AM1303", ] <- dat1
+dat1 <- PM_MB_means[PM_MB_means$trial_ref == "AM1303", ]
+
+controlY <-
+   mean(dat1[dat1$fungicide == "control", "grain_yield.t.ha."])
+
+dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
+dat1$prop_YG <- dat1$yield_gain / controlY
+dat1[dat1$fungicide == "control", c("yield_gain", "prop_YG")] <- NA
+PM_MB_means[PM_MB_means$trial_ref == "AM1303", ] <- dat1
 
 write.csv(PM_MB_means,
-          "data/1902 PM_MB_means&Ygains.csv")
+          "data/1911_PM_MB_means&Ygains.csv")
 ```
@@
 
-slim_PM_dat[slim_PM_dat$fungicide_ai == "control", c("fungicide_timing_1", "fungicide_timing_2", "fungicide_timing_3",
-                                                     "cluster_1", "cluster_2","cluster_3")] <- "control"
+slim_PM_dat[slim_PM_dat$fungicide_ai == "control",
+            c("fungicide_timing_1", "fungicide_timing_2", "fungicide_timing_3",
+              "cluster_1", "cluster_2","cluster_3"
+              )] <- "control"
+
+write.csv(slim_PM_dat, file = "data/slim_PM_clusterdat.csv", row.names = FALSE)
 

### 2019-11-05 05_MetaAnalysis.Rmd
Moved sample variance calculation to the prep_data.Rmd

@@
 
-```
-
-## Standardising sample variance
-
-The type of variance needs to be standardised between trials and treatments for the meta-analysis.
-
-```{r variance}
-# PM_MB_means$Y_error_type <- forcats::fct_explicit_na(PM_MB_means$Y_error_type, na_level = NA)
-# Trials using tebuconazole
-PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole",
-         row_spacing == 0.75) %>%
-   group_by(trial_ref, location, Y_error_type) %>%
-   summarise(tebuconazole_trts = length(Y_error_type))
-
-# Trials using propiconazole
-PM_MB_means %>%
-   filter(fungicide_ai == "propiconazole",
-          row_spacing == 0.75) %>%
-   group_by(trial_ref, location, Y_error_type) %>%
-   summarise(propiconazole_trts = length(Y_error_type))
-```
-
-### Converting least-squares to sample variance
-
-```{r all_LSD_trials}
-Trials <- PM_MB_means %>%
-   filter(
-      #fungicide_ai == "tebuconazole",
-      #    row_spacing == 0.75,
-          Y_error_type == "lsd (P=0.05)") %>%
-   select(trial_ref) %>%
-   distinct()
-Trials
-```
-
-The trial, `mung1112/02` uses Least Square Differences (LSD) to describe the variation within the experiment.
-The following code attempts to convert this to sampling variance as per the method in [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
-Ideas for using a T-critical value of 1.697 came from reading a [statisics-how-to website](https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/).
-A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted where 30 degrees of freedom within experiment was used to find the 'T-crit' value of 1.697.
-
-![Calculating sampling variance from mean squared error Paul et al. (2008)](Paul_etal_2008.PNG)
-
-```{r LSD_2_Sampling Variance}
-# Formula and modifications based off information found at https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/
-
-for (Trial2012 in Trials$trial_ref) {
-   Tcrit <-
-      1.697  # 0.05 and DFw = 30 # T critical value for which there is significant difference between two groups; This value is the same for both trials "mung1112/01" and "mung1112/02"
-   DFw <-
-      sum(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates) -
-      length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates) # degrees of freedom within groups
-   # n.A <- PM_MB_means[PM_MB_means$trial_ref == "Trial2012,]$replicates[1]
-   # n.B <- PM_MB_means[PM_MB_means$trial_ref == "Trial2012,]$replicates[2]
-   LSD <-
-      PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error[1]
-
-   # SSwithin <- #unknown
-   # MSW <- SSwithin / DFw # mean square within (SS within / DF within)
-
-   #  LSD = (Tcrit) * sqrt(MSW * (1/n.A + 1/n.B))
-   #  (LSD/Tcrit) = sqrt(MSW * (1/n.A + 1/n.B))
-   #  (LSD/Tcrit)^2 = MSW * (1/n.A + 1/n.B)
-   #  (LSD/Tcrit)^2/(1/n.A + 1/n.B) = MSW
-   #  MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B) # This formula was abandon in favor for the formula in Nugugi et. at (2011)
-   MSE <-
-      PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[1] * (LSD /
-                                                                            Tcrit) ^ 2 / 2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
-
-   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates)) {
-      if (j == 1) {
-         Sv <-
-            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates))
-      }
-      #  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates[j] *
-      #                   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$grain_yield.t.ha[j])
-      # Balance equation
-      Sv[j] = sqrt(MSE / (
-         PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j] *
-            as.numeric(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$grain_yield.t.ha[j])
-      ))
-
-   }
-
-   # and replacing the values in the dataset
-
-   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error <-
-      Sv
-   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$Y_error_type <-
-      "SamplingVariance"
-
-}
-```
-
-### Converting standard deviation to sample variance
-Now to estimate the variance from the standard deviation
-
-```{r stdev2SampVariance}
-# subset data by those which describe the Yield error with standard deviation
-Trials <- PM_MB_means %>%
-   filter(#fungicide_ai == "tebuconazole",
-      #row_spacing.m == 0.75,
-      Y_error_type == "stdev") %>%
-   select(trial_ref) %>%
-   distinct()
-
-# calculate the Sampling variance from the standard deviation
-# standard error of the mean equals the standard deviation divided by the square root of the number of samples
-# Sv <- sem^2 <- stdev/sqrt(n)
-# Sampling variance equals the square of the standard error.
-# Sv <- (stdev/sqrt(n))^2
-
-# Therefore
-
-for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error)) {
-   # create empty vector at first iteration with length of j
-   if (j == 1) {
-      Sv <-
-         vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error))
-   }
-
-   # Equation to convert standard deviation to Sampling Variance
-   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error[j]) ^
-      2
-}
-
-# and replacing the values in the dataset
-PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error <-
-   Sv
-PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$Y_error_type <-
-   "SamplingVariance"
 ```

### 2019-11-05 04_Prep_data.Rmd
Correct clustering code to handle NA values

@@
 
-slim_PM_dat %<>%
+slim_PM_dat %>%
   mutate(
@@
     cluster_2 = case_when(
+      is.na(fungicide_timing_2) ~ NA_character_,
       fungicide_timing_2 < 13 ~ "Early",
@@
       fungicide_timing_3 < 14 ~ "Early",
+      is.na(fungicide_timing_3) ~ NA_character_,
       TRUE ~ "Recommended"

### 2019-11-05 05_MetaAnalysis.Rmd
Some LMmodels on slim data

@@
 library(bomrang)
+library(lme4)
 
@@
 
-### Estimating variance for trials without reported error
+## Estimating variance for trials without reported error
 
@@
 
-#### Random effects model to predict trial variance
+### Random effects model to predict trial variance
 Just for kicks lets look at the linear regression model as a random effects model where `grain_yield.t.ha` is set as a random slope to the random intercept `trial_ref`.
@@
 
-## Between trial variation
+### Between trial variation
 
@@
 ```
+
+## Preliminary meta-analysis
+
+```{r}
+slim_PM_dat <- read.csv("data/slim_PM_clusterdat.csv")
+
+m1 <- lmer(grain_yield.t.ha*1000 ~ factor(total_fungicide) + (factor(total_fungicide) | trial_ref), data = slim_PM_dat)
+
+m2 <- lmer(grain_yield.t.ha*1000 ~ factor(total_fungicide) + (1 | trial_ref), data = slim_PM_dat)
+
+anova(m1,m2)
+
+m3 <- lmer(log(grain_yield.t.ha*1000) ~ factor(total_fungicide) + (factor(total_fungicide) | trial_ref), data = slim_PM_dat)
+
+anova(m1, m3)
+summary(m3)
+
+```
+
+```{r}
+
+```

### 2019-11-05 Cluster Timing/MB_PM_data.Rmd
Changed clustering to handle NA values

--- 2019-11-03 Cluster Timing/MB_PM_data.Rmd
@@
     cluster_1 = case_when(
+      is.na(fungicide_timing_1) ~ NA_character_,
       fungicide_timing_1 < 0 ~ "Early",
@@
     cluster_3 = case_when(
+      is.na(fungicide_timing_3) ~ NA_character_,
       fungicide_timing_3 < 14 ~ "Early",
-      TRUE ~ "Recommended"
+      fungicide_timing_3 == 14 ~ "Recommended"
     )

### 2019-11-05 04_Prep_data.Rmd
Created new cluster variable (spray_management) with six levels

--- 2019-11-05 04_Prep_data.Rmd
@@
 ```
+
+Cluster the clusters
+
+```{r cluster_clusters}
+
+clusters <- unique(slim_PM_dat[c("cluster_1","cluster_2","cluster_3")])
+
+for(i in 1:nrow(clusters)){
+   if(i == 1){clusters$n <- NA
+   clusters$n_x_trial <- NA}
+
+   clusters[i,"n"] <- nrow(slim_PM_dat[slim_PM_dat$cluster_1 == clusters[i,"cluster_1"] &
+                                          slim_PM_dat$cluster_2 == clusters[i,"cluster_2"] &
+                                          slim_PM_dat$cluster_3 == clusters[i,"cluster_3"],
+                                       ])
+
+   clusters[i,"n_x_trial"] <- length(unique(slim_PM_dat[slim_PM_dat$cluster_1 == clusters[i,"cluster_1"] &
+                                          slim_PM_dat$cluster_2 == clusters[i,"cluster_2"] &
+                                          slim_PM_dat$cluster_3 == clusters[i,"cluster_3"],
+                                       "trial_ref"]))
+
+}
+
+knitr::kable(clusters)
+
+```
+
+From this we can see that there are 16 different cluster combinations, which would make the analysis too difficult. I will reduce this to 6 levels within one variable.
+
+Single sprays either early, recommended timing or late.
+
+Two sprays or more where the first spray was either early, recommended timing, or late.
+
+```{r simple_clusters}
+
+slim_PM_dat %>%
+  mutate(
+    spray_management = case_when(
+       fungicide_timing_1 < 0 &
+          is.na(fungicide_application_2) &
+          is.na(fungicide_application_3) ~ "Early",
+       fungicide_timing_1 >= 0 &
+          fungicide_timing_1 < 4 &
+          is.na(fungicide_application_2) &
+          is.na(fungicide_application_3) ~ "Recommended",
+      fungicide_timing_1 >= 4 &
+          is.na(fungicide_application_2) &
+          is.na(fungicide_application_3) ~ "Late",
+      fungicide_timing_1 < 0 &
+          !is.na(fungicide_application_2) ~ "Early_plus",
+       fungicide_timing_1 >= 0 &
+          fungicide_timing_1 < 4 &
+          !is.na(fungicide_application_2) ~ "Recommended_plus",
+      fungicide_timing_1 >= 4 &
+          !is.na(fungicide_application_2) ~ "Late_plus",
+      TRUE ~ NA_character_
+    )
+  )
+
+slim_PM_dat[slim_PM_dat$fungicide_ai == "control",
+            c("fungicide_timing_1", "fungicide_timing_2", "fungicide_timing_3",
+              "spray_management"
+              )] <- "control"
+
+write.csv(slim_PM_dat, file = "data/slim_PM_clusterdat.csv", row.names = FALSE)
+```

### 2019-11-05 04_Prep_data.Rmd
Spray management cluster code correction

@@
 
-slim_PM_dat %>%
+slim_PM_dat <- slim_PM_dat %>%
    mutate(
@@
       fungicide_timing_1 >= 4 &
-          !is.na(fungicide_application_2) ~ "Late_plus",
-      TRUE ~ NA_character_
+          !is.na(fungicide_application_2) ~ "Late_plus"
     )

### 2019-11-05 05_MetaAnalysis.Rmd
Some ME models on the clustered spray management data

@@
 ```{r}
+slim_PM_dat <- read.csv("data/slim_PM_clusterdat.csv")
+slim_PM_dat$spray_management
+
+m4 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) + (factor(spray_management) | trial_ref), data = slim_PM_dat)
+
+m5 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + (factor(spray_management) | trial_ref), data = slim_PM_dat)
+
+anova(m4,m5) # m5 has a much lower AIC and significantly better model
+
+summary(m5)
 

### 2019-11-06 05_MetaAnalysis.Rmd
updated LME models to include spray managment without early_plus or late_plus

--- 2019-11-05 05_MetaAnalysis.Rmd
@@
 ```{r}
+slim_PM_dat <- read.csv("data/slim_PM_clusterdat.csv")
+
+m4 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) + (factor(spray_management) | trial_ref), data = slim_PM_dat)
+
+m5 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + (factor(spray_management) | trial_ref), data = slim_PM_dat) # Model failed to converge
+
+m5.0 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + (1 | trial_ref), data = slim_PM_dat) # Model failed to converge
+
+anova(m4,m5) # m5 has a much lower AIC and significantly better model
+
+anova(m5,m5.0)
+
+summary(m5.0)
 
 ```
+
+```{r LME_cluster_disease_mod}
+m6 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) * PM_final_severity +
+              (factor(spray_management) | trial_ref), 
+           data = slim_PM_dat)
+
+m7 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) * PM_final_severity + 
+              (factor(spray_management) | trial_ref), 
+           data = slim_PM_dat)
+
+anova(m5,m6) # 65 has a lower AIC but not evaluated as a significantly better model
+
+summary(m6)
+
+```
+
+```{r LME_slimer_cluster_disease_mod}
+slimer_PM_dat <- read.csv("data/slimer_PM_clusterdat.csv")
+
+m8 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) +
+              (factor(spray_management) | trial_ref), 
+           data = slimer_PM_dat)
+
+m9 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + 
+              (factor(spray_management) | trial_ref), 
+           data = slimer_PM_dat)
+
+anova(m8,m9) # 65 has a lower AIC but not evaluated as a significantly better model
+
+summary(m9)
+
+```

### 2019-11-06 04_Prep_data.Rmd
Sliming the clusters to ones without low replicates

@@
           !is.na(fungicide_application_2) ~ "Recommended_plus",
-      fungicide_timing_1 >= 4 &
-          !is.na(fungicide_application_2) ~ "Late_plus"
+      fungicide_timing_1 >= 4 ~ "Late_plus",
+      TRUE ~ "Other"
     )
@@
 
+table(slim_PM_dat$spray_management)
+
 write.csv(slim_PM_dat, file = "data/slim_PM_clusterdat.csv", row.names = FALSE)
 ```
+
+```{r simpler_clusters_REMOVE}
+
+slim_PM_dat <- slim_PM_dat %>%
+   mutate(
+    spray_management = case_when(
+       fungicide_timing_1 < 0 &
+          is.na(fungicide_application_2) &
+          is.na(fungicide_application_3) ~ "Early",
+       fungicide_timing_1 >= 0 &
+          fungicide_timing_1 < 4 &
+          is.na(fungicide_application_2) &
+          is.na(fungicide_application_3) ~ "Recommended",
+      fungicide_timing_1 >= 4 &
+          is.na(fungicide_application_2) &
+          is.na(fungicide_application_3) ~ "Late",
+      fungicide_timing_1 < 0 &
+          !is.na(fungicide_application_2) ~ "Early_plus",
+       fungicide_timing_1 >= 0 &
+          fungicide_timing_1 < 4 &
+          !is.na(fungicide_application_2) ~ "Recommended_plus",
+      fungicide_timing_1 >= 4 ~ "Late_plus",
+      TRUE ~ "Other"
+    )
+  )
+
+slim_PM_dat[slim_PM_dat$fungicide_ai == "control",
+            c("fungicide_timing_1", "fungicide_timing_2", "fungicide_timing_3",
+              "spray_management"
+              )] <- "control"
+
+table(slim_PM_dat$spray_management)
+
+# Remove "Early_plus" and "Late" due to lack of replicates
+
+slimer_PM_dat <- slim_PM_dat[slim_PM_dat$spray_management != "Late" & 
+               slim_PM_dat$spray_management != "Early_plus",]
+
+write.csv(slimer_PM_dat, file = "data/slimer_PM_clusterdat.csv", row.names = FALSE)
+```

### 2019-11-07 05_MetaAnalysis.Rmd
Plotting model

@@
 
-anova(m8,m9) # 65 has a lower AIC but not evaluated as a significantly better model
+anova(m8,m9) # m9 is significantly better model
 
 summary(m9)
+# m9_summary <- as.data.frame(coef(summary(m9)))
+# m9_summary[1,1] <- 0
+# m9_summary$treats <- row.names(m9_summary)
+# 
+# class(m9_summary)
+# 
+# 
+# m9_summary %>%
+#    ggplot(aes(x = treats, y = exp(Estimate)))+
+#    geom_point()+
+#    geom_linerange(ymin = exp(m9_summary[,1] - m9_summary[,2]),
+#                   ymax = exp(m9_summary[,1] + m9_summary[,2]))+
+#    geom_hline(yintercept = m9_summary[1,1])+
+#    geom_rect(ymin = exp(m9_summary[1,1] - m9_summary[1,2]),
+#              ymax = exp(m9_summary[1,1] + m9_summary[1,2]),
+#              xmin = -Inf, xmax = -Inf,
+#              fill = "red", alpha = 0.5)+
+#    coord_flip()
+# 
+#
 

### 2019-11-07 05_MetaAnalysis.Rmd
attempting rma.mv analysis

--- 2019-11-06 05_MetaAnalysis.Rmd
@@
 
-anova(m8,m9) # 65 has a lower AIC but not evaluated as a significantly better model
+m10 <- lmer(log(grain_yield.t.ha*1000) ~ (factor(spray_management) | trial_ref), 
+           data = slimer_PM_dat)
+
+anova(m8,m9) # m9 is significantly better model
+anova(m9,m10) # m9 is significantly better model
 
@@
 ```
+
+```{r}
+library(metafor)
+
+slimer_PM_dat <- slimer_PM_dat[!is.na(slimer_PM_dat$yield_error),]
+slimer_PM_dat$yi <- log(slimer_PM_dat$grain_yield.t.ha*1000)
+slimer_PM_dat$spray_management
+
+PM_mv_AI <- rma.mv(yi,yield_error,
+                   mods = spray_management,
+                   method = "ML",
+                   random = list(~ spray_management | trial_ref),
+                   struct = "UN",
+                   data = slimer_PM_dat)
+
+PM_mv_AI
+
+anova(PM_mv_AI, L = rbind(c(0,1,-1,0,0), 
+                          c(0,0,-1,1,0),
+                          c(0,0,-1,0,1),
+                          c(0,0,0,-1,1)))
+
+```

### 2019-11-07 R/slimming_PM_dat.R
Adding replicates to the slim datasets

@@ -13,6 +13,7 @@ slim_PM_dat <- data.frame(
    year = as.integer(PM_MB_means$year),
    location = as.character(PM_MB_means$location),
    row_spacing = as.double(PM_MB_means$row_spacing),
+   n = as.integer(PM_MB_means$replicates),
    first_sign_disease = as.Date(PM_MB_means$first_sign_disease, format = "%Y-%m-%d"),
    fungicide_ai = as.character(PM_MB_means$fungicide_ai),
    fungicide_application_1 = as.Date(PM_MB_means$fungicide_application_1, format = "%Y-%m-%d"),

### 2019-11-11 04_Prep_data.Rmd
Adding replicates to the slim datasets
Impute missing yield variances, correct slimmer spelling from slimer

@@
 table(slim_PM_dat$spray_management)
+sum(table(slim_PM_dat$spray_management)[1:7])
+nrow(slim_PM_dat)
 
@@
 
-slimer_PM_dat <- slim_PM_dat[slim_PM_dat$spray_management != "Late" & 
+slimmer_PM_dat <- slim_PM_dat[slim_PM_dat$spray_management != "Late" & 
                slim_PM_dat$spray_management != "Early_plus",]
 
-write.csv(slimer_PM_dat, file = "data/slimer_PM_clusterdat.csv", row.names = FALSE)
+write.csv(slimmer_PM_dat, file = "data/slimmer_PM_clusterdat.csv", row.names = FALSE)
 ```

### 2019-11-11 05_MetaAnalysis.Rmd
Impute missing yield variances, correct slimmer spelling from slimer

--- 2019-11-06 05_MetaAnalysis.Rmd
@@
 
-```{r LME_slimer_cluster_disease_mod}
-slimer_PM_dat <- read.csv("data/slimer_PM_clusterdat.csv")
+```{r LME_slimmer_cluster_disease_mod}
+slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
 
@@
               (factor(spray_management) | trial_ref), 
-           data = slimer_PM_dat)
+           data = slimmer_PM_dat)
 
@@
               (factor(spray_management) | trial_ref), 
-           data = slimer_PM_dat)
+           data = slimmer_PM_dat)
 
-anova(m8,m9) # 65 has a lower AIC but not evaluated as a significantly better model
+m10 <- lmer(log(grain_yield.t.ha*1000) ~ (factor(spray_management) | trial_ref), 
+           data = slimmer_PM_dat)
+
+anova(m8,m9) # m9 is significantly better model
+anova(m9,m10) # m9 is significantly better model
 
@@
 ```
+
+```{r}
+library(metafor)
+sum(is.na(slimmer_PM_dat$yield_error)) # 14 treatments have no error
+sum(!is.na(slimmer_PM_dat$yield_error)) # 152 treatments with error
+
+hist(slimmer_PM_dat$yield_error) # yield error is not normally distributed
+hist(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is normally distributed
+
+# generate yield error values
+log_Yerror <- rnorm(14, mean = mean(log(slimmer_PM_dat$yield_error), na.rm = TRUE),
+                    sd = sd(log(slimmer_PM_dat$yield_error), na.rm = TRUE))
+
+# Lets plot the values to see if they are significantly different
+# First lets convert Variance to standard error for all the variables that have variance recorded
+slimmer_PM_dat$yield_SE <- sqrt(slimmer_PM_dat$yield_error)/sqrt(slimmer_PM_dat$n)
+
+# Second; adding the imputed standard errors
+slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"] <- sqrt(exp(log_Yerror))/sqrt(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"n"]) # 14 treatments have no error
+
+# Plot the imputed errors for each trial
+slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),] %>%
+   ggplot(aes(y = grain_yield.t.ha, trial))+
+   #geom_point()+
+   geom_pointrange(ymin = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] - (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+                  ymax = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] + (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+                  position = "jitter"
+                 )+
+   ylim(0.2,1.5)
+
+# all errorbars shoul overlap so they are consistant with the meta-data describing no significant difference bettween treatments
+# lets test to make sure
+if(max(outer(X = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] - (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+             Y = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] + (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+             FUN = "-")) > 0){
+   message("\nWarning!!: Imputed yield errors show significant differences when they should not, rerun chunk")
+}else{
+                message("\nImputed variances show no significant distances :)\n Now adding variances to data")
+   slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_error"] <- exp(log_Yerror)
+       }
+
+slimmer_PM_dat$yield_error
+
+slimmer_PM_dat$yi <- log(slimmer_PM_dat$grain_yield.t.ha*1000)
+slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management)
+
+table(slimmer_PM_dat$spray_management)
+
+PM_mv_AI <- rma.mv(yi,log(yield_error*1000),
+ #                  mods = spray_management,
+                   method = "ML",
+                   random = list(~ spray_management | trial_ref),
+                   struct = "UN",
+                   data = slimmer_PM_dat)
+
+PM_mv_AI
+
+anova(PM_mv_AI, L = rbind(c(0,1,-1,0,0), 
+                          c(0,0,-1,1,0),
+                          c(0,0,-1,0,1),
+                          c(0,0,0,-1,1)))
+
+There are outcomes with non-positive sampling variances.Negative sampling variances constrained to zero.'V' appears to be not positive definite.Some combinations of the levels of the inner factor never occurred.
+Corresponding rho value(s) fixed to 0.diag(.) had 0 or NA entries; non-finite result is doubtfulError in .ll.rma.mv(opt.res$par, reml = reml, Y = Y, M = V, A = A, X.fit = X,  :
+  Final variance-covariance matrix not positive definite.
+
+There are outcomes with non-positive sampling variances.Negative sampling variances constrained to zero.'V' appears to be not positive definite.Some combinations of the levels of the inner factor never occurred.
+Corresponding rho value(s) fixed to 0.diag(.) had 0 or NA entries; non-finite result is doubtfulError in .ll.rma.mv(opt.res$par, reml = reml, Y = Y, M = V, A = A, X.fit = X,  :
+  Final variance-covariance matrix not positive definite.
+```

### 2019-11-12 04_Prep_data.Rmd
Added trial variance

@@
 ```
+
+```{r Trial_variance}
+
+slimmer_PM_dat$SSquare <- 
+   slimmer_PM_dat$yield_error * (slimmer_PM_dat$n - 1)
+
+slimmer_PM_dat$pop_var <- NA
+
+for(i in unique(slimmer_PM_dat$trial)){
+   pop_var <- sqrt(
+      sum(slimmer_PM_dat[slimmer_PM_dat$trial == i,"SSquare"])/
+         sum(slimmer_PM_dat[slimmer_PM_dat$trial == i,"n"])
+      )
+
+slimmer_PM_dat[slimmer_PM_dat$trial == i, "pop_var"] <- pop_var
+
+}
+
+write.csv(slimmer_PM_dat, file = "data/slimmer_PM_clusterdat.csv", row.names = FALSE)
+
+```

### 2019-11-12 03_Preliminary_analysis.Rmd
tiny changes to spelling, load libraries, etc

@@
 library(tidyverse)
+library(bomrang)
 library(openxlsx)
@@
 
-   9) irrigated vs non-irrigated trials
+   9) Irrigated vs non-irrigated trials
 
@@
 
-   12) Two pathogen species cause PM (new discovery)
+   12) Two pathogen species cause PM (new discovery in 2018)
 

### 2019-11-13 03_Preliminary_analysis.Rmd
Updates, remove meta on log values

--- 2019-11-04 03_Preliminary_analysis.Rmd
@@
 
-summary(lm(rainfall_sum ~ grain_yield, 
-                             data = rain_dat_sum[rain_dat_sum$location != "Hermitage",]))
+rain_lm <- lm(rainfall_sum ~ grain_yield, 
+                             data = rain_dat_sum[rain_dat_sum$location != "Hermitage",])
+
+summary(rain_lm)
 
@@
    geom_abline(intercept = -167.98, slope = 284.44, colour = "red")
+
+resid_rain_lm <- residuals(rain_lm)
 
@@
 ```
+
+We need to also define the relationship between yield loss and disease severity. When exploring this data we should look primarily at the no spray control plots
+
+```{r yield_x_PMseverity}
+
+PM_MB_means %>%
+   filter(fungicide == "control") %>%
+   ggplot(aes(x = PM_final_severity, y = grain_yield.t.ha.)) +
+   geom_point()+
+   geom_smooth(method = "lm")
+
+PM_MB_means %>%
+   ggplot(aes(x = PM_final_severity, y = prop_YG)) +
+   geom_point()+
+   geom_smooth(method = "lm")
+
+```

### 2019-11-13 04_Prep_data.Rmd
tiny changes to spelling, load libraries, etc
Updates, remove meta on log values

--- 2019-11-11 04_Prep_data.Rmd
@@
 write.csv(slim_PM_dat, file = "data/slim_PM_clusterdat.csv", row.names = FALSE)
+
+slim_PM_dat[slim_PM_dat$spray_management == "Late_plus",]
 ```
@@
 
+#slimmer_PM_dat <- slim_PM_dat[slim_PM_dat$spray_management != "Late",]
+
 write.csv(slimmer_PM_dat, file = "data/slimmer_PM_clusterdat.csv", row.names = FALSE)

### 2019-11-13 05_MetaAnalysis.Rmd
Updates, remove meta on log values

--- 2019-11-07 05_MetaAnalysis.Rmd
@@
 
-```{r LME_slimer_cluster_disease_mod}
-slimer_PM_dat <- read.csv("data/slimer_PM_clusterdat.csv")
+```{r LME_slimmer_cluster_disease_mod}
+library(lme4)
+slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
 
@@
               (factor(spray_management) | trial_ref), 
-           data = slimer_PM_dat)
+           data = slimmer_PM_dat)
 
 m10 <- lmer(log(grain_yield.t.ha*1000) ~ (factor(spray_management) | trial_ref), 
-           data = slimer_PM_dat)
+           data = slimmer_PM_dat)
 
@@
 
-```{r}
+We need to impute the variances
+
+```{r imputing_variances}
+
+table(slimmer_PM_dat$spray_management)
+
+sum(is.na(slimmer_PM_dat$yield_error)) # 14 treatments have no error
+sum(!is.na(slimmer_PM_dat$yield_error)) # 152 treatments with error
+
+hist(slimmer_PM_dat$yield_error) # yield error is not normally distributed
+hist(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is normally distributed
+
+# generate yield error values
+again <- 0
+for(i in seq(from = again, to = 500, by = 0.1)){
+if(i == 0){log_Yerror <- vector()}
+
+   x1 <- rnorm(1, mean = mean(log(slimmer_PM_dat$yield_error), na.rm = TRUE), #+ i,
+                  sd = sd(log(slimmer_PM_dat$yield_error), na.rm = TRUE)) 
+   if(x1 <= -7){again <- i
+      next()}
+   log_Yerror <- c(log_Yerror,x1)
+
+   if(length(log_Yerror) < 14){again <- i
+      next()}
+
+   if(length(log_Yerror) > 14){ stop(message("length of log_Yerror exceeded 14"))}
+
+# Lets plot the values to see if they are significantly different
+# First lets convert Variance to standard error for all the variables that have variance recorded
+slimmer_PM_dat$yield_SE <- sqrt(slimmer_PM_dat$yield_error)/sqrt(slimmer_PM_dat$n)
+
+# Second; adding the imputed standard errors
+slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"] <- sqrt(exp(log_Yerror))/sqrt(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"n"]) # 14 treatments have no error
+
+# all errorbars shoul overlap so they are consistant with the meta-data describing no significant difference bettween treatments
+# lets test to make sure
+if(max(outer(X = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] - (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+             Y = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] + (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+             FUN = "-")) > 0){
+   message(paste("\nWarning!!: Imputed yield errors show significant differences when they should not, rerun chunk", "i =",i))
+   log_Yerror <- vector()
+   next()
+}else{
+                message(paste(#"\nA value of",i,"was added to the mean distribution from which imputed erorrs were sampled. This led to 
+                   "imputed variances now show no significant distances :)\n Now adding variances to data"))
+   slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_error"] <- exp(log_Yerror)
+       break()}
+}
+
+# # Plot the imputed errors for each trial
+# slimmer_PM_dat[is.na(slimmer_PM_dat$),] %>%
+#    ggplot(aes(y = grain_yield.t.ha, trial))+
+#    #geom_point()+
+#    geom_pointrange(ymin = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] - (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+#                   ymax = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] + (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+#                   position = "jitter"
+#                  )+
+#    ylim(0.2,1.5)
+#
+
+```
+
+```{r meta_1}
 library(metafor)
 
-slimer_PM_dat <- slimer_PM_dat[!is.na(slimer_PM_dat$yield_error),]
-slimer_PM_dat$yi <- log(slimer_PM_dat$grain_yield.t.ha*1000)
-slimer_PM_dat$spray_management
+slimmer_PM_dat$yi <- slimmer_PM_dat$grain_yield.t.ha
+slimmer_PM_dat$vi <- slimmer_PM_dat$yield_error
 
-PM_mv_AI <- rma.mv(yi,yield_error,
-                   mods = spray_management,
+slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management)
+table(slimmer_PM_dat$spray_management)
+
+PM_mv_AI <- rma.mv(yi,vi,
+#                   mods = spray_management,
                    method = "ML",
-                   random = list(~ spray_management | trial_ref),
+                   random = ~ spray_management | trial,
                    struct = "UN",
-                   data = slimer_PM_dat)
+                   data = slimmer_PM_dat)
 
-PM_mv_AI
+summary(PM_mv_AI)
 
@@
 ```
+
+```{r meta_2}
+# Using trial instead of trial_ref
+
+head(slimmer_PM_dat)
+
+slimmer_PM_dat$yi <- log(slimmer_PM_dat$grain_yield.t.ha)
+slimmer_PM_dat$vi <- log(slimmer_PM_dat$pop_var)
+slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management)
+
+table(slimmer_PM_dat$spray_management)
+
+PM_mv_AI <- rma.mv(yi,vi,
+#                   mods = spray_management,
+                   method = "ML",
+                   random = list(~ spray_management | trial),
+                   struct = "UN",
+                   data = slimmer_PM_dat2)
+
+summary(PM_mv_AI)
+
+```
+
+```{r inspect_for_outliers}
+head(slimmer_PM_dat)
+
+slimmer_PM_dat %>%
+#   filter(spray_management == "Late_plus") %>%
+   ggplot(aes(prop_yield_gain, fill = spray_management))+
+   geom_histogram(alpha = 0.5)
+
+slimmer_PM_dat %>%
+   filter(spray_management == "Late_plus") %>%
+   ggplot(aes(prop_yield_gain, fill = trial_ref))+
+   geom_histogram(alpha = 0.5)
+
+slimmer_PM_dat %>%
+   filter(spray_management == "Recommended") %>%
+   ggplot(aes(prop_yield_gain, fill = trial_ref))+
+   geom_histogram(alpha = 0.5)
+
+```

### 2019-11-13 R/slimming_PM_dat.R
Commit back old code

@@ -28,10 +28,27 @@ slim_PM_dat <- data.frame(
    PM_final_severity_error = as.double(PM_MB_means$disease_error)
 )
 
+
+for(i in levels(slim_PM_dat$trial_ref)){
+   if(i == levels(slim_PM_dat$trial_ref)[1]){
+      rows_to_delete <- vector()
+   }
+   
+   if(any(slim_PM_dat[slim_PM_dat$trial_ref == i,"fungicide_ai"] == "tebuconazole" |
+          slim_PM_dat[slim_PM_dat$trial_ref == i,"fungicide_ai"] == "propiconazole")){
+      next()
+   }else
+      rows_to_delete <- c(rows_to_delete, which(slim_PM_dat$trial_ref == i))
+}
+
+slim_PM_dat <- slim_PM_dat[-rows_to_delete,]
+
+
 slim_PM_dat <- slim_PM_dat[slim_PM_dat$fungicide_ai == "control" |
                               slim_PM_dat$fungicide_ai == "tebuconazole" |
                               slim_PM_dat$fungicide_ai == "propiconazole" ,
                            ]
+
 
 
 write.csv(slim_PM_dat, file = "data/slim_PM_dat.csv", row.names = FALSE)

### 2019-11-13 02_Weather.Rmd

@@
 ```{r import_libraries_&_data}
+library(ggplot2)
 source("R/import_data.R")

### 2019-11-13 05_MetaAnalysis.Rmd
Mods in or out? hmmm
clean up imputing code

--- 2019-11-07 05_MetaAnalysis.Rmd
@@
 
-m5 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + (factor(spray_management) | trial_ref), data = slim_PM_dat) # Model failed to converge
+m5 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + (factor(spray_management) | trial_ref), data = slim_PM_dat)
 
@@
 
-```{r}
+We need to impute the variances which are missing for a few of the trials.
+These trials `r paste(unique(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),c("location","year", "trial_ref")])` were analysed and reported that there was no significant difference between the treatments in each trial.
+So therefore we need the imputed variances not to show a significant difference.
+
+There are `r sum(is.na(slimmer_PM_dat$yield_error))` treatments without yield error in our data, and `r sum(!is.na(slimmer_PM_dat$yield_error))` where yield error was recorded.
+
+Plotting a histogram of the variances show that the yield is not normally distributed.
+A log transformation, however, shows a normal disrtubution.
+We can use the mean and standard deviation of the log(V) to sample variances for the treatments where V is mission.
+
+We will evaluate wheather the imputed variances confer a significant difference to the recorded means.
+I created a distance matrix of two standard errors above the mean against two standard errors below the mean.
+If any errors don't overlap, infering signicifant difference, the imputed variances are discarded and resampled until all treatment variances show no significant differences.
+
+```{r imputing_variances}
+
+hist(slimmer_PM_dat$yield_error) # yield error is not normally distributed
+hist(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is normally distributed
+
+# generate yield error values
+for(i in 0:500){
+
+   # Imputing missing log variances
+   log_Yerror <- rnorm(n = sum(is.na(slimmer_PM_dat$yield_error)),
+               mean = mean(log(slimmer_PM_dat$yield_error), na.rm = TRUE),
+               sd = sd(log(slimmer_PM_dat$yield_error), na.rm = TRUE))
+
+   # First lets convert Variance to standard error for all the variables that have variance recorded
+   slimmer_PM_dat$yield_SE <- 
+      sqrt(slimmer_PM_dat$yield_error)/sqrt(slimmer_PM_dat$n)
+
+   # Second; adding the imputed standard errors
+   slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"] <-
+      sqrt(exp(log_Yerror))/sqrt(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"n"])
+
+# all errorbars should overlap so they are consistant with the meta-data describing no significant difference bettween treatments
+# lets test to make sure
+if(
+   max(outer(X = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] -
+               (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+             Y = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] +
+               (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+             FUN = "-")
+       ) > 0){
+
+   message(paste("\nWarning!!: Imputed yield errors show significant differences when they should not, rerun chunk", "i =",i))
+   next()
+   }else{
+      message(paste(i,"iterations: ", "imputed variances now show no significant distances :)\n Now adding variances to data "))
+
+      # Plot the imputed errors for each trial
+      Vplot <- slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),] %>%
+         ggplot(aes(y = grain_yield.t.ha, trial))+
+         #geom_point()+
+         geom_pointrange(ymin = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] -
+                            (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+                         ymax = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] +
+                            (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+                         position = "jitter"
+                         )+
+         ylim(0.2,1.5)
+
+      slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_error"] <- exp(log_Yerror)
+      print(Vplot)
+      break()}
+}
+
+```
+
+```{r meta_1}
 library(metafor)
 
-slimer_PM_dat <- slimer_PM_dat[!is.na(slimer_PM_dat$yield_error),]
-slimer_PM_dat$yi <- log(slimer_PM_dat$grain_yield.t.ha*1000)
-slimer_PM_dat$spray_management
+slimmer_PM_dat$yi <- slimmer_PM_dat$grain_yield.t.ha
+slimmer_PM_dat$vi <- slimmer_PM_dat$yield_error
 
-PM_mv_AI <- rma.mv(yi,yield_error,
-                   mods = spray_management,
-                   method = "ML",
-                   random = list(~ spray_management | trial_ref),
+slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management)
+table(slimmer_PM_dat$spray_management)
+
+PM_mv_AI <- rma.mv(yi,vi,
+                   mods = ~ spray_management,
+#                   method = "ML",
+                   random = list(~ spray_management | trial),
                    struct = "UN",
-                   data = slimer_PM_dat)
+                   data = slimmer_PM_dat)
 
-PM_mv_AI
-
-anova(PM_mv_AI, L = rbind(c(0,1,-1,0,0), 
-                          c(0,0,-1,1,0),
-                          c(0,0,-1,0,1),
-                          c(0,0,0,-1,1)))
+summary(PM_mv_AI)
 
 ```
+
+```{r inspect_for_outliers}
+head(slimmer_PM_dat)
+
+slimmer_PM_dat %>%
+#   filter(spray_management == "Late_plus") %>%
+   ggplot(aes(prop_yield_gain, fill = spray_management))+
+   geom_histogram(alpha = 0.5)
+
+slimmer_PM_dat %>%
+   filter(spray_management == "Late_plus") %>%
+   ggplot(aes(prop_yield_gain, fill = trial_ref))+
+   geom_histogram(alpha = 0.5)
+
+slimmer_PM_dat %>%
+   filter(spray_management == "Recommended") %>%
+   ggplot(aes(prop_yield_gain, fill = trial_ref))+
+   geom_histogram(alpha = 0.5)
+
+```

### 2019-11-17 R/import_data.R
Updating fungicide to fungicide_ai

@@ -19,7 +19,7 @@ import_data <- function() {
    x$trial_ref <- as.factor(x$trial_ref)
    x$location <- as.factor(x$location)
    x$host_genotype <- as.factor(x$host_genotype)
-   x$fungicide_ai <- as.factor(x$fungicide)
+   x$fungicide_ai <- as.factor(x$fungicide_ai)
    x$trade_name <- as.factor(x$trade_name)
    x$year <- as.factor(x$year)
    x$replicates <- as.numeric(x$replicates)

### 2019-11-17 R/Cleaning historical data.R
Updating file paths

@@ -1,15 +1,7 @@
 # This script is dedicated to
 # importing and cleaning previous powdery mildew experimental field trial data.
 
-# install.packages("openxlsx")
-# install.packages("readxl")
-# install.packages("tidyr")
 
-library(openxlsx)
-library(readxl)
-library(tidyr)
-library(dplyr)
-library(data.table)
 
 # Year #  Trial location  #  Sowing date
 
@@ -17,14 +9,21 @@ library(data.table)
 # _____________            Hermitage  2010        ____________
 
 Herm_10 <-
-   read_xls(
-      "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/Past Trials/2010/2010 PMmung Herm/2010 PMmung hermitage RAW field book.xls",
+   as.data.frame(read_xls(
+      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2010/2010 PMmung Herm/2010 PMmung hermitage RAW field book.xls",
       sheet = "For analysis"
-   )
+   ), stringsAsFactors == FALSE)
+
+Herm_10[1:20,]
+
+
 
 Herm_10_m <- Herm_10 %>%
    group_by(`Cultivar!`, `Treat!`, `Description!`) %>%
    summarise_all(list(~ mean(., na.rm = TRUE),  ~ sd(., na.rm = TRUE)))
+
+head(Herm_10_m)
+colnames((Herm_10_m))
 
 write.csv(
    as.data.frame(Herm_10_m),

### 2019-11-17 191115_PMMB_DataWrangling_PM.Rmd
Initialising Cleaning histortical data script into markdown file

# Data wrangling

## Import Libraries
```{r}
# install.packages("openxlsx")
# install.packages("readxl")
# install.packages("tidyr")
install.packages("agricolae")

library(openxlsx)
library(readxl)
library(tidyr)
library(dplyr)
library(data.table)
library(agricolae)

source("R/import_data.R")
PM_MB_means <- import_data()

```

## Functions
```{r functions}

fold_data <- function(new_DataFrame, template_DataFrame){
   for(i in colnames(new_DataFrame)){
      if(i == colnames(new_DataFrame)[1]){
         x1 <- vector()}

      cnames1 <- as.character(colnames(new_DataFrame))
      cnames2 <- as.character(colnames(template_DataFrame))

      x1 <- c(x1,match(i, cnames2, nomatch = NA)) # MAke a index vector for the location of new_DataFrame col names in template_DataFrame
   }

   new_DataFrame[cnames2[!(cnames2 %in% cnames1)]] <- NA # adding column names to new_DataFrame not in template_DataFrame
   new_DataFrame <- 
      new_DataFrame[,c(cnames2, cnames1[is.na(x1)])]  # adding column names to new_DataFrame not in template_DataFrame
   return(new_DataFrame)
}
```

## Data wrangling for each trial
### Hermitage 2010

```{r Hermitage_2010}

Herm_10 <-
   as.data.frame(read_xls(
      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2010/2010 PMmung Herm/2010 PMmung hermitage RAW field book.xls",
      sheet = "For analysis"
   ), stringsAsFactors == FALSE)

Herm_10 <- Herm_10 %>%
   mutate(trade_name = case_when(`Schedule!` == "U/S" ~ NA_character_,
                                 `Schedule!` == "FirstsignC" ~ " ",
                                 TRUE ~ "Kendon"))%>%
   mutate(fungicide = case_when(`Schedule!` == "U/S" ~ "control",
                                 `Schedule!` == "FirstsignC" ~ "carbendazim",
                                 TRUE ~ "sulphur"))%>%
   mutate(dose_ai.ha = case_when(`Schedule!` == "U/S" ~ 0,
                                 `Schedule!` == "FirstsignC" ~ 250,
                                 TRUE ~ 2400))%>%
   mutate(fungicide_application_1 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-02-19", format = "%Y-%m-%d"),
                                              `Schedule!` == "Early Sp" ~ as.Date("2010-02-19", format = "%Y-%m-%d"),
                                              `Schedule!` == "FirstsignC" ~ as.Date("2010-03-18", format = "%Y-%m-%d"),
                                              `Schedule!` == "FirstsignS" ~ as.Date("2010-03-18", format = "%Y-%m-%d"),
                                              `Schedule!` == "U/S" ~ as.Date(NA),
                                              TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_2 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-02-26", format = "%Y-%m-%d"),
                                              `Schedule!` == "Early Sp" ~ as.Date("2010-02-26", format = "%Y-%m-%d"),
                                              TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_3 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-03-05", format = "%Y-%m-%d"),
                                              TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_4 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-03-11", format = "%Y-%m-%d"),
                                              TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_5 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-03-18", format = "%Y-%m-%d"),
                                              TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_6 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-03-25", format = "%Y-%m-%d"),
                                              TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_7 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-03-07", format = "%Y-%m-%d"),
                                              TRUE ~ as.Date(NA)))%>%
   mutate(total_fungicide = case_when(`Schedule!` == "Full Sp" ~ 7,
                                      `Schedule!` == "Early Sp" ~ 2,
                                      `Schedule!` == "FirstsignC" ~ 1,
                                      `Schedule!` == "FirstsignS" ~ 1,
                                      `Schedule!` == "U/S" ~ 0,
                                      TRUE ~ 9999))

Herm_10_dat <- 
   data.frame(trial_ref = "mung0910/01",
              year = "2010",
              location = "Hermitage",
              host_genotype = Herm_10$`Cultivar!`,
              trial_design = "RB",
              plot_length = Herm_10$`Length (m)`,
              plot_width = 4,
              plant_density = NA,
              row_spacing = 0.25,
              replicate = Herm_10$`Rep!`,
              planting_date = as.Date("2010-01-22"),
              emergence_date = NA,
              flowering_date = NA,
              pod_fill_date = NA,
              mid_late_pod_fill = NA,
              first_sign_disease = as.Date("2010-03-18"),
              trade_name = Herm_10$trade_name,
              fungicide_ai = Herm_10$fungicide,
              dose_ai.ha = Herm_10$dose_ai.ha,
              n_treatment = Herm_10$`Treat!`,
              fungicide_application_1 = Herm_10$fungicide_application_1,
              fungicide_application_2 = Herm_10$fungicide_application_2,
              fungicide_application_3 = Herm_10$fungicide_application_3,
              fungicide_application_4 = Herm_10$fungicide_application_4,
              fungicide_application_5 = Herm_10$fungicide_application_5,
              fungicide_application_6 = Herm_10$fungicide_application_6,
              fungicide_application_7 = Herm_10$fungicide_application_7,
              total_fungicide = Herm_10$total_fungicide,
              harvest_date = as.Date("2010-05-14"),
              final_assessment = as.Date("2010-04-20"),
              PM_final_severity = Herm_10$P.M.13wap,
              rating_scale = "1-9",
              grain_yield.t.ha. = Herm_10$`Kg/ha`,
              AUDPC = apply(Herm_10[,c("P.M.9wap","P.M.11wap","P.M.13wap")],1, FUN = audpc, dates = c(9*7,11*7,13*7)),
              stringsAsFactors = FALSE
              )

Herm_10_m <- Herm_10_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = sum(replicate),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = NA,
              pod_fill_date = NA,
              mid_late_pod_fill = NA,
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              fungicide_application_4 = unique(fungicide_application_4),
              fungicide_application_5 = unique(fungicide_application_5),
             fungicide_application_6 = unique(fungicide_application_6),
             fungicide_application_6 = unique(fungicide_application_7),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE),
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
              AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
              meanSq = anova(lm(grain_yield.t.ha. ~ host_genotype + factor(n_treatment), data = Herm_10_dat))[2,3]
   )

Herm_10_m <- fold_data(Herm_10_m, PM_MB_means)

write.csv(
   as.data.frame(Herm_10_m),
   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2010/2010 PMmung Herm/2010 PMmung Hermitage means.csv"
)

```

### Hermitage 2011
```{r Herm_2011}

Herm_11 <-
   as.data.frame(read_xls(
      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2011/2011 PMmung Herm/pmhermratings2011.xls",
      sheet = "Analyses factor"
   ), stringsAsFactors = FALSE)

Herm_11 <- Herm_11 %>%
   mutate(trade_name = 
             case_when(`Treatment!` == "1 spray AMI-X" ~ "Amistar Xtra",
                       `Treatment!` == "3 spray AMI-X" ~ "Amistar Xtra",
                       `Treatment!` == "1 spray SULPHUR" ~ "Kendon",
                       `Treatment!` == "3 spray SULPHUR" ~ "Kendon",
                       `Treatment!` == "1 spray FOLICUR" ~ "Folicur",
                       TRUE ~ "control"))%>%
   mutate(fungicide_ai = 
             case_when(`Treatment!` == "1 spray AMI-X" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
                       `Treatment!` == "3 spray AMI-X" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
                       `Treatment!` == "1 spray SULPHUR" ~ "sulphur",
                       `Treatment!` == "3 spray SULPHUR" ~ "sulphur",
                       `Treatment!` == "1 spray FOLICUR" ~ "tebuconazole",
                       TRUE ~ "control"))%>%
   mutate(dose_ai.ha = 
             case_when(`Treatment!` == "1 spray AMI-X" ~ 120,
                       `Treatment!` == "3 spray AMI-X" ~ 120,
                       `Treatment!` == "1 spray SULPHUR" ~ 3000,
                       `Treatment!` == "3 spray SULPHUR" ~ 3000,
                       `Treatment!` == "1 spray FOLICUR" ~ 62.35,
                       TRUE ~ 0))%>%
   mutate(fungicide_application_1 = 
             case_when(`Treatment!` == "1 spray AMI-X" ~ as.Date("2011-03-28", format = "%Y-%m-%d"),
                       `Treatment!` == "3 spray AMI-X" ~ as.Date("2011-02-28", format = "%Y-%m-%d"),
                       `Treatment!` == "1 spray SULPHUR" ~ as.Date("2011-03-28", format = "%Y-%m-%d"),
                       `Treatment!` == "3 spray SULPHUR" ~ as.Date("2011-02-28", format = "%Y-%m-%d"),
                       `Treatment!` == "1 spray FOLICUR" ~ as.Date("2011-03-28", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_2 = 
             case_when(`Treatment!` == "3 spray AMI-X" ~ as.Date("2011-03-14", format = "%Y-%m-%d"),
                       `Treatment!` == "3 spray SULPHUR" ~ as.Date("2011-03-14", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_3 = 
             case_when(`Treatment!` == "3 spray AMI-X" ~ as.Date("2011-03-14", format = "%Y-%m-%d"),
                       `Treatment!` == "3 spray SULPHUR" ~ as.Date("2011-03-14", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(total_fungicide = 
             case_when(`Treatment!` == "1 spray AMI-X" ~ 1,
                       `Treatment!` == "3 spray AMI-X" ~ 3,
                       `Treatment!` == "1 spray SULPHUR" ~ 1,
                       `Treatment!` == "3 spray SULPHUR" ~ 3,
                       `Treatment!` == "1 spray FOLICUR" ~ 1,
                       TRUE ~ 0))

Herm_11_dat <- 
   data.frame(trial_ref = "mung1011/01",
              year = "2011",
              location = "Hermitage",
              host_genotype = Herm_11$`Cultivar!`,
              trial_design = "RCB",
              plot_length = 11,
              plot_width = 4,
              plant_density = NA,
              row_spacing = 0.75,
              replicate = Herm_11$`Rep!`,
              planting_date = as.Date("2011-01-24", format = "%Y-%m-%d"),
              emergence_date = NA,
              flowering_date = as.Date("2011-03-22", format = "%Y-%m-%d"),
              pod_fill_date = NA,
              mid_late_pod_fill = NA,
              first_sign_disease = as.Date("2011-03-28", format = "%Y-%m-%d"),
              trade_name = as.factor(Herm_11$trade_name),
              fungicide_ai = Herm_11$fungicide_ai,
              dose_ai.ha = Herm_11$dose_ai.ha,
              n_treatment = Herm_11$Tr,
              fungicide_application_1 = Herm_11$fungicide_application_1,
              fungicide_application_2 = Herm_11$fungicide_application_2,
              fungicide_application_3 = Herm_11$fungicide_application_3,
              total_fungicide = Herm_11$total_fungicide,
              harvest_date = as.Date("2011-04-25", format = "%Y-%m-%d"),
              final_assessment = as.Date("2010-04-11", format = "%Y-%m-%d"),
              PM_final_severity = Herm_11$`P.M. 11  w.a.p.`,
              rating_scale = "1-9",
              grain_yield.t.ha. = Herm_11$`Yld Kg/ha`
              )

Herm_11_m <- Herm_11_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = sum(replicate),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = NA,
              mid_late_pod_fill = NA,
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE),
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
              meanSq = anova(lm(grain_yield.t.ha. ~ host_genotype + factor(n_treatment), data = Herm_11_dat))[2,3]
   )

Herm_11_m <- fold_data(Herm_11_m, PM_MB_means)

write.csv(
   as.data.frame(Herm_11_m),
   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2011/2011 PMmung Herm/2011 PMmung Herm means.csv"
)

```

### Kingaroy 2011
```{r King_11}
King_11 <-
   as.data.frame(read_xls(
      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2011/2011 PMmung King/pmKing ratings2011.xls",
      sheet = "analyses"
   ), stringsAsFactors = FALSE)

tmp1 <- do.call(rbind.data.frame, strsplit(King_11$`Treatment!`, " "))
colnames(tmp1) <- c("cultivar" , "spray_n", "spray", "fungicide")
King_11 <- cbind(tmp1, King_11)

King_11 <- King_11 %>%
   mutate(trade_name = 
             case_when(fungicide == "AMIS-X" ~ "Amistar Xtra",
                       fungicide == "SULPHUR" ~ "Kendon",
                       fungicide == "FOLICUR" ~ "Folicur",
                       TRUE ~ "control"))%>%
   mutate(fungicide_ai = 
             case_when(fungicide == "AMIS-X" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
                       fungicide == "SULPHUR" ~ "sulphur",
                       fungicide == "FOLICUR" ~ "tebuconazole",
                       TRUE ~ "control"))%>%
   mutate(dose_ai.ha = 
             case_when(fungicide == "AMIS-X" ~ 120,
                       fungicide == "SULPHUR" ~ 3000,
                       fungicide == "FOLICUR" ~ 62.35,
                       TRUE ~ 0))%>%
   mutate(fungicide_application_1 = 
             case_when(spray_n == 1 ~ as.Date("2011-03-23", format = "%Y-%m-%d"),
                       spray_n == 2 ~ as.Date("2011-03-23", format = "%Y-%m-%d"),
                       spray_n == 3 ~ as.Date("2011-03-09", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%

   mutate(fungicide_application_2 = 
             case_when(spray_n == 2 ~ as.Date("2011-04-13", format = "%Y-%m-%d"),
                       spray_n == 3 ~ as.Date("2011-03-30", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_3 = 
             case_when(spray_n == 3 ~ as.Date("2011-04-12", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))

King_11_dat <- 
   data.frame(trial_ref = "mung1011/02",
              year = "2011",
              location = "Kingaroy",
              host_genotype = King_11$cultivar,
              trial_design = "RCB",
              plot_length = 11,
              plot_width = 4,
              plant_density = NA,
              row_spacing = 0.75,
              replicate = King_11$`rep!`,
              planting_date = as.Date("2011-02-02", format = "%Y-%m-%d"),
              emergence_date = NA,
              flowering_date = NA,
              pod_fill_date = NA,
              mid_late_pod_fill = NA,
              first_sign_disease = as.Date("2011-03-22", format = "%Y-%m-%d"),
              trade_name = as.factor(King_11$trade_name),
              fungicide_ai = King_11$fungicide_ai,
              dose_ai.ha = King_11$dose_ai.ha,
              n_treatment = King_11$`trt!`,
              fungicide_application_1 = King_11$fungicide_application_1,
              fungicide_application_2 = King_11$fungicide_application_2,
              fungicide_application_3 = King_11$fungicide_application_3,
              total_fungicide = King_11$spray_n,
              harvest_date = as.Date(NA),
              final_assessment = as.Date("2010-05-11", format = "%Y-%m-%d"),
              PM_final_severity = King_11$`14 w.a.p.`,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(King_11$`Yld kg ha`),
              AUDPC = apply(King_11[,c("9 w.a.p.", "11 w.a.p.", "12 w.a.p.", "14 w.a.p.")],1, FUN = audpc, dates = c(9*7,11*7,12*7, 14*7))
              )

King_11_m <- King_11_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = sum(replicate),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = NA,
              mid_late_pod_fill = NA,
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE),
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
              meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = King_11_dat))[2,3]
   )

King_11_m <- fold_data(King_11_m, PM_MB_means)

write.csv(
   King_11_m,
   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2011/2011 PMmung Herm/2011 PMmung Kingaroy means.csv"
)

```

### Goolhi 2013
```{r Goolhi_2013}

for(D_assessment in c("16 DAT1", "33DAT1")){

# Import final disease survey
Goolhi.13 <-
   as.data.frame(
      read_xlsx(
         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1305 Fungicides for powdery mildew in mungbean - Goolhi.xlsx",
         sheet = D_assessment,
         range = "A15:AG75",
         col_names = TRUE
      )
   )

Goolhi.13 <- Goolhi.13[order(Goolhi.13[,1],Goolhi.13[,2],Goolhi.13[,3],Goolhi.13[,4]),]

# Replace empty cells / NAs with zeros
for (i in 7:33) {
   Goolhi.13[is.na(Goolhi.13[, i]), i] <- 0
}

# Calculate incidence
#     Sites      1     2     3
# low canopy  c(7:9, 16:18, 25:27)
# mid canopy c(10:12, 19:21, 28:30)
# upp canopy c(13:15, 22:24, 31:33)

incidence1 <-
   vector(mode = "numeric", length = length(Goolhi.13[, 1]))

# Convert disease survey data to 1-9 Incidence rating scale
for (i in seq_along(incidence1)) {
   # incidence = 1
   if (all(Goolhi.13[i, 7:33] == 0)) {
      incidence1[i] <- 1
      next()
   }

   # incidence = 2
   if (all(Goolhi.13[i, c(10:15, 19:24, 28, 33)] == 0) &&
       (sum(Goolhi.13[i, c(7:9, 16:18, 25:27)] > 0) /
        length(Goolhi.13[i, c(7:9, 16:18, 25:27)])) <= 0.75) {
      incidence1[i] <- 2
      next()
   }

   # incidence = 3
   if (all(Goolhi.13[i, c(13:15, 22:24, 31:33)] == 0) &&
       sum(Goolhi.13[i, c(10:12, 19:21, 28:30)] != 0) <= 3 &&
       (sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] > 0) /
        length(Goolhi.13[i, c(7:12, 16:21, 25:30)])) > 0.75) {
      incidence1[i] <- 3
   } else{
      # if it is in the lower half of the canopy and in less than 75% of plants then incidence = 2.5
      if (all(Goolhi.13[i, c(13:15, 22:24, 31:33)] == 0) &&
          sum(Goolhi.13[i, c(10:12, 19:21, 28:30)] != 0) <= 3 &&
          (sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] > 0) /
           length(Goolhi.13[i, c(7:12, 16:21, 25:30)])) <= 0.75) {
         incidence1[i] <- 2.5
         next()
      }
   }

   # incidence = 4
   if (all(Goolhi.13[i, c(13:15, 22:24, 31:33)] == 0) &&
       sum(Goolhi.13[i, c(10:12, 19:21, 28:30)] != 0) > 3 &&
       (sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] > 0) /
        length(Goolhi.13[i, c(7:12, 16:21, 25:30)])) <= 0.75) {
      incidence1[i] <- 4
      next()
   }

   # incidence = 5
   if (all(Goolhi.13[i, c(13:15, 22:24, 31:33)] == 0) &&
       sum(Goolhi.13[i, c(10:12, 19:21, 28:30)] != 0) > 3 &&
       (sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] > 0) /
        length(Goolhi.13[i, c(7:12, 16:21, 25:30)])) > 0.75 &&
       any(Goolhi.13[i, c(7:12, 16:21, 25:30)] == 0)) {
      incidence1[i] <- 5
      next()
   }

   # incidence = 6
   if (all(Goolhi.13[i, c(13:15, 22:24, 31:33)] == 0) &&
       all(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0)) {
      incidence1[i] <- 6
      next()
   }

   # incidence = 7
   if (sum(Goolhi.13[i, c(13:15, 22:24, 31:33)] != 0) <= 3 &&
       all(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0)) {
      incidence1[i] <- 7
      next()
   }

   # incidence = 8
   if ((sum(Goolhi.13[i, c(13:15, 22:24, 31:33)] != 0) > 3 |
        sum(Goolhi.13[i, c(13:15, 22:24, 31:33)]) <= 200) &&
       all(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0) &&
       (sum(Goolhi.13[i, 7:33] > 0) /
        length(Goolhi.13[i, 7:33]) > 0.75) &&
       sum(Goolhi.13[i, 7:33]) <= 2000) {
      incidence1[i] <- 8
      next()
   }

   # incidence = 9
   if (sum(Goolhi.13[i, c(13:15, 22:24, 31:33)] != 0) > 3 &&
       all(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0) &&
       (sum(Goolhi.13[i, 7:33] > 0) /
        length(Goolhi.13[i, 7:33]) > 0.75) &&
       sum(Goolhi.13[i, 7:33]) > 2000) {
      incidence1[i] <- 9
      next()
   }

   # if not in the lower canopy but small colonies in mid and upper canopy
   if (all(Goolhi.13[i, c(7:9, 16:18, 25:27)] == 0) &&
       (sum(Goolhi.13[i, c(10:15, 19:24, 28, 33)] > 0) /
        length(Goolhi.13[i, 7:33]) <= 0.5)) {
      incidence1[i] <- 2.5
      next()
   }

   # incidence = 7.5
   if (sum(Goolhi.13[i, c(13:15, 22:24, 31:33)] != 0) > 3 &&
       sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0) > 10 &&
       any(Goolhi.13[i, c(7:12, 16:21, 25:30)] == 0) &&
       (sum(Goolhi.13[i, 7:33] > 0) /
        length(Goolhi.13[i, 7:33]) > 0.7) &&
       sum(Goolhi.13[i, 7:33]) <= 2000) {
      incidence1[i] <- 7.5
      next()
   }

   # incidence = 6.5
   if (sum(Goolhi.13[i, c(13:15, 22:24, 31:33)] != 0) > 3 &&
       sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0) <= 12 &&
       sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0) >= 10 &&
       (sum(Goolhi.13[i, 7:33] > 0) /
        length(Goolhi.13[i, 7:33]) <= 0.75) &&
       sum(Goolhi.13[i, 7:33]) <= 2000) {
      incidence1[i] <- 6.5
      next()
   }

   # incidence = 4.5
   if (sum(Goolhi.13[i, c(13:15, 22:24, 31:33)] != 0) > 3 &&
       sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0) < 10 &&
       sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0) > 5 &&
       (sum(Goolhi.13[i, 7:33] > 0) /
        length(Goolhi.13[i, 7:33]) <= 0.75) &&
       sum(Goolhi.13[i, 7:33]) <= 2000) {
      incidence1[i] <- 4.5
      next()
   } else{
      # If none of the conditions are met give the incidence zero
      incidence1[i] <- 0
   }

}

# check data to make sure there are no zeros
incidence1
length(Goolhi.13[incidence1 == 0, 1])
Goolhi.13[incidence1 == 0, ]
hist(incidence1)

# Re-format data-frame
if(D_assessment == "16 DAT1"){
Goolhi.13D <- Goolhi.13[,c("Treat", "Rep", "Run", "Plot")]
Goolhi.13D$Inc_16D <-  incidence1

}

if(D_assessment == "33DAT1"){
Goolhi.13D$Inc_33D <-  incidence1
}
}

# head(Goolhi.13D)
# Goolhi.13D <- Goolhi.13D %>%
#    group_by(Treat) %>%
#    summarise(M.inc = mean(Incidence, na.rm = TRUE),
#              sd.inc = sd(Incidence, na.rm = TRUE))

write.csv(
   Goolhi.13D,
   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/Mungbean/Past trials/2013/AM1305-Goolhi-Disease_means.csv"
)

#_____________________
# Read in Harvest data
Goolhi.13Y <-
   as.data.frame(
      read_xlsx(
         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1305 Fungicides for powdery mildew in mungbean - Goolhi.xlsx",
         sheet = "Yield",
         range = "A15:F75",
         col_names = TRUE
      )
   )

Goolhi.13Y <- Goolhi.13Y[order(Goolhi.13Y[,1],Goolhi.13Y[,2],Goolhi.13Y[,3],Goolhi.13Y[,4]),]

Goolhi_13 <- left_join(Goolhi.13D, Goolhi.13Y)

Goolhi_13 <- Goolhi_13 %>%
   mutate(trade_name = 
             case_when(Treat == "1" ~ NA_character_,
                       Treat == "2" ~ "Spin-flo",
                       Treat == "3" ~ "Tilt",
                       Treat == "4" ~ "Amistar Xtra",
                       Treat == "5" ~ "Amistar Xtra + adj",
                       Treat == "6" ~ "Cabrio",
                       Treat == "7" ~ "Spin-flo",
                       Treat == "8" ~ "Tilt",
                       Treat == "9" ~ "Amistar Xtra + adj",
                       Treat == "10" ~ "Cabrio",
                       Treat == "11" ~ "Tilt",
                       TRUE ~ "control"))%>%
   mutate(fungicide_ai = 
             case_when(fungicide == "AMIS-X" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
                       fungicide == "SULPHUR" ~ "sulphur",
                       fungicide == "FOLICUR" ~ "tebuconazole",
                       TRUE ~ "control"))%>%
   mutate(dose_ai.ha = 
             case_when(fungicide == "AMIS-X" ~ 120,
                       fungicide == "SULPHUR" ~ 3000,
                       fungicide == "FOLICUR" ~ 62.35,
                       TRUE ~ 0))%>%
   mutate(fungicide_application_1 = 
             case_when(spray_n == 1 ~ as.Date("2011-03-23", format = "%Y-%m-%d"),
                       spray_n == 2 ~ as.Date("2011-03-23", format = "%Y-%m-%d"),
                       spray_n == 3 ~ as.Date("2011-03-09", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%

   mutate(fungicide_application_2 = 
             case_when(spray_n == 2 ~ as.Date("2011-04-13", format = "%Y-%m-%d"),
                       spray_n == 3 ~ as.Date("2011-03-30", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_3 = 
             case_when(spray_n == 3 ~ as.Date("2011-04-12", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))

King_11_dat <- 
   data.frame(trial_ref = "mung1011/02",
              year = "2011",
              location = "Kingaroy",
              host_genotype = King_11$cultivar,
              trial_design = "RCB",
              plot_length = 11,
              plot_width = 4,
              plant_density = NA,
              row_spacing = 0.75,
              replicate = King_11$`rep!`,
              planting_date = as.Date("2011-02-02", format = "%Y-%m-%d"),
              emergence_date = NA,
              flowering_date = NA,
              pod_fill_date = NA,
              mid_late_pod_fill = NA,
              first_sign_disease = as.Date("2011-03-22", format = "%Y-%m-%d"),
              trade_name = as.factor(King_11$trade_name),
              fungicide_ai = King_11$fungicide_ai,
              dose_ai.ha = King_11$dose_ai.ha,
              n_treatment = King_11$`trt!`,
              fungicide_application_1 = King_11$fungicide_application_1,
              fungicide_application_2 = King_11$fungicide_application_2,
              fungicide_application_3 = King_11$fungicide_application_3,
              total_fungicide = King_11$spray_n,
              harvest_date = as.Date(NA),
              final_assessment = as.Date("2010-05-11", format = "%Y-%m-%d"),
              PM_final_severity = King_11$`14 w.a.p.`,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(King_11$`Yld kg ha`),
              AUDPC = apply(King_11[,c("9 w.a.p.", "11 w.a.p.", "12 w.a.p.", "14 w.a.p.")],1, FUN = audpc, dates = c(9*7,11*7,12*7, 14*7))
              )

King_11_m <- King_11_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = sum(replicate),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = NA,
              mid_late_pod_fill = NA,
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE),
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
              meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = King_11_dat))[2,3]
   )

King_11_m <- fold_data(King_11_m, PM_MB_means)

Goolhi.13Y <- Goolhi.13Y %>%
   group_by(Treat) %>%
   summarise(
      M.Yield = mean(`Yield Kg/ha`, na.rm = TRUE),
      sd.Yield = sd(`Yield Kg/ha`, na.rm = TRUE)
   )
write.csv(
   Goolhi.13Y,
   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/Mungbean/Past trials/2013/AM1305-Goolhi-Yield_means.csv"
)

```

### 2019-11-17 191115_PMMB_DataWrangling_PM.Rmd
Goolhi done

@@
               harvest_date = as.Date("2011-04-25", format = "%Y-%m-%d"),
-              final_assessment = as.Date("2010-04-11", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2011-04-11", format = "%Y-%m-%d"),
               PM_final_severity = Herm_11$`P.M. 11  w.a.p.`,
@@
               harvest_date = as.Date(NA),
-              final_assessment = as.Date("2010-05-11", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2011-05-11", format = "%Y-%m-%d"),
               PM_final_severity = King_11$`14 w.a.p.`,
@@
 
-write.csv(
-   Goolhi.13D,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/Mungbean/Past trials/2013/AM1305-Goolhi-Disease_means.csv"
-)
+# write.csv(
+#    Goolhi.13D,
+#    "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/Mungbean/Past trials/2013/AM1305-Goolhi-Disease_means.csv"
+# )
 
@@
    )
-
 Goolhi.13Y <- Goolhi.13Y[order(Goolhi.13Y[,1],Goolhi.13Y[,2],Goolhi.13Y[,3],Goolhi.13Y[,4]),]
 
+# Join disease and Yield data
 Goolhi_13 <- left_join(Goolhi.13D, Goolhi.13Y)
@@
    mutate(trade_name = 
-             case_when(Treat == "1" ~ NA_character_,
+             case_when(Treat == "1" ~ "control",
                        Treat == "2" ~ "Spin-flo",
@@
                        Treat == "11" ~ "Tilt",
-                       TRUE ~ "control"))%>%
+                       TRUE ~ "other"))%>%
    mutate(fungicide_ai = 
-             case_when(fungicide == "AMIS-X" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
-                       fungicide == "SULPHUR" ~ "sulphur",
-                       fungicide == "FOLICUR" ~ "tebuconazole",
-                       TRUE ~ "control"))%>%
+             case_when(Treat == "1" ~ "control",
+                       Treat == "2" ~ "carbendazim",
+                       Treat == "3" ~ "propiconazole",
+                       Treat == "4" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "5" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "6" ~ "pyraclostrobin",
+                       Treat == "7" ~ "carbendazim",
+                       Treat == "8" ~ "propiconazole",
+                       Treat == "9" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "10" ~ "pyraclostrobin",
+                       Treat == "11" ~ "propiconazole",
+                       TRUE ~ "other"))%>%
    mutate(dose_ai.ha = 
-             case_when(fungicide == "AMIS-X" ~ 120,
-                       fungicide == "SULPHUR" ~ 3000,
-                       fungicide == "FOLICUR" ~ 62.35,
+             case_when(Treat == "1" ~ 0,
+                       Treat == "2" ~ 250,
+                       Treat == "3" ~ 62.5,
+                       Treat == "4" ~ 40,
+                       Treat == "5" ~ 40,
+                       Treat == "6" ~ 125,
+                       Treat == "7" ~ 250,
+                       Treat == "8" ~ 62.5,
+                       Treat == "9" ~ 40,
+                       Treat == "10" ~ 125,
+                       Treat == "11" ~ 62.5,
                        TRUE ~ 0))%>%
    mutate(fungicide_application_1 = 
-             case_when(spray_n == 1 ~ as.Date("2011-03-23", format = "%Y-%m-%d"),
-                       spray_n == 2 ~ as.Date("2011-03-23", format = "%Y-%m-%d"),
-                       spray_n == 3 ~ as.Date("2011-03-09", format = "%Y-%m-%d"),
+             case_when(Treat == "1" ~ as.Date(NA),
+                       Treat == "2" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "3" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "4" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "5" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "6" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "7" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
                        TRUE ~ as.Date(NA)))%>%
-
    mutate(fungicide_application_2 = 
-             case_when(spray_n == 2 ~ as.Date("2011-04-13", format = "%Y-%m-%d"),
-                       spray_n == 3 ~ as.Date("2011-03-30", format = "%Y-%m-%d"),
+             case_when(Treat == "7" ~ as.Date("2013-04-13", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-04-13", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-04-13", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-04-13", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-04-13", format = "%Y-%m-%d"),
                        TRUE ~ as.Date(NA)))%>%
    mutate(fungicide_application_3 = 
-             case_when(spray_n == 3 ~ as.Date("2011-04-12", format = "%Y-%m-%d"),
-                       TRUE ~ as.Date(NA)))
+             case_when(Treat == "11" ~ as.Date("2013-04-27", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Treat == "1" ~ 0,
+                       Treat == "7" ~ 2,
+                       Treat == "8" ~ 2,
+                       Treat == "9" ~ 2,
+                       Treat == "10" ~ 2,
+                       Treat == "11" ~ 3,
+                       TRUE ~ 1))
 
-King_11_dat <- 
-   data.frame(trial_ref = "mung1011/02",
-              year = "2011",
-              location = "Kingaroy",
-              host_genotype = King_11$cultivar,
-              trial_design = "RCB",
-              plot_length = 11,
+Goolhi_13_dat <- 
+   data.frame(trial_ref = "AM1305",
+              year = "2013",
+              location = "Goolhi",
+              host_genotype = "Crystal",
+              trial_design = "RB",
+              plot_length = 12,
               plot_width = 4,
               plant_density = NA,
-              row_spacing = 0.75,
-              replicate = King_11$`rep!`,
-              planting_date = as.Date("2011-02-02", format = "%Y-%m-%d"),
+              row_spacing = 0.33,
+              replicate = Goolhi_13$Rep,
+              planting_date = NA,
               emergence_date = NA,
-              flowering_date = NA,
-              pod_fill_date = NA,
+              flowering_date = as.Date("2013-04-04", format = "%Y-%m-%d"),
+              pod_fill_date = as.Date("2013-04-18", format = "%Y-%m-%d"),
               mid_late_pod_fill = NA,
-              first_sign_disease = as.Date("2011-03-22", format = "%Y-%m-%d"),
-              trade_name = as.factor(King_11$trade_name),
-              fungicide_ai = King_11$fungicide_ai,
-              dose_ai.ha = King_11$dose_ai.ha,
-              n_treatment = King_11$`trt!`,
-              fungicide_application_1 = King_11$fungicide_application_1,
-              fungicide_application_2 = King_11$fungicide_application_2,
-              fungicide_application_3 = King_11$fungicide_application_3,
-              total_fungicide = King_11$spray_n,
-              harvest_date = as.Date(NA),
-              final_assessment = as.Date("2010-05-11", format = "%Y-%m-%d"),
-              PM_final_severity = King_11$`14 w.a.p.`,
+              first_sign_disease = as.Date("2013-03-25", format = "%Y-%m-%d"),
+              trade_name = as.factor(Goolhi_13$trade_name),
+              fungicide_ai = Goolhi_13$fungicide_ai,
+              dose_ai.ha = Goolhi_13$dose_ai.ha,
+              n_treatment = Goolhi_13$Treat,
+              fungicide_application_1 = Goolhi_13$fungicide_application_1,
+              fungicide_application_2 = Goolhi_13$fungicide_application_2,
+              fungicide_application_3 = Goolhi_13$fungicide_application_3,
+              total_fungicide = Goolhi_13$spray_n,
+              harvest_date = as.Date("2013-06-20", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2013-04-30", format = "%Y-%m-%d"),
+              PM_final_severity = Goolhi_13$Inc_33D,
               rating_scale = "1-9",
-              grain_yield.t.ha. = as.numeric(King_11$`Yld kg ha`),
-              AUDPC = apply(King_11[,c("9 w.a.p.", "11 w.a.p.", "12 w.a.p.", "14 w.a.p.")],1, FUN = audpc, dates = c(9*7,11*7,12*7, 14*7))
+              grain_yield.t.ha. = as.numeric(Goolhi_13$`Yield Kg/ha`),
+              AUDPC = apply(Goolhi_13[,c("Inc_16D","Inc_33D")],1, FUN = audpc, dates = c(16,33))
               )
 
-King_11_m <- King_11_dat %>%
-   group_by(trial_ref, year, location, host_genotype, trial_design, trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
+Goolhi_13_m <- Goolhi_13_dat %>%
+   group_by(trial_ref, year, location, host_genotype, trial_design, 
+            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
    summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
@@
               flowering_date = unique(flowering_date),
-              pod_fill_date = NA,
-              mid_late_pod_fill = NA,
+              pod_fill_date = unique(pod_fill_date),
+              mid_late_pod_fill = unique(mid_late_pod_fill),
               first_sign_disease = unique(first_sign_disease),
@@
              AUDPC.sd = sd(AUDPC),
-              meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = King_11_dat))[2,3]
+              meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Goolhi_13_dat))[2,3]
    )
 
-King_11_m <- fold_data(King_11_m, PM_MB_means)
+Goolhi_13_m <- fold_data(Goolhi_13_m, PM_MB_means)
 
-Goolhi.13Y <- Goolhi.13Y %>%
-   group_by(Treat) %>%
-   summarise(
-      M.Yield = mean(`Yield Kg/ha`, na.rm = TRUE),
-      sd.Yield = sd(`Yield Kg/ha`, na.rm = TRUE)
-   )
+Goolhi_13_m <- Goolhi_13_m[Goolhi_13_m$trade_name != "other",]
+
 write.csv(
-   Goolhi.13Y,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/Mungbean/Past trials/2013/AM1305-Goolhi-Yield_means.csv"
+   Goolhi_13_m,
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1305_Goolhi_means.csv"
 )

### 2019-11-18 191115_PMMB_DataWrangling_PM.Rmd
Working on Marys mount

@@
 ```
+
+```{r MarysM_13}
+
+for(D_assess in c("18 DAT1 18-3-2013","19 DAT1 19-3-2013")){
+
+# Import  disease survey
+MarysM.13D <-
+   as.data.frame(
+      read_xlsx(
+         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1304 Fungicides for powdery mildew in mungbean - Marys Mount.xlsx",
+         sheet = D_assess,
+         range = "A14:DC72",
+         col_names = TRUE
+      )
+   )
+
+if(D_assess == "18 DAT1 18-3-2013"){
+   col_ref <- 33:57
+   col_ref2 <- 7:31
+}
+if(D_assess == "19 DAT1 19-3-2013"){
+   col_ref <- 58:107
+   col_ref2 <- 7:56
+}
+
+# Replace empty cells / NAs with zeros
+for (i in c(col_ref2,col_ref)) {
+   MarysM.13D[is.na(MarysM.13D[, i]), i] <- 0
+}
+
+incidence2 <-
+   vector(mode = "numeric", length = length(MarysM.13D[, 1]))
+
+# Convert disease survey data to 1-9 Incidence rating scale
+for (i in seq_along(incidence2)) {
+   # incidence = 1
+   if (all(MarysM.13D[i, col_ref] == 0)) {
+      incidence2[i] <- 1
+      next()
+   }
+
+   # incidence = 2
+   if (sum(MarysM.13D[i, col_ref] == 2) == 0 &&
+       sum(MarysM.13D[i, col_ref] == 1) == 0 &&
+       (sum(MarysM.13D[i, col_ref] == 3) /
+        length(MarysM.13D[i, col_ref])) <= 0.75) {
+      incidence2[i] <- 2
+      next()
+   }
+
+   # incidence = 3
+   if (sum(MarysM.13D[i, col_ref] == 1) == 0 &&
+       sum(MarysM.13D[i, col_ref] == 2) <= 8 &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref])) > 0.75) {
+      incidence2[i] <- 3
+   } else{
+      # if it is in the lower half of the canopy and in less than 75% of plants then incidence = 2.5
+      if (sum(MarysM.13D[i, col_ref] == 1) == 0 &&
+          sum(MarysM.13D[i, col_ref] == 2) <= 8 &&
+          sum(MarysM.13D[i, col_ref] == 3) > 0 &&
+          (sum(MarysM.13D[i, col_ref] > 0) /
+           length(MarysM.13D[i, col_ref])) <= 0.75) {
+         incidence2[i] <- 2.5
+         next()
+      }
+   }
+
+   # incidence = 4
+   if (sum(MarysM.13D[i, col_ref] == 1) == 0 &&
+       sum(MarysM.13D[i, col_ref] == 2) > 0 &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref])) <= 0.75) {
+      incidence2[i] <- 4
+      next()
+   }
+
+   # incidence = 5
+   if (sum(MarysM.13D[i, col_ref] == 1) == 0 &&
+       sum(MarysM.13D[i, col_ref] == 2) > 0 &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref])) > 0.75) {
+      incidence2[i] <- 5
+      next()
+   }
+
+   # incidence = 6
+   if (sum(MarysM.13D[i, col_ref] == 1) == 0 &&
+       sum(MarysM.13D[i, col_ref] >= 2) > 0 &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref])) > 0.95) {
+      incidence2[i] <- 6
+      next()
+   }
+
+   # incidence = 7
+   if (sum(MarysM.13D[i, col_ref] == 1) <= 8 &&
+       sum(MarysM.13D[i, col_ref] >= 2) > 0 &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref])) > 0.95) {
+      incidence2[i] <- 7
+      next()
+   }
+
+   # incidence = 8
+   if (sum(MarysM.13D[i, col_ref] >= 1) > 0 &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref])) > 0.75) {
+      incidence2[i] <- 8
+      next()
+   }
+
+   # incidence = 9
+   if (sum(MarysM.13D[i, col_ref] >= 1) > 0 &&
+       sum(MarysM.13D[i, col_ref2] >= (10 * 5 * 100 * 0.75)) &&
+       # ten leaves from 5 sample sites with a maximum % leaf area infected with PM of 100% * 0.75 as a threshold for leaf drop
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref])) > 0.75) {
+      incidence2[i] <- 9
+      next()
+   }
+
+   # if there are few (< 10%) leaves with very small infections in all parts of the canopy OR
+   # if there is a stray colony on a upper leaf in addition to all lower
+   if (sum(MarysM.13D[i, col_ref] == 3) >= 1 &&
+       sum(MarysM.13D[i, col_ref] == 1) <= 2 &&
+       sum(MarysM.13D[i, col_ref] == 2) <= 2 &&
+       sum(MarysM.13D[i, col_ref2]) <= 150) {
+      incidence2[i] <- 2.5
+      next()
+   }
+
+   # incidence = 7.5  In the upper canopy with less than 75% plants infected
+   if (sum(MarysM.13D[i, col_ref] == 3) > 0 &&
+       sum(MarysM.13D[i, col_ref] == 2) > 0 &&
+       sum(MarysM.13D[i, col_ref] == 1) > 0 &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref]) <= 0.75) &&
+       sum(MarysM.13D[i, col_ref2]) >= 2000) {
+      incidence2[i] <- 7.5
+      next()
+   }
+   #
+   # incidence = 6.5
+   if (sum(MarysM.13D[i, col_ref] == 1) > 3 &&
+       sum(MarysM.13D[i, col_ref] >= 2) > 0 &&
+       sum(MarysM.13D[i, col_ref2] <= 500)  &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref]) >= 0.65)) {
+      incidence2[i] <- 6.5
+      next()
+   }
+   #
+   #
+   # incidence = 4.5 If PM is in the the lower and mid-canopy in less than 75% of plants and one or two in the upper canopy
+   if (sum(MarysM.13D[i, col_ref] == 1) <= 3 &&
+       sum(MarysM.13D[i, col_ref] >= 2) > 0 &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref])) <= 0.75) {
+      incidence2[i] <- 4.5
+      next()
+   } else{
+      # If none of the conditions are met give the incidence zero
+      incidence2[i] <- 0
+   }
+
+# Re-format data-frame
+if(D_assess == "18 DAT1 18-3-2013"){
+MarysM.13D.1 <- MarysM.13D[,c("Treat", "Rep", "Run", "Plot")]
+MarysM.13D.1$Inc_18D <-  incidence2
+#cat(incidence2,"\n",length(incidence2), sep = ", ")
+}
+
+if(D_assess == "19 DAT1 19-3-2013"){
+   MarysM.13D.1$Inc_19D <-  incidence2
+   #cat(incidence2,"\n",length(incidence2), sep = ", ")
+}
+
+}
+
+}
+
+# Check for Zeros which indicat the above code could not fit the data into an incidence rating on the 1-9 scale
+incidence2
+MarysM.13D[incidence2 == 0, 1:5]
+dim(MarysM.13D[incidence2 == 0, ])
+hist(incidence2)
+
+# Re-format data-frame
+MarysM.13D$Incidence <- incidence2
+MarysM.13D <-
+   MarysM.13D[, c("Treat", "Rep", "Run", "Plot", "Incidence")]
+
+MarysM.13D <- MarysM.13D %>%
+   group_by(Treat) %>%
+   summarise(M.inc = mean(Incidence, na.rm = TRUE),
+             sd.inc = sd(Incidence, na.rm = TRUE))
+write.csv(
+   MarysM.13D,
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/Mungbean/Past trials/2013/AM1304-MaryMount-Disease_means.csv"
+)
+
+# read in yield and format
+MarysM.13Y <-
+   as.data.frame(
+      read_xlsx(
+         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/Mungbean/Past trials/2013/AM1304 Fungicides for powdery mildew in mungbean - Marys Mount.xlsx",
+         sheet = "42 DAT1 Yield",
+         range = "A14:F58",
+         col_names = TRUE
+      )
+   )
+head(MarysM.13Y)
+
+MarysM.13Y <- MarysM.13Y %>%
+   group_by(Treat) %>%
+   summarise(
+      M.Yield = mean(`Yield Kg/ha`, na.rm = TRUE),
+      sd.Yield = sd(`Yield Kg/ha`, na.rm = TRUE)
+   )
+write.csv(
+   MarysM.13Y,
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/Mungbean/Past trials/2013/AM1304-MarysMount-Yield_means.csv"
+)
+
+```

### 2019-11-18 191115_PMMB_DataWrangling_PM.Rmd
Marys mount wrangling complete

@@
               grain_yield.t.ha. = Herm_10$`Kg/ha`,
-              AUDPC = apply(Herm_10[,c("P.M.9wap","P.M.11wap","P.M.13wap")],1, FUN = audpc, dates = c(9*7,11*7,13*7)),
+              AUDPC = apply(Herm_10[,c("P.M.9wap","P.M.11wap","P.M.13wap")]-1,1, FUN = audpc, dates = c(9*7,11*7,13*7)), # -1 to the data because zero disease = 1 on rating scale
               stringsAsFactors = FALSE
@@
               grain_yield.t.ha. = as.numeric(King_11$`Yld kg ha`),
-              AUDPC = apply(King_11[,c("9 w.a.p.", "11 w.a.p.", "12 w.a.p.", "14 w.a.p.")],1, FUN = audpc, dates = c(9*7,11*7,12*7, 14*7))
+              AUDPC = apply(King_11[,c("9 w.a.p.", "11 w.a.p.", "12 w.a.p.", "14 w.a.p.")]-1,1, FUN = audpc, dates = c(9*7,11*7,12*7, 14*7))# -1 to the data because zero disease = 1 on rating scale
               )
@@
               grain_yield.t.ha. = as.numeric(Goolhi_13$`Yield Kg/ha`),
-              AUDPC = apply(Goolhi_13[,c("Inc_16D","Inc_33D")],1, FUN = audpc, dates = c(16,33))
+              AUDPC = apply(Goolhi_13[,c("Inc_16D","Inc_33D")]-1,1, FUN = audpc, dates = c(16,33))# -1 to the data because zero disease = 1 on rating scale
               )
@@
 
+colnames(MarysM.13D)[1:4] <- c("Treat", "Rep", "Run", "Plot")
+MarysM.13D <- MarysM.13D[order(MarysM.13D[,1],MarysM.13D[,2],MarysM.13D[,3],MarysM.13D[,4]),]
+
 if(D_assess == "18 DAT1 18-3-2013"){
@@
 
+}# End of incidence2 loop
+
+if(any(incidence2 == 0)){
+   warning("Code caluculated incidence on '0' which is off the incidence scale")
+}
+
 # Re-format data-frame
@@
 
-}
-
-}
-
-# Check for Zeros which indicat the above code could not fit the data into an incidence rating on the 1-9 scale
-incidence2
-MarysM.13D[incidence2 == 0, 1:5]
-dim(MarysM.13D[incidence2 == 0, ])
-hist(incidence2)
-
-# Re-format data-frame
-MarysM.13D$Incidence <- incidence2
-MarysM.13D <-
-   MarysM.13D[, c("Treat", "Rep", "Run", "Plot", "Incidence")]
-
-MarysM.13D <- MarysM.13D %>%
-   group_by(Treat) %>%
-   summarise(M.inc = mean(Incidence, na.rm = TRUE),
-             sd.inc = sd(Incidence, na.rm = TRUE))
+} #end of loop on disease observations
+
 write.csv(
-   MarysM.13D,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/Mungbean/Past trials/2013/AM1304-MaryMount-Disease_means.csv"
+   MarysM.13D.1,
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1304-MaryMount-Disease_means.csv"
 )
@@
       read_xlsx(
-         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/Mungbean/Past trials/2013/AM1304 Fungicides for powdery mildew in mungbean - Marys Mount.xlsx",
+         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1304 Fungicides for powdery mildew in mungbean - Marys Mount.xlsx",
          sheet = "42 DAT1 Yield",
@@
    )
-head(MarysM.13Y)
-
-MarysM.13Y <- MarysM.13Y %>%
-   group_by(Treat) %>%
-   summarise(
-      M.Yield = mean(`Yield Kg/ha`, na.rm = TRUE),
-      sd.Yield = sd(`Yield Kg/ha`, na.rm = TRUE)
-   )
+dim(MarysM.13Y)
+dim(MarysM.13D.1)
+
+MarysM.13Y$Treat <- as.character(MarysM.13Y$Treat)
+MarysM.13Y$Rep <- as.character(MarysM.13Y$Rep)
+
+MarysM.13Y <- MarysM.13Y[order(MarysM.13Y[,1],MarysM.13Y[,2],MarysM.13Y[,3],MarysM.13Y[,4]),]
+
+MarysM_13 <- left_join(MarysM.13D.1,MarysM.13Y)
+
+MarysM_13 <- MarysM_13 %>%
+   mutate(trade_name = 
+             case_when(Treat == "1" ~ "control",
+                       Treat == "2" ~ "Spin-flo",
+                       Treat == "3" ~ "Tilt",
+                       Treat == "4" ~ "Amistar Xtra",
+                       Treat == "5" ~ "Amistar Xtra + adj",
+                       Treat == "6" ~ "Cabrio",
+                       Treat == "7" ~ "Spin-flo",
+                       Treat == "8" ~ "Tilt",
+                       Treat == "9" ~ "Amistar Xtra + adj",
+                       Treat == "10" ~ "Cabrio",
+                       Treat == "11" ~ "Tilt",
+                       TRUE ~ "other"))%>%
+   mutate(fungicide_ai = 
+             case_when(Treat == "1" ~ "control",
+                       Treat == "2" ~ "carbendazim",
+                       Treat == "3" ~ "propiconazole",
+                       Treat == "4" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "5" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "6" ~ "pyraclostrobin",
+                       Treat == "7" ~ "carbendazim",
+                       Treat == "8" ~ "propiconazole",
+                       Treat == "9" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "10" ~ "pyraclostrobin",
+                       Treat == "11" ~ "propiconazole",
+                       TRUE ~ "other"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Treat == "1" ~ 0,
+                       Treat == "2" ~ 250,
+                       Treat == "3" ~ 62.5,
+                       Treat == "4" ~ 40,
+                       Treat == "5" ~ 40,
+                       Treat == "6" ~ 125,
+                       Treat == "7" ~ 250,
+                       Treat == "8" ~ 62.5,
+                       Treat == "9" ~ 40,
+                       Treat == "10" ~ 125,
+                       Treat == "11" ~ 62.5,
+                       TRUE ~ 0))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Treat == "1" ~ as.Date(NA),
+                       Treat == "2" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "3" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "4" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "5" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "6" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "7" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Treat == "7" ~ as.Date("2013-03-18", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-03-18", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-03-18", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-03-18", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-03-18", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_3 = 
+             case_when(Treat == "11" ~ as.Date("2013-04-02", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Treat == "1" ~ 0,
+                       Treat == "2" ~ 1,
+                       Treat == "3" ~ 1,
+                       Treat == "4" ~ 1,
+                       Treat == "5" ~ 1,
+                       Treat == "6" ~ 1,
+                       Treat == "7" ~ 2,
+                       Treat == "8" ~ 2,
+                       Treat == "9" ~ 2,
+                       Treat == "10" ~ 2,
+                       Treat == "11" ~ 2, # third spray not applied ?
+                       TRUE ~ 0))
+
+MarysM_13_dat <- 
+   data.frame(trial_ref = "AM1304",
+              year = "2013",
+              location = "Mary's mount",
+              host_genotype = "Crystal",
+              trial_design = "RCB",
+              plot_length = 12,
+              plot_width = 4,
+              plant_density = NA,
+              row_spacing = 1,
+              replicate = MarysM_13$Rep,
+              planting_date = NA,
+              emergence_date = NA,
+              flowering_date = NA,
+              pod_fill_date = as.Date("2013-02-28", format = "%Y-%m-%d"),
+              mid_late_pod_fill = NA,
+              first_sign_disease = as.Date("2013-03-16", format = "%Y-%m-%d"),
+              trade_name = as.factor(MarysM_13$trade_name),
+              fungicide_ai = MarysM_13$fungicide_ai,
+              dose_ai.ha = MarysM_13$dose_ai.ha,
+              n_treatment = MarysM_13$Treat,
+              fungicide_application_1 = MarysM_13$fungicide_application_1,
+              fungicide_application_2 = MarysM_13$fungicide_application_2,
+              fungicide_application_3 = MarysM_13$fungicide_application_3,
+              total_fungicide = MarysM_13$spray_n,
+              harvest_date = as.Date("2013-04-11", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2013-03-26", format = "%Y-%m-%d"),
+              PM_final_severity = MarysM_13$Inc_19D,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(MarysM_13$`Yield Kg/ha`)/1000,
+              AUDPC = apply(MarysM_13[,c("Inc_18D","Inc_19D")]-1,1, FUN = audpc, dates = c(12,12+19)) # -1 to the data because zero disease = 1 on rating scale
+              )
+
+MarysM_13_m <- MarysM_13_dat %>%
+   group_by(trial_ref, year, location, host_genotype, trial_design, 
+            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
+   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
+              plot_width.m. = mean(plot_width, na.rm = TRUE),
+              plant_density = unique(plant_density),
+              row_spacing = unique(row_spacing),
+              replicates = sum(as.numeric(replicate)),
+              planting_date = unique(planting_date),
+              emergence_date = NA,
+              flowering_date = unique(flowering_date),
+              pod_fill_date = unique(pod_fill_date),
+              mid_late_pod_fill = unique(mid_late_pod_fill),
+              first_sign_disease = unique(first_sign_disease),
+              fungicide_application_1 = unique(fungicide_application_1),
+              fungicide_application_2 = unique(fungicide_application_2),
+              fungicide_application_3 = unique(fungicide_application_3),
+              total_fungicide = unique(total_fungicide),
+              harvest_date = unique(harvest_date),
+              final_assessment = unique(final_assessment),
+              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+              rating_scale = unique(rating_scale),
+              disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+              D_error_type = "stdev",
+              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+              raw_graded = NA,
+              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+              Y_error_type = "stdev",
+             AUDPC.m = mean(AUDPC),
+             AUDPC.sd = sd(AUDPC),
+              meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = MarysM_13_dat))[2,3]
+   )
+
+MarysM_13_m <- fold_data(MarysM_13_m, PM_MB_means)
+
+MarysM_13_m <- MarysM_13_m[MarysM_13_m$trade_name != "other",]
+
+MarysM_13_m[,c("disease_error","yield_error")] <- 
+   MarysM_13_dat %>%
+   group_by(n_treatment) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("disease_error","yield_error"))
+
 write.csv(
-   MarysM.13Y,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/Mungbean/Past trials/2013/AM1304-MarysMount-Yield_means.csv"
+   MarysM_13_m,
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1304-MarysMount_means.csv"
 )

### 2019-11-18 191115_PMMB_DataWrangling_PM.Rmd
Millmerran and Premer data rewrangled

@@
 
+### Mary's Mount 2013
 ```{r MarysM_13}
@@
 
+# For some wierd reason standard deviations are comming back NA in the code above
 MarysM_13_m[,c("disease_error","yield_error")] <- 
@@
 ```
+
+### Premer
+#### Convert disease scores
+```{r Premer_13_convert_scores}
+
+for(D_assess in c("19 DAT1 19-3-2013","31 DAT1 31-3-2013")){
+
+# Import final disease survey
+Premer.13D <-
+   as.data.frame(
+      read_xlsx(
+         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1303 Fungicides for powdery mildew in mungbean - Premer.xlsx",
+         sheet = D_assess,
+         range = "A14:DC64",
+         col_names = TRUE
+      )
+   )
+
+colnames(Premer.13D)[1:4] <- c("Treat", "Rep", "Run", "Plot")
+Premer.13D <- Premer.13D[order(Premer.13D[,1],Premer.13D[,2],Premer.13D[,3],Premer.13D[,4]),]
+
+# remove Plots not surveyed
+for (i in seq_along(Premer.13D[, 1])) {
+   if (i == 1) {
+      plotsRecorded <- vector(length = length(Premer.13D[, 1]))
+   }
+
+   plotsRecorded[i] <- all(is.na(Premer.13D[i, 7:56]))
+
+   if (i == length(Premer.13D[, 1])) {
+      print(!plotsRecorded)
+   }
+}
+# remove Plots not surveyed
+Premer.13D <- Premer.13D[!plotsRecorded, ]
+
+incidence3 <-
+   vector(mode = "numeric", length = length(Premer.13D[, 1]))
+
+# Convert disease survey data to 1-9 Incidence rating scale
+for (i in seq_along(incidence3)) {
+   # # NAs
+   # if (all(is.na(Premer.13D[i, 58:107]))) {
+   #    incidence3[i] <- NA
+   #    next()
+   # }
+
+   # incidence = 1
+   if (all(Premer.13D[i, 58:107] == 0)) {
+      incidence3[i] <- 1
+      next()
+   }
+
+   # incidence = 2
+   if (sum(Premer.13D[i, 58:107] == 2, na.rm = TRUE) == 0 &&
+       sum(Premer.13D[i, 58:107] == 1, na.rm = TRUE) == 0 &&
+       (sum(Premer.13D[i, 58:107] == 3, na.rm = TRUE) /
+        length(Premer.13D[i, 58:107])) <= 0.75) {
+      incidence3[i] <- 2
+      next()
+   }
+
+   # incidence = 3
+   if (sum(Premer.13D[i, 58:107] == 1, na.rm = TRUE) == 0 &&
+       sum(Premer.13D[i, 58:107] == 2, na.rm = TRUE) <= 8 &&
+       (sum(Premer.13D[i, 58:107] > 0, na.rm = TRUE) /
+        length(Premer.13D[i, 58:107])) > 0.75) {
+      incidence3[i] <- 3
+   } else{
+      # if it is in the lower half of the canopy and in less than 75% of plants then incidence = 2.5
+      if (sum(Premer.13D[i, 58:107] == 1, na.rm = TRUE) == 0 &&
+          sum(Premer.13D[i, 58:107] == 2, na.rm = TRUE) <= 8 &&
+          sum(Premer.13D[i, 58:107] == 3, na.rm = TRUE) > 0 &&
+          (sum(Premer.13D[i, 58:107] > 0, na.rm = TRUE) /
+           length(Premer.13D[i, 58:107])) <= 0.75) {
+         incidence3[i] <- 2.5
+         next()
+      }
+   }
+
+   # incidence = 4
+   if (sum(Premer.13D[i, 58:107] == 1, na.rm = TRUE) == 0 &&
+       sum(Premer.13D[i, 58:107] == 2, na.rm = TRUE) > 0 &&
+       (sum(Premer.13D[i, 58:107] > 0, na.rm = TRUE) /
+        length(Premer.13D[i, 58:107])) <= 0.75) {
+      incidence3[i] <- 4
+      next()
+   }
+
+   # incidence = 5
+   if (sum(Premer.13D[i, 58:107] == 1, na.rm = TRUE) == 0 &&
+       sum(Premer.13D[i, 58:107] == 2, na.rm = TRUE) > 0 &&
+       (sum(Premer.13D[i, 58:107] > 0, na.rm = TRUE) /
+        length(Premer.13D[i, 58:107])) > 0.75) {
+      incidence3[i] <- 5
+      next()
+   }
+
+   # incidence = 6
+   if (sum(Premer.13D[i, 58:107] == 1, na.rm = TRUE) == 0 &&
+       sum(Premer.13D[i, 58:107] >= 2, na.rm = TRUE) > 0 &&
+       (sum(Premer.13D[i, 58:107] > 0, na.rm = TRUE) /
+        length(Premer.13D[i, 58:107])) > 0.95) {
+      incidence3[i] <- 6
+      next()
+   }
+
+   # incidence = 7
+   if (sum(Premer.13D[i, 58:107] == 1, na.rm = TRUE) <= 8 &&
+       sum(Premer.13D[i, 58:107] >= 2, na.rm = TRUE) > 0 &&
+       (sum(Premer.13D[i, 58:107] > 0, na.rm = TRUE) /
+        length(Premer.13D[i, 58:107])) > 0.95) {
+      incidence3[i] <- 7
+      next()
+   }
+
+   # incidence = 8
+   if (sum(Premer.13D[i, 58:107] >= 1, na.rm = TRUE) > 0 &&
+       (sum(Premer.13D[i, 58:107] > 0, na.rm = TRUE) /
+        length(Premer.13D[i, 58:107])) > 0.75) {
+      incidence3[i] <- 8
+      next()
+   }
+
+   # incidence = 9
+   if (sum(Premer.13D[i, 58:107] >= 1) > 0 &&
+       sum(Premer.13D[i, 7:56] >= (10 * 5 * 100 * 0.75)) &&
+       # ten leaves from 5 sample sites with a maximum % leaf area infected with PM of 100% * 0.75 as a threshold for leaf drop
+       (sum(Premer.13D[i, 58:107] > 0) /
+        length(Premer.13D[i, 58:107])) > 0.75) {
+      incidence3[i] <- 9
+      next()
+   }
+
+   # if there are few (< 10%) leaves with very small infections in all parts of the canopy OR
+   # if there is a stray colony on a upper leaf in addition to all lower
+   if (sum(Premer.13D[i, 58:107] == 3) >= 1 &&
+       sum(Premer.13D[i, 58:107] == 1) <= 2 &&
+       sum(Premer.13D[i, 58:107] == 2) <= 2 &&
+       sum(Premer.13D[i, 7:56]) <= 150) {
+      incidence3[i] <- 2.5
+      next()
+   }
+
+   # incidence = 7.5  In the upper canopy with less than 75% plants infected
+   if (sum(Premer.13D[i, 58:107] == 3) >= 0 &&
+       sum(Premer.13D[i, 58:107] == 2) > 0 &&
+       sum(Premer.13D[i, 58:107] == 1) > 0 &&
+       (sum(Premer.13D[i, 58:107] > 0) /
+        length(Premer.13D[i, 58:107]) <= 0.75) &&
+       sum(Premer.13D[i, 7:56]) >= 150) {
+      incidence3[i] <- 7.5
+      next()
+   }
+   #
+   # incidence = 6.5
+   if (sum(Premer.13D[i, 58:107] == 1) > 3 &&
+       sum(Premer.13D[i, 58:107] >= 2) > 0 &&
+       sum(Premer.13D[i, 7:56] <= 500)  &&
+       (sum(Premer.13D[i, 58:107] > 0) /
+        length(Premer.13D[i, 58:107]) >= 0.65)) {
+      incidence3[i] <- 6.5
+      next()
+   }
+   #
+   #
+   # incidence = 4.5 If PM is in the the lower and mid-canopy in less than 75% of plants and one or two in the upper canopy
+   if (sum(Premer.13D[i, 58:107] == 1) <= 3 &&
+       sum(Premer.13D[i, 58:107] >= 2) > 0 &&
+       (sum(Premer.13D[i, 58:107] > 0) /
+        length(Premer.13D[i, 58:107])) <= 0.75) {
+      incidence3[i] <- 4.5
+      next()
+   } else{
+      # If none of the conditions are met give the incidence zero
+      incidence3[i] <- 0
+   }
+
+}# end incidence loop
+
+if(any(incidence3 == 0)){
+   warning("Code caluculated incidence on '0' which is off the incidence scale")}
+
+# Re-format data-frame
+if(D_assess == "19 DAT1 19-3-2013"){
+   Premer.13D.1 <- Premer.13D[,c("Treat", "Rep", "Run", "Plot")]
+   Premer.13D.1$Inc_19D <-  incidence3}
+
+if(D_assess == "31 DAT1 31-3-2013"){
+   Premer.13D.2 <- Premer.13D[,c("Treat", "Rep", "Run", "Plot")]
+   Premer.13D.2$Inc_31D <-  incidence3}
+
+}# end disease assessment loop
+
+# The 19 Days after T1 only assessed the first 6 treatments
+# Therefore it will be dropped
+#Premer.13D <- left_join(Premer.13D.1,Premer.13D.2)
+Premer.13D <- Premer.13D.2
+
+# read in yield and format
+Premer.13Y <-
+   as.data.frame(
+      read_xlsx(
+         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1303 Fungicides for powdery mildew in mungbean - Premer.xlsx",
+         sheet = "Yield 18-4-2013",
+         range = "A14:F58",
+         col_names = TRUE
+      )
+   )
+Premer.13Y$Treat <- as.character(Premer.13Y$Treat)
+
+Premer_13 <- left_join(Premer.13D,Premer.13Y)
+
+```
+
+#### Define treatment data
+```{r Premer13_define_treat}
+
+Premer_13 <- Premer_13 %>%
+   mutate(trade_name = 
+             case_when(Treat == "1" ~ "control",
+                       Treat == "2" ~ "Spin-flo",
+                       Treat == "3" ~ "Tilt",
+                       Treat == "4" ~ "Amistar Xtra",
+                       Treat == "5" ~ "Amistar Xtra + adj",
+                       Treat == "6" ~ "Cabrio",
+                       Treat == "7" ~ "Spin-flo",
+                       Treat == "8" ~ "Tilt",
+                       Treat == "9" ~ "Amistar Xtra + adj",
+                       Treat == "10" ~ "Cabrio",
+                       Treat == "11" ~ "Tilt",
+                       TRUE ~ "other"))%>%
+   mutate(fungicide_ai = 
+             case_when(Treat == "1" ~ "control",
+                       Treat == "2" ~ "carbendazim",
+                       Treat == "3" ~ "propiconazole",
+                       Treat == "4" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "5" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "6" ~ "pyraclostrobin",
+                       Treat == "7" ~ "carbendazim",
+                       Treat == "8" ~ "propiconazole",
+                       Treat == "9" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "10" ~ "pyraclostrobin",
+                       Treat == "11" ~ "propiconazole",
+                       TRUE ~ "other"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Treat == "1" ~ 0,
+                       Treat == "2" ~ 250,
+                       Treat == "3" ~ 62.5,
+                       Treat == "4" ~ 40,
+                       Treat == "5" ~ 40,
+                       Treat == "6" ~ 125,
+                       Treat == "7" ~ 250,
+                       Treat == "8" ~ 62.5,
+                       Treat == "9" ~ 40,
+                       Treat == "10" ~ 125,
+                       Treat == "11" ~ 62.5,
+                       TRUE ~ 0))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Treat == "1" ~ as.Date(NA),
+                       Treat == "2" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "3" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "4" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "5" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "6" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "7" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Treat == "7" ~ as.Date("2013-03-19", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-03-19", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-03-19", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-03-19", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-03-19", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_3 = 
+             case_when(Treat == "11" ~ as.Date("2013-03-31", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Treat == "1" ~ 0,
+                       Treat == "2" ~ 1,
+                       Treat == "3" ~ 1,
+                       Treat == "4" ~ 1,
+                       Treat == "5" ~ 1,
+                       Treat == "6" ~ 1,
+                       Treat == "7" ~ 2,
+                       Treat == "8" ~ 2,
+                       Treat == "9" ~ 2,
+                       Treat == "10" ~ 2,
+                       Treat == "11" ~ 2, 
+                       TRUE ~ 0))
+```
+
+#### Input trial data
+```{r Prem13_Trialdat}
+
+Premer_13_dat <- 
+   data.frame(trial_ref = "AM1303",
+              year = "2013",
+              location = "Premer",
+              host_genotype = "Crystal",
+              trial_design = "RCB",
+              plot_length = 12,
+              plot_width = 4,
+              plant_density = as.Date(NA),
+              row_spacing = as.Date(NA),
+              replicate = Premer_13$Rep,
+              planting_date = as.Date("2013-12-28", format = "%Y-%m-%d"),
+              emergence_date = as.Date(NA),
+              flowering_date = as.Date("2013-02-28", format = "%Y-%m-%d"),
+              pod_fill_date = as.Date(NA),
+              mid_late_pod_fill = as.Date(NA),
+              first_sign_disease = as.Date("2013-02-28", format = "%Y-%m-%d"),
+              trade_name = as.factor(Premer_13$trade_name),
+              fungicide_ai = Premer_13$fungicide_ai,
+              dose_ai.ha = Premer_13$dose_ai.ha,
+              n_treatment = Premer_13$Treat,
+              fungicide_application_1 = Premer_13$fungicide_application_1,
+              fungicide_application_2 = Premer_13$fungicide_application_2,
+              fungicide_application_3 = Premer_13$fungicide_application_3,
+              total_fungicide = Premer_13$spray_n,
+              harvest_date = as.Date("2013-04-18", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2013-03-31", format = "%Y-%m-%d"),
+              PM_final_severity = Premer_13$Inc_31D,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(Premer_13$`Yield kg/ha`)/1000
+             # AUDPC = apply(Premer_13[,c("Inc_19D","Inc_31D")]-1,1, FUN = audpc, dates = c(19,12+19)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
+              )
+
+```
+
+#### Calculating the treatment means
+```{r Prem13_TreatmentMeans}
+Premer_13_m <- Premer_13_dat %>%
+   group_by(trial_ref, year, location, host_genotype, trial_design, 
+            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
+   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
+              plot_width.m. = mean(plot_width, na.rm = TRUE),
+              plant_density = unique(plant_density),
+              row_spacing = unique(row_spacing),
+              replicates = sum(as.numeric(replicate)),
+              planting_date = unique(planting_date),
+              emergence_date = NA,
+              flowering_date = unique(flowering_date),
+              pod_fill_date = unique(pod_fill_date),
+              mid_late_pod_fill = unique(mid_late_pod_fill),
+              first_sign_disease = unique(first_sign_disease),
+              fungicide_application_1 = unique(fungicide_application_1),
+              fungicide_application_2 = unique(fungicide_application_2),
+              fungicide_application_3 = unique(fungicide_application_3),
+              total_fungicide = unique(total_fungicide),
+              harvest_date = unique(harvest_date),
+              final_assessment = unique(final_assessment),
+              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+              rating_scale = unique(rating_scale),
+              disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+              D_error_type = "stdev",
+              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+              raw_graded = NA,
+              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+              Y_error_type = "stdev",
+             #AUDPC.m = mean(AUDPC),
+             #AUDPC.sd = sd(AUDPC),
+              meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Premer_13_dat))[2,3]
+   )
+
+Premer_13_m <- fold_data(Premer_13_m, PM_MB_means)
+
+Premer_13_m <- Premer_13_m[Premer_13_m$trade_name != "other",]
+
+write.csv(
+   Premer_13_m,
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1303-Premer-Disease_means.csv"
+)
+
+```

### 2019-11-18 191115_PMMB_DataWrangling_PM.Rmd
Premer 2013 added

@@
 ### Mary's Mount 2013
-```{r MarysM_13}
+#### Convert disease scores
+```{r MarysM_13_Convertdisease}
 
@@
 MarysM_13 <- left_join(MarysM.13D.1,MarysM.13Y)
-
+```
+
+#### Define treatment data
+```{r}
 MarysM_13 <- MarysM_13 %>%
@@
                        TRUE ~ 0))
-
+```
+
+#### Input trial data
+```{r Marys_TrialData}
 MarysM_13_dat <- 
@@
               )
-
+```
+
+#### Calculating the treatment means
+```{r Marys_means}
 MarysM_13_m <- MarysM_13_dat %>%
@@
 
-### Premer
+### Premer 2013
 #### Convert disease scores
@@
                        Treat == "10" ~ 2,
-                       Treat == "11" ~ 2, 
+                       Treat == "11" ~ 3, 
                        TRUE ~ 0))
@@
 
+# For some wierd reason standard deviations are comming back NA in the code above
+Premer_13_m[,c("disease_error","yield_error")] <- 
+   Premer_13_dat %>%
+   group_by(n_treatment) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("disease_error","yield_error"))
+
 Premer_13_m <- fold_data(Premer_13_m, PM_MB_means)
@@
 ```
+
+### Millmerran 2013
+#### Convert disease scores
+```{r Premer_13_convert_scores}
+
+for(D_assess in c("Assessment Sheet 5.4.2013","Assessment Sheet 24.4.2013")){
+
+# Import final disease survey
+Millm_13D <-
+   as.data.frame(
+      read_xlsx(
+         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/BB1305 Fungicides for powdery mildew in mungbean - Millmerran.xlsx",
+         sheet = D_assess,
+         range = "A12:AH56",
+         col_names = TRUE
+      )
+   )
+
+colnames(Millm_13D)[1:4] <- c("Run", "Plot", "Treat", "Rep")
+Millm_13D <- Millm_13D[order(Millm_13D[,1],Millm_13D[,2],Millm_13D[,3],Millm_13D[,4]),]
+
+sum(is.na(Millm_13D[, 5:34]))
+# replace NAs with zero Plots not surveyed
+for (i in 5:34) {
+   for (j in seq_along(Millm_13D[, i])) {
+      if (is.na(Millm_13D[j, i])) {
+         Millm_13D[j, i] <- 0
+      }
+   }
+}
+
+incidence4 <-
+   vector(mode = "numeric", length = length(Millm_13D[, 1]))
+
+# Calculate incidence
+#     Sites
+# low canopy  c(5:13)
+# mid canopy c(15:23)
+# upp canopy c(25:33)
+
+# Convert disease survey data to 1-9 Incidence rating scale
+for (i in seq_along(incidence4)) {
+   # incidence = 1
+   if (all(Millm_13D[i, c(5:13, 15:23, 25:33)] == 0)) {
+      incidence4[i] <- 1
+      next()
+   }
+
+   # incidence = 2
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       all(Millm_13D[i, 15:23] == 0) &&
+       all(Millm_13D[i, 25:33] == 0) &&
+       (sum(Millm_13D[i, c(5:13)] > 0) /
+        length(Millm_13D[i, c(5:13)])) <= 0.75) {
+      incidence4[i] <- 2
+      next()
+   }
+
+   # incidence = 3
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       sum(Millm_13D[i, 15:23] != 0) <= 3 &&
+       sum(Millm_13D[i, 25:33] == 0) == 0 &&
+       (sum(Millm_13D[i, c(5:13, 15:23)] > 0) /
+        length(Millm_13D[i, c(5:13, 15:23)])) >= 0.75) {
+      incidence4[i] <- 3
+   } else{
+      # if it is in the lower half of the canopy and in less than 75% of plants then incidence = 2.5
+      if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+          sum(Millm_13D[i, 15:23] != 0) <= 3 &&
+          sum(Millm_13D[i, 25:33] == 0) == 0 &&
+          (sum(Millm_13D[i, c(5:13, 15:23)] > 0) /
+           length(Millm_13D[i, c(5:13, 15:23)])) <= 0.75) {
+         incidence4[i] <- 2.5
+         next()
+      }
+   }
+
+   # incidence = 4
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       sum(Millm_13D[i, 15:23] != 0) >= 1 &&
+       all(Millm_13D[i, 25:33] == 0) &&
+       (sum(Millm_13D[i, c(5:13, 15:23)] > 0) /
+        length(Millm_13D[i, c(5:13, 15:23)])) <= 0.75) {
+      incidence4[i] <- 4
+      next()
+   }
+
+   # incidence = 5
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       sum(Millm_13D[i, 15:23] != 0) >= 1 &&
+       all(Millm_13D[i, 25:33] == 0) &&
+       (sum(Millm_13D[i, c(5:13, 15:23)] > 0) /
+        length(Millm_13D[i, c(5:13, 15:23)])) >= 0.75) {
+      incidence4[i] <- 5
+      next()
+   }
+
+   # incidence = 6
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       sum(Millm_13D[i, 15:23] != 0) >= 1 &&
+       all(Millm_13D[i, 25:33] == 0) &&
+       (sum(Millm_13D[i, c(5:13, 15:23)] > 0) /
+        length(Millm_13D[i, c(5:13, 15:23)])) >= 0.90) {
+      incidence4[i] <- 6
+      next()
+   }
+
+   # incidence = 7
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       sum(Millm_13D[i, 15:23] != 0) >= 1 &&
+       sum(Millm_13D[i, 25:33] != 0) <= 3 &&
+       (sum(Millm_13D[i, c(5:13, 15:23)] > 0) /
+        length(Millm_13D[i, c(5:13, 15:23)])) >= 0.90) {
+      incidence4[i] <- 7
+      next()
+   }
+
+   # incidence = 8
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       sum(Millm_13D[i, 15:23] != 0) >= 1 &&
+       sum(Millm_13D[i, 25:33] != 0) >= 1 &&
+       (sum(Millm_13D[i, c(5:13, 15:23, 25:33)] > 0) /
+        length(Millm_13D[i, c(5:13, 15:23, 25:33)])) >= 0.75) {
+      incidence4[i] <- 8
+      next()
+   }
+
+   # incidence = 9
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       sum(Millm_13D[i, 15:23] != 0) >= 1 &&
+       sum(Millm_13D[i, 25:33] != 0) >= 1 &&
+       (sum(Millm_13D[i, c(5:13, 15:23, 25:33)] > 0) /
+        length(Millm_13D[i, c(5:13, 15:23, 25:33)])) >= 0.75 &&
+       sum(Millm_13D[i, c(5:13, 15:23, 25:33)]) > (9 * 3 * 100) * 0.75) {
+      incidence4[i] <- 9
+      next()
+   }
+
+   # if there are few (< 10%) leaves with very small infections in all parts of the canopy OR
+   # if there is a stray colony on a upper leaf in addition to all lower
+
+   if (sum(Millm_13D[i, 15:23] != 0) <= 3 &&
+       sum(Millm_13D[i, 25:33] != 0) <= 3 &&
+       (sum(Millm_13D[i, c(5:13, 15:23, 25:33)]) /
+        length(Millm_13D[i, c(5:13, 15:23, 25:33)]) / 100) <= 0.1) {
+      incidence4[i] <- 2.5
+      next()
+   }
+
+   # incidence = 7.5  In the upper canopy with less than 75% plants infected
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       sum(Millm_13D[i, 15:23] != 0) >= 1 &&
+       sum(Millm_13D[i, 25:33] != 0) >= 3 &&
+       (sum(Millm_13D[i, c(5:13, 15:23, 25:33)] > 0) /
+        length(Millm_13D[i, c(5:13, 15:23, 25:33)])) <= 0.75) {
+      incidence4[i] <- 7.5
+      next()
+   }
+
+   # if there are few more colonies(< 10%) leaves with very small infections in all parts of the canopy OR
+   # if there is a stray colony on a upper leaf in addition to all lower
+
+   if (sum(Millm_13D[i, 15:23] != 0) <= 6 &&
+       sum(Millm_13D[i, 25:33] != 0) <= 3 &&
+       (sum(Millm_13D[i, c(5:13, 15:23, 25:33)]) /
+        length(Millm_13D[i, c(5:13, 15:23, 25:33)]) / 100) <= 0.1) {
+      incidence4[i] <- 3.5
+      next()
+   }
+
+   if (sum(Millm_13D[i, 15:23] != 0) >= 1 &&
+       sum(Millm_13D[i, 25:33] != 0) <= 3 &&
+       (sum(Millm_13D[i, c(5:13, 15:23, 25:33)]) /
+        length(Millm_13D[i, c(5:13, 15:23, 25:33)]) / 100) <= 0.5) {
+      incidence4[i] <- 6.5
+      next()
+   }
+   else{
+      # If none of the conditions are met give the incidence zero
+      incidence4[i] <- 0
+   }
+}
+# end incidence loop
+
+if(any(incidence3 == 0)){
+   warning("Code caluculated incidence on '0' which is off the incidence scale")}
+
+# Re-format data-frame
+if(D_assess == "Assessment Sheet 5.4.2013"){
+   Millm_13D.1 <- Millm_13D[,c("Treat", "Rep", "Run", "Plot")]
+   Millm_13D.1$Inc_23D <-  incidence4}
+
+if(D_assess == "Assessment Sheet 24.4.2013"){
+   Millm_13D.2 <- Millm_13D[,c("Treat", "Rep", "Run", "Plot")]
+   Millm_13D.2$Inc_42D <-  incidence4}
+
+}# end disease assessment loop
+
+# The 19 Days after T1 only assessed the first 6 treatments
+# Therefore it will be dropped
+Millm_13D <- left_join(Millm_13D.1, Millm_13D.2)
+
+# read in yield and format
+# read in yield and format
+Millm.13Y <-
+   as.data.frame(
+      read_xlsx(
+         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/BB1305 Fungicides for powdery mildew in mungbean - Millmerran.xlsx",
+         sheet = "Harvest Sheet 6.5.2013",
+         range = "A11:F55",
+         col_names = TRUE
+      )
+   )
+Millm.13Y$Treatment <- as.character(Millm.13Y$Treatment)
+colnames(Millm.13Y)[1:4] <- c("Run", "Plot","Treat", "Rep")
+
+Millm_13 <- left_join(Millm_13D,Millm.13Y)
+
+```
+
+#### Define treatment data
+```{r Millm_13_define_treat}
+
+Millm_13 <- Millm_13 %>%
+   mutate(trade_name = 
+             case_when(Treat == "1" ~ "control",
+                       Treat == "2" ~ "Spin-flo",
+                       Treat == "3" ~ "Tilt",
+                       Treat == "4" ~ "Amistar Xtra",
+                       Treat == "5" ~ "Amistar Xtra + adj",
+                       Treat == "6" ~ "Cabrio",
+                       Treat == "7" ~ "Spin-flo",
+                       Treat == "8" ~ "Tilt",
+                       Treat == "9" ~ "Amistar Xtra + adj",
+                       Treat == "10" ~ "Cabrio",
+                       Treat == "11" ~ "Tilt",
+                       TRUE ~ "other"))%>%
+   mutate(fungicide_ai = 
+             case_when(Treat == "1" ~ "control",
+                       Treat == "2" ~ "carbendazim",
+                       Treat == "3" ~ "propiconazole",
+                       Treat == "4" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "5" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "6" ~ "pyraclostrobin",
+                       Treat == "7" ~ "carbendazim",
+                       Treat == "8" ~ "propiconazole",
+                       Treat == "9" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "10" ~ "pyraclostrobin",
+                       Treat == "11" ~ "propiconazole",
+                       TRUE ~ "other"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Treat == "1" ~ 0,
+                       Treat == "2" ~ 250,
+                       Treat == "3" ~ 62.5,
+                       Treat == "4" ~ 40,
+                       Treat == "5" ~ 40,
+                       Treat == "6" ~ 125,
+                       Treat == "7" ~ 250,
+                       Treat == "8" ~ 62.5,
+                       Treat == "9" ~ 40,
+                       Treat == "10" ~ 125,
+                       Treat == "11" ~ 62.5,
+                       TRUE ~ 0))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Treat == "1" ~ as.Date(NA),
+                       Treat == "2" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "3" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "4" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "5" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "6" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "7" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Treat == "7" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_3 = 
+             case_when(Treat == "11" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Treat == "1" ~ 0,
+                       Treat == "2" ~ 1,
+                       Treat == "3" ~ 1,
+                       Treat == "4" ~ 1,
+                       Treat == "5" ~ 1,
+                       Treat == "6" ~ 1,
+                       Treat == "7" ~ 2,
+                       Treat == "8" ~ 2,
+                       Treat == "9" ~ 2,
+                       Treat == "10" ~ 2,
+                       Treat == "11" ~ 3, 
+                       TRUE ~ 0))
+```
+
+#### Input trial data
+```{r Millm13_Trialdat}
+
+Millm_13_dat <- 
+   data.frame(trial_ref = "BB1305",
+              year = "2013",
+              location = "Millmerran",
+              host_genotype = "Crystal",
+              trial_design = "RCB",
+              plot_length = 12,
+              plot_width = 4,
+              plant_density = as.Date(NA),
+              row_spacing = 1/3,
+              replicate = Millm_13$Rep,
+              planting_date = as.Date(NA),
+              emergence_date = as.Date(NA),
+              flowering_date = as.Date(NA),
+              pod_fill_date = as.Date("2013-03-21", format = "%Y-%m-%d"),
+              mid_late_pod_fill = as.Date("2013-03-28", format = "%Y-%m-%d"),
+              first_sign_disease = as.Date("2013-03-13", format = "%Y-%m-%d"),
+              trade_name = as.factor(Millm_13$trade_name),
+              fungicide_ai = Millm_13$fungicide_ai,
+              dose_ai.ha = Millm_13$dose_ai.ha,
+              n_treatment = Millm_13$Treat,
+              fungicide_application_1 = Millm_13$fungicide_application_1,
+              fungicide_application_2 = Millm_13$fungicide_application_2,
+              fungicide_application_3 = Millm_13$fungicide_application_3,
+              total_fungicide = Millm_13$spray_n,
+              harvest_date = as.Date("2013-05-06", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2013-04-24", format = "%Y-%m-%d"),
+              PM_final_severity = Millm_13$Inc_42D,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(Millm_13$`kg/Ha`)/1000,
+              AUDPC = apply(Millm_13[,c("Inc_23D","Inc_42D")]-1,1, FUN = audpc, dates = c(23,42)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
+              )
+
+```
+
+#### Calculating the treatment means
+```{r Millm13_TreatmentMeans}
+Millm_13_m <- Millm_13_dat %>%
+   group_by(trial_ref, year, location, host_genotype, trial_design, 
+            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
+   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
+             plot_width.m. = mean(plot_width, na.rm = TRUE),
+             plant_density = unique(plant_density),
+             row_spacing = unique(row_spacing),
+             replicates = length(as.numeric(replicate)),
+             planting_date = unique(planting_date),
+             emergence_date = NA,
+             flowering_date = unique(flowering_date),
+             pod_fill_date = unique(pod_fill_date),
+             mid_late_pod_fill = unique(mid_late_pod_fill),
+             first_sign_disease = unique(first_sign_disease),
+             fungicide_application_1 = unique(fungicide_application_1),
+             fungicide_application_2 = unique(fungicide_application_2),
+             fungicide_application_3 = unique(fungicide_application_3),
+             total_fungicide = unique(total_fungicide),
+             harvest_date = unique(harvest_date),
+             final_assessment = unique(final_assessment),
+             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+             rating_scale = unique(rating_scale),
+             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+             D_error_type = "stdev",
+             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+             raw_graded = NA,
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+             Y_error_type = "stdev",
+             AUDPC.m = mean(AUDPC),
+             AUDPC.sd = sd(AUDPC),
+             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Millm_13_dat))[2,3]
+   )
+
+# For some wierd reason standard deviations are comming back NA in the code above
+Millm_13_m[,c("disease_error","yield_error")] <- 
+   Millm_13_dat %>%
+   group_by(n_treatment) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("disease_error","yield_error"))
+
+Millm_13_m <- fold_data(Millm_13_m, PM_MB_means)
+
+Millm_13_m <- Millm_13_m[Millm_13_m$trade_name != "other",]
+
+write.csv(
+   Millm_13_m,
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/BB1305_Millmerran_means.csv"
+)
+
+```
+
+### Hermitage 2015
+```{r Herm_15}
+# ____________________________________________________________
+# _____________            Hermitage  2015        ____________
+
+# Yield data from 2016 Hermitage trial with final disease severity
+Herm_15 <-
+   read.xlsx(
+      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2015 PMmung Herm/Mugbean powdery mildew 2014-15 inc results v2.xlsx",
+      sheet = "HRS yield data",
+      startRow = 4,
+      colNames = TRUE,
+      detectDates = TRUE
+   )[1:31, 1:9]
+
+Herm_15$Year <- 2015
+Herm_15$location <- "Hermitage"
+
+# Disease incidence assessments through the 2016 season
+Herm_15.DR  <-
+   read.xlsx(
+      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2015 PMmung Herm/Mugbean powdery mildew 2014-15 inc results v2.xlsx",
+      sheet = "HRS ratings & graphs",
+      startRow = 5,
+      colNames = TRUE
+   )[1:31, 1:8]
+
+Herm_15$Plot.Length <- as.numeric(Herm_15$Plot.Length)
+Herm_15$Plot.Weight <- as.numeric(Herm_15$Plot.Weight)
+Herm_15$Plot.weight <- as.numeric(Herm_15$Plot.weight)
+Herm_15$`Plot.Yield.(kg/ha)` <-
+   as.numeric(Herm_15$`Plot.Yield.(kg/ha)`)
+Herm_15$`Plot.Yield.(t/ha)` <-
+   as.numeric(Herm_15$`Plot.Yield.(t/ha)`)
+
+#as.numeric(unlist(strsplit(Herm_15.DR$Treatment,)))
+Herm_15$disease_severity <- as.numeric(Herm_15.DR[, 8])
+
+unique(Herm_15.DR$Treatment)
+Herm_15.DR[is.na(Herm_15.DR$Treatment),]
+```
+
+```{r Herm_15_Treats}
+
+Millm_13 <- Herm_15.DR %>%
+   mutate(trade_name = 
+             case_when(Treatment == "control" ~ "control",
+                       TRUE ~ "Folicur"))%>%
+   mutate(fungicide_ai = 
+             case_when(Treat == "1" ~ "control",
+                       Treat == "2" ~ "carbendazim",
+                       Treat == "3" ~ "propiconazole",
+                       Treat == "4" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "5" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "6" ~ "pyraclostrobin",
+                       Treat == "7" ~ "carbendazim",
+                       Treat == "8" ~ "propiconazole",
+                       Treat == "9" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "10" ~ "pyraclostrobin",
+                       Treat == "11" ~ "propiconazole",
+                       TRUE ~ "other"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Treat == "1" ~ 0,
+                       Treat == "2" ~ 250,
+                       Treat == "3" ~ 62.5,
+                       Treat == "4" ~ 40,
+                       Treat == "5" ~ 40,
+                       Treat == "6" ~ 125,
+                       Treat == "7" ~ 250,
+                       Treat == "8" ~ 62.5,
+                       Treat == "9" ~ 40,
+                       Treat == "10" ~ 125,
+                       Treat == "11" ~ 62.5,
+                       TRUE ~ 0))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Treat == "1" ~ as.Date(NA),
+                       Treat == "2" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "3" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "4" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "5" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "6" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "7" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Treat == "7" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_3 = 
+             case_when(Treat == "11" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Treat == "1" ~ 0,
+                       Treat == "2" ~ 1,
+                       Treat == "3" ~ 1,
+                       Treat == "4" ~ 1,
+                       Treat == "5" ~ 1,
+                       Treat == "6" ~ 1,
+                       Treat == "7" ~ 2,
+                       Treat == "8" ~ 2,
+                       Treat == "9" ~ 2,
+                       Treat == "10" ~ 2,
+                       Treat == "11" ~ 3, 
+                       TRUE ~ 0))
+```
+
+Herm_15_m <- as.data.table(Herm_15[, c(4, 5, 7:12)] %>%
+                              group_by(`Year`, `location`, `Treatment`) %>%
+                              summarise_all(list( ~ mean(., na.rm = TRUE),  ~ sd(., na.rm = TRUE))))
+
+write.csv(
+   Herm_15_m[2:7, ],
+   "C:/Users/U8011054/OneDrive - USQ/Cloudstor/R/Powdery_mildew_Mungbean/Herm_15_means.csv"
+)
+
+```

### 2019-11-18 191115_PMMB_DataWrangling_PM.Rmd
Save it before I loose it

@@
 ```{r Herm_15}
-# ____________________________________________________________
-# _____________            Hermitage  2015        ____________
-
-# Yield data from 2016 Hermitage trial with final disease severity
+
 Herm_15 <-
@@
 
-unique(Herm_15.DR$Treatment)
-Herm_15.DR[is.na(Herm_15.DR$Treatment),]
-```
-
+Herm_15.DR <- Herm_15.DR[!is.na(Herm_15.DR$Treatment),]
+```
+
+#### Define treatment data
 ```{r Herm_15_Treats}
 
-Millm_13 <- Herm_15.DR %>%
+Herm_15_dat <- Herm_15.DR %>%
    mutate(trade_name = 
@@
    mutate(fungicide_ai = 
-             case_when(Treat == "1" ~ "control",
-                       Treat == "2" ~ "carbendazim",
-                       Treat == "3" ~ "propiconazole",
-                       Treat == "4" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
-                       Treat == "5" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
-                       Treat == "6" ~ "pyraclostrobin",
-                       Treat == "7" ~ "carbendazim",
-                       Treat == "8" ~ "propiconazole",
-                       Treat == "9" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
-                       Treat == "10" ~ "pyraclostrobin",
-                       Treat == "11" ~ "propiconazole",
-                       TRUE ~ "other"))%>%
+             case_when(Treatment == "control" ~ "control",
+                       TRUE ~ "tebuconazole"))%>%
    mutate(dose_ai.ha = 
-             case_when(Treat == "1" ~ 0,
-                       Treat == "2" ~ 250,
-                       Treat == "3" ~ 62.5,
-                       Treat == "4" ~ 40,
-                       Treat == "5" ~ 40,
-                       Treat == "6" ~ 125,
-                       Treat == "7" ~ 250,
-                       Treat == "8" ~ 62.5,
-                       Treat == "9" ~ 40,
-                       Treat == "10" ~ 125,
-                       Treat == "11" ~ 62.5,
-                       TRUE ~ 0))%>%
+             case_when(Treatment == "control" ~ 0,
+                       TRUE ~ 62.35))%>%
    mutate(fungicide_application_1 = 
-             case_when(Treat == "1" ~ as.Date(NA),
-                       Treat == "2" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
-                       Treat == "3" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
-                       Treat == "4" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
-                       Treat == "5" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
-                       Treat == "6" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
-                       Treat == "7" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
-                       Treat == "8" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
-                       Treat == "9" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
-                       Treat == "10" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
-                       Treat == "11" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+             case_when(Treatment == "1st sign +1" ~ as.Date("2015-03-17", format = "%Y-%m-%d"),
+                       Treatment == "control" ~ as.Date(NA),
+                       Treatment == "1st sign" ~ as.Date("2015-03-17", format = "%Y-%m-%d"),
+                       Treatment == "1/3C + 1" ~ as.Date("2015-03-23", format = "%Y-%m-%d"),
+                       Treatment == "5wks+2" ~ as.Date("2015-03-02", format = "%Y-%m-%d"),
+                       Treatment == "1/3C" ~ as.Date("2015-03-23", format = "%Y-%m-%d"),
                        TRUE ~ as.Date(NA)))%>%
    mutate(fungicide_application_2 = 
-             case_when(Treat == "7" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
-                       Treat == "8" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
-                       Treat == "9" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
-                       Treat == "10" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
-                       Treat == "11" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
+             case_when(Treatment == "1st sign +1" ~ as.Date("2015-03-31", format = "%Y-%m-%d"),
+                       Treatment == "control" ~ as.Date(NA),
+                       Treatment == "1/3C + 1" ~ as.Date("2015-04-07", format = "%Y-%m-%d"),
+                       Treatment == "5wks+2" ~ as.Date("2015-03-17", format = "%Y-%m-%d"),
                        TRUE ~ as.Date(NA)))%>%
    mutate(fungicide_application_3 = 
-             case_when(Treat == "11" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+             case_when(Treatment == "5wks+2" ~ as.Date("2015-03-31", format = "%Y-%m-%d"),
                        TRUE ~ as.Date(NA)))%>%
    mutate(spray_n = 
-             case_when(Treat == "1" ~ 0,
-                       Treat == "2" ~ 1,
-                       Treat == "3" ~ 1,
-                       Treat == "4" ~ 1,
-                       Treat == "5" ~ 1,
-                       Treat == "6" ~ 1,
-                       Treat == "7" ~ 2,
-                       Treat == "8" ~ 2,
-                       Treat == "9" ~ 2,
-                       Treat == "10" ~ 2,
-                       Treat == "11" ~ 3, 
-                       TRUE ~ 0))
-```
+             case_when(Treatment == "1st sign +1" ~ 2,
+                       Treatment == "control" ~ 0,
+                       Treatment == "1st sign" ~ 1,
+                       Treatment == "1/3C + 1" ~ 2,
+                       Treatment == "5wks+2" ~ 3,
+                       Treatment == "1/3C" ~ 1,
+                       TRUE ~ 9999))
+Herm_15_dat
+
+```
+
+#### Input trial data
+```{r Herm15_Trialdat}
+
+Herm_15_dat <- 
+   data.frame(trial_ref = "mung1415/01",
+              year = "2015",
+              location = "Hermitage",
+              host_genotype = "Jade",
+              trial_design = "RCB",
+              plot_length = 12,
+              plot_width = 4,
+              plant_density = NA,
+              row_spacing = 0.75,
+              replicate = Herm_15_dat$Rep,
+              planting_date = as.Date("2015-01-19", format = "%Y-%m-%d"),
+              emergence_date = as.Date("2015-01-24", format = "%Y-%m-%d"),
+              flowering_date = as.Date(NA),
+              pod_fill_date = as.Date(NA),
+              mid_late_pod_fill = as.Date(NA),
+              first_sign_disease = as.Date("2013-03-16", format = "%Y-%m-%d"),
+              trade_name = as.factor(Herm_15_dat$trade_name),
+              fungicide_ai = Herm_15_dat$fungicide_ai,
+              dose_ai.ha = Herm_15_dat$dose_ai.ha,
+              n_treatment = Herm_15_dat$Treat,
+              fungicide_application_1 = Herm_15_dat$fungicide_application_1,
+              fungicide_application_2 = Herm_15_dat$fungicide_application_2,
+              fungicide_application_3 = Herm_15_dat$fungicide_application_3,
+              total_fungicide = Herm_15_dat$spray_n,
+              harvest_date = as.Date("2013-04-20", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2013-04-06", format = "%Y-%m-%d"),
+              PM_final_severity = Herm_15_dat$Inc_42D,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(Herm_15_dat$`kg/Ha`)/1000,
+              AUDPC = apply(Herm_15_dat[,c("Inc_23D","Inc_42D")]-1,1, FUN = audpc, dates = c(23,42)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
+              )
+
+```
+
+```{r}
 

### 2019-11-19 191115_PMMB_DataWrangling_PM.Rmd
Hermitage 2015 wrangled

@@
 ## Import Libraries
-```{r}
+```{r message=FALSE, warning=FALSE}
 # install.packages("openxlsx")
@@
 # install.packages("tidyr")
-install.packages("agricolae")
+# install.packages("agricolae")
 
@@
 
-#as.numeric(unlist(strsplit(Herm_15.DR$Treatment,)))
-Herm_15$disease_severity <- as.numeric(Herm_15.DR[, 8])
-
+# Rename the plot column and remove lines without data
+colnames(Herm_15)[3] <- "Plot"
 Herm_15.DR <- Herm_15.DR[!is.na(Herm_15.DR$Treatment),]
+
+# rename the disease assesment columns
+# For comparing between trials I am forcing the assumption 
+#   that the disease did not exist prior to it being spotted in the trial. 
+#   Therefore day0 observes zero disease and day1 is first sign
+colnames(Herm_15.DR)[4:8] <- c("day0", "day1", "day8", "day15","day22") 
+Herm_15.DR$day0 <- as.numeric(Herm_15.DR$day0)
+Herm_15.DR$day1 <- as.numeric(Herm_15.DR$day1)
+Herm_15.DR$day8 <- as.numeric(Herm_15.DR$day8)
+Herm_15.DR$day15 <- as.numeric(Herm_15.DR$day15)
+Herm_15.DR$day22 <- as.numeric(Herm_15.DR$day22)
+
+# Merge yield and disease data
+Herm_15 <- left_join(Herm_15.DR, Herm_15)
+
 ```
@@
 
-Herm_15_dat <- Herm_15.DR %>%
+Herm_15_dat <- Herm_15 %>%
    mutate(trade_name = 
@@
                        TRUE ~ 9999))
-Herm_15_dat
 
@@
               mid_late_pod_fill = as.Date(NA),
-              first_sign_disease = as.Date("2013-03-16", format = "%Y-%m-%d"),
+              first_sign_disease = as.Date("2015-03-16", format = "%Y-%m-%d"),
               trade_name = as.factor(Herm_15_dat$trade_name),
@@
               total_fungicide = Herm_15_dat$spray_n,
-              harvest_date = as.Date("2013-04-20", format = "%Y-%m-%d"),
-              final_assessment = as.Date("2013-04-06", format = "%Y-%m-%d"),
-              PM_final_severity = Herm_15_dat$Inc_42D,
+              harvest_date = as.Date("2015-04-20", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2015-04-06", format = "%Y-%m-%d"),
+              PM_final_severity = Herm_15_dat$day22,
               rating_scale = "1-9",
-              grain_yield.t.ha. = as.numeric(Herm_15_dat$`kg/Ha`)/1000,
-              AUDPC = apply(Herm_15_dat[,c("Inc_23D","Inc_42D")]-1,1, FUN = audpc, dates = c(23,42)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
+              grain_yield.t.ha. = as.numeric(Herm_15_dat$`Plot.Yield.(t/ha)`),
+              AUDPC = apply(Herm_15_dat[,c("day0", "day1", "day8", "day15","day22")]-1,1, 
+                            FUN = audpc, dates = c(0,1,8,15,22)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
               )
@@
 
+#### Calculating treatment means
 ```{r}
-
-Herm_15_m <- as.data.table(Herm_15[, c(4, 5, 7:12)] %>%
-                              group_by(`Year`, `location`, `Treatment`) %>%
-                              summarise_all(list( ~ mean(., na.rm = TRUE),  ~ sd(., na.rm = TRUE))))
+Herm_15_m <- Herm_15_dat %>%
+   group_by(trial_ref, year, location, host_genotype, trial_design, 
+            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
+   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
+             plot_width.m. = mean(plot_width, na.rm = TRUE),
+             plant_density = unique(plant_density),
+             row_spacing = unique(row_spacing),
+             replicates = length(as.numeric(replicate)),
+             planting_date = unique(planting_date),
+             emergence_date = unique(emergence_date),
+             flowering_date = unique(flowering_date),
+             pod_fill_date = unique(pod_fill_date),
+             mid_late_pod_fill = unique(mid_late_pod_fill),
+             first_sign_disease = unique(first_sign_disease),
+             fungicide_application_1 = unique(fungicide_application_1),
+             fungicide_application_2 = unique(fungicide_application_2),
+             fungicide_application_3 = unique(fungicide_application_3),
+             total_fungicide = unique(total_fungicide),
+             harvest_date = unique(harvest_date),
+             final_assessment = unique(final_assessment),
+             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+             rating_scale = unique(rating_scale),
+             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+             D_error_type = "stdev",
+             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+             raw_graded = NA,
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+             Y_error_type = "stdev",
+             AUDPC.m = mean(AUDPC),
+             AUDPC.sd = sd(AUDPC),
+             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Herm_15_dat))[2,3]
+   )
+
+# For some wierd reason standard deviations are comming back NA in the code above
+Herm_15_m[,c("disease_error","yield_error")] <- 
+   Herm_15_dat %>%
+   group_by(n_treatment) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("disease_error","yield_error"))
+
+Herm_15_m <- fold_data(Herm_15_m, PM_MB_means)
 
 write.csv(
-   Herm_15_m[2:7, ],
-   "C:/Users/U8011054/OneDrive - USQ/Cloudstor/R/Powdery_mildew_Mungbean/Herm_15_means.csv"
+   Herm_15_m,
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2015 PMmung Herm/Herm_15_means.csv"
 )

### 2019-11-19 191115_PMMB_DataWrangling_PM.Rmd
Hermitage 2015, 2016 and Kingaroy 2016 wrangled

@@
 Herm_15_dat <- Herm_15 %>%
+   mutate(n_treatment = 
+             case_when(Treatment == "1st sign +1" ~ 4,
+                       Treatment == "control" ~ 1,
+                       Treatment == "1st sign" ~ 3,
+                       Treatment == "1/3C + 1" ~ 6,
+                       Treatment == "5wks+2" ~ 2,
+                       Treatment == "1/3C" ~ 5,
+                       TRUE ~ 9998))%>%
    mutate(trade_name = 
@@
               dose_ai.ha = Herm_15_dat$dose_ai.ha,
-              n_treatment = Herm_15_dat$Treat,
+              n_treatment = as.numeric(Herm_15_dat$n_treatment),
               fungicide_application_1 = Herm_15_dat$fungicide_application_1,
@@
 #### Calculating treatment means
-```{r}
+```{r Herm15_means}
 Herm_15_m <- Herm_15_dat %>%
-   group_by(trial_ref, year, location, host_genotype, trial_design, 
-            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
-   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
+   group_by(host_genotype, n_treatment) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             location = unique(location),
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             fungicide_ai = unique(fungicide_ai),
+             dose_ai.ha = unique(dose_ai.ha),
+             trial_ref = unique(trial_ref),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
@@
 
-```
+Herm_16
+```
+
+### Hermitage 2016  
+Disease data for Hermitage 2016 only exists as a mean of treatments within the `2016 Mungbean PM trials summary.xlsx` file.  
+```{r Herm16_dataimport}
+# Yield data from 2016 Hermitage trial with final disease severity
+Herm_16 <-
+   read.xlsx(
+      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2016/Yeild Data 2016 Kingaroy Hermitage (PaulM adjusted).xlsx",
+      sheet = "Hermitage",
+      startRow = 1,
+      colNames = TRUE
+   )[1:28, 1:9]
+
+Herm_16$Year <- 2016
+Herm_16$location <- "Hermitage"
+
+Herm_16$Plot <- as.numeric(unlist(strsplit(
+   Herm_16$Plot, "P"))[
+      seq(from = 2, to = 56, by = 2)])
+
+unique(Herm_16$Treatment)
+```
+
+#### Define treatment data
+```{r Herm16_treatmentDefine}
+Herm_16_dat <- Herm_16 %>%
+   mutate(trade_name = 
+             case_when(Treatment == "1" ~ "control",
+                       TRUE ~ "Folicur"))%>%
+   mutate(fungicide_ai = 
+             case_when(Treatment == "1" ~ "control",
+                       TRUE ~ "tebuconazole"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Treatment == "1" ~ 0,
+                       TRUE ~ 62.35))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Treatment == "1" ~ as.Date(NA),
+                       Treatment == "2" ~ as.Date("2016-03-17", format = "%Y-%m-%d"),
+                       Treatment == "3" ~ as.Date("2016-03-17", format = "%Y-%m-%d"),
+                       Treatment == "4" ~ as.Date("2016-03-17", format = "%Y-%m-%d"),
+                       Treatment == "5" ~ as.Date("2016-03-8", format = "%Y-%m-%d"),
+                       Treatment == "6" ~ as.Date("2016-03-8", format = "%Y-%m-%d"),
+                       Treatment == "7" ~ as.Date("2016-03-17", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Treatment == "1" ~ as.Date(NA),
+                       Treatment == "3" ~ as.Date("2016-03-30", format = "%Y-%m-%d"),
+                       Treatment == "4" ~ as.Date("2016-03-30", format = "%Y-%m-%d"),
+                       Treatment == "6" ~ as.Date("2016-03-22", format = "%Y-%m-%d"),
+                       Treatment == "7" ~ as.Date("2016-03-30", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_3 = 
+             case_when(Treatment == "4" ~ as.Date("2016-04-13", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Treatment == "1" ~ 0,
+                       Treatment == "2" ~ 1,
+                       Treatment == "3" ~ 2,
+                       Treatment == "4" ~ 3,
+                       Treatment == "5" ~ 1,
+                       Treatment == "6" ~ 2,
+                       Treatment == "7" ~ 2,
+                       TRUE ~ 9999))
+
+```
+
+#### Input trial data
+```{r Herm15_Trialdat}
+
+Herm_16_dat <- 
+   data.frame(trial_ref = "mung1516/01",
+              year = "2016",
+              location = "Hermitage",
+              host_genotype = "Jade",
+              trial_design = "RCB",
+              plot_length = 12,
+              plot_width = 4,
+              plant_density = NA,
+              row_spacing = 0.75,
+              replicate = Herm_16_dat$rep,
+              planting_date = as.Date("2016-02-03", format = "%Y-%m-%d"),
+              emergence_date = as.Date("2016-02-12", format = "%Y-%m-%d"),
+              flowering_date = as.Date(NA),
+              pod_fill_date = as.Date(NA),
+              mid_late_pod_fill = as.Date("2016-04-15", format = "%Y-%m-%d"),
+              first_sign_disease = as.Date("2016-03-08", format = "%Y-%m-%d"),
+              trade_name = as.factor(Herm_16_dat$trade_name),
+              fungicide_ai = Herm_16_dat$fungicide_ai,
+              dose_ai.ha = Herm_16_dat$dose_ai.ha,
+              n_treatment = as.numeric(Herm_16_dat$Treatment),
+              fungicide_application_1 = Herm_16_dat$fungicide_application_1,
+              fungicide_application_2 = Herm_16_dat$fungicide_application_2,
+              fungicide_application_3 = Herm_16_dat$fungicide_application_3,
+              total_fungicide = Herm_16_dat$spray_n,
+              harvest_date = as.Date("2015-05-06", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2015-04-15", format = "%Y-%m-%d"),
+              PM_final_severity = NA,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(Herm_16_dat$`Raw.Adjusted.Yeild./.ha`)
+              )
+```
+
+#### Calculating treatment means
+```{r Herm16_means}
+Herm_16_m <- Herm_16_dat %>%
+   group_by(host_genotype, n_treatment) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             location = unique(location),
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             fungicide_ai = unique(fungicide_ai),
+             dose_ai.ha = unique(dose_ai.ha),
+             trial_ref = unique(trial_ref),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
+             plot_width.m. = mean(plot_width, na.rm = TRUE),
+             plant_density = unique(plant_density),
+             row_spacing = unique(row_spacing),
+             replicates = length(as.numeric(replicate)),
+             planting_date = unique(planting_date),
+             emergence_date = unique(emergence_date),
+             flowering_date = unique(flowering_date),
+             pod_fill_date = unique(pod_fill_date),
+             mid_late_pod_fill = unique(mid_late_pod_fill),
+             first_sign_disease = unique(first_sign_disease),
+             fungicide_application_1 = unique(fungicide_application_1),
+             fungicide_application_2 = unique(fungicide_application_2),
+             fungicide_application_3 = unique(fungicide_application_3),
+             total_fungicide = unique(total_fungicide),
+             harvest_date = unique(harvest_date),
+             final_assessment = unique(final_assessment),
+             #PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+             rating_scale = unique(rating_scale),
+             #disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+             #D_error_type = "stdev",
+             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+             raw_graded = "Yes",
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+             Y_error_type = "stdev",
+             #AUDPC.m = mean(AUDPC),
+             #AUDPC.sd = sd(AUDPC),
+             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Herm_16_dat))[2,3]
+   )
+
+# For some wierd reason standard deviations are comming back NA in the code above
+Herm_16_m[,"yield_error"] <- 
+   Herm_16_dat %>%
+   group_by(n_treatment) %>%
+   summarise(yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("yield_error"))
+
+# Mean Disease incidence assessments through the 2016 season
+Herm_16.DR  <-
+   read.xlsx(
+      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2016/2016 Mungbean PM trials summary.xlsx",
+      sheet = "Hermitage_2016",
+      startRow = 5,
+      colNames = TRUE
+   )
+names(Herm_16.DR)[1:6] <- c("Treatment", "dae24","dae38","dae48","dae63","Final_Yield_tHa")
+names(Herm_16.DR)[6] <- "Final_Yield_tHa"
+Herm_16.DR$n_treatment <- c(4,3,7,5,2,6,1)
+
+Herm_16_m
+
+Herm_16_m <- left_join(Herm_16_m,Herm_16.DR)
+Herm_16_m$AUDPC.m <- apply(Herm_16_m[,c("dae24", "dae38", "dae48", "dae63")]-1,1, 
+                            FUN = audpc, dates = c(0,14,24,39))
+
+Herm_16_m <- fold_data(Herm_16_m, PM_MB_means)
+
+write.csv(
+   Herm_16_m,
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2016/Hermitage/Herm_16_means.csv"
+)
+
+```
+
+### Kingaroy 2016  
+Disease data for Kingaroy 2016 only exists as a mean of treatments within the `2016 Mungbean PM trials summary.xlsx` file.  
+```{r Herm16_dataimport}
+# Yield data from 2016 Hermitage trial with final disease severity
+King_16 <-
+   read.xlsx(
+      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past Trials/2016/Yeild Data 2016 Kingaroy Hermitage (PaulM adjusted).xlsx",
+      sheet = "Kingaroy",
+      startRow = 1,
+      colNames = TRUE
+   )[1:28, 1:9]
+
+King_16$Year <- 2016
+King_16$location <- "Kingaroy"
+
+King_16$Plot <- as.numeric(unlist(strsplit(
+   King_16$Plot, "P"))[
+      seq(from = 2, to = 56, by = 2)])
+
+```
+
+#### Define treatment data
+```{r King16_treatmentDefine}
+King_16_dat <- King_16 %>%
+   mutate(trade_name = 
+             case_when(Treatment == "1" ~ "control",
+                       TRUE ~ "Folicur"))%>%
+   mutate(fungicide_ai = 
+             case_when(Treatment == "1" ~ "control",
+                       TRUE ~ "tebuconazole"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Treatment == "1" ~ 0,
+                       TRUE ~ 62.35))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Treatment == "1" ~ as.Date(NA),
+                       Treatment == "2" ~ as.Date("2016-03-22", format = "%Y-%m-%d"),
+                       Treatment == "3" ~ as.Date("2016-03-22", format = "%Y-%m-%d"),
+                       Treatment == "4" ~ as.Date("2016-03-22", format = "%Y-%m-%d"),
+                       Treatment == "5" ~ as.Date("2016-03-09", format = "%Y-%m-%d"),
+                       Treatment == "6" ~ as.Date("2016-03-09", format = "%Y-%m-%d"),
+                       Treatment == "7" ~ as.Date("2016-03-22", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Treatment == "1" ~ as.Date(NA),
+                       Treatment == "3" ~ as.Date("2016-04-05", format = "%Y-%m-%d"),
+                       Treatment == "4" ~ as.Date("2016-04-05", format = "%Y-%m-%d"),
+                       Treatment == "6" ~ as.Date("2016-03-22", format = "%Y-%m-%d"),
+                       Treatment == "7" ~ as.Date("2016-04-05", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_3 = 
+             case_when(Treatment == "4" ~ as.Date("2016-04-19", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Treatment == "1" ~ 0,
+                       Treatment == "2" ~ 1,
+                       Treatment == "3" ~ 2,
+                       Treatment == "4" ~ 3,
+                       Treatment == "5" ~ 1,
+                       Treatment == "6" ~ 2,
+                       Treatment == "7" ~ 2,
+                       TRUE ~ 9999))
+
+```
+
+#### Input trial data
+```{r King16_Trialdat}
+
+King_16_dat <- 
+   data.frame(trial_ref = "mung1516/02",
+              year = "2016",
+              location = "Kingaroy",
+              host_genotype = "Jade",
+              trial_design = "RCB",
+              plot_length = 12,
+              plot_width = 4,
+              plant_density = NA,
+              row_spacing = 0.75,
+              replicate = King_16_dat$rep,
+              planting_date = as.Date("2016-02-11", format = "%Y-%m-%d"),
+              emergence_date = as.Date("2016-02-19", format = "%Y-%m-%d"),
+              flowering_date = as.Date(NA),
+              pod_fill_date = as.Date("2016-04-05", format = "%Y-%m-%d"),
+              mid_late_pod_fill = as.Date(NA),
+              first_sign_disease = as.Date("2016-03-09", format = "%Y-%m-%d"),
+              trade_name = as.factor(King_16_dat$trade_name),
+              fungicide_ai = King_16_dat$fungicide_ai,
+              dose_ai.ha = King_16_dat$dose_ai.ha,
+              n_treatment = as.numeric(King_16_dat$Treatment),
+              fungicide_application_1 = King_16_dat$fungicide_application_1,
+              fungicide_application_2 = King_16_dat$fungicide_application_2,
+              fungicide_application_3 = King_16_dat$fungicide_application_3,
+              total_fungicide = King_16_dat$spray_n,
+              harvest_date = as.Date("2015-05-10", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2015-04-19", format = "%Y-%m-%d"),
+              PM_final_severity = NA,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(King_16_dat$`Raw.Adjusted.Yeild./.ha`)
+              )
+```
+
+#### Calculating treatment means
+```{r King16_means}
+King_16_m <- King_16_dat %>%
+   group_by(host_genotype, n_treatment) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             location = unique(location),
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             fungicide_ai = unique(fungicide_ai),
+             dose_ai.ha = unique(dose_ai.ha),
+             trial_ref = unique(trial_ref),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
+             plot_width.m. = mean(plot_width, na.rm = TRUE),
+             plant_density = unique(plant_density),
+             row_spacing = unique(row_spacing),
+             replicates = length(as.numeric(replicate)),
+             planting_date = unique(planting_date),
+             emergence_date = unique(emergence_date),
+             flowering_date = unique(flowering_date),
+             pod_fill_date = unique(pod_fill_date),
+             mid_late_pod_fill = unique(mid_late_pod_fill),
+             first_sign_disease = unique(first_sign_disease),
+             fungicide_application_1 = unique(fungicide_application_1),
+             fungicide_application_2 = unique(fungicide_application_2),
+             fungicide_application_3 = unique(fungicide_application_3),
+             total_fungicide = unique(total_fungicide),
+             harvest_date = unique(harvest_date),
+             final_assessment = unique(final_assessment),
+             #PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+             rating_scale = unique(rating_scale),
+             #disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+             #D_error_type = "stdev",
+             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+             raw_graded = "Yes",
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+             Y_error_type = "stdev",
+             #AUDPC.m = mean(AUDPC),
+             #AUDPC.sd = sd(AUDPC),
+             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = King_16_dat))[2,3]
+   )
+
+# For some wierd reason standard deviations are comming back NA in the code above
+King_16_m[,"yield_error"] <- 
+   King_16_dat %>%
+   group_by(n_treatment) %>%
+   summarise(yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("yield_error"))
+
+# Mean Disease incidence assessments through the 2016 season
+King_16.DR  <-
+   read.xlsx(
+      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2016/2016 Mungbean PM trials summary.xlsx",
+      sheet = "Kingaroy_2016",
+      startRow = 5,
+      colNames = TRUE
+   )
+names(King_16.DR)[1:6] <- c("Treatment", "dae20","dae34","dae46","dae60","Final_Yield_tHa")
+names(King_16.DR)[6] <- "Final_Yield_tHa"
+King_16.DR$n_treatment <- c(3,2,7,6,5,4,1)
+
+King_16_m <- left_join(King_16_m,King_16.DR)
+King_16_m$AUDPC.m <- apply(King_16_m[,c("dae20", "dae34", "dae46", "dae60")]-1,1, 
+                            FUN = audpc, dates = c(1,14,26,40))
+
+King_16_m <- fold_data(King_16_m, PM_MB_means)
+
+write.csv(
+   King_16_m,
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2016/Kingaroy/King_16_means.csv"
+)
+
+```

### 2019-11-19 191115_PMMB_DataWrangling_PM.Rmd
Correcting years in King2016

@@
               total_fungicide = King_16_dat$spray_n,
-              harvest_date = as.Date("2015-05-10", format = "%Y-%m-%d"),
-              final_assessment = as.Date("2015-04-19", format = "%Y-%m-%d"),
+              harvest_date = as.Date("2016-05-10", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2016-04-19", format = "%Y-%m-%d"),
               PM_final_severity = NA,
@@
    )
-names(King_16.DR)[1:6] <- c("Treatment", "dae20","dae34","dae46","dae60","Final_Yield_tHa")
-names(King_16.DR)[6] <- "Final_Yield_tHa"
+names(King_16.DR)[1:6] <- c("Treatment", "dae20","dae34","dae46","PM_final_severity","Final_Yield_tHa")
 King_16.DR$n_treatment <- c(3,2,7,6,5,4,1)
@@
 King_16_m <- left_join(King_16_m,King_16.DR)
-King_16_m$AUDPC.m <- apply(King_16_m[,c("dae20", "dae34", "dae46", "dae60")]-1,1, 
+King_16_m$AUDPC.m <- apply(King_16_m[,c("dae20", "dae34", "dae46", "PM_final_severity")]-1,1, 
                             FUN = audpc, dates = c(1,14,26,40))
@@
    King_16_m,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2016/Kingaroy/King_16_means.csv"
-)
-
-```
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2016/Kingaroy/King_16_means.csv",
+   row.names = FALSE
+)
+
+```

### 2019-11-19 191115_PMMB_DataWrangling_PM.Rmd
missen flats wrangled

@@
 ```
+
+### Missen Flats 2017
+```{r Missen2017}
+# ____________________________________________________________
+# _____________   Missen Flats (Fogarty's) 2017     ____________
+Fogerty_17 <-
+   read.xlsx(
+      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2017/MissenFlats/Fogerty Work File 2017 (Autosaved).xlsx",
+      sheet = "Data",
+      startRow = 3,
+      colNames = TRUE,
+      detectDates = TRUE
+   )[, 1:43]
+
+#dim(Fogerty_17)   # 162 rows , 43 Columns
+
+# Columns to keep
+Fogerty_17 <- Fogerty_17[, c('Plot', 'Rep', 'Row', 'Column', 'Chem.Trt',
+                           'Chemical', 'Row.Spacing.(m)', 'Treatment.No',
+                           'Treatment', 'Population.plsnts/ha',
+                           '2017-03-07', '2017-03-19', '2017-03-24',
+                           '2017-04-02', '2017-04-10', '2017-04-18',
+                           'Yield.t/ha', 'Grain.Moisture.%', 'Temp.moisture.Taken',
+                           '100.grain.wt.Grams')]
+
+Fogerty_17$Treatment.No <- as.numeric(unlist(strsplit(
+   Fogerty_17$Treatment.No, "T"))[
+      seq(from = 2, to = 324, by = 2)])
+
+# Fog_17_sum <- Fogerty_17 %>%
+#    group_by(Treatment, Chemical, `Row.Spacing.(m)`) %>%
+#    summarise(
+#       m_disease = mean(`2017-04-18`, na.rm = TRUE),
+#       sd_disease = sd(`2017-04-18`, na.rm = TRUE),
+#       m_Yield = mean(`Yield.t/ha`, na.rm = TRUE),
+#       sd_Yield = sd(`Yield.t/ha`, na.rm = TRUE)
+#    )
+# 
+# write.csv(
+#    Fog_17_sum,
+#    "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/Fogerty_17_mean.csv"
+# )
+# 
+# 
+# # gather the incidence assessment into long format
+# Fogerty_17.1 <-
+#    gather(Fogerty_17,
+#           key = Incidence_assessment_date,
+#           value = Incidence,
+#           colnames(Fogerty_17)[c(11:16)])
+# #Fogerty_17.1$Severity <- gather(Fogerty_17, key = assessment_date, value = Severity,
+# #                                colnames(Fogerty_17)[c(15,18)])
+# Fogerty_17.1$location <- "Fogerty"
+# 
+#
+
+head(Fogerty_17)
+unique(Fogerty_17$Chem.Trt)
+unique(Fogerty_17$Chemical)
+Fogerty_17[,7:11]
+```
+
+#### Define treatment data
+```{r King16_treatmentDefine}
+Fogerty_17_dat <- Fogerty_17 %>%
+   mutate(trade_name = 
+             case_when(Chem.Trt == 1 ~ "Folicur",
+                       Chem.Trt == 2 ~ "Throttle",
+                       Chem.Trt == 3 ~ "Custodia",
+                       TRUE ~ "other"))%>%
+   mutate(fungicide_ai = 
+             case_when(Chem.Trt == 1 ~ "tebuconazole",
+                       Chem.Trt == 2 ~ "propiconazole",
+                       Chem.Trt == 3 ~ "200 g/L tebuconazole + 120 g/L azoxystrobin",
+                       TRUE ~ "other"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Chem.Trt == 1 ~ 62,
+                       Chem.Trt == 2 ~ 125,
+                       Chem.Trt == 3 ~ 60,
+                       TRUE ~ 9999))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Treatment.No == 1 ~ as.Date(NA),
+                       Treatment.No == 2 ~ as.Date("2017-02-22", format = "%Y-%m-%d"),
+                       Treatment.No == 3 ~ as.Date("2017-03-08", format = "%Y-%m-%d"),
+                       Treatment.No == 4 ~ as.Date("2017-03-08", format = "%Y-%m-%d"),
+                       Treatment.No == 5 ~ as.Date("2017-03-19", format = "%Y-%m-%d"),
+                       Treatment.No == 6 ~ as.Date("2017-03-08", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Treatment.No == 4 ~ as.Date("2017-03-24", format = "%Y-%m-%d"),
+                       Treatment.No == 6 ~ as.Date("2017-04-02", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Treatment == 1 ~ 0,
+                       Treatment == 4 ~ 2,
+                       Treatment == 6 ~ 2,
+                       TRUE ~ 1))
+
+```
+
+#### Input trial data
+```{r King16_Trialdat}
+# Remove zeros
+Fogerty_17_dat[Fogerty_17_dat$`2017-03-07` == 0 ,c("2017-03-07")] <- 1
+
+Fogerty_17_dat <- 
+   data.frame(trial_ref = "mung1617/02",
+              year = "2016",
+              location = "Missen Flats",
+              host_genotype = "Jade",
+              trial_design = "RCB",
+              plot_length = 10,
+              plot_width = 2,
+              plant_density = Fogerty_17_dat$`Population.plsnts/ha`,
+              row_spacing = Fogerty_17_dat$`Row.Spacing.(m)`,
+              replicate = Fogerty_17_dat$Rep,
+              planting_date = as.Date("2017-01-27", format = "%Y-%m-%d"),
+              emergence_date = as.Date("2017-02-01", format = "%Y-%m-%d"),
+              flowering_date = as.Date(NA),
+              pod_fill_date = as.Date(NA),
+              mid_late_pod_fill = as.Date(NA),
+              first_sign_disease = as.Date("2017-03-07", format = "%Y-%m-%d"),
+              trade_name = as.factor(Fogerty_17_dat$trade_name),
+              fungicide_ai = Fogerty_17_dat$fungicide_ai,
+              dose_ai.ha = Fogerty_17_dat$dose_ai.ha,
+              n_treatment = as.numeric(Fogerty_17_dat$Treatment.No),
+              fungicide_application_1 = Fogerty_17_dat$fungicide_application_1,
+              fungicide_application_2 = Fogerty_17_dat$fungicide_application_2,
+              total_fungicide = Fogerty_17_dat$spray_n,
+              harvest_date = as.Date("2017-05-11", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2017-04-18", format = "%Y-%m-%d"),
+              PM_final_severity = Fogerty_17_dat$`2017-04-18`,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(Fogerty_17_dat$`Yield.t/ha`),
+              AUDPC = apply(Fogerty_17_dat[,c("2017-03-07", "2017-03-19", "2017-03-24", "2017-04-02","2017-04-10","2017-04-18")]-1,1, 
+                            FUN = audpc, dates = c(1,12,17,26,34,42)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
+              )
+```
+
+#### Calculating treatment means
+```{r Missen17_means}
+
+Fogerty_17_m <- Fogerty_17_dat %>%
+   group_by(host_genotype, n_treatment, row_spacing, fungicide_ai) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             location = unique(location),
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             dose_ai.ha = unique(dose_ai.ha),
+             trial_ref = unique(trial_ref),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
+             plot_width.m. = mean(plot_width, na.rm = TRUE),
+             plant_density = mean(plant_density, na.rm = TRUE),
+             replicates = length(as.numeric(replicate)),
+             planting_date = unique(planting_date),
+             emergence_date = unique(emergence_date),
+             flowering_date = unique(flowering_date),
+             pod_fill_date = unique(pod_fill_date),
+             mid_late_pod_fill = unique(mid_late_pod_fill),
+             first_sign_disease = unique(first_sign_disease),
+             fungicide_application_1 = unique(fungicide_application_1),
+             fungicide_application_2 = unique(fungicide_application_2),
+             total_fungicide = unique(total_fungicide),
+             harvest_date = unique(harvest_date),
+             final_assessment = unique(final_assessment),
+             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+             rating_scale = unique(rating_scale),
+             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+             D_error_type = "stdev",
+             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+             raw_graded = NA,
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+             Y_error_type = "stdev",
+             AUDPC.m = mean(AUDPC),
+             AUDPC.sd = sd(AUDPC),
+             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment) + fungicide_ai + row_spacing, data = subset(Fogerty_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
+   )
+
+# For some weird reason standard deviations are comming back NA in the code above
+Fogerty_17_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
+   Fogerty_17_dat %>%
+   group_by(n_treatment, row_spacing, fungicide_ai) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("disease_error","yield_error"))
+
+write.csv(
+   Fogerty_17_m,
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2017/MissenFlats/Fogerty_17_mean.csv",
+   row.names = FALSE
+)
+
+```

### 2019-11-20 191115_PMMB_DataWrangling_PM.Rmd
Have obtained all the mean squares that i need, but this file needs more work

@@
 # Data wrangling
+This file is not complete and there are a number of things that need checking
+   - Mean squares are only calculated for the triazoles and controls
+   - If the years for each trial are input correctly
+   - If the disease and yield errors are calculated and that they are shuffled correctly into the data frame
+   - AUDPC needs to be checked for starting dates and if trials have been omitted
+   - Check that what is generated from this file matches the main file and update
+   - write.csv should have row.names = FALSE
 
@@
               D_error_type = "stdev",
-              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+              grain_yield.t.ha. = mean(grain_yield.t.ha./1000, na.rm = TRUE),
               raw_graded = NA,
-              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+              yield_error = sd(grain_yield.t.ha./1000, na.rm = TRUE),
               Y_error_type = "stdev",
-              meanSq = anova(lm(grain_yield.t.ha. ~ host_genotype + factor(n_treatment), data = Herm_11_dat))[2,3]
+              meanSq = anova(lm(grain_yield.t.ha./1000 ~ factor(n_treatment) + host_genotype, 
+                                data = Herm_11_dat[Herm_11_dat$fungicide_ai == "tebuconazole" | 
+                                                        Herm_11_dat$fungicide_ai == "control" ,]))[1,3]
    )
@@
               D_error_type = "stdev",
-              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE)/1000,
               raw_graded = NA,
-              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+              yield_error = sd(grain_yield.t.ha./1000, na.rm = TRUE),
               Y_error_type = "stdev",
@@
              AUDPC.sd = sd(AUDPC),
-              meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = King_11_dat))[2,3]
+              meanSq = anova(lm(grain_yield.t.ha./1000 ~ factor(n_treatment) + host_genotype, 
+                                data = King_11_dat[King_11_dat$fungicide_ai == "tebuconazole" | 
+                                                        King_11_dat$fungicide_ai == "control" ,]))[1,3]
    )
@@
 ### Goolhi 2013
+#### Convert disease scores
 ```{r Goolhi_2013}
@@
 Goolhi_13 <- left_join(Goolhi.13D, Goolhi.13Y)
+
+```
+
+#### Define treatment data
+```{r GoolhiDefine}
 
@@
 
+```
+
+#### Input trial data
+```{r Goolhis_TrialData}
+
 Goolhi_13_dat <- 
@@
               rating_scale = "1-9",
-              grain_yield.t.ha. = as.numeric(Goolhi_13$`Yield Kg/ha`),
+              grain_yield.t.ha. = as.numeric(Goolhi_13$`Yield Kg/ha`)/1000,
               AUDPC = apply(Goolhi_13[,c("Inc_16D","Inc_33D")]-1,1, FUN = audpc, dates = c(16,33))# -1 to the data because zero disease = 1 on rating scale
               )
+
+```
+
+#### Calculating the treatment means
+```{r Goolhis_means}
 
@@
              AUDPC.sd = sd(AUDPC),
-              meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Goolhi_13_dat))[2,3]
-   )
-
+              meanSq = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
+                                data = Goolhi_13_dat[Goolhi_13_dat$fungicide_ai == "propiconazole" | 
+                                                        Goolhi_13_dat$fungicide_ai == "control" ,]))[1,3]
+   )
+
+#!!!!!!!!!!!!!!!!!! Check to see if errors are calculated
 Goolhi_13_m <- fold_data(Goolhi_13_m, PM_MB_means)
@@
 #### Define treatment data
-```{r}
+```{r MarysDefine}
 MarysM_13 <- MarysM_13 %>%
@@
               row_spacing = unique(row_spacing),
-              replicates = sum(as.numeric(replicate)),
+              replicates = length(as.numeric(replicate)),
               planting_date = unique(planting_date),
@@
              AUDPC.sd = sd(AUDPC),
-              meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = MarysM_13_dat))[2,3]
-   )
-
-MarysM_13_m <- fold_data(MarysM_13_m, PM_MB_means)
-
-MarysM_13_m <- MarysM_13_m[MarysM_13_m$trade_name != "other",]
+              meanSq = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
+                                data = MarysM_13_dat[MarysM_13_dat$fungicide_ai == "propiconazole" | 
+                                                        MarysM_13_dat$fungicide_ai == "control" ,]))[1,3]
+
+   )
 
 # For some wierd reason standard deviations are comming back NA in the code above
-MarysM_13_m[,c("disease_error","yield_error")] <- 
-   MarysM_13_dat %>%
+# Because of n_treatment being converted to a factor I need to wrangle carefully here
+Mary_tmp <- MarysM_13_dat %>%
    group_by(n_treatment) %>%
    summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
-             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
-   select(c("disease_error","yield_error"))
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE))
+
+# Remive the existing yield_error columns and replace with new ones
+MarysM_13_m <- left_join(MarysM_13_m[,colnames(MarysM_13_m)[c(-29,-33)]], Mary_tmp)
+
+# Remove other plots not in experiment
+MarysM_13_m <- MarysM_13_m[MarysM_13_m$trade_name != "other",]
+
+MarysM_13_m$n_treatment <- as.numeric(as.character(MarysM_13_m$n_treatment))
+MarysM_13_m <- fold_data(MarysM_13_m, PM_MB_means)
 
 write.csv(
-   MarysM_13_m,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1304-MarysMount_means.csv"
-)
+   MarysM_13_m[order(as.numeric(MarysM_13_m$n_treatment)),],
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1304-MarysMount_means.csv",
+   row.names = FALSE
+)
+
+sd(MarysM_13_dat[MarysM_13_dat$n_treatment == 9,"grain_yield.t.ha."])
 
@@
              #AUDPC.sd = sd(AUDPC),
-              meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Premer_13_dat))[2,3]
-   )
-
+              meanSq = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
+                                data = Premer_13_dat[Premer_13_dat$fungicide_ai == "propiconazole" | 
+                                                        Premer_13_dat$fungicide_ai == "control" ,]))[1,3]
+   )
+
+# For some wierd reason standard deviations are comming back NA in the code above
+# Because of n_treatment being converted to a factor I need to wrangle carefully here
+Prem_tmp <- Premer_13_dat %>%
+   group_by(n_treatment) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE))
+
+# Remive the existing yield_error columns and replace with new ones
+Premer_13_m <- left_join(Premer_13_m[,colnames(Premer_13_m)[c(-29,-33)]], Prem_tmp)
+
+# Remove other plots not in experiment
+Premer_13_m <- Premer_13_m[Premer_13_m$trade_name != "other",]
+
+Premer_13_m$n_treatment <- as.numeric(as.character(Premer_13_m$n_treatment))
+Premer_13_m <- fold_data(Premer_13_m, PM_MB_means)
+
+write.csv(
+   Premer_13_m[order(as.numeric(Premer_13_m$n_treatment)),],
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/BB1305_Millmerran_means.csv",
+   row.names = FALSE
+)
+##########################
 # For some wierd reason standard deviations are comming back NA in the code above
@@
 
-if(any(incidence3 == 0)){
+if(any(incidence4 == 0)){
    warning("Code caluculated incidence on '0' which is off the incidence scale")}
@@
 Millm.13Y$Treatment <- as.character(Millm.13Y$Treatment)
+Millm.13Y$Treat <- as.double(Millm.13Y$Treat)
 colnames(Millm.13Y)[1:4] <- c("Run", "Plot","Treat", "Rep")
@@
              AUDPC.sd = sd(AUDPC),
-             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Millm_13_dat))[2,3]
+             meanSq = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
+                                data = Millm_13_dat[Millm_13_dat$fungicide_ai == "propiconazole" | 
+                                                        Millm_13_dat$fungicide_ai == "control" ,]))[1,3]
    )
@@
 # For some wierd reason standard deviations are comming back NA in the code above
-Millm_13_m[,c("disease_error","yield_error")] <- 
-   Millm_13_dat %>%
+# Because of n_treatment being converted to a factor I need to wrangle carefully here
+Millm_tmp <- Millm_13_dat %>%
    group_by(n_treatment) %>%
    summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
-             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
-   select(c("disease_error","yield_error"))
-
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE))
+
+# Remive the existing yield_error columns and replace with new ones
+Millm_13_m <- left_join(Millm_13_m[,colnames(Millm_13_m)[c(-29,-33)]], Millm_tmp)
+
+# Remove other plots not in experiment
+Millm_13_m <- Millm_13_m[Millm_13_m$trade_name != "other",]
+
+Millm_13_m$n_treatment <- as.numeric(as.character(Millm_13_m$n_treatment))
 Millm_13_m <- fold_data(Millm_13_m, PM_MB_means)
 
-Millm_13_m <- Millm_13_m[Millm_13_m$trade_name != "other",]
-
 write.csv(
-   Millm_13_m,
+   Millm_13_m[order(as.numeric(Millm_13_m$n_treatment)),],
    "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/BB1305_Millmerran_means.csv"
@@
              AUDPC.sd = sd(AUDPC),
-             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Herm_15_dat))[2,3]
+             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Herm_15_dat))[1,3]
    )
@@
              #AUDPC.sd = sd(AUDPC),
-             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Herm_16_dat))[2,3]
+             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Herm_16_dat))[1,3]
    )
@@
              #AUDPC.sd = sd(AUDPC),
-             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = King_16_dat))[2,3]
+             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = King_16_dat))[1,3]
    )
@@
 ```
+
+### Hermitage 2017
+```{r Herm_17}
+
+# _____________   Hermitage  2017     ____________
+Herm_17 <-
+   read.xlsx(
+      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past Trials/2017/Hermitage/Hermitage working file 2017 .xlsx",
+      sheet = "Hermitage Trial",
+      rows = 3:165,
+      cols = 1:38,
+      colNames = TRUE,
+      detectDates = TRUE
+   )
+
+# Adjust the Yield to 12% moisture
+Herm_17$`Yield.T/Ha` <-
+   (Herm_17$`Yield.T/Ha` / Herm_17$`Moisture%`) * 12
+
+# Columns to keep
+Fogerty_17 <- Fogerty_17[, c('Plot', 'Rep', 'Row', 'Column', 'Chem.Trt',
+                           'Chemical', 'Row.Spacing.(m)', 'Treatment.No',
+                           'Treatment', 'Population.plsnts/ha',
+                           '2017-03-07', '2017-03-19', '2017-03-24',
+                           '2017-04-02', '2017-04-10', '2017-04-18',
+                           'Yield.t/ha', 'Grain.Moisture.%', 'Temp.moisture.Taken',
+                           '100.grain.wt.Grams')]
+
+Fogerty_17$Treatment.No <- as.numeric(unlist(strsplit(
+   Fogerty_17$Treatment.No, "T"))[
+      seq(from = 2, to = 324, by = 2)])
+
+# Create summarised data set for collated means meta-dataset
+# NEXT STEP - sort and copy it to dataset
+Herm_17_sum <- Herm_17 %>%
+   group_by(Chemical,
+            Chemical.Trt,
+            `Row.Spacing.(m)`,
+            Manage.Trt,
+            Management) %>%
+   summarise(
+      PM_final_severity = mean(`I_11/05/2017`, na.rm = TRUE),
+      Disease_error = sd(`I_11/05/2017`, na.rm = TRUE),
+      `grain_yield(t/ha)` = mean(`Yield.T/Ha`, na.rm = TRUE),
+      Yield_error = sd(`Yield.T/Ha`, na.rm = TRUE),
+      meanSq = anova(lm(`Yield.T/Ha` ~ factor(Manage.Trt) + factor(Trt) + `Row.Spacing.(m)`, data = subset(Herm_17, Chemical != "Custodia® 320 SC")))[1,3] # of only triazoles
+   )
+
+Herm_17_sum <-
+   with(Herm_17_sum, Herm_17_sum[order(Manage.Trt, Chemical, `Row.Spacing.(m)`), ])
+
+# inserted meansquare in manually
+
+# Columns to keep
+Herm_17 <- Herm_17[, c(1, 2, 4, 5, 7, 10, 9, 11, 12, 13,
+                       17, 19, 21, 23, 25, 27, 29,
+                       #                      18,20,22,24,26,28,30,
+                       34, 36, 37, 35)]
+
+```
+
+### Wellcamp 2018
+```{r Wellcamp2018}
+Well_18 <-
+   read.xlsx(
+      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past Trials/2018/Wellcamp/Wellcamp Fungicide x Row Spacing x Plant Population - Experimental Design Fogarty 2018.xlsx",
+      sheet = "Data",
+      startRow = 1,
+      colNames = TRUE
+   )
+
+#dim(Well_18)   # 72 rows , 32 Columns
+#names(Well_18)
+
+# Columns to keep
+Well_18 <- Well_18[, c('Plot','Rep','Plant.Pop','Row.Spacing',
+            'Fungicide','Treatment','IR.23-3-18',
+            'IR.5-4-18','IR.11-4-18','IR.18-4-18',
+            'IR.26-4-18','IR.2-5-18','S.23-3-18',
+            'S.5-4-18','S.11-4-18','S.18-4-18',
+            'S.26-4-18','S.2-5-18','Row.Length','Yield./.ha')]
+
+Well_18_means <- Well_18 %>%
+   group_by(Row.Spacing, Fungicide, Plant.Pop) %>%
+   summarise(
+      Yield = mean(`Yield./.ha`, na.rm = TRUE),
+      Incidence  = max(Well_18.1$Incidence),
+      Severity  = max(Severity, na.rm = TRUE)
+   )
+
+# respectively
+# plot and treatment variables
+# Incidence assessment
+# severity assessment
+# Yield assessment
+
+Well_18_inc <-
+   reshape(
+      data = Well_18,
+      idvar = "Plot",
+      direction = "long",
+      varying = list(incidence = names(Well_18)[7:12]),
+      timevar = "ass_date_i"
+   )
+
+Well_18_sev <-
+   reshape(
+      data = Well_18,
+      idvar = "Plot",
+      direction = "long",
+      varying = list(incidence = names(Well_18)[13:18]),
+      timevar = "ass_date_s"
+   )
+
+Well_18.1 <- cbind(Well_18_inc[, c(1:6, 13:16)], Well_18_sev[, 15:16])
+
+names(Well_18.1)[10] <- c("Incidence")
+names(Well_18.1)[12] <- c("Severity")
+Well_18.1$ass_date_i <- rep(names(Well_18_inc)[7:12], each = 72)
+Well_18.1$ass_date_i <-
+   as.Date(gsub("S.", "", Well_18.1$ass_date_i), format = "%d-%m-%y")
+names(Well_18.1)[9] <- c("Assessment_date")
+Well_18.1 <- Well_18.1[c(1:10, 12)]
+
+Well_18.1$Row.Spacing <-
+   as.numeric(unlist(strsplit(Well_18.1$Row.Spacing, " mtr")))
+
+write.csv(
+   Well_18.1,
+   "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/2018_Wellcamp.csv"
+)
+
+Well_18$FungVCon <- Well_18$Fung.Trt
+Well_18[Well_18$FungVCon == 1,"FungVCon"] <- 3
+Well_18[Well_18$FungVCon == 4,"FungVCon"] <- 1
+Well_18[Well_18$FungVCon == 3,"FungVCon"] <- 2
+
+Well_18_means <- Well_18.1 %>%
+   group_by(Row.Spacing, Fungicide, Plant.Pop) %>%
+   summarise(
+      Yield = mean(`Yield./.ha`, na.rm = TRUE),
+      Incidence  = max(Well_18.1$Incidence),
+      Severity  = max(Severity, na.rm = TRUE),
+      meanSq = anova(lm(`Yield./.ha` ~ factor(Plant.Pop) + factor(FungVCon) + `Row.Spacing`, data = subset(Well_18, Fungicide != "Custodia")))[2,3] # of only triazoles
+   )
+
+```
+
+### Hermitage 2019
+```{r Herm19}
+PM_MB_19 <-
+   read.xlsx(
+      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/1901_Herm_PM/1901 Mungbean powdery mildew disease and yeild data.xlsx",
+      startRow = 2,
+      cols = c(1:21)
+   )
+
+# Remove these plots as the results can't be trusted
+PM_MB_19 <- subset(PM_MB_19, Harvest.Plot.Number != 5)
+PM_MB_19 <- subset(PM_MB_19, Harvest.Plot.Number != 6)
+
+PM_MB_19$AUDPC <- apply(PM_MB_19[,c("15-4-19.Incedence", "23-4-19.Incedence", "1-5-19.Incedence")]-1,1,FUN = audpc, dates = c(3,8,21))
+
+PM_MB_19$Yeild
+
+PM19_means <- PM_MB_19 %>%
+   group_by(TOS.NUM, `T/ment.NUM`) %>%
+   summarise(
+      Incidence190423 = mean(`23-4-19.Incedence`, na.rm = TRUE),
+      Inc.sd.190423 = sd(`23-4-19.Incedence`, na.rm = TRUE),
+      Inc.error.190423 = "Stdev",
+      Incidence190501 = mean(`1-5-19.Incedence`, na.rm = TRUE),
+      Inc.sd.190501 = sd(`1-5-19.Incedence`, na.rm = TRUE),
+      Inc.error.190501 = "Stdev",
+      Plot_length = mean(Plot.Lengths, na.rm = TRUE),
+      Yield = mean(Yeild/1000, na.rm = TRUE),
+      Yield_error = sd(Yeild/1000, na.rm = TRUE),
+      AUDPC = mean(AUDPC, na.rm = TRUE),
+      meanSq = anova(lm(Yeild/1000 ~ factor(TOS.NUM) + factor(`T/ment.NUM`), data = PM_MB_19))[2,3]
+   )
+
+library(agricolae)
+
+colnames(PM_MB_19)
+
+audpc(PM_MB_19[PM_MB_19$TOS.NUM == 2 , c(5, 7, 9)], c(70, 78, 86))
+
+PM_MB_19$AUDPC <- NA
+PM_MB_19[PM_MB_19$TOS.NUM == 1 , "AUDPC"] <-
+   audpc(PM_MB_19[PM_MB_19$TOS.NUM == 1 , c(5, 7)], c(70, 78))
+PM_MB_19[PM_MB_19$TOS.NUM == 2 , "AUDPC"] <-
+   audpc(PM_MB_19[PM_MB_19$TOS.NUM == 2 , c(5, 7, 9)], c(70, 78, 86))
+
+boxplot(AUDPC ~ as.factor(`T/ment.NUM`) * as.factor(TOS.NUM) , data = PM_MB_19)
+
+as.Date("2019-05-22") - as.Date("2019-02-04")
+as.Date("2019-04-15") - as.Date("2019-02-04")
+as.Date("2019-04-23") - as.Date("2019-02-04")
+as.Date("2019-05-01") - as.Date("2019-02-04")
+
+```

### 2019-11-20 04_Prep_data.Rmd
Correcting Variance formula
Some adjustments to sampling variance formulas and the incorporation of MSE into the slimmer dataset

@@
-# Place holder
-
 ```{r load_libraries}
@@
    #  MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B) # This formula was abandon in favor for the formula in Nugugi et. at (2011)
-   MSE <-
-      PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[1] * (LSD /
-                                                                            Tcrit) ^ 2 / 2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
+   V_yield <-
+      (PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[1] * (LSD /
+                                                                            Tcrit) ^ 2) / 2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
 
@@
       # Balance equation
-      Sv[j] = sqrt(MSE / (
-         PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j] *
-            as.numeric(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$grain_yield.t.ha[j])
-      ))
+      # Sv[j] = V_yield / 
+      #    (PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j] *
+      #       as.numeric(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$grain_yield.t.ha[j])^2)
+      # 
+      Sv[j] = V_yield / 
+         PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j]
+
+      # Sv[j] = MSE / 
+      #    (PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j] *
+      #       as.numeric(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$grain_yield.t.ha[j])^2)
+      #
+
+      ### -> This formula should be V = (n * (LSD/1.96)^2) / 2
 
@@
    "SamplingVariance"
+
 ```
 
-## Yield gains  
-Yield gains and yield gains proportional to the control.
+## Yield saving  
+Yield saving and Yield saving proportional to the control.
 
@@
 ```
+
+```{r}
+
+slimmer_PM_dat$vi <- slimmer_PM_dat$Y_Msquare/(slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha^2)
+
+slimmer_PM_dat %>%
+   ggplot(aes(y= grain_yield.t.ha, x = vi))+
+   geom_point()
+
+```

### 2019-11-20 05_MetaAnalysis.Rmd
Added the imputation of MSE

@@
 slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
+unique(slimmer_PM_dat$trial_ref, slimmer_PM_dat$location, slimmer_PM_dat$year)
 
@@
 
+```{r imputing_MSE}
+hist(unique(slimmer_PM_dat$Y_Msquare))
+hist(log(unique(slimmer_PM_dat$Y_Msquare))) # log mean square has a more normal distribution
+
+TrialMSQ <- slimmer_PM_dat %>%
+   group_by(trial_ref)%>%
+   summarise(unique(Y_Msquare))
+
+TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), "trial_ref"]
+
+for(i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`),]$trial_ref){
+   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i,"Y_Msquare"] <- 
+      exp(
+         rnorm(n = 1,
+               mean = mean(TrialMSQ$`unique(Y_Msquare)`, na.rm = TRUE),
+               sd(TrialMSQ$`unique(Y_Msquare)`, na.rm = TRUE)
+         )
+      )
+   }
+
+```
+
 ```{r meta_1}
@@
 slimmer_PM_dat$yi <- slimmer_PM_dat$grain_yield.t.ha
-slimmer_PM_dat$vi <- slimmer_PM_dat$yield_error
+slimmer_PM_dat$vi <- slimmer_PM_dat$Y_Msquare/(slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha^2)
 
@@
                    mods = ~ spray_management,
-#                   method = "ML",
+                   method = "ML",
                    random = list(~ spray_management | trial),

### 2019-11-20 R/slimming_PM_dat.R
Added MSE for yield to the slimmer dataset

@@ -26,7 +26,7 @@ slim_PM_dat <- data.frame(
    prop_yield_gain = as.double(PM_MB_means$prop_YG),
    PM_final_severity = as.double(PM_MB_means$PM_final_severity),
    PM_final_severity_error = as.double(PM_MB_means$disease_error),
-   PM_MB_means$Y_Msquare = as.double(PM_MB_means$Y_Msquare)
+   Y_Msquare = as.double(PM_MB_means$Y_Msquare)
 )
 
 

### 2019-11-22 explore.Rmd
create explore

---
title: "analysis"
author: "Emerson"
date: "10/29/2019"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(tidyverse)
library(readxl)
library(janitor)
```

```{r}
datPM <- read_csv("data/slimmer_PM_clusterdat.csv")

```

# Fungicide treatments

```{r}
datPM %>% 
   tabyl(fungicide_ai)

```

```{r}

datPM %>%
   group_by(trial_ref, year, fungicide_ai) %>% 
   tally(sort = TRUE) %>% 
   ggplot(aes(x = fungicide_ai, fill = as.factor(year))) +
   geom_bar() +
   coord_flip()
```

```{r}
datPM %>% 
   filter(fungicide_ai %in% c("control", "tebuconazole", "propiconazole")) %>% 
   tabyl(year, fungicide_ai) %>% 
   gather(fungicide_ai, n, 2:4) %>% 
   ggplot(aes(factor(year), n, fill = fungicide_ai))+
   geom_col()
```

```{r}
datPM <- datPM %>% 
   mutate(V = case_when(is.na(Y_Msquare) ~ mean(datPM$Y_Msquare, na.rm = TRUE),
                    TRUE ~ Y_Msquare),
          yi = grain_yield.t.ha,
          vi = V/n, 
          id = 1:nrow(datPM))

```

```{r}
library(metafor)

PM_mv1 <- rma.mv(yi, vi, 
                    mods = ~ spray_management, 
                    method="ML",
                    random = list(~ spray_management | trial, ~1 | id), 
                    struct="UN", data=datPM)

```

```{r}
anova(PM_mv1, L=rbind(c(0,1,-1,0,0), 
                        c(0,0,1,-1,0),
                        c(0,0,1,0,-1),
                        c(0,0,0,-1,1),
                        c(0,1,0,0,1)))
```

```{r}
results <- data.frame(cbind(PM_mv1$b, 
                             PM_mv1$ci.lb,
                             PM_mv1$ci.ub))
results <- cbind(rownames(results), results)
rownames(results) <- NULL
colnames(results)<- c("treat","mean","lci", "uci")

results %>%
   filter(treat != "intrcpt") %>% 
   ggplot(aes(treat, mean))+
   geom_point(aes(size = 1/(uci-lci)), shape =15)+
   geom_errorbar(aes(ymin = lci, ymax = uci), width = 0.1)+
   coord_flip()

```

### 2019-11-23 explore.Rmd
added netmeta results

@@
 ```{r}
+control <- datPM %>% 
+   filter(spray_management == "control") %>% 
+group_by(trial) %>% 
+summarize(sev_control = mean(PM_final_severity))
+
+control %>% 
+   ggplot(aes(sev_control))+
+   geom_histogram()
+
+datPM2 <- left_join(control, datPM) %>% 
+   filter(year != 2019)
+
+datPM2 %>% 
+   ggplot(aes(spray_management, yi, size = 1/vi, color = sev_control))+
+   geom_jitter(width = 0.1)+
+   facet_wrap(~year)
+
+datPM2 %>% 
+   filter(spray_management == "control") %>% 
+   ggplot(aes(row_spacing, yi, size = 1/vi, color = sev_control))+
+   geom_jitter(width = 0.1)
+
+```
+
+```{r}
 library(metafor)
@@
                     mods = ~ spray_management, 
-                    method="ML",
                     random = list(~ spray_management | trial, ~1 | id), 
-                    struct="UN", data=datPM)
+                    struct="UN", data=datPM2)
 
@@
 ```
+
+```{r}
+library(netmeta)
+
+datPM3 <- datPM2 %>% 
+   group_by(trial, spray_management, n) %>% 
+      summarize(yi_mean = mean(yi), 
+             vi_mean = mean(vi)) %>% 
+   ungroup()
+
+PM_con <- pairwise(treat = spray_management,
+                  n = n,
+                  mean = yi_mean,
+                  sd = sqrt(vi_mean),
+                  studlab= trial,
+                  data = datPM3, 
+                  sm="MD")
+
+```
+
+```{r}
+net_con <- netmeta(TE, 
+                seTE, 
+                treat1, 
+                treat2, 
+                studlab, 
+                data=PM_con, 
+                sm="MD")
+
+summary(net_con)
+```
+
+```{r}
+forest(net_con, reference.group = 4,
+       rightcols=c("effect", "ci", "Pscore"),
+       rightlabs="P-Score", small.values = "bad")
+```
+
+```{r}
+netrank(net_con, small.values = "bad")
+```
+
+```{r}
+netgraph(net_con, 
+         plastic = FALSE,
+         col = "orange",
+         thickness =  "number.of.studies",
+         points = FALSE, 
+         col.points = "black", 
+         cex.points = 1,
+         number.of.studies = TRUE,
+         cex.number.of.studies = 1,
+         col.number.of.studies = "black",
+         bg.number.of.studies = "orange",
+         multiarm = FALSE,
+         col.multiarm = "lightblue",
+         pos.number.of.studies = 0.5)
+```
+
+```{r}
+netleague(net_con)
+```
+
+```{r}
+decomp.design(net_con)
+```
+
+```{r}
+netsplit(net_con)
+```
+```{r}
+nm1 <- netmeasures(net_con)
+
+plot(nm1$meanpath, nm1$minpar, pch="",
+     xlab="Mean path length", ylab="Minimal parallelism")
+text(nm1$meanpath, nm1$minpar, names(nm1$meanpath), cex=0.8)
+```

### 2019-11-23 explore.Rmd
cleaning

@@
 
-```
-
-```{r}
-
-datPM %>%
-   group_by(trial_ref, year, fungicide_ai) %>% 
-   tally(sort = TRUE) %>% 
-   ggplot(aes(x = fungicide_ai, fill = as.factor(year))) +
-   geom_bar() +
-   coord_flip()
-```
-
-```{r}
-datPM %>% 
-   filter(fungicide_ai %in% c("control", "tebuconazole", "propiconazole")) %>% 
-   tabyl(year, fungicide_ai) %>% 
-   gather(fungicide_ai, n, 2:4) %>% 
-   ggplot(aes(factor(year), n, fill = fungicide_ai))+
-   geom_col()
 ```

### 2019-12-04 02_Weather.Rmd
Corrected code and cleaned up

--- 2019-11-01 02_Weather.Rmd
@@
 ```{r import_libraries_&_data}
+library(ggplot2)
+library(dplyr)
 source("R/import_data.R")
@@
 source("R/year2day.r")
+source("R/gg_color_hue_function.R")
 
-```
-
-```{r weather1, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
-# This chunk has been removed as the get_PPD2 function has stopped working and needs fixing
-# Update: I have included data files instead of seeking the data from the web. 
-# issue has something to do with website certificates not being appropriate
-
-# Import dataset
-
-# Need weather data between 2011 and 2017
-
-# function to extract date from the year
-# format should be Universal time format
-source("R/year2day.r")
-
-# Function to generate some of the ggplot grouping colours
-gg_color_hue <- function(n) {
-   hues = seq(15, 375, length = n + 1)
-   hcl(h = hues, l = 65, c = 100)[1:n]
-}
 cols1 <- gg_color_hue(4)
 
+# import data from SILO interpolated datasets downloaded from the QLD longpaddock website
 silo_war_Tmax <- read.csv("./data/silo_war_Tmax.csv")
@@
 silo_emerald_Tmax <- read.csv("./data/silo_emerald_Tmax.csv")
+
 ```
 
+Lets have a look at the climate for the main field experiment sites
+
 ### Kingaroy historical weather
-```{r Kingaroy_weather, include=FALSE}
+```{r Kingaroy_weather, echo=FALSE}
 # Smoothing temperatures by taking a rolling7 day average
@@
 # Add columns for Year and date to data
-king_Tm_aver <- king_Tm_aver %>%
-   mutate(
-      Year = substr(king_Tm_aver$date, start = 1, stop = 4),
-      Day = year2day(king_Tm_aver$date)
-   )
+king_Tm_aver$year <- substr(king_Tm_aver$date, start = 1, stop = 4)
+king_Tm_aver$day <- sapply(king_Tm_aver$date,year2day)
 
 # Create data subset of powdery mildew data means for the first sign of the disease by location
-King_FS <- PM.dat %>%
-   group_by(trial_ref, location, year) %>%
-   summarise(first_sign = mean(as.Date(first_sign_disease), na.rm = T)) %>%
-   filter(location == "Kingaroy") %>%
-   mutate(day = year2day(first_sign))
+PM.dat_sum <- as.data.frame(do.call(rbind,
+                   by(PM.dat, PM.dat$trial_ref, function(x){
+                      c(location = unique(as.character(x$location)),
+                        year = unique(as.character(x$year)),
+                        first_sign = unique(as.character(x$first_sign_disease)),
+                        day = as.numeric(unique(sapply(x$first_sign_disease,year2day))))
+                   }
+                      )), stringsAsFactors = FALSE)
 
-ggplot(subset(king_Tm_aver, year == levels(factor(King_FS$year))),
-       aes(day)) +
+King_FS <- PM.dat_sum[PM.dat_sum$location == "Kingaroy",]
+King_FS$day <- as.numeric(King_FS$day)
+
+king_Tm_aver[king_Tm_aver$year == "2002"|
+                king_Tm_aver$year == "2010"|
+                king_Tm_aver$year == "2011"|
+                king_Tm_aver$year == "2012"|
+                king_Tm_aver$year == "2016", ] %>%
+   ggplot(aes(x = day)) +
    geom_line(aes(y = max_T, colour = year)) +
    #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
-   geom_line(aes(y = min_T, colour = Year)) +
+   geom_line(aes(y = min_T, colour = year)) +
    #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
@@
         title = "Maximum and minimum daily temperatures in Kingaroy") +
-   scale_y_continuous(limits = c(0, 40)) +
    scale_x_continuous(
       limits = c(0, 200),
-      labels = c(subset(king_Tm_aver, Year == 2016)$date[c(1, 50, 100, 150, 200)]),
+      labels = c(subset(king_Tm_aver, year == 2016)$date[c(1, 50, 100, 150, 200)]),
       breaks = c(1, 50, 100, 150, 200)
@@
    geom_vline(
-      xintercept = King_FS$Day[3],
+      xintercept = King_FS$day[3],
       size = 1,
@@
    ) +
-   geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5) +
-   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))
+   geom_area(aes(y = daily_rain, fill = year), alpha = 0.5) +
+   scale_y_continuous(limits = c(0, 40),sec.axis = dup_axis(name = "Rainfall (mm)"))
 #   scale_x_continuous(limits = c(1,180),
@@
 ### Hermitage historical weather
-```{r Hermitage_weather, include=FALSE}
+```{r Hermitage_weather, echo=FALSE}
 # ______  Hermitage  _______
@@
 # Add columns for Year and date to data
-war_Tm_aver <- war_Tm_aver %>%
-   mutate(
-      Year = substr(war_Tm_aver$date, start = 1, stop = 4),
-      Day = year2day(war_Tm_aver$date)
-   )
+war_Tm_aver$year <- substr(war_Tm_aver$date, start = 1, stop = 4)
+war_Tm_aver$day <- sapply(war_Tm_aver$date,year2day)
 
 # Create data subset of powdery mildew data means for the first sign of the disease by location
-Herm_FS <- PM.dat %>%
-   group_by(Trial_ref, Location, Year) %>%
-   summarise(First_sign = mean(as.Date(first_sign_disease), na.rm = T)) %>%
-   filter(Location == "Hermitage") %>%
-   mutate(Day = year2day(First_sign))
 
-ggplot(subset(war_Tm_aver, Year == levels(factor(Herm_FS$Year))),
-       aes(Day)) +
-   geom_line(aes(y = max_T, colour = Year)) +
+Herm_FS <- PM.dat_sum[PM.dat_sum$location == "Hermitage",]
+Herm_FS$day <- as.numeric(Herm_FS$day)
+
+ggplot(subset(war_Tm_aver, year == levels(factor(Herm_FS$year))),
+       aes(day)) +
+   geom_line(aes(y = max_T, colour = year)) +
    #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
-   geom_line(aes(y = min_T, color = Year)) +
+   geom_line(aes(y = min_T, color = year)) +
    #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
@@
         title = "Maximum and minimum daily temperatures in Hermitage") +
-   scale_y_continuous(limits = c(0, 45)) +
-   scale_x_continuous(
-      limits = c(0, 200),
-      labels = c(subset(war_Tm_aver, Year == 2016)$date[c(1, 50, 100, 150, 200)]),
-      breaks = c(1, 50, 100, 150, 200)
-   ) +
    theme(
@@
    geom_vline(
-      xintercept = Herm_FS$Day[1],
+      xintercept = Herm_FS$day[1],
       size = 1,
@@
    geom_vline(
-      xintercept = Herm_FS$Day[2],
+      xintercept = Herm_FS$day[2],
       size = 1.5,
@@
    geom_vline(
-      xintercept = Herm_FS$Day[3],
+      xintercept = Herm_FS$day[3],
       size = 1,
@@
    ) +
-   geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5) +
-   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)")) +
+   geom_area(aes(y = daily_rain, fill = year), alpha = 0.5) +
+   scale_y_continuous(limits = c(0, 45),sec.axis = dup_axis(name = "Rainfall (mm)")) +
    scale_x_continuous(
@@
 ### Gatton historical weather
-```{r Gatton_weather, include=FALSE}
+```{r Gatton_weather, echo=FALSE}
 # ______  Gatton  _______
@@
 # Add columns for Year and date to data
-Gat_Tm_aver <- Gat_Tm_aver %>%
-   mutate(
-      Year = substr(Gat_Tm_aver$date, start = 1, stop = 4),
-      Day = year2day(Gat_Tm_aver$date)
-   )
+# Add columns for Year and date to data
+Gat_Tm_aver$year <- substr(Gat_Tm_aver$date, start = 1, stop = 4)
+Gat_Tm_aver$day <- sapply(Gat_Tm_aver$date,year2day)
 
 # Create data subset of powdery mildew data means for the first sign of the disease by location
-Gatton_FS <- PM.dat %>%
-   group_by(Trial_ref, Location) %>%
-   summarise(First_sign = mean(as.Date(first_sign_disease), na.rm = T)) %>%
-   filter(Location == "Gatton") %>%
-   mutate(Year = factor(substr(First_sign, 1, 4)),
-          Day = year2day(First_sign))
 
-ggplot(subset(Gat_Tm_aver, Year == 2012),
-       aes(Day)) +
-   geom_line(aes(y = max_T, colour = Year)) +
-   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
-   geom_line(aes(y = min_T, colour = Year)) +
-   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
+Gatton_FS <- PM.dat_sum[PM.dat_sum$location == "Gatton",]
+Gatton_FS$day <- as.numeric(Gatton_FS$day)
+
+ggplot(subset(Gat_Tm_aver, year == 2012),
+       aes(day)) +
+   geom_line(aes(y = max_T, colour = year)) +
+   geom_line(aes(y = min_T, colour = year)) +
    labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
         title = "Maximum and minimum daily temperatures in Gatton") +
-   scale_y_continuous(limits = c(0, 40)) +
-   scale_x_continuous(
-      limits = c(0, 200),
-      labels = c(subset(
-         Gat_Tm_aver, Year == levels(Gatton_FS$Year)
-      )$date[c(1, 50, 100, 150, 200)]),
-      breaks = c(1, 50, 100, 150, 200)
-   ) +
    theme(
@@
    ) +
-   geom_vline(xintercept = Gatton_FS$Day,
+   geom_vline(xintercept = Gatton_FS$day,
               colour = "green",
               size = 1) +
-   geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5) +
+   geom_area(aes(y = daily_rain, fill = year), alpha = 0.5) +
    scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)")) +
@@
    )
-#   scale_x_continuous(limits = as.Date(c("2012-01-01","2012-06-01")))
+
 ```

### 2019-12-04 02_Weather.Rmd
Remove redundant lines

@@
    geom_line(aes(y = max_T, colour = year)) +
-   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
    geom_line(aes(y = min_T, colour = year)) +
-   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
    labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
@@
    scale_y_continuous(limits = c(0, 40),sec.axis = dup_axis(name = "Rainfall (mm)"))
-#   scale_x_continuous(limits = c(1,180),
-#                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
-#                      labels = c("2012-Jan-01","2012-Feb-01","2012-Mar-01","2012-Apr-01","2012-May-01","2012-Jun-01","2012-Jul-01"))
 ```
@@
    geom_line(aes(y = max_T, colour = year)) +
-   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
    geom_line(aes(y = min_T, color = year)) +
-   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
    labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
@@
 # Add columns for Year and date to data
-# Add columns for Year and date to data
 Gat_Tm_aver$year <- substr(Gat_Tm_aver$date, start = 1, stop = 4)
@@
 # Create data subset of powdery mildew data means for the first sign of the disease by location
-
 Gatton_FS <- PM.dat_sum[PM.dat_sum$location == "Gatton",]

### 2019-12-04 01_Meta-analysis_experiments.Rmd
Save the experimental sites to a csv
Added some explaination and removed some old commented code

@@
 # Studies considered in meta-analysis
+
+This meta-analysis uses data collected by a number of researchers from the Department of Agriculture and Primary Industries and the University of Southern Queensland.
+It is worth noting Malcolm Riley and Dr Sue Thompsons effort in establishing and coordinating early field trials between 2010 and 2016.
 
@@
    + Premer  
-   + Milmerran   
+   + Millmerran   
    + Mt Mary   
@@
 
-# source("Cleaning historical data.R", echo = FALSE, print.eval = FALSE)
-# ___ Datasets available ___
-# data   Herm_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2017, Hermitage and Fogerty
-# data   King_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2016, Hermitage and Kingaroy
-# data   Fogerty_17.1   - Full disease ratings and yeild data from Fogerty field trial in 2017
-# data   Herm_17.1      - Full disease ratings and yeild data from Hermitage field trial in 2017
-# data   PM_MB_17       - Full disease ratings and yeild data from Hermitage and Fogerty in 2017
-# data   PM_MB_16       - End of season powdery mildew rating and Yield data from two field trials in 2016, Hermitage and Kingaroy
-# data   PM_MB_means    - Mean disease rating and yeild data, from trial reports
-
 PM.dat <- import_data()
-
-glimpse(PM.dat)
 
@@
 ```
+
+## Powdery mildew ratings
+
+   1. No powdery mildew colonies observed on any plant  
+   2. Small colonies in lower 1/3 of canopy, up to 75% of plants affected  
+   3. Colonies in lower 1/2 of canopy, >75% of plants affected  
+   4. Colonies in lower 2/3 of canopy, up to 75% of plants affected  
+   5. Colonies in lower 2/3 of canopy, >75% of plants affected  
+   6. Colonies in lower 2/3 of canopy, 100% of plants affected  
+   7. Colonies in lower 2/3 of canopy of 100% of plants, some plants with colonies also in top 1/3 of canopy  
+   8. Colonies to top of plant with >75% of plants affected  
+   9. Colonies to top of plant with 100% of plants affected and heavy leaf drop
 
@@
 
+write.csv(experiment_sites,"data/Mungbean_experiment_sites.csv", row.names = FALSE)
+
 leaflet(experiment_sites) %>%
@@
    addMarkers(lng = ~lon, lat = ~lat, popup = ~htmlEscape(location))
-#   addPopups(lng = experiment_sites$lon, lat = experiment_sites$lat, popup = experiment_sites$location)
 

### 2019-12-05 03_Preliminary_analysis.Rmd
Correcting/updating broken code

@@
 
-### Fungicides
-#### Fungicide type
 The data plotted below are from `r length(unique(PM_MB_means$trial_ref))` field trials between (`r first(levels(PM_MB_means$year))` - `r last(levels(PM_MB_means$year))`) of which the details are described in [Studies considered in meta-analysis section](#studies-considered-in-meta-analysis).
@@
 Some experiments have in-season observations of disease incidence and severity, however here we have summarised the data to show only the end of season observations.
+
+### Fungicides
+#### Fungicide type
+Let's explore how many different types of fungicide were used and at what frequency.
+
 ```{r Fungicides}
@@
 
-   - Tebuconazole and propiconazole might be able to be pooled as a triazole fungicide treatment.
+   - Tebuconazole and propiconazole could be pooled as a triazole or demethylation inhibitors (DMI) fungicide treatment.
 
@@
 
-   - Perhaps best way forward is to do an analysis of only the triazoles/demethylation inhibitors. Then do another including azoxystrobin as a comparison.
+   - Perhaps best way forward is to do an analysis of only the triazoles/DMIs. Then do another including azoxystrobin as a comparison.
 
@@
 
-```{r Fungicide_x_nSprays, message=FALSE}
+```{r Fungicide_x_nSprays_tble, message=FALSE}
 PM_MB_means %>%
@@
 
-class(PM_MB_means$fungicide)
+```
+
+Plot one and two applications of the main sprays
+
+```{r Fungicide_x_nSprays_tble, message=FALSE}
+
+PM_MB_means[PM_MB_means$fungicide_ai == "sulphur (SC)"|
+               PM_MB_means$fungicide_ai == "sulphur (WP)"|
+               PM_MB_means$fungicide_ai == "sulphur (Ultra SC)","fungicide_ai"] <- "sulphur"
+
+PM_MB_means$sprays <- sapply(PM_MB_means$total_fungicide, FUN = function(x){if(x == 1){return("one")}else{return("plus")}})
 
 PM_MB_means %>%
-   mutate(fungicide = as.factor(PM_MB_means$fungicide)) %>%
+   mutate(fungicide_ai = as.factor(PM_MB_means$fungicide_ai)) %>%
    filter(total_fungicide == 1 | total_fungicide == 2) %>%
    filter(
-      fungicide != "pyrazophos" &
-         fungicide != "control" &
-         fungicide != "benomyl" &
-         fungicide != "Acibenzolar-S-methyl"
-   ) %>%
-   mutate(fungicide = factor(fungicide, 
+      fungicide_ai != "pyrazophos" &
+         fungicide_ai != "control" &
+         fungicide_ai != "benomyl" &
+         fungicide_ai != "Acibenzolar-S-methyl") %>%
+   mutate(fungicide_ai = factor(fungicide_ai, 
                              levels = c("carbendazim", "pyraclostrobin",
@@
                                         "200 g/L tebuconazole + 120 g/L azoxystrobin"))) %>%
-   ggplot(aes(y = prop_YG, x = fungicide)) +
+   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
    facet_grid(rows = vars(total_fungicide)) +
-   geom_boxplot(aes(fill = fungicide, alpha = 0.5)) +
+   geom_boxplot(aes(fill = fungicide_ai, alpha = 0.5)) +
    geom_hline(aes(yintercept = 0), size = 0.5) +
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
    labs(y = "Proportion of grain yield saved",
@@
    theme(legend.position = "none") +
-   # coord_cartesian() +
-   # scale_x_discrete(
-   #    limits = c(
-   #       "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin",
-   #       "Propiconazole",
-   #       "Tebeconazole",
-   #       "200g/L Azoxystrobin + 80 g/L Cyproconazole",
-   #       "Sulphur",
-   #       "Carbendazim",
-   #       "Pyraclostrobin",
-   #       "Azoxystrobin"
-   #    )
-   # ) +
-   #  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
    coord_flip()
-#scale_x_continuous(limits = c(-0.3,0.6))
+
+PM_MB_means %>%
+   mutate(fungicide_ai = as.factor(PM_MB_means$fungicide_ai)) %>%
+#   filter(total_fungicide == 1 | total_fungicide == 2) %>%
+   filter(
+      fungicide_ai != "pyrazophos" &
+         fungicide_ai != "control" &
+         fungicide_ai != "benomyl" &
+         fungicide_ai != "Acibenzolar-S-methyl") %>%
+   mutate(fungicide_ai = factor(fungicide_ai, 
+                             levels = c("carbendazim", "pyraclostrobin",
+                                        "sulphur", "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                                        "tebuconazole", "propiconazole", 
+                                        "200 g/L tebuconazole + 120 g/L azoxystrobin"))) %>%
+   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
+   facet_grid(rows = vars(sprays)) +
+   geom_boxplot(aes(fill = fungicide_ai, alpha = 0.5)) +
+   geom_hline(aes(yintercept = 0), size = 0.5) +
+   labs(y = "Proportion of grain yield saved",
+        title = "Grain yield proportion saved\ngrouped by Fungicide type") +
+   theme_usq() +
+   theme(legend.position = "none") +
+   coord_flip()
 

### 2019-12-06 03_Preliminary_analysis.Rmd
Correct code and focus more on both DMI

@@
 library(devtools)
+library(reshape2)
 library(lme4)
@@
 unique(PM_MB_means[
-   grep("sulphur",PM_MB_means$fungicide),
-   "fungicide"])
-PM_MB_means[grep("sulphur",PM_MB_means$fungicide),"fungicide"] <- "sulphur"
+   grep("sulphur",PM_MB_means$fungicide_ai),
+   "fungicide_ai"])
+PM_MB_means[grep("sulphur",PM_MB_means$fungicide_ai),"fungicide_ai"] <- "sulphur"
 
@@
 
-First lets investigate the difference in the effect of fungicide on proportion of yield saved?
+First lets investigate the difference in the effect of the type of fungicide on proportion of yield saved?
 
@@
 PM_MB_means %>%
-   group_by(fungicide, total_fungicide) %>%
+   group_by(fungicide_ai, total_fungicide) %>%
    summarise(
@@
 
-Plot one and two applications of the main sprays
+Lets visualise this in a plot for one and two sprays only.
 
 ```{r Fungicide_x_nSprays_tble, message=FALSE}
-
-PM_MB_means[PM_MB_means$fungicide_ai == "sulphur (SC)"|
-               PM_MB_means$fungicide_ai == "sulphur (WP)"|
-               PM_MB_means$fungicide_ai == "sulphur (Ultra SC)","fungicide_ai"] <- "sulphur"
-
-PM_MB_means$sprays <- sapply(PM_MB_means$total_fungicide, FUN = function(x){if(x == 1){return("one")}else{return("plus")}})
 
@@
 
-PM_MB_means %>%
-   mutate(fungicide_ai = as.factor(PM_MB_means$fungicide_ai)) %>%
-#   filter(total_fungicide == 1 | total_fungicide == 2) %>%
-   filter(
-      fungicide_ai != "pyrazophos" &
-         fungicide_ai != "control" &
-         fungicide_ai != "benomyl" &
-         fungicide_ai != "Acibenzolar-S-methyl") %>%
-   mutate(fungicide_ai = factor(fungicide_ai, 
-                             levels = c("carbendazim", "pyraclostrobin",
-                                        "sulphur", "200 g/L azoxystrobin + 80 g/L cyproconazole",
-                                        "tebuconazole", "propiconazole", 
-                                        "200 g/L tebuconazole + 120 g/L azoxystrobin"))) %>%
-   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
-   facet_grid(rows = vars(sprays)) +
-   geom_boxplot(aes(fill = fungicide_ai, alpha = 0.5)) +
-   geom_hline(aes(yintercept = 0), size = 0.5) +
-   labs(y = "Proportion of grain yield saved",
-        title = "Grain yield proportion saved\ngrouped by Fungicide type") +
-   theme_usq() +
-   theme(legend.position = "none") +
-   coord_flip()
-
 ```
@@
 
-```{r tebu_dose}
+```{r tebuAndPropi_dose}
 PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole") %>%
+   filter(fungicide_ai == "tebuconazole"|
+             fungicide_ai == "propiconazole") %>%
    select(trial_ref,
@@
           first_sign_disease,
+          fungicide_ai,
           dose_ai.ha,
           total_fungicide) %>%
-   ggplot(aes(x = as.factor(dose_ai.ha))) +
+   ggplot(aes(x = as.factor(dose_ai.ha), fill = fungicide_ai)) +
    xlab("Dose (g ai/ha)") +
@@
    geom_bar() +
+   facet_grid(rows = vars(fungicide_ai))+
    scale_fill_usq() +
@@
 
-#### Number of fungicide sprays
+There is much variation in the propiconazole dose, lets inspect the difference in yields for each dose.
 
-#### Timing of fungicide sprays
-
-### Mungbean cultivars  
-Host genotype may need to be analysed to determine the effect.
-
-```{r Host_genotype}
+```{r PropiDoseEffect}
 PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole",
-         row_spacing == 0.75) %>%
-   group_by(host_genotype, trial_ref) %>%
-   summarise() %>%
-   count() %>%
-   rename(Treatments = n) %>%
-   ggplot(aes(x = host_genotype, y = Treatments)) +
-   xlab("Cultivar") +
-   ylab("N Trials") +
-   ggtitle(label = "Cultivars used in tebuconazole trials with 0.75 m row spacing") +
-   geom_col() +
+   filter(fungicide_ai == "propiconazole") %>%
+   ggplot(aes(x = relevel(as.factor(dose_ai.ha),"62.5"), y = prop_YG)) +
+   xlab("Dose (g ai/ha)") +
+   ggtitle(label = "Yield for each respective propiconazole dose") +
+   geom_boxplot() +
    scale_fill_usq() +
@@
    theme_usq()
+
 ```
+
+#### Number of fungicide sprays
+
+Lets look at the frequency of sprays per fungicide.
+```{r Fungicide_x_nSprays}
+table(PM_MB_means$fungicide_ai, PM_MB_means$total_fungicide)
+
+PM_MB_means[PM_MB_means$fungicide_ai == "control"
+               ,]
+
+```
+
+#### Timing of fungicide sprays  
+When are fungicides sprayed in relation to first sign.
+
+```{r spray_relative2FS}
+PM_MB_means %>%
+   mutate(s1_DfromFS = fungicide_application_1 - first_sign_disease,
+          s2_DfromFS = fungicide_application_2 - first_sign_disease,
+          s3_DfromFS = fungicide_application_3 - first_sign_disease,
+          s4_DfromFS = fungicide_application_4 - first_sign_disease,
+          s5_DfromFS = fungicide_application_5 - first_sign_disease) %>%
+   gather(key = spray, value = n_days, s1_DfromFS, s2_DfromFS, s3_DfromFS, s4_DfromFS, s5_DfromFS)%>%
+   ggplot(aes(x = spray, y = n_days))+
+   geom_violin()
+
+```
+
+### Mungbean cultivars  
+What role does host genotype have in tolerating disease preasure and is it likely to influence the meta-analysis.
 
@@
    - Jade: Moderately susceptible
+
+Lets plot a stacked barplot of the number of sprays for both demethylation inhibitors, tebuconazole and propiconazole against each cultivar.
+
+```{r Host_genotype}
+PM_MB_means %>%
+   filter(fungicide_ai == "tebuconazole"|
+             fungicide_ai == "propiconazole")%>%
+   group_by(host_genotype, fungicide_ai, trial_ref) %>%
+   summarise() %>%
+   count() %>%
+   rename(Treatments = n) %>%
+   ggplot(aes(x = host_genotype, y = Treatments, fill = fungicide_ai)) +
+   xlab("Cultivar") +
+   ylab("N Trials") +
+   ggtitle(label = "Cultivars used in tebuconazole trials") +
+   geom_col() +
+   scale_fill_usq() +
+   scale_colour_usq() +
+   theme_usq()
+```
 

### 2019-12-09 03_Preliminary_analysis.Rmd
Corrections and additions to make easier for flow.

@@
 
-First lets investigate the difference in the effect of the type of fungicide on proportion of yield saved?
+First lets investigate the difference in the effect of the type of fungicide on proportion of yield saved. Proportion of yield saved is used in attempt to reduce variation between trials.
 
@@
 
+There is a small yield effect when applying fungicide and it is unclear how much a second spray improves yield saved. Interestingly Sulpur sprays might be worth investigating when sprayed twice.
+
 #### Fungicide Doses  
-
-All trials that used tebuconazole used approximately the same dose.
-Dose of the active ingredient ranged from 62.35&nbsp;g per hectare to 60&nbsp;g per hectare.
+We should check that all fungicide doses that were used were roughly the same if we are to compare between trials were dose might be different.
 
@@
 
-There is much variation in the propiconazole dose, lets inspect the difference in yields for each dose.
+All trials that used tebuconazole used approximately the same dose. Dose of the active ingredient ranged from 62.35&nbsp;g per hectare to 60&nbsp;g per hectare.
+
+There is a large amount of variation in the propiconazole dose, lets inspect the difference in yields for each dose.
 
@@
    theme_usq()
+```
+
+Which studies used which doses?
+
+```{r}
 
@@
 table(PM_MB_means$fungicide_ai, PM_MB_means$total_fungicide)
-
-PM_MB_means[PM_MB_means$fungicide_ai == "control"
-               ,]
 

### 2019-12-09 03_Preliminary_analysis.Rmd
Investigate the influence of propiconazole on yield

@@
 
-Which studies used which doses?
+This dose effect should be acknowledged in the meta-analysis. How many treatments of each dose have been investigated per trial?
 
-```{r}
+```{r table_PropiDoses}
+table(as.character(PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole",]$trial_ref), 
+      PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole",]$dose_ai.ha)
+```
 
+Two trials show both doses were applied in the same trial, mung1112/01 and mung1112/02. Let look at the difference in proportion of yield saved in these trials.
+
+```{r PropiDoses_TrialCompar}
+
+boxplot(prop_YG ~ dose_ai.ha, data = PM_MB_means[(PM_MB_means$trial_ref == "mung1112/01" |
+                                                    PM_MB_means$trial_ref == "mung1112/02") &
+                                                    PM_MB_means$fungicide_ai == "propiconazole",])
 ```
+
+This plox plot, however, indicated the previous plot might be skewed by high yielding trials.
 
@@
    ggplot(aes(x = spray, y = n_days))+
-   geom_violin()
+   geom_violin() +
+   scale_x_discrete(labels = c("First\nSpray", "Second\nspray","Third\nspray","Fourth\nspray","Fifth\nspray"))+
+   theme_usq()
 

### 2019-12-17 03_Preliminary_analysis.Rmd
update genotype volatility

@@
 # Import data
-PM_MB_means <- import_data()
+PM_MB_means <- import_data() # link expires 2021-12-01
 
@@
 ### Mungbean cultivars  
-What role does host genotype have in tolerating disease preasure and is it likely to influence the meta-analysis.
-
-In general the mungbean varieties have the following resistance to powdery mildew.
+In general, the mungbean varieties have the following resistance to powdery mildew.
 
@@
 
-Lets plot a stacked barplot of the number of sprays for both demethylation inhibitors, tebuconazole and propiconazole against each cultivar.
+Let's view a stacked bar plot of the number of sprays for both demethylation inhibitors, tebuconazole and propiconazole against each cultivar.
 
@@
 
-Host genotype seems to contribute to the variation in yield. Berken shows higher yields compared to crystal and jade.
+Does host cultivar significantly impact the yield?
+Lets look at the volitility in yields to see if any cultivar yields better or has greater toleratance to powdery mildew.
+Below we plot distributions of mean trial yields for each cultivar.
+
+First lets look at overall yields for each cultivar , where trial is not a factor, for all treatments (spray and no spray).  
 ```{r yield_vol}
@@
 YV1[[3]]
+```
+Now lets look at overall yields for each cultivar, where trial is not a factor, in only the no spray treatments.
+```{r yieldVol_control}
+
 YV2 <- yield_volatility(genotype_by_trial = FALSE, control_only = TRUE)
 YV2[[2]]
+YV2[[3]]
 
+```
+Volitility of the cultivars are fairly similar when trial is not considered as a factor.
+Green diamond shows little volatility however this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trials.
+
+Lets examine the same plots as above but only for the most commonly used trial site, Hermitage.  
+```{r yieldVol_Herm}
 YV1_herm <- yield_volatility(genotype_by_trial = FALSE, control_only = FALSE, location = "Hermitage")
@@
 
+```
+Jade shows a large amount of volitility, excluding Green Diamond, Crystal shows the next least volatility.
+
+Lets take a closer look at Crystal with spray managment treatments and without.  
+```{r YieldVol_Crystal}
 YV1_crystal <- yield_volatility("Crystal",control_only = FALSE)
@@
 
-YV2_crystal <- yield_volatility("Crystal",control_only = TRUE)
+YV2_crystal <- yield_volatility("Jade",control_only = TRUE)
 YV2_crystal[[2]]
 
+```
+
+```{r}
 YV1_herm_jade <- yield_volatility("Jade",control_only = FALSE, location = "Hermitage")
@@
 ```
+Host genotype seems to contribute to the variation in yield. Berken shows higher yields compared to crystal and jade.
 

### 2019-12-29 03_Preliminary_analysis.Rmd
Cultivar prelim analysis

@@
    ylab("N Trials") +
-   ggtitle(label = "Cultivars used in tebuconazole trials") +
+   ggtitle(label = "Cultivars used in either tebuconazole or propiconazole trials") +
    geom_col() +
@@
 ```
-Volitility of the cultivars are fairly similar when trial is not considered as a factor.
+Volitility of the cultivars are fairly similar when trial is not considered as a factor (when we inspect plots of all treatments and only spray treatments).
 Green diamond shows little volatility however this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trials.
@@
 ```{r YieldVol_Crystal}
-YV1_crystal <- yield_volatility("Crystal",control_only = FALSE)
+YV1_crystal <- yield_volatility(genotype = "Crystal",control_only = FALSE)
+YV1_crystal[[2]]
+YV1_crystal <- yield_volatility(genotype = "Crystal",control_only = TRUE)
 YV1_crystal[[2]]
 
-YV2_crystal <- yield_volatility("Jade",control_only = TRUE)
+```
+There is a lot of variation between field trials for Crystal, but little variation within field trials.
+
+Lets look at Jade, to see if it differs.
+```{r YieldVol_Jade}
+YV2_crystal <- yield_volatility("Jade",control_only = FALSE)
 YV2_crystal[[2]]
+```
+For Jade there is high variation between trials and with in. Perhaps indicating lower tolerance. Lets look at the same plot with data only from no spray controls to see if the variation is the same.
 
+```{r YieldVol_JadeControl}
+YV3_crystal <- yield_volatility("Jade",control_only = TRUE)
+YV3_crystal[[2]]
 ```
+There seems to be a noticible shift in the probability curves between the two plots.
+Indicating that the tolerance in Jade may not as good as Crystal.
+A comparison between the fungicide efficacy for reducing powdery mildew severity and fungicide efficacy at mitigating yield loss.
 
-```{r}
-YV1_herm_jade <- yield_volatility("Jade",control_only = FALSE, location = "Hermitage")
-YV2_jade <- yield_volatility("Jade",control_only = TRUE)
-
-```
-Host genotype seems to contribute to the variation in yield. Berken shows higher yields compared to crystal and jade.
+Overall there seems to be an influence of cultuvar however this variation is not as distinct as the variation between trials.
 

### 2019-12-30 03_Preliminary_analysis.Rmd
complete revised row spacing. starting on revised in crop rainfall

@@
 
-Were there any statistical difference between all row spacing or only some?
-Can we pool certain row spacing that have no significant difference?  
-From the preliminary analysis, the graphs seem to imply if there is a lower overall yield there is no effect of row spacing on yield.
-However, if the average yield is more than approximately 0.6 - 1 t/ha then smaller row spacing has the potential to provide greater yield per hectare.
-
-```{r row_spacing}
-
+Lets plot the row spacing treatments for the response variables yield and disease severity. The main questions are:  
+   - Were there any statistical differences for mungbean yield or powdery mildew severity between row spacing treatments?  
+   - Can we pool certain row spacing that have no significant difference?
+
+```{r RS_severity}
+PM_MB_means$fungicide_ai
 # Which row spacing leads to the higher disease severity
@@
              year == 2018) %>%
-   filter(fungicide == "control") %>%
+   filter(fungicide_ai == "control") %>%
    ggplot(aes(y = PM_final_severity, x = factor(row_spacing))) +
@@
    #  geom_smooth()+
-   scale_y_continuous(limits = c(-5, 15)) +
+ #  scale_y_continuous(limits = c(-5, 15)) +
    theme_usq()+
@@
 
+```
+
+```{r RS_severity_x_trial}
+PM_MB_means$fungicide_ai
+# Which row spacing leads to the higher disease severity
+PM_MB_means %>%
+   filter(year == 2017 |
+             year == 2018) %>%
+   filter(fungicide_ai == "control") %>%
+   ggplot(aes(y = PM_final_severity, x = factor(row_spacing))) +
+   geom_boxplot() +
+   #  geom_smooth()+
+ #  scale_y_continuous(limits = c(-5, 15)) +
+   theme_usq()+
+   facet_grid(cols = vars(location))
+   ggtitle("Powdery mildew variation between different row spacing")
+
+```
+In the Wellcamp site, wider row spacing reduces PM severity, the other sites it seems there was not enough variation to make a distinction between row spacing treatments.
+
+```{r RS_yield}
 # Which row spacing leads to the higher yeild potential
@@
    theme_usq()+
-   ggtitle("Grain yield results for different row spacing at three locations")
-
-```
+   ggtitle("Grain yield results for different row spacing at three locations")+
+   xlab("Row spacing (m)")+
+   ylab("Grain yield - tonne per hectare")
+
+```
+The plots seem to imply when yield is limited, presumably by other abiotic factors, there is no effect of row spacing on yield, like in the Hertmitage trial.
+However, if the average yield is more than approximately 1 t/ha then smaller row spacing has the potential to provide greater yield per hectare.
+
+Overall row spacing may influence both powdery mildew severity and yield.
 
@@
 In crop rain could be a significant factor which contributes to the end of season grain yield.
-To investigate any relationship I will loop a linear model over time periods from 20 days prior to planting, to 100 days after planting.
-
-Loop over the dates at the start of the season (to 90 days after planting) to find which date fits the best linear model for grain weight and in-crop rainfall.
+To investigate this effect I will use a linear model (GY ~ SR) where seasonal rainfall represents a specific time frame with respect to planting time.
+Multiple time frames were tested from 20 days prior to planting, to 100 days after planting.
+
+The multiple time frames were tested by a loop over the dates at the start of the season (to 90 days after planting) to find which date fits the best linear model for grain weight and in-crop rainfall.
 The code for this process was moved to be contained within it's own script and can be run as a job as it can take a long time.
@@
 lm_rain <- rbind(lm_rain1,lm_rain2,lm_rain3,lm_rain4)
-
+```
+
+Now we have read in the data from the previously computed models lets find the linear model which has:  
+   - The lowest P value  
+   - the highest adjusted r squared value
+
+```{r WhichLModel}
 lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)),]
@@
 
+```
+
+To visualise the model fits we will use a heat map to describe how the models faired in relation to the rainfall windows.
+log of the p value was used to improve the resolution of small very small p values.
+```{r rainLMpvalue}
 ggplot(lm_rain, aes(x = start_day, y = end_day, z = log(lm_pval)))+
@@
    geom_contour(bins = 15, colour = "white")+
-   geom_abline(intercept = 0, slope = 1, colour = "red")+
    geom_point(data = lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)),], aes(x = start_day, y = end_day), colour =" red")+
    scale_fill_distiller(palette ="RdBu", direction = -1)
+
+```
+
+```{r }
 

### 2019-12-30 03_Preliminary_analysis.Rmd
Rainfall review done

@@
 
-```{r }
-
+```{r rainLMrsquared}
 ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_rsquared))+
@@
    geom_contour(bins = 15, colour = "white")+
-   geom_abline(intercept = 0, slope = 1, colour = "red")+
    geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),], aes(x = start_day, y = end_day), colour =" red")+
    scale_fill_distiller(palette ="RdBu") 
-
+```
+
+```{r rainLMadjrsquared}
 ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_adj_rsquared))+
@@
    scale_fill_distiller(palette ="RdBu") 
-
-source("R/AUS_rainfall_function.r")
-source("R/rainfall_sum_dat.R")
-
-for(i in rain_dat_sum$trial_ref){
-dat_rain <- rain_dat_sum[rain_dat_sum$trial_ref == i,]
-
-   rain_dat_sum[which(rain_dat_sum$trial_ref == i), "rainfall_sum"] <- 
-      AUS_rainfall(StartDate = as.Date(dat_rain$planting_date) +
-                   lm_rain[which(lm_rain$lm_adj_rsquared == max(lm_rain$lm_adj_rsquared)), "start_day"],
-                EndDate = as.Date(dat_rain$planting_date) +
-                   lm_rain[which(lm_rain$lm_adj_rsquared == max(lm_rain$lm_adj_rsquared)), "end_day"],
-                latlong = as.vector(unlist(dat_rain[, 5:6])))
-}
-
-rain_lm <- lm(rainfall_sum ~ grain_yield, 
-                             data = rain_dat_sum[rain_dat_sum$location != "Hermitage",])
-
-summary(rain_lm)
-
-rain_dat_sum %>%
-   ggplot(aes(x = grain_yield, y = rainfall_sum, colour = location))+
-   geom_point() + 
-   geom_abline(intercept = -167.98, slope = 284.44, colour = "red")
-
-resid_rain_lm <- residuals(rain_lm)
-
 ```

### 2020-01-01 03_Preliminary_analysis.Rmd
Remove old analyses

@@
    geom_contour(bins = 15, colour = "white")+
-   geom_abline(intercept = 0, slope = 1, colour = "red")+
    geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),], aes(x = start_day, y = end_day), colour =" red")+
@@
 ### Season range and first incidence
+Mungbean is a summer crop and powdery mildew is requires cool conditions to establish.
+Therefore the disease can be avoided by planting early in summer or spring, avoiding cooler temperatures at the end of some seasons.
+Can we visualise when PM is most likely to establish over the calender year.
 
+I'll build a plot of horizontal lines indicating the season length and use a dot on the line to indicating the day of the year first sign was observed for that trial.  
 ```{r first_incidence}
-# Here I want to build a plot of horizontal lines indicating the season length and
-# place a dot on the line to indicating the day of the year first sign was observed for that trial
-
+# Create the data frame for the plot
 season_dates <- PM_MB_means %>%
@@
 # I used First sign because all trials have recorded this
-season_dates$trial_ref <- factor(season_dates$trial_ref, levels = levels(season_dates$trial_ref)[rev(order(season_dates$First_sign_PM))])
+season_dates$trial_ref <- 
+   factor(season_dates$trial_ref, 
+          levels = levels(season_dates$trial_ref)[rev(order(season_dates$First_sign_PM))])
 
+# Plot
 season_dates %>%
@@
 
+In most years, regardless of the age of the crop, powdery mildew establishes in March.
+
 #### Effect of Fungicide 
-**on proportional yield gain with respect to time of application**
+**Fungicide effect on proportional yield gain with respect to time of application**
 First lets look at the quantiles for each fungicide irrespective of other factors.
@@
 PM_MB_means %>%
-   group_by(fungicide) %>%
+   group_by(fungicide_ai) %>%
    summarise(
@@
 
-unique(PM_MB_means$fungicide)
 # plot table as a box plot
@@
    filter(
-      fungicide == c(
+      fungicide_ai == c(
          "200 g/L tebuconazole + 120 g/L azoxystrobin" ,
@@
          "tebuconazole",
-         "propiconazole"
+         "propiconazole",
+         "sulphur"
       )
    ) %>%
-   ggplot(aes(y = prop_YG, x = fungicide)) +
+   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
    geom_boxplot() +
@@
    guides(fill = guide_legend(title = "Fungicide")) +
-   coord_cartesian() +
    coord_flip()
@@
 ```{r Fungicide_lmer}
-levels(PM_MB_means$Fungicide)
 
-PM_MB_means$Fungicide <-
+PM_MB_means$fungicide_ai <-
    factor(
-      PM_MB_means$Fungicide,
+      PM_MB_means$fungicide_ai,
       levels = c(
@@
          "Acibenzolar-S-Methyl",
-         "Sulphur",
-         "Sulphur (SC)",
-         "Sulphur (Ultra SC)",
-         "Sulphur (WP)"
+         "Sulphur"
       )
@@
 
+class(PM_MB_means$trial_ref)
+
 PM_MB_lmer.1 <-
    lmer(
-      prop_YG ~ Fungicide * as.factor(total_Fungicide) + row_spacing + (1 |
-                                                                           Trial_ref),
-      data = subset(PM_MB_means, total_Fungicide == 1 |
-                       total_Fungicide == 2)
+      prop_YG ~ fungicide_ai * as.factor(n_treatment) + row_spacing + (1 |trial_ref),
+      data = subset(PM_MB_means, 
+                    n_treatment == 1 | n_treatment == 2)
    )
@@
 Propiconazole, on average, out performs other fungicides when mitigating yield loss.
-
-How many trials contain all of the most studied fungicides
-```{r Trials_with_top_three_Fungicides}
-Tebe_trials <-
-   unique(PM_MB_means[PM_MB_means$Fungicide == "Tebeconazole", ]$Trial_ref)
-Propi_trials <-
-   unique(PM_MB_means[PM_MB_means$Fungicide == "Propiconazole", ]$Trial_ref)
-Azoxystrobin_trials <-
-   unique(PM_MB_means[PM_MB_means$Fungicide == "Azoxystrobin", ]$Trial_ref)
-
-intersect(intersect(Tebe_trials, Propi_trials)
-          , Azoxystrobin_trials)
-
-```
-
-```{r Calculate_cuts, echo=FALSE}
-# removing 2017 and control data
-# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
-PM_MB_means1 <- PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-   #   filter(total_Fungicide ==1) %>%
-   mutate(days_from_1st = as.numeric(
-      as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") -
-         as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")
-   ))
-
-days_from_fungicid <- function(FSD, F1, F2, F3) {
-   dF1 <- as.numeric(as.Date(F1) - as.Date(FSD))
-   dF2 <- as.numeric(as.Date(F2) - as.Date(FSD))
-   dF3 <- as.numeric(as.Date(F3) - as.Date(FSD))
-   if (is.na(dF1)) {
-      return(NA)
-   } else{
-      if (between(dF1, lower = -1, upper = 1000)) {
-         return(dF1)
-      } else{
-         if (is.na(dF2)) {
-            return(dF1)
-         } else{
-            if (between(dF2, lower = dF1, upper = -0.1)) {
-               return(dF2)
-            } else{
-               return(dF3)
-            }
-         }
-      }
-   }
-}
-vec1 <- vector()
-for (i in 1:dim(PM_MB_means1)[1]) {
-   dF1 <-
-      as.numeric(
-         as.Date(PM_MB_means1$Fungicide_application_1, format = "%d/%m/%Y")[i] -
-            as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i]
-      )
-   dF2 <-
-      as.numeric(
-         as.Date(PM_MB_means1$Fungicide_application_2, format = "%d/%m/%Y")[i] -
-            as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i]
-      )
-   dF3 <-
-      as.numeric(
-         as.Date(PM_MB_means1$Fungicide_application_3, format = "%d/%m/%Y")[i] -
-            as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i]
-      )
-   if (is.na(dF1)) {
-      vec1 <- c(vec1, dF1)
-   } else{
-      if (between(as.numeric(dF1), -1, 1000)) {
-         vec1 <- c(vec1, dF1)
-      } else{
-         if (is.na(dF2)) {
-            vec1 <- c(vec1, dF1)
-         } else{
-            if (between(as.numeric(dF2), as.numeric(dF1), -1.1)) {
-               vec1 <- c(vec1, dF2)
-            } else{
-               if (is.na(dF3)) {
-                  vec1 <- c(vec1, dF2)
-               } else{
-                  if (as.numeric(dF3) >= 0) {
-                     vec1 <- c(vec1, dF2)
-                  } else{
-                     vec1 <- c(vec1, dF3)
-                  }
-               }
-            }
-         }
-      }
-   }
-}
-PM_MB_means1$spray_diff <-
-   vec1 # gives the closest fungicide application date to the first sign of disease
-#PM_MB_means1$days_from_1st
-
-```
-
-```{r Sulphur_efficacy, echo=FALSE}
-
-# unique(
-# PM_MB_means1 %>%
-#    group_by(Fungicide) %>%
-#    filter(n() >= 5) %>%
-#    select(days_from_1st))
-# 
-# 
-# PM_MB_means1 %>%
-#    group_by(Fungicide) %>%
-#    filter(n() >= 5) %>%
-# ggplot(aes(prop_YG))+
-#    geom_density(aes(fill = cut(spray_diff, c(-1,2,7,10,12,20))), alpha = 0.5)+
-#    geom_vline(aes(xintercept = 0), size =0.5)+
-#    facet_grid(rows = vars(cut(spray_diff, c(1,2,7,10,12,20))), cols = vars(Fungicide))+
-#    #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-#    labs(x = "Proportion of grain yeild saved",
-#    title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-#    theme(panel.grid.major = element_line(colour = "grey80"),
-#          panel.grid.minor = element_line(colour = "grey50"),
-#          panel.background = element_rect(fill = NA))+
-#    guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-#    scale_x_continuous(limits = c(-0.2,0.55))
-# 
-#
-
-#__________________________________________________________________________________________________________
-# levels(factor(PM_MB_means$Fungicide))
-
-# combine Sulphur treatments
-PM_MB_means2 <- PM_MB_means1 %>%
-   filter(
-      Fungicide == "Sulphur" |
-         Fungicide == "Sulphur (SC)" |
-         Fungicide == "Sulphur (Ultra SC)" |
-         Fungicide == "Sulphur (WP)"
-   )
-
-unique(PM_MB_means2$spray_diff)
-
-ggplot(PM_MB_means2, aes(prop_YG)) +
-   geom_density(aes(fill = cut(
-      PM_MB_means2$spray_diff, c(-30, -19, -15, -10, -1, 2, 7, 10, 12, 21)
-   )), alpha = 0.5) +
-   geom_vline(aes(xintercept = 0), size = 0.5) +
-   facet_grid(cut(PM_MB_means2$spray_diff, c(-30, -19, -15, -10, -1, 2, 7, 10, 12, 21)) ~
-                 .) +
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yield saved",
-        title = "Grain yield proportion saved grouped by\nwhen the first Sulphur fungicide application was made\nrelative to when Powdery Mildew was first seen") +
-   theme(
-      panel.grid.major = element_line(colour = "grey80"),
-      panel.grid.minor = element_line(colour = "grey50"),
-      panel.background = element_rect(fill = NA)
-   ) +
-   guides(
-      fill = guide_legend(title = "Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease")
-   ) +
-   scale_x_continuous(limits = c(-0.3, 0.6))
-
-```
-This plot shows that there is not a good probability that Sulphur will help save yield, even when it is sprayed at the ideal time.
-
-```{r each_fungicide}
-Chemical <-
-   c("Azoxystrobin", "Carbendazim", "Tebeconazole", "Propiconazole")
-levels(factor(PM_MB_means$Fungicide))
-
-# Generates multiple plots for each type of fungicide tested
-for (Chem in Chemical) {
-   PM_MB_means2 <- PM_MB_means1 %>%
-      filter(Fungicide == Chem)
-
-   cat(Chem)
-
-   # the following code 'spray_group' sets the spray_diff groupings that are used in the plots
-   spray_group <- c(min(unique(PM_MB_means2$spray_diff)) - 1,
-                    -5, 5,
-                    max(unique(PM_MB_means2$spray_diff)) + 1)
-
-   spray_group < -c(sort(unique(PM_MB_means2$spray_diff) - 1), max(unique(PM_MB_means2$spray_diff)))
-
-   print(spray_group)
-
-   p1 <- ggplot(PM_MB_means2, aes(prop_YG)) +
-      geom_density(aes(fill = cut(PM_MB_means2$spray_diff, spray_group)), alpha = 0.5) +
-      geom_vline(aes(xintercept = 0), size = 0.5) +
-      facet_grid(cut(PM_MB_means2$spray_diff, spray_group) ~ .) +
-      #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-      labs(x = "Proportion of grain yield saved",
-           title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen") +
-      theme(
-         panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA)
-      ) +
-      guides(fill = guide_legend(
-         title = paste(
-            Chem,
-            "Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"
-         )
-      )) +
-      scale_x_continuous(limits = c(-1, 1))
-
-   print(p1)
-
-}
-```
-It seems the calculation of spray diff does not elucidate any differences between application dates.
-
-### Yield saved 
-**Number of fungicide applications**
-The following density plots show mean yield saved in relation to how many sprays were applied.
-
-```{r PA_Yield, warning=FALSE, echo=FALSE}
-
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PMy <- PM_MB_means %>%
-   filter(fungicide != "control") %>%
-   group_by(total_fungicide) %>%
-   summarise(
-      n = length(yield_gain),
-      lower_2.5 = quantile(yield_gain, na.rm = T, c(0.025)),
-      median = median(yield_gain, na.rm = T),
-      mean = mean(yield_gain, na.rm = T),
-      upper_97.5 = quantile(yield_gain, na.rm = T, c(0.975))
-   )
-
-# Density plot of Number of fungicide applications and the resulting yeild saved (as a proportion)
-ggplot(subset(PM_MB_means, fungicide != "control"), aes(yield_gain)) +
-   geom_density(aes(
-      group = factor(total_fungicide),
-      fill = factor(total_fungicide)
-   ), alpha = 0.6) +
-   geom_vline(xintercept = 0, size = 1) +
-   labs(x = "Grain yield saved (t/ha)",
-        title = "Density plot of grain yield saved from differing numbers of fungicide applications") +
-   theme(
-      panel.grid.major = element_line(colour = "grey80"),
-      panel.grid.minor = element_line(colour = "grey50"),
-      panel.background = element_rect(fill = NA)
-   ) +
-   geom_vline(
-      data = quant_PMy,
-      aes(xintercept = lower_2.5,
-          colour = factor(total_fungicide)),
-      size = 0.9,
-      linetype =  "dashed"
-   ) +
-   geom_vline(
-      data = quant_PMy,
-      aes(xintercept = upper_97.5,
-          colour = factor(total_fungicide)),
-      size = 0.9,
-      linetype =  "dashed"
-   ) +
-   guides(
-      colour = guide_legend(title = "Upper (97.5%) and \nLower (2.5%) percentiles"),
-      fill = guide_legend(title = "Number of \nFungicide applications")
-   ) +
-   scale_x_continuous(limits = c(-0.3, 0.8))
-
-kable(quant_PMy,
-      caption = "Yield gain for each number of fungicide applications") %>%
-   kable_styling(fixed_thead = T, full_width = T)
-
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PM <- PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-   group_by(total_Fungicide) %>%
-   summarise(
-      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
-      median = median(prop_YG, na.rm = T),
-      mean = mean(prop_YG, na.rm = T),
-      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
-   )
-
-# Density plot of proportion of yield saved
-ggplot(subset(PM_MB_means, Fungicide != "control"), aes(prop_YG)) +
-   geom_density(aes(
-      group = factor(total_Fungicide),
-      fill = factor(total_Fungicide)
-   ), alpha = 0.6) +
-   geom_vline(xintercept = 0, size = 1) +
-   labs(x = "Proportion of grain yield saved",
-        title = "Density plot of the grain yield proportion saved \n by the number of fungicide applications") +
-   theme(
-      panel.grid.major = element_line(colour = "grey80"),
-      panel.grid.minor = element_line(colour = "grey50"),
-      panel.background = element_rect(fill = NA)
-   ) +
-   geom_vline(
-      data = quant_PM,
-      aes(xintercept = lower_2.5,
-          colour = factor(total_Fungicide)),
-      size = 0.9,
-      linetype =  "dashed"
-   ) +
-   geom_vline(
-      data = quant_PM,
-      aes(xintercept = upper_97.5,
-          colour = factor(total_Fungicide)),
-      size = 0.9,
-      linetype =  "dashed"
-   ) +
-   guides(
-      colour = guide_legend(title = "Upper (97.5%) and \nLower (2.5%) percentiles"),
-      fill = guide_legend(title = "Number of \nFungicide applications")
-   ) +
-   scale_x_continuous(limits = c(-0.3, 0.55))
-
-kable(quant_PM,
-      caption = "Proportion of yield gain for each number of fungicide applications") %>%
-   kable_styling(fixed_thead = T, full_width = T)
-#knitr::kable(quant_PM,
-#             col.names = c("Number of sprays", "2.5 percentile", "97.5 percentile"))
-#caption = "The 'upper' and 'lower' percentiles for proportion of yeild saved against the number of Fungicide sprays in a season.
-Data from 2011-2017 mungbean experimental means.
-Data ignores factors such as fungicide, dose, season or location of experiment")
-```
-
-\n\n\n\n\n\n\n
-
-#### Timing of Fungicide application
-The following density plots show mean yield saved (t / Ha) or proportion yield saved in relation to when the first fungicide spray was applied in relation to when powdery mildew was first seen in the mungbean crop.
-
-```{r eval = FALSE, message = FALSE, warning = FALSE, include = FALSE}
-PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-   #   filter(total_Fungicide ==1) %>%
-   mutate(days_from_1st = as.numeric(
-      as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") -
-         as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")
-   ))
-
-```
-
-```{r spray_timing&PropYield}
-# What range of
-unique(PM_MB_means1$days_from_1st)
-PM_MB_means1 %>%
-   group_by(cut(
-      PM_MB_means1$days_from_1st,
-      c(-41, -20, -15, -12, -0.5, 1.5, 7, 10, 12, 20)
-   )) %>%
-   summarise(
-      n = length(prop_YG),
-      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
-      median = median(prop_YG, na.rm = T),
-      mean = mean(prop_YG, na.rm = T),
-      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
-   ) %>%
-   kable(caption = "Difference in days between first sign of disease and first fungicide application and the effect on proportion of yield gain") %>%
-   kable_styling(fixed_thead = T, full_width = T)
-
-ggplot(PM_MB_means1, aes(prop_YG)) +
-   geom_density(aes(fill = cut(
-      PM_MB_means1$days_from_1st,
-      c(-41, -20, -15, -12, -0.5, 1.5, 7, 10, 12, 20)
-   )), alpha = 0.5) +
-   geom_vline(aes(xintercept = 0), size = 0.5) +
-   facet_grid(cut(
-      PM_MB_means1$days_from_1st,
-      c(-41, -20, -15, -12, -0.5, 1.5, 7, 10, 12, 20)
-   ) ~ .) +
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yield saved",
-        title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen") +
-   theme(
-      panel.grid.major = element_line(colour = "grey80"),
-      panel.grid.minor = element_line(colour = "grey50"),
-      panel.background = element_rect(fill = NA)
-   ) +
-   guides(
-      fill = guide_legend(title = "Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease")
-   ) +
-   scale_x_continuous(limits = c(-0.2, 0.55))
-```
 

### 2020-01-02 03_Preliminary_analysis.Rmd
Spell check and remove lmer

@@
 
-   4) Timing of fungicide spray/s relative to first sign of disease (ie. when pathogen is present)
+   4) Timing of fungicide spray/s relative to first sign of disease (_i.e_. when pathogen is present)
 
-   5) Host cultivars (probably is a covariate with season due to changing cultivars over time)
+   5) Host cultivars (probably is a co-variate with season due to changing cultivars over time)
 
@@
 
-There is a small yield effect when applying fungicide and it is unclear how much a second spray improves yield saved. Interestingly Sulpur sprays might be worth investigating when sprayed twice.
+There is a small yield effect when applying fungicide and it is unclear how much a second spray improves yield saved. Interestingly Sulphur sprays might be worth investigating when sprayed twice.
 
@@
 
-This plox plot, however, indicated the previous plot might be skewed by high yielding trials.
+This plot plot, however, indicated the previous plot might be skewed by high yielding trials.
 
@@
    geom_violin() +
-   scale_x_discrete(labels = c("First\nSpray", "Second\nspray","Third\nspray","Fourth\nspray","Fifth\nspray"))+
+   scale_x_discrete(labels = c("First\nspray", "Second\nspray","Third\nspray","Fourth\nspray","Fifth\nspray"))+
    theme_usq()
@@
 Does host cultivar significantly impact the yield?
-Lets look at the volitility in yields to see if any cultivar yields better or has greater toleratance to powdery mildew.
+Lets look at the volatility in yields to see if any cultivar yields better or has greater tolerance to powdery mildew.
 Below we plot distributions of mean trial yields for each cultivar.
@@
 ```
-Volitility of the cultivars are fairly similar when trial is not considered as a factor (when we inspect plots of all treatments and only spray treatments).
+Volatility of the cultivars are fairly similar when trial is not considered as a factor (when we inspect plots of all treatments and only spray treatments).
 Green diamond shows little volatility however this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trials.
@@
 ```
-Jade shows a large amount of volitility, excluding Green Diamond, Crystal shows the next least volatility.
+Jade shows a large amount of volatility, excluding Green Diamond, Crystal shows the next least volatility.
 
-Lets take a closer look at Crystal with spray managment treatments and without.  
+Lets take a closer look at Crystal with spray management treatments and without.  
 ```{r YieldVol_Crystal}
@@
 ```
-There seems to be a noticible shift in the probability curves between the two plots.
+There seems to be a noticeable shift in the probability curves between the two plots.
 Indicating that the tolerance in Jade may not as good as Crystal.
@@
 
-Overall there seems to be an influence of cultuvar however this variation is not as distinct as the variation between trials.
+Overall there seems to be an influence of cultivar however this variation is not as distinct as the variation between trials.
 
@@
 ```
-The plots seem to imply when yield is limited, presumably by other abiotic factors, there is no effect of row spacing on yield, like in the Hertmitage trial.
+The plots seem to imply when yield is limited, presumably by other abiotic factors, there is no effect of row spacing on yield, like in the Hermitage trial.
 However, if the average yield is more than approximately 1 t/ha then smaller row spacing has the potential to provide greater yield per hectare.
@@
    labs(x = "Proportion of grain yield saved",
-        title = "Grain yield proportion saved grouped by\nFungicide type") +
+        title = "Grain yield proportion saved grouped by\nfungicide type") +
    theme(
@@
 ```
-There was some hope groups of fungicide could be combined, _i.e._ Propiconazole and Tebeconazole, however it seems that they have different efficacies.
+There was some hope groups of fungicide could be combined, _i.e._ propiconazole and tebuconazole, however it seems that they have different efficacies.
 Let us look to see if there is anything skewing the above.
-
-Lets run this by a quick linear mixed effect model
-```{r Fungicide_lmer}
-
-PM_MB_means$fungicide_ai <-
-   factor(
-      PM_MB_means$fungicide_ai,
-      levels = c(
-         "control",
-         "Propiconazole",
-         "Tebeconazole",
-         "Azoxystrobin",
-         "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin",
-         "Carbendazim",
-         "Benomyl",
-         "Pyrazophos",
-         "Acibenzolar-S-Methyl",
-         "Sulphur"
-      )
-   )
-
-class(PM_MB_means$trial_ref)
-
-PM_MB_lmer.1 <-
-   lmer(
-      prop_YG ~ fungicide_ai * as.factor(n_treatment) + row_spacing + (1 |trial_ref),
-      data = subset(PM_MB_means, 
-                    n_treatment == 1 | n_treatment == 2)
-   )
-
-summary(PM_MB_lmer.1)
-
-```
-There is no significant difference between Fungicides, except for Sulphur which is significantly less effective than Propiconazole.
-Propiconazole, on average, out performs other fungicides when mitigating yield loss.
 
@@
 PM_MB_means %>%
-   filter(fungicide == "control") %>%
+   filter(fungicide_ai == "control") %>%
    ggplot(aes(x = PM_final_severity, y = grain_yield.t.ha.)) +
@@
 
-PM_MB_means %>%
-   ggplot(aes(x = PM_final_severity, y = prop_YG)) +
-   geom_point()+
-   geom_smooth(method = "lm")
+```
 
-```
+From the data we have it is difficult to determine if there is an association between powdery mildew severity and grain yield.

### 2020-01-02 04_Prep_data.Rmd
correct obsolete code

@@
       controlY <-
-         mean(dat2[dat2$fungicide == "control", "grain_yield.t.ha."])
+         mean(dat2[dat2$fungicide_ai == "control", "grain_yield.t.ha."])
 
@@
 
-      dat2[dat2$fungicide == "control", c("yield_gain", "prop_YG")] <-
+      dat2[dat2$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
          NA
@@
               )] <- "control"
-
+table(slim_PM_dat$spray_management)
 write.csv(slim_PM_dat, file = "data/slim_PM_clusterdat.csv", row.names = FALSE)
@@
 slimmer_PM_dat %>%
-   ggplot(aes(y= grain_yield.t.ha, x = vi))+
+   ggplot(aes(x= grain_yield.t.ha, y = vi))+
    geom_point()
 
+slimmer_PM_dat %>%
+   ggplot(aes(x= grain_yield.t.ha, y = Y_Msquare))+
+   geom_point()
+
+slimmer_PM_dat[slimmer_PM_dat$vi > 0.5,]
+
+boxplot(PM_MB_means$prop_YG, na.rm = TRUE)
+
+boxplot(PM_MB_means$yield_gain/PM_MB_means$grain_yield.t.ha., main = "Yield loss proportion")
+summary(PM_MB_means$yield_gain/PM_MB_means$grain_yield.t.ha., na.rm = TRUE)
+unique(PM_MB_means$trial_ref)
+
+boxplot(yield_gain/grain_yield.t.ha. ~ year,data = PM_MB_means, main = "Yield loss proportion")
+
+unique(PM_MB_means$fungicide_ai)
+
 ```

### 2020-01-02 05_MetaAnalysis.Rmd
code checks and meta_contrasts

@@
 library(lme4)
+library(kableExtra)
 
@@
 If any errors don't overlap, infering signicifant difference, the imputed variances are discarded and resampled until all treatment variances show no significant differences.
-
+### Imputing sample variances
 ```{r imputing_variances}
@@
 
+#### Imputing sample variances from Mean squares
 ```{r imputing_MSE}
+slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
 hist(unique(slimmer_PM_dat$Y_Msquare))
@@
          rnorm(n = 1,
-               mean = mean(TrialMSQ$`unique(Y_Msquare)`, na.rm = TRUE),
-               sd(TrialMSQ$`unique(Y_Msquare)`, na.rm = TRUE)
+               mean = mean(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE),
+               sd(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE)
          )
@@
 
+Before plotting lets have a look at how the trimmed down, modified data looks.
+
+```{r treatment_means_plot}
+slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management, levels(slimmer_PM_dat$spray_management)[rev(c(1,2,4,5,3))])
+
+slimmer_PM_dat %>%
+   ggplot(aes(y = prop_yield_gain, x = spray_management))+
+   geom_boxplot()+
+   #geom_point(position = "jitter", alpha = 1/5)+
+   geom_jitter(width = 0.1, alpha = 1/5)+
+   theme_usq()+
+   labs(x = "Spray management variable", 
+        y = "Grain yield (t/Ha)",
+        title = "Mean grain yield from each treatment \n categorised by spray management scenario")+
+   theme(plot.title = element_text(hjust = 0.5))+
+   coord_flip()
+
+kableExtra::kable(table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year), align=rep('c', 8))%>%  #commented as was redering empty, needs a look in
+   kable_styling("striped", fixed_thead = TRUE, full_width = FALSE, position = "center")
+
+```
+
+## Meta-analysis
 ```{r meta_1}
 library(metafor)
+slimmer_PM_dat$spray_management <-
+   factor(slimmer_PM_dat$spray_management,levels(slimmer_PM_dat$spray_management)[c(2,3,1,4,5)])
 
-slimmer_PM_dat$yi <- slimmer_PM_dat$grain_yield.t.ha
+slimmer_PM_dat$yi <- log(slimmer_PM_dat$grain_yield.t.ha)
 slimmer_PM_dat$vi <- slimmer_PM_dat$Y_Msquare/(slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha^2)
@@
 slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management)
-table(slimmer_PM_dat$spray_management)
+slimmer_PM_dat$trial_ref <- factor(slimmer_PM_dat$trial_ref)
+slimmer_PM_dat$trial <- factor(slimmer_PM_dat$trial)
 
@@
 
-```{r inspect_for_outliers}
-head(slimmer_PM_dat)
+```{r compare_meta&lmer}
+lme_PM <- lmer(yi ~ spray_management + (spray_management | trial), data = slimmer_PM_dat)
 
-slimmer_PM_dat %>%
-#   filter(spray_management == "Late_plus") %>%
-   ggplot(aes(prop_yield_gain, fill = spray_management))+
-   geom_histogram(alpha = 0.5)
-
-slimmer_PM_dat %>%
-   filter(spray_management == "Late_plus") %>%
-   ggplot(aes(prop_yield_gain, fill = trial_ref))+
-   geom_histogram(alpha = 0.5)
-
-slimmer_PM_dat %>%
-   filter(spray_management == "Recommended") %>%
-   ggplot(aes(prop_yield_gain, fill = trial_ref))+
-   geom_histogram(alpha = 0.5)
+summary(lme_PM)
 
 ```
+
+```{r meta_contrasts}
+anova(PM_mv_AI, L=rbind(c(0,1,-1,0,0),  # early vs late plus
+                        c(0,1,0,-1,0),  # early vs recommended
+                        c(0,1,0,0,-1),  # early vs recommended plus
+                        c(0,0,-1,1,0),  # late plus vs recommended 
+                        c(0,0,-1,0,1),  # late plus vs recommended  Plus
+                        c(0,0,0,-1,1))) # recommended vs recommended plus
+```
+Results show that Early applications are not significantly different to the no spray control or the one and two spray management options at the recommended time. Lets view this on a plot.
+
+```{r meta_results}
+results_AI <- data.frame(cbind(exp(PM_mv_AI$b), 
+                              exp((PM_mv_AI$ci.lb)),
+                              exp(PM_mv_AI$ci.ub)))
+
+results_AI <- data.frame(cbind(PM_mv_AI$b, 
+                              (PM_mv_AI$ci.lb),
+                              PM_mv_AI$ci.ub))
+
+treat <- c("control", "Early", "Recommended", "Recommended_plus","Late_plus")
+efficacy <- tbl_df(results_AI)
+efficacy$treat <- treat
+efficacy$se <- PM_mv_AI$se
+colnames(efficacy) <- c("Mean", "CIsup", "CIinf", "Treatment", "SE")
+efficacy
+```
+
+```{r meta_plot}
+efficacy %>% 
+  ggplot(aes(Treatment, Mean))+
+  geom_point(aes(size=1/SE), shape=15)+
+  geom_linerange(aes(ymin = CIinf, ymax = CIsup))+
+  coord_flip()+
+  theme_grey()+
+   geom_hline(yintercept = efficacy[efficacy$Treatment == "control",]$CIinf)
+
+```
+
+Check the yeild
+
+```{r}
+boxplot(slimmer_PM_dat$grain_yield.t.ha ~ slimmer_PM_dat$spray_management)
+
+```

### 2020-01-02 R/import_data.R
comment lines

@@ -10,7 +10,7 @@
 #' PM_MB_means <- import_data()
 #'
 
-#devtools::install_github("PaulMelloy/cloudy")
+# devtools::install_github("PaulMelloy/cloudy")
 
 
 x <- 

### 2020-01-02 R/yield_volatility.R
correct typos

@@ -12,13 +12,13 @@ yield_volatility <- function(genotype,
                              PM_MB_means$Y_error_type == "stdev" &
                              PM_MB_means$trial_ref != "mung1718/01" &  # Outlier
                              PM_MB_means$fungicide_ai == "control", ]
-      PlotTitle2 <- "/nin no spray control plots only"
+      PlotTitle2 <- "\nin no spray control plots only"
       
    }else{
       dat1 <- PM_MB_means[PM_MB_means$host_genotype == genotype &
                              PM_MB_means$trial_ref != "mung1718/01" & # Outlier
                              PM_MB_means$Y_error_type == "stdev", ]    
-      PlotTitle2 <- "/nin no spray control and spray treated plots"
+      PlotTitle2 <- "\nin no spray control and spray treated plots"
    }
    
    dat1 <- dat1[!is.na(dat1$trial_ref),]
@@ -46,7 +46,7 @@ yield_volatility <- function(genotype,
       ggplot(aes(x = values))+
       geom_density(aes(fill = trial), alpha = 0.4)+
       xlim(0.25,2.25)+
-      title(paste0(PlotTitle1,PlotTitle2))
+      ggtitle(paste0(PlotTitle1,PlotTitle2))
    
    mean_Y_volatility <- dat3 %>%
       group_by(trial) %>%
@@ -71,14 +71,14 @@ yield_volatility <- function(genotype,
                                    PM_MB_means$location == location &
                                    PM_MB_means$trial_ref != "mung1718/01" &  # Outlier
                                    PM_MB_means$fungicide_ai == "control", ]
-            PlotTitle2 <- "/nin no spray control plots only"
+            PlotTitle2 <- "\nin no spray control plots only"
             
             }
          if(is.na(location)){
             dat1 <- PM_MB_means[PM_MB_means$Y_error_type == "stdev" &
                                    PM_MB_means$trial_ref != "mung1718/01" &  # Outlier
                                    PM_MB_means$fungicide_ai == "control", ]
-            PlotTitle2 <- "/nin no spray control and treated plots"
+            PlotTitle2 <- "\nin no spray control and treated plots"
             
          }
             

### 2020-01-02 04_Prep_data.Rmd
Merge two tables to one and, clarify explaination

@@
+## Set environment and import data
+
 ```{r load_libraries}
@@
 ## Standardising sample variance  
+Meta-analyses use variance from the data to calculate the effect sizes. The type of variance needs to be the same across all the data incorporated in the meta-analysis.
 
-The type of variance needs to be standardised between trials and treatments for the meta-analysis.
+We are narrowing the meta-analysis to only include demethylation inhibitors, tebuconazole and propiconazole. Within studies which have used these fungicides, what type of error was reported?
 
@@
 PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole",
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole",
          row_spacing == 0.75) %>%
-   group_by(trial_ref, location, Y_error_type) %>%
-   summarise(tebuconazole_trts = length(Y_error_type))
+   group_by(trial_ref, location, Y_error_type, fungicide_ai) %>%
+   summarise(tebuconazole_trts = length(Y_error_type))%>%
+   arrange(Y_error_type)
 
-# Trials using propiconazole
-PM_MB_means %>%
-   filter(fungicide_ai == "propiconazole",
-          row_spacing == 0.75) %>%
-   group_by(trial_ref, location, Y_error_type) %>%
-   summarise(propiconazole_trts = length(Y_error_type))
 ```
 
-The experiment summaries report either standard deviation, least square differences or no error term (`NA`). Below we will convert LSD and standard deviation to sample variance
+The experiment summaries report either standard deviation, least square differences or no error term (`NA`).
+Below we will convert LSD and standard deviation to sample variance.
+In addition, we need to impute variances for the trials which did not report any form of variance (`NA`).
 

### 2020-01-02 04_Prep_data.Rmd
REmoving superflouos code and comments and editing explainations

@@
 library(readr)
+library(kableExtra)
 ```
@@
 ```{r variance_types}
-# PM_MB_means$Y_error_type <- forcats::fct_explicit_na(PM_MB_means$Y_error_type, na_level = NA)
-# Trials using tebuconazole
 PM_MB_means %>%
@@
    group_by(trial_ref, location, Y_error_type, fungicide_ai) %>%
-   summarise(tebuconazole_trts = length(Y_error_type))%>%
-   arrange(Y_error_type)
+   summarise(DMI_trts = length(Y_error_type))%>%
+   arrange(Y_error_type)%>%
+   kable(caption = "Number of treatments for each trial and the error type reported") %>%
+   kable_styling(fixed_thead = T) %>%
+   footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
 
@@
    distinct()
-Trials
 ```
 
-The trial, `mung1112/02` uses Least Square Differences (LSD) to describe the variation within the experiment.
-The following code attempts to convert this to sampling variance as per the method in [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
+The following code attempts to convert 'least square differences' (LSD) to sampling variance as per the method in [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
 Ideas for using a T-critical value of 1.697 came from reading a [statisics-how-to website](https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/).
@@
 ```{r LSD_2_Sampling Variance}
-# Formula and modifications based off information found at https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/
 
@@
       length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates) # degrees of freedom within groups
-   # n.A <- PM_MB_means[PM_MB_means$trial_ref == "Trial2012,]$replicates[1]
-   # n.B <- PM_MB_means[PM_MB_means$trial_ref == "Trial2012,]$replicates[2]
+
    LSD <-
@@
 
-   # SSwithin <- #unknown
-   # MSW <- SSwithin / DFw # mean square within (SS within / DF within)
-
-   #  LSD = (Tcrit) * sqrt(MSW * (1/n.A + 1/n.B))
-   #  (LSD/Tcrit) = sqrt(MSW * (1/n.A + 1/n.B))
-   #  (LSD/Tcrit)^2 = MSW * (1/n.A + 1/n.B)
-   #  (LSD/Tcrit)^2/(1/n.A + 1/n.B) = MSW
-   #  MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B) # This formula was abandon in favor for the formula in Nugugi et. at (2011)
    V_yield <-
       (PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[1] * (LSD /
-                                                                            Tcrit) ^ 2) / 2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
+                                                                            Tcrit) ^ 2) / 2 # method - Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
 
@@
             vector(length = length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates))
-      }
+      } # reset Sv vector if this is the first loop
+
+      ###############################################3
+      # ___ Adjusting formula to suit our data_______
+      #
       #  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates[j] *
@@
       #       as.numeric(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$grain_yield.t.ha[j])^2)
-      # 
+      # #################################################################
+
       Sv[j] = V_yield / 
@@
 Trials <- PM_MB_means %>%
-   filter(#fungicide_ai == "tebuconazole",
-      #row_spacing.m == 0.75,
-      Y_error_type == "stdev") %>%
+   filter(Y_error_type == "stdev") %>%
    select(trial_ref) %>%
@@
 for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error)) {
-   # create empty vector at first iteration with length of j
    if (j == 1) {
@@
          vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error))
-   }
+   }# create empty vector at first iteration with length of j
 
-   # Equation to convert standard deviation to Sampling Variance
    Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error[j]) ^
@@
 
+## Reduce dataset to required variables  
+Lets tidy up the dataset into a data frame of only the variables which are required for the analysis.
+
+First remove the irrelevant columns/variables.
+Then calculate fungicide application timing variables relative to the first sign of disease.
+Entries with NA in the grain yield or powdery mildew severity are also removed from the data.
+
 ```{r clustered_fungicide_applications}
-source("R/slimming_PM_dat.R")
-head(slim_PM_dat)
+source("R/slimming_PM_dat.R") # see R script for the code which reduces the data.
 
@@
 
+head(slim_PM_dat)
 ```
+
+### Cluster fungicide applications  
+We are going to define 'fungicide application timing' as a categorical variable, relative to the first sign of powdery mildew.
+
+These categorical variables are named:  
+   - **Early**: First fungicide application was prior to first sign of disease.  
+   - **Recommended**: First fungicide application was applied on the day powdery mildew was observed, or within three days of first sign.  
+   - **Late**: First fungicide application was four or more days after first sign of disease being observed.
+
+Follow up fungicide applications (cluster_2 and cluster_3) were also categorised as either, early, recommened or late.
 
@@
 
-Cluster the clusters
+Lets look at these clusters to see where we have the most degrees of freedom.
 

### 2020-01-02 04_Prep_data.Rmd
cut down unneccercary code and commenting. expanded on explanations between chunks

@@
 library(kableExtra)
+library(ggplot2)
 ```
@@
 
-Follow up fungicide applications (cluster_2 and cluster_3) were also categorised as either, early, recommened or late.
+Follow up fungicide applications (cluster_2 and cluster_3) were also categorised as either, early, recommended or late.
 
@@
   )
-
-slim_PM_dat[slim_PM_dat$fungicide_ai == "control",
-            c("fungicide_timing_1", "fungicide_timing_2", "fungicide_timing_3",
-              "cluster_1", "cluster_2","cluster_3"
-              )] <- "control"
-table(slim_PM_dat$spray_management)
-write.csv(slim_PM_dat, file = "data/slim_PM_clusterdat.csv", row.names = FALSE)
 
@@
 table(slim_PM_dat$spray_management)
-sum(table(slim_PM_dat$spray_management)[1:7])
-nrow(slim_PM_dat)
 
-write.csv(slim_PM_dat, file = "data/slim_PM_clusterdat.csv", row.names = FALSE)
-
-slim_PM_dat[slim_PM_dat$spray_management == "Late_plus",]
 ```
+There are few 'Early_plus' and 'late' treatments, these treatments therefore will have too few comparisons with other treatments in the meta-analysis to be provide accurate results.
+Therefore we will remove 'Early_plus' and 'Late' from the analysis.
 
 ```{r simpler_clusters_REMOVE}
-
-slim_PM_dat <- slim_PM_dat %>%
-   mutate(
-    spray_management = case_when(
-       fungicide_timing_1 < 0 &
-          is.na(fungicide_application_2) &
-          is.na(fungicide_application_3) ~ "Early",
-       fungicide_timing_1 >= 0 &
-          fungicide_timing_1 < 4 &
-          is.na(fungicide_application_2) &
-          is.na(fungicide_application_3) ~ "Recommended",
-      fungicide_timing_1 >= 4 &
-          is.na(fungicide_application_2) &
-          is.na(fungicide_application_3) ~ "Late",
-      fungicide_timing_1 < 0 &
-          !is.na(fungicide_application_2) ~ "Early_plus",
-       fungicide_timing_1 >= 0 &
-          fungicide_timing_1 < 4 &
-          !is.na(fungicide_application_2) ~ "Recommended_plus",
-      fungicide_timing_1 >= 4 ~ "Late_plus",
-      TRUE ~ "Other"
-    )
-  )
-
-slim_PM_dat[slim_PM_dat$fungicide_ai == "control",
-            c("fungicide_timing_1", "fungicide_timing_2", "fungicide_timing_3",
-              "spray_management"
-              )] <- "control"
-
-table(slim_PM_dat$spray_management)
-
-# Remove "Early_plus" and "Late" due to lack of replicates
 
@@
 
-#slimmer_PM_dat <- slim_PM_dat[slim_PM_dat$spray_management != "Late",]
-
 write.csv(slimmer_PM_dat, file = "data/slimmer_PM_clusterdat.csv", row.names = FALSE)
@@
 
-```{r}
+Our data currently uses sample variance to define the yield error. We should expect that when yield increases so does the variance. Lets quickly plot this to check.
 
-slimmer_PM_dat$vi <- slimmer_PM_dat$Y_Msquare/(slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha^2)
+```{r Var_mean_sqaures}
+# redefine sample variance calculated from mean square
+slimmer_PM_dat$vi <- 
+   slimmer_PM_dat$Y_Msquare / 
+   (slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha ^ 2)
 
@@
    geom_point()
+```
 
+We see here that the sample variance generally decreases or has no association with the grain yield.
+This might be due to the unpredictable nature of mungbeans, however going forward we will use mean squares which defines between trial variation and is a the more generic error term.
+
+```{r Var_MeanSquarePlot}
 slimmer_PM_dat %>%
@@
 
-slimmer_PM_dat[slimmer_PM_dat$vi > 0.5,]
-
-boxplot(PM_MB_means$prop_YG, na.rm = TRUE)
-
-boxplot(PM_MB_means$yield_gain/PM_MB_means$grain_yield.t.ha., main = "Yield loss proportion")
-summary(PM_MB_means$yield_gain/PM_MB_means$grain_yield.t.ha., na.rm = TRUE)
-unique(PM_MB_means$trial_ref)
-
-boxplot(yield_gain/grain_yield.t.ha. ~ year,data = PM_MB_means, main = "Yield loss proportion")
-
-unique(PM_MB_means$fungicide_ai)
-
 ```

### 2020-01-03 05_MetaAnalysis.Rmd
Removed preliminary lmer models which are not used to inform the final model

@@
 
-#### Mixed effect model to estimate variance
-
-```{r na2Sampling_variance, message=FALSE}
-library(lme4)
-library(scales)
-
-# for(i in PM_MB_means$trial_ref){
-#
-# log(V)[i] = a + b * log(
-#    mean(subset(PM_MB_means$grain_yield.t.ha[i], fungicide_ai == "control"),
-#         subset(PM_MB_means$grain_yield.t.ha[i], fungicide_ai == "tebuconazole")))
-# # need to know what parameters a and b are here
-# # I am guessing they represent prediction parameters for each "study" for each of the treatments, "control" and tebuconazole"
-# }
-
-# method as described by Emerson
-PM_MB_train <- PM_MB_means %>%
-   filter(Y_error_type == "SamplingVariance")
-
-PM_MB_train$trial_ref <- as.factor(PM_MB_train$trial_ref)
-
-plot(PM_MB_train$yield_error,
-     log(PM_MB_train$grain_yield.t.ha))
-
-length(unique(PM_MB_train$trial_ref))
-
-# Run a linear model with grain_yield.t.ha as a fixed effect predictor and trial as a random intercept
-PM_MB_trainLMER <- lmer(yield_error ~ grain_yield.t.ha. +
-                           (1 | trial_ref), data = PM_MB_train)
-summary(PM_MB_trainLMER)
-
-# grain yield (in this model) IS a significant predictor for yield error
-# (t value = 5.826)
-# And the variance increases as the mean increases does log transformation
-# improve the model?
-
-PM_MB_trainLMER.1 <- lmer(log(yield_error) ~ `grain_yield.t.ha` +
-                             (1 | trial_ref), data = PM_MB_train)
-summary(PM_MB_trainLMER.1) # grain yield a significant predictor of log(yield error)
-anova(PM_MB_trainLMER, PM_MB_trainLMER.1) # no significant difference between the models
-
-PM_MB_trainLMER.2 <- lmer(yield_error ~ log(`grain_yield.t.ha`) +
-                             (1 | trial_ref), data = PM_MB_train)
-summary(PM_MB_trainLMER.2) # log(grain yeild) is a significant predictor of yield error
-anova(PM_MB_trainLMER, PM_MB_trainLMER.2) # no significant difference between the models
-
-PM_MB_trainLMER.3 <-
-   lmer(log(yield_error) ~ log(`grain_yield.t.ha`) +
-           (1 | trial_ref),
-        data = PM_MB_train)
-summary(PM_MB_trainLMER.3) # log(grain yeild) is a significant predictor of log(yielderror)
-anova(PM_MB_trainLMER, PM_MB_trainLMER.3) # no significant difference between the models
-
-# Lets try with Fungicide as a fixed effect
-PM_MB_trainLMER.4 <-
-   lmer(yield_error ~ `grain_yield.t.ha` + as.factor(fungicide_ai) +
-           (1 | trial_ref),
-        data = PM_MB_train)
-summary(PM_MB_trainLMER.4)
-anova(PM_MB_trainLMER, PM_MB_trainLMER.4) # no significant difference between the models
-
-#log transforming the response or predictor variables did not improve the model therefore I will leave it untransformed
-# I will be using the first model PM_MB_trainLMER for further analyses beyond this point
-
-# Extract the model coefficients
-paramA <-
-   (summary(PM_MB_trainLMER)$coef)[2, 1] # Extract the overall mean slope to predict Yield error
-InterC <-
-   (summary(PM_MB_trainLMER)$coef)[1, 1] # Extract the overall mean intercept to predict Yield error
-lmer.coef <-
-   coef(PM_MB_trainLMER) # extracting the mean random intercept for each of trial variables
-
-# for(i in NATrials$Trial_ref){
-# #Sv <- (log(PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped
-# 
-# Sv <- (PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.` * paramA) + InterC
-# 
-# PM_MB_means[PM_MB_means$Trial_ref == i,]$Yield_error <- Sv
-# PM_MB_means[PM_MB_means$Trial_ref == i,]$Y_error.type <- "SamplingVariance"
-# }
-
-# plot of the mixed effect model, Black line shows the mean lmer regression line
-ggplot(PM_MB_train) +
-   geom_point(aes(y = yield_error, x = grain_yield.t.ha, colour = trial_ref)) +
-   geom_abline(
-      intercept = c(InterC, lmer.coef$trial_ref[, 1]),
-      slope = c(paramA, lmer.coef$trial_ref[, 2]),
-      size = 1,
-      colour = c("Black", hue_pal()(length(unique(PM_MB_train$trial_ref))))
-   ) +
-   coord_cartesian(xlim = c(0, 3)) +
-   theme_usq()
-```
-
-```{r na2Sv_formula}
-# commented until a reliable model can be written
-
-# for (i in NATrials$trial_ref) {
-#    #Sv <- (log(PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped
-#    
-#    Sv <-
-#       (PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha` * paramA) + InterC
-#    
-#    PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <- Sv
-#    PM_MB_means[PM_MB_means$trial_ref == i,]$Y_error_type <-
-#       "SamplingVariance"
-# }
-
-```
-
-Let's look at the model without the trial mung1718/01, as it looks to be adding some skew.
-
-```{r lmer_remove_mung1718-01}
-# remove from mung1718/01 from training dataset
-PM_MB_train.2 <-
-   PM_MB_train[PM_MB_train$trial_ref != "mung1718/01",]
-
-# Rerun the model
-PM_MB_trainLMER.5 <- lmer(yield_error ~ `grain_yield.t.ha` +
-                             (1 | trial_ref), data = PM_MB_train.2)
-summary(PM_MB_trainLMER.5) # no significant effect of mean grain yield on yield error
-
-# Extract the cooeficients
-paramA <-
-   (summary(PM_MB_trainLMER.5)$coef)[2, 1] # Extract the overall mean Slope to predict Yield error
-InterC <-
-   (summary(PM_MB_trainLMER.5)$coef)[1, 1] # Extract the overall mean intercept to predict Yield error
-lmer.coef <-
-   coef(PM_MB_trainLMER.5) # extracting the mean random intercept for each of trial variables
-
-# plot the data with the predicted slopes overlayed
-
-ggplot(PM_MB_train.2) +
-   geom_point(aes(y = yield_error, x = grain_yield.t.ha, colour = trial_ref)) +
-   geom_abline(
-      intercept = c(InterC, lmer.coef$trial_ref[, 1]),
-      slope = c(paramA, lmer.coef$trial_ref[, 2]),
-      size = 1,
-      colour = c("Black", hue_pal()(length(unique(PM_MB_train.2$Trial_ref))))
-   ) +
-   coord_cartesian(ylim = c(0, 0.33)) +
-   xlab("Grain Yield (t/ha)") +
-   ylab("Yield Error") +
-   scale_colour_discrete("Trial Reference") +
-   theme_usq()
-
-```
-
-### Random effects model to predict trial variance
-Just for kicks lets look at the linear regression model as a random effects model where `grain_yield.t.ha` is set as a random slope to the random intercept `trial_ref`.
-
-The model fits better as shown by an ANOVA comparison. But how to impute from this model if mean variance for a trial is unknown...
-
-```{r random_slope_model} 
-# This code chunk broke with the addition of new data, I will re-inspect the data and remodel.
-
-# Run a linear model with yield error as a fixed effect predictor and trial as a random intercept
-PM_MB_trainLMERx <- lmer(yield_error ~ 1 +
-                            (grain_yield.t.ha |
-                                trial_ref), data = PM_MB_train)
-
-anova(PM_MB_trainLMER, PM_MB_trainLMERx) # random slope model NOT significantly better # P = 0.6677
-
-summary(PM_MB_trainLMERx)
-
-InterC <-
-   (summary(PM_MB_trainLMER)$coef)[1, 1] # Extract the overall mean intercept
-
-lmer.coefx <- coef(PM_MB_trainLMERx)
-
-# plot of the mixed effect model, Black line shows the mean lmer regression line
-ggplot(PM_MB_train) +
-   geom_point(aes(y = yield_error, x = grain_yield.t.ha, colour = trial_ref)) +
-   geom_abline(
-      intercept = lmer.coefx$trial_ref[, 2],
-      slope = lmer.coefx$trial_ref[, 1],
-      size = 1,
-      colour = hue_pal()(length(unique(PM_MB_train$Trial_ref)))
-   ) +
-   coord_cartesian(xlim = c(0, 3),
-                   ylim = c(0, 1)) +
-   xlab("Grain Yield (t/ha)") +
-   ylab("Yield Error") +
-   scale_colour_discrete("Trial Reference") +
-   theme_usq()
-```
-After much deliberation I don't think this is possible to use the model with grain yield t/ha as a random slope.
-Even though we know the grain yields and the mean of the grain yields, we still can't predict the effect of the random intercept trial on the yield error.
-
-I also re-ran the model without including the trial in which we used LSD to interpret the sampling variance and the model lost a lot of significance.
-
-### Between trial variation
-
-Emerson proposed I look at the between trial variation
-```{r between_trial_variation}
-unique(PM_MB_means$Y_error_type)
-
-PM_MB_means.SV <- PM_MB_means[PM_MB_means$Y_error_type == "SamplingVariance",]
-meta_mean.GY <- mean(PM_MB_means.SV$grain_yield.t.ha.,na.rm = TRUE)
-
-# find the mean and variance of each trial
-PM_MB_means_T <- PM_MB_means %>%
-   filter(Y_error_type == "SamplingVariance") %>%
-   group_by(trial_ref) %>%
-   summarise(trial_mean = mean(grain_yield.t.ha., na.rm = TRUE),
-             BW_trial_variance = sd(grain_yield.t.ha., na.rm = TRUE) ^ 2
-             ) # I am not sure I have calculated between trial variance or trial variance// Should I be using a denominator (N-1) or (N), sd by default uses (N-1)
-
-# by excluding the standard deviation of each treatment I have discarded much of the variance.
-Should I simulate a larger number of samples for each treatment to reflect the sample distribution of each treatment and then take the mean and standard deviation of the whole trial of the simulated data?
-
-# update the main data set with Trial variance
-SV_Trials <- unique(PM_MB_means_T$Trial_ref)
-PM_MB_means$TrialVariance <- NA
-
-for(i in SV_Trials){
-   PM_MB_means[PM_MB_means$Trial_ref == i, "TrialVariance"] <- PM_MB_means_T[PM_MB_means_T$Trial_ref == i,"BW_trial_variance"]
-}
-PM_MB_means$TrialVariance
-# OR ?
-PM_MB_means <- left_join(PM_MB_means, PM_MB_means_T, by = "trial_ref")
-
-SV_mod1 <- lm(Trial_variance ~ trial_mean, data = PM_MB_means_T)
-summary(SV_mod1)
-
-plot(Trial_variance ~ trial_mean, data = PM_MB_means_T)
-abline(SV_mod1)
-
-```
-
 ## Preliminary meta-analysis
 
-```{r}
-slim_PM_dat <- read.csv("data/slim_PM_clusterdat.csv")
-
-m1 <- lmer(grain_yield.t.ha*1000 ~ factor(total_fungicide) + (factor(total_fungicide) | trial_ref), data = slim_PM_dat)
-
-m2 <- lmer(grain_yield.t.ha*1000 ~ factor(total_fungicide) + (1 | trial_ref), data = slim_PM_dat)
-
-anova(m1,m2)
-
-m3 <- lmer(log(grain_yield.t.ha*1000) ~ factor(total_fungicide) + (factor(total_fungicide) | trial_ref), data = slim_PM_dat)
-
-anova(m1, m3)
-summary(m3)
-
-```
-
-```{r}
+```{r slim_lmer}
 slim_PM_dat <- read.csv("data/slim_PM_clusterdat.csv")
@@
 
-m5.0 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + (1 | trial_ref), data = slim_PM_dat) # Model failed to converge
+m5.0 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + (1 | trial_ref), data = slim_PM_dat)
 
 anova(m4,m5) # m5 has a much lower AIC and significantly better model
+anova(m5,m5.0) # no difference
+```
 
-anova(m5,m5.0)
-
-summary(m5.0)
-
-```
+Model 5 (m5) is a significantly better fit than model 4 (m4).
+Model 5.0 (m5.0), a simpler model with less variables, was not significantly different from m5.
+This analyis suggests that model 5.0 is the best fit.
+`r summary(m5.0)`
 

### 2020-01-16 05_MetaAnalysis.Rmd
Remove lmer analysis of "slim" data

@@
 # devtools::install_github("https://github.com/PaulMelloy/bomrang")
-# devtools::install_github("https://github.com/adamhsparks/theme.usq")
+devtools::install_github("https://github.com/adamhsparks/theme.usq", dependencies = TRUE)
 # install.packages("lme4")
@@
 library(kableExtra)
-
 ```
@@
 
-Now for the trickier part creating 'Sampling Variance' for treatments where only mean yield is recorded.  
+Now for the tricy part creating 'Sampling Variance' for treatments where only mean yield is recorded.  
 The trial which does not report any type of variance also reports that there is no significant difference between the means.
 
-```{r}
+```{r NAtrials}
 NATrials <- PM_MB_means %>%
@@
 
-A single trial `mung1516/03` within the current scope of the meta-analysis fails to report a variance statistic.
+Two trials `mung1516/03` and `mung1112/01` within the scope of the meta-analysis fail to report variance statistics.
 According to [Machado F.
@@
 al (2017)](http://apsjournals.apsnet.org/doi/10.1094/PDIS-03-17-0340-RE) [Paul et al.
-(2007)](https://apsjournals.apsnet.org/doi/pdfplus/10.1094/PHYTO-97-2-0211) uses linear regression model to estimate sampling variance.
+(2007)](https://apsjournals.apsnet.org/doi/pdfplus/10.1094/PHYTO-97-2-0211) we can use a linear regression model to estimate sampling variance.
 
 ## Preliminary meta-analysis
-
-```{r slim_lmer}
-slim_PM_dat <- read.csv("data/slim_PM_clusterdat.csv")
-
-m4 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) + (factor(spray_management) | trial_ref), data = slim_PM_dat)
-
-m5 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + (factor(spray_management) | trial_ref), data = slim_PM_dat)
-
-m5.0 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + (1 | trial_ref), data = slim_PM_dat)
-
-anova(m4,m5) # m5 has a much lower AIC and significantly better model
-anova(m5,m5.0) # no difference
-```
-
-Model 5 (m5) is a significantly better fit than model 4 (m4).
-Model 5.0 (m5.0), a simpler model with less variables, was not significantly different from m5.
-This analyis suggests that model 5.0 is the best fit.
-`r summary(m5.0)`
-
-```{r LME_cluster_disease_mod}
-m6 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) * PM_final_severity +
-              (factor(spray_management) | trial_ref), 
-           data = slim_PM_dat)
-
-m7 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) * PM_final_severity + 
-              (factor(spray_management) | trial_ref), 
-           data = slim_PM_dat)
-
-anova(m5,m6) # 65 has a lower AIC but not evaluated as a significantly better model
-
-summary(m6)
-
-```
 
@@
 slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
-unique(slimmer_PM_dat$trial_ref, slimmer_PM_dat$location, slimmer_PM_dat$year)
 
@@
 
-m10 <- lmer(log(grain_yield.t.ha*1000) ~ (factor(spray_management) | trial_ref), 
+m10 <- lmer(log(grain_yield.t.ha*1000) ~ 
+               (factor(spray_management) | trial_ref), 
+           data = slimmer_PM_dat)
+
+m11 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + 
+              (1 | trial_ref), 
            data = slimmer_PM_dat)
@@
 anova(m9,m10) # m9 is significantly better model
+anova(m9,m11) # m11 is a simpler model which is no different to m9
 

### 2020-01-16 05_MetaAnalysis.Rmd
More explaination to lmer

@@
 # devtools::install_github("https://github.com/PaulMelloy/bomrang")
-devtools::install_github("https://github.com/adamhsparks/theme.usq", dependencies = TRUE)
+# devtools::install_github("https://github.com/adamhsparks/theme.usq", dependencies = TRUE)
 # install.packages("lme4")
@@
 
+This linear mixed effect model shows indicates:  
+   - A single early spray before first sign of powdery mildew is not likely to increase yields.  
+   - A single or single spray with one or more follow sprays starting  at the `recommended` first spray , within 3 days of powdery mildew first sign are likely to produce significantly higher grain yields compared to the no spray control.
+   - The `recommended_plus` spray which has one or more follow-up sprays after first sign are likley to increase the mean grain yield.  
+   - `Late_plus` spray treatments showed the highest mean grain yield, and was significantly higher than the no spray control. However showed no difference to either of the `recommended` treatments.
+
+### Imputing sample variances
+
 We need to impute the variances which are missing for a few of the trials.
-These trials `r paste(unique(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),c("location","year", "trial_ref")])` were analysed and reported that there was no significant difference between the treatments in each trial.
+These trials `r unique(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),c("location","year", "trial_ref")])` were analysed and reported that there was no significant difference between the treatments in each trial.
 So therefore we need the imputed variances not to show a significant difference.
@@
 A log transformation, however, shows a normal disrtubution.
-We can use the mean and standard deviation of the log(V) to sample variances for the treatments where V is mission.
+We can use the mean and standard deviation of the log(V) to sample variances for the treatments where V is missing.
+
+```{r variance_histograms}
+hist(slimmer_PM_dat$yield_error) # yield error is not normally distributed
+hist(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is normally distributed 
+```
 
@@
 If any errors don't overlap, infering signicifant difference, the imputed variances are discarded and resampled until all treatment variances show no significant differences.
-### Imputing sample variances
+
 ```{r imputing_variances}
-
-hist(slimmer_PM_dat$yield_error) # yield error is not normally distributed
-hist(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is normally distributed
 
@@
 
-   message(paste("\nWarning!!: Imputed yield errors show significant differences when they should not, rerun chunk", "i =",i))
+   message(paste("\nWarning!!: Imputed yield errors show significant differences when they should not, imputation will automatically rerun - iteration", "i =",i))
    next()
@@
          geom_pointrange(ymin = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] -
-                            (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+                            (1.95*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
                          ymax = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] +
-                            (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+                            (1.95*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
                          position = "jitter"
@@
 ## Meta-analysis
-```{r meta_1}
+Let's load the metafor package we are using to analyse the data, then rearrange the factors we want to examine by placing the control treatment first.
+This way all treatments will be compared to the no spray controls.
+Next we are log transforming the grain yield and calculating the variance from the trial mean squares.  
+Finally we will assign factor classes to the main variables in the meta-analysis.  
+```{r meta_organisation}
 library(metafor)
 slimmer_PM_dat$spray_management <-
-   factor(slimmer_PM_dat$spray_management,levels(slimmer_PM_dat$spray_management)[c(2,3,1,4,5)])
+   factor(slimmer_PM_dat$spray_management,c("control", "Early", "Recommended", "Recommended_plus","Late_plus"))
 
@@
 slimmer_PM_dat$trial <- factor(slimmer_PM_dat$trial)
+```
+
+```{r Meta-analysis}
 

### 2020-01-17 05_MetaAnalysis.Rmd
Removed old method for imputing NA variance. Also some corrections to code and chunks

@@
 # Meta-analysis
-
-```{r data_import, message=FALSE, echo=FALSE}
-source("R/import_data.R")
-PM_MB_means <- import_data()
-
-# see Yield vs in-season rain section on the influence of rain and irrigation on grain yield
-PM_MB_means$irrigation <- NA
-PM_MB_means[PM_MB_means$location == "Hermitage", "irrigation"] <- TRUE
-PM_MB_means[PM_MB_means$location != "Hermitage", "irrigation"] <- FALSE
-
-```
-
-## Estimating variance for trials without reported error
-
-Now for the tricy part creating 'Sampling Variance' for treatments where only mean yield is recorded.  
-The trial which does not report any type of variance also reports that there is no significant difference between the means.
-
-```{r NAtrials}
-NATrials <- PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole",
-          row_spacing == 0.75,
-          is.na(Y_error_type)) %>%
-   select(trial_ref) %>%
-   distinct()
-```
-
-Two trials `mung1516/03` and `mung1112/01` within the scope of the meta-analysis fail to report variance statistics.
-According to [Machado F.
-et.
-al (2017)](http://apsjournals.apsnet.org/doi/10.1094/PDIS-03-17-0340-RE) [Paul et al.
-(2007)](https://apsjournals.apsnet.org/doi/pdfplus/10.1094/PHYTO-97-2-0211) we can use a linear regression model to estimate sampling variance.
-
 ## Preliminary meta-analysis
@@
 We need to impute the variances which are missing for a few of the trials.
-These trials `r unique(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),c("location","year", "trial_ref")])` were analysed and reported that there was no significant difference between the treatments in each trial.
+These trials `r unique(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),c("location","year", "trial_ref")])$trial_ref` were analysed and reported that there was no significant difference between the treatments in each trial.
 So therefore we need the imputed variances not to show a significant difference.
@@
 
+The imputed variances calculated above don't show the expected positive correlation between grain yield and variance.
+This is unexpected and reflects the inherent variability of the data.
+Therefore we will calculate the trial mean squares and use this to calculate the variance for each sample.
+
 #### Imputing sample variances from Mean squares
-```{r imputing_MSE}
+```{r imputing_MSE_dataSpread}
 slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
@@
 
+```
+
+Imputing using a log transformation of the data is required. Which trials need variance imputation?
+
+```{r imputing_MSE}
 TrialMSQ <- slimmer_PM_dat %>%
@@
 TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), "trial_ref"]
+```
+
+```{r imputation_MSE}
 
@@
 
-Before plotting lets have a look at how the trimmed down, modified data looks.
+Before analysis lets have a look at the trimmed down modified data.
 
@@
 slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management, levels(slimmer_PM_dat$spray_management)[rev(c(1,2,4,5,3))])
+
+slimmer_PM_dat %>%
+   ggplot(aes(y = grain_yield.t.ha, x = spray_management))+
+   geom_boxplot()+
+   #geom_point(position = "jitter", alpha = 1/5)+
+   geom_jitter(width = 0.1, alpha = 1/5)+
+   theme_usq()+
+   labs(x = "Spray management variable", 
+        y = "Grain yield (t/Ha)",
+        title = "Mean grain yield from each treatment \n categorised by spray management scenario")+
+   theme(plot.title = element_text(hjust = 0.5))+
+   geom_hline(yintercept = 0, linetype = 2)+
+   coord_flip()
+```
+
+There seems like no difference between the treatments, with exception to Late_plus.
+Lets do this plo again, but use the proportion of yield increase compared to the no spray control as the response variable.
+
+It is also important to visualise how well the data is compared across the trial years and trials.
+
+```{r table_of_nTreatments}
+kableExtra::kable(table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year), align=rep('c', 8))%>%  #commented as was redering empty, needs a look in
+   kable_styling("striped", fixed_thead = TRUE, full_width = FALSE, position = "center")
+
+```
+Treatments Late_plus and early don't have very good comparison to other treatments.
+
+```{r plot_yieldProportion}
+slimmer_PM_dat$spray_management <-
+   factor(slimmer_PM_dat$spray_management,rev(c("control", "Early", "Recommended", "Recommended_plus","Late_plus")))
 
@@
    theme(plot.title = element_text(hjust = 0.5))+
+   geom_hline(yintercept = 0, linetype = 2)+
    coord_flip()
-
-kableExtra::kable(table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year), align=rep('c', 8))%>%  #commented as was redering empty, needs a look in
-   kable_styling("striped", fixed_thead = TRUE, full_width = FALSE, position = "center")
-
 ```
@@
 Next we are log transforming the grain yield and calculating the variance from the trial mean squares.  
-Finally we will assign factor classes to the main variables in the meta-analysis.  
+Finally we will assign factor classes to the main variables in the meta-analysis. Note that variable trial is a combination of:  
+   - Trial identifier  
+   - Trial year  
+   - Trial location  
+   - Host genotype  
+   - Trial row spacing
+
 ```{r meta_organisation}
@@
 
+When we compare these results to those of the linear mixed effect model we notice the metafor model is less certain about the `recommended` and `recommended_plus` treatments.
+Subsequently there is no signiciant difference between the `recommended` and `recommended_plus` treatments and the no spray control.
+
 ```{r compare_meta&lmer}
@@
 
+To make it easier to compare each of the treatments we can compute the contrasts.
 ```{r meta_contrasts}
-anova(PM_mv_AI, L=rbind(c(0,1,-1,0,0),  # early vs late plus
-                        c(0,1,0,-1,0),  # early vs recommended
-                        c(0,1,0,0,-1),  # early vs recommended plus
-                        c(0,0,-1,1,0),  # late plus vs recommended 
-                        c(0,0,-1,0,1),  # late plus vs recommended  Plus
-                        c(0,0,0,-1,1))) # recommended vs recommended plus
+anova(PM_mv_AI, L=rbind(c(0,1,-1,0,0),  # early vs Recomended
+                        c(0,1,0,-1,0),  # early vs recommended plus
+                        c(0,1,0,0,-1),  # early vs Late plus
+                        c(0,0,-1,1,0),  # Recommended vs recommended_plus
+                        c(0,0,-1,0,1),  # Recommended vs Late_Plus
+                        c(0,0,0,-1,1))) # recommended_plus vs Late_plus
 ```
-Results show that Early applications are not significantly different to the no spray control or the one and two spray management options at the recommended time. Lets view this on a plot.
+Results show that early applications are not significantly different to the no spray control or the one and two spray management options at the recommended time. Lets view this on a plot.
 
@@
 
-results_AI <- data.frame(cbind(PM_mv_AI$b, 
-                              (PM_mv_AI$ci.lb),
-                              PM_mv_AI$ci.ub))
+# results_AI <- data.frame(cbind(PM_mv_AI$b, 
+#                               (PM_mv_AI$ci.lb),
+#                               PM_mv_AI$ci.ub))
 
@@
 ```{r meta_plot}
+efficacy$Treatment <-
+   factor(efficacy$Treatment,c("control", "Early", "Recommended", "Recommended_plus","Late_plus"))
+
 efficacy %>% 
    ggplot(aes(Treatment, Mean))+
+   geom_hline(yintercept = c(0.8,1,1.2,1.4), color = "grey80", linetype = 3)+
    geom_point(aes(size=1/SE), shape=15)+
@@
    coord_flip()+
-  theme_grey()+
-   geom_hline(yintercept = efficacy[efficacy$Treatment == "control",]$CIinf)
+   theme_usq()
 
@@
 
-Check the yeild
-
-```{r}
-boxplot(slimmer_PM_dat$grain_yield.t.ha ~ slimmer_PM_dat$spray_management)
-
-```
+What is interesting here is that the variance in the control has increased while the treatments have decreased.
+This is despite the control being the best represented accross all experiments.
+However it could also be because it also has a low number of pooled reps per trial.

### 2020-01-19 index.Rmd
Yaml header

@@
 author: "Paul Melloy, Emerson Del Ponte, Charles T. Gray and Adam H. Sparks"
-date: "`r Sys.Date()`"
-output:
-  bookdown::html_book:
-    theme: united
+date: "`r format(Sys.time(), '%d %B, %Y')`"
+site: bookdown::bookdown_site
+output: bookdown::gitbook
+documentclass: book
+bibliography: 
+biblio-style: apalike
+link-citations: yes
+github-repo: PaulMelloy/Powdery_mildew_Mungbean
+description: "A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew."
 ---

### 2020-01-19 03_Preliminary_analysis.Rmd
conflicting labels

@@
 
-```{r Fungicide_x_nSprays_tble, message=FALSE}
+```{r Fungicide_x_nSprays_tble2, message=FALSE}
 PM_MB_means %>%
@@
 
-```{r Fungicide_x_nSprays_tble, message=FALSE}
+```{r Fungicide_x_nSprays_tble1, message=FALSE}
 

### 2020-01-19 05_MetaAnalysis.Rmd
Remove yaml header

@@
----
-title: "Meta-analysis"
-author: "P. Melloy"
-date: "`r Sys.Date()`"
-output: html_document
----
-
-```{r MEsummary_Libraries, message=FALSE}
+```{r MEsummary_Libraries1, message=FALSE}
 # install.packages("tidyverse")
@@
 There seems like no difference between the treatments, with exception to Late_plus.
-Lets do this plo again, but use the proportion of yield increase compared to the no spray control as the response variable.
+Lets do this plot again, but use the proportion of yield increase compared to the no spray control as the response variable.
 

### 2020-01-21 05_MetaAnalysis.Rmd
Chunk names and adding a separation between meta-analysis from different packages

@@
 ```{r LME_slimmer_cluster_disease_mod}
-library(lme4)
+
 slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
@@
 ## Meta-analysis  
+### metafor package  
 Let's load the metafor package we are using to analyse the data, then rearrange the factors we want to examine by placing the control treatment first.
@@
 
-```{r meta_organisation}
+```{r metafor_organisation}
 library(metafor)
@@
 
-```{r Meta-analysis}
+```{r Metafor-analysis}
 
@@
 To make it easier to compare each of the treatments we can compute the contrasts.
-```{r meta_contrasts}
+```{r metafor_contrasts}
 anova(PM_mv_AI, L=rbind(c(0,1,-1,0,0),  # early vs Recomended
@@
 
-```{r meta_results}
+```{r metafor_results}
 results_AI <- data.frame(cbind(exp(PM_mv_AI$b), 
@@
 efficacy$se <- PM_mv_AI$se
-colnames(efficacy) <- c("Mean", "CIsup", "CIinf", "Treatment", "SE")
+colnames(efficacy) <- c("Mean", "CIs_lower", "CI_upper", "Treatment", "SE")
 efficacy
@@
 
-```{r meta_plot}
+```{r metafor_plot}
 efficacy$Treatment <-
@@
 However it could also be because it also has a low number of pooled reps per trial.
+Lets look at how well each of the treatments compare to each other.
+We can use the netmeta package to give a graphical representation of this.
+
+### netmeta package  
+Lets analyse the data again using a different statistical approach to see if our outcome with the `metafor` package was robust.
+The netmeta package uses a frequentist approach to the analysis, and focuses on the pairwise comparisons between treatments.
+
+```{r netmeta-analysis}
+library(netmeta)
+
+datPM3 <- slimmer_PM_dat %>% 
+   group_by(trial, spray_management, n) %>% 
+      summarize(yi_mean = mean(yi), 
+             vi_mean = mean(vi)) %>% 
+   ungroup()
+
+PM_con <- pairwise(treat = spray_management,
+                  n = n,
+                  mean = yi_mean,
+                  sd = sqrt(vi_mean),
+                  studlab= trial,
+                  data = datPM3, 
+                  sm="MD")
+
+net_con <- netmeta(TE, 
+                seTE, 
+                treat1, 
+                treat2, 
+                studlab, 
+                data=PM_con, 
+                sm="MD")
+
+summary(net_con)
+
+```
+Now lets visualise this as a forest plot
+
+```{r netmeta-forest}
+forest(net_con, reference.group = 4,
+       rightcols=c("effect", "ci", "Pscore"),
+       rightlabs="P-Score", small.values = "bad")
+
+```

### 2020-01-21 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Updating data wrangling code for AUDPC. need to continue at Hermitage 2017

--- 2019-11-20 191115_PMMB_DataWrangling_PM.Rmd
@@
 
-source("R/import_data.R")
+source("C:/Users/U8011054/OneDrive - USQ/Cloudstor/R/Mungbean_projects/Mungbean_PM/R/import_data.R")
 PM_MB_means <- import_data()
@@
               grain_yield.t.ha. = Herm_10$`Kg/ha`,
-              AUDPC = apply(Herm_10[,c("P.M.9wap","P.M.11wap","P.M.13wap")]-1,1, FUN = audpc, dates = c(9*7,11*7,13*7)), # -1 to the data because zero disease = 1 on rating scale
+              #AUDPC = apply(Herm_10[,c("P.M.9wap","P.M.11wap","P.M.13wap")]-1,1, FUN = audpc, dates = c(9*7,11*7,13*7)), # -1 to the data because zero disease = 1 on rating scale
               stringsAsFactors = FALSE
+              )
+
+Herm_10_dat <- cbind(Herm_10_dat,
+                          AUDPC = apply(data.frame(zero = 1,
+                                                   Herm_10[,c("P.M.9wap","P.M.11wap","P.M.13wap")]-1),
+                                        1, 
+                                        FUN = audpc, 
+                                        dates = c((Herm_10_dat$first_sign_disease[1]-7)-
+                                                     Herm_10_dat$planting_date[1],
+                                                  9*7,11*7,13*7)
+                                        )
                           )
@@
               PM_final_severity = Herm_11$`P.M. 11  w.a.p.`,
+              AUDPC = apply(data.frame(zero = rep(1,42),
+                                       wap11 = Herm_11[,c("P.M. 11  w.a.p.")]-1),1, 
+                            FUN = audpc, dates = c((as.Date("2011-03-28", format = "%Y-%m-%d")-7)- # First sign of disease minus planting date. Gives when there is no disease
+                                                      as.Date("2011-01-24", format = "%Y-%m-%d"),
+                               77)), # -1 to the data because zero disease = 1 on rating scale
               rating_scale = "1-9",
@@
               Y_error_type = "stdev",
+             AUDPC.m = mean(AUDPC),
+             AUDPC.sd = sd(AUDPC),
               meanSq = anova(lm(grain_yield.t.ha./1000 ~ factor(n_treatment) + host_genotype, 
@@
               rating_scale = "1-9",
-              grain_yield.t.ha. = as.numeric(King_11$`Yld kg ha`),
-              AUDPC = apply(King_11[,c("9 w.a.p.", "11 w.a.p.", "12 w.a.p.", "14 w.a.p.")]-1,1, FUN = audpc, dates = c(9*7,11*7,12*7, 14*7))# -1 to the data because zero disease = 1 on rating scale
+              grain_yield.t.ha. = as.numeric(King_11$`Yld kg ha`)
+              #AUDPC = apply(King_11[,c("9 w.a.p.", "11 w.a.p.", "12 w.a.p.", "14 w.a.p.")]-1,1, FUN = audpc, dates = c(9*7,11*7,12*7, 14*7))# -1 to the data because zero disease = 1 on rating scale
+              )
+
+King_11_dat <- cbind(King_11_dat,
+                          AUDPC = apply(data.frame(zero = 1,
+                                                   King_11[,c("9 w.a.p.", "11 w.a.p.", 
+                                                              "12 w.a.p.", "14 w.a.p.")])-1,
+                                        1, 
+                                        FUN = audpc, 
+                                        dates = c((King_11_dat$first_sign_disease[1]-7)-
+                                                     King_11_dat$planting_date[1],
+                                           9*7,11*7,12*7, 14*7))
                      )
@@
               rating_scale = "1-9",
-              grain_yield.t.ha. = as.numeric(Goolhi_13$`Yield Kg/ha`)/1000,
-              AUDPC = apply(Goolhi_13[,c("Inc_16D","Inc_33D")]-1,1, FUN = audpc, dates = c(16,33))# -1 to the data because zero disease = 1 on rating scale
+              grain_yield.t.ha. = as.numeric(Goolhi_13$`Yield Kg/ha`)/1000
+              #AUDPC = apply(Goolhi_13[,c("Inc_16D","Inc_33D")]-1,1, FUN = audpc, dates = c(16,33))# -1 to the data because zero disease = 1 on rating scale
+              )
+
+Goolhi_13_dat <- cbind(Goolhi_13_dat,
+                          AUDPC = apply(data.frame(zero = 1,
+                                                   Goolhi_13[,c("Inc_16D","Inc_33D")]-1),
+                                        1, 
+                                        FUN = audpc, 
+                                        dates = c((Goolhi_13_dat$first_sign_disease[1]-7)-
+                                                     Goolhi_13_dat$planting_date[1],
+                                                  16,33)
+                                        )
                           )
@@
               rating_scale = "1-9",
-              grain_yield.t.ha. = as.numeric(MarysM_13$`Yield Kg/ha`)/1000,
-              AUDPC = apply(MarysM_13[,c("Inc_18D","Inc_19D")]-1,1, FUN = audpc, dates = c(12,12+19)) # -1 to the data because zero disease = 1 on rating scale
+              grain_yield.t.ha. = as.numeric(MarysM_13$`Yield Kg/ha`)/1000
+              #AUDPC = apply(MarysM_13[,c("Inc_18D","Inc_19D")]-1,1, FUN = audpc, dates = c(12,12+19)) # -1 to the data because zero disease = 1 on rating scale
+              )
+
+MarysM_13_dat <- cbind(MarysM_13_dat,
+                          AUDPC = apply(data.frame(zero = 1,
+                                                   MarysM_13[,c("Inc_18D","Inc_19D")]-1),
+                                        1, 
+                                        FUN = audpc, 
+                                        dates = c((MarysM_13_dat$first_sign_disease[1]-7)-
+                                                     MarysM_13_dat$planting_date[1],
+                                                  12,12+19)
+                                        )
                           )
@@
 
+Premer_13_dat <- cbind(Premer_13_dat,
+                          AUDPC = apply(data.frame(zero = 1,
+                                                   Premer_13[,c("Inc_31D")]-1),
+                                        1, 
+                                        FUN = audpc, 
+                                        dates = c((Premer_13_dat$first_sign_disease[1]-7)-
+                                                     Premer_13_dat$planting_date[1],
+                                                  12+19)
+                                        )
+                          )
+
 ```
@@
               Y_error_type = "stdev",
-             #AUDPC.m = mean(AUDPC),
-             #AUDPC.sd = sd(AUDPC),
+             AUDPC.m = mean(AUDPC),
+             AUDPC.sd = sd(AUDPC),
               meanSq = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
@@
 #### Convert disease scores
-```{r Premer_13_convert_scores}
+```{r Millm_13_convert_scores}
 
@@
 Millm.13Y$Treat <- as.double(Millm.13Y$Treat)
-colnames(Millm.13Y)[1:4] <- c("Run", "Plot","Treat", "Rep")
-
-Millm_13 <- left_join(Millm_13D,Millm.13Y)
+colnames(Millm.13Y)[1:4] <- c("Run", "Plot","TreatY", "Rep")
+
+Millm_13 <- left_join(Millm_13D, Millm.13Y, by = c("Run", "Plot","Treat", "Rep"))
 
@@
               rating_scale = "1-9",
-              grain_yield.t.ha. = as.numeric(Millm_13$`kg/Ha`)/1000,
-              AUDPC = apply(Millm_13[,c("Inc_23D","Inc_42D")]-1,1, FUN = audpc, dates = c(23,42)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
-              )
-
+              grain_yield.t.ha. = as.numeric(Millm_13$`kg/Ha`)/1000
+              #AUDPC = apply(Millm_13[,c("Inc_23D","Inc_42D")]-1,1, FUN = audpc, dates = c(23,42)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
+              )
+
+Millm_13_dat <- cbind(Millm_13_dat,
+                          AUDPC = apply(data.frame(zero = 1,
+                                                   Millm_13[,c("Inc_23D","Inc_42D")]-1),
+                                        1, 
+                                        FUN = audpc, 
+                                        dates = c((Millm_13_dat$first_sign_disease[1]-7)-
+                                                     Millm_13_dat$planting_date[1],
+                                                  23,42)
+                                        )
+                          )
 ```
@@
 #### Input trial data
-```{r Herm15_Trialdat}
+```{r Herm16_Trialdat}
 
@@
 
-Herm_16_m
-
 Herm_16_m <- left_join(Herm_16_m,Herm_16.DR)
@@
    data.frame(trial_ref = "mung1617/02",
-              year = "2016",
+              year = "2017",
               location = "Missen Flats",
@@
 
+```
+
+#### Define treatment data
+```{r Herm_17_treatmentDefine}
+Herm_17_dat <- Herm_17 %>%
+   mutate(trade_name = 
+             case_when(Chemical.Trt == 1 ~ "Folicur",
+                       Chemical.Trt == 2 ~ "Throttle",
+                       Chemical.Trt == 3 ~ "Custodia",
+                       TRUE ~ "other"))%>%
+   mutate(fungicide_ai = 
+             case_when(Chemical.Trt == 1 ~ "tebuconazole",
+                       Chemical.Trt == 2 ~ "propiconazole",
+                       Chemical.Trt == 3 ~ "200 g/L tebuconazole + 120 g/L azoxystrobin",
+                       TRUE ~ "other"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Chemical.Trt == 1 ~ 62,
+                       Chemical.Trt == 2 ~ 125,
+                       Chemical.Trt == 3 ~ 60,
+                       TRUE ~ 9999))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Manage.Trt == "1" ~ as.Date(NA),
+                       Manage.Trt == "T2" ~ as.Date("2017-03-13", format = "%Y-%m-%d"),
+                       Manage.Trt == "T3" ~ as.Date("2017-03-24", format = "%Y-%m-%d"),
+                       Manage.Trt == "T4" ~ as.Date("2017-03-27", format = "%Y-%m-%d"),
+                       Manage.Trt == "T5" ~ as.Date("2017-03-27", format = "%Y-%m-%d"),
+                       Manage.Trt == "T6" ~ as.Date("2017-04-05", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Manage.Trt == "T3" ~ as.Date("2017-04-07", format = "%Y-%m-%d"),
+                       Manage.Trt == "T5" ~ as.Date("2017-04-11", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Manage.Trt == "1" ~ 0,
+                       Manage.Trt == "T3" ~ 2,
+                       Manage.Trt == "T5" ~ 2,
+                       TRUE ~ 1))
+
+```
+
+#### Input trial data
+```{r Herm17_Trialdat}
+# Remove zeros
+#Herm_17_dat[Herm_17_dat$`2017-03-07` == 0 ,c("2017-03-07")] <- 1
+
+Herm_17_dat <- 
+   data.frame(trial_ref = "mung1617/01",
+              year = "2017",
+              location = "Hermitage",
+              host_genotype = "Jade",
+              trial_design = "RCB",
+              plot_length = Herm_17_dat$Plot.Length,
+              plot_width = 2,
+              plant_density = NA,
+              row_spacing = Herm_17_dat$`Row.Spacing.(m)`,
+              replicate = Herm_17_dat$Rep,
+              planting_date = as.Date("2017-01-27", format = "%Y-%m-%d"),
+              emergence_date = as.Date("2017-02-01", format = "%Y-%m-%d"),
+              flowering_date = as.Date(NA),
+              pod_fill_date = as.Date(NA),
+              mid_late_pod_fill = as.Date(NA),
+              first_sign_disease = as.Date("2017-03-13", format = "%Y-%m-%d"),
+              trade_name = as.factor(Herm_17_dat$trade_name),
+              fungicide_ai = Herm_17_dat$fungicide_ai,
+              dose_ai.ha = Herm_17_dat$dose_ai.ha,
+              n_treatment = as.numeric(unlist(strsplit(Herm_17_dat$Manage.Trt, "T"))[unlist(strsplit(Herm_17_dat$Manage.Trt, "T")) != ""]),
+              fungicide_application_1 = Herm_17_dat$fungicide_application_1,
+              fungicide_application_2 = Herm_17_dat$fungicide_application_2,
+              total_fungicide = Herm_17_dat$spray_n,
+              harvest_date = as.Date("2017-06-26", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2017-05-11", format = "%Y-%m-%d"),
+              PM_final_severity = Herm_17_dat$`I_11/05/2017`,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(Herm_17_dat$`Yield.T/Ha`)
+               # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
+              )
+
+Herm_17_dat <- cbind(Herm_17_dat,
+                          AUDPC = apply(data.frame(zero = 1,
+                                                   Herm_17[,c("2017-03-24","I_2/04/2017", "I_11/04/2017", "I_18/04/2017", "I_24/04/2017","I_3/05/2017","I_11/05/2017")]-1),
+                                        1, 
+                                        FUN = audpc, 
+                                        dates = c((Herm_17_dat$first_sign_disease[1]-7)-
+                                                     Herm_17_dat$planting_date[1],
+                                                  39,48,57,64,70,79,87)
+                                        )
+                          )
+
+```
+
+# Pick up from here
+
+```{r}
 # Columns to keep
@@
                            '100.grain.wt.Grams')]
-
-Fogerty_17$Treatment.No <- as.numeric(unlist(strsplit(
-   Fogerty_17$Treatment.No, "T"))[
-      seq(from = 2, to = 324, by = 2)])
 
@@
 
+#### Calculating treatment means
+```{r Missen17_means}
+
+Fogerty_17_m <- Fogerty_17_dat %>%
+   group_by(host_genotype, n_treatment, row_spacing, fungicide_ai) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             location = unique(location),
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             dose_ai.ha = unique(dose_ai.ha),
+             trial_ref = unique(trial_ref),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
+             plot_width.m. = mean(plot_width, na.rm = TRUE),
+             plant_density = mean(plant_density, na.rm = TRUE),
+             replicates = length(as.numeric(replicate)),
+             planting_date = unique(planting_date),
+             emergence_date = unique(emergence_date),
+             flowering_date = unique(flowering_date),
+             pod_fill_date = unique(pod_fill_date),
+             mid_late_pod_fill = unique(mid_late_pod_fill),
+             first_sign_disease = unique(first_sign_disease),
+             fungicide_application_1 = unique(fungicide_application_1),
+             fungicide_application_2 = unique(fungicide_application_2),
+             total_fungicide = unique(total_fungicide),
+             harvest_date = unique(harvest_date),
+             final_assessment = unique(final_assessment),
+             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+             rating_scale = unique(rating_scale),
+             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+             D_error_type = "stdev",
+             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+             raw_graded = NA,
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+             Y_error_type = "stdev",
+             AUDPC.m = mean(AUDPC),
+             AUDPC.sd = sd(AUDPC),
+             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment) + fungicide_ai + row_spacing, data = subset(Fogerty_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
+   )
+
+# For some weird reason standard deviations are comming back NA in the code above
+Fogerty_17_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
+   Fogerty_17_dat %>%
+   group_by(n_treatment, row_spacing, fungicide_ai) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("disease_error","yield_error"))
+
+write.csv(
+   Fogerty_17_m,
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2017/MissenFlats/Fogerty_17_mean.csv",
+   row.names = FALSE
+)
+
+```
+
 ### Wellcamp 2018

### 2020-01-21 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
More AUDPC

@@
 
-# Pick up from here
-
-```{r}
-# Columns to keep
-Fogerty_17 <- Fogerty_17[, c('Plot', 'Rep', 'Row', 'Column', 'Chem.Trt',
-                           'Chemical', 'Row.Spacing.(m)', 'Treatment.No',
-                           'Treatment', 'Population.plsnts/ha',
-                           '2017-03-07', '2017-03-19', '2017-03-24',
-                           '2017-04-02', '2017-04-10', '2017-04-18',
-                           'Yield.t/ha', 'Grain.Moisture.%', 'Temp.moisture.Taken',
-                           '100.grain.wt.Grams')]
-
-# Create summarised data set for collated means meta-dataset
-# NEXT STEP - sort and copy it to dataset
-Herm_17_sum <- Herm_17 %>%
-   group_by(Chemical,
-            Chemical.Trt,
-            `Row.Spacing.(m)`,
-            Manage.Trt,
-            Management) %>%
-   summarise(
-      PM_final_severity = mean(`I_11/05/2017`, na.rm = TRUE),
-      Disease_error = sd(`I_11/05/2017`, na.rm = TRUE),
-      `grain_yield(t/ha)` = mean(`Yield.T/Ha`, na.rm = TRUE),
-      Yield_error = sd(`Yield.T/Ha`, na.rm = TRUE),
-      meanSq = anova(lm(`Yield.T/Ha` ~ factor(Manage.Trt) + factor(Trt) + `Row.Spacing.(m)`, data = subset(Herm_17, Chemical != "Custodia® 320 SC")))[1,3] # of only triazoles
-   )
-
-Herm_17_sum <-
-   with(Herm_17_sum, Herm_17_sum[order(Manage.Trt, Chemical, `Row.Spacing.(m)`), ])
-
-# inserted meansquare in manually
-
-# Columns to keep
-Herm_17 <- Herm_17[, c(1, 2, 4, 5, 7, 10, 9, 11, 12, 13,
-                       17, 19, 21, 23, 25, 27, 29,
-                       #                      18,20,22,24,26,28,30,
-                       34, 36, 37, 35)]
-
-```
-
 #### Calculating treatment means
-```{r Missen17_means}
-
-Fogerty_17_m <- Fogerty_17_dat %>%
+```{r Herm17_means}
+
+Herm_17_m <- Herm_17_dat %>%
    group_by(host_genotype, n_treatment, row_spacing, fungicide_ai) %>%
@@
              AUDPC.sd = sd(AUDPC),
-             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment) + fungicide_ai + row_spacing, data = subset(Fogerty_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
-   )
+             meanSq = anova(lm(grain_yield.t.ha. ~ 
+                                  factor(n_treatment) + fungicide_ai + row_spacing, 
+                               data = subset(Herm_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
+   )
+sd(Herm_17_dat$PM_final_severity)
 
 # For some weird reason standard deviations are comming back NA in the code above
-Fogerty_17_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
-   Fogerty_17_dat %>%
+Herm_17_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
+   Herm_17_dat %>%
    group_by(n_treatment, row_spacing, fungicide_ai) %>%
@@
 write.csv(
-   Fogerty_17_m,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2017/MissenFlats/Fogerty_17_mean.csv",
+   Herm_17_m,
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2017/Hermitage/Hermitage_17_mean.csv",
    row.names = FALSE
@@
 ```
+
+# Start from here
 

### 2020-01-23 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Wrangled the AUDPC into the data

@@
 
-head(Fogerty_17)
-unique(Fogerty_17$Chem.Trt)
-unique(Fogerty_17$Chemical)
-Fogerty_17[,7:11]
 ```
@@
    select(c("disease_error","yield_error"))
+
+Fogerty_17_m <- fold_data(Fogerty_17_m, PM_MB_means)
 
@@
 
+Herm_17_m <- fold_data(Herm_17_m, PM_MB_means)
+
 write.csv(
@@
 ```
-
-# Start from here
 
@@
 
-#dim(Well_18)   # 72 rows , 32 Columns
-#names(Well_18)
-
-# Columns to keep
-Well_18 <- Well_18[, c('Plot','Rep','Plant.Pop','Row.Spacing',
-            'Fungicide','Treatment','IR.23-3-18',
-            'IR.5-4-18','IR.11-4-18','IR.18-4-18',
-            'IR.26-4-18','IR.2-5-18','S.23-3-18',
-            'S.5-4-18','S.11-4-18','S.18-4-18',
-            'S.26-4-18','S.2-5-18','Row.Length','Yield./.ha')]
-
-Well_18_means <- Well_18 %>%
-   group_by(Row.Spacing, Fungicide, Plant.Pop) %>%
-   summarise(
-      Yield = mean(`Yield./.ha`, na.rm = TRUE),
-      Incidence  = max(Well_18.1$Incidence),
-      Severity  = max(Severity, na.rm = TRUE)
-   )
-
-# respectively
-# plot and treatment variables
-# Incidence assessment
-# severity assessment
-# Yield assessment
-
-Well_18_inc <-
-   reshape(
-      data = Well_18,
-      idvar = "Plot",
-      direction = "long",
-      varying = list(incidence = names(Well_18)[7:12]),
-      timevar = "ass_date_i"
-   )
-
-Well_18_sev <-
-   reshape(
-      data = Well_18,
-      idvar = "Plot",
-      direction = "long",
-      varying = list(incidence = names(Well_18)[13:18]),
-      timevar = "ass_date_s"
-   )
-
-Well_18.1 <- cbind(Well_18_inc[, c(1:6, 13:16)], Well_18_sev[, 15:16])
-
-names(Well_18.1)[10] <- c("Incidence")
-names(Well_18.1)[12] <- c("Severity")
-Well_18.1$ass_date_i <- rep(names(Well_18_inc)[7:12], each = 72)
-Well_18.1$ass_date_i <-
-   as.Date(gsub("S.", "", Well_18.1$ass_date_i), format = "%d-%m-%y")
-names(Well_18.1)[9] <- c("Assessment_date")
-Well_18.1 <- Well_18.1[c(1:10, 12)]
-
-Well_18.1$Row.Spacing <-
-   as.numeric(unlist(strsplit(Well_18.1$Row.Spacing, " mtr")))
+colnames(Well_18)[13:14] <- c("Row.Spacing_ID", "Fungicide_ID")
+
+```
+
+#### Define treatment data
+```{r Well_18_treatmentDefine}
+Well_18_dat <- Well_18 %>%
+   mutate(trade_name = 
+             case_when(Fung.Trt == 1 ~ "Folicur",
+                       Fung.Trt == 3 ~ "Throttle",
+                       Fung.Trt == 2 ~ "Custodia",
+                       Fung.Trt == 4 ~ "control",
+                       TRUE ~ "other"))%>%
+   mutate(fungicide_ai = 
+             case_when(Fung.Trt == 1 ~ "tebuconazole",
+                       Fung.Trt == 3 ~ "propiconazole",
+                       Fung.Trt == 2 ~ "200 g/L tebuconazole + 120 g/L azoxystrobin",
+                       Fung.Trt == 4 ~ "control",
+                       TRUE ~ "other"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Fung.Trt == 1 ~ 60,
+                       Fung.Trt == 2 ~ 62,
+                       Fung.Trt == 3 ~ 125,
+                       Fung.Trt == 4 ~ NA_real_,
+                       TRUE ~ 9999))%>%
+   mutate(Row.Spacing = 
+             case_when(Row.Sp.Trt == 1 ~ 0.25,
+                       Row.Sp.Trt == 2 ~ 0.5,
+                       Row.Sp.Trt == 3 ~ 1,
+                       TRUE ~ 9999))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Fung.Trt <= 3 ~ as.Date("2018-04-16", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Fung.Trt == 4 ~ as.Date(NA),
+                       Fung.Trt == 1 ~ as.Date("2018-03-28", format = "%Y-%m-%d"),
+                       Fung.Trt == 2 ~ as.Date("2018-03-28", format = "%Y-%m-%d"),
+                       Fung.Trt == 3 ~ as.Date("2018-03-28", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Fung.Trt <= 3 ~ 2,
+                       TRUE ~ NA_real_))
+
+```
+
+#### Input trial data
+```{r Well18_Trialdat}
+
+Well_18_dat <- 
+   data.frame(trial_ref = "mung1718/01",
+              year = "2018",
+              location = "Wellcamp",
+              host_genotype = "Jade",
+              trial_design = "RCB",
+              plot_length = Well_18_dat$Row.Length,
+              plot_width = 2,
+              plant_density = Well_18_dat$Plant.Pop,
+              row_spacing = Well_18_dat$Row.Spacing,
+              replicate = Well_18_dat$Rep,
+              planting_date = as.Date("2018-02-13", format = "%Y-%m-%d"),
+              emergence_date = as.Date(NA),
+              flowering_date = as.Date(NA),
+              pod_fill_date = as.Date(NA),
+              mid_late_pod_fill = as.Date(NA),
+              first_sign_disease = as.Date("2018-03-21", format = "%Y-%m-%d"),
+              trade_name = as.factor(Well_18_dat$trade_name),
+              fungicide_ai = Well_18_dat$fungicide_ai,
+              dose_ai.ha = Well_18_dat$dose_ai.ha,
+              n_treatment = Well_18_dat$Treatment,
+              fungicide_application_1 = Well_18_dat$fungicide_application_1,
+              fungicide_application_2 = Well_18_dat$fungicide_application_2,
+              total_fungicide = Well_18_dat$spray_n,
+              harvest_date = as.Date("2018-05-31", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2018-05-02", format = "%Y-%m-%d"),
+              PM_final_severity = Well_18_dat$`IR.2-5-18`,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(Well_18_dat$`Yield./.ha`)
+               # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
+              )
+
+Well_18_dat <- cbind(Well_18_dat,
+                          AUDPC = apply(data.frame(zero = 1,
+                                                   Well_18[,c("IR.23-3-18","IR.5-4-18", "IR.11-4-18", "IR.18-4-18","IR.26-4-18","IR.2-5-18")]-1),
+                                        1, 
+                                        FUN = audpc, 
+                                        dates = c((Well_18_dat$first_sign_disease[1]-7)-
+                                                     Well_18_dat$planting_date[1],
+                                                  38,51 ,57,64,72,78)
+                                        )
+                          )
+
+```
+
+#### Calculating treatment means
+```{r Well17_means}
+
+Well_18_m <- Well_18_dat %>%
+   group_by(host_genotype, n_treatment, row_spacing, fungicide_ai) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             location = unique(location),
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             dose_ai.ha = unique(dose_ai.ha),
+             trial_ref = unique(trial_ref),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
+             plot_width.m. = mean(plot_width, na.rm = TRUE),
+             plant_density = mean(plant_density, na.rm = TRUE),
+             replicates = length(as.numeric(replicate)),
+             planting_date = unique(planting_date),
+             emergence_date = unique(emergence_date),
+             flowering_date = unique(flowering_date),
+             pod_fill_date = unique(pod_fill_date),
+             mid_late_pod_fill = unique(mid_late_pod_fill),
+             first_sign_disease = unique(first_sign_disease),
+             fungicide_application_1 = unique(fungicide_application_1),
+             fungicide_application_2 = unique(fungicide_application_2),
+             total_fungicide = unique(total_fungicide),
+             harvest_date = unique(harvest_date),
+             final_assessment = unique(final_assessment),
+             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+             rating_scale = unique(rating_scale),
+             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+             D_error_type = "stdev",
+             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+             raw_graded = NA,
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+             Y_error_type = "stdev",
+             AUDPC.m = mean(AUDPC),
+             AUDPC.sd = sd(AUDPC),
+             meanSq = anova(lm(grain_yield.t.ha. ~ 
+                                  factor(n_treatment) + fungicide_ai + row_spacing, 
+                               data = subset(Well_18_dat, trade_name != "Custodia")))[1,3] # of only triazoles
+   )
+
+# For some weird reason standard deviations are comming back NA in the code above
+Well_18_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
+   Well_18_dat %>%
+   group_by(n_treatment, row_spacing, fungicide_ai) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("disease_error","yield_error"))
+
+Well_18_m <- fold_data(Well_18_m, PM_MB_means)
 
 write.csv(
-   Well_18.1,
-   "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/2018_Wellcamp.csv"
-)
-
-Well_18$FungVCon <- Well_18$Fung.Trt
-Well_18[Well_18$FungVCon == 1,"FungVCon"] <- 3
-Well_18[Well_18$FungVCon == 4,"FungVCon"] <- 1
-Well_18[Well_18$FungVCon == 3,"FungVCon"] <- 2
-
-Well_18_means <- Well_18.1 %>%
-   group_by(Row.Spacing, Fungicide, Plant.Pop) %>%
-   summarise(
-      Yield = mean(`Yield./.ha`, na.rm = TRUE),
-      Incidence  = max(Well_18.1$Incidence),
-      Severity  = max(Severity, na.rm = TRUE),
-      meanSq = anova(lm(`Yield./.ha` ~ factor(Plant.Pop) + factor(FungVCon) + `Row.Spacing`, data = subset(Well_18, Fungicide != "Custodia")))[2,3] # of only triazoles
+   Well_18_m,
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2018/Wellcamp/Wellcamp_18_mean.csv",
+   row.names = FALSE
 )
@@
    )
-
+?audpc
 # Remove these plots as the results can't be trusted
@@
 
-PM_MB_19$AUDPC <- apply(PM_MB_19[,c("15-4-19.Incedence", "23-4-19.Incedence", "1-5-19.Incedence")]-1,1,FUN = audpc, dates = c(3,8,21))
-
-PM_MB_19$Yeild
-
+# Calculate area under the disease progress curve
+PM_MB_19$AUDPC <- apply(data.frame(zero = 1,PM_MB_19[,c("15-4-19.Incedence", "23-4-19.Incedence", "1-5-19.Incedence")]-1),1,FUN = audpc, dates = c(60, 70,78,86))
+
+# Calculate area under the disease progress curve for plots which were not assessed at on 2019-05-01
+PM_MB_19[is.na(PM_MB_19$`1-5-19.Incedence`),"AUDPC"] <- 
+   apply(data.frame(zero = 1,PM_MB_19[is.na(PM_MB_19$`1-5-19.Incedence`) ,c("15-4-19.Incedence", "23-4-19.Incedence")]-1),1,FUN = audpc, dates = c(60, 70,78))
+```
+
+#### Define treatment data
+```{r Well_18_treatmentDefine}
+Herm_19_dat <- PM_MB_19 %>%
+   mutate(fungicide_application_1 = 
+             case_when(`T/ment.NUM` == 1 ~ as.Date("2018-04-15", format = "%Y-%m-%d"),
+                       `T/ment.NUM` == 2 ~ as.Date("2018-04-15", format = "%Y-%m-%d"),
+                       `T/ment.NUM` == 3 ~ as.Date("2018-04-23", format = "%Y-%m-%d"),
+                       `T/ment.NUM` == 4 ~ as.Date(NA),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(`T/ment.NUM` == 2 ~ as.Date("2018-04-29", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(`T/ment.NUM` == 3 ~ 2,
+                       `T/ment.NUM` <= 2 ~ 1,
+                       TRUE ~ NA_real_))%>%
+   mutate(trial_ref = 
+             case_when(TOS.NUM == 1 ~ "mung1819/01",
+                       TOS.NUM == 2 ~ "mung1819/02",
+                       TRUE ~ NA_character_))%>%
+   mutate(planting_date = 
+             case_when(TOS.NUM == 1 ~ as.Date("2018-02-04", format = "%Y-%m-%d"),
+                       TOS.NUM == 2 ~ as.Date("2018-02-18", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(emergence_date = 
+             case_when(TOS.NUM == 1 ~ as.Date("2018-02-11", format = "%Y-%m-%d"),
+                       TOS.NUM == 2 ~ as.Date("2018-02-25", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(final_assessment = 
+             case_when(TOS.NUM == 1 ~ as.Date("2018-04-24", format = "%Y-%m-%d"),
+                       TOS.NUM == 2 ~ as.Date("2018-05-01", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(PM_final_severity = 
+             case_when(is.na(`1-5-19.Incedence`) ~ `23-4-19.Incedence`,
+                       TRUE ~ `1-5-19.Incedence`))%>%
+   mutate(trade_name = 
+             case_when(`T/ment.NUM` == 4 ~ NA_character_,
+                       TRUE ~ "Folicur"))%>%
+   mutate(fungicide_ai = 
+             case_when(`T/ment.NUM` == 4 ~ NA_character_,
+                       TRUE ~ "tebuconazole"))%>%
+
+   mutate(dose_ai.ha = 
+             case_when(`T/ment.NUM` == 4 ~ NA_real_,
+                       TRUE ~ 62))%>%
+   mutate(meanSq = 
+             case_when(TOS.NUM == 1 ~ anova(lm(Yeild/1000 ~ 
+                                  factor(`T/ment.NUM`) , 
+                               data = PM_MB_19[PM_MB_19$TOS.NUM == 1,]))[1,3],
+                       TOS.NUM == 2 ~ anova(lm(Yeild/1000 ~ 
+                                  factor(`T/ment.NUM`) , 
+                               data = PM_MB_19[PM_MB_19$TOS.NUM == 2,]))[1,3],
+                       TRUE ~ NA_real_))
+
+```
+
+#### Input trial data
+```{r Well18_Trialdat}
+
+Herm_19_dat <- 
+   data.frame(trial_ref = Herm_19_dat$trial_ref,
+              year = "2019",
+              location = "Hermitage",
+              host_genotype = "Jade",
+              trial_design = "RCB",
+              plot_length = Herm_19_dat$Plot.Lengths,
+              plot_width = 2,
+              plant_density = NA_character_,
+              row_spacing = 0.25,
+              replicate = Herm_19_dat$Rep.Num,
+              planting_date = Herm_19_dat$planting_date,
+              emergence_date = Herm_19_dat$emergence_date,
+              flowering_date = as.Date(NA),
+              pod_fill_date = as.Date(NA),
+              mid_late_pod_fill = as.Date(NA),
+              first_sign_disease = as.Date("2018-04-12", format = "%Y-%m-%d"),
+              trade_name = as.factor(Herm_19_dat$trade_name),
+              fungicide_ai = Herm_19_dat$fungicide_ai,
+              dose_ai.ha = Herm_19_dat$dose_ai.ha,
+              n_treatment = Herm_19_dat$`T/ment.NUM`,
+              fungicide_application_1 = Herm_19_dat$fungicide_application_1,
+              fungicide_application_2 = Herm_19_dat$fungicide_application_2,
+              total_fungicide = Herm_19_dat$spray_n,
+              harvest_date = as.Date("2018-05-22", format = "%Y-%m-%d"),
+              final_assessment = Herm_19_dat$final_assessment,
+              PM_final_severity = Herm_19_dat$PM_final_severity,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(Herm_19_dat$Yeild)/1000,
+              meanSq = Herm_19_dat$meanSq
+              )
+
+Herm_19_dat$plant_density
+
+unique(Herm_19_dat$plot_length)
+mean(Herm_19_dat$plant_density, na.rm = TRUE)
+
+```
+
+```{r Herm19_means}
+
+Herm_19_m <- Herm_19_dat %>%
+   group_by(trial_ref, n_treatment) %>%
+   summarise(year = unique(year),
+             location = unique(location),
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             dose_ai.ha = unique(dose_ai.ha),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
+             plot_width.m. = mean(plot_width, na.rm = TRUE),
+             plant_density = NA_character_,
+             replicates = length(as.numeric(replicate)),
+             planting_date = unique(planting_date),
+             emergence_date = unique(emergence_date),
+             flowering_date = unique(flowering_date),
+             pod_fill_date = unique(pod_fill_date),
+             mid_late_pod_fill = unique(mid_late_pod_fill),
+             first_sign_disease = unique(first_sign_disease),
+             fungicide_application_1 = unique(fungicide_application_1),
+             fungicide_application_2 = unique(fungicide_application_2),
+             total_fungicide = unique(total_fungicide),
+             harvest_date = unique(harvest_date),
+             final_assessment = unique(final_assessment),
+             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+             rating_scale = unique(rating_scale),
+             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+             D_error_type = "stdev",
+             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+             raw_graded = NA,
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+             Y_error_type = "stdev",
+             AUDPC.m = mean(AUDPC),
+             AUDPC.sd = sd(AUDPC),
+             meanSq = unique(meanSq)
+   )
+
+# For some weird reason standard deviations are comming back NA in the code above
+# Herm_17_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
+#    Herm_17_dat %>%
+#    group_by(n_treatment, row_spacing, fungicide_ai) %>%
+#    summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+#              yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+#    select(c("disease_error","yield_error"))
+#
+
+Herm_19_m <- fold_data(Herm_19_m, PM_MB_means)
+
+write.csv(
+   Herm_17_m,
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2019/Hermitage/Hermitage_19_mean.csv",
+   row.names = FALSE
+)
+
+```
+
+```{r}
 PM19_means <- PM_MB_19 %>%
@@
 
-library(agricolae)
-
 colnames(PM_MB_19)

### 2020-01-23 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
change filepath 2019

@@
    Herm_17_m,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2019/Hermitage/Hermitage_19_mean.csv",
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2019/Hermitage_19_mean.csv",
    row.names = FALSE

### 2020-01-24 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Code corrections

@@
 
-source("C:/Users/U8011054/OneDrive - USQ/Cloudstor/R/Mungbean_projects/Mungbean_PM/R/import_data.R")
+source("../R/import_data.R")
 PM_MB_means <- import_data()
@@
               replicate = Herm_17_dat$Rep,
-              planting_date = as.Date("2017-01-27", format = "%Y-%m-%d"),
-              emergence_date = as.Date("2017-02-01", format = "%Y-%m-%d"),
+              planting_date = as.Date("2017-02-13", format = "%Y-%m-%d"),
+              emergence_date = as.Date("2017-02-20", format = "%Y-%m-%d"),
               flowering_date = as.Date(NA),
@@
               mid_late_pod_fill = as.Date(NA),
-              first_sign_disease = as.Date("2017-03-13", format = "%Y-%m-%d"),
+              first_sign_disease = as.Date("2017-03-24", format = "%Y-%m-%d"),
               trade_name = as.factor(Herm_17_dat$trade_name),
@@
                           )
-
+Herm_17_m
 ```
@@
 Herm_17_m <- Herm_17_dat %>%
-   group_by(host_genotype, n_treatment, row_spacing, fungicide_ai) %>%
+   group_by(n_treatment, fungicide_ai,row_spacing) %>%
    summarise(trial_ref = unique(trial_ref),
@@
              AUDPC.sd = sd(AUDPC),
-             meanSq = anova(lm(grain_yield.t.ha. ~ 
+             Y_Msquare = anova(lm(grain_yield.t.ha. ~ 
                                   factor(n_treatment) + fungicide_ai + row_spacing, 
@@
    )
-sd(Herm_17_dat$PM_final_severity)
 
 # For some weird reason standard deviations are comming back NA in the code above
-Herm_17_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
+Herm_17_m[,c("n_treatment","fungicide_ai","row_spacing", "disease_error","yield_error")] <-
    Herm_17_dat %>%
-   group_by(n_treatment, row_spacing, fungicide_ai) %>%
+   group_by(n_treatment, fungicide_ai,row_spacing) %>%
    summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
-   select(c("disease_error","yield_error"))
+   select(c("n_treatment","fungicide_ai","row_spacing","disease_error","yield_error"))
+
+Herm_17_m[Herm_17_m$n_treatment == 1, "fungicide_ai"] <- as.factor("control")
+Herm_17_m[Herm_17_m$n_treatment == 1,"dose_ai.ha"] <- NA_real_
+Herm_17_m[Herm_17_m$n_treatment == 1, "trade_name"] <- NA
 
@@
    mutate(spray_n = 
-             case_when(`T/ment.NUM` == 3 ~ 2,
-                       `T/ment.NUM` <= 2 ~ 1,
-                       TRUE ~ NA_real_))%>%
+             case_when(`T/ment.NUM` == 2 ~ 2,
+                       `T/ment.NUM` == 1 ~ 1,
+                       `T/ment.NUM` == 3 ~ 1,
+                       TRUE ~ 0))%>%
    mutate(trial_ref = 
@@
 #### Input trial data
-```{r Well18_Trialdat}
+```{r Herm_19_Trialdat}
 
@@
               grain_yield.t.ha. = as.numeric(Herm_19_dat$Yeild)/1000,
-              meanSq = Herm_19_dat$meanSq
-              )
-
-Herm_19_dat$plant_density
-
-unique(Herm_19_dat$plot_length)
-mean(Herm_19_dat$plant_density, na.rm = TRUE)
-
+              meanSq = Herm_19_dat$meanSq,
+              AUDPC = Herm_19_dat$AUDPC
+              )
+
+Herm_19_m
 ```
@@
              location = unique(location),
+             host_genotype = "Jade",
              trial_design = unique(trial_design),
@@
              plot_width.m. = mean(plot_width, na.rm = TRUE),
-             plant_density = NA_character_,
+             plant_density = "40k",
+             row_spacing = unique(row_spacing),
              replicates = length(as.numeric(replicate)),
@@
              total_fungicide = unique(total_fungicide),
+             fungicide_ai = unique(fungicide_ai),
              harvest_date = unique(harvest_date),
@@
              AUDPC.sd = sd(AUDPC),
-             meanSq = unique(meanSq)
+             Y_Msquare = unique(meanSq)
    )
@@
 # For some weird reason standard deviations are comming back NA in the code above
-# Herm_17_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
-#    Herm_17_dat %>%
-#    group_by(n_treatment, row_spacing, fungicide_ai) %>%
-#    summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
-#              yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
-#    select(c("disease_error","yield_error"))
-#
+Herm_19_m[,c("trial_ref","disease_error","yield_error")] <-
+   Herm_19_dat %>%
+   group_by(trial_ref, n_treatment) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("disease_error","yield_error"))
 
@@
 write.csv(
-   Herm_17_m,
+   Herm_19_m,
    "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2019/Hermitage_19_mean.csv",
@@
 ```
-
-```{r}
-PM19_means <- PM_MB_19 %>%
-   group_by(TOS.NUM, `T/ment.NUM`) %>%
-   summarise(
-      Incidence190423 = mean(`23-4-19.Incedence`, na.rm = TRUE),
-      Inc.sd.190423 = sd(`23-4-19.Incedence`, na.rm = TRUE),
-      Inc.error.190423 = "Stdev",
-      Incidence190501 = mean(`1-5-19.Incedence`, na.rm = TRUE),
-      Inc.sd.190501 = sd(`1-5-19.Incedence`, na.rm = TRUE),
-      Inc.error.190501 = "Stdev",
-      Plot_length = mean(Plot.Lengths, na.rm = TRUE),
-      Yield = mean(Yeild/1000, na.rm = TRUE),
-      Yield_error = sd(Yeild/1000, na.rm = TRUE),
-      AUDPC = mean(AUDPC, na.rm = TRUE),
-      meanSq = anova(lm(Yeild/1000 ~ factor(TOS.NUM) + factor(`T/ment.NUM`), data = PM_MB_19))[2,3]
-   )
-
-colnames(PM_MB_19)
-
-audpc(PM_MB_19[PM_MB_19$TOS.NUM == 2 , c(5, 7, 9)], c(70, 78, 86))
-
-PM_MB_19$AUDPC <- NA
-PM_MB_19[PM_MB_19$TOS.NUM == 1 , "AUDPC"] <-
-   audpc(PM_MB_19[PM_MB_19$TOS.NUM == 1 , c(5, 7)], c(70, 78))
-PM_MB_19[PM_MB_19$TOS.NUM == 2 , "AUDPC"] <-
-   audpc(PM_MB_19[PM_MB_19$TOS.NUM == 2 , c(5, 7, 9)], c(70, 78, 86))
-
-boxplot(AUDPC ~ as.factor(`T/ment.NUM`) * as.factor(TOS.NUM) , data = PM_MB_19)
-
-as.Date("2019-05-22") - as.Date("2019-02-04")
-as.Date("2019-04-15") - as.Date("2019-02-04")
-as.Date("2019-04-23") - as.Date("2019-02-04")
-as.Date("2019-05-01") - as.Date("2019-02-04")
-
-```

### 2020-01-24 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
2016 Kingaroy AUDPC entered and some other code improvements

@@
 
-unique(Herm_16$Treatment)
 ```
@@
               rating_scale = "1-9",
-              grain_yield.t.ha. = as.numeric(Herm_16_dat$`Raw.Adjusted.Yeild./.ha`)
-              )
+              grain_yield.t.ha. = as.numeric(Herm_16_dat$`Raw.Adjusted.Yeild./.ha`),
+              stringsAsFactors = FALSE)
 ```
@@
               rating_scale = "1-9",
-              grain_yield.t.ha. = as.numeric(King_16_dat$`Raw.Adjusted.Yeild./.ha`)
-              )
+              grain_yield.t.ha. = as.numeric(King_16_dat$`Raw.Adjusted.Yeild./.ha`),
+              stringsAsFactors = FALSE)
 ```
@@
              #AUDPC.sd = sd(AUDPC),
-             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = King_16_dat))[1,3]
+             Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = King_16_dat))[1,3]
    )
@@
 King_16_m <- left_join(King_16_m,King_16.DR)
-King_16_m$AUDPC.m <- apply(King_16_m[,c("dae20", "dae34", "dae46", "PM_final_severity")]-1,1, 
-                            FUN = audpc, dates = c(1,14,26,40))
+King_16_m$AUDPC_m <- apply(King_16_m[,c("dae20", "dae34", "dae46", "PM_final_severity")]-1,1, 
+                            FUN = audpc, dates = c(20,34,46,60))
+King_16_m$AUDPC_se <- NA
 
 King_16_m <- fold_data(King_16_m, PM_MB_means)
+King_16_m <- King_16_m[,!colnames(King_16_m) %in% c('Treatment',"dae20","dae34","dae46","Final_Yield_tHa", "AUDPC.m")]
 
@@
 #### Define treatment data
-```{r King16_treatmentDefine}
+```{r Fog17_treatmentDefine}
 Fogerty_17_dat <- Fogerty_17 %>%
@@
    mutate(fungicide_ai = 
-             case_when(Chem.Trt == 1 ~ "tebuconazole",
+             as.character(case_when(Chem.Trt == 1 ~ "tebuconazole",
                                     Chem.Trt == 2 ~ "propiconazole",
                                     Chem.Trt == 3 ~ "200 g/L tebuconazole + 120 g/L azoxystrobin",
-                       TRUE ~ "other"))%>%
+                                    TRUE ~ "other")))%>%
    mutate(dose_ai.ha = 
@@
    mutate(spray_n = 
-             case_when(Treatment == 1 ~ 0,
-                       Treatment == 4 ~ 2,
-                       Treatment == 6 ~ 2,
+             case_when(Treatment.No == 1 ~ 0,
+                       Treatment.No == 4 ~ 2,
+                       Treatment.No == 6 ~ 2,
                        TRUE ~ 1))
@@
               trade_name = as.factor(Fogerty_17_dat$trade_name),
-              fungicide_ai = Fogerty_17_dat$fungicide_ai,
+              fungicide_ai = as.character(Fogerty_17_dat$fungicide_ai),
               dose_ai.ha = Fogerty_17_dat$dose_ai.ha,
@@
                             FUN = audpc, dates = c(1,12,17,26,34,42)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
-              )
+              , stringsAsFactors = FALSE)
 ```
@@
 Fogerty_17_m <- Fogerty_17_dat %>%
-   group_by(host_genotype, n_treatment, row_spacing, fungicide_ai) %>%
+   group_by(n_treatment, row_spacing, fungicide_ai) %>%
    summarise(trial_ref = unique(trial_ref),
@@
              location = unique(location),
+             host_genotype = unique(host_genotype),
              trial_design = unique(trial_design),
@@
              AUDPC.sd = sd(AUDPC),
-             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment) + fungicide_ai + row_spacing, data = subset(Fogerty_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
+             Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment) + fungicide_ai + row_spacing, data = subset(Fogerty_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
    )
@@
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
-   select(c("disease_error","yield_error"))
+   select(c("n_treatment","row_spacing","disease_error","yield_error"))
+
+Fogerty_17_m[Fogerty_17_m$n_treatment == 1, "fungicide_ai"] <- "control"
+Fogerty_17_m[Fogerty_17_m$n_treatment == 1,"dose_ai.ha"] <- NA_real_
+Fogerty_17_m[Fogerty_17_m$n_treatment == 1, "trade_name"] <- NA
 

### 2020-01-24 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
AUDPC and code corrections to Herm 16

@@
              #AUDPC.sd = sd(AUDPC),
-             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Herm_16_dat))[1,3]
+             Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Herm_16_dat))[1,3]
    )
@@
    group_by(n_treatment) %>%
-   summarise(yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   summarise(PM_final_severity = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
    select(c("yield_error"))
@@
 Herm_16_m <- left_join(Herm_16_m,Herm_16.DR)
-Herm_16_m$AUDPC.m <- apply(Herm_16_m[,c("dae24", "dae38", "dae48", "dae63")]-1,1, 
-                            FUN = audpc, dates = c(0,14,24,39))
+Herm_16_m$AUDPC_m <- apply(Herm_16_m[,c("dae24", "dae38", "dae48", "dae63")]-1,1, 
+                            FUN = audpc, dates = c(9,13,23,38))
+Herm_16_m$AUDPC_se <- NA
+
+Herm_16_m$PM_final_severity <- Herm_16_m$dae63
 
 Herm_16_m <- fold_data(Herm_16_m, PM_MB_means)
+Herm_16_m <- Herm_16_m[,!colnames(Herm_16_m) %in% c('Treatment',"dae24","dae38","dae48","dae63","Final_Yield_tHa", "AUDPC.m")]
 

### 2020-01-28 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Updated 2013 code

@@
               Y_error_type = "stdev",
-              AUDPC.m = mean(AUDPC),
-             AUDPC.sd = sd(AUDPC),
-              meanSq = anova(lm(grain_yield.t.ha. ~ host_genotype + factor(n_treatment), data = Herm_10_dat))[2,3]
+              AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+              Y_Msquare = anova(lm(grain_yield.t.ha. ~ host_genotype + factor(n_treatment), data = Herm_10_dat))[2,3]
    )
@@
               Y_error_type = "stdev",
-             AUDPC.m = mean(AUDPC),
-             AUDPC.sd = sd(AUDPC),
-              meanSq = anova(lm(grain_yield.t.ha./1000 ~ factor(n_treatment) + host_genotype, 
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+              Y_Msquare = anova(lm(grain_yield.t.ha./1000 ~ factor(n_treatment) + host_genotype, 
                                 data = Herm_11_dat[Herm_11_dat$fungicide_ai == "tebuconazole" | 
@@
               Y_error_type = "stdev",
-             AUDPC.m = mean(AUDPC),
-             AUDPC.sd = sd(AUDPC),
-              meanSq = anova(lm(grain_yield.t.ha./1000 ~ factor(n_treatment) + host_genotype, 
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+              Y_Msquare = anova(lm(grain_yield.t.ha./1000 ~ factor(n_treatment) + host_genotype, 
                                 data = King_11_dat[King_11_dat$fungicide_ai == "tebuconazole" | 
@@
               Y_error_type = "stdev",
-             AUDPC.m = mean(AUDPC),
-             AUDPC.sd = sd(AUDPC),
-              meanSq = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                 data = Goolhi_13_dat[Goolhi_13_dat$fungicide_ai == "propiconazole" | 
@@
               Y_error_type = "stdev",
-             AUDPC.m = mean(AUDPC),
-             AUDPC.sd = sd(AUDPC),
-              meanSq = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                 data = MarysM_13_dat[MarysM_13_dat$fungicide_ai == "propiconazole" | 
@@
    if (i == length(Premer.13D[, 1])) {
-      print(!plotsRecorded)
+      #print(!plotsRecorded)
    }
@@
 Premer_13_m <- Premer_13_dat %>%
-   group_by(trial_ref, year, location, host_genotype, trial_design, 
-            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
-   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
+   group_by(n_treatment) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             location = unique(location),
+             host_genotype = unique(host_genotype),
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             fungicide_ai = unique(fungicide_ai),
+             dose_ai.ha = unique(dose_ai.ha),
+            plot_length.m. = mean(plot_length, na.rm = TRUE),
               plot_width.m. = mean(plot_width, na.rm = TRUE),
@@
               Y_error_type = "stdev",
-             AUDPC.m = mean(AUDPC),
-             AUDPC.sd = sd(AUDPC),
-              meanSq = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                 data = Premer_13_dat[Premer_13_dat$fungicide_ai == "propiconazole" | 
@@
 
-write.csv(
-   Premer_13_m[order(as.numeric(Premer_13_m$n_treatment)),],
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/BB1305_Millmerran_means.csv",
-   row.names = FALSE
-)
 ##########################
@@
 
-Premer_13_m <- Premer_13_m[Premer_13_m$trade_name != "other",]
+#Premer_13_m <- Premer_13_m[Premer_13_m$trade_name != "other",]
 
@@
 
-# read in yield and format
 # read in yield and format
@@
               rating_scale = "1-9",
-              grain_yield.t.ha. = as.numeric(Millm_13$`kg/Ha`)/1000
+              grain_yield.t.ha. = as.numeric(Millm_13$`kg/Ha`)/1000,
               #AUDPC = apply(Millm_13[,c("Inc_23D","Inc_42D")]-1,1, FUN = audpc, dates = c(23,42)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
-              )
+              stringsAsFactors = FALSE)
 
@@
                                         FUN = audpc, 
-                                        dates = c((Millm_13_dat$first_sign_disease[1]-7)-
-                                                     Millm_13_dat$planting_date[1],
-                                                  23,42)
+                                        dates = c(1,23,42)
                                         )
@@
              Y_error_type = "stdev",
-             AUDPC.m = mean(AUDPC),
-             AUDPC.sd = sd(AUDPC),
-             meanSq = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+             Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                 data = Millm_13_dat[Millm_13_dat$fungicide_ai == "propiconazole" | 
@@
                        Treatment == "5wks+2" ~ as.Date("2015-03-02", format = "%Y-%m-%d"),
-                       Treatment == "1/3C" ~ as.Date("2015-03-23", format = "%Y-%m-%d"),
+                       Treatment == "1/3C" ~ as.Date("2015-03-24", format = "%Y-%m-%d"),
                        TRUE ~ as.Date(NA)))%>%
@@
               AUDPC = apply(Herm_15_dat[,c("day0", "day1", "day8", "day15","day22")]-1,1, 
-                            FUN = audpc, dates = c(0,1,8,15,22)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
-              )
+                            FUN = audpc, dates = c(0,1,8,15,22)),# -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
+              stringsAsFactors = FALSE)
 
@@
              Y_error_type = "stdev",
-             AUDPC.m = mean(AUDPC),
-             AUDPC.sd = sd(AUDPC),
-             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Herm_15_dat))[1,3]
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+             Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Herm_15_dat))[1,3]
    )
@@
              Y_error_type = "stdev",
-             #AUDPC.m = mean(AUDPC),
-             #AUDPC.sd = sd(AUDPC),
+             #AUDPC_m = mean(AUDPC),
+             #AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Herm_16_dat))[1,3]
@@
 Herm_16_m <- fold_data(Herm_16_m, PM_MB_means)
-Herm_16_m <- Herm_16_m[,!colnames(Herm_16_m) %in% c('Treatment',"dae24","dae38","dae48","dae63","Final_Yield_tHa", "AUDPC.m")]
+Herm_16_m <- Herm_16_m[,!colnames(Herm_16_m) %in% c('Treatment',"dae24","dae38","dae48","dae63","Final_Yield_tHa", "AUDPC_m")]
 
@@
              Y_error_type = "stdev",
-             #AUDPC.m = mean(AUDPC),
-             #AUDPC.sd = sd(AUDPC),
+             #AUDPC_m = mean(AUDPC),
+             #AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = King_16_dat))[1,3]
@@
 King_16_m <- fold_data(King_16_m, PM_MB_means)
-King_16_m <- King_16_m[,!colnames(King_16_m) %in% c('Treatment',"dae20","dae34","dae46","Final_Yield_tHa", "AUDPC.m")]
+King_16_m <- King_16_m[,!colnames(King_16_m) %in% c('Treatment',"dae20","dae34","dae46","Final_Yield_tHa", "AUDPC_m")]
 
@@
              Y_error_type = "stdev",
-             AUDPC.m = mean(AUDPC),
-             AUDPC.sd = sd(AUDPC),
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment) + fungicide_ai + row_spacing, data = subset(Fogerty_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
@@
              Y_error_type = "stdev",
-             AUDPC.m = mean(AUDPC),
-             AUDPC.sd = sd(AUDPC),
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ 
@@
                        TRUE ~ 62))%>%
-   mutate(meanSq = 
+   mutate(Y_Msquare = 
              case_when(TOS.NUM == 1 ~ anova(lm(Yeild/1000 ~ 
@@
               grain_yield.t.ha. = as.numeric(Herm_19_dat$Yeild)/1000,
-              meanSq = Herm_19_dat$meanSq,
+              Y_Msquare = Herm_19_dat$Y_Msquare,
               AUDPC = Herm_19_dat$AUDPC
@@
              Y_error_type = "stdev",
-             AUDPC.m = mean(AUDPC),
-             AUDPC.sd = sd(AUDPC),
-             Y_Msquare = unique(meanSq)
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+             Y_Msquare = unique(Y_Msquare)
    )

### 2020-01-28 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
correction of code, No planting date in NGA trials were giving NAs

@@
                                         FUN = audpc, 
-                                        dates = c((Goolhi_13_dat$first_sign_disease[1]-7)-
-                                                     Goolhi_13_dat$planting_date[1],
+                                        dates = c(1,
                                                   16,33)
@@
               row_spacing = unique(row_spacing),
-              replicates = sum(replicate),
+              replicates = length(replicate),
               planting_date = unique(planting_date),
@@
               rating_scale = unique(rating_scale),
-              disease_error = sd(PM_final_severity, na.rm = TRUE),
+              #disease_error = sd(PM_final_severity, na.rm = TRUE),
               D_error_type = "stdev",
@@
               raw_graded = NA,
-              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+              #yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
               Y_error_type = "stdev",
@@
 
-#!!!!!!!!!!!!!!!!!! Check to see if errors are calculated
+# For some wierd reason standard deviations are comming back NA in the code above
+# Because of n_treatment being converted to a factor I need to wrangle carefully here
+Goolhi_tmp <- Goolhi_13_dat %>%
+   group_by(n_treatment) %>%
+   summarise(#PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+             disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE))
+
+Goolhi_13_m <- left_join(Goolhi_13_m, Goolhi_tmp)
+
 Goolhi_13_m <- fold_data(Goolhi_13_m, PM_MB_means)
@@
                                         FUN = audpc, 
-                                        dates = c((MarysM_13_dat$first_sign_disease[1]-7)-
-                                                     MarysM_13_dat$planting_date[1],
-                                                  12,12+19)
+                                        dates = c(1,12,12+19)
                                         )
@@
 MarysM_13_m <- MarysM_13_dat %>%
-   group_by(trial_ref, year, location, host_genotype, trial_design, 
-            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
-   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
+   group_by(n_treatment) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             location = unique(location),
+             host_genotype = unique(host_genotype),
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             fungicide_ai = unique(fungicide_ai),
+             dose_ai.ha = unique(dose_ai.ha),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
               plot_width.m. = mean(plot_width, na.rm = TRUE),

### 2020-01-28 index.Rmd
Update metadata in index.Rmd and add files

--- 2019-11-03 index.Rmd
@@
 title: "Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis."
-author: "Paul Melloy, Emerson Del Ponte, Charles T. Gray and Adam H. Sparks"
-date: "`r Sys.Date()`"
-output:
-  bookdown::html_book:
-    theme: united
+author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
+date: "`r format(Sys.time(), '%d %B, %Y')`"
+site: bookdown::bookdown_site
+output: bookdown::gitbook
+documentclass: book
+bibliography: 
+biblio-style: apalike
+link-citations: yes
+github-repo: OpenPlantPathology/Mungbean_PM
+description: "A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew."
 ---

### 2020-01-29 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
AUDPC complete for Hermitage 2011

@@
 ### Hermitage 2011
+#### Define treatments
 ```{r Herm_2011}
@@
 
+```
+
+#### Input trial data  
+```{r Herm11_dataInput}
 Herm_11_dat <- 
@@
               rating_scale = "1-9",
-              grain_yield.t.ha. = Herm_11$`Yld Kg/ha`
-              )
+              grain_yield.t.ha. = Herm_11$`Yld Kg/ha`,
+              stringsAsFactors = FALSE)
+
+```
+
+#### Treatment means
+```{r Herm11_means}
+Herm_11_dat[Herm_11_dat$n_treatment == 5, "n_treatment"] <- 1
+Herm_11_dat[Herm_11_dat$n_treatment == 12, "n_treatment"] <- 8
 
@@
 
+Herm_tmp <- Herm_11_dat %>% 
+   group_by(host_genotype,n_treatment)%>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha./1000, na.rm = TRUE))
+
+Herm_11_m[order(Herm_11_m$n_treatment),"disease_error"] <- Herm_tmp[order(Herm_tmp$n_treatment),"disease_error"]
+Herm_11_m[order(Herm_11_m$n_treatment),"yield_error"] <- Herm_tmp[order(Herm_tmp$n_treatment),"yield_error"]
+
 Herm_11_m <- fold_data(Herm_11_m, PM_MB_means)
@@
 King_11 <- cbind(tmp1, King_11)
-
+```
+
+#### Define treatment data
+```{r King_11_define}
 King_11 <- King_11 %>%
@@
 
+```
+
+#### Input trial data
+```{r King_11_input}
 King_11_dat <- 
@@
               rating_scale = "1-9",
-              grain_yield.t.ha. = as.numeric(King_11$`Yld kg ha`)
+              grain_yield.t.ha. = as.numeric(King_11$`Yld kg ha`),
               #AUDPC = apply(King_11[,c("9 w.a.p.", "11 w.a.p.", "12 w.a.p.", "14 w.a.p.")]-1,1, FUN = audpc, dates = c(9*7,11*7,12*7, 14*7))# -1 to the data because zero disease = 1 on rating scale
-              )
+              stringsAsFactors = FALSE)
 
@@
                      )
-
+```
+
+#### Treatment means  
+```{r King_11_means}
 King_11_m <- King_11_dat %>%
-   group_by(trial_ref, year, location, host_genotype, trial_design, trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
-   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
+   group_by(host_genotype, fungicide_ai,n_treatment) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             trade_name = unique(trade_name),
+             location = unique(location),
+             trial_design = unique(trial_design),
+             dose_ai.ha = unique(dose_ai.ha),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
               plot_width.m. = mean(plot_width, na.rm = TRUE),
@@
               raw_graded = NA,
-              yield_error = sd(grain_yield.t.ha./1000, na.rm = TRUE),
+              #yield_error = sd(grain_yield.t.ha./1000, na.rm = TRUE),
               Y_error_type = "stdev",
@@
 
+# For some wierd reason standard deviations are comming back NA in the code above
+# Because of n_treatment being converted to a factor I need to wrangle carefully here
+King_tmp <- King_11_dat %>%
+   group_by(host_genotype, fungicide_ai,n_treatment) %>%
+   summarise(#PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+             disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha./1000, na.rm = TRUE))
+
+King_11_m <- left_join(King_11_m,King_tmp)
 King_11_m <- fold_data(King_11_m, PM_MB_means)
@@
    King_11_m,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2011/2011 PMmung Herm/2011 PMmung Kingaroy means.csv"
+   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2011/2011 PMmung King/2011 PMmung Kingaroy means.csv"
 )

### 2020-01-29 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
AUDPC code updated for all trials with raw data

@@
 
+```
+
+```{r Herm10_dataInput}
 Herm_10_dat <- 
@@
               rating_scale = "1-9",
-              grain_yield.t.ha. = Herm_10$`Kg/ha`,
+              grain_yield.t.ha. = Herm_10$`Kg/ha`/1000,
               #AUDPC = apply(Herm_10[,c("P.M.9wap","P.M.11wap","P.M.13wap")]-1,1, FUN = audpc, dates = c(9*7,11*7,13*7)), # -1 to the data because zero disease = 1 on rating scale
@@
 
+```
+
+#### Treatment means  
+```{r Herm10_means}
+
 Herm_10_m <- Herm_10_dat %>%
@@
    )
+
+Herm_tentmp <- Herm_10_dat %>% 
+   group_by(host_genotype,n_treatment)%>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE))
+
+Herm_10_m[order(Herm_10_m$n_treatment),"disease_error"] <- Herm_tentmp[order(Herm_tentmp$n_treatment),"disease_error"]
+Herm_10_m[order(Herm_10_m$n_treatment),"yield_error"] <- Herm_tentmp[order(Herm_tentmp$n_treatment),"yield_error"]
 

### 2020-01-29 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Wierd dplyr glitch

@@
               final_assessment = unique(final_assessment),
-              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
               rating_scale = unique(rating_scale),
               disease_error = sd(PM_final_severity, na.rm = TRUE),
+              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
               D_error_type = "stdev",
-              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
               raw_graded = NA,
               yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
               Y_error_type = "stdev",

### 2020-01-29 04_Prep_data.Rmd
Spellcheck
Prep AUDPC data and inspect on plot

@@
 controlY <-
-   mean(dat1[dat1$fungicide == "control", "grain_yield.t.ha."])
+   mean(dat1[dat1$fungicide_ai == "control", "grain_yield.t.ha."])
 
@@
 dat1$prop_YG <- dat1$yield_gain / controlY
-dat1[dat1$fungicide == "control", c("yield_gain", "prop_YG")] <- NA
+dat1[dat1$fungicide_ai == "control", c("yield_gain", "prop_YG")] <- c(NA,NA)
 PM_MB_means[PM_MB_means$trial_ref == "AM1303", ] <- dat1
@@
 
-## Reduce dataset to required variables  
-Lets tidy up the dataset into a data frame of only the variables which are required for the analysis.
+## Reduce data set to required variables  
+Lets tidy up the data set into a data frame of only the variables which are required for the analysis.
 
@@
 ```
+
+```{r Yield_vs_AUDPC}
+
+slimmer_PM_dat %>%
+   filter(AUDPC_m <=280)%>%
+#   filter(fungicide_ai == "control")%>%
+   ggplot(aes(x = grain_yield.t.ha, y = AUDPC_m))+
+   geom_point()
+
+summary(lm(grain_yield.t.ha ~ AUDPC_m, data = subset(slimmer_PM_dat, AUDPC_m <= 280)))
+
+plot(grain_yield.t.ha. ~ AUDPC_m,data = subset(PM_MB_means, AUDPC_m <= 280) )
+abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = subset(PM_MB_means, AUDPC_m <= 280)))
+
+for(i in unique(PM_MB_means$trial_ref)){
+
+   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
+   if(any(is.na(dat1$grain_yield.t.ha.))){next}
+   if(any(is.na(dat1$AUDPC_m))){next}
+
+plot(grain_yield.t.ha. ~ AUDPC_m, data = dat1, main = paste(dat1$location[1],(dat1$year[1])),ylim = c(0,2.5) , xlim = c(0,300))
+abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = dat1))
+points(grain_yield.t.ha. ~ AUDPC_m, data = dat1[dat1$fungicide_ai == "control",], col = "red")
+
+}
+
+```

### 2020-01-29 04_Prep_data.Rmd
Plots of AUDPC and grain yield

@@
 
-for(i in unique(PM_MB_means$trial_ref)){
+sm2lg <- PM_MB_means%>%
+   group_by(trial_ref)%>%
+   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE))%>%
+   arrange(TY)
 
+for(i in sm2lg$trial_ref){
    dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
@@
 
-plot(grain_yield.t.ha. ~ AUDPC_m, data = dat1, main = paste(dat1$location[1],(dat1$year[1])),ylim = c(0,2.5) , xlim = c(0,300))
+plot(grain_yield.t.ha. ~ AUDPC_m, 
+     data = dat1, main = paste(dat1$location[1],(dat1$year[1])),
+     ylim = c(0,max(PM_MB_means$grain_yield.t.ha., na.rm = TRUE)), 
+     xlim = c(0,max(PM_MB_means$AUDPC_m, na.rm = TRUE)))
 abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = dat1))

### 2020-01-29 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Correct AUDPC calculation in Premer

@@
                                         dates = c((Premer_13_dat$first_sign_disease[1]-7)-
-                                                     Premer_13_dat$planting_date[1],
+                                                     as.Date("2013-01-28", format = "%Y-%m-%d"),
                                                   12+19)

### 2020-01-31 05_MetaAnalysis.Rmd
first test of lmer of AUDPC

@@
 library(kableExtra)
+
+# Data
+slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
 ```
@@
 # Meta-analysis
-## Preliminary meta-analysis
+## Grain yield meta-analysis
 
 ```{r LME_slimmer_cluster_disease_mod}
-
-slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
 
@@
 ```
+
+## AUPDC and PM severity meta-analysis
+
+```{r LMER_AUDPC}
+
+Me_mod1 <- lmer(grain_yield.t.ha ~ AUDPC_m + (1|trial),
+              data = slimmer_PM_dat)
+summary(Me_mod1)
+
+Me_mod2 <- lmer(grain_yield.t.ha ~ AUDPC_m + (AUDPC_m|trial),
+              data = slimmer_PM_dat)
+summary(Me_mod2)
+
+anova(Me_mod1, Me_mod2)
+
+```
+
+```{r LMER_finalSev}
+
+Me_mod3 <- lmer(grain_yield.t.ha ~ PM_final_severity + (1|trial),
+              data = slimmer_PM_dat)
+summary(Me_mod3)
+
+Me_mod4 <- lmer(grain_yield.t.ha ~ PM_final_severity + (PM_final_severity|trial),
+              data = slimmer_PM_dat)
+summary(Me_mod4)
+
+anova(Me_mod1, Me_mod2)
+
+```

### 2020-01-31 06_Publication_wireframe_and_8Questions.Rmd
Commencing publication wireframe and response to 8 questions to assist in publication

---
title: Meta-analysis of fungicide application timing for powdery mildew management
  in mungbean.
author: "P. Melloy"
date: "31/01/2020"
output: html_document
---

## Who are the intended readers? - list 3 to 5 of them by name  
   * Adam Sparks – disease modeller  
   * Levente Kiss – Powdery mildew taxonomist  
   * Lisa Kelly – Plant pathologist  
   * Paul MacIntosh – Mungbean/ pulse agronomist  
   * Ross Pomroy – Agronomist  
   * Jean galloway – Plant disease modeller  
   * Art Diggle – Plant disease modeller

## what did you do? (limit - 50 words)
Undertook a meta-analysis of twenty four field trials aimed at improving the efficiency and timing of fungicides for control of powdery mildew on mungbean.

## Why did you do it? (limit - 50 words)  
The unpublished field trial data singularly did not provide a clear indication for when to apply fungicide to best mitigate yield losses from powdery mildew. By analysing the collective data we aim to provide a better estimate for fungicide application timing to mitigate the yield loss from powdery mildew.

## what happened? (limit - 50 words)  
We found that fungicide sprays prior to when the powdery mildew was first spotted in the mungbean crop on average provided the no yield protection. A fungicide spray schedule of one or more fungicide applications commencing within three days of first sign of the disease significantly mitigated yield loss to the disease. However a fungicide spray schedule of 2 or more applications commencing four days or later than first sign of disease saved the most yield.

## What do the results mean in theory? (limit - 50 words)  
Fungicide spray schedules for control of powdery mildew in mungbean should commence around seven to nine days following the first signs of the disease.

## What do the results mean in practice? (limit - 50 words)  
Primarily that fungicide spray scheduales that commence prior to signs of the disease establishing in the mungbean canopy are likely to be ineffective at mitigating the diseses impact on yield. We also don't have data on at what point is starting a fungicide spray scheduale is too late. Growers can't scout thier crop three times a week in the fashion of researchers and are unlikely to identifiy the true date when signs of powdery mildew become apparent. Therefore these results reinforce the message to growers to spray for powdery mildew as soon as it is observed in the crop to protect yields.

## what is the key benefit for your readers? (limit - 25 words).  
This study is the most robust analysis of management of powdery mildew in mungbean using fungicides. It provide a more certain timeframe for growers to plan for when to commence a fungicide spray scheduale.  
Fewer fungicide applications will reduce costs for growers and prolong the efficacy of fungicides before the disease develops resistance.

## What remains unresolved? (no word limit).  
Within the meta-analysis, some comparisons between spray management factors contained fewer replicates in comparison to other spray management factor combinations.  
Only a few studies incorportated in the meta-analysis contained comparisons between the "Late plus" factor and the: negative spray control, a single spray at first sign, and spray at first sign with one or more follow-up applications.

### 2020-02-03 06_Publication_wireframe_and_8Questions.Rmd
Create and use function to replace data which has been recalculated. in this case AUDPC_m ect.

@@
 ## Who are the intended readers? - list 3 to 5 of them by name  
-   * Adam Sparks – disease modeller  
+   * Adam Sparks – disease modeler  
    * Levente Kiss – Powdery mildew taxonomist  
@@
    * Ross Pomroy – Agronomist  
-   * Jean galloway – Plant disease modeller  
+   * Jean Galloway – Plant disease modeller  
    * Art Diggle – Plant disease modeller
@@
 ## What do the results mean in practice? (limit - 50 words)  
-Primarily that fungicide spray scheduales that commence prior to signs of the disease establishing in the mungbean canopy are likely to be ineffective at mitigating the diseses impact on yield.
-We also don't have data on at what point is starting a fungicide spray scheduale is too late.
-Growers can't scout thier crop three times a week in the fashion of researchers and are unlikely to identifiy the true date when signs of powdery mildew become apparent.
+Primarily that fungicide spray schedules that commence prior to signs of the disease establishing in the mungbean canopy are likely to be ineffective at mitigating the diseases impact on yield.
+We also don't have data on at what point is starting a fungicide spray schedule is too late.
+Growers can't scout their crop three times a week in the fashion of researchers and are unlikely to identify the true date when signs of powdery mildew become apparent.
 Therefore these results reinforce the message to growers to spray for powdery mildew as soon as it is observed in the crop to protect yields.
@@
 This study is the most robust analysis of management of powdery mildew in mungbean using fungicides.
-It provide a more certain timeframe for growers to plan for when to commence a fungicide spray scheduale.
+It provide a more certain time frame for growers to plan for when to commence a fungicide spray schedule.
 Fewer fungicide applications will reduce costs for growers and prolong the efficacy of fungicides before the disease develops resistance.
@@
 Within the meta-analysis, some comparisons between spray management factors contained fewer replicates in comparison to other spray management factor combinations.  
-Only a few studies incorportated in the meta-analysis contained comparisons between the "Late plus" factor and the: negative spray control, a single spray at first sign, and spray at first sign with one or more follow-up applications.
+Only a few studies incorporated in the meta-analysis contained comparisons between the "Late plus" factor and the: negative spray control, a single spray at first sign, and spray at first sign with one or more follow-up applications.

### 2020-02-03 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Create and use function to replace data which has been recalculated. in this case AUDPC_m ect.

@@
 }
+
+source("../R/data_mesh.R")
 ```
@@
 Herm_10_dat <- cbind(Herm_10_dat,
-                          AUDPC = apply(data.frame(zero = 1,
+                          AUDPC = apply(data.frame(zero = 0,
                                                    Herm_10[,c("P.M.9wap","P.M.11wap","P.M.13wap")]-1),
@@
 
+source("../R/data_mesh.R")
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Herm_10_m, 
+                            new_data_column = "AUDPC_m", 
+                            ignore_columns = c(6,17,30:46))
+
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Herm_10_m, 
+                            new_data_column = "AUDPC_sd", 
+                            ignore_columns = c(6,17,30:46))
+
 write.csv(
@@
 )
+
+PM_MB_means[PM_MB_means$trial_ref == "mung0910/01",]
+Herm_10_m
 

### 2020-02-03 R/data_mesh.R

@@ -1,0 +1,79 @@
+
+# Searches a dataframe (template_data) based on all columns which are not "ignored".
+#     at the first match the function inserts data entry from the "new_data_column in the 
+#     dataframe new_data into the column with the same name in template_data.
+# returns a dataframe
+
+replace_data <- function(template_data, new_data, new_data_column, ignore_columns = NULL){
+   if(any(colnames(template_data) != colnames(new_data))){warning("columns don't match ")
+      stop()}
+   
+   if(missing(template_data)){warning("\nTemplate data set needed ")
+      stop()}
+   if(missing(new_data)){warning("\nnew_data set needed ")
+      stop()}
+   if(missing(new_data_column)){warning("\nplease specifiy column name ")
+      stop()}
+   
+   template_data <- as.data.frame(template_data)
+   new_data <- as.data.frame(new_data)
+   
+   if(all(new_data_column != colnames(template_data))){warning("\nCan't find index column in template dataset ")
+      stop()}
+   if(class(ignore_columns) == "numeric"){
+      ignore_columns <- colnames(template_data)[ignore_columns]
+   }
+   
+   if(any(colnames(template_data) != colnames(new_data))){warning("\nColumns from data don't match")
+      stop()}
+   
+   if(!is.null(ignore_columns)){
+      if(class(ignore_columns) != "character"){warning("\nignore_columns not a character vector ")
+         
+      }
+      if(any(colnames(template_data) %in% ignore_columns) == FALSE){
+         message(paste("\nNone of the specified columns",ignore_columns,"are included in the template_data "))
+      }   
+     
+      }
+   
+   #specify the columns to match
+   cols1 <- colnames(template_data)[colnames(template_data) %in% c(new_data_column,ignore_columns)]
+   message("\nExcluding columns from match: \n",paste(cols1, collapse = ", "))
+   
+   
+   # subset datasets
+   dat1 <- template_data[,!colnames(template_data) %in% cols1]
+   dat2 <- new_data[,!colnames(new_data) %in% cols1]
+   
+   #iterator1 <- 1
+   report_rows <- vector(mode = "numeric")
+   
+   for(i in 1:dim(dat1)[1]){
+      for(j in 1:dim(dat2)[1]){
+   
+               
+         if(any(is.na(dat1[i,]) != is.na(dat2[j,])) == FALSE){
+            if(all(dat1[i,!is.na(dat1[i,])] == dat2[j,!is.na(dat2[j,])])){
+               
[…]

### 2020-02-03 R/data_mesh.R
Adding some reporting messages

@@ -20,7 +20,7 @@ replace_data <- function(template_data, new_data, new_data_column, ignore_column
    
    if(all(new_data_column != colnames(template_data))){warning("\nCan't find index column in template dataset ")
       stop()}
-   if(class(ignore_columns) == "numeric"){
+   if(is.numeric(ignore_columns)){
       ignore_columns <- colnames(template_data)[ignore_columns]
    }
    
@@ -48,6 +48,7 @@ replace_data <- function(template_data, new_data, new_data_column, ignore_column
    
    #iterator1 <- 1
    report_rows <- vector(mode = "numeric")
+   matched_rows <- vector(mode = "numeric")
    
    for(i in 1:dim(dat1)[1]){
       for(j in 1:dim(dat2)[1]){
@@ -56,8 +57,12 @@ replace_data <- function(template_data, new_data, new_data_column, ignore_column
          if(any(is.na(dat1[i,]) != is.na(dat2[j,])) == FALSE){
             if(all(dat1[i,!is.na(dat1[i,])] == dat2[j,!is.na(dat2[j,])])){
                
+               matched_rows <- c(matched_rows,i)
+               
+               
+               if(template_data[i,new_data_column] == new_data[j,new_data_column]){next()}
                template_data[i,new_data_column] <- new_data[j,new_data_column]
-               j <- j +1 
+               
                report_rows <- c(report_rows,i)
                #message("working")
          
@@ -69,9 +74,10 @@ replace_data <- function(template_data, new_data, new_data_column, ignore_column
    }
    
       
-   if(length(report_rows)==0){message("No data changed")}else{
+   if(length(report_rows)==0){message("No data changed ", 
+                                      length(report_rows),"/",length(matched_rows))}else{
       message("\nRows from template data replaced\n",paste(report_rows, collapse = ", "),
-              "\ntotal replacements = ",length(report_rows))}
+              "\ntotal replacements = ",length(report_rows),"/",length(matched_rows))}
    
 return(template_data)
    }

### 2020-02-04 R/data_mesh.R
Added more reporting messages and warnings to datamesh. Warning if number of rows replaced don't match the replacement rows

@@ -4,7 +4,7 @@
 #     dataframe new_data into the column with the same name in template_data.
 # returns a dataframe
 
-replace_data <- function(template_data, new_data, new_data_column, ignore_columns = NULL){
+replace_data <- function(template_data, new_data, new_data_column, ignore_columns = NULL, trial_ref = NULL){
    if(any(colnames(template_data) != colnames(new_data))){warning("columns don't match ")
       stop()}
    
@@ -15,8 +15,8 @@ replace_data <- function(template_data, new_data, new_data_column, ignore_column
    if(missing(new_data_column)){warning("\nplease specifiy column name ")
       stop()}
    
-   template_data <- as.data.frame(template_data)
-   new_data <- as.data.frame(new_data)
+   template_data <- data.frame(template_data, stringsAsFactors = FALSE)
+   new_data <- as.data.frame(new_data, stringsAsFactors = FALSE)
    
    if(all(new_data_column != colnames(template_data))){warning("\nCan't find index column in template dataset ")
       stop()}
@@ -50,6 +50,68 @@ replace_data <- function(template_data, new_data, new_data_column, ignore_column
    report_rows <- vector(mode = "numeric")
    matched_rows <- vector(mode = "numeric")
    
+   
+   
+   
+   if(is.null(trial_ref) == FALSE){
+      NMC <- vector()
+     if(any(trial_ref %in% unique(template_data$trial_ref))){
+        
+        dat3 <- template_data[template_data$trial_ref == unique(new_data$trial_ref),]
+        
+        for(i2 in 1:length(colnames(template_data))){
+           message(colnames(template_data)[i2], "match = ",
+              unique(template_data[template_data$trial_ref == trial_ref,1]) != unique(King_11_m[,1])
+           )
+           
+        }
+        
+        
+        # for(i1 in colnames(dat3)){
+        #    if(class(dat3[,i1]) == "factor"){
+        #       dat3[,i1] <- as.character(dat3[,i1])
+        #    }
+        #    
+        #    if(length(unique(dat3[,i1])) != length(unique(new_data[,i1]))){
+        #       NMC <- c(NMC,i1)
+        #    }else{
+        #       if(any(unique(dat3[,i1]) != unique(new_data[,i1]))){
+        #          NMC <- c(NMC,i1)
+        #       }}
+        #    }
+        # return(NMC)
+     stop()
+        }
+      
+      for(i in 1:dim(dat1)[1]){
[…]

### 2020-02-04 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Corrected some aspects of the data wrangle. Control rows need to be specified better

@@
 
-PM_MB_means[PM_MB_means$trial_ref == "mung0910/01",]
-Herm_10_m
-
 ```
@@
               PM_final_severity = Herm_11$`P.M. 11  w.a.p.`,
-              AUDPC = apply(data.frame(zero = rep(1,42),
+              AUDPC = apply(data.frame(zero = rep(0,42),
                                        wap11 = Herm_11[,c("P.M. 11  w.a.p.")]-1),1, 
@@
 Herm_11_m <- fold_data(Herm_11_m, PM_MB_means)
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Herm_11_m, 
+                            new_data_column = "AUDPC_m", 
+                            ignore_columns = c(30:46))
+
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Herm_11_m, 
+                            new_data_column = "AUDPC_sd", 
+                            ignore_columns = c(6,17,30:46))
 
@@
 King_11_dat <- cbind(King_11_dat,
-                          AUDPC = apply(data.frame(zero = 1,
+                          AUDPC = apply(data.frame(zero = 0,
                                                    King_11[,c("9 w.a.p.", "11 w.a.p.", 
@@
 King_11_m <- fold_data(King_11_m, PM_MB_means)
+King_11_m <- copy_class(PM_MB_means,King_11_m)
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = King_11_m, 
+                            new_data_column = "AUDPC_m", 
+                            ignore_columns = c(5:10,30:46))
+
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = King_11_m, 
+                            new_data_column = "AUDPC_sd", 
+                            ignore_columns = c(5:10,30:46))
 
@@
 Goolhi_13_dat <- cbind(Goolhi_13_dat,
-                          AUDPC = apply(data.frame(zero = 1,
+                          AUDPC = apply(data.frame(zero = 0,
                                                    Goolhi_13[,c("Inc_16D","Inc_33D")]-1),
@@
 Goolhi_13_m <- fold_data(Goolhi_13_m, PM_MB_means)
-
 Goolhi_13_m <- Goolhi_13_m[Goolhi_13_m$trade_name != "other",]
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Goolhi_13_m, 
+                            new_data_column = "AUDPC_m", 
+                            ignore_columns = c(5:10,30:46))
+
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Goolhi_13_m, 
+                            new_data_column = "AUDPC_sd", 
+                            ignore_columns = c(5:10,30:46))
 
@@
 MarysM_13_dat <- cbind(MarysM_13_dat,
-                          AUDPC = apply(data.frame(zero = 1,
+                          AUDPC = apply(data.frame(zero = 0,
                                                    MarysM_13[,c("Inc_18D","Inc_19D")]-1),
@@
 MarysM_13_m <- fold_data(MarysM_13_m, PM_MB_means)
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = MarysM_13_m, 
+                            new_data_column = "AUDPC_m", 
+                            ignore_columns = c(5:10,30:46))
+
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = MarysM_13_m, 
+                            new_data_column = "AUDPC_sd", 
+                            ignore_columns = c(5:10,30:46))
 
@@
 
-#Premer_13_m <- Premer_13_m[Premer_13_m$trade_name != "other",]
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Premer_13_m, 
+                            new_data_column = "AUDPC_m", 
+                            ignore_columns = c(5:10,30:46))
+
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Premer_13_m, 
+                            new_data_column = "AUDPC_sd", 
+                            ignore_columns = c(5:10,30:46))
 
@@
 Millm_13_dat <- cbind(Millm_13_dat,
-                          AUDPC = apply(data.frame(zero = 1,
+                          AUDPC = apply(data.frame(zero = 0,
                                                    Millm_13[,c("Inc_23D","Inc_42D")]-1),
@@
 Millm_13_m <- fold_data(Millm_13_m, PM_MB_means)
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Millm_13_m, 
+                            new_data_column = "AUDPC_m", 
+                            ignore_columns = c(5:10,30:46))
+
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Millm_13_m, 
+                            new_data_column = "AUDPC_sd", 
+                            ignore_columns = c(5:10,30:46))
 
@@
 
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Herm_15_m, 
+                            new_data_column = "AUDPC_m", 
+                            ignore_columns = c(5:10,30:46))
+
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Herm_15_m, 
+                            new_data_column = "AUDPC_sd", 
+                            ignore_columns = c(5:10,30:46))
+
 write.csv(
@@
 Herm_16_m <- left_join(Herm_16_m,Herm_16.DR)
+
+# dae24 recorded no incidence
 Herm_16_m$AUDPC_m <- apply(Herm_16_m[,c("dae24", "dae38", "dae48", "dae63")]-1,1, 
                             FUN = audpc, dates = c(9,13,23,38))
-Herm_16_m$AUDPC_se <- NA
-
+Herm_16_m$AUDPC_sd <- NA
 Herm_16_m$PM_final_severity <- Herm_16_m$dae63
@@
 Herm_16_m <- fold_data(Herm_16_m, PM_MB_means)
-Herm_16_m <- Herm_16_m[,!colnames(Herm_16_m) %in% c('Treatment',"dae24","dae38","dae48","dae63","Final_Yield_tHa", "AUDPC_m")]
+Herm_16_m <- Herm_16_m[,!colnames(Herm_16_m) %in%
+                          c('Treatment',"dae24","dae38","dae48","dae63","Final_Yield_tHa")]
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Herm_16_m, 
+                            new_data_column = "AUDPC_m", 
+                            ignore_columns = c(5:8,30:46))
 
@@
                             FUN = audpc, dates = c(20,34,46,60))
-King_16_m$AUDPC_se <- NA
+King_16_m$AUDPC_sd <- NA
 
 King_16_m <- fold_data(King_16_m, PM_MB_means)
-King_16_m <- King_16_m[,!colnames(King_16_m) %in% c('Treatment',"dae20","dae34","dae46","Final_Yield_tHa", "AUDPC_m")]
+King_16_m <- King_16_m[,!colnames(King_16_m) %in% c('Treatment',"dae20","dae34","dae46","Final_Yield_tHa")]
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = King_16_m, 
+                            new_data_column = "AUDPC_m", 
+                            ignore_columns = c(5:10,30:46))
 
@@
               first_sign_disease = as.Date("2017-03-07", format = "%Y-%m-%d"),
-              trade_name = as.factor(Fogerty_17_dat$trade_name),
+              trade_name = as.character(Fogerty_17_dat$trade_name),
               fungicide_ai = as.character(Fogerty_17_dat$fungicide_ai),
@@
               , stringsAsFactors = FALSE)
+
+Fogerty_17_dat[Fogerty_17_dat$n_treatment == 1, "fungicide_ai"] <- "control"
+Fogerty_17_dat[Fogerty_17_dat$n_treatment == 1,"dose_ai.ha"] <- 0
+Fogerty_17_dat[Fogerty_17_dat$n_treatment == 1, "trade_name"] <- "control"
+
 ```
@@
 
-Fogerty_17_m[Fogerty_17_m$n_treatment == 1, "fungicide_ai"] <- "control"
-Fogerty_17_m[Fogerty_17_m$n_treatment == 1,"dose_ai.ha"] <- NA_real_
-Fogerty_17_m[Fogerty_17_m$n_treatment == 1, "trade_name"] <- NA
-
 Fogerty_17_m <- fold_data(Fogerty_17_m, PM_MB_means)
-
+Fogerty_17_m <- copy_class(PM_MB_means, Fogerty_17_m)
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Fogerty_17_m, 
+                            new_data_column = "AUDPC_m", 
+                            ignore_columns = c(5:8,10:16,29:46))
+
+PM_MB_means <- replace_data(template_data = PM_MB_means,
+                            new_data = Fogerty_17_m,
+                            new_data_column = "AUDPC_sd",
+                            ignore_columns = c(5:8,10:16,29:46))
+
+dim(Fogerty_17_m)
 write.csv(
@@
               first_sign_disease = as.Date("2017-03-24", format = "%Y-%m-%d"),
-              trade_name = as.factor(Herm_17_dat$trade_name),
+              trade_name = as.character(Herm_17_dat$trade_name),
               fungicide_ai = Herm_17_dat$fungicide_ai,
@@
               rating_scale = "1-9",
-              grain_yield.t.ha. = as.numeric(Herm_17_dat$`Yield.T/Ha`)
+              grain_yield.t.ha. = as.numeric(Herm_17_dat$`Yield.T/Ha`),
                # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
-              )
+              stringsAsFactors = FALSE)
 
 Herm_17_dat <- cbind(Herm_17_dat,
-                          AUDPC = apply(data.frame(zero = 1,
+                          AUDPC = apply(data.frame(zero = 0,
                                                    Herm_17[,c("2017-03-24","I_2/04/2017", "I_11/04/2017", "I_18/04/2017", "I_24/04/2017","I_3/05/2017","I_11/05/2017")]-1),
@@
                           )
-Herm_17_m
+
 ```
@@
 
-Herm_17_m[Herm_17_m$n_treatment == 1, "fungicide_ai"] <- as.factor("control")
-Herm_17_m[Herm_17_m$n_treatment == 1,"dose_ai.ha"] <- NA_real_
-Herm_17_m[Herm_17_m$n_treatment == 1, "trade_name"] <- NA
+Herm_17_m <- data.frame(Herm_17_m)
+Herm_17_m[Herm_17_m$n_treatment == 1, "fungicide_ai"] <- "control"
+Herm_17_m[Herm_17_m$n_treatment == 1,"dose_ai.ha"] <- 0
+Herm_17_m[Herm_17_m$n_treatment == 1, "trade_name"] <- "control"
 
 Herm_17_m <- fold_data(Herm_17_m, PM_MB_means)
+Herm_17_m <- copy_class(PM_MB_means,Herm_17_m)
+
+# COULD NOT GET TO MATCH
+# insert new calculations into data
+# #PM_MB_means <- 
+#    replace_data(template_data = PM_MB_means, 
+#                             new_data = Herm_17_m, 
+#                             new_data_column = "AUDPC_m", 
+#                             ignore_columns = c(4,5,7,8,10:16,29:46))
+# 
+# PM_MB_means <- replace_data(template_data = PM_MB_means,
+#                             new_data = Herm_17_m,
+#                             new_data_column = "AUDPC_sd",
+#                             ignore_columns = c(5:8,10:16,29:46))
+
+Herm_17_m
+PM_MB_means[PM_MB_means$trial_ref == "mung1617/01",]
+
+colnames(PM_MB_means)
 
@@
                        Fung.Trt == 3 ~ 125,
-                       Fung.Trt == 4 ~ NA_real_,
+                       Fung.Trt == 4 ~ 0,
                        TRUE ~ 9999))%>%
@@
 Well_18_dat <- cbind(Well_18_dat,
-                          AUDPC = apply(data.frame(zero = 1,
+                          AUDPC = apply(data.frame(zero = 0,
                                                    Well_18[,c("IR.23-3-18","IR.5-4-18", "IR.11-4-18", "IR.18-4-18","IR.26-4-18","IR.2-5-18")]-1),
@@
 
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Well_18_m, 
+                            new_data_column = "AUDPC_m", 
+                            ignore_columns = c(5:8,10:16,29:46))
+
+PM_MB_means <- replace_data(template_data = PM_MB_means,
+                            new_data = Well_18_m,
+                            new_data_column = "AUDPC_sd",
+                            ignore_columns = c(5:8,10:16,29:46))
+
 write.csv(
@@
    )
-?audpc
+
 # Remove these plots as the results can't be trusted
@@
 PM_MB_19[is.na(PM_MB_19$`1-5-19.Incedence`),"AUDPC"] <- 
-   apply(data.frame(zero = 1,PM_MB_19[is.na(PM_MB_19$`1-5-19.Incedence`) ,c("15-4-19.Incedence", "23-4-19.Incedence")]-1),1,FUN = audpc, dates = c(60, 70,78))
+   apply(data.frame(zero = 0,PM_MB_19[is.na(PM_MB_19$`1-5-19.Incedence`) ,c("15-4-19.Incedence", "23-4-19.Incedence")]-1),1,FUN = audpc, dates = c(60, 70,78))
 ```
@@
    mutate(trade_name = 
-             case_when(`T/ment.NUM` == 4 ~ NA_character_,
+             case_when(`T/ment.NUM` == 4 ~ "control",
                        TRUE ~ "Folicur"))%>%
    mutate(fungicide_ai = 
-             case_when(`T/ment.NUM` == 4 ~ NA_character_,
+             case_when(`T/ment.NUM` == 4 ~ "control",
                        TRUE ~ "tebuconazole"))%>%
@@
    mutate(dose_ai.ha = 
-             case_when(`T/ment.NUM` == 4 ~ NA_real_,
+             case_when(`T/ment.NUM` == 4 ~ 0,
                        TRUE ~ 62))%>%
@@
 
-Herm_19_m
 ```
@@
 
+# insert new calculations into data
+PM_MB_means <- 
+   replace_data(template_data = PM_MB_means, 
+                            new_data = Herm_19_m, 
+                            new_data_column = "AUDPC_m", 
+                            ignore_columns = c(5:8,10:16,29:46))
+
+PM_MB_means <- replace_data(template_data = PM_MB_means,
+                            new_data = Herm_19_m,
+                            new_data_column = "AUDPC_sd",
+                            ignore_columns = c(5:8,10:16,29:46))
+
 write.csv(

### 2020-02-04 copy_class.R
simple function to implement the same column classes from one dataset onto another

@@ -1,0 +1,32 @@
+copy_class <- function(template_data, incompatible_class_data){
+
+#Data Checks
+   if(any(colnames(template_data) != colnames(incompatible_class_data))){
+      warning("columns don't match ")
+      stop()}
+   if(missing(template_data)){warning("\nTemplate data set needed ")
+      stop()}
+   if(missing(incompatible_class_data)){
+      warning("\nincompatible_class_data set needed ")
+      stop()}
+   if(missing(incompatible_class_data)){
+      warning("\nplease specifiy column name ")
+      stop()}
+   
+   template_data <- data.frame(template_data, stringsAsFactors = FALSE)
+   incompatible_class_data <- as.data.frame(incompatible_class_data, stringsAsFactors = FALSE)
+   
+   
+   for(i in colnames(template_data)){
+      col_class <- class(template_data[,i])
+      if(col_class == "factor"){
+         incompatible_class_data[,i] <- as.factor(incompatible_class_data[,i])
+      }else{
+         class(incompatible_class_data[,i]) <- col_class   
+      }
+   }
+
+   
+      
+   return(incompatible_class_data)
+}

### 2020-02-05 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Comment Fogerty17 datareplacement function and insert data over the top

@@
 }
-
+source("../copy_class.R")
 source("../R/data_mesh.R")
@@
 King_11 <- cbind(tmp1, King_11)
+King_11$spray_n <- as.numeric(as.character(King_11$spray_n))
 ```
@@
                             new_data_column = "AUDPC_m", 
-                            ignore_columns = c(5:10,30:46))
+                            ignore_columns = c(5:8,10:16,29:46))
 
@@
 
-sd(MarysM_13_dat[MarysM_13_dat$n_treatment == 9,"grain_yield.t.ha."])
-
 ```
@@
 Premer_13_dat <- cbind(Premer_13_dat,
-                          AUDPC = apply(data.frame(zero = 1,
+                          AUDPC = apply(data.frame(zero = 0,
                                                    Premer_13[,c("Inc_31D")]-1),
@@
 
-Herm_16
 ```
@@
 ### Missen Flats 2017
-```{r Missen2017}
+```{r fog2017}
 # ____________________________________________________________
@@
 
+# could also use gsub to remove Ts
 Fogerty_17$Treatment.No <- as.numeric(unlist(strsplit(
@@
                        Chem.Trt == 3 ~ 60,
-                       TRUE ~ 9999))%>%
+                       TRUE ~ NA_real_))%>%
    mutate(fungicide_application_1 = 
@@
 #### Input trial data
-```{r King16_Trialdat}
-# Remove zeros
+```{r Fog17_Trialdat}
+# Remove zeros because of recording errors (some people recorded zero for no incidence when it should be 1)
 Fogerty_17_dat[Fogerty_17_dat$`2017-03-07` == 0 ,c("2017-03-07")] <- 1
@@
 
-Fogerty_17_dat[Fogerty_17_dat$n_treatment == 1, "fungicide_ai"] <- "control"
-Fogerty_17_dat[Fogerty_17_dat$n_treatment == 1,"dose_ai.ha"] <- 0
-Fogerty_17_dat[Fogerty_17_dat$n_treatment == 1, "trade_name"] <- "control"
-
 ```
@@
 #### Calculating treatment means
-```{r Missen17_means}
+```{r Fog17_means}
 
@@
              AUDPC_sd = sd(AUDPC),
-             Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment) + fungicide_ai + row_spacing, data = subset(Fogerty_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
-   )
+             Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment) + fungicide_ai + row_spacing, 
+                                  data = subset(Fogerty_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
+   )
+
+dim(Fogerty_17_m)
 
@@
 
+Fogerty_17_m[Fogerty_17_m$n_treatment == 1, "fungicide_ai"] <- "control"
+Fogerty_17_m[Fogerty_17_m$n_treatment == 1,"dose_ai.ha"] <- 0
+Fogerty_17_m[Fogerty_17_m$n_treatment == 1, "trade_name"] <- "control"
+
 Fogerty_17_m <- fold_data(Fogerty_17_m, PM_MB_means)
@@
 
+# I have comment out this code because it does not replace the control plots properly
 # insert new calculations into data
-PM_MB_means <- replace_data(template_data = PM_MB_means, 
-                            new_data = Fogerty_17_m, 
-                            new_data_column = "AUDPC_m", 
-                            ignore_columns = c(5:8,10:16,29:46))
-
-PM_MB_means <- replace_data(template_data = PM_MB_means,
-                            new_data = Fogerty_17_m,
-                            new_data_column = "AUDPC_sd",
-                            ignore_columns = c(5:8,10:16,29:46))
-
-dim(Fogerty_17_m)
+# PM_MB_means <-   replace_data(template_data = PM_MB_means, 
+#                             new_data = Fogerty_17_m, 
+#                             new_data_column = "AUDPC_m", 
+#                             ignore_columns = c(5:8,10:16,29:46))
+# 
+# PM_MB_means <- replace_data(template_data = PM_MB_means,
+#                             new_data = Fogerty_17_m,
+#                             new_data_column = "AUDPC_sd",
+#                             ignore_columns = c(5:8,10:16,29:46))
+
+PM_MB_means[PM_MB_means$trial_ref == "mung1617/02",] <- 
+   Fogerty_17_m
+
 write.csv(
@@
 # Calculate area under the disease progress curve
-PM_MB_19$AUDPC <- apply(data.frame(zero = 1,PM_MB_19[,c("15-4-19.Incedence", "23-4-19.Incedence", "1-5-19.Incedence")]-1),1,FUN = audpc, dates = c(60, 70,78,86))
+PM_MB_19$AUDPC <- apply(data.frame(zero = 0,PM_MB_19[,c("15-4-19.Incedence", "23-4-19.Incedence", "1-5-19.Incedence")]-1),1,FUN = audpc, dates = c(60, 70,78,86))
 

### 2020-02-05 05_MetaAnalysis.Rmd
couple of edits corrections

@@
    geom_point(aes(size=1/SE), shape=15)+
-   geom_linerange(aes(ymin = CIinf, ymax = CIsup))+
+   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper))+
    coord_flip()+
@@
 
+coef(Me_mod2)
 ```
 
+Lets compare the area under the disease progress curve (AUDPC) to final severity.
 ```{r LMER_finalSev}
@@
 
-anova(Me_mod1, Me_mod2)
+anova(Me_mod3, Me_mod4)
 
 ```
+
+Final severity as a measurement does not model as well as AUDPC. Also it is less significant of a predictor.

### 2020-02-05 04_Prep_data.Rmd
Adding some reporting messages
add explaination of the sequence of AUDPC x grain yeild graphs

@@
 
+# Calculate AUDPC using final severity and first sign of disease - 7 days
+source("R/AUDPC_for_single_obs.R") 
 ```
@@
 
-head(slim_PM_dat)
 ```
@@
 ```
+
+This sequence of graphs show that AUDPC and disease incidence does not impact on yields if the season is a low yielding, ie lower than 1 tonne per hectare.  
+The higher the yield the greater greater the influence on the disease on the yield especially if the crop is high yielding and a large AUDPC.

### 2020-02-05 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
completion of AUDPC calculations and edits to ensure the correct data is upgraded

@@
    #                          ignore_columns = c(4,5,7,8,10:16,29:46))
-# 
+
 # PM_MB_means <- replace_data(template_data = PM_MB_means,
@@
 #                             ignore_columns = c(5:8,10:16,29:46))
-
-Herm_17_m
-PM_MB_means[PM_MB_means$trial_ref == "mung1617/01",]
-
-colnames(PM_MB_means)
 
@@
 ```
+
+```{r Save_PM_MB_means}
+
+write.csv(PM_MB_means, file = "/data/PM_MB_updated.csv")
+
+```

### 2020-02-05 R/import_data.R
import from the updated collated means file. comment out the original shared file. Collated means file can now be found in the data folder

@@ -17,7 +17,7 @@ x <-
 
 import_data <- function() {
    # x <-
-   #    cloudy::fetch_data(url = "https://usqprd-my.sharepoint.com/:x:/g/personal/u8011054_usq_edu_au/ER13jFzyQqNMq_SEZkNW9NoBiJI8R68dfkKfWXB9wJgETw?e=mylMrZ", 
+   #    cloudy::fetch_data(url = "https://usqprd-my.sharepoint.com/:x:/g/personal/u8011054_usq_edu_au/ER13jFzyQqNMq_SEZkNW9NoBiJI8R68dfkKfWXB9wJgETw?e=mylMrZ",
    #                       file_ext = ".csv")
    x <- read.csv(file = "data/PM_MB_updated.csv")
    x$trial_ref <- as.factor(x$trial_ref)
@@ -27,21 +27,21 @@ import_data <- function() {
    x$trade_name <- as.factor(x$trade_name)
    x$year <- as.factor(x$year)
    x$replicates <- as.numeric(x$replicates)
-   x$planting_date <- as.Date(x$planting_date, format = "%d/%m/%Y")
-   x$emergence_date <- as.Date(x$emergence_date, format = "%d/%m/%Y")
-   x$flowering_date <- as.Date(x$flowering_date, format = "%d/%m/%Y")
-   x$pod_fill_date <- as.Date(x$pod_fill_date, format = "%d/%m/%Y")
-   x$mid_late_pod_fill <- as.Date(x$mid_late_pod_fill, format = "%d/%m/%Y")
-   x$first_sign_disease <- as.Date(x$first_sign_disease, format = "%d/%m/%Y")
-   x$fungicide_application_1 <- as.Date(x$fungicide_application_1, format = "%d/%m/%Y")
-   x$fungicide_application_2 <- as.Date(x$fungicide_application_2, format = "%d/%m/%Y")
-   x$fungicide_application_3 <- as.Date(x$fungicide_application_3, format = "%d/%m/%Y")
-   x$fungicide_application_4 <- as.Date(x$fungicide_application_4, format = "%d/%m/%Y")
-   x$fungicide_application_5 <- as.Date(x$fungicide_application_5, format = "%d/%m/%Y")
-   x$fungicide_application_6 <- as.Date(x$fungicide_application_6, format = "%d/%m/%Y")
-   x$fungicide_application_7 <- as.Date(x$fungicide_application_7, format = "%d/%m/%Y")
[…]

### 2020-02-05 R/slimming_PM_dat.R
removed superflous line of code

@@ -1,7 +1,7 @@
 # This script takes the large dataset and slims it down
 # The slimed down dataset will be used for the Meta-analysis
 
-source("R/import_data.R")
+#source("R/import_data.R")
 # PM_MB_means <- import_data()
 PM_MB_means <- read.csv("data/1911_PM_MB_means&Ygains.csv")
 

### 2020-02-05 R/AUDPC_for_single_obs.R
function to create a AUDPC value from final incidence and first sign of disease

@@ -1,0 +1,29 @@
+# estimating_AUDPC_for_trials with no raw data
+
+
+
+estAUDPC <- PM_MB_means[is.na(PM_MB_means$AUDPC_m) &
+                           !is.na(PM_MB_means$PM_final_severity),]
+
+# are there any entries which don't state the first sign of disease?
+any(is.na(estAUDPC$first_sign_disease)) # No
+
+
+# are there any entries which don't state when they were assessed for disease at the end of the trial
+any(is.na(estAUDPC$final_assessment)) # No
+
+#Good! Lets begin 
+
+estAUDPC$tInf <- as.Date(estAUDPC$final_assessment, format = "%Y-%m-%d") - 
+   as.Date(estAUDPC$first_sign_disease, format = "%Y-%m-%d")
+
+for(i in unique(estAUDPC$trial_ref)){
+   x1 <- apply(data.frame(zero = rep(0, times = length(estAUDPC[estAUDPC$trial_ref == i,"final_assessment"])),
+                          FSev = estAUDPC[estAUDPC$trial_ref == i,"PM_final_severity"]-1),1,
+               FUN = audpc, dates = c(0, unique(estAUDPC[estAUDPC$trial_ref == i,"tInf"])+7)
+   )
+   estAUDPC[estAUDPC$trial_ref == i,"AUDPC_m"] <- x1
+}
+
+PM_MB_means[is.na(PM_MB_means$AUDPC_m) &
+               !is.na(PM_MB_means$PM_final_severity),"AUDPC_m"] <- estAUDPC$AUDPC_m

### 2020-02-07 05_MetaAnalysis.Rmd
Further modelling of AUDPC on grain yield in fungicide management trials.

@@
 ```
+Results show that yields in single early spray treatments are not significantly different to the no spray control.
+Commencing spray manangement schedules at first sign of disease (Recommended), or between 7 - 19 days after first sign (late) produced significantly higher yields compared to the no spray control.
+On average a spray scheduale with two or more applications stating late (7-19 days after first sign of powdery mildew) produced the highest yields.
 
-When we compare these results to those of the linear mixed effect model we notice the metafor model is less certain about the `recommended` and `recommended_plus` treatments.
-Subsequently there is no signiciant difference between the `recommended` and `recommended_plus` treatments and the no spray control.
+When we compare these results to those of the linear mixed effect model there is little difference in the outcome.
+The most noteable difference is the linear mixed-effect model is somewhat less certain about the `Late_plus` treatment, and the mean yield lower than the `recommended_plus` treatment.
 
@@
 
-To make it easier to compare each of the treatments we can compute the contrasts.
+To make it easier to compare each of the treatments we can compute the meta-analysis contrasts.
 ```{r metafor_contrasts}
@@
 ```
-Results show that early applications are not significantly different to the no spray control or the one and two spray management options at the recommended time. Lets view this on a plot.
+Results show with the exclusion of the no spray control, none of the treatments are significantly different, however, early applications treatments on average produced lower yields.
+Lets view this on a plot.
 
@@
 What is interesting here is that the variance in the control has increased while the treatments have decreased.
-This is despite the control being the best represented accross all experiments.
+This is despite the control being the best represented across all experiments.
 However it could also be because it also has a low number of pooled reps per trial.
@@
 Lets analyse the data again using a different statistical approach to see if our outcome with the `metafor` package was robust.
-The netmeta package uses a frequentist approach to the analysis, and focuses on the pairwise comparisons between treatments.
+The `netmeta` package uses a frequentist approach to the analysis, and focuses on the pairwise comparisons between treatments.
 
@@
 
+The `netmeta` analysis suggests the spray scheduale commencing early are no different to any other treatment including the no spray control.
+It estimates the mean is very similar to the recommended treatments.
+The recommended plus and late_plus treatments show higher mean estimates, however not significantly different from the early estimate.
+
 ## AUPDC and PM severity meta-analysis
 
-```{r LMER_AUDPC}
+```{r LM_AUDPC}
+summary(lm(grain_yield.t.ha ~ AUDPC_m, data = slimmer_PM_dat))
 
+```
+
+Area under the disease progress curve (AUDPC) shows no linear relationship with the grain yield data when analysed without respect to any other factor.
+Lets use a mixed effect model which incorporates `trial` as a random effect.
+This makes sense given when we plotted the data subset by trial we could see a better relationship between grain yield and AUDPC.
+
+```{r LMER_AUDPC1}
 Me_mod1 <- lmer(grain_yield.t.ha ~ AUDPC_m + (1|trial),
@@
 summary(Me_mod1)
+```
 
+AUDPC becomes a significant predictor of grain yield when the random effect `trial` is accounted for.
+However we noticed in the plots earlier that not only the intercept but the slope varies depending on the trial.
+Lets see if the model improves when AUDPC is used as a random slope for trial.
+
+```{r LMER_AUDPC2}
 Me_mod2 <- lmer(grain_yield.t.ha ~ AUDPC_m + (AUDPC_m|trial),
               data = slimmer_PM_dat)
-summary(Me_mod2)
-
 anova(Me_mod1, Me_mod2)
 
-coef(Me_mod2)
 ```
+The model is significantly improved, lower AIC and a higher log likelihood.
+
+```{r LMER_AUDPC2_results}
+summary(Me_mod2)
+coef(Me_mod2)[["trial"]][
+   order(coef(Me_mod2)[["trial"]]$AUDPC_m),]
+```
+Here the intercept represents an estimate of the trial yield without the limitation of the disease.
+AUDPC_m shows the slope of the regression for grain yield as AUDPC increases.
+The coefficients of the model (ordered by AUDPC) show that higher yielding trials had a steeper negative slope.
+In other words higher yielding mungbean crops were likely to see greater losses from disease.
 
@@
 
-Final severity as a measurement does not model as well as AUDPC. Also it is less significant of a predictor.
+Powdery mildew incidence at the end of the season was a significant covariate for grain yield, however was a weeker predictor compared to AUDPC.
+
+We shall proceed by including the spray management predictor into the analysis.
+
+```{r AUDPC_spraymanagement}
+Me_mod5 <- lmer(grain_yield.t.ha ~ AUDPC_m + spray_management+ (AUDPC_m|trial),
+              data = slimmer_PM_dat)
+
+Me_mod6 <- lmer(grain_yield.t.ha ~  AUDPC_m : spray_management+ (AUDPC_m|trial),
+              data = slimmer_PM_dat)
+summary(Me_mod6)
+anova(Me_mod2, Me_mod5)
+anova(Me_mod5, Me_mod6)
+
+Me_mod7 <- lmer(grain_yield.t.ha ~  AUDPC_m : spray_management+ (AUDPC_m|trial),
+              data = slimmer_PM_dat)
+
+```

### 2020-02-08 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
correct date input error

@@
               total_fungicide = Herm_16_dat$spray_n,
-              harvest_date = as.Date("2015-05-06", format = "%Y-%m-%d"),
-              final_assessment = as.Date("2015-04-15", format = "%Y-%m-%d"),
+              harvest_date = as.Date("2016-05-06", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2016-04-15", format = "%Y-%m-%d"),
               PM_final_severity = NA,

### 2020-02-11 04_Prep_data.Rmd
Table to show when spray schedules commenced
add agricolae library

@@
 library(ggplot2)
+library(agricolae)
 ```
@@
 
+table(slim_PM_dat$spray_management,slim_PM_dat$fungicide_timing_1)
+
 ```
@@
 The higher the yield the greater greater the influence on the disease on the yield especially if the crop is high yielding and a large AUDPC.
+
+```{r delete_this_chunk}
+PM_MB_means$infected_days <- as.numeric(PM_MB_means$harvest_date - PM_MB_means$first_sign_disease)
+
+plot(AUDPC_m ~ infected_days, data = PM_MB_means)
+plot(grain_yield.t.ha. ~ infected_days, data = PM_MB_means)
+
+PM_MB_means$harvest_date - PM_MB_means$first_sign_disease
+PM_MB_means[0 > as.Date(PM_MB_means$harvest_date, format = "%Y-%m-%d")-
+as.Date(PM_MB_means$first_sign_disease, format = "%Y-%m-%d"),]
+
+# correct dates (this has been done in wrangle file but not updated yet in the data-set)
+PM_MB_means[PM_MB_means$trial_ref == "mung1516/01", "harvest_date"] <- as.Date("2016-05-06", format = "%Y-%m-%d")
+PM_MB_means[PM_MB_means$trial_ref == "mung1516/01", "final_assessment"] <- final_assessment = as.Date("2016-04-15", format = "%Y-%m-%d")
+
+#curiouspw10-
+```

### 2020-02-11 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Plotting some AUDPC curves and calculating some AUDPS

@@
 PM_MB_means <- import_data()
-
 ```
@@
 
+```
+
+#### AUDPC curve
+```{r}
+library(ggplot2)
+
 Herm_10_dat <- cbind(Herm_10_dat,
@@
                                              9*7,11*7,13*7)
-                                        )
-                          )
+                                   ),
+                     AUDPS = apply(data.frame(zero = 0,
+                                                   Herm_10[,c("P.M.9wap","P.M.11wap","P.M.13wap")]-1),
+                                        1, 
+                                        FUN = audps, 
+                                        dates = c((Herm_10_dat$first_sign_disease[1]-7)-
+                                                     Herm_10_dat$planting_date[1],
+                                                  9*7,11*7,13*7)
+                                        )
+                          )
+
+Herm_10$PM_zero <- 1
+Herm_plot <- melt(Herm_10, id.vars = c("Description!","Treat!", "Rep!","Cultivar!","fungicide","total_fungicide"),
+                  measure.vars = c("PM_zero","P.M.9wap","P.M.11wap","P.M.13wap"))
+
+Herm_plot <- Herm_plot %>%
+   mutate(T_var = case_when(variable == "PM_zero" ~ 
+                               as.numeric((Herm_10_dat$first_sign_disease[1]-7) - Herm_10_dat$planting_date[1]),
+                            variable == "P.M.9wap" ~ 9*7,
+                            variable == "P.M.11wap" ~ 11*7,
+                            variable == "P.M.13wap" ~ 13 * 7)
+   )
+Herm_plot$`Treat!` <- as.factor(Herm_plot$`Treat!`)
+Herm_plot %>%
+   ggplot(aes(x = T_var, y = value, color = `Treat!`, shape = `Treat!`))+
+   geom_jitter(width = 1)+
+   geom_smooth()
 
@@
               PM_final_severity = Herm_11$`P.M. 11  w.a.p.`,
-              AUDPC = apply(data.frame(zero = rep(0,42),
-                                       wap11 = Herm_11[,c("P.M. 11  w.a.p.")]-1),1, 
-                            FUN = audpc, dates = c((as.Date("2011-03-28", format = "%Y-%m-%d")-7)- # First sign of disease minus planting date. Gives when there is no disease
-                                                      as.Date("2011-01-24", format = "%Y-%m-%d"),
-                               77)), # -1 to the data because zero disease = 1 on rating scale
+              # AUDPC = apply(data.frame(zero = rep(0,42),
+              #                          wap11 = Herm_11[,c("P.M. 11  w.a.p.")]-1),1, 
+              #               FUN = audpc, dates = c((as.Date("2011-03-28", format = "%Y-%m-%d")-7)- # First sign of disease minus planting date. Gives when there is no disease
+              #                                         as.Date("2011-01-24", format = "%Y-%m-%d"),
+              #                  77)), # -1 to the data because zero disease = 1 on rating scale
               rating_scale = "1-9",
@@
               stringsAsFactors = FALSE)
+
+```
+
+#### AUDPC curve
+```{r}
+
+Herm_11_dat <- cbind(Herm_11_dat,
+                     AUDPC = apply(data.frame(zero = rep(0,42),
+                                       wap11 = Herm_11[,c("P.M. 11  w.a.p.")]-1),1, 
+                            FUN = audpc, dates = c((as.Date("2011-03-28", format = "%Y-%m-%d")-7)- 
+                                                      as.Date("2011-01-24", format = "%Y-%m-%d"),
+                                                   77)
+                     ),
+                     AUDPS = apply(data.frame(zero = rep(0,42),
+                                       wap11 = Herm_11[,c("P.M. 11  w.a.p.")]-1),
+                                        1, 
+                                   FUN = audps, 
+                                        dates = c((as.Date("2011-03-28", format = "%Y-%m-%d")-7)- 
+                                                      as.Date("2011-01-24", format = "%Y-%m-%d"),
+                                                  77)
+                                        )
+                          )
+Herm_11$`P.M. 11  w.a.p.`
+Herm_11$PM_zero <- 1
+Herm11_plot <- melt(Herm_11, id.vars = c("Treatment!", "Cultivar!","Tr","Rep!","fungicide_ai","total_fungicide"),
+                  measure.vars = c("PM_zero","P.M. 11  w.a.p."))
+
+Herm11_plot <- Herm11_plot %>%
+   mutate(T_var = case_when(variable == "PM_zero" ~ 
+                               as.numeric((Herm_11_dat$first_sign_disease[1]-7) - Herm_11_dat$planting_date[1]),
+                            variable == "P.M. 11  w.a.p." ~ 11*7)
+   )
+Herm11_plot$`Treatment!` <- as.factor(Herm11_plot$`Treatment!`)
+Herm11_plot %>%
+   ggplot(aes(x = T_var, y = value, color = `Treatment!`, shape = `Treatment!`))+
+   geom_jitter(width = .5, height = 0.05)+
+   geom_smooth(method = "lm")
 
@@
               stringsAsFactors = FALSE)
+```
+
+#### AUDPC curve
+```{r}
+library(ggplot2)
 
@@
                      AUDPC = apply(data.frame(zero = 0,
-                                                   King_11[,c("9 w.a.p.", "11 w.a.p.", 
-                                                              "12 w.a.p.", "14 w.a.p.")])-1,
+                                              King_11[,c("9 w.a.p.","11 w.a.p.","14 w.a.p.")]-1),
                                    1, 
@@
                                                 King_11_dat$planting_date[1],
-                                           9*7,11*7,12*7, 14*7))
-                     )
+                                             9*7,11*7,14*7)
+                                   ),
+                     AUDPS = apply(data.frame(zero = 0,
+                                                   King_11[,c("9 w.a.p.","11 w.a.p.","14 w.a.p.")]-1),
+                                        1, 
+                                        FUN = audps, 
+                                        dates = c((King_11_dat$first_sign_disease[1]-7)-
+                                                     King_11_dat$planting_date[1],
+                                                  9*7,11*7,14*7)
+                                        )
+                          )
+
+King_11$PM_zero <- 1
+King11_plot <- melt(King_11, id.vars = c("Treatment!","cultivar","rep!","spray_n","fungicide"),
+                  measure.vars = c("PM_zero","9 w.a.p.","11 w.a.p.","14 w.a.p."))
+
+King11_plot <- King11_plot %>%
+   mutate(T_var = case_when(variable == "PM_zero" ~ 
+                               as.numeric((King_11_dat$first_sign_disease[1]-7) - King_11_dat$planting_date[1]),
+                            variable == "9 w.a.p." ~ 9*7,
+                            variable == "11 w.a.p." ~ 11*7,
+                            variable == "14 w.a.p." ~ 14 *7)
+   )
+
+King11_plot$Treat <- paste0(King11_plot$fungicide,King11_plot$spray_n)
+
+King11_plot %>%
+   ggplot(aes(x = T_var, y = value, color = Treat, shape = Treat))+
+   geom_jitter(width = 0.7, height = 0.07)+
+   geom_smooth()
+
 ```
@@
 
-write.csv(PM_MB_means, file = "/data/PM_MB_updated.csv")
-
-```
+write.csv(PM_MB_means, file = "../data/PM_MB_updated.csv")
+
+```

### 2020-02-11 R/import_data.R
Correcting importing data due to bugs from pwd

@@ -13,13 +13,15 @@
 # devtools::install_github("PaulMelloy/cloudy")
 
 
-x <- 
 
 import_data <- function() {
    # x <-
    #    cloudy::fetch_data(url = "https://usqprd-my.sharepoint.com/:x:/g/personal/u8011054_usq_edu_au/ER13jFzyQqNMq_SEZkNW9NoBiJI8R68dfkKfWXB9wJgETw?e=mylMrZ",
    #                       file_ext = ".csv")
-   x <- read.csv(file = "data/PM_MB_updated.csv")
+   if(getwd() == "C:/Users/U8011054/OneDrive - USQ/Cloudstor/R/Mungbean_projects/Mungbean_PM/DataWrangle"){
+      x <- read.csv(file = "../data/PM_MB_updated.csv") 
+   }else{
+   x <- read.csv(file = "data/PM_MB_updated.csv")}
    x$trial_ref <- as.factor(x$trial_ref)
    x$location <- as.factor(x$location)
    x$host_genotype <- as.factor(x$host_genotype)
@@ -47,6 +49,8 @@ import_data <- function() {
    #delete when base data is corrected
    x[x$trial_ref == "mung1516/01", "harvest_date"] <- as.Date("2016-05-06", format = "%Y-%m-%d")
    x[x$trial_ref == "mung1516/01", "final_assessment"] <- as.Date("2016-04-15", format = "%Y-%m-%d")
+   
+   x <- x[,!(colnames(x) == "X")]
    
    return(x)
 }

### 2020-02-11 R/slimming_PM_dat.R
did something here

@@ -2,33 +2,33 @@
 # The slimed down dataset will be used for the Meta-analysis
 
 #source("R/import_data.R")
-# PM_MB_means <- import_data()
-PM_MB_means <- read.csv("data/1911_PM_MB_means&Ygains.csv")
+# PM_MB_Mtemp <- import_data()
+PM_MB_Mtemp <- read.csv("data/1911_PM_MB_means&Ygains.csv")
 
 slim_PM_dat <- data.frame(
-   trial = paste(PM_MB_means$trial_ref, PM_MB_means$year,
-                 PM_MB_means$location,PM_MB_means$host_genotype,
-                 PM_MB_means$row_spacing, sep = "_"),
-   trial_ref = as.character(PM_MB_means$trial_ref),
-   year = as.integer(PM_MB_means$year),
-   location = as.character(PM_MB_means$location),
-   row_spacing = as.double(PM_MB_means$row_spacing),
-   n = as.integer(PM_MB_means$replicates),
-   first_sign_disease = as.Date(PM_MB_means$first_sign_disease, format = "%Y-%m-%d"),
-   fungicide_ai = as.character(PM_MB_means$fungicide_ai),
-   fungicide_application_1 = as.Date(PM_MB_means$fungicide_application_1, format = "%Y-%m-%d"),
-   fungicide_application_2 = as.Date(PM_MB_means$fungicide_application_2, format = "%Y-%m-%d"),
-   fungicide_application_3 = as.Date(PM_MB_means$fungicide_application_3, format = "%Y-%m-%d"),
-   total_fungicide = as.integer(PM_MB_means$total_fungicide),
-   grain_yield.t.ha = as.double(PM_MB_means$grain_yield.t.ha.),
-   yield_error = as.double(PM_MB_means$yield_error),
-   yield_gain = as.double(PM_MB_means$yield_gain),
-   prop_yield_gain = as.double(PM_MB_means$prop_YG),
-   PM_final_severity = as.double(PM_MB_means$PM_final_severity),
-   PM_final_severity_error = as.double(PM_MB_means$disease_error),
-   Y_Msquare = as.double(PM_MB_means$Y_Msquare),
-   AUDPC_m = as.double(PM_MB_means$AUDPC_m),
[…]

### 2020-02-12 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Add code to input AUDPC. Done years 2010-11

@@
               grain_yield.t.ha. = Herm_10$`Kg/ha`/1000,
-              #AUDPC = apply(Herm_10[,c("P.M.9wap","P.M.11wap","P.M.13wap")]-1,1, FUN = audpc, dates = c(9*7,11*7,13*7)), # -1 to the data because zero disease = 1 on rating scale
               stringsAsFactors = FALSE
@@
              AUDPC_sd = sd(AUDPC),
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ host_genotype + factor(n_treatment), data = Herm_10_dat))[2,3],
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ host_genotype + factor(n_treatment), data = Herm_10_dat))[2,3]
+
    )
@@
                             new_data = Herm_10_m, 
-                            new_data_column = "AUDPC_m", 
-                            ignore_columns = c(6,17,30:46))
-
-PM_MB_means <- replace_data(template_data = PM_MB_means, 
-                            new_data = Herm_10_m, 
-                            new_data_column = "AUDPC_sd", 
-                            ignore_columns = c(6,17,30:46))
+                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
+                            #ignore_columns = c(6,17,30:ncol(Herm_10_m))
 
@@
                           )
-Herm_11$`P.M. 11  w.a.p.`
+
 Herm_11$PM_zero <- 1
@@
                                as.numeric((Herm_11_dat$first_sign_disease[1]-7) - Herm_11_dat$planting_date[1]),
-                            variable == "P.M. 11  w.a.p." ~ 11*7)
-   )
+                            variable == "P.M. 11  w.a.p." ~ 11*7))
+
 Herm11_plot$`Treatment!` <- as.factor(Herm11_plot$`Treatment!`)
@@
              AUDPC_sd = sd(AUDPC),
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ host_genotype + factor(n_treatment), 
+                               data = Herm_11_dat[Herm_11_dat$fungicide_ai == "tebuconazole" | 
+                                                        Herm_11_dat$fungicide_ai == "control" ,]))[2,3],
               Y_Msquare = anova(lm(grain_yield.t.ha./1000 ~ factor(n_treatment) + host_genotype, 
@@
                             new_data = Herm_11_m, 
-                            new_data_column = "AUDPC_m", 
-                            ignore_columns = c(30:46))
-
-PM_MB_means <- replace_data(template_data = PM_MB_means, 
-                            new_data = Herm_11_m, 
-                            new_data_column = "AUDPC_sd", 
-                            ignore_columns = c(6,17,30:46))
+                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
 
@@
 #### AUDPC curve
-```{r}
+```{r King11_AUDPC}
 library(ggplot2)
@@
              AUDPC_sd = sd(AUDPC),
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ host_genotype + factor(n_treatment), 
+                               data = King_11_dat[King_11_dat$fungicide_ai == "tebuconazole" | 
+                                                        King_11_dat$fungicide_ai == "control" ,]))[2,3],
               Y_Msquare = anova(lm(grain_yield.t.ha./1000 ~ factor(n_treatment) + host_genotype, 
                                 data = King_11_dat[King_11_dat$fungicide_ai == "tebuconazole" | 
-                                                        King_11_dat$fungicide_ai == "control" ,]))[1,3]
-   )
+                                                        King_11_dat$fungicide_ai == "control" ,]))[1,3])
 
@@
                             new_data = King_11_m, 
-                            new_data_column = "AUDPC_m", 
-                            ignore_columns = c(5:8,10:16,29:46))
-
-PM_MB_means <- replace_data(template_data = PM_MB_means, 
-                            new_data = King_11_m, 
-                            new_data_column = "AUDPC_sd", 
-                            ignore_columns = c(5:10,30:46))
+                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
 
@@
 
+```
+
+#### AUDPC curve
+```{r King11_AUDPC}
 Goolhi_13_dat <- cbind(Goolhi_13_dat,
@@
                                         FUN = audpc, 
-                                        dates = c(1,
-                                                  16,33)
+                                        dates = c(1,16,33)
+                                        ),
+                     AUDPS = apply(data.frame(zero = 0,
+                                                   Goolhi_13[,c("Inc_16D","Inc_33D")]-1),
+                                        1, 
+                                        FUN = audps, 
+                                        dates = c(1,16,33)
                                         )

### 2020-02-12 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Extra calculations for AUDPStairs added, updated for all trials

@@
 #### AUDPC curve
-```{r King11_AUDPC}
+```{r Goolhi13_AUDPC}
 Goolhi_13_dat <- cbind(Goolhi_13_dat,
@@
              AUDPC_sd = sd(AUDPC),
-              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ factor(n_treatment), 
+                               data = Goolhi_13_dat[Goolhi_13_dat$fungicide_ai == "propiconazole" | 
+                                                        Goolhi_13_dat$fungicide_ai == "control" ,]))[1,3],
+              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), 
                                 data = Goolhi_13_dat[Goolhi_13_dat$fungicide_ai == "propiconazole" | 
@@
                             new_data = Goolhi_13_m, 
-                            new_data_column = "AUDPC_m", 
-                            ignore_columns = c(5:10,30:46))
-
-PM_MB_means <- replace_data(template_data = PM_MB_means, 
-                            new_data = Goolhi_13_m, 
-                            new_data_column = "AUDPC_sd", 
-                            ignore_columns = c(5:10,30:46))
+                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
 
@@
 
+```
+
+#### AUDPC curve
+```{r Mary13_AUDPC}
 MarysM_13_dat <- cbind(MarysM_13_dat,
@@
                                         dates = c(1,12,12+19)
-                                        )
-                          )
+                                        ),
+                     AUDPS = apply(data.frame(zero = 0,
+                                                   MarysM_13[,c("Inc_18D","Inc_19D")]-1),
+                                        1, 
+                                        FUN = audps, 
+                                        dates = c(1,12,12+19)
+                                        )
+                          )
+
 ```
@@
              AUDPC_sd = sd(AUDPC),
-              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ factor(n_treatment), 
+                               data = MarysM_13_dat[MarysM_13_dat$fungicide_ai == "propiconazole" | 
+                                                        MarysM_13_dat$fungicide_ai == "control" ,]))[1,3],
+              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), 
                                 data = MarysM_13_dat[MarysM_13_dat$fungicide_ai == "propiconazole" | 
                                                         MarysM_13_dat$fungicide_ai == "control" ,]))[1,3]
-
              )
@@
                             new_data = MarysM_13_m, 
-                            new_data_column = "AUDPC_m", 
-                            ignore_columns = c(5:10,30:46))
-
-PM_MB_means <- replace_data(template_data = PM_MB_means, 
-                            new_data = MarysM_13_m, 
-                            new_data_column = "AUDPC_sd", 
-                            ignore_columns = c(5:10,30:46))
+                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
 
@@
 
+```
+
+#### AUDPC curve
+```{r Prem13_AUDPC}
 Premer_13_dat <- cbind(Premer_13_dat,
@@
                                         FUN = audpc, 
+                                        dates = c((Premer_13_dat$first_sign_disease[1]-7)-
+                                                     as.Date("2013-01-28", format = "%Y-%m-%d"),
+                                                  12+19)
+                                        ),
+                     AUDPS = apply(data.frame(zero = 0,
+                                                           Premer_13[,c("Inc_31D")]-1),
+                                        1, 
+                                        FUN = audps, 
                                         dates = c((Premer_13_dat$first_sign_disease[1]-7)-
@@
              AUDPC_sd = sd(AUDPC),
-              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
+            AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ factor(n_treatment), 
+                               data = Premer_13_dat[Premer_13_dat$fungicide_ai == "propiconazole" | 
+                                                        Premer_13_dat$fungicide_ai == "control" ,]))[1,3],
+              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), 
                                 data = Premer_13_dat[Premer_13_dat$fungicide_ai == "propiconazole" | 
@@
                             new_data = Premer_13_m, 
-                            new_data_column = "AUDPC_m", 
-                            ignore_columns = c(5:10,30:46))
-
-PM_MB_means <- replace_data(template_data = PM_MB_means, 
-                            new_data = Premer_13_m, 
-                            new_data_column = "AUDPC_sd", 
-                            ignore_columns = c(5:10,30:46))
+                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
 
@@
 
+```
+
+#### AUDPC curve
+```{r Mill13_AUDPC}
 Millm_13_dat <- cbind(Millm_13_dat,
@@
                                         dates = c(1,23,42)
-                                        )
-                          )
+                                        ),
+                     AUDPS = apply(data.frame(zero = 0,
+                                                           Millm_13[,c("Inc_23D","Inc_42D")]-1),
+                                        1, 
+                                        FUN = audps, 
+                                        dates = c(1,23,42)
+                                        )
+                          )
+
 ```
@@
              AUDPC_sd = sd(AUDPC),
-             Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ factor(n_treatment), 
+                               data = Millm_13_dat[Millm_13_dat$fungicide_ai == "propiconazole" | 
+                                                        Millm_13_dat$fungicide_ai == "control" ,]))[1,3],
+              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), 
                                 data = Millm_13_dat[Millm_13_dat$fungicide_ai == "propiconazole" | 
@@
                             new_data = Millm_13_m, 
-                            new_data_column = "AUDPC_m", 
-                            ignore_columns = c(5:10,30:46))
-
-PM_MB_means <- replace_data(template_data = PM_MB_means, 
-                            new_data = Millm_13_m, 
-                            new_data_column = "AUDPC_sd", 
-                            ignore_columns = c(5:10,30:46))
+                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
 
@@
               AUDPC = apply(Herm_15_dat[,c("day0", "day1", "day8", "day15","day22")]-1,1, 
-                            FUN = audpc, dates = c(0,1,8,15,22)),# -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
+                            FUN = audpc, 
+                            dates = c(0,1,8,15,22)),
+              # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
+              AUDPS = apply(Herm_15_dat[,c("day0", "day1", "day8", "day15","day22")]-1,1, 
+                            FUN = audps, 
+                            dates = c(0,1,8,15,22)),
               stringsAsFactors = FALSE)
@@
              AUDPC_sd = sd(AUDPC),
-             Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Herm_15_dat))[1,3]
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ factor(n_treatment), 
+                               data = Herm_15_dat))[1,3],
+              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), 
+                                data = Herm_15_dat))[1,3]
    )
@@
                             new_data = Herm_15_m, 
-                            new_data_column = "AUDPC_m", 
-                            ignore_columns = c(5:10,30:46))
-
-PM_MB_means <- replace_data(template_data = PM_MB_means, 
-                            new_data = Herm_15_m, 
-                            new_data_column = "AUDPC_sd", 
-                            ignore_columns = c(5:10,30:46))
+                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
 
@@
              Y_error_type = "stdev",
-             #AUDPC_m = mean(AUDPC),
-             #AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Herm_16_dat))[1,3]
@@
 
-# Mean Disease incidence assessments through the 2016 season
+```
+
+#### Mean disease incidence data
+```{r}
 Herm_16.DR  <-
@@
 names(Herm_16.DR)[1:6] <- c("Treatment", "dae24","dae38","dae48","dae63","Final_Yield_tHa")
-names(Herm_16.DR)[6] <- "Final_Yield_tHa"
-Herm_16.DR$n_treatment <- c(4,3,7,5,2,6,1)
+
+Herm_16.DR <- Herm_16.DR %>%
+   mutate(n_treatment = 
+             case_when(Treatment == "5wk + 2s (3s)" ~ 4,
+                       Treatment == "5wk+1 (2s)" ~ 3,
+                       Treatment == "1/3+1 (2s)" ~ 7,
+                       Treatment == "1st sign (1s)" ~ 5,
+                       Treatment == "5wk (1s)" ~ 2,
+                       Treatment == "1st sign+1 (2s)" ~ 6,
+                       Treatment == "Unsprayed" ~ 1,
+                       TRUE ~ 9999))
 
@@
 Herm_16_m$AUDPC_m <- apply(Herm_16_m[,c("dae24", "dae38", "dae48", "dae63")]-1,1, 
-                            FUN = audpc, dates = c(9,13,23,38))
+                            FUN = audpc, 
+                           dates = c(9,13,23,38))
+
+Herm_16_m$AUDPS_m <- apply(Herm_16_m[,c("dae24", "dae38", "dae48", "dae63")]-1,1, 
+                            FUN = audps, 
+                           dates = c(9,13,23,38))
+
 Herm_16_m$AUDPC_sd <- NA
+Herm_16_m$AUDPS_sd <- NA
 Herm_16_m$PM_final_severity <- Herm_16_m$dae63
-
+Herm_16_m$Inc_Ms <- anova(lm(AUDPC_m ~ factor(n_treatment), data = Herm_16_m))[1,3] #ANOVA F-tests on an essentially perfect fit are unreliable
+
+```
+
+#### Tidy and save data
+```{r Herm16_tidyAndSaveData}
 Herm_16_m <- fold_data(Herm_16_m, PM_MB_means)
@@
 
+#final Yields from disease data different to yield data set
+
 # insert new calculations into data
@@
                             new_data = Herm_16_m, 
-                            new_data_column = "AUDPC_m", 
-                            ignore_columns = c(5:8,30:46))
+                             new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
 
@@
 
-# Mean Disease incidence assessments through the 2016 season
+```
+#### Mean Disease incidence assessments through the 2016 season
+```{r King16_disease}
 King_16.DR  <-
@@
 names(King_16.DR)[1:6] <- c("Treatment", "dae20","dae34","dae46","PM_final_severity","Final_Yield_tHa")
-King_16.DR$n_treatment <- c(3,2,7,6,5,4,1)
+
+King_16.DR <- King_16.DR %>%
+   mutate(n_treatment = 
+             case_when(Treatment == "4wk+2 (3s)" ~ 4,
+                       Treatment == "4wk+1 (2s)" ~ 3,
+                       Treatment == "1/3+1 (2s)" ~ 7,
+                       Treatment == "1st sign (1s)" ~ 5,
+                       Treatment == "4wk (1s)" ~ 2,
+                       Treatment == "1st sign+1 (2s)" ~ 6,
+                       Treatment == "Unsprayed" ~ 1,
+                       TRUE ~ 9999))
 
@@
 King_16_m$AUDPC_m <- apply(King_16_m[,c("dae20", "dae34", "dae46", "PM_final_severity")]-1,1, 
-                            FUN = audpc, dates = c(20,34,46,60))
+                            FUN = audps, dates = c(20,34,46,60))
+King_16_m$AUDPS_m <- apply(King_16_m[,c("dae20", "dae34", "dae46", "PM_final_severity")]-1,1, 
+                            FUN = audps, dates = c(20,34,46,60))
+King_16_m$AUDPS_sd <- NA
 King_16_m$AUDPC_sd <- NA
-
+King_16_m$Inc_Ms <- anova(lm(AUDPC_m ~ factor(n_treatment), 
+                             data = King_16_m))[1,3] #ANOVA F-tests on an essentially perfect fit are unreliable
+```
+
+#### Tidy and save data
+```{r tidyKing16}
 King_16_m <- fold_data(King_16_m, PM_MB_means)
@@
                             new_data = King_16_m, 
-                            new_data_column = "AUDPC_m", 
-                            ignore_columns = c(5:10,30:46))
+                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
 
@@
               grain_yield.t.ha. = as.numeric(Fogerty_17_dat$`Yield.t/ha`),
-              AUDPC = apply(Fogerty_17_dat[,c("2017-03-07", "2017-03-19", "2017-03-24", "2017-04-02","2017-04-10","2017-04-18")]-1,1, 
-                            FUN = audpc, dates = c(1,12,17,26,34,42)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
-              , stringsAsFactors = FALSE)
-
+              AUDPC = apply(Fogerty_17_dat[,c("2017-03-07", "2017-03-19", "2017-03-24",
+                                              "2017-04-02","2017-04-10","2017-04-18")]-1,1, 
+                            FUN = audpc, dates = c(1,12,17,26,34,42)), # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
+              AUDPS = apply(Fogerty_17_dat[,c("2017-03-07", "2017-03-19", "2017-03-24",
+                                              "2017-04-02","2017-04-10","2017-04-18")]-1,1, 
+                            FUN = audps, dates = c(1,12,17,26,34,42)),
+              stringsAsFactors = FALSE)
 ```
@@
              AUDPC_sd = sd(AUDPC),
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ factor(n_treatment) + fungicide_ai + row_spacing, 
+                                  data = subset(Fogerty_17_dat, trade_name != "Custodia")))[1,3], # of only triazoles
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment) + fungicide_ai + row_spacing, 
@@
    )
-
-dim(Fogerty_17_m)
 
@@
 #
-# PM_MB_means <- replace_data(template_data = PM_MB_means,
-#                             new_data = Fogerty_17_m,
-#                             new_data_column = "AUDPC_sd",
-#                             ignore_columns = c(5:8,10:16,29:46))
-
+
+if(all(dim(Fogerty_17_m) == dim(PM_MB_means[PM_MB_means$trial_ref == "mung1617/02",]))){
 PM_MB_means[PM_MB_means$trial_ref == "mung1617/02",] <- 
    Fogerty_17_m
+}else{warning("Dimensions don't match check data")}
 
@@
               grain_yield.t.ha. = as.numeric(Herm_17_dat$`Yield.T/Ha`),
-               # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
               stringsAsFactors = FALSE)
 
-Herm_17_dat <- cbind(Herm_17_dat,
+Herm_17_dat <- cbind(Herm_17_dat,data.frame(
    AUDPC = apply(data.frame(zero = 0,
-                                                   Herm_17[,c("2017-03-24","I_2/04/2017", "I_11/04/2017", "I_18/04/2017", "I_24/04/2017","I_3/05/2017","I_11/05/2017")]-1),
-                                        1, 
+                            Herm_17[,c("2017-03-24","I_2/04/2017", "I_11/04/2017", 
+                                       "I_18/04/2017", "I_24/04/2017","I_3/05/2017","I_11/05/2017")]-1),1, 
                  FUN = audpc, 
@@
                            39,48,57,64,70,79,87)
-                                        )
-                          )
+                 ),
+   AUDPS = apply(data.frame(zero = 0,
+                            Herm_17[,c("2017-03-24","I_2/04/2017", "I_11/04/2017", 
+                                       "I_18/04/2017", "I_24/04/2017","I_3/05/2017","I_11/05/2017")]-1),1, 
+                 FUN = audps, 
+                 dates = c((Herm_17_dat$first_sign_disease[1]-7)-
+                              Herm_17_dat$planting_date[1],
+                           39,48,57,64,70,79,87))
+   ))
 
@@
              AUDPC_sd = sd(AUDPC),
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ 
+                                  factor(n_treatment) + fungicide_ai + row_spacing, 
+                               data = subset(Herm_17_dat, trade_name != "Custodia")))[1,3], # of only triazoles
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ 
@@
    #                          new_data_column = "AUDPC_m",
-   #                          ignore_columns = c(4,5,7,8,10:16,29:46))
+   #                          filter_cols = c("trial_ref","grain_yield.t.ha.","year","location",
+   #                                          "host_genotype","n_treatment", "fungicide_ai","row_spacing"))
 
@@
 #                             ignore_columns = c(5:8,10:16,29:46))
+
+if(all(dim(Herm_17_m) == dim(PM_MB_means[PM_MB_means$trial_ref == "mung1617/01",]))){
+PM_MB_means[PM_MB_means$trial_ref == "mung1617/01",] <- 
+   Herm_17_m
+}else{warning("Dimensions don't match check data")}
 
@@
                                         FUN = audpc, 
+                                        dates = c((Well_18_dat$first_sign_disease[1]-7)-
+                                                     Well_18_dat$planting_date[1],
+                                                  38,51 ,57,64,72,78)
+                                        ),
+                     AUDPS = apply(data.frame(zero = 0,
+                                                   Well_18[,c("IR.23-3-18","IR.5-4-18", "IR.11-4-18", "IR.18-4-18","IR.26-4-18","IR.2-5-18")]-1),
+                                        1, 
+                                        FUN = audps, 
                                         dates = c((Well_18_dat$first_sign_disease[1]-7)-
@@
              AUDPC_sd = sd(AUDPC),
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ 
+                                  factor(n_treatment) + fungicide_ai + row_spacing, 
+                               data = subset(Well_18_dat, trade_name != "Custodia")))[1,3], # of only triazoles
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ 
@@
 Well_18_m <- fold_data(Well_18_m, PM_MB_means)
+Well_18_m <- copy_class(PM_MB_means,Well_18_m)
 
 # insert new calculations into data
-PM_MB_means <- replace_data(template_data = PM_MB_means, 
+#PM_MB_means <- 
+   replace_data(template_data = PM_MB_means, 
                             new_data = Well_18_m, 
-                            new_data_column = "AUDPC_m", 
-                            ignore_columns = c(5:8,10:16,29:46))
+                            new_data_column = c("AUDPC_m", "AUDPC_sd"),#"AUDPS_m", "AUDPS_sd","Inc_Ms"),
+                            filter_cols = c("trial_ref","year","location","n_treatment"))
+
+dim(Well_18_m) ==
+dim(PM_MB_means[PM_MB_means$trial_ref == "mung1718/01",])
+
+   # Not sure why replace data will not replcae the following columns
+   PM_MB_means[c(324: 347),
+               c("AUDPS_m", "AUDPS_sd","Inc_Ms")] <-
+      Well_18_m[,c("AUDPS_m", "AUDPS_sd","Inc_Ms")]
 
@@
 PM_MB_19$AUDPC <- apply(data.frame(zero = 0,PM_MB_19[,c("15-4-19.Incedence", "23-4-19.Incedence", "1-5-19.Incedence")]-1),1,FUN = audpc, dates = c(60, 70,78,86))
+PM_MB_19$AUDPS <- apply(data.frame(zero = 0,PM_MB_19[,c("15-4-19.Incedence", "23-4-19.Incedence", "1-5-19.Incedence")]-1),1,FUN = audps, dates = c(60, 70,78,86))
 
@@
 PM_MB_19[is.na(PM_MB_19$`1-5-19.Incedence`),"AUDPC"] <- 
-   apply(data.frame(zero = 0,PM_MB_19[is.na(PM_MB_19$`1-5-19.Incedence`) ,c("15-4-19.Incedence", "23-4-19.Incedence")]-1),1,FUN = audpc, dates = c(60, 70,78))
+   apply(data.frame(zero = 0,PM_MB_19[is.na(PM_MB_19$`1-5-19.Incedence`),
+                                      c("15-4-19.Incedence", "23-4-19.Incedence")]-1),
+         1,FUN = audpc,
+         dates = c(60, 70,78))
+PM_MB_19[is.na(PM_MB_19$`1-5-19.Incedence`),"AUDPS"] <- 
+   apply(data.frame(zero = 0,PM_MB_19[is.na(PM_MB_19$`1-5-19.Incedence`),
+                                      c("15-4-19.Incedence", "23-4-19.Incedence")]-1),
+         1,FUN = audps, 
+         dates = c(60, 70,78))
 ```
@@
                        TOS.NUM == 2 ~ anova(lm(Yeild/1000 ~ 
+                                  factor(`T/ment.NUM`) , 
+                               data = PM_MB_19[PM_MB_19$TOS.NUM == 2,]))[1,3],
+                       TRUE ~ NA_real_))%>%
+   mutate(Inc_Ms = 
+             case_when(TOS.NUM == 1 ~ anova(lm(AUDPC ~ 
+                                  factor(`T/ment.NUM`) , 
+                               data = PM_MB_19[PM_MB_19$TOS.NUM == 1,]))[1,3],
+                       TOS.NUM == 2 ~ anova(lm(AUDPC ~ 
                                   factor(`T/ment.NUM`) , 
@@
               Y_Msquare = Herm_19_dat$Y_Msquare,
-              AUDPC = Herm_19_dat$AUDPC
+              Inc_Ms = Herm_19_dat$Inc_Ms,
+              AUDPC = Herm_19_dat$AUDPC,
+              AUDPS = Herm_19_dat$AUDPS
               )
@@
              AUDPC_sd = sd(AUDPC),
-             Y_Msquare = unique(Y_Msquare)
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Y_Msquare = unique(Y_Msquare),
+             Inc_Ms = unique(Inc_Ms)
    )
@@
 # insert new calculations into data
-PM_MB_means <- 
-   replace_data(template_data = PM_MB_means, 
-                            new_data = Herm_19_m, 
-                            new_data_column = "AUDPC_m", 
-                            ignore_columns = c(5:8,10:16,29:46))
-
 PM_MB_means <- replace_data(template_data = PM_MB_means, 
                             new_data = Herm_19_m, 
-                            new_data_column = "AUDPC_sd",
-                            ignore_columns = c(5:8,10:16,29:46))
+                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
 

### 2020-02-12 R/data_mesh.R
Some code improvements

@@ -66,15 +66,15 @@ replace_data <- function(template_data, new_data, new_data_column, ignore_column
    
    
    
-   if(is.null(trial_ref) == FALSE){
+   if(is.null(trial_ref) == FALSE){ # this functionality has not been complete, it seems it is an attempt to speed up the function by using the trial_ref to filter the match
       NMC <- vector()
      if(any(trial_ref %in% unique(template_data$trial_ref))){
         
         dat3 <- template_data[template_data$trial_ref == unique(new_data$trial_ref),]
         
-        for(i2 in 1:length(colnames(template_data))){
+        for(i2 in 1:ncol(template_data)){
            message(colnames(template_data)[i2], "match = ",
-              unique(template_data[template_data$trial_ref == trial_ref,1]) != unique(King_11_m[,1])
+              unique(template_data[template_data$trial_ref == trial_ref,1]) != unique(new_data[,1])
            )
            
         }
@@ -125,8 +125,8 @@ replace_data <- function(template_data, new_data, new_data_column, ignore_column
    
    
    
-   for(i in 1:dim(dat1)[1]){
-      for(j in 1:dim(dat2)[1]){
+   for(i in 1:nrow(dat1)){
+      for(j in 1:nrow(dat2)){
    
                
          if(any(is.na(dat1[i,]) != is.na(dat2[j,])) == FALSE){

### 2020-02-12 R/AUDPC_for_single_obs.R
Added AUDPStairs calculations for single observations

@@ -27,3 +27,33 @@ for(i in unique(estAUDPC$trial_ref)){
 
 PM_MB_means[is.na(PM_MB_means$AUDPC_m) &
                !is.na(PM_MB_means$PM_final_severity),"AUDPC_m"] <- estAUDPC$AUDPC_m
+
+#____________________________AUDPStairs________________________________________________
+# estimating_AUDPStairs_for_trials with no raw data
+
+estAUDPS <- PM_MB_means[is.na(PM_MB_means$AUDPS_m) &
+                           !is.na(PM_MB_means$PM_final_severity),]
+
+# are there any entries which don't state the first sign of disease?
+any(is.na(estAUDPS$first_sign_disease)) # No
+
+
+# are there any entries which don't state when they were assessed for disease at the end of the trial
+any(is.na(estAUDPS$final_assessment)) # No
+
+#Good! Lets begin 
+
+estAUDPS$tInf <- as.Date(estAUDPS$final_assessment, format = "%Y-%m-%d") - 
+   as.Date(estAUDPS$first_sign_disease, format = "%Y-%m-%d")
+
+for(i in unique(estAUDPS$trial_ref)){
+   x1 <- apply(data.frame(zero = rep(0, times = length(estAUDPS[estAUDPS$trial_ref == i,"final_assessment"])),
+                          FSev = estAUDPS[estAUDPS$trial_ref == i,"PM_final_severity"]-1),1,
+               FUN = audps, dates = c(0, unique(estAUDPS[estAUDPS$trial_ref == i,"tInf"])+7)
+   )
+   estAUDPS[estAUDPS$trial_ref == i,"AUDPS_m"] <- x1
+}
+
+PM_MB_means[is.na(PM_MB_means$AUDPS_m) &
+               !is.na(PM_MB_means$PM_final_severity),"AUDPS_m"] <- estAUDPS$AUDPS_m
+

### 2020-02-12 04_Prep_data.Rmd
Updated with AUDPStairs

@@
 
+```{r Yield_vs_AUDPS}
+
+slimmer_PM_dat %>%
+   #filter(AUDPC_m <=280)%>%
+#   filter(fungicide_ai == "control")%>%
+   ggplot(aes(x = grain_yield.t.ha, y = AUDPS_m))+
+   geom_point()
+
+summary(lm(grain_yield.t.ha ~ AUDPS_m, data = slimmer_PM_dat, AUDPS_m <= 280))
+
+plot(grain_yield.t.ha. ~ AUDPS_m,data = PM_MB_means)
+abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means))
+
+sm2lg <- PM_MB_means%>%
+   group_by(trial_ref)%>%
+   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE))%>%
+   arrange(TY)
+
+for(i in sm2lg$trial_ref){
+   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
+   if(any(is.na(dat1$grain_yield.t.ha.))){next}
+   if(any(is.na(dat1$AUDPS_m))){next}
+
+plot(grain_yield.t.ha. ~ AUDPS_m, 
+     data = dat1, main = paste(dat1$location[1],(dat1$year[1])),
+     ylim = c(0,max(PM_MB_means$grain_yield.t.ha., na.rm = TRUE)), 
+     xlim = c(0,max(PM_MB_means$AUDPS_m, na.rm = TRUE)))
+abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = dat1))
+points(grain_yield.t.ha. ~ AUDPS_m, data = dat1[dat1$fungicide_ai == "control",], col = "red")
+
+}
+
+```
+
 ```{r delete_this_chunk}
@@
 
-# correct dates (this has been done in wrangle file but not updated yet in the data-set)
-PM_MB_means[PM_MB_means$trial_ref == "mung1516/01", "harvest_date"] <- as.Date("2016-05-06", format = "%Y-%m-%d")
-PM_MB_means[PM_MB_means$trial_ref == "mung1516/01", "final_assessment"] <- final_assessment = as.Date("2016-04-15", format = "%Y-%m-%d")
-
-#curiouspw10-
 ```

### 2020-02-13 05_MetaAnalysis.Rmd
Exploration of lmer analysis where AUDPC is used as a fixed effect moderator to spray_management

@@
 ```
+
 Results show that yields in single early spray treatments are not significantly different to the no spray control.
@@
 ```{r LM_AUDPC}
+library(MuMIn)
+summary(lm(grain_yield.t.ha ~ AUDPC_m, data = slimmer_PM_dat))
+summary(lm(grain_yield.t.ha ~ AUDPS_m, data = slimmer_PM_dat))
+```
+
+Area under the disease progress stairs (AUDPS) shows almost the same fit as the AUDPC linear model.
+
+```{r LMER_AUDPC1}
+Me_mod1 <- lmer(grain_yield.t.ha ~ AUDPC_m + (1|trial),
+              data = slimmer_PM_dat)
+summary(Me_mod1)
+r.squaredGLMM(Me_mod1)
+
+Me_mod1.s <- lmer(grain_yield.t.ha ~ AUDPS_m + (1|trial),
+              data = slimmer_PM_dat)
+summary(Me_mod1.s)
+r.squaredGLMM(Me_mod1)
+r.squaredGLMM(Me_mod1.s)
+anova(Me_mod1,Me_mod1.s)
+```
+
+AUDPC becomes a significant predictor of grain yield when the random effect `trial` is accounted for.
+However we noticed in the plots earlier that not only the intercept but the slope varies depending on the trial.
+Lets see if the model improves when AUDPC is used as a random slope for trial.
+
+```{r LMER_AUDPC2}
+Me_mod2 <- lmer(grain_yield.t.ha ~ AUDPC_m + (AUDPC_m|trial),
+              data = slimmer_PM_dat)
+anova(Me_mod1, Me_mod2)
+
+```
+The model is significantly improved, lower AIC and a higher log likelihood. Lets see if AUDPS improves in the same way.
+
+```{r LMER_AUDPS2}
+Me_mod2.s <- lmer(grain_yield.t.ha ~ AUDPS_m + (AUDPS_m|trial),
+              data = slimmer_PM_dat)
+anova(Me_mod1.s, Me_mod2.s)
+
+```
+The model did improve, however AUDPC still shows a better fit as shown by a lower AIC and a model which converged.
+
+```{r AUDPCvsAUPDS}
+r.squaredGLMM(Me_mod2.s)
+r.squaredGLMM(Me_mod2)
+```
+
+The R-squared of the AUDPC model is a better fit compared to the AUDPS model. From here on we will use AUDPC
+
+Lets compare the area under the disease progress curve (AUDPC) to final severity.
+```{r LMER_finalSev}
+
+Me_mod3 <- lmer(grain_yield.t.ha ~ PM_final_severity + (1|trial),
+              data = slimmer_PM_dat)
+Me_mod4 <- lmer(grain_yield.t.ha ~ PM_final_severity + (PM_final_severity|trial),
+              data = slimmer_PM_dat)
+anova(Me_mod3, Me_mod4)
+
+summary(Me_mod4)
+
+# PM_final_incidence vs AUDPC
+anova(Me_mod4,Me_mod2)
+```
+
+Powdery mildew incidence at the end of the season was a significant covariate for grain yield, however was a weeker predictor compared to AUDPC.
+In fact a model comparison shows AUDPC is significantly better at predicting grain yield.
+We shall proceed by including the spray management predictor into the analysis.  
+First lets assess the `spray_management` variable as an additive fixed effect.
+
+```{r AUDPC_spraymanagement}
+Me_mod5 <- lmer(grain_yield.t.ha ~ AUDPC_m + spray_management+ (AUDPC_m|trial),
+              data = slimmer_PM_dat)
+
+anova(Me_mod2, Me_mod5)
+
+```
+This model is significantly better and shows a lower AIC.
+However makes more sense to use `spray_management` as a interactive term with AUDPC_m.
+As you would assume AUDPC would be dependant on the `spray_management`.
+
+Also there is no reason to include these terms individually in the model to assess their independant effect on grain yield as we know the application of fungicide to mitigate yield loss is aimed at reducing the disease in the crop.
+
+```{r AUDPC:spraymangement}
+Me_mod6 <- lmer(grain_yield.t.ha ~ AUDPC_m : spray_management+ (AUDPC_m|trial),
+              data = slimmer_PM_dat)
+
+anova(Me_mod5, Me_mod6)
+```
+As we would hope this improves out model again.
+Not only do we want to know how much spray_management moderates the effect disease (AUDPC) on yield.
+We might also want to know on average what effect did each of the spray management have on yield.
+
+```{r AUDPCplusspraymangement}
+Me_mod7 <- lmer(grain_yield.t.ha ~ AUDPC_m : spray_management+ spray_management + (AUDPC_m|trial),
+              data = slimmer_PM_dat)
+
+anova(Me_mod6, Me_mod7)
+```
+The model with an additive spray_management term did not significantly improve the model, however we don't need the term in the model to answer our hypothesis.
+We can still determine the effect of spray_management on yields through the interactive AUDPC:spray_management term.
+
+I will try to use the AUDPC:spray_management interative term as a random effect slope to trial, however I think this may overfit the model preventing convergance.
+
+```{r AUDPC:spraymangement}
+Me_mod8 <- lmer(grain_yield.t.ha ~ AUDPC_m : spray_management + (AUDPC_m: spray_management|trial),
+              data = slimmer_PM_dat)
+
+anova(Me_mod6, Me_mod8)
+```
+As expected the model produced an error warning theat the maximum number of evaluations were exceeded.
+Also the model comparisons show that the newer Me_mod7 was not a better model.
+We we proceed with Me_mod6 as the model with the best fit.
+
+```{r LMER_AUDPC2_results}
+summary(Me_mod6)
+coef(Me_mod6)[["trial"]][
+   order(coef(Me_mod6)[["trial"]]$AUDPC_m),]
+```
+The first output shows our random effects do a good job of explaining the variation leaving less residual variation than what is explained by the random intercept, trial.  
+In the fixed effects the intercept gives an estimate of the average yield across all treatments.
+The other fixed effects show the change in predicted yield as AUDPC increases under each of the spray_management factors.
+Spray_management treatments, control, Early, and recommended show significant declines in grain_yields as AUDPC increases.
+Recommended_plus and Late_plus show no significant decline in grain yield as AUDPC increases.
+
+Here the intercept represents an estimate of the trial yield without the limitation of the disease.
+AUDPC_m shows the slope of the regression for grain yield as AUDPC increases.
+The coefficients of the model (ordered by AUDPC) show that higher yielding trials had a steeper negative slope.
+In other words higher yielding mungbean crops were likely to see greater losses from disease.
+
+## AUPDC and PM severity meta-analysis
+
+```{r LM_AUDPC}
 summary(lm(grain_yield.t.ha ~ AUDPC_m, data = slimmer_PM_dat))

### 2020-02-14 05_MetaAnalysis.Rmd
Adding more explaination to the analysis

@@
 ## AUPDC and PM severity meta-analysis
-
+Now it's time to look at how the spray managment scenarios might impact disease pressure on the mungbean yields.
+First lets evaulate which measure of disease is the most robust predictor for yield loss, AUDPC, AUDPS or disease incidence at the end of the season.
 ```{r LM_AUDPC}
@@
 Area under the disease progress stairs (AUDPS) shows almost the same fit as the AUDPC linear model.
+AUDPC and AUDPS are not good predictors of loss in yield overall, without the inclusion of a `trial` parameter.
+Lets test the model with the inclusion of `trial` as a random effect.
 
@@
 
-AUDPC becomes a significant predictor of grain yield when the random effect `trial` is accounted for.
+AUDPC becomes a significant predictor of grain yield when the random effect when accounting for `trial`.
 However we noticed in the plots earlier that not only the intercept but the slope varies depending on the trial.
@@
 ```{r AUDPCvsAUPDS}
-r.squaredGLMM(Me_mod2.s)
-r.squaredGLMM(Me_mod2)
+r.squaredGLMM(Me_mod2.s) # Rsquared for AUDPStairs
+r.squaredGLMM(Me_mod2)# Rsquared for AUDPCurve
 ```
 
-The R-squared of the AUDPC model is a better fit compared to the AUDPS model. From here on we will use AUDPC
+The R-squared of the AUDPC model is a better fit compared to the AUDPS model.  
+> From here on we will use AUDPC.
 
@@
 summary(Me_mod4)
+r.squaredGLMM(Me_mod4)
 
@@
 Powdery mildew incidence at the end of the season was a significant covariate for grain yield, however was a weeker predictor compared to AUDPC.
-In fact a model comparison shows AUDPC is significantly better at predicting grain yield.
+In addition model comparison shows AUDPC is significantly better at predicting grain yield.
+### Spray management and AUDPC
 We shall proceed by including the spray management predictor into the analysis.  
@@
 
-Also there is no reason to include these terms individually in the model to assess their independant effect on grain yield as we know the application of fungicide to mitigate yield loss is aimed at reducing the disease in the crop.
+It is also worth noting there is no reason to include these parameters individually in the model to assess their independant effect on grain yield as we know the application of fungicide to mitigate yield loss is aimed at reducing the disease in the crop.
 
@@
 ```
-As we would hope this improves out model again.
-Not only do we want to know how much spray_management moderates the effect disease (AUDPC) on yield.
-We might also want to know on average what effect did each of the spray management have on yield.
-
-```{r AUDPCplusspraymangement}
-Me_mod7 <- lmer(grain_yield.t.ha ~ AUDPC_m : spray_management+ spray_management + (AUDPC_m|trial),
-              data = slimmer_PM_dat)
-
-anova(Me_mod6, Me_mod7)
-```
-The model with an additive spray_management term did not significantly improve the model, however we don't need the term in the model to answer our hypothesis.
-We can still determine the effect of spray_management on yields through the interactive AUDPC:spray_management term.
 
@@
 ```
-As expected the model produced an error warning theat the maximum number of evaluations were exceeded.
+As expected the model produced an error warning stating the maximum number of evaluations were exceeded.
 Also the model comparisons show that the newer Me_mod7 was not a better model.
@@
 The first output shows our random effects do a good job of explaining the variation leaving less residual variation than what is explained by the random intercept, trial.  
-In the fixed effects the intercept gives an estimate of the average yield across all treatments.
+In the fixed effects the intercept gives an estimate of the average yield across all treatments (1.29 t/Ha).
 The other fixed effects show the change in predicted yield as AUDPC increases under each of the spray_management factors.
@@
 
-Here the intercept represents an estimate of the trial yield without the limitation of the disease.
+The second output is the random effect coeficients.
+Here the intercept represents a yield estimate for each trial without the limitation of the disease.
 AUDPC_m shows the slope of the regression for grain yield as AUDPC increases.
@@
 ## AUPDC and PM severity meta-analysis
-
-```{r LM_AUDPC}
-summary(lm(grain_yield.t.ha ~ AUDPC_m, data = slimmer_PM_dat))
-
-```
-
-Area under the disease progress curve (AUDPC) shows no linear relationship with the grain yield data when analysed without respect to any other factor.
-Lets use a mixed effect model which incorporates `trial` as a random effect.
-This makes sense given when we plotted the data subset by trial we could see a better relationship between grain yield and AUDPC.
-
-```{r LMER_AUDPC1}
-Me_mod1 <- lmer(grain_yield.t.ha ~ AUDPC_m + (1|trial),
-              data = slimmer_PM_dat)
-summary(Me_mod1)
-```
-
-AUDPC becomes a significant predictor of grain yield when the random effect `trial` is accounted for.
-However we noticed in the plots earlier that not only the intercept but the slope varies depending on the trial.
-Lets see if the model improves when AUDPC is used as a random slope for trial.
-
-```{r LMER_AUDPC2}
-Me_mod2 <- lmer(grain_yield.t.ha ~ AUDPC_m + (AUDPC_m|trial),
-              data = slimmer_PM_dat)
-anova(Me_mod1, Me_mod2)
-
-```
-The model is significantly improved, lower AIC and a higher log likelihood.
-
-```{r LMER_AUDPC2_results}
-summary(Me_mod2)
-coef(Me_mod2)[["trial"]][
-   order(coef(Me_mod2)[["trial"]]$AUDPC_m),]
-```
-Here the intercept represents an estimate of the trial yield without the limitation of the disease.
-AUDPC_m shows the slope of the regression for grain yield as AUDPC increases.
-The coefficients of the model (ordered by AUDPC) show that higher yielding trials had a steeper negative slope.
-In other words higher yielding mungbean crops were likely to see greater losses from disease.
-
-Lets compare the area under the disease progress curve (AUDPC) to final severity.
-```{r LMER_finalSev}
-
-Me_mod3 <- lmer(grain_yield.t.ha ~ PM_final_severity + (1|trial),
-              data = slimmer_PM_dat)
-summary(Me_mod3)
-
-Me_mod4 <- lmer(grain_yield.t.ha ~ PM_final_severity + (PM_final_severity|trial),
-              data = slimmer_PM_dat)
-summary(Me_mod4)
-
-anova(Me_mod3, Me_mod4)
-
-```
-
-Powdery mildew incidence at the end of the season was a significant covariate for grain yield, however was a weeker predictor compared to AUDPC.
-
-We shall proceed by including the spray management predictor into the analysis.
-
-```{r AUDPC_spraymanagement}
-Me_mod5 <- lmer(grain_yield.t.ha ~ AUDPC_m + spray_management+ (AUDPC_m|trial),
-              data = slimmer_PM_dat)
-
-Me_mod6 <- lmer(grain_yield.t.ha ~  AUDPC_m : spray_management+ (AUDPC_m|trial),
-              data = slimmer_PM_dat)
-summary(Me_mod6)
-anova(Me_mod2, Me_mod5)
-anova(Me_mod5, Me_mod6)
-
-Me_mod7 <- lmer(grain_yield.t.ha ~  AUDPC_m : spray_management+ (AUDPC_m|trial),
-              data = slimmer_PM_dat)
-
-```

### 2020-02-17 05_MetaAnalysis.Rmd
Remove AUDPC analysis to add to separate file

--- 2020-02-07 05_MetaAnalysis.Rmd
@@
 
-## AUPDC and PM severity meta-analysis
-
-```{r LM_AUDPC}
-summary(lm(grain_yield.t.ha ~ AUDPC_m, data = slimmer_PM_dat))
+```{r Save_meta_data}
+write.csv(slimmer_PM_dat, file = "data/GYmeta_data.csv")
 
 ```
-
-Area under the disease progress curve (AUDPC) shows no linear relationship with the grain yield data when analysed without respect to any other factor.
-Lets use a mixed effect model which incorporates `trial` as a random effect.
-This makes sense given when we plotted the data subset by trial we could see a better relationship between grain yield and AUDPC.
-
-```{r LMER_AUDPC1}
-Me_mod1 <- lmer(grain_yield.t.ha ~ AUDPC_m + (1|trial),
-              data = slimmer_PM_dat)
-summary(Me_mod1)
-```
-
-AUDPC becomes a significant predictor of grain yield when the random effect `trial` is accounted for.
-However we noticed in the plots earlier that not only the intercept but the slope varies depending on the trial.
-Lets see if the model improves when AUDPC is used as a random slope for trial.
-
-```{r LMER_AUDPC2}
-Me_mod2 <- lmer(grain_yield.t.ha ~ AUDPC_m + (AUDPC_m|trial),
-              data = slimmer_PM_dat)
-anova(Me_mod1, Me_mod2)
-
-```
-The model is significantly improved, lower AIC and a higher log likelihood.
-
-```{r LMER_AUDPC2_results}
-summary(Me_mod2)
-coef(Me_mod2)[["trial"]][
-   order(coef(Me_mod2)[["trial"]]$AUDPC_m),]
-```
-Here the intercept represents an estimate of the trial yield without the limitation of the disease.
-AUDPC_m shows the slope of the regression for grain yield as AUDPC increases.
-The coefficients of the model (ordered by AUDPC) show that higher yielding trials had a steeper negative slope.
-In other words higher yielding mungbean crops were likely to see greater losses from disease.
-
-Lets compare the area under the disease progress curve (AUDPC) to final severity.
-```{r LMER_finalSev}
-
-Me_mod3 <- lmer(grain_yield.t.ha ~ PM_final_severity + (1|trial),
-              data = slimmer_PM_dat)
-summary(Me_mod3)
-
-Me_mod4 <- lmer(grain_yield.t.ha ~ PM_final_severity + (PM_final_severity|trial),
-              data = slimmer_PM_dat)
-summary(Me_mod4)
-
-anova(Me_mod3, Me_mod4)
-
-```
-
-Powdery mildew incidence at the end of the season was a significant covariate for grain yield, however was a weeker predictor compared to AUDPC.
-
-We shall proceed by including the spray management predictor into the analysis.
-
-```{r AUDPC_spraymanagement}
-Me_mod5 <- lmer(grain_yield.t.ha ~ AUDPC_m + spray_management+ (AUDPC_m|trial),
-              data = slimmer_PM_dat)
-
-Me_mod6 <- lmer(grain_yield.t.ha ~  AUDPC_m : spray_management+ (AUDPC_m|trial),
-              data = slimmer_PM_dat)
-summary(Me_mod6)
-anova(Me_mod2, Me_mod5)
-anova(Me_mod5, Me_mod6)
-
-Me_mod7 <- lmer(grain_yield.t.ha ~  AUDPC_m : spray_management+ (AUDPC_m|trial),
-              data = slimmer_PM_dat)
-
-```

### 2020-02-17 06_AUDPC_MetaAnalysis.Rmd
Initiate new chapter for AUDPC meta-anlysis

```{r MEsummary_Libraries1, message=FALSE}
# install.packages("tidyverse")
# install.packages("devtools")
# devtools::install_github("https://github.com/PaulMelloy/bomrang")
# devtools::install_github("https://github.com/adamhsparks/theme.usq", dependencies = TRUE)
# install.packages("lme4")

library(RColorBrewer)
library(tidyverse)
library(theme.usq)
library(bomrang)
library(lme4)
library(kableExtra)

# Data
PM_Mdat <- read.csv("data/GYmeta_data.csv")
```

# AUPDC meta-analysis
Now it's time to look at how the spray managment scenarios might impact disease pressure on the mungbean yields. First lets evaulate which measure of disease is the most robust predictor for yield loss, AUDPC, AUDPS or disease incidence at the end of the season.  
```{r LM_AUDPC}
library(MuMIn)
summary(lm(grain_yield.t.ha ~ AUDPC_m, data = PM_Mdat))
summary(lm(grain_yield.t.ha ~ AUDPS_m, data = PM_Mdat))
```

Area under the disease progress stairs (AUDPS) shows almost the same fit as the AUDPC linear model. AUDPC and AUDPS are not good predictors of loss in yield overall, without the inclusion of a `trial` parameter. Lets test the model with the inclusion of `trial` as a random effect.

```{r LMER_AUDPC1}
Me_mod1 <- lmer(grain_yield.t.ha ~ AUDPC_m + (1|trial),
              data = PM_Mdat)
summary(Me_mod1)
r.squaredGLMM(Me_mod1)

Me_mod1.s <- lmer(grain_yield.t.ha ~ AUDPS_m + (1|trial),
              data = PM_Mdat)
summary(Me_mod1.s)
r.squaredGLMM(Me_mod1)
r.squaredGLMM(Me_mod1.s)
anova(Me_mod1,Me_mod1.s)
```

AUDPC becomes a significant predictor of grain yield when the random effect when accounting for `trial`. However we noticed in the plots earlier that not only the intercept but the slope varies depending on the trial. Lets see if the model improves when AUDPC is used as a random slope for trial.

```{r LMER_AUDPC2}
Me_mod2 <- lmer(grain_yield.t.ha ~ AUDPC_m + (AUDPC_m|trial),
              data = PM_Mdat)
anova(Me_mod1, Me_mod2)

```
The model is significantly improved, lower AIC and a higher log likelihood. Lets see if AUDPS improves in the same way.

```{r LMER_AUDPS2}
Me_mod2.s <- lmer(grain_yield.t.ha ~ AUDPS_m + (AUDPS_m|trial),
              data = PM_Mdat)
anova(Me_mod1.s, Me_mod2.s)

```
The model did improve, however AUDPC still shows a better fit as shown by a lower AIC and a model which converged.

```{r AUDPCvsAUPDS}
r.squaredGLMM(Me_mod2.s) # Rsquared for AUDPStairs
r.squaredGLMM(Me_mod2)# Rsquared for AUDPCurve
```

The R-squared of the AUDPC model is a better fit compared to the AUDPS model.  
> From here on we will use AUDPC.

Lets compare the area under the disease progress curve (AUDPC) to final severity.
```{r LMER_finalSev}

Me_mod3 <- lmer(grain_yield.t.ha ~ PM_final_severity + (1|trial),
              data = PM_Mdat)
Me_mod4 <- lmer(grain_yield.t.ha ~ PM_final_severity + (PM_final_severity|trial),
              data = PM_Mdat)
anova(Me_mod3, Me_mod4)

summary(Me_mod4)
r.squaredGLMM(Me_mod4)

# PM_final_incidence vs AUDPC
anova(Me_mod4,Me_mod2)
```

Powdery mildew incidence at the end of the season was a significant covariate for grain yield, however was a weeker predictor compared to AUDPC. In addition model comparison shows AUDPC is significantly better at predicting grain yield.  
### Spray management and AUDPC
We shall proceed by including the spray management predictor into the analysis.  
First lets assess the `spray_management` variable as an additive fixed effect.

```{r AUDPC_spraymanagement}
Me_mod5 <- lmer(grain_yield.t.ha ~ AUDPC_m + spray_management+ (AUDPC_m|trial),
              data = PM_Mdat)

anova(Me_mod2, Me_mod5)

```
This model is significantly better and shows a lower AIC. However makes more sense to use `spray_management` as a interactive term with AUDPC_m. As you would assume AUDPC would be dependant on the `spray_management`.

It is also worth noting there is no reason to include these parameters individually in the model to assess their independant effect on grain yield as we know the application of fungicide to mitigate yield loss is aimed at reducing the disease in the crop.

```{r AUDPC:spraymangement}
Me_mod6 <- lmer(grain_yield.t.ha ~ AUDPC_m : spray_management+ (AUDPC_m|trial),
              data = PM_Mdat)

anova(Me_mod5, Me_mod6)
```

I will try to use the AUDPC:spray_management interative term as a random effect slope to trial, however I think this may overfit the model preventing convergance.

```{r AUDPC:spraymangement}
Me_mod8 <- lmer(grain_yield.t.ha ~ AUDPC_m : spray_management + (AUDPC_m: spray_management|trial),
              data = PM_Mdat)

anova(Me_mod6, Me_mod8)

Me_mod9 <- lmer(grain_yield.t.ha ~ AUDPC_m : spray_management + (1|trial),
              data = PM_Mdat)

anova(Me_mod6, Me_mod8)
anova(Me_mod6, Me_mod9)
```
As expected the model produced an error warning stating the maximum number of evaluations were exceeded. Also the model comparisons show that the newer Me_mod7 was not a better model. We we proceed with Me_mod6 as the model with the best fit.

```{r LMER_AUDPC2_results}
summary(Me_mod6)
coef(Me_mod6)[["trial"]][
   order(coef(Me_mod6)[["trial"]]$AUDPC_m),]

```
The first output shows our random effects do a good job of explaining the variation leaving less residual variation than what is explained by the random intercept, trial.  
In the fixed effects the intercept gives an estimate of the average yield across all treatments (1.29 t/Ha). The other fixed effects show the change in predicted yield as AUDPC increases under each of the spray_management factors. Spray_management treatments, control, Early, and recommended show significant declines in grain_yields as AUDPC increases. Recommended_plus and Late_plus show no significant decline in grain yield as AUDPC increases.

The second output is the random effect coeficients. Here the intercept represents a yield estimate for each trial without the limitation of the disease. AUDPC_m shows the slope of the regression for grain yield as AUDPC increases. The coefficients of the model (ordered by AUDPC) show that higher yielding trials had a steeper negative slope. In other words higher yielding mungbean crops were likely to see greater losses from disease.

## AUPDC impact on grain yield meta-analysis

```{r Metafor-analysis_withAUDPC}
PM_Mdat$AUDPC_log <- log(PM_Mdat$AUDPC_m)

PM_mv_AI <- rma.mv(yi,vi,
                   mods = ~ log(AUDPC_m+1):spray_management,
                   method = "ML",
                   random = list(~ spray_management | trial),
                   struct = "UN",
                   data = PM_Mdat)

summary(PM_mv_AI)

```
```{r}
exp(-0.1196)

```

### 2020-02-17 07_Publication_wireframe_and_8Questions.Rmd
Rename file to maintain order to the book

--- 2020-02-03 06_Publication_wireframe_and_8Questions.Rmd
@@
 ## Who are the intended readers? - list 3 to 5 of them by name  
-   * Adam Sparks – disease modeler  
+   * Adam Sparks – disease modeller  
    * Levente Kiss – Powdery mildew taxonomist  

### 2020-02-17 05_MetaAnalysis.Rmd
edit chunk title

@@
-```{r MEsummary_Libraries1, message=FALSE}
+```{r MEsummary_Libraries2, message=FALSE}
 # install.packages("tidyverse")

### 2020-02-17 03_Preliminary_analysis.Rmd
Formatting

@@
 
+&nbsp;  
+&nbsp;
+
 The primary focus of this research is the effect of fungicide on mitigating yield loss to disease.
@@
 ```
+&nbsp;  
+&nbsp;
 
@@
 There is a small yield effect when applying fungicide and it is unclear how much a second spray improves yield saved. Interestingly Sulphur sprays might be worth investigating when sprayed twice.
+
+&nbsp;  
+&nbsp;
 
@@
 ```
+&nbsp;
 
@@
 
-boxplot(prop_YG ~ dose_ai.ha, data = PM_MB_means[(PM_MB_means$trial_ref == "mung1112/01" |
+boxplot(prop_YG ~ dose_ai.ha, 
+        data = PM_MB_means[(PM_MB_means$trial_ref == "mung1112/01" |
                               PM_MB_means$trial_ref == "mung1112/02") &
@@
 This plot plot, however, indicated the previous plot might be skewed by high yielding trials.
+
+&nbsp;  
+&nbsp;
 
@@
 ```
+
+&nbsp;  
+&nbsp;
 
@@
 
+&nbsp;
+
 #### Genotype yield variability
@@
 Green diamond shows little volatility however this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trials.
+&nbsp;
 
@@
 ```
+
 Jade shows a large amount of volatility, excluding Green Diamond, Crystal shows the next least volatility.
@@
 ```
+
 There is a lot of variation between field trials for Crystal, but little variation within field trials.
@@
 ```
+
 For Jade there is high variation between trials and with in. Perhaps indicating lower tolerance. Lets look at the same plot with data only from no spray controls to see if the variation is the same.
@@
 ```
+
 There seems to be a noticeable shift in the probability curves between the two plots.
@@
 Overall there seems to be an influence of cultivar however this variation is not as distinct as the variation between trials.
+
+&nbsp;
 
@@
 ```{r RS_severity}
-PM_MB_means$fungicide_ai
 # Which row spacing leads to the higher disease severity
@@
 ```{r RS_severity_x_trial}
-PM_MB_means$fungicide_ai
 # Which row spacing leads to the higher disease severity
@@
    theme_usq()+
-   facet_grid(cols = vars(location))
+   facet_grid(cols = vars(location))+
    ggtitle("Powdery mildew variation between different row spacing")
@@
 ```
+
 In the Wellcamp site, wider row spacing reduces PM severity, the other sites it seems there was not enough variation to make a distinction between row spacing treatments.
@@
 ```
+
 The plots seem to imply when yield is limited, presumably by other abiotic factors, there is no effect of row spacing on yield, like in the Hermitage trial.
@@
 Overall row spacing may influence both powdery mildew severity and yield.
+
+&nbsp;  
+&nbsp;
 
@@
 
+&nbsp;  
+&nbsp;
+
 #### Effect of Fungicide 
@@
    coord_flip()
-#theme(axis.text.x = element_text(angle = 30, hjust =.6, vjust = 0.83))
-#scale_x_continuous(limits = c(-0.3,0.6))
 
 ```
+
 There was some hope groups of fungicide could be combined, _i.e._ propiconazole and tebuconazole, however it seems that they have different efficacies.

### 2020-02-17 05_MetaAnalysis.Rmd
Input code from emersons explore markdown

@@
 
+```{r netgraphGW}
+netgraph(net_con, 
+         plastic = FALSE,
+         col = "orange",
+         thickness =  "number.of.studies",
+         points = FALSE, 
+         col.points = "black", 
+         cex.points = 1,
+         number.of.studies = TRUE,
+         cex.number.of.studies = 1,
+         col.number.of.studies = "black",
+         bg.number.of.studies = "orange",
+         multiarm = FALSE,
+         col.multiarm = "lightblue",
+         pos.number.of.studies = 0.5)
+```
+
+```{r}
+netleague(net_con)
+```
+
+```{r}
+decomp.design(net_con)
+```
+
+```{r}
+netsplit(net_con)
+```
+```{r}
+nm1 <- netmeasures(net_con)
+
+plot(nm1$meanpath, nm1$minpar, pch="",
+     xlab="Mean path length", ylab="Minimal parallelism")
+text(nm1$meanpath, nm1$minpar, names(nm1$meanpath), cex=0.8)
+```
+
 ```{r Save_meta_data}

### 2020-02-17 Trial analyses/explore.Rmd
Move explore markdown to trial analyses folder

--- 2019-11-23 explore.Rmd
@@
 ```{r}
+PM_mv1
+
 anova(PM_mv1, L=rbind(c(0,1,-1,0,0), 
@@
 
+results$treat <- factor(results$treat, levels = results$treat[c(1,3,5,4,2)])
+
 results %>%
@@
    geom_point(aes(size = 1/(uci-lci)), shape =15)+
+   scale_size(name = "1/(upper - lower\nconfidence intervals)")+
    geom_errorbar(aes(ymin = lci, ymax = uci), width = 0.1)+
-   coord_flip()
+   scale_x_discrete(labels = c("Late with \n follow spray/s","Recommended with\n follow spray/s","Recommended\n single spray","Early single spray"))+
+   labs(y = "Mean yield difference (t/Ha) relative to no spray control",
+        x = " ") +
+   geom_hline(yintercept = seq(from =  0,to = 0.5, by = 0.1), colour = "grey")+
+   coord_flip()+
+   theme_usq()
 

### 2020-02-17 04_Prep_data.Rmd
add heading
Embarassing spelling error in the TITLE!!!
Formatting and text improvements

@@
+# Prepare data for meta-anlysis
 ## Set environment and import data
@@
               )] <- "control"
+```
 
+Now to view the number break-down of the `spray_management` treatments
+
+```{r tableSprayManagement}
 table(slim_PM_dat$spray_management)
 
+# For each treatment, when were the first fungicide applications made 
+# relative to the first sign of disease
 table(slim_PM_dat$spray_management,slim_PM_dat$fungicide_timing_1)
+```
 
-```
 There are few 'Early_plus' and 'late' treatments, these treatments therefore will have too few comparisons with other treatments in the meta-analysis to be provide accurate results.
@@
 
+&nbsp;  
+&nbsp;  
+&nbsp;
+
+## AUDPC visualise raw data
+
+>How well does 'area under the disease progress curve' (AUDPC) predict grain yield?
+
+and _Does spray_management scenario mitigate yield loss through reducing AUDPC?_
+
+We would expect to see grain yield decline with increasing AUDPC. Lets just plot yield vs AUDPC.
+
 ```{r Yield_vs_AUDPC}
 
-slimmer_PM_dat %>%
-   filter(AUDPC_m <=280)%>%
-#   filter(fungicide_ai == "control")%>%
-   ggplot(aes(x = grain_yield.t.ha, y = AUDPC_m))+
-   geom_point()
+plot(grain_yield.t.ha. ~ AUDPC_m,data = PM_MB_means)
+abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means))
 
-summary(lm(grain_yield.t.ha ~ AUDPC_m, data = subset(slimmer_PM_dat, AUDPC_m <= 280)))
+```
 
-plot(grain_yield.t.ha. ~ AUDPC_m,data = subset(PM_MB_means, AUDPC_m <= 280) )
-abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = subset(PM_MB_means, AUDPC_m <= 280)))
+There appears to be no relationship between the two continuous variables.  
+Does a linear model confirm this?
 
+```{r AUDPClm}
+summary(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means))
+```
+
+There is no relationship as per the linear model.
+
+Perhaps the variation due to trial location, season, row spacing, and other seasonal variables are preventing us from seeing a relationship.
+Lets do the plot again for each trial where there are no missing values.
+Note: The plots are ordered by mean yield of the trial.
+
+```{r AUDPCxTrial}
 sm2lg <- PM_MB_means%>%
@@
 This sequence of graphs show that AUDPC and disease incidence does not impact on yields if the season is a low yielding, ie lower than 1 tonne per hectare.  
-The higher the yield the greater greater the influence on the disease on the yield especially if the crop is high yielding and a large AUDPC.
+The higher the yield the greater greater the influence on the disease on the yield especially if the crop is high yielding with AUDPC also being large enough to reduce yield.
+
+Lets have a look again at the same sequance of graphs and analyses for area under the disease progress _stairs_.
 
 ```{r Yield_vs_AUDPS}
-
-slimmer_PM_dat %>%
-   #filter(AUDPC_m <=280)%>%
-#   filter(fungicide_ai == "control")%>%
-   ggplot(aes(x = grain_yield.t.ha, y = AUDPS_m))+
-   geom_point()
-
-summary(lm(grain_yield.t.ha ~ AUDPS_m, data = slimmer_PM_dat, AUDPS_m <= 280))
-
 plot(grain_yield.t.ha. ~ AUDPS_m,data = PM_MB_means)
 abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means))
+
+summary(lm(grain_yield.t.ha ~ AUDPS_m, data = PM_MB_means))
 
@@
 
-```{r delete_this_chunk}
+```{r delete_this_chunk, eval=FALSE, include=FALSE}
 PM_MB_means$infected_days <- as.numeric(PM_MB_means$harvest_date - PM_MB_means$first_sign_disease)

### 2020-02-17 05_MetaAnalysis.Rmd
Text and formatting improvements

@@
 # install.packages("devtools")
-# devtools::install_github("https://github.com/PaulMelloy/bomrang")
 # devtools::install_github("https://github.com/adamhsparks/theme.usq", dependencies = TRUE)
@@
 ## Grain yield meta-analysis
+
+Lets get started with the analysis by first finding the best model fit that answers our research question.
+
+> Which spray management scenario provides the greatest yield protection from powdery mildew.
+
+   - Grain yield is our response variable.  
+   - Trial, which resolves combinations of categorical variables: year, location, row spacing and cultivar; is set as a random intercept.  
+   - We will test spray management (our treatment) as a fixed effect and random slope to trial.
 
@@
 
+```
+
+The best model from the four above is `m9` with the lower AIC of -29.357.
+
+```{r}
 summary(m9)
-
 ```
@@
 ```
-
+&nbsp;  
+&nbsp;  
 To make it easier to compare each of the treatments we can compute the meta-analysis contrasts.

### 2020-02-21 07_Publication_wireframe_and_8Questions.Rmd
More writing

@@
 ---
+
+# Manuscript wireframe
 
@@
 ## Why did you do it? (limit - 50 words)  
-The unpublished field trial data singularly did not provide a clear indication for when to apply fungicide to best mitigate yield losses from powdery mildew.
+The unpublished field trial data independantly did not provide a clear indication for when to apply fungicide to best mitigate yield losses from powdery mildew.
 By analysing the collective data we aim to provide a better estimate for fungicide application timing to mitigate the yield loss from powdery mildew.
@@
 ## what happened? (limit - 50 words)  
-We found that fungicide sprays prior to when the powdery mildew was first spotted in the mungbean crop on average provided the no yield protection.
+We found that fungicide sprays prior to when the powdery mildew was first spotted in the mungbean crop on average provided no yield protection.
 A fungicide spray schedule of one or more fungicide applications commencing within three days of first sign of the disease significantly mitigated yield loss to the disease.
@@
 Only a few studies incorporated in the meta-analysis contained comparisons between the "Late plus" factor and the: negative spray control, a single spray at first sign, and spray at first sign with one or more follow-up applications.
+
+# Manuscript
+
+## Introduction  
+Mungbean is a short season summer pulse crop which can provide a high returns for growers in eastern Australia.
+Mungbean can potentially yield up to 2.3 tonnes per hectare, and worth up to \$ 1300 a tonne [AgMargins; 2019](https://agmargins.net.au/Reports/Details/fced3a80-a762-481c-b812-9953e33410e6).
+Powdery mildew _Podosphaera xanthii_ can potentially cause yield losses on mungbean of up to 43%.
+Fortunatley a number of strategies are employed to reduce the damage powdery mildew inflicts on yields.
+### Managements strategies  
+#### and conditions for infection  
+Powdery mildew infection requires cool temperatures (22$^\circ$ - 26$^\circ$C) and a leaf surface that is not overly wet for infection [Kelly et.
+al 2017](https://grdc.com.au/resources-and-publications/grdc-update-papers/tab-content/grdc-update-papers/2017/07/mungbean-and-sorghum-disease-update).
+In southern Queensland and northern New South Wales, planting dates between late spring (November) and mid-summer (January) are advised to avoid the conducsive cooler autumn temperatures which normally commence in March in the southern hemisphere conducive for powdery mildew establishment.
+Signs of powdery mildew are almost always first observed when temperatures start to cool.
+
+### Fungicide resistance
+Lucritive returns of \$ 2260 over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than they are needed.
+
+### Previous studies
+
+### Meta-analyes
+
+### Aims
+
+## Materials and methods

### 2020-02-22 02_Weather.Rmd
Use lubridate

@@
 
-Below I am plotting the mean maximum temperatures over 7 days during the growing season at each mungbean trial site.
-The vertical lines indicate when powdery mildew was first observed in that season.
-Variation may exist in the sowing date of each trial.
+Below I am plotting the mean maximum temperatures over 7 days during the growing
+season at each mungbean trial site.
+The vertical lines indicate when powdery mildew was first observed in that
+season. Variation may exist in the sowing date of each trial.
 
@@
 library(dplyr)
+library(lubridate)
 source("R/import_data.R")
-PM.dat <- import_data()  # importing means yield and disease severity for each treatment within each powdery mildew trial on mungbean
+PM.dat <-
+   import_data()  # importing means yield and disease severity for each treatment within each powdery mildew trial on mungbean
 source("R/year2day.r")
@@
 
-# Add columns for Year and date to data
-king_Tm_aver$year <- substr(king_Tm_aver$date, start = 1, stop = 4)
-king_Tm_aver$day <- sapply(king_Tm_aver$date,year2day)
+# Add columns for year and day of year to data
+king_Tm_aver$year <- year(king_Tm_aver$date)
+king_Tm_aver$day <- yday(king_Tm_aver$date)
 
@@
 PM.dat_sum <- as.data.frame(do.call(rbind,
-                   by(PM.dat, PM.dat$trial_ref, function(x){
-                      c(location = unique(as.character(x$location)),
+                                    by(PM.dat, PM.dat$trial_ref, function(x) {
+                                       c(
+                                          location = unique(as.character(x$location)),
                                           year = unique(as.character(x$year)),
                                           first_sign = unique(as.character(x$first_sign_disease)),
-                        day = as.numeric(unique(sapply(x$first_sign_disease,year2day))))
-                   }
-                      )), stringsAsFactors = FALSE)
+                                          day = as.numeric(unique(
+                                             sapply(x$first_sign_disease, year2day)
+                                          ))
+                                       )
+                                    })), stringsAsFactors = FALSE)
 
-King_FS <- PM.dat_sum[PM.dat_sum$location == "Kingaroy",]
+King_FS <- PM.dat_sum[PM.dat_sum$location == "Kingaroy", ]
 King_FS$day <- as.numeric(King_FS$day)
 
-king_Tm_aver[king_Tm_aver$year == "2002"|
-                king_Tm_aver$year == "2010"|
-                king_Tm_aver$year == "2011"|
-                king_Tm_aver$year == "2012"|
-                king_Tm_aver$year == "2016", ] %>%
+king_Tm_aver[king_Tm_aver$year == "2002" |
+                king_Tm_aver$year == "2010" |
+                king_Tm_aver$year == "2011" |
+                king_Tm_aver$year == "2012" |
+                king_Tm_aver$year == "2016",] %>%
    ggplot(aes(x = day)) +
@@
    geom_area(aes(y = daily_rain, fill = year), alpha = 0.5) +
-   scale_y_continuous(limits = c(0, 40),sec.axis = dup_axis(name = "Rainfall (mm)"))
+   scale_y_continuous(limits = c(0, 40),
+                      sec.axis = dup_axis(name = "Rainfall (mm)"))
 ```

### 2020-02-22 02_Weather.Rmd

@@
 silo_emerald_Tmax <- read.csv("./data/silo_emerald_Tmax.csv")
+
 ```
@@
                 king_Tm_aver$year == "2016",] %>%
+
+# Create data subset of powdery mildew data means for the first sign of the disease by location
+PM.dat_sum <- as.data.frame(do.call(rbind,
+                   by(PM.dat, PM.dat$trial_ref, function(x){
+                      c(location = unique(as.character(x$location)),
+                        year = unique(as.character(x$year)),
+                        first_sign = unique(as.character(x$first_sign_disease)),
+                        day = as.numeric(unique(sapply(x$first_sign_disease,year2day))))
+                   }
+                      )), stringsAsFactors = FALSE)
+
+King_FS <- PM.dat_sum[PM.dat_sum$location == "Kingaroy",]
+King_FS$day <- as.numeric(King_FS$day)
+
+king_Tm_aver[king_Tm_aver$year == "2002"|
+                king_Tm_aver$year == "2010"|
+                king_Tm_aver$year == "2011"|
+                king_Tm_aver$year == "2012"|
+                king_Tm_aver$year == "2016", ] %>%
    ggplot(aes(x = day)) +

### 2020-02-22 R/import_data.R
Clean up import_data()

@@ -3,25 +3,19 @@
 #'
 #' Imports mungbean powdery mildew data and formats columns correctly.
 #'
-#' @return a Tibble of mungbean powdery mildew trial data
+#' @return a `data.frame` of mungbean powdery mildew trial data
 #'
 #' @examples
 #'
 #' PM_MB_means <- import_data()
 #'
 
-# devtools::install_github("PaulMelloy/cloudy")
-
-
-
 import_data <- function() {
-   # x <-
-   #    cloudy::fetch_data(url = "https://usqprd-my.sharepoint.com/:x:/g/personal/u8011054_usq_edu_au/ER13jFzyQqNMq_SEZkNW9NoBiJI8R68dfkKfWXB9wJgETw?e=mylMrZ",
-   #                       file_ext = ".csv")
-   if(getwd() == "C:/Users/U8011054/OneDrive - USQ/Cloudstor/R/Mungbean_projects/Mungbean_PM/DataWrangle"){
-      x <- read.csv(file = "../data/PM_MB_updated.csv") 
-   }else{
-   x <- read.csv(file = "data/PM_MB_updated.csv")}
+   if (getwd() == "C:/Users/U8011054/OneDrive - USQ/Cloudstor/R/Mungbean_projects/Mungbean_PM/DataWrangle") {
+      x <- read.csv(file = "../data/PM_MB_updated.csv")
+   } else{
+      x <- read.csv(file = "data/PM_MB_updated.csv")
+   }
    x$trial_ref <- as.factor(x$trial_ref)
    x$location <- as.factor(x$location)
    x$host_genotype <- as.factor(x$host_genotype)
@@ -30,32 +24,45 @@ import_data <- function() {
    x$year <- as.factor(x$year)
    x$replicates <- as.numeric(x$replicates)
    x$planting_date <- as.Date(x$planting_date, format = "%Y-%m-%d")
-   x$emergence_date <- as.Date(x$emergence_date, format = "%Y-%m-%d")
-   x$flowering_date <- as.Date(x$flowering_date, format = "%Y-%m-%d")
+   x$emergence_date <-
+      as.Date(x$emergence_date, format = "%Y-%m-%d")
+   x$flowering_date <-
+      as.Date(x$flowering_date, format = "%Y-%m-%d")
    x$pod_fill_date <- as.Date(x$pod_fill_date, format = "%Y-%m-%d")
[…]

### 2020-02-22 01_Meta-analysis_experiments.Rmd
Line breaks, location formatting, use cache dir

@@
 
-This meta-analysis uses data collected by a number of researchers from the Department of Agriculture and Primary Industries and the University of Southern Queensland.
-It is worth noting Malcolm Riley and Dr Sue Thompsons effort in establishing and coordinating early field trials between 2010 and 2016.
+This meta-analysis uses data collected by a number of researchers from the
+Department of Agriculture and Primary Industries and the University of Southern
+Queensland. It is worth noting Professor Malcolm Riley and Dr Sue Thompson's
+effort in establishing and coordinating early field trials between 2010 and
+2016.
 
@@
    + Millmerran   
-   + Mt Mary   
+   + Marys Mount  
    + Goolhi
@@
 Trial data were obtained from a non-published manuscript.  
-Ratings for powdery mildew were on a 1-5 rating scale and can be read in the file "Powdery mildew paper#1.doc".  
-Comparing trials which have not used the same rating scale will be done using a percentage change.
+Ratings for powdery mildew were on a 1-5 rating scale and can be read in the
+file "Powdery mildew paper#1.doc". Comparing trials which have not used the same
+rating scale will be done using a percentage change.
 
 **2013 Field trials**  
-Trials were conducted by the National Growers Alliance (NGA).
-The raw data were obtained from Lawrie Price.
-NGA data were formatted to be compliant with existing data rating and scales in the R script `Cleaning historical data.R`.
+Trials were conducted by the National Growers Alliance (NGA). The raw data were
+obtained from Lawrie Price. NGA data were formatted to be compliant with
+existing data rating and scales in the R script `Cleaning historical data.R`.
 
@@
    6. Colonies in lower 2/3 of canopy, 100% of plants affected  
-   7. Colonies in lower 2/3 of canopy of 100% of plants, some plants with colonies also in top 1/3 of canopy  
+   7. Colonies in lower 2/3 of canopy of 100% of plants, some plants with
+   colonies also in top 1/3 of canopy  
    8. Colonies to top of plant with >75% of plants affected  
@@
    ),
-   lat = c(-28.215 , -26.58, -27.56, -23.54, -27.51666, -31.43449, -27.923674, -31.0142, -31.00246, -27.905313, -27.564277),
-   lon = c(152.1003, 151.83, 152.32, 148.19, 151.450,150.0052, 151.242706, 150.05018, 149.82507, 151.9772,151.867879)
+   lat = c(
+      -28.215 ,
+      -26.58,
+      -27.56,
+      -23.54,
+      -27.51666,
+      -31.43449,
+      -27.923674,
+      -31.0142,
+      -31.00246,
+      -27.905313,
+      -27.564277
+   ),
+   lon = c(
+      152.1003,
+      151.83,
+      152.32,
+      148.19,
+      151.450,
+      150.0052,
+      151.242706,
+      150.05018,
+      149.82507,
+      151.9772,
+      151.867879
+   )
 )
 
-write.csv(experiment_sites,"data/Mungbean_experiment_sites.csv", row.names = FALSE)
+write.csv(experiment_sites,
+          "data/Mungbean_experiment_sites.csv",
+          row.names = FALSE)
 
@@
    addProviderTiles("Esri.WorldTopoMap") %>%
-   setView(lat = -27.31, lng = 150.456,zoom = 5) %>%
-   addMarkers(lng = ~lon, lat = ~lat, popup = ~htmlEscape(location))
-
+   setView(lat = -27.31,
+           lng = 150.456,
+           zoom = 5) %>%
+   addMarkers(
+      lng = ~ lon,
+      lat = ~ lat,
+      popup = ~ htmlEscape(location)
+   )
 ```

### 2020-02-22 01_Meta-analysis_experiments.Rmd
Use cache dir not data for newly written files
grammar

@@
 Department of Agriculture and Primary Industries and the University of Southern
-Queensland. It is worth noting Professor Malcolm Riley and Dr Sue Thompson's
+Queensland. It is worth noting Professor Malcolm Riley's and Dr Sue Thompson's
 effort in establishing and coordinating early field trials between 2010 and
@@
 write.csv(experiment_sites,
-          "data/Mungbean_experiment_sites.csv",
+          "cache/Mungbean_experiment_sites.csv",
           row.names = FALSE)

### 2020-02-22 01_Meta-analysis_experiments.Rmd
Update 01_Meta-analysis_experiments.Rmd
Use kable styling

@@
 Ratings for powdery mildew were on a 1-5 rating scale and can be read in the
-file "Powdery mildew paper#1.doc". Comparing trials which have not used the same
-rating scale will be done using a percentage change.
+file "Powdery mildew paper#1.doc".  
+Comparing trials which have not used the same rating scale will be done using a
+percentage change.
 
@@
 ```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}
-
 PM.dat <- import_data()
@@
    caption = "Description of Experiments"
- ) # %>%  #commented as was redering empty, needs a look in
-#    kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
-#    scroll_box(width = "900px", height = "500px")
+)  %>%
+   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
+   scroll_box(width = "900px", height = "500px")
 

### 2020-02-23 01_Meta-analysis_experiments.Rmd
tidy spaces

@@
    scroll_box(width = "900px", height = "500px")
-
 ```

### 2020-02-23 R/year2day.r
Delete year2day.r

@@ -1,11 +1,0 @@
-# function to extract date from the year
-# format should be Universal time format
-year2day <- function(date) {
-   if (is.na(date) == TRUE) {
-      return(NA)
-   } else {
-      return(as.numeric(as.Date(date) - as.Date(paste0(
-         substr(date, start = 1, stop = 4), "-01-01"
-      ))))
-   }
-}

### 2020-02-23 02_Weather.Rmd
Fix a few items, still borked though
Need to determine if this is useful/necessary to keep

--- 2020-02-22 02_Weather.Rmd
@@
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
+```
+
 # Weather data
@@
 The vertical lines indicate when powdery mildew was first observed in that
-season. Variation may exist in the sowing date of each trial.
+season.
+Variation may exist in the sowing date of each trial.
 
@@
 library(lubridate)
+library(theme.usq)
 source("R/import_data.R")
 PM.dat <-
-   import_data()  # importing means yield and disease severity for each treatment within each powdery mildew trial on mungbean
-source("R/year2day.r")
+   import_data()  # importing means yield and disease severity for each
+# treatment within each powdery mildew trial on mungbean
 source("R/gg_color_hue_function.R")
@@
 silo_emerald_Tmax <- read.csv("./data/silo_emerald_Tmax.csv")
+
 ```
 
-Lets have a look at the climate for the main field experiment sites
+Let's have a look at the weather for the main field experiment sites.
+
+```{r first-sign}
+# Create data subset of powdery mildew data means for the first sign of the
+# disease by location
+
+PM.dat_sum <- 
+   PM.dat %>% 
+   distinct(location, year, first_sign_disease) %>% 
+   mutate(day = yday(first_sign_disease))
+```
 
@@
 ```{r Kingaroy_weather, echo=FALSE}
-# Smoothing temperatures by taking a rolling7 day average
-max_T <- vector()
-min_T <- vector()
+# Smoothing temperatures by taking a rolling 7-day average
+min_T <- max_T <- vector(mode = "double", length = length(silo_king_Tmax[, 1]))
+
 for (i in 1:length(silo_king_Tmax[, 1])) {
-   max_T <- c(max_T, mean(silo_king_Tmax$max_temp[i:(i + 7)]))
-   min_T <- c(min_T, mean(silo_king_Tmax$min_temp[i:(i + 7)]))
+   max_T <- c(max_T, mean(silo_king_Tmax$max_temp[i:(i + 7)], na.rm = TRUE))
+   min_T <- c(min_T, mean(silo_king_Tmax$min_temp[i:(i + 7)], na.rm = TRUE))
 }
@@
 
-# Create data subset of powdery mildew data means for the first sign of the disease by location
-PM.dat_sum <- as.data.frame(do.call(rbind,
-                                    by(PM.dat, PM.dat$trial_ref, function(x) {
-                                       c(
-                                          location = unique(as.character(x$location)),
-                                          year = unique(as.character(x$year)),
-                                          first_sign = unique(as.character(x$first_sign_disease)),
-                                          day = as.numeric(unique(
-                                             sapply(x$first_sign_disease, year2day)
-                                          ))
-                                       )
-                                    })), stringsAsFactors = FALSE)
+# set year to factor
+king_Tm_aver$year <- as.factor(king_Tm_aver$year)
 
-King_FS <- PM.dat_sum[PM.dat_sum$location == "Kingaroy", ]
-King_FS$day <- as.numeric(King_FS$day)
+King_FS <- PM.dat_sum[PM.dat_sum$location == "Kingaroy",]
 
@@
 # ______  Hermitage  _______
-max_T <- vector()
-min_T <- vector()
-for (i in 1:length(silo_war_Tmax[, 1])) {
-   max_T <- c(max_T, mean(silo_war_Tmax$max_temp[i:(i + 7)]))
-   min_T <- c(min_T, mean(silo_war_Tmax$min_temp[i:(i + 7)]))
+min_T <- max_T <- vector(mode = "double", length = length(silo_war_Tmax[, 1]))
+
+for (i in 1:length(silo_king_Tmax[, 1])) {
+   max_T <- c(max_T, mean(silo_war_Tmax$max_temp[i:(i + 7)], na.rm = TRUE))
+   min_T <- c(min_T, mean(silo_war_Tmax$min_temp[i:(i + 7)], na.rm = TRUE))
 }
@@
 
-# Add columns for Year and date to data
-war_Tm_aver$year <- substr(war_Tm_aver$date, start = 1, stop = 4)
-war_Tm_aver$day <- sapply(war_Tm_aver$date,year2day)
+# Add columns for year and day of year to data
+war_Tm_aver$year <- year(war_Tm_aver$date)
+war_Tm_aver$day <- yday(war_Tm_aver$date)
 
 # Create data subset of powdery mildew data means for the first sign of the disease by location
+Herm_FS <- PM.dat_sum[PM.dat_sum$location == "Hermitage",]
 
-Herm_FS <- PM.dat_sum[PM.dat_sum$location == "Hermitage",]
-Herm_FS$day <- as.numeric(Herm_FS$day)
-
-ggplot(subset(war_Tm_aver, year == levels(factor(Herm_FS$year))),
+ggplot(data = subset(war_Tm_aver, war_Tm_aver$year %in% levels(Herm_FS$year)),
        aes(day)) +
@@
    geom_line(aes(y = min_T, color = year)) +
-   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
+   labs(x = "Date",
+        y = "Daily maximum temperature averaged over 7 days",
         title = "Maximum and minimum daily temperatures in Hermitage") +

### 2020-02-23 03_Preliminary_analysis.Rmd
Update preliminary analysis

@@
 
-```{r PA_Libraries, include=FALSE}
+```{r PA_Libraries, include=FALSE, message=FALSE}
 library(tidyverse)
+library(lubridate)
 library(bomrang)
@@
 #source("./getPPD2.R")
+theme_set(theme_usq())
 ```
 
-## Explore and visualise Data
+## Explore and Visualise Data
 
@@
    scale_colour_usq() +
-   theme_usq() +
    coord_flip()
@@
 
-   - Amistar Xtra and Custodia are both contain strobilurin and triazole, however, they because they contain differing dose ratios (inverted) pooling may not be appropriate.
+   - Amistar Xtra and Custodia are both contain strobilurin and triazole, however, because they contain differing dose ratios (inverted) pooling may not be appropriate.
 
-   - Perhaps best way forward is to do an analysis of only the triazoles/DMIs. Then do another including azoxystrobin as a comparison.
+   - Perhaps best way forward is to do an analysis of only the triazoles/DMIs.
+   Then do another including azoxystrobin as a comparison.
 
-&nbsp;  
-&nbsp;
+*****
 
 The primary focus of this research is the effect of fungicide on mitigating yield loss to disease.
-To reduce the affect of location and seasonal influences we will investigate the proportion of grain yield saved, relative to the no spray controls.
+To reduce the effect of location and seasonal influences we will investigate the proportion of grain yield saved relative to the no spray control.
 
-First lets investigate the difference in the effect of the type of fungicide on proportion of yield saved. Proportion of yield saved is used in attempt to reduce variation between trials.
+First, let's investigate the difference in the effect of the type of fungicide on proportion of yield saved. Proportion of yield saved is used in attempt to reduce variation between trials.
 
@@
 ```
-&nbsp;  
-&nbsp;
 
-Lets visualise this in a plot for one and two sprays only.
+*****
+
+Let's visualise this in a plot for one and two sprays only.
 
@@
          fungicide_ai != "benomyl" &
-         fungicide_ai != "Acibenzolar-S-methyl") %>%
-   mutate(fungicide_ai = factor(fungicide_ai, 
-                             levels = c("carbendazim", "pyraclostrobin",
-                                        "sulphur", "200 g/L azoxystrobin + 80 g/L cyproconazole",
-                                        "tebuconazole", "propiconazole", 
-                                        "200 g/L tebuconazole + 120 g/L azoxystrobin"))) %>%
+         fungicide_ai != "Acibenzolar-S-methyl"
+   ) %>%
+   mutate(fungicide_ai = factor(
+      fungicide_ai,
+      levels = c(
+         "carbendazim",
+         "pyraclostrobin",
+         "sulphur",
+         "200 g/L azoxystrobin +\n80 g/L cyproconazole",
+         "tebuconazole",
+         "propiconazole",
+         "200 g/L tebuconazole +\n120 g/L azoxystrobin"
+      )
+   )) %>%
    ggplot(aes(y = prop_YG, x = fungicide_ai)) +
@@
    labs(y = "Proportion of grain yield saved",
-        title = "Grain yield proportion saved\ngrouped by Fungicide type") +
-   theme_usq() +
+        title = "Grain yield proportion saved\ngrouped by fungicide type") +
    theme(legend.position = "none") +
    coord_flip()
-
 ```
 
-There is a small yield effect when applying fungicide and it is unclear how much a second spray improves yield saved. Interestingly Sulphur sprays might be worth investigating when sprayed twice.
+There is a small yield effect when applying fungicide and it is unclear how much a second spray improves yield saved. Interestingly sulphur sprays might be worth investigating when sprayed twice.
 
-&nbsp;  
-&nbsp;
+*****
 
@@
 PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole"|
+   filter(fungicide_ai == "tebuconazole" |
              fungicide_ai == "propiconazole") %>%
-   select(trial_ref,
+   select(
+      trial_ref,
       year,
@@
       dose_ai.ha,
-          total_fungicide) %>%
+      total_fungicide
+   ) %>%
    ggplot(aes(x = as.factor(dose_ai.ha), fill = fungicide_ai)) +
@@
    geom_bar() +
-   facet_grid(rows = vars(fungicide_ai))+
    scale_fill_usq() +
@@
 
-There is a large amount of variation in the propiconazole dose, lets inspect the difference in yields for each dose.
+There is a large amount of variation in the propiconazole dose, let's inspect the difference in yields for each dose.
 
@@
    filter(fungicide_ai == "propiconazole") %>%
-   ggplot(aes(x = relevel(as.factor(dose_ai.ha),"62.5"), y = prop_YG)) +
+   ggplot(aes(x = relevel(as.factor(dose_ai.ha), "62.5"), y = prop_YG)) +
    xlab("Dose (g ai/ha)") +
@@
 ```
-&nbsp;
 
@@
 ```{r table_PropiDoses}
-table(as.character(PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole",]$trial_ref), 
-      PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole",]$dose_ai.ha)
+table(as.character(PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole", ]$trial_ref),
+      PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole", ]$dose_ai.ha)
 ```
@@
 ```{r PropiDoses_TrialCompar}
-
-boxplot(prop_YG ~ dose_ai.ha, 
+boxplot_usq(prop_YG ~ dose_ai.ha,
             data = PM_MB_means[(PM_MB_means$trial_ref == "mung1112/01" |
@@
 
-&nbsp;  
-&nbsp;
+*****
 
@@
 
-Lets look at the frequency of sprays per fungicide.  
+Let's look at the frequency of sprays per fungicide.  
 ```{r Fungicide_x_nSprays}
 table(PM_MB_means$fungicide_ai, PM_MB_means$total_fungicide)
+```
 
-```
-&nbsp;  
-&nbsp;
+*****
 
@@
 PM_MB_means %>%
-   mutate(s1_DfromFS = fungicide_application_1 - first_sign_disease,
+   mutate(
+      s1_DfromFS = fungicide_application_1 - first_sign_disease,
       s2_DfromFS = fungicide_application_2 - first_sign_disease,
@@
       s4_DfromFS = fungicide_application_4 - first_sign_disease,
-          s5_DfromFS = fungicide_application_5 - first_sign_disease) %>%
-   gather(key = spray, value = n_days, s1_DfromFS, s2_DfromFS, s3_DfromFS, s4_DfromFS, s5_DfromFS)%>%
-   ggplot(aes(x = spray, y = n_days))+
+      s5_DfromFS = fungicide_application_5 - first_sign_disease
+   ) %>%
+   gather(
+      key = spray,
+      value = n_days,
+      s1_DfromFS,
+      s2_DfromFS,
+      s3_DfromFS,
+      s4_DfromFS,
+      s5_DfromFS
+   ) %>%
+   drop_na(n_days) %>% 
+   ggplot(aes(x = spray, y = as.numeric(n_days))) +
    geom_violin() +
-   scale_x_discrete(labels = c("First\nspray", "Second\nspray","Third\nspray","Fourth\nspray","Fifth\nspray"))+
+   scale_x_discrete(
+      labels = c(
+         "First\nspray",
+         "Second\nspray",
+         "Third\nspray",
+         "Fourth\nspray",
+         "Fifth\nspray"
+      )
+   ) +
    theme_usq()
-
 ```
 
-&nbsp;  
-&nbsp;
+*****
 
@@
 PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole"|
-             fungicide_ai == "propiconazole")%>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole") %>%
    group_by(host_genotype, fungicide_ai, trial_ref) %>%
@@
 Does host cultivar significantly impact the yield?
-Lets look at the volatility in yields to see if any cultivar yields better or has greater tolerance to powdery mildew.
+Let's look at the volatility in yields to see if any cultivar yields better or has greater tolerance to powdery mildew.
 Below we plot distributions of mean trial yields for each cultivar.
 
-First lets look at overall yields for each cultivar , where trial is not a factor, for all treatments (spray and no spray).  
+First lets look at overall yields for each cultivar, where trial is not a factor, for all treatments (spray and no spray).  
 ```{r yield_vol}
@@
 
-YV1 <- yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
+YV1 <-
+   yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
 YV1[[2]]
@@
 
-YV2 <- yield_volatility(genotype_by_trial = FALSE, control_only = TRUE)
+YV2 <-
+   yield_volatility(genotype_by_trial = FALSE, control_only = TRUE)
 YV2[[2]]
 YV2[[3]]
+```
 
-```
 Volatility of the cultivars are fairly similar when trial is not considered as a factor (when we inspect plots of all treatments and only spray treatments).
-Green diamond shows little volatility however this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trials.
-&nbsp;
+Green Diamond shows little volatility however this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trials.
+
+*****
 
@@
 ```{r yieldVol_Herm}
-YV1_herm <- yield_volatility(genotype_by_trial = FALSE, control_only = FALSE, location = "Hermitage")
+YV1_herm <-
+   yield_volatility(
+      genotype_by_trial = FALSE,
+      control_only = FALSE,
+      location = "Hermitage"
+   )
 YV1_herm[[2]]
-
 ```
@@
 ```{r YieldVol_Crystal}
-YV1_crystal <- yield_volatility(genotype = "Crystal",control_only = FALSE)
+YV1_crystal <-
+   yield_volatility(genotype = "Crystal", control_only = FALSE)
 YV1_crystal[[2]]
-YV1_crystal <- yield_volatility(genotype = "Crystal",control_only = TRUE)
+YV1_crystal <-
+   yield_volatility(genotype = "Crystal", control_only = TRUE)
 YV1_crystal[[2]]
-
 ```
@@
 ```{r YieldVol_JadeControl}
-YV3_crystal <- yield_volatility("Jade",control_only = TRUE)
+YV3_crystal <- yield_volatility("Jade", control_only = TRUE)
 YV3_crystal[[2]]
@@
 
-&nbsp;
+*****
 
@@
 PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole" | fungicide_ai == "propiconazole") %>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole") %>%
    group_by(fungicide_ai, row_spacing, trial_ref) %>%
@@
    geom_boxplot() +
-   #  geom_smooth()+
- #  scale_y_continuous(limits = c(-5, 15)) +
-   theme_usq()+
    ggtitle("Powdery mildew variation between different row spacing")
-
 ```
@@
    geom_boxplot() +
-   #  geom_smooth()+
- #  scale_y_continuous(limits = c(-5, 15)) +
-   theme_usq()+
-   facet_grid(cols = vars(location))+
+   facet_grid(cols = vars(location)) +
    ggtitle("Powdery mildew variation between different row spacing")
-
 ```
@@
 PM_MB_means %>%
-   filter(year == 2017|
+   filter(year == 2017 |
              year == 2018) %>%
@@
    geom_jitter(width = 0.01) +
-   #   scale_y_continuous(limits = c(-5,15))+
-   theme_usq()+
-   ggtitle("Grain yield results for different row spacing at three locations")+
-   xlab("Row spacing (m)")+
-   ylab("Grain yield - tonne per hectare")
-
+   ggtitle("Grain yield results for different row spacing at three locations") +
+   xlab("Row spacing (m)") +
+   ylab("Grain yield - tonnes per hectare")
 ```
@@
 
-lm_rain1 <- read.csv("data/lmInSeasonRainfall_-10.09_30.64.csv",stringsAsFactors = FALSE)
-lm_rain2 <- read.csv("data/lmInSeasonRainfall_-10.09_65.100.csv",stringsAsFactors = FALSE)
-lm_rain3 <- read.csv("data/lmInSeasonRainfall_10.30_30.64.csv",stringsAsFactors = FALSE)
-lm_rain4 <- read.csv("data/lmInSeasonRainfall_10.30_65.100.csv",stringsAsFactors = FALSE)
+lm_rain1 <-
+   read.csv("data/lmInSeasonRainfall_-10.09_30.64.csv",
+            stringsAsFactors = FALSE)
+lm_rain2 <-
+   read.csv("data/lmInSeasonRainfall_-10.09_65.100.csv",
+            stringsAsFactors = FALSE)
+lm_rain3 <-
+   read.csv("data/lmInSeasonRainfall_10.30_30.64.csv",
+            stringsAsFactors = FALSE)
+lm_rain4 <-
+   read.csv("data/lmInSeasonRainfall_10.30_65.100.csv",
+            stringsAsFactors = FALSE)
 
-lm_rain <- rbind(lm_rain1,lm_rain2,lm_rain3,lm_rain4)
+lm_rain <- rbind(lm_rain1, lm_rain2, lm_rain3, lm_rain4)
 ```
@@
 ```{r WhichLModel}
-lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)),]
-lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),]
-lm_rain[which(lm_rain$lm_adj_rsquared == max(lm_rain$lm_adj_rsquared)),]
-
+lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)), ]
+lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)), ]
+lm_rain[which(lm_rain$lm_adj_rsquared == max(lm_rain$lm_adj_rsquared)), ]
 ```
@@
 ```{r rainLMpvalue}
-ggplot(lm_rain, aes(x = start_day, y = end_day, z = log(lm_pval)))+
-   geom_raster(aes(fill = log(lm_pval)), interpolate = TRUE)+
-   geom_contour(bins = 15, colour = "white")+
-   geom_point(data = lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)),], aes(x = start_day, y = end_day), colour =" red")+
-   scale_fill_distiller(palette ="RdBu", direction = -1)
-
+ggplot(lm_rain, aes(x = start_day, y = end_day, z = log(lm_pval))) +
+   geom_raster(aes(fill = log(lm_pval)), interpolate = TRUE) +
+   geom_contour(bins = 15, colour = "white") +
+   geom_point(data = lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)), ],
+              aes(x = start_day, y = end_day),
+              colour = " red") +
+   scale_fill_distiller(palette = "RdBu", direction = -1) 
 ```
@@
 ```{r rainLMrsquared}
-ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_rsquared))+
-   geom_raster(aes(fill = lm_rsquared), interpolate = TRUE)+
-   geom_contour(bins = 15, colour = "white")+
-   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),], aes(x = start_day, y = end_day), colour =" red")+
-   scale_fill_distiller(palette ="RdBu") 
+ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_rsquared)) +
+   geom_raster(aes(fill = lm_rsquared), interpolate = TRUE) +
+   geom_contour(bins = 15, colour = "white") +
+   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)), ],
+              aes(x = start_day, y = end_day),
+              colour = " red") +
+   scale_fill_distiller(palette = "RdBu") 
 ```
@@
 ```{r rainLMadjrsquared}
-ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_adj_rsquared))+
-   geom_raster(aes(fill = lm_adj_rsquared), interpolate = TRUE)+
-   geom_contour(bins = 15, colour = "white")+
-   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),], aes(x = start_day, y = end_day), colour =" red")+
-   scale_fill_distiller(palette ="RdBu") 
+ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_adj_rsquared)) +
+   geom_raster(aes(fill = lm_adj_rsquared), interpolate = TRUE) +
+   geom_contour(bins = 15, colour = "white") +
+   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)), ],
+              aes(x = start_day, y = end_day),
+              colour = " red") +
+   scale_fill_distiller(palette = "RdBu") 
 ```
@@
 
+*****
+
 ### Season range and first incidence
-Mungbean is a summer crop and powdery mildew is requires cool conditions to establish.
+Mungbean is a summer crop and powdery mildew requires cool conditions to establish.
 Therefore the disease can be avoided by planting early in summer or spring, avoiding cooler temperatures at the end of some seasons.
-Can we visualise when PM is most likely to establish over the calender year.
+Can we visualise when PM is most likely to establish over the calender year?
 
@@
 season_dates <- PM_MB_means %>%
-   group_by(trial_ref)%>%
-   summarise(Planting_date = unique(planting_date),
+   group_by(trial_ref) %>%
+   summarise(
+      Planting_date = unique(planting_date),
       Harvest_date = unique(harvest_date),
@@
 
-# function to extract date from the year
-# format should be Universal time format
-source("R/year2day.r")
+season_dates$Planting_day <- yday(season_dates$Planting_date)
+season_dates$Disease_day <- yday(season_dates$First_sign_PM)
+season_dates$Harvest_day <-
+   season_dates$Planting_day + season_dates$season_length
 
-season_dates$Planting_day <- unlist(lapply(season_dates$Planting_date,year2day))
-season_dates$Disease_day <- unlist(lapply(season_dates$First_sign_PM,year2day))
-season_dates$Harvest_day <- season_dates$Planting_day + season_dates$season_length
-
-season_dates[1,"Planting_day"] <- year2day(as.Date("2012-02-28")-7) # planted in december and emerged in February, Assuming due to lack of rain or recording error.
-Using 7 days prior to emergence day as planting day
+season_dates[1, "Planting_day"] <-
+   yday(as.Date("2012-02-28") - 7) # planted in december and emerged in February, Assuming due to lack of rain or recording error. Using 7 days prior to emergence day as planting day
 
 first_day_month <- c(0, 31, 59, 90, 120, 151, 181, 211, 243, 273)
-axis_labels_date <- c(format(Sys.Date() - year2day(Sys.Date()) + first_day_month[1], "%b-%d"),  # Jan
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[2], "%b-%d"), # Feb
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[3], "%b-%d"), # March
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[4], "%b-%d"), # April
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[5], "%b-%d"), # May
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[6], "%b-%d"), # June
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[7], "%b-%d"), # July
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[8], "%b-%d"), # August
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[9], "%b-%d"), # Sept
-                         format(Sys.Date() - year2day(Sys.Date()) + first_day_month[10], "%b-%d") # October
+axis_labels_date <-
+   c(
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[1], "%b-%d"),
+      # Jan
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[2], "%b-%d"),
+      # Feb
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[3], "%b-%d"),
+      # March
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[4], "%b-%d"),
+      # April
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[5], "%b-%d"),
+      # May
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[6], "%b-%d"),
+      # June
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[7], "%b-%d"),
+      # July
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[8], "%b-%d"),
+      # August
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[9], "%b-%d"),
+      # Sept
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[10], "%b-%d") # October
    )
@@
 season_dates %>%
-   ggplot()+
-   geom_pointrange(aes(x = trial_ref, y = Disease_day, ymin = Planting_day, ymax = Harvest_day))+
-   scale_y_continuous(
-      limits = c(0, max(season_dates$Planting_day + 
+   ggplot() +
+   geom_pointrange(aes(
+      x = trial_ref,
+      y = Disease_day,
+      ymin = Planting_day,
+      ymax = Harvest_day
+   )) +
+   scale_y_continuous(limits = c(
+      0,
+      max(
+         season_dates$Planting_day +
             season_dates$season_length,
-                        na.rm = TRUE)),
+         na.rm = TRUE
+      )
+   ),
    labels = axis_labels_date,
-      breaks = first_day_month
-   )+
-   geom_point(aes(x = trial_ref, y = Disease_day))+
-   coord_flip()+
+   breaks = first_day_month) +
+   geom_point(aes(x = trial_ref, y = Disease_day)) +
+   coord_flip() +
    ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
-
 ```
 
-In most years, regardless of the age of the crop, powdery mildew establishes in March.
+In most years, regardless of the age of the crop, PM establishes in March.
 
-&nbsp;  
-&nbsp;
+*****
 
 #### Effect of Fungicide
+
 **Fungicide effect on proportional yield gain with respect to time of application**  
@@
       fungicide_ai == c(
-         "200 g/L tebuconazole + 120 g/L azoxystrobin" ,
-         "200 g/L azoxystrobin + 80 g/L cyproconazole",
+         "200 g/L tebuconazole +\n120 g/L azoxystrobin" ,
+         "200 g/L azoxystrobin +\n80 g/L cyproconazole",
          "tebuconazole",
@@
    coord_flip()
-
 ```
@@
 ```{r yield_x_PMseverity}
-
 PM_MB_means %>%
@@
    ggplot(aes(x = PM_final_severity, y = grain_yield.t.ha.)) +
-   geom_point()+
+   geom_point() +
    geom_smooth(method = "lm")
-
 ```
 
-From the data we have it is difficult to determine if there is an association between powdery mildew severity and grain yield.
+From the data that we have, it is difficult to determine if there is an association between powdery mildew severity and grain yield.

### 2020-02-23 06_AUDPC_MetaAnalysis.Rmd
chunk names
AUDPC funnel plot

@@
 # AUPDC meta-analysis
+
+```{r AUDPC_funnel}
+PM_Mdat$slope <- NA
+PM_Mdat$SE <- NA
+for(i in PM_Mdat$trial){
+   PM_Mdat[PM_Mdat$trial == i,c("slope", "SE")] <-
+      coef(summary(lm(grain_yield.t.ha ~ AUDPC_m,data = PM_Mdat[PM_Mdat$trial == i,])))[2,1:2]
+}
+
+plot(1/SE ~ slope, data = PM_Mdat, ylim = c(-3000,6000))
+```
+
 Now it's time to look at how the spray managment scenarios might impact disease pressure on the mungbean yields.
@@
 
-```{r AUDPC:spraymangement}
+```{r AUDPC:spraymangement2}
 Me_mod8 <- lmer(grain_yield.t.ha ~ AUDPC_m : spray_management + (AUDPC_m: spray_management|trial),

### 2020-02-23 07_Publication_wireframe_and_8Questions.Rmd
spelling and grammar check

@@
 date: "31/01/2020"
-output: html_document
+output:
+  html_document: default
 ---
@@
    * Lisa Kelly – Plant pathologist  
-   * Paul MacIntosh – Mungbean/ pulse agronomist  
+   * Paul Macintosh – Mungbean/ pulse agronomist  
    * Ross Pomroy – Agronomist  
@@
 ## Why did you do it? (limit - 50 words)  
-The unpublished field trial data independantly did not provide a clear indication for when to apply fungicide to best mitigate yield losses from powdery mildew.
+Data from unpublished field trials independently did not provide a clear indication for when to apply fungicide to best mitigate yield losses from powdery mildew.
 By analysing the collective data we aim to provide a better estimate for fungicide application timing to mitigate the yield loss from powdery mildew.
@@
 Primarily that fungicide spray schedules that commence prior to signs of the disease establishing in the mungbean canopy are likely to be ineffective at mitigating the diseases impact on yield.
-We also don't have data on at what point is starting a fungicide spray schedule is too late.
-Growers can't scout their crop three times a week in the fashion of researchers and are unlikely to identify the true date when signs of powdery mildew become apparent.
-Therefore these results reinforce the message to growers to spray for powdery mildew as soon as it is observed in the crop to protect yields.
+We also don’t have data on at what point starting a fungicide spray schedule is too late.
+Growers can’t scout their crop three times a week in the fashion of researchers and are unlikely to identify the true date when signs of powdery mildew become apparent.
+Therefore these results reinforce the message to growers to spray for powdery mildew as soon as it is observed in their crop to protect yields.
 
@@
 This study is the most robust analysis of management of powdery mildew in mungbean using fungicides.
-It provide a more certain time frame for growers to plan for when to commence a fungicide spray schedule.
+It provides a more certain time frame for growers to plan when to commence a fungicide spray schedule.
+
 Fewer fungicide applications will reduce costs for growers and prolong the efficacy of fungicides before the disease develops resistance.
@@
 Within the meta-analysis, some comparisons between spray management factors contained fewer replicates in comparison to other spray management factor combinations.
-Only a few studies incorporated in the meta-analysis contained comparisons between the "Late plus" factor and the: negative spray control, a single spray at first sign, and spray at first sign with one or more follow-up applications.
+Only a few studies incorporated in the meta-analysis contained comparisons between the “Late plus” factor and the treatments: negative spray control, a single spray at first sign, and spray at first sign with one or more follow-up applications.
 

### 2020-02-24 02_Preliminary_analysis.Rmd
Use pacman

--- 2019-06-19 02_Preliminary_analysis.Rmd
@@
 
-```{r PA_Libraries, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-library(dplyr)
-library(openxlsx)
-library(kableExtra)
-library(ggplot2)
+```{r PA_Libraries, include=FALSE, message=FALSE}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(tidyverse, lubridate, bomrang, openxlsx, devtools, reshape2, lme4)
+source("R/import_data.R")
+if (!require("theme.usq")) devtools::install_github("adamhsparks/theme.usq")
+library(theme.usq)
+#source("./getPPD2.R")
+theme_set(theme_usq())
+```
+
+## Explore and Visualise Data
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
+# Import data
+PM_MB_means <- import_data() # link expires 2021-12-01
+
+#remove the variation in different sulphur formulations
+unique(PM_MB_means[
+   grep("sulphur",PM_MB_means$fungicide_ai),
+   "fungicide_ai"])
+PM_MB_means[grep("sulphur",PM_MB_means$fungicide_ai),"fungicide_ai"] <- "sulphur"
 
@@
 
-## Summary of data
+Various factors have been studied in the previous experiments which may influence the following results.
+However unless stated the following plots and analyses were made disregarding effects from other factors not mentioned.
 
-```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}
+   1) Fungicide type
 
-source("Cleaning historical data.R", echo = FALSE, print.eval = FALSE)
-# ___ Datasets available ___
-# data   Herm_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2017, Hermitage and Fogerty
-# data   King_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2016, Hermitage and Kingaroy
-# data   Fogerty_17.1   - Full disease ratings and yeild data from Fogerty field trial in 2017
-# data   Herm_17.1      - Full disease ratings and yeild data from Hermitage field trial in 2017
-# data   PM_MB_17       - Full disease ratings and yeild data from Hermitage and Fogerty in 2017
-# data   PM_MB_16       - End of season powdery mildew rating and Yield data from two field trials in 2016, Hermitage and Kingaroy
-# data   PM_MB_means    - Mean disease rating and yeild data, from trial reports
+   2) Fungicide dose (varies only slightly within some fungicide types)
 
-PM.dat <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
+   3) Number of fungicide sprays
 
-glimpse(PM.dat)
+   4) Timing of fungicide spray/s relative to first sign of disease (_i.e_. when pathogen is present)
 
-kable(PM.dat %>%
-   group_by(Trial_ref, Year, Location, trial_design, Replicates, planting_date, emergence_date, first_sign_disease) %>%
-   summarise(Treatments = length(E_treatment)),
-   caption = "Description of Experiments") %>%
+   5) Host cultivars (probably is a co-variate with season due to changing cultivars over time)
+
+   6) Experiment location
+
+   7) Row spacing
+
+   8) In-crop rainfall
+
+   9) Irrigated vs non-irrigated trials
+
+   10) Mean daily temperature in the weeks following spray application
+
+   11) Final disease rating
+
+   12) Two pathogen species cause PM (new discovery in 2018)
+
+The data plotted below are from `r length(unique(PM_MB_means$trial_ref))` field trials between (`r first(levels(PM_MB_means$year))` - `r last(levels(PM_MB_means$year))`) of which the details are described in [Studies considered in meta-analysis section](#studies-considered-in-meta-analysis).
+All data explored below are a list of mean values from each treatment applied in each experiment.
+Some experiments have in-season observations of disease incidence and severity, however here we have summarised the data to show only the end of season observations.
+
+### Fungicides
+#### Fungicide type
+Let's explore how many different types of fungicide were used and at what frequency.
+
+```{r Fungicides}
+PM_MB_means %>%
+   group_by(fungicide_ai, trial_ref) %>%
+   summarise() %>%
+   count(sort = TRUE) %>%
+   rename(Trials = n) %>%
+   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
+   xlab("Fungicide active ingredient") +
+   ylab("N Trials") +
+   geom_col() +
+   scale_fill_usq() +
+   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
+   scale_colour_usq() +
+   coord_flip()
+```
+
+   - Tebuconazole and propiconazole could be pooled as a triazole or demethylation inhibitors (DMI) fungicide treatment.
+
+   - Amistar Xtra and Custodia are both contain strobilurin and triazole, however, because they contain differing dose ratios (inverted) pooling may not be appropriate.
+
+   - Perhaps best way forward is to do an analysis of only the triazoles/DMIs.
+   Then do another including azoxystrobin as a comparison.
+
+*****
+
+The primary focus of this research is the effect of fungicide on mitigating yield loss to disease.
+To reduce the effect of location and seasonal influences we will investigate the proportion of grain yield saved relative to the no spray control.
+
+First, let's investigate the difference in the effect of the type of fungicide on proportion of yield saved. Proportion of yield saved is used in attempt to reduce variation between trials.
+
+```{r Fungicide_x_nSprays_tble2, message=FALSE}
+PM_MB_means %>%
+   group_by(fungicide_ai, total_fungicide) %>%
+   summarise(
+      n = length(prop_YG),
+      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
+      median = median(prop_YG, na.rm = T),
+      mean = mean(prop_YG, na.rm = T),
+      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
+   ) %>%
+   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
+   arrange(desc(median)) %>%
+   kable(caption = "Fungicide effect on proportion of yield gain.") %>%
    kable_styling(fixed_thead = T, full_width = T) %>%
-   scroll_box(width = "900px", height = "500px")
-
-PM.dat$Trial_ref <- factor(PM.dat$Trial_ref)
-PM.dat$Location <- factor(PM.dat$Location)
-PM.dat$Year <- factor(PM.dat$Year)
-PM.dat$host_genotype <- factor(PM.dat$host_genotype)
-PM.dat$Fungicide <- factor(PM.dat$Fungicide)
-PM.dat$Trade_name <- factor(PM.dat$Trade_name)
+   footnote(general = "Fungicides with less than five observations were omitted from this table")
 
@@
 
-## Weather data
+*****
 
-The mungbean DSS determines the need to spray on:  
-   1. The presence of the disease  
-   2. The forecasted maximum temperatures in the next seven days  
-   3. The number of days over the next seven days with rainfall
+Let's visualise this in a plot for one and two sprays only.
 
-Below I am plotting the mean maximum temperures over 7 days during the growing season at each Mungbean trial site.
-The vertical lines indicate when powdery mildew was first observed in that season.
-Variation may exist in the sowing date of each trial.
+```{r Fungicide_x_nSprays_tble1, message=FALSE}
 
-```{r echo=FALSE, message=FALSE, warning=FALSE}
-# Need weather data between 2011 and 2017
-
-# function to extract date from the year
-# format should be Universal time format
-year.day <- function(date){
-   if(is.na(date) == TRUE){ 
-      print(NA)
-      } else {
-as.numeric(as.Date(date) - as.Date(paste0(substr(date, start = 1, stop = 4),"-01-01")))
-      }
-   }
-# Function to generate some of the ggplot grouping colours
-gg_color_hue <- function(n) {
-  hues = seq(15, 375, length = n + 1)
-  hcl(h = hues, l = 65, c = 100)[1:n]
-}
-cols1 <- gg_color_hue(4)
-silo_war_Tmax <- getPPD2(station_id = 041525,start = 20110101,end = 20160630, silo.apikey = silo.API, variables = "max_temp,min_temp,daily_rain")
-# retrieve the maximum temperatures from the six yearsd between 2011 and 2017 at weather station 041525 (Hermitage)
-silo_king_Tmax <- getPPD2(lat = -26.58, long = 151.83, start = 20110101, end = 20160630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
-silo_gatton_Tmax <- getPPD2(lat = -27.56, long = 152.32, start = 20110101, end = 20170630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
-silo_emerald_Tmax <- getPPD2(lat = -23.54, long = 148.19, start = 20110101, end = 20170630, silo.apikey =  silo.API, variables = "max_temp,min_temp,daily_rain")
-experiment_sites <- data.frame(
-   location = c("Hermitage", "Kingaroy research station","Gatton", "Emerald Agricultural College"),
-   lat = c(-28.215 ,-26.58,-27.56,-23.54),
-   lon = c(152.1003,151.83,152.32,148.19)
+PM_MB_means %>%
+   mutate(fungicide_ai = as.factor(PM_MB_means$fungicide_ai)) %>%
+   filter(total_fungicide == 1 | total_fungicide == 2) %>%
+   filter(
+      fungicide_ai != "pyrazophos" &
+         fungicide_ai != "control" &
+         fungicide_ai != "benomyl" &
+         fungicide_ai != "Acibenzolar-S-methyl"
+   ) %>%
+   mutate(fungicide_ai = factor(
+      fungicide_ai,
+      levels = c(
+         "carbendazim",
+         "pyraclostrobin",
+         "sulphur",
+         "200 g/L azoxystrobin +\n80 g/L cyproconazole",
+         "tebuconazole",
+         "propiconazole",
+         "200 g/L tebuconazole +\n120 g/L azoxystrobin"
       )
-# leaflet() %>%
-#    addProviderTiles("Esri.WorldTopoMap") %>%
-#    addMarkers(lng = experiment_sites$lon, lat = experiment_sites$lat)
-# head(silo_gatton_Tmax)
-# ______  Kingaroy_______
-max_T <- vector()
-min_T <- vector()
-for(i in 1:length(silo_king_Tmax[,1])){
-   max_T <- c(max_T,mean(silo_king_Tmax$max_temp[i:(i+7)]))
-   min_T <- c(min_T,mean(silo_king_Tmax$min_temp[i:(i+7)]))
-}
-king_Tm_aver <- data.frame(location = "Kingaroy", date = as.Date(silo_king_Tmax$date), max_T, min_T, daily_rain = silo_king_Tmax$daily_rain)
-# Add columns for Year and date to data
-king_Tm_aver <- king_Tm_aver %>%
-   mutate(Year = substr(king_Tm_aver$date, start = 1, stop = 4),
-          Day = year.day(king_Tm_aver$date)) 
-# Create data subset of Powdery mildew data means for the first sign of the disease by location
-King_FS <- PM.dat %>%
-   group_by(Trial_ref, Location, Year) %>%
-   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
-   filter(Location == "Kingaroy") %>%
-   mutate(Day = year.day(First_sign))
-ggplot(subset(king_Tm_aver, Year == levels(factor(King_FS$Year))),
-              aes(Day))+
-   geom_line(aes(y = max_T, colour = Year))+
-   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
-   geom_line(aes(y = min_T, colour=Year))+
-   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
-   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
-   title = "Maximum and minimum daily temperatures in Kingaroy")+
-   scale_y_continuous(limits = c(0,40))+
-   scale_x_continuous(limits = c(0,200), 
-                      labels = c(subset(king_Tm_aver, Year == 2016)$date[c(1,50,100,150,200)]),
-                      breaks = c(1,50,100,150,200))+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(xintercept = King_FS$Day[1], size =1, colour = cols1[1], linetype = "dotted")+
-   geom_vline(xintercept = King_FS$Day[2], size =1.5, colour = cols1[2], linetype = "dotted")+
-   geom_vline(xintercept = King_FS$Day[3], size =1, colour = cols1[3], linetype = "dashed")+
-   geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
-   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
-   scale_x_continuous(limits = c(1,180),
-                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
-                      labels = c("2012-Jan-01","2012-Feb-01","2012-Mar-01","2012-Apr-01","2012-May-01","2012-Jun-01","2012-Jul-01"))
-# ______  Hermitage  _______
-max_T <- vector()
-min_T <- vector()
-for(i in 1:length(silo_war_Tmax[,1])){
-   max_T <- c(max_T,mean(silo_war_Tmax$max_temp[i:(i+7)]))
-   min_T <- c(min_T,mean(silo_war_Tmax$min_temp[i:(i+7)]))
-}
-war_Tm_aver <- data.frame(location = "Hermitage", date = as.Date(silo_war_Tmax$date), max_T, min_T, daily_rain = silo_war_Tmax$daily_rain)
-# Add columns for Year and date to data
-war_Tm_aver <- war_Tm_aver %>%
-   mutate(Year = substr(war_Tm_aver$date, start = 1, stop = 4),
-          Day = year.day(war_Tm_aver$date)) 
-# Create data subset of Powdery mildew data means for the first sign of the disease by location
-Herm_FS <- PM.dat %>%
-   group_by(Trial_ref, Location, Year) %>%
-   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
-   filter(Location == "Hermitage") %>%
-   mutate(Day = year.day(First_sign))
-ggplot(subset(war_Tm_aver, Year == levels(factor(Herm_FS$Year))),
-              aes(Day))+
-   geom_line(aes(y = max_T, colour = Year))+
-   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
-   geom_line(aes(y = min_T, color = Year))+
-   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
-   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
-   title = "Maximum and minimum daily temperatures in Hermitage")+
-   scale_y_continuous(limits = c(0,40))+
-   scale_x_continuous(limits = c(0,200), 
-                      labels = c(subset(war_Tm_aver, Year == 2016)$date[c(1,50,100,150,200)]),
-                      breaks = c(1,50,100,150,200))+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(xintercept = Herm_FS$Day[1], size =1, colour = cols1[1], linetype = "dotted")+
-   geom_vline(xintercept = Herm_FS$Day[2], size =1.5, colour = cols1[2], linetype = "dotted")+
-   geom_vline(xintercept = Herm_FS$Day[3], size =1, colour = cols1[3], linetype = "dashed")+
-      geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
-   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
-   scale_x_continuous(limits = c(1,180),
-                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
-                      labels = c("Jan-01","Feb-01","Mar-01","Apr-01","May-01","Jun-01","Jul-01"))
-# ______  Gatton  _______
-max_T <- vector()
-min_T <- vector()
-for(i in 1:length(silo_gatton_Tmax[,1])){
-   max_T <- c(max_T,mean(silo_gatton_Tmax$max_temp[i:(i+7)]))
-   min_T <- c(min_T,mean(silo_gatton_Tmax$min_temp[i:(i+7)]))
-}
-# put maximum, minimum temperatures into a dataframe corresponding with thier corresponding date
-Gat_Tm_aver <- data.frame(location = "Gatton", date = as.Date(silo_gatton_Tmax$date), max_T, min_T, daily_rain = silo_gatton_Tmax$daily_rain)
-# Add columns for Year and date to data
-Gat_Tm_aver <- Gat_Tm_aver %>%
-   mutate(Year = substr(Gat_Tm_aver$date, start = 1, stop = 4),
-          Day = year.day(Gat_Tm_aver$date)) 
-# Create data subset of Powdery mildew data means for the first sign of the disease by location
-Gatton_FS <- PM.dat %>%
-   group_by(Trial_ref, Location) %>%
-   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
-   filter(Location == "Gatton") %>%
-   mutate(Year = factor(substr(First_sign,1,4)),
-          Day = year.day(First_sign))
-ggplot(subset(Gat_Tm_aver, Year == levels(Gatton_FS$Year)),
-               aes(Day))+
-   geom_line(aes(y = max_T, colour = Year))+
-   #geom_smooth(method = "lm", aes(y = max_T), colour = "darkred")+
-   geom_line(aes(y = min_T, colour = Year))+
-   #geom_smooth(method = "lm", aes(y = min_T), colour = "darkblue")+
-   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
-   title = "Maximum and minimum daily temperatures in Gatton")+
-   scale_y_continuous(limits = c(0,40))+
-   scale_x_continuous(limits = c(0,200), 
-                      labels = c(subset(Gat_Tm_aver, Year == levels(Gatton_FS$Year))$date[c(1,50,100,150,200)]),
-                      breaks = c(1,50,100,150,200))+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(xintercept = Gatton_FS$Day, colour = "green", size =1)+
-      geom_area(aes(y = daily_rain, fill = Year), alpha = 0.5)+
-   scale_y_continuous(sec.axis = dup_axis(name = "Rainfall (mm)"))+
-   scale_x_continuous(limits = c(1,180),
-                      breaks = c(1,32,(31+29),(31+29+31),(31+29+31+30),(31+29+31+30+31),(31+29+31+30+31+30)),
-                      labels = c("2012-Jan-01","2012-Feb-01","2012-Mar-01","2012-Apr-01","2012-May-01","2012-Jun-01","2012-Jul-01"))
-#   scale_x_continuous(limits = as.Date(c("2012-01-01","2012-06-01")))
-
-# line 259
-vec1 <- year.day(Herm_FS$First_sign)
+   )) %>%
+   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
+   facet_grid(rows = vars(total_fungicide)) +
+   geom_boxplot(aes(fill = fungicide_ai, alpha = 0.5)) +
+   geom_hline(aes(yintercept = 0), size = 0.5) +
+   labs(y = "Proportion of grain yield saved",
+        title = "Grain yield proportion saved\ngrouped by fungicide type") +
+   theme(legend.position = "none") +
+   coord_flip()
 ```
 
-### Yield saved from fungicide applications
+There is a small yield effect when applying fungicide and it is unclear how much a second spray improves yield saved. Interestingly sulphur sprays might be worth investigating when sprayed twice.
 
-The data plotted below are from the past field trials (2011 - 2017) described in the aforementioned table.
-All data are a list of mean values from each treatment applied in each experiment.
-Various factors have been studied in the previous experiments which may influence the following results.
-The following variables were disregarded in the plots below.
+*****
 
-   1) Fungicide type
-   2) Fungicide dose
-   3) row spacing
-   4) Host cultivars
-   5) Experiment location
-   6) Final disease rating
+#### Fungicide Doses  
+We should check that all fungicide doses that were used were roughly the same if we are to compare between trials were dose might be different.
 
-```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
-library(lme4)
-# What row spacing leads to the highest yield penalty
-head(PM_MB_17)
-class(PM_MB_17$Incidence_assessment_date)
-class(PM_MB_17$Incidence)
-# `2017-05-11` # last assessment Fogerty
-subset(PM_MB_17, location == "Hermitage")
-ggplot(subset(PM_MB_17, Treatment.No == "T1"||"1"), 
-       aes(y = Incidence, x = Incidence_assessment_date, colour = location))+
-   geom_point()+
-   geom_smooth()+
-   scale_y_continuous(limits = c(-5,15))
-# PM_MB_means <- subset(PM_MB_means, Fungicide != "control")   
-# PM_MB_means$Fungicide <- factor(PM_MB_means$Fungicide, levels = c("Sulphur", "Amistar", "propiconazole", "Tebeconazole"))
-PM_MB_means$Fungicide <- factor(PM_MB_means$Fungicide, levels = c("control", "Sulphur", "Amistar", "propiconazole", "Tebeconazole"))
-yield_lmer1 <- lmer(`yield_gain` ~ factor(total_Fungicide) + Fungicide + factor(Year) + (factor(Year)|Location), 
-                    data = PM_MB_means, na.action = na.omit, REML = F)
-# removed the Year interaction with location
-yield_lmer2 <- lmer(`yield_gain` ~ factor(total_Fungicide) + Fungicide + factor(Year) + (1|Location), 
-                    data = PM_MB_means, na.action = na.omit, REML = F)
-# Removing Fungicide as different fungicides were sprayed a different number of times
-yield_lmer3 <- lmer(`yield_gain` ~ factor(total_Fungicide)  + factor(Year) + (1|Location), 
-                    data = PM_MB_means, na.action = na.omit, REML = F)
-# Removing Fungicide as different fungicides were sprayed a different number of times
-yield_lmer4 <- lmer(`yield_gain` ~ factor(total_Fungicide)  + factor(Year) + (1|Location) + (1|Fungicide), 
-                    data = PM_MB_means, na.action = na.omit, REML = T)
-ranef(yield_lmer4)
-anova(yield_lmer1, yield_lmer2) # P = 0.8943  # removed random intercept 'Year' for each random slope 'Location' # Keep simpler model 
-anova(yield_lmer2, yield_lmer3) # P = 0.8005  # Removed (FE) Fungicide     #     Fungicide showed not to be significant in protecting yield
-anova(yield_lmer3, yield_lmer4) # P = 1       # Added Fungicide as a random effect #     Fungicide showed not to contribute to variation and 
-yield_lmer <- lmer(`yield_gain` ~ factor(total_Fungicide) + factor(Year) + (1|Location), 
-                    data = PM_MB_means, na.action = na.omit)
-summary(yield_lmer)
-ranef(yield_lmer)
+```{r tebuAndPropi_dose}
+PM_MB_means %>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole") %>%
+   select(
+      trial_ref,
+      year,
+      location,
+      first_sign_disease,
+      fungicide_ai,
+      dose_ai.ha,
+      total_fungicide
+   ) %>%
+   ggplot(aes(x = as.factor(dose_ai.ha), fill = fungicide_ai)) +
+   xlab("Dose (g ai/ha)") +
+   ggtitle(label = "Total number of treatments for each respective tebuconazole dose") +
+   geom_bar() +
+   scale_fill_usq() +
+   scale_colour_usq() +
+   theme_usq()
 ```
 
-#### Yield saved 
-##### Number of fungicide applications
-The following density plots show mean yield saved in relation to how many sprays were applied.
+All trials that used tebuconazole used approximately the same dose. Dose of the active ingredient ranged from 62.35&nbsp;g per hectare to 60&nbsp;g per hectare.
 
-```{r warning=FALSE, echo=FALSE}
-library(ggplot2)
-PM_MB_means <- read.xlsx("C:/Users/U8011054/Documents/GitHub/Mungbean_PM/data/1902 powdery mildew-Mungbean - Collated means.xlsx", detectDates = TRUE)
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PMy <- PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-   group_by(total_Fungicide) %>%
-   summarise(lower = quantile(yield_gain, na.rm = T, c(0.025)),
-             upper = quantile(yield_gain, na.rm = T, c(0.975)))
-# Density plot of Number of fungicide applications and the resulting yeild saved (as a proportion)
-ggplot(subset(PM_MB_means,Fungicide != "control"), aes(yield_gain))+
-   geom_density(aes(group = factor(total_Fungicide), fill = factor(total_Fungicide)), alpha = 0.6)+
-   geom_vline(xintercept = 0, size =1)+
-   labs(x = "Grain yeild saved (t/ha)",
-   title = "Density plot of grain yield saved from differing numbers of fungicide applications")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(data = quant_PMy, aes(xintercept = lower, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   geom_vline(data = quant_PMy, aes(xintercept = upper, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   guides(colour = guide_legend(title="Upper (97.5%) and \nLower (2.5%) percentiles"),
-          fill=guide_legend(title="Number of \nFungicide applications"))+
-   scale_x_continuous(limits = c(-0.3,0.8))
+There is a large amount of variation in the propiconazole dose, let's inspect the difference in yields for each dose.
 
-names(quant_PMy) <- c("Number of sprays", "2.5 percentile", "97.5 percentile")
-knitr::kable(quant_PMy)
-#             col.names = c("Number of sprays", "2.5 percentile", "97.5 percentile"))
-#            caption = "The 'upper' and 'lower' percentiles for yeild saved (t/Ha) against the number of Fungicide sprays in a season.
-Data from 2011-2017 mungbean experimental means.
-Data ignores factors such as fungicide, dose, season or location of experiment")
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PM <- PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-   group_by(total_Fungicide) %>%
-   summarise(lower = quantile(prop_YG, na.rm = T, c(0.025)),
-             upper = quantile(prop_YG, na.rm = T, c(0.975)))
-# Density plot of proportion of yield saved
-ggplot(subset(PM_MB_means,Fungicide != "control"), aes(prop_YG))+
-   geom_density(aes(group = factor(total_Fungicide), fill = factor(total_Fungicide)), alpha = 0.6)+
-   geom_vline(xintercept = 0, size =1)+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Density plot of the grain yield proportion saved \n by the number of fungicide applications")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   geom_vline(data = quant_PM, aes(xintercept = lower, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   geom_vline(data = quant_PM, aes(xintercept = upper, 
-               colour = factor(total_Fungicide)),size =0.9, linetype =  "dashed")+
-   guides(colour = guide_legend(title="Upper (97.5%) and \nLower (2.5%) percentiles"),
-          fill=guide_legend(title="Number of \nFungicide applications"))+
-   scale_x_continuous(limits = c(-0.3,0.55))
-names(quant_PM) <- c("Number of sprays", "2.5 percentile", "97.5 percentile")
-knitr::kable(quant_PM)   
-#knitr::kable(quant_PM, 
-#             col.names = c("Number of sprays", "2.5 percentile", "97.5 percentile"))
-             #caption = "The 'upper' and 'lower' percentiles for proportion of yeild saved against the number of Fungicide sprays in a season.
-Data from 2011-2017 mungbean experimental means.
-Data ignores factors such as fungicide, dose, season or location of experiment")
+```{r PropiDoseEffect}
+PM_MB_means %>%
+   filter(fungicide_ai == "propiconazole") %>%
+   ggplot(aes(x = relevel(as.factor(dose_ai.ha), "62.5"), y = prop_YG)) +
+   xlab("Dose (g ai/ha)") +
+   ggtitle(label = "Yield for each respective propiconazole dose") +
+   geom_boxplot() +
+   scale_fill_usq() +
+   scale_colour_usq() +
+   theme_usq()
 ```
 
-\n\n\n\n\n\n\n
+This dose effect should be acknowledged in the meta-analysis. How many treatments of each dose have been investigated per trial?
 
-#### Timing of Fungicide application
-The following density plots show mean yield saved (t/Ha) or proportion yield saved in relation to when the first fungicide spray was applied in relation to when powdery mildew was first seen in the mungbean crop.
-
-```{r echo = FALSE, message=FALSE, warning=FALSE}
-# removing 2017 and control data
-# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
-PM_MB_means1 <- PM_MB_means %>%
-   filter(Fungicide != "control") %>%
-   filter(Year != 2017) %>%
-#   filter(total_Fungicide ==1) %>%
-   mutate(days_from_1st = as.numeric(as.Date(Fungicide_application_1) - first_sign_disease))
-colnames(PM_MB_means)
-days_from_fungicid <- function(FSD,F1,F2,F3){
-   dF1 <- as.numeric(as.Date(F1) - as.Date(FSD))
-   dF2 <- as.numeric(as.Date(F2) - as.Date(FSD))
-   dF3 <- as.numeric(as.Date(F3) - as.Date(FSD))
-   if(is.na(dF1)){
-      return(NA)} else{
-   if(between(dF1,lower = -1, upper = 1000)){
-      return(dF1)}else{
-   if(is.na(dF2)){
-      return(dF1)}else{
-      if(between(dF2,lower = dF1, upper = -0.1)){
-            return(dF2)} else{
-               return(dF3)}}
-            }}
-}
-vec1<- vector()
-for(i in 1:dim(PM_MB_means1)[1]){
-   dF1 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_1)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
-   dF2 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_2)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
-   dF3 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_3)[i] - as.Date(PM_MB_means1$first_sign_disease)[i])
-   if(is.na(dF1)){
-      vec1 <- c(vec1,dF1)} else{
-         if(between(as.numeric(dF1),-1, 1000)){
-            vec1 <- c(vec1,dF1)}else{
-               if(is.na(dF2)){
-                  vec1 <- c(vec1,dF1)}else{
-                     if(between(as.numeric(dF2),as.numeric(dF1), -1.1)){
-            vec1 <- c(vec1,dF2)} else{
-               if(as.numeric(dF3)>=0){
-                  vec1 <- c(vec1,dF2)} else{
-                     vec1 <- c(vec1,dF3)}}}
-            }}
-}
-PM_MB_means1$spray_diff <- vec1 # gives the 
-PM_MB_means1$days_from_1st
-#summary(factor(PM_MB_means1$days_from_1st))
-# Density plot of proportion of yield saved
-ggplot(PM_MB_means1, aes(prop_YG))+
-   geom_density(aes(group = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20)), 
-                    fill = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20))), alpha = 0.3)+
-   geom_vline(xintercept = 0, size =1)+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="First spray window\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.3,0.55))
-###########################################3
-unique(PM_MB_means1$days_from_1st)
-ggplot(PM_MB_means1, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means1$days_from_1st, c(-41,-20,-15,-12,-0.5,1.5,7,10,12,20))~., factor(PM_MB_means1$Fungicide))+
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.2,0.55))
-unique(PM_MB_means1$spray_diff)
-ggplot(PM_MB_means1, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means1$spray_diff, c(-29,-20,-15,-12,-0.5,1.5,7,10,12,20))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means1$spray_diff, c(-29,-20,-15,-12,-0.5,1.5,7,10,12,20))~.)+
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.2,0.55))
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PM_prop <- PM_MB_means1 %>%
-   mutate(cut_daysfrom1st = cut(PM_MB_means1$days_from_1st, c(-15,-6,-0.5,0.5,2,10,20))) %>%
-   group_by(cut_daysfrom1st) %>%
-   summarise(lower = quantile(prop_YG, na.rm = T, c(0.025)),
-             upper = quantile(prop_YG, na.rm = T, c(0.975)))
-names(quant_PM_prop) <- c("Days relative to\nfirst incidence", "2.5 percentile", "97.5 percentile")
-cat("Lower (2.5) and Upper (97.5) quantiles for the proportion of yield gained, when the first fungicide applied relative to when powdery mildew is first seen")
-knitr::kable(quant_PM_prop)   
-ggplot(PM_MB_means1, aes(yield_gain))+
-   geom_density(aes(fill = cut(PM_MB_means1$days_from_1st, c(-29,-15,-6,-0.5,0.5,2,10,20))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means1$days_from_1st, c(-29,-15,-6,-0.5,0.5,2,10,20))~.)+
-   scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Grain yield (t/Ha) saved",
-   title = "Grain yield (t/Ha) saved, grouped by when the\nfirst fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.4,1.2))
-# Making a table of showing the upper and lower percentiles (95%)
-quant_PM_prop <- PM_MB_means1 %>%
-   mutate(cut_daysfrom1st = cut(PM_MB_means1$days_from_1st, c(-29,-20,-15,-6,-0.5,0.5,2,10,20))) %>%
-   group_by(cut_daysfrom1st) %>%
-   summarise(lower = quantile(yield_gain, na.rm = T, c(0.025)),
-             upper = quantile(yield_gain, na.rm = T, c(0.975)))
-names(quant_PM_prop) <- c("Days relative to\nfirst incidence", "2.5 percentile", "97.5 percentile")
-print("Yield gain quantiles when the first fungicide applied relative to when powdery mildew is first seen, Lower (2.5) and Upper (97.5) quantiles of yeild ")
-knitr::kable(quant_PM_prop)  
+```{r table_PropiDoses}
+table(as.character(PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole", ]$trial_ref),
+      PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole", ]$dose_ai.ha)
 ```
 
-```{r}
-PM_MB_means2 <- PM_MB_means1 %>%
-   filter(Fungicide == "Tebeconazole")
-unique(PM_MB_means2$spray_diff)
-ggplot(PM_MB_means2, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-1,2,7,10,12,20))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means2$spray_diff, c(1,2,7,10,12,20))~.)+
+Two trials show both doses were applied in the same trial, mung1112/01 and mung1112/02. Let look at the difference in proportion of yield saved in these trials.
+
+```{r PropiDoses_TrialCompar}
+boxplot_usq(prop_YG ~ dose_ai.ha,
+            data = PM_MB_means[(PM_MB_means$trial_ref == "mung1112/01" |
+                                   PM_MB_means$trial_ref == "mung1112/02") &
+                                  PM_MB_means$fungicide_ai == "propiconazole",])
+```
+
+This plot plot, however, indicated the previous plot might be skewed by high yielding trials.
+
+*****
+
+#### Number of fungicide sprays
+
+Let's look at the frequency of sprays per fungicide.  
+```{r Fungicide_x_nSprays}
+table(PM_MB_means$fungicide_ai, PM_MB_means$total_fungicide)
+```
+
+*****
+
+#### Timing of fungicide sprays  
+When are fungicides sprayed in relation to first sign.
+
+```{r spray_relative2FS}
+PM_MB_means %>%
+   mutate(
+      s1_DfromFS = fungicide_application_1 - first_sign_disease,
+      s2_DfromFS = fungicide_application_2 - first_sign_disease,
+      s3_DfromFS = fungicide_application_3 - first_sign_disease,
+      s4_DfromFS = fungicide_application_4 - first_sign_disease,
+      s5_DfromFS = fungicide_application_5 - first_sign_disease
+   ) %>%
+   gather(
+      key = spray,
+      value = n_days,
+      s1_DfromFS,
+      s2_DfromFS,
+      s3_DfromFS,
+      s4_DfromFS,
+      s5_DfromFS
+   ) %>%
+   drop_na(n_days) %>% 
+   ggplot(aes(x = spray, y = as.numeric(n_days))) +
+   geom_violin() +
+   scale_x_discrete(
+      labels = c(
+         "First\nspray",
+         "Second\nspray",
+         "Third\nspray",
+         "Fourth\nspray",
+         "Fifth\nspray"
+      )
+   ) +
+   theme_usq()
+```
+
+*****
+
+### Mungbean cultivars  
+In general, the mungbean varieties have the following resistance to powdery mildew.
+
+   - Berken: Highly susceptible
+
+   - Crystal: Susceptible
+
+   - Jade: Moderately susceptible
+
+Let's view a stacked bar plot of the number of sprays for both demethylation inhibitors, tebuconazole and propiconazole against each cultivar.
+
+```{r Host_genotype}
+PM_MB_means %>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole") %>%
+   group_by(host_genotype, fungicide_ai, trial_ref) %>%
+   summarise() %>%
+   count() %>%
+   rename(Treatments = n) %>%
+   ggplot(aes(x = host_genotype, y = Treatments, fill = fungicide_ai)) +
+   xlab("Cultivar") +
+   ylab("N Trials") +
+   ggtitle(label = "Cultivars used in either tebuconazole or propiconazole trials") +
+   geom_col() +
+   scale_fill_usq() +
+   scale_colour_usq() +
+   theme_usq()
+```
+
+&nbsp;
+
+#### Genotype yield variability
+
+Does host cultivar significantly impact the yield?
+Let's look at the volatility in yields to see if any cultivar yields better or has greater tolerance to powdery mildew.
+Below we plot distributions of mean trial yields for each cultivar.
+
+First lets look at overall yields for each cultivar, where trial is not a factor, for all treatments (spray and no spray).  
+```{r yield_vol}
+# this could be converted into a shiny app as a chunk. Make each input for the function a shiny option
+# Outputs the table and graph
+source("R/yield_volatility.r") #function to investigate the volatility in yields
+# Volitility is the range between the upper and lower 97.5 and 2.5 % quartiles
+
+YV1 <-
+   yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
+YV1[[2]]
+YV1[[3]]
+```
+Now lets look at overall yields for each cultivar, where trial is not a factor, in only the no spray treatments.
+```{r yieldVol_control}
+
+YV2 <-
+   yield_volatility(genotype_by_trial = FALSE, control_only = TRUE)
+YV2[[2]]
+YV2[[3]]
+```
+
+Volatility of the cultivars are fairly similar when trial is not considered as a factor (when we inspect plots of all treatments and only spray treatments).
+Green Diamond shows little volatility however this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trials.
+
+*****
+
+Lets examine the same plots as above but only for the most commonly used trial site, Hermitage.  
+```{r yieldVol_Herm}
+YV1_herm <-
+   yield_volatility(
+      genotype_by_trial = FALSE,
+      control_only = FALSE,
+      location = "Hermitage"
+   )
+YV1_herm[[2]]
+```
+
+Jade shows a large amount of volatility, excluding Green Diamond, Crystal shows the next least volatility.
+
+Lets take a closer look at Crystal with spray management treatments and without.  
+```{r YieldVol_Crystal}
+YV1_crystal <-
+   yield_volatility(genotype = "Crystal", control_only = FALSE)
+YV1_crystal[[2]]
+YV1_crystal <-
+   yield_volatility(genotype = "Crystal", control_only = TRUE)
+YV1_crystal[[2]]
+```
+
+There is a lot of variation between field trials for Crystal, but little variation within field trials.
+
+Lets look at Jade, to see if it differs.
+```{r YieldVol_Jade}
+YV2_crystal <- yield_volatility("Jade",control_only = FALSE)
+YV2_crystal[[2]]
+```
+
+For Jade there is high variation between trials and with in. Perhaps indicating lower tolerance. Lets look at the same plot with data only from no spray controls to see if the variation is the same.
+
+```{r YieldVol_JadeControl}
+YV3_crystal <- yield_volatility("Jade", control_only = TRUE)
+YV3_crystal[[2]]
+```
+
+There seems to be a noticeable shift in the probability curves between the two plots.
+Indicating that the tolerance in Jade may not as good as Crystal.
+A comparison between the fungicide efficacy for reducing powdery mildew severity and fungicide efficacy at mitigating yield loss.
+
+Overall there seems to be an influence of cultivar however this variation is not as distinct as the variation between trials.
+
+*****
+
+### Row spacing
+
+Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease.
+The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows in most cases increased yield significantly.
+This finding has also been shown by Kerry McKenzie's work as well.
+Eight trials used a row spacing of 0.75&nbsp;meters and tebuconazole as an active ingredient (AI).
+
+```{r row_spacing.m}
+PM_MB_means %>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole") %>%
+   group_by(fungicide_ai, row_spacing, trial_ref) %>%
+   summarise() %>%
+   count() %>%
+   rename(Trials = n) %>%
+   ggplot(aes(x = as.factor(row_spacing), y = Trials)) +
+   xlab("Row Spacing (m)") +
+   ylab("N Trials") +
+   ggtitle(label = "Trial row spacing using tebuconazole") +
+   geom_col(aes(fill = fungicide_ai),
+            position = "dodge") +
+   scale_fill_usq(name = "Fungicide AI") +
+   theme_usq()
+
+PM_MB_means %>%
+   filter(fungicide_ai == "tebuconazole",
+          row_spacing == 0.75) %>%
+   glimpse()
+```
+
+Lets plot the row spacing treatments for the response variables yield and disease severity. The main questions are:  
+   - Were there any statistical differences for mungbean yield or powdery mildew severity between row spacing treatments?  
+   - Can we pool certain row spacing that have no significant difference?
+
+```{r RS_severity}
+# Which row spacing leads to the higher disease severity
+PM_MB_means %>%
+   filter(year == 2017 |
+             year == 2018) %>%
+   filter(fungicide_ai == "control") %>%
+   ggplot(aes(y = PM_final_severity, x = factor(row_spacing))) +
+   geom_boxplot() +
+   ggtitle("Powdery mildew variation between different row spacing")
+```
+
+```{r RS_severity_x_trial}
+# Which row spacing leads to the higher disease severity
+PM_MB_means %>%
+   filter(year == 2017 |
+             year == 2018) %>%
+   filter(fungicide_ai == "control") %>%
+   ggplot(aes(y = PM_final_severity, x = factor(row_spacing))) +
+   geom_boxplot() +
+   facet_grid(cols = vars(location)) +
+   ggtitle("Powdery mildew variation between different row spacing")
+```
+
+In the Wellcamp site, wider row spacing reduces PM severity, the other sites it seems there was not enough variation to make a distinction between row spacing treatments.
+
+```{r RS_yield}
+# Which row spacing leads to the higher yeild potential
+PM_MB_means %>%
+   filter(year == 2017 |
+             year == 2018) %>%
+   #   filter(Fungicide == "control") %>%
+   ggplot(aes(
+      y = as.numeric(grain_yield.t.ha.),
+      x = row_spacing,
+      colour = location
+   )) +
+   geom_smooth(method = "gam") +
+   geom_jitter(width = 0.01) +
+   ggtitle("Grain yield results for different row spacing at three locations") +
+   xlab("Row spacing (m)") +
+   ylab("Grain yield - tonnes per hectare")
+```
+
+The plots seem to imply when yield is limited, presumably by other abiotic factors, there is no effect of row spacing on yield, like in the Hermitage trial.
+However, if the average yield is more than approximately 1 t/ha then smaller row spacing has the potential to provide greater yield per hectare.
+
+Overall row spacing may influence both powdery mildew severity and yield.
+
+*****
+
+### Yield vs in-season rain
+
+In crop rain could be a significant factor which contributes to the end of season grain yield.
+To investigate this effect I will use a linear model (GY ~ SR) where seasonal rainfall represents a specific time frame with respect to planting time.
+Multiple time frames were tested from 20 days prior to planting, to 100 days after planting.
+
+The multiple time frames were tested by a loop over the dates at the start of the season (to 90 days after planting) to find which date fits the best linear model for grain weight and in-crop rainfall.
+The code for this process was moved to be contained within it's own script and can be run as a job as it can take a long time.
+To speed up the computation I split the script into four, ran the jobs and bound the data into one frame.
+The output of the script is saved with the prefix `lmInSeasonRainfall` followed by the time windows the model is run.
+For example `lmInSeasonRainfall_20.40_50.80.csv` holds the model results for start days between 20 and 40 days after planting to end window dates between 50 and 80 days after planting.
+
+```{r rainfall_sum_Sstart}
+# The four data files were created from four scripts run as four jobs in Rstudio
+# when the four jobs are finished they can be imported and combined into one data.frame
+# source(Rainfall_x_cropYield_s-10.09_e30.65.R)
+# source(Rainfall_x_cropYield_s-10.09_e65.100.R)
+# source(Rainfall_x_cropYield_s10.30_e30.65.R)
+# source(Rainfall_x_cropYield_s10.30_e65.10.R)
+
+lm_rain1 <-
+   read.csv("data/lmInSeasonRainfall_-10.09_30.64.csv",
+            stringsAsFactors = FALSE)
+lm_rain2 <-
+   read.csv("data/lmInSeasonRainfall_-10.09_65.100.csv",
+            stringsAsFactors = FALSE)
+lm_rain3 <-
+   read.csv("data/lmInSeasonRainfall_10.30_30.64.csv",
+            stringsAsFactors = FALSE)
+lm_rain4 <-
+   read.csv("data/lmInSeasonRainfall_10.30_65.100.csv",
+            stringsAsFactors = FALSE)
+
+lm_rain <- rbind(lm_rain1, lm_rain2, lm_rain3, lm_rain4)
+```
+
+Now we have read in the data from the previously computed models lets find the linear model which has:  
+   - The lowest P value  
+   - the highest adjusted r squared value
+
+```{r WhichLModel}
+lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)), ]
+lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)), ]
+lm_rain[which(lm_rain$lm_adj_rsquared == max(lm_rain$lm_adj_rsquared)), ]
+```
+
+To visualise the model fits we will use a heat map to describe how the models faired in relation to the rainfall windows.
+log of the p value was used to improve the resolution of small very small p values.
+```{r rainLMpvalue}
+ggplot(lm_rain, aes(x = start_day, y = end_day, z = log(lm_pval))) +
+   geom_raster(aes(fill = log(lm_pval)), interpolate = TRUE) +
+   geom_contour(bins = 15, colour = "white") +
+   geom_point(data = lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)), ],
+              aes(x = start_day, y = end_day),
+              colour = " red") +
+   scale_fill_distiller(palette = "RdBu", direction = -1) 
+```
+
+```{r rainLMrsquared}
+ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_rsquared)) +
+   geom_raster(aes(fill = lm_rsquared), interpolate = TRUE) +
+   geom_contour(bins = 15, colour = "white") +
+   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)), ],
+              aes(x = start_day, y = end_day),
+              colour = " red") +
+   scale_fill_distiller(palette = "RdBu") 
+```
+
+```{r rainLMadjrsquared}
+ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_adj_rsquared)) +
+   geom_raster(aes(fill = lm_adj_rsquared), interpolate = TRUE) +
+   geom_contour(bins = 15, colour = "white") +
+   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)), ],
+              aes(x = start_day, y = end_day),
+              colour = " red") +
+   scale_fill_distiller(palette = "RdBu") 
+```
+
+The approximate period when in-crop rainfall impacts the most on the mean harvest is between 14 - 67 days after planting.
+
+*****
+
+### Season range and first incidence
+Mungbean is a summer crop and powdery mildew requires cool conditions to establish.
+Therefore the disease can be avoided by planting early in summer or spring, avoiding cooler temperatures at the end of some seasons.
+Can we visualise when PM is most likely to establish over the calender year?
+
+I'll build a plot of horizontal lines indicating the season length and use a dot on the line to indicating the day of the year first sign was observed for that trial.  
+```{r first_incidence}
+# Create the data frame for the plot
+season_dates <- PM_MB_means %>%
+   group_by(trial_ref) %>%
+   summarise(
+      Planting_date = unique(planting_date),
+      Harvest_date = unique(harvest_date),
+      First_sign_PM = unique(first_sign_disease),
+      season_length = as.integer(as.Date(unique(harvest_date)) - as.Date(unique(planting_date)))
+   )
+
+season_dates$Planting_day <- yday(season_dates$Planting_date)
+season_dates$Disease_day <- yday(season_dates$First_sign_PM)
+season_dates$Harvest_day <-
+   season_dates$Planting_day + season_dates$season_length
+
+season_dates[1, "Planting_day"] <-
+   yday(as.Date("2012-02-28") - 7) # planted in december and emerged in February, Assuming due to lack of rain or recording error. Using 7 days prior to emergence day as planting day
+
+first_day_month <- c(0, 31, 59, 90, 120, 151, 181, 211, 243, 273)
+axis_labels_date <-
+   c(
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[1], "%b-%d"),
+      # Jan
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[2], "%b-%d"),
+      # Feb
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[3], "%b-%d"),
+      # March
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[4], "%b-%d"),
+      # April
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[5], "%b-%d"),
+      # May
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[6], "%b-%d"),
+      # June
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[7], "%b-%d"),
+      # July
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[8], "%b-%d"),
+      # August
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[9], "%b-%d"),
+      # Sept
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[10], "%b-%d") # October
+   )
+
+# reorder the factors so they will appear in chronilogical order
+# I used First sign because all trials have recorded this
+season_dates$trial_ref <-
+   factor(season_dates$trial_ref,
+          levels = levels(season_dates$trial_ref)[rev(order(season_dates$First_sign_PM))])
+
+# Plot
+season_dates %>%
+   ggplot() +
+   geom_pointrange(aes(
+      x = trial_ref,
+      y = Disease_day,
+      ymin = Planting_day,
+      ymax = Harvest_day
+   )) +
+   scale_y_continuous(limits = c(
+      0,
+      max(
+         season_dates$Planting_day +
+            season_dates$season_length,
+         na.rm = TRUE
+      )
+   ),
+   labels = axis_labels_date,
+   breaks = first_day_month) +
+   geom_point(aes(x = trial_ref, y = Disease_day)) +
+   coord_flip() +
+   ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
+```
+
+In most years, regardless of the age of the crop, PM establishes in March.
+
+*****
+
+#### Effect of Fungicide
+
+**Fungicide effect on proportional yield gain with respect to time of application**  
+First lets look at the quantiles for each fungicide irrespective of other factors.
+We will focus on proportional yield gain, compared to no treatment control, as this should partially correct for some spatial and seasonal effects.  
+```{r fungicide_proportion_yield}
+PM_MB_means %>%
+   group_by(fungicide_ai) %>%
+   summarise(
+      n = length(prop_YG),
+      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
+      median = median(prop_YG, na.rm = T),
+      mean = mean(prop_YG, na.rm = T),
+      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
+   ) %>%
+   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
+   arrange(desc(median)) %>%
+   kable(caption = "Fungicide effect on proportion of yield gain") %>%
+   kable_styling(fixed_thead = T, full_width = T)
+
+# plot table as a box plot
+PM_MB_means %>%
+   filter(
+      fungicide_ai == c(
+         "200 g/L tebuconazole +\n120 g/L azoxystrobin" ,
+         "200 g/L azoxystrobin +\n80 g/L cyproconazole",
+         "tebuconazole",
+         "propiconazole",
+         "sulphur"
+      )
+   ) %>%
+   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
+   geom_boxplot() +
+   geom_hline(aes(yintercept = 0), size = 0.5) +
    #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
+   labs(x = "Proportion of grain yield saved",
+        title = "Grain yield proportion saved grouped by\nfungicide type") +
+   theme(
+      panel.grid.major = element_line(colour = "grey80"),
       panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.2,0.55))
-#__________________________________________________________________________________________________________
-levels(factor(PM_MB_means$Fungicide))
-PM_MB_means2 <- PM_MB_means1 %>%
-   filter(Fungicide == "Sulphur" |
-             Fungicide == "Sulphur (SC)" |
-             Fungicide == "Sulphur (Ultra SC)" |
-             Fungicide == "Sulphur (WP)")
-unique(PM_MB_means2$spray_diff)
-ggplot(PM_MB_means2, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))~.)+
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
-   scale_x_continuous(limits = c(-0.3,0.6))
-Chemical <- c("Amistar","Carbendazim","Tebeconazole", "propiconazole")
-levels(factor(PM_MB_means$Fungicide))
-for(Chem in Chemical){
-PM_MB_means2 <- PM_MB_means1 %>%
-   filter(Fungicide == Chem)
-cat(Chem)
-cat(unique(PM_MB_means2$spray_diff))
-p1 <- ggplot(PM_MB_means2, aes(prop_YG))+
-   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))), alpha = 0.5)+
-   geom_vline(aes(xintercept = 0), size =0.5)+
-   facet_grid(cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))~.)+
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yeild saved",
-   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
-   theme(panel.grid.major = element_line(colour = "grey80"),
-         panel.grid.minor = element_line(colour = "grey50"),
-         panel.background = element_rect(fill = NA))+
-   guides(fill=guide_legend(title=paste(Chem,"Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease")))+
-   scale_x_continuous(limits = c(-0.3,0.6))
-print(p1)
-Sys.sleep(10)
-}
+      panel.background = element_rect(fill = NA)
+   ) +
+   guides(fill = guide_legend(title = "Fungicide")) +
+   coord_flip()
 ```
+
+There was some hope groups of fungicide could be combined, _i.e._ propiconazole and tebuconazole, however it seems that they have different efficacies.
+Let us look to see if there is anything skewing the above.
+
+We need to also define the relationship between yield loss and disease severity. When exploring this data we should look primarily at the no spray control plots
+
+```{r yield_x_PMseverity}
+PM_MB_means %>%
+   filter(fungicide_ai == "control") %>%
+   ggplot(aes(x = PM_final_severity, y = grain_yield.t.ha.)) +
+   geom_point() +
+   geom_smooth(method = "lm")
+```
+
+From the data that we have, it is difficult to determine if there is an association between powdery mildew severity and grain yield.

### 2020-02-24 04_MetaAnalysis.Rmd
Use pacman

@@
----
-title: "Meta-analysis"
-author: "P. Melloy"
-date: "04/07/2019"
-output: html_document
----
+```{r MEsummary_Libraries2, message=FALSE}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer)
+
+if (!require("theme.usq")) devtools::install_github("adamhsparks/theme.usq")
+library(theme.usq)
+
+# Data
+slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
+```
 
 # Meta-analysis
+## Grain yield meta-analysis
 
-## Data-wrangling
+Lets get started with the analysis by first finding the best model fit that answers our research question.
 
-```{r}
-PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
-str(PM_MB_means)
-```
+> Which spray management scenario provides the greatest yield protection from powdery mildew.
 
-When investigating previous studies into Powdery Mildew Fungicide efficacy on Mungbean `r length(unique(PM_MB_means$Trial_ref))` trials were found, however only eleven Tebeconazol were used for the following meta-analysis, followed by the next common Fungicide Propiconazole.
-Sulphur was disregarded due to it's inconsistancy in efficacy.
+   - Grain yield is our response variable.  
+   - Trial, which resolves combinations of categorical variables: year, location, row spacing and cultivar; is set as a random intercept.  
+   - We will test spray management (our treatment) as a fixed effect and random slope to trial.
 
-```{r Fungicides}
-unique(PM_MB_means$Fungicide)
-PM_MB_means %>%
-   group_by(Fungicide,Trial_ref) %>%
-   summarise() %>%
-   count() %>%
-   rename(Trials = n) %>%
-   kable()
+```{r LME_slimmer_cluster_disease_mod}
+
+m8 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) +
+              (factor(spray_management) | trial_ref), 
+           data = slimmer_PM_dat)
+
+m9 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + 
+              (factor(spray_management) | trial_ref), 
+           data = slimmer_PM_dat)
+
+m10 <- lmer(log(grain_yield.t.ha*1000) ~ 
+               (factor(spray_management) | trial_ref), 
+           data = slimmer_PM_dat)
+
+m11 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + 
+              (1 | trial_ref), 
+           data = slimmer_PM_dat)
+
+anova(m8,m9) # m9 is significantly better model
+anova(m9,m10) # m9 is significantly better model
+anova(m9,m11) # m11 is a simpler model which is no different to m9
 
@@
 
-### Fungicide Doses
-All trials that used Tebeconazole used approimately the same dose. dose of the active ingredient ranged from 62.35 grams per hectare to 60 grams per hectare. 
-```{r Tebe_dose}
-PM_MB_means %>%
-   filter(Fungicide == "Tebeconazole") %>%
-   select(Trial_ref, Year, Location, first_sign_disease, Dose.ai.ha., total_Fungicide) %>%
-   kable()
+The best model from the four above is `m9` with the lower AIC of -29.357.
+
+```{r}
+summary(m9)
 ```
 
-### Row spacing
+This linear mixed effect model shows indicates:  
+   - A single early spray before first sign of powdery mildew is not likely to increase yields.  
+   - A single or single spray with one or more follow sprays starting  at the `recommended` first spray , within 3 days of powdery mildew first sign are likely to produce significantly higher grain yields compared to the no spray control.
+   - The `recommended_plus` spray which has one or more follow-up sprays after first sign are likley to increase the mean grain yield.  
+   - `Late_plus` spray treatments showed the highest mean grain yield, and was significantly higher than the no spray control. However showed no difference to either of the `recommended` treatments.
 
-Some experiments were designed to investigate the effect of row spacing and plant density on Powdery Mildew disease and crop yield.
-The results showed that shorter distances between rows increase crop yields and mitigated the yield impact of the disease.
+### Imputing sample variances
 
-```{r row_spacing}
-PM_MB_means %>%
-   filter(Fungicide == "Tebeconazole") %>%
-   group_by(row_spacing,Trial_ref) %>%
-   summarise() %>%
-   count() %>%
-   rename(Treatments = n) %>%
-   kable()
+We need to impute the variances which are missing for a few of the trials.
+These trials `r unique(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),c("location","year", "trial_ref")])$trial_ref` were analysed and reported that there was no significant difference between the treatments in each trial.
+So therefore we need the imputed variances not to show a significant difference.
+
+There are `r sum(is.na(slimmer_PM_dat$yield_error))` treatments without yield error in our data, and `r sum(!is.na(slimmer_PM_dat$yield_error))` where yield error was recorded.
+
+Plotting a histogram of the variances show that the yield is not normally distributed.
+A log transformation, however, shows a normal disrtubution.
+We can use the mean and standard deviation of the log(V) to sample variances for the treatments where V is missing.
+
+```{r variance_histograms}
+hist(slimmer_PM_dat$yield_error) # yield error is not normally distributed
+hist(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is normally distributed 
+```
+
+We will evaluate wheather the imputed variances confer a significant difference to the recorded means.
+I created a distance matrix of two standard errors above the mean against two standard errors below the mean.
+If any errors don't overlap, infering signicifant difference, the imputed variances are discarded and resampled until all treatment variances show no significant differences.
+
+```{r imputing_variances}
+
+# generate yield error values
+for(i in 0:500){
+
+   # Imputing missing log variances
+   log_Yerror <- rnorm(n = sum(is.na(slimmer_PM_dat$yield_error)),
+               mean = mean(log(slimmer_PM_dat$yield_error), na.rm = TRUE),
+               sd = sd(log(slimmer_PM_dat$yield_error), na.rm = TRUE))
+
+   # First lets convert Variance to standard error for all the variables that have variance recorded
+   slimmer_PM_dat$yield_SE <- 
+      sqrt(slimmer_PM_dat$yield_error)/sqrt(slimmer_PM_dat$n)
+
+   # Second; adding the imputed standard errors
+   slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"] <-
+      sqrt(exp(log_Yerror))/sqrt(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"n"])
+
+# all errorbars should overlap so they are consistant with the meta-data describing no significant difference bettween treatments
+# lets test to make sure
+if(
+   max(outer(X = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] -
+               (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+             Y = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] +
+               (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+             FUN = "-")
+       ) > 0){
+
+   message(paste("\nWarning!!: Imputed yield errors show significant differences when they should not, imputation will automatically rerun - iteration", "i =",i))
+   next()
+   }else{
+      message(paste(i,"iterations: ", "imputed variances now show no significant distances :)\n Now adding variances to data "))
+
+      # Plot the imputed errors for each trial
+      Vplot <- slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),] %>%
+         ggplot(aes(y = grain_yield.t.ha, trial))+
+         #geom_point()+
+         geom_pointrange(ymin = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] -
+                            (1.95*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+                         ymax = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] +
+                            (1.95*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
+                         position = "jitter"
+                         )+
+         ylim(0.2,1.5)
+
+      slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_error"] <- exp(log_Yerror)
+      print(Vplot)
+      break()}
+}
 
 ```
+
+The imputed variances calculated above don't show the expected positive correlation between grain yield and variance.
+This is unexpected and reflects the inherent variability of the data.
+Therefore we will calculate the trial mean squares and use this to calculate the variance for each sample.
+
+#### Imputing sample variances from Mean squares
+```{r imputing_MSE_dataSpread}
+slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
+hist(unique(slimmer_PM_dat$Y_Msquare))
+hist(log(unique(slimmer_PM_dat$Y_Msquare))) # log mean square has a more normal distribution
+
+```
+
+Imputing using a log transformation of the data is required. Which trials need variance imputation?
+
+```{r imputing_MSE}
+TrialMSQ <- slimmer_PM_dat %>%
+   group_by(trial_ref)%>%
+   summarise(unique(Y_Msquare))
+
+TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), "trial_ref"]
+```
+
+```{r imputation_MSE}
+
+for(i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`),]$trial_ref){
+   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i,"Y_Msquare"] <- 
+      exp(
+         rnorm(n = 1,
+               mean = mean(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE),
+               sd(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE)
+         )
+      )
+   }
+
+```
+
+Before analysis lets have a look at the trimmed down modified data.
+
+```{r treatment_means_plot}
+slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management, levels(slimmer_PM_dat$spray_management)[rev(c(1,2,4,5,3))])
+
+slimmer_PM_dat %>%
+   ggplot(aes(y = grain_yield.t.ha, x = spray_management))+
+   geom_boxplot()+
+   #geom_point(position = "jitter", alpha = 1/5)+
+   geom_jitter(width = 0.1, alpha = 1/5)+
+   theme_usq()+
+   labs(x = "Spray management variable", 
+        y = "Grain yield (t/Ha)",
+        title = "Mean grain yield from each treatment \n categorised by spray management scenario")+
+   theme(plot.title = element_text(hjust = 0.5))+
+   geom_hline(yintercept = 0, linetype = 2)+
+   coord_flip()
+```
+
+There seems like no difference between the treatments, with exception to Late_plus.
+Lets do this plot again, but use the proportion of yield increase compared to the no spray control as the response variable.
+
+It is also important to visualise how well the data is compared across the trial years and trials.
+
+```{r table_of_nTreatments}
+kableExtra::kable(table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year), align=rep('c', 8))%>%  #commented as was redering empty, needs a look in
+   kable_styling("striped", fixed_thead = TRUE, full_width = FALSE, position = "center")
+
+```
+Treatments Late_plus and early don't have very good comparison to other treatments.
+
+```{r plot_yieldProportion}
+slimmer_PM_dat$spray_management <-
+   factor(slimmer_PM_dat$spray_management,rev(c("control", "Early", "Recommended", "Recommended_plus","Late_plus")))
+
+slimmer_PM_dat %>%
+   ggplot(aes(y = prop_yield_gain, x = spray_management))+
+   geom_boxplot()+
+   #geom_point(position = "jitter", alpha = 1/5)+
+   geom_jitter(width = 0.1, alpha = 1/5)+
+   theme_usq()+
+   labs(x = "Spray management variable", 
+        y = "Grain yield (t/Ha)",
+        title = "Mean grain yield from each treatment \n categorised by spray management scenario")+
+   theme(plot.title = element_text(hjust = 0.5))+
+   geom_hline(yintercept = 0, linetype = 2)+
+   coord_flip()
+```
+
+## Meta-analysis  
+### metafor package  
+Let's load the metafor package we are using to analyse the data, then rearrange the factors we want to examine by placing the control treatment first.
+This way all treatments will be compared to the no spray controls.
+Next we are log transforming the grain yield and calculating the variance from the trial mean squares.  
+Finally we will assign factor classes to the main variables in the meta-analysis. Note that variable trial is a combination of:  
+   - Trial identifier  
+   - Trial year  
+   - Trial location  
+   - Host genotype  
+   - Trial row spacing
+
+```{r metafor_organisation}
+library(metafor)
+slimmer_PM_dat$spray_management <-
+   factor(slimmer_PM_dat$spray_management,c("control", "Early", "Recommended", "Recommended_plus","Late_plus"))
+
+slimmer_PM_dat$yi <- log(slimmer_PM_dat$grain_yield.t.ha)
+slimmer_PM_dat$vi <- slimmer_PM_dat$Y_Msquare/(slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha^2)
+
+slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management)
+slimmer_PM_dat$trial_ref <- factor(slimmer_PM_dat$trial_ref)
+slimmer_PM_dat$trial <- factor(slimmer_PM_dat$trial)
+```
+
+```{r Metafor-analysis}
+
+PM_mv_AI <- rma.mv(yi,vi,
+                   mods = ~ spray_management,
+                   method = "ML",
+                   random = list(~ spray_management | trial),
+                   struct = "UN",
+                   data = slimmer_PM_dat)
+
+summary(PM_mv_AI)
+
+```
+
+Results show that yields in single early spray treatments are not significantly different to the no spray control.
+Commencing spray manangement schedules at first sign of disease (Recommended), or between 7 - 19 days after first sign (late) produced significantly higher yields compared to the no spray control.
+On average a spray scheduale with two or more applications stating late (7-19 days after first sign of powdery mildew) produced the highest yields.
+
+When we compare these results to those of the linear mixed effect model there is little difference in the outcome.
+The most noteable difference is the linear mixed-effect model is somewhat less certain about the `Late_plus` treatment, and the mean yield lower than the `recommended_plus` treatment.
+
+```{r compare_meta&lmer}
+lme_PM <- lmer(yi ~ spray_management + (spray_management | trial), data = slimmer_PM_dat)
+
+summary(lme_PM)
+
+```
+&nbsp;  
+&nbsp;  
+To make it easier to compare each of the treatments we can compute the meta-analysis contrasts.
+```{r metafor_contrasts}
+anova(PM_mv_AI, L=rbind(c(0,1,-1,0,0),  # early vs Recomended
+                        c(0,1,0,-1,0),  # early vs recommended plus
+                        c(0,1,0,0,-1),  # early vs Late plus
+                        c(0,0,-1,1,0),  # Recommended vs recommended_plus
+                        c(0,0,-1,0,1),  # Recommended vs Late_Plus
+                        c(0,0,0,-1,1))) # recommended_plus vs Late_plus
+```
+Results show with the exclusion of the no spray control, none of the treatments are significantly different, however, early applications treatments on average produced lower yields.
+Lets view this on a plot.
+
+```{r metafor_results}
+results_AI <- data.frame(cbind(exp(PM_mv_AI$b), 
+                              exp((PM_mv_AI$ci.lb)),
+                              exp(PM_mv_AI$ci.ub)))
+
+# results_AI <- data.frame(cbind(PM_mv_AI$b, 
+#                               (PM_mv_AI$ci.lb),
+#                               PM_mv_AI$ci.ub))
+
+treat <- c("control", "Early", "Recommended", "Recommended_plus","Late_plus")
+efficacy <- tbl_df(results_AI)
+efficacy$treat <- treat
+efficacy$se <- PM_mv_AI$se
+colnames(efficacy) <- c("Mean", "CIs_lower", "CI_upper", "Treatment", "SE")
+efficacy
+```
+
+```{r metafor_plot}
+efficacy$Treatment <-
+   factor(efficacy$Treatment,c("control", "Early", "Recommended", "Recommended_plus","Late_plus"))
+
+efficacy %>% 
+   ggplot(aes(Treatment, Mean))+
+   geom_hline(yintercept = c(0.8,1,1.2,1.4), color = "grey80", linetype = 3)+
+   geom_point(aes(size=1/SE), shape=15)+
+   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper))+
+   coord_flip()+
+   theme_usq()
+
+```
+
+What is interesting here is that the variance in the control has increased while the treatments have decreased.
+This is despite the control being the best represented across all experiments.
+However it could also be because it also has a low number of pooled reps per trial.
+Lets look at how well each of the treatments compare to each other.
+We can use the netmeta package to give a graphical representation of this.
+
+### netmeta package  
+Lets analyse the data again using a different statistical approach to see if our outcome with the `metafor` package was robust.
+The `netmeta` package uses a frequentist approach to the analysis, and focuses on the pairwise comparisons between treatments.
+
+```{r netmeta-analysis}
+library(netmeta)
+
+datPM3 <- slimmer_PM_dat %>% 
+   group_by(trial, spray_management, n) %>% 
+      summarize(yi_mean = mean(yi), 
+             vi_mean = mean(vi)) %>% 
+   ungroup()
+
+PM_con <- pairwise(treat = spray_management,
+                  n = n,
+                  mean = yi_mean,
+                  sd = sqrt(vi_mean),
+                  studlab= trial,
+                  data = datPM3, 
+                  sm="MD")
+
+net_con <- netmeta(TE, 
+                seTE, 
+                treat1, 
+                treat2, 
+                studlab, 
+                data=PM_con, 
+                sm="MD")
+
+summary(net_con)
+
+```
+Now lets visualise this as a forest plot
+
+```{r netmeta-forest}
+forest(net_con, reference.group = 4,
+       rightcols=c("effect", "ci", "Pscore"),
+       rightlabs="P-Score", small.values = "bad")
+
+```
+
+The `netmeta` analysis suggests the spray scheduale commencing early are no different to any other treatment including the no spray control.
+It estimates the mean is very similar to the recommended treatments.
+The recommended plus and late_plus treatments show higher mean estimates, however not significantly different from the early estimate.
+
+```{r netgraphGW}
+netgraph(net_con, 
+         plastic = FALSE,
+         col = "orange",
+         thickness =  "number.of.studies",
+         points = FALSE, 
+         col.points = "black", 
+         cex.points = 1,
+         number.of.studies = TRUE,
+         cex.number.of.studies = 1,
+         col.number.of.studies = "black",
+         bg.number.of.studies = "orange",
+         multiarm = FALSE,
+         col.multiarm = "lightblue",
+         pos.number.of.studies = 0.5)
+```
+
+```{r}
+netleague(net_con)
+```
+
+```{r}
+decomp.design(net_con)
+```
+
+```{r}
+netsplit(net_con)
+```
+```{r}
+nm1 <- netmeasures(net_con)
+
+plot(nm1$meanpath, nm1$minpar, pch="",
+     xlab="Mean path length", ylab="Minimal parallelism")
+text(nm1$meanpath, nm1$minpar, names(nm1$meanpath), cex=0.8)
+```
+
+```{r Save_meta_data}
+write.csv(slimmer_PM_dat, file = "data/GYmeta_data.csv")
+
+```

### 2020-02-24 05_AUDPC_MetaAnalysis.Rmd
Use pacman

--- 2020-02-17 06_AUDPC_MetaAnalysis.Rmd
@@
 ```{r MEsummary_Libraries1, message=FALSE}
-# install.packages("tidyverse")
-# install.packages("devtools")
-# devtools::install_github("https://github.com/PaulMelloy/bomrang")
-# devtools::install_github("https://github.com/adamhsparks/theme.usq", dependencies = TRUE)
-# install.packages("lme4")
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer)
 
-library(RColorBrewer)
-library(tidyverse)
+if (!require("theme.usq")) devtools::install_github("adamhsparks/theme.usq")
 library(theme.usq)
-library(bomrang)
-library(lme4)
-library(kableExtra)
 

### 2020-02-24 06_Publication_wireframe_and_8Questions.Rmd
Use pacman

@@
 
+# Manuscript wireframe
+
 ## Who are the intended readers? - list 3 to 5 of them by name  
-   * Adam Sparks – disease modeler  
+   * Adam Sparks – Plant disease modeller  
    * Levente Kiss – Powdery mildew taxonomist  
@@
 
-## what is the key benefit for your readers? (limit - 25 words).  
+## What is the key benefit for your readers? (limit - 25 words).  
 This study is the most robust analysis of management of powdery mildew in mungbean using fungicides.

### 2020-02-24 R/import_data.R
check working dir more portably

@@ -11,7 +11,7 @@
 #'
 
 import_data <- function() {
-   if (getwd() == "C:/Users/U8011054/OneDrive - USQ/Cloudstor/R/Mungbean_projects/Mungbean_PM/DataWrangle") {
+   if (basename(getwd()) == "DataWrangle") {
       x <- read.csv(file = "../data/PM_MB_updated.csv")
    } else{
       x <- read.csv(file = "data/PM_MB_updated.csv")

### 2020-02-24 02_Preliminary_analysis.Rmd
Mainly grammar changes

@@
 ```{r PA_Libraries, include=FALSE, message=FALSE}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, lubridate, bomrang, openxlsx, devtools, reshape2, lme4)
+if (!require("pacman"))
+   install.packages("pacman")
+pacman::p_load(tidyverse,
+               lubridate,
+               bomrang,
+               openxlsx,
+               devtools,
+               reshape2,
+               lme4,
+               kableExtra)
 source("R/import_data.R")
-if (!require("theme.usq")) devtools::install_github("adamhsparks/theme.usq")
+if (!require("theme.usq"))
+   devtools::install_github("adamhsparks/theme.usq")
 library(theme.usq)
 #source("./getPPD2.R")
-theme_set(theme_usq())
+theme_set(theme_usq()
+)
 ```
@@
    ) +
+   ylab("Days to First Sign of Disease") +
    theme_usq()
@@
 
-First lets look at overall yields for each cultivar, where trial is not a factor, for all treatments (spray and no spray).  
+First let's look at overall yields for each cultivar, where trial is not a factor, for all treatments (spray and no spray).  
 ```{r yield_vol}
@@
 ```
-Now lets look at overall yields for each cultivar, where trial is not a factor, in only the no spray treatments.
+Now let's look at overall yields for each cultivar, where trial is not a factor, in only the no spray treatments.
 ```{r yieldVol_control}
@@
 
-Lets examine the same plots as above but only for the most commonly used trial site, Hermitage.  
+Let's examine the same plots as above but only for the most commonly used trial site, Hermitage.  
 ```{r yieldVol_Herm}
@@
 
-Lets take a closer look at Crystal with spray management treatments and without.  
+*****
+
+Let's take a closer look at Crystal with spray management treatments and without.  
 ```{r YieldVol_Crystal}
@@
 
-Lets look at Jade, to see if it differs.
+Let's look at Jade, to see if it differs.
 ```{r YieldVol_Jade}
@@
 
-For Jade there is high variation between trials and with in. Perhaps indicating lower tolerance. Lets look at the same plot with data only from no spray controls to see if the variation is the same.
+For Jade there is high variation between trials and with in. Perhaps indicating lower tolerance. Let's look at the same plot with data only from no spray controls to see if the variation is the same.
 
@@
 
-Lets plot the row spacing treatments for the response variables yield and disease severity. The main questions are:  
-   - Were there any statistical differences for mungbean yield or powdery mildew severity between row spacing treatments?  
-   - Can we pool certain row spacing that have no significant difference?
+Let's plot the row spacing treatments for the response variables yield and disease severity. The main questions are:
+
+   * Were there any statistical differences for mungbean yield or powdery mildew severity between row spacing treatments?
+
+   * Can we pool certain row spacing that have no significant difference?
 
@@
 
-Now we have read in the data from the previously computed models lets find the linear model which has:  
+Now we have read in the data from the previously computed models let's find the linear model which has:  
    - The lowest P value  
@@
 **Fungicide effect on proportional yield gain with respect to time of application**  
-First lets look at the quantiles for each fungicide irrespective of other factors.
+First let's look at the quantiles for each fungicide irrespective of other factors.
 We will focus on proportional yield gain, compared to no treatment control, as this should partially correct for some spatial and seasonal effects.  

### 2020-02-24 03_Prep_data.Rmd
Use pacman
Grammar and code formatting changes

--- 2020-02-17 04_Prep_data.Rmd
@@
 
-```{r load_libraries}
-library(dplyr)
-library(readr)
-library(kableExtra)
-library(ggplot2)
-library(agricolae)
+```{r load_libraries, include=FALSE}
+if (!require("pacman"))
+   install.packages("pacman")
+pacman::p_load(tidyverse, kableExtra, agricolae
+)
 ```
@@
    group_by(trial_ref, location, Y_error_type, fungicide_ai) %>%
-   summarise(DMI_trts = length(Y_error_type))%>%
-   arrange(Y_error_type)%>%
+   summarise(DMI_trts = length(Y_error_type)) %>%
+   arrange(Y_error_type) %>%
    kable(caption = "Number of treatments for each trial and the error type reported") %>%
@@
    footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
-
 ```
@@
 Trials <- PM_MB_means %>%
-   filter(
-          Y_error_type == "lsd (P=0.05)") %>%
+   filter(Y_error_type == "lsd (P=0.05)") %>%
    select(trial_ref) %>%
@@
    DFw <-
-      sum(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates) -
-      length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates) # degrees of freedom within groups
+      sum(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates) -
+      length(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates) # degrees of freedom within groups
 
    LSD <-
-      PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error[1]
+      PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$yield_error[1]
 
    V_yield <-
-      (PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[1] * (LSD /
+      (PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates[1] * (LSD /
                                                                             Tcrit) ^ 2) / 2 # method - Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
 
-   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates)) {
+   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates)) {
       if (j == 1) {
          Sv <-
-            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates))
+            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates))
       } # reset Sv vector if this is the first loop
@@
       Sv[j] = V_yield /
-         PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j]
+         PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates[j]
 
@@
 
-   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error <-
+   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$yield_error <-
       Sv
-   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$Y_error_type <-
+   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Y_error_type <-
       "SamplingVariance"
@@
 
-for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error)) {
+for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$yield_error)) {
    if (j == 1) {
       Sv <-
-         vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error))
+         vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$yield_error))
    }# create empty vector at first iteration with length of j
 
-   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error[j]) ^
+   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$yield_error[j]) ^
       2
@@
 # and replacing the values in the dataset
-PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error <-
+PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$yield_error <-
    Sv
-PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$Y_error_type <-
+PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$Y_error_type <-
    "SamplingVariance"
-
 ```
@@
 for (i in unique(PM_MB_means$trial_ref)) {
-   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
+   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i,]
 
@@
    for (j in unique(dat1$row_spacing)) {
-      dat2 <- dat1[dat1$row_spacing == j, ]
+      dat2 <- dat1[dat1$row_spacing == j,]
       controlY <-
@@
 
-      dat1[dat1$row_spacing == j, ] <- dat2
+      dat1[dat1$row_spacing == j,] <- dat2
    }
-   PM_MB_means[PM_MB_means$trial_ref == i, ] <- dat1
+   PM_MB_means[PM_MB_means$trial_ref == i,] <- dat1
 }
@@
 
-dat1 <- PM_MB_means[PM_MB_means$trial_ref == "AM1303", ]
+dat1 <- PM_MB_means[PM_MB_means$trial_ref == "AM1303",]
 
@@
 dat1$prop_YG <- dat1$yield_gain / controlY
-dat1[dat1$fungicide_ai == "control", c("yield_gain", "prop_YG")] <- c(NA,NA)
-PM_MB_means[PM_MB_means$trial_ref == "AM1303", ] <- dat1
+dat1[dat1$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
+   c(NA, NA)
+PM_MB_means[PM_MB_means$trial_ref == "AM1303",] <- dat1
 
@@
 ## Reduce data set to required variables  
-Lets tidy up the data set into a data frame of only the variables which are required for the analysis.
+Let's tidy up the data set into a data frame of only the variables which are required for the analysis.
 
@@
 ```{r cluster}
-
 slim_PM_dat %<>%
@@
    )
-
 ```
 
-Lets look at these clusters to see where we have the most degrees of freedom.
+Let's look at these clusters to see where we have the most degrees of freedom.
 
 ```{r cluster_clusters}
+clusters <-
+   unique(slim_PM_dat[c("cluster_1", "cluster_2", "cluster_3")])
 
-clusters <- unique(slim_PM_dat[c("cluster_1","cluster_2","cluster_3")])
+for (i in 1:nrow(clusters)) {
+   if (i == 1) {
+      clusters$n <- NA
+      clusters$n_x_trial <- NA
+   }
 
-for(i in 1:nrow(clusters)){
-   if(i == 1){clusters$n <- NA
-   clusters$n_x_trial <- NA}
+   clusters[i, "n"] <-
+      nrow(slim_PM_dat[slim_PM_dat$cluster_1 == clusters[i, "cluster_1"] &
+                          slim_PM_dat$cluster_2 == clusters[i, "cluster_2"] &
+                          slim_PM_dat$cluster_3 == clusters[i, "cluster_3"],])
 
-   clusters[i,"n"] <- nrow(slim_PM_dat[slim_PM_dat$cluster_1 == clusters[i,"cluster_1"] &
-                                          slim_PM_dat$cluster_2 == clusters[i,"cluster_2"] &
-                                          slim_PM_dat$cluster_3 == clusters[i,"cluster_3"],
-                                       ])
-
-   clusters[i,"n_x_trial"] <- length(unique(slim_PM_dat[slim_PM_dat$cluster_1 == clusters[i,"cluster_1"] &
-                                          slim_PM_dat$cluster_2 == clusters[i,"cluster_2"] &
-                                          slim_PM_dat$cluster_3 == clusters[i,"cluster_3"],
+   clusters[i, "n_x_trial"] <-
+      length(unique(slim_PM_dat[slim_PM_dat$cluster_1 == clusters[i, "cluster_1"] &
+                                   slim_PM_dat$cluster_2 == clusters[i, "cluster_2"] &
+                                   slim_PM_dat$cluster_3 == clusters[i, "cluster_3"],
                                 "trial_ref"]))
@@
 knitr::kable(clusters)
-
 ```
@@
 ```{r simple_clusters}
-
 slim_PM_dat <- slim_PM_dat %>%
@@
 slim_PM_dat[slim_PM_dat$fungicide_ai == "control",
-            c("fungicide_timing_1", "fungicide_timing_2", "fungicide_timing_3",
+            c(
+               "fungicide_timing_1",
+               "fungicide_timing_2",
+               "fungicide_timing_3",
                "spray_management"
@@
 
-Our data currently uses sample variance to define the yield error. We should expect that when yield increases so does the variance. Lets quickly plot this to check.
+Our data currently uses sample variance to define the yield error. We should expect that when yield increases so does the variance. Let's quickly plot this to check.
 
@@
 
-We would expect to see grain yield decline with increasing AUDPC. Lets just plot yield vs AUDPC.
+We would expect to see grain yield decline with increasing AUDPC. Let's just plot yield vs AUDPC.
 
@@
 Perhaps the variation due to trial location, season, row spacing, and other seasonal variables are preventing us from seeing a relationship.
-Lets do the plot again for each trial where there are no missing values.
+Let's do the plot again for each trial where there are no missing values.
 Note: The plots are ordered by mean yield of the trial.
@@
 
-Lets have a look again at the same sequance of graphs and analyses for area under the disease progress _stairs_.
+Let's have a look again at the same sequance of graphs and analyses for area under the disease progress _stairs_.
 
@@
 
-summary(lm(grain_yield.t.ha ~ AUDPS_m, data = PM_MB_means))
+summary(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means))
 

### 2020-02-24 04_MetaAnalysis.Rmd
Grammar and code formatting changes

--- 2019-07-04 04_MetaAnalysis.Rmd
@@
----
-title: "Meta-analysis"
-author: "P. Melloy"
-date: "04/07/2019"
-output: html_document
----
+```{r MEsummary_Libraries2, message=FALSE}
+if (!require("pacman"))
+   install.packages("pacman")
+pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer)
+
+if (!require("theme.usq"))
+   devtools::install_github("adamhsparks/theme.usq")
+library(theme.usq)
+theme_set(theme_usq())
+
+# Data
+slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv"
+)
+```
 
 # Meta-analysis
+## Grain yield meta-analysis
 
-## Data-wrangling
+Let's get started with the analysis by first finding the best model fit that answers our research question.
+
+> Which spray management scenario provides the greatest yield protection from powdery mildew.
+
+   - Grain yield is our response variable.  
+   - Trial, which resolves combinations of categorical variables: year, location, row spacing and cultivar; is set as a random intercept.  
+   - We will test spray management (our treatment) as a fixed effect and random slope to trial.
+
+```{r LME_slimmer_cluster_disease_mod}
+m8 <- lmer(grain_yield.t.ha * 1000 ~ factor(spray_management) +
+              (factor(spray_management) | trial_ref),
+           data = slimmer_PM_dat)
+
+m9 <- lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
+              (factor(spray_management) | trial_ref),
+           data = slimmer_PM_dat)
+
+m10 <- lmer(log(grain_yield.t.ha * 1000) ~
+               (factor(spray_management) | trial_ref),
+            data = slimmer_PM_dat)
+
+m11 <- lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
+               (1 | trial_ref),
+            data = slimmer_PM_dat)
+
+anova(m8, m9) # m9 is significantly better model
+anova(m9, m10) # m9 is significantly better model
+anova(m9, m11) # m11 is a simpler model which is no different to m9
+```
+
+The best model from the four above is `m9` with the lower AIC of -29.357.
 
 ```{r}
-PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")
-str(PM_MB_means)
+summary(m9)
 ```
 
-When investigating previous studies into Powdery Mildew Fungicide efficacy on Mungbean `r length(unique(PM_MB_means$Trial_ref))` trials were found, however only eleven Tebeconazol were used for the following meta-analysis, followed by the next common Fungicide Propiconazole.
-Sulphur was disregarded due to it's inconsistancy in efficacy.
+This linear mixed effect model shows indicates:
 
-```{r Fungicides}
-unique(PM_MB_means$Fungicide)
-PM_MB_means %>%
-   group_by(Fungicide,Trial_ref) %>%
-   summarise() %>%
-   count() %>%
-   rename(Trials = n) %>%
-   kable()
+   - A single early spray before first sign of powdery mildew is not likely to increase yields.
+
+   - A single or single spray with one or more follow sprays starting  at the `recommended` first spray , within 3 days of powdery mildew first sign are likely to produce significantly higher grain yields compared to the no spray control.
+
+   - The `recommended_plus` spray which has one or more follow-up sprays after first sign are likely to increase the mean grain yield.
+
+   - `Late_plus` spray treatments showed the highest mean grain yield, and was significantly higher than the no spray control. However showed no difference to either of the `recommended` treatments.
+
+### Imputing sample variances
+
+We need to impute the variances which are missing for a few of the trials.
+These trials `r unique(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),c("location","year", "trial_ref")])$trial_ref` were analysed and reported that there was no significant difference between the treatments in each trial.
+So therefore we need the imputed variances not to show a significant difference.
+
+There are `r sum(is.na(slimmer_PM_dat$yield_error))` treatments without yield error in our data, and `r sum(!is.na(slimmer_PM_dat$yield_error))` where yield error was recorded.
+
+Plotting a histogram of the variances show that the yield is not normally distributed.
+A log transformation, however, shows a normal distribution.
+We can use the mean and standard deviation of the log(V) to sample variances for the treatments where V is missing.
+
+```{r variance_histograms}
+hist(slimmer_PM_dat$yield_error) # yield error is not normally distributed
+hist(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is normally distributed 
+```
+
+We will evaluate whether the imputed variances confer a significant difference to the recorded means.
+I created a distance matrix of two standard errors above the mean against two standard errors below the mean.
+If any errors don't overlap, inferring significant difference, the imputed variances are discarded and re-sampled until all treatment variances show no significant differences.
+
+```{r imputing_variances}
+# generate yield error values
+for (i in 0:500) {
+   # Imputing missing log variances
+   log_Yerror <- rnorm(
+      n = sum(is.na(slimmer_PM_dat$yield_error)),
+      mean = mean(log(slimmer_PM_dat$yield_error), na.rm = TRUE),
+      sd = sd(log(slimmer_PM_dat$yield_error), na.rm = TRUE)
+   )
+
+   # First let's convert Variance to standard error for all the variables that have variance recorded
+   slimmer_PM_dat$yield_SE <-
+      sqrt(slimmer_PM_dat$yield_error) / sqrt(slimmer_PM_dat$n)
+
+   # Second; adding the imputed standard errors
+   slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"] <-
+      sqrt(exp(log_Yerror)) / sqrt(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "n"])
+
+   # all errorbars should overlap so they are consistant with the meta-data describing no significant difference bettween treatments
+   # let's test to make sure
+   if (max(outer(
+      X = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] -
+      (2 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
+      Y = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] +
+      (2 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
+      FUN = "-"
+   )) > 0) {
+      message(
+         paste(
+            "\nWarning!!: Imputed yield errors show significant differences when they should not, imputation will automatically rerun - iteration",
+            "i =",
+            i
+         )
+      )
+      next()
+   } else{
+      message(
+         paste(
+            i,
+            "iterations: ",
+            "imputed variances now show no significant distances :)\n Now adding variances to data "
+         )
+      )
+
+      # Plot the imputed errors for each trial
+      Vplot <-
+         slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),] %>%
+         ggplot(aes(y = grain_yield.t.ha, trial)) +
+         #geom_point()+
+         geom_pointrange(
+            ymin = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] -
+               (1.95 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
+            ymax = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] +
+               (1.95 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
+            position = "jitter"
+         ) +
+         ylim(0.2, 1.5)
+
+      slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_error"] <-
+         exp(log_Yerror)
+      print(Vplot)
+      break()
+   }
+}
+```
+
+The imputed variances calculated above don't show the expected positive correlation between grain yield and variance.
+This is unexpected and reflects the inherent variability of the data.
+Therefore we will calculate the trial mean squares and use this to calculate the variance for each sample.
+
+#### Imputing sample variances from Mean squares
+```{r imputing_MSE_dataSpread}
+slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
+hist(unique(slimmer_PM_dat$Y_Msquare))
+hist(log(unique(slimmer_PM_dat$Y_Msquare))) # log mean square has a more normal distribution
 
@@
 
-### Fungicide Doses
-All trials that used Tebeconazole used approimately the same dose. dose of the active ingredient ranged from 62.35 grams per hectare to 60 grams per hectare. 
-```{r Tebe_dose}
-PM_MB_means %>%
-   filter(Fungicide == "Tebeconazole") %>%
-   select(Trial_ref, Year, Location, first_sign_disease, Dose.ai.ha., total_Fungicide) %>%
-   kable()
+Imputing using a log transformation of the data is required. Which trials need variance imputation?
+
+```{r imputing_MSE}
+TrialMSQ <- slimmer_PM_dat %>%
+   group_by(trial_ref)%>%
+   summarise(unique(Y_Msquare))
+
+TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), "trial_ref"]
 ```
 
-### Row spacing
+```{r imputation_MSE}
+for (i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`),]$trial_ref) {
+   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "Y_Msquare"] <-
+      exp(rnorm(
+         n = 1,
+         mean = mean(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE),
+         sd(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE)
+      ))
+}
+```
 
-Some experiments were designed to investigate the effect of row spacing and plant density on Powdery Mildew disease and crop yield.
-The results showed that shorter distances between rows increase crop yields and mitigated the yield impact of the disease.
+Before analysis let's have a look at the trimmed down modified data.
 
-```{r row_spacing}
-PM_MB_means %>%
-   filter(Fungicide == "Tebeconazole") %>%
-   group_by(row_spacing,Trial_ref) %>%
-   summarise() %>%
-   count() %>%
-   rename(Treatments = n) %>%
-   kable()
+```{r treatment_means_plot}
+slimmer_PM_dat$spray_management <-
+   factor(slimmer_PM_dat$spray_management,
+          levels(slimmer_PM_dat$spray_management)[rev(c(1, 2, 4, 5, 3))])
+
+slimmer_PM_dat %>%
+   ggplot(aes(y = grain_yield.t.ha, x = spray_management)) +
+   geom_boxplot() +
+   #geom_point(position = "jitter", alpha = 1/5)+
+   geom_jitter(width = 0.1, alpha = 1 / 5) +
+   theme_usq() +
+   labs(x = "Spray management variable",
+        y = "Grain yield (t/Ha)",
+        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
+   theme(plot.title = element_text(hjust = 0.5)) +
+   geom_hline(yintercept = 0, linetype = 2) +
+   coord_flip()
+```
+
+There seems like no difference between the treatments, with exception to Late_plus.
+Let's do this plot again, but use the proportion of yield increase compared to the no spray control as the response variable.
+
+It is also important to visualise how well the data is compared across the trial years and trials.
+
+```{r table_of_nTreatments}
+kableExtra::kable(table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year),
+                  align = rep('c', 8)) %>%  #commented as was redering empty, needs a look in
+   kable_styling(
+      "striped",
+      fixed_thead = TRUE,
+      full_width = FALSE,
+      position = "center"
+   )
+```
+Treatments Late_plus and early don't have very good comparison to other treatments.
+
+```{r plot_yieldProportion}
+slimmer_PM_dat$spray_management <-
+   factor(slimmer_PM_dat$spray_management, rev(
+      c(
+         "control",
+         "Early",
+         "Recommended",
+         "Recommended_plus",
+         "Late_plus"
+      )
+   ))
+
+slimmer_PM_dat %>%
+   ggplot(aes(y = prop_yield_gain, x = spray_management)) +
+   geom_boxplot() +
+   #geom_point(position = "jitter", alpha = 1/5)+
+   geom_jitter(width = 0.1, alpha = 1 / 5) +
+   theme_usq() +
+   labs(x = "Spray management variable",
+        y = "Grain yield (t/Ha)",
+        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
+   theme(plot.title = element_text(hjust = 0.5)) +
+   geom_hline(yintercept = 0, linetype = 2) +
+   coord_flip()
+```
+
+## Meta-analysis  
+### metafor package  
+Let's load the metafor package we are using to analyse the data, then rearrange the factors we want to examine by placing the control treatment first.
+This way all treatments will be compared to the no spray controls.
+Next we are log transforming the grain yield and calculating the variance from the trial mean squares.  
+Finally we will assign factor classes to the main variables in the meta-analysis. Note that variable trial is a combination of:  
+   - Trial identifier  
+   - Trial year  
+   - Trial location  
+   - Host genotype  
+   - Trial row spacing
+
+```{r metafor_organisation}
+library(metafor)
+slimmer_PM_dat$spray_management <-
+   factor(
+      slimmer_PM_dat$spray_management,
+      c(
+         "control",
+         "Early",
+         "Recommended",
+         "Recommended_plus",
+         "Late_plus"
+      )
+   )
+
+slimmer_PM_dat$yi <- log(slimmer_PM_dat$grain_yield.t.ha)
+slimmer_PM_dat$vi <-
+   slimmer_PM_dat$Y_Msquare / (slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha ^
+                                  2)
+
+slimmer_PM_dat$spray_management <-
+   factor(slimmer_PM_dat$spray_management)
+slimmer_PM_dat$trial_ref <- factor(slimmer_PM_dat$trial_ref)
+slimmer_PM_dat$trial <- factor(slimmer_PM_dat$trial)
+```
+
+```{r Metafor-analysis}
+PM_mv_AI <- rma.mv(
+   yi,
+   vi,
+   mods = ~ spray_management,
+   method = "ML",
+   random = list( ~ spray_management | trial),
+   struct = "UN",
+   data = slimmer_PM_dat
+)
+
+summary(PM_mv_AI)
+```
+
+Results show that yields in single early spray treatments are not significantly different to the no spray control.
+Commencing spray management schedules at first sign of disease (Recommended), or between 7 - 19 days after first sign (late) produced significantly higher yields compared to the no spray control.
+On average a spray schedule with two or more applications stating late (7-19 days after first sign of powdery mildew) produced the highest yields.
+
+When we compare these results to those of the linear mixed effect model there is little difference in the outcome.
+The most notable difference is the linear mixed-effect model is somewhat less certain about the `Late_plus` treatment, and the mean yield lower than the `recommended_plus` treatment.
+
+```{r compare_meta&lmer}
+lme_PM <-
+   lmer(yi ~ spray_management + (spray_management |
+                                    trial), data = slimmer_PM_dat)
+
+summary(lme_PM)
+```
+&spun;  
+&spun;  
+To make it easier to compare each of the treatments we can compute the meta-analysis contrasts.
+```{r metafor_contrasts}
+anova(PM_mv_AI, L = rbind(
+   c(0, 1, -1, 0, 0),
+   # early vs Recomended
+   c(0, 1, 0, -1, 0),
+   # early vs recommended plus
+   c(0, 1, 0, 0, -1),
+   # early vs Late plus
+   c(0, 0, -1, 1, 0),
+   # Recommended vs recommended_plus
+   c(0, 0, -1, 0, 1),
+   # Recommended vs Late_Plus
+   c(0, 0, 0, -1, 1)
+)) # recommended_plus vs Late_plus
+```
+Results show with the exclusion of the no spray control, none of the treatments are significantly different, however, early applications treatments on average produced lower yields.
+Let's view this on a plot.
+
+```{r metafor_results}
+results_AI <- data.frame(cbind(exp(PM_mv_AI$b),
+                               exp((PM_mv_AI$ci.lb)),
+                               exp(PM_mv_AI$ci.ub)))
+
+# results_AI <- data.frame(cbind(PM_mv_AI$b,
+#                               (PM_mv_AI$ci.lb),
+#                               PM_mv_AI$ci.ub))
+
+treat <-
+   c("control",
+     "Early",
+     "Recommended",
+     "Recommended_plus",
+     "Late_plus")
+efficacy <- tbl_df(results_AI)
+efficacy$treat <- treat
+efficacy$se <- PM_mv_AI$se
+colnames(efficacy) <-
+   c("Mean", "CIs_lower", "CI_upper", "Treatment", "SE")
+efficacy
+```
+
+```{r metafor_plot}
+efficacy$Treatment <-
+   factor(
+      efficacy$Treatment,
+      c(
+         "control",
+         "Early",
+         "Recommended",
+         "Recommended_plus",
+         "Late_plus"
+      )
+   )
+
+efficacy %>%
+   ggplot(aes(Treatment, Mean)) +
+   geom_hline(
+      yintercept = c(0.8, 1, 1.2, 1.4),
+      color = "grey80",
+      linetype = 3
+   ) +
+   geom_point(aes(size = 1 / SE), shape = 15) +
+   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper)) +
+   coord_flip() +
+   theme_usq()
+```
+
+What is interesting here is that the variance in the control has increased while the treatments have decreased.
+This is despite the control being the best represented across all experiments.
+However it could also be because it also has a low number of pooled reps per trial.
+Let's look at how well each of the treatments compare to each other.
+We can use the netmeta package to give a graphical representation of this.
+
+### netmeta package  
+Let's analyse the data again using a different statistical approach to see if our outcome with the `metafor` package was robust.
+The `netmeta` package uses a frequentness approach to the analysis, and focuses on the pairwise comparisons between treatments.
+
+```{r netmeta-analysis}
+library(netmeta)
+
+datPM3 <- slimmer_PM_dat %>%
+   group_by(trial, spray_management, n) %>%
+   summarize(yi_mean = mean(yi),
+             vi_mean = mean(vi)) %>%
+   ungroup()
+
+PM_con <- pairwise(
+   treat = spray_management,
+   n = n,
+   mean = yi_mean,
+   sd = sqrt(vi_mean),
+   studlab = trial,
+   data = datPM3,
+   sm = "MD"
+)
+
+net_con <- netmeta(TE,
+                   seTE,
+                   treat1,
+                   treat2,
+                   studlab,
+                   data = PM_con,
+                   sm = "MD")
+
+summary(net_con)
+```
+Now let's visualise this as a forest plot
+
+```{r netmeta-forest}
+forest(
+   net_con,
+   reference.group = 4,
+   rightcols = c("effect", "ci", "Pscore"),
+   rightlabs = "P-Score",
+   small.values = "bad"
+)
 
 ```
+
+The `netmeta` analysis suggests the spray schedule commencing early are no different to any other treatment including the no spray control.
+It estimates the mean is very similar to the recommended treatments.
+The recommended plus and late_plus treatments show higher mean estimates, however not significantly different from the early estimate.
+
+```{r netgraphGW}
+netgraph(
+   net_con,
+   plastic = FALSE,
+   col = "orange",
+   thickness =  "number.of.studies",
+   points = FALSE,
+   col.points = "black",
+   cex.points = 1,
+   number.of.studies = TRUE,
+   cex.number.of.studies = 1,
+   col.number.of.studies = "black",
+   bg.number.of.studies = "orange",
+   multiarm = FALSE,
+   col.multiarm = "lightblue",
+   pos.number.of.studies = 0.5
+)
+```
+
+```{r}
+netleague(net_con)
+
+decomp.design(net_con)
+
+netsplit(net_con)
+
+nm1 <- netmeasures(net_con)
+
+plot(
+   nm1$meanpath,
+   nm1$minpar,
+   pch = "",
+   xlab = "Mean path length",
+   ylab = "Minimal parallelism"
+)
+text(nm1$meanpath, nm1$minpar, names(nm1$meanpath), cex = 0.8)
+```
+
+```{r Save_meta_data, eval=FALSE}
+write.csv(slimmer_PM_dat, file = "data/GYmeta_data.csv")
+
+```

### 2020-02-24 04_MetaAnalysis.Rmd
Apply theme_usq() globally

@@
-```{r MEsummary_Libraries2, message=FALSE}
+```{r MEsummary_Libraries2, message=FALSE, include=FALSE}
 if (!require("pacman"))
@@
    geom_jitter(width = 0.1, alpha = 1 / 5) +
-   theme_usq() +
    labs(x = "Spray management variable",
@@
    geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper)) +
-   coord_flip() +
-   theme_usq()
+   coord_flip()
 ```

### 2020-02-24 05_AUDPC_MetaAnalysis.Rmd
Grammar and code formatting

@@
-```{r MEsummary_Libraries1, message=FALSE}
+```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer)
-
-if (!require("theme.usq")) devtools::install_github("adamhsparks/theme.usq")
-library(theme.usq)
+pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer, metafor)
 
@@
 # AUPDC meta-analysis
-Now it's time to look at how the spray managment scenarios might impact disease pressure on the mungbean yields.
-First lets evaulate which measure of disease is the most robust predictor for yield loss, AUDPC, AUDPS or disease incidence at the end of the season.
+Now it's time to look at how the spray management scenarios might impact disease pressure on the mungbean yields.
+First let's evaluate which measure of disease is the most robust predictor for yield loss, AUDPC, AUDPS or disease incidence at the end of the season.
 ```{r LM_AUDPC}
@@
 AUDPC and AUDPS are not good predictors of loss in yield overall, without the inclusion of a `trial` parameter.
-Lets test the model with the inclusion of `trial` as a random effect.
+Let's test the model with the inclusion of `trial` as a random effect.
 
@@
 However we noticed in the plots earlier that not only the intercept but the slope varies depending on the trial.
-Lets see if the model improves when AUDPC is used as a random slope for trial.
+Let's see if the model improves when AUDPC is used as a random slope for trial.
 
@@
 ```
-The model is significantly improved, lower AIC and a higher log likelihood. Lets see if AUDPS improves in the same way.
+The model is significantly improved, lower AIC and a higher log likelihood. Let's see if AUDPS improves in the same way.
 
@@
 
-Lets compare the area under the disease progress curve (AUDPC) to final severity.
+Let's compare the area under the disease progress curve (AUDPC) to final severity.
 ```{r LMER_finalSev}
@@
 
-Powdery mildew incidence at the end of the season was a significant covariate for grain yield, however was a weeker predictor compared to AUDPC.
+Powdery mildew incidence at the end of the season was a significant covariate for grain yield, however was a weaker predictor compared to AUDPC.
 In addition model comparison shows AUDPC is significantly better at predicting grain yield.
@@
 We shall proceed by including the spray management predictor into the analysis.  
-First lets assess the `spray_management` variable as an additive fixed effect.
+First let's assess the `spray_management` variable as an additive fixed effect.
 
@@
 
-It is also worth noting there is no reason to include these parameters individually in the model to assess their independant effect on grain yield as we know the application of fungicide to mitigate yield loss is aimed at reducing the disease in the crop.
+It is also worth noting there is no reason to include these parameters individually in the model to assess their independent effect on grain yield as we know the application of fungicide to mitigate yield loss is aimed at reducing the disease in the crop.
 
@@
 
-I will try to use the AUDPC:spray_management interative term as a random effect slope to trial, however I think this may overfit the model preventing convergance.
+I will try to use the AUDPC:spray_management iterative term as a random effect slope to trial, however I think this may over fit the model preventing convergence.
 
@@
 The other fixed effects show the change in predicted yield as AUDPC increases under each of the spray_management factors.
-Spray_management treatments, control, Early, and recommended show significant declines in grain_yields as AUDPC increases.
+Spray_management treatments, control, early, and recommended show significant declines in grain_yields as AUDPC increases.
 Recommended_plus and Late_plus show no significant decline in grain yield as AUDPC increases.
 
-The second output is the random effect coeficients.
+The second output is the random effect coefficients.
 Here the intercept represents a yield estimate for each trial without the limitation of the disease.

### 2020-02-24 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
reknit book

@@
 Disease data for Kingaroy 2016 only exists as a mean of treatments within the `2016 Mungbean PM trials summary.xlsx` file.  
-```{r Herm16_dataimport}
+```{r Kroy16_dataimport}
 # Yield data from 2016 Hermitage trial with final disease severity
@@
 #### Define treatment data
-```{r Well_18_treatmentDefine}
+```{r Herm_19_treatement_data}
 Herm_19_dat <- PM_MB_19 %>%
@@
 
-```{r Save_PM_MB_means}
+```{r Save_PM_MB_means, eval=FALSE}
 

### 2020-02-24 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Update ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd

@@
 This file is not complete and there are a number of things that need checking
+
    - Mean squares are only calculated for the triazoles and controls
+
    - If the years for each trial are input correctly
+
    - If the disease and yield errors are calculated and that they are shuffled correctly into the data frame
+
    - AUDPC needs to be checked for starting dates and if trials have been omitted
+
    - Check that what is generated from this file matches the main file and update
+
    - write.csv should have row.names = FALSE
@@
 ```{r message=FALSE, warning=FALSE}
-# install.packages("openxlsx")
-# install.packages("readxl")
-# install.packages("tidyr")
-# install.packages("agricolae")
-
-library(openxlsx)
-library(readxl)
-library(tidyr)
-library(dplyr)
-library(data.table)
-library(agricolae)
+if (!require("pacman"))
+   install.packages("pacman")
+pacman::p_load(tidyverse,
+               lubridate,
+               readxl,
+               data.table,
+               devtools,
+               agricolae)
+source("R/import_data.R")
+if (!require("theme.usq"))
+   devtools::install_github("adamhsparks/theme.usq")
+library(theme.usq)
+#source("./getPPD2.R")
+theme_set(theme_usq()
+)
 
@@
 ```{r functions}
-
-fold_data <- function(new_DataFrame, template_DataFrame){
-   for(i in colnames(new_DataFrame)){
-      if(i == colnames(new_DataFrame)[1]){
-         x1 <- vector()}
+fold_data <- function(new_DataFrame, template_DataFrame) {
+   for (i in colnames(new_DataFrame)) {
+      if (i == colnames(new_DataFrame)[1]) {
+         x1 <- vector()
+      }
 
@@
 
-      x1 <- c(x1,match(i, cnames2, nomatch = NA)) # MAke a index vector for the location of new_DataFrame col names in template_DataFrame
-   }
-
-   new_DataFrame[cnames2[!(cnames2 %in% cnames1)]] <- NA # adding column names to new_DataFrame not in template_DataFrame
+      x1 <-
+         c(x1, match(i, cnames2, nomatch = NA)) # MAke a index vector for the location of new_DataFrame col names in template_DataFrame
+   }
+
+   new_DataFrame[cnames2[!(cnames2 %in% cnames1)]] <-
+      NA # adding column names to new_DataFrame not in template_DataFrame
    new_DataFrame <-
-      new_DataFrame[,c(cnames2, cnames1[is.na(x1)])]  # adding column names to new_DataFrame not in template_DataFrame
+      new_DataFrame[, c(cnames2, cnames1[is.na(x1)])]  # adding column names to new_DataFrame not in template_DataFrame
    return(new_DataFrame)
@@
 Herm_10 <-
-   as.data.frame(read_xls(
+   as.data.frame(
+      read_xls(
          "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2010/2010 PMmung Herm/2010 PMmung hermitage RAW field book.xls",
          sheet = "For analysis"
-   ), stringsAsFactors == FALSE)
+      ),
+      stringsAsFactors == FALSE
+   )
 
 Herm_10 <- Herm_10 %>%
-   mutate(trade_name = case_when(`Schedule!` == "U/S" ~ NA_character_,
+   mutate(
+      trade_name = case_when(
+         `Schedule!` == "U/S" ~ NA_character_,
          `Schedule!` == "FirstsignC" ~ " ",
-                                 TRUE ~ "Kendon"))%>%
-   mutate(fungicide = case_when(`Schedule!` == "U/S" ~ "control",
+         TRUE ~ "Kendon"
+      )
+   ) %>%
+   mutate(
+      fungicide = case_when(
+         `Schedule!` == "U/S" ~ "control",
          `Schedule!` == "FirstsignC" ~ "carbendazim",
-                                 TRUE ~ "sulphur"))%>%
-   mutate(dose_ai.ha = case_when(`Schedule!` == "U/S" ~ 0,
+         TRUE ~ "sulphur"
+      )
+   ) %>%
+   mutate(dose_ai.ha = case_when(
+      `Schedule!` == "U/S" ~ 0,
       `Schedule!` == "FirstsignC" ~ 250,
-                                 TRUE ~ 2400))%>%
-   mutate(fungicide_application_1 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-02-19", format = "%Y-%m-%d"),
+      TRUE ~ 2400
+   )) %>%
+   mutate(
+      fungicide_application_1 = case_when(
+         `Schedule!` == "Full Sp" ~ as.Date("2010-02-19", format = "%Y-%m-%d"),
          `Schedule!` == "Early Sp" ~ as.Date("2010-02-19", format = "%Y-%m-%d"),
@@
          `Schedule!` == "U/S" ~ as.Date(NA),
-                                              TRUE ~ as.Date(NA)))%>%
-   mutate(fungicide_application_2 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-02-26", format = "%Y-%m-%d"),
+         TRUE ~ as.Date(NA)
+      )
+   ) %>%
+   mutate(
+      fungicide_application_2 = case_when(
+         `Schedule!` == "Full Sp" ~ as.Date("2010-02-26", format = "%Y-%m-%d"),
          `Schedule!` == "Early Sp" ~ as.Date("2010-02-26", format = "%Y-%m-%d"),
-                                              TRUE ~ as.Date(NA)))%>%
-   mutate(fungicide_application_3 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-03-05", format = "%Y-%m-%d"),
-                                              TRUE ~ as.Date(NA)))%>%
-   mutate(fungicide_application_4 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-03-11", format = "%Y-%m-%d"),
-                                              TRUE ~ as.Date(NA)))%>%
-   mutate(fungicide_application_5 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-03-18", format = "%Y-%m-%d"),
-                                              TRUE ~ as.Date(NA)))%>%
-   mutate(fungicide_application_6 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-03-25", format = "%Y-%m-%d"),
-                                              TRUE ~ as.Date(NA)))%>%
-   mutate(fungicide_application_7 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-03-07", format = "%Y-%m-%d"),
-                                              TRUE ~ as.Date(NA)))%>%
-   mutate(total_fungicide = case_when(`Schedule!` == "Full Sp" ~ 7,
+         TRUE ~ as.Date(NA)
+      )
+   ) %>%
+   mutate(fungicide_application_3 = case_when(
+      `Schedule!` == "Full Sp" ~ as.Date("2010-03-05", format = "%Y-%m-%d"),
+      TRUE ~ as.Date(NA)
+   )) %>%
+   mutate(fungicide_application_4 = case_when(
+      `Schedule!` == "Full Sp" ~ as.Date("2010-03-11", format = "%Y-%m-%d"),
+      TRUE ~ as.Date(NA)
+   )) %>%
+   mutate(fungicide_application_5 = case_when(
+      `Schedule!` == "Full Sp" ~ as.Date("2010-03-18", format = "%Y-%m-%d"),
+      TRUE ~ as.Date(NA)
+   )) %>%
+   mutate(fungicide_application_6 = case_when(
+      `Schedule!` == "Full Sp" ~ as.Date("2010-03-25", format = "%Y-%m-%d"),
+      TRUE ~ as.Date(NA)
+   )) %>%
+   mutate(fungicide_application_7 = case_when(
+      `Schedule!` == "Full Sp" ~ as.Date("2010-03-07", format = "%Y-%m-%d"),
+      TRUE ~ as.Date(NA)
+   )) %>%
+   mutate(
+      total_fungicide = case_when(
+         `Schedule!` == "Full Sp" ~ 7,
          `Schedule!` == "Early Sp" ~ 2,
@@
          `Schedule!` == "U/S" ~ 0,
-                                      TRUE ~ 9999))
+         TRUE ~ 9999
+      )
+   )
 
@@
 Herm_10_dat <- 
-   data.frame(trial_ref = "mung0910/01",
+   data.frame(
+      trial_ref = "mung0910/01",
       year = "2010",
@@
       rating_scale = "1-9",
-              grain_yield.t.ha. = Herm_10$`Kg/ha`/1000,
+      grain_yield.t.ha. = Herm_10$`Kg/ha` / 1000,
       stringsAsFactors = FALSE
@@
 
-Herm_10_dat <- cbind(Herm_10_dat,
-                     AUDPC = apply(data.frame(zero = 0,
-                                              Herm_10[,c("P.M.9wap","P.M.11wap","P.M.13wap")]-1),
+Herm_10_dat <- cbind(
+   Herm_10_dat,
+   AUDPC = apply(
+      data.frame(zero = 0,
+                 Herm_10[, c("P.M.9wap", "P.M.11wap", "P.M.13wap")] -
+                    1),
       1,
       FUN = audpc,
-                                   dates = c((Herm_10_dat$first_sign_disease[1]-7)-
+      dates = c((Herm_10_dat$first_sign_disease[1] -
+                    7) -
                    Herm_10_dat$planting_date[1],
-                                             9*7,11*7,13*7)
+                9 * 7,
+                11 * 7,
+                13 * 7
+      )
    ),
-                     AUDPS = apply(data.frame(zero = 0,
-                                                   Herm_10[,c("P.M.9wap","P.M.11wap","P.M.13wap")]-1),
+   AUDPS = apply(
+      data.frame(zero = 0,
+                 Herm_10[, c("P.M.9wap", "P.M.11wap", "P.M.13wap")] -
+                    1),
       1,
       FUN = audps,
-                                        dates = c((Herm_10_dat$first_sign_disease[1]-7)-
+      dates = c((Herm_10_dat$first_sign_disease[1] -
+                    7) -
                    Herm_10_dat$planting_date[1],
-                                                  9*7,11*7,13*7)
+                9 * 7,
+                11 * 7,
+                13 * 7
+      )
    )
@@
 Herm_10$PM_zero <- 1
-Herm_plot <- melt(Herm_10, id.vars = c("Description!","Treat!", "Rep!","Cultivar!","fungicide","total_fungicide"),
-                  measure.vars = c("PM_zero","P.M.9wap","P.M.11wap","P.M.13wap"))
+Herm_plot <-
+   melt(
+      Herm_10,
+      id.vars = c(
+         "Description!",
+         "Treat!",
+         "Rep!",
+         "Cultivar!",
+         "fungicide",
+         "total_fungicide"
+      ),
+      measure.vars = c("PM_zero", "P.M.9wap", "P.M.11wap", "P.M.13wap")
+   )
 
 Herm_plot <- Herm_plot %>%
-   mutate(T_var = case_when(variable == "PM_zero" ~ 
-                               as.numeric((Herm_10_dat$first_sign_disease[1]-7) - Herm_10_dat$planting_date[1]),
-                            variable == "P.M.9wap" ~ 9*7,
-                            variable == "P.M.11wap" ~ 11*7,
-                            variable == "P.M.13wap" ~ 13 * 7)
+   mutate(
+      T_var = case_when(
+         variable == "PM_zero" ~
+            as.numeric((Herm_10_dat$first_sign_disease[1] -
+                           7) - Herm_10_dat$planting_date[1]
+            ),
+         variable == "P.M.9wap" ~ 9 * 7,
+         variable == "P.M.11wap" ~ 11 * 7,
+         variable == "P.M.13wap" ~ 13 * 7
+      )
    )
@@
 Herm_plot %>%
-   ggplot(aes(x = T_var, y = value, color = `Treat!`, shape = `Treat!`))+
-   geom_jitter(width = 1)+
+   ggplot(aes(
+      x = T_var,
+      y = value,
+      color = `Treat!`,
+      shape = `Treat!`
+   )) +
+   geom_jitter(width = 1) +
    geom_smooth()
@@
 Herm_10_m <- Herm_10_dat %>%
-   group_by(trial_ref, year, location, host_genotype, trial_design, trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
-   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
+   group_by(
+      trial_ref,
+      year,
+      location,
+      host_genotype,
+      trial_design,
+      trade_name,
+      fungicide_ai,
+      dose_ai.ha,
+      n_treatment
+   ) %>%
+   summarise(
+      plot_length.m. = mean(plot_length, na.rm = TRUE),
       plot_width.m. = mean(plot_width, na.rm = TRUE),
@@
       AUDPS_sd = sd(AUDPS),
-             Inc_Ms = anova(lm(AUDPC ~ host_genotype + factor(n_treatment), data = Herm_10_dat))[2,3],
-             Y_Msquare = anova(lm(grain_yield.t.ha. ~ host_genotype + factor(n_treatment), data = Herm_10_dat))[2,3]
+      Inc_Ms = anova(lm(
+         AUDPC ~ host_genotype + factor(n_treatment), data = Herm_10_dat
+      ))[2, 3],
+      Y_Msquare = anova(
+         lm(grain_yield.t.ha. ~ host_genotype + factor(n_treatment), data = Herm_10_dat)
+      )[2, 3]
 
@@
 Herm_tentmp <- Herm_10_dat %>%
-   group_by(host_genotype,n_treatment)%>%
-   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
-             yield_error = sd(grain_yield.t.ha., na.rm = TRUE))
-
-Herm_10_m[order(Herm_10_m$n_treatment),"disease_error"] <- Herm_tentmp[order(Herm_tentmp$n_treatment),"disease_error"]
-Herm_10_m[order(Herm_10_m$n_treatment),"yield_error"] <- Herm_tentmp[order(Herm_tentmp$n_treatment),"yield_error"]
+   group_by(host_genotype, n_treatment) %>%
+   summarise(
+      disease_error = sd(PM_final_severity, na.rm = TRUE),
+      yield_error = sd(grain_yield.t.ha., na.rm = TRUE)
+   )
+
+Herm_10_m[order(Herm_10_m$n_treatment), "disease_error"] <-
+   Herm_tentmp[order(Herm_tentmp$n_treatment), "disease_error"]
+Herm_10_m[order(Herm_10_m$n_treatment), "yield_error"] <-
+   Herm_tentmp[order(Herm_tentmp$n_treatment), "yield_error"]
 
@@
 # insert new calculations into data
-PM_MB_means <- replace_data(template_data = PM_MB_means, 
+PM_MB_means <- replace_data(
+   template_data = PM_MB_means,
    new_data = Herm_10_m,
-                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
-                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
-                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
+   new_data_column = c(
+      "AUDPC_m",
+      "AUDPC_sd",
+      "AUDPS_m",
+      "AUDPS_sd",
+      "Y_Msquare",
+      "Inc_Ms"
+   ),
+   filter_cols = c(
+      "trial_ref",
+      "year",
+      "location",
+      "host_genotype",
+      "fungicide_ai",
+      "dose_ai.ha",
+      "n_treatment"
+   )
+)
 #ignore_columns = c(6,17,30:ncol(Herm_10_m))
@@
    as.data.frame(Herm_10_m),
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2010/2010 PMmung Herm/2010 PMmung Hermitage means.csv"
+   "../data/Past trials/2010/2010 PMmung Herm/2010 PMmung Hermitage means.csv"
 )

### 2020-02-24 05_AUDPC_MetaAnalysis.Rmd

@@
 # AUPDC meta-analysis
+
 Now it's time to look at how the spray management scenarios might impact disease pressure on the mungbean yields.
 First let's evaluate which measure of disease is the most robust predictor for yield loss, AUDPC, AUDPS or disease incidence at the end of the season.
+
+```{r AUDPC_funnel}
+PM_Mdat$slope <- NA
+PM_Mdat$SE <- NA
+for(i in PM_Mdat$trial){
+   PM_Mdat[PM_Mdat$trial == i,c("slope", "SE")] <-
+      coef(summary(lm(grain_yield.t.ha ~ AUDPC_m,data = PM_Mdat[PM_Mdat$trial == i,])))[2,1:2]
+}
+
+plot(1/SE ~ slope, data = PM_Mdat, ylim = c(-3000,6000))
+```
+
+Now it's time to look at how the spray managment scenarios might impact disease pressure on the mungbean yields.
+First lets evaulate which measure of disease is the most robust predictor for yield loss, AUDPC, AUDPS or disease incidence at the end of the season.
+
 ```{r LM_AUDPC}

### 2020-02-24 06_Publication_wireframe_and_7_Questions.Rmd
Rename file

--- 2020-02-24 06_Publication_wireframe_and_8Questions.Rmd
@@
 ## Why did you do it? (limit - 50 words)
-The unpublished field trial data singularly did not provide a clear indication for when to apply fungicide to best mitigate yield losses from powdery mildew.
+The unpublished field trial data independantly did not provide a clear indication for when to apply fungicide to best mitigate yield losses from powdery mildew.
 By analysing the collective data we aim to provide a better estimate for fungicide application timing to mitigate the yield loss from powdery mildew.
@@
 Only a few studies incorporated in the meta-analysis contained comparisons between the "Late plus" factor and the: negative spray control, a single spray at first sign, and spray at first sign with one or more follow-up applications.
+
+# Manuscript
+
+## Introduction
+Mungbean is a short season summer pulse crop which can provide a high returns for growers in eastern Australia.
+Mungbean can potentially yield up to 2.3 tonnes per hectare, and worth up to \$ 1300 a tonne [AgMargins; 2019](https://agmargins.net.au/Reports/Details/fced3a80-a762-481c-b812-9953e33410e6).
+Powdery mildew _Podosphaera xanthii_ can potentially cause yield losses on mungbean of up to 43%.
+Fortunatley a number of strategies are employed to reduce the damage powdery mildew inflicts on yields.
+### Managements strategies
+#### and conditions for infection
+Powdery mildew infection requires cool temperatures (22$^\circ$ - 26$^\circ$C) and a leaf surface that is not overly wet for infection [Kelly et.
+al 2017](https://grdc.com.au/resources-and-publications/grdc-update-papers/tab-content/grdc-update-papers/2017/07/mungbean-and-sorghum-disease-update).
+In southern Queensland and northern New South Wales, planting dates between late spring (November) and mid-summer (January) are advised to avoid the conducsive cooler autumn temperatures which normally commence in March in the southern hemisphere conducive for powdery mildew establishment.
+Signs of powdery mildew are almost always first observed when temperatures start to cool.
+
+### Fungicide resistance
+Lucritive returns of \$ 2260 over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than they are needed.
+
+### Previous studies
+
+### Meta-analyes
+
+### Aims
+
+## Materials and methods

### 2020-02-25 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Create cache folder and relocate data files to make datawrangling file more portable

--- 2020-02-12 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
@@
 library(agricolae)
-
-source("../R/import_data.R")
+library(here)
+
+source(here("R/import_data.R"))
 PM_MB_means <- import_data()
@@
 }
-source("../copy_class.R")
-source("../R/data_mesh.R")
+source(here("copy_class.R"))
+source(here("R/data_mesh.R"))
 ```
@@
 Herm_10 <-
-   as.data.frame(read_xls(
-      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2010/2010 PMmung Herm/2010 PMmung hermitage RAW field book.xls",
+   as.data.frame(read_xls(here(
+      "data/2010 PMmung hermitage RAW field book.xls"),
       sheet = "For analysis"
@@
 
-source("../R/data_mesh.R")
 # insert new calculations into data
@@
    as.data.frame(Herm_10_m),
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2010/2010 PMmung Herm/2010 PMmung Hermitage means.csv"
+   "cache/2010 PMmung Herm/2010 PMmung Hermitage means.csv", row.names = FALSE
 )

### 2020-02-25 R/import_data.R

@@ -12,13 +12,13 @@
 
 # devtools::install_github("PaulMelloy/cloudy")
 
-
+library(here)
 
 import_data <- function() {
    # x <-
    #    cloudy::fetch_data(url = "https://usqprd-my.sharepoint.com/:x:/g/personal/u8011054_usq_edu_au/ER13jFzyQqNMq_SEZkNW9NoBiJI8R68dfkKfWXB9wJgETw?e=mylMrZ",
    #                       file_ext = ".csv")
-   x <- read.csv(file = "data/PM_MB_updated.csv")
+   x <- read.csv(file = here("cache/PM_MB_updated.csv"))
    x$trial_ref <- as.factor(x$trial_ref)
    x$location <- as.factor(x$location)
    x$host_genotype <- as.factor(x$host_genotype)

### 2020-02-25 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
updated filepaths using the here() function

@@
    as.data.frame(Herm_10_m),
-   "cache/2010 PMmung Herm/2010 PMmung Hermitage means.csv", row.names = FALSE
+   here("cache/2010 PMmung Hermitage means.csv"), row.names = FALSE
 )
@@
    as.data.frame(read_xls(
-      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2011/2011 PMmung Herm/pmhermratings2011.xls",
+      here("data/pmhermratings2011.xls"),
       sheet = "Analyses factor"
@@
    as.data.frame(Herm_11_m),
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2011/2011 PMmung Herm/2011 PMmung Herm means.csv"
+   here("cache/2011 PMmung Herm means.csv"), row.names = FALSE
 )
@@
    as.data.frame(read_xls(
-      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2011/2011 PMmung King/pmKing ratings2011.xls",
+      here("data/pmKing ratings2011.xls"),
       sheet = "analyses"
@@
    King_11_m,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2011/2011 PMmung King/2011 PMmung Kingaroy means.csv"
+   here("cache/2011 PMmung Kingaroy means.csv"),row.names = FALSE
 )
@@
       read_xlsx(
-         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1305 Fungicides for powdery mildew in mungbean - Goolhi.xlsx",
+         path = here("data/AM1305 Fungicides for powdery mildew in mungbean - Goolhi.xlsx"),
          sheet = D_assessment,
@@
 
-# head(Goolhi.13D)
-# Goolhi.13D <- Goolhi.13D %>%
-#    group_by(Treat) %>%
-#    summarise(M.inc = mean(Incidence, na.rm = TRUE),
-#              sd.inc = sd(Incidence, na.rm = TRUE))
-
-# write.csv(
-#    Goolhi.13D,
-#    "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/Mungbean/Past trials/2013/AM1305-Goolhi-Disease_means.csv"
-# )
-
 #_____________________
@@
       read_xlsx(
-         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1305 Fungicides for powdery mildew in mungbean - Goolhi.xlsx",
+         path = here("data/AM1305 Fungicides for powdery mildew in mungbean - Goolhi.xlsx"),
          sheet = "Yield",
@@
    Goolhi_13_m,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1305_Goolhi_means.csv"
+   here("cache/AM1305_Goolhi_means.csv"),row.names = FALSE
 )
@@
       read_xlsx(
-         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1304 Fungicides for powdery mildew in mungbean - Marys Mount.xlsx",
+         path = here("data/AM1304 Fungicides for powdery mildew in mungbean - Marys Mount.xlsx"),
          sheet = D_assess,
@@
    MarysM.13D.1,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1304-MaryMount-Disease_means.csv"
+   here("cache/AM1304-MaryMount-Disease_means.csv"),
+   row.names = FALSE
 )
@@
       read_xlsx(
-         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1304 Fungicides for powdery mildew in mungbean - Marys Mount.xlsx",
+         path = here("data/AM1304 Fungicides for powdery mildew in mungbean - Marys Mount.xlsx"),
          sheet = "42 DAT1 Yield",
@@
    MarysM_13_m[order(as.numeric(MarysM_13_m$n_treatment)),],
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1304-MarysMount_means.csv",
+   here("cache/AM1304-MarysMount_means.csv"),
    row.names = FALSE
@@
       read_xlsx(
-         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1303 Fungicides for powdery mildew in mungbean - Premer.xlsx",
+         path = here("data/AM1303 Fungicides for powdery mildew in mungbean - Premer.xlsx"),
          sheet = D_assess,
@@
       read_xlsx(
-         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1303 Fungicides for powdery mildew in mungbean - Premer.xlsx",
+         path = here("data/AM1303 Fungicides for powdery mildew in mungbean - Premer.xlsx"),
          sheet = "Yield 18-4-2013",
@@
    Premer_13_m,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/AM1303-Premer-Disease_means.csv"
+   here("cache/AM1303-Premer-Disease_means.csv"),row.names = FALSE
 )
@@
       read_xlsx(
-         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/BB1305 Fungicides for powdery mildew in mungbean - Millmerran.xlsx",
+         path = here("data/BB1305 Fungicides for powdery mildew in mungbean - Millmerran.xlsx"),
          sheet = D_assess,
@@
       read_xlsx(
-         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/BB1305 Fungicides for powdery mildew in mungbean - Millmerran.xlsx",
+         path = here("data/BB1305 Fungicides for powdery mildew in mungbean - Millmerran.xlsx"),
          sheet = "Harvest Sheet 6.5.2013",
@@
    Millm_13_m[order(as.numeric(Millm_13_m$n_treatment)),],
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/BB1305_Millmerran_means.csv"
+   here("cache/BB1305_Millmerran_means.csv"), row.names = FALSE
 )
@@
    read.xlsx(
-      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2015 PMmung Herm/Mugbean powdery mildew 2014-15 inc results v2.xlsx",
+      here("data/Mugbean powdery mildew 2014-15 inc results v2.xlsx"),
       sheet = "HRS yield data",
@@
    read.xlsx(
-      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2015 PMmung Herm/Mugbean powdery mildew 2014-15 inc results v2.xlsx",
+      here("data/Mugbean powdery mildew 2014-15 inc results v2.xlsx"),
       sheet = "HRS ratings & graphs",
@@
    Herm_15_m,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2015 PMmung Herm/Herm_15_means.csv"
+   here("cache/Herm_15_means.csv"),row.names = FALSE
 )
@@
    read.xlsx(
-      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2016/Yeild Data 2016 Kingaroy Hermitage (PaulM adjusted).xlsx",
+      here("data/Yeild Data 2016 Kingaroy Hermitage (PaulM adjusted).xlsx"),
       sheet = "Hermitage",
@@
    read.xlsx(
-      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2016/2016 Mungbean PM trials summary.xlsx",
+      here("data/2016 Mungbean PM trials summary.xlsx"),
       sheet = "Hermitage_2016",
@@
    Herm_16_m,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2016/Hermitage/Herm_16_means.csv"
+   here("cache/Herm_16_means.csv"),row.names = FALSE
 )
@@
    read.xlsx(
-      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past Trials/2016/Yeild Data 2016 Kingaroy Hermitage (PaulM adjusted).xlsx",
+      here("data/Yeild Data 2016 Kingaroy Hermitage (PaulM adjusted).xlsx"),
       sheet = "Kingaroy",
@@
    read.xlsx(
-      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2016/2016 Mungbean PM trials summary.xlsx",
+      here("data/2016 Mungbean PM trials summary.xlsx"),
       sheet = "Kingaroy_2016",
@@
    King_16_m,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2016/Kingaroy/King_16_means.csv",
+   here("cache/King_16_means.csv"),
    row.names = FALSE
@@
    read.xlsx(
-      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2017/MissenFlats/Fogerty Work File 2017 (Autosaved).xlsx",
+      here("data/Fogerty Work File 2017 (Autosaved).xlsx"),
       sheet = "Data",
@@
       seq(from = 2, to = 324, by = 2)])
-
-# Fog_17_sum <- Fogerty_17 %>%
-#    group_by(Treatment, Chemical, `Row.Spacing.(m)`) %>%
-#    summarise(
-#       m_disease = mean(`2017-04-18`, na.rm = TRUE),
-#       sd_disease = sd(`2017-04-18`, na.rm = TRUE),
-#       m_Yield = mean(`Yield.t/ha`, na.rm = TRUE),
-#       sd_Yield = sd(`Yield.t/ha`, na.rm = TRUE)
-#    )
-# 
-# write.csv(
-#    Fog_17_sum,
-#    "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/Fogerty_17_mean.csv"
-# )
-# 
-# 
-# # gather the incidence assessment into long format
-# Fogerty_17.1 <-
-#    gather(Fogerty_17,
-#           key = Incidence_assessment_date,
-#           value = Incidence,
-#           colnames(Fogerty_17)[c(11:16)])
-# #Fogerty_17.1$Severity <- gather(Fogerty_17, key = assessment_date, value = Severity,
-# #                                colnames(Fogerty_17)[c(15,18)])
-# Fogerty_17.1$location <- "Fogerty"
-# 
-#
 
@@
    Fogerty_17_m,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2017/MissenFlats/Fogerty_17_mean.csv",
+   here("cache/Fogerty_17_mean.csv"),
    row.names = FALSE
@@
    read.xlsx(
-      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past Trials/2017/Hermitage/Hermitage working file 2017 .xlsx",
+      here("data/Hermitage working file 2017 .xlsx"),
       sheet = "Hermitage Trial",
@@
    Herm_17_m,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2017/Hermitage/Hermitage_17_mean.csv",
+   here("cache/Hermitage_17_mean.csv"),
    row.names = FALSE
@@
    read.xlsx(
-      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past Trials/2018/Wellcamp/Wellcamp Fungicide x Row Spacing x Plant Population - Experimental Design Fogarty 2018.xlsx",
+      here("data/Wellcamp Fungicide x Row Spacing x Plant Population - Experimental Design Fogarty 2018.xlsx"),
       sheet = "Data",
@@
    Well_18_m,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2018/Wellcamp/Wellcamp_18_mean.csv",
+   here("cache/Wellcamp_18_mean.csv"),
    row.names = FALSE
@@
    read.xlsx(
-      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/1901_Herm_PM/1901 Mungbean powdery mildew disease and yeild data.xlsx",
+      here("data/1901 Mungbean powdery mildew disease and yeild data.xlsx"),
       startRow = 2,
@@
    Herm_19_m,
-   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2019/Hermitage_19_mean.csv",
+   here("cache/Hermitage_19_mean.csv"),
    row.names = FALSE
@@
 
-write.csv(PM_MB_means, file = "../data/PM_MB_updated.csv")
-
-```
+write.csv(PM_MB_means, file = here("cache/PM_MB_updated.csv"), row.names = FALSE)
+
+```

### 2020-02-26 01_Meta-analysis_experiments.Rmd

@@
 ```{r MEsummary_Libraries, message=FALSE, echo=FALSE}
-library(dplyr)
-library(readr)
-library(kableExtra)
-library(leaflet)
-library(htmltools)
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(tidyverse, kableExtra, leaflet, htmltools)
 source("R/import_data.R")
@@
    6. Colonies in lower 2/3 of canopy, 100% of plants affected  
-   7. Colonies in lower 2/3 of canopy of 100% of plants, some plants with
-   colonies also in top 1/3 of canopy  
+   7. Colonies in lower 2/3 of canopy of 100% of plants, some plants with colonies also in top 1/3 of canopy  
    8. Colonies to top of plant with >75% of plants affected  

### 2020-02-26 02_Preliminary_analysis.Rmd

@@
 #source("./getPPD2.R")
-theme_set(theme_usq()
-)
+theme_set(theme_usq())
 ```

### 2020-02-26 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Some formatting done

@@
 ```{r Hermitage_2010}
-
 Herm_10 <-
    as.data.frame(read_xls(here(
-      "data/2010 PMmung hermitage RAW field book.xls"),
-      sheet = "For analysis"
-   ), stringsAsFactors == FALSE)
+      "data/2010 PMmung hermitage RAW field book.xls"
+   ),
+   sheet = "For analysis"),
+   stringsAsFactors == FALSE)
 
 Herm_10 <- Herm_10 %>%
-   mutate(trade_name = case_when(`Schedule!` == "U/S" ~ NA_character_,
+   mutate(
+      trade_name = case_when(
+         `Schedule!` == "U/S" ~ NA_character_,
          `Schedule!` == "FirstsignC" ~ " ",
-                                 TRUE ~ "Kendon"))%>%
-   mutate(fungicide = case_when(`Schedule!` == "U/S" ~ "control",
+         TRUE ~ "Kendon"
+      )
+   ) %>%
+   mutate(
+      fungicide = case_when(
+         `Schedule!` == "U/S" ~ "control",
          `Schedule!` == "FirstsignC" ~ "carbendazim",
-                                 TRUE ~ "sulphur"))%>%
-   mutate(dose_ai.ha = case_when(`Schedule!` == "U/S" ~ 0,
+         TRUE ~ "sulphur"
+      )
+   ) %>%
+   mutate(dose_ai.ha = case_when(
+      `Schedule!` == "U/S" ~ 0,
       `Schedule!` == "FirstsignC" ~ 250,
-                                 TRUE ~ 2400))%>%
-   mutate(fungicide_application_1 = case_when(`Schedule!` == "Full Sp" ~ as.Date("2010-02-19", format = "%Y-%m-%d"),
+      TRUE ~ 2400
+   )) %>%
+   mutate(
+      fungicide_application_1 = case_when(
+         `Schedule!` == "Full Sp" ~ as.Date("2010-02-19", format = "%Y-%m-%d"),
          `Schedule!` == "Early Sp" ~ as.Date("2010-02-19", format = "%Y-%m-%d"),
@@
 Herm_10_dat <-
-   data.frame(trial_ref = "mung0910/01",
+   data.frame(
+      trial_ref = "mung0910/01",
       year = "2010",
@@
 
-```{r Save_PM_MB_means}
+```{r Save_PM_MB_means, eval=FALSE, include=FALSE}
 

### 2020-02-26 R/import_data.R

@@ -27,32 +27,50 @@ import_data <- function() {
    x$year <- as.factor(x$year)
    x$replicates <- as.numeric(x$replicates)
    x$planting_date <- as.Date(x$planting_date, format = "%Y-%m-%d")
-   x$emergence_date <- as.Date(x$emergence_date, format = "%Y-%m-%d")
-   x$flowering_date <- as.Date(x$flowering_date, format = "%Y-%m-%d")
+   x$emergence_date <-
+      as.Date(x$emergence_date, format = "%Y-%m-%d")
+   x$flowering_date <-
+      as.Date(x$flowering_date, format = "%Y-%m-%d")
    x$pod_fill_date <- as.Date(x$pod_fill_date, format = "%Y-%m-%d")
-   x$mid_late_pod_fill <- as.Date(x$mid_late_pod_fill, format = "%Y-%m-%d")
-   x$first_sign_disease <- as.Date(x$first_sign_disease, format = "%Y-%m-%d")
-   x$fungicide_application_1 <- as.Date(x$fungicide_application_1, format = "%Y-%m-%d")
-   x$fungicide_application_2 <- as.Date(x$fungicide_application_2, format = "%Y-%m-%d")
-   x$fungicide_application_3 <- as.Date(x$fungicide_application_3, format = "%Y-%m-%d")
-   x$fungicide_application_4 <- as.Date(x$fungicide_application_4, format = "%Y-%m-%d")
-   x$fungicide_application_5 <- as.Date(x$fungicide_application_5, format = "%Y-%m-%d")
-   x$fungicide_application_6 <- as.Date(x$fungicide_application_6, format = "%Y-%m-%d")
-   x$fungicide_application_7 <- as.Date(x$fungicide_application_7, format = "%Y-%m-%d")
+   x$mid_late_pod_fill <-
+      as.Date(x$mid_late_pod_fill, format = "%Y-%m-%d")
+   x$first_sign_disease <-
+      as.Date(x$first_sign_disease, format = "%Y-%m-%d")
+   x$fungicide_application_1 <-
+      as.Date(x$fungicide_application_1, format = "%Y-%m-%d")
+   x$fungicide_application_2 <-
+      as.Date(x$fungicide_application_2, format = "%Y-%m-%d")
+   x$fungicide_application_3 <-
[…]

### 2020-02-26 06_Publication_wireframe_and_7_Questions.Rmd
Correct conflict errors

@@
 Primarily that fungicide spray schedules that commence prior to signs of the disease establishing in the mungbean canopy are likely to be ineffective at mitigating the diseases impact on yield.
-We also don't have data on at what point is starting a fungicide spray schedule is too late.
-Growers can't scout their crop three times a week in the fashion of researchers and are unlikely to identify the true date when signs of powdery mildew become apparent.
-Therefore these results reinforce the message to growers to spray for powdery mildew as soon as it is observed in the crop to protect yields.
+We also don’t have data on at what point starting a fungicide spray schedule is too late.
+Growers can’t scout their crop three times a week in the fashion of researchers and are unlikely to identify the true date when signs of powdery mildew become apparent.
+Therefore these results reinforce the message to growers to spray for powdery mildew as soon as it is observed in their crop to protect yields.
 
-## What is the key benefit for your readers? (limit - 25 words).
+## what is the key benefit for your readers? (limit - 25 words).  
 This study is the most robust analysis of management of powdery mildew in mungbean using fungicides.
-It provide a more certain time frame for growers to plan for when to commence a fungicide spray schedule.
+It provides a more certain time frame for growers to plan when to commence a fungicide spray schedule.
+
 Fewer fungicide applications will reduce costs for growers and prolong the efficacy of fungicides before the disease develops resistance.

### 2020-02-26 06_Publication_wireframe_and_7_Questions.Rmd
A sentance to a line and specify bibliography

@@
   html_document: default
+bibliography: Mungbean.bib
 ---
@@
 Mungbean is a short season summer pulse crop which can provide a high returns for growers in eastern Australia. 
-Mungbean can potentially yield up to 2.3 tonnes per hectare, and worth up to \$ 1300 a tonne [AgMargins; 2019](https://agmargins.net.au/Reports/Details/fced3a80-a762-481c-b812-9953e33410e6).
-Powdery mildew _Podosphaera xanthii_ can potentially cause yield losses on mungbean of up to 43%.
+Mungbean can potentially yield up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [AgMargins; 2019](https://agmargins.net.au/Reports/Details/fced3a80-a762-481c-b812-9953e33410e6). 
+Powdery mildew _Podosphaera xanthii_ can potentially cause yield losses on mungbean of up to 43% [Kelly et.
+al 2017](https://grdc.com.au/resources-and-publications/grdc-update-papers/tab-content/grdc-update-papers/2017/07/mungbean-and-sorghum-disease-update).
 Fortunatley a number of strategies are employed to reduce the damage powdery mildew inflicts on yields.

### 2020-02-26 06_Publication_wireframe_and_7_Questions.Rmd
Add bibliography file

@@
 Mungbean is a short season summer pulse crop which can provide a high returns for growers in eastern Australia. 
-Mungbean can potentially yield up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [AgMargins; 2019](https://agmargins.net.au/Reports/Details/fced3a80-a762-481c-b812-9953e33410e6). 
-Powdery mildew _Podosphaera xanthii_ can potentially cause yield losses on mungbean of up to 43% [Kelly et.
-al 2017](https://grdc.com.au/resources-and-publications/grdc-update-papers/tab-content/grdc-update-papers/2017/07/mungbean-and-sorghum-disease-update).
+Mungbean can potentially yield up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
+Powdery mildew _Podosphaera xanthii_ can potentially cause yield losses on mungbean of up to 43% [@Kelly2017a]. 
 Fortunatley a number of strategies are employed to reduce the damage powdery mildew inflicts on yields.
@@
 #### and conditions for infection
-Powdery mildew infection requires cool temperatures (22$^\circ$ - 26$^\circ$C) and a leaf surface that is not overly wet for infection [Kelly et.
-al 2017](https://grdc.com.au/resources-and-publications/grdc-update-papers/tab-content/grdc-update-papers/2017/07/mungbean-and-sorghum-disease-update).
+Powdery mildew infection requires cool temperatures (22$^\circ$ - 26$^\circ$C) and a leaf surface that is not overly wet for infection [@Kelly2017a]. 
 In southern Queensland and northern New South Wales, planting dates between late spring (November) and mid-summer (January) are advised to avoid the conducsive cooler autumn temperatures which normally commence in March in the southern hemisphere conducive for powdery mildew establishment.
+
 Signs of powdery mildew are almost always first observed when temperatures start to cool.
@@
 ## Materials and methods
+
+## References

### 2020-02-26 index.Rmd
Linebreaks
Added Bibliography

@@
 documentclass: book
-bibliography: 
+bibliography: "Mungbean.bib"
 biblio-style: apalike
@@
 
-+ When is the optimum time to spray fungicide to limit the impact of powdery mildew on mungbean yields?
++ When is the optimum time to spray fungicide to limit the impact of powdery
+mildew on mungbean yields?
 
-+ How has the first sign of powdery mildew changed over the seasons and between experimental sites?
++ How has the first sign of powdery mildew changed over the seasons and between
+experimental sites?
 
-+ Is there an ideal planting time, or fungicide management strategy, which could make use of powdery mildew defoliation during pod maturation resulting in an increased yield?
++ Is there an ideal planting time, or fungicide management strategy, which could
+make use of powdery mildew defoliation during pod maturation resulting in an
+increased yield?
 
@@
 + What is the length of a mungbean season and how has it varied in this trial?
-   - This data has not been collected or is not accurate enough to be useful to answer this question.
+
+   - This data has not been collected or is not accurate enough to be useful to
+   answer this question.
 
@@
 + Variability among host genotypes.  
-   + The probable influence of season might be influenced by host genotype. This is because newer varieties were adopted into experimental trials as they were released.  
-   + Between 2001 and 2015 mungbean genotype changed from Green Diamond, Berken, Crystal to Jade. Jade was the only cultivar used between 2015 and 2019.
+   + The probable influence of season might be influenced by host genotype. This
+   is because newer varieties were adopted into experimental trials as they were
+   released.
 
-+ Estimations of plant maturity stages over each growing season. These estimations might able to be computed using APSIM.
+   + Between 2001 and 2015 mungbean genotype changed from Green Diamond, Berken,
+   Crystal to Jade. Jade was the only cultivar used between 2015 and 2019.
+
+   + Estimations of plant maturity stages over each growing season. These
+   estimations might able to be computed using APSIM.

### 2020-02-26 06_Publication_wireframe_and_7_Questions.Rmd
Added Bibliography
writing

@@
   html_document: default
-bibliography: Mungbean.bib
 ---
@@
 
+*****
+
 # Manuscript
@@
 Mungbean can potentially yield up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
-Powdery mildew _Podosphaera xanthii_ can potentially cause yield losses on mungbean of up to 43% [@Kelly2017a]. 
+However these potenitial crop yields can be limited by powdery mildew (*Podosphaera xanthii*)by up to 40% [@Kelly2017a]. 
 Fortunatley a number of strategies are employed to reduce the damage powdery mildew inflicts on yields.
+
 ### Managements strategies
 #### and conditions for infection
+Planting date is an effective way of preventing the development of powdery mildew in mungbean. 
 Powdery mildew infection requires cool temperatures (22$^\circ$ - 26$^\circ$C) and a leaf surface that is not overly wet for infection [@Kelly2017a]. 
-In southern Queensland and northern New South Wales, planting dates between late spring (November) and mid-summer (January) are advised to avoid the conducsive cooler autumn temperatures which normally commence in March in the southern hemisphere conducive for powdery mildew establishment.
+In southern Queensland and northern New South Wales, sowing dates between late spring (November) and mid-summer (January) are advised to avoid the conducive cooler autumn temperatures which normally commence in March.
+Therefore when sowing is delayed there is a greater chance powdery mildew will infect earlier in the crop development leading to greater yield losses.
 
-Signs of powdery mildew are almost always first observed when temperatures start to cool.
+Commercially available mungbean cultivars in Australia lack suficient resistance to be used soley as a management strategy to avoid yield losses.
+Quantitative disease resistance has been shown in a few cultivars such as Jade-AU, however other management strategies, such as fungicides, are still required.
+
+Treatment of powdery mildew in mungbean with fungicide is currently an effective method for reducing the impact of the disease.
 
@@
 
+*****
 ## Materials and methods
-
-## References

### 2020-02-26 06_Publication_wireframe_and_7_Questions.Rmd
more text, editing and references added

@@
 
-Commercially available mungbean cultivars in Australia lack suficient resistance to be used soley as a management strategy to avoid yield losses.
-Quantitative disease resistance has been shown in a few cultivars such as Jade-AU, however other management strategies, such as fungicides, are still required.
+Commercially available mungbean cultivars in Australia lack sufficient resistance to be used soley as a management strategy for mitigating yield losses.
+Quantitative disease resistance has been observed in breeding lines [@Pandey2018; @Chankaew2013] and mungbean cultivars such as Jade-AU, however other management strategies, such as fungicides, are still required[@Kelly2017a].
 

### 2020-02-26 06_Publication_wireframe_and_7_Questions.Rmd
Writing and editing

@@
 ## Introduction
-Mungbean is a short season summer pulse crop which can provide a high returns for growers in eastern Australia. 
-Mungbean can potentially yield up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
-However these potenitial crop yields can be limited by powdery mildew (*Podosphaera xanthii*)by up to 40% [@Kelly2017a]. 
-Fortunatley a number of strategies are employed to reduce the damage powdery mildew inflicts on yields.
+Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown for human consumption in south-east asia where it is an affordable source of protein [@PulseAustralia]. 
+The bean pod or grain can be consumed raw or added to meals after sprouting. 
+The dried grain can also be ground into a protein enriched flour for uses such as noodles, biscuits and cakes [@Chankaew2013].
+
+Mungbean is grown as a short season summer legume crop which can provide a high returns for growers in eastern Australia. 
+A crop potentially yields up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
+However these potenitial crop yields can be limited by diseases such as powdery mildew (*Podosphaera xanthii*) by up to 40% [@Kelly2017a; @Chankaew2013]. 
+Fortunatley a number of strategies are able to be employed to reduce the damage powdery mildew inflicts on yields.
 

### 2020-02-26 06_Publication_wireframe_and_7_Questions.Rmd
spell check

@@
 
-# Manuscript wireframe
+# Manuscript wire frame
 
@@
 ## Introduction
-Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown for human consumption in south-east asia where it is an affordable source of protein [@PulseAustralia]. 
+Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown for human consumption in south-east Asia where it is an affordable source of protein [@PulseAustralia]. 
 The bean pod or grain can be consumed raw or added to meals after sprouting. 
@@
 A crop potentially yields up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
-However these potenitial crop yields can be limited by diseases such as powdery mildew (*Podosphaera xanthii*) by up to 40% [@Kelly2017a; @Chankaew2013]. 
-Fortunatley a number of strategies are able to be employed to reduce the damage powdery mildew inflicts on yields.
+However these potential crop yields can be limited by diseases such as powdery mildew (*Podosphaera xanthii*) by up to 40% [@Kelly2017a; @Chankaew2013]. 
+Fortunately a number of strategies are able to be employed to reduce the damage powdery mildew inflicts on yields.
 
@@
 
-Commercially available mungbean cultivars in Australia lack sufficient resistance to be used soley as a management strategy for mitigating yield losses.
+Commercially available mungbean cultivars in Australia lack sufficient resistance to be used solely as a management strategy for mitigating yield losses.
 Quantitative disease resistance has been observed in breeding lines [@Pandey2018; @Chankaew2013] and mungbean cultivars such as Jade-AU, however other management strategies, such as fungicides, are still required[@Kelly2017a].
@@
 ### Fungicide resistance
-Lucritive returns of \$ 2260 over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than they are needed.
+Lucrative returns of \$ 2260 over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than they are needed.
 

### 2020-02-27 06_Publication_wireframe_and_7_Questions.Rmd
Edits and writing

@@
 ---
-title: Meta-analysis of fungicide application timing for powdery mildew management
+title: Meta-analysis of fungicide application timing experiments for powdery mildew management
   in mungbean.
@@
 
-Mungbean is grown as a short season summer legume crop which can provide a high returns for growers in eastern Australia. 
-A crop potentially yields up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
+In Australia Mungbean is grown in southern Queensland and northern New South Wales as a short season summer legume crop, with approimatley 90% of yields exported. 
+Mungbean can provide a good return for growers with a potential yield of up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
 However these potential crop yields can be limited by diseases such as powdery mildew (*Podosphaera xanthii*) by up to 40% [@Kelly2017a; @Chankaew2013]. 
-Fortunately a number of strategies are able to be employed to reduce the damage powdery mildew inflicts on yields.
+Fortunately a number of strategies are available to be employed to reduce the damage powdery mildew inflicts on yields.
 
@@
 In southern Queensland and northern New South Wales, sowing dates between late spring (November) and mid-summer (January) are advised to avoid the conducive cooler autumn temperatures which normally commence in March.
-Therefore when sowing is delayed there is a greater chance powdery mildew will infect earlier in the crop development leading to greater yield losses.
+Therefore a delayed sowing date increases the possibility powdery mildew will infect earlier in the crop development leading to greater yield losses.
 
-Commercially available mungbean cultivars in Australia lack sufficient resistance to be used solely as a management strategy for mitigating yield losses.
-Quantitative disease resistance has been observed in breeding lines [@Pandey2018; @Chankaew2013] and mungbean cultivars such as Jade-AU, however other management strategies, such as fungicides, are still required[@Kelly2017a].
+Commercially available mungbean cultivars in Australia lack sufficient resistance to be used as a sole powdery mildew management strategy.
+Quantitative disease resistance has been observed in some breeding lines [@Pandey2018; @Chankaew2013]. 
+In Australia there are very few availble powdery mildew resistant cultivars. 
+Jade-AU is recommended as containing the best disease resistance to powdery mildew and other foliar diseases, such as tan spot and halo blight.
+However other disease management strategies, such as fungicides, are still required [@Kelly2017a].
 

### 2020-02-28 06_Publication_wireframe_and_7_Questions.Rmd
editing and writing

@@
 In Australia there are very few availble powdery mildew resistant cultivars. 
-Jade-AU is recommended as containing the best disease resistance to powdery mildew and other foliar diseases, such as tan spot and halo blight.
+Jade-AU is recommended as containing the best disease resistance to powdery mildew (moderately susceptible), and other foliar diseases, such as tan spot and halo blight [@AustralianMungbeanAssociation].
 However other disease management strategies, such as fungicides, are still required [@Kelly2017a].
@@
 Treatment of powdery mildew in mungbean with fungicide is currently an effective method for reducing the impact of the disease. 
+Past field trials in eastern Australia have trialed a range of fungicides, some of which have been registered with the APVMA (Australian Pes.....) for treating powdery mildew in mungbean [@Kelly2017a; insert all published trials here].
 

### 2020-02-28 04_MetaAnalysis.Rmd

@@
    install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer)
+pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer, netmeta)
 
@@
 # Data
-slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv"
+slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv"
 )
@@
 ```{r variance_histograms}
-hist(slimmer_PM_dat$yield_error) # yield error is not normally distributed
-hist(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is normally distributed 
+hist_usq(slimmer_PM_dat$yield_error) # yield error is not normally distributed
+hist_usq(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is normally distributed 
 ```
@@
 ```{r imputing_MSE_dataSpread}
-slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
-hist(unique(slimmer_PM_dat$Y_Msquare))
-hist(log(unique(slimmer_PM_dat$Y_Msquare))) # log mean square has a more normal distribution
+slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv")
+hist_usq(unique(slimmer_PM_dat$Y_Msquare))
+hist_usq(log(unique(slimmer_PM_dat$Y_Msquare))) # log mean square has a more normal distribution
 
@@
 Finally we will assign factor classes to the main variables in the meta-analysis. Note that variable trial is a combination of:
-   - Trial identifier  
-   - Trial year  
-   - Trial location  
-   - Host genotype  
-   - Trial row spacing
+
+   * Trial identifier
+
+   * Trial year
+
+   * Trial location
+
+   * Host genotype
+
+   * Trial row spacing
 
@@
 ```
-&spun;  
-&spun;  
+
+*****s
+
 To make it easier to compare each of the treatments we can compute the meta-analysis contrasts.
@@
 Let's analyse the data again using a different statistical approach to see if our outcome with the `metafor` package was robust.
-The `netmeta` package uses a frequentness approach to the analysis, and focuses on the pairwise comparisons between treatments.
+The `netmeta` package uses a frequentist approach to the analysis and focuses on the pairwise comparisons between treatments.
 
 ```{r netmeta-analysis}
-library(netmeta)
-
 datPM3 <- slimmer_PM_dat %>%

### 2020-02-28 05_AUDPC_MetaAnalysis.Rmd
Change data/ location to cache/

@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer, metafor)
+pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer, metafor, here)
 
 # Data
-PM_Mdat <- read.csv("data/GYmeta_data.csv")
+PM_Mdat <- read.csv(here("cache/GYmeta_data.csv"))
 ```

### 2020-03-01 06_Publication_wireframe_and_7_Questions.Rmd
Update references

@@
 
-Treatment of powdery mildew in mungbean with fungicide is currently an effective method for reducing the impact of the disease. 
-Past field trials in eastern Australia have trialed a range of fungicides, some of which have been registered with the APVMA (Australian Pes.....) for treating powdery mildew in mungbean [@Kelly2017a; insert all published trials here].
+If the planting date late, treatment of powdery mildew in mungbean with fungicide is currently the next best method for reducing mungbean yield damage caused by the disease. 
+Past field trials in eastern Australia have trialed a range of fungicides [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
+Some of the trialed fungicides have been registered with the APVMA (Australian Pes.....) for treating powdery mildew in mungbean [@Kelly2017a; insert all published trials here].
 

### 2020-03-01 01_Meta-analysis_experiments.Rmd
Correct table so one line per trial

@@
          trial_ref,
-         year,
-         location,
-         trial_design,
-         replicates,
-         planting_date,
-         emergence_date,
-         first_sign_disease
       ) %>%
-      summarise(treatments = length(n_treatment)),
+      summarise(year = unique(year),
+                location = unique(location),
+                mean_treat_replicates = mean(replicates),
+                planting_date = unique(planting_date),
+                first_sign_disease = unique(first_sign_disease),
+                treatments = length(n_treatment)),
    caption = "Description of Experiments"

### 2020-03-01 06_Publication_wireframe_and_7_Questions.Rmd
editing and writing, and referencing

--- 2020-02-28 06_Publication_wireframe_and_7_Questions.Rmd
@@
 
-Treatment of powdery mildew in mungbean with fungicide is currently an effective method for reducing the impact of the disease. 
-Past field trials in eastern Australia have trialed a range of fungicides, some of which have been registered with the APVMA (Australian Pes.....) for treating powdery mildew in mungbean [@Kelly2017a; insert all published trials here].
+If the planting date is not suficiently early to avoid conducive conditions for powdery mildew, treating mungbean with fungicide is currently the next best method for reducing mungbean yield damage caused by the disease.
+Past field trials in eastern Australia have trialed a range of fungicide active ingredients (table), while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
+Early trials indicated to obtain maximum efficacy a single fungicide application at first sign of the disease with another follow-up application two weeks later if necessary []. 
+Some of the trialed fungicides have been registered with the APVMA [@APVMA] for treating powdery mildew in mungbean [@Kelly2017a; insert all published trials here].
 
@@
 ## Materials and methods
+
+The data for this study was obtained from through personal correspondance with collegues and collaborating institutions.
+Prior to 2012 experimental trials were undertaken by Malcolmn Riley and Dr Sue Thompson with The Department of Agriculture and Primary industres. 
+Trials undertaken in 2013 were conducted by the Northern growers alliance [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013].

### 2020-03-01 01_Meta-analysis_experiments.Rmd
arrange table

--- 2020-02-26 01_Meta-analysis_experiments.Rmd
@@
    PM.dat %>%
-      group_by(
-         trial_ref,
-         year,
-         location,
-         trial_design,
-         replicates,
-         planting_date,
-         emergence_date,
-         first_sign_disease
-      ) %>%
-      summarise(treatments = length(n_treatment)),
+      group_by(trial_ref,) %>%
+      summarise(year = unique(year),
+                location = unique(location),
+                mean_treat_replicates = mean(replicates),
+                planting_date = unique(planting_date),
+                first_sign_disease = unique(first_sign_disease),
+                treatments = length(n_treatment))%>%
+      arrange(year),
    caption = "Description of Experiments"

### 2020-03-02 06_Publication_wireframe_and_7_Questions.Rmd
Insert table 1 of experiments

@@
 *****
+
 ## Materials and methods
@@
 The data for this study was obtained from through personal correspondance with collegues and collaborating institutions.
-Prior to 2012 experimental trials were undertaken by Malcolmn Riley and Dr Sue Thompson with The Department of Agriculture and Primary industres. 
+The majority of the trials were undertaken by Malcolmn Riley and Dr Sue Thompson with The Department of Agriculture and Primary industres (DAF). 
 Trials undertaken in 2013 were conducted by the Northern growers alliance [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013].
+The most recent trials from 2017 were undertaken by DAF and the University of Southern Queensland (USQ) from 2017 to 2019 (Table 1).
+
+```{r Table1_, echo=TRUE, message=FALSE, warning=FALSE}
+PM.dat <- import_data()
+
+PM.dat %>%
+      group_by(trial_ref,) %>%
+      summarise(year = unique(year),
+                location = unique(location),
+                planting_date = unique(planting_date),
+                first_sign_disease = unique(first_sign_disease))%>%
+      arrange(year)%>%
+   left_join(data.frame(trial_ref = unique(PM.dat$trial_ref),
+                        Research_org =
+                           c(rep("Queensland DAF",times =12),
+                             rep("Northern Growers Alliance", times = 4),
+               rep("Queensland DAF",times =5),
+               rep("USQ", times = 5))))%>%
+kable(caption = "Table 1: Description of Experiments")%>%
+   kable_styling(fixed_thead = TRUE,
+                 full_width = TRUE) %>%
+   scroll_box(width = "900px", height = "500px")
+```

### 2020-03-02 06_Publication_wireframe_and_7_Questions.Rmd
more text

@@
 Jade-AU is recommended as containing the best disease resistance to powdery mildew (moderately susceptible), and other foliar diseases, such as tan spot and halo blight [@AustralianMungbeanAssociation].
-However other disease management strategies, such as fungicides, are still required [@Kelly2017a].
+Because cultivar choice does not confer complete resistance to powdery mildew treating mungbean with fungicide is still required to limit yield damage when conditions for the disease are suitable.
 
-If the planting date is not suficiently early to avoid conducive conditions for powdery mildew, treating mungbean with fungicide is currently the next best method for reducing mungbean yield damage caused by the disease.
+### Previous studies - fungicide work
+There is almost a complete lack of peer-reviewed experiments testing fungicide efficacy on powdery mildew in Mungbean. What information is available
 Past field trials in eastern Australia have trialed a range of fungicide active ingredients (table), while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
@@
 Lucrative returns of \$ 2260 over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than they are needed.
-
-### Previous studies
 
@@
 The most recent trials from 2017 were undertaken by DAF and the University of Southern Queensland (USQ) from 2017 to 2019 (Table 1). 
+The data from the collection of trials were in different formats with varying levels of information.
+Some trial data reporting means of each treatment, others we were able to obtain the complete raw data.
 
-```{r Table1_, echo=TRUE, message=FALSE, warning=FALSE}
+Details of trial data is presented within a research compendium which was prepared to suppliment this publication [insert referance to compendium].
+
+The inclusion of trial data was set to the following criteria; an field trial testing the efficacy of Dimethylase inhibitor (DMI) for control of powdery mildew in the northern grains regions, in eastern Australia.
+All the trials included in this analysis were trial have not previously been published in peer-reviewed literature.
+
+```{r Table1_ExperimentalDetail, echo=TRUE, message=FALSE, warning=FALSE}
 PM.dat <- import_data()

### 2020-03-06 06_Publication_wireframe_and_7_Questions.Rmd
more writing

@@
 
-In Australia Mungbean is grown in southern Queensland and northern New South Wales as a short season summer legume crop, with approimatley 90% of yields exported. 
+In Australia Mungbean is grown in southern Queensland and northern New South Wales as a short season summer legume crop, with approximately 90% of yields exported. 
 Mungbean can provide a good return for growers with a potential yield of up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
@@
 Quantitative disease resistance has been observed in some breeding lines [@Pandey2018; @Chankaew2013]. 
-In Australia there are very few availble powdery mildew resistant cultivars. 
+In Australia there are very few available powdery mildew resistant cultivars. 
 Jade-AU is recommended as containing the best disease resistance to powdery mildew (moderately susceptible), and other foliar diseases, such as tan spot and halo blight [@AustralianMungbeanAssociation].
@@
 There is almost a complete lack of peer-reviewed experiments testing fungicide efficacy on powdery mildew in Mungbean. What information is available
-Past field trials in eastern Australia have trialed a range of fungicide active ingredients (table), while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
+Past field trials in eastern Australia have trialled a range of fungicide active ingredients (table), while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
 Early trials indicated to obtain maximum efficacy a single fungicide application at first sign of the disease with another follow-up application two weeks later if necessary []. 
-Some of the trialed fungicides have been registered with the APVMA [@APVMA] for treating powdery mildew in mungbean [@Kelly2017a; insert all published trials here].
+Some of the trialled fungicides have been registered with the APVMA [@APVMA] for treating powdery mildew in mungbean [@Kelly2017a; insert all published trials here].
 
@@
 
-### Meta-analyes
+### Meta-analysis
 
@@
 
-The data for this study was obtained from through personal correspondance with collegues and collaborating institutions.
-The majority of the trials were undertaken by Malcolmn Riley and Dr Sue Thompson with The Department of Agriculture and Primary industres (DAF). 
+The data for this study was obtained from through personal correspondence with colleagues and collaborating institutions.
+The majority of the trials were undertaken by Malcolm Riley and Dr Sue Thompson with The Department of Agriculture and Primary industries (DAF). 
 Trials undertaken in 2013 were conducted by the Northern growers alliance [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013].
@@
 
-Details of trial data is presented within a research compendium which was prepared to suppliment this publication [insert referance to compendium].
+Details of trial data is presented within a research compendium which was prepared to supplement this publication [insert reference to compendium].
 
-The inclusion of trial data was set to the following criteria; an field trial testing the efficacy of Dimethylase inhibitor (DMI) for control of powdery mildew in the northern grains regions, in eastern Australia.
-All the trials included in this analysis were trial have not previously been published in peer-reviewed literature.
+The inclusion of trial data was set to the following criteria; an field trial testing the efficacy of demethylase inhibitors (DMI), tebuconazole or propiconazole, for powdery mildew control on mungbean in the northern grains regions of eastern Australia.
+All the trials included in this analysis were  not previously been published in peer-reviewed literature.
+Some trials and results were reported online via the Grains Research and Development Corporation.
+
+Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 - 9 ordinal scale [ref].
+The NGA 2013 trials reported incidence as a percentage of leaves covered by the disease. 
+Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, it was easy to calculate the equivalent incidence on the ordinal 1 - 9 scale.
+
+Fungicide application timing, with reference to when the disease first occurred in the trial, and number of applications were used to define a treatment variable.
+'Early' fungicide applications, referred to when a fungicide spray schedule commenced with it's first spray prior to the disease being observed in the trial. 
+'Recommended' refereed to fungicide spray schedules which commenced within three days of the first sign of disease, and 'late' treatments which commenced four days or later than first sign. 
+The number of fungicide applications were binned in to two categories.
+A spray schedule with a single spray, and a spray schedule with one or more sprays, where there was a maximum of three applications.
 

### 2020-03-12 06_Publication_wireframe_and_7_Questions.Rmd
writing and editing

@@
 
-In Australia Mungbean is grown in southern Queensland and northern New South Wales as a short season summer legume crop, with approximately 90% of yields exported. 
-Mungbean can provide a good return for growers with a potential yield of up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
-However these potential crop yields can be limited by diseases such as powdery mildew (*Podosphaera xanthii*) by up to 40% [@Kelly2017a; @Chankaew2013]. 
+In Australia Mungbean is grown in southern Queensland and northern New South Wales as a short season summer legume crop. 
+Approximately 90% of mungbean yields are exported providing good returns for growers. 
+Mungbean potentially yields up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
+However these potential crop yields can be limited by a range of diseases[@Kelly2017a].
+Powdery mildew (*Podosphaera xanthii*), for instance limits yields by up to 40% [@Chankaew2013]. 
 Fortunately a number of strategies are available to be employed to reduce the damage powdery mildew inflicts on yields.
@@
 Commercially available mungbean cultivars in Australia lack sufficient resistance to be used as a sole powdery mildew management strategy.
-Quantitative disease resistance has been observed in some breeding lines [@Pandey2018; @Chankaew2013]. 
-In Australia there are very few available powdery mildew resistant cultivars. 
+Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013]. 
+While some quantitive resistance has been incorporated into Australian varieties there remain few powdery mildew resistant cultivars. 
 Jade-AU is recommended as containing the best disease resistance to powdery mildew (moderately susceptible), and other foliar diseases, such as tan spot and halo blight [@AustralianMungbeanAssociation].
@@
 
+The recent release of 'PowderyMildewMDM' a desicion support system (DSS) increases the ease for preparing a fungicide spray scheduale to manage powdery mildew. 
+PowderyMildewMDM provides a cost benefit analysis to growers for spray scheduale scenarios.
+The user inputs weather, crop, and economic inputs into the DSS and the app returns the probability one or two fungicide sprays would protect yields suffiently to cover the costs of the fungicide applications.
+
 ### Previous studies - fungicide work
-There is almost a complete lack of peer-reviewed experiments testing fungicide efficacy on powdery mildew in Mungbean. What information is available
-Past field trials in eastern Australia have trialled a range of fungicide active ingredients (table), while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
-Early trials indicated to obtain maximum efficacy a single fungicide application at first sign of the disease with another follow-up application two weeks later if necessary []. 
-Some of the trialled fungicides have been registered with the APVMA [@APVMA] for treating powdery mildew in mungbean [@Kelly2017a; insert all published trials here].
+There is almost a complete lack of peer-reviewed literature summarising fungicide efficacy on powdery mildew in Mungbean. 
+Many of the experimental work has been published by funding agencies and state government extension departments. 
+Past field trials in eastern Australia have trialed a range of fungicide active ingredients (table), while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
+Early trials showed for a fungicide application to provide maximum efficacy a single fungicide application at first sign of the disease with another follow-up application two weeks later if necessary [@Sparks2017].
+Some of the trialled fungicides for treating powdery mildew in mungbean have been registered with the APVMA [@APVMA; @Kelly2017a; insert all published trials here].
 
@@
 The majority of the trials were undertaken by Malcolm Riley and Dr Sue Thompson with The Department of Agriculture and Primary industries (DAF). 
-Trials undertaken in 2013 were conducted by the Northern growers alliance [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013].
+Trials undertaken in 2013 season were conducted by the Northern growers alliance [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013].
 The most recent trials from 2017 were undertaken by DAF and the University of Southern Queensland (USQ) from 2017 to 2019 (Table 1). 
-The data from the collection of trials were in different formats with varying levels of information.
-Some trial data reporting means of each treatment, others we were able to obtain the complete raw data.
+The data from trials were in different formats with varying levels of information.
+Some trial data reporting means of each treatment, others contained the complete raw data.
 
@@
 
-The inclusion of trial data was set to the following criteria; an field trial testing the efficacy of demethylase inhibitors (DMI), tebuconazole or propiconazole, for powdery mildew control on mungbean in the northern grains regions of eastern Australia.
+The inclusion of trial data required a field trial testing the efficacy of  for powdery mildew control on mungbean in the northern grains regions of eastern Australia. 
 All the trials included in this analysis were not previously been published in peer-reviewed literature.
@@
 
+Differences between each trial were likely to influence the analysis and in an effort to reduce confounding effects we only included treatments within trials which had been sprayed with one of fungcides from demethylase inhibitors (DMI) group.
+Fungicide actives from the DMI group was the main inclusion factor for the analysis which reduced the number of studies from 24 to 17 experiments.
+DMI fungicides which were used for experimentation for powdery mildew control on mungbean were tebuconazole and propiconazole,
+
 Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 - 9 ordinal scale [ref].
-The NGA 2013 trials reported incidence as a percentage of leaves covered by the disease. 
+The NGA 2013 trials reported incidence as a percentage of leaves covered by the disease at different plant heights. 
 Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, it was easy to calculate the equivalent incidence on the ordinal 1 - 9 scale.

### 2020-03-13 06_Publication_wireframe_and_7_Questions.Rmd
editing and writing

@@
 The data from trials were in different formats with varying levels of information.
-Some trial data reporting means of each treatment, others contained the complete raw data.
+Some trial data reporting means of each treatment, with all but one study reporting variance along with the mean. 
+While other trials the raw data were available.
 
@@
 
-The inclusion of trial data required a field trial testing the efficacy of  for powdery mildew control on mungbean in the northern grains regions of eastern Australia. 
+The criteria for inclusion of trial data in the meta-analysis, required a field trial testing fungicide efficacy for powdery mildew control on mungbean in the northern grains regions of eastern Australia.
 All the trials included in this analysis were not previously been published in peer-reviewed literature.
@@
 
-Differences between each trial were likely to influence the analysis and in an effort to reduce confounding effects we only included treatments within trials which had been sprayed with one of fungcides from demethylase inhibitors (DMI) group.
-Fungicide actives from the DMI group was the main inclusion factor for the analysis which reduced the number of studies from 24 to 17 experiments.
-DMI fungicides which were used for experimentation for powdery mildew control on mungbean were tebuconazole and propiconazole,
+Differences between each trial were likely to influence the analysis therefore in an effort to reduce confounding effects we only included treatments within trials which had been sprayed with a fungicide which has a mode of action which categoraises it as a demethylase inhibitor (DMI).
+Fungicide active from the DMI group was the main inclusion factor for the analysis which reduced the number of trials from 24 to 17 experiments. 
+DMI fungicides which were used for experimentation for powdery mildew control on mungbean were tebuconazole and propiconazole.
 
 Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 - 9 ordinal scale [ref]. 
-The NGA 2013 trials reported incidence as a percentage of leaves covered by the disease at different plant heights. 
+The 2013 NGA trials reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the canopy; lower, middle or upper canopy. 
 Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, it was easy to calculate the equivalent incidence on the ordinal 1 - 9 scale.
 
-Fungicide application timing, with reference to when the disease first occurred in the trial, and number of applications were used to define a treatment variable.
-'Early' fungicide applications, referred to when a fungicide spray schedule commenced with it's first spray prior to the disease being observed in the trial. 
-'Recommended' refereed to fungicide spray schedules which commenced within three days of the first sign of disease, and 'late' treatments which commenced four days or later than first sign. 
+The timing of fungicide applications, with reference to when the disease first occurred in the trial, and number of applications were used to define a treatment variable.
+An 'Early' fungicide application, refers to a fungicide spray schedule that commences with it's first spray prior to the disease being observed in the trial.  
+'Recommended' refers to a fungicide spray schedule which commences within three days following the first sign of disease, and 'late' treatments which commence four days or later than first sign. 
 The number of fungicide applications were binned in to two categories.
-A spray schedule with a single spray, and a spray schedule with one or more sprays, where there was a maximum of three applications.
+A spray schedule with a single spray, and a spray schedule with one or more sprays where there was a maximum of three applications.  
+The division of the treatments into these six categories created two categories with insuffient numbers of treatments to provide a reliable sample. 
+Single late sprays contained two treatments and Mulitple early sprays contained five treatments therefore they were removed from the subsequent meta-analysis.
+
+What remained was the mean yield for total of 173 treatments, forty of which were left unsprayed, in the following four spray schedule categories: single early spray, single recommended spray, recommended with multiple sprays, late with multiple sprays.
 

### 2020-04-01 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Updating planting dates for NGA trials and some data input correction

@@
               replicate = Goolhi_13$Rep,
-              planting_date = NA,
+              planting_date = as.Date("2013-01-23", format = "%Y-%m-%d"),
               emergence_date = NA,
@@
               year = "2013",
-              location = "Mary's mount",
+              location = "Marys Mount",
               host_genotype = "Crystal",
@@
               replicate = MarysM_13$Rep,
-              planting_date = NA,
+              planting_date = as.Date("2012-12-24", format = "%Y-%m-%d"),
               emergence_date = NA,
@@
               replicate = Premer_13$Rep,
-              planting_date = as.Date("2013-12-28", format = "%Y-%m-%d"),
+              planting_date = as.Date("2012-12-28", format = "%Y-%m-%d"),
               emergence_date = as.Date(NA),
@@
               replicate = Millm_13$Rep,
-              planting_date = as.Date(NA),
+              planting_date = as.Date("2013-01-12", format = "%Y-%m-%d"), # Lawrie prices guess for planting date
               emergence_date = as.Date(NA),
@@
 ```
+
 #### Mean Disease incidence assessments through the 2016 season
@@
 #### Define treatment data
-```{r Well_18_treatmentDefine}
+```{r Herm_19_treatmentDefine}
 Herm_19_dat <- PM_MB_19 %>%

### 2020-04-01 02_Preliminary_analysis.Rmd
Correct filepath

@@
 lm_rain1 <-
-   read.csv("data/lmInSeasonRainfall_-10.09_30.64.csv",
+   read.csv("cache/lmInSeasonRainfall_-10.09_30.64.csv",
             stringsAsFactors = FALSE)
 lm_rain2 <-
-   read.csv("data/lmInSeasonRainfall_-10.09_65.100.csv",
+   read.csv("cache/lmInSeasonRainfall_-10.09_65.100.csv",
             stringsAsFactors = FALSE)
 lm_rain3 <-
-   read.csv("data/lmInSeasonRainfall_10.30_30.64.csv",
+   read.csv("cache/lmInSeasonRainfall_10.30_30.64.csv",
             stringsAsFactors = FALSE)
 lm_rain4 <-
-   read.csv("data/lmInSeasonRainfall_10.30_65.100.csv",
+   read.csv("cache/lmInSeasonRainfall_10.30_65.100.csv",
             stringsAsFactors = FALSE)

### 2020-04-01 R/slimming_PM_dat.R
Updated filepaths

@@ -3,7 +3,7 @@
 
 #source("R/import_data.R")
 # PM_MB_Mtemp <- import_data()
-PM_MB_Mtemp <- read.csv("data/1911_PM_MB_means&Ygains.csv")
+PM_MB_Mtemp <- read.csv("cache/1911_PM_MB_means&Ygains.csv")
 
 slim_PM_dat <- data.frame(
    trial = paste(PM_MB_Mtemp$trial_ref, PM_MB_Mtemp$year,

### 2020-04-02 03_Prep_data.Rmd
Updated filepaths

@@
 write.csv(PM_MB_means,
-          "data/1911_PM_MB_means&Ygains.csv")
+          "cache/1911_PM_MB_means&Ygains.csv")
 ```
@@
 
-write.csv(slimmer_PM_dat, file = "data/slimmer_PM_clusterdat.csv", row.names = FALSE)
+write.csv(slimmer_PM_dat, file = "cache/slimmer_PM_clusterdat.csv", row.names = FALSE)
 ```

### 2020-04-02 02_Preliminary_analysis.Rmd
Correct planting date plot

@@
 # Create the data frame for the plot
+source("R/import_data.R")
+PM_MB_means <- import_data()
 season_dates <- PM_MB_means %>%
@@
       First_sign_PM = unique(first_sign_disease),
-      season_length = as.integer(as.Date(unique(harvest_date)) - as.Date(unique(planting_date)))
+      season_length = as.Date(unique(harvest_date)) - as.Date(unique(planting_date))
    )
@@
 season_dates$Disease_day <- yday(season_dates$First_sign_PM)
+
+season_dates[1:2, "Planting_day"] <- 1
+ #  yday(as.Date("2012-02-28") - 7) # Correct dplanted in december and emerged in February, Assuming due to lack of rain or recording error. Using 7 days prior to emergence day as planting day
+
 season_dates$Harvest_day <-
@@
 
-season_dates[1, "Planting_day"] <-
-   yday(as.Date("2012-02-28") - 7) # planted in december and emerged in February, Assuming due to lack of rain or recording error. Using 7 days prior to emergence day as planting day
-
-first_day_month <- c(0, 31, 59, 90, 120, 151, 181, 211, 243, 273)
+first_day_month <- c(0, 31, 59, 90, 120, 151, 181, 211, 243, 273)+1
 axis_labels_date <-
@@
    ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
+warnings()
 ```

### 2020-04-03 06_Publication_wireframe_and_7_Questions.Rmd
edits and writing
writing and editing

@@
 
-In Australia Mungbean is grown in southern Queensland and northern New South Wales as a short season summer legume crop. 
+In Australia mungbean is grown in southern Queensland and northern New South Wales as a short season summer legume crop. 
 Approximately 90% of mungbean yields are exported providing good returns for growers. 
@@
 #### and conditions for infection
-Planting date is an effective way of preventing the development of powdery mildew in mungbean. 
-Powdery mildew infection requires cool temperatures (22$^\circ$ - 26$^\circ$C) and a leaf surface that is not overly wet for infection [@Kelly2017a]. 
+Planting date is an effective strategy for preventing the development of powdery mildew in mungbean. 
+Powdery mildew infection requires cool temperatures, between 22$^\circ$ and 26$^\circ$C, and a leaf surface that is not overly wet for infection [@Kelly2017a]. 
 In southern Queensland and northern New South Wales, sowing dates between late spring (November) and mid-summer (January) are advised to avoid the conducive cooler autumn temperatures which normally commence in March.
@@
 Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013]. 
-While some quantitive resistance has been incorporated into Australian varieties there remain few powdery mildew resistant cultivars. 
-Jade-AU is recommended as containing the best disease resistance to powdery mildew (moderately susceptible), and other foliar diseases, such as tan spot and halo blight [@AustralianMungbeanAssociation].
-Because cultivar choice does not confer complete resistance to powdery mildew treating mungbean with fungicide is still required to limit yield damage when conditions for the disease are suitable.
+While some quantitive resistance has also been incorporated into Australian varieties, only a couple of powdery mildew resistant cultivars are commercially available. 
+Jade-AU is recommended as containing the best disease resistance to powdery mildew (moderately susceptible), while also confering quantifiable resistance to other foliar diseases such as tan spot and halo blight [@AustralianMungbeanAssociation].
+Because cultivar choice does not confer complete resistance to powdery mildew additional strategies such as fungicide treatments are necessary to limit yield damage when conditions for the disease are suitable.
 
 The recent release of 'PowderyMildewMDM' a desicion support system (DSS) increases the ease for preparing a fungicide spray scheduale to manage powdery mildew. 
-PowderyMildewMDM provides a cost benefit analysis to growers for spray scheduale scenarios.
-The user inputs weather, crop, and economic inputs into the DSS and the app returns the probability one or two fungicide sprays would protect yields suffiently to cover the costs of the fungicide applications.
+PowderyMildewMDM provides a cost benefit analysis to growers for fungcide spray scheduale scenarios.
+The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability one or two fungicide sprays would protect yields suffiently to cover the costs of the fungicide applications and yield a profit.
+
+### Fungicide resistance
+Lucrative returns of \$ 2260 over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than they are needed.
 
@@
 Some of the trialled fungicides for treating powdery mildew in mungbean have been registered with the APVMA [@APVMA; @Kelly2017a; insert all published trials here].
-
-### Fungicide resistance
-Lucrative returns of \$ 2260 over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than they are needed.
 
@@
 The most recent trials from 2017 were undertaken by DAF and the University of Southern Queensland (USQ) from 2017 to 2019 (Table 1). 
-The data from trials were in different formats with varying levels of information.
+Trial data were in different formats with varying levels of information.
 Some trial data reporting means of each treatment, with all but one study reporting variance along with the mean. 
-While other trials the raw data were available.
+For XX trials the raw data were obtained.
 
@@
 The criteria for inclusion of trial data in the meta-analysis, required a field trial testing fungicide efficacy for powdery mildew control on mungbean in the northern grains regions of eastern Australia.
-All the trials included in this analysis were not previously been published in peer-reviewed literature.
+Trial data had to include the date when powdery mildew was first observed. 
+Trials needed to have tested a demethylase inhibitor (DMI) fungicide.
+
+All trials included in this analysis were not previously published in peer-reviewed literature.
 Some trials and results were reported online via the Grains Research and Development Corporation.
 
-Differences between each trial were likely to influence the analysis therefore in an effort to reduce confounding effects we only included treatments within trials which had been sprayed with a fungicide which has a mode of action which categoraises it as a demethylase inhibitor (DMI).
+While the main aim of all the trials collected for this study were the same, assess the efficacy of fungicides for control of powdery mildew, most also aimed to test the effect of different variables on fungicide efficacy.
+Some of the variable which were suspected to influence powdery mildew incidence and the effect on yield were: trial location, trial season, row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar, irrigation and rainfall.
+To account for this variation between trials and thr treatments within the trial a single 'trial' factor was created to describe the main variables; Trial location, trial season, host genotype and row spacing.
+
+To reduce confounding effects of various fungicides we only included treatments within trials which had been sprayed with a fungicide which has a DMI mode of action, such as tebeconazole and propiconazole.
 Fungicide active from the DMI group was the main inclusion factor for the analysis which reduced the number of trials from 24 to 17 experiments.
-DMI fungicides which were used for experimentation for powdery mildew control on mungbean were tebuconazole and propiconazole.
 
@@
 The division of the treatments into these six categories created two categories with insuffient numbers of treatments to provide a reliable sample. 
-Single late sprays contained two treatments and Mulitple early sprays contained five treatments therefore they were removed from the subsequent meta-analysis.
+Single late sprays contained two replicates and mulitple early sprays contained five replicates and were therefore removed from the subsequent meta-analysis.
 
-What remained was the mean yield for total of 173 treatments, forty of which were left unsprayed, in the following four spray schedule categories: single early spray, single recommended spray, recommended with multiple sprays, late with multiple sprays.
+What remained was the mean yield for total of 173 treatments in the following five spray schedule categories: no spray control, single early spray, single recommended spray, recommended with multiple sprays and late with multiple sprays.
+
+Trials where we obtained the raw data the response variables were summarised into the treatment means and variance. 
+The remainder of the trial data reported treatment means and variance. 
+Two of the trials, Gatton 2012 and Emerald 2015, reported treatment means without accompaning variance. 
+For these trials the trial variance was imputed by randomly sampling the trial mean squared error from a distribution of log trial MSE.  
+$rnorm(\overline{x}_{log(MSE_{1}) \dots, log(MSE_{n})}, \sigma_{log(MSE_{1}) \dots, log(MSE_{n})}) $  
+Where MSE is the mean squared error of each trial.
+
+$v_i = MSE_{y}/(n * Y_{i}^2) $
+
+The data were analysed in the R statistical software environment using two meta-analysis packages, `metafor` and `netmeta`.
 

### 2020-04-03 R/slimming_PM_dat.R
add genotype

@@ -11,6 +11,7 @@ slim_PM_dat <- data.frame(
                  PM_MB_Mtemp$row_spacing, sep = "_"),
    trial_ref = as.character(PM_MB_Mtemp$trial_ref),
    year = as.integer(PM_MB_Mtemp$year),
+   host_genotype = PM_MB_Mtemp$host_genotype,
    location = as.character(PM_MB_Mtemp$location),
    row_spacing = as.double(PM_MB_Mtemp$row_spacing),
    n = as.integer(PM_MB_Mtemp$replicates),

### 2020-04-20 06_Publication_wireframe_and_7_Questions.Rmd
writing and editing

@@
 ## Introduction
-Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown for human consumption in south-east Asia where it is an affordable source of protein [@PulseAustralia]. 
+Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown in south-east Asia for human consumption, and constitutes an affordable source of protein [@PulseAustralia]. 
 The bean pod or grain can be consumed raw or added to meals after sprouting. 
@@
 Approximately 90% of mungbean yields are exported providing good returns for growers. 
-Mungbean potentially yields up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
+Mungbean potentially yields up to 2.3 tonnes per hectare, with a value of up to \$ 1300 AUD a tonne [@QueenslandGovernment2019]. 
 However these potential crop yields can be limited by a range of diseases[@Kelly2017a].
@@
 Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013]. 
-While some quantitive resistance has also been incorporated into Australian varieties, only a couple of powdery mildew resistant cultivars are commercially available. 
+In Australia, quantitive resistance has also been incorporated a couple of varieties which have been made commercially available. 
 Jade-AU is recommended as containing the best disease resistance to powdery mildew (moderately susceptible), while also confering quantifiable resistance to other foliar diseases such as tan spot and halo blight [@AustralianMungbeanAssociation].
-Because cultivar choice does not confer complete resistance to powdery mildew additional strategies such as fungicide treatments are necessary to limit yield damage when conditions for the disease are suitable.
+Because cultivar choice does not confer complete resistance to powdery mildew additional strategies such as fungicide treatments are necessary to limit yield loss when conditions for the disease are suitable.
 
@@
 PowderyMildewMDM provides a cost benefit analysis to growers for fungcide spray scheduale scenarios.
-The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability one or two fungicide sprays would protect yields suffiently to cover the costs of the fungicide applications and yield a profit.
+The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability one or two fungicide sprays would protect yields suffiently to increase the net profit.
 
 ### Fungicide resistance
-Lucrative returns of \$ 2260 over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than they are needed.
+Fungicide application costs in Australia are relativly cheap, and we estimate these to be approximatley \$ 20 AUD per hectare. 
+Lucrative returns of up to \$ 2260 per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than neccercary. 
+This poses a problem for diseases such as powdery mildew which is well known for evolving fungicide resistance if spray schedules are not applied with reducing fungicide resistance risk in mind. 
+Fungicide resistant strains of powdery mildew have been known to establish rapidly. 
+In cucurbits, powdery mildew has evolved resistance to numerous fungicide classes, such as benzimidazoles, DMIs, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines [@techreport].
 
@@
 ```
+
+## Discussion
+
+At the time of writing, in Australia two fungicides are registered to treat powdery mildew in mungbean, Veritas/Custodia (200 g/L tebuconazole with 120 g/L azoxystrobin) and tebuconazole.
+Having only a two fungicides registered with similar modes of action may also be contributing to decreased sensitivity of the pathogen.
+Alternating fungicide applications with
+Registation of a fungicide with a different mode of action should be available for growers to alternate fungicides and reduce the speed at which fungicide resistance can develop.

### 2020-04-20 06_Publication_wireframe_and_7_Questions.Rmd
Made changes so document would render

@@
 ---
-title: Meta-analysis of fungicide application timing experiments for powdery mildew management
-  in mungbean.
+title: Meta-analysis of fungicide application timing experiments for powdery mildew
+  management in mungbean.
 author: "P. Melloy"
@@
 output:
+  word_document: default
   html_document: default
 ---
+
+```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(tidyverse, kableExtra, here)
+
+# Data
+PM_Mdat <- read.csv(here("cache/PM_MB_updated.csv"))
+
+```
 
@@
 ```{r Table1_ExperimentalDetail, echo=TRUE, message=FALSE, warning=FALSE}
-PM.dat <- import_data()
 
-PM.dat %>%
+PM_Mdat %>%
       group_by(trial_ref,) %>%
@@
       arrange(year)%>%
-   left_join(data.frame(trial_ref = unique(PM.dat$trial_ref),
+   left_join(data.frame(trial_ref = unique(PM_Mdat$trial_ref),
                         Research_org =

### 2020-05-11 06_Publication_wireframe_and_7_Questions.Rmd
writing and edits

@@
 ## What do the results mean in practice? (limit - 50 words)  
-Primarily that fungicide spray schedules that commence prior to signs of the disease establishing in the mungbean canopy are likely to be ineffective at mitigating the diseases impact on yield. 
+Fungicide spray schedules that commence prior to signs of the disease establishing in the mungbean canopy are likely to be ineffective at mitigating the diseases impact on yield. 
 We also don’t have data on at what point starting a fungicide spray schedule is too late. 
@@
 In Australia mungbean is grown in southern Queensland and northern New South Wales as a short season summer legume crop. 
-Approximately 90% of mungbean yields are exported providing good returns for growers. 
+Approximately 90% of mungbean yields are exported and economic returns can be lucritive for growers. 
 Mungbean potentially yields up to 2.3 tonnes per hectare, with a value of up to \$ 1300 AUD a tonne [@QueenslandGovernment2019]. 
 However these potential crop yields can be limited by a range of diseases[@Kelly2017a].
-Powdery mildew (*Podosphaera xanthii*), for instance limits yields by up to 40% [@Chankaew2013]. 
+Powdery mildew (*Podosphaera xanthii*), for instance, can reduce yields by up to 40% [@Chankaew2013]. 
 Fortunately a number of strategies are available to be employed to reduce the damage powdery mildew inflicts on yields.
@@
 Jade-AU is recommended as containing the best disease resistance to powdery mildew (moderately susceptible), while also confering quantifiable resistance to other foliar diseases such as tan spot and halo blight [@AustralianMungbeanAssociation].
-Because cultivar choice does not confer complete resistance to powdery mildew additional strategies such as fungicide treatments are necessary to limit yield loss when conditions for the disease are suitable.
+Because cultivar choice does not confer complete resistance to powdery mildew, additional strategies such as fungicide treatments are necessary to limit yield loss when conditions for the disease are suitable.
 
-The recent release of 'PowderyMildewMDM' a desicion support system (DSS) increases the ease for preparing a fungicide spray scheduale to manage powdery mildew. 
+The recent release of 'PowderyMildewMDM', a desicion support system (DSS), increases the ease for preparing a fungicide spray scheduale to manage powdery mildew [@misc]. 
 PowderyMildewMDM provides a cost benefit analysis to growers for fungcide spray scheduale scenarios.
-The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability one or two fungicide sprays would protect yields suffiently to increase the net profit.
+The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability that one or two fungicide sprays would protect yields suffiently to increase the net profit.
 
 ### Fungicide resistance
-Fungicide application costs in Australia are relativly cheap, and we estimate these to be approximatley \$ 20 AUD per hectare. 
-Lucrative returns of up to \$ 2260 per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than neccercary. 
-This poses a problem for diseases such as powdery mildew which is well known for evolving fungicide resistance if spray schedules are not applied with reducing fungicide resistance risk in mind. 
-Fungicide resistant strains of powdery mildew have been known to establish rapidly. 
+Fungicide application costs in Australia are relativly cheap, and we estimate these costs to be approximatley \$ 20 AUD per hectare. 
+Lucrative returns of up to \$ 2260 per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than neccersary. 
+The evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with fungicide resistance potential in mind. 
+Powdery mildew is one such disease with an extensive track record of rapidly developing fungicide resistance. 
 In cucurbits, powdery mildew has evolved resistance to numerous fungicide classes, such as benzimidazoles, DMIs, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines [@techreport].

### 2020-05-11 06_Publication_wireframe_and_7_Questions.Rmd
writing and edits

@@
 
+To extend the time that a fungicide remains effective against the target pathogen, strategic use of the fungicide must be considered.
+Excessive fungicide sprays increase the selection preassure on the pathogen to evolve resistance.
+If any strains of the pathogen with resistance to the fungicide are present in a population regular use of the fungicide will increase it's proportion in the population. 
+Managing the disease with fungicides for the highest economic return is likely not to require eradication of the causal pathogen. 
+Integrated pest management practices focus on using only the required number of chemical control to protect the economic return. 
+These strategies permit the presence of yield limiting diseases and pests if intervening would cost more than the economic return of protection.
+
+The timing of funcide sprays are critical for thier efficacy and for limiting fungicide resistant strains from emerging. 
+Fungicide applications made too early would increase costs without providing any benefit to yields. 
+Applications which are made too late allow the disease to establish and damage the crop productivity, while making subsequent sprays difficult to reduce the disease incidence.
+
 ### Previous studies - fungicide work
@@
 ### Aims
+
+The aim of this meta-analysis was to determine, from a colection of unpublished studies, when is the ideal time to apply fungicide with respect to the first sign of disease, and does multiple fungicide applications provide better protection for mungbean yields.
 

### 2020-05-13 06_Publication_wireframe_and_7_Questions.Rmd
writing and editing about fungicide resistance

@@
 The evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with fungicide resistance potential in mind.
+Powdery mildew in cucurbits evolved resistance to benzimidazole within three years of it's registration [@peterson]1973.
+In cereal crops _Erysphe graminis_ showed lower sensitivity to strobilurins in 1998, two years after the fungicide began being used in Europe [@chin2001].
 Powdery mildew is one such disease with an extensive track record of rapidly developing fungicide resistance. 
@@
 
-At the time of writing, in Australia two fungicides are registered to treat powdery mildew in mungbean, Veritas/Custodia (200 g/L tebuconazole with 120 g/L azoxystrobin) and tebuconazole.
-Having only a two fungicides registered with similar modes of action may also be contributing to decreased sensitivity of the pathogen.
-Alternating fungicide applications with
-Registation of a fungicide with a different mode of action should be available for growers to alternate fungicides and reduce the speed at which fungicide resistance can develop.
+According to the Fungicide resistance Action Commitee (FRAC) it is important to alternate or mix Fungicides with different modes of action to avoid fungicide resistance. 
+At the time of writing, in Australia one fungicide is registered with the to treat powdery mildew in mungbean, Veritas/Custodia (200 g/L tebuconazole with 120 g/L azoxystrobin). 
+This funigicide provides dual action: tebeconazole disrupts C-14 demethylase, required in sterol biosynthesis for cell membranes; and azoxystrobin, a Quinone outside inhibitor. 
+Quinone is required in cell metabolism and active in the mitochondial complex III. 
+However FRAC recommends that applications of QoIs or strombilarins, singularly or as a mixture, should not be applied consecutivley and alternated with a fungicide from a different group [@Brent&Holman].
+For mungbean, past experiments have shown some success with sulphur applications to control powdery mildew. 
+Sulphur is a non-systemic protectant and thus provides an excellent option for rotation to limit the emergence of fungicide resistance.

### 2020-05-13 06_Publication_wireframe_and_7_Questions.Rmd
Edits and writing and citations

@@
   html_document: default
+bibliography: MyCollection.bib
 ---
@@
 
-The recent release of 'PowderyMildewMDM', a desicion support system (DSS), increases the ease for preparing a fungicide spray scheduale to manage powdery mildew [@misc]. 
+The recent release of 'PowderyMildewMDM', a desicion support system (DSS), increases the ease for preparing a fungicide spray scheduale to manage powdery mildew [@Diggle]. 
 PowderyMildewMDM provides a cost benefit analysis to growers for fungcide spray scheduale scenarios.
@@
 The evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with fungicide resistance potential in mind.
-Powdery mildew in cucurbits evolved resistance to benzimidazole within three years of it's registration [@peterson]1973.
-In cereal crops _Erysphe graminis_ showed lower sensitivity to strobilurins in 1998, two years after the fungicide began being used in Europe [@chin2001].
+Powdery mildew in cucurbits evolved resistance to benzimidazole within three years of it's registration [@Peterson1973].
+In cereal crops _Erysphe graminis_ showed lower sensitivity to strobilurins in 1998, two years after the fungicide began being used in Europe [@Chin2001].
 Powdery mildew is one such disease with an extensive track record of rapidly developing fungicide resistance. 
-In cucurbits, powdery mildew has evolved resistance to numerous fungicide classes, such as benzimidazoles, DMIs, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines [@techreport].
+In cucurbits, powdery mildew has evolved resistance to numerous fungicide classes, such as benzimidazoles, DMIs, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines [@Mcgrath2001].
 
 To extend the time that a fungicide remains effective against the target pathogen, strategic use of the fungicide must be considered. 
-Excessive fungicide sprays increase the selection preassure on the pathogen to evolve resistance.
+Excessive fungicide sprays by a single active increase the selection preassure on the pathogen to evolve resistance [@Brent2007]. 
 If any strains of the pathogen with resistance to the fungicide are present in a population regular use of the fungicide will increase it's proportion in the population. 
@@
 Quinone is required in cell metabolism and active in the mitochondial complex III. 
-However FRAC recommends that applications of QoIs or strombilarins, singularly or as a mixture, should not be applied consecutivley and alternated with a fungicide from a different group [@Brent&Holman].
+However FRAC recommends that applications of QoIs or strombilarins, singularly or as a mixture, should not be applied consecutivley and alternated with a fungicide from a different group [@Brent2007].
 For mungbean, past experiments have shown some success with sulphur applications to control powdery mildew. 

### 2020-05-18 06_Publication_wireframe_and_7_Questions.Rmd
update citations
Edits

@@
 output:
+  html_document: default
   word_document: default
-  html_document: default
-bibliography: MyCollection.bib
 ---
@@
 Powdery mildew (*Podosphaera xanthii*), for instance, can reduce yields by up to 40% [@Chankaew2013]. 
-Fortunately a number of strategies are available to be employed to reduce the damage powdery mildew inflicts on yields.
+Fortunately a number of strategies are available to be employed to reduce the damage powdery mildew inflicts on mungbean yields.
 
@@
 Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013]. 
-In Australia, quantitive resistance has also been incorporated a couple of varieties which have been made commercially available. 
+In Australia, quantitive resistance has also been incorporated a couple of varieties which are commercially available. 
 Jade-AU is recommended as containing the best disease resistance to powdery mildew (moderately susceptible), while also confering quantifiable resistance to other foliar diseases such as tan spot and halo blight [@AustralianMungbeanAssociation].
@@
 PowderyMildewMDM provides a cost benefit analysis to growers for fungcide spray scheduale scenarios.
-The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability that one or two fungicide sprays would protect yields suffiently to increase the net profit.
+The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability that one or two fungicide sprays would protect yields sufficiently to increase the net profit.
 
 ### Fungicide resistance
-Fungicide application costs in Australia are relativly cheap, and we estimate these costs to be approximatley \$ 20 AUD per hectare. 
+Fungicide application costs in Australia are relatively cheap, and we estimate these costs to be approximatley \$ 20 AUD per hectare. 
 Lucrative returns of up to \$ 2260 per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than neccersary. 
+Excessive use of fungicides are not only costly, but lead to problems such as fungicide resistance. 
+*Podosphaera xanthii* is categorised by FRAC as a 'High risk' candidate to evolve fungicide resistance. 
 The evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with fungicide resistance potential in mind.
@@
 
+### Fungicide resistance
 According to the Fungicide resistance Action Commitee (FRAC) it is important to alternate or mix Fungicides with different modes of action to avoid fungicide resistance. 

### 2020-05-19 06_Publication_wireframe_and_7_Questions.Rmd
Method edits

@@
 
-The data for this study was obtained from through personal correspondence with colleagues and collaborating institutions.
+The data for this study were obtained from through personal correspondence with colleagues and collaborating institutions.
 The majority of the trials were undertaken by Malcolm Riley and Dr Sue Thompson with The Department of Agriculture and Primary industries (DAF). 
@@
 Trial data were in different formats with varying levels of information.
-Some trial data reporting means of each treatment, with all but one study reporting variance along with the mean. 
-For XX trials the raw data were obtained.
+Some trial data reported means of each treatment, with all but one study reporting variance along with the mean. 
+For 17 trials the raw data were obtained (Table 1).
 
@@
 
-The criteria for inclusion of trial data in the meta-analysis, required a field trial testing fungicide efficacy for powdery mildew control on mungbean in the northern grains regions of eastern Australia.
+The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the northern grains regions of eastern Australia.
 Trial data had to include the date when powdery mildew was first observed. 
-Trials needed to have tested a demethylase inhibitor (DMI) fungicide.
+Trials needed to include either demethylase inhibitor (DMI), tebuconazole or propiconazole.
 
@@
 
-While the main aim of all the trials collected for this study were the same, assess the efficacy of fungicides for control of powdery mildew, most also aimed to test the effect of different variables on fungicide efficacy.
-Some of the variable which were suspected to influence powdery mildew incidence and the effect on yield were: trial location, trial season, row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar, irrigation and rainfall.
-To account for this variation between trials and thr treatments within the trial a single 'trial' factor was created to describe the main variables; Trial location, trial season, host genotype and row spacing.
+While the main aim of all the trials collected for this study were to assess the efficacy of fungicide for control of powdery mildew, some trials  included additional variables in the experimental design.
+Some variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar and  supplimentary irrigation, in addition to trial location and season.
+To account for this variation between trials, and the treatments within trials, a single 'trial' factor was created to describe the main variables; trial location, trial season, host genotype and row spacing.
 
-To reduce confounding effects of various fungicides we only included treatments within trials which had been sprayed with a fungicide which has a DMI mode of action, such as tebeconazole and propiconazole.
-Fungicide active from the DMI group was the main inclusion factor for the analysis which reduced the number of trials from 24 to 17 experiments.
+To reduce confounding effects of various fungicides we only included treatments within trials which used a DMI as a fungicide active, such as tebeconazole and propiconazole. 
+Fungicide active from the DMI group was the main inclusion factor for the analysis which reduced the number of trials from 26 to 17 experiments.
 
 Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 - 9 ordinal scale [ref]. 
-The 2013 NGA trials reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the canopy; lower, middle or upper canopy. 
-Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, it was easy to calculate the equivalent incidence on the ordinal 1 - 9 scale.
+The 2013 NGA trials however, reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the canopy; lower, middle or upper canopy. 
+Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, it was strait-forward to calculate the equivalent incidence on the ordinal 1 - 9 scale.
 
 The timing of fungicide applications, with reference to when the disease first occurred in the trial, and number of applications were used to define a treatment variable.
-An 'Early' fungicide application, refers to a fungicide spray schedule that commences with it's first spray prior to the disease being observed in the trial.  
+An 'Early' fungicide application, refers to a fungicide spray schedule that commences with the first spray prior to the disease being observed in the trial.  
 'Recommended' refers to a fungicide spray schedule which commences within three days following the first sign of disease, and 'late' treatments which commence four days or later than first sign. 
@@
 
-Trials where we obtained the raw data the response variables were summarised into the treatment means and variance. 
-The remainder of the trial data reported treatment means and variance. 
-Two of the trials, Gatton 2012 and Emerald 2015, reported treatment means without accompaning variance. 
+Response variables were averaged in trials which we had access to the raw data. 
+For the remainder of the trial data except two trials, Gatton 2012 and Emerald 2015, only the treatment means and variance were reported. 
+Gatton and Emerald trials were were only able to obtain treatment means without accompaning variance. 
 For these trials the trial variance was imputed by randomly sampling the trial mean squared error from a distribution of log trial MSE.  
@@
 PM_Mdat %>%
-      group_by(trial_ref,) %>%
+   filter(fungicide_ai == "tebuconazole" | fungicide_ai == "propiconazole") %>%
+   group_by(trial_ref) %>%
    summarise(year = unique(year),
@@
    arrange(year)%>%
-   left_join(data.frame(trial_ref = unique(PM_Mdat$trial_ref),
-                        Research_org =
-                           c(rep("Queensland DAF",times =12),
+   mutate(Research_org = c(rep("Queensland DAF",times =4),
                            rep("Northern Growers Alliance", times = 4),
-               rep("Queensland DAF",times =5),
-               rep("USQ", times = 5))))%>%
+                           rep("Queensland DAF",times =4),
+                           rep("USQ", times = 5))) %>%
    kable(caption = "Table 1: Description of Experiments")%>%
@@
 ```
+## Results
 

### 2020-05-20 06_Publication_wireframe_and_7_Questions.Rmd
More edits

@@
 The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the northern grains regions of eastern Australia.
-Trial data had to include the date when powdery mildew was first observed. 
-Trials needed to include either demethylase inhibitor (DMI), tebuconazole or propiconazole.
+Trial data had to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; and crop yield. 
+A total of 26 trials were collated and from these trials we selected the most frequently tested fungicides that had the same mode of action. 
+The data were subset to only include treatments using demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole to reduce confounding effects of fungicides with varying modes of action.
+Subsequently the 26 trials were reduced to 17 using the same fungicide doses.
 
-All trials included in this analysis were not previously published in peer-reviewed literature.
+All trials included in this analysis were a randomised complete block design and not previously published in peer-reviewed literature.
 Some trials and results were reported online via the Grains Research and Development Corporation.
@@
 While the main aim of all the trials collected for this study were to assess the efficacy of fungicide for control of powdery mildew, some trials  included additional variables in the experimental design.
-Some variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar and  supplimentary irrigation, in addition to trial location and season.
+These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar and  supplimentary irrigation, in addition to trial location and season.
 To account for this variation between trials, and the treatments within trials, a single 'trial' factor was created to describe the main variables; trial location, trial season, host genotype and row spacing.
 
-To reduce confounding effects of various fungicides we only included treatments within trials which used a DMI as a fungicide active, such as tebeconazole and propiconazole. 
-Fungicide active from the DMI group was the main inclusion factor for the analysis which reduced the number of trials from 26 to 17 experiments.
-
-Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 - 9 ordinal scale [ref]. 
+Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 - 9 ordinal scale [Table_PMScale]. 
 The 2013 NGA trials however, reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the canopy; lower, middle or upper canopy. 
@@
 
-Response variables were averaged in trials which we had access to the raw data. 
-For the remainder of the trial data except two trials, Gatton 2012 and Emerald 2015, only the treatment means and variance were reported. 
-Gatton and Emerald trials were were only able to obtain treatment means without accompaning variance. 
+For the trials which we had raw data, mean grain yields for each were calculated and the mean squared error within trial obtained from an anova of each study.
+For the remainder of the trial data only the treatment means and variance were reported, except for Gatton in 2012 and Emerald in 2015. 
+The Gatton and Emerald trials only reported treatment means without accompaning variance. 
 For these trials the trial variance was imputed by randomly sampling the trial mean squared error from a distribution of log trial MSE.  
-$rnorm(\overline{x}_{log(MSE_{1}) \dots, log(MSE_{n})}, \sigma_{log(MSE_{1}) \dots, log(MSE_{n})}) $  
-Where MSE is the mean squared error of each trial.
+$rnorm(\overline{x}_{log(MSE_{1}) \dots, log(MSE_{n})}, \sigma_{log(MSE_{1}) \dots, log(MSE_{n})})$  
+Where $MSE$ is the mean squared error of each trial and $n$ is the total number of trials.
 
-$v_i = MSE_{y}/(n * Y_{i}^2) $
+Sample variance was computed from the trial MSE using the following equation, where $i$ is the $i$th trial, n is the number of replicates and $\overline{Y}$ is the mean grain yield for that treatment.
+$v_i = MSE_{i}/(n_{i} * \overline{Y}_{i}^2)$
 
@@
 ```
+
+```{r}
+data.frame(Scale = 1:9,
+           `Scale Description` = c("No sign of powdery mildew",
+                                "Small colonies in lower 1/3 of canopy, up to 75% of plants affected",
+                                "Colonies in lower 1/2 of canopy, > 75 % of plants affected",
+                                "Colonies in lower 2/3 of canopy, up to 75 % of plants affected",
+                                "Colonies in lower 2/3 of canopy, > 75 % of plants affected",
+                                "Colonies in lower 2/3 of canopy, 100 % of plants affected",
+                                "Colonies in lower 2/3 of canopy, 100 % of plants, with some plants with colonies in the top 1/3 of canopy",
+                                "Colonies to top of the plant with > 75 % of plants affected",
+                                "Colonies to top of the plant with > 100 % of plants affected and heavy leaf drop"
+                                )) %>%
+   kable(caption = "Table 2: Powdery Mildew severity scoring scale")%>%
+   kable_styling(fixed_thead = T, full_width = T)
+```
+
 ## Results

### 2020-05-21 06_Publication_wireframe_and_7_Questions.Rmd
Writing and edite

@@
 Many of the experimental work has been published by funding agencies and state government extension departments. 
-Past field trials in eastern Australia have trialed a range of fungicide active ingredients (table), while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
+Past field trials in eastern Australia have trialed a range of fungicide active ingredients, while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
 Early trials showed for a fungicide application to provide maximum efficacy a single fungicide application at first sign of the disease with another follow-up application two weeks later if necessary [@Sparks2017].
@@
 ### Meta-analysis
+Meta-analyses are statistical tools which can analyse a collection of experiments which have a similar aim and estimates the difference between the control and treatment means. 
+The outcome of a meta-analysis provides a more accurate estimation of the true treatments effect, because it considers the amount of variance in each study, and weights the influence of each study on the treatment effects according to the study statistical accuracy.
+Using a meta-analysis on the
 
@@
 Trials undertaken in 2013 season were conducted by the Northern growers alliance [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013].
-The most recent trials from 2017 were undertaken by DAF and the University of Southern Queensland (USQ) from 2017 to 2019 (Table 1). 
+The most recent trials from 2017 were undertaken by DAF and the University of Southern Queensland (USQ) from 2017 to 2019. 
 Trial data were in different formats with varying levels of information.
 Some trial data reported means of each treatment, with all but one study reporting variance along with the mean. 
-For 17 trials the raw data were obtained (Table 1).
+For 17 trials the raw data were obtained.
 
@@
 The data were subset to only include treatments using demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole to reduce confounding effects of fungicides with varying modes of action. 
-Subsequently the 26 trials were reduced to 17 using the same fungicide doses.
+Subsequently the 26 trials were reduced to 17 using the same fungicide doses (Table 1). 
+With only a small number of trials to increase the replication, we made no distinction between the tebuconazole and propiconazole in the analysis.
 
@@
 Some trials and results were reported online via the Grains Research and Development Corporation. 
-
 While the main aim of all the trials collected for this study were to assess the efficacy of fungicide for control of powdery mildew, some trials  included additional variables in the experimental design.
@@
 To account for this variation between trials, and the treatments within trials, a single 'trial' factor was created to describe the main variables; trial location, trial season, host genotype and row spacing.
-
-Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 - 9 ordinal scale [Table_PMScale]. 
-The 2013 NGA trials however, reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the canopy; lower, middle or upper canopy. 
+Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 - 9 ordinal scale (Table 2). 
+The 2013 NGA trials however (table 1), reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the canopy; lower, middle or upper canopy. 
 Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, it was strait-forward to calculate the equivalent incidence on the ordinal 1 - 9 scale.
@@
 The number of fungicide applications were binned in to two categories. 
-A spray schedule with a single spray, and a spray schedule with one or more sprays where there was a maximum of three applications. 
+A spray schedule with a single spray, and a spray schedule with one or more sprays to a maximum of three applications. 
 The division of the treatments into these six categories created two categories with insuffient numbers of treatments to provide a reliable sample. 
@@
 For the trials which we had raw data, mean grain yields for each were calculated and the mean squared error within trial obtained from an anova of each study. 
+Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 1.697 and the approach reported in Ngugi et al.
+[@Ngugi2011].
+The T-critical value was determined from the 30 degrees of freedom using a t-distribution table.
 For the remainder of the trial data only the treatment means and variance were reported, except for Gatton in 2012 and Emerald in 2015. 
-The Gatton and Emerald trials only reported treatment means without accompaning variance. 
-For these trials the trial variance was imputed by randomly sampling the trial mean squared error from a distribution of log trial MSE.  
+The Gatton and Emerald trials reported treatment means without accompaning variance. 
+Trial variance was imputed by sampling from a normal distribution where the mean and standard deviation were calculated from the log of all the trials mean square errors.  
 $rnorm(\overline{x}_{log(MSE_{1}) \dots, log(MSE_{n})}, \sigma_{log(MSE_{1}) \dots, log(MSE_{n})})$  

### 2020-05-22 03_Prep_data.Rmd
Spell check all files

@@
-# Prepare data for meta-anlysis
+# Prepare data for meta-analysis
 ## Set environment and import data
@@
 
-Let's have a look again at the same sequance of graphs and analyses for area under the disease progress _stairs_.
+Let's have a look again at the same sequence of graphs and analyses for area under the disease progress _stairs_.
 

### 2020-05-22 05_AUDPC_MetaAnalysis.Rmd
Minor edits
Spell check all files

@@
 
-Now it's time to look at how the spray managment scenarios might impact disease pressure on the mungbean yields.
-First lets evaulate which measure of disease is the most robust predictor for yield loss, AUDPC, AUDPS or disease incidence at the end of the season.
+Now it's time to look at how the spray management scenarios might impact disease pressure on the mungbean yields.
+First lets evaluate which measure of disease is the most robust predictor for yield loss, AUDPC, AUDPS or disease incidence at the end of the season.
 
@@
 
-The R-squared of the AUDPC model is a better fit compared to the AUDPS model.
+The R-squared of the AUDPC model is a better fit compared to the AUDPS model, and has a conditional $R^2$ value of `r round(r.squaredGLMM(Me_mod2)[2],4)`. 
 > From here on we will use AUDPC.
@@
 In addition model comparison shows AUDPC is significantly better at predicting grain yield.
+
 ### Spray management and AUDPC

### 2020-05-22 06_Publication_wireframe_and_7_Questions.Rmd
Spell check all files

--- 2020-05-19 06_Publication_wireframe_and_7_Questions.Rmd
@@
 In Australia mungbean is grown in southern Queensland and northern New South Wales as a short season summer legume crop. 
-Approximately 90% of mungbean yields are exported and economic returns can be lucritive for growers. 
+Approximately 90% of mungbean yields are exported and economic returns can be lucrative for growers. 
 Mungbean potentially yields up to 2.3 tonnes per hectare, with a value of up to \$ 1300 AUD a tonne [@QueenslandGovernment2019]. 
@@
 Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013]. 
-In Australia, quantitive resistance has also been incorporated a couple of varieties which are commercially available. 
-Jade-AU is recommended as containing the best disease resistance to powdery mildew (moderately susceptible), while also confering quantifiable resistance to other foliar diseases such as tan spot and halo blight [@AustralianMungbeanAssociation].
+In Australia, quantitative resistance has also been incorporated a couple of varieties which are commercially available. 
+Jade-AU is recommended as containing the best disease resistance to powdery mildew (moderately susceptible), while also conferring quantifiable resistance to other foliar diseases such as tan spot and halo blight [@AustralianMungbeanAssociation].
 Because cultivar choice does not confer complete resistance to powdery mildew, additional strategies such as fungicide treatments are necessary to limit yield loss when conditions for the disease are suitable.
 
-The recent release of 'PowderyMildewMDM', a desicion support system (DSS), increases the ease for preparing a fungicide spray scheduale to manage powdery mildew [@Diggle]. 
-PowderyMildewMDM provides a cost benefit analysis to growers for fungcide spray scheduale scenarios.
+The recent release of 'PowderyMildewMBM', a decision support system (DSS), increases the ease for preparing a fungicide spray schedule to manage powdery mildew [@Diggle]. 
+PowderyMildewMBM provides a cost benefit analysis to growers for fungicide spray schedule scenarios.
 The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability that one or two fungicide sprays would protect yields sufficiently to increase the net profit.
@@
 ### Fungicide resistance
-Fungicide application costs in Australia are relatively cheap, and we estimate these costs to be approximatley \$ 20 AUD per hectare. 
-Lucrative returns of up to \$ 2260 per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than neccersary. 
+Fungicide application costs in Australia are relatively cheap, and we estimate these costs to be approximately \$ 20 AUD per hectare. 
+Lucrative returns of up to \$ 2260 per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than necessary. 
 Excessive use of fungicides are not only costly, but lead to problems such as fungicide resistance. 
@@
 Powdery mildew in cucurbits evolved resistance to benzimidazole within three years of it's registration [@Peterson1973].
-In cereal crops _Erysphe graminis_ showed lower sensitivity to strobilurins in 1998, two years after the fungicide began being used in Europe [@Chin2001].
+In cereal crops _Blumeria graminis_ showed lower sensitivity to strobilurins in 1998, two years after the fungicide began being used in Europe [@Chin2001].
 Powdery mildew is one such disease with an extensive track record of rapidly developing fungicide resistance. 
@@
 To extend the time that a fungicide remains effective against the target pathogen, strategic use of the fungicide must be considered. 
-Excessive fungicide sprays by a single active increase the selection preassure on the pathogen to evolve resistance [@Brent2007]. 
+Excessive fungicide sprays by a single active increase the selection pressure on the pathogen to evolve resistance [@Brent2007]. 
 If any strains of the pathogen with resistance to the fungicide are present in a population regular use of the fungicide will increase it's proportion in the population. 
@@
 
-The timing of funcide sprays are critical for thier efficacy and for limiting fungicide resistant strains from emerging. 
+The timing of fungicide sprays are critical for their efficacy and for limiting fungicide resistant strains from emerging. 
 Fungicide applications made too early would increase costs without providing any benefit to yields. 
@@
 
-The aim of this meta-analysis was to determine, from a colection of unpublished studies, when is the ideal time to apply fungicide with respect to the first sign of disease, and does multiple fungicide applications provide better protection for mungbean yields.
+The aim of this meta-analysis was to determine, from a collection of unpublished studies, when is the ideal time to apply fungicide with respect to the first sign of disease, and does multiple fungicide applications provide better protection for mungbean yields.
 
@@
 
-The data for this study were obtained from through personal correspondence with colleagues and collaborating institutions.
+The data for this study was obtained from through personal correspondence with colleagues and collaborating institutions.
 The majority of the trials were undertaken by Malcolm Riley and Dr Sue Thompson with The Department of Agriculture and Primary industries (DAF). 
@@
 Trial data were in different formats with varying levels of information.
-Some trial data reported means of each treatment, with all but one study reporting variance along with the mean. 
-For 17 trials the raw data were obtained (Table 1).
+Some trial data reporting means of each treatment, with all but one study reporting variance along with the mean. 
+For XX trials the raw data were obtained.
 
@@
 
-The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the northern grains regions of eastern Australia.
+The criteria for inclusion of trial data in the meta-analysis, required a field trial testing fungicide efficacy for powdery mildew control on mungbean in the northern grains regions of eastern Australia.
 Trial data had to include the date when powdery mildew was first observed. 
-Trials needed to include either demethylase inhibitor (DMI), tebuconazole or propiconazole.
+Trials needed to have tested a demethylase inhibitor (DMI) fungicide.
 
@@
 
-While the main aim of all the trials collected for this study were to assess the efficacy of fungicide for control of powdery mildew, some trials  included additional variables in the experimental design.
-Some variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar and  supplimentary irrigation, in addition to trial location and season.
-To account for this variation between trials, and the treatments within trials, a single 'trial' factor was created to describe the main variables; trial location, trial season, host genotype and row spacing.
+While the main aim of all the trials collected for this study were the same, assess the efficacy of fungicides for control of powdery mildew, most also aimed to test the effect of different variables on fungicide efficacy.
+Some of the variable which were suspected to influence powdery mildew incidence and the effect on yield were: trial location, trial season, row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar, irrigation and rainfall.
+To account for this variation between trials and their treatments within the trial a single 'trial' factor was created to describe the main variables; Trial location, trial season, host genotype and row spacing.
 
-To reduce confounding effects of various fungicides we only included treatments within trials which used a DMI as a fungicide active, such as tebeconazole and propiconazole. 
-Fungicide active from the DMI group was the main inclusion factor for the analysis which reduced the number of trials from 26 to 17 experiments.
+To reduce confounding effects of various fungicides we only included treatments within trials which had been sprayed with a fungicide which has a DMI mode of action, such as tebeconazole and propiconazole.
+Fungicide active from the DMI group was the main inclusion factor for the analysis which reduced the number of trials from 24 to 17 experiments.
 
 Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 - 9 ordinal scale [ref]. 
-The 2013 NGA trials however, reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the canopy; lower, middle or upper canopy. 
-Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, it was strait-forward to calculate the equivalent incidence on the ordinal 1 - 9 scale.
+The 2013 NGA trials reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the canopy; lower, middle or upper canopy. 
+Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, it was easy to calculate the equivalent incidence on the ordinal 1 - 9 scale.
 
 The timing of fungicide applications, with reference to when the disease first occurred in the trial, and number of applications were used to define a treatment variable.
-An 'Early' fungicide application, refers to a fungicide spray schedule that commences with the first spray prior to the disease being observed in the trial.  
+An 'Early' fungicide application, refers to a fungicide spray schedule that commences with it's first spray prior to the disease being observed in the trial.  
 'Recommended' refers to a fungicide spray schedule which commences within three days following the first sign of disease, and 'late' treatments which commence four days or later than first sign. 
@@
 A spray schedule with a single spray, and a spray schedule with one or more sprays where there was a maximum of three applications. 
-The division of the treatments into these six categories created two categories with insuffient numbers of treatments to provide a reliable sample. 
-Single late sprays contained two replicates and mulitple early sprays contained five replicates and were therefore removed from the subsequent meta-analysis.
+The division of the treatments into these six categories created two categories with insufficient numbers of treatments to provide a reliable sample. 
+Single late sprays contained two replicates and multiple early sprays contained five replicates and were therefore removed from the subsequent meta-analysis.
 
@@
 
-Response variables were averaged in trials which we had access to the raw data. 
-For the remainder of the trial data except two trials, Gatton 2012 and Emerald 2015, only the treatment means and variance were reported. 
-Gatton and Emerald trials were were only able to obtain treatment means without accompaning variance. 
+Trials where we obtained the raw data the response variables were summarised into the treatment means and variance. 
+The remainder of the trial data reported treatment means and variance. 
+Two of the trials, Gatton 2012 and Emerald 2015, reported treatment means without accompanying variance. 
 For these trials the trial variance was imputed by randomly sampling the trial mean squared error from a distribution of log trial MSE.  
@@
 PM_Mdat %>%
-   filter(fungicide_ai == "tebuconazole" | fungicide_ai == "propiconazole") %>%
-   group_by(trial_ref) %>%
+      group_by(trial_ref,) %>%
       summarise(year = unique(year),
@@
       arrange(year)%>%
-   mutate(Research_org = c(rep("Queensland DAF",times =4),
+   left_join(data.frame(trial_ref = unique(PM_Mdat$trial_ref),
+                        Research_org =
+                           c(rep("Queensland DAF",times =12),
                              rep("Northern Growers Alliance", times = 4),
-                           rep("Queensland DAF",times =4),
-                           rep("USQ", times = 5))) %>%
+               rep("Queensland DAF",times =5),
+               rep("USQ", times = 5))))%>%
 kable(caption = "Table 1: Description of Experiments")%>%
@@
 ```
-## Results
 
@@
 ### Fungicide resistance
-According to the Fungicide resistance Action Commitee (FRAC) it is important to alternate or mix Fungicides with different modes of action to avoid fungicide resistance. 
+According to the Fungicide resistance Action Committee (FRAC) it is important to alternate or mix Fungicides with different modes of action to avoid fungicide resistance. 
 At the time of writing, in Australia one fungicide is registered with the to treat powdery mildew in mungbean, Veritas/Custodia (200 g/L tebuconazole with 120 g/L azoxystrobin). 
-This funigicide provides dual action: tebeconazole disrupts C-14 demethylase, required in sterol biosynthesis for cell membranes; and azoxystrobin, a Quinone outside inhibitor. 
-Quinone is required in cell metabolism and active in the mitochondial complex III. 
-However FRAC recommends that applications of QoIs or strombilarins, singularly or as a mixture, should not be applied consecutivley and alternated with a fungicide from a different group [@Brent2007].
+This fungicide provides dual action: tebeconazole disrupts C-14 demethylase, required in sterol biosynthesis for cell membranes; and azoxystrobin, a Quinone outside inhibitor. 
+Quinone is required in cell metabolism and active in the mitochondrial complex III. 
+However FRAC recommends that applications of QoIs or strobilurins, singularly or as a mixture, should not be applied consecutively and alternated with a fungicide from a different group [@Brent2007]. 
 For mungbean, past experiments have shown some success with sulphur applications to control powdery mildew. 

### 2020-05-22 02_Preliminary_analysis.Rmd
Spell check all files
Clean up visualsation to use USQ colours and clean up code, etc.

@@
    footnote(general = "Fungicides with less than five observations were omitted from this table")
-
 ```
@@
    theme(legend.position = "none") +
+   scale_fill_usq() +
    coord_flip()
@@
 #### Fungicide Doses  
-We should check that all fungicide doses that were used were roughly the same if we are to compare between trials were dose might be different.
+We should check that all fungicide doses that were used were roughly the same if we are to compare between trials where dose might be different.
 
@@
    scale_fill_usq() +
-   scale_colour_usq() +
-   theme_usq()
+   scale_colour_usq()
 ```
@@
    ) +
-   ylab("Days to First Sign of Disease") +
-   theme_usq()
+   ylab("Days to First Sign of Disease")
 ```
@@
    geom_col() +
-   scale_fill_usq() +
-   scale_colour_usq() +
-   theme_usq()
+   scale_fill_usq()
 ```
-
-&nbsp;
 
@@
    yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
-YV1[[2]]
+YV1[[2]] + 
+   scale_fill_usq()
+
 YV1[[3]]
@@
    yield_volatility(genotype_by_trial = FALSE, control_only = TRUE)
-YV2[[2]]
+YV2[[2]] +
+   scale_fill_usq()
 YV2[[3]]
@@
 Volatility of the cultivars are fairly similar when trial is not considered as a factor (when we inspect plots of all treatments and only spray treatments).
-Green Diamond shows little volatility however this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trials.
+Green Diamond shows little volatility however this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trials
 
@@
    )
-YV1_herm[[2]]
+YV1_herm[[2]] +
+   scale_fill_usq()
 ```
@@
    yield_volatility(genotype = "Crystal", control_only = FALSE)
-YV1_crystal[[2]]
+YV1_crystal[[2]] +
+   scale_fill_usq()
+
 YV1_crystal <-
    yield_volatility(genotype = "Crystal", control_only = TRUE)
-YV1_crystal[[2]]
+YV1_crystal[[2]] +
+   scale_fill_usq()
 ```
@@
 YV2_crystal <- yield_volatility("Jade",control_only = FALSE)
-YV2_crystal[[2]]
+YV2_crystal[[2]] +
+   scale_fill_usq()
 ```
@@
 YV3_crystal <- yield_volatility("Jade", control_only = TRUE)
-YV3_crystal[[2]]
+YV3_crystal[[2]] +
+   scale_fill_usq()
 ```
@@
             position = "dodge") +
-   scale_fill_usq(name = "Fungicide AI") +
-   theme_usq()
+   scale_fill_usq(name = "Fungicide AI")
 
@@
 ```{r RS_yield}
-# Which row spacing leads to the higher yeild potential
+# Which row spacing leads to the higher yield potential
 PM_MB_means %>%
@@
              year == 2018) %>%
-   #   filter(Fungicide == "control") %>%
    ggplot(aes(
@@
    )) +
-   geom_smooth(method = "gam") +
    geom_jitter(width = 0.01) +
@@
    xlab("Row spacing (m)") +
-   ylab("Grain yield - tonnes per hectare")
+   ylab("Grain yield - tonnes per hectare") +
+   scale_colour_usq()
 ```
@@
 Therefore the disease can be avoided by planting early in summer or spring, avoiding cooler temperatures at the end of some seasons.
-Can we visualise when PM is most likely to establish over the calender year?
+Can we visualise when PM is most likely to establish over the calendar year?
 
 I'll build a plot of horizontal lines indicating the season length and use a dot on the line to indicating the day of the year first sign was observed for that trial.
+
 ```{r first_incidence}
@@
 
-first_day_month <- c(0, 31, 59, 90, 120, 151, 181, 211, 243, 273)+1
+first_day_month <- c(0, 31, 59, 90, 120, 151, 181, 211, 243, 273) + 1
 axis_labels_date <-
@@
    geom_boxplot() +
-   geom_hline(aes(yintercept = 0), size = 0.5) +
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
+   geom_hline(aes(yintercept = 0), size = 0.5, colour = "red") +
    labs(x = "Proportion of grain yield saved",

### 2020-05-22 04_MetaAnalysis.Rmd
writing and editing
Clean up visualsation to use USQ colours and clean up code, etc.

@@
 
-m11 <- lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
+m11 <-
+   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
            (1 | trial_ref),
@@
       Vplot <-
-         slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),] %>%
+         slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), ] %>%
          ggplot(aes(y = grain_yield.t.ha, trial)) +
@@
 ```{r imputation_MSE}
-for (i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`),]$trial_ref) {
+for (i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), ]$trial_ref) {
    slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "Y_Msquare"] <-
@@
    method = "ML",
-   random = list( ~ spray_management | trial),
+   random = list(~ spray_management | trial),
    struct = "UN",
@@
 summary(PM_mv_AI)
+```
+
+```{r Metafor-analysis}
+PM_mv_AI <- rma.mv(
+   yi,
+   vi,
+   mods = ~ slimmer_PM_dat$spray_management + slimmer_PM_dat$row_spacing + slimmer_PM_dat$host_genotype,
+   method = "ML",
+   random = list(~ spray_management | trial_ref),
+   struct = "UN",
+   data = slimmer_PM_dat
+)
+
+summary(PM_mv_AI)
+
 ```
@@
                                exp(PM_mv_AI$ci.ub)))
-
-# results_AI <- data.frame(cbind(PM_mv_AI$b,
-#                               (PM_mv_AI$ci.lb),
-#                               PM_mv_AI$ci.ub))
 
@@
 write.csv(slimmer_PM_dat, file = "data/GYmeta_data.csv")
-
 ```

### 2020-05-22 R/import_data.R

@@ -22,6 +22,7 @@ import_data <- function() {
    x$fungicide_ai <- as.factor(x$fungicide_ai)
    x$trade_name <- as.factor(x$trade_name)
    x$year <- as.factor(x$year)
+   x$row_spacing <- round(x$row_spacing, 2) # deals with 0.33 vs 0.3333333 values
    x$replicates <- as.numeric(x$replicates)
    x$planting_date <- as.Date(x$planting_date, format = "%Y-%m-%d")
    x$emergence_date <-

### 2020-05-22 04_MetaAnalysis.Rmd
Reword some of the examples after data has changed

--- 2020-02-28 04_MetaAnalysis.Rmd
@@
 
-   - The `recommended_plus` spray which has one or more follow-up sprays after first sign are likely to increase the mean grain yield.
+   - The `Late_plus` spray which has one or more follow-up sprays after first sign are likely to increase the mean grain yield.
 
-   - `Late_plus` spray treatments showed the highest mean grain yield, and was significantly higher than the no spray control. However showed no difference to either of the `recommended` treatments.
+   - `Recommended_plus` spray treatments showed the highest mean grain yield, and was significantly higher than the no spray control.
+However showed no difference to either the `recommended` or `Late_plus` treatments.
 
@@
 hist_usq(slimmer_PM_dat$yield_error) # yield error is not normally distributed
-hist_usq(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is normally distributed 
+hist_usq(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is close to normally distributed 
 ```
@@
 
+```{r Metafor-analysis}
+PM_mv_AI <- rma.mv(
+   yi,
+   vi,
+   mods = ~ slimmer_PM_dat$spray_management + slimmer_PM_dat$row_spacing + slimmer_PM_dat$host_genotype,
+   method = "ML",
+   random = list( ~ spray_management | trial_ref),
+   struct = "UN",
+   data = slimmer_PM_dat
+)
+
+summary(PM_mv_AI)
+
+```
+
 Results show that yields in single early spray treatments are not significantly different to the no spray control.

### 2020-05-22 06_Publication_wireframe_and_7_Questions.Rmd
Editing and writing

--- 2020-05-21 06_Publication_wireframe_and_7_Questions.Rmd
@@
 
-The aim of this meta-analysis was to determine, from a colection of unpublished studies, when is the ideal time to apply fungicide with respect to the first sign of disease, and does multiple fungicide applications provide better protection for mungbean yields.
+The aim of this meta-analysis was to determine, from a collection of unpublished studies, what spray management scenario provides the greatest yield protection from powdery mildew in mungbean.
 
@@
 For the trials which we had raw data, mean grain yields for each were calculated and the mean squared error within trial obtained from an anova of each study. 
-Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 1.697 and the approach reported in Ngugi et al.
-[@Ngugi2011].
+Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 1.697 and the approach reported in Ngugi et al. [@Ngugi2011]. 
 The T-critical value was determined from the 30 degrees of freedom using a t-distribution table. 
@@
 The Gatton and Emerald trials reported treatment means without accompaning variance. 
+The Gatton and Emerald trials also reported no significant difference in yield between the treatments. 
+When imputing the variance for these trials they were checked to ensure the new variances did not confer a significant difference between the treatments. 
+If the new variance did confer a significant differance between any of the treatments the imputation function was rerun.
 Trial variance was imputed by sampling from a normal distribution where the mean and standard deviation were calculated from the log of all the trials mean square errors.  

### 2020-05-22 03_Prep_data.Rmd

@@
 
-The following code attempts to convert 'least square differences' (LSD) to sampling variance as per the method in [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
+The following code cnverts 'least square differences' (LSD) to sampling variance as per the method in [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
 Ideas for using a T-critical value of 1.697 came from reading a [statisics-how-to website](https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/).
@@
    DFw <-
-      sum(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates) -
-      length(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates) # degrees of freedom within groups
+      sum(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates) -
+      length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates) # degrees of freedom within groups
 
    LSD <-
-      PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$yield_error[1]
+      PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error[1]
 
    V_yield <-
-      (PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates[1] * (LSD /
+      (PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[1] * (LSD /
                                                                              Tcrit) ^ 2) / 2 # method - Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
 
-   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates)) {
+   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates)) {
       if (j == 1) {
          Sv <-
-            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates))
+            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates))
       } # reset Sv vector if this is the first loop
@@
       Sv[j] = V_yield /
-         PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates[j]
+         PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j]
 
@@
 
-   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$yield_error <-
+   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error <-
       Sv
-   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Y_error_type <-
+   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$Y_error_type <-
       "SamplingVariance"
@@
 
-for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$yield_error)) {
+for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error)) {
    if (j == 1) {
       Sv <-
-         vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$yield_error))
+         vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error))
    }# create empty vector at first iteration with length of j
 
-   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$yield_error[j]) ^
+   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error[j]) ^
       2
@@
 # and replacing the values in the dataset
-PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$yield_error <-
+PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error <-
    Sv
-PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$Y_error_type <-
+PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$Y_error_type <-
    "SamplingVariance"
@@
 for (i in unique(PM_MB_means$trial_ref)) {
-   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i,]
+   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
 
@@
    for (j in unique(dat1$row_spacing)) {
-      dat2 <- dat1[dat1$row_spacing == j,]
+      dat2 <- dat1[dat1$row_spacing == j, ]
       controlY <-
@@
 
-      dat1[dat1$row_spacing == j,] <- dat2
+      dat1[dat1$row_spacing == j, ] <- dat2
    }
-   PM_MB_means[PM_MB_means$trial_ref == i,] <- dat1
+   PM_MB_means[PM_MB_means$trial_ref == i, ] <- dat1
 }
@@
 
-dat1 <- PM_MB_means[PM_MB_means$trial_ref == "AM1303",]
+dat1 <- PM_MB_means[PM_MB_means$trial_ref == "AM1303", ]
 
@@
    c(NA, NA)
-PM_MB_means[PM_MB_means$trial_ref == "AM1303",] <- dat1
+PM_MB_means[PM_MB_means$trial_ref == "AM1303", ] <- dat1
 
@@
 ```{r simpler_clusters_REMOVE}
-
-slimmer_PM_dat <- slim_PM_dat[slim_PM_dat$spray_management != "Late" & 
-               slim_PM_dat$spray_management != "Early_plus",]
+slimmer_PM_dat <-
+   slim_PM_dat[slim_PM_dat$spray_management != "Late" &
+                  slim_PM_dat$spray_management != "Early_plus", ]
 
@@
 slimmer_PM_dat %>%
-   ggplot(aes(x= grain_yield.t.ha, y = vi))+
+   ggplot(aes(x = grain_yield.t.ha, y = vi)) +
    geom_point()
@@
 slimmer_PM_dat %>%
-   ggplot(aes(x= grain_yield.t.ha, y = Y_Msquare))+
+   ggplot(aes(x = grain_yield.t.ha, y = Y_Msquare)) +
    geom_point()
-
 ```
@@
 
-plot(grain_yield.t.ha. ~ AUDPC_m,data = PM_MB_means)
+plot(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means)
 abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means))
@@
 ```{r AUDPCxTrial}
-sm2lg <- PM_MB_means%>%
-   group_by(trial_ref)%>%
-   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE))%>%
+sm2lg <- PM_MB_means %>%
+   group_by(trial_ref) %>%
+   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
    arrange(TY)
 
-for(i in sm2lg$trial_ref){
+for (i in sm2lg$trial_ref) {
    dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
-   if(any(is.na(dat1$grain_yield.t.ha.))){next}
-   if(any(is.na(dat1$AUDPC_m))){next}
+   if (any(is.na(dat1$grain_yield.t.ha.))) {
+      next
+   }
+   if (any(is.na(dat1$AUDPC_m))) {
+      next
+   }
 
-plot(grain_yield.t.ha. ~ AUDPC_m, 
-     data = dat1, main = paste(dat1$location[1],(dat1$year[1])),
-     ylim = c(0,max(PM_MB_means$grain_yield.t.ha., na.rm = TRUE)), 
-     xlim = c(0,max(PM_MB_means$AUDPC_m, na.rm = TRUE)))
+   plot(
+      grain_yield.t.ha. ~ AUDPC_m,
+      data = dat1,
+      main = paste(dat1$location[1], (dat1$year[1])),
+      ylim = c(0, max(PM_MB_means$grain_yield.t.ha., na.rm = TRUE)),
+      xlim = c(0, max(PM_MB_means$AUDPC_m, na.rm = TRUE))
+   )
    abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = dat1))
-points(grain_yield.t.ha. ~ AUDPC_m, data = dat1[dat1$fungicide_ai == "control",], col = "red")
+   points(grain_yield.t.ha. ~ AUDPC_m,
+          data = dat1[dat1$fungicide_ai == "control",],
+          col = "red")
 
 }
-
 ```
@@
 ```{r Yield_vs_AUDPS}
-plot(grain_yield.t.ha. ~ AUDPS_m,data = PM_MB_means)
+plot(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means)
 abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means))
@@
 
-sm2lg <- PM_MB_means%>%
-   group_by(trial_ref)%>%
-   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE))%>%
+sm2lg <- PM_MB_means %>%
+   group_by(trial_ref) %>%
+   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
    arrange(TY)
 
-for(i in sm2lg$trial_ref){
-   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
-   if(any(is.na(dat1$grain_yield.t.ha.))){next}
-   if(any(is.na(dat1$AUDPS_m))){next}
+for (i in sm2lg$trial_ref) {
+   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i,]
+   if (any(is.na(dat1$grain_yield.t.ha.))) {
+      next
+   }
+   if (any(is.na(dat1$AUDPS_m))) {
+      next
+   }
 
-plot(grain_yield.t.ha. ~ AUDPS_m, 
-     data = dat1, main = paste(dat1$location[1],(dat1$year[1])),
-     ylim = c(0,max(PM_MB_means$grain_yield.t.ha., na.rm = TRUE)), 
-     xlim = c(0,max(PM_MB_means$AUDPS_m, na.rm = TRUE)))
+   plot(
+      grain_yield.t.ha. ~ AUDPS_m,
+      data = dat1,
+      main = paste(dat1$location[1], (dat1$year[1])),
+      ylim = c(0, max(
+         PM_MB_means$grain_yield.t.ha., na.rm = TRUE
+      )),
+      xlim = c(0, max(PM_MB_means$AUDPS_m, na.rm = TRUE))
+   )
    abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = dat1))
-points(grain_yield.t.ha. ~ AUDPS_m, data = dat1[dat1$fungicide_ai == "control",], col = "red")
+   points(grain_yield.t.ha. ~ AUDPS_m,
+          data = dat1[dat1$fungicide_ai == "control", ],
+          col = "red")
 
@@
 as.Date(PM_MB_means$first_sign_disease, format = "%Y-%m-%d"),]
-
 ```

### 2020-05-22 05_AUDPC_MetaAnalysis.Rmd

@@
 PM_Mdat$SE <- NA
-for(i in PM_Mdat$trial){
-   PM_Mdat[PM_Mdat$trial == i,c("slope", "SE")] <-
-      coef(summary(lm(grain_yield.t.ha ~ AUDPC_m,data = PM_Mdat[PM_Mdat$trial == i,])))[2,1:2]
+for (i in PM_Mdat$trial) {
+   PM_Mdat[PM_Mdat$trial == i, c("slope", "SE")] <-
+      coef(summary(lm(grain_yield.t.ha ~ AUDPC_m, data = PM_Mdat[PM_Mdat$trial == i, ])))[2, 1:2]
 }
 
-plot(1/SE ~ slope, data = PM_Mdat, ylim = c(-3000,6000))
+plot(1 / SE ~ slope,
+     data = PM_Mdat,
+     ylim = c(-3000, 6000))
 ```
@@
 ```{r LMER_AUDPC1}
-Me_mod1 <- lmer(grain_yield.t.ha ~ AUDPC_m + (1|trial),
+Me_mod1 <- lmer(grain_yield.t.ha ~ AUDPC_m + (1 | trial),
                 data = PM_Mdat)
@@
 
-Me_mod1.s <- lmer(grain_yield.t.ha ~ AUDPS_m + (1|trial),
+Me_mod1.s <- lmer(grain_yield.t.ha ~ AUDPS_m + (1 | trial),
                   data = PM_Mdat)
@@
 r.squaredGLMM(Me_mod1.s)
-anova(Me_mod1,Me_mod1.s)
+anova(Me_mod1, Me_mod1.s)
 ```
@@
 ```{r LMER_AUDPC2}
-Me_mod2 <- lmer(grain_yield.t.ha ~ AUDPC_m + (AUDPC_m|trial),
+Me_mod2 <- lmer(grain_yield.t.ha ~ AUDPC_m + (AUDPC_m | trial),
                 data = PM_Mdat)
@@
 ```{r LMER_AUDPS2}
-Me_mod2.s <- lmer(grain_yield.t.ha ~ AUDPS_m + (AUDPS_m|trial),
+Me_mod2.s <- lmer(grain_yield.t.ha ~ AUDPS_m + (AUDPS_m | trial),
                   data = PM_Mdat)
@@
 
-Me_mod3 <- lmer(grain_yield.t.ha ~ PM_final_severity + (1|trial),
+Me_mod3 <- lmer(grain_yield.t.ha ~ PM_final_severity + (1 | trial),
                 data = PM_Mdat)
-Me_mod4 <- lmer(grain_yield.t.ha ~ PM_final_severity + (PM_final_severity|trial),
+Me_mod4 <-
+   lmer(grain_yield.t.ha ~ PM_final_severity + (PM_final_severity |
+                                                   trial),
         data = PM_Mdat)
@@
 # PM_final_incidence vs AUDPC
-anova(Me_mod4,Me_mod2)
+anova(Me_mod4, Me_mod2)
 ```
@@
 ```{r AUDPC_spraymanagement}
-Me_mod5 <- lmer(grain_yield.t.ha ~ AUDPC_m + spray_management+ (AUDPC_m|trial),
+Me_mod5 <-
+   lmer(grain_yield.t.ha ~ AUDPC_m + spray_management + (AUDPC_m |
+                                                            trial),
         data = PM_Mdat)
@@
 ```{r AUDPC:spraymangement}
-Me_mod6 <- lmer(grain_yield.t.ha ~ AUDPC_m : spray_management+ (AUDPC_m|trial),
+Me_mod6 <-
+   lmer(grain_yield.t.ha ~ AUDPC_m:spray_management + (AUDPC_m | trial),
         data = PM_Mdat)
@@
 ```{r AUDPC:spraymangement2}
-Me_mod8 <- lmer(grain_yield.t.ha ~ AUDPC_m : spray_management + (AUDPC_m: spray_management|trial),
-              data = PM_Mdat)
+Me_mod8 <-
+   lmer(
+      grain_yield.t.ha ~ AUDPC_m:spray_management + (AUDPC_m:spray_management |
+                                                        trial),
+      data = PM_Mdat
+   )
 
@@
 
-Me_mod9 <- lmer(grain_yield.t.ha ~ AUDPC_m : spray_management + (1|trial),
+Me_mod9 <-
+   lmer(grain_yield.t.ha ~ AUDPC_m:spray_management + (1 | trial),
         data = PM_Mdat)
@@
 summary(Me_mod6)
-coef(Me_mod6)[["trial"]][
-   order(coef(Me_mod6)[["trial"]]$AUDPC_m),]
-
+coef(Me_mod6)[["trial"]][order(coef(Me_mod6)[["trial"]]$AUDPC_m),]
 ```
@@
 
-PM_mv_AI <- rma.mv(yi,vi,
-                   mods = ~ log(AUDPC_m+1):spray_management,
+PM_mv_AI <- rma.mv(
+   yi,
+   vi,
+   mods = ~ log(AUDPC_m + 1):spray_management,
    method = "ML",
-                   random = list(~ spray_management | trial),
+   random = list( ~ spray_management | trial),
    struct = "UN",
-                   data = PM_Mdat)
+   data = PM_Mdat
+)
 
 summary(PM_mv_AI)
+```
 
-```
 ```{r}

### 2020-05-22 vignette/191115_PMMB_DataWrangling_PM.Rmd
Tidy up repository and remove unnesercary files

--- 2020-04-01 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
@@
                             new_data = Goolhi_13_m, 
-                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            new_data_column = c("planting_date","AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
                             filter_cols = c("trial_ref", "year", "location", "host_genotype", 
@@
                             new_data = MarysM_13_m, 
-                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            new_data_column = c("planting_date","AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
                             filter_cols = c("trial_ref", "year", "location", "host_genotype", 
@@
                             new_data = Premer_13_m, 
-                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            new_data_column = c("planting_date","AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
                             filter_cols = c("trial_ref", "year", "location", "host_genotype", 
@@
                             new_data = Millm_13_m, 
-                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            new_data_column = c("planting_date","AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
                             filter_cols = c("trial_ref", "year", "location", "host_genotype", 

### 2020-05-22 tmp/climogram.R

@@ -1,131 +1,0 @@
-
-## This file can be used to clean up/update 02_weather.Rmd if we use it.
-## Delete this file before publishing. Either after incorporation into
-## 02_weather.Rmd or upon deletion of that file.
-
-library(ggplot2)
-library(dplyr)
-library(lubridate)
-library(theme.usq)
-library(caTools)
-source("R/import_data.R")
-PM.dat <-
-   import_data()  # importing means yield and disease severity for each
-# treatment within each powdery mildew trial on mungbean
-source("R/gg_color_hue_function.R")
-
-cols1 <- gg_color_hue(4)
-
-# import data from SILO interpolated datasets downloaded from the QLD longpaddock website
-silo_war_Tmax <- read.csv("./data/silo_war_Tmax.csv")
-silo_king_Tmax <- read.csv("./data/silo_king_Tmax.csv")
-silo_gatton_Tmax <- read.csv("./data/silo_gatton_Tmax.csv")
-silo_emerald_Tmax <- read.csv("./data/silo_emerald_Tmax.csv")
-
-
-
-PM.dat_sum <-
-   PM.dat %>%
-   distinct(location, year, first_sign_disease) %>%
-   mutate(day = yday(first_sign_disease))
-
-# Smoothing temperatures by taking a rolling 7-day average, runmean() from caTools
-max_T <- runmean(silo_king_Tmax$max_temp, 7)
-min_T <- runmean(silo_king_Tmax$min_temp, 7)
-
-king_Tm_aver <-
-   data.frame(
-      location = "Kingaroy",
-      date = as.Date(silo_king_Tmax$date),
-      max_T,
-      min_T,
-      daily_rain = silo_king_Tmax$daily_rain
-   )
-
-# Add columns for year and day of year to data
-king_Tm_aver$year <- year(king_Tm_aver$date)
-king_Tm_aver$day <- yday(king_Tm_aver$date)
-
-# set year to factor
-king_Tm_aver$year <- as.factor(king_Tm_aver$year)
-
-# set up axis
-# max rainfall set from
-ylim.prim <- c(0, round(max(king_Tm_aver$daily_rain), digits = 0))
-ylim.sec <- c(round(min(king_Tm_aver$min_T), digits = 0),
-              round(max(king_Tm_aver$max_T), digits = 0))
-
-b <- diff(ylim.prim) / diff(ylim.sec)
[…]

### 2020-05-22 01_Meta-analysis_experiments.Rmd
wordsmithing in chapter 2, fix incorrect reference for NGA and delete  temp file

--- 2020-02-26 01_Meta-analysis_experiments.Rmd
@@
 # Studies considered in meta-analysis
-
-This meta-analysis uses data collected by a number of researchers from the
-Department of Agriculture and Primary Industries and the University of Southern
-Queensland. It is worth noting Professor Malcolm Riley's and Dr Sue Thompson's
-effort in establishing and coordinating early field trials between 2010 and
-2016.
 
@@
 ```
+
+This meta-analysis uses data collected by a number of researchers from the Department of Agriculture and Primary Industries and the University of Southern
+Queensland.
+It is worth noting Professor Malcolm Riley's and Dr Sue Thompson's effort in establishing and coordinating early field trials between 2010 and 2016.
+
+Studies were conducted in the following locations and years and were considered for inclusion in this analysis.
 
@@
 Trial data were obtained from a non-published manuscript.  
-Ratings for powdery mildew were on a 1-5 rating scale and can be read in the
-file "Powdery mildew paper#1.doc".  
-Comparing trials which have not used the same rating scale will be done using a
-percentage change.
+Ratings for powdery mildew were on a 1-5 rating scale and can be read in the file "Powdery mildew paper#1.doc".
+Comparing trials, which have not used the same rating scale will be done using a percentage change.
 
 **2013 Field trials**  
-Trials were conducted by the National Growers Alliance (NGA). The raw data were
-obtained from Lawrie Price. NGA data were formatted to be compliant with
-existing data rating and scales in the R script `Cleaning historical data.R`.
+Trials were conducted by the [Northern Growers Alliance (NGA)](https://www.nga.org.au/).
+The raw data were obtained from Lawrie Price.
+NGA data were formatted to be compliant with existing data rating and scales using the R script [`R/Cleaning historical data.R`](https://github.com/openplantpathology/Mungbean_PM/blob/master/R/Cleaning%20historical%20data.R).
 
@@
 
-```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}
+```{r data_summary, echo=FALSE, message=FALSE, warning=FALSE}
 PM.dat <- import_data()
@@
    PM.dat %>%
-      group_by(
-         trial_ref,
-         year,
-         location,
-         trial_design,
-         replicates,
-         planting_date,
-         emergence_date,
-         first_sign_disease
+      group_by(trial_ref, ) %>%
+      summarise(
+         year = unique(year),
+         location = unique(location),
+         mean_treat_replicates = mean(replicates),
+         planting_date = unique(planting_date),
+         first_sign_disease = unique(first_sign_disease),
+         treatments = length(n_treatment)
       ) %>%
-      summarise(treatments = length(n_treatment)),
+      arrange(year),
    caption = "Description of Experiments"
@@
    1. No powdery mildew colonies observed on any plant
+
    2. Small colonies in lower 1/3 of canopy, up to 75% of plants affected
+
    3. Colonies in lower 1/2 of canopy, >75% of plants affected
+
    4. Colonies in lower 2/3 of canopy, up to 75% of plants affected
+
    5. Colonies in lower 2/3 of canopy, >75% of plants affected
+
    6. Colonies in lower 2/3 of canopy, 100% of plants affected
+
    7. Colonies in lower 2/3 of canopy of 100% of plants, some plants with colonies also in top 1/3 of canopy
+
    8. Colonies to top of plant with >75% of plants affected
+
    9. Colonies to top of plant with 100% of plants affected and heavy leaf drop
 
-## Experimental locations
+## Experiment locations
 
-Experimental locations where data was sufficient to include in meta-analysis.
+The following map displays experiment locations where data was sufficient to include in this meta-analysis.
 
-```{r Experiment_locations}
+```{r Experiment_locations, echo=FALSE}
 experiment_sites <- data.frame(

### 2020-05-22 01_Meta-analysis_experiments.Rmd
Added in the whole rating system in instead of the reference to the incomplete paper

--- 2020-03-01 01_Meta-analysis_experiments.Rmd
@@
 Trial data were obtained from a non-published manuscript.  
-Ratings for powdery mildew were on a 1-5 rating scale and can be read in the
-file "Powdery mildew paper#1.doc".  
+Ratings for powdery mildew were on a 1-5 rating scale where 1 = no sign of disease, 2 = 1-30% diseased leaf area, 3 = 31-65% diseased leaf area, 4 = 66-99% diseased leaf area and 5 = complete defoliation.
 Comparing trials which have not used the same rating scale will be done using a

### 2020-05-22 01_Meta-analysis_experiments.Rmd

--- 2020-05-22 01_Meta-analysis_experiments.Rmd
@@
 Trial data were obtained from a non-published manuscript.  
-Ratings for powdery mildew were on a 1-5 rating scale and can be read in the file "Powdery mildew paper#1.doc".
-Comparing trials, which have not used the same rating scale will be done using a percentage change.
+Ratings for powdery mildew were on a 1-5 rating scale where 1 = no sign of disease, 2 = 1-30% diseased leaf area, 3 = 31-65% diseased leaf area, 4 = 66-99% diseased leaf area and 5 = complete defoliation.
+Comparing trials which have not used the same rating scale will be done using a
+percentage change.
 

### 2020-05-22 02_Preliminary_analysis.Rmd

@@
 Various factors have been studied in the previous experiments which may influence the following results.
-However unless stated the following plots and analyses were made disregarding effects from other factors not mentioned.
+However, unless stated, the following plots and analyses were made disregarding effects from other factors not mentioned.
 
-   1) Fungicide type
+   1 Fungicide type
 
-   2) Fungicide dose (varies only slightly within some fungicide types)
+   2 Fungicide dose (varies only slightly within some fungicide types)
 
-   3) Number of fungicide sprays
+   3 Number of fungicide sprays
 
-   4) Timing of fungicide spray/s relative to first sign of disease (_i.e_. when pathogen is present)
+   4 Timing of fungicide spray/s relative to first sign of disease
 
-   5) Host cultivars (probably is a co-variate with season due to changing cultivars over time)
+   5 Host cultivars (probably is a co-variate with season due to changing cultivars over time)
 
-   6) Experiment location
+   6 Experiment location
 
-   7) Row spacing
+   7 Row spacing
 
-   8) In-crop rainfall
+   8 In-crop rainfall
 
-   9) Irrigated vs non-irrigated trials
+   9 Irrigated vs non-irrigated trials
 
-   10) Mean daily temperature in the weeks following spray application
+   10 Mean daily temperature in the weeks following spray application
 
-   11) Final disease rating
+   11 Final disease rating
 
-   12) Two pathogen species cause PM (new discovery in 2018)
+   12 Two pathogen species cause PM (new discovery in 2018)
 
 The data plotted below are from `r length(unique(PM_MB_means$trial_ref))` field trials between (`r first(levels(PM_MB_means$year))` - `r last(levels(PM_MB_means$year))`) of which the details are described in [Studies considered in meta-analysis section](#studies-considered-in-meta-analysis).
+
 All data explored below are a list of mean values from each treatment applied in each experiment.
-Some experiments have in-season observations of disease incidence and severity, however here we have summarised the data to show only the end of season observations.
+Some experiments have in-season observations of disease incidence and severity.
+However, here we have summarised the data to show only the end of season observations.
 
 ### Fungicides
+
 #### Fungicide type
+
 Let's explore how many different types of fungicide were used and at what frequency.
@@
 
-First, let's investigate the difference in the effect of the type of fungicide on proportion of yield saved. Proportion of yield saved is used in attempt to reduce variation between trials.
+First, let's investigate the difference in the effect of the type of fungicide on proportion of yield saved.
+Proportion of yield saved is used in attempt to reduce variation between trials.
 
@@
    facet_grid(rows = vars(total_fungicide)) +
-   geom_boxplot(aes(fill = fungicide_ai, alpha = 0.5)) +
+   geom_boxplot(aes(fill = fungicide_ai)) +
    geom_hline(aes(yintercept = 0), size = 0.5) +
@@
 
-There is a small yield effect when applying fungicide and it is unclear how much a second spray improves yield saved. Interestingly sulphur sprays might be worth investigating when sprayed twice.
+There is a small yield effect when applying fungicide and it is unclear how much a second spray improves yield saved.
+Interestingly sulphur sprays might be worth investigating when sprayed twice.
 
@@
 
-All trials that used tebuconazole used approximately the same dose. Dose of the active ingredient ranged from 62.35&nbsp;g per hectare to 60&nbsp;g per hectare.
+All trials that used tebuconazole used approximately the same dose.
+Dose of the active ingredient ranged from 62.35&nbsp;g per hectare to 60&nbsp;g per hectare.
 
@@
    ggtitle(label = "Yield for each respective propiconazole dose") +
-   geom_boxplot() +
-   scale_fill_usq() +
-   scale_colour_usq()
+   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5)
 ```
 
-This dose effect should be acknowledged in the meta-analysis. How many treatments of each dose have been investigated per trial?
+This dose effect should be acknowledged in the meta-analysis.
+How many treatments of each dose have been investigated per trial?
 
@@
 
-This plot plot, however, indicated the previous plot might be skewed by high yielding trials.
+This plot, however, indicates that the previous plot might be skewed by high yielding trials.
 
@@
    geom_col() +
-   scale_fill_usq()
+   scale_fill_usq(name = "Fungicide AI")
 ```
@@
 Does host cultivar significantly impact the yield?
-Let's look at the volatility in yields to see if any cultivar yields better or has greater tolerance to powdery mildew.
-Below we plot distributions of mean trial yields for each cultivar.
+Let's look at the volatility in yields to see if any cultivar yields better or has greater tolerance to powdery mildew. Below we plot distributions of mean trial yields for each cultivar.
 
 First let's look at overall yields for each cultivar, where trial is not a factor, for all treatments (spray and no spray).
+
 ```{r yield_vol}
@@
 ```
+
 Now let's look at overall yields for each cultivar, where trial is not a factor, in only the no spray treatments.
+
 ```{r yieldVol_control}
@@
 Let's examine the same plots as above but only for the most commonly used trial site, Hermitage.
+
 ```{r yieldVol_Herm}
@@
 Let's look at Jade, to see if it differs.
+
 ```{r YieldVol_Jade}
@@
 
-For Jade there is high variation between trials and with in. Perhaps indicating lower tolerance. Let's look at the same plot with data only from no spray controls to see if the variation is the same.
+For Jade there is high variation between trials and with-in.
+Perhaps indicating lower tolerance. Let's look at the same plot with data only from no spray controls to see if the variation is the same.
 
@@
    ggplot(aes(y = PM_final_severity, x = factor(row_spacing))) +
-   geom_boxplot() +
+   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
    ggtitle("Powdery mildew variation between different row spacing")
@@
    ggplot(aes(y = PM_final_severity, x = factor(row_spacing))) +
-   geom_boxplot() +
+   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
    facet_grid(cols = vars(location)) +
-   ggtitle("Powdery mildew variation between different row spacing")
+   ggtitle("Powdery mildew variation between different row spacing") +
+   ylab("Final severity rating") +
+   xlab("Row spacing (m)")
 ```
@@
    xlab("Row spacing (m)") +
-   ylab("Grain yield - tonnes per hectare") +
+   ylab("Grain yield (t/ha)") +
    scale_colour_usq()
@@
 log of the p value was used to improve the resolution of small very small p values.
+
 ```{r rainLMpvalue}
@@
 We will focus on proportional yield gain, compared to no treatment control, as this should partially correct for some spatial and seasonal effects.
+
 ```{r fungicide_proportion_yield}
-PM_MB_means %>%
-   group_by(fungicide_ai) %>%
-   summarise(
-      n = length(prop_YG),
-      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
-      median = median(prop_YG, na.rm = T),
-      mean = mean(prop_YG, na.rm = T),
-      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
-   ) %>%
-   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
-   arrange(desc(median)) %>%
-   kable(caption = "Fungicide effect on proportion of yield gain") %>%
-   kable_styling(fixed_thead = T, full_width = T)
-
 # plot table as a box plot
@@
    ggplot(aes(y = prop_YG, x = fungicide_ai)) +
-   geom_boxplot() +
+   geom_boxplot(aes(fill = fungicide_ai)) +
    geom_hline(aes(yintercept = 0), size = 0.5, colour = "red") +
    labs(x = "Proportion of grain yield saved",
-        title = "Grain yield proportion saved grouped by\nfungicide type") +
+        title = "Grain yield proportion saved,\ngrouped by fungicide type") +
    theme(
@@
    guides(fill = guide_legend(title = "Fungicide")) +
+   scale_fill_usq() +
    coord_flip()
@@
 
-We need to also define the relationship between yield loss and disease severity. When exploring this data we should look primarily at the no spray control plots
+We need to also define the relationship between yield loss and disease severity.
+When exploring this data we should look primarily at the no spray control plots
 

### 2020-05-22 01_Meta-analysis_experiments.Rmd
as per repository issue #20 column heading and contents made more clear and removed trial_ref

@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, leaflet, htmltools)
+pacman::p_load(tidyverse, kableExtra, leaflet, htmltools,schoolmath)
 source("R/import_data.R")
@@
          location = unique(location),
-         mean_treat_replicates = mean(replicates),
+         replicates_per_treatment = if(is.whole(mean(replicates))){
+            as.character(mean(replicates))}else{
+               as.character(paste(min(replicates),"-",max(replicates)))},
          planting_date = unique(planting_date),
@@
       ) %>%
-      arrange(year),
+      arrange(year)%>%
+      select(-trial_ref),
    caption = "Description of Experiments"
@@
    scroll_box(width = "900px", height = "500px")
+
 ```

### 2020-05-25 vignette/191115_PMMB_DataWrangling_PM.Rmd
Correct and document fold_data() code

@@
 ```{r message=FALSE, warning=FALSE}
-# install.packages("openxlsx")
-# install.packages("readxl")
-# install.packages("tidyr")
-# install.packages("agricolae")
-
 library(openxlsx)
@@
 fold_data <- function(new_DataFrame, template_DataFrame) {
+   # This function formats a dataframe to have the same column order as a template data.frame
+   # If colums are missing from the new_DataFrame that are in the template_DataFrame, it creates them 
+   # with NA values. 
+   # Columns in the new_DataFrame, which are not in the template_DataFrame are appended to the right-hand-side
+   # of the new_DataFrame
+   # Using this function assists in joining the two data.frames together so colums are in the same order
+
    for (i in colnames(new_DataFrame)) {
@@
 
-   new_DataFrame[cnames2[!(cnames2 %in% cnames1)]] <-
-      NA # adding column names to new_DataFrame not in template_DataFrame
+   new_DataFrame <- as.data.frame(new_DataFrame)
+
+   new_DataFrame[,cnames2[!(cnames2 %in% cnames1)]] <-
+      NA # adding column names to new_DataFrame which are in the template_DataFrame
    new_DataFrame <-
-      new_DataFrame[, c(cnames2, cnames1[is.na(x1)])]  # adding column names to new_DataFrame not in template_DataFrame
+      new_DataFrame[, c(cnames2, cnames1[is.na(x1)])]  # adding columns to new_DataFrame not in template_DataFrame  # aranges column names to new_DataFrame not in template_DataFrame
+
    return(new_DataFrame)
 }
-source(here("copy_class.R"))
+source(here("R/copy_class.R"))
 source(here("R/data_mesh.R"))

### 2020-05-25 06_7Questions_to_assist_Publication_Structure.Rmd
Seperate the 7 questions from the manuscript. Create a new file for the manuscript

--- 2020-05-22 06_Publication_wireframe_and_7_Questions.Rmd
@@
 ---
-title: Meta-analysis of fungicide application timing experiments for powdery mildew
-  management in mungbean.
+title: "Publication wireframe"
 author: "P. Melloy"
-date: "31/01/2020"
-output:
-  html_document: default
-  word_document: default
+date: "25/05/2020"
+output: html_document
 ---
-
-```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, here)
-
-# Data
-PM_Mdat <- read.csv(here("cache/PM_MB_updated.csv"))
-
-```
 
@@
 Only a few studies incorporated in the meta-analysis contained comparisons between the “Late plus” factor and the treatments: negative spray control, a single spray at first sign, and spray at first sign with one or more follow-up applications.
-
-*****
-
-# Manuscript
-
-## Introduction
-Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown in south-east Asia for human consumption, and constitutes an affordable source of protein [@PulseAustralia]. 
-The bean pod or grain can be consumed raw or added to meals after sprouting. 
-The dried grain can also be ground into a protein enriched flour for uses such as noodles, biscuits and cakes [@Chankaew2013].
-
-In Australia mungbean is grown in southern Queensland and northern New South Wales as a short season summer legume crop. 
-Approximately 90% of mungbean yields are exported and economic returns can be lucrative for growers. 
-Mungbean potentially yields up to 2.3 tonnes per hectare, with a value of up to \$ 1300 AUD a tonne [@QueenslandGovernment2019]. 
-However these potential crop yields can be limited by a range of diseases[@Kelly2017a].
-Powdery mildew (*Podosphaera xanthii*), for instance, can reduce yields by up to 40% [@Chankaew2013]. 
-Fortunately a number of strategies are available to be employed to reduce the damage powdery mildew inflicts on mungbean yields.
-
-### Managements strategies
-#### and conditions for infection
-Planting date is an effective strategy for preventing the development of powdery mildew in mungbean. 
-Powdery mildew infection requires cool temperatures, between 22$^\circ$ and 26$^\circ$C, and a leaf surface that is not overly wet for infection [@Kelly2017a]. 
-In southern Queensland and northern New South Wales, sowing dates between late spring (November) and mid-summer (January) are advised to avoid the conducive cooler autumn temperatures which normally commence in March.
-Therefore a delayed sowing date increases the possibility powdery mildew will infect earlier in the crop development leading to greater yield losses.
-
-Commercially available mungbean cultivars in Australia lack sufficient resistance to be used as a sole powdery mildew management strategy.
-Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013]. 
-In Australia, quantitative resistance has also been incorporated a couple of varieties which are commercially available. 
-Jade-AU is recommended as containing the best disease resistance to powdery mildew (moderately susceptible), while also conferring quantifiable resistance to other foliar diseases such as tan spot and halo blight [@AustralianMungbeanAssociation].
-Because cultivar choice does not confer complete resistance to powdery mildew, additional strategies such as fungicide treatments are necessary to limit yield loss when conditions for the disease are suitable.
-
-The recent release of 'PowderyMildewMBM', a decision support system (DSS), increases the ease for preparing a fungicide spray schedule to manage powdery mildew [@Diggle]. 
-PowderyMildewMBM provides a cost benefit analysis to growers for fungicide spray schedule scenarios.
-The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability that one or two fungicide sprays would protect yields sufficiently to increase the net profit.
-
-### Fungicide resistance
-Fungicide application costs in Australia are relatively cheap, and we estimate these costs to be approximately \$ 20 AUD per hectare. 
-Lucrative returns of up to \$ 2260 per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than necessary. 
-Excessive use of fungicides are not only costly, but lead to problems such as fungicide resistance. 
-*Podosphaera xanthii* is categorised by FRAC as a 'High risk' candidate to evolve fungicide resistance. 
-The evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with fungicide resistance potential in mind.
-Powdery mildew in cucurbits evolved resistance to benzimidazole within three years of it's registration [@Peterson1973].
-In cereal crops _Blumeria graminis_ showed lower sensitivity to strobilurins in 1998, two years after the fungicide began being used in Europe [@Chin2001].
-Powdery mildew is one such disease with an extensive track record of rapidly developing fungicide resistance. 
-In cucurbits, powdery mildew has evolved resistance to numerous fungicide classes, such as benzimidazoles, DMIs, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines [@Mcgrath2001].
-
-To extend the time that a fungicide remains effective against the target pathogen, strategic use of the fungicide must be considered. 
-Excessive fungicide sprays by a single active increase the selection pressure on the pathogen to evolve resistance [@Brent2007]. 
-If any strains of the pathogen with resistance to the fungicide are present in a population regular use of the fungicide will increase it's proportion in the population. 
-Managing the disease with fungicides for the highest economic return is likely not to require eradication of the causal pathogen. 
-Integrated pest management practices focus on using only the required number of chemical control to protect the economic return. 
-These strategies permit the presence of yield limiting diseases and pests if intervening would cost more than the economic return of protection.
-
-The timing of fungicide sprays are critical for their efficacy and for limiting fungicide resistant strains from emerging. 
-Fungicide applications made too early would increase costs without providing any benefit to yields. 
-Applications which are made too late allow the disease to establish and damage the crop productivity, while making subsequent sprays difficult to reduce the disease incidence.
-
-### Previous studies - fungicide work
-There is almost a complete lack of peer-reviewed literature summarising fungicide efficacy on powdery mildew in Mungbean. 
-Many of the experimental work has been published by funding agencies and state government extension departments. 
-Past field trials in eastern Australia have trialed a range of fungicide active ingredients (table), while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
-Early trials showed for a fungicide application to provide maximum efficacy a single fungicide application at first sign of the disease with another follow-up application two weeks later if necessary [@Sparks2017].
-Some of the trialled fungicides for treating powdery mildew in mungbean have been registered with the APVMA [@APVMA; @Kelly2017a; insert all published trials here].
-
-### Meta-analysis
-
-### Aims
-
-The aim of this meta-analysis was to determine, from a collection of unpublished studies, when is the ideal time to apply fungicide with respect to the first sign of disease, and does multiple fungicide applications provide better protection for mungbean yields.
-
-*****
-
-## Materials and methods
-
-The data for this study was obtained from through personal correspondence with colleagues and collaborating institutions.
-The majority of the trials were undertaken by Malcolm Riley and Dr Sue Thompson with The Department of Agriculture and Primary industries (DAF). 
-Trials undertaken in 2013 season were conducted by the Northern growers alliance [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013].
-The most recent trials from 2017 were undertaken by DAF and the University of Southern Queensland (USQ) from 2017 to 2019 (Table 1). 
-Trial data were in different formats with varying levels of information.
-Some trial data reporting means of each treatment, with all but one study reporting variance along with the mean. 
-For XX trials the raw data were obtained.
-
-Details of trial data is presented within a research compendium which was prepared to supplement this publication [insert reference to compendium].
-
-The criteria for inclusion of trial data in the meta-analysis, required a field trial testing fungicide efficacy for powdery mildew control on mungbean in the northern grains regions of eastern Australia.
-Trial data had to include the date when powdery mildew was first observed. 
-Trials needed to have tested a demethylase inhibitor (DMI) fungicide.
-
-All trials included in this analysis were not previously published in peer-reviewed literature.
-Some trials and results were reported online via the Grains Research and Development Corporation.
-
-While the main aim of all the trials collected for this study were the same, assess the efficacy of fungicides for control of powdery mildew, most also aimed to test the effect of different variables on fungicide efficacy.
-Some of the variable which were suspected to influence powdery mildew incidence and the effect on yield were: trial location, trial season, row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar, irrigation and rainfall.
-To account for this variation between trials and their treatments within the trial a single 'trial' factor was created to describe the main variables; Trial location, trial season, host genotype and row spacing.
-
-To reduce confounding effects of various fungicides we only included treatments within trials which had been sprayed with a fungicide which has a DMI mode of action, such as tebeconazole and propiconazole.
-Fungicide active from the DMI group was the main inclusion factor for the analysis which reduced the number of trials from 24 to 17 experiments.
-
-Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 - 9 ordinal scale [ref]. 
-The 2013 NGA trials reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the canopy; lower, middle or upper canopy. 
-Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, it was easy to calculate the equivalent incidence on the ordinal 1 - 9 scale.
-
-The timing of fungicide applications, with reference to when the disease first occurred in the trial, and number of applications were used to define a treatment variable.
-An 'Early' fungicide application, refers to a fungicide spray schedule that commences with it's first spray prior to the disease being observed in the trial.  
-'Recommended' refers to a fungicide spray schedule which commences within three days following the first sign of disease, and 'late' treatments which commence four days or later than first sign. 
-The number of fungicide applications were binned in to two categories.
-A spray schedule with a single spray, and a spray schedule with one or more sprays where there was a maximum of three applications. 
-The division of the treatments into these six categories created two categories with insufficient numbers of treatments to provide a reliable sample. 
-Single late sprays contained two replicates and multiple early sprays contained five replicates and were therefore removed from the subsequent meta-analysis.
-
-What remained was the mean yield for total of 173 treatments in the following five spray schedule categories: no spray control, single early spray, single recommended spray, recommended with multiple sprays and late with multiple sprays.
-
-Trials where we obtained the raw data the response variables were summarised into the treatment means and variance. 
-The remainder of the trial data reported treatment means and variance. 
-Two of the trials, Gatton 2012 and Emerald 2015, reported treatment means without accompanying variance. 
-For these trials the trial variance was imputed by randomly sampling the trial mean squared error from a distribution of log trial MSE.  
-$rnorm(\overline{x}_{log(MSE_{1}) \dots, log(MSE_{n})}, \sigma_{log(MSE_{1}) \dots, log(MSE_{n})}) $  
-Where MSE is the mean squared error of each trial.
-
-$v_i = MSE_{y}/(n * Y_{i}^2) $
-
-The data were analysed in the R statistical software environment using two meta-analysis packages, `metafor` and `netmeta`.
-
-```{r Table1_ExperimentalDetail, echo=TRUE, message=FALSE, warning=FALSE}
-
-PM_Mdat %>%
-      group_by(trial_ref,) %>%
-      summarise(year = unique(year),
-                location = unique(location),
-                planting_date = unique(planting_date),
-                first_sign_disease = unique(first_sign_disease))%>%
-      arrange(year)%>%
-   left_join(data.frame(trial_ref = unique(PM_Mdat$trial_ref),
-                        Research_org =
-                           c(rep("Queensland DAF",times =12),
-                             rep("Northern Growers Alliance", times = 4),
-               rep("Queensland DAF",times =5),
-               rep("USQ", times = 5))))%>%
-kable(caption = "Table 1: Description of Experiments")%>%
-   kable_styling(fixed_thead = TRUE,
-                 full_width = TRUE) %>%
-   scroll_box(width = "900px", height = "500px")
-```
-
-## Discussion
-
-### Fungicide resistance
-According to the Fungicide resistance Action Committee (FRAC) it is important to alternate or mix Fungicides with different modes of action to avoid fungicide resistance. 
-At the time of writing, in Australia one fungicide is registered with the to treat powdery mildew in mungbean, Veritas/Custodia (200 g/L tebuconazole with 120 g/L azoxystrobin). 
-This fungicide provides dual action: tebeconazole disrupts C-14 demethylase, required in sterol biosynthesis for cell membranes; and azoxystrobin, a Quinone outside inhibitor. 
-Quinone is required in cell metabolism and active in the mitochondrial complex III. 
-However FRAC recommends that applications of QoIs or strobilurins, singularly or as a mixture, should not be applied consecutively and alternated with a fungicide from a different group [@Brent2007]. 
-For mungbean, past experiments have shown some success with sulphur applications to control powdery mildew. 
-Sulphur is a non-systemic protectant and thus provides an excellent option for rotation to limit the emergence of fungicide resistance.

### 2020-05-25 vignette/191115_PMMB_DataWrangling_PM.Rmd
Chunk names Remove commented lines add missing AUDPC scoring in king11

@@
 #### AUDPC curve
-```{r}
+```{r Herm10_audpc}
 library(ggplot2)
@@
               PM_final_severity = Herm_11$`P.M. 11  w.a.p.`,
-              # AUDPC = apply(data.frame(zero = rep(0,42),
-              #                          wap11 = Herm_11[,c("P.M. 11  w.a.p.")]-1),1, 
-              #               FUN = audpc, dates = c((as.Date("2011-03-28", format = "%Y-%m-%d")-7)- # First sign of disease minus planting date. Gives when there is no disease
-              #                                         as.Date("2011-01-24", format = "%Y-%m-%d"),
-              #                  77)), # -1 to the data because zero disease = 1 on rating scale
               rating_scale = "1-9",
@@
 #### AUDPC curve
-```{r}
+```{r Herm_audpc}
 
@@
                      AUDPC = apply(data.frame(zero = 0,
-                                              King_11[,c("9 w.a.p.","11 w.a.p.","14 w.a.p.")]-1),
+                                              King_11[,c("9 w.a.p.","11 w.a.p.","12 w.a.p.","14 w.a.p.")]-1),
                                    1, 
@@
                                                 King_11_dat$planting_date[1],
-                                             9*7,11*7,14*7)
+                                             9*7,11*7,12*7,14*7)
                                    ),
                      AUDPS = apply(data.frame(zero = 0,
-                                                   King_11[,c("9 w.a.p.","11 w.a.p.","14 w.a.p.")]-1),
+                                                   King_11[,c("9 w.a.p.","11 w.a.p.","12 w.a.p.","14 w.a.p.")]-1),
                                         1, 
@@
                                                      King_11_dat$planting_date[1],
-                                                  9*7,11*7,14*7)
+                                                  9*7,11*7,12*7,14*7)
                                         )
@@
 King_11$PM_zero <- 1
-King11_plot <- melt(King_11, id.vars = c("Treatment!","cultivar","rep!","spray_n","fungicide"),
-                  measure.vars = c("PM_zero","9 w.a.p.","11 w.a.p.","14 w.a.p."))
+King11_plot <- reshape2::melt(King_11, id.vars = c("Treatment!","cultivar","rep!","spray_n","fungicide"),
+                  measure.vars = c("PM_zero","9 w.a.p.","11 w.a.p.","12 w.a.p.","14 w.a.p."))
 
@@
                             variable == "11 w.a.p." ~ 11*7,
+                            variable == "12 w.a.p." ~ 12*7,
                             variable == "14 w.a.p." ~ 14 *7)

### 2020-05-26 vignette/191115_PMMB_DataWrangling_PM.Rmd
Remove commented code correct imported rows on Kingaroy15 Added some code descriptions

@@
               grain_yield.t.ha. = as.numeric(King_11$`Yld kg ha`),
-              #AUDPC = apply(King_11[,c("9 w.a.p.", "11 w.a.p.", "12 w.a.p.", "14 w.a.p.")]-1,1, FUN = audpc, dates = c(9*7,11*7,12*7, 14*7))# -1 to the data because zero disease = 1 on rating scale
               stringsAsFactors = FALSE)
@@
               rating_scale = unique(rating_scale),
-              #disease_error = sd(PM_final_severity, na.rm = TRUE),
+              #disease_error = sd(PM_final_severity, na.rm = TRUE),  # this is commented because it never worked for some reason. 
               D_error_type = "stdev",
@@
               raw_graded = NA,
-              #yield_error = sd(grain_yield.t.ha./1000, na.rm = TRUE),
+              #yield_error = sd(grain_yield.t.ha./1000, na.rm = TRUE),  # this is commented because it never worked for some reason. 
               Y_error_type = "stdev",
@@
    group_by(host_genotype, fungicide_ai,n_treatment) %>%
-   summarise(#PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
-             disease_error = sd(PM_final_severity, na.rm = TRUE),
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
              yield_error = sd(grain_yield.t.ha./1000, na.rm = TRUE))
@@
 
+# This table gives the column references for each respective 
+# location in the canopy
 # Calculate incidence
@@
 for (i in seq_along(incidence1)) {
-   # incidence = 1
+   # when incidence = 1
    if (all(Goolhi.13[i, 7:33] == 0)) {
@@
 
-   # incidence = 2
+   # when incidence = 2
    if (all(Goolhi.13[i, c(10:15, 19:24, 28, 33)] == 0) &&
@@
 
-   # incidence = 3
+   # when incidence = 3
    if (all(Goolhi.13[i, c(13:15, 22:24, 31:33)] == 0) &&
@@
 
-   # incidence = 4
+   # when incidence = 4
    if (all(Goolhi.13[i, c(13:15, 22:24, 31:33)] == 0) &&
@@
 
-   # incidence = 5
+   # when incidence = 5
    if (all(Goolhi.13[i, c(13:15, 22:24, 31:33)] == 0) &&
@@
 
-   # incidence = 6
+   # when incidence = 6
    if (all(Goolhi.13[i, c(13:15, 22:24, 31:33)] == 0) &&
@@
 
-   # incidence = 7
+   # when incidence = 7
    if (sum(Goolhi.13[i, c(13:15, 22:24, 31:33)] != 0) <= 3 &&
@@
 
-   # incidence = 8
+   # when incidence = 8
    if ((sum(Goolhi.13[i, c(13:15, 22:24, 31:33)] != 0) > 3 |
@@
 
-   # incidence = 9
+   # when incidence = 9
    if (sum(Goolhi.13[i, c(13:15, 22:24, 31:33)] != 0) > 3 &&
@@
               grain_yield.t.ha. = as.numeric(Goolhi_13$`Yield Kg/ha`)/1000
-              #AUDPC = apply(Goolhi_13[,c("Inc_16D","Inc_33D")]-1,1, FUN = audpc, dates = c(16,33))# -1 to the data because zero disease = 1 on rating scale
               )
@@
               rating_scale = unique(rating_scale),
-              #disease_error = sd(PM_final_severity, na.rm = TRUE),
+              #disease_error = sd(PM_final_severity, na.rm = TRUE), # Commented because were not being calculated and included in the summary function
               D_error_type = "stdev",
@@
               raw_graded = NA,
-              #yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+              #yield_error = sd(grain_yield.t.ha., na.rm = TRUE), # Commented because were not being calculated and included in the summary function
               Y_error_type = "stdev",
@@
    group_by(n_treatment) %>%
-   summarise(#PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
-             disease_error = sd(PM_final_severity, na.rm = TRUE),
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE))
@@
 MarysM.13D.1$Inc_18D <-  incidence2
-#cat(incidence2,"\n",length(incidence2), sep = ", ")
 }
@@
    MarysM.13D.1$Inc_19D <-  incidence2
-   #cat(incidence2,"\n",length(incidence2), sep = ", ")
 }
@@
    )
-dim(MarysM.13Y)
-dim(MarysM.13D.1)
 
@@
               grain_yield.t.ha. = as.numeric(MarysM_13$`Yield Kg/ha`)/1000
-              #AUDPC = apply(MarysM_13[,c("Inc_18D","Inc_19D")]-1,1, FUN = audpc, dates = c(12,12+19)) # -1 to the data because zero disease = 1 on rating scale
               )
@@
               rating_scale = unique(rating_scale),
-              disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+              disease_error = sd(PM_final_severity, na.rm = TRUE), # this not calculating sd and returning NAs?
               D_error_type = "stdev",
@@
 
-   if (i == length(Premer.13D[, 1])) {
-      #print(!plotsRecorded)
-   }
 }
@@
 for (i in seq_along(incidence3)) {
-   # # NAs
-   # if (all(is.na(Premer.13D[i, 58:107]))) {
-   #    incidence3[i] <- NA
-   #    next()
-   # }
 
@@
 # Therefore it will be dropped
-#Premer.13D <- left_join(Premer.13D.1,Premer.13D.2)
 Premer.13D <- Premer.13D.2
@@
               grain_yield.t.ha. = as.numeric(Premer_13$`Yield kg/ha`)/1000
-             # AUDPC = apply(Premer_13[,c("Inc_19D","Inc_31D")]-1,1, FUN = audpc, dates = c(19,12+19)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
               )
@@
                           AUDPC = apply(data.frame(zero = 0,
-                                                           Premer_13[,c("Inc_31D")]-1),
+                                                           Premer_13[,c("Inc_31D")]-1),# -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
                                         1, 
@@
               rating_scale = unique(rating_scale),
-              disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+              disease_error = sd(PM_final_severity, na.rm = TRUE), # Produces NAs and needs to be reproduced again below
               D_error_type = "stdev",
@@
 
+# column index table for incidence ratings
 # Calculate incidence
@@
 for (i in seq_along(incidence4)) {
+
    # incidence = 1
@@
               grain_yield.t.ha. = as.numeric(Millm_13$`kg/Ha`)/1000,
-              #AUDPC = apply(Millm_13[,c("Inc_23D","Inc_42D")]-1,1, FUN = audpc, dates = c(23,42)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
               stringsAsFactors = FALSE)
@@
              rating_scale = unique(rating_scale),
-             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+             disease_error = sd(PM_final_severity, na.rm = TRUE), # Createds NAs and need repeating below
              D_error_type = "stdev",
@@
       detectDates = TRUE
-   )[1:31, 1:9]
+   )[1:30, 1:9]
 
@@
       colNames = TRUE
-   )[1:31, 1:8]
+   )[1:30, 1:8]
 
@@
 # Rename the plot column and remove lines without data
-colnames(Herm_15)[3] <- "Plot"
+colnames(Herm_15[,"Plot.#"]) <- "Plot"
 Herm_15.DR <- Herm_15.DR[!is.na(Herm_15.DR$Treatment),]

### 2020-05-26 04_MetaAnalysis.Rmd
Improve clarity of message statement

@@
          paste(
-            "\nWarning!!: Imputed yield errors show significant differences when they should not, imputation will automatically rerun - iteration",
+            "\nWarning!!: Imputed yield errors bestow significant differences on the means.\n",
+            "The orignal experiment reported no significant differances in the yields, therefore values will be discarded and the imputation function run again - iteration number:",
             "i =",

### 2020-05-26 04_MetaAnalysis.Rmd
spelling
Fixed on my ipad

--- 2020-05-22 04_MetaAnalysis.Rmd
@@
          paste(
-            "\nWarning!!: Imputed yield errors show significant differences when they should not, imputation will automatically rerun - iteration",
+            "\nWarning!!: Imputed yield errors bestow significant differences on the means.\n",
+            "The original experiment reported no significant differences in the yields, therefore values will be discarded and the imputation function run again - iteration number:",
             "i =",

### 2020-05-26 04_MetaAnalysis.Rmd
Move impute yield error to function to reduce code in metaAnalysis Rmd

--- 2020-05-22 04_MetaAnalysis.Rmd
@@
 ```{r imputing_variances}
-# generate yield error values
-for (i in 0:500) {
-   # Imputing missing log variances
-   log_Yerror <- rnorm(
-      n = sum(is.na(slimmer_PM_dat$yield_error)),
-      mean = mean(log(slimmer_PM_dat$yield_error), na.rm = TRUE),
-      sd = sd(log(slimmer_PM_dat$yield_error), na.rm = TRUE)
-   )
+source("./R/impute_yield_err.R")
 
-   # First let's convert Variance to standard error for all the variables that have variance recorded
-   slimmer_PM_dat$yield_SE <-
-      sqrt(slimmer_PM_dat$yield_error) / sqrt(slimmer_PM_dat$n)
+imputed_error_list <- impute_yield_err(slimmer_PM_dat, "grain_yield.t.ha", "yield_error","n")
 
-   # Second; adding the imputed standard errors
-   slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"] <-
-      sqrt(exp(log_Yerror)) / sqrt(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "n"])
+slimmer_PM_dat <- imputed_error_list[["new_dataFrame"]]
 
-   # all errorbars should overlap so they are consistant with the meta-data describing no significant difference bettween treatments
-   # let's test to make sure
-   if (max(outer(
-      X = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] -
-      (2 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
-      Y = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] +
-      (2 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
-      FUN = "-"
-   )) > 0) {
-      message(
-         paste(
-            "\nWarning!!: Imputed yield errors show significant differences when they should not, imputation will automatically rerun - iteration",
-            "i =",
-            i
-         )
-      )
-      next()
-   } else{
-      message(
-         paste(
-            i,
-            "iterations: ",
-            "imputed variances now show no significant distances :)\n Now adding variances to data "
-         )
-      )
-
-      # Plot the imputed errors for each trial
-      Vplot <-
-         slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), ] %>%
-         ggplot(aes(y = grain_yield.t.ha, trial)) +
-         #geom_point()+
-         geom_pointrange(
-            ymin = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] -
-               (1.95 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
-            ymax = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] +
-               (1.95 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
-            position = "jitter"
-         ) +
-         ylim(0.2, 1.5)
-
-      slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_error"] <-
-         exp(log_Yerror)
-      print(Vplot)
-      break()
-   }
-}
 ```

### 2020-05-26 R/impute_yield_err.R

@@ -1,0 +1,75 @@
+impute_yield_err <- function(dat,xbar, Var,reps){
+# dat is the whole dataframe containing all the values
+# xbar  (character class) is column name of the means of the variable that needs imputation
+# Var (character class)is the repective column name of the Variance of the variable that needs imputation
+   
+   
+# generate yield error values
+for (i in 0:500) {
+   # Imputing missing log variances
+   log_Yerror <- rnorm(
+      n = sum(is.na(dat[,Var])),
+      mean = mean(log(dat[,Var]), na.rm = TRUE),
+      sd = sd(log(dat[,Var]), na.rm = TRUE)
+   )
+   
+   # First let's convert Variance to standard error for all the variables that have variance recorded
+   dat$yield_SE <-
+      sqrt(dat[,Var]) / sqrt(dat[,reps])
+   
+   
+   # Second; adding the imputed standard errors
+   dat[is.na(dat[,Var]), "yield_SE"] <-
+      sqrt(exp(log_Yerror)) / sqrt(dat[is.na(dat[,Var]), reps])
+   
+   # all errorbars should overlap so they are consistant with the meta-data describing no significant difference bettween treatments
+   # let's test to make sure
+   if (max(outer(
+      X = dat[is.na(dat[,Var]), xbar] -
+      (2 * dat[is.na(dat[,Var]), "yield_SE"]),
+      Y = dat[is.na(dat[,Var]), xbar] +
+      (2 * dat[is.na(dat[,Var]), "yield_SE"]),
+      FUN = "-"
+   )) > 0) {
+      message(
+         paste(
+            "\nWarning!!: Imputed yield errors bestow significant differences on the means.\n",
+            "The original experiment reported no significant differences in the yields, therefore values will be discarded and the imputation function run again - iteration number:",
+            "i =",
+            i
+         )
+      )
+      next()
+   } else{
+      message(
+         paste(
+            i,
+            "iterations: ",
+            "imputed variances now show no significant distances :)\n Now adding variances to data "
+         )
+      )
+      
+      # Plot the imputed errors for each trial
+      # Plot will not work without the dataset it was designed for.
+      Vplot <-
+         dat[is.na(dat[,Var]), ] %>%
+         ggplot(aes(y = grain_yield.t.ha, trial)) +
+         geom_pointrange(
[…]

### 2020-05-27 04_MetaAnalysis.Rmd
formating, description and MSE imputation description

@@
 
-imputed_error_list <- impute_yield_err(slimmer_PM_dat, "grain_yield.t.ha", "yield_error","n")
+imputed_error_list <- impute_yield_err(dat = slimmer_PM_dat, 
+                                       xbar = "grain_yield.t.ha", 
+                                       Var = "yield_error",
+                                       reps = "n")
 
@@
 This is unexpected and reflects the inherent variability of the data.
-Therefore we will calculate the trial mean squares and use this to calculate the variance for each sample.
+Therefore we will equalise the variance by using the trial mean squares and use this to calculate the variance for each sample.
 
@@
 TrialMSQ <- slimmer_PM_dat %>%
-   group_by(trial_ref)%>%
+   group_by(trial_ref,location,year)%>%
    summarise(unique(Y_Msquare))
 
-TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), "trial_ref"]
+TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), c("trial_ref", "location","year")]
 ```

### 2020-05-27 04_MetaAnalysis.Rmd
Correct treatment means plot Move library(metafor) to pacman at the top of the document

@@
    install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer, netmeta)
+pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer,metafor, netmeta)
 
@@
 ```{r treatment_means_plot}
+# class spray_managment as a factor and reorder them for the plot
 slimmer_PM_dat$spray_management <-
    factor(slimmer_PM_dat$spray_management,
-          levels(slimmer_PM_dat$spray_management)[rev(c(1, 2, 4, 5, 3))])
+          levels(factor(slimmer_PM_dat$spray_management))[rev(c(1, 2, 4, 5, 3))])
 
@@
 ```{r table_of_nTreatments}
-kableExtra::kable(table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year),
-                  align = rep('c', 8)) %>%  #commented as was redering empty, needs a look in
+kable(table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year),
+                  align = rep('c', 8),
+      caption = "Which treatments and how many treatments are represented in each year") %>%  
    kable_styling(
@@
         y = "Grain yield (t/Ha)",
-        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
+        title = "Mean grain yield difference to the control for each treatment \n categorised by spray management scenario") +
    theme(plot.title = element_text(hjust = 0.5)) +
@@
 ```{r metafor_organisation}
-library(metafor)
 slimmer_PM_dat$spray_management <-

### 2020-05-27 04_MetaAnalysis.Rmd
Remove code chunk. Not in line with investigations
description and comments. Need to followup the forrest plotting error in chunk - line 357

@@
 
-```{r Metafor-analysis}
-PM_mv_AI <- rma.mv(
-   yi,
-   vi,
-   mods = ~ slimmer_PM_dat$spray_management + slimmer_PM_dat$row_spacing + slimmer_PM_dat$host_genotype,
-   method = "ML",
-   random = list(~ spray_management | trial_ref),
-   struct = "UN",
-   data = slimmer_PM_dat
-)
+The first table in this output shows the tau^2 (variance) of each random effects and the number of occurances for each treatment in the analysis.
+The second table is in two parts(left and right).
+The left part indicates the level of acceptable rho (variation) when comparing treatments.
+All comparisons were acceptable except for a comparison between `Early` and `Late_plus`, `0.000` rho.
+`Early` and `Late_plus` treatments never occured within the same trial which is indicated by the right side of the table.
 
-summary(PM_mv_AI)
-
-```
-
-Results show that yields in single early spray treatments are not significantly different to the no spray control.
-Commencing spray management schedules at first sign of disease (Recommended), or between 7 - 19 days after first sign (late) produced significantly higher yields compared to the no spray control.
-On average a spray schedule with two or more applications stating late (7-19 days after first sign of powdery mildew) produced the highest yields.
+The fixed effects, in the last table, showed that yields in single early spray treatments are not significantly different to the no spray control. 
+Also commencing spray management schedules at first sign of disease (Recommended), or between 7 - 19 days after first sign (late) produced significantly higher yields compared to the no spray control.
+On average a spray schedule with two or more applications stating late (7 - 19 days after first sign of powdery mildew) produced the highest yields.
 
 When we compare these results to those of the linear mixed effect model there is little difference in the outcome.
-The most notable difference is the linear mixed-effect model is somewhat less certain about the `Late_plus` treatment, and the mean yield lower than the `recommended_plus` treatment.
 
@@
 
-*****s
+*****
 
@@
    c(0, 0, -1, 1, 0),
-   # Recommended vs recommended_plus
+   # Recommended plus vs recommended
    c(0, 0, -1, 0, 1),
-   # Recommended vs Late_Plus
+   # Late_Plus vs Recommended
    c(0, 0, 0, -1, 1)
-)) # recommended_plus vs Late_plus
+)) # Late_plus vs Recommended plus
 ```
 Results show with the exclusion of the no spray control, none of the treatments are significantly different, however, early applications treatments on average produced lower yields.
-Let's view this on a plot.
+Also the model was almost significant when assessing recommended_plus as saving more yield than recommended.
+This is probably due to the fact there were more comparisons between these two treatments which allowed a more certain outcome.
+Let's view these comparisons in a plot.
 
+First we will format the results into a dataframe and back-transform the log values by using the exponent function
 ```{r metafor_results}
@@
 
-treat <-
-   c("control",
-     "Early",
-     "Recommended",
-     "Recommended_plus",
-     "Late_plus")
 efficacy <- tbl_df(results_AI)
-efficacy$treat <- treat
-efficacy$se <- PM_mv_AI$se
-colnames(efficacy) <-
-   c("Mean", "CIs_lower", "CI_upper", "Treatment", "SE")
-efficacy
-```
-
-```{r metafor_plot}
 efficacy$Treatment <-
    factor(
-      efficacy$Treatment,
       c(
@@
 
+efficacy$se <- PM_mv_AI$se
+colnames(efficacy) <-
+   c("Mean", "CIs_lower", "CI_upper", "Treatment", "SE")
+efficacy
+```
+
+```{r metafor_plot}
 efficacy %>%
@@
 However it could also be because it also has a low number of pooled reps per trial.
-Let's look at how well each of the treatments compare to each other.
+Let's look at how well each of the number treatments compare to each other.
 We can use the netmeta package to give a graphical representation of this.
@@
 ```{r netmeta-forest}
+# I don't know why this is not working I will need to follow up on this
 forest(

### 2020-05-29 04_MetaAnalysis.Rmd
Variation in grain.yield metafor outcome. Trying numerous iterations and Plotting them

@@
 # Data
-slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv"
-)
+slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv")
 ```
@@
 
-The first table in this output shows the tau^2 (variance) of each random effects and the number of occurances for each treatment in the analysis.
+```{r ReRunMetafor}
+dat1 <- data.frame(
+   iteration = 0,
+   mods = names(coef(PM_mv_AI)),
+   coefs = coef(PM_mv_AI),
+   se = PM_mv_AI$se,
+   zval = PM_mv_AI$zval,
+   pval = PM_mv_AI$pval,
+   ci.lb = PM_mv_AI$ci.lb,
+   ci.ub = PM_mv_AI$ci.ub,
+   row.names = NULL
+   )
+
+# Each time below is run dat1 will add the extra iterations to the bottom of dat1
+
+for(i2 in (max(dat1$iteration) +1):(max(dat1$iteration) +3)){
+   # Read in data again
+slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv")
+
+# Identify trials without variance
+TrialMSQ <- slimmer_PM_dat %>%
+   group_by(trial_ref,location,year)%>%
+   summarise(unique(Y_Msquare))
+
+# impute variance
+for (i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), ]$trial_ref) {
+   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "Y_Msquare"] <-
+      exp(rnorm(
+         n = 1,
+         mean = mean(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE),
+         sd(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE)
+      ))
+}
+
+#######
+
+#reformat data
+slimmer_PM_dat$yi <- log(slimmer_PM_dat$grain_yield.t.ha)
+slimmer_PM_dat$vi <-
+   slimmer_PM_dat$Y_Msquare / (slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha ^
+                                  2)
+
+slimmer_PM_dat$spray_management <-
+   factor(slimmer_PM_dat$spray_management)
+slimmer_PM_dat$trial_ref <- factor(slimmer_PM_dat$trial_ref)
+slimmer_PM_dat$trial <- factor(slimmer_PM_dat$trial)
+
+# Run meta-analysis
+PM_mv_AI <- rma.mv(
+   yi,
+   vi,
+   mods = ~ spray_management,
+   method = "ML",
+   random = list(~ spray_management | trial),
+   struct = "UN",
+   data = slimmer_PM_dat
+)
+
+dat2 <- data.frame(
+   iteration = i2,
+   mods = names(coef(PM_mv_AI)),
+   coefs = coef(PM_mv_AI),
+   se = PM_mv_AI$se,
+   zval = PM_mv_AI$zval,
+   pval = PM_mv_AI$pval,
+   ci.lb = PM_mv_AI$ci.lb,
+   ci.ub = PM_mv_AI$ci.ub,
+   row.names = NULL
+   )
+
+dat1 <- rbind(dat1,dat2)
+}
+dat1
+
+```
+```{r}
+dat1 %>%
+   ggplot(aes(x = iteration ,y = coefs,))+
+   geom_ribbon(aes(ymax = ci.ub, ymin = ci.lb, x = iteration), fill = "grey70")+
+   geom_line()+
+   facet_grid(cols = vars(mods))
+
+```
+
+The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis.
 The second table is in two parts(left and right).
@@
 
-First we will format the results into a dataframe and back-transform the log values by using the exponent function
+First we will format the results into a data frame and back-transform the log values by using the exponent function
 ```{r metafor_results}

### 2020-05-29 04_MetaAnalysis.Rmd
added pval plot

@@
 ```
-```{r}
+```{r coef_iteration}
 dat1 %>%
@@
    geom_line()+
+   facet_grid(cols = vars(mods))
+
+```
+
+```{r pval_iteration}
+dat1 %>%
+   ggplot(aes(x = iteration ,y = pval,))+
+   geom_line()+
+   geom_hline(yintercept = 0.05, colour = "grey50", linetype = 2)+
    facet_grid(cols = vars(mods))

### 2020-05-29 04_MetaAnalysis.Rmd
metafor iterations changed to run as a job script

--- 2020-05-27 04_MetaAnalysis.Rmd
@@
 
-The first table in this output shows the tau^2 (variance) of each random effects and the number of occurances for each treatment in the analysis.
+```{r Initiak_ReRunMetafor}
+dat1 <- data.frame(
+   iteration = 0,
+   mods = names(coef(PM_mv_AI)),
+   coefs = coef(PM_mv_AI),
+   se = PM_mv_AI$se,
+   zval = PM_mv_AI$zval,
+   pval = PM_mv_AI$pval,
+   ci.lb = PM_mv_AI$ci.lb,
+   ci.ub = PM_mv_AI$ci.ub,
+   row.names = NULL
+   )
+
+write.csv(dat1, "./cache/metaIteration.csv", row.names = FALSE)
+```
+
+```{r run_iterations_asJobscript}
+# WARNING don't run a high number of iterations without increasing sys.sleep
+# sys.sleep should not be reduced below 4 for 50 iterations and
+# below 0.5 for 10 iterations
+for(ITERATE in 1:10){
+rstudioapi::jobRunScript(
+  "./R/ReRun_metafor-grainyield.R",
+  workingDir = here::here(),
+  name = "metafor_iteration",
+)
+   Sys.sleep(1)
+}
+```
+
+```{r coef_iteration}
+dat1 <- read.csv("./cache/metaIteration.csv")
+table(dat1$iteration)
+dat1 %>%
+   ggplot(aes(x = iteration ,y = coefs,))+
+   geom_ribbon(aes(ymax = ci.ub, ymin = ci.lb, x = iteration), fill = "grey70")+
+   geom_line()+
+   facet_grid(cols = vars(mods))
+
+```
+
+```{r pval_iteration_plot}
+dat1 %>%
+   ggplot(aes(x = iteration ,y = pval,))+
+   geom_line()+
+   geom_hline(yintercept = 0.05, colour = "grey50", linetype = 2)+
+   facet_grid(cols = vars(mods))
+
+```
+
+The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis.
 The second table is in two parts(left and right).

### 2020-05-29 R/ReRun_metafor-grainyield.R

@@ -1,0 +1,77 @@
+# read in data
+library(metafor)
+library(dplyr)
+
+
+slimmer_PM_dat <- read.csv("./cache/slimmer_PM_clusterdat.csv")
+dat1 <- read.csv("./cache/metaIteration.csv")
+
+i2 <- max(dat1$iteration)
+
+# Identify trials without variance
+   TrialMSQ <- slimmer_PM_dat %>%
+      group_by(trial_ref,location,year)%>%
+      summarise(unique(Y_Msquare))
+   
+   # impute variance
+   for (i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), ]$trial_ref) {
+      slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "Y_Msquare"] <-
+         exp(rnorm(
+            n = 1,
+            mean = mean(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE),
+            sd(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE)
+         ))
+   }
+   
+   #######
+   
+   #reformat data
+   slimmer_PM_dat$yi <- log(slimmer_PM_dat$grain_yield.t.ha)
+   slimmer_PM_dat$vi <-
+      slimmer_PM_dat$Y_Msquare / (slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha ^
+                                     2)
+   
+   slimmer_PM_dat$spray_management <-
+      factor(slimmer_PM_dat$spray_management)
+   slimmer_PM_dat$trial_ref <- factor(slimmer_PM_dat$trial_ref)
+   slimmer_PM_dat$trial <- factor(slimmer_PM_dat$trial)
+   
+   
+   # Run meta-analysis
+   PM_mv_AI <- rma.mv(
+      yi,
+      vi,
+      mods = ~ spray_management,
+      method = "ML",
+      random = list(~ spray_management | trial),
+      struct = "UN",
+      data = slimmer_PM_dat
+   )
+   
+   dat2 <- data.frame(
+      iteration = i2+1,
+      mods = names(coef(PM_mv_AI)),
+      coefs = coef(PM_mv_AI),
+      se = PM_mv_AI$se,
+      zval = PM_mv_AI$zval,
+      pval = PM_mv_AI$pval,
+      ci.lb = PM_mv_AI$ci.lb,
+      ci.ub = PM_mv_AI$ci.ub,
+      row.names = NULL
+   )
+   
+   
[…]

### 2020-06-02 04_MetaAnalysis.Rmd
Remove MSE imputation Slice out trials with no variation formatting and spelling edits Change a few chunks so they are not evaulated Use labbeller function to rename facets in plots

@@
 
-```{r imputation_MSE}
+```{r imputation_MSE, eval=FALSE, include=FALSE}
 for (i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), ]$trial_ref) {
@@
 
+The use of these imputed MSE was giving a varied outcome each time it was run. We the next code chunk removes the studies without variation to observe what the meta-analysis outcome would be.
+
+```{r remove_NA_MSE}
+slimmer_PM_dat <- 
+   slimmer_PM_dat[!is.na(slimmer_PM_dat$Y_Msquare),]
+
+```
+
 Before analysis let's have a look at the trimmed down modified data.
@@
 ```{r treatment_means_plot}
-# class spray_managment as a factor and reorder them for the plot
+# class spray_management as a factor and reorder them for the plot
 slimmer_PM_dat$spray_management <-
@@
 ### metafor package  
-Let's load the metafor package we are using to analyse the data, then rearrange the factors we want to examine by placing the control treatment first.
+Let's load the `metafor` package we are using to analyse the data, then rearrange the factors we want to examine by placing the control treatment first.
 This way all treatments will be compared to the no spray controls.
@@
 
-```{r Initiak_ReRunMetafor}
+```{r Initiak_ReRunMetafor, eval=FALSE, include=FALSE}
 dat1 <- data.frame(
@@
 
-write.csv(dat1, "./cache/metaIteration.csv", row.names = FALSE)
+# commented the code below so the file does not get overwritten
+#write.csv(dat1, "./cache/metaIteration.csv", row.names = FALSE)
 ```
 
-```{r run_iterations_asJobscript}
+```{r run_iterations_asJobscript, eval=FALSE, include=FALSE}
 # WARNING don't run a high number of iterations without increasing sys.sleep
@@
 ```{r coef_iteration}
+change_labels <- function(x1){
+   x1 <- gsub(pattern = "spray_management",replacement = "",x = x1)
+   x1 <- gsub(pattern = "_",replacement = "\n",x = x1)
+   x1
+}
+
 dat1 <- read.csv("./cache/metaIteration.csv")
-table(dat1$iteration)
 dat1 %>%
@@
    geom_line()+
-   facet_grid(cols = vars(mods))
+   facet_grid(cols = vars(mods), labeller = labeller(mods = change_labels))+
+   theme(strip.text.x = element_text(size = 9))
 
@@
    geom_line()+
+   scale_y_log10()+
    geom_hline(yintercept = 0.05, colour = "grey50", linetype = 2)+
-   facet_grid(cols = vars(mods))
+   facet_grid(cols = vars(mods), labeller = labeller(mods = change_labels))+
+   theme(strip.text.x = element_text(size = 9))
 
+temp_labels(dat1)
+labeller()
 ```
@@
 All comparisons were acceptable except for a comparison between `Early` and `Late_plus`, `0.000` rho.
-`Early` and `Late_plus` treatments never occured within the same trial which is indicated by the right side of the table.
+`Early` and `Late_plus` treatments never occurred within the same trial which is indicated by the right side of the table.
 
@@
    c(0, 1, -1, 0, 0),
-   # early vs Recomended
+   # early vs Recommended
    c(0, 1, 0, -1, 0),

### 2020-06-03 04_MetaAnalysis.Rmd
More code descriptions and description of hetrogeneity in the model

@@
 )
+```
+
+#### Investigate impact of imputing Mean square errors on the meta-analysis outcomes
+
+```{r Initiak_ReRunMetafor, eval=FALSE, include=FALSE}
+# It was noticed that the meta analysis was giving different outcomes.
+#     (not just small variations in estimates and p-values, but large variations)
+# The following chunks investigate how much these values vary and change the outcomes
+#
+# This chunk creates a data.frame from the meta-analysis which was run in the previous chunk `Metafor-analysis`
+# and sets the iteration number as 0
+# this data.frame is appended with additional iterations to in the following chunk
 
 summary(PM_mv_AI)
-```
 
-```{r Initiak_ReRunMetafor, eval=FALSE, include=FALSE}
 dat1 <- data.frame(
@@
 ```{r run_iterations_asJobscript, eval=FALSE, include=FALSE}
+# This chunk iterates the imputation of MSEs and reruns the metafor analysis
+# each time it iterates it appends some of the output information into the "metaIteration.csv" file
+# To increase the speed the calculations/iterations it is send to multiple jobs in the background.
+#
 # WARNING don't run a high number of iterations without increasing sys.sleep
@@
 # below 0.5 for 10 iterations
-for(ITERATE in 1:10){
+for (ITERATE in 1:10) {
    rstudioapi::jobRunScript(
@@
 
-```{r coef_iteration}
+```{r coef_iteration, eval=FALSE, include=FALSE}
+# This chunk plots the coefficients and corresponding confidence intervals 
+#     for each iteration of the metafor calculation to visualise how much variation 
+#     the imputed MSE imbue on the moderator coefs
+
+# This function alters the moderator names so they are plotted legibly in the facet strips
 change_labels <- function(x1){
@@
 
-dat1 <- read.csv("./cache/metaIteration.csv")
-dat1 %>%
+metaI <- read.csv("./cache/metaIteration.csv")
+metaI %>%
    ggplot(aes(x = iteration ,y = coefs,))+
@@
    facet_grid(cols = vars(mods), labeller = labeller(mods = change_labels))+
-   theme(strip.text.x = element_text(size = 9))
+   theme(strip.text.x = element_text(size = 9)) # change facet strip label font size
 
@@
 ```{r pval_iteration_plot}
-dat1 %>%
-   ggplot(aes(x = iteration ,y = pval,))+
-   geom_line()+
-   scale_y_log10()+
-   geom_hline(yintercept = 0.05, colour = "grey50", linetype = 2)+
-   facet_grid(cols = vars(mods), labeller = labeller(mods = change_labels))+
-   theme(strip.text.x = element_text(size = 9))
+# Plot the p - values of the spray_management moderators
+# transform y axis on log scale
+metaI %>%
+   ggplot(aes(x = iteration , y = pval, )) +
+   geom_line() +
+   scale_y_log10() +
+   geom_hline(
+      yintercept = c(0.05, 0.001),
+      colour = "grey50",
+      linetype = 2
+   ) +
+   facet_grid(cols = vars(mods),
+              labeller = labeller(mods = change_labels)) +
+   theme(strip.text.x = element_text(size = 9)) +
+   geom_text(
+      aes(
+         y = 0.05,
+         x = 1,
+         label = c("P = 0.05")
+      ),
+      size = 3,
+      colour = "grey50",
+      hjust = 0,
+      vjust = -0.5
+   )+
+      geom_text(
+      aes(
+         y = 0.001,
+         x = 1,
+         label = c("P = 0.001")
+      ),
+      size = 3,
+      colour = "grey50",
+      hjust = 0,
+      vjust = -0.5
+   )
 
-temp_labels(dat1)
-labeller()
 ```
+
+```{r metafor_summary}
+summary(PM_mv_AI)
+rstudent.rma.mv(PM_mv_AI)
+# confint(PM_mv_AI) Can't finish running
+```
+
+According to the results of the omnibus test ($Q_M = 10.65, df = 4, p = 0.0308$) we can reject the null hypothesis $H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$ that the tested spray management schedules have no benefit to protecting mungbean yields[@Viechtbauer2010].
+However Late plus ($\beta_4$) was the only moderator showing a significant effect on yields ($z = 3.2276; p = 0.0012$). 
+The analysis shows there is still a considerable amount of residual heterogeneity ($Q_E = 5096.04, df = 125, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
 

### 2020-06-04 04_MetaAnalysis.Rmd
Don't evaluate pval_iteration chunk

@@
 
-```{r pval_iteration_plot}
+```{r pval_iteration_plot, eval=FALSE, include=FALSE}
 # Plot the p - values of the spray_management moderators
@@
 summary(PM_mv_AI)
-rstudent.rma.mv(PM_mv_AI)
-# confint(PM_mv_AI) Can't finish running
 ```

### 2020-06-04 index.Rmd
Simplify index page to table of contents

--- 2020-01-28 index.Rmd
@@
 ---
+# Home
 
-# Research questions
+This compendium details the statistical analysis and methods while undertaking a meta-analysis of fungicide efficacy trials for control of powdery mildew in mungbean. 
+This meta-analysis will focus on the main aim of:
 
-+ When is the optimum time to spray fungicide to limit the impact of powdery mildew on mungbean yields?
+> When is the optimum time to spray fungicide to limit the impact of powdery mildew on mungbean yields?
 
-+ How has the first sign of powdery mildew changed over the seasons and between experimental sites?
+## Contents
+This compendia is broken down into seven sections:
 
-+ Is there an ideal planting time, or fungicide management strategy, which could make use of powdery mildew defoliation during pod maturation resulting in an increased yield?
+   1. [Details of the experiments which were included in the analysis][Studies considered in meta-analysis].  
+   2. [Preliminary data exploration which investigates possible variables that could influence the meta-analysis.][Preliminary Analysis]  
+      a. [Fungicides][Fungicides]  
+      b. [Mungbean cultivar][Mungbean cultivars]  
+      c. [Row spacing][Row spacing]  
+      d. [Rainfall][Yield vs in-season rain]  
+      e. [When conditions become suitable for powdery mildew infection][Season range and first incidence]  
+   3. [Preparation of data for the meta-analysis][Prepare data for meta-analysis]  
+   4. [Meta-analysis of the effect of fungicide spray scheduale on yield loss][Meta-analysis]  
+   5. [Meta-analysis of the effect of fungicide spray scheduale on disease severity and yield loss][AUPDC meta-analysis]
+   6. [Manuscript Wireframe][Manuscript wire frame]
+   7. [Manuscript: A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew.][Manuscript]
+
+## Other research questions which are not the focus of this study
++ How has the first sign of powdery mildew changed over the seasons and between
+experimental sites?
+
++ Is there an ideal planting time, or fungicide management strategy, which could
+make use of powdery mildew defoliation during pod maturation resulting in an
+increased yield?
 
@@
 + What is the length of a mungbean season and how has it varied in this trial?
-   - This data has not been collected or is not accurate enough to be useful to answer this question.
 
-## Parts of analysis that need checking
+   - This data has not been collected or is not accurate enough to be useful to
+   answer this question.
+
+## Possible sources of variation in this analysis.
 
 + Variability among host genotypes.  
-   + The probable influence of season might be influenced by host genotype. This is because newer varieties were adopted into experimental trials as they were released.  
-   + Between 2001 and 2015 mungbean genotype changed from Green Diamond, Berken, Crystal to Jade. Jade was the only cultivar used between 2015 and 2019.
+   + The probable influence of season might be influenced by host genotype. This
+   is because newer varieties were adopted into experimental trials as they were
+   released.
 
-+ Estimations of plant maturity stages over each growing season. These estimations might able to be computed using APSIM.
+   + Between 2001 and 2015 mungbean genotype changed from Green Diamond, Berken,
+   Crystal to Jade. Jade was the only cultivar used between 2015 and 2019.
+
+   + Estimations of plant maturity stages over each growing season. These
+   estimations might able to be computed using APSIM.

### 2020-06-04 01_Meta-analysis_experiments.Rmd
Clarification and editing

@@
 Queensland.
-It is worth noting Professor Malcolm Riley's and Dr Sue Thompson's effort in establishing and coordinating early field trials between 2010 and 2016.
+It is worth noting in particular Professor Malcolm Riley's and Dr Sue Thompson's effort in establishing and coordinating early field trials between 2010 and 2016.
 
@@
 
-**2001 - 2004 trials**  
-Trial data were obtained from a non-published manuscript.  
-Ratings for powdery mildew were on a 1-5 rating scale where 1 = no sign of disease, 2 = 1-30% diseased leaf area, 3 = 31-65% diseased leaf area, 4 = 66-99% diseased leaf area and 5 = complete defoliation.
-Comparing trials which have not used the same rating scale will be done using a
-percentage change.
-
-**2013 Field trials**  
-Trials were conducted by the [Northern Growers Alliance (NGA)](https://www.nga.org.au/).
-The raw data were obtained from Lawrie Price.
-NGA data were formatted to be compliant with existing data rating and scales using the R script [`R/Cleaning historical data.R`](https://github.com/openplantpathology/Mungbean_PM/blob/master/R/Cleaning%20historical%20data.R).
-
-## Summary of data
+## Summary of trials
 
@@
       summarise(
-         year = unique(year),
-         location = unique(location),
-         replicates_per_treatment = if(is.whole(mean(replicates))){
+         Year = unique(year),
+         Location = unique(location),
+         `Replicates per treatment` = if(is.whole(mean(replicates))){
             as.character(mean(replicates))}else{
                as.character(paste(min(replicates),"-",max(replicates)))},
-         planting_date = unique(planting_date),
-         first_sign_disease = unique(first_sign_disease),
-         treatments = length(n_treatment)
+         `Planting date` = unique(planting_date),
+         `First sign of disease` = unique(first_sign_disease),
+         `Fungicide treatments` = length(n_treatment),
       ) %>%
-      arrange(year)%>%
+      arrange(Year)%>%
       select(-trial_ref),
-   caption = "Description of Experiments"
+   caption = "Description of Experiments",
+   align = "c",
+   col.names = c("Year", "Location", "Replicates\nper treatments",
+                 "Planting date", "First sign\nof disease", "Fungicide\n treatments")
 )  %>%
    kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
+   column_spec(c(3,5:6), width = "3cm") %>% 
    scroll_box(width = "900px", height = "500px")
 
+kable()
 ```
 
-## Powdery mildew ratings
+## Powdery mildew rating scales
+
+**2001 - 2004 trials**  
+Trial data were obtained from a non-published manuscript.  
+Ratings for powdery mildew were on a 1-5 rating scale where 1 = no sign of disease, 2 = 1-30% diseased leaf area, 3 = 31-65% diseased leaf area, 4 = 66-99% diseased leaf area and 5 = complete defoliation.
+Comparing these trials which have not used the 1-9 rating scale will be converted using a
+percentage change.
+
+**2013 Field trials**  
+Trials from 2013 were all conducted by the [Northern Growers Alliance (NGA)](https://www.nga.org.au/).
+The raw data were obtained from Lawrie Price.
+NGA data were formatted to be compliant with the 1 - 9 rating scale used in all other experiments.
+Detailed code for the conversion can be found in the following vignette [191115_PMMB_DataWrangling_PM.Rmd](./vignette/191115_PMMB_DataWrangling_PM.Rmd).
+
+### 1 - 9 Powdery mildew rating scale
 
@@
 
-The following map displays experiment locations where data was sufficient to include in this meta-analysis.
+The following map displays experiment locations which were considered for inclusion in this meta-analysis.
 

### 2020-06-04 R/Cleaning historical data.R
Code moved into vignette DataWrangle

@@ -1,1689 +1,0 @@
-# This script is dedicated to
-# importing and cleaning previous powdery mildew experimental field trial data.
-
-
-
-# Year #  Trial location  #  Sowing date
-
-# ____________________________________________________________
-# _____________            Hermitage  2010        ____________
-
-Herm_10 <-
-   as.data.frame(read_xls(
-      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2010/2010 PMmung Herm/2010 PMmung hermitage RAW field book.xls",
-      sheet = "For analysis"
-   ), stringsAsFactors == FALSE)
-
-Herm_10[1:20,]
-
-
-
-Herm_10_m <- Herm_10 %>%
-   group_by(`Cultivar!`, `Treat!`, `Description!`) %>%
-   summarise_all(list(~ mean(., na.rm = TRUE),  ~ sd(., na.rm = TRUE)))
-
-head(Herm_10_m)
-colnames((Herm_10_m))
-
-write.csv(
-   as.data.frame(Herm_10_m),
-   "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/2010 PMmung Hermitage means.csv"
-)
-
-
-# ____________________________________________________________
-# _____________            Hermitage  2011        ____________
-
-Herm_11 <-
-   read_xls(
-      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2011/2011 PMmung Herm/pmhermratings2011.xls",
-      sheet = "Analyses factor"
-   )
-
-
-new_cols <- as.data.table(tstrsplit(Herm_11$'Treatment!', " "))
-colnames(new_cols) <- c("spray_n", "spray", "fungicide")
-Herm_11 <-
-   cbind(new_cols, as.data.table(Herm_11)[, 'Treatment!' := NULL])
-#Herm_11$`Yld Kg ha` <- as.numeric(Herm_11$`Yld Kg ha`)
-head(Herm_11)
-
-Herm_11_m <- Herm_11 %>%
-   group_by(`Cultivar!`, `fungicide`, `spray_n`) %>%
[…]

### 2020-06-04 02_Preliminary_analysis.Rmd
Edits and clarification

@@
 library(theme.usq)
-#source("./getPPD2.R")
 theme_set(theme_usq())
@@
 ## Explore and Visualise Data
-
+First lets import the data. Each row provides the mean yield for each experimental treatment.
 ```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
 # Import data
-PM_MB_means <- import_data() # link expires 2021-12-01
-
-#remove the variation in different sulphur formulations
-unique(PM_MB_means[
-   grep("sulphur",PM_MB_means$fungicide_ai),
-   "fungicide_ai"])
-PM_MB_means[grep("sulphur",PM_MB_means$fungicide_ai),"fungicide_ai"] <- "sulphur"
-
+PM_MB_means <- import_data() 
 ```
 
-Various factors have been studied in the previous experiments which may influence the following results.
-However, unless stated, the following plots and analyses were made disregarding effects from other factors not mentioned.
+The data explored in the `PM_MB_means` data frame is a list of mean values from each treatment in each respective experiment.
+These preliminary analyses will focus on the change in mungbean yields which is attributable to the fungicide treatment. 
+Later in this document we will also consider the impact of fungicide treatments on disease incidence/severity. 
+Mean powdery mildew incidence was recorded at the end of each growing season. 
+Some experiments recorded disease incidence throughout the season and these were summarised with AUDPC. 
+AUDPC for trials which only provided final powdery mildew incidence was calculated using the record of 'first sign of disease' and final assessment. 
+More details on how the `PM_MB_means` data was compiled can be found in the ['Data wrangle vingette'][./vignette/191115_PMMB_DataWrangling_PM.Rmd]
+
+Various factors have been studied in the previous experiments which may influence the subsequent meta-analysis.
+On this page, unless stated, the following plots and analyses were made disregarding effects the following factors which have the potential to influence mungbean grain yield and/or powdery mildew mean plot severity.
 
@@
 
-All data explored below are a list of mean values from each treatment applied in each experiment.
-Some experiments have in-season observations of disease incidence and severity.
-However, here we have summarised the data to show only the end of season observations.
-
 ### Fungicides
@@
 #### Fungicide type
+
+First lets standardise the sulphur treatments. Some early experiments tested different formulations. There was no difference in the sulphur formulations so we will refer to all of them as "sulphur".
+
+```{r sulphur_simplify}
+# Remove the variation in different sulphur formulations
+unique(PM_MB_means[grep("sulphur", PM_MB_means$fungicide_ai),
+                   "fungicide_ai"])
+PM_MB_means[grep("sulphur", PM_MB_means$fungicide_ai), "fungicide_ai"] <-
+   "sulphur"
+
+```
 
@@
 
-   - Tebuconazole and propiconazole could be pooled as a triazole or demethylation inhibitors (DMI) fungicide treatment.
+The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in included in the highest frequencies, along with sulphur.
+The DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.
 
-   - Amistar Xtra and Custodia are both contain strobilurin and triazole, however, because they contain differing dose ratios (inverted) pooling may not be appropriate.
+Amistar Xtra and Custodia are both contain strobilurin and triazole mixes, however, because they contain differing dose ratios (inverted) pooling may not be appropriate.
 
-   - Perhaps best way forward is to do an analysis of only the triazoles/DMIs.
-   Then do another including azoxystrobin as a comparison.
+Perhaps best way forward is to focus the meta-analysis on only the triazoles/DMIs. This can then be compared to an additional meta-analysis including azoxystrobin as a comparison.
 
@@
 
-The primary focus of this research is the effect of fungicide on mitigating yield loss to disease.
-To reduce the effect of location and seasonal influences we will investigate the proportion of grain yield saved relative to the no spray control.
+Before we exclude non-DMI fungicides lets have a look at the efficacy of the other fungicides in comparison to the DMIs.
+For this comparison we will focus on the proportional yield saved, relative to the no spray control.
+The primary focus of this research is the effect of fungicide on mitigating yield loss due to disease.
+We are using proportional yield, realative to the no spray control, to reduce the effect of location and seasonal influences.
 

### 2020-06-05 01_Meta-analysis_experiments.Rmd
Edit scroll box dimensions

@@
    column_spec(c(3,5:6), width = "3cm") %>% 
-   scroll_box(width = "900px", height = "500px")
+   scroll_box(height = "500px")
 
-kable()
 ```

### 2020-06-05 vignette/191115_PMMB_DataWrangling_PM.Rmd
Rename duplcate label

@@
 # Rename the plot column and remove lines without data
-colnames(Herm_15[,"Plot.#"]) <- "Plot"
+colnames(Herm_15)[3] <- "Plot"
 Herm_15.DR <- Herm_15.DR[!is.na(Herm_15.DR$Treatment),]
@@
              rating_scale = unique(rating_scale),
-             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+             disease_error = sd(PM_final_severity, na.rm = TRUE), # generates NAs and needs repeating below
              D_error_type = "stdev",
@@
              final_assessment = unique(final_assessment),
-             #PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
-             #disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
-             #D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
@@
    group_by(n_treatment) %>%
-   summarise(PM_final_severity = sd(PM_final_severity, na.rm = TRUE),
-             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   summarise(yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
    select(c("yield_error"))
@@
 Disease data for Kingaroy 2016 only exists as a mean of treatments within the `2016 Mungbean PM trials summary.xlsx` file.  
-```{r Herm16_dataimport}
+```{r King16_dataimport}
 # Yield data from 2016 Hermitage trial with final disease severity
@@
 
+# Create Year and location variables
 King_16$Year <- 2016
@@
 
+# Convert plot values to numeric and remove "P" prefix
 King_16$Plot <- as.numeric(unlist(strsplit(
@@
              final_assessment = unique(final_assessment),
-             #PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
-             #disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
-             #D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = "Yes",
-             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE), # Calculation returned as NA, repeated below
              Y_error_type = "stdev",
-             #AUDPC_m = mean(AUDPC),
-             #AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = King_16_dat))[1,3]
@@
    )
-names(King_16.DR)[1:6] <- c("Treatment", "dae20","dae34","dae46","PM_final_severity","Final_Yield_tHa")
-
+
+# Rename columns
+colnames(King_16.DR)[1:6] <- c("Treatment", "dae20","dae34","dae46","PM_final_severity","Final_Yield_tHa")
+
+# Define Treatments
 King_16.DR <- King_16.DR %>%
@@
 
+# Join disease assesment data with grain yield data
 King_16_m <- left_join(King_16_m,King_16.DR)
+
+# Calculate AUDPC
 King_16_m$AUDPC_m <- apply(King_16_m[,c("dae20", "dae34", "dae46", "PM_final_severity")]-1,1, 
@@
                             FUN = audps, dates = c(20,34,46,60))
+
+# Create AUDPC/S standard deviation columns
+#  defined as NA because we only had treatment mean data
+#  for this experiment
 King_16_m$AUDPS_sd <- NA
 King_16_m$AUDPC_sd <- NA
+
+# Calculate disease mean squares
 King_16_m$Inc_Ms <- anova(lm(AUDPC_m ~ factor(n_treatment), 
@@
 
-# could also use gsub to remove Ts
+# could also use gsub to remove Ts in the treatment variable
 Fogerty_17$Treatment.No <- as.numeric(unlist(strsplit(
@@
              rating_scale = unique(rating_scale),
-             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+             disease_error = sd(PM_final_severity, na.rm = TRUE), # Generating NAs so it will be repeated below
              D_error_type = "stdev",
@@
 
+# Define control treatments
 Fogerty_17_m[Fogerty_17_m$n_treatment == 1, "fungicide_ai"] <- "control"
@@
 
+# Format and organise the dataframe
 Fogerty_17_m <- fold_data(Fogerty_17_m, PM_MB_means)
@@
 ```{r Herm17_Trialdat}
-# Remove zeros
-#Herm_17_dat[Herm_17_dat$`2017-03-07` == 0 ,c("2017-03-07")] <- 1
-
 Herm_17_dat <- 
@@
               dose_ai.ha = Herm_17_dat$dose_ai.ha,
-              n_treatment = as.numeric(unlist(strsplit(Herm_17_dat$Manage.Trt, "T"))[unlist(strsplit(Herm_17_dat$Manage.Trt, "T")) != ""]),
+              n_treatment = as.numeric(unlist(strsplit(Herm_17_dat$Manage.Trt, "T")
+                                              )[unlist(strsplit(Herm_17_dat$Manage.Trt, "T")) != ""]),
               fungicide_application_1 = Herm_17_dat$fungicide_application_1,
@@
 ```{r Herm17_means}
-
 Herm_17_m <- Herm_17_dat %>%
@@
 
+# Add control treatment detail
 Herm_17_m <- data.frame(Herm_17_m)
@@
 Herm_17_m <- copy_class(PM_MB_means,Herm_17_m)
-
-# COULD NOT GET TO MATCH
-# insert new calculations into data
-# #PM_MB_means <- 
-   # replace_data(template_data = PM_MB_means,
-   #                          new_data = Herm_17_m,
-   #                          new_data_column = "AUDPC_m",
-   #                          filter_cols = c("trial_ref","grain_yield.t.ha.","year","location",
-   #                                          "host_genotype","n_treatment", "fungicide_ai","row_spacing"))
-
-# PM_MB_means <- replace_data(template_data = PM_MB_means,
-#                             new_data = Herm_17_m,
-#                             new_data_column = "AUDPC_sd",
-#                             ignore_columns = c(5:8,10:16,29:46))
 
@@
               grain_yield.t.ha. = as.numeric(Well_18_dat$`Yield./.ha`)
-               # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
-              )
-
+              )
+
+# Calculate AUDPC
 Well_18_dat <- cbind(Well_18_dat,
@@
              rating_scale = unique(rating_scale),
-             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+             disease_error = sd(PM_final_severity, na.rm = TRUE), # Generates NAs repeated below
              D_error_type = "stdev",
@@
 # insert new calculations into data
-#PM_MB_means <- 
+PM_MB_means <- 
    replace_data(template_data = PM_MB_means, 
                             new_data = Well_18_m, 
-                            new_data_column = c("AUDPC_m", "AUDPC_sd"),#"AUDPS_m", "AUDPS_sd","Inc_Ms"),
+                            new_data_column = c("AUDPC_m", "AUDPC_sd"),
                             filter_cols = c("trial_ref","year","location","n_treatment"))
 
+# check the same dimensions
 dim(Well_18_m) ==
@@
 
-   # Not sure why replace data will not replcae the following columns
+   # Not sure why replace_data will not replcae the following columns
    PM_MB_means[c(324: 347),
-               c("AUDPS_m", "AUDPS_sd","Inc_Ms")] <-
+               c("AUDPS_m", "AUDPS_sd","Inc_Ms")] #<-
       Well_18_m[,c("AUDPS_m", "AUDPS_sd","Inc_Ms")]
-
-   PM_MB_means <- replace_data(template_data = PM_MB_means,
-                            new_data = Well_18_m,
-                            new_data_column = "AUDPC_sd",
-                            ignore_columns = c(5:8,10:16,29:46))
 
@@
              rating_scale = unique(rating_scale),
-             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+             disease_error = sd(PM_final_severity, na.rm = TRUE), # Producing NAs so code is repeated below
              D_error_type = "stdev",

### 2020-06-05 01_Meta-analysis_experiments.Rmd
edit link to html

@@
 NGA data were formatted to be compliant with the 1 - 9 rating scale used in all other experiments.
-Detailed code for the conversion can be found in the following vignette [191115_PMMB_DataWrangling_PM.Rmd](./vignette/191115_PMMB_DataWrangling_PM.Rmd).
+Detailed code for the conversion can be found in the following vignette [191115_PMMB_DataWrangling_PM.Rmd](./vignette/191115_PMMB_DataWrangling_PM.html).
 

### 2020-06-05 R/replace_data.R
Rename from data_mesh to replace_data. Better annotation of code. Some functionality improvements

@@ -1,0 +1,191 @@
+
+# Searches a dataframe (template_data) based on all columns which are not "ignored".
+#     at the first match the function inserts data entry from the "new_data_column in the 
+#     dataframe new_data into the column with the same name in template_data.
+# returns a dataframe
+
+replace_data <- function(template_data, new_data, new_data_column, ignore_columns = NULL, filter_cols = NULL,subset_factor = NULL){
+   if(any(colnames(template_data) != colnames(new_data))){warning("columns don't match ")
+      stop()}
+   
+   if(missing(template_data)){warning("\nTemplate data set needed ")
+      stop()}
+   if(missing(new_data)){warning("\nnew_data set needed ")
+      stop()}
+   if(missing(new_data_column)){warning("\nplease specifiy column name ")
+      stop()}
+   
+   template_data <- data.frame(template_data, stringsAsFactors = FALSE)
+   new_data <- as.data.frame(new_data, stringsAsFactors = FALSE)
+   
+   if(any(!new_data_column %in% colnames(template_data))){warning("\nCan't find index column in template dataset ")
+      stop()}
+   
+   if(any(colnames(template_data) != colnames(new_data))){warning("\nColumns from data don't match")
+      stop()}
+   if(all(!is.null(ignore_columns) & !is.null(filter_cols))){warning("\nSpecify only one criteria, not both filter_cols and ignore_columns ")
+      stop()}
+   
+   if(is.numeric(ignore_columns)){
+      ignore_columns <- colnames(template_data)[ignore_columns]
+   }
+   if(!is.null(ignore_columns)){
+      if(class(ignore_columns) != "character"){warning("\nignore_columns not a character vector ")
+         
+      }
+      if(any(colnames(template_data) %in% ignore_columns) == FALSE){
+         message(paste("\nNone of the specified columns",ignore_columns,"are included in the template_data "))
+      }
+      
+      #specify the columns to match
+      cols1 <- colnames(template_data)[colnames(template_data) %in% c(new_data_column,ignore_columns)]
+      message("\nExcluding columns from match: \n",paste(cols1, collapse = ", "))
+      
+   }else{# when ignore_columns is NULL
+         if(is.numeric(filter_cols)){
+            filter_cols <- colnames(template_data)[filter_cols]
+            
+            #specify the columns to match
+            message("\n Matching by columns: \n",paste(filter_cols, collapse = ", "))
+            
+               }
[…]

### 2020-06-05 02_Preliminary_analysis.Rmd
more clarification and simplification and flow

@@
 The primary focus of this research is the effect of fungicide on mitigating yield loss due to disease.
-We are using proportional yield, realative to the no spray control, to reduce the effect of location and seasonal influences.
+We are using proportional yield, relative to the no spray control, to reduce the effect of location and seasonal influences.
 
 First, let's investigate the difference in the effect of the type of fungicide on proportion of yield saved.
-Proportion of yield saved is used in attempt to reduce variation between trials.
 
@@
    arrange(desc(median)) %>%
-   kable(caption = "Fungicide effect on proportion of yield gain.") %>%
+   kable(caption = "Fungicide effect on proportion of yield gain.",
+         col.names = c("Fungicide active ingredient", "Total fungicide applications","*n* Treatments","Lower 2.5% quartile","Median proportional grain yield", "Mean proportional grain yield","97.5 % quartile")) %>%
    kable_styling(fixed_thead = T, full_width = T) %>%

### 2020-06-05 vignette/191115_PMMB_DataWrangling_PM.Rmd
Some description improvements and removal of useless code

@@
    # This function formats a dataframe to have the same column order as a template data.frame
-   # If colums are missing from the new_DataFrame that are in the template_DataFrame, it creates them 
+   # If columns are missing from the new_DataFrame that are in the template_DataFrame, it creates them 
    # with NA values. 
@@
    # of the new_DataFrame
-   # Using this function assists in joining the two data.frames together so colums are in the same order
+   # Using this function assists in joining the two data.frames together so columns are in the same order
 
@@
    new_DataFrame <-
-      new_DataFrame[, c(cnames2, cnames1[is.na(x1)])]  # adding columns to new_DataFrame not in template_DataFrame  # aranges column names to new_DataFrame not in template_DataFrame
+      new_DataFrame[, c(cnames2, cnames1[is.na(x1)])]  # adding columns to new_DataFrame not in template_DataFrame  # arranges column names to new_DataFrame not in template_DataFrame
 
@@
 source(here("R/copy_class.R"))
-source(here("R/data_mesh.R"))
+source(here("R/replace_data.R"))
 ```
@@
 #### AUDPC curve
-```{r Herm_audpc}
+```{r Herm_audpc, warning=FALSE}
 
@@
 #### AUDPC curve
-```{r King11_AUDPC}
+```{r King11_AUDPC, warning=FALSE}
 library(ggplot2)
@@
              case_when(Fung.Trt <= 3 ~ 2,
+                       Fung.Trt == 4 ~ 0,
                        TRUE ~ NA_real_))
@@
                           )
-
+Well_18_dat$total_fungicide
 ```
@@
 
-# For some weird reason standard deviations are comming back NA in the code above
+# For some weird reason standard deviations are coming back NA in the code above
 Well_18_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
@@
 
+source(here("R/replace_data.R"))
+
 # insert new calculations into data
@@
                             new_data = Well_18_m, 
-                            new_data_column = c("AUDPC_m", "AUDPC_sd"),
+                            new_data_column = c("total_fungicide","AUDPC_m", "AUDPC_sd"),
                             filter_cols = c("trial_ref","year","location","n_treatment"))
-
-# check the same dimensions
-dim(Well_18_m) ==
-dim(PM_MB_means[PM_MB_means$trial_ref == "mung1718/01",])
-
-   # Not sure why replace_data will not replcae the following columns
-   PM_MB_means[c(324: 347),
-               c("AUDPS_m", "AUDPS_sd","Inc_Ms")] #<-
-      Well_18_m[,c("AUDPS_m", "AUDPS_sd","Inc_Ms")]
 
@@
 
-```{r Save_PM_MB_means, eval=FALSE, include=FALSE}
+```{r Save_PM_MB_means, echo=TRUE}
 
 write.csv(PM_MB_means, file = here("cache/PM_MB_updated.csv"), row.names = FALSE)
-
-```
+getwd()
+```

### 2020-06-08 vignette/191115_PMMB_DataWrangling_PM.Rmd
Tidy up some errant lines

@@
 
-#dim(Fogerty_17)   # 162 rows , 43 Columns
-
 # Columns to keep
@@
 
-# I have comment out this code because it does not replace the control plots properly
+# I have comment out this code because it does not replace the control plots properly as there is nothing to separate them from each other
 # insert new calculations into data
-# PM_MB_means <-   replace_data(template_data = PM_MB_means, 
+#PM_MB_means <-   
+   # replace_data(template_data = PM_MB_means,
    #                          new_data = Fogerty_17_m,
    #                          new_data_column = "AUDPC_m",
-#                             ignore_columns = c(5:8,10:16,29:46))
-#
+   #                          ignore_columns = c(5:8,10:16,29:46),
+   #                          subset_factor = "mung1617/02")
 
@@
                           )
-Well_18_dat$total_fungicide
+
 ```
@@
 
-source(here("R/replace_data.R"))
-
 # insert new calculations into data
@@
 write.csv(PM_MB_means, file = here("cache/PM_MB_updated.csv"), row.names = FALSE)
-getwd()
-```
+
+```

### 2020-06-08 02_Preliminary_analysis.Rmd
corrections

@@
 AUDPC for trials which only provided final powdery mildew incidence was calculated using the record of 'first sign of disease' and final assessment. 
-More details on how the `PM_MB_means` data was compiled can be found in the ['Data wrangle vingette'][./vignette/191115_PMMB_DataWrangling_PM.Rmd]
+More details on how the `PM_MB_means` data was compiled can be found in the ['Data wrangle vingette'](./vignette/191115_PMMB_DataWrangling_PM.html)
 
 Various factors have been studied in the previous experiments which may influence the subsequent meta-analysis.
-On this page, unless stated, the following plots and analyses were made disregarding effects the following factors which have the potential to influence mungbean grain yield and/or powdery mildew mean plot severity.
+On this page, unless stated, the following plots and analyses were made disregarding other effects.
+The following factors are propostulated to potentially influence mungbean grain yield and/or powdery mildew mean plot severity.
 
@@
 
-The data plotted below are from `r length(unique(PM_MB_means$trial_ref))` field trials between (`r first(levels(PM_MB_means$year))` - `r last(levels(PM_MB_means$year))`) of which the details are described in [Studies considered in meta-analysis section](#studies-considered-in-meta-analysis).
+The data plotted below are from `r length(unique(PM_MB_means$trial_ref))` field trials between (`r first(levels(PM_MB_means$year))` - `r last(levels(PM_MB_means$year))`) of which the details are described in the [studies considered in meta-analysis section](#studies-considered-in-meta-analysis).
 
@@
 
-The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in included in the highest frequencies, along with sulphur.
+The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in the highest frequencies, along with sulphur.
 The DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.
@@
 
-Perhaps best way forward is to focus the meta-analysis on only the triazoles/DMIs. This can then be compared to an additional meta-analysis including azoxystrobin as a comparison.
+Perhaps best way forward is to focus the meta-analysis on only the triazoles/DMIs. 
+This can then be compared to an additional meta-analysis including azoxystrobin as a comparison.
 
@@
    kable(caption = "Fungicide effect on proportion of yield gain.",
-         col.names = c("Fungicide active ingredient", "Total fungicide applications","*n* Treatments","Lower 2.5% quartile","Median proportional grain yield", "Mean proportional grain yield","97.5 % quartile")) %>%
+         col.names = c("Fungicide active ingredient", "Total fungicide applications","n Treatments"," 2.5% quartile","Median proportional grain yield", "Mean proportional grain yield","97.5 % quartile")) %>%
    kable_styling(fixed_thead = T, full_width = T) %>%
    footnote(general = "Fungicides with less than five observations were omitted from this table")
+
+PM_MB_means[PM_MB_means$location == "Wellcamp",]
 ```
@@
 
-```{r Fungicide_x_nSprays_tble1, message=FALSE}
+```{r Fungicide_x_nSprays_tble1, message=FALSE, warning=FALSE}
 

### 2020-06-08 02_Preliminary_analysis.Rmd
move proportional yeild gain calculation to prep data

@@
 
-First, let's investigate the difference in the effect of the type of fungicide on proportion of yield saved.
+Let's investigate the difference in the effect of the type of fungicide on proportion of yield saved, but first we need to calculate yield saved relative to the no spray control.
+
+## Yield saving  
+Yield saving and Yield saving proportional to the control.
+
+Data from `r length(unique(PM_MB_means$trial_ref))` trials were collected and the means of each treatment calculated in the [Data wrangling vignette](`here("vignette/191115_PMMB_DataWrangling_PM.Rmd")`).
+These data were combined into one file `1902 powdery mildew-Mungbean - Collated means.csv`.
+
+```{r Calculate_yield-gains}
+PM_MB_means$grain_yield.t.ha. <-
+   as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data
+
+for (i in unique(PM_MB_means$trial_ref)) {
+   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
+
+   if (any(is.na(unique(dat1$row_spacing)))) {
+      warning(
+         paste(
+            unique(dat1$trial_ref),
+            "at",
+            unique(dat1$location),
+            "in year",
+            unique(dat1$year),
+            "has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n"
+         )
+      )
+      next()
+   }
+
+   for (j in unique(dat1$row_spacing)) {
+      dat2 <- dat1[dat1$row_spacing == j, ]
+      controlY <-
+         mean(dat2[dat2$fungicide_ai == "control", "grain_yield.t.ha."])
+
+      dat2$yield_gain <- dat2$grain_yield.t.ha. - controlY
+      dat2$prop_YG <- dat2$yield_gain  /  controlY
+
+      dat2[dat2$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
+         NA
+
+      dat1[dat1$row_spacing == j, ] <- dat2
+   }
+   PM_MB_means[PM_MB_means$trial_ref == i, ] <- dat1
+}
+
+# ____________________________________________
+# calculate yield gain and prop_yield gain for experiments with no row spacing data
+
+dat1 <- PM_MB_means[PM_MB_means$trial_ref == "AM1303", ]
+
+controlY <-
+   mean(dat1[dat1$fungicide_ai == "control", "grain_yield.t.ha."])
+
+dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
+dat1$prop_YG <- dat1$yield_gain / controlY
+dat1[dat1$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
+   c(NA, NA)
+PM_MB_means[PM_MB_means$trial_ref == "AM1303", ] <- dat1
+
+write.csv(PM_MB_means,
+          "cache/1911_PM_MB_means&Ygains.csv")
+```
 
@@
 
-PM_MB_means[PM_MB_means$location == "Wellcamp",]
 ```

### 2020-06-09 02_Preliminary_analysis.Rmd
Editing and corrections

@@
 
-## Yield saving  
-Yield saving and Yield saving proportional to the control.
-
-Data from `r length(unique(PM_MB_means$trial_ref))` trials were collected and the means of each treatment calculated in the [Data wrangling vignette](`here("vignette/191115_PMMB_DataWrangling_PM.Rmd")`).
-These data were combined into one file `1902 powdery mildew-Mungbean - Collated means.csv`.
-
 ```{r Calculate_yield-gains}
@@
 
+Now we have calculated proportional yield gains we can inpect the difference between the fungicide active ingredients
+
 ```{r Fungicide_x_nSprays_tble2, message=FALSE}
@@
          "sulphur",
-         "200 g/L azoxystrobin +\n80 g/L cyproconazole",
+         "200 g/L azoxystrobin + 80 g/L cyproconazole",
          "tebuconazole",
          "propiconazole",
-         "200 g/L tebuconazole +\n120 g/L azoxystrobin"
+         "200 g/L tebuconazole + 120 g/L azoxystrobin"
       )
@@
 
-There is a small yield effect when applying fungicide and it is unclear how much a second spray improves yield saved.
-Interestingly sulphur sprays might be worth investigating when sprayed twice.
+There is a small yield effect among the strobilurin fungicide mixes and the DMI fungicides. 
+The follow up spray seems to show an increase in yield protection.
+Interestingly sulphur sprays show good protection when sprayed twice.
 
@@
 #### Fungicide Doses  
-We should check that all fungicide doses that were used were roughly the same if we are to compare between trials where dose might be different.
+Hear after we will investigate only the DMI fungicides, tebuconazole and propiconazole and disregard the action of other fungicides.
+
+We should check that all fungicide doses that were used were roughly the same, if we are to compare between trials where dose might be different.
 
@@
    xlab("Dose (g ai/ha)") +
-   ggtitle(label = "Yield for each respective propiconazole dose") +
-   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5)
+   ggtitle(label = "Yield for each respective propiconazole dose, faceted by number of applications") +
+   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
+   facet_grid(cols = vars(total_fungicide))
+
 ```
@@
 ```{r PropiDoses_TrialCompar}
-boxplot_usq(prop_YG ~ dose_ai.ha,
-            data = PM_MB_means[(PM_MB_means$trial_ref == "mung1112/01" |
+
+PM_MB_means[(PM_MB_means$trial_ref == "mung1112/01" |
                 PM_MB_means$trial_ref == "mung1112/02") &
-                                  PM_MB_means$fungicide_ai == "propiconazole",])
+                PM_MB_means$fungicide_ai == "propiconazole",] %>%
+   mutate(dose_ai.ha = as.factor(dose_ai.ha)) %>%
+               ggplot(aes(y = prop_YG, x = dose_ai.ha))+
+   geom_boxplot()+
+   facet_grid(cols = vars(total_fungicide)) +
+   xlab("Dose (g ai/ha)") +
+   ggtitle(label = "Yield for each respective propiconazole dose, faceted by number of applications") +
+   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5)
 ```
 
-This plot, however, indicates that the previous plot might be skewed by high yielding trials.
+This plot is similar to the previous plot, indicating dose needs to be considered in the analysis. Especially as there is a interaction between dose and number of sprays.
 
@@
 
+This table shows that the majority of treatments inspected one and two spray manangement practices.
+
 *****
@@
 #### Timing of fungicide sprays  
-When are fungicides sprayed in relation to first sign.
+The timing of fungicide application can be crucial for maximum disease control and yield mitigation. 
+The experiments all relied on natural infection and thus infection at a standardised crop maturity stage was not possible. 
+To best estimate the effect of fungicide application timing we will use the day when the disease was first scouted in the field as a reference.
+The first sign of disease is a useful reference as it can be assessed with little to no cost or training for growers and farm staff.
+
+First lets make a plot to visualise when one or more spray management regimes were made in relation to the first sign of disease regardless of fungicide active. 
+The plot is faceted by number of spray applications.
 
@@
       labels = c(
-         "First\nspray",
-         "Second\nspray",
-         "Third\nspray",
-         "Fourth\nspray",
-         "Fifth\nspray"
+         "First spray",
+         "Second spray",
+         "Third spray",
+         "Fourth spray",
+         "Fifth spray"
       )
    ) +
-   ylab("Days to First Sign of Disease")
+   ylab("Days to First Sign of Disease")+
+   facet_grid(cols = vars(total_fungicide))+
+   theme(axis.text.x = element_text(angle = 90, hjust = 1))
 ```
+
+The plot shows single fungicide applications are mostly made at zero, first sign of disease in the crop. 
+Experiments that tested two spray treatments also tend to make the first application at first sign of disease, and the second spray between 10 and 25 days later.
+Three spray treatments seemed to be mostly used in experiments where they were testing preventative sprays as the first fungicide application.
 
@@
 ### Mungbean cultivars  
-In general, the mungbean varieties have the following resistance to powdery mildew.
+In general, mungbean varieties have the following resistance to powdery mildew.
 
@@
 Does host cultivar significantly impact the yield?
-Let's look at the volatility in yields to see if any cultivar yields better or has greater tolerance to powdery mildew. Below we plot distributions of mean trial yields for each cultivar.
+Let's look at the volatility in yields to see if any cultivar yields better or has greater tolerance to powdery mildew.
+Below we plot distributions of mean trial yields for each cultivar.
+The following plots use data that includes all fungicide types.
 
@@
 ```{r yield_vol}
-# this could be converted into a shiny app as a chunk. Make each input for the function a shiny option
 # Outputs the table and graph
 source("R/yield_volatility.r") #function to investigate the volatility in yields
-# Volitility is the range between the upper and lower 97.5 and 2.5 % quartiles
+# Volatility is the range between the upper and lower 97.5 and 2.5 % quartiles
 
@@
 ```
+This plot shows a large amount of yield volatility in all cultivars except green diamond.
+Green Diamond shows little volatility probably because this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trials.
 
@@
 
-Volatility of the cultivars are fairly similar when trial is not considered as a factor (when we inspect plots of all treatments and only spray treatments).
-Green Diamond shows little volatility however this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trials
+Volatility of the cultivars are less, albeit fairly similar, when trial is not considered as a factor (when we inspect plots of all treatments).
 
@@
    scale_fill_usq()
+
+YV1_herm[[3]]
 ```
@@
 
-YV1_crystal <-
+YV1_crystal[[3]]
+
+YV2_crystal <-
    yield_volatility(genotype = "Crystal", control_only = TRUE)
-YV1_crystal[[2]] +
+YV2_crystal[[2]] +
    scale_fill_usq()
+
+YV2_crystal[[3]]
 ```
 
-There is a lot of variation between field trials for Crystal, but little variation within field trials.
+There is a lot of variation between field trials for Crystal, but little variation within field trials. This indicates that trial should be fit as a random effect when we fit a model to this data.
 
@@
 ```{r YieldVol_Jade}
-YV2_crystal <- yield_volatility("Jade",control_only = FALSE)
-YV2_crystal[[2]] +
+YV1_jade <- yield_volatility("Jade",control_only = FALSE)
+YV1_jade[[2]] +
    scale_fill_usq()
+
+YV1_jade[[3]]
 ```
@@
 For Jade there is high variation between trials and with-in.
-Perhaps indicating lower tolerance. Let's look at the same plot with data only from no spray controls to see if the variation is the same.
+Perhaps indicating lower tolerance. 
+Let's look at the same plot with data only from no spray controls to see if the variation is the same.
 
 ```{r YieldVol_JadeControl}
-YV3_crystal <- yield_volatility("Jade", control_only = TRUE)
-YV3_crystal[[2]] +
+YV2_jade <- yield_volatility("Jade", control_only = TRUE)
+YV2_jade[[2]] +
    scale_fill_usq()
+
+YV2_jade[[3]]
 ```
 
-There seems to be a noticeable shift in the probability curves between the two plots.
-Indicating that the tolerance in Jade may not as good as Crystal.
-A comparison between the fungicide efficacy for reducing powdery mildew severity and fungicide efficacy at mitigating yield loss.
+There still remains a higher volatility in Jade and perhaps a greater shift in the probability curve including fungicide treatments vs probability curves including only no spray controls.
+Indicating that there might be a difference in powdery mildew tolerance between Jade and Crystal.
 
@@
 
-   * Can we pool certain row spacing that have no significant difference?
+   * If not, can we pool certain row spacing that have no significant difference?
 

### 2020-06-10 02_Preliminary_analysis.Rmd
Alter season length and first sign of disease plot to include estimated season lengths where planting dates or harvest dates were missing

@@
 
+This tests when rainfall during the cropping season could be best associated with yield
+
 ```{r rainfall_sum_Sstart}
@@
 # Create the data frame for the plot
-source("R/import_data.R")
-PM_MB_means <- import_data()
 season_dates <- PM_MB_means %>%
@@
       First_sign_PM = unique(first_sign_disease),
-      season_length = as.Date(unique(harvest_date)) - as.Date(unique(planting_date))
+      season_length = as.Date(unique(harvest_date)) - as.Date(unique(planting_date)),
+      cropping_season = "Actual"
    )
+
+# For some trials where planting date and Harvest date is missing lets estimate 
+#     the season length by using the mean of all season lengths
+season_dates[is.na(season_dates$season_length),"cropping_season"] <- "Estimated"
+
+season_dates[is.na(season_dates$Planting_date),"Planting_date"] <- 
+   season_dates[is.na(season_dates$Planting_date),"Harvest_date"] - 
+   as.numeric(mean(season_dates$season_length, na.rm = TRUE))
+
+season_dates[is.na(season_dates$Harvest_date),"Harvest_date"] <- 
+   season_dates[is.na(season_dates$Harvest_date),"Planting_date"] + 
+   as.numeric(mean(season_dates$season_length, na.rm = TRUE))
+
+season_dates[is.na(season_dates$season_length),"season_length"] <- 
+   mean(season_dates$season_length, na.rm = TRUE)
 
@@
 
-season_dates[1:2, "Planting_day"] <- 1
+season_dates[c(1:2,6), "Planting_day"] <- 1
 #  yday(as.Date("2012-02-28") - 7) # Correct dplanted in december and emerged in February, Assuming due to lack of rain or recording error. Using 7 days prior to emergence day as planting day
@@
 
-# reorder the factors so they will appear in chronilogical order
+# reorder the factors so they will appear in chronological order
 # I used First sign because all trials have recorded this
@@
       ymin = Planting_day,
-      ymax = Harvest_day
+      ymax = Harvest_day,
+      colour = cropping_season
    )) +
@@
    coord_flip() +
+   scale_color_manual(values=c("black","grey70"))+
    ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
-warnings()
+
 ```

### 2020-06-10 02_Preliminary_analysis.Rmd
tidy up code and simplify explanation

@@
 
-first_day_month <- c(0, 31, 59, 90, 120, 151, 181, 211, 243, 273) + 1
+first_day_month <- c(0, 31, 60, 91, 121, 152, 182, 212, 244, 274) + 1
 axis_labels_date <-
@@
 
-In most years, regardless of the age of the crop, PM establishes in March.
+In most years, regardless of the age of the crop, powdery mildew establishes in March.
 
@@
       fungicide_ai == c(
-         "200 g/L tebuconazole +\n120 g/L azoxystrobin" ,
-         "200 g/L azoxystrobin +\n80 g/L cyproconazole",
+         "200 g/L tebuconazole + 120 g/L azoxystrobin" ,
+         "200 g/L azoxystrobin + 80 g/L cyproconazole",
          "tebuconazole",
@@
          "sulphur"
-      )
+      ),
+      total_fungicide != 3
    ) %>%
@@
    scale_fill_usq() +
+   facet_grid(rows = vars(total_fungicide))+
    coord_flip()
+
 ```
 
-There was some hope groups of fungicide could be combined, _i.e._ propiconazole and tebuconazole, however it seems that they have different efficacies.
-Let us look to see if there is anything skewing the above.
+While there is some differences in the variation between tebuconazole and propiconazole, the medians are very similar. 
+I think it is safe to combine these fungicides, with the same mode of action in the meta-analysis.
 
@@
 
-From the data that we have, it is difficult to determine if there is an association between powdery mildew severity and grain yield.
+From the data that we have, it is difficult to determine if there is an association between powdery mildew severity and grain yield in no spray control plots.

### 2020-06-10 03_Prep_data.Rmd
tidy up code and simplify explanation

@@
 ## Standardising sample variance  
-Meta-analyses use variance from the data to calculate the effect sizes. The type of variance needs to be the same across all the data incorporated in the meta-analysis.
+Meta-analyses use variance from the data to calculate the effect sizes. 
+The type of variance needs to be the same across all the data incorporated in the meta-analysis.
 
-We are narrowing the meta-analysis to only include demethylation inhibitors, tebuconazole and propiconazole. Within studies which have used these fungicides, what type of error was reported?
+We are narrowing the meta-analysis to only include treatments that used demethylation inhibitors, tebuconazole and propiconazole. 
+Lets look at what type of statistical error was reported for the trials that used these fungicides.
 
@@
 The experiment summaries report either standard deviation, least square differences or no error term (`NA`). 
-Below we will convert LSD and standard deviation to sample variance.
-In addition, we need to impute variances for the trials which did not report any form of variance (`NA`).
+First we will convert LSD and standard deviation to sample variance. 
+Then we will impute variances for the trials which did not report any form of variance (`NA`).
 
@@
 
+First lets get a list of trials that reported LSD.  
 ```{r all_LSD_trials}
@@
 
-The following code cnverts 'least square differences' (LSD) to sampling variance as per the method in [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
-Ideas for using a T-critical value of 1.697 came from reading a [statisics-how-to website](https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/).
-A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted where 30 degrees of freedom within experiment was used to find the 'T-crit' value of 1.697.
+We will follow the method of converting 'least square differences' (LSD) to sampling variance reported by [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
+A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted to select the T-crit value in the equation. 
+Our data contained 30 degrees of freedom which equates to a 'T-crit' value of 1.697.
 
@@
 
-      ###############################################3
-      # ___ Adjusting formula to suit our data_______
-      #
-      #  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates[j] *
-      #                   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$grain_yield.t.ha[j])
-      # Balance equation
-      # Sv[j] = V_yield /
-      #    (PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j] *
-      #       as.numeric(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$grain_yield.t.ha[j])^2)
-      # #################################################################
-
       Sv[j] = V_yield /
@@
 
-      # Sv[j] = MSE /
-      #    (PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j] *
-      #       as.numeric(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$grain_yield.t.ha[j])^2)
-      #
-
-      ### -> This formula should be V = (n * (LSD/1.96)^2) / 2
-
    }
 
-   # and replacing the values in the dataset
-
+   # Replace the values in the dataset
    PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error <-
@@
 
-for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error)) {
+for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$yield_error)) {
    if (j == 1) {
       Sv <-
-         vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error))
+         vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$yield_error))
    }# create empty vector at first iteration with length of j
 
-   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error[j]) ^
-      2
+   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$yield_error[j]) ^ 2
 }
@@
 # and replacing the values in the dataset
-PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error <-
+PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$yield_error <-
    Sv
-PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$Y_error_type <-
+PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$Y_error_type <-
    "SamplingVariance"
-```
-
-## Yield saving  
-Yield saving and Yield saving proportional to the control.
-
-Data from `r length(PM_MB_means$trial_ref)` trials were collected and the means of each treatment calculated (`R/Cleaning historical data.R`).
-These data were combined into one file `1902 powdery mildew-Mungbean - Collated means.csv`.
-
-```{r Calculate_yield-gains}
-PM_MB_means$grain_yield.t.ha. <-
-   as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data
-
-for (i in unique(PM_MB_means$trial_ref)) {
-   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
-
-   if (any(is.na(unique(dat1$row_spacing)))) {
-      warning(
-         paste(
-            unique(dat1$trial_ref),
-            "at",
-            unique(dat1$location),
-            "in year",
-            unique(dat1$year),
-            "has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n"
-         )
-      )
-      next()
-   }
-
-   for (j in unique(dat1$row_spacing)) {
-      dat2 <- dat1[dat1$row_spacing == j, ]
-      controlY <-
-         mean(dat2[dat2$fungicide_ai == "control", "grain_yield.t.ha."])
-
-      dat2$yield_gain <- dat2$grain_yield.t.ha. - controlY
-      dat2$prop_YG <- dat2$yield_gain  /  controlY
-
-      dat2[dat2$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
-         NA
-
-      dat1[dat1$row_spacing == j, ] <- dat2
-   }
-   PM_MB_means[PM_MB_means$trial_ref == i, ] <- dat1
-}
-
-# ____________________________________________
-# calculate yield gain and prop_yield gain for experiments with no row spacing data
-
-dat1 <- PM_MB_means[PM_MB_means$trial_ref == "AM1303", ]
-
-controlY <-
-   mean(dat1[dat1$fungicide_ai == "control", "grain_yield.t.ha."])
-
-dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
-dat1$prop_YG <- dat1$yield_gain / controlY
-dat1[dat1$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
-   c(NA, NA)
-PM_MB_means[PM_MB_means$trial_ref == "AM1303", ] <- dat1
-
-write.csv(PM_MB_means,
-          "cache/1911_PM_MB_means&Ygains.csv")
 ```

### 2020-06-10 R/same.R
Create function to help test if elements in vectors match. Does not return NAs Treats NAs with more certainty

@@ -1,0 +1,63 @@
+# This function tests two vectors for each respectivley placed element is the same
+# This works like testing x1 == x2 with the difference being it handles NA values differently
+# The function treats NAs a meaningful test and returns if it is the same.
+# ie. same(NA,NA) returns TRUE; where NA == NA return NA
+#     same(1, NA) returns FALSE; where 1 == NA returns NA 
+
+same <- function(x1, x2) {
+   if (length(x1) == length(x2)) {
+      return(apply(cbind(x1, x2), 1, function(xx) {
+         if (is.na(xx[1]) &
+             is.na(xx[2])) {
+            return(TRUE)
+         } else{
+            if (is.na(xx[1]) |
+                is.na(xx[2])) {
+               return(FALSE)
+            } else{
+               return(xx[1] == xx[2])
+            }
+         }
+         
+      }))
+   }
+   
+   if (length(x1) == 1 &
+       length(x2) > 1) {
+      return(sapply(x2, function(xx = x2) {
+         if (is.na(xx) &
+             is.na(x1)) {
+            return(TRUE)
+         } else{
+            if (is.na(xx) |
+                is.na(x1)) {
+               return(FALSE)
+            } else{
+               return(x1 == xx)
+            }
+            
+         }
+      }))
+      
+   }
+   
+   if (length(x1) > 1 &
+       length(x2) == 1) {
+      return(sapply(x1, function(xx = x1) {
+         if (is.na(xx) &
+             is.na(x2)) {
+            return(TRUE)
+         } else{
+            if (is.na(xx) |
+                is.na(x2)) {
+               return(FALSE)
+            } else{
+               return(x2 == xx)
+            }
+            
+         }
+      }))
+   }else{stop("length of vectors must be the same length")}
+   
+   
+}

### 2020-06-10 03_Prep_data.Rmd
simplification and corrections

@@
 
-# Calculate AUDPC using final severity and first sign of disease - 7 days
-source("R/AUDPC_for_single_obs.R") 
+source("R/AUDPC_for_single_obs.R") # Calculate AUDPC using final severity and first sign of disease - 7 days
+source("R/same.R") # matches each element of a vector and does not return NAs
 ```
@@
    filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole",
-          row_spacing == 0.75) %>%
+             fungicide_ai == "propiconazole") %>%
    group_by(trial_ref, location, Y_error_type, fungicide_ai) %>%
@@
    kable(caption = "Number of treatments for each trial and the error type reported") %>%
-   kable_styling(fixed_thead = T) %>% 
+   #kable_styling(fixed_thead = T) %>% 
    footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
@@
    clusters[i, "n"] <-
-      nrow(slim_PM_dat[slim_PM_dat$cluster_1 == clusters[i, "cluster_1"] &
-                          slim_PM_dat$cluster_2 == clusters[i, "cluster_2"] &
-                          slim_PM_dat$cluster_3 == clusters[i, "cluster_3"],])
+      nrow(slim_PM_dat[same(slim_PM_dat$cluster_1, clusters[i, "cluster_1"]) &
+                          same(slim_PM_dat$cluster_2, clusters[i, "cluster_2"]) &
+                          same(slim_PM_dat$cluster_3, clusters[i, "cluster_3"]),])
 
    clusters[i, "n_x_trial"] <-
-      length(unique(slim_PM_dat[slim_PM_dat$cluster_1 == clusters[i, "cluster_1"] &
-                                   slim_PM_dat$cluster_2 == clusters[i, "cluster_2"] &
-                                   slim_PM_dat$cluster_3 == clusters[i, "cluster_3"],
+      length(unique(slim_PM_dat[same(slim_PM_dat$cluster_1, clusters[i, "cluster_1"]) &
+                                   same(slim_PM_dat$cluster_2, clusters[i, "cluster_2"]) &
+                                   same(slim_PM_dat$cluster_3, clusters[i, "cluster_3"]),
                                 "trial_ref"]))

### 2020-06-11 03_Prep_data.Rmd
Update prep_data chunk with clarifications

@@
 
-From this we can see that there are 16 different cluster combinations, which would make the analysis too difficult. I will reduce this to 6 levels within one variable.
+From this we can see that there are 16 different cluster combinations, which would make the analysis too difficult. We will reduce this to 6 levels within one variable.
 
@@
 
-Two sprays or more where the first spray was either early, recommended timing, or late.
+Two or more sprays where the first spray was either early, recommended timing, or late.
 
@@
 
-# For each treatment, when were the first fungicide applications made 
-# relative to the first sign of disease
-table(slim_PM_dat$spray_management,slim_PM_dat$fungicide_timing_1)
 ```
@@
 
-There appears to be no relationship between the two continuous variables.  
+There appears to be a weak positive relationship between the two continuous variables.  
 Does a linear model confirm this?
@@
 
-There is no relationship as per the linear model.
+The linear model confirms a significant positive relationship between grain yield and AUDPC. 
+This is not what we would expect and the low R squared value of `r round(summary(lm(grain_yield.t.ha.
+~ AUDPC_m, data = PM_MB_means))$adj.r.squared,3)` perhaps there are additional factors influencing this relationship.
 
-Perhaps the variation due to trial location, season, row spacing, and other seasonal variables are preventing us from seeing a relationship.
+Lets tease out variation due to trial location, season, row spacing, and other seasonal variables are preventing us from seeing the expected relationship. 
 Let's do the plot again for each trial where there are no missing values.  
@@
 
-This sequence of graphs show that AUDPC and disease incidence does not impact on yields if the season is a low yielding, ie lower than 1 tonne per hectare.  
+This sequence of graphs show that AUDPC and disease incidence tends not impact on yields if the season is a low yielding, ie lower than 1 tonne per hectare.  
 The higher the yield the greater greater the influence on the disease on the yield especially if the crop is high yielding with AUDPC also being large enough to reduce yield.
@@
 ```
+The plots from the AUPDS is similar to the AUDPC, however according to the linear model the AUDPC is a better, significant fit.
+
+A mixed effect model would be more suitable to investigate the interactive effects of location, season, and trial. 
+The mixed effect model will help us decide on the best approach and structure for our meta-analysis model.
 
@@
 PM_MB_means$harvest_date - PM_MB_means$first_sign_disease
-PM_MB_means[0 > as.Date(PM_MB_means$harvest_date, format = "%Y-%m-%d")-
-as.Date(PM_MB_means$first_sign_disease, format = "%Y-%m-%d"),]
 ```

### 2020-06-11 02_Preliminary_analysis.Rmd
Corrections and removing irrelevant lines

@@
 First lets import the data. Each row provides the mean yield for each experimental treatment.
-```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
+```{r echo=TRUE, message=FALSE, warning=FALSE}
 # Import data
@@
 
-Now we have calculated proportional yield gains we can inpect the difference between the fungicide active ingredients
+Now we have calculated proportional yield gains we can inspect the difference between the fungicide active ingredients
 
@@
    kable(caption = "Fungicide effect on proportion of yield gain.",
-         col.names = c("Fungicide active ingredient", "Total fungicide applications","n Treatments"," 2.5% quartile","Median proportional grain yield", "Mean proportional grain yield","97.5 % quartile")) %>%
+         col.names = c("Fungicide active ingredient", "Total fungicide applications","n Treatments"," 2.5% quartile","Median proportional grain yield", "Mean proportional grain yield","97.5 % quartile"),
+         align = "c") %>%
    kable_styling(fixed_thead = T, full_width = T) %>%
+   column_spec(c(2,3), width = "1cm") %>% 
    footnote(general = "Fungicides with less than five observations were omitted from this table")
@@
 There is a small yield effect among the strobilurin fungicide mixes and the DMI fungicides. 
+While there is some differences in the variation between tebuconazole and propiconazole, the medians are very similar. 
+I think it is safe to combine these fungicides, with the same mode of action in the meta-analysis.
 The follow up spray seems to show an increase in yield protection.
@@
 
-There is a large amount of variation in the propiconazole dose, let's inspect the difference in yields for each dose.
+Doses for propiconazole range from 62.5 to 125, a large variation.
+Let's inspect the difference in yields for each dose.
 
@@
    xlab("Dose (g ai/ha)") +
-   ggtitle(label = "Yield for each respective propiconazole dose, faceted by number of applications") +
+   ggtitle(label = "Yield for each respective propiconazole dose,\nfaceted by number of applications") +
    geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
@@
 
-This table shows that the majority of treatments inspected one and two spray manangement practices.
+This table shows that the majority of treatments inspected one and two spray management practices.
 
@@
 This plot shows a large amount of yield volatility in all cultivars except green diamond.
-Green Diamond shows little volatility probably because this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trials.
+Green Diamond shows little volatility probably because this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trial.
 
-Now let's look at overall yields for each cultivar, where trial is not a factor, in only the no spray treatments.
+Now let's look at overall yields for each cultivar, where trial is not a factor, in only the no spray control treatments.
 
@@
 
-Volatility of the cultivars are less, albeit fairly similar, when trial is not considered as a factor (when we inspect plots of all treatments).
+Volatility of the cultivars are less, albeit fairly similar, in control plots when trial is not considered as a factor.
 
@@
 
-PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole",
-          row_spacing == 0.75) %>%
-   glimpse()
 ```
@@
 
-```{r rainLMrsquared}
-ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_rsquared)) +
-   geom_raster(aes(fill = lm_rsquared), interpolate = TRUE) +
-   geom_contour(bins = 15, colour = "white") +
-   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)), ],
-              aes(x = start_day, y = end_day),
-              colour = " red") +
-   scale_fill_distiller(palette = "RdBu") 
-```
-
 ```{r rainLMadjrsquared}
@@
 season_dates[c(1:2,6), "Planting_day"] <- 1
-#  yday(as.Date("2012-02-28") - 7) # Correct dplanted in december and emerged in February, Assuming due to lack of rain or recording error. Using 7 days prior to emergence day as planting day
 
@@
 In most years, regardless of the age of the crop, powdery mildew establishes in March.
-
-*****
-
-#### Effect of Fungicide
-
-**Fungicide effect on proportional yield gain with respect to time of application**  
-First let's look at the quantiles for each fungicide irrespective of other factors.
-We will focus on proportional yield gain, compared to no treatment control, as this should partially correct for some spatial and seasonal effects.
-
-```{r fungicide_proportion_yield}
-# plot table as a box plot
-PM_MB_means %>%
-   filter(
-      fungicide_ai == c(
-         "200 g/L tebuconazole + 120 g/L azoxystrobin" ,
-         "200 g/L azoxystrobin + 80 g/L cyproconazole",
-         "tebuconazole",
-         "propiconazole",
-         "sulphur"
-      ),
-      total_fungicide != 3
-   ) %>%
-   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
-   geom_boxplot(aes(fill = fungicide_ai)) +
-   geom_hline(aes(yintercept = 0), size = 0.5, colour = "red") +
-   labs(x = "Proportion of grain yield saved",
-        title = "Grain yield proportion saved,\ngrouped by fungicide type") +
-   theme(
-      panel.grid.major = element_line(colour = "grey80"),
-      panel.grid.minor = element_line(colour = "grey50"),
-      panel.background = element_rect(fill = NA)
-   ) +
-   guides(fill = guide_legend(title = "Fungicide")) +
-   scale_fill_usq() +
-   facet_grid(rows = vars(total_fungicide))+
-   coord_flip()
-
-```
-
-While there is some differences in the variation between tebuconazole and propiconazole, the medians are very similar. 
-I think it is safe to combine these fungicides, with the same mode of action in the meta-analysis.
-
-We need to also define the relationship between yield loss and disease severity.
-When exploring this data we should look primarily at the no spray control plots
-
-```{r yield_x_PMseverity}
-PM_MB_means %>%
-   filter(fungicide_ai == "control") %>%
-   ggplot(aes(x = PM_final_severity, y = grain_yield.t.ha.)) +
-   geom_point() +
-   geom_smooth(method = "lm")
-```
-
-From the data that we have, it is difficult to determine if there is an association between powdery mildew severity and grain yield in no spray control plots.

### 2020-06-11 03_Prep_data.Rmd
typos, spelling

@@
 
-source("R/AUDPC_for_single_obs.R") # Calculate AUDPC using final severity and first sign of disease - 7 days
 source("R/same.R") # matches each element of a vector and does not return NAs
@@
 
-We are narrowing the meta-analysis to only include treatments that used demethylation inhibitors, tebuconazole and propiconazole. 
+We are narrowing the meta-analysis to only include treatments using demethylation inhibitors, tebuconazole and propiconazole. 
 Lets look at what type of statistical error was reported for the trials that used these fungicides.
@@
    kable(caption = "Number of treatments for each trial and the error type reported") %>%
-   #kable_styling(fixed_thead = T) %>% 
+   #kable_styling(fixed_thread = T) %>% 
    footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")

### 2020-06-12 03_Prep_data.Rmd
Correct clustering code

@@
             !is.na(fungicide_application_2) ~ "Recommended_plus",
-         fungicide_timing_1 >= 4 ~ "Late_plus",
+         fungicide_timing_1 >= 4 &
+            !is.na(fungicide_application_2) ~ "Late_plus",
          TRUE ~ "Other"
@@
 slimmer_PM_dat <-
-   slim_PM_dat[slim_PM_dat$spray_management != "Late" &
+   slim_PM_dat[#slim_PM_dat$spray_management != "Late" &
                   slim_PM_dat$spray_management != "Early_plus", ]

### 2020-06-12 R/slimming_PM_dat.R
Add in dose factor

@@ -5,10 +5,14 @@
 # PM_MB_Mtemp <- import_data()
 PM_MB_Mtemp <- read.csv("cache/1911_PM_MB_means&Ygains.csv")
 
+PM_MB_Mtemp$dose <- NA
+PM_MB_Mtemp[PM_MB_Mtemp$dose_ai.ha <= 70, "dose"] <- "lowDose"
+PM_MB_Mtemp[PM_MB_Mtemp$dose_ai.ha > 70, "dose"] <- "highDose"
+
 slim_PM_dat <- data.frame(
    trial = paste(PM_MB_Mtemp$trial_ref, PM_MB_Mtemp$year,
                  PM_MB_Mtemp$location,PM_MB_Mtemp$host_genotype,
-                 PM_MB_Mtemp$row_spacing, sep = "_"),
+                 PM_MB_Mtemp$row_spacing, PM_MB_Mtemp$dose,sep = "_"),
    trial_ref = as.factor(PM_MB_Mtemp$trial_ref),
    year = as.integer(PM_MB_Mtemp$year),
    host_genotype = PM_MB_Mtemp$host_genotype,
@@ -21,6 +25,7 @@ slim_PM_dat <- data.frame(
    fungicide_application_2 = as.Date(PM_MB_Mtemp$fungicide_application_2, format = "%Y-%m-%d"),
    fungicide_application_3 = as.Date(PM_MB_Mtemp$fungicide_application_3, format = "%Y-%m-%d"),
    total_fungicide = as.integer(PM_MB_Mtemp$total_fungicide),
+   dose_ai.ha = as.double(PM_MB_Mtemp$dose_ai.ha),
    grain_yield.t.ha = as.double(PM_MB_Mtemp$grain_yield.t.ha.),
    yield_error = as.double(PM_MB_Mtemp$yield_error),
    yield_gain = as.double(PM_MB_Mtemp$yield_gain),

### 2020-06-12 04_MetaAnalysis.Rmd
Update meta-analysis and descriptions

@@
 
-   - Grain yield is our response variable.  
+   - Grain yield is our response variable and will be converted to Kg / Ha.  
    - Trial, which resolves combinations of categorical variables: year, location, row spacing and cultivar; is set as a random intercept.  
@@
 
+First lets compare models with and without a log transformed response variable to evaluate if the log transformed model better fits our assumptions of normality.  
+Next we will test whether including `spray_management` as a significantly accounts for enough variation as a fixed effect variable to be included in the model.  
+Finally we will test whether including `spray_management` as a significantly accounts for enough variation as a random slope to the trial variable.
+
 ```{r LME_slimmer_cluster_disease_mod}
 m8 <- lmer(grain_yield.t.ha * 1000 ~ factor(spray_management) +
-              (factor(spray_management) | trial_ref),
+              (factor(spray_management) | trial),
            data = slimmer_PM_dat)
@@
 m9 <- lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
-              (factor(spray_management) | trial_ref),
+              (factor(spray_management) | trial),
            data = slimmer_PM_dat)
@@
 m10 <- lmer(log(grain_yield.t.ha * 1000) ~
-               (factor(spray_management) | trial_ref),
+               (factor(spray_management) | trial),
             data = slimmer_PM_dat)
@@
    lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
-           (1 | trial_ref),
+           (1 | trial),
         data = slimmer_PM_dat)
+```
 
+```{r m8_vs_m9}
 anova(m8, m9) # m9 is significantly better model
+```
+There is a significant difference between `m8` and `m9`, with `m9` showing the best fit and lowest AIC: `r min(anova(m8, m9)$AIC)`.
+
+```{r m9_vs_m10}
 anova(m9, m10) # m9 is significantly better model
+```
+There is a significant difference between `m10` and `m9`, with `m9` showing the best fit and lowest AIC: `r min(anova(m9, m10)$AIC)`.
+
+```{r m9_vs_m11}
 anova(m9, m11) # m11 is a simpler model which is no different to m9
@@
 
-The best model from the four above is `m9` with the lower AIC of -29.357.
+The best model from the four above is `m11` with the lower AIC of -`r min(anova(m9, m11)$AIC)`
 
 ```{r}
-summary(m9)
+summary(m11)
 ```
@@
 
-   - A single early spray before first sign of powdery mildew is not likely to increase yields.
+   - A single `early` spray before first sign of powdery mildew is not likely to increase yields.
 
-   - A single or single spray with one or more follow sprays starting  at the `recommended` first spray , within 3 days of powdery mildew first sign are likely to produce significantly higher grain yields compared to the no spray control.
+   - One spray at the `recommended` timing, or two sprays starting at the `recommended` first spray, are likely to produce significantly higher grain yields compared to the no spray control.
 
@@
 
-```{r imputing_variances}
+```{r imputing_variances, eval=FALSE, include=FALSE}
 source("./R/impute_yield_err.R")
@@
 #### Imputing sample variances from Mean squares
-```{r imputing_MSE_dataSpread}
+```{r imputing_MSE_dataSpread, eval=FALSE, include=FALSE}
 slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv")
@@
 
-```{r imputing_MSE}
+```{r imputing_MSE, eval=FALSE, include=FALSE}
 TrialMSQ <- slimmer_PM_dat %>%
@@
    factor(slimmer_PM_dat$spray_management,
-          levels(factor(slimmer_PM_dat$spray_management))[rev(c(1, 2, 4, 5, 3))])
+          levels(factor(slimmer_PM_dat$spray_management))[rev(c(1, 2, 5, 6, 3,4))])
 
@@
          "Recommended_plus",
+         "Late",
          "Late_plus"
@@
    geom_boxplot() +
-   #geom_point(position = "jitter", alpha = 1/5)+
    geom_jitter(width = 0.1, alpha = 1 / 5) +
@@
 slimmer_PM_dat$yi <- log(slimmer_PM_dat$grain_yield.t.ha)
+
 slimmer_PM_dat$vi <-
@@
 
-slimmer_PM_dat$spray_management <-
-   factor(slimmer_PM_dat$spray_management)
 slimmer_PM_dat$trial_ref <- factor(slimmer_PM_dat$trial_ref)
@@
    yi,
-   vi,
+   yield_error,
    mods = ~ spray_management,
@@
 )
+
 ```
@@
 # below 0.5 for 10 iterations
-for (ITERATE in 1:10) {
+for (ITERATE in 1:50) {
    rstudioapi::jobRunScript(
@@
    )
-   Sys.sleep(1)
+   Sys.sleep(15)
 }

### 2020-06-12 04_MetaAnalysis.Rmd
Update meta-analysis explaination and contrasts with the extra spray_management variable

@@
 
-According to the results of the omnibus test ($Q_M = 10.65, df = 4, p = 0.0308$) we can reject the null hypothesis $H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$ that the tested spray management schedules have no benefit to protecting mungbean yields[@Viechtbauer2010].
-However Late plus ($\beta_4$) was the only moderator showing a significant effect on yields ($z = 3.2276; p = 0.0012$). 
-The analysis shows there is still a considerable amount of residual heterogeneity ($Q_E = 5096.04, df = 125, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
+According to the results of the omnibus test ($Q_M = 7.32, df = 5, p = 0.1979$) we can't reject the null hypothesis $H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$ that the tested spray management schedules have no benefit to protecting mungbean yields [@Viechtbauer2010].
+However Late plus ($\beta_4$) was the only moderator showing a significant effect on yields ($z = 2.598; p = 0.0094$). 
+The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 538.26, df = 141, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
 
@@
 
-When we compare these results to those of the linear mixed effect model there is little difference in the outcome.
-
-```{r compare_meta&lmer}
-lme_PM <-
-   lmer(yi ~ spray_management + (spray_management |
-                                    trial), data = slimmer_PM_dat)
-
-summary(lme_PM)
-```
-
 *****
@@
 ```{r metafor_contrasts}
-anova(PM_mv_AI, L = rbind(
-   c(0, 1, -1, 0, 0),
+meta_cont <- anova(PM_mv_AI, L = rbind(
+   c(0, 1, -1, 0, 0,0),
    # early vs Recommended
-   c(0, 1, 0, -1, 0),
+   c(0, 1, 0, -1, 0,0),
    # early vs recommended plus
-   c(0, 1, 0, 0, -1),
+   c(0, 1, 0, 0, -1,0),
+   # early vs Late 
+   c(0, 1, 0, 0, 0,-1),
    # early vs Late plus
-   c(0, 0, -1, 1, 0),
+   c(0, 0, -1, 1, 0,0),
    # Recommended plus vs recommended
-   c(0, 0, -1, 0, 1),
-   # Late_Plus vs Recommended
-   c(0, 0, 0, -1, 1)
-)) # Late_plus vs Recommended plus
+   c(0, 0, -1, 0, 1,0),
+   # Late  vs Recommended
+   c(0, 0, -1, 0, 0,1),
+   # Late_plus  vs Recommended
+   c(0, 0, 0, -1, 1,0),
+   # Late vs Recommended plus
+   c(0, 0, 0, -1, 0,1),
+   # Late_plus  vs Recommended plus
+   c(0, 0, 0, 0, -1,1)
+)) # Late vs Late_plus
+
+change_labels <- function(x1){
+   x1 <- gsub(pattern = "spray_management",replacement = "",x = x1)
+   x1
+}
+
+data.frame(contrasts = change_labels(meta_cont$hyp[,1]),
+      estimates = meta_cont$Lb,
+      se = meta_cont$se,
+      z_val = meta_cont$zval,
+      pval = meta_cont$pval)
 ```
 Results show with the exclusion of the no spray control, none of the treatments are significantly different, however, early applications treatments on average produced lower yields.
-Also the model was almost significant when assessing recommended_plus as saving more yield than recommended.
+Also the model was almost significant when assessing `Late_plus` as saving more yield than `Recommended`.
 This is probably due to the fact there were more comparisons between these two treatments which allowed a more certain outcome.
@@
 
-What is interesting here is that the variance in the control has increased while the treatments have decreased.
-This is despite the control being the best represented across all experiments.
-However it could also be because it also has a low number of pooled reps per trial.
-Let's look at how well each of the number treatments compare to each other.
-We can use the netmeta package to give a graphical representation of this.
+Let's look at how well each of the number treatments compare to each other. We can use the netmeta package to give a graphical representation of this.
 
@@
    net_con,
-   reference.group = 4,
+   reference.group = 5,
    rightcols = c("effect", "ci", "Pscore"),

### 2020-06-15 03_Prep_data.Rmd
Add disease risk factor

@@
 
+****
+
+### Disease presure factor
+We may wish to investigate the impact of spray management in mitigating the yield loss through the effect on the disease pressure.
+We will set a categorical variable to indicate the amount of disease pressure in the trial, which will be evaluated on the control plot.
+We will create two categories, `lowD` and `highD`. 
+We will use the median `AUDPC` to separate the trials into these two groups.
+
+```{r}
+
+slimmer_PM_dat$D_pres <- NA_character_
+
+Trial_Dpress <- slimmer_PM_dat %>%
+   group_by(trial_ref) %>%
+   filter(fungicide_ai == "control") %>%
+   summarise(AUDPC_C = mean(AUDPC_m, na.rm = TRUE))
+
+median_AUDPC <- median(as.vector(Trial_Dpress$AUDPC_C), na.rm = TRUE)
+
+sort(Trial_Dpress$AUDPC_C)
+
+for(i in unique(slimmer_PM_dat$trial_ref)) {
+   if (is.na(Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"])) {
+      next()
+   }
+
+   if (Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"] < median_AUDPC)
+   {
+      slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <- "lowD"
+   } else{
+      if (Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"] >= median_AUDPC) {
+         slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <- "highD"
+      } else{
+         slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <-
+            NA_character_
+      }
+
+   }
+}
+
+```
+
+Lets have a quick look to examine weather trials with high disease pressure sustain a greater yield loss.
+
+```{r}
+slimmer_PM_dat %>%
+   ggplot(aes(x = D_pres, y = grain_yield.t.ha))+
+   geom_boxplot()
+```
+
+From this plot we see that in the trials with high disease pressure treatments on tended to produce lower yields. 
+There are `r length(unique(slimmer_PM_dat[is.na(slimmer_PM_dat$D_pres),"trial_ref"]))` trials that contained no data for AUDPC and thus produced `NA` values.
+
 ```{r delete_this_chunk, eval=FALSE, include=FALSE}

### 2020-06-15 03_Prep_data.Rmd
add lme to test dose effect in models

@@
    install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, agricolae
+pacman::p_load(tidyverse, kableExtra, agricolae, lme4
 )
@@
    group_by(trial_ref, location, Y_error_type, fungicide_ai) %>%
-   summarise(DMI_trts = length(Y_error_type)) %>%
+   summarise(DMI_treatments = length(Y_error_type)) %>%
    arrange(Y_error_type) %>%
-   kable(caption = "Number of treatments for each trial and the error type reported") %>%
-   #kable_styling(fixed_thread = T) %>% 
+   select(!fungicide_ai)%>%
+   kable(caption = "Number of treatments for each trial and the error type reported", align = "c") %>%
    footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
@@
 
-First lets get a list of trials that reported LSD.  
+First lets get a list the of trials that reported LSD.  
 ```{r all_LSD_trials}
@@
 
-```{r cluster_clusters}
+```{r cluster_clusters, warning=FALSE}
 clusters <-
@@
 
-Single sprays either early, recommended timing or late.
+Single sprays of either:  
+   a) early,  
+   b) recommended timing,  
+   c) late.
 
-Two or more sprays where the first spray was either early, recommended timing, or late.
+Two or more sprays where the first spray was either:  
+   d) early,  
+   e) recommended timing,  
+   f) late.
 
@@
 table(slim_PM_dat$spray_management)
+```
+
+There are few 'Early_plus' treatments, these treatments therefore will have too few comparisons with other treatments in the meta-analysis to provide accurate results.
+Therefore we will remove 'Early_plus' from the analysis.
+
+```{r simpler_clusters_REMOVE}
+slimmer_PM_dat <-
+   slim_PM_dat[slim_PM_dat$spray_management != "Early_plus", ]
 
@@
 
-There are few 'Early_plus' and 'late' treatments, these treatments therefore will have too few comparisons with other treatments in the meta-analysis to be provide accurate results.
-Therefore we will remove 'Early_plus' and 'Late' from the analysis.
+## Test dose effect
 
-```{r simpler_clusters_REMOVE}
-slimmer_PM_dat <-
-   slim_PM_dat[#slim_PM_dat$spray_management != "Late" &
-                  slim_PM_dat$spray_management != "Early_plus", ]
+Earlier we noted there were different doses of propiconazole which might influence our analysis. 
+Lets check this by comparing a linear mixed effect model including and excluding dose. 
+We already have a factor breaking down the dose in the `trial` variable, lets make a new one without dose.
 
+```{r dose_test}
+slimmer_PM_dat$trial_noDose <- paste(slimmer_PM_dat$trial_ref, slimmer_PM_dat$year,
+                 slimmer_PM_dat$location,slimmer_PM_dat$host_genotype,
+                 slimmer_PM_dat$row_spacing,sep = "_")
+
+cbind(Dose = head(slimmer_PM_dat$trial),
+      NoDose = head(slimmer_PM_dat$trial_noDose)) %>%
+   kable()
+```
+
+Lets test the dose effect in a basic linear mixed effect model
+
+```{r dose_lmer}
+
+m1 <-
+   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
+           (1 | trial),
+        data = slimmer_PM_dat)
+
+m2 <-
+   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
+           (1 | trial_noDose),
+        data = slimmer_PM_dat)
+
+anova(m1,m2)
+
+```
+
+Using the model without dose produces a better fit, as shown by the lower AIC and is significantly different from the model `m1`. 
+We will remove the dose term from the trial grouping.
+
+```{r}
+slimmer_PM_dat$trial <- slimmer_PM_dat$trial_noDose
+slimmer_PM_dat <- slimmer_PM_dat[,colnames(slimmer_PM_dat) != "trial_noDose"] #remove second trial column
 write.csv(slimmer_PM_dat, file = "cache/slimmer_PM_clusterdat.csv", row.names = FALSE)
@@
 
-The linear model confirms a significant positive relationship between grain yield and AUDPC. 
 This is not what we would expect and the low R squared value of `r round(summary(lm(grain_yield.t.ha.
@@
 ```{r}
+slimmer_PM_dat <- read.csv(here("cache/slimmer_PM_clusterdat.csv"))
 
@@
 
+write.csv(slimmer_PM_dat, file = here("cache/slimmer_PM_clusterdat.csv"), row.names = FALSE)
 ```

### 2020-06-15 04_MetaAnalysis.Rmd
small corrections

@@
    - Grain yield is our response variable and will be converted to Kg / Ha.  
-   - Trial, which resolves combinations of categorical variables: year, location, row spacing and cultivar; is set as a random intercept.  
+   - Trial, which resolves combinations of categorical variables: year, location, row spacing, fungicide dose and cultivar; is set as a random intercept.  
    - We will test spray management (our treatment) as a fixed effect and random slope to trial.
@@
 First lets compare models with and without a log transformed response variable to evaluate if the log transformed model better fits our assumptions of normality.  
-Next we will test whether including `spray_management` as a significantly accounts for enough variation as a fixed effect variable to be included in the model.  
-Finally we will test whether including `spray_management` as a significantly accounts for enough variation as a random slope to the trial variable.
+Next we will test whether including `spray_management` as a fixed effect variable significantly accounts for enough variation to be included in the model.  
+Finally we will test whether including `spray_management`  as a random slope significantly accounts for enough variation to be used in the model.
 
@@
         data = slimmer_PM_dat)
+
 ```
@@
    method = "ML",
-   random = list(~ spray_management | trial),
-   struct = "UN",
+   random = ~ 1|trial,
+#   struct = "UN",
    data = slimmer_PM_dat

### 2020-06-15 index.Rmd
wordsmithing

@@
 This compendium details the statistical analysis and methods while undertaking a meta-analysis of fungicide efficacy trials for control of powdery mildew in mungbean. 
-This meta-analysis will focus on the main aim of:
+This meta-analysis will focus on the main aim of determining:
 
-> When is the optimum time to spray fungicide to limit the impact of powdery mildew on mungbean yields?
+> When is the optimum time to spray fungicide to limit the effect of powdery mildew on mungbean yields?
 

### 2020-06-16 03_Prep_data.Rmd
improvements to code flow and improved the retention of some data

@@
    install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, agricolae, lme4
+pacman::p_load(tidyverse, kableExtra, agricolae, lme4, here
 )
@@
 ```{r import_data}
-source("R/import_data.R")
-PM_MB_means <- import_data()
+PM_MB_means <- read.csv("cache/1911_PM_MB_means&Ygains.csv")
 
 source("R/same.R") # matches each element of a vector and does not return NAs
+```
+
+The trials `r unique(PM_MB_means[is.na(PM_MB_means$AUDPC_m),"trial_ref"]) `Some trials don't have an estimate of AUDPC and need to be filled in. 
+The following script estimates AUDPC from the final disease severity rating and the first sign of disease information.
+
+```{r}
+source(here("R/AUDPC_for_single_obs.R"))
+
 ```
@@
 
-```{r simpler_clusters_REMOVE}
+```{r simpler_clusters_remove}
 slimmer_PM_dat <-
@@
    geom_boxplot()
+
+slimmer_PM_dat[is.na(slimmer_PM_dat$D_pres),]
 ```

### 2020-06-16 R/slimming_PM_dat.R

@@ -1,9 +1,9 @@
 # This script takes the large dataset and slims it down
-# The slimed down dataset will be used for the Meta-analysis
+# The slimmed down dataset will be used for the Meta-analysis
 
 #source("R/import_data.R")
 # PM_MB_Mtemp <- import_data()
-PM_MB_Mtemp <- read.csv("cache/1911_PM_MB_means&Ygains.csv")
+PM_MB_Mtemp <- PM_MB_means
 
 PM_MB_Mtemp$dose <- NA
 PM_MB_Mtemp[PM_MB_Mtemp$dose_ai.ha <= 70, "dose"] <- "lowDose"

### 2020-06-17 03_Prep_data.Rmd
Changes to incorporate standardised mean differneces in the analysis

@@
 
-write.csv(slimmer_PM_dat, file = here("cache/slimmer_PM_clusterdat.csv"), row.names = FALSE)
 ```
@@
 
-```{r}
+```{r plot_disease_pressure}
 slimmer_PM_dat %>%
@@
 
+### Row spacing
+
+We may want to consider rowspacing in the trials, However one of the locations has NA as the row spacing. 
+Fow now lets assign the most used row spacing of 0.33
+```{r}
+slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),]
+slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),"row_spacing"] <- 0.33
+
+write.csv(slimmer_PM_dat, file = here("cache/slimmer_PM_clusterdat.csv"), row.names = FALSE)
+```
+
 ```{r delete_this_chunk, eval=FALSE, include=FALSE}

### 2020-06-17 04_MetaAnalysis.Rmd
Changes to incorporate standardised mean differneces in the analysis

@@
 
-The best model from the four above is `m11` with the lower AIC of -`r min(anova(m9, m11)$AIC)`
+There is no difference between the models, which means the the simpler model `m11` is the better model, also making it the best model from the four above with the lower AIC of -`r min(anova(m9, m11)$AIC)`
 
@@
 However showed no difference to either the `recommended` or `Late_plus` treatments.
-
-### Imputing sample variances
-
-We need to impute the variances which are missing for a few of the trials.
-These trials `r unique(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),c("location","year", "trial_ref")])$trial_ref` were analysed and reported that there was no significant difference between the treatments in each trial.
-So therefore we need the imputed variances not to show a significant difference.
-
-There are `r sum(is.na(slimmer_PM_dat$yield_error))` treatments without yield error in our data, and `r sum(!is.na(slimmer_PM_dat$yield_error))` where yield error was recorded.
-
-Plotting a histogram of the variances show that the yield is not normally distributed.
-A log transformation, however, shows a normal distribution.
-We can use the mean and standard deviation of the log(V) to sample variances for the treatments where V is missing.
-
-```{r variance_histograms}
-hist_usq(slimmer_PM_dat$yield_error) # yield error is not normally distributed
-hist_usq(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is close to normally distributed 
-```
-
-We will evaluate whether the imputed variances confer a significant difference to the recorded means.
-I created a distance matrix of two standard errors above the mean against two standard errors below the mean.
-If any errors don't overlap, inferring significant difference, the imputed variances are discarded and re-sampled until all treatment variances show no significant differences.
-
-```{r imputing_variances, eval=FALSE, include=FALSE}
-source("./R/impute_yield_err.R")
-
-imputed_error_list <- impute_yield_err(dat = slimmer_PM_dat, 
-                                       xbar = "grain_yield.t.ha", 
-                                       Var = "yield_error",
-                                       reps = "n")
-
-slimmer_PM_dat <- imputed_error_list[["new_dataFrame"]]
-
-```
-
-The imputed variances calculated above don't show the expected positive correlation between grain yield and variance.
-This is unexpected and reflects the inherent variability of the data.
-Therefore we will equalise the variance by using the trial mean squares and use this to calculate the variance for each sample.
 
@@
 
-The use of these imputed MSE was giving a varied outcome each time it was run. We the next code chunk removes the studies without variation to observe what the meta-analysis outcome would be.
+The use of these imputed MSE was giving a varied outcome each time it was run. 
+The next code chunk removes the studies without variation to observe what the meta-analysis outcome would be.
 
@@
 Before analysis let's have a look at the trimmed down modified data.
+
+First, how well the data is compared across the trial years and trials.
+
+```{r table_of_nTreatments}
+kable(table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year),
+                  align = rep('c', 8),
+      caption = "Which treatments and how many treatments are represented in each year") %>%  
+   kable_styling(
+      "striped",
+      fixed_thead = TRUE,
+      full_width = FALSE,
+      position = "center"
+   )
+```
+Treatments Late_plus and early don't have very good comparison to other treatments.
 
@@
 
-There seems like no difference between the treatments, with exception to Late_plus.
-Let's do this plot again, but use the proportion of yield increase compared to the no spray control as the response variable.
-
-It is also important to visualise how well the data is compared across the trial years and trials.
-
-```{r table_of_nTreatments}
-kable(table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year),
-                  align = rep('c', 8),
-      caption = "Which treatments and how many treatments are represented in each year") %>%  
-   kable_styling(
-      "striped",
-      fixed_thead = TRUE,
-      full_width = FALSE,
-      position = "center"
-   )
-```
-Treatments Late_plus and early don't have very good comparison to other treatments.
+There seems like little difference between the treatments, with exception to Late_plus. 
+Let's do this plot again, but lets look at the proportional mean difference between the treatments and the no spray control for each study.  
+This should reduce variation in yield due between trials.
 
@@
 
+Using the mean difference in the treatment effect seems to show the impact of each treatment better than just raw yield.
+We know there is a good deal of variability in our studies and between them. 
+Mungbean produces variable yields between seasons so we should use a response that highlights the difference in the treatment effects that we are interested in and reduce the variability.
+Lets calculate the standardised mean difference for each treatment to reduce the variability in the meta-analysis.
+
+### Caluculate standardised mean differences
+We may wish to undertake the meta-analysis using standardised mean differences. 
+Lets calculate them and add them to the dataframe.
+
+#### Calculate sample variance from mean square errors
+
+```{r MSE_2_SVar}
+slimmer_PM_dat$vi <-
+   slimmer_PM_dat$Y_Msquare / (slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha ^
+                                  2)
+```
+
+```{r}
+slimmer_PM_dat$pooledSD <- NA
+slimmer_PM_dat$vi_C <- NA
+for(T_ref in slimmer_PM_dat$trial_ref){
+
+   # First we neee to Calculate the pooled standard deviation
+   slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "pooledSD"] <- 
+   sqrt(sum((slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"n" ]-1) * slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"vi"])/
+           (sum( slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"n"]) - nrow( slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, ])))
+
+   # Then Create a column with the value of the mean grain yield of the no spray control for comparisons to the treatments means
+   slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"yi_C"] <-  
+      mean(slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref &
+                        slimmer_PM_dat$fungicide_ai == "control",
+                        "grain_yield.t.ha"], na.rm = TRUE)
+
+}
+# Calculate standardised mean difference
+slimmer_PM_dat$grain_SMD <- (slimmer_PM_dat$grain_yield.t.ha - slimmer_PM_dat$yi_C)/ slimmer_PM_dat$pooledSD
+
+```
+
 ## Meta-analysis  
@@
 ```{r metafor_organisation}
-slimmer_PM_dat$spray_management <-
+#remove controls from the data
+dat1 <- slimmer_PM_dat[!slimmer_PM_dat$fungicide_ai == "control",]
+
+dat1$spray_management <-
    factor(
-      slimmer_PM_dat$spray_management,
-      c(
-         "control",
-         "Early",
+      dat1$spray_management,
+      c( "Early",
          "Recommended",
@@
 
-slimmer_PM_dat$yi <- log(slimmer_PM_dat$grain_yield.t.ha)
-
-slimmer_PM_dat$vi <-
-   slimmer_PM_dat$Y_Msquare / (slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha ^
-                                  2)
-
-slimmer_PM_dat$trial_ref <- factor(slimmer_PM_dat$trial_ref)
-slimmer_PM_dat$trial <- factor(slimmer_PM_dat$trial)
 ```
 
+Lets inspect the data to determine if we need to transform the response variable
+
+```{r}
+hist(dat1$grain_yield.t.ha)
+hist(log(dat1$grain_yield.t.ha))
+hist(sqrt(dat1$grain_yield.t.ha))
+hist(dat1$grain_SMD)
+```
+Standardised mean differences have a bit of a long tail however this is not bad and transformations with log or sqrt will not work on negative values.
+
+Lets undertake the meta-analysis, we are using the `spray_management` variable as a moderator and a interactive term to the `trial` variable.
+Because we want to know the difference between all treatments and we have no reference treatment, we will remove the intercept.
 ```{r Metafor-analysis}
-PM_mv_AI <- rma.mv(
+PM_mv <- rma.mv(
+   yi = grain_SMD,
+   vi, 
+   mods = ~ spray_management -1,
+   method = "ML",
+   random = ~ spray_management|trial,
+   struct = "UN",
+   data = dat1
+)
+summary(PM_mv)
+```
+In this result we can see that the `Early` treatment is not significantly different to zero. 
+However the other treatments are significantly different to zero.
+the Qm omnibus test of moderators show the moderators significantly influence the model and we can reject the null hypothesis that there is no difference between the moderators. 
+The Qe test shoes there is a large significant amount of residual Heterogeneity.
+
+Lets see if we can improve this model by including some other random effects and improving the random effect structure in the model.
+
+#### CONTINUE FROM HERE!!!!!!!!!!
+
+```{r}
+
+PM_mv_AI2 <- rma.mv(
    yi,
-   yield_error,
+   vi, # vi or yield error
    mods = ~ spray_management,
@@
    random = ~ 1|trial,
-#   struct = "UN",
    data = slimmer_PM_dat
 )
+
+anova(PM_mv_AI,PM_mv_AI2) # There is no significant difference between these models, Therefore use the simpler model with the lower AIC (PM_mv_AI2)
+
+PM_mv_AI3 <- rma.mv(
+   yi,
+   vi, # vi or yield error
+   mods = ~ spray_management,
+   method = "ML",
+   random = list(~ 1 | location/year/trial_ref, ~ 1 | host_genotype, ~ 1 | row_spacing),
+   data = slimmer_PM_dat
+)
+
+anova(PM_mv_AI2,PM_mv_AI3) # There IS a significant difference between these models, Therefore use the more complicated model with the lower AIC (PM_mv_AI3)
+
+PM_mv_AI4 <- rma.mv(
+   yi,
+   vi, # vi or yield error
+   mods = ~ spray_management,
+   method = "ML",
+   random = list(~ 1 | location/year/trial_ref, ~ 1 | host_genotype),
+   data = slimmer_PM_dat
+)
+
+anova(PM_mv_AI3,PM_mv_AI4) # There is no significant difference between these models, Therefore use the simpler model with the lower AIC (PM_mv_AI4)
+
+profile(PM_mv_AI4, sigma2 = 1)
+
+PM_mv_AI5 <- rma.mv(
+   yi,
+   vi, # vi or yield error
+   mods = ~ spray_management,
+   method = "ML",
+   random = list(~ 1 | location/year/trial_ref),
+   data = slimmer_PM_dat
+)
+
+anova(PM_mv_AI4,PM_mv_AI5) # There is no significant difference between these models, Therefore use the simpler model with the lower AIC (PM_mv_AI4)
+
+summary(PM_mv_AI4)
+
+PM_mv_AI6 <- rma.mv(
+   yi,
+   vi, # vi or yield error
+   mods = ~ spray_management,
+   method = "ML",
+   random = list(~ 1 | location/year/trial_ref, ~ 1 | host_genotype, ~ spray_management | D_pres),
+   data = slimmer_PM_dat
+)
+
+anova(PM_mv_AI6,PM_mv_AI4) # There is no significant difference between these models, Therefore use the simpler model with the lower AIC (PM_mv_AI4)
+
+anova(PM_mv_AI2, PM_mv_AI3)
+
+summary(PM_mv_AI2)
+
+slimmer_PM_dat[is.na(slimmer_PM_dat$AUDPC_m),]
+slimmer_PM_dat[slimmer_PM_dat$location == "Emerald", ]
+table(slimmer_PM_dat$spray_management)
+```
+Lets try analysing the data as a risk reduction. 
+For this we will use the proportion of yield reductions
+```{r}
+dat1 <- slimmer_PM_dat[!slimmer_PM_dat$fungicide_ai == "control",]
+
+dat1$yi <- dat1$grain_SMD
+
+PM_mv_MD <- rma.mv(
+   yi = yi,
+   vi, # vi or yield error
+   mods = ~ spray_management - 1,
+   method = "ML",
+   random = list(~ 1 | location/year , ~1|host_genotype ,~ spray_management|D_pres),
+   data = dat1
+)
+
+summary(PM_mv_MD)
+
+dat1$D_pres
+
+hist(dat1$grain_SMD)
 
@@
 
-According to the results of the omnibus test ($Q_M = 7.32, df = 5, p = 0.1979$) we can't reject the null hypothesis $H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$ that the tested spray management schedules have no benefit to protecting mungbean yields [@Viechtbauer2010].
+According to the results of the [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) ($Q_M = 7.32, df = 5, p = 0.1979$) we can't reject the null hypothesis $H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$ that the tested spray management schedules have no benefit to protecting mungbean yields [@Viechtbauer2010].
 However Late plus ($\beta_4$) was the only moderator showing a significant effect on yields ($z = 2.598; p = 0.0094$). 
@@
 ```{r metafor_contrasts}
-meta_cont <- anova(PM_mv_AI, L = rbind(
+meta_cont <- anova(PM_mv_MD, L = rbind(
    c(0, 1, -1, 0, 0,0),

### 2020-06-18 04_MetaAnalysis.Rmd
Change the mean square error to sampling variance calculation till the formula can be verified.
Edit explaination -still needs editing

@@
 
+```{r remove_studies}
+#slimmer_PM_dat <-
+  # slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),]
+```
+
 #### Calculate sample variance from mean square errors
 
-```{r MSE_2_SVar}
+```{r MSE_2_SVar, eval=FALSE, include=FALSE}
+#calculation when using log of response
 slimmer_PM_dat$vi <-
@@
                                   2)
+
 ```
@@
 
-   # First we neee to Calculate the pooled standard deviation
+   # First we need to Calculate the pooled standard deviation
    slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "pooledSD"] <- 
-   sqrt(sum((slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"n" ]-1) * slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"vi"])/
+   sqrt(sum((slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"n" ]-1) * slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"yield_error"])/
            (sum( slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"n"]) - nrow( slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, ])))
@@
 ```{r Metafor-analysis}
+dat1$vi <- dat1$yield_error
+
 PM_mv <- rma.mv(
@@
 ```
-In this result we can see that the `Early` treatment is not significantly different to zero. 
+In this result we can see that the `Early` treatment is not significantly different to zero, which in this case is the mean of the no spray control. 
 However the other treatments are significantly different to zero.
-the Qm omnibus test of moderators show the moderators significantly influence the model and we can reject the null hypothesis that there is no difference between the moderators. 
-The Qe test shoes there is a large significant amount of residual Heterogeneity.
+The Qm [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, show the moderators significantly influence the model ($Q_M = 7.32, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
+The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 40994.51, df = 105, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
 
@@
 
-#### CONTINUE FROM HERE!!!!!!!!!!
-
 ```{r}
 
-PM_mv_AI2 <- rma.mv(
-   yi,
-   vi, # vi or yield error
+PM_mv_St <- rma.mv(
+   yi = grain_SMD,
+   vi, 
    mods = ~ spray_management,
    method = "ML",
-   random = ~ 1|trial,
-   data = slimmer_PM_dat
-)
-
-anova(PM_mv_AI,PM_mv_AI2) # There is no significant difference between these models, Therefore use the simpler model with the lower AIC (PM_mv_AI2)
-
-PM_mv_AI3 <- rma.mv(
-   yi,
-   vi, # vi or yield error
-   mods = ~ spray_management,
-   method = "ML",
-   random = list(~ 1 | location/year/trial_ref, ~ 1 | host_genotype, ~ 1 | row_spacing),
-   data = slimmer_PM_dat
-)
-
-anova(PM_mv_AI2,PM_mv_AI3) # There IS a significant difference between these models, Therefore use the more complicated model with the lower AIC (PM_mv_AI3)
-
-PM_mv_AI4 <- rma.mv(
-   yi,
-   vi, # vi or yield error
-   mods = ~ spray_management,
-   method = "ML",
-   random = list(~ 1 | location/year/trial_ref, ~ 1 | host_genotype),
-   data = slimmer_PM_dat
-)
-
-anova(PM_mv_AI3,PM_mv_AI4) # There is no significant difference between these models, Therefore use the simpler model with the lower AIC (PM_mv_AI4)
-
-profile(PM_mv_AI4, sigma2 = 1)
-
-PM_mv_AI5 <- rma.mv(
-   yi,
-   vi, # vi or yield error
-   mods = ~ spray_management,
-   method = "ML",
-   random = list(~ 1 | location/year/trial_ref),
-   data = slimmer_PM_dat
-)
-
-anova(PM_mv_AI4,PM_mv_AI5) # There is no significant difference between these models, Therefore use the simpler model with the lower AIC (PM_mv_AI4)
-
-summary(PM_mv_AI4)
-
-PM_mv_AI6 <- rma.mv(
-   yi,
-   vi, # vi or yield error
-   mods = ~ spray_management,
-   method = "ML",
-   random = list(~ 1 | location/year/trial_ref, ~ 1 | host_genotype, ~ spray_management | D_pres),
-   data = slimmer_PM_dat
-)
-
-anova(PM_mv_AI6,PM_mv_AI4) # There is no significant difference between these models, Therefore use the simpler model with the lower AIC (PM_mv_AI4)
-
-anova(PM_mv_AI2, PM_mv_AI3)
-
-summary(PM_mv_AI2)
-
-slimmer_PM_dat[is.na(slimmer_PM_dat$AUDPC_m),]
-slimmer_PM_dat[slimmer_PM_dat$location == "Emerald", ]
-table(slimmer_PM_dat$spray_management)
-```
-Lets try analysing the data as a risk reduction. 
-For this we will use the proportion of yield reductions
-```{r}
-dat1 <- slimmer_PM_dat[!slimmer_PM_dat$fungicide_ai == "control",]
-
-dat1$yi <- dat1$grain_SMD
-
-PM_mv_MD <- rma.mv(
-   yi = yi,
-   vi, # vi or yield error
-   mods = ~ spray_management - 1,
-   method = "ML",
-   random = list(~ 1 | location/year , ~1|host_genotype ,~ spray_management|D_pres),
+   random = list(~ 1|trial),
    data = dat1
@@
 
-summary(PM_mv_MD)
-
-dat1$D_pres
-
-hist(dat1$grain_SMD)
-
+AIC(PM_mv_St)
+anova(PM_mv, PM_mv_St)
 ```
+The simpler `PM_mv_St` model explains significantly less variation as the more complicated model `PM_mv`. So we will keep the original model.
 
@@
 
-According to the results of the [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) ($Q_M = 7.32, df = 5, p = 0.1979$) we can't reject the null hypothesis $H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$ that the tested spray management schedules have no benefit to protecting mungbean yields [@Viechtbauer2010].
-However Late plus ($\beta_4$) was the only moderator showing a significant effect on yields ($z = 2.598; p = 0.0094$). 
-The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 538.26, df = 141, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
-
 The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis.
@@
 
+### Profile plots  
+Lets inspect the profile plots to ensure the model is not over-fitted. 
+We expect to see the estimate align with the peak of the curve. 
+Also that the shape of the line is a curve.
+
+```{r}
+profile(PM_mv , tau2 = 1)
+profile(PM_mv , tau2 = 2)
+profile(PM_mv , tau2 = 3)
+profile(PM_mv , tau2 = 4)
+profile(PM_mv , tau2 = 5)
+```
+
 *****
@@
 ```{r metafor_contrasts}
-meta_cont <- anova(PM_mv_MD, L = rbind(
-   c(0, 1, -1, 0, 0,0),
-   # early vs Recommended
-   c(0, 1, 0, -1, 0,0),
-   # early vs recommended plus
-   c(0, 1, 0, 0, -1,0),
-   # early vs Late 
-   c(0, 1, 0, 0, 0,-1),
-   # early vs Late plus
-   c(0, 0, -1, 1, 0,0),
-   # Recommended plus vs recommended
-   c(0, 0, -1, 0, 1,0),
-   # Late  vs Recommended
-   c(0, 0, -1, 0, 0,1),
-   # Late_plus  vs Recommended
-   c(0, 0, 0, -1, 1,0),
-   # Late vs Recommended plus
-   c(0, 0, 0, -1, 0,1),
-   # Late_plus  vs Recommended plus
-   c(0, 0, 0, 0, -1,1)
-)) # Late vs Late_plus
+meta_cont <- anova(PM_mv, L = rbind(
+   c(-1, 1, 0, 0,0),
+   c(-1, 0, 1, 0,0),
+   c(-1, 0, 0, 1,0),
+   c(-1, 0, 0, 0,1),
+   c(0, -1, 1, 0,0),
+   c(0, -1, 0, 1,0),
+   c(0, -1, 0, 0,1),
+   c(0, 0, -1, 1,0),
+   c(0, 0, -1, 0,1),
+   c(0, 0, 0, -1,1)
+   ))
 
@@
 
+source("R/p_star.R")
+
 data.frame(contrasts = change_labels(meta_cont$hyp[,1]),
@@
       z_val = meta_cont$zval,
-      pval = meta_cont$pval)
+      pval = meta_cont$pval,
+      VisP = p_star(meta_cont$pval))
 ```
-Results show with the exclusion of the no spray control, none of the treatments are significantly different, however, early applications treatments on average produced lower yields.
-Also the model was almost significant when assessing `Late_plus` as saving more yield than `Recommended`.
-This is probably due to the fact there were more comparisons between these two treatments which allowed a more certain outcome.
+Results show with the exclusion of the no spray control, `Early` applications are significantly worse than all other treatments leading to lower yield estimates. 
+`Late_plus` is estimated as saving the most yield compared and is significantly higher than all other treatments except `recommended_plus`.  
 Let's view these comparisons in a plot.
 
-First we will format the results into a data frame and back-transform the log values by using the exponent function
+First we will format the results into a data frame.
 ```{r metafor_results}
-results_AI <- data.frame(cbind(exp(PM_mv_AI$b),
-                               exp((PM_mv_AI$ci.lb)),
-                               exp(PM_mv_AI$ci.ub)))
+results_AI <- data.frame(cbind(PM_mv$b,
+                               PM_mv$ci.lb,
+                               PM_mv$ci.ub))
 
@@
    factor(
-      c(
-         "control",
-         "Early",
+      c( "Early",
          "Recommended",
@@
 
-efficacy$se <- PM_mv_AI$se
+efficacy$se <- PM_mv$se
 colnames(efficacy) <-
@@
    geom_hline(
-      yintercept = c(0.8, 1, 1.2, 1.4),
+      yintercept = seq(-0.5,1.5, by = 0.2),
       color = "grey80",
@@
 
-Let's look at how well each of the number treatments compare to each other. We can use the netmeta package to give a graphical representation of this.
+Let's look at how well each of the number treatments compare to each other.
+
+We can use the netmeta package to give a graphical representation of the pairwise comparisons.
 
@@
    group_by(trial, spray_management, n) %>%
-   summarize(yi_mean = mean(yi),
-             vi_mean = mean(vi)) %>%
+   summarize(yi_mean = mean(grain_SMD),
+             vi_mean = mean(yield_error)) %>%
    ungroup()

### 2020-06-18 R/p_star.R
Function for easily visualise pvals

@@ -1,0 +1,11 @@
+p_star <- function(x){
+   if(x > 0.08)return("")
+   if(x <= 0.08 &
+      x > 0.05) return(".")
+   if(x <= 0.05 &
+      x > 0.01) return("*")
+   if(x <= 0.01 &
+      x > 0.001) return("**")
+   if(x < 0.001) return("***")
+   
+}

### 2020-06-19 04_MetaAnalysis.Rmd
I finally understood why we divide by n to get sample variance from mean squared error. And some other tidying up

@@
 
-### Caluculate standardised mean differences
-We may wish to undertake the meta-analysis using standardised mean differences. 
-Lets calculate them and add them to the dataframe.
+### Formatting Variance
 
 ```{r remove_studies}
-#slimmer_PM_dat <-
-  # slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),]
+any(is.na(slimmer_PM_dat$yield_error))
+
+slimmer_PM_dat$vi <- slimmer_PM_dat$yield_error
 ```
@@
 
-```{r MSE_2_SVar, eval=FALSE, include=FALSE}
+$MSE = Var + bias$  
+However if our MSE was calculated from an unbiased sample we can assume $bias = 0$ and therefore:  
+$MSE = Var$
+
+To calculate the sample variance (for each treatment in the tria) from the mean square error (Trial variance) all we need to do is divide by the number of samples in each treatment.
+We can show this because:  
+$MSE = \frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n - 1}$  
+Where the sum of squares for the fungicide treatment estimator ($y$) is divided by the number of fungicide treatments ($n$).
+
+The sample variance is a similar formula except we use $x$ instead of $y$.  
+$S_{Var} = \frac{\sum_{x_1}^{x_n}(x_i - \overline{x})^2}{n - 1}$  
+$x$ being each observation within the experiment and $n$ being the number of samples in the whole trial.
+Therefore: 
+$S_{Var} = \frac{\frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n_y - 1}}{n_{x}}$  
+Where $n_x$ is the number of samples within each treatment.
+
+```{r MSE_2_SVar}
 #calculation when using log of response
-slimmer_PM_dat$vi <-
-   slimmer_PM_dat$Y_Msquare / (slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha ^
-                                  2)
+# slimmer_PM_dat$vi <-
+#    slimmer_PM_dat$Y_Msquare / (slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha ^
+#                                   2)
+#
+slimmer_PM_dat$vi2 <- 
+   slimmer_PM_dat$Y_Msquare / 
+   slimmer_PM_dat$n
 
@@
 
-```{r}
+We have removed the studies that don't report any variance from the analysis.
+
+### Caluculate standardised mean differences
+We may wish to undertake the meta-analysis using standardised mean differences. 
+Lets calculate them and add them to the dataframe.
+```{r StandardisedMeanDifference}
 slimmer_PM_dat$pooledSD <- NA
@@
 
+We can use the same sample variance because if you add or subtract from a random variable the variance does not change.
+
+Lets simplify our data
+```{r metafor_organisation}
+dat1 <-
+   slimmer_PM_dat %>%
+   filter(fungicide_ai != "control") %>% #remove controls from the data
+   mutate(spray_management =
+             factor(
+      spray_management,
+      c( "Early",
+         "Recommended",
+         "Recommended_plus",
+         "Late",
+         "Late_plus"
+      )))%>%
+   select(
+      trial,
+      trial_ref,
+      location,
+      year,
+      row_spacing,
+      host_genotype ,
+      spray_management,
+      fungicide_ai,
+      D_pres,
+      grain_yield.t.ha,
+      grain_SMD,
+      vi,
+      vi2
+   )
+```
+
 ## Meta-analysis  
@@
 
-```{r metafor_organisation}
-#remove controls from the data
-dat1 <- slimmer_PM_dat[!slimmer_PM_dat$fungicide_ai == "control",]
-
-dat1$spray_management <-
-   factor(
-      dat1$spray_management,
-      c( "Early",
-         "Recommended",
-         "Recommended_plus",
-         "Late",
-         "Late_plus"
-      )
-   )
-
-```
-
 Lets inspect the data to determine if we need to transform the response variable
@@
 ```{r Metafor-analysis}
-dat1$vi <- dat1$yield_error
-
 PM_mv <- rma.mv(
@@
 However the other treatments are significantly different to zero.
-The Qm [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, show the moderators significantly influence the model ($Q_M = 7.32, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
+The Qm [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, show the moderators significantly influence the model ($Q_M = 85.232, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
 The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 40994.51, df = 105, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
@@
 
-#### Investigate impact of imputing Mean square errors on the meta-analysis outcomes
-
-```{r Initiak_ReRunMetafor, eval=FALSE, include=FALSE}
-# It was noticed that the meta analysis was giving different outcomes.
-#     (not just small variations in estimates and p-values, but large variations)
-# The following chunks investigate how much these values vary and change the outcomes
-#
-# This chunk creates a data.frame from the meta-analysis which was run in the previous chunk `Metafor-analysis`
-# and sets the iteration number as 0
-# this data.frame is appended with additional iterations to in the following chunk
-
-summary(PM_mv_AI)
-
-dat1 <- data.frame(
-   iteration = 0,
-   mods = names(coef(PM_mv_AI)),
-   coefs = coef(PM_mv_AI),
-   se = PM_mv_AI$se,
-   zval = PM_mv_AI$zval,
-   pval = PM_mv_AI$pval,
-   ci.lb = PM_mv_AI$ci.lb,
-   ci.ub = PM_mv_AI$ci.ub,
-   row.names = NULL
-)
-
-# commented the code below so the file does not get overwritten
-#write.csv(dat1, "./cache/metaIteration.csv", row.names = FALSE)
-```
-
-```{r run_iterations_asJobscript, eval=FALSE, include=FALSE}
-# This chunk iterates the imputation of MSEs and reruns the metafor analysis
-# each time it iterates it appends some of the output information into the "metaIteration.csv" file
-# To increase the speed the calculations/iterations it is send to multiple jobs in the background.
-#
-# WARNING don't run a high number of iterations without increasing sys.sleep
-# sys.sleep should not be reduced below 4 for 50 iterations and
-# below 0.5 for 10 iterations
-for (ITERATE in 1:50) {
-   rstudioapi::jobRunScript(
-      "./R/ReRun_metafor-grainyield.R",
-      workingDir = here::here(),
-      name = "metafor_iteration",
-   )
-   Sys.sleep(15)
-}
-```
-
-```{r coef_iteration, eval=FALSE, include=FALSE}
-# This chunk plots the coefficients and corresponding confidence intervals 
-#     for each iteration of the metafor calculation to visualise how much variation 
-#     the imputed MSE imbue on the moderator coefs
-
-# This function alters the moderator names so they are plotted legibly in the facet strips
-change_labels <- function(x1){
-   x1 <- gsub(pattern = "spray_management",replacement = "",x = x1)
-   x1 <- gsub(pattern = "_",replacement = "\n",x = x1)
-   x1
-}
-
-metaI <- read.csv("./cache/metaIteration.csv")
-metaI %>%
-   ggplot(aes(x = iteration ,y = coefs,))+
-   geom_ribbon(aes(ymax = ci.ub, ymin = ci.lb, x = iteration), fill = "grey70")+
-   geom_line()+
-   facet_grid(cols = vars(mods), labeller = labeller(mods = change_labels))+
-   theme(strip.text.x = element_text(size = 9)) # change facet strip label font size
-
-```
-
-```{r pval_iteration_plot, eval=FALSE, include=FALSE}
-# Plot the p - values of the spray_management moderators
-# transform y axis on log scale
-metaI %>%
-   ggplot(aes(x = iteration , y = pval, )) +
-   geom_line() +
-   scale_y_log10() +
-   geom_hline(
-      yintercept = c(0.05, 0.001),
-      colour = "grey50",
-      linetype = 2
-   ) +
-   facet_grid(cols = vars(mods),
-              labeller = labeller(mods = change_labels)) +
-   theme(strip.text.x = element_text(size = 9)) +
-   geom_text(
-      aes(
-         y = 0.05,
-         x = 1,
-         label = c("P = 0.05")
-      ),
-      size = 3,
-      colour = "grey50",
-      hjust = 0,
-      vjust = -0.5
-   )+
-      geom_text(
-      aes(
-         y = 0.001,
-         x = 1,
-         label = c("P = 0.001")
-      ),
-      size = 3,
-      colour = "grey50",
-      hjust = 0,
-      vjust = -0.5
-   )
-
-```
-
-```{r metafor_summary}
-summary(PM_mv_AI)
-```
-
 The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis.
 The second table is in two parts(left and right). 
-The left part indicates the level of acceptable rho (variation) when comparing treatments.
+The left part, rho, is the correlation of variation between the specified treatments. 
 All comparisons were acceptable except for a comparison between `Early` and `Late_plus`, `0.000` rho.
-`Early` and `Late_plus` treatments never occurred within the same trial which is indicated by the right side of the table.
+`Early` and `Late_plus` treatments never occurred within the same trial which is indicated by the right side of the table (hence the warning).
 
-The fixed effects, in the last table, showed that yields in single early spray treatments are not significantly different to the no spray control. 
-Also commencing spray management schedules at first sign of disease (Recommended), or between 7 - 19 days after first sign (late) produced significantly higher yields compared to the no spray control.
-On average a spray schedule with two or more applications stating late (7 - 19 days after first sign of powdery mildew) produced the highest yields.
+The fixed effects, in the last table, showed that yields in single early spray treatments are not significantly different to zero, or the no spray control.
 
@@
 Also that the shape of the line is a curve.  
+Caution! this will take some time to run.
 
@@
 *****
+### Metafor comparisons
 

### 2020-06-19 R/p_star.R
use sapply to make the function work

@@ -1,4 +1,5 @@
-p_star <- function(x){
+p_star <- function(v1){
+   sapply(v1, function(x){
    if(x > 0.08)return("")
    if(x <= 0.08 &
       x > 0.05) return(".")
@@ -7,5 +8,5 @@ p_star <- function(x){
    if(x <= 0.01 &
       x > 0.001) return("**")
    if(x < 0.001) return("***")
-   
+   })
 }

### 2020-06-19 03_Prep_data.Rmd
Typos and some words for clarification

@@
    distinct()
+Trials
 ```
+Lets use this list of trials to subset the data and calculate sampling variances.
 
@@
 
-```{r LSD_2_Sampling Variance}
+```{r LSD_2_Sampling_Variance}
 
@@
 
-We may want to consider rowspacing in the trials, However one of the locations has NA as the row spacing. 
+We may want to consider row spacing in the trials, However one of the locations has NA as the row spacing. 
 Fow now lets assign the most used row spacing of 0.33

### 2020-06-22 index.Rmd
Grammar and spelling edits, Markdown styling
Also removes one "Other research question" that's not important to this work

@@
 
-This compendium details the statistical analysis and methods while undertaking a meta-analysis of fungicide efficacy trials for control of powdery mildew in mungbean. 
-This meta-analysis will focus on the main aim of determining:
+This research compendium details the statistical analysis and methods of a meta-analysis of fungicide efficacy trials for controlling powdery mildew in mungbean.
+The meta-analysis's main aim is to determine:
 
@@
 ## Contents
-This compendia is broken down into seven sections:
+This compendium is broken down into seven sections:
 
-   1. [Details of the experiments which were included in the analysis][Studies considered in meta-analysis].  
-   2. [Preliminary data exploration which investigates possible variables that could influence the meta-analysis.][Preliminary Analysis]  
+   1. [Details of the experiments, which were included in the analysis][Studies considered in meta-analysis]  
+   2. [Preliminary data exploration which investigates possible variables that could influence the meta-analysis][Preliminary Analysis]  
       a. [Fungicides][Fungicides]  
@@
    3. [Preparation of data for the meta-analysis][Prepare data for meta-analysis]  
-   4. [Meta-analysis of the effect of fungicide spray scheduale on yield loss][Meta-analysis]  
-   5. [Meta-analysis of the effect of fungicide spray scheduale on disease severity and yield loss][AUPDC meta-analysis]
+   4. [Meta-analysis of the effect of fungicide spray schedule on yield loss][Meta-analysis]  
+   5. [Meta-analysis of the effect of fungicide spray schedule on disease severity and yield loss][AUPDC meta-analysis]
    6. [Manuscript Wireframe][Manuscript wire frame]
@@
 
-## Other research questions which are not the focus of this study
-+ How has the first sign of powdery mildew changed over the seasons and between
-experimental sites?
+## Other research questions, which are not the focus of this study
 
-+ Is there an ideal planting time, or fungicide management strategy, which could
-make use of powdery mildew defoliation during pod maturation resulting in an
-increased yield?
++ How has the first sign of powdery mildew changed between the seasons and experimental sites?
+
++ Is there an ideal planting time, or fungicide management strategy, which could make use of powdery mildew defoliation during pod maturation resulting in an increased yield?
 
 + Do infections that occur before flowering increase the probable yield loss?
-
-+ What is the length of a mungbean season and how has it varied in this trial?
-
-   - This data has not been collected or is not accurate enough to be useful to
-   answer this question.
 
@@
 + Variability among host genotypes.
-   + The probable influence of season might be influenced by host genotype. This
-   is because newer varieties were adopted into experimental trials as they were
-   released.
 
-   + Between 2001 and 2015 mungbean genotype changed from Green Diamond, Berken,
-   Crystal to Jade. Jade was the only cultivar used between 2015 and 2019.
+   + The probable influence of season might be influenced by host genotype.
+   This is because newer varieties were adopted into experimental trials as they were released.
 
-   + Estimations of plant maturity stages over each growing season. These
-   estimations might able to be computed using APSIM.
+   + Between 2001 and 2015 mungbean genotype changed from Green Diamond, Berken, Crystal to Jade.
+   Jade was the only cultivar used between 2015 and 2019.
+
+   + Estimations of plant maturity stages over each growing season.
+    These estimations might able to be computed using APSIM.

### 2020-06-22 02_Preliminary_analysis.Rmd
Move AUDPC plotting to Preliminary analysis

@@
 In most years, regardless of the age of the crop, powdery mildew establishes in March.
+
+### AUDPC visualise raw data
+
+First lets check we have all the AUDPC observations.
+
+```{r AUDPC_check}
+PM_MB_means %>%
+   filter(is.na(AUDPC_m)) %>%
+   distinct(trial_ref, location, year,AUDPC_m, first_sign_disease, final_assessment)%>%
+   kable(align = "c")
+```
+
+The trials `r unique(PM_MB_means[is.na(PM_MB_means$AUDPC_m),"trial_ref"]) ` don't have an estimate of AUDPC and need to be filled in. 
+The following script estimates AUDPC from the final disease severity rating and the first sign of disease information.
+
+```{r SingleObsAUDPC}
+source(here("R/AUDPC_for_single_obs.R"))
+write.csv(PM_MB_means,
+          "cache/1911_PM_MB_means&Ygains.csv", row.names = FALSE)
+```
+
+>How well does 'area under the disease progress curve' (AUDPC) predict grain yield?
+
+and _Does spray_management scenario mitigate yield loss through reducing AUDPC?_
+
+We would expect to see grain yield decline with increasing AUDPC. Let's just plot yield vs AUDPC.
+
+```{r Yield_vs_AUDPC}
+
+plot(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means)
+abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means))
+
+```
+
+There appears to be a weak positive relationship between the two continuous variables.  
+Does a linear model confirm this?
+
+```{r AUDPClm}
+summary(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means))
+```
+
+This is not what we would expect and the low R squared value of `r round(summary(lm(grain_yield.t.ha.
+~ AUDPC_m, data = PM_MB_means))$adj.r.squared,3)` perhaps there are additional factors influencing this relationship.
+
+Lets tease out variation due to trial location, season, row spacing, and other seasonal variables are preventing us from seeing the expected relationship. 
+Let's do the plot again for each trial where there are no missing values.  
+Note: The plots are ordered by mean yield of the trial.
+
+```{r AUDPCxTrial}
+sm2lg <- PM_MB_means %>%
+   group_by(trial_ref) %>%
+   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
+   arrange(TY)
+
+for (i in sm2lg$trial_ref) {
+   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
+   if (any(is.na(dat1$grain_yield.t.ha.))) {
+      next
+   }
+   if (any(is.na(dat1$AUDPC_m))) {
+      next
+   }
+
+   plot(
+      grain_yield.t.ha. ~ AUDPC_m,
+      data = dat1,
+      main = paste(dat1$location[1], (dat1$year[1])),
+      ylim = c(0, max(PM_MB_means$grain_yield.t.ha., na.rm = TRUE)),
+      xlim = c(0, max(PM_MB_means$AUDPC_m, na.rm = TRUE))
+   )
+   abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = dat1))
+   points(grain_yield.t.ha. ~ AUDPC_m,
+          data = dat1[dat1$fungicide_ai == "control",],
+          col = "red")
+
+}
+```
+
+This sequence of graphs show that AUDPC and disease incidence tends not impact on yields if the season is a low yielding, ie lower than 1 tonne per hectare.  
+The higher the yield the greater greater the influence on the disease on the yield especially if the crop is high yielding with AUDPC also being large enough to reduce yield.
+
+Let's have a look again at the same sequence of graphs and analyses for area under the disease progress _stairs_.
+
+```{r Yield_vs_AUDPS}
+plot(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means)
+abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means))
+
+summary(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means))
+
+sm2lg <- PM_MB_means %>%
+   group_by(trial_ref) %>%
+   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
+   arrange(TY)
+
+for (i in sm2lg$trial_ref) {
+   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i,]
+   if (any(is.na(dat1$grain_yield.t.ha.))) {
+      next
+   }
+   if (any(is.na(dat1$AUDPS_m))) {
+      next
+   }
+
+   plot(
+      grain_yield.t.ha. ~ AUDPS_m,
+      data = dat1,
+      main = paste(dat1$location[1], (dat1$year[1])),
+      ylim = c(0, max(
+         PM_MB_means$grain_yield.t.ha., na.rm = TRUE
+      )),
+      xlim = c(0, max(PM_MB_means$AUDPS_m, na.rm = TRUE))
+   )
+   abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = dat1))
+   points(grain_yield.t.ha. ~ AUDPS_m,
+          data = dat1[dat1$fungicide_ai == "control", ],
+          col = "red")
+
+}
+
+```
+The plots from the AUPDS is similar to the AUDPC, however according to the linear model the AUDPC is a better, significant fit.
+
+A mixed effect model would be more suitable to investigate the interactive effects of location, season, and trial. 
+The mixed effect model will help us decide on the best approach and structure for our meta-analysis model.

### 2020-06-22 03_Prep_data.Rmd
Move AUDPC plotting to Preliminary analysis
Change headings order to improve flow

@@
 
-The trials `r unique(PM_MB_means[is.na(PM_MB_means$AUDPC_m),"trial_ref"]) `Some trials don't have an estimate of AUDPC and need to be filled in. 
-The following script estimates AUDPC from the final disease severity rating and the first sign of disease information.
-
-```{r}
-source(here("R/AUDPC_for_single_obs.R"))
-
-```
-
 ## Standardising sample variance  
@@
              fungicide_ai == "propiconazole") %>%
-   group_by(trial_ref, location, Y_error_type, fungicide_ai) %>%
+   group_by(trial_ref, location,year ,Y_error_type, fungicide_ai) %>%
    summarise(DMI_treatments = length(Y_error_type)) %>%
@@
    # Replace the values in the dataset
-   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error <-
+   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$yield_error <-
       Sv
-   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$Y_error_type <-
+   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Y_error_type <-
       "SamplingVariance"
@@
 ```
+
+### Check variance of data-set
+Our data currently uses sample variance to define the yield error. We should expect that when yield increases so does the variance. Let's quickly plot this to check.
+
+```{r Var_mean_sqaures}
+# redefine sample variance calculated from mean square
+PM_MB_means$vi <-
+   PM_MB_means$Y_Msquare /
+   (PM_MB_means$n * PM_MB_means$grain_yield.t.ha ^ 2)
+
+PM_MB_means %>%
+   ggplot(aes(x = grain_yield.t.ha, y = vi)) +
+   geom_point()
+```
+
+We see here that the sample variance generally decreases or has no association with the grain yield.
+This might be due to the unpredictable nature of mungbeans, however going forward we will use mean squares which defines between trial variation and is a the more generic error term.
+
+```{r Var_MeanSquarePlot}
+slimmer_PM_dat %>%
+   ggplot(aes(x = grain_yield.t.ha, y = Y_Msquare)) +
+   geom_point()
+```
+
+&nbsp;  
+&nbsp;  
+&nbsp;
 
@@
 
+****
+
 ## Test dose effect
@@
 
-Using the model without dose produces a better fit, as shown by the lower AIC and is significantly different from the model `m1`. 
-We will remove the dose term from the trial grouping.
+Using the model without dose produces a lower AIC, however we should accept the data with dose as there is a significant difference between the models and we should accept the more complicated model `m2`.
+We will retain dose in the trial factor.
 
 ```{r}
-slimmer_PM_dat$trial <- slimmer_PM_dat$trial_noDose
 slimmer_PM_dat <- slimmer_PM_dat[,colnames(slimmer_PM_dat) != "trial_noDose"] #remove second trial column
@@
 ```
-
-Our data currently uses sample variance to define the yield error. We should expect that when yield increases so does the variance. Let's quickly plot this to check.
-
-```{r Var_mean_sqaures}
-# redefine sample variance calculated from mean square
-slimmer_PM_dat$vi <-
-   slimmer_PM_dat$Y_Msquare /
-   (slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha ^ 2)
-
-slimmer_PM_dat %>%
-   ggplot(aes(x = grain_yield.t.ha, y = vi)) +
-   geom_point()
-```
-
-We see here that the sample variance generally decreases or has no association with the grain yield.
-This might be due to the unpredictable nature of mungbeans, however going forward we will use mean squares which defines between trial variation and is a the more generic error term.
-
-```{r Var_MeanSquarePlot}
-slimmer_PM_dat %>%
-   ggplot(aes(x = grain_yield.t.ha, y = Y_Msquare)) +
-   geom_point()
-```
-
-&nbsp;  
-&nbsp;  
-&nbsp;
-
-## AUDPC visualise raw data
-
->How well does 'area under the disease progress curve' (AUDPC) predict grain yield?
-
-and _Does spray_management scenario mitigate yield loss through reducing AUDPC?_
-
-We would expect to see grain yield decline with increasing AUDPC. Let's just plot yield vs AUDPC.
-
-```{r Yield_vs_AUDPC}
-
-plot(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means)
-abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means))
-
-```
-
-There appears to be a weak positive relationship between the two continuous variables.  
-Does a linear model confirm this?
-
-```{r AUDPClm}
-summary(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means))
-```
-
-This is not what we would expect and the low R squared value of `r round(summary(lm(grain_yield.t.ha.
-~ AUDPC_m, data = PM_MB_means))$adj.r.squared,3)` perhaps there are additional factors influencing this relationship.
-
-Lets tease out variation due to trial location, season, row spacing, and other seasonal variables are preventing us from seeing the expected relationship. 
-Let's do the plot again for each trial where there are no missing values.  
-Note: The plots are ordered by mean yield of the trial.
-
-```{r AUDPCxTrial}
-sm2lg <- PM_MB_means %>%
-   group_by(trial_ref) %>%
-   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
-   arrange(TY)
-
-for (i in sm2lg$trial_ref) {
-   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
-   if (any(is.na(dat1$grain_yield.t.ha.))) {
-      next
-   }
-   if (any(is.na(dat1$AUDPC_m))) {
-      next
-   }
-
-   plot(
-      grain_yield.t.ha. ~ AUDPC_m,
-      data = dat1,
-      main = paste(dat1$location[1], (dat1$year[1])),
-      ylim = c(0, max(PM_MB_means$grain_yield.t.ha., na.rm = TRUE)),
-      xlim = c(0, max(PM_MB_means$AUDPC_m, na.rm = TRUE))
-   )
-   abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = dat1))
-   points(grain_yield.t.ha. ~ AUDPC_m,
-          data = dat1[dat1$fungicide_ai == "control",],
-          col = "red")
-
-}
-```
-
-This sequence of graphs show that AUDPC and disease incidence tends not impact on yields if the season is a low yielding, ie lower than 1 tonne per hectare.  
-The higher the yield the greater greater the influence on the disease on the yield especially if the crop is high yielding with AUDPC also being large enough to reduce yield.
-
-Let's have a look again at the same sequence of graphs and analyses for area under the disease progress _stairs_.
-
-```{r Yield_vs_AUDPS}
-plot(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means)
-abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means))
-
-summary(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means))
-
-sm2lg <- PM_MB_means %>%
-   group_by(trial_ref) %>%
-   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
-   arrange(TY)
-
-for (i in sm2lg$trial_ref) {
-   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i,]
-   if (any(is.na(dat1$grain_yield.t.ha.))) {
-      next
-   }
-   if (any(is.na(dat1$AUDPS_m))) {
-      next
-   }
-
-   plot(
-      grain_yield.t.ha. ~ AUDPS_m,
-      data = dat1,
-      main = paste(dat1$location[1], (dat1$year[1])),
-      ylim = c(0, max(
-         PM_MB_means$grain_yield.t.ha., na.rm = TRUE
-      )),
-      xlim = c(0, max(PM_MB_means$AUDPS_m, na.rm = TRUE))
-   )
-   abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = dat1))
-   points(grain_yield.t.ha. ~ AUDPS_m,
-          data = dat1[dat1$fungicide_ai == "control", ],
-          col = "red")
-
-}
-
-```
-The plots from the AUPDS is similar to the AUDPC, however according to the linear model the AUDPC is a better, significant fit.
-
-A mixed effect model would be more suitable to investigate the interactive effects of location, season, and trial. 
-The mixed effect model will help us decide on the best approach and structure for our meta-analysis model.
-
-****
 

### 2020-06-22 03_Prep_data.Rmd
Correct Variance calculation as we are not log transforming grain yield in the plot Change data for variance plotting to be in line with the flow of the document

@@
    PM_MB_means$Y_Msquare /
-   (PM_MB_means$n * PM_MB_means$grain_yield.t.ha ^ 2)
+   (PM_MB_means$n)
 
 PM_MB_means %>%
-   ggplot(aes(x = grain_yield.t.ha, y = vi)) +
+   ggplot(aes(x = grain_yield.t.ha., y = vi)) +
    geom_point()
+
 ```
@@
 ```{r Var_MeanSquarePlot}
-slimmer_PM_dat %>%
-   ggplot(aes(x = grain_yield.t.ha, y = Y_Msquare)) +
+PM_MB_means %>%
+   ggplot(aes(x = grain_yield.t.ha., y = Y_Msquare)) +
    geom_point()

### 2020-06-22 03_Prep_data.Rmd
spell check

@@
 
-### Disease presure factor
+### Disease pressure factor
 We may wish to investigate the impact of spray management in mitigating the yield loss through the effect on the disease pressure.
@@
 
-Lets have a quick look to examine weather trials with high disease pressure sustain a greater yield loss.
+Lets have a quick look to examine whether trials with high disease pressure sustain a greater yield loss.
 
@@
    geom_boxplot()
-
-slimmer_PM_dat[is.na(slimmer_PM_dat$D_pres),]
 ```
@@
 We may want to consider row spacing in the trials, However one of the locations has NA as the row spacing. 
-Fow now lets assign the most used row spacing of 0.33
+For now lets assign the most used row spacing of 0.33
 ```{r}

### 2020-06-22 02_Preliminary_analysis.Rmd
Spellcheck and Markdown formatting

@@
 library(theme.usq)
-theme_set(theme_usq())
+theme_set(theme_usq()
+)
 ```
@@
 ## Explore and Visualise Data
-First lets import the data. Each row provides the mean yield for each experimental treatment.
+First let's import the data.
+Each row provides the mean yield for each experimental treatment.
+
 ```{r echo=TRUE, message=FALSE, warning=FALSE}
-# Import data
 PM_MB_means <- import_data() 
@@
 The data explored in the `PM_MB_means` data frame is a list of mean values from each treatment in each respective experiment.
-These preliminary analyses will focus on the change in mungbean yields which is attributable to the fungicide treatment. 
+These preliminary analyses will focus on the change in mungbean yields, which is attributable to the fungicide treatment. 
 Later in this document we will also consider the impact of fungicide treatments on disease incidence/severity.
@@
 On this page, unless stated, the following plots and analyses were made disregarding other effects.
-The following factors are propostulated to potentially influence mungbean grain yield and/or powdery mildew mean plot severity.
+The following factors are postulated to influence mungbean grain yield and/or powdery mildew mean plot severity.
 
@@
 
-   5 Host cultivars (probably is a co-variate with season due to changing cultivars over time)
+   5 Host cultivar (probably is a co-variate with season due to changing cultivars over time)
 
@@
 
-   9 Irrigated vs non-irrigated trials
+   9 Irrigated versus non-irrigated trials
 
@@
 
-First lets standardise the sulphur treatments. Some early experiments tested different formulations. There was no difference in the sulphur formulations so we will refer to all of them as "sulphur".
+First let's standardise the sulphur treatments.
+Some early experiments tested different formulations.
+There was no difference in the sulphur formulations so we will refer to all of them as "sulphur".
 
@@
    "sulphur"
-
 ```
@@
 
-```{r Calculate_yield-gains}
+```{r Calculate_yield-savings}
 PM_MB_means$grain_yield.t.ha. <-
@@
       warning(
-         paste(
          unique(dat1$trial_ref),
@@
          "has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n"
-         )
       )
@@
    arrange(desc(median)) %>%
-   kable(caption = "Fungicide effect on proportion of yield gain.",
-         col.names = c("Fungicide active ingredient", "Total fungicide applications","n Treatments"," 2.5% quartile","Median proportional grain yield", "Mean proportional grain yield","97.5 % quartile"),
-         align = "c") %>%
+   kable(
+      caption = "Fungicide effect on proportion of yield gain.",
+      col.names = c(
+         "Fungicide active ingredient",
+         "Total fungicide applications",
+         "n Treatments",
+         " 2.5% quartile",
+         "Median proportional grain yield",
+         "Mean proportional grain yield",
+         "97.5 % quartile"
+      ),
+      align = "c"
+   ) %>%
    kable_styling(fixed_thead = T, full_width = T) %>%
-   column_spec(c(2,3), width = "1cm") %>% 
+   column_spec(c(2, 3), width = "1cm") %>%
    footnote(general = "Fungicides with less than five observations were omitted from this table")
-
 ```
 
-*****
+**  **  *
 
@@
 ```{r Fungicide_x_nSprays_tble1, message=FALSE, warning=FALSE}
-
 PM_MB_means %>%
@@
 #### Fungicide Doses  
-Hear after we will investigate only the DMI fungicides, tebuconazole and propiconazole and disregard the action of other fungicides.
+From this point on we will investigate only the DMI fungicides, tebuconazole and propiconazole and disregard all other fungicide modes-of-action.
 
@@
    facet_grid(cols = vars(total_fungicide))
-
 ```
@@
 ```{r table_PropiDoses}
-table(as.character(PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole", ]$trial_ref),
-      PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole", ]$dose_ai.ha)
+table(as.character(PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole",]$trial_ref),
+      PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole",]$dose_ai.ha)
 ```
 
-Two trials show both doses were applied in the same trial, mung1112/01 and mung1112/02. Let look at the difference in proportion of yield saved in these trials.
+Two trials show both doses were applied in the same trial, mung1112/01 and mung1112/02.
+Let's look at the difference in proportion of yield saved in these trials.
 
-```{r PropiDoses_TrialCompar}
-
+```{r PropiDoses_TrialCompare}
 PM_MB_means[(PM_MB_means$trial_ref == "mung1112/01" |
@@
 The experiments all relied on natural infection and thus infection at a standardised crop maturity stage was not possible. 
-To best estimate the effect of fungicide application timing we will use the day when the disease was first scouted in the field as a reference.
-The first sign of disease is a useful reference as it can be assessed with little to no cost or training for growers and farm staff.
+To best estimate the effect of fungicide application timing we will use the day when the disease was first found in the field as a reference.
+The first sign of disease is a useful reference as it can be assessed with little training for the assessor.
 
-First lets make a plot to visualise when one or more spray management regimes were made in relation to the first sign of disease regardless of fungicide active. 
+First let's make a plot to visualise when one or more spray management regimes were made in relation to the first sign of disease regardless of fungicide active. 
 The plot is faceted by number of spray applications.
@@
    ylab("Days to First Sign of Disease")+
-   facet_grid(cols = vars(total_fungicide))+
-   theme(axis.text.x = element_text(angle = 90, hjust = 1))
+   facet_grid(cols = vars(total_fungicide)) +
+   coord_flip()
 ```
@@
 Experiments that tested two spray treatments also tend to make the first application at first sign of disease, and the second spray between 10 and 25 days later.
-Three spray treatments seemed to be mostly used in experiments where they were testing preventative sprays as the first fungicide application.
+Three spray treatments seemed to be mostly used in experiments where preventative sprays as the first fungicide application were made.
 
@@
 # Outputs the table and graph
-source("R/yield_volatility.r") #function to investigate the volatility in yields
+source("R/yield_volatility.r") # function to investigate the volatility in yields
 # Volatility is the range between the upper and lower 97.5 and 2.5 % quartiles
@@
 ```
-This plot shows a large amount of yield volatility in all cultivars except green diamond.
+
+This plot shows a large amount of yield volatility in all cultivars except Green Diamond.
 Green Diamond shows little volatility probably because this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trial.
@@
 ```{r yieldVol_control}
-
 YV2 <-
@@
 Let's take a closer look at Crystal with spray management treatments and without.
+
 ```{r YieldVol_Crystal}
@@
 The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows in most cases increased yield significantly.
-This finding has also been shown by Kerry McKenzie's work as well.
+This finding has also been shown by several other researchers' work in Queensland and New South Wales as well.
 Eight trials used a row spacing of 0.75&nbsp;meters and tebuconazole as an active ingredient (AI).
@@
    scale_fill_usq(name = "Fungicide AI")
-
 ```
@@
 ```{r rainfall_sum_Sstart}
-# The four data files were created from four scripts run as four jobs in Rstudio
+# The four data files were created from four scripts run as four jobs in RStudio
 # when the four jobs are finished they can be imported and combined into one data.frame

### 2020-06-22 02_Preliminary_analysis.Rmd
Clarify fungicides used in analysis
Edit for clarity

@@
 
-Amistar Xtra and Custodia are both contain strobilurin and triazole mixes, however, because they contain differing dose ratios (inverted) pooling may not be appropriate.
+Amistar Xtra and Custodia both contain strobilurin and triazole, however, because they contain differing dose ratios (inverted) pooling may not be appropriate.
 
-Perhaps best way forward is to focus the meta-analysis on only the triazoles/DMIs.
+Perhaps best way forward is to focus the meta-analysis on only the DMIs.
 This can then be compared to an additional meta-analysis including azoxystrobin as a comparison.

### 2020-06-22 02_Preliminary_analysis.Rmd
More grammar and Markdown syntax edits

@@
 
-Before we exclude non-DMI fungicides lets have a look at the efficacy of the other fungicides in comparison to the DMIs.
+Before we exclude non-DMI fungicides let's have a look at the efficacy of the other fungicides in comparison to the DMIs.
 For this comparison we will focus on the proportional yield saved, relative to the no spray control.
@@
 
-Now we have calculated proportional yield gains we can inspect the difference between the fungicide active ingredients
+Now we have calculated proportional yield savings we can inspect the difference between the fungicide active ingredients
 
@@
          "n Treatments",
-         " 2.5% quartile",
+         "2.5% quartile",
          "Median proportional grain yield",
@@
 I think it is safe to combine these fungicides, with the same mode of action in the meta-analysis.
-The follow up spray seems to show an increase in yield protection.
+The follow-up spray seems to show an increase in yield protection.
 Interestingly sulphur sprays show good protection when sprayed twice.
@@
 #### Fungicide Doses  
-From this point on we will investigate only the DMI fungicides, tebuconazole and propiconazole and disregard all other fungicide modes-of-action.
+From this point on we will investigate only the DMI fungicides, tebuconazole and propiconazole, and disregard all other fungicide modes-of-action.
 
@@
 
-The approximate period when in-crop rainfall impacts the most on the mean harvest is between 14 - 67 days after planting.
+The approximate period when in-crop rainfall affects the most on the mean harvest is between 14 - 67 days after planting.
 
@@
 ### Season range and first incidence
+
 Mungbean is a summer crop and powdery mildew requires cool conditions to establish.
@@
 
-# For some trials where planting date and Harvest date is missing lets estimate 
+# For some trials where planting date and Harvest date is missing let's estimate 
 #     the season length by using the mean of all season lengths
@@
    ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
-
 ```
@@
 
-First lets check we have all the AUDPC observations.
+First let's check we have all the AUDPC observations.
 
@@
 
->How well does 'area under the disease progress curve' (AUDPC) predict grain yield?
+      _How well does 'area under the disease progress curve' (AUDPC) predict grain yield?_
 
-and _Does spray_management scenario mitigate yield loss through reducing AUDPC?_
+   and
 
-We would expect to see grain yield decline with increasing AUDPC. Let's just plot yield vs AUDPC.
+      _Does spray_management scenario mitigate yield loss through reducing AUDPC?_
+
+We would expect to see grain yield decline with increasing AUDPC.
+Let's just plot yield vs AUDPC.
 
@@
 
-Lets tease out variation due to trial location, season, row spacing, and other seasonal variables are preventing us from seeing the expected relationship. 
+let's tease out variation due to trial location, season, row spacing, and other seasonal variables are preventing us from seeing the expected relationship. 
 Let's do the plot again for each trial where there are no missing values.  
@@
 
-This sequence of graphs show that AUDPC and disease incidence tends not impact on yields if the season is a low yielding, ie lower than 1 tonne per hectare.  
-The higher the yield the greater greater the influence on the disease on the yield especially if the crop is high yielding with AUDPC also being large enough to reduce yield.
+This sequence of graphs show that AUDPC and disease incidence tends not affect yields if the season is a low yielding season, _i.e._ lower than 1 tonne per hectare.
+The higher the yield, the greater greater the influence on the disease on the yield especially if the crop is high yielding with AUDPC also being large enough to reduce yield.
 

### 2020-06-22 02_Preliminary_analysis.Rmd
We're mitigating yield loss, not yield
Add labels to graphs, Markdown syntax edits

@@
 #### Timing of fungicide sprays  
-The timing of fungicide application can be crucial for maximum disease control and yield mitigation. 
+The timing of fungicide application can be crucial for maximum disease control and yield loss mitigation. 
 The experiments all relied on natural infection and thus infection at a standardised crop maturity stage was not possible. 
@@
    geom_violin() +
-   scale_x_discrete(
-      labels = c(
+   scale_x_discrete(labels = c(
       "First spray",
@@
       "Fifth spray"
-      )
-   ) +
-   ylab("Days to First Sign of Disease")+
+   )) +
+   ylab("Days to First Sign of Disease") +
    facet_grid(cols = vars(total_fungicide)) +
@@
 ### Mungbean cultivars
-In general, mungbean varieties have the following resistance to powdery mildew.
+
+Australian mungbean varieties have the following resistance to powdery mildew.
 
@@
 # Volatility is the range between the upper and lower 97.5 and 2.5 % quartiles
-
 YV1 <-
@@
    scale_fill_usq()
-
 YV1[[3]]
@@
 This plot shows a large amount of yield volatility in all cultivars except Green Diamond.
-Green Diamond shows little volatility probably because this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trial.
+Green Diamond shows little volatility probably because this cultivar was only used in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trial.
 
@@
 
-There still remains a higher volatility in Jade and perhaps a greater shift in the probability curve including fungicide treatments vs probability curves including only no spray controls.
+There still remains a higher volatility in Jade and perhaps a greater shift in the probability curve including fungicide treatments versus probability curves including only no spray controls.
 Indicating that there might be a difference in powdery mildew tolerance between Jade and Crystal.
 
-Overall there seems to be an influence of cultivar however this variation is not as distinct as the variation between trials.
+Overall there seems to be an influence of cultivar.
+However this variation is not as distinct as the variation between trials.
 
@@
 
-Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease.
+Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease as well as fungicide timing and efficacy.
 The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows in most cases increased yield significantly.
@@
 
-Let's plot the row spacing treatments for the response variables yield and disease severity. The main questions are:
+Let's plot the row spacing treatments for the response variables yield and disease severity.
+The main questions are:
 
@@
    geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
+   ylab("Final severity rating") +
+   xlab("Row spacing (m)") +
    ggtitle("Powdery mildew variation between different row spacing")
@@
       y = as.numeric(grain_yield.t.ha.),
-      x = row_spacing,
+      x = as.factor(row_spacing),
       colour = location
    )) +
-   geom_jitter(width = 0.01) +
+   geom_jitter(width = 0.1) +
    ggtitle("Grain yield results for different row spacing at three locations") +
@@
 Overall row spacing may influence both powdery mildew severity and yield.
+However, in the studies that were conducted, no interaction was found between row spacing, powdery mildew severity and yield.
+That is, the row spacing appeared to increase yield even if the amount of powdery mildew increased and no relationship could be detected between an interaction of the three.
 

### 2020-06-22 02_Preliminary_analysis.Rmd
Add labels to graphs, Markdown syntax edits

@@
    scale_fill_usq()
-YV1[[3]]
+V1[[3]]
 ```
@@
 
-In crop rain could be a significant factor which contributes to the end of season grain yield.
+In0-crop rain could be a significant factor which contributes to the end of season grain yield.
 To investigate this effect I will use a linear model (GY ~ SR) where seasonal rainfall represents a specific time frame with respect to planting time.

### 2020-06-22 03_Prep_data.Rmd
Dose factor complicates the model, therefore it will be removed and tested as a random factor later

@@
 Using the model without dose produces a lower AIC, however we should accept the data with dose as there is a significant difference between the models and we should accept the more complicated model `m2`.
-We will retain dose in the trial factor.
+We will try and evaluate dose in the meta-analysis, however for now we will remove the dose factor to reduce the possibility of overfitting the model.
 
 ```{r}
+slimmer_PM_dat$trial <- slimmer_PM_dat$trial_noDose
 slimmer_PM_dat <- slimmer_PM_dat[,colnames(slimmer_PM_dat) != "trial_noDose"] #remove second trial column

### 2020-06-22 01_Meta-analysis_experiments.Rmd

@@
 
-This meta-analysis uses data collected by a number of researchers from the Department of Agriculture and Primary Industries and the University of Southern
-Queensland.
-It is worth noting in particular Professor Malcolm Riley's and Dr Sue Thompson's effort in establishing and coordinating early field trials between 2010 and 2016.
+This meta-analysis uses data collected by a number of researchers from the Department of Agriculture and Primary Industries and the University of Southern Queensland.
+It is worth noting in particular Professor Malcolm Riley's and Dr. Sue Thompson's effort in establishing and coordinating early field trials between 2010 and 2016.
 
@@
 **2001 - 2004 trials**
+
 Trial data were obtained from a non-published manuscript.
-Ratings for powdery mildew were on a 1-5 rating scale where 1 = no sign of disease, 2 = 1-30% diseased leaf area, 3 = 31-65% diseased leaf area, 4 = 66-99% diseased leaf area and 5 = complete defoliation.
-Comparing these trials which have not used the 1-9 rating scale will be converted using a
-percentage change.
+
+### 1 - 5 powdery mildew rating scale
+
+Ratings for powdery mildew were on a 1 - 5 rating scale where
+
+   1 - No sign of disease
+
+   2 - 1 - 30&nbsp;% diseased leaf area
+
+   3 - 31 - 65&nbsp;% diseased leaf area
+
+   4 - 66 - 99&nbsp;% diseased leaf area and
+
+   5 - Complete defoliation
+
+Comparing these trials which have not used the 1 - 9 rating scale will be converted using a percentage change.
 
 **2013 Field trials**
+
 Trials from 2013 were all conducted by the [Northern Growers Alliance (NGA)](https://www.nga.org.au/).
@@
 
-### 1 - 9 Powdery mildew rating scale
+### 1 - 9 powdery mildew rating scale
 
-   1. No powdery mildew colonies observed on any plant
+   1 - No powdery mildew colonies observed on any plant
 
-   2. Small colonies in lower 1/3 of canopy, up to 75% of plants affected
+   2 - Small colonies in lower 1/3 of canopy, up to 75&nbsp;% of plants affected
 
-   3. Colonies in lower 1/2 of canopy, >75% of plants affected
+   3 - Colonies in lower 1/2 of canopy, >75&nbsp;% of plants affected
 
-   4. Colonies in lower 2/3 of canopy, up to 75% of plants affected
+   4 - Colonies in lower 2/3 of canopy, up to 7&nbsp;5% of plants affected
 
-   5. Colonies in lower 2/3 of canopy, >75% of plants affected
+   5 - Colonies in lower 2/3 of canopy, >75&nbsp;% of plants affected
 
-   6. Colonies in lower 2/3 of canopy, 100% of plants affected
+   6 - Colonies in lower 2/3 of canopy, 100&nbsp;% of plants affected
 
-   7. Colonies in lower 2/3 of canopy of 100% of plants, some plants with colonies also in top 1/3 of canopy
+   7 - Colonies in lower 2/3 of canopy of 10&nbsp;0% of plants, some plants with colonies also in top 1/3 of canopy
 
-   8. Colonies to top of plant with >75% of plants affected
+   8 - Colonies to top of plant with >75&nbsp;% of plants affected
 
-   9. Colonies to top of plant with 100% of plants affected and heavy leaf drop
+   9 - Colonies to top of plant with 100&nbsp;% of plants affected and heavy leaf drop
 

### 2020-06-22 02_Preliminary_analysis.Rmd

--- 2020-06-22 02_Preliminary_analysis.Rmd
@@
 
-In most years, regardless of the age of the crop, powdery mildew establishes in March.
+In most years, regardless of the age of the crop, powdery mildew establishes in March, which is to be expected.
+The disease is driven by weather conditions and the plant is vulnerable at any growth stage.
 
@@
 
-let's tease out variation due to trial location, season, row spacing, and other seasonal variables are preventing us from seeing the expected relationship. 
+Let's tease out variation due to trial location, season, row spacing, and other seasonal variables are preventing us from seeing the expected relationship.
 Let's do the plot again for each trial where there are no missing values.
@@
 for (i in sm2lg$trial_ref) {
-   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i,]
+   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
    if (any(is.na(dat1$grain_yield.t.ha.))) {
@@
    points(grain_yield.t.ha. ~ AUDPS_m,
-          data = dat1[dat1$fungicide_ai == "control", ],
+          data = dat1[dat1$fungicide_ai == "control",],
           col = "red")
@@
 }
+```
 
-```
 The plots from the AUPDS is similar to the AUDPC, however according to the linear model the AUDPC is a better, significant fit.

### 2020-06-22 03_Prep_data.Rmd
Replace "Lets" with "Let's"

@@
    install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, agricolae, lme4, here
-)
+pacman::p_load(tidyverse, kableExtra, agricolae, lme4, here)
 ```
@@
 We are narrowing the meta-analysis to only include treatments using demethylation inhibitors, tebuconazole and propiconazole.
-Lets look at what type of statistical error was reported for the trials that used these fungicides.
+Let's look at what type of statistical error was reported for the trials that used these fungicides.
 
@@
              fungicide_ai == "propiconazole") %>%
-   group_by(trial_ref, location,year ,Y_error_type, fungicide_ai) %>%
+   group_by(trial_ref, location, year , Y_error_type, fungicide_ai) %>%
    summarise(DMI_treatments = length(Y_error_type)) %>%
    arrange(Y_error_type) %>%
-   select(!fungicide_ai)%>%
+   select(!fungicide_ai) %>%
    kable(caption = "Number of treatments for each trial and the error type reported", align = "c") %>%
@@
 
-First lets get a list the of trials that reported LSD.  
+First Let's get a list the of trials that reported LSD.
+
 ```{r all_LSD_trials}
@@
 ```
-Lets use this list of trials to subset the data and calculate sampling variances.
+Let's use this list of trials to subset the data and calculate sampling variances.
 
@@
 Earlier we noted there were different doses of propiconazole which might influence our analysis. 
-Lets check this by comparing a linear mixed effect model including and excluding dose. 
-We already have a factor breaking down the dose in the `trial` variable, lets make a new one without dose.
+Let's check this by comparing a linear mixed effect model including and excluding dose. 
+We already have a factor breaking down the dose in the `trial` variable, Let's make a new one without dose.
 
@@
 
-Lets test the dose effect in a basic linear mixed effect model
+Let's test the dose effect in a basic linear mixed effect model
 
@@
 
-Lets have a quick look to examine whether trials with high disease pressure sustain a greater yield loss.
+Let's have a quick look to examine whether trials with high disease pressure sustain a greater yield loss.
 
@@
 We may want to consider row spacing in the trials, However one of the locations has NA as the row spacing. 
-For now lets assign the most used row spacing of 0.33
+For now Let's assign the most used row spacing of 0.33
 ```{r}

### 2020-06-22 03_Prep_data.Rmd
Work on loop
Move constant outside the loop, `Tcrit`.

Revise to use more standard notation, `i` in the loop in place of `Trial2012` to make it more readable to most users familiar with loop syntax

@@
 ```
+
 Let's use this list of trials to subset the data and calculate sampling variances.
@@
 
+`Tcrit` is the T critical value for which there is significant difference between two groups.
+This value is the same for both trials "mung1112/01" and "mung1112/02".
+
 ```{r LSD_2_Sampling_Variance}
+Tcrit <- 1.697 # 0.05 and DFw = 30
 
-for (Trial2012 in Trials$trial_ref) {
-   Tcrit <-
-      1.697  # 0.05 and DFw = 30 # T critical value for which there is significant difference between two groups; This value is the same for both trials "mung1112/01" and "mung1112/02"
+for (i in Trials$trial_ref) {
    DFw <-
-      sum(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates) -
-      length(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates) # degrees of freedom within groups
+      sum(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates) -
+      length(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates) # degrees of freedom within groups
 
    LSD <-
-      PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$yield_error[1]
+      PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error[1]
 
    V_yield <-
-      (PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates[1] * (LSD /
+      (PM_MB_means[PM_MB_means$trial_ref == i,]$replicates[1] * (LSD /
                                                                             Tcrit) ^ 2) / 2 # method - Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
 
-   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates)) {
+   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates)) {
       if (j == 1) {
          Sv <-
-            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates))
+            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates))
       } # reset Sv vector if this is the first loop
@@
       Sv[j] = V_yield /
-         PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates[j]
+         PM_MB_means[PM_MB_means$trial_ref == i,]$replicates[j]
 
@@
    # Replace the values in the dataset
-   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$yield_error <-
+   PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <-
       Sv
-   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$Y_error_type <-
+   PM_MB_means[PM_MB_means$trial_ref == i,]$Y_error_type <-
       "SamplingVariance"
@@
 ### Converting standard deviation to sample variance
-Now to estimate the variance from the standard deviation
+
+Now to estimate the variance from the standard deviation.
 

### 2020-06-22 03_Prep_data.Rmd
Correct Let's/let's and all sentences on own line

@@
 
-First Let's get a list the of trials that reported LSD.
+First let's get a list the of trials that reported LSD.
 
@@
 ### Check variance of data-set
-Our data currently uses sample variance to define the yield error. We should expect that when yield increases so does the variance. Let's quickly plot this to check.
+Our data currently uses sample variance to define the yield error.
+We should expect that when yield increases so does the variance.
+Let's quickly plot this to check.
 
@@
 ## Reduce data set to required variables
+
 Let's tidy up the data set into a data frame of only the variables which are required for the analysis.
@@
 Then calculate fungicide application timing variables relative to the first sign of disease.
-Entries with NA in the grain yield or powdery mildew severity are also removed from the data.
+Entries with `NA` in the grain yield or powdery mildew severity are also removed from the data.
 
@@
 Let's check this by comparing a linear mixed effect model including and excluding dose.
-We already have a factor breaking down the dose in the `trial` variable, Let's make a new one without dose.
+We already have a factor breaking down the dose in the `trial` variable.
+Let's make a new one without dose.
 
@@
 
-Let's test the dose effect in a basic linear mixed effect model
+Let's test the dose effect in a basic linear mixed effect model.
 
@@
 We may want to consider row spacing in the trials, However one of the locations has NA as the row spacing. 
-For now Let's assign the most used row spacing of 0.33
+For now let's assign the most used row spacing of 0.33 m.
+
 ```{r}

### 2020-06-22 03_Prep_data.Rmd
grammar

@@
 We see here that the sample variance generally decreases or has no association with the grain yield.
-This might be due to the unpredictable nature of mungbeans, however going forward we will use mean squares which defines between trial variation and is a the more generic error term.
+This might be due to the unpredictable nature of mungbeans, however going forward we will use mean squares which defines between trial variation and is the more generic error term.
 

### 2020-06-22 R/slimming_PM_dat.R
Add dose column as a factor

@@ -37,7 +37,8 @@ slim_PM_dat <- data.frame(
    AUDPC_m = as.double(PM_MB_Mtemp$AUDPC_m),
    AUDPC_sd = as.double(PM_MB_Mtemp$AUDPC_sd),
    AUDPS_m = as.double(PM_MB_Mtemp$AUDPS_m),
-   AUDPS_sd = as.double(PM_MB_Mtemp$AUDPS_sd)
+   AUDPS_sd = as.double(PM_MB_Mtemp$AUDPS_sd),
+   dose = PM_MB_Mtemp$dose
    
 )
 

### 2020-06-22 R/slimming_PM_dat.R
Dose as a factor.....

@@ -38,7 +38,7 @@ slim_PM_dat <- data.frame(
    AUDPC_sd = as.double(PM_MB_Mtemp$AUDPC_sd),
    AUDPS_m = as.double(PM_MB_Mtemp$AUDPS_m),
    AUDPS_sd = as.double(PM_MB_Mtemp$AUDPS_sd),
-   dose = PM_MB_Mtemp$dose
+   dose = factor(PM_MB_Mtemp$dose)
    
 )
 

### 2020-06-22 03_Prep_data.Rmd

@@
 # Prepare data for meta-analysis
+
 ## Set environment and import data
@@
 pacman::p_load(tidyverse, kableExtra, agricolae, lme4, here)
+if (!require("theme.usq"))
+   devtools::install_github("adamhsparks/theme.usq")
+library(theme.usq)
+theme_set(theme_usq())
 ```
@@
    geom_point()
-
 ```

### 2020-06-22 03_Prep_data.Rmd
remove warning suppression on code chunk
Markdown syntax, delete chunk that said "delete me"

@@
 ### Cluster fungicide applications
+
 We are going to define 'fungicide application timing' as a categorical variable, relative to the first sign of powdery mildew.
@@
 These categorical variables are named:
+
    - **Early**: First fungicide application was prior to first sign of disease.
+
    - **Recommended**: First fungicide application was applied on the day powdery mildew was observed, or within three days of first sign.
+
    - **Late**: First fungicide application was four or more days after first sign of disease being observed.
@@
 Single sprays of either:
+
    a) early,
+
    b) recommended timing,
+
    c) late.
@@
 Two or more sprays where the first spray was either:
+
    d) early,
+
    e) recommended timing,
+
    f) late.
@@
    slim_PM_dat[slim_PM_dat$spray_management != "Early_plus", ]
-
 ```
@@
 ```{r dose_lmer}
-
 m1 <-
@@
 
-anova(m1,m2)
-
+anova(m1, m2)
 ```
@@
 slimmer_PM_dat$trial <- slimmer_PM_dat$trial_noDose
-slimmer_PM_dat <- slimmer_PM_dat[,colnames(slimmer_PM_dat) != "trial_noDose"] #remove second trial column
+slimmer_PM_dat <-
+   slimmer_PM_dat[, colnames(slimmer_PM_dat) != "trial_noDose"] #remove second trial column
 write.csv(slimmer_PM_dat, file = "cache/slimmer_PM_clusterdat.csv", row.names = FALSE)
@@
 
-median_AUDPC <- median(as.vector(Trial_Dpress$AUDPC_C), na.rm = TRUE)
+median_AUDPC <-
+   median(as.vector(Trial_Dpress$AUDPC_C), na.rm = TRUE)
 
@@
 
-for(i in unique(slimmer_PM_dat$trial_ref)) {
+for (i in unique(slimmer_PM_dat$trial_ref)) {
    if (is.na(Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"])) {
@@
 }
-
 ```
@@
 
-We may want to consider row spacing in the trials, However one of the locations has NA as the row spacing. 
+We may want to consider row spacing in the trials, However one of the locations has `NA` as the row spacing. 
 For now let's assign the most used row spacing of 0.33 m.
 
-```{r}
+```{r assign_row_spacing_missing}
 slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),]
@@
 ```
-
-```{r delete_this_chunk, eval=FALSE, include=FALSE}
-PM_MB_means$infected_days <- as.numeric(PM_MB_means$harvest_date - PM_MB_means$first_sign_disease)
-
-plot(AUDPC_m ~ infected_days, data = PM_MB_means)
-plot(grain_yield.t.ha. ~ infected_days, data = PM_MB_means)
-
-PM_MB_means$harvest_date - PM_MB_means$first_sign_disease
-```

### 2020-06-22 03_Prep_data.Rmd
commas with "which"

@@
 First we will convert LSD and standard deviation to sample variance.
-Then we will impute variances for the trials which did not report any form of variance (`NA`).
+Then we will impute variances for the trials, which did not report any form of variance (`NA`).
 
@@
 We see here that the sample variance generally decreases or has no association with the grain yield.
-This might be due to the unpredictable nature of mungbeans, however going forward we will use mean squares which defines between trial variation and is the more generic error term.
+This might be due to the unpredictable nature of mungbeans, however going forward we will use mean squares, which defines between trial variation and is the more generic error term.
 
@@
 
-Let's tidy up the data set into a data frame of only the variables which are required for the analysis.
+Let's tidy up the data set into a data frame of only the variables, which are required for the analysis.
 
@@
 ```{r clustered_fungicide_applications}
-source("R/slimming_PM_dat.R") # see R script for the code which reduces the data.
+source("R/slimming_PM_dat.R") # see R script for the code, which reduces the data.
 
@@
 
-Earlier we noted there were different doses of propiconazole which might influence our analysis.
+Earlier we noted there were different doses of propiconazole, which might influence our analysis.
 Let's check this by comparing a linear mixed effect model including and excluding dose.
@@
 
-We may want to consider row spacing in the trials, However one of the locations has `NA` as the row spacing. 
+We may want to consider row spacing in the trials.
+However one of the locations has `NA` as the row spacing.
 For now let's assign the most used row spacing of 0.33 m.

### 2020-06-22 03_Prep_data.Rmd
Edits for clarity and grammar

@@
    DFw <-
-      sum(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates) -
-      length(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates) # degrees of freedom within groups
+      sum(PM_MB_means[PM_MB_means$trial_ref == i, ]$replicates) -
+      length(PM_MB_means[PM_MB_means$trial_ref == i, ]$replicates) # degrees of freedom within groups
 
    LSD <-
-      PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error[1]
+      PM_MB_means[PM_MB_means$trial_ref == i, ]$yield_error[1]
 
    V_yield <-
-      (PM_MB_means[PM_MB_means$trial_ref == i,]$replicates[1] * (LSD /
-                                                                            Tcrit) ^ 2) / 2 # method - Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
+      (PM_MB_means[PM_MB_means$trial_ref == i, ]$replicates[1] * 
+          (LSD / Tcrit) ^ 2) / 2 
+   # method - Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
 
@@
       "SamplingVariance"
-
 }
@@
 # calculate the Sampling variance from the standard deviation
-# standard error of the mean equals the standard deviation divided by the square root of the number of samples
+# standard error of the mean equals the standard deviation divided by the square
+#  root of the number of samples
 # Sv <- sem^2 <- stdev/sqrt(n)
@@
 
-for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$yield_error)) {
+for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error)) {
    if (j == 1) {
       Sv <-
-         vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$yield_error))
+         vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error))
    }# create empty vector at first iteration with length of j
 
-   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref, ]$yield_error[j]) ^ 2
+   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error[j]) ^ 2
 }
@@
 
-&nbsp;  
-&nbsp;  
-&nbsp;
-
 ## Reduce data set to required variables
@@
    filter(!is.na(PM_final_severity))
-
 ```
@@
    - **Late**: First fungicide application was four or more days after first sign of disease being observed. 
-
-Follow up fungicide applications (cluster_2 and cluster_3) were also categorised as either, early, recommended or late.
+Follow up fungicide applications (cluster_2 and cluster_3) were also categorised as either early, recommended or late.
 
@@
 ### Disease pressure factor
+
 We may wish to investigate the impact of spray management in mitigating the yield loss through the effect on the disease pressure.
@@
       }
-
    }
@@
 
-From this plot we see that in the trials with high disease pressure treatments on tended to produce lower yields. 
+From this plot we see that in the trials with high disease pressure tended to produce lower yields. 
 There are `r length(unique(slimmer_PM_dat[is.na(slimmer_PM_dat$D_pres),"trial_ref"]))` trials that contained no data for AUDPC and thus produced `NA` values.

### 2020-06-22 04_MetaAnalysis.Rmd
Wordsmithing and flow

@@
 
-First lets compare models with and without a log transformed response variable to evaluate if the log transformed model better fits our assumptions of normality.  
+First let's compare models with and without a log transformed response variable to evaluate if the log transformed model better fits our assumptions of normality.  
 Next we will test whether including `spray_management` as a fixed effect variable significantly accounts for enough variation to be included in the model.  
@@
 
-This linear mixed effect model shows indicates:
+This linear mixed effect model shows:
 
@@
 
-```{r remove_NA_MSE}
+```{r remove_yieldErrorNAs}
 slimmer_PM_dat <- 
-   slimmer_PM_dat[!is.na(slimmer_PM_dat$Y_Msquare),]
+   slimmer_PM_dat[!is.na(slimmer_PM_dat$yield_error),]
 
@@
 Treatments Late_plus and early don't have very good comparison to other treatments.
+
+Let's visualise the spread of data in each treatments with box-plots.
 
@@
 There seems like little difference between the treatments, with exception to Late_plus. 
-Let's do this plot again, but lets look at the proportional mean difference between the treatments and the no spray control for each study.  
+Let's do this plot again, but let's look at the proportional mean difference between the treatments and the no spray control for each study.  
 This should reduce variation in yield due between trials.
@@
 
-Using the mean difference in the treatment effect seems to show the impact of each treatment better than just raw yield.
+Using the mean difference in the treatment effect seems to show the impact of each treatment better than just raw yield and reduces the variability in the treatments.
 We know there is a good deal of variability in our studies and between them. 
 Mungbean produces variable yields between seasons so we should use a response that highlights the difference in the treatment effects that we are interested in and reduce the variability.
-Lets calculate the standardised mean difference for each treatment to reduce the variability in the meta-analysis.
+Let's calculate the standardised mean difference for each treatment to reduce the variability in the meta-analysis.
 
@@
 #### Calculate sample variance from mean square errors
+
+Currently our data frame has the sample variance calculated earlier, however we can approximate it using the mean squared error.
+Let's show the rational for our calculation and then add a secondary variance column (`vi2`)
 
@@
 Therefore: 
-$S_{Var} = \frac{\frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n_y - 1}}{n_{x}}$  
+$S_{Var} = \frac{1}{n_{x}} \frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n_y - 1} $  
 Where $n_x$ is the number of samples within each treatment.
@@
 
-### Caluculate standardised mean differences
-We may wish to undertake the meta-analysis using standardised mean differences. 
-Lets calculate them and add them to the dataframe.
+### Calculate standardised mean differences
+
+Let's calculate standardised mean differences and add them to the data frame.
 ```{r StandardisedMeanDifference}
@@
 
-We can use the same sample variance because if you add or subtract from a random variable the variance does not change.
+We can use the same sample variance with the standardised mean difference.
+This is because if you add or subtract from a random variable, the variance does not change.
 
-Lets simplify our data
+Let's simplify our data
 ```{r metafor_organisation}
@@
 ### metafor package  
-Let's load the `metafor` package we are using to analyse the data, then rearrange the factors we want to examine by placing the control treatment first.
-This way all treatments will be compared to the no spray controls.
-Next we are log transforming the grain yield and calculating the variance from the trial mean squares.  
-Finally we will assign factor classes to the main variables in the meta-analysis. Note that variable trial is a combination of:
-
-   * Trial identifier
-
-   * Trial year
-
-   * Trial location
-
-   * Host genotype
-
-   * Trial row spacing
-
-Lets inspect the data to determine if we need to transform the response variable
+Let's inspect the data to determine if we need to transform the response variable
 
@@
 
-Lets undertake the meta-analysis, we are using the `spray_management` variable as a moderator and a interactive term to the `trial` variable.
+Let's undertake the meta-analysis using the package `metafor`.
+Ee are using the `spray_management` variable as a moderator and a interactive term to the `trial` random variable.
 Because we want to know the difference between all treatments and we have no reference treatment, we will remove the intercept.
@@
 The Qm [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, show the moderators significantly influence the model ($Q_M = 85.232, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
-The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 40994.51, df = 105, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
+The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 47501.48, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
 
-Lets see if we can improve this model by including some other random effects and improving the random effect structure in the model.
+Let's see if we can improve this model by including some other random effects and improving the random effect structure in the model.
 
-```{r}
+```{r rma_noRandomInteractiveTerm}
 
@@
 ```
-The simpler `PM_mv_St` model explains significantly less variation as the more complicated model `PM_mv`. So we will keep the original model.
+The simpler `PM_mv_St` model explains significantly less variation as the more complicated model `PM_mv`. So we will keep the original model `PM_mv`.
 
@@
 ### Profile plots  
-Lets inspect the profile plots to ensure the model is not over-fitted. 
+Let's inspect the profile plots to ensure the model is not over-fitted. 
 We expect to see the estimate align with the peak of the curve. 

### 2020-06-22 03_Prep_data.Rmd
Add proper x and y axis labels

@@
 
-```{r cluster_clusters, warning=FALSE}
+```{r cluster_clusters}
 clusters <-
@@
    ggplot(aes(x = D_pres, y = grain_yield.t.ha))+
-   geom_boxplot()
+   geom_boxplot() +
+   xlab("Disease pressure") +
+   ylab("Grain yield (t/ha)")
 ```

### 2020-06-22 04_MetaAnalysis.Rmd
Markdown syntax, USQ colours and histograms, suppress long outputs

@@
    install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer,metafor, netmeta)
+pacman::p_load(tidyverse,
+               kableExtra,
+               bomrang,
+               lme4,
+               RColorBrewer,
+               metafor,
+               netmeta)
 
@@
 # Data
-slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv")
+slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv"
+)
 ```
@@
 
-   - Grain yield is our response variable and will be converted to Kg / Ha.  
-   - Trial, which resolves combinations of categorical variables: year, location, row spacing, fungicide dose and cultivar; is set as a random intercept.  
-   - We will test spray management (our treatment) as a fixed effect and random slope to trial.
+To do this, in our model:
+
+   - Grain yield is our response variable and will be converted to kg / ha
+
+   - Trial, which resolves combinations of categorical variables: year, location, row spacing, fungicide dose and cultivar; is set as a random intercept
+
+   - We will test spray management (our treatment) as a fixed effect and random slope to trial
 
@@
         data = slimmer_PM_dat)
-
 ```
@@
 ```
+
 There is a significant difference between `m10` and `m9`, with `m9` showing the best fit and lowest AIC: `r min(anova(m9, m10)$AIC)`.
@@
 
-There is no difference between the models, which means the the simpler model `m11` is the better model, also making it the best model from the four above with the lower AIC of -`r min(anova(m9, m11)$AIC)`
+There is no difference between the models, which means the the simpler model `m11` is the better model, also making it the best model from the four above with the lower AIC of -`r min(anova(m9, m11)$AIC)`).
 
@@
 #### Imputing sample variances from Mean squares
+
 ```{r imputing_MSE_dataSpread, eval=FALSE, include=FALSE}
@@
 hist_usq(log(unique(slimmer_PM_dat$Y_Msquare))) # log mean square has a more normal distribution
-
 ```
 
-Imputing using a log transformation of the data is required. Which trials need variance imputation?
+Imputing using a log transformation of the data is required.
+Which trials need variance imputation?
 
@@
 TrialMSQ <- slimmer_PM_dat %>%
-   group_by(trial_ref,location,year)%>%
+   group_by(trial_ref, location, year) %>%
    summarise(unique(Y_Msquare))
@@
 ```{r imputation_MSE, eval=FALSE, include=FALSE}
-for (i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), ]$trial_ref) {
+for (i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`),]$trial_ref) {
    slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "Y_Msquare"] <-
@@
    slimmer_PM_dat[!is.na(slimmer_PM_dat$yield_error),]
-
 ```
@@
 ```{r table_of_nTreatments}
-kable(table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year),
+kable(
+   table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year),
    align = rep('c', 8),
-      caption = "Which treatments and how many treatments are represented in each year") %>%  
+   caption = "Which treatments and how many treatments are represented in each year"
+) %>%
    kable_styling(
@@
 ```
+
 Treatments Late_plus and early don't have very good comparison to other treatments.
@@
    factor(slimmer_PM_dat$spray_management,
-          levels(factor(slimmer_PM_dat$spray_management))[rev(c(1, 2, 5, 6, 3,4))])
+          levels(factor(slimmer_PM_dat$spray_management))[rev(c(1, 2, 5, 6, 3, 4))])
 
@@
 
-There seems like little difference between the treatments, with exception to Late_plus. 
-Let's do this plot again, but let's look at the proportional mean difference between the treatments and the no spray control for each study.  
-This should reduce variation in yield due between trials.
+There seems like little difference between the treatments, with exception to `Late_plus`.
+Let's do this plot again, but let's look at the proportional mean difference between the treatments and the no spray control for each study, this should reduce variation in yield due between trials.
 
@@
 
-Using the mean difference in the treatment effect seems to show the impact of each treatment better than just raw yield and reduces the variability in the treatments.
+Using the mean difference in the treatment effect seems to show the effect of each treatment better than just raw yield and reduces the variability in the treatments.
 We know there is a good deal of variability in our studies and between them.
@@
 Currently our data frame has the sample variance calculated earlier, however we can approximate it using the mean squared error.
-Let's show the rational for our calculation and then add a secondary variance column (`vi2`)
+Let's show the rational for our calculation and then add a secondary variance column (`vi2`).
 
 $MSE = Var + bias$
+
 However if our MSE was calculated from an unbiased sample we can assume $bias = 0$ and therefore:
+
 $MSE = Var$
 
-To calculate the sample variance (for each treatment in the tria) from the mean square error (Trial variance) all we need to do is divide by the number of samples in each treatment.
+To calculate the sample variance (for each treatment in the trial) from the mean square error (Trial variance) all we need to do is divide by the number of samples in each treatment.
 We can show this because:
@@
    slimmer_PM_dat$n
-
 ```
@@
 Let's calculate standardised mean differences and add them to the data frame.
+
 ```{r StandardisedMeanDifference}
@@
 slimmer_PM_dat$vi_C <- NA
-for(T_ref in slimmer_PM_dat$trial_ref){
-
+for (T_ref in slimmer_PM_dat$trial_ref) {
    # First we need to Calculate the pooled standard deviation
    slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "pooledSD"] <-
-   sqrt(sum((slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"n" ]-1) * slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"yield_error"])/
-           (sum( slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"n"]) - nrow( slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, ])))
+      sqrt(sum((slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "n"] - 1) * slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "yield_error"]) /
+              (sum(slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "n"]) - nrow(slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,])))
 
    # Then Create a column with the value of the mean grain yield of the no spray control for comparisons to the treatments means
-   slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,"yi_C"] <-  
+   slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "yi_C"] <-
       mean(slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref &
@@
 # Calculate standardised mean difference
-slimmer_PM_dat$grain_SMD <- (slimmer_PM_dat$grain_yield.t.ha - slimmer_PM_dat$yi_C)/ slimmer_PM_dat$pooledSD
-
+slimmer_PM_dat$grain_SMD <-
+   (slimmer_PM_dat$grain_yield.t.ha - slimmer_PM_dat$yi_C) / slimmer_PM_dat$pooledSD 
 ```
@@
 
-Let's simplify our data
+Let's simplify our data.
+
 ```{r metafor_organisation}
@@
                 spray_management,
-      c( "Early",
+                c(
+                   "Early",
                    "Recommended",
@@
                    "Late_plus"
-      )))%>%
+                )
+             )) %>%
    select(
@@
 ## Meta-analysis
+
 ### metafor package
-Let's inspect the data to determine if we need to transform the response variable
+
+Let's inspect the data to determine if we need to transform the response variable.
 
 ```{r}
-hist(dat1$grain_yield.t.ha)
-hist(log(dat1$grain_yield.t.ha))
-hist(sqrt(dat1$grain_yield.t.ha))
-hist(dat1$grain_SMD)
+hist_usq(dat1$grain_yield.t.ha)
+hist_usq(log(dat1$grain_yield.t.ha))
+hist_usq(sqrt(dat1$grain_yield.t.ha))
+hist_usq(dat1$grain_SMD)
 ```
-Standardised mean differences have a bit of a long tail however this is not bad and transformations with log or sqrt will not work on negative values.
+
+Standardised mean differences have a bit of a long tail however this is not bad and transformations with log or square root will not work on negative values.
 
@@
 Because we want to know the difference between all treatments and we have no reference treatment, we will remove the intercept.
+
 ```{r Metafor-analysis}
@@
    vi,
-   mods = ~ spray_management -1,
+   mods = ~ spray_management - 1,
    method = "ML",
-   random = ~ spray_management|trial,
+   random = ~ spray_management | trial,
    struct = "UN",
@@
 ```{r rma_noRandomInteractiveTerm}
-
 PM_mv_St <- rma.mv(
@@
 ```
-The simpler `PM_mv_St` model explains significantly less variation as the more complicated model `PM_mv`. So we will keep the original model `PM_mv`.
+
+The simpler `PM_mv_St` model explains significantly less variation as the more complicated model `PM_mv`.
+So we will keep the original model `PM_mv`.
 
@@
 
-The fixed effects, in the last table, showed that yields in single early spray treatments are not significantly different to zero, or the no spray control.
+The fixed effects, in the last table, showed that yields in single early spray treatments are not significantly different from zero, or the no spray control.
 
 ### Profile plots
+
 Let's inspect the profile plots to ensure the model is not over-fitted. 
@@
 
-```{r}
-profile(PM_mv , tau2 = 1)
-profile(PM_mv , tau2 = 2)
-profile(PM_mv , tau2 = 3)
-profile(PM_mv , tau2 = 4)
-profile(PM_mv , tau2 = 5)
+```{r profile_plots, message=FALSE, results="hide"}
+profile(PM_mv, tau2 = 1)
+profile(PM_mv, tau2 = 2)
+profile(PM_mv, tau2 = 3)
+profile(PM_mv, tau2 = 4)
+profile(PM_mv, tau2 = 5)
 ```
@@
 *****
+
 ### Metafor comparisons
@@
 To make it easier to compare each of the treatments we can compute the meta-analysis contrasts.
+
 ```{r metafor_contrasts}
 meta_cont <- anova(PM_mv, L = rbind(
-   c(-1, 1, 0, 0,0),
-   c(-1, 0, 1, 0,0),
-   c(-1, 0, 0, 1,0),
-   c(-1, 0, 0, 0,1),
-   c(0, -1, 1, 0,0),
-   c(0, -1, 0, 1,0),
-   c(0, -1, 0, 0,1),
-   c(0, 0, -1, 1,0),
-   c(0, 0, -1, 0,1),
-   c(0, 0, 0, -1,1)
+   c(-1, 1, 0, 0, 0),
+   c(-1, 0, 1, 0, 0),
+   c(-1, 0, 0, 1, 0),
+   c(-1, 0, 0, 0, 1),
+   c(0, -1, 1, 0, 0),
+   c(0, -1, 0, 1, 0),
+   c(0, -1, 0, 0, 1),
+   c(0, 0, -1, 1, 0),
+   c(0, 0, -1, 0, 1),
+   c(0, 0, 0, -1, 1)
 ))
 
-change_labels <- function(x1){
-   x1 <- gsub(pattern = "spray_management",replacement = "",x = x1)
+change_labels <- function(x1) {
+   x1 <- gsub(pattern = "spray_management",
+              replacement = "",
+              x = x1)
    x1
@@
 
-data.frame(contrasts = change_labels(meta_cont$hyp[,1]),
+data.frame(
+   contrasts = change_labels(meta_cont$hyp[, 1]),
    estimates = meta_cont$Lb,
@@
    pval = meta_cont$pval,
-      VisP = p_star(meta_cont$pval))
+   VisP = p_star(meta_cont$pval)
+)
 ```
+
 Results show with the exclusion of the no spray control, `Early` applications are significantly worse than all other treatments leading to lower yield estimates. 
@@
 First we will format the results into a data frame.
+
 ```{r metafor_results}
@@
 efficacy$Treatment <-
-   factor(
-      c( "Early",
+   factor(c(
+      "Early",
       "Recommended",
@@
       "Late_plus"
-      )
-   )
+   ))
 
@@
    geom_hline(
-      yintercept = seq(-0.5,1.5, by = 0.2),
-      color = "grey80",
+      yintercept = seq(-0.5, 1.5, by = 0.2),
+      color = usq_cols("usq charcoal"),
       linetype = 3
@@
 ### netmeta package
+
 Let's analyse the data again using a different statistical approach to see if our outcome with the `metafor` package was robust.
@@
 ```
-Now let's visualise this as a forest plot
+
+Now let's visualise this as a forest plot.
 
 ```{r netmeta-forest}
-# I don't know why this is not working I will need to follow up on this
 forest(
@@
 )
-
 ```
@@
 It estimates the mean is very similar to the recommended treatments.
-The recommended plus and late_plus treatments show higher mean estimates, however not significantly different from the early estimate.
+The recommended plus and late_plus treatments show higher mean estimates, however are not significantly different from the early estimate.
 
@@
    plastic = FALSE,
-   col = "orange",
+   col = usq_cols("support orange"),
    thickness =  "number.of.studies",
    points = FALSE,
-   col.points = "black",
+   col.points = usq_cols("usq charcoal"),
    cex.points = 1,
@@
    col.number.of.studies = "black",
-   bg.number.of.studies = "orange",
+   bg.number.of.studies = usq_cols("support orange"),
    multiarm = FALSE,
-   col.multiarm = "lightblue",
+   col.multiarm = usq_cols("support turquiose"),
    pos.number.of.studies = 0.5

### 2020-06-23 03_Prep_data.Rmd
small edits for more logical flow

--- 2020-06-22 03_Prep_data.Rmd
@@
 Using the model without dose produces a lower AIC, however we should accept the data with dose as there is a significant difference between the models and we should accept the more complicated model `m2`.
-We will try and evaluate dose in the meta-analysis, however for now we will remove the dose factor to reduce the possibility of overfitting the model.
+We will retain dose as a variable inside the `trial` factor.
 
-```{r}
-slimmer_PM_dat$trial <- slimmer_PM_dat$trial_noDose
+```{r saveDat}
 slimmer_PM_dat <-
    slimmer_PM_dat[, colnames(slimmer_PM_dat) != "trial_noDose"] #remove second trial column
-write.csv(slimmer_PM_dat, file = "cache/slimmer_PM_clusterdat.csv", row.names = FALSE)
 ```
@@
 
-```{r}
-slimmer_PM_dat <- read.csv(here("cache/slimmer_PM_clusterdat.csv"))
-
+```{r DiseasePressure}
 slimmer_PM_dat$D_pres <- NA_character_

### 2020-06-23 04_MetaAnalysis.Rmd
Edits corrections and testing the random effect struction of the meta-analysis

--- 2020-06-22 04_MetaAnalysis.Rmd
@@
 The use of these imputed MSE was giving a varied outcome each time it was run. 
-The next code chunk removes the studies without variation to observe what the meta-analysis outcome would be.
+The next code chunk removes the studies without variation, given we can't reliably impute them.
 
@@
          "Late",
-         "Late_plus"
-      )))%>%
+         "Late_plus")),
+      TrialDose = factor(paste(trial, dose, sep = "_"))
+      )%>%
    select(
@@
 Let's undertake the meta-analysis using the package `metafor`.
-Ee are using the `spray_management` variable as a moderator and a interactive term to the `trial` random variable.
+We are using the `spray_management` variable as a moderator and an interactive term to the `trial` random variable.
 Because we want to know the difference between all treatments and we have no reference treatment, we will remove the intercept.
@@
 
-AIC(PM_mv_St)
-anova(PM_mv, PM_mv_St)
+dat1$trial[1]
+
+PM_mv_St1 <- rma.mv(
+   yi = grain_SMD,
+   vi, 
+   mods = ~ spray_management,
+   method = "ML",
+   random = list(~ 1|location/year/trial_ref/dose/host_genotype/factor(row_spacing)/spray_management),
+   data = dat1
+)
+
+AIC(PM_mv) # Printing the AIC of the model helps differentiate the models in the anova output
+anova(PM_mv, PM_mv_St1) # PM_mv is the better model
+
 ```
-The simpler `PM_mv_St` model explains significantly less variation as the more complicated model `PM_mv`. So we will keep the original model `PM_mv`.
+
+The simpler `PM_mv_St` model explains significantly less variation as the more complicated model `PM_mv`. 
+So we will keep the original model `PM_mv`.
 
@@
 
-```{r}
+```{r rmaProfilePlots}
 profile(PM_mv , tau2 = 1)

### 2020-06-23 04_MetaAnalysis.Rmd

--- 2020-06-22 04_MetaAnalysis.Rmd
@@
 
-AIC(PM_mv_St)
-anova(PM_mv, PM_mv_St)
+dat1$trial[1]
+
+PM_mv_St1 <- rma.mv(
+   yi = grain_SMD,
+   vi, 
+   mods = ~ spray_management,
+   method = "ML",
+   random = list(~ 1|location/year/trial_ref/dose/host_genotype/factor(row_spacing)/spray_management),
+   data = dat1
+)
+
+AIC(PM_mv) # Printing the AIC of the model helps differentiate the models in the anova output
+anova(PM_mv, PM_mv_St1) # PM_mv is the better model
+
 ```

### 2020-06-23 04_MetaAnalysis.Rmd
Add meta-evaluation of disease pressure

@@
                 )
-             )) %>%
+             ),
+          D_pres = 
+             factor(D_pres,
+                    c("lowD",
+                      "highD"))) %>%
    select(
@@
    coord_flip()
+
+max(slimmer_PM_dat[slimmer_PM_dat$cluster_1 == "Late" &
+                      ,"fungicide_timing_1"], na.rm = TRUE)
 ```
@@
 Let's look at how well each of the number treatments compare to each other.
+
+### Disease pressure effect
+
+We also want to know if disease pressure exerts an effect on the desicion for spray control.
+Above we can see spraying at the first sign of powdery mildew or with in `r min(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"| slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` - `r min(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"|                   slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` days after first sign is effective at mitigating yield loss.
+Does this change between years of low and high disease pressure.
+
+We will add the intercept back into this model for ease of interpretation. 
+```{r D_pres-Meta}
+PM_mv_Dp <- rma.mv(
+   yi = grain_SMD,
+   vi,
+   mods = ~ spray_management *D_pres,
+   method = "ML",
+   random = ~ spray_management | trial,
+   struct = "UN",
+   data = dat1
+)
+
+summary(PM_mv_Dp)
+```
+
+These results show that the spray management variable we tested are not significantly better or worse between the two levels of disease pressure.
+It also shows that in trials with high disease pressure all treatments produced lower standardised mean differences. 
+Indicating that fungicide treatments were less effective at mitigating yeild loss in seasons which developed heavier infestations.  
+Finally lets compare the disease pressure model to the orignal model to see which one fits better.
+
+```{r compareDvNDP}
+anova(PM_mv, PM_mv_Dp)
+```
+No significant difference which informs us to use the origninal model `PM_mv` which is the simplest.
+
+****
 

### 2020-06-23 04_MetaAnalysis.Rmd
Remove lmer analysis and variance imputation

@@
 
-First let's compare models with and without a log transformed response variable to evaluate if the log transformed model better fits our assumptions of normality.
-Next we will test whether including `spray_management` as a fixed effect variable significantly accounts for enough variation to be included in the model.
-Finally we will test whether including `spray_management`  as a random slope significantly accounts for enough variation to be used in the model.
-
-```{r LME_slimmer_cluster_disease_mod}
-m8 <- lmer(grain_yield.t.ha * 1000 ~ factor(spray_management) +
-              (factor(spray_management) | trial),
-           data = slimmer_PM_dat)
-
-m9 <- lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
-              (factor(spray_management) | trial),
-           data = slimmer_PM_dat)
-
-m10 <- lmer(log(grain_yield.t.ha * 1000) ~
-               (factor(spray_management) | trial),
-            data = slimmer_PM_dat)
-
-m11 <-
-   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
-           (1 | trial),
-        data = slimmer_PM_dat)
-```
-
-```{r m8_vs_m9}
-anova(m8, m9) # m9 is significantly better model
-```
-There is a significant difference between `m8` and `m9`, with `m9` showing the best fit and lowest AIC: `r min(anova(m8, m9)$AIC)`.
-
-```{r m9_vs_m10}
-anova(m9, m10) # m9 is significantly better model
-```
-
-There is a significant difference between `m10` and `m9`, with `m9` showing the best fit and lowest AIC: `r min(anova(m9, m10)$AIC)`.
-
-```{r m9_vs_m11}
-anova(m9, m11) # m11 is a simpler model which is no different to m9
-```
-
-There is no difference between the models, which means the the simpler model `m11` is the better model, also making it the best model from the four above with the lower AIC of -`r min(anova(m9, m11)$AIC)`).
-
-```{r}
-summary(m11)
-```
-
-This linear mixed effect model shows:
-
-   - A single `early` spray before first sign of powdery mildew is not likely to increase yields.
-
-   - One spray at the `recommended` timing, or two sprays starting at the `recommended` first spray, are likely to produce significantly higher grain yields compared to the no spray control.
-
-   - The `Late_plus` spray which has one or more follow-up sprays after first sign are likely to increase the mean grain yield.
-
-   - `Recommended_plus` spray treatments showed the highest mean grain yield, and was significantly higher than the no spray control.
-However showed no difference to either the `recommended` or `Late_plus` treatments.
-
-#### Imputing sample variances from Mean squares
-
-```{r imputing_MSE_dataSpread, eval=FALSE, include=FALSE}
-slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv")
-hist_usq(unique(slimmer_PM_dat$Y_Msquare))
-hist_usq(log(unique(slimmer_PM_dat$Y_Msquare))) # log mean square has a more normal distribution
-```
-
-Imputing using a log transformation of the data is required.
-Which trials need variance imputation?
-
-```{r imputing_MSE, eval=FALSE, include=FALSE}
-TrialMSQ <- slimmer_PM_dat %>%
-   group_by(trial_ref, location, year) %>%
-   summarise(unique(Y_Msquare))
-
-TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), c("trial_ref", "location","year")]
-```
-
-```{r imputation_MSE, eval=FALSE, include=FALSE}
-for (i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`),]$trial_ref) {
-   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "Y_Msquare"] <-
-      exp(rnorm(
-         n = 1,
-         mean = mean(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE),
-         sd(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE)
-      ))
-}
-```
-
-The use of these imputed MSE was giving a varied outcome each time it was run. 
-The next code chunk removes the studies without variation, given we can't reliably impute them.
-
-```{r remove_yieldErrorNAs}
-slimmer_PM_dat <- 
-   slimmer_PM_dat[!is.na(slimmer_PM_dat$yield_error),]
-```
-
-Before analysis let's have a look at the trimmed down modified data.
-
 First, how well the data is compared across the trial years and trials.
@@
 ```
+
+Before analysis let's have a look at the trimmed down modified data.
 
@@
 
+First lets remove any entries missing variance.
+
 ```{r remove_studies}
 any(is.na(slimmer_PM_dat$yield_error))
+
+slimmer_PM_dat <- 
+   slimmer_PM_dat[!is.na(slimmer_PM_dat$yield_error),]
 

### 2020-06-23 04_MetaAnalysis.Rmd
select - dose,

@@
       grain_SMD,
+      dose,
       vi,

### 2020-06-23 04_MetaAnalysis.Rmd
delete random bits of code
Typos, code corrections, and plotting order

@@
 Therefore: 
-$S_{Var} = \frac{1}{n_{x}} \frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n_y - 1} $  
+$S_{Var}\approx\frac{1}{n_{x}}\frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n_y - 1}$  
 Where $n_x$ is the number of samples within each treatment.
@@
 However the other treatments are significantly different to zero.
-The Qm [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, show the moderators significantly influence the model ($Q_M = 85.232, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
-The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 47501.48, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
+The $Q_M$ [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, shows the moderators significantly influence the model ($Q_M = 24.4769, df = 5, p = 0.0002$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
+The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 47501.76, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
 
@@
 )
-
-dat1$trial[1]
 
@@
 efficacy %>%
+   mutate(Treatment = factor(Treatment, levels = rev(c("Early", "Recommended", "Recommended_plus","Late","Late_plus"))))%>%
    ggplot(aes(Treatment, Mean)) +
    geom_hline(
-      yintercept = seq(-0.5, 1.5, by = 0.2),
+      yintercept = seq(-0.4, 1.8, by = 0.2),
       color = usq_cols("usq charcoal"),
@@
    ) +
+   geom_hline(yintercept = 0)+
    geom_point(aes(size = 1 / SE), shape = 15) +
@@
 
-max(slimmer_PM_dat[slimmer_PM_dat$cluster_1 == "Late" &
-                      ,"fungicide_timing_1"], na.rm = TRUE)
 ```
@@
 We also want to know if disease pressure exerts an effect on the desicion for spray control.
-Above we can see spraying at the first sign of powdery mildew or with in `r min(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"| slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` - `r min(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"|                   slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` days after first sign is effective at mitigating yield loss.
+Above we can see spraying at the first sign of powdery mildew or with in `r min(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"| slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` - `r max(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"|                   slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` days after first sign is effective at mitigating yield loss.
 Does this change between years of low and high disease pressure.

### 2020-06-24 03_Prep_data.Rmd
revert

@@
    filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole") %>%
+             fungicide_ai == "propiconazole"|
+             fungicide_ai == "200 g/L azoxystrobin + 80 g/L cyproconazole") %>%
    group_by(trial_ref, location, year , Y_error_type, fungicide_ai) %>%

### 2020-06-24 04_MetaAnalysis.Rmd
Cleaning, editing, colours, grammar, spelling, headings, etc.

@@
 
-# Meta-analysis
-## Grain yield meta-analysis
+# Grain yield meta-analysis
 
@@
 
-First, how well the data is compared across the trial years and trials.
+First, how well does the data compare across the trial years and trials?
 
 ```{r table_of_nTreatments}
+# class spray_management as a factor and reorder them for the plot
+slimmer_PM_dat$spray_management <-
+   factor(slimmer_PM_dat$spray_management, rev(
+      c(
+         "control",
+         "Early",
+         "Recommended",
+         "Recommended_plus",
+         "Late",
+         "Late_plus"
+      )
+   ))
+
+ggplot(slimmer_PM_dat, aes(x = as.factor(year), fill = spray_management)) +
+   geom_bar(position = "dodge2") +
+   scale_fill_usq(name = "Spray Management") +
+   xlab("Year")
+
 kable(
@@
 
-Before analysis let's have a look at the trimmed down modified data.
-
-Treatments Late_plus and early don't have very good comparison to other treatments.
+Treatments `Late_plus` and `Early` don't have very good comparison to other treatments.
 
@@
 ```{r treatment_means_plot}
-# class spray_management as a factor and reorder them for the plot
-slimmer_PM_dat$spray_management <-
-   factor(slimmer_PM_dat$spray_management,
-          levels(factor(slimmer_PM_dat$spray_management))[rev(c(1, 2, 5, 6, 3, 4))])
-
 slimmer_PM_dat %>%
-   ggplot(aes(y = grain_yield.t.ha, x = spray_management)) +
-   geom_boxplot() +
-   #geom_point(position = "jitter", alpha = 1/5)+
-   geom_jitter(width = 0.1, alpha = 1 / 5) +
+   ggplot(
+      aes(
+         y = grain_yield.t.ha,
+         x = spray_management,
+         fill = spray_management,
+         colour = spray_management
+      )
+   ) +
+   geom_boxplot(alpha = 0.25) +
+   geom_jitter(width = 0.1, alpha = 0.5) +
    labs(x = "Spray management variable",
@@
    geom_hline(yintercept = 0, linetype = 2) +
-   coord_flip()
+   scale_fill_usq() +
+   scale_colour_usq() +
+   coord_flip() +
+   guides(fill = FALSE, color = FALSE)
 ```
 
-There seems like little difference between the treatments, with exception to `Late_plus`.
+There seems like little difference between the treatments, with exception of `Late_plus`.
 Let's do this plot again, but let's look at the proportional mean difference between the treatments and the no spray control for each study, this should reduce variation in yield due between trials.
@@
 ```{r plot_yieldProportion}
-slimmer_PM_dat$spray_management <-
-   factor(slimmer_PM_dat$spray_management, rev(
-      c(
-         "control",
-         "Early",
-         "Recommended",
-         "Recommended_plus",
-         "Late",
-         "Late_plus"
+slimmer_PM_dat %>%
+   filter(spray_management != "control") %>% 
+   ggplot(
+      aes(
+         y = prop_yield_gain,
+         x = spray_management,
+         fill = spray_management,
+         colour = spray_management
       )
-   ))
-
-slimmer_PM_dat %>%
-   ggplot(aes(y = prop_yield_gain, x = spray_management)) +
-   geom_boxplot() +
-   geom_jitter(width = 0.1, alpha = 1 / 5) +
+   ) +
+   geom_boxplot(alpha = 0.25) +
+   geom_jitter(width = 0.1, alpha = 0.5) +
    labs(x = "Spray management variable",
         y = "Grain yield (t/Ha)",
-        title = "Mean grain yield difference to the control for each treatment \n categorised by spray management scenario") +
+        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
    theme(plot.title = element_text(hjust = 0.5)) +
    geom_hline(yintercept = 0, linetype = 2) +
-   coord_flip()
+   scale_fill_usq() +
+   scale_colour_usq() +
+   coord_flip() +
+   guides(fill = FALSE, color = FALSE)
 ```
@@
 
-First lets remove any entries missing variance.
+First let's remove any entries missing variance.
 
@@
 slimmer_PM_dat <-
-   slimmer_PM_dat[!is.na(slimmer_PM_dat$yield_error),]
+   slimmer_PM_dat[!is.na(slimmer_PM_dat$yield_error), ]
 
@@
 #                                   2)
-#
+
 slimmer_PM_dat$vi2 <- 
@@
 slimmer_PM_dat$vi_C <- NA
-for (T_ref in slimmer_PM_dat$trial_ref) {
+for (i in slimmer_PM_dat$trial_ref) {
    # First we need to Calculate the pooled standard deviation
-   slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "pooledSD"] <-
-      sqrt(sum((slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "n"] - 1) * slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "yield_error"]) /
-              (sum(slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "n"]) - nrow(slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref,])))
+   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "pooledSD"] <-
+      sqrt(sum((slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "n"] - 1) * slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "yield_error"]) /
+              (sum(slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "n"]) - nrow(slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, ])))
 
-   # Then Create a column with the value of the mean grain yield of the no spray control for comparisons to the treatments means
-   slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref, "yi_C"] <-
-      mean(slimmer_PM_dat[slimmer_PM_dat$trial_ref == T_ref &
+   # Create a column with the value of the mean grain yield of the no spray
+   #  control for comparisons to the treatments means
+   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "yi_C"] <-
+      mean(slimmer_PM_dat[slimmer_PM_dat$trial_ref == i &
                              slimmer_PM_dat$fungicide_ai == "control",
@@
 }
+
 # Calculate standardised mean difference
@@
 
-Let's simplify our data.
+Let's simplify our data by removing the control data, converting disease pressure (`D_pres`) to a factor and selecting only the columns of data necessary for analysis.
 
@@
 
-## Meta-analysis
+## metafor analysis
 
-### metafor package
+For the first grain yield meta-analysis, we'll use the `metafor` package [@Viechtbauer2010].
 
@@
 Standardised mean differences have a bit of a long tail however this is not bad and transformations with log or square root will not work on negative values.
+So it looks like no transformation is necessary before we start the meta-analysis.
 
@@
 ```
-In this result we can see that the `Early` treatment is not significantly different to zero, which in this case is the mean of the no spray control. 
-However the other treatments are significantly different to zero.
+
+In this result we can see that the `Early` treatment is not significantly different from zero, which in this case is the mean of the no spray `control`.
+However the other treatments are significantly different from zero.
 The $Q_M$ [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, shows the moderators significantly influence the model ($Q_M = 24.4769, df = 5, p = 0.0002$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
@@
    method = "ML",
-   random = list(~ 1|trial),
+   random = list( ~ 1 | trial),
    data = dat1
@@
    method = "ML",
-   random = list(~ 1|location/year/trial_ref/dose/host_genotype/factor(row_spacing)/spray_management),
+   random = list(
+      ~ 1 |
+         location / year / trial_ref / dose / host_genotype / factor(row_spacing) /
+         spray_management
+   ),
    data = dat1
@@
 anova(PM_mv, PM_mv_St1) # PM_mv is the better model
-
 ```
 
-The simpler `PM_mv_St` model explains significantly less variation as the more complicated model `PM_mv`.
+The simpler `PM_mv_St` model explains significantly less variation than the more complicated model `PM_mv`.
 So we will keep the original model `PM_mv`.
@@
 The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis.
-The second table is in two parts(left and right). 
+The second table is in two parts (left and right). 
 The left part, rho, is the correlation of variation between the specified treatments.
 All comparisons were acceptable except for a comparison between `Early` and `Late_plus`, `0.000` rho.
-`Early` and `Late_plus` treatments never occurred within the same trial which is indicated by the right side of the table (hence the warning).
+`Early` and `Late_plus` treatments never occurred within the same trial, which is indicated by the right side of the table (hence the warning).
 
-The fixed effects, in the last table, showed that yields in single early spray treatments are not significantly different from zero, or the no spray control.
+The fixed effects, in the last table, show that yields in single early spray treatments are not significantly different from zero, or the no spray control.
 
@@
 
-Results show with the exclusion of the no spray control, `Early` applications are significantly worse than all other treatments leading to lower yield estimates. 
-`Late_plus` is estimated as saving the most yield compared and is significantly higher than all other treatments except `recommended_plus`.
-Let's view these comparisons in a plot.
+Results show with the exclusion of the no spray `control`, `Early` applications are significantly worse than all other treatments leading to lower yield estimates.
+`Late_plus` is estimated to save the most yield compared and is significantly higher than all other treatments except `Recommended_plus`.
+Let's look at how well each of the number treatments compare to each other.
 
@@
 
-efficacy <- tbl_df(results_AI)
+efficacy <- as_tibble(results_AI)
 efficacy$Treatment <-
@@
 
+Let's view these comparisons in a plot.
+
 ```{r metafor_plot}
 efficacy %>%
-   mutate(Treatment = factor(Treatment, levels = rev(c("Early", "Recommended", "Recommended_plus","Late","Late_plus"))))%>%
+   mutate(Treatment = factor(Treatment, levels = rev(
+      c(
+         "Early",
+         "Recommended",
+         "Recommended_plus",
+         "Late",
+         "Late_plus"
+      )
+   ))) %>%
    ggplot(aes(Treatment, Mean)) +
@@
    ) +
-   geom_hline(yintercept = 0)+
+   geom_hline(yintercept = 0) +
    geom_point(aes(size = 1 / SE), shape = 15) +
@@
    coord_flip()
-
 ```
-
-Let's look at how well each of the number treatments compare to each other.
 
@@
 
-We also want to know if disease pressure exerts an effect on the desicion for spray control.
+We also want to know if disease pressure exerts an effect on the decision for spray control.
 Above we can see spraying at the first sign of powdery mildew or with in `r min(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"| slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` - `r max(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"|                   slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` days after first sign is effective at mitigating yield loss.
@@
 These results show that the spray management variable we tested are not significantly better or worse between the two levels of disease pressure.
-It also shows that in trials with high disease pressure all treatments produced lower standardised mean differences. 
-Indicating that fungicide treatments were less effective at mitigating yeild loss in seasons which developed heavier infestations.  
-Finally lets compare the disease pressure model to the orignal model to see which one fits better.
+It also shows that in trials with high disease pressure, all treatments produced lower standardised mean differences. 
+Indicating that fungicide treatments were less effective at mitigating yield loss in seasons, which developed more severe infection levels.
+Finally let's compare the disease pressure model to the original model to see which one fits better.
 
@@
 ```
-No significant difference which informs us to use the origninal model `PM_mv` which is the simplest.
+
+No significant difference which informs us to use the original model `PM_mv`, which is the simplest.
 
@@
 
-We can use the netmeta package to give a graphical representation of the pairwise comparisons.
+## netmeta analysis
 
-### netmeta package
+We can use the `netmeta` package to give a graphical representation of the pairwise comparisons.
 
@@
 
-The `netmeta` analysis suggests the spray schedule commencing early are no different to any other treatment including the no spray control.
+The `netmeta` analysis suggests the spray schedule commencing early are no different to any other treatment including the no spray `control`.
 It estimates the mean is very similar to the recommended treatments.
-The recommended plus and late_plus treatments show higher mean estimates, however are not significantly different from the early estimate.
+The `Recommended_plus` and `Late_plus` treatments show higher mean estimates, however are not significantly different from the `Early` estimate.
 

### 2020-06-24 05_AUDPC_MetaAnalysis.Rmd
Markdown syntax, code formatting, grammar,

@@
 ```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer, metafor, here)
+if (!require("pacman"))
+   install.packages("pacman")
+pacman::p_load(tidyverse,
+               kableExtra,
+               bomrang,
+               lme4,
+               RColorBrewer,
+               metafor,
+               here)
 
 # Data
-PM_Mdat <- read.csv(here("cache/GYmeta_data.csv"))
+PM_Mdat <- read.csv(here("cache/GYmeta_data.csv")
+)
 ```
@@
 
-Now it's time to look at how the spray management scenarios might impact disease pressure on the mungbean yields.
+Now it's time to look at how the spray management scenarios might affect disease pressure effects on the mungbean yields.
 First let's evaluate which measure of disease is the most robust predictor for yield loss, AUDPC, AUDPS or disease incidence at the end of the season.
@@
    PM_Mdat[PM_Mdat$trial == i, c("slope", "SE")] <-
-      coef(summary(lm(grain_yield.t.ha ~ AUDPC_m, data = PM_Mdat[PM_Mdat$trial == i, ])))[2, 1:2]
+      coef(summary(lm(grain_yield.t.ha ~ AUDPC_m, data = PM_Mdat[PM_Mdat$trial == i,])))[2, 1:2]
 }
@@
 
-Now it's time to look at how the spray management scenarios might impact disease pressure on the mungbean yields.
-First lets evaluate which measure of disease is the most robust predictor for yield loss, AUDPC, AUDPS or disease incidence at the end of the season.
+Now it's time to look at how the spray management scenarios might affect disease pressure on the mungbean yields.
+First, let's evaluate which measure of disease is the most robust predictor for yield loss, AUDPC, AUDPS or disease incidence at the end of the season.
 
@@
 Area under the disease progress stairs (AUDPS) shows almost the same fit as the AUDPC linear model.
-AUDPC and AUDPS are not good predictors of loss in yield overall, without the inclusion of a `trial` parameter.
+AUDPC and AUDPS are not good predictors of loss in yield overall without the inclusion of a `trial` parameter.
 Let's test the model with the inclusion of `trial` as a random effect.
@@
 AUDPC becomes a significant predictor of grain yield when the random effect when accounting for `trial`.
-However we noticed in the plots earlier that not only the intercept but the slope varies depending on the trial.
+However, we noticed in the plots earlier that not only the intercept but the slope varies depending on the trial.
 Let's see if the model improves when AUDPC is used as a random slope for trial.
@@
 anova(Me_mod1, Me_mod2)
+```
 
-```
-The model is significantly improved, lower AIC and a higher log likelihood. Let's see if AUDPS improves in the same way.
+The model is significantly improved, lower AIC and a higher log likelihood.
+Let's see if AUDPS improves in the same way.
 
@@
 anova(Me_mod1.s, Me_mod2.s)
-
 ```
@@
 The R-squared of the AUDPC model is a better fit compared to the AUDPS model, and has a conditional $R^2$ value of `r round(r.squaredGLMM(Me_mod2)[2],4)`.
+
 > From here on we will use AUDPC.
@@
 Let's compare the area under the disease progress curve (AUDPC) to final severity.
+
 ```{r LMER_finalSev}
-
 Me_mod3 <- lmer(grain_yield.t.ha ~ PM_final_severity + (1 | trial),
@@
 Powdery mildew incidence at the end of the season was a significant covariate for grain yield, however was a weaker predictor compared to AUDPC.
-In addition model comparison shows AUDPC is significantly better at predicting grain yield.
+In addition, a model comparison shows AUDPC is significantly better at predicting grain yield.
 
 ### Spray management and AUDPC
+
 We shall proceed by including the spray management predictor into the analysis.
-First let's assess the `spray_management` variable as an additive fixed effect.
+First, let's assess the `spray_management` variable as an additive fixed effect.
 
@@
 anova(Me_mod2, Me_mod5)
+```
 
-```
 This model is significantly better and shows a lower AIC.
-However makes more sense to use `spray_management` as a interactive term with AUDPC_m.
-As you would assume AUDPC would be dependant on the `spray_management`.
+However, it makes more sense to use `spray_management` as an interactive term with AUDPC_m, as you would assume AUDPC would be dependant on the `spray_management`.
 
@@
 ```
+
 As expected the model produced an error warning stating the maximum number of evaluations were exceeded.
-Also the model comparisons show that the newer Me_mod7 was not a better model.
-We we proceed with Me_mod6 as the model with the best fit.
+Also the model comparisons show that the newer `Me_mod7` was not a better model.
+ We we proceed with `Me_mod6` as the model with the best fit.
 
@@
 ```
+
 The first output shows our random effects do a good job of explaining the variation leaving less residual variation than what is explained by the random intercept, trial.
@@
 The other fixed effects show the change in predicted yield as AUDPC increases under each of the spray_management factors.
-Spray_management treatments, control, early, and recommended show significant declines in grain_yields as AUDPC increases.
-Recommended_plus and Late_plus show no significant decline in grain yield as AUDPC increases.
+`Spray_management` treatments, `control`, `Early`, and `Recommended` show significant declines in `grain_yields` as AUDPC increases.
+`Recommended_plus` and `Late_plus` show no significant decline in grain yield as AUDPC increases.
 
@@
 Here the intercept represents a yield estimate for each trial without the limitation of the disease.
-AUDPC_m shows the slope of the regression for grain yield as AUDPC increases.
+`AUDPC_m` shows the slope of the regression for grain yield as AUDPC increases.
 The coefficients of the model (ordered by AUDPC) show that higher yielding trials had a steeper negative slope.
-In other words higher yielding mungbean crops were likely to see greater losses from disease.
+In other words, higher yielding mungbean crops were more likely to see greater losses from disease.
 
-## AUPDC impact on grain yield meta-analysis
+## AUPDC effect on grain yield meta-analysis
 
@@
 exp(-0.1196)
-
 ```

### 2020-06-24 07_Manuscript.Rmd
edits and additions

--- 2020-05-22 06_Publication_wireframe_and_7_Questions.Rmd
@@
----
-title: Meta-analysis of fungicide application timing experiments for powdery mildew
-  management in mungbean.
-author: "P. Melloy"
-date: "31/01/2020"
-output:
-  html_document: default
-  word_document: default
----
-
 ```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
@@
 
-# Manuscript wire frame
-
-## Who are the intended readers? - list 3 to 5 of them by name
-   * Adam Sparks – Plant disease modeller
-   * Levente Kiss – Powdery mildew taxonomist
-   * Lisa Kelly – Plant pathologist
-   * Paul MacIntosh – Mungbean/ pulse agronomist
-   * Ross Pomroy – Agronomist
-   * Jean Galloway – Plant disease modeller
-   * Art Diggle – Plant disease modeller
-
-## what did you do? (limit - 50 words)
-Undertook a meta-analysis of twenty four field trials aimed at improving the efficiency and timing of fungicides for control of powdery mildew on mungbean.
-
-## Why did you do it? (limit - 50 words)  
-Data from unpublished field trials independently did not provide a clear indication for when to apply fungicide to best mitigate yield losses from powdery mildew. 
-By analysing the collective data we aim to provide a better estimate for fungicide application timing to mitigate the yield loss from powdery mildew.
-
-## what happened? (limit - 50 words)  
-We found that fungicide sprays prior to when the powdery mildew was first spotted in the mungbean crop on average provided no yield protection. 
-A fungicide spray schedule of one or more fungicide applications commencing within three days of first sign of the disease significantly mitigated yield loss to the disease. 
-However a fungicide spray schedule of 2 or more applications commencing four days or later than first sign of disease saved the most yield.
-
-## What do the results mean in theory? (limit - 50 words)
-Fungicide spray schedules for control of powdery mildew in mungbean should commence around seven to nine days following the first signs of the disease.
-
-## What do the results mean in practice? (limit - 50 words)  
-Fungicide spray schedules that commence prior to signs of the disease establishing in the mungbean canopy are likely to be ineffective at mitigating the diseases impact on yield. 
-We also don’t have data on at what point starting a fungicide spray schedule is too late. 
-Growers can’t scout their crop three times a week in the fashion of researchers and are unlikely to identify the true date when signs of powdery mildew become apparent. 
-Therefore these results reinforce the message to growers to spray for powdery mildew as soon as it is observed in their crop to protect yields.
-
-## what is the key benefit for your readers? (limit - 25 words).  
-This study is the most robust analysis of management of powdery mildew in mungbean using fungicides. 
-It provides a more certain time frame for growers to plan when to commence a fungicide spray schedule.
-
-Fewer fungicide applications will reduce costs for growers and prolong the efficacy of fungicides before the disease develops resistance.
-
-## What remains unresolved? (no word limit).  
-Within the meta-analysis, some comparisons between spray management factors contained fewer replicates in comparison to other spray management factor combinations.
-Only a few studies incorporated in the meta-analysis contained comparisons between the “Late plus” factor and the treatments: negative spray control, a single spray at first sign, and spray at first sign with one or more follow-up applications.
-
-*****
-
 # Manuscript
@@
 The bean pod or grain can be consumed raw or added to meals after sprouting. 
-The dried grain can also be ground into a protein enriched flour for uses such as noodles, biscuits and cakes [@Chankaew2013].
+Dried mungbean grain can also be ground into a protein enriched flour for uses such as noodles, biscuits and cakes [@Chankaew2013].
 
 In Australia mungbean is grown in southern Queensland and northern New South Wales as a short season summer legume crop. 
-Approximately 90% of mungbean yields are exported and economic returns can be lucritive for growers. 
-Mungbean potentially yields up to 2.3 tonnes per hectare, with a value of up to \$ 1300 AUD a tonne [@QueenslandGovernment2019]. 
+Approximately 90% of mungbean yields are exported and economic returns can be lucrative for growers. 
+Mungbean potentially yields up to 2.3 tonnes per hectare and has a value of up to \$ 1300 AUD a tonne [@QueenslandGovernment2019]. 
 However these potential crop yields can be limited by a range of diseases[@Kelly2017a].
 Powdery mildew (*Podosphaera xanthii*), for instance, can reduce yields by up to 40% [@Chankaew2013]. 
-Fortunately a number of strategies are available to be employed to reduce the damage powdery mildew inflicts on mungbean yields.
+Fortunately a number of strategies are available to reduce the damage powdery mildew inflicts on mungbean yields.
 
@@
 ### Fungicide resistance
-Fungicide application costs in Australia are relatively cheap, and we estimate these costs to be approximatley \$ 20 AUD per hectare. 
-Lucrative returns of up to \$ 2260 per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than neccersary. 
-Excessive use of fungicides are not only costly, but lead to problems such as fungicide resistance. 
-*Podosphaera xanthii* is categorised by FRAC as a 'High risk' candidate to evolve fungicide resistance. 
+Fungicide application costs in Australia are relatively cheap, and we estimate these costs to be approximately \$ 20 AUD per hectare. 
+Lucrative returns of up to \$ 2260 per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than necessary. 
+Excessive use of fungicides may not only be a cost not regained, but also leads to fungicide resistance. 
+*Podosphaera xanthii* is categorised by FRAC as a 'High risk' candidate to evolve fungicide resistance [@FRACrisk2019]. 
 The evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with fungicide resistance potential in mind.
-Powdery mildew in cucurbits evolved resistance to benzimidazole within three years of it's registration [@Peterson1973].
-In cereal crops _Erysphe graminis_ showed lower sensitivity to strobilurins in 1998, two years after the fungicide began being used in Europe [@Chin2001].
-Powdery mildew is one such disease with an extensive track record of rapidly developing fungicide resistance. 
+Powdery mildew has an extensive track record of rapidly developing fungicide resistance. 
 In cucurbits, powdery mildew has evolved resistance to numerous fungicide classes, such as benzimidazoles, DMIs, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines [@Mcgrath2001].
+The resistance to benzimidazole was developed within three years of it's registration [@Peterson1973]. 
+In cereal crops _Blumeria graminis_ [OR Erysiphe???] showed lower sensitivity to strobilurins in 1998, two years after the fungicide began being used in Europe [@Chin2001].
 
 To extend the time that a fungicide remains effective against the target pathogen, strategic use of the fungicide must be considered. 
-Excessive fungicide sprays by a single active increase the selection preassure on the pathogen to evolve resistance [@Brent2007]. 
-If any strains of the pathogen with resistance to the fungicide are present in a population regular use of the fungicide will increase it's proportion in the population. 
+Excessive fungicide sprays by a single active increase the selection pressure on the pathogen to evolve resistance [@Brent2007]. 
+If any pathogen strains which contain fungicide resistance are present in a population, regular use of that fungicide will increase it's proportion of fungicide resistant strains in the population. 
 Managing the disease with fungicides for the highest economic return is likely not to require eradication of the causal pathogen. 
@@
 
-The timing of funcide sprays are critical for thier efficacy and for limiting fungicide resistant strains from emerging. 
-Fungicide applications made too early would increase costs without providing any benefit to yields. 
+The timing of fungicide sprays are critical for their efficacy and for limiting fungicide resistant strains from emerging. 
+Fungicide applications made too early would increase costs without providing any benefit to yields, while potentially selecting for pathogen strains possessing fungicide resistance. 
 Applications which are made too late allow the disease to establish and damage the crop productivity, while making subsequent sprays difficult to reduce the disease incidence.
@@
 ### Previous studies - fungicide work
-There is almost a complete lack of peer-reviewed literature summarising fungicide efficacy on powdery mildew in Mungbean. 
-Many of the experimental work has been published by funding agencies and state government extension departments. 
-Past field trials in eastern Australia have trialed a range of fungicide active ingredients, while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
-Early trials showed for a fungicide application to provide maximum efficacy a single fungicide application at first sign of the disease with another follow-up application two weeks later if necessary [@Sparks2017].
-Some of the trialled fungicides for treating powdery mildew in mungbean have been registered with the APVMA [@APVMA; @Kelly2017a; insert all published trials here].
+There is almost a complete lack of peer-reviewed literature summarising fungicide efficacy on powdery mildew in mungbean despite numerous experimental trials.
+Results of these past trials have been published as reports on websites or newsletters produced by funding agencies and state government extension departments. 
+Past field trials in eastern Australia have trialled a range of fungicide active ingredients, while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
+
+{A number of fungicides for treating powdery mildew in mungbean have been registered with the APVMA [@APVMA; @Kelly2017a; insert all published trials here]. 
+However } _remove_
 
 ### Meta-analysis
-Meta-analyses are statistical tools which can analyse a collection of experiments which have a similar aim and estimates the difference between the control and treatment means. 
+Meta-analyses are statistical tools which can aggregate the results from a collection of experiments in order to provide a weighted estimate of the true size of the 'effect'.
+When aggregating studies, each one should have a similar aim and measure the same effects. 
 The outcome of a meta-analysis provides a more accurate estimation of the true treatments effect, because it considers the amount of variance in each study, and weights the influence of each study on the treatment effects according to the study statistical accuracy.
-Using a meta-analysis on the
 
@@
 
-The data for this study were obtained from through personal correspondence with colleagues and collaborating institutions.
+The data for this meta-analysis study were obtained from through personal correspondence with colleagues and collaborating institutions.
 The majority of the trials were undertaken by Malcolm Riley and Dr Sue Thompson with The Department of Agriculture and Primary industries (DAF). 
 Trials undertaken in 2013 season were conducted by the Northern growers alliance [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013].
-The most recent trials from 2017 were undertaken by DAF and the University of Southern Queensland (USQ) from 2017 to 2019. 
-Trial data were in different formats with varying levels of information.
+The most recent trials were undertaken by DAF and the University of Southern Queensland (USQ) from 2017 to 2019. 
+Trial data from all years were in different formats with varying levels of information.
 Some trial data reported means of each treatment, with all but one study reporting variance along with the mean. 
-For 17 trials the raw data were obtained.
+Twenty six trials in total were collated, Raw data were obtained from 17 trials and the treatment means were obtained for the remainder.
 
-Details of trial data is presented within a research compendium which was prepared to supplement this publication [insert reference to compendium].
+Details of trial data are presented within a research compendium which was prepared to supplement this publication [insert reference to compendium].
 
 The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the northern grains regions of eastern Australia.
-Trial data had to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; and crop yield. 
-A total of 26 trials were collated and from these trials we selected the most frequently tested fungicides that had the same mode of action. 
-The data were subset to only include treatments using demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole to reduce confounding effects of fungicides with varying modes of action. 
+Trial data had to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; the fungicide active ingredients; fungicide dose; and crop yield.
+The data were subset to only include treatments with the same mode of action; demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole were thus retained in the dataset. 
 Subsequently the 26 trials were reduced to 17 using the same fungicide doses (Table 1). 
@@
 All trials included in this analysis were a randomised complete block design and not previously published in peer-reviewed literature.
-Some trials and results were reported online via the Grains Research and Development Corporation. 
-While the main aim of all the trials collected for this study were to assess the efficacy of fungicide for control of powdery mildew, some trials  included additional variables in the experimental design.
-These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar and  supplimentary irrigation, in addition to trial location and season.
-To account for this variation between trials, and the treatments within trials, a single 'trial' factor was created to describe the main variables; trial location, trial season, host genotype and row spacing.
+
+While the main aim of all the trials collected for this study were to assess the efficacy of fungicide for control of powdery mildew, some trials tested additional variables in the experimental design.
+These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar and supplementary irrigation.
+To account for this variation, and the variation from season and location, between trials, a single 'trial' factor was created to describe the main variables; trial location, trial season, host genotype, row spacing, and dose.
 Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 - 9 ordinal scale (Table 2). 
 The 2013 NGA trials however (table 1), reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the canopy; lower, middle or upper canopy. 
-Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, it was strait-forward to calculate the equivalent incidence on the ordinal 1 - 9 scale.
+Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, conversion to the ordinal scale 1 - 9 was strait-forward.
 
-The timing of fungicide applications, with reference to when the disease first occurred in the trial, and number of applications were used to define a treatment variable. 
-An 'Early' fungicide application, refers to a fungicide spray schedule that commences with the first spray prior to the disease being observed in the trial. 
-'Recommended' refers to a fungicide spray schedule which commences within three days following the first sign of disease, and 'late' treatments which commence four days or later than first sign. 
-The number of fungicide applications were binned in to two categories. 
-A spray schedule with a single spray, and a spray schedule with one or more sprays to a maximum of three applications. 
-The division of the treatments into these six categories created two categories with insuffient numbers of treatments to provide a reliable sample. 
-Single late sprays contained two replicates and mulitple early sprays contained five replicates and were therefore removed from the subsequent meta-analysis.
+The timing of fungicide application treatments, was defined with reference to the recorded date when powdery mildew first occurred in the trial. 
+An 'Early' fungicide application treatment, refers to a fungicide spray schedule that commences with the first spray prior to the disease being observed in the trial. 
+'Recommended' refers to a fungicide spray schedule which commences within three days following the first sign of disease, and 'late' treatments which commence between 7 - 13 days after the first sign of disease.
+The total number of fungicide applications were binned in to two categories. 
+A spray schedule with a single spray, and a spray schedule with two or three spray applications (_plus). 
+The division of the treatments into these six categories created one category with insufficient numbers of treatments to provide a reliable sample. 
+'Early' treatments with more than one spray contained five replicates and were therefore removed from the subsequent meta-analysis.
 
@@
 Where $MSE$ is the mean squared error of each trial and $n$ is the total number of trials. 
-
 Sample variance was computed from the trial MSE using the following equation, where $i$ is the $i$th trial, n is the number of replicates and $\overline{Y}$ is the mean grain yield for that treatment.

### 2020-06-24 07_Manuscript.Rmd
edits and removal of imputation of variance explaination

@@
 
-What remained was the mean yield for total of 173 treatments in the following five spray schedule categories: no spray control, single early spray, single recommended spray, recommended with multiple sprays and late with multiple sprays.
+What remained was the mean yield for total of 173 treatments in the following five spray schedule categories: no spray control, single early spray, single recommended spray, recommended with multiple sprays, single late spray, and late with multiple sprays.
 
-For the trials which we had raw data, mean grain yields for each were calculated and the mean squared error within trial obtained from an anova of each study. 
+For the trials which we had raw data, mean grain yields and sample variance for each treatments calculated. 
 Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 1.697 and the approach reported in Ngugi et al. [@Ngugi2011]. 
 The T-critical value was determined from the 30 degrees of freedom using a t-distribution table. 
-For the remainder of the trial data only the treatment means and variance were reported, except for Gatton in 2012 and Emerald in 2015. 
-The Gatton and Emerald trials reported treatment means without accompaning variance. 
-The Gatton and Emerald trials also reported no significant difference in yield between the treatments. 
-When imputing the variance for these trials they were checked to ensure the new variances did not confer a significant difference between the treatments. 
-If the new variance did confer a significant differance between any of the treatments the imputation function was rerun.
-Trial variance was imputed by sampling from a normal distribution where the mean and standard deviation were calculated from the log of all the trials mean square errors.  
-$rnorm(\overline{x}_{log(MSE_{1}) \dots, log(MSE_{n})}, \sigma_{log(MSE_{1}) \dots, log(MSE_{n})})$  
-Where $MSE$ is the mean squared error of each trial and $n$ is the total number of trials. 
-Sample variance was computed from the trial MSE using the following equation, where $i$ is the $i$th trial, n is the number of replicates and $\overline{Y}$ is the mean grain yield for that treatment.
-$v_i = MSE_{i}/(n_{i} * \overline{Y}_{i}^2)$
+For the remainder of the trial data, the treatment means and variance were reported, except for Gatton in 2012 and Emerald in 2015. 
+The Gatton and Emerald trials reported treatment means without accompanying variance and were thus removed prior to the analysis.
 

### 2020-06-24 07_Manuscript.Rmd
Edits for clarity, move FR content to Discussion

@@
 PM_Mdat <- read.csv(here("cache/PM_MB_updated.csv"))
-
 ```
@@
 ## Introduction
-Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown in south-east Asia for human consumption, and constitutes an affordable source of protein [@PulseAustralia]. 
+
+Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown in south-east Asia for human consumption and constitutes an affordable source of protein [@PulseAustralia].
 The bean pod or grain can be consumed raw or added to meals after sprouting.
-Dried mungbean grain can also be ground into a protein enriched flour for uses such as noodles, biscuits and cakes [@Chankaew2013].
+The dried grain can also be ground into a protein enriched flour for uses such as noodles, biscuits and cakes [@Chankaew2013].
 
 In Australia mungbean is grown in southern Queensland and northern New South Wales as a short season summer legume crop.
-Approximately 90% of mungbean yields are exported and economic returns can be lucrative for growers. 
-Mungbean potentially yields up to 2.3 tonnes per hectare and has a value of up to \$ 1300 AUD a tonne [@QueenslandGovernment2019]. 
-However these potential crop yields can be limited by a range of diseases[@Kelly2017a].
-Powdery mildew (*Podosphaera xanthii*), for instance, can reduce yields by up to 40% [@Chankaew2013]. 
-Fortunately a number of strategies are available to reduce the damage powdery mildew inflicts on mungbean yields.
+Approximately 90&nbsp;% of Australian mungbean produced is exported and economic returns can be lucrative for growers.
+Mungbean potentially yields up to 2.3 tonnes per hectare, with a value of up to \$&nbsp;1300 AU a tonne [@QueenslandGovernment2019].
+However, these potential crop yields can be limited by a range of diseases [@Kelly2017a].
+For instance, powdery mildew is caused by two separate genera of fungi in Australia _Podosphaera xanthii_ and an unnamed _Psuedoidium sp._ (Kiss and Kelly Personal Communication) and can reduce yields by up to 40% [@Chankaew2013].
+Fortunately a number of strategies are available to be employed to reduce the damage powdery mildew inflicts on mungbean yields.
 
-### Managements strategies
-#### and conditions for infection
+### Management Strategies
+
 Planting date is an effective strategy for preventing the development of powdery mildew in mungbean.
-Powdery mildew infection requires cool temperatures, between 22$^\circ$ and 26$^\circ$C, and a leaf surface that is not overly wet for infection [@Kelly2017a]. 
-In southern Queensland and northern New South Wales, sowing dates between late spring (November) and mid-summer (January) are advised to avoid the conducive cooler autumn temperatures which normally commence in March.
-Therefore a delayed sowing date increases the possibility powdery mildew will infect earlier in the crop development leading to greater yield losses.
+Powdery mildew infection requires cool temperatures, between 22&deg; and 26&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
+In southern Queensland and northern New South Wales, sowing dates between late spring (November) and mid-summer (January) are advised to avoid the conducive cooler autumn temperatures, which normally commence in March.
+Therefore, a delayed sowing date of late January into February increases the possibility powdery mildew will infect earlier in the crop development cycle and cause greater yield losses than in earlier sown mungbean crops.
 
-Commercially available mungbean cultivars in Australia lack sufficient resistance to be used as a sole powdery mildew management strategy.
+Commercially available mungbean cultivars in Australia lack sufficient resistance to be used as a sole powdery mildew management strategy. <!-- Citation needed -->
 Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013].
-In Australia, quantitative resistance has also been incorporated a couple of varieties which are commercially available. 
-Jade-AU is recommended as containing the best disease resistance to powdery mildew (moderately susceptible), while also conferring quantifiable resistance to other foliar diseases such as tan spot and halo blight [@AustralianMungbeanAssociation].
-Because cultivar choice does not confer complete resistance to powdery mildew, additional strategies such as fungicide treatments are necessary to limit yield loss when conditions for the disease are suitable.
+In Australia, quantitative resistance has also been incorporated into few commercially available varieties.
+Jade-AU <!-- Need PBR emblem here --> has the the best disease resistance to powdery mildew (moderately susceptible), while also conferring quantifiable resistance to other foliar diseases such as tan spot (_Curtobacterium flaccumfaciens_ pv.
+_flaccumfaciens_) and halo blight (_ Pseudomonas savastanoi_ pv.
+_phaseolicola_) [@AustralianMungbeanAssociation].
+Because cultivar choice does not confer complete resistance to powdery mildew, additional strategies such as fungicide treatments are necessary to limit yield loss when conditions for the disease are conducive.
 
-The recent release of 'PowderyMildewMBM', a decision support system (DSS), increases the ease for preparing a fungicide spray schedule to manage powdery mildew [@Diggle]. 
+A recent development, the release of an app for tablet devices, 'PowderyMildewMBM' a decision support system (DSS) tool, increases the ease of preparing a fungicide spray schedule to manage powdery mildew [@Diggle].
 PowderyMildewMBM provides a cost benefit analysis to growers for fungicide spray schedule scenarios.
 The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability that one or two fungicide sprays would protect yields sufficiently to increase the net profit.
+<!-- this might need more -->
 
-### Fungicide resistance
-Fungicide application costs in Australia are relatively cheap, and we estimate these costs to be approximately \$ 20 AUD per hectare. 
-Lucrative returns of up to \$ 2260 per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than necessary. 
-Excessive use of fungicides may not only be a cost not regained, but also leads to fungicide resistance. 
-*Podosphaera xanthii* is categorised by FRAC as a 'High risk' candidate to evolve fungicide resistance [@FRACrisk2019]. 
-The evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with fungicide resistance potential in mind.
-Powdery mildew has an extensive track record of rapidly developing fungicide resistance. 
-In cucurbits, powdery mildew has evolved resistance to numerous fungicide classes, such as benzimidazoles, DMIs, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines [@Mcgrath2001].
-The resistance to benzimidazole was developed within three years of it's registration [@Peterson1973]. 
-In cereal crops _Blumeria graminis_ [OR Erysiphe???] showed lower sensitivity to strobilurins in 1998, two years after the fungicide began being used in Europe [@Chin2001].
+### Previous Studies
 
-To extend the time that a fungicide remains effective against the target pathogen, strategic use of the fungicide must be considered. 
-Excessive fungicide sprays by a single active increase the selection pressure on the pathogen to evolve resistance [@Brent2007]. 
-If any pathogen strains which contain fungicide resistance are present in a population, regular use of that fungicide will increase it's proportion of fungicide resistant strains in the population. 
-Managing the disease with fungicides for the highest economic return is likely not to require eradication of the causal pathogen. 
-Integrated pest management practices focus on using only the required number of chemical control to protect the economic return. 
-These strategies permit the presence of yield limiting diseases and pests if intervening would cost more than the economic return of protection.
-
-The timing of fungicide sprays are critical for their efficacy and for limiting fungicide resistant strains from emerging. 
-Fungicide applications made too early would increase costs without providing any benefit to yields, while potentially selecting for pathogen strains possessing fungicide resistance. 
-Applications which are made too late allow the disease to establish and damage the crop productivity, while making subsequent sprays difficult to reduce the disease incidence.
-
-### Previous studies - fungicide work
-There is almost a complete lack of peer-reviewed literature summarising fungicide efficacy on powdery mildew in mungbean despite numerous experimental trials.
-Results of these past trials have been published as reports on websites or newsletters produced by funding agencies and state government extension departments. 
-Past field trials in eastern Australia have trialled a range of fungicide active ingredients, while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
-
-{A number of fungicides for treating powdery mildew in mungbean have been registered with the APVMA [@APVMA; @Kelly2017a; insert all published trials here]. 
-However } _remove_
+There is almost a complete lack of peer-reviewed literature summarising fungicide efficacy on powdery mildew in mungbean. 
+Much of the experimental work has been published by funding agencies and state government extension departments as extension bulletins or other related type materials.
+Past field trials in eastern Australia have tested a range of fungicide active ingredients while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
+Early trials showed that for a fungicide application to provide maximum efficacy, a single fungicide application at first sign of the disease with another follow-up application two weeks later if necessary was the most effective [@Sparks2017].
+Some of the fungicides tested for controlling powdery mildew in mungbean have been registered with the APVMA [@APVMA; @Kelly2017a; <!-- insert all published trials here -->].
 
 ### Meta-analysis
-Meta-analyses are statistical tools which can aggregate the results from a collection of experiments in order to provide a weighted estimate of the true size of the 'effect'.
-When aggregating studies, each one should have a similar aim and measure the same effects. 
-The outcome of a meta-analysis provides a more accurate estimation of the true treatments effect, because it considers the amount of variance in each study, and weights the influence of each study on the treatment effects according to the study statistical accuracy.
+
+Meta-analyses are statistical tools which can analyse a collection of experiments, which have a similar aim, and estimates the difference between the control and treatment means. 
+The outcome of a meta-analysis provides a more accurate estimation of the true treatments effect, because it considers the amount of variance in each study and weights the influence of each on the treatment effects according to the study's statistical accuracy.
+Using a meta-analysis on the <!-- more goes here ? -->
 
@@
 
-The aim of this meta-analysis was to determine, from a collection of unpublished studies, what spray management scenario provides the greatest yield protection from powdery mildew in mungbean.
+The aim of this meta-analysis was to determine, from a collection of unpublished studies, what spray management scenario provides the greatest yield protection from powdery mildew in Australian mungbean.
 
-*****
+## Materials and Methods
 
-## Materials and methods
+The data for this study were obtained from through personal correspondence with colleagues and collaborating institutions.
+The majority of the trials were undertaken by Professor Malcolm Riley and Dr Sue Thompson with the Queensland Department of Agriculture, Fisheries and Forestry (DAF). 
+Trials undertaken in the 2013 season were conducted by the Northern Growers Alliance (NGA) [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013].
+<!-- should check, Sue and Mal moved to USQ in 2015 I think.
+Therefore the trials probably started with USQ earlier --> The most recent trials starting from 2016 were undertaken by the University of Southern Queensland (USQ) with the assistance of Queensland DAF from 2016 to 2019.
+Trial data were in different formats with varying levels of information.
+Some trial data reported means of each treatment, with all but one study reporting variance along with the mean. 
+Raw data were obtained for 26 trials in total.
 
-The data for this meta-analysis study were obtained from through personal correspondence with colleagues and collaborating institutions.
-The majority of the trials were undertaken by Malcolm Riley and Dr Sue Thompson with The Department of Agriculture and Primary industries (DAF). 
-Trials undertaken in 2013 season were conducted by the Northern growers alliance [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013].
-The most recent trials were undertaken by DAF and the University of Southern Queensland (USQ) from 2017 to 2019. 
-Trial data from all years were in different formats with varying levels of information.
-Some trial data reported means of each treatment, with all but one study reporting variance along with the mean. 
-Twenty six trials in total were collated, Raw data were obtained from 17 trials and the treatment means were obtained for the remainder.
+Details of trial data are presented within a research compendium which was prepared to supplement this publication [<!-- DOI to reference to compendium -->].
 
-Details of trial data are presented within a research compendium which was prepared to supplement this publication [insert reference to compendium].
+The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the Grains Research and Development (GRDC) northern grains regions of eastern Australia, which grows the majority of Australia's summer crops.
+Trial data had to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; and crop yield.
+A total of 26 trials were collated and from these trials we selected the most frequently tested fungicides that had the same mode of action. 
+The data were subset to only include treatments using demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole, to reduce confounding effects of fungicides with different modes of action.
+Subsequently the 26 trials were reduced to 17 using the same fungicide doses (Table 1). 
+With only a small number of trials and to increase the replication, we made no distinction between the tebuconazole and propiconazole in the analysis.
 
-The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the northern grains regions of eastern Australia.
-Trial data had to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; the fungicide active ingredients; fungicide dose; and crop yield.
-The data were subset to only include treatments with the same mode of action; demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole were thus retained in the dataset. 
-Subsequently the 26 trials were reduced to 17 using the same fungicide doses (Table 1). 
-With only a small number of trials to increase the replication, we made no distinction between the tebuconazole and propiconazole in the analysis.
+All trials included in this analysis were a randomised complete block designs and not previously published in peer-reviewed literature.
+Some trials and results were reported online via the GRDC. 
+While the main aim of all the trials collected for this study were to assess the efficacy of fungicide for control of powdery mildew, some trials included additional variables in the experimental design.
+These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar and supplementary irrigation, in addition to trial location and season.
+To account for this variation between trials, and the treatments within trials, a single 'trial' factor was created to describe the main variables; trial location, trial season, host genotype and row spacing.
+Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 -- 9 ordinal scale (Table 2). 
+However, the 2013 NGA trials (Table 1) reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the canopy; lower, middle or upper canopy.
+Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, it was strait-forward to calculate the equivalent incidence on the ordinal 1 -- 9 scale.
 
-All trials included in this analysis were a randomised complete block design and not previously published in peer-reviewed literature.
-
-While the main aim of all the trials collected for this study were to assess the efficacy of fungicide for control of powdery mildew, some trials tested additional variables in the experimental design.
-These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar and supplementary irrigation.
-To account for this variation, and the variation from season and location, between trials, a single 'trial' factor was created to describe the main variables; trial location, trial season, host genotype, row spacing, and dose.
-Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 - 9 ordinal scale (Table 2). 
-The 2013 NGA trials however (table 1), reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the canopy; lower, middle or upper canopy. 
-Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, conversion to the ordinal scale 1 - 9 was strait-forward.
-
-The timing of fungicide application treatments, was defined with reference to the recorded date when powdery mildew first occurred in the trial. 
-An 'Early' fungicide application treatment, refers to a fungicide spray schedule that commences with the first spray prior to the disease being observed in the trial. 
-'Recommended' refers to a fungicide spray schedule which commences within three days following the first sign of disease, and 'late' treatments which commence between 7 - 13 days after the first sign of disease.
-The total number of fungicide applications were binned in to two categories. 
-A spray schedule with a single spray, and a spray schedule with two or three spray applications (_plus). 
-The division of the treatments into these six categories created one category with insufficient numbers of treatments to provide a reliable sample. 
-'Early' treatments with more than one spray contained five replicates and were therefore removed from the subsequent meta-analysis.
+The timing of fungicide applications, with reference to when the disease first occurred in the trial, and number of applications were used to define a treatment variable. 
+An 'Early' fungicide application, refers to a fungicide spray schedule that commences with the first spray prior to the disease being observed in the trial.
+'Recommended' refers to a fungicide spray schedule which commences within three days following the first sign of disease, and 'late' treatments which commence four days or later than first sign.
+The number of fungicide applications were binned in to two categories.
+A spray schedule with a single spray, and a spray schedule with one or more sprays to a maximum of three applications.
+The division of the treatments into these six categories created two categories with insufficient numbers of treatments to provide a reliable sample.
+Single late sprays contained two replicates and multiple early sprays contained five replicates and were therefore removed from the subsequent meta-analysis.
 
@@
 
-For the trials which we had raw data, mean grain yields and sample variance for each treatments calculated. 
-Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 1.697 and the approach reported in Ngugi et al. [@Ngugi2011]. 
+Mean grain yields and sample variance for each treatment was calculated for trials for which we had the raw data.
+Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 1.697 and the approach reported in Ngugi et al. [-@Ngugi2011].
 The T-critical value was determined from the 30 degrees of freedom using a t-distribution table.
@@
 
-The data were analysed in the R statistical software environment using two meta-analysis packages, `metafor` and `netmeta`.
+The data were analysed in the R statistical software environment, version 4.0.1, [@RCoreTeam2020] using two contributed meta-analysis packages, `metafor`, version 2-4.0, [@Viechtbauer2010] and `netmeta`, version 1.2-1, [@Rucker2020].
 
-```{r Table1_ExperimentalDetail, echo=TRUE, message=FALSE, warning=FALSE}
-
+```{r Table1_ExperimentalDetail, echo=FALSE, message=FALSE, warning=FALSE}
 PM_Mdat %>%
-   filter(fungicide_ai == "tebuconazole" | fungicide_ai == "propiconazole") %>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole") %>%
    group_by(trial_ref) %>%
-   summarise(year = unique(year),
+   summarise(
+      year = unique(year),
       location = unique(location),
       planting_date = unique(planting_date),
-             first_sign_disease = unique(first_sign_disease))%>%
-   arrange(year)%>%
-   mutate(Research_org = c(rep("Queensland DAF",times =4),
+      first_sign_disease = unique(first_sign_disease)
+   ) %>%
+   arrange(year) %>%
+   mutate(Research_org = c(
+      rep("Queensland DAF", times = 4),
       rep("Northern Growers Alliance", times = 4),
-                           rep("Queensland DAF",times =4),
-                           rep("USQ", times = 5))) %>%
-   kable(caption = "Table 1: Description of Experiments")%>%
+      rep("Queensland DAF", times = 4),
+      rep("USQ", times = 5)
+   )) %>%
+   kable(caption = "Table 1: Description of Experiments") %>%
    kable_styling(fixed_thead = TRUE,
@@
 
-```{r}
-data.frame(Scale = 1:9,
-           `Scale Description` = c("No sign of powdery mildew",
+```{r Table2_1to9Scale, echo=FALSE}
+data.frame(
+   Scale = 1:9,
+   `Scale Description` = c(
+      "No sign of powdery mildew",
       "Small colonies in lower 1/3 of canopy, up to 75% of plants affected",
@@
       "Colonies to top of the plant with > 100 % of plants affected and heavy leaf drop"
-                                )) %>%
-   kable(caption = "Table 2: Powdery Mildew severity scoring scale")%>%
+   )
+) %>%
+   kable(caption = "Table 2: Powdery Mildew severity scoring scale") %>%
    kable_styling(fixed_thead = T, full_width = T)
@@
 
-### Fungicide resistance
-According to the Fungicide resistance Action Committee (FRAC) it is important to alternate or mix Fungicides with different modes of action to avoid fungicide resistance. 
+### Fungicide Resistance
+
+Fungicide application costs in Australia are relatively cheap.
+We estimate these costs to be approximately \$&nbsp;20 AU per hectare.
+Lucrative returns of up to \$&nbsp;2260 AU per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than necessary.
+Excessive use of fungicides are not only costly, but lead to problems such as fungicide resistance.
+_Podosphaera xanthii_ is categorised by the Australian Fungicide resistance Action Committee (FRAC) as a 'High risk' candidate to evolve fungicide resistance.
+Prior experiences confirm that the evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with potential fungicide resistance in mind.
+Powdery mildew is one such group of fungal pathogens with an extensive track record of rapidly developing fungicide resistance.
+In cucurbits, it evolved resistance to benzimidazole within three years of its registration [@Peterson1973] and has evolved resistance to numerous fungicide classes, such as benzimidazoles, demethylation inhibitors, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines since [@Mcgrath2001].
+In cereal crops _Blumeria graminis_ showed reduced sensitivity to strobilurins in 1998, two years after the fungicides began being used in Europe [@Chin2001].
+
+To extend the time that a fungicide remains effective against the target pathogen, strategic use of the fungicide must be considered.
+Excessive fungicide sprays by a single active increase the selection pressure on the pathogen to evolve resistance [@Brent2007]. 
+If any strains of the pathogen with resistance to the fungicide are present in a population regular use of the fungicide will increase it's proportion in the population. 
+Managing the disease with fungicides for the highest economic return is likely not to require eradication of the causal pathogen. 
+Integrated pest management practices focus on using only the required number of chemical control to protect the economic return. 
+These strategies permit the presence of yield limiting diseases and pests if intervening would cost more than the economic return of protection.
+
+The timing of fungicide sprays are critical for their efficacy and for limiting fungicide resistant strains from emerging. 
+Fungicide applications made too early would increase costs without providing any benefit to yields. 
+Applications which are made too late allow the disease to establish and damage the crop productivity, while making subsequent sprays difficult to reduce the disease incidence.
+
+According to the Fungicide resistance Action Committee (FRAC) it is important to alternate or mix fungicides with different modes of action to avoid fungicide resistance. 
 At the time of writing, in Australia one fungicide is registered with the to treat powdery mildew in mungbean, Veritas/Custodia (200 g/L tebuconazole with 120 g/L azoxystrobin).
@@
 Sulphur is a non-systemic protectant and thus provides an excellent option for rotation to limit the emergence of fungicide resistance.
+
+# References

### 2020-06-24 07_Manuscript.Rmd
Revise the structure of the paper again and add references

@@
 In Australia mungbean is grown in southern Queensland and northern New South Wales as a short season summer legume crop.
-Approximately 90&nbsp;% of Australian mungbean produced is exported and economic returns can be lucrative for growers.
-Mungbean potentially yields up to 2.3 tonnes per hectare, with a value of up to \$&nbsp;1300 AU a tonne [@QueenslandGovernment2019].
-However, these potential crop yields can be limited by a range of diseases [@Kelly2017a].
-For instance, powdery mildew is caused by two separate genera of fungi in Australia _Podosphaera xanthii_ and an unnamed _Psuedoidium sp._ (Kiss and Kelly Personal Communication) and can reduce yields by up to 40% [@Chankaew2013].
-Fortunately a number of strategies are available to be employed to reduce the damage powdery mildew inflicts on mungbean yields.
+Approximately 90&nbsp;% of Australian mungbean produced is exported and economic returns can be lucrative for growers with a value of up to \$1300&nbsp;AU a tonne [@QueenslandGovernment2019].
+Mungbean potentially yields up to 3 tonnes per hectare but the average Australian farm still yields less than 1 tonne per hectare [@Chauhan2018].
 
-### Management Strategies
+Part of the low yields can be attributed to a range of diseases that affect the crop [@Kelly2017a].
+Two major foliar diseases, tan spot or common wilt (_Curtobacterium flaccumfaciens_ pv.
+_flaccumfaciens_) and halo blight (_Pseudomonas savastanoi_ pv.
+_phaseolicola_), are the main focus of the Australian Mungbean Improvement programme's resistance breeding efforts due to lack of effective chemical controls for them.
+While a third disease, powdery mildew, is frequently controlled through an integrated disease management strategy of fungicide treatments and cultural practices.
+The disease can reduce yields by up to 40% [@Chankaew2013] in susceptible cultivars.
 
-Planting date is an effective strategy for preventing the development of powdery mildew in mungbean.
-Powdery mildew infection requires cool temperatures, between 22&deg; and 26&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
+Powdery mildew is caused by two separate genera of fungi in Australia _Podosphaera xanthii_ and an unnamed _Psuedoidium sp._ (Kiss and Kelly Personal Communication).
+While the pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified.
+
+Weather conditions that favour the development of the disease are cool temperatures between 22&deg; and 26&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
+Because of this, planting date is an effective strategy for preventing the development of powdery mildew in mungbean.
 In southern Queensland and northern New South Wales, sowing dates between late spring (November) and mid-summer (January) are advised to avoid the conducive cooler autumn temperatures, which normally commence in March.
@@
 In Australia, quantitative resistance has also been incorporated into few commercially available varieties.
-Jade-AU <!-- Need PBR emblem here --> has the the best disease resistance to powdery mildew (moderately susceptible), while also conferring quantifiable resistance to other foliar diseases such as tan spot (_Curtobacterium flaccumfaciens_ pv.
-_flaccumfaciens_) and halo blight (_ Pseudomonas savastanoi_ pv.
-_phaseolicola_) [@AustralianMungbeanAssociation].
+Jade-AU <!-- Need PBR emblem here --> has the the best disease resistance to powdery mildew (moderately susceptible).
 Because cultivar choice does not confer complete resistance to powdery mildew, additional strategies such as fungicide treatments are necessary to limit yield loss when conditions for the disease are conducive.
 
-A recent development, the release of an app for tablet devices, 'PowderyMildewMBM' a decision support system (DSS) tool, increases the ease of preparing a fungicide spray schedule to manage powdery mildew [@Diggle].
-PowderyMildewMBM provides a cost benefit analysis to growers for fungicide spray schedule scenarios.
-The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability that one or two fungicide sprays would protect yields sufficiently to increase the net profit.
-<!-- this might need more -->
-
-### Previous Studies
-
-There is almost a complete lack of peer-reviewed literature summarising fungicide efficacy on powdery mildew in mungbean. 
+There is almost a complete lack of peer-reviewed literature summarising fungicide efficacy on powdery mildew in Australian mungbean. 
 Much of the experimental work has been published by funding agencies and state government extension departments as extension bulletins or other related type materials.
@@
 
-### Meta-analysis
-
 Meta-analyses are statistical tools which can analyse a collection of experiments, which have a similar aim, and estimates the difference between the control and treatment means.
+Using a meta-analysis can be useful in situations like this where several studies exist, that have the same objective but may not provide a clear answer to the question due to variation in the results within the individual studies.
 The outcome of a meta-analysis provides a more accurate estimation of the true treatments effect, because it considers the amount of variance in each study and weights the influence of each on the treatment effects according to the study's statistical accuracy.
@@
 
+A recent development, the release of an app for tablet devices, 'PowderyMildewMBM' a decision support system (DSS) tool, increases the ease of preparing a fungicide spray schedule to manage powdery mildew [@Diggle].
+PowderyMildewMBM provides a cost benefit analysis to growers for fungicide spray schedule scenarios.
+The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability that one or two fungicide sprays would protect yields sufficiently to increase the net profit.
+<!-- Think about how to word this, that we are using this to validate the app: The findings of this meta-analysis confirm the recommendations that PowderyMildewMBM gives in most situations would be correct.
+-->
+
 ### Fungicide Resistance
@@
 Fungicide application costs in Australia are relatively cheap.
-We estimate these costs to be approximately \$&nbsp;20 AU per hectare.
-Lucrative returns of up to \$&nbsp;2260 AU per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than necessary.
+We estimate these costs to be approximately \$20&nbsp;AU per hectare.
+Lucrative returns of up to \$2260&nbsp;AU per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than necessary.
 Excessive use of fungicides are not only costly, but lead to problems such as fungicide resistance.

### 2020-06-25 07_Manuscript.Rmd
Edits and writing

--- 2020-06-24 07_Manuscript.Rmd
@@
 These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar and supplementary irrigation.
-To account for this variation, and the variation from season and location, between trials, a single 'trial' factor was created to describe the main variables; trial location, trial season, host genotype, row spacing, and dose.
+To account for this variation, and the variation from season and location, between trials, a single 'trial' factor was created to describe the main variables; a trial reference code, trial location, trial season, host genotype, row spacing, and dose.
 Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 - 9 ordinal scale (Table 2). 
@@
 A spray schedule with a single spray, and a spray schedule with two or three spray applications (_plus). 
-The division of the treatments into these six categories created one category with insufficient numbers of treatments to provide a reliable sample. 
-'Early' treatments with more than one spray contained five replicates and were therefore removed from the subsequent meta-analysis.
+The division of the treatments categorised: 13 Early treatments; 5 'EarlyPlus', 32 'Recommended'; 46 'RecommendedPlus'; 17 'Late'; and 20 'LatePlus.
+Due to insufficient sample size of 'EarlyPlus' treatments they were removed from the subsequent meta-analysis.
+
+A two level categorical disease pressure factor, 'low disease pressure' or 'high disease pressure' was binned using the mean AUDPC of the no spray control plot.
+The two levels were separated via the median AUDPC (153.63) of the no spray control plots.
 
@@
 
-For the trials which we had raw data, mean grain yields and sample variance for each treatments calculated. 
+Mean grain yields for each treatment were either obtained directly from trial reports, or calculated from the raw data when available.
+The sample variance was calculated from the raw data when available or the least squares statistic in trial reports. 
 Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 1.697 and the approach reported in Ngugi et al. [@Ngugi2011]. 
 The T-critical value was determined from the 30 degrees of freedom using a t-distribution table. 
-For the remainder of the trial data, the treatment means and variance were reported, except for Gatton in 2012 and Emerald in 2015. 
-The Gatton and Emerald trials reported treatment means without accompanying variance and were thus removed prior to the analysis.
+The 2012 Gatton and 2015 Emerald trials reported treatment means without accompanying variance and were thus removed from the dataset  prior to the analysis.
 

### 2020-06-25 03_Prep_data.Rmd
Revert "revert"
This reverts commit 30490337c4f7b9c9bb7bdccc0a51f93beb21c7a1.
Fix heading levels and report the median disease pressure

--- 2020-06-23 03_Prep_data.Rmd
@@
 
-### Disease pressure factor
+## Disease pressure factor
 
@@
    median(as.vector(Trial_Dpress$AUDPC_C), na.rm = TRUE)
+median_AUDPC
 
@@
 
-### Row spacing
+## Row spacing
 
@@
 However one of the locations has `NA` as the row spacing.
-For now let's assign the most used row spacing of 0.33 m.
+For now let's assign the most used row spacing of 0.33 m as an approximation so the model can analyse this as a continuous variable. 
+If we decide to use the row_spacing column as a factor in the final model we will need to remove this approximation.
 

### 2020-07-01 07_Manuscript.Rmd
some small edits

--- 2020-06-24 07_Manuscript.Rmd
@@
 Trial data were in different formats with varying levels of information.
-Some trial data reported means of each treatment, with all but one study reporting variance along with the mean. 
-Raw data were obtained for 26 trials in total.
+Some trial data reported means of each treatment, with all but one study reporting some form of variance along with the mean.
+
+Twenty six trials in total were collated.
 
 Details of trial data are presented within a research compendium which was prepared to supplement this publication [<!-- DOI to reference to compendium -->].
+The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the Grains Research and Development (GRDC) northern grains regions of eastern Australia, which grows the majority of Australia's summer crops.
+Trial data had to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; the fungicide active ingredients; fungicide dose; and crop yield.
+The data were subset to only include treatments with the same mode of action; demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole were thus retained in the dataset. 
+Subsequently the 26 trials were reduced to 16 using the same fungicide doses (Table 1). 
+With only a small number of trials, and to increase the replication, we made no distinction between the tebuconazole and propiconazole in the analysis.
 
-The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the Grains Research and Development (GRDC) northern grains regions of eastern Australia, which grows the majority of Australia's summer crops.
-Trial data had to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; and crop yield.
-A total of 26 trials were collated and from these trials we selected the most frequently tested fungicides that had the same mode of action. 
-The data were subset to only include treatments using demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole, to reduce confounding effects of fungicides with different modes of action.
-Subsequently the 26 trials were reduced to 17 using the same fungicide doses (Table 1).
-With only a small number of trials and to increase the replication, we made no distinction between the tebuconazole and propiconazole in the analysis.
+All trials included in this analysis were randomised complete block designs and not previously published in peer-reviewed literature.
 
-All trials included in this analysis were a randomised complete block designs and not previously published in peer-reviewed literature.
-Some trials and results were reported online via the GRDC. 
-While the main aim of all the trials collected for this study were to assess the efficacy of fungicide for control of powdery mildew, some trials included additional variables in the experimental design.
-These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar and supplementary irrigation, in addition to trial location and season.
-To account for this variation between trials, and the treatments within trials, a single 'trial' factor was created to describe the main variables; trial location, trial season, host genotype and row spacing.
+While the main aim of all the trials collected for this study were to assess the efficacy of fungicide for control of powdery mildew, some trials tested additional variables in the experimental design.
+
+These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar and supplementary irrigation.
+To account for the variation between trials, and the treatments within trials, a single 'trial' factor was created to describe the main variables; a trial reference code, trial location, trial season, host genotype, row spacing, and dose.
 Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 -- 9 ordinal scale (Table 2). 
 However, the 2013 NGA trials (Table 1) reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the canopy; lower, middle or upper canopy.
-Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, it was strait-forward to calculate the equivalent incidence on the ordinal 1 -- 9 scale.
 
-The timing of fungicide applications, with reference to when the disease first occurred in the trial, and number of applications were used to define a treatment variable. 
-An 'Early' fungicide application, refers to a fungicide spray schedule that commences with the first spray prior to the disease being observed in the trial.
-'Recommended' refers to a fungicide spray schedule which commences within three days following the first sign of disease, and 'late' treatments which commence four days or later than first sign.
+Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, a conversion to mean plot incidence on the ordinal 1 -- 9 scale was straight-forward.
+
+The timing of fungicide application treatments, was defined in relation to the recorded date when powdery mildew first occurred in the trial. 
+An 'Early' fungicide application treatment, referred to a fungicide spray schedule that commenced the first spray prior to the disease being observed in the trial. 
+'Recommended' refers to a fungicide spray schedule which commences following the first sign of disease, within three days. 
+'Late' treatments commence between 7 - 13 days after the first sign of disease. 
 The number of fungicide applications were binned in to two categories.
-A spray schedule with a single spray, and a spray schedule with one or more sprays to a maximum of three applications.
-The division of the treatments into these six categories created two categories with insufficient numbers of treatments to provide a reliable sample.
-Single late sprays contained two replicates and multiple early sprays contained five replicates and were therefore removed from the subsequent meta-analysis.
+A spray schedule with a single spray, and a spray schedule with two or three spray applications (Plus). 
+The division of the treatments categorised: 13 Early treatments; 5 'EarlyPlus', 32 'Recommended'; 46 'RecommendedPlus'; 17 'Late'; and 20 'LatePlus.
+'EarlyPlus' treatments were removed from the subsequent meta-analysis, due to an insufficient sample size.
 
@@
 
-Mean grain yields and sample variance for each treatment was calculated for trials for which we had the raw data.
+A categorical disease pressure factor was created by binning trials based on the mean AUDPC of the no spray control plot into two levels: 'low disease pressure' or 'high disease pressure'.
+The two levels were separated via the median AUDPC (153.63) of the no spray control plots.
+
+Mean grain yields for each treatment were either obtained directly from trial reports, or calculated from the raw data when available.
+The sample variance was calculated from the raw data when available or the least squares statistic in trial reports. 
 Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 1.697 and the approach reported in Ngugi et al. [-@Ngugi2011].
 The T-critical value was determined from the 30 degrees of freedom using a t-distribution table. 
-For the remainder of the trial data, the treatment means and variance were reported, except for Gatton in 2012 and Emerald in 2015.
-The Gatton and Emerald trials reported treatment means without accompanying variance and were thus removed prior to the analysis.
+The 2012 Gatton and 2015 Emerald trials reported treatment means without accompanying variance and were thus removed from the dataset  prior to the analysis.
+
+This analysis use the grain yield standardised mean difference (SMD) as the response variable. 
+SMD were chosen to reduce the inherent variability between trials due to location and seasonal effects on grain yields.  
+$SMD = \frac{Y_i-\overline{Y_c}}{\sigma_p}$ [@HigginsGreen]  
+Where $Y_i$ is the treatment mean, $Y_c$ is the no spray control treatment mean and $\sigma_p$ is the trial pooled standard deviation.
+
+Similar to Paul et. al. [-@Paul2007], we fitted a multivariate random effects model  
+$Y_i \sim N(\mu,s_i^2 + \sigma^2)$  
+where $Y_i$ is the response, a vector of the SMD grain yield for each treatment in the $i$th trial over total number ($K$) of trials($i$  = 1, ...$K$). 
+$Y_i$ is estimated from a normal distribution with the mean $\mu$, sample variance of $Si_^2$ and a between trial variance of $\sigma^2$.  
+**Moderator variables.** The random effects meta-analysis was expanded to evaluate if the residual heterogeneity could be explained by spray schedule ($SPRAY_{Sched}$). 
+The intercept was omitted from the model so each treatment would be reported against zero, which represents the control mean. 
+Linear contrasts were used to compare the mean effect sizes between each spray schedule treatment and their respecting standard errors and confidence intervals.
 

### 2020-07-01 04_MetaAnalysis.Rmd
insert formula for Standardised mean differences
one line addition
Changed the response to response ratio, or mean difference for easier interpretation of the results

@@
 
+To visualise this formula in mathematical notation:  
+$SMD = \frac{Y_i-\overline{Y_c}}{\sigma_p}$
+
 We can use the same sample variance with the standardised mean difference.
@@
 Let's simplify our data by removing the control data, converting disease pressure (`D_pres`) to a factor and selecting only the columns of data necessary for analysis.
+We will also include the mean difference or response ratio `grain_MD`, between the treatment and control as a comparison of responses.
 
@@
                     c("lowD",
-                      "highD"))) %>%
+                      "highD")),
+          grain_MD = grain_yield.t.ha - yi_C) %>%
    select(
@@
       grain_SMD,
+      grain_MD,
       dose,
@@
 hist_usq(sqrt(dat1$grain_yield.t.ha))
-hist_usq(dat1$grain_SMD)
+hist_usq(dat1$grain_MD)
 ```
@@
 PM_mv <- rma.mv(
-   yi = grain_SMD,
+   yi = grain_MD,
    vi,
@@
 PM_mv_St <- rma.mv(
-   yi = grain_SMD,
+   yi = grain_MD,
    vi,
@@
 PM_mv_St1 <- rma.mv(
-   yi = grain_SMD,
+   yi = grain_MD,
    vi,
@@
    geom_hline(
-      yintercept = seq(-0.4, 1.8, by = 0.2),
+      yintercept = seq(-0.05, 0.3, by = 0.05),
       color = usq_cols("usq charcoal"),
@@
 PM_mv_Dp <- rma.mv(
-   yi = grain_SMD,
+   yi = grain_MD,
    vi,
-   mods = ~ spray_management *D_pres,
+   mods = ~ spray_management * D_pres - 1,
    method = "ML",

### 2020-07-01 04_MetaAnalysis.Rmd
update explaination of metafor analysis using response ratio

@@
 However the other treatments are significantly different from zero.
-The $Q_M$ [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, shows the moderators significantly influence the model ($Q_M = 24.4769, df = 5, p = 0.0002$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
-The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 47501.76, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
+The $Q_M$ [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, shows the moderators significantly influence the model ($Q_M = 26.22, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
+The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 568.31, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
 
@@
 
-Results show with the exclusion of the no spray `control`, `Early` applications are significantly worse than all other treatments leading to lower yield estimates.
-`Late_plus` is estimated to save the most yield compared and is significantly higher than all other treatments except `Recommended_plus`.
-Let's look at how well each of the number treatments compare to each other.
+Results show with the exclusion of the no spray `control` and `Late` treatments, `Early` applications are significantly worse than all other treatments leading to lower yield estimates.
+`Late_plus` is estimated to save the most yield however it is only significantly higher than `Early` and `Late` treatments.
+Let's put these values in a plot to visualise the differences between treatments.
 
@@
 These results show that the spray management variable we tested are not significantly better or worse between the two levels of disease pressure.
-It also shows that in trials with high disease pressure, all treatments produced lower standardised mean differences. 
-Indicating that fungicide treatments were less effective at mitigating yield loss in seasons, which developed more severe infection levels.
-Finally let's compare the disease pressure model to the original model to see which one fits better.
+It seems that disease preasure does not improve the models ability to assess the most effective fungicide spray management option.
+Let's compare the disease pressure model to the original model to test this assumption.
 

### 2020-07-01 07_Manuscript.Rmd
Commence Results section

@@
 
+Overall the meta-analysis indicated that, with the exception of `Early` single sprays all the the spray schedules were effective at protecting mungbean yields, relative to the no spray controls (Figure 1).
+Treatments which incorporated multiple fungicide applications, `recommendedPlus` and `LatePlus` produced the highest yield protection estimates at 196 and 220 kg / ha respectively (Table 3). 
+Both `RecommendedPlus` and `LatePlus` were also significantly higher than single applications starting `Early` (P = 0.008 and P = 0.003 respectively) and `Late`(P = 0.05 and P = 0.03 respectively). 
+Within the single fungicide application treatments `recommended` provided the highest yield protection, and was estimated at saving an average of 160 kg / ha relative to the no spray control (P < 0.0001).
+`recommended` treatments were was also significantly higher than `Early` treatments by 122 kg / ha (P = 0.004).
+
+The $Q_M$ omnibus test of moderators, shows the moderators significantly influence the model ($Q_M = 26.22, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
+The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 568.31, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
+
+A log-ratio test, based on a chi-squared distribution, indicated that retaining the SpraySchedule variable as a random interactive term provided a significantly better model (P = 0.0179).
+
+```{r table3_Contrasts}
+T3 <- read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
+T3 %>%
+   kable()
+
+```
+
 ## Discussion

### 2020-07-01 04_MetaAnalysis.Rmd
Save contrasts data into file for manuscript Add here() as a library for interoperability additional description to log ratio test of models

@@
                metafor,
+               here,
                netmeta)
@@
 AIC(PM_mv) # Printing the AIC of the model helps differentiate the models in the anova output
-anova(PM_mv, PM_mv_St1) # PM_mv is the better model
+anova(PM_mv, PM_mv_St) # PM_mv is the better model
+AIC(PM_mv_St)
+anova(PM_mv_St, PM_mv_St1) # PM_mv_St is the better model
 ```
@@
 So we will keep the original model `PM_mv`.
+
+I have also tested the structure for testing the random trial and spray_management variables, these show that there is no significant difference to the models `PM_mv_St` and `PM_mv_St1` and that the originally method of specifying the random variables within the `trial` factor provides us with the best model.
 
@@
 
-data.frame(
+table3 <- data.frame(
    contrasts = change_labels(meta_cont$hyp[, 1]),
@@
 )
+write.csv(table3, here("cache/Table3_contrasts.csv"), row.names = FALSE)
 ```

### 2020-07-03 03_Prep_data.Rmd
correction

@@
 
-Using the model without dose produces a lower AIC, however we should accept the data with dose as there is a significant difference between the models and we should accept the more complicated model `m2`.
+Using the model without dose produces a lower AIC, however we should accept the data with dose as there is a significant difference between the models and we should accept the more complicated model `m1`.
 We will retain dose as a variable inside the `trial` factor.

### 2020-07-07 07_Manuscript.Rmd
Add a few comments and minor copy-edits to manuscript

--- 2020-07-01 07_Manuscript.Rmd
@@
 
-Commercially available mungbean cultivars in Australia lack sufficient resistance to be used as a sole powdery mildew management strategy. <!-- Citation needed -->
+Commercially available mungbean cultivars in Australia lack sufficient resistance to be used as the primary powdery mildew management strategy. <!-- Citation needed -->
 Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013].
@@
 A categorical disease pressure factor was created by binning trials based on the mean AUDPC of the no spray control plot into two levels: 'low disease pressure' or 'high disease pressure'.
-The two levels were separated via the median AUDPC (153.63) of the no spray control plots.
+The two levels were separated via the median AUDPC <!-- Should this be encoded not hard coded in case it changes? -->(153.63) of the no spray control plots.
 
@@
 
-This analysis use the grain yield standardised mean difference (SMD) as the response variable. 
+This analysis uses the grain yield standardised mean difference (SMD) as the response variable. 
 SMD were chosen to reduce the inherent variability between trials due to location and seasonal effects on grain yields.
@@
 
+Overall the meta-analysis indicated that, with the exception of `Early` single sprays all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure 1).
+Treatments incorporating multiple fungicide applications, `recommendedPlus` and `LatePlus` produced the highest yield protection estimates at 196 and 220&nbsp;kg&nbsp;/&nbsp;ha respectively (Table 3).
+Both `RecommendedPlus` and `LatePlus` were also significantly higher than single applications starting `Early` (P = 0.008 and P = 0.003 respectively) and `Late`(P = 0.05 and P = 0.03 respectively). 
+Within the single fungicide application treatments `recommended` provided the highest yield protection, and was estimated at saving an average of 160 kg / ha relative to the no spray control (P < 0.0001).
+`recommended` treatments were was also significantly higher than `Early` treatments by 122 kg / ha (P = 0.004).
+
+The $Q_M$ omnibus test of moderators, shows the moderators significantly influence the model ($Q_M = 26.22, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
+The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 568.31, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators, which might influence grain yield.
+
+A log-ratio test, based on a chi-squared distribution, indicated that retaining the `SpraySchedule` variable as a random interactive term provided a significantly better model (P = 0.0179).
+
+```{r table3_Contrasts}
+T3 <- read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
+T3 %>%
+   kable()
+```
+
 ## Discussion
@@
 We estimate these costs to be approximately \$20&nbsp;AU per hectare.
-Lucrative returns of up to \$2260&nbsp;AU per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than necessary.
+Lucrative returns of up to \$2260&nbsp;AU per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew when they are unnecessary.
 Excessive use of fungicides are not only costly, but lead to problems such as fungicide resistance.

### 2020-07-07 07_Manuscript.Rmd
Adams changes incorporated Moving sections between discussion and introduction. Writing

@@
 
-Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown in south-east Asia for human consumption and constitutes an affordable source of protein [@PulseAustralia].
+Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown in south-east Asia for human consumption as an affordable source of protein [@PulseAustralia].
 The bean pod or grain can be consumed raw or added to meals after sprouting.
@@
 
-In Australia mungbean is grown in southern Queensland and northern New South Wales as a short season summer legume crop.
-Approximately 90&nbsp;% of Australian mungbean produced is exported and economic returns can be lucrative for growers with a value of up to \$1300&nbsp;AU a tonne [@QueenslandGovernment2019].
-Mungbean potentially yields up to 3 tonnes per hectare but the average Australian farm still yields less than 1 tonne per hectare [@Chauhan2018].
+Mungbean was first brought to Australia in the 1930s for use as a forage or green manure crop and it was not until the 1960s until that mungbean was grown commercially [@aboutAMA].
+At the end of the 1980s between 3 - 10 thousand hectares were being harvested for dried beans, of which mungbean is included.
+In the decade leading up to 2018 35 - 86.4 thousand hectares of dried beans are being planted per year [@FAOSTAT]. 
+This increase is attributed to the improved yields in the new cultivars and value of the crop [@Clarry2016].
+Currently mungbean is predominantly grown in southern Queensland and northern New South Wales as a short season summer legume crop.
+In 2019, approximately 90&nbsp;% of Australian mungbean produced is exported and economic returns can be lucrative for growers with a value of up to \$1300&nbsp;AU a tonne [@QueenslandGovernment2019].
+Mungbean potentially yields up to 3 tonnes per hectare, but due to high variability in yields between seasons and locations, the average Australian farm still yields less than 1 tonne per hectare [@Chauhan2018].
 
-Part of the low yields can be attributed to a range of diseases that affect the crop [@Kelly2017a].
-Two major foliar diseases, tan spot or common wilt (_Curtobacterium flaccumfaciens_ pv.
+Low yields, in part, can be attributed to a range of diseases that affect the crop [@Kelly2017a].
+Two major foliar diseases, tan spot or common wilt (*Curtobacterium flaccumfaciens* pv.
 _flaccumfaciens_) and halo blight (_Pseudomonas savastanoi_ pv.
@@
 A categorical disease pressure factor was created by binning trials based on the mean AUDPC of the no spray control plot into two levels: 'low disease pressure' or 'high disease pressure'.
-The two levels were separated via the median AUDPC <!-- Should this be encoded not hard coded in case it changes? -->(153.63) of the no spray control plots.
+The two levels were separated via the median AUDPC (`r as.double(read.csv(here("cache/median_AUDPC_C.csv")))`) of the no spray control plots.
 
@@
 $Y_i$ is estimated from a normal distribution with the mean $\mu$, sample variance of $Si_^2$ and a between trial variance of $\sigma^2$.
+
 **Moderator variables.** The random effects meta-analysis was expanded to evaluate if the residual heterogeneity could be explained by spray schedule ($SPRAY_{Sched}$).
@@
 Linear contrasts were used to compare the mean effect sizes between each spray schedule treatment and their respecting standard errors and confidence intervals.
+
+Additional meta-analysis models tested variables ... for their influence on the SpraySheduale variables ability to mitigate yield loss. 
+For the variable disease pressure a Wald-type test was used to test the impact of this variable on the model as a whole.
 
@@
 
-Overall the meta-analysis indicated that, with the exception of `Early` single sprays all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure 1).
-Treatments incorporating multiple fungicide applications, `recommendedPlus` and `LatePlus` produced the highest yield protection estimates at 196 and 220&nbsp;kg&nbsp;/&nbsp;ha respectively (Table 3).
+<!-- Write about first sign of disease in March -->
+Overall the meta-analysis indicated that, with the exception of `Early` single sprays all the the spray schedules were effective at protecting mungbean yields, relative to the no spray controls (Figure 1).
+Treatments which incorporating multiple fungicide applications, `RecommendedPlus` and `LatePlus` produced the highest mean yield protection estimates at 196.4 (SE = 48.7&nbsp;kg&nbsp;/&nbsp;ha) and 219.9&nbsp;kg&nbsp;/&nbsp;ha (SE = 47.4&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3).
 Both `RecommendedPlus` and `LatePlus` were also significantly higher than single applications starting `Early` (P = 0.008 and P = 0.003 respectively) and `Late`(P = 0.05 and P = 0.03 respectively). 
-Within the single fungicide application treatments `recommended` provided the highest yield protection, and was estimated at saving an average of 160 kg / ha relative to the no spray control (P < 0.0001).
-`recommended` treatments were was also significantly higher than `Early` treatments by 122 kg / ha (P = 0.004).
+However, comparing `LatePlus` and `Early` should done with caution given these treatments did not occur within the same trial for any of the 15 trials included in the meta-analysis. 
+Within the single fungicide application treatments `Recommended` provided the highest yield protection, and was estimated at saving an average of 159.9 kg / ha (SE = 30.5 kg / ha) relative to the no spray control (P < 0.0001).
+`Recommended` treatments were was also significantly higher than `Early` treatments by 122.1 kg / ha (SE = 42.1 kg / ha)(P = 0.004). 
+Single `Late` applications were effective at significantly mitigating the effect of powdery mildew on yield by a mean of 122 kg / ha (SE = 39.2 kg / ha)(P = 0.0019). 
+However, this estimate was not significantly different to single `Early` or `Recommended` treatments (P = 0.119; P = 0.278 respectively).
 
@@
 A log-ratio test, based on a chi-squared distribution, indicated that retaining the `SpraySchedule` variable as a random interactive term provided a significantly better model (P = 0.0179). 
+An inspection of log-likelihood profile plots showed the model, for each random interactive term, provided a reasonable estimate of $\tau^2$, with no indication the variables were over-fit.
+
+While the addition of disease pressure, as an interactive moderator term to `SpraySchedule`, did explain slightly more residual heterogeneity, shown by a lower $Q_E = 409.91,$. 
+The model including disease pressure did not significantly improve the model (P = 0.4859) and did not significantly explain differences in the SpraySchedule term, and therefore disease pressure was not included in the final model.
 
@@
 ## Discussion
+Mungbeans have only recently been cultivated in Australia, with the first commercial crops planted in the 1960s [].
+
+Despite the improved knowledge for cultivating mungbean this 40 year period from 1980 and today, variability in yields and quality persist due to seasonal differences and the need to refine best management practices.
+Between trial variability was
 
@@
 -->
+
+Within a normal meta-analysis the number direct treatment comparisons, undertaken within the same trial, for each treatment is important for understanding how robust the meta-analysis estimates are for those treatments.
+However network meta-analyses permit indirect comparisons, for when two treatments may not occur in the same experiment. 
+For the indirect difference between two treatments is equal to the difference between the difference in those two treatments with one other treament in common ($d_{AB} = d_{AC} - d_{BC}$)[@Jansen2011]
+For example treatments `Early` and `LatePlus` never occurred within the same trial for any trials included in the meta-analysis. 
+M
 

### 2020-07-07 02_Preliminary_analysis.Rmd
Draft inspection/plot of FAOSTAT data for dry bean (mungbeans) production in australia

@@
 The mixed effect model will help us decide on the best approach and structure for our meta-analysis model.
+
+```{r}
+beans <- read.csv(here("data/FAOSTAT_data_7-6-2020.csv"))
+
+glimpse(beans)
+
+beans %>%
+   filter(Item == "Beans, dry",
+          Element == "Area harvested")%>%
+   select(Year,Value)
+   ggplot(aes(y = Value, x = Year))+
+   geom_point()+
+   geom_smooth()
+
+beans %>%
+   filter(Item == "Beans, dry",
+          Element == "Yield")%>%
+   ggplot(aes(y = Value *0.1, x = Year))+
+   geom_point()+
+   geom_smooth()
+
+beans %>%
+   filter(Item == "Beans, dry",
+          Element == "Production")%>%
+   ggplot(aes(y = Value, x = Year))+
+   geom_point()+
+   geom_smooth(method = "lm")
+
+```

### 2020-07-07 04_MetaAnalysis.Rmd
add a wald test on Disease pressure moderator
Started at building a forest plot for the manuscript. Also a small analysis of indiect comparison data (to be deleted later)

@@
 
+Lets look at the trial variability in this model with a forest plot
+```{r forestP, fig.height= 40, fig.width=10}
+# If anyone knows how to fix the margins here it would be helpful!!!!!!!!!!!!!!!!
+metafor::forest(PM_mv, cex =0.75 , width = 5,
+                ilab = cbind(dat1$trial_ref, dat1$location, dat1$year, dat1$row_spacing, dat1$host_genotype, dat1$dose,
+                             as.character(dat1$spray_management)),
+                ilab.xpos = c(-6.5, -5.5,-4.75,-4.15,-3.4,-2.5,-1),
+                slab = NA, 
+                xlim = c(-7, 3.5),
+                ylim = c(4,119),
+                xlab = "Grain yield mean difference")
+
+### add text with Q-value, dfs, p-value, and I^2 statistic
+text(-5.1, -0.8, pos=3, cex=0.75, bquote(paste("RE Model for All Studies (Q = ",
+     .(formatC(PM_mv$QE, digits=2, format="f")), ", df = ", .(PM_mv$k - PM_mv$p),
+     ", p = ", .(formatC(PM_mv$QEp, digits=3, format="f")), ") ")))
+
+### add column headings to the plot
+text(c(-6.5, -5.5,-4.75,-4.15,-3.4,-2.5,-1), 117.9,cex = 0.85, 
+     c("Trial\nReference", "Location", "Year", "Row\nSpacing","Host\nCultivar","DMI dose","SM"),
+     font = 2)
+
+```
+
 Let's see if we can improve this model by including some other random effects and improving the random effect structure in the model.
@@
 ```{r compareDvNDP}
+AIC(PM_mv_Dp)
+anova(PM_mv_Dp, btt = "D_pres")
 anova(PM_mv, PM_mv_Dp)
@@
 
+A Wald test of `D_pres` shows the moderator is not significant in accounting for heterogeneity (P = 0.4859).
 No significant difference which informs us to use the original model `PM_mv`, which is the simplest.
+
+### Test for bias in indirect comparisons 
+Treatments `Early` and `LatePlus` did not co-occur in any of the trials considered in the meta-analysis.
+Indirect comparisons are ok to interpret in the results of a network meta-analysis, however if there are biases between trials including `Early` or `LatePlus` treatments then the results are likely bias.
+Therefore we wish to do a quick check that the trials which included `Early` treatments did not significantly differ from trials which incorportated `LatePlus`,
+Lets create a data.frame of values for this comparison
+
+```{r}
+Ear <- 
+   dat1 %>%
+   filter(spray_management == "Early")%>%
+   distinct(trial_ref)
+
+LP <- 
+   dat1 %>%
+   filter(spray_management == "Late_plus")%>%
+   distinct(trial_ref)
+
+dat1$indirectC <- NA
+
+dat1 %>%
+   filter(trial_ref == Ear$trial_ref)
+
+dat1[dat1$trial_ref == Ear$trial_ref, "indirectC"] <- "Ear"
+dat1[dat1$trial_ref == LP$trial_ref, "indirectC"] <- "LP"
+
+dat1 %>%
+   filter(!is.na(indirectC))%>%
+   ggplot(aes(x = indirectC, y = grain_MD))+
+   geom_boxplot()
+
+dat1 %>%
+   filter(!is.na(indirectC),
+          spray_management != "Early",
+          spray_management != "Late_plus")%>%
+   ggplot(aes(x = indirectC, y = grain_MD))+
+   geom_boxplot()
+
+dat1[dat1$trial_ref == LP$trial_ref, "indirectC"] <- "LP"
+dat1[dat1$trial_ref == Ear$trial_ref, "indirectC"] <- "Ear"
+
+dat2 <- dat1 %>%
+   filter(!is.na(indirectC),
+          spray_management != "Early",
+          spray_management != "Late_plus")
+
+table(dat2$spray_management, dat2$indirectC)
+
+summary(aov(grain_MD ~ indirectC + spray_management + trial_ref, data = dat2))
+
+```
+
+This anova shows that there is no significant difference between the trials, spray_management or the specific trials with either `Early` or `Late_plus`. 
+Therefore there is low risk that interpreting results from this indirect comparison between `Early` and `Late_plus`.
 

### 2020-07-07 04_MetaAnalysis.Rmd
fixing the forestplot

@@
 Lets look at the trial variability in this model with a forest plot
-```{r forestP, fig.height= 40, fig.width=10}
-# If anyone knows how to fix the margins here it would be helpful!!!!!!!!!!!!!!!!
-metafor::forest(PM_mv, cex =0.75 , width = 5,
-                ilab = cbind(dat1$trial_ref, dat1$location, dat1$year, dat1$row_spacing, dat1$host_genotype, dat1$dose,
-                             as.character(dat1$spray_management)),
-                ilab.xpos = c(-6.5, -5.5,-4.75,-4.15,-3.4,-2.5,-1),
+```{r forestP, fig.height= 25, fig.width=20}
+polys <- data.frame(ref = names(coef(PM_mv)),
+                    x = coef(PM_mv),
+                    ci.lb = PM_mv$ci.lb,
+                    ci.ub = PM_mv$ci.ub,
+                    rows = c(112.8, 64.8, 22.8,93.5, 1.8))
+
+metafor::forest(PM_mv, cex = 1.25 , width = 5,
+                order = "fit",
+                rows = c(126:114, 111:95, 92:66, 63:24, 21:3),
+                ilab = cbind(dat1$trial_ref, dat1$location, dat1$year, 
+                             dat1$row_spacing, dat1$host_genotype, dat1$dose),
+                ilab.xpos = c(-2.8, -2.2,-2.05,-1.95,-1.7,-1.5),
                 slab = NA, 
-                xlim = c(-7, 3.5),
-                ylim = c(4,119),
-                xlab = "Grain yield mean difference")
+                xlim = c(-3, 2.2),
+                ylim = c(4,129),
+                xlab = "Grain yield mean difference",
+                addfit = FALSE,
+                efac = c(0.5,2,0.2))
 
@@
 ### add column headings to the plot
-text(c(-6.5, -5.5,-4.75,-4.15,-3.4,-2.5,-1), 117.9,cex = 0.85, 
-     c("Trial\nReference", "Location", "Year", "Row\nSpacing","Host\nCultivar","DMI dose","SM"),
+text(c(-6.5, -5.5,-4.75,-4.15,-3.4,-2.5), 127.9,cex = 0.85, 
+     c("Trial\nReference", "Location", "Year", "Row\nSpacing","Host\nCultivar","DMI dose"),
      font = 2)
 
+addpoly(x = polys$x,
+        ci.lb = polys$ci.lb,
+        ci.ub = polys$ci.ub,
+        col ="black",
+        rows = polys$rows,
+        cex = 1.3,
+        efac = 0.2,
+        font = "Arial Rounded MT Bold")
 ```

### 2020-07-07 04_MetaAnalysis.Rmd
Draft Forest plot of trials updated

--- 2020-07-07 04_MetaAnalysis.Rmd
@@
 Lets look at the trial variability in this model with a forest plot
-```{r forestP, fig.height= 40, fig.width=10}
-# If anyone knows how to fix the margins here it would be helpful!!!!!!!!!!!!!!!!
-metafor::forest(PM_mv, cex =0.75 , width = 5,
-                ilab = cbind(dat1$trial_ref, dat1$location, dat1$year, dat1$row_spacing, dat1$host_genotype, dat1$dose,
-                             as.character(dat1$spray_management)),
-                ilab.xpos = c(-6.5, -5.5,-4.75,-4.15,-3.4,-2.5,-1),
+```{r forestP, fig.height= 25, fig.width=20}
+change_labels <- function(x1) {
+   x1 <- gsub(pattern = "spray_management",
+              replacement = "",
+              x = x1)
+   x1
+}
+
+polys <- data.frame(ref = change_labels(names(coef(PM_mv))),
+                    x = coef(PM_mv),
+                    ci.lb = PM_mv$ci.lb,
+                    ci.ub = PM_mv$ci.ub,
+                    rows = c(120.60, 68.6, 24.6,99.6, 1.6))
+
+metafor::forest(PM_mv, cex = 1.15 , width = 5,
+                order = "fit",
+                rows = c(134:122, 117:101, 96:70, 65:26, 21:3),
+                ilab = cbind(dat1$trial_ref, dat1$location, dat1$year, 
+                             dat1$row_spacing, dat1$host_genotype, dat1$dose),
+                ilab.xpos = c(-3.3, -2.85,-2.55,-2.35,-2.15,-1.85),
                 slab = NA, 
-                xlim = c(-7, 3.5),
-                ylim = c(4,119),
-                xlab = "Grain yield mean difference")
+                xlim = c(-3.5, 2.5),
+                ylim = c(4,137),
+                xlab = "Grain yield mean difference",
+                addfit = FALSE,
+                efac = c(0.5,2,0.2))
 
@@
 ### add column headings to the plot
-text(c(-6.5, -5.5,-4.75,-4.15,-3.4,-2.5,-1), 117.9,cex = 0.85, 
-     c("Trial\nReference", "Location", "Year", "Row\nSpacing","Host\nCultivar","DMI dose","SM"),
+text(c(-3.3, -2.85,-2.55,-2.35,-2.15,-1.85, -1.5), 137.9,cex = 1, 
+     c("Trial\nReference", "Location", "Year", "Row\nSpacing","Host\nCultivar","DMI dose"),
      font = 2)
+
+text(-2.35, polys$rows ,cex = 1.3, 
+     paste0(polys$ref," Spray Schedule - (tau^2 = " ,round(PM_mv$tau2, digits = 3), ") "),
+     font = 2)
+
+addpoly(x = polys$x,
+        ci.lb = polys$ci.lb,
+        ci.ub = polys$ci.ub,
+        col ="black",
+        rows = polys$rows,
+        cex = 1.3,
+        efac = 0.2,
+        font = "Arial Rounded MT Bold")
 

### 2020-07-08 04_MetaAnalysis.Rmd
reordering forest plot, Its a mess right now don't look

--- 2020-07-07 04_MetaAnalysis.Rmd
@@
 ```
+```{r}
+(PM_mv$b - PM_mv$ci.ub) / PM_mv$se
+```
 
@@
 Lets look at the trial variability in this model with a forest plot
-```{r forestP, fig.height= 40, fig.width=10}
-# If anyone knows how to fix the margins here it would be helpful!!!!!!!!!!!!!!!!
-metafor::forest(PM_mv, cex =0.75 , width = 5,
-                ilab = cbind(dat1$trial_ref, dat1$location, dat1$year, dat1$row_spacing, dat1$host_genotype, dat1$dose,
+```{r forestP, fig.height= 40, fig.width=20}
+change_labels <- function(x1) {
+   x1 <- gsub(pattern = "spray_management",
+              replacement = "",
+              x = x1)
+   x1
+}
+
+for_rows <- function(head_row, gap = NULL, r_order = NULL, ord_var){
+   if(is.null(gap)){gap <- 0}
+
+   stitle_row <- head_row - c(2,
+                              15 + gap,
+                              32 + (gap*2),
+                              59 + (gap*3),
+                              99 + (gap*4))
+
+   ord_rows <- order(order(dat1[,ord_var]))
+
+   ks1 <- c(sum(dat1$spray_management == "Early"),
+            sum(dat1$spray_management == "Late"),
+            sum(dat1$spray_management == "Recommended"),
+            sum(dat1$spray_management == "Recommended_plus"),
+            sum(dat1$spray_management == "Late_plus"))
+
+   dat2 <- list(stitle_row = stitle_row,
+
+              pred_row = stitle_row - c(15,29,42,19,21),
+
+            trows2 = c((stitle_row[1] - 2.5) - ord_rows[1:ks1[1]],
+                       (stitle_row[2] - 2.5) - ord_rows[ks1[1]+1:ks1[2]],
+                       (stitle_row[3] - 2.5) - ord_rows[ks1[2]+1:ks1[3]],
+                       (stitle_row[4] - 2.5) - ord_rows[ks1[3]+1:ks1[4]],
+                       (stitle_row[5] - 2.5) - ord_rows[ks1[4]+1:ks1[5]]
+                       ),
+            trows3 = ord_rows
+
+              trows = c((stitle_row[1]-1.5):(stitle_row[1]-0.5 - ks1[1]),
+                        (stitle_row[2]-1.5):(stitle_row[2]-0.5 - ks1[2]),
+                        (stitle_row[3]-1.5):(stitle_row[3]-0.5 - ks1[3]),
+                        (stitle_row[4]-1.5):(stitle_row[4]-0.5 - ks1[4]),
+                        (stitle_row[5]-1.5):(stitle_row[5]-0.5 - ks1[5])))
+
+   if(is.null(r_order) == FALSE){
+      dat2$trows <- dat2$trows[r_order]
+   }
+   dat2
+}
+
+rows1 <- for_rows(156, ord_var = "spray_management")
+
+polys <- data.frame(ref = change_labels(names(coef(PM_mv))),
+                    x = coef(PM_mv),
+                    ci.lb = PM_mv$ci.lb,
+                    ci.ub = PM_mv$ci.ub,
+                    rows = rows1$pred_row)
+
+dat1$ID <- 1:116
+
+index1 <- dat1 %>%
+   arrange(desc(spray_management), location, desc(grain_MD))%>%
+   select(ID) %>%
+   mutate(ID2 = order(ID))
+
+forest1  <- metafor::forest(PM_mv, cex = 1.15 , width = 5,
+                #order = "fit",
+                rows = (index1$ID2)+50,
+                ilab = cbind(dat1$trial_ref, dat1$location, dat1$year, 
+                             dat1$row_spacing, dat1$host_genotype, dat1$dose,
                              as.character(dat1$spray_management)),
-                ilab.xpos = c(-6.5, -5.5,-4.75,-4.15,-3.4,-2.5,-1),
+                ilab.xpos = c(-3.3, -2.85,-2.55,-2.35,-2.15,-1.85, -1.5),
                 slab = NA, 
-                xlim = c(-7, 3.5),
-                ylim = c(4,119),
-                xlab = "Grain yield mean difference")
+                xlim = c(-3.5, 2.5),
+                ylim = c(11,157),
+                xlab = "Grain yield mean difference",
+                addfit = FALSE,
+                efac = c(0.5,2,0.2))
 
@@
 ### add column headings to the plot
-text(c(-6.5, -5.5,-4.75,-4.15,-3.4,-2.5,-1), 117.9,cex = 0.85, 
-     c("Trial\nReference", "Location", "Year", "Row\nSpacing","Host\nCultivar","DMI dose","SM"),
+text(c(-3.3, -2.85,-2.55,-2.35,-2.13,-1.85), 156,cex = 1, 
+     c("Trial\nReference", "Location", "Year", "Row\nSpacing","Host\nCultivar","DMI dose"),
      font = 2)
+
+text(-0.8, rows1$stitle_row ,cex = 1.3, 
+     paste0(polys$ref," Spray Schedule - (tau^2 = " ,round(PM_mv$tau2, digits = 3), ") "),
+     font = 2)
+
+text(-3.45, -3:160, cex=1,-3:160)
+
+addpoly(x = polys$x,
+        ci.lb = polys$ci.lb,
+        ci.ub = polys$ci.ub,
+        col ="black",
+        rows = polys$rows,
+        cex = 1.3,
+        efac = 0.2,
+        font = "Arial Rounded MT Bold")
+abline(h = rows1$pred_row -2)
 

### 2020-07-08 04_MetaAnalysis.Rmd
Finally have order and gaps working in forest plot

@@
 
-for_rows <- function(head_row, gap = NULL, r_order = NULL, ord_var){
+for_rows <- function(head_row, gap = NULL, r_order = NULL, ord_var, index){
    if(is.null(gap)){gap <- 0}
+
+   trows_F <- function(x1, head_row, gap){
+   if(x1 <= length(dat1$spray_management) &&
+      x1 > length(dat1$spray_management) - (sum(dat1$spray_management == "Early"))){
+      return(x1 + (head_row - length(dat1$spray_management)) - 2)}
+   if(x1 <= length(dat1$spray_management) - (sum(dat1$spray_management == "Early")) &&
+      x1 > length(dat1$spray_management) - 
+      (sum(dat1$spray_management == "Early") + sum(dat1$spray_management == "Late"))){
+      return(x1 + (head_row - length(dat1$spray_management)) - (2 + gap))}
+   if(x1 <= length(dat1$spray_management) - 
+      (sum(dat1$spray_management == "Early") + sum(dat1$spray_management == "Late"))&&
+      x1 > length(dat1$spray_management) - 
+      (sum(dat1$spray_management == "Early") + sum(dat1$spray_management == "Late") +
+       sum(dat1$spray_management == "Recommended"))){
+      return(x1 + (head_row - length(dat1$spray_management)) - (2 + gap * 2))}
+   if(x1 <= length(dat1$spray_management) - 
+      (sum(dat1$spray_management == "Early") + sum(dat1$spray_management == "Late") +
+       sum(dat1$spray_management == "Recommended")) &&
+      x1 > length(dat1$spray_management) - 
+      (sum(dat1$spray_management == "Early") + sum(dat1$spray_management == "Late") +
+       sum(dat1$spray_management == "Recommended") + sum(dat1$spray_management == "Recommended_plus"))){
+      return(x1 + (head_row - length(dat1$spray_management)) - (2 + gap * 3))}
+   if(x1 <= length(dat1$spray_management) - 
+      (sum(dat1$spray_management == "Early") + sum(dat1$spray_management == "Late") +
+       sum(dat1$spray_management == "Recommended") + sum(dat1$spray_management == "Recommended_plus")) &&
+      x1 > length(dat1$spray_management) - 
+      (sum(dat1$spray_management == "Early") + sum(dat1$spray_management == "Late") +
+       sum(dat1$spray_management == "Recommended") + sum(dat1$spray_management == "Recommended_plus") +
+       sum(dat1$spray_management == "Late_plus"))){
+      return(x1 + (head_row - length(dat1$spray_management)) - (2 + gap * 4))}
+
+      }
 
@@
                        ),
-            trows3 = ord_rows
 
-              trows = c((stitle_row[1]-1.5):(stitle_row[1]-0.5 - ks1[1]),
-                        (stitle_row[2]-1.5):(stitle_row[2]-0.5 - ks1[2]),
-                        (stitle_row[3]-1.5):(stitle_row[3]-0.5 - ks1[3]),
-                        (stitle_row[4]-1.5):(stitle_row[4]-0.5 - ks1[4]),
-                        (stitle_row[5]-1.5):(stitle_row[5]-0.5 - ks1[5])))
+            trows3 = unlist(sapply(index1$ID2,trows_F, head_row = head_row, gap = gap)),
+
+              trows = index)
 
@@
 }
-
-rows1 <- for_rows(156, ord_var = "spray_management")
 
@@
 index1 <- dat1 %>%
+   mutate(spray_management = factor(spray_management, levels = c("Early", "Late","Recommended", "Recommended_plus","Late_plus")))%>%
    arrange(desc(spray_management), location, desc(grain_MD))%>%
@@
 
+rows1 <- for_rows(156, index = index1$ID2, gap = 5)
+
 forest1  <- metafor::forest(PM_mv, cex = 1.15 , width = 5,
                 #order = "fit",
-                rows = (index1$ID2)+50,
+                rows = rows1$trows3,
                 ilab = cbind(dat1$trial_ref, dat1$location, dat1$year, 

### 2020-07-09 04_MetaAnalysis.Rmd
Completed forest plot showing the variation of mean grain differences in each trial

--- 2020-07-07 04_MetaAnalysis.Rmd
@@
 Lets look at the trial variability in this model with a forest plot
-```{r forestP, fig.height= 25, fig.width=20}
-change_labels <- function(x1) {
-   x1 <- gsub(pattern = "spray_management",
-              replacement = "",
-              x = x1)
-   x1
-}
+```{r forestP, fig.height= 40, fig.width=17}
+source(here("R/change_labels.R"))
+source(here("R/forest_rows.R"))
 
+### Sort and arrange data-frame occordingly and produce a index vector to inform the order of each "Trial" on the plot
+index1 <- dat1 %>%
+   mutate(ID = seq_along(trial_ref)) %>%
+   mutate(spray_management = 
+             factor(spray_management, 
+                    levels = c("Early","Late","Recommended",
+                    "Recommended_plus","Late_plus"))) %>%
+   arrange(desc(spray_management), location, desc(grain_MD)) %>%
+   mutate(ID2 = order(ID))%>%
+   pull(ID2)
+
+### Use forest rows function to return a list of where to place on the plot: sub-titles, each trial row, and summary prediction for each treatment.
+### this list can be used below to reference where to plot each variable
+rows1 <- forest_rows(head_row = 156, 
+                     ord_var = dat1$spray_management, 
+                     index = index1, 
+                     gap = 5, 
+                     row_offset = -2)
+
+### A data-frame of meta-model coefficients used to produce the summary polygons for each treatment
 polys <- data.frame(ref = change_labels(names(coef(PM_mv))),
@@
                     ci.lb = PM_mv$ci.lb,
-                    ci.ub = PM_mv$ci.ub,
-                    rows = c(120.60, 68.6, 24.6,99.6, 1.6))
+                    ci.ub = PM_mv$ci.ub)[c(1,4,2,3,5),]
+polys$rows <- rows1$pred_row - 1.5
 
-metafor::forest(PM_mv, cex = 1.15 , width = 5,
-                order = "fit",
-                rows = c(134:122, 117:101, 96:70, 65:26, 21:3),
-                ilab = cbind(dat1$trial_ref, dat1$location, dat1$year, 
+forest1  <- metafor::forest(PM_mv, cex = 1.15 , width = 5,
+                #order = "fit",
+                rows = rows1$trows-1.5,
+                ilab = cbind(dat1$year, 
                              dat1$row_spacing, dat1$host_genotype, dat1$dose),
-                ilab.xpos = c(-3.3, -2.85,-2.55,-2.35,-2.15,-1.85),
+                ilab.xpos = c(-2.35,-2.1,-1.8,-1.4),
                 slab = NA, 
-                xlim = c(-3.5, 2.5),
-                ylim = c(4,137),
+                xlim = c(-2.9, 2.2),
+                ylim = c(18,157),
                 xlab = "Grain yield mean difference",
                 addfit = FALSE,
-                efac = c(0.5,2,0.2))
+                efac = c(0.2,0.15,0.2),
+                at = seq(-1,1.5, 0.5))
 
-### add text with Q-value, dfs, p-value, and I^2 statistic
-text(-5.1, -0.8, pos=3, cex=0.75, bquote(paste("RE Model for All Studies (Q = ",
-     .(formatC(PM_mv$QE, digits=2, format="f")), ", df = ", .(PM_mv$k - PM_mv$p),
-     ", p = ", .(formatC(PM_mv$QEp, digits=3, format="f")), ") ")))
-
-### add column headings to the plot
-text(c(-3.3, -2.85,-2.55,-2.35,-2.15,-1.85, -1.5), 137.9,cex = 1, 
-     c("Trial\nReference", "Location", "Year", "Row\nSpacing","Host\nCultivar","DMI dose"),
-     font = 2)
-
-text(-2.35, polys$rows ,cex = 1.3, 
-     paste0(polys$ref," Spray Schedule - (tau^2 = " ,round(PM_mv$tau2, digits = 3), ") "),
-     font = 2)
-
-addpoly(x = polys$x,
-        ci.lb = polys$ci.lb,
-        ci.ub = polys$ci.ub,
-        col ="black",
-        rows = polys$rows,
-        cex = 1.3,
-        efac = 0.2,
-        font = "Arial Rounded MT Bold")
+### code which puts lines and annotations on the plot, its a bit long...
+source(here("R/add_annotations.R"))
 

### 2020-07-09 R/add_annotations.R
code which puts lines and annotations on the forest plot in the meta-analysis.RmD, its a bit long to include in the Markdown file

@@ -1,0 +1,103 @@
+   ### add text with Q-value, dfs, p-value, and I^2 statistic
+   text(-5.1, min(rows1$trows)-2, pos=3, cex=0.75, bquote(paste("RE Model for All Studies (Q = ",
+                                                                .(formatC(PM_mv$QE, digits=2, format="f")), ", df = ", .(PM_mv$k - PM_mv$p),
+                                                                ", p = ", .(formatC(PM_mv$QEp, digits=3, format="f")), ") ")))
+
+
+### add column headings to the plot
+text(c(-2.7, -2.35,-2.1,-1.8,-1.4), 156,cex = 1, 
+     c("Location", "Year", "Row\nSpacing","Host\nCultivar","DMI dose"),
+     font = 2)
+
+### Add subtitles for each SpraySchedule breakdown
+text(-2, rows1$stitle_row ,cex = 1.3, 
+     paste0(c("Early", "Late", "Recommended", "RecommededPlus", "LatePlus")," Spray Schedule - (tau^2 = " ,round(PM_mv$tau2, digits = 3), ") "),
+     font = 2)
+
+addpoly(x = polys$x,
+        ci.lb = polys$ci.lb,
+        ci.ub = polys$ci.ub,
+        col ="black",
+        rows = polys$rows,
+        cex = 1.3,
+        efac = 0.2,
+        font = "Arial Rounded MT Bold")
+abline(h = rows1$stitle_row +1)
+
+### Early lines
+lines(c(-2.9,-1.25),c(153,153), col = "grey70")
+text(x = -2.7, y = 152.5, 
+     labels = "Missen Flats" ,cex=1)
+lines(c(-2.9,-1.25),c(147,147), col = "grey70")
+text(x = -2.7, y = 146.5, 
+     labels = "Marys Mount" ,cex=1)
+lines(c(-2.9,-1.25),c(146,146), col = "grey70")
+text(x = -2.7, y = 145.5, 
+     labels = "Hermitage" ,cex=1)
+lines(c(-2.9,-1.25),c(140,140), col = "grey70")
+
+### Late lines
+lines(c(-2.9,-1.25),c(135,135), col = "grey70")
+text(x = -2.7, y = 134.5, 
[…]

### 2020-07-09 R/change_labels.R
simple function that edits spray_management labels on tables and plots

@@ -1,0 +1,6 @@
+change_labels <- function(x1) {
+   x1 <- gsub(pattern = "spray_management",
+              replacement = "",
+              x = x1)
+   x1
+}

### 2020-07-09 R/forest_rows.R
Function which returns a list of where to place trial data on the forest plot: sub-titles, each trial row, and summary prediction for each treatment. Simplifying the main document

@@ -1,0 +1,58 @@
+forest_rows <- function(head_row, ord_var, index,
+                        gap = 0, row_offset = 4, stitle_row_offset = 2){
+   
+   breaks <- c(sum(ord_var == "Early"),
+               sum(ord_var == "Early") + sum(ord_var == "Late"),
+               sum(ord_var == "Early") + sum(ord_var == "Late") + 
+                  sum(ord_var == "Recommended"),
+               sum(ord_var == "Early") + sum(ord_var == "Late") + 
+                  sum(ord_var == "Recommended") + sum(ord_var == "Recommended_plus"),
+               sum(ord_var == "Early") + sum(ord_var == "Late") + 
+                  sum(ord_var == "Recommended") + sum(ord_var == "Recommended_plus") + sum(ord_var == "Late_plus"))
+   
+   trows_F <- function(x1, head_row, gap){
+      if(x1 <= length(ord_var) &&
+         x1 > length(ord_var) - (breaks[1])){
+         return(x1 + (head_row - length(ord_var)))}
+      
+      if(x1 <= length(ord_var) - (breaks[1]) &&
+         x1 > length(ord_var) - 
+         (breaks[2])){
+         return(x1 + (head_row - length(ord_var)) - (gap))}
+      
+      if(x1 <= length(ord_var) - breaks[2] &&
+         x1 > length(ord_var) - breaks[3]){
+         return(x1 + (head_row - length(ord_var)) - (gap * 2))}
+      
+      if(x1 <= length(ord_var) - breaks[3] &&
+         x1 > length(ord_var) - breaks[4]){
+         return(x1 + (head_row - length(ord_var)) - (gap * 3))}
+      
+      if(x1 <= length(ord_var) - breaks[4] &&
+         x1 > length(ord_var) - breaks[5]){
+         return(x1 + (head_row - length(ord_var)) - (gap * 4))}
+      
+   }
+   
+   stitle_row <- head_row - c(stitle_row_offset,
+                              stitle_row_offset + breaks[1] + gap,
+                              stitle_row_offset + breaks[2] + (gap*2),
+                              stitle_row_offset + breaks[3] + (gap*3),
+                              stitle_row_offset + breaks[4] + (gap*4))
+   
+   
+   dat2 <- list(stitle_row = stitle_row,
+                
+                pred_row = head_row - c(stitle_row_offset + breaks[1],
+                                        stitle_row_offset + breaks[2] + gap,
+                                        stitle_row_offset + breaks[3] + (gap*2),
[…]

### 2020-07-09 02_Preliminary_analysis.Rmd
added chunk to calculated Yield loss in Jade in 2016 experiments

@@
 
+Based on a GRDC report by Sue Thompson [-@SueThompson2016] we want to know what the yield loss was in on cultivar Jade in the 2016 Trials.
+```{r}
+dat3 <- PM_MB_means %>%
+   filter(year == "2016",
+          host_genotype == "Jade",
+          fungicide_ai == "control")%>%
+   group_by(location)%>%
+   summarise(C_Yield = mean(grain_yield.t.ha., na.rm = TRUE))
+
+dat3$F_Yield <- PM_MB_means %>%
+   filter(year == "2016",
+          host_genotype == "Jade",
+          fungicide_ai != "control")%>%
+   group_by(location)%>%
+   summarise(F_Yield = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
+   pull(F_Yield)
+
+dat3 %>% 
+   mutate(diff = F_Yield - C_Yield) %>%
+   mutate(percent = (diff/F_Yield)*100)
+
+```
+
 This sequence of graphs show that AUDPC and disease incidence tends not affect yields if the season is a low yielding season, _i.e._ lower than 1 tonne per hectare.

### 2020-07-09 07_Manuscript.Rmd
Some more edits and writing

@@
 
+<!-- Mungbean is a new crop to Australia, Despite being introduced in Austlalia in the 1930s Mungbean has only been commercially produced as late as 1960s -->
 Mungbean was first brought to Australia in the 1930s for use as a forage or green manure crop and it was not until the 1960s until that mungbean was grown commercially [@aboutAMA].
-At the end of the 1980s between 3 - 10 thousand hectares were being harvested for dried beans, of which mungbean is included.
-In the decade leading up to 2018 35 - 86.4 thousand hectares of dried beans are being planted per year [@FAOSTAT]. 
-This increase is attributed to the improved yields in the new cultivars and value of the crop [@Clarry2016].
+At the end of the 1980s between 3 - 10 thousand hectares were being harvested for dried beans, of which mungbean is categorised at the FAO statistics data repository [@FAOSTAT].
+In the decade leading up to 2018 between 35 - 86.4 thousand hectares of dried beans were planted annually. 
+This increase is attributed high value export markets and to the improved yields in the new cultivars [@Clarry2016].
 Currently mungbean is predominantly grown in southern Queensland and northern New South Wales as a short season summer legume crop.
-In 2019, approximately 90&nbsp;% of Australian mungbean produced is exported and economic returns can be lucrative for growers with a value of up to \$1300&nbsp;AU a tonne [@QueenslandGovernment2019].
+In 2019, approximately 90&nbsp;% of Australian mungbean was grown for export with lucrative returns of up to \$1300&nbsp;AU a tonne [@QueenslandGovernment2019].
 Mungbean potentially yields up to 3 tonnes per hectare, but due to high variability in yields between seasons and locations, the average Australian farm still yields less than 1 tonne per hectare [@Chauhan2018].
@@
 _phaseolicola_), are the main focus of the Australian Mungbean Improvement programme's resistance breeding efforts due to lack of effective chemical controls for them.
-While a third disease, powdery mildew, is frequently controlled through an integrated disease management strategy of fungicide treatments and cultural practices.
-The disease can reduce yields by up to 40% [@Chankaew2013] in susceptible cultivars.
+While a third disease, powdery mildew, can reduce yields by up to 40% [@Chankaew2013] in susceptible cultivars, the damage can be mitigated through an integrated disease management strategy of fungicide treatments and cultural practices.
 
@@
 
-Commercially available mungbean cultivars in Australia lack sufficient resistance to be used as the primary powdery mildew management strategy. <!-- Citation needed -->
+In Australia, quantitative resistance to powdery mildew has also been incorporated into few commercially available varieties.
+Jade-AU <!-- Need PBR emblem here --> has the the best disease resistance to powdery mildew (moderately susceptible), with cv. Green Diamond also containing some notable resistance [@Sparks2017].
+Commercially available mungbean cultivars in Australia lack sufficient resistance to be used as the primary powdery mildew management strategy. 
+Evidence of this is shown by the 2016 field trials with the moderately susceptible cultivar, Jade-AU, where yield losses of up to 21 % were recorded [@SueThompson2016].
+<!-- Citation does not mention 21% loss I calculated it, the citation is in reference to that field trial though, acceptable???
+-->
 Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013].
-In Australia, quantitative resistance has also been incorporated into few commercially available varieties.
-Jade-AU <!-- Need PBR emblem here --> has the the best disease resistance to powdery mildew (moderately susceptible).
-Because cultivar choice does not confer complete resistance to powdery mildew, additional strategies such as fungicide treatments are necessary to limit yield loss when conditions for the disease are conducive.
+Additional strategies to cultivar choice, such as fungicide treatments, are necessary to limit yield loss when conditions for the disease are conducive.
 

### 2020-07-10 07_Manuscript.Rmd
writing and editing

@@
 
-<!-- Mungbean is a new crop to Australia, Despite being introduced in Austlalia in the 1930s Mungbean has only been commercially produced as late as 1960s -->
-Mungbean was first brought to Australia in the 1930s for use as a forage or green manure crop and it was not until the 1960s until that mungbean was grown commercially [@aboutAMA].
+Mungbean was first brought to Australia in the 1930s for use as a forage or green manure crop and it was only as recent as the 1960s until that mungbean was grown commercially [@aboutAMA].
 At the end of the 1980s between 3 - 10 thousand hectares were being harvested for dried beans, of which mungbean is categorised at the FAO statistics data repository [@FAOSTAT].
@@
 
-Low yields, in part, can be attributed to a range of diseases that affect the crop [@Kelly2017a].
+The high variability in yields, in part, can be attributed to a range of diseases that affect the crop [@Kelly2017a].
 Two major foliar diseases, tan spot or common wilt (*Curtobacterium flaccumfaciens* pv.
-_flaccumfaciens_) and halo blight (_Pseudomonas savastanoi_ pv.
-_phaseolicola_), are the main focus of the Australian Mungbean Improvement programme's resistance breeding efforts due to lack of effective chemical controls for them.
+_flaccumfaciens_) and halo blight (*Pseudomonas savastanoi* pv.
+*phaseolicola*), are the main focus of the Australian Mungbean Improvement programme's resistance breeding efforts due to lack of effective chemical controls for them.
 While a third disease, powdery mildew, can reduce yields by up to 40% [@Chankaew2013] in susceptible cultivars, the damage can be mitigated through an integrated disease management strategy of fungicide treatments and cultural practices.
 
-Powdery mildew is caused by two separate genera of fungi in Australia _Podosphaera xanthii_ and an unnamed _Psuedoidium sp._ (Kiss and Kelly Personal Communication).
+Powdery mildew is caused by two separate genera of fungi in Australia *Podosphaera xanthii* and an unnamed *Psuedoidium sp.* (Kiss and Kelly Personal Communication).
 While the pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified.
@@
 
+Cultivar selection is an additional strategy to mitigate yield damage from powdery mildew. 
 In Australia, quantitative resistance to powdery mildew has also been incorporated into few commercially available varieties.
 Jade-AU <!-- Need PBR emblem here --> has the the best disease resistance to powdery mildew (moderately susceptible), with cv. Green Diamond also containing some notable resistance [@Sparks2017].
-Commercially available mungbean cultivars in Australia lack sufficient resistance to be used as the primary powdery mildew management strategy. 
+However commercially available mungbean cultivars in Australia lack sufficient resistance to be used as the primary powdery mildew management strategy. 
 Evidence of this is shown by the 2016 field trials with the moderately susceptible cultivar, Jade-AU, where yield losses of up to 21 % were recorded [@SueThompson2016].
@@
 Early trials showed that for a fungicide application to provide maximum efficacy, a single fungicide application at first sign of the disease with another follow-up application two weeks later if necessary was the most effective [@Sparks2017].
+However due to the variability in the results between seasons and experiments very few of these studies produced a clear result based on a statistical analysis. 
+This variability between the result of field trials, for the best time to apply fungicide treatments to mitigate yield damage presents an uncertainty for the best practice of fungicide application. 
+<!-- This is where I am working right now :) :) :) -->
+
 Some of the fungicides tested for controlling powdery mildew in mungbean have been registered with the APVMA [@APVMA; @Kelly2017a; <!-- insert all published trials here -->].
@@
 Excessive use of fungicides are not only costly, but lead to problems such as fungicide resistance.
-_Podosphaera xanthii_ is categorised by the Australian Fungicide resistance Action Committee (FRAC) as a 'High risk' candidate to evolve fungicide resistance.
+*Podosphaera xanthii* is categorised by the Australian Fungicide resistance Action Committee (FRAC) as a 'High risk' candidate to evolve fungicide resistance.
 Prior experiences confirm that the evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with potential fungicide resistance in mind.
@@
 In cucurbits, it evolved resistance to benzimidazole within three years of its registration [@Peterson1973] and has evolved resistance to numerous fungicide classes, such as benzimidazoles, demethylation inhibitors, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines since [@Mcgrath2001].
-In cereal crops _Blumeria graminis_ showed reduced sensitivity to strobilurins in 1998, two years after the fungicides began being used in Europe [@Chin2001].
+In cereal crops *Blumeria graminis* showed reduced sensitivity to strobilurins in 1998, two years after the fungicides began being used in Europe [@Chin2001].
 

### 2020-07-10 07_Manuscript.Rmd
More words in the introduction

@@
 However commercially available mungbean cultivars in Australia lack sufficient resistance to be used as the primary powdery mildew management strategy. 
-Evidence of this is shown by the 2016 field trials with the moderately susceptible cultivar, Jade-AU, where yield losses of up to 21 % were recorded [@SueThompson2016].
-<!-- Citation does not mention 21% loss I calculated it, the citation is in reference to that field trial though, acceptable???
--->
+Evidence of this is shown by the 2016 field trials with the moderately susceptible cultivar, Jade-AU, where yield losses of up to 32.7 % were recorded [@SueThompson2016]. 
 Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013].
@@
 Past field trials in eastern Australia have tested a range of fungicide active ingredients while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
-Early trials showed that for a fungicide application to provide maximum efficacy, a single fungicide application at first sign of the disease with another follow-up application two weeks later if necessary was the most effective [@Sparks2017].
-However due to the variability in the results between seasons and experiments very few of these studies produced a clear result based on a statistical analysis. 
-This variability between the result of field trials, for the best time to apply fungicide treatments to mitigate yield damage presents an uncertainty for the best practice of fungicide application. 
-<!-- This is where I am working right now :) :) :) -->
+Early trials showed that for fungicide applications to protect yield, a single fungicide application at first sign of the disease with another follow-up application two weeks later if necessary was the most effective [@SueThompson2016; @Sparks2017].
+However due to the variability in the results between seasons and experiments few of these studies produced a clear result based on a statistical analysis. 
+This variability thus presents some uncertainty for the best practice of fungicide spray schedules to mitigate yield losses from powdery mildew.
 
-Some of the fungicides tested for controlling powdery mildew in mungbean have been registered with the APVMA [@APVMA; @Kelly2017a; <!-- insert all published trials here -->].
+The collection of experiments mentioned above and other unpublished trials proved an excellent opportunity for a meta-analysis.
+Meta-analyses are statistical tools which can analyse a collection of experiments, which have a similar aim, and produces a more accurate estimate of the true effect being measured.
+Using a meta-analysis can be useful in situations like this where several studies exist, that have the same objective but may not provide a clear answer to the question due to variation in the results within the individual studies.
+The outcome of a meta-analysis provides a more accurate estimation of the true treatments effect, because it considers the amount of variance in each study and weights the influence of each studies treatment effects according to it's statistical accuracy.
+Typically meta-analyses consider the effect of a single treatment against a control group accross multiple independant studies [@Madden2011]. 
+However meta-analyses can also consider effect differences between multiple treatments and a control group, these are called multi-variate or network meta-analyses [@MaddenEtAl2016]. 
+Multi-variate meta-analyses are particularly useful when there are no direct comparisons between two treatments in any of the included studies. 
+In-direct comparisons can be made between these two treatments if the both had direct comparisons with one or more treatments in common, assuming no significant bias in the studies which investigated each of the treatments which are subject to a indirect comparison [@Jansen2011].
 
-Meta-analyses are statistical tools which can analyse a collection of experiments, which have a similar aim, and estimates the difference between the control and treatment means.
-Using a meta-analysis can be useful in situations like this where several studies exist, that have the same objective but may not provide a clear answer to the question due to variation in the results within the individual studies.
-The outcome of a meta-analysis provides a more accurate estimation of the true treatments effect, because it considers the amount of variance in each study and weights the influence of each on the treatment effects according to the study's statistical accuracy.
-Using a meta-analysis on the <!-- more goes here ? -->
-
-### Aims
-
+Considering the recent launch in 2019 of the decision support system (DSS) PowderyMildewMDM [@Diggle], which provides a cost benefit analysis to assists growers in thier decidion 'if' and 'when' apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
 The aim of this meta-analysis was to determine, from a collection of unpublished studies, what spray management scenario provides the greatest yield protection from powdery mildew in Australian mungbean.
 
+<!--Some of the fungicides tested for controlling powdery mildew in mungbean have been registered with the APVMA [@APVMA; @Kelly2017a;  insert all published trials here -->.
+
 ## Materials and Methods
-
+<!-- This is where I am working right now (Paul) :) :) :) -->
 The data for this study were obtained from through personal correspondence with colleagues and collaborating institutions.

### 2020-07-13 07_Manuscript.Rmd
edits and writing

@@
 Mungbean was first brought to Australia in the 1930s for use as a forage or green manure crop and it was only as recent as the 1960s until that mungbean was grown commercially [@aboutAMA].
-At the end of the 1980s between 3 - 10 thousand hectares were being harvested for dried beans, of which mungbean is categorised at the FAO statistics data repository [@FAOSTAT].
+At the end of the 1980s between 3 - 10 thousand hectares were being harvested for dried beans, of which mungbean is categorised by the FAO statistics data repository [@FAOSTAT].
 In the decade leading up to 2018 between 35 - 86.4 thousand hectares of dried beans were planted annually. 
@@
 While the pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified.
+<!-- Perhaps some more information here about the biology, infection time, latent period, how long in a cycle -PM-->
 
 Weather conditions that favour the development of the disease are cool temperatures between 22&deg; and 26&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
+
 Because of this, planting date is an effective strategy for preventing the development of powdery mildew in mungbean.
@@
 
-Considering the recent launch in 2019 of the decision support system (DSS) PowderyMildewMDM [@Diggle], which provides a cost benefit analysis to assists growers in thier decidion 'if' and 'when' apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
+Considering the recent launch in 2019 of the decision support system (DSS) PowderyMildewMDM [@Diggle], which provides a cost benefit analysis to assists growers in their decision 'if' and 'when' apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
 The aim of this meta-analysis was to determine, from a collection of unpublished studies, what spray management scenario provides the greatest yield protection from powdery mildew in Australian mungbean.
@@
 <!-- should check, Sue and Mal moved to USQ in 2015 I think.
-Therefore the trials probably started with USQ earlier --> The most recent trials starting from 2016 were undertaken by the University of Southern Queensland (USQ) with the assistance of Queensland DAF from 2016 to 2019.
+Therefore the trials probably started with USQ earlier --> The most recent trials starting from 2015 were undertaken by the University of Southern Queensland (USQ) with the assistance of Queensland DAF from 2015 to 2019.
 Trial data were in different formats with varying levels of information.
@@
 
-These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar and supplementary irrigation.
-To account for the variation between trials, and the treatments within trials, a single 'trial' factor was created to describe the main variables; a trial reference code, trial location, trial season, host genotype, row spacing, and dose.
+These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications and cultivar.
+To account for the variation attributed to some of these variables between trials, and the treatments within trials, a single 'trial' factor was created to describe the main variables; a trial reference code, trial location, trial season, host genotype, row spacing, and fungicide dose.
 Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 -- 9 ordinal scale (Table 2). 
@@
 A spray schedule with a single spray, and a spray schedule with two or three spray applications (Plus). 
-The division of the treatments categorised: 13 Early treatments; 5 'EarlyPlus', 32 'Recommended'; 46 'RecommendedPlus'; 17 'Late'; and 20 'LatePlus.
+The division of the treatments categorised: 13 'Early' treatments; 5 'EarlyPlus', 32 'Recommended'; 46 'RecommendedPlus'; 17 'Late'; and 20 'LatePlus.
 'EarlyPlus' treatments were removed from the subsequent meta-analysis, due to an insufficient sample size.
@@
 Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 1.697 and the approach reported in Ngugi et al. [-@Ngugi2011].
-The T-critical value was determined from the 30 degrees of freedom using a t-distribution table. 
+The T-critical value was determined from the 30 degrees of freedom and probability of $a = 0.1$ using a t-distribution table.
+<!-- Checking this reference the T-critical value might need to be adjusted to 2.042 using an alpha of 0.05, or as Ngugi choses df = inf and alpha of 0.05 -->
 The 2012 Gatton and 2015 Emerald trials reported treatment means without accompanying variance and were thus removed from the dataset  prior to the analysis.
 
-This analysis uses the grain yield standardised mean difference (SMD) as the response variable. 
-SMD were chosen to reduce the inherent variability between trials due to location and seasonal effects on grain yields. 
-$SMD = \frac{Y_i-\overline{Y_c}}{\sigma_p}$ [@HigginsGreen] 
-Where $Y_i$ is the treatment mean, $Y_c$ is the no spray control treatment mean and $\sigma_p$ is the trial pooled standard deviation.
+This analysis uses response ratio, or means difference (MD) as the response variable. 
+MD were chosen to reduce the inherent variability between trials due to location and seasonal effects on grain yields by assessing the effect of fungicide spray schedule on the difference between the treatments and no spray control plot.
+$MD = {Y_i-\overline{Y_c}}$ [@HigginsGreen] 
+Where $Y_i$ is the treatment mean, $Y_c$ is the no spray control treatment mean .
 
@@
 $Y_i \sim N(\mu,s_i^2 + \sigma^2)$
-where $Y_i$ is the response, a vector of the SMD grain yield for each treatment in the $i$th trial over total number ($K$) of trials($i$  = 1, ...$K$). 
+where $Y_i$ is the response, a vector of the MD grain yield for each treatment in the $i$th trial over total number ($K$) of trials($i$  = 1, ...$K$). 
 $Y_i$ is estimated from a normal distribution with the mean $\mu$, sample variance of $Si_^2$ and a between trial variance of $\sigma^2$.
@@
 **Moderator variables.** The random effects meta-analysis was expanded to evaluate if the residual heterogeneity could be explained by spray schedule ($SPRAY_{Sched}$). 
+`SpraySchedule` was assigned as an inside factor to the outside factor `trial` to provide correlated random effects between the different `SpraySchedule` treatments within `trials`.
+
 The intercept was omitted from the model so each treatment would be reported against zero, which represents the control mean. 
-Linear contrasts were used to compare the mean effect sizes between each spray schedule treatment and their respecting standard errors and confidence intervals.
+Linear contrasts were used to compare the mean effect sizes between each spray schedule treatment and their respective standard errors and confidence intervals.
 
-Additional meta-analysis models tested variables ... for their influence on the SpraySheduale variables ability to mitigate yield loss. 
+Additional meta-analysis models tested variables ... for their influence on the SpraySchedule variables ability to mitigate yield loss. 
 For the variable disease pressure a Wald-type test was used to test the impact of this variable on the model as a whole.
@@
 ## Discussion
-Mungbeans have only recently been cultivated in Australia, with the first commercial crops planted in the 1960s [].
+The current advice provided to growers for when to commence fungicide applications for control of powdery mildew is at the first sign of the disease [@SueThompson2016].
+This meta-analysis confirms this advice by showing that applying the first fungicide application, within three days of first sign (Recommended) and up to 13 days for as was seen in the `Late` treatments.
+In addition spray schedules with follow-up fungicide applications made at least two weeks after the first application were on average more effective at reducing yield loss due to powdery mildew, which again follows the advice given by Thompson et.
+al [@SueThompson2016].
+Fungicide applications which were made prior to any sign of the disease we not effective at saving yield.
 
@@
 However network meta-analyses permit indirect comparisons, for when two treatments may not occur in the same experiment. 
-For the indirect difference between two treatments is equal to the difference between the difference in those two treatments with one other treament in common ($d_{AB} = d_{AC} - d_{BC}$)[@Jansen2011]
+For the indirect difference between two treatments is equal to the difference between the difference in those two treatments with one other treatment in common ($d_{AB} = d_{AC} - d_{BC}$)[@Jansen2011]
 For example treatments `Early` and `LatePlus` never occurred within the same trial for any trials included in the meta-analysis. 

### 2020-07-13 08_MetaAnalysis_Emerson.Rmd
Corrected meta-analysis by Emerson based on the arm-based approach

--- 2020-07-09 04_MetaAnalysis.Rmd
@@
+---
+output: html_document
+editor_options: 
+  chunk_output_type: inline
+---
+
 ```{r MEsummary_Libraries2, message=FALSE, include=FALSE}
@@
    slimmer_PM_dat %>%
-   filter(fungicide_ai != "control") %>% #remove controls from the data
+   mutate(vi = vi/n) %>% 
+   #filter(fungicide_ai != "control") %>% #remove controls from the data
    mutate(spray_management =
@@
                 c(
+                   "control",
                    "Early",
@@
       vi,
-      vi2
+      yield_error,
+      vi2,
+      n
       )
@@
 ```{r Metafor-analysis}
+dat1$id <- 1:nrow(dat1)
+
 PM_mv <- rma.mv(
-   yi = grain_MD,
-   vi,
-   mods = ~ spray_management - 1,
-   method = "ML",
-   random = ~ spray_management | trial,
-   struct = "UN",
-   data = dat1
-)
-summary(PM_mv)
-```
-```{r}
-(PM_mv$b - PM_mv$ci.ub) / PM_mv$se
-```
-
-In this result we can see that the `Early` treatment is not significantly different from zero, which in this case is the mean of the no spray `control`.
-However the other treatments are significantly different from zero.
-The $Q_M$ [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, shows the moderators significantly influence the model ($Q_M = 26.22, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
-The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 568.31, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
-
-Lets look at the trial variability in this model with a forest plot
-```{r forestP, fig.height= 40, fig.width=17}
-source(here("R/change_labels.R"))
-source(here("R/forest_rows.R"))
-
-### Sort and arrange data-frame occordingly and produce a index vector to inform the order of each "Trial" on the plot
-index1 <- dat1 %>%
-   mutate(ID = seq_along(trial_ref)) %>%
-   mutate(spray_management = 
-             factor(spray_management, 
-                    levels = c("Early","Late","Recommended",
-                    "Recommended_plus","Late_plus"))) %>%
-   arrange(desc(spray_management), location, desc(grain_MD)) %>%
-   mutate(ID2 = order(ID))%>%
-   pull(ID2)
-
-### Use forest rows function to return a list of where to place on the plot: sub-titles, each trial row, and summary prediction for each treatment.
-### this list can be used below to reference where to plot each variable
-rows1 <- forest_rows(head_row = 156, 
-                     ord_var = dat1$spray_management, 
-                     index = index1, 
-                     gap = 5, 
-                     row_offset = -2)
-
-### A data-frame of meta-model coefficients used to produce the summary polygons for each treatment
-polys <- data.frame(ref = change_labels(names(coef(PM_mv))),
-                    x = coef(PM_mv),
-                    ci.lb = PM_mv$ci.lb,
-                    ci.ub = PM_mv$ci.ub)[c(1,4,2,3,5),]
-polys$rows <- rows1$pred_row - 1.5
-
-forest1  <- metafor::forest(PM_mv, cex = 1.15 , width = 5,
-                #order = "fit",
-                rows = rows1$trows-1.5,
-                ilab = cbind(dat1$year, 
-                             dat1$row_spacing, dat1$host_genotype, dat1$dose),
-                ilab.xpos = c(-2.35,-2.1,-1.8,-1.4),
-                slab = NA, 
-                xlim = c(-2.9, 2.2),
-                ylim = c(18,157),
-                xlab = "Grain yield mean difference",
-                addfit = FALSE,
-                efac = c(0.2,0.15,0.2),
-                at = seq(-1,1.5, 0.5))
-
-### code which puts lines and annotations on the plot, its a bit long...
-source(here("R/add_annotations.R"))
-
-```
-
-Let's see if we can improve this model by including some other random effects and improving the random effect structure in the model.
-
-```{r rma_noRandomInteractiveTerm}
-PM_mv_St <- rma.mv(
-   yi = grain_MD,
+   yi = grain_yield.t.ha,
    vi,
@@
    method = "ML",
-   random = list( ~ 1 | trial),
+   random = list(~ spray_management | trial, ~1 | id), 
+   struct = "UN",
+   control=list(optimizer="optim"),
    data = dat1
@@
 
-PM_mv_St1 <- rma.mv(
-   yi = grain_MD,
+summary(PM_mv)
+library(multcomp)
+summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none"))
+plot(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))))
+
+PM_mv2 <- rma.mv(
+   yi = grain_yield.t.ha,
    vi,
-   mods = ~ spray_management,
+   mods = ~ spray_management*D_pres,
    method = "ML",
-   random = list(
-      ~ 1 |
-         location / year / trial_ref / dose / host_genotype / factor(row_spacing) /
-         spray_management
-   ),
+   random = list(~ spray_management | trial, ~1 | id), 
+   struct = "UN",
+   control=list(optimizer="optim"),
    data = dat1
 )
+summary(glht(PM_mv2, linfct=cbind(contrMat(rep(7,12), type="Tukey"))), test=adjusted("none"))
+plot(glht(PM_mv2, linfct=cbind(contrMat(rep(7,12), type="Tukey"))))
 
-AIC(PM_mv) # Printing the AIC of the model helps differentiate the models in the anova output
-anova(PM_mv, PM_mv_St) # PM_mv is the better model
-AIC(PM_mv_St)
-anova(PM_mv_St, PM_mv_St1) # PM_mv_St is the better model
+anova(PM_mv, PM_mv2)
+
 ```
-
-The simpler `PM_mv_St` model explains significantly less variation than the more complicated model `PM_mv`.
-So we will keep the original model `PM_mv`.
-
-I have also tested the structure for testing the random trial and spray_management variables, these show that there is no significant difference to the models `PM_mv_St` and `PM_mv_St1` and that the originally method of specifying the random variables within the `trial` factor provides us with the best model.
-
-The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis.
-The second table is in two parts (left and right). 
-The left part, rho, is the correlation of variation between the specified treatments.
-All comparisons were acceptable except for a comparison between `Early` and `Late_plus`, `0.000` rho.
-`Early` and `Late_plus` treatments never occurred within the same trial, which is indicated by the right side of the table (hence the warning).
-
-The fixed effects, in the last table, show that yields in single early spray treatments are not significantly different from zero, or the no spray control.
 
@@
 
-### Metafor comparisons
-
-To make it easier to compare each of the treatments we can compute the meta-analysis contrasts.
-
-```{r metafor_contrasts}
-meta_cont <- anova(PM_mv, L = rbind(
-   c(-1, 1, 0, 0, 0),
-   c(-1, 0, 1, 0, 0),
-   c(-1, 0, 0, 1, 0),
-   c(-1, 0, 0, 0, 1),
-   c(0, -1, 1, 0, 0),
-   c(0, -1, 0, 1, 0),
-   c(0, -1, 0, 0, 1),
-   c(0, 0, -1, 1, 0),
-   c(0, 0, -1, 0, 1),
-   c(0, 0, 0, -1, 1)
-))
-
-change_labels <- function(x1) {
-   x1 <- gsub(pattern = "spray_management",
-              replacement = "",
-              x = x1)
-   x1
-}
-
-source("R/p_star.R")
-
-table3 <- data.frame(
-   contrasts = change_labels(meta_cont$hyp[, 1]),
-   estimates = meta_cont$Lb,
-   se = meta_cont$se,
-   z_val = meta_cont$zval,
-   pval = meta_cont$pval,
-   VisP = p_star(meta_cont$pval)
-)
-write.csv(table3, here("cache/Table3_contrasts.csv"), row.names = FALSE)
-```
-
 Results show with the exclusion of the no spray `control` and `Late` treatments, `Early` applications are significantly worse than all other treatments leading to lower yield estimates.
@@
    factor(c(
+
+       "control",
       "Early",
@@
 efficacy %>%
+   filter(Treatment != "control") %>% 
    mutate(Treatment = factor(Treatment, levels = rev(
       c(
+
          "Early",
@@
 ```
-
-### Disease pressure effect
-
-We also want to know if disease pressure exerts an effect on the decision for spray control.
-Above we can see spraying at the first sign of powdery mildew or with in `r min(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"| slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` - `r max(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"|                   slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` days after first sign is effective at mitigating yield loss.
-Does this change between years of low and high disease pressure.
-
-We will add the intercept back into this model for ease of interpretation. 
-```{r D_pres-Meta}
-PM_mv_Dp <- rma.mv(
-   yi = grain_MD,
-   vi,
-   mods = ~ spray_management * D_pres - 1,
-   method = "ML",
-   random = ~ spray_management | trial,
-   struct = "UN",
-   data = dat1
-)
-
-summary(PM_mv_Dp)
-```
-
-These results show that the spray management variable we tested are not significantly better or worse between the two levels of disease pressure.
-It seems that disease preasure does not improve the models ability to assess the most effective fungicide spray management option.
-Let's compare the disease pressure model to the original model to test this assumption.
-
-```{r compareDvNDP}
-AIC(PM_mv_Dp)
-anova(PM_mv_Dp, btt = "D_pres")
-anova(PM_mv, PM_mv_Dp)
-```
-
-A Wald test of `D_pres` shows the moderator is not significant in accounting for heterogeneity (P = 0.4859).
-No significant difference which informs us to use the original model `PM_mv`, which is the simplest.
 
@@
    group_by(trial, spray_management, n) %>%
-   summarize(yi_mean = mean(grain_SMD),
+   summarize(yi_mean = mean(grain_yield.t.ha),
              vi_mean = mean(yield_error)) %>%
@@
    net_con,
-   reference.group = 5,
+   reference.group = 1,
    rightcols = c("effect", "ci", "Pscore"),

### 2020-07-14 02_Preliminary_analysis.Rmd
Save plots and data to file for use in manuscript.rmd

@@
 # Plot
-season_dates %>%
+SeasonPlot <- season_dates %>%
    ggplot() +
@@
    ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
+
+SeasonPlot
 ```
@@
 ```
+
+```{r}
+save(SeasonPlot, file = here("cache/PreliminaryData.Rdata"))
+```

### 2020-07-14 08_MetaAnalysis_Emerson.Rmd
Save plots and data to file for use in manuscript.rmd

@@
 ```{r metafor_plot}
-efficacy %>%
+YieldContrasts <- efficacy %>%
    filter(Treatment != "control") %>% 
@@
    coord_flip()
+
+YieldContrasts
 ```
@@
 Indirect comparisons are ok to interpret in the results of a network meta-analysis, however if there are biases between trials including `Early` or `LatePlus` treatments then the results are likely bias.
-Therefore we wish to do a quick check that the trials which included `Early` treatments did not significantly differ from trials which incorportated `LatePlus`,
+Therefore we wish to do a quick check that the trials which included `Early` treatments did not significantly differ from trials which incorporated `LatePlus`,
 Lets create a data.frame of values for this comparison
@@
 write.csv(slimmer_PM_dat, file = "data/GYmeta_data.csv")
+save(dat1, efficacy, PM_mv, YieldContrasts, file = here("cache/Meta-analysisData.Rdata"))
 ```

### 2020-07-14 07_Manuscript.Rmd
writing corrections, loading data and plots for figures tables and hard-coded results

@@
 PM_Mdat <- read.csv(here("cache/PM_MB_updated.csv"))
+load(file = here("cache/Meta-analysisData.Rdata"))
+load(file = here("cache/PreliminaryData.Rdata"))
 ```
@@
 ## Materials and Methods
-<!-- This is where I am working right now (Paul) :) :) :) -->
 The data for this study were obtained from through personal correspondence with colleagues and collaborating institutions.
@@
 
+<!-- Passage here about trial sowing times and first sign of disease (Figure 1)  PM -->
+
 What remained was the mean yield for total of 173 treatments in the following five spray schedule categories: no spray control, single early spray, single recommended spray, recommended with multiple sprays, single late spray, and late with multiple sprays.
@@
 The data were analysed in the R statistical software environment, version 4.0.1, [@RCoreTeam2020] using two contributed meta-analysis packages, `metafor`, version 2-4.0, [@Viechtbauer2010] and `netmeta`, version 1.2-1, [@Rucker2020].
+
+```{r Figure2_treatForest}
+YieldContrasts
+```
 
@@
 <!-- Write about first sign of disease in March -->
-Overall the meta-analysis indicated that, with the exception of `Early` single sprays all the the spray schedules were effective at protecting mungbean yields, relative to the no spray controls (Figure 1).
+Overall the meta-analysis indicated that, with the exception of `Early` single sprays all the the spray schedules were effective at protecting mungbean yields, relative to the no spray controls (Figure 2).
 Treatments which incorporating multiple fungicide applications, `RecommendedPlus` and `LatePlus` produced the highest mean yield protection estimates at 196.4 (SE = 48.7&nbsp;kg&nbsp;/&nbsp;ha) and 219.9&nbsp;kg&nbsp;/&nbsp;ha (SE = 47.4&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3).
@@
 
+```{r Figure1}
+SeasonPlot
+```
+
 ```{r table3_Contrasts}
@@
 ## Discussion
-The current advice provided to growers for when to commence fungicide applications for control of powdery mildew is at the first sign of the disease [@SueThompson2016].
-This meta-analysis confirms this advice by showing that applying the first fungicide application, within three days of first sign (Recommended) and up to 13 days for as was seen in the `Late` treatments.
-In addition spray schedules with follow-up fungicide applications made at least two weeks after the first application were on average more effective at reducing yield loss due to powdery mildew, which again follows the advice given by Thompson et.
+The current advice provided to growers for when to commence fungicide applications for control of powdery mildew, is spray at the first sign of the disease and if necessary a follow-up spray two weeks later [@SueThompson2016; @Sparks2017].
+This meta-analysis confirms that advice, by showing that applying the first fungicide application, within three days of first sign will significantly mitigate yield loss from powdery mildew ($Recommended$, P = `r signif(PM_mv$pval[3],2)`).
+However in addition to this the analysis also showed spray schedules which commenced 'late', up to 13 days after first sign of the disease was still effective at mitigating yield loss ($Late$, P =  `r signif(PM_mv$pval[5],2)`).
+Additionally, spray schedules with follow-up fungicide applications made at least two weeks after the first application were on average more effective at reducing yield loss due to powdery mildew, which again follows the advice given by Thompson et.
 al [@SueThompson2016].
-Fungicide applications which were made prior to any sign of the disease we not effective at saving yield.
+This meta-analysis adds certainty to the advice which is currently given to growers, especially around any uncertainty that Early sprays might be effective at suppressing the disease. 
+We show here that Early fungicide applications, which were made prior to any sign of the disease, were not effective at mitigating yield loss.
+
+The results also provide a effective spray window for mitigating yield losses, given that spray schedules commenced `Late` were still significantly effective at mitigating yield loss (P = `signif(PM_mv$pval[5],2)`) at least up to 13 days after the first sign of disease.
+Growers typically don't have the time to inspect their crop regularly for the first sign of powdery mildew. 
+Also weather conditions and logistical issues might prevent them from getting machinery in the paddock to treat the disease immediately after it is spotted. 
+These issues and perhaps other on farm duties might delay a timely application, which might permit the disease time to establish. 
+Knowing a delay of up to two weeks will not lead to significant yield losses can allow growers to incorporate other integrated pest management options, such as insecticide, with the fungicide spray saving on spray application costs.
+However care should be taken to ensure if a second follow-up fungicide application is necessary, sufficient time should be permitted to schedule the spray and avoid the end of season withholding periods on fungicides.
+
+It is important to note, the studies included in this meta-analysis were intentionally sown late to ensure infection during the experiment. 
+While growers may have to choose sowing mungbeans late, if the crop is sown too late there is a risk of it being frosted-out.
+Regardless in most cases growers will likely have sown earlier than the trials used here reducing the risk of powdery mildew, and also reducing the requirements for fungicide applications.
+Despite the confidence in the result of this model discretion is still required for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.
+<!-- Insert Powdery mildew plug here-->
+<!-- This is where I am working right now (Paul) :) :) :) -->
+
+These results suggest that when weather conditions cool and become suitable for powdery mildew growers should scout their every week to two weeks
 

### 2020-07-15 08_MetaAnalysis_Emerson.Rmd
Tidy some code Make function to add names to glht function add comparison between PowderyMildew mitigation and our model

@@
                here,
-               netmeta)
+               netmeta,
+               multcomp)
 
@@
                       "highD")),
-          grain_MD = grain_yield.t.ha - yi_C) %>%
+          grain_MD = grain_yield.t.ha - yi_C,
+          id = row_number()) %>%
    select(
@@
       vi2,
-      n
-      )
+      n,
+      id)
 ```
@@
 ```{r Metafor-analysis}
-dat1$id <- 1:nrow(dat1)
-
 PM_mv <- rma.mv(
@@
 summary(PM_mv)
-library(multcomp)
+```
+
+```{r PM_Mv_Contrast}
+source("R/simple_summary.R")
 summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none"))
+simple_summary(summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none")))
 plot(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))))
+```
 
+```{r DisPressComparison}
 PM_mv2 <- rma.mv(
@@
 )
+summary(PM_mv2)
 summary(glht(PM_mv2, linfct=cbind(contrMat(rep(7,12), type="Tukey"))), test=adjusted("none"))
@@
 ```
+
+```{r compare2PowderyMildewMDM}
+
+PMBM <- 
+   data.frame(Sprays = c(rep(1,20), rep(2,20)),
+              Disease = rep(c(rep("NotPresent", 5),
+                          rep("LowerCanopy", 5),
+                          rep("MidCanopy", 5),
+                          rep("UpperCanopy", 5)),2),
+              CropMaturity = rep(c("Vegetative", "Budding", "Flowering",
+                                   "EarlyPod", "LatePod"), 8),
+              mitigation = c(0.57, 0.855, 0.95,0.95,0.95,
+                             0.45995, 0.52919,0.5530,0.390,0.1642,
+                             0.291258,0.351051, 0.2454,0.1409,0.4717,
+                             0,0.059597,0.093034,0.0682476,0.0215584,
+                             0.95,0.95,0.95,0.95,0.95,
+                             0.766588,0.6991,0.55042,0.390056,0.1642,
+                             0.485429,0.390,0.2454,0.140904,0.0471684,
+                             0.0791,0.086068,0.093034,0.0682476,0.0215584))
+
+# what is the mean age of the plant in our data when disease first occurs and we apply the first spray?
+source("R/import_data.R")
+PM_MB_dat <- import_data()
+mean(PM_MB_dat$first_sign_disease - PM_MB_dat$planting_date, na.rm =TRUE) # 46.3 days (which is when the plant is flowering)
+
+#What proportion of the yield was saved?
+1 - (coef(PM_mv)[1] /(coef(PM_mv)[1] + coef(PM_mv)[3]))
+1- (coef(PM_mv)[1] /(coef(PM_mv)[1] + coef(PM_mv)[4]))
+
+PMBM %>%
+   filter(CropMaturity == "Flowering")
+
+```

### 2020-07-15 07_Manuscript.Rmd
Writing and edits

@@
 ## Discussion
-The current advice provided to growers for when to commence fungicide applications for control of powdery mildew, is spray at the first sign of the disease and if necessary a follow-up spray two weeks later [@SueThompson2016; @Sparks2017].
+The current advice provided to growers for when to commence fungicide applications for control of powdery mildew, is spray at the first sign of the disease then if necessary a follow-up spray two weeks later [@SueThompson2016; @Sparks2017].
 This meta-analysis confirms that advice, by showing that applying the first fungicide application, within three days of first sign will significantly mitigate yield loss from powdery mildew ($Recommended$, P = `r signif(PM_mv$pval[3],2)`).
-However in addition to this the analysis also showed spray schedules which commenced 'late', up to 13 days after first sign of the disease was still effective at mitigating yield loss ($Late$, P =  `r signif(PM_mv$pval[5],2)`).
-Additionally, spray schedules with follow-up fungicide applications made at least two weeks after the first application were on average more effective at reducing yield loss due to powdery mildew, which again follows the advice given by Thompson et.
+In addition, spray schedules which commenced 'late', up to 13 days after first sign of the disease were still effective at mitigating yield loss ($Late$, P =  `r signif(PM_mv$pval[5],2)`).
+Spray schedules which included follow-up fungicide applications were on average more effective at reducing yield loss due to powdery mildew, which again follows the advice given by Thompson et.
 al [@SueThompson2016].
@@
 
-The results also provide a effective spray window for mitigating yield losses, given that spray schedules commenced `Late` were still significantly effective at mitigating yield loss (P = `signif(PM_mv$pval[5],2)`) at least up to 13 days after the first sign of disease.
-Growers typically don't have the time to inspect their crop regularly for the first sign of powdery mildew. 
-Also weather conditions and logistical issues might prevent them from getting machinery in the paddock to treat the disease immediately after it is spotted. 
-These issues and perhaps other on farm duties might delay a timely application, which might permit the disease time to establish. 
-Knowing a delay of up to two weeks will not lead to significant yield losses can allow growers to incorporate other integrated pest management options, such as insecticide, with the fungicide spray saving on spray application costs.
-However care should be taken to ensure if a second follow-up fungicide application is necessary, sufficient time should be permitted to schedule the spray and avoid the end of season withholding periods on fungicides.
+The results also provide a effective spray window for mitigating yield losses, given that spray schedules which commenced 'Late' were still significantly effective at mitigating yield loss (P = `signif(PM_mv$pval[5],2)`) at least 13 days after the first sign of disease.
+Growers typically don't have the time to inspect their crop regularly for the first sign of powdery mildew and therefore powdery mildew may not be spotted within the first couple of days of it establishing.
+Also weather conditions and logistical issues might prevent growers from getting machinery in the paddock to treat the disease immediately after it is spotted. 
+These issues, and perhaps other on farm duties, might delay a timely application, permitting the disease more time to establish. 
+Knowing a delay of up to two weeks may not lead to yield losses can allow growers to incorporate other integrated pest management options, such as insecticide, with the fungicide spray saving on spray application costs.
+However care should be taken to ensure if a second follow-up fungicide application is necessary, sufficient time should be permitted to schedule the spray and avoid the end of season fungicide withholding periods.
 
-It is important to note, the studies included in this meta-analysis were intentionally sown late to ensure infection during the experiment. 
-While growers may have to choose sowing mungbeans late, if the crop is sown too late there is a risk of it being frosted-out.
-Regardless in most cases growers will likely have sown earlier than the trials used here reducing the risk of powdery mildew, and also reducing the requirements for fungicide applications.
-Despite the confidence in the result of this model discretion is still required for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.
-<!-- Insert Powdery mildew plug here-->
+It is important to note, the studies included in this meta-analysis were intentionally sown late in the season to ensure infection during the experiment (Figure 1). 
+While certain circumstances may force growers to sow mungbeans late, if the crop is sown too late there is a risk of frost impacting on the yield.
+Regardless in most cases growers are likely to sow earlier in the season, lowering their risk of powdery mildew and reducing the requirements for fungicide applications.
+Despite the significance in the result some discretion for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.
+The PowderyMildewMBM considers these variables, crop growth stage and weather, to assist decision making whether to spray or not to spray [@Diggle].
+
 <!-- This is where I am working right now (Paul) :) :) :) -->
@@
 
-Despite the improved knowledge for cultivating mungbean this 40 year period from 1980 and today, variability in yields and quality persist due to seasonal differences and the need to refine best management practices.
-Between trial variability was
-
 A recent development, the release of an app for tablet devices, 'PowderyMildewMBM' a decision support system (DSS) tool, increases the ease of preparing a fungicide spray schedule to manage powdery mildew [@Diggle].
@@
 The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability that one or two fungicide sprays would protect yields sufficiently to increase the net profit.
+The meta-analysis is limited in scope to the timing of application and therefore we can't validate all the variables available in PowderyMildewMDM. 
+However our results validate the decision of the app developers to not recommend prophylactic fungicide applications. 
+If the powdery mildew is not observed in the crop the app advises the user to keep monitoring for disease.  
 <!-- Think about how to word this, that we are using this to validate the app: The findings of this meta-analysis confirm the recommendations that PowderyMildewMBM gives in most situations would be correct.
 -->
-
-Within a normal meta-analysis the number direct treatment comparisons, undertaken within the same trial, for each treatment is important for understanding how robust the meta-analysis estimates are for those treatments.
-However network meta-analyses permit indirect comparisons, for when two treatments may not occur in the same experiment. 
-For the indirect difference between two treatments is equal to the difference between the difference in those two treatments with one other treatment in common ($d_{AB} = d_{AC} - d_{BC}$)[@Jansen2011]
-For example treatments `Early` and `LatePlus` never occurred within the same trial for any trials included in the meta-analysis. 
-M
+<!-- I am finding it difficult to say that our findings confirm recommendations of the app, given the app does not advise on early late or recommended spray timing AND we don't investigate the differences in yield mitigations under the variables in the app (growth stage and weather) [Paul]-->
 

### 2020-07-15 R/simple_summary.R
assist in providing names to multiple comparisons tests, needs work

@@ -1,0 +1,34 @@
+# This function adds the comparison names to the multiple comparisons Tukey test
+# it requires the summary of a glht test on a model object
+
+source(here::here("R/p_star.R"))
+
+simple_summary <-
+   function(sum_meta){
+      names1 <- colnames(sum_meta[["model"]]$G)
+      ind_names <- names(sum_meta[["test"]]$coefficients)
+      
+      rename_index <- function(index_name, char_name){
+         #if(length(index_name) != length(char_name)){stop("index_name and char_name not the same length")}
+         for(i in rev(seq_along(char_name))){
+            if(i == rev(seq_along(char_name))[1]){new_name <- index_name}
+            new_name <- gsub(as.character(i),char_name[i], new_name)
+         }
+         return(new_name)
+      }
+      
+      data.frame(contrast = rename_index(index_name = ind_names, char_name = names1),
+                 coefficients = sum_meta[["test"]]$coefficients,
+                 pvals = sum_meta[["test"]]$pvalues,
+                 sig = p_star(sum_meta[["test"]]$pvalues)
+                                         )
+         
+   }
+
+
+
+#### TESTING
+# 
+# summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none"))[["test"]]$pvalues
+# colnames(summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none"))[["test"]]$coefficients)
+simple_summary(summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none")))

### 2020-07-16 07_Manuscript.Rmd
Writing and editing

@@
 load(file = here("cache/PreliminaryData.Rdata"))
+PM_MB_dat%>% 
+   filter(fungicide_ai == "tebuconazole")
 ```
@@
 However due to the variability in the results between seasons and experiments few of these studies produced a clear result based on a statistical analysis. 
-This variability thus presents some uncertainty for the best practice of fungicide spray schedules to mitigate yield losses from powdery mildew.
+This variability presents uncertainty for the best practice of fungicide spray schedules to mitigate yield losses from powdery mildew.
 
@@
 The outcome of a meta-analysis provides a more accurate estimation of the true treatments effect, because it considers the amount of variance in each study and weights the influence of each studies treatment effects according to it's statistical accuracy.
-Typically meta-analyses consider the effect of a single treatment against a control group accross multiple independant studies [@Madden2011]. 
+Typically meta-analyses consider the effect of a single treatment against a control group across multiple independent studies [@Madden2011]. 
 However meta-analyses can also consider effect differences between multiple treatments and a control group, these are called multi-variate or network meta-analyses [@MaddenEtAl2016]. 
@@
 ## Discussion
-The current advice provided to growers for when to commence fungicide applications for control of powdery mildew, is spray at the first sign of the disease then if necessary a follow-up spray two weeks later [@SueThompson2016; @Sparks2017].
+The current advice provided to growers for when to commence fungicide applications for control of powdery mildew, is to spray at the first sign of the disease then if necessary a follow-up spray two weeks later [@SueThompson2016; @Sparks2017].
 This meta-analysis confirms that advice, by showing that applying the first fungicide application, within three days of first sign will significantly mitigate yield loss from powdery mildew ($Recommended$, P = `r signif(PM_mv$pval[3],2)`).
@@
 
-The results also provide a effective spray window for mitigating yield losses, given that spray schedules which commenced 'Late' were still significantly effective at mitigating yield loss (P = `signif(PM_mv$pval[5],2)`) at least 13 days after the first sign of disease.
-Growers typically don't have the time to inspect their crop regularly for the first sign of powdery mildew and therefore powdery mildew may not be spotted within the first couple of days of it establishing.
+This meta-analysis also provides a effective spray window for mitigating yield losses, given that spray schedules which commenced 'Late' were still significantly effective at mitigating yield loss (P = `signif(PM_mv$pval[5],2)`) 7 - 13 days after the first sign of disease.
+Growers typically don't have the time to inspect their crop regularly for the first sign of powdery mildew and therefore the disease may not be spotted within the first couple of days of it establishing.
 Also weather conditions and logistical issues might prevent growers from getting machinery in the paddock to treat the disease immediately after it is spotted. 
 These issues, and perhaps other on farm duties, might delay a timely application, permitting the disease more time to establish. 
-Knowing a delay of up to two weeks may not lead to yield losses can allow growers to incorporate other integrated pest management options, such as insecticide, with the fungicide spray saving on spray application costs.
+Knowing a delay of up to two weeks may not lead to yield losses, can allow growers to incorporate other integrated pest management options, such as insecticide, with the fungicide spray saving on spray application costs.
 However care should be taken to ensure if a second follow-up fungicide application is necessary, sufficient time should be permitted to schedule the spray and avoid the end of season fungicide withholding periods.
@@
 While certain circumstances may force growers to sow mungbeans late, if the crop is sown too late there is a risk of frost impacting on the yield.
-Regardless in most cases growers are likely to sow earlier in the season, lowering their risk of powdery mildew and reducing the requirements for fungicide applications.
-Despite the significance in the result some discretion for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.
+Regardless in most cases growers are likely to sow mungbeans earlier in the season, lowering their risk of powdery mildew and reducing the requirements for fungicide applications.
+Despite the significance in these results, some discretion for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.
 The PowderyMildewMBM considers these variables, crop growth stage and weather, to assist decision making whether to spray or not to spray [@Diggle].
 
-<!-- This is where I am working right now (Paul) :) :) :) -->
-
-These results suggest that when weather conditions cool and become suitable for powdery mildew growers should scout their every week to two weeks
-
-A recent development, the release of an app for tablet devices, 'PowderyMildewMBM' a decision support system (DSS) tool, increases the ease of preparing a fungicide spray schedule to manage powdery mildew [@Diggle].
-PowderyMildewMBM provides a cost benefit analysis to growers for fungicide spray schedule scenarios.
+PowderyMildewMBM provides a cost-benefit analysis to growers for fungicide spray schedule scenarios.
 The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability that one or two fungicide sprays would protect yields sufficiently to increase the net profit.
-The meta-analysis is limited in scope to the timing of application and therefore we can't validate all the variables available in PowderyMildewMDM. 
-However our results validate the decision of the app developers to not recommend prophylactic fungicide applications. 
+The scope of the meta-analysis is limited to the timing of application and therefore we can't validate all the variables available in PowderyMildewMDM. 
+However our results validate the decision of the app developers not to recommend prophylactic fungicide applications. 
 If the powdery mildew is not observed in the crop the app advises the user to keep monitoring for disease.  
@@
 
-### Fungicide Resistance
+Scouting the crop for powdery mildew might not be necessary during the warmer months of the season. 
+However when weather conditions cool and become suitable for powdery mildew, our results suggest weekly inspections would be ideal to ensure timely fungicide applications if necessary. 
+Scouting at intervals greater than 12-13 days, might risk crop losses if a spray schedule does not commence within the spray window mentioned above.
+More work is needed to understand when 'late' fungicide applications are too late.
+Data from the trials included in this experiment show regardless of crop sowing date, powdery mildew establishes on average in the month of March
 
-Fungicide application costs in Australia are relatively cheap.
-We estimate these costs to be approximately \$20&nbsp;AU per hectare.
-Lucrative returns of up to \$2260&nbsp;AU per hectare over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew when they are unnecessary.
-Excessive use of fungicides are not only costly, but lead to problems such as fungicide resistance.
-*Podosphaera xanthii* is categorised by the Australian Fungicide resistance Action Committee (FRAC) as a 'High risk' candidate to evolve fungicide resistance.
-Prior experiences confirm that the evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with potential fungicide resistance in mind.
+We estimate the costs of applying tebuconazole fungicide at \$4.18 AUD / ha, if fungicide is purchased at \$15 / L [@Simfendorfer2011] and applications cost are $2 per hectare [@QueenslandGovernment2019].
+The meta-analysis estimates yield savings of between `r coef(PM_mv)[3]*1000` kg / ha (Recommended) and `r coef(PM_mv)[4]*1000` kg / ha (RecommendedPlus). 
+These average yield savings would save \$`r (coef(PM_mv)[3]*1000)` AUD / ha for a single application at first sign and `r coef(PM_mv)[4]*1000` AUD / ha if a follow-up application is made.
+Lucrative returns such as these may tempt growers into applying fungicide to control diseases such as powdery mildew when they are unnecessary.
+Excessive use of fungicides are highly likely to lead ongoing problems such as fungicide resistance.
+*Podosphaera xanthii* is categorised by the Australian Fungicide resistance Action Committee (FRAC) as a 'High risk' candidate to evolve fungicide resistance [@FRACrisk2019].
+Evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with potential fungicide resistance in mind.
 Powdery mildew is one such group of fungal pathogens with an extensive track record of rapidly developing fungicide resistance.
@@
 Sulphur is a non-systemic protectant and thus provides an excellent option for rotation to limit the emergence of fungicide resistance.
+<!-- This is where I am working right now (Paul) :) :) :) -->
+
+A recent development, the release of an app for tablet devices, 'PowderyMildewMBM' a decision support system (DSS) tool, increases the ease of preparing a fungicide spray schedule to manage powdery mildew [@Diggle].
 

### 2020-07-16 08_MetaAnalysis_Emerson.Rmd
more explaination

@@
 
+One aspect we would like to consider is how the results of this meta-analysis compares to how the PowderyMildewMBM estimates the effect of fungicide applications on grain yields.
+Below we create a data frame of the mitigation factors for each spray scenario so we can compare them to the outcomes of the meta-analysis.
 ```{r compare2PowderyMildewMDM}
@@
 ```
+To to a better comparison I need to know how the mitigation factor is calculated with the estimated yields

### 2020-07-16 07_Manuscript.Rmd
more edits

@@
 
-It is important to note, the studies included in this meta-analysis were intentionally sown late in the season to ensure infection during the experiment (Figure 1). 
+It is important to note, the studies included in this meta-analysis were intentionally sown late in the season to ensure powdery mildew infection (Figure 1). 
 While certain circumstances may force growers to sow mungbeans late, if the crop is sown too late there is a risk of frost impacting on the yield.
-Regardless in most cases growers are likely to sow mungbeans earlier in the season, lowering their risk of powdery mildew and reducing the requirements for fungicide applications.
+Regardless according to the Australian Mungbean Assocsiation sowing guide [@AMA], mungbeans should not be sown later than January in the Darling Downs, the region where the majority of trials were undertaken.
+If mungbeans are planted according to this guide the crops are at a lower risk of powdery mildew, reducing the requirement for fungicide applications.<!-- This is where I am working right now (Paul) :) :) :) -->
 Despite the significance in these results, some discretion for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.
@@
 Sulphur is a non-systemic protectant and thus provides an excellent option for rotation to limit the emergence of fungicide resistance.
-<!-- This is where I am working right now (Paul) :) :) :) -->
 

### 2020-07-17 07_Manuscript.Rmd
More writing and edits, adding some more references

@@
 
-Mungbean was first brought to Australia in the 1930s for use as a forage or green manure crop and it was only as recent as the 1960s until that mungbean was grown commercially [@aboutAMA].
+Mungbean was first brought to Australia in the 1930s for use as a forage or green manure crop and it was only as recent as the 1960s until that mungbean was grown commercially [@aboutAMA, @Chuahan2018].
 At the end of the 1980s between 3 - 10 thousand hectares were being harvested for dried beans, of which mungbean is categorised by the FAO statistics data repository [@FAOSTAT].
@@
 In 2019, approximately 90&nbsp;% of Australian mungbean was grown for export with lucrative returns of up to \$1300&nbsp;AU a tonne [@QueenslandGovernment2019].
-Mungbean potentially yields up to 3 tonnes per hectare, but due to high variability in yields between seasons and locations, the average Australian farm still yields less than 1 tonne per hectare [@Chauhan2018].
+Mungbean potentially yields up to 3 tonnes per hectare [@ThomasRobert2004], but due to high variability in yields between seasons and locations, the average Australian farm still yields less than 1 tonne per hectare [@Chauhan2018].
 
@@
 While the pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified. 
-<!-- Perhaps some more information here about the biology, infection time, latent period, how long in a cycle -PM-->
+The disease lifecycle can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia which disseminate to new infection sites [@Sparks2017].
+Weather conditions that favour the rapid development of the disease are cool temperatures between 22&deg; and 26&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
 
-Weather conditions that favour the development of the disease are cool temperatures between 22&deg; and 26&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
-
-Because of this, planting date is an effective strategy for preventing the development of powdery mildew in mungbean.
+Due to the requirement for cooler temperatures for infection, planting date is an effective strategy for preventing the development of powdery mildew in mungbean [@AMAplanting].
 In southern Queensland and northern New South Wales, sowing dates between late spring (November) and mid-summer (January) are advised to avoid the conducive cooler autumn temperatures, which normally commence in March.
@@
 Evidence of this is shown by the 2016 field trials with the moderately susceptible cultivar, Jade-AU, where yield losses of up to 32.7 % were recorded [@SueThompson2016]. 
-Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013].
+Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013], however no evidence for how they compare to Australian varietal resistance could be found.
 Additional strategies to cultivar choice, such as fungicide treatments, are necessary to limit yield loss when conditions for the disease are conducive.
@@
 Past field trials in eastern Australia have tested a range of fungicide active ingredients while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
-Early trials showed that for fungicide applications to protect yield, a single fungicide application at first sign of the disease with another follow-up application two weeks later if necessary was the most effective [@SueThompson2016; @Sparks2017].
+Early trials showed that for fungicide applications to protect yield, a single fungicide application at first sign of the disease with another follow-up application two weeks later, if necessary, was the most effective [@SueThompson2016; @Sparks2017].
 However due to the variability in the results between seasons and experiments few of these studies produced a clear result based on a statistical analysis. 
@@
 
-The collection of experiments mentioned above and other unpublished trials proved an excellent opportunity for a meta-analysis.
+<!--Some of the fungicides tested for controlling powdery mildew in mungbean have been registered with the APVMA [@APVMA; @Kelly2017a;  insert all published trials here -->.
+
+The collection of experiments mentioned above and other unpublished trials present an excellent opportunity for a meta-analysis.
 Meta-analyses are statistical tools which can analyse a collection of experiments, which have a similar aim, and produces a more accurate estimate of the true effect being measured.
@@
 The aim of this meta-analysis was to determine, from a collection of unpublished studies, what spray management scenario provides the greatest yield protection from powdery mildew in Australian mungbean.
-
-<!--Some of the fungicides tested for controlling powdery mildew in mungbean have been registered with the APVMA [@APVMA; @Kelly2017a;  insert all published trials here -->.
 
@@
 Knowing a delay of up to two weeks may not lead to yield losses, can allow growers to incorporate other integrated pest management options, such as insecticide, with the fungicide spray saving on spray application costs.
-However care should be taken to ensure if a second follow-up fungicide application is necessary, sufficient time should be permitted to schedule the spray and avoid the end of season fungicide withholding periods.
+However attention should be made to the label requirements when first planning a spray schedule.
+Second applications, if they are needed, should be applied at least 10 - 14 days after the first application and not within 21 days of harvest [@APVMAcustodia].
 
@@
 While certain circumstances may force growers to sow mungbeans late, if the crop is sown too late there is a risk of frost impacting on the yield.
-Regardless according to the Australian Mungbean Assocsiation sowing guide [@AMA], mungbeans should not be sown later than January in the Darling Downs, the region where the majority of trials were undertaken.
+Regardless, according to the Australian Mungbean Association sowing guide [@AMAplanting], mungbeans should not be sown later than January in the Darling Downs, the region where the majority of trials were undertaken.
 If mungbeans are planted according to this guide the crops are at a lower risk of powdery mildew, reducing the requirement for fungicide applications.<!-- This is where I am working right now (Paul) :) :) :) -->

### 2020-07-17 07_Manuscript.Rmd
Add comment on text to be moved to acknowledgements

@@
 The majority of the trials were undertaken by Professor Malcolm Riley and Dr Sue Thompson with the Queensland Department of Agriculture, Fisheries and Forestry (DAF).
+<!-- This should not be in the paper, they can be acknowledged at the end -->
 Trials undertaken in the 2013 season were conducted by the Northern Growers Alliance (NGA) [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013].
-<!-- should check, Sue and Mal moved to USQ in 2015 I think.
-Therefore the trials probably started with USQ earlier --> The most recent trials starting from 2015 were undertaken by the University of Southern Queensland (USQ) with the assistance of Queensland DAF from 2015 to 2019.
+<!-- should check, Sue and Mal moved to USQ in 2015 I think. Therefore the trials probably started with USQ earlier --> 
+The most recent trials starting from 2015 were undertaken by the University of Southern Queensland (USQ) with the assistance of Queensland DAF from 2015 to 2019. 
 Trial data were in different formats with varying levels of information.

### 2020-07-17 07_Manuscript.Rmd
Correct references and remove redundant code

--- 2020-07-17 07_Manuscript.Rmd
@@
 load(file = here("cache/PreliminaryData.Rdata"))
-PM_MB_dat%>% 
-   filter(fungicide_ai == "tebuconazole")
 ```
@@
 
-Mungbean was first brought to Australia in the 1930s for use as a forage or green manure crop and it was only as recent as the 1960s until that mungbean was grown commercially [@aboutAMA, @Chuahan2018].
+Mungbean was first brought to Australia in the 1930s for use as a forage or green manure crop and it was only as recent as the 1960s until that mungbean was grown commercially [@aboutAMA, @Chauhan2018].
 At the end of the 1980s between 3 - 10 thousand hectares were being harvested for dried beans, of which mungbean is categorised by the FAO statistics data repository [@FAOSTAT].

### 2020-07-17 07_Manuscript.Rmd
small edits

--- 2020-07-17 07_Manuscript.Rmd
@@
 The data for this study were obtained from through personal correspondence with colleagues and collaborating institutions.
-The majority of the trials were undertaken by Professor Malcolm Riley and Dr Sue Thompson with the Queensland Department of Agriculture, Fisheries and Forestry (DAF). 
 Trials undertaken in the 2013 season were conducted by the Northern Growers Alliance (NGA) [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013].
-<!-- should check, Sue and Mal moved to USQ in 2015 I think.
-Therefore the trials probably started with USQ earlier --> The most recent trials starting from 2015 were undertaken by the University of Southern Queensland (USQ) with the assistance of Queensland DAF from 2015 to 2019.
+<!-- should check, Sue and Mal moved to USQ in 2015 I think. Therefore the trials probably started with USQ earlier --> 
+The most recent trials starting from 2015 were undertaken by the University of Southern Queensland (USQ) with the assistance of Queensland DAF from 2015 to 2019. 
 Trial data were in different formats with varying levels of information.
-Some trial data reported means of each treatment, with all but one study reporting some form of variance along with the mean.
-
+Some trials we obtained the raw data others the reported means of each treatment, with all but one study reporting some form of variance along with the mean. 
 Twenty six trials in total were collated.
 
-Details of trial data are presented within a research compendium which was prepared to supplement this publication [<!-- DOI to reference to compendium -->].
+To ensure the correct question was asked of the analysis the data needed to conform to a strict criteria. 
 The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the Grains Research and Development (GRDC) northern grains regions of eastern Australia, which grows the majority of Australia's summer crops.
@@
 Subsequently the 26 trials were reduced to 16 using the same fungicide doses (Table 1). 
+Details of trial data are presented within a research compendium which was prepared to supplement this publication [<!-- DOI to reference to compendium -->].
 With only a small number of trials, and to increase the replication, we made no distinction between the tebuconazole and propiconazole in the analysis. 
-
 All trials included in this analysis were randomised complete block designs and not previously published in peer-reviewed literature.
@@
 While the main aim of all the trials collected for this study were to assess the efficacy of fungicide for control of powdery mildew, some trials tested additional variables in the experimental design.
-
 These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications and cultivar.
@@
 
+### Future work
+
 A recent development, the release of an app for tablet devices, 'PowderyMildewMBM' a decision support system (DSS) tool, increases the ease of preparing a fungicide spray schedule to manage powdery mildew [@Diggle].
 
+# Acknowldgments
+The authors wish to acknowledge the work done by Professor Malcolm Riley and Dr Sue Thompson whom undertook many of the trials incorporated in this analysis from 2004 - 2015. 
+The Queensland Department of Agriculture, Fisheries and Forestry (DAF). 
+The National Growers association and Lawrie Price for contributing data.
+The Grains Research and Development Corporation who funded this research.
+
 # References

### 2020-07-17 07_Manuscript.Rmd
Copy edits to manuscript and fixes for formatting

--- 2020-07-17 07_Manuscript.Rmd
@@
 
-Considering the recent launch in 2019 of the decision support system (DSS) PowderyMildewMDM [@Diggle], which provides a cost benefit analysis to assists growers in their decision 'if' and 'when' apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
+Considering the recent launch in 2019 of the decision support system (DSS) PowderyMildewMBM [@Diggle], which provides a cost benefit analysis to assists growers in their decision 'if' and 'when' apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
 The aim of this meta-analysis was to determine, from a collection of unpublished studies, what spray management scenario provides the greatest yield protection from powdery mildew in Australian mungbean.
@@
 
-This meta-analysis also provides a effective spray window for mitigating yield losses, given that spray schedules which commenced 'Late' were still significantly effective at mitigating yield loss (P = `signif(PM_mv$pval[5],2)`) 7 - 13 days after the first sign of disease.
-Growers typically don't have the time to inspect their crop regularly for the first sign of powdery mildew and therefore the disease may not be spotted within the first couple of days of it establishing.
-Also weather conditions and logistical issues might prevent growers from getting machinery in the paddock to treat the disease immediately after it is spotted. 
+This meta-analysis also provides a effective spray window for mitigating yield losses, given that spray schedules which commenced `Late` were still significantly effective at mitigating yield loss (P = `r signif(PM_mv$pval[5],2)`) 7 - 13 days after the first sign of disease.
+Growers typically do not have the time to inspect their crop regularly for the first sign of powdery mildew and therefore the disease may not be spotted within the first couple of days of it establishing.
+Also, weather conditions and logistical issues might prevent growers from getting machinery in the paddock to treat the disease immediately after it is spotted. 
 These issues, and perhaps other on farm duties, might delay a timely application, permitting the disease more time to establish. 
@@
 The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability that one or two fungicide sprays would protect yields sufficiently to increase the net profit.
-The scope of the meta-analysis is limited to the timing of application and therefore we can't validate all the variables available in PowderyMildewMDM. 
+The scope of the meta-analysis is limited to the timing of application and therefore we can't validate all the variables available in PowderyMildewMBM. 
 However our results validate the decision of the app developers not to recommend prophylactic fungicide applications. 
@@
 However when weather conditions cool and become suitable for powdery mildew, our results suggest weekly inspections would be ideal to ensure timely fungicide applications if necessary. 
-Scouting at intervals greater than 12-13 days, might risk crop losses if a spray schedule does not commence within the spray window mentioned above.
+Scouting at intervals greater than 12 - 13 days, might risk crop losses if a spray schedule does not commence within the spray window mentioned above.
 More work is needed to understand when 'late' fungicide applications are too late.

### 2020-07-17 07_Manuscript.Rmd

@@
 The data for this study were obtained from through personal correspondence with colleagues and collaborating institutions.
-The majority of the trials were undertaken by Professor Malcolm Riley and Dr Sue Thompson with the Queensland Department of Agriculture, Fisheries and Forestry (DAF).
-<!-- This should not be in the paper, they can be acknowledged at the end -->
 Trials undertaken in the 2013 season were conducted by the Northern Growers Alliance (NGA) [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013].
@@
 Trial data were in different formats with varying levels of information.
-Some trial data reported means of each treatment, with all but one study reporting some form of variance along with the mean.
-
+Some trials we obtained the raw data others the reported means of each treatment, with all but one study reporting some form of variance along with the mean. 
 Twenty six trials in total were collated.
 
-Details of trial data are presented within a research compendium which was prepared to supplement this publication [<!-- DOI to reference to compendium -->].
+To ensure the correct question was asked of the analysis the data needed to conform to a strict criteria. 
 The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the Grains Research and Development (GRDC) northern grains regions of eastern Australia, which grows the majority of Australia's summer crops.

### 2020-07-20 07_Manuscript.Rmd
more edits and hardcoded results

@@
 load(file = here("cache/PreliminaryData.Rdata"))
+source(here("R/reportP.R"))
 ```
@@
 The current advice provided to growers for when to commence fungicide applications for control of powdery mildew, is to spray at the first sign of the disease then if necessary a follow-up spray two weeks later [@SueThompson2016; @Sparks2017].
-This meta-analysis confirms that advice, by showing that applying the first fungicide application, within three days of first sign will significantly mitigate yield loss from powdery mildew ($Recommended$, P = `r signif(PM_mv$pval[3],2)`).
-In addition, spray schedules which commenced 'late', up to 13 days after first sign of the disease were still effective at mitigating yield loss ($Late$, P =  `r signif(PM_mv$pval[5],2)`).
-Spray schedules which included follow-up fungicide applications were on average more effective at reducing yield loss due to powdery mildew, which again follows the advice given by Thompson et.
-al [@SueThompson2016].
+This meta-analysis confirms that advice, by showing that applying the first fungicide application, within three days of first sign will significantly mitigate yield loss from powdery mildew by between `r round(PM_mv$ci.lb[3],5)*1000` to `r round(PM_mv$ci.ub[3],5)*1000` kg / ha ($Recommended$, `r reportP(PM_mv$pval[3])`).
+In addition, spray schedules which commenced 'late', up to 13 days after first sign of the disease were still effective at mitigating yield loss by  `r round(PM_mv$ci.lb[5],5)*1000` to `r round(PM_mv$ci.ub[5],5)*1000` kg / ha ($Late$,`r reportP(PM_mv$pval[5])`).
+Spray schedules which included follow-up fungicide applications were on average more effective at reducing yield loss due to powdery mildew by; 
+`r round(PM_mv$ci.lb[4],5)*1000` to `r round(PM_mv$ci.ub[4],5)*1000` kg / ha in the $RecommendedPlus$ treatments (`r reportP(PM_mv$pval[4])`) and
+`r round(PM_mv$ci.lb[6],5)*1000` to `r round(PM_mv$ci.ub[6],5)*1000` kg / ha in the $LatePlus$ treatments (`r reportP(PM_mv$pval[6])`) (Figure 1)
+which again follows the advice given by Thompson et. al [@SueThompson2016].
 This meta-analysis adds certainty to the advice which is currently given to growers, especially around any uncertainty that Early sprays might be effective at suppressing the disease. 
-We show here that Early fungicide applications, which were made prior to any sign of the disease, were not effective at mitigating yield loss.
+We show here Early fungicide applications, which were made prior to any sign of the disease, were not effective at mitigating yield loss.
 
-This meta-analysis also provides a effective spray window for mitigating yield losses, given that spray schedules which commenced `Late` were still significantly effective at mitigating yield loss (P = `r signif(PM_mv$pval[5],2)`) 7 - 13 days after the first sign of disease.
+This meta-analysis also provides a effective spray window for fungicide applications, given that spray schedules which commenced 'late' were still significantly effective at mitigating yield loss ($Late$ `r reportP(PM_mv$pval[5])`) 7 - 13 days after the first sign of disease.
 Growers typically do not have the time to inspect their crop regularly for the first sign of powdery mildew and therefore the disease may not be spotted within the first couple of days of it establishing.
@@
 Second applications, if they are needed, should be applied at least 10 - 14 days after the first application and not within 21 days of harvest [@APVMAcustodia].
+If time permitted a second spray after the first 'late' application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(T3$estimates[10], 4)*1000` kg / ha, when compared to the $Late$, single spray treatment `r reportP(T3$pval[10]`).
 
-It is important to note, the studies included in this meta-analysis were intentionally sown late in the season to ensure powdery mildew infection (Figure 1). 
-While certain circumstances may force growers to sow mungbeans late, if the crop is sown too late there is a risk of frost impacting on the yield.
+It is important to note, the studies included in this meta-analysis may not reflect a 'normal' mungbean season. 
+All the included experiments were intentionally sown late in the season to ensure powdery mildew infection (Figure 1). 
+While certain circumstances may force growers to sow mungbeans late, many may decide to fallow their fields instead of risking an early frost damaging the crop and yields.
 Regardless, according to the Australian Mungbean Association sowing guide [@AMAplanting], mungbeans should not be sown later than January in the Darling Downs, the region where the majority of trials were undertaken.
-If mungbeans are planted according to this guide the crops are at a lower risk of powdery mildew, reducing the requirement for fungicide applications.<!-- This is where I am working right now (Paul) :) :) :) -->
+If the planting guide is adhered to the mungbean would be at a lower risk of powdery mildew, reducing the requirement for fungicide applications.<!-- This is where I am working right now (Paul) :) :) :) -->
 Despite the significance in these results, some discretion for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.

### 2020-07-20 R/reportP.R
Function to assist reporting correctly formatted P values when rendered in Rmarkdown

@@ -1,0 +1,7 @@
+reportP <- function(p){
+   if(p < 0.0001){
+      return("P < 0.0001")
+   }else{
+      return(paste("P =", format(round(p, digits =  4), scientific = FALSE)))
+   }
+}

### 2020-07-21 03_Prep_data.Rmd
Save median AUDPC so it can be retrieved in the manuscript
Added an inspection of data on the efficacy of fungicide when fungicide applications are late

@@
 
+write.csv(median_AUDPC, here("cache/median_AUDPC_C.csv"), row.names = FALSE)
+
 sort(Trial_Dpress$AUDPC_C)
@@
 ```
+
+### Mungbeans age and yield saved
+The time at which powdery mildew infects in the seasons and the age of the plant might affect the AUDPC and the loss in yield.
+Lets have a look at the age of each trial when each powdery mildew infected it.
+We will use the difference between `planting_date` and `first_sign_disease` as a proxy for crop maturity.
+```{r age_andYield}
+dat1 <- slimmer_PM_dat %>%
+   mutate(days2PM = first_sign_disease - planting_date)%>%
+   arrange(desc(days2PM))%>%
+   select(trial_ref, year, location,spray_management, days2PM,grain_yield.t.ha, 
+          yield_gain, prop_yield_gain,  AUDPC_m,D_pres,PM_final_severity)
+dat1
+```
+From these trials I am most interested in the experiments that directly compare `Recommended` with `Recommended_P_plus` and/or `Late` with `Late_plus`. 
+Therefore I will not inspect, `AM1304` (Marys Mount).
+
+We can see that the crops which were likely the most mature, did not show large yield gains, in particular:
+   * Hermitage 2019  
+   * Premer  
+   * Goolhi  
+   * Millmerran
+
+Lets look at this in a quick box plot. 
+We will only look at trials where powdery mildew set in at flowering which is approximately 60 days after planting.
+```{r ageBoxPlot}
+dat1 %>%
+   filter(days2PM >= 60) %>%
+   filter(spray_management != "control" &
+             trial_ref != "AM1304" )%>%
+   group_by(trial_ref,spray_management)%>%
+   ggplot(aes(x= spray_management, y = yield_gain, colour = trial_ref))+
+   geom_boxplot()+
+   geom_hline(yintercept = 0)
+```
+We can see in these experiments five experiments there is clearly no benefit to applying a second fungicide application.
+
+For completeness lets test this with powdery mildew infection commencing 40 - 60 days after planting, instead of greater than 60.
+
+```{r PM40_2_59_days}
+dat1 %>%
+   filter(days2PM < 60 &
+             days2PM >= 40) %>%
+   filter(spray_management != "control")%>%
+   group_by(trial_ref,spray_management)%>%
+   ggplot(aes(x= spray_management, y = yield_gain, colour = trial_ref))+
+   geom_boxplot()+
+   geom_hline(yintercept = 0)
+```
+We can see here all four experiments benefited, on average, from more than one spray.
+
+Lets estimate the age of the crop based on crop maturity observations, we will use the `PM_MB_means` which include some observations of crop maturity.
+
+```{r whatAreTheAges}
+dat2 <- PM_MB_means%>%
+   mutate(flower = lubridate::ymd(flowering_date) - lubridate::ymd(planting_date),
+          pod = lubridate::ymd(pod_fill_date) - lubridate::ymd(planting_date),
+          late_pod = lubridate::ymd(mid_late_pod_fill) - lubridate::ymd(planting_date))%>%
+   select(location, year, flower, pod, late_pod)%>%
+   distinct()%>%
+   arrange(desc(flower))
+
+index1 <- apply(dat2, 1 , function(X) !all(is.na(X[c("flower", "pod", "late_pod")])))
+
+dat2[index1,]   
+as.double(mean(dat2[index1,"flower"], na.rm = TRUE))
+as.double(mean(dat2[index1,"pod"], na.rm = TRUE))
+as.double(mean(dat2[index1,"late_pod"], na.rm = TRUE))
+```
+
+We can see that flowering and podding can be variable, and depends on the cumulative degree days <!-- reference here to APSIM model-->. 
+however on average flowering starts `r as.double(mean(dat2[index1,"flower"], na.rm = TRUE))` days after sowing, podding starts `r as.double(mean(dat2[index1,"pod"], na.rm = TRUE))`, and late podding `r as.double(mean(dat2[index1,"late_pod"], na.rm = TRUE))`
+
+```{r}
+#filter(location == "Premer" | location == "Millmerran")%>%
+   group_by(trial, trial_ref,location,year)%>%
+   summarise(latent = mean(days2PM))%>%
+   pull(latent)
+
+sum(temp2 < 60)/length(temp2)
+
+dat2[,c("flower", "pod", "black_pod")]
+
+mean(   
+-0.030637255,
+-0.058210784)
+
+mean(
+-0.076933551,
+-0.087826797)
+```

### 2020-07-21 02_Preliminary_analysis.Rmd
Add missing pipe

@@
           Element == "Area harvested")%>%
-   select(Year,Value)
+   select(Year,Value)%>%
    ggplot(aes(y = Value, x = Year))+

### 2020-07-21 07_Manuscript.Rmd
More edits and words

@@
 It is important to note, the studies included in this meta-analysis may not reflect a 'normal' mungbean season. 
-All the included experiments were intentionally sown late in the season to ensure powdery mildew infection (Figure 1). 
-While certain circumstances may force growers to sow mungbeans late, many may decide to fallow their fields instead of risking an early frost damaging the crop and yields.
+All the included experiments were intentionally sown late in the season, from January through to as late as early March, to ensure powdery mildew infection (Figure 1). 
+While certain circumstances may force growers to sow mungbeans late, many may decide to fallow their fields instead of risking a powdery mildew epidemics and an early frost damaging the crop and yields.
 Regardless, according to the Australian Mungbean Association sowing guide [@AMAplanting], mungbeans should not be sown later than January in the Darling Downs, the region where the majority of trials were undertaken.
-If the planting guide is adhered to the mungbean would be at a lower risk of powdery mildew, reducing the requirement for fungicide applications.<!-- This is where I am working right now (Paul) :) :) :) -->
+If the planting guide is adhered to the mungbean would be at a lower risk of powdery mildew, reducing the requirement for fungicide applications. 
+An example of this are the 2013 trials in Premer (AM1303) and Millmerran (BB1305) where the first sign of powdery mildew was sighted 60 and 62 days after planting, when the crop was flowering. 
+Both trials reported a significant difference in powdery mildew severity between the fungicide treatments, however neither trial showed a significant difference in yield [@Millmerran2013, @premer2013].
+The average yield saved for single $Recommended$ fungicide applications were 28.59 and 0.61 kg / ha for Premer and Millmerran respectively. 
+However the average yield saved from the treatments categorised $RecommendedPlus$ were -76.93 and -30.64 kg / ha for Premer and Millmerran respectively.
+<!-- This is where I am working right now (Paul) :) :) :) -->
 Despite the significance in these results, some discretion for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.
-The PowderyMildewMBM considers these variables, crop growth stage and weather, to assist decision making whether to spray or not to spray [@Diggle].
+The PowderyMildewMBM considers crop growth stage and weather, to assist decision making whether to spray or not to spray [@Diggle].
 
-PowderyMildewMBM provides a cost-benefit analysis to growers for fungicide spray schedule scenarios.
+PowderyMildewMBM also provides a cost-benefit analysis to growers for fungicide spray schedule scenarios.
 The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability that one or two fungicide sprays would protect yields sufficiently to increase the net profit.
-The scope of the meta-analysis is limited to the timing of application and therefore we can't validate all the variables available in PowderyMildewMBM. 
+The scope of the meta-analysis is limited to the timing of fungicide application and therefore we can't validate all the variables available in PowderyMildewMBM. 
 However our results validate the decision of the app developers not to recommend prophylactic fungicide applications. 

### 2020-07-21 R/slimming_PM_dat.R
Added planting date variable for age of crop when powdery mildew is first seen calculations

@@ -19,6 +19,7 @@ slim_PM_dat <- data.frame(
    location = as.character(PM_MB_Mtemp$location),
    row_spacing = as.double(PM_MB_Mtemp$row_spacing),
    n = as.integer(PM_MB_Mtemp$replicates),
+   planting_date = as.Date(PM_MB_Mtemp$planting_date),
    first_sign_disease = as.Date(PM_MB_Mtemp$first_sign_disease, format = "%Y-%m-%d"),
    fungicide_ai = as.character(PM_MB_Mtemp$fungicide_ai),
    fungicide_application_1 = as.Date(PM_MB_Mtemp$fungicide_application_1, format = "%Y-%m-%d"),

### 2020-07-21 07_Manuscript.Rmd
Discussion - More words and edits

@@
 If the planting guide is adhered to the mungbean would be at a lower risk of powdery mildew, reducing the requirement for fungicide applications. 
-An example of this are the 2013 trials in Premer (AM1303) and Millmerran (BB1305) where the first sign of powdery mildew was sighted 60 and 62 days after planting, when the crop was flowering. 
-Both trials reported a significant difference in powdery mildew severity between the fungicide treatments, however neither trial showed a significant difference in yield [@Millmerran2013, @premer2013].
-The average yield saved for single $Recommended$ fungicide applications were 28.59 and 0.61 kg / ha for Premer and Millmerran respectively. 
-However the average yield saved from the treatments categorised $RecommendedPlus$ were -76.93 and -30.64 kg / ha for Premer and Millmerran respectively.
-<!-- This is where I am working right now (Paul) :) :) :) -->
-Despite the significance in these results, some discretion for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.
+An example of this is if we inspect the six trials which powdery mildew manifested 60 days or greater after planting (Trial references: AM1304, mung1819/01, mung1011/01, AM1303, AM1305 and BB1305). 
+Of these trials, four directly compared single $Recommended$ fungicide applications and $RecommendedPlus$ (AM1303, AM1305, BB1305 and mung1819/01), two of which (AM1305 and mung1819/01) produced at least one treatment $RecommendedPlus$ treatment with a higher grain yield the $Recommended$ treatments.
+However, neither AM1305 or mung1819/01 neither contained $Recommended$ or $RecommendedPlus$ treatments with higher mean yields than the no-spray control.
+This indicating there is likely no benefit to applying two fungicide applications when the disease manifests later than 60 days into the growing season. 
+Further the trials undertaken in 2013, such as Premer (AM1303), Goolhi (AM1305) Marys Mount (AM1304) and Millmerran (BB1305) reported a significant difference in powdery mildew severity between the fungicide treatments, however neither trial showed a significant difference in grain yield between treatments [@Millmerran2013, @premer2013, @Marysmount2013, @goolhi2013].
+Therefore, discretion is still required for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.
 The PowderyMildewMBM considers crop growth stage and weather, to assist decision making whether to spray or not to spray [@Diggle].
@@
 Scouting the crop for powdery mildew might not be necessary during the warmer months of the season. 
-However when weather conditions cool and become suitable for powdery mildew, our results suggest weekly inspections would be ideal to ensure timely fungicide applications if necessary. 
-Scouting at intervals greater than 12 - 13 days, might risk crop losses if a spray schedule does not commence within the spray window mentioned above.
+Data from the trials included in this experiment show regardless of crop sowing date, powdery mildew establishes on average in the month of March which marks the beginning of Autumn (Figure 1).
+Considering the results of the meta-analysis, weekly inspections would be ideal to ensure timely fungicide applications if necessary. 
+Scouting at intervals greater than 12 - 13 days, might risk crop losses if a spray schedule does not commence within aforementioned the spray window.
 More work is needed to understand when 'late' fungicide applications are too late.
-Data from the trials included in this experiment show regardless of crop sowing date, powdery mildew establishes on average in the month of March
 
 We estimate the costs of applying tebuconazole fungicide at \$4.18 AUD / ha, if fungicide is purchased at \$15 / L [@Simfendorfer2011] and applications cost are $2 per hectare [@QueenslandGovernment2019].
-The meta-analysis estimates yield savings of between `r coef(PM_mv)[3]*1000` kg / ha (Recommended) and `r coef(PM_mv)[4]*1000` kg / ha (RecommendedPlus). 
+The meta-analysis estimates average yield savings of between `r coef(PM_mv)[3]*1000` kg / ha ($Recommended$) and `r coef(PM_mv)[4]*1000` kg / ha ($RecommendedPlus$). 
 These average yield savings would save \$`r (coef(PM_mv)[3]*1000)` AUD / ha for a single application at first sign and `r coef(PM_mv)[4]*1000` AUD / ha if a follow-up application is made.
@@
 Powdery mildew is one such group of fungal pathogens with an extensive track record of rapidly developing fungicide resistance.
-In cucurbits, it evolved resistance to benzimidazole within three years of its registration [@Peterson1973] and has evolved resistance to numerous fungicide classes, such as benzimidazoles, demethylation inhibitors, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines since [@Mcgrath2001].
+In cucurbits, *P.
+xanthii* evolved resistance to benzimidazole within three years of its registration [@Peterson1973] and has evolved resistance to numerous fungicide classes, such as benzimidazoles, demethylation inhibitors, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines since [@Mcgrath2001].
 In cereal crops *Blumeria graminis* showed reduced sensitivity to strobilurins in 1998, two years after the fungicides began being used in Europe [@Chin2001].
-
-To extend the time that a fungicide remains effective against the target pathogen, strategic use of the fungicide must be considered.
-Excessive fungicide sprays by a single active increase the selection pressure on the pathogen to evolve resistance [@Brent2007]. 
-If any strains of the pathogen with resistance to the fungicide are present in a population regular use of the fungicide will increase it's proportion in the population. 
-Managing the disease with fungicides for the highest economic return is likely not to require eradication of the causal pathogen. 
-Integrated pest management practices focus on using only the required number of chemical control to protect the economic return. 
-These strategies permit the presence of yield limiting diseases and pests if intervening would cost more than the economic return of protection.
-
-The timing of fungicide sprays are critical for their efficacy and for limiting fungicide resistant strains from emerging. 
-Fungicide applications made too early would increase costs without providing any benefit to yields. 
-Applications which are made too late allow the disease to establish and damage the crop productivity, while making subsequent sprays difficult to reduce the disease incidence.
 
@@
 Sulphur is a non-systemic protectant and thus provides an excellent option for rotation to limit the emergence of fungicide resistance.
+
+To extend the time that a fungicide remains effective against the target pathogen, strategic use of the fungicide must be considered.
+Excessive fungicide sprays by a single active increase the selection pressure on the pathogen to evolve resistance [@Brent2007]. 
+If any strains of the pathogen with resistance to the fungicide are present in a population regular use of the fungicide will increase it's proportion in the population. 
+Therefore, managing the disease with fungicides for the highest economic return is likely not to require eradication of the causal pathogen. 
+Integrated pest management practices focus on using only the required number of chemical control to protect the economic return. 
+These strategies permit the presence of yield limiting diseases and pests if intervening would cost more than the economic return of protection.
 

### 2020-07-22 07_Manuscript.Rmd
More writing - Discussion - possible effect of fungicide on nitrogen fixing symbionts - Future work section

@@
 # Manuscript
-
+<!-- need to ensure the format of this manuscript adheres to the MDPI Agronomy style guide -->
 ## Introduction
@@
 
+Advising use of fungicide for disease control to protect yields should also consider the harm it may do to symbiotic relationships with microbiota. 
+While some nitrogen fixing symbiont show a level of tolerance to fungicides, all are detrimentally affected by increasing concentrations of fungicide leading to lower nodulation and biomass accumulation [@Ahemad2011, @Shahid2019].
+Therefore if a grower is relying on rhizobia inoculation to help meet the crops nitrogen requirements, untimely and excessive applications of a systemic fungicide for powdery mildew control may actually reduce yields.
+
 ### Future work
+This meta-analysis provides a ballast for the direction of future powdery mildew research in mungbean. 
+However it does not provide enough certainty to when late fungicide applications would be too late to protect yield losses due to the disease. 
+Future experiments should take note of physiological maturity of the crop throughout the season so 'crop age' might be considered as a covariate in future analyses.
+In cases where mungbean physiological maturity may not have been recorded the APSIM mungbean module [@RobertsonAPSIMlegume2002].
 
-A recent development, the release of an app for tablet devices, 'PowderyMildewMBM' a decision support system (DSS) tool, increases the ease of preparing a fungicide spray schedule to manage powdery mildew [@Diggle].
+Early detection of powdery mildew is vital for an effective fungicidal control response.
+Data from the collection of 26 studies in the Northern Grain region, indicate powdery mildew is likely to manifest on crops in the first month of autumn. 
+This data together with additional observations may permit models to predict the likely onset of the disease given weather parameters, providing an early warning system for growers to scout their crop for signs of powdery mildew.
+However an improved understanding of the pathogen biology is also needed to ensure models are as accurate as they can be.
+The population genetics, epidemiology and alternate hosts are all poorly understood in this host-pathogen relationship.
+The recent discovery of a second powdery mildew species which infects mungbean highlights the paucity of knowledge on this disease.
 
-# Acknowldgments
+## Acknowledgments
 The authors wish to acknowledge the work done by Professor Malcolm Riley and Dr Sue Thompson whom undertook many of the trials incorporated in this analysis from 2004 - 2015. 
@@
 
-# References
+## References

### 2020-07-22 04_MetaAnalysis.Rmd
Updated Emersons meta-analysis file (08) with changes made in the original (04)file

@@
 ```
-```{r}
-(PM_mv$b - PM_mv$ci.ub) / PM_mv$se
-```
-
-In this result we can see that the `Early` treatment is not significantly different from zero, which in this case is the mean of the no spray `control`.
-However the other treatments are significantly different from zero.
-The $Q_M$ [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, shows the moderators significantly influence the model ($Q_M = 26.22, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
-The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 568.31, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
-
-Lets look at the trial variability in this model with a forest plot
-```{r forestP, fig.height= 40, fig.width=17}
-source(here("R/change_labels.R"))
-source(here("R/forest_rows.R"))
-
-### Sort and arrange data-frame occordingly and produce a index vector to inform the order of each "Trial" on the plot
-index1 <- dat1 %>%
-   mutate(ID = seq_along(trial_ref)) %>%
-   mutate(spray_management = 
-             factor(spray_management, 
-                    levels = c("Early","Late","Recommended",
-                    "Recommended_plus","Late_plus"))) %>%
-   arrange(desc(spray_management), location, desc(grain_MD)) %>%
-   mutate(ID2 = order(ID))%>%
-   pull(ID2)
-
-### Use forest rows function to return a list of where to place on the plot: sub-titles, each trial row, and summary prediction for each treatment.
-### this list can be used below to reference where to plot each variable
-rows1 <- forest_rows(head_row = 156, 
-                     ord_var = dat1$spray_management, 
-                     index = index1, 
-                     gap = 5, 
-                     row_offset = -2)
-
-### A data-frame of meta-model coefficients used to produce the summary polygons for each treatment
-polys <- data.frame(ref = change_labels(names(coef(PM_mv))),
-                    x = coef(PM_mv),
-                    ci.lb = PM_mv$ci.lb,
-                    ci.ub = PM_mv$ci.ub)[c(1,4,2,3,5),]
-polys$rows <- rows1$pred_row - 1.5
-
-forest1  <- metafor::forest(PM_mv, cex = 1.15 , width = 5,
-                #order = "fit",
-                rows = rows1$trows-1.5,
-                ilab = cbind(dat1$year, 
-                             dat1$row_spacing, dat1$host_genotype, dat1$dose),
-                ilab.xpos = c(-2.35,-2.1,-1.8,-1.4),
-                slab = NA, 
-                xlim = c(-2.9, 2.2),
-                ylim = c(18,157),
-                xlab = "Grain yield mean difference",
-                addfit = FALSE,
-                efac = c(0.2,0.15,0.2),
-                at = seq(-1,1.5, 0.5))
-
-### code which puts lines and annotations on the plot, its a bit long...
-source(here("R/add_annotations.R"))
-
-```
 
@@
 The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis.
+This effectively shows the heterogeneity between experiments for these partivular treatments.
+
 The second table is in two parts (left and right). 

### 2020-07-22 08_MetaAnalysis_Emerson.Rmd
Updated Emersons meta-analysis file (08) with changes made in the original (04)file

@@
 theme_set(theme_usq())
+source(here("R/reportP.R"))
 
@@
    mutate(vi = vi/n) %>% 
-   #filter(fungicide_ai != "control") %>% #remove controls from the data
    mutate(spray_management =
@@
           id = row_number()) %>%
-   select(
+   dplyr::select(
       trial,
@@
       row_spacing,
-      host_genotype ,
+      host_genotype,
       spray_management,
@@
       grain_yield.t.ha,
-      grain_SMD,
       grain_MD,
@@
 ```
+The distribution of data does not seem to be improved by transformation of the data.
+We will retain the continuous variable grain_yield.t.ha as the response.
+Mean differences won't be used as we are following the methodology of a ARM-based model, where mean differences are calculated following the meta-analysis.
 
-Standardised mean differences have a bit of a long tail however this is not bad and transformations with log or square root will not work on negative values.
-So it looks like no transformation is necessary before we start the meta-analysis.
-
-Let's undertake the meta-analysis using the package `metafor`.
+To do a ARM based model we will use the package `metafor`.
 We are using the `spray_management` variable as a moderator and an interactive term to the `trial` random variable.
-Because we want to know the difference between all treatments and we have no reference treatment, we will remove the intercept.
 
@@
 
+The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis.
+This effectively shows the heterogeneity between experiments for these partivular treatments.
+
+The tau^2 also gives us the heterogeneity between trials and indicates `Recommended_plus` showed the highest heterogeneity between experiments followed by `Late_plus`, `Late` then `Recommended`, with `Early` and the no-spray `control` showing the least heterogeneity.
+
+The second table is in two parts (left and right). 
+The left part, rho, is the correlation of variation between the specified treatments.
+All comparisons were acceptable except for a comparison between `Early` and `Late_plus`, `0.000` rho.
+`Early` and `Late_plus` treatments never occurred within the same trial, which is indicated by the right side of the table (hence the warning).
+
+In this result we can see that the `Early` treatment is not significantly different to the intercept, which in this case is the mean of the no spray `control`.
+However the other treatments are significantly different from the no-spray control (intercept).
+The $Q_M$ [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, shows the moderators significantly influence the model ($Q_M =$ `r PM_mv$QM` $, df = $ `r PM_mv$m`, `r reportP(PM_mv$QMp)`) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
+The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = $`r PM_mv$QM` $, df = $`r PM_mv$k - PM_mv$m`, `r reportP(PM_mv$QEp)` ) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
+
 ```{r PM_Mv_Contrast}
@@
 simple_summary(summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none")))
+```
+
+These contrasts can be viewed in a plot
+```{r plotContrasts}
 plot(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))))
 ```
+
+Does disease pressure on the crop affect the optimum spray scenario? 
+Above we can see spraying at the first sign of powdery mildew or with in `r min(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"| slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` - `r max(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"|                   slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` days after first sign is effective at mitigating yield loss.
+Lets test this hypothesis by adding it as a moderator and comparing the new model with the original model above.
 
@@
 )
+
+anova(PM_mv, PM_mv2)
+```
+We can see that the lower $QE$ indicates that disease preasure moderator helped explain some of the residual heterogeneity in differences in grain yield between treatments. 
+However according to the Wald-test the models were not significantly different and we should use the orriginal "Reduced" model.
+
+The P value was close to the 0.05 cut-off so we will present the model output for the interest of the readers.
+```{r DissPressMetMod}
 summary(PM_mv2)
@@
 plot(glht(PM_mv2, linfct=cbind(contrMat(rep(7,12), type="Tukey"))))
-
-anova(PM_mv, PM_mv2)
-
 ```
@@
 
-Results show with the exclusion of the no spray `control` and `Late` treatments, `Early` applications are significantly worse than all other treatments leading to lower yield estimates.
-`Late_plus` is estimated to save the most yield however it is only significantly higher than `Early` and `Late` treatments.
-Let's put these values in a plot to visualise the differences between treatments.
-
-First we will format the results into a data frame.
+Lets present the meta-analysis results for the moderator variables in a forest style plot.
+First lets create a table of the results.
 
@@
 YieldContrasts
+```
+
+### Forest plot of trial treatment effect per trial
+Lets look at the trial variability in this model with a forest plot
+```{r forestP, fig.height= 40, fig.width=17}
+source(here("R/change_labels.R"))
+source(here("R/forest_rows.R"))
+
+### Sort and arrange data-frame accordingly and produce a index vector to inform the order of each "Trial" on the plot
+index1 <- dat1 %>%
+   mutate(ID = seq_along(trial_ref)) %>%
+   mutate(spray_management = 
+             factor(spray_management, 
+                    levels = c("Early","Late","Recommended",
+                    "Recommended_plus","Late_plus"))) %>%
+   arrange(desc(spray_management), location, desc(grain_MD)) %>%
+   mutate(ID2 = order(ID))%>%
+   pull(ID2)
+
+### Use forest rows function to return a list of where to place on the plot: sub-titles, each trial row, and summary prediction for each treatment.
+### this list can be used below to reference where to plot each variable
+rows1 <- forest_rows(head_row = 156, 
+                     ord_var = dat1$spray_management, 
+                     index = index1, 
+                     gap = 5, 
+                     row_offset = -2)
+
+### A data-frame of meta-model coefficients used to produce the summary polygons for each treatment
+polys <- data.frame(ref = change_labels(names(coef(PM_mv))),
+                    x = coef(PM_mv),
+                    ci.lb = PM_mv$ci.lb,
+                    ci.ub = PM_mv$ci.ub)[c(1,4,2,3,5),]
+polys$rows <- rows1$pred_row - 1.5
+
+forest1  <- metafor::forest(PM_mv, cex = 1.15 , width = 5,
+                #order = "fit",
+                rows = rows1$trows-1.5,
+                ilab = cbind(dat1$year, 
+                             dat1$row_spacing, dat1$host_genotype, dat1$dose),
+                ilab.xpos = c(-2.35,-2.1,-1.8,-1.4),
+                slab = NA, 
+                xlim = c(-2.9, 2.2),
+                ylim = c(18,157),
+                xlab = "Grain yield mean difference",
+                addfit = FALSE,
+                efac = c(0.2,0.15,0.2),
+                at = seq(-1,1.5, 0.5))
+
+### code which puts lines and annotations on the plot, its a bit long...
+source(here("R/add_annotations.R"))
+
 ```
@@
 ```
-To to a better comparison I need to know how the mitigation factor is calculated with the estimated yields
+To to a better comparison I need to know how the mitigation factor is calculated with the estimated yields.

### 2020-07-23 07_Manuscript.Rmd
Correct Rmd so that it knits

@@
 Second applications, if they are needed, should be applied at least 10 - 14 days after the first application and not within 21 days of harvest [@APVMAcustodia].
-If time permitted a second spray after the first 'late' application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(T3$estimates[10], 4)*1000` kg / ha, when compared to the $Late$, single spray treatment `r reportP(T3$pval[10]`).
+If time permitted a second spray after the first 'late' application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(T3$estimates[10], 4)*1000` kg / ha, when compared to the $Late$, single spray treatment `r reportP(T3$pval[10])`.
 

### 2020-07-23 07_Manuscript.Rmd
Insert Lambrides2007 mungbean ref
This is a better reference to use than Pulse AU

@@
 
-Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown in south-east Asia for human consumption as an affordable source of protein [@PulseAustralia].
+Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown in south-east Asia for human consumption as an affordable source of protein [@Lambrides2007].
 The bean pod or grain can be consumed raw or added to meals after sprouting.

### 2020-07-23 R/add_annotations.R
ReKint changes in Meta-analysis.rmd

@@ -5,13 +5,14 @@
 
 
 ### add column headings to the plot
-text(c(-2.7, -2.35,-2.1,-1.8,-1.4), 156,cex = 1, 
+text(c(-2.7, -2.35,-2.1,-1.8,-1.4)+1, 156,cex = 1, 
      c("Location", "Year", "Row\nSpacing","Host\nCultivar","DMI dose"),
      font = 2)
 
 ### Add subtitles for each SpraySchedule breakdown
-text(-2, rows1$stitle_row ,cex = 1.3, 
-     paste0(c("Early", "Late", "Recommended", "RecommededPlus", "LatePlus")," Spray Schedule - (tau^2 = " ,round(PM_mv$tau2, digits = 3), ") "),
+text(-1, rows1$stitle_row ,cex = 1.3, 
+     paste0(c("control","Early", "Late", "Recommended", "RecommededPlus", "LatePlus"),
+            " Spray Schedule - (tau^2 = " ,round(PM_mv$tau2, digits = 3), ") "),
      font = 2)
 
 addpoly(x = polys$x,
@@ -25,16 +26,16 @@ addpoly(x = polys$x,
 abline(h = rows1$stitle_row +1)
 
 ### Early lines
-lines(c(-2.9,-1.25),c(153,153), col = "grey70")
+lines(c(-2.9,-1.25)+1,c(153,153), col = "grey70")
 text(x = -2.7, y = 152.5, 
      labels = "Missen Flats" ,cex=1)
-lines(c(-2.9,-1.25),c(147,147), col = "grey70")
+lines(c(-2.9,-1.25)+1,c(147,147), col = "grey70")
 text(x = -2.7, y = 146.5, 
      labels = "Marys Mount" ,cex=1)
-lines(c(-2.9,-1.25),c(146,146), col = "grey70")
+lines(c(-2.9,-1.25)+1,c(146,146), col = "grey70")
 text(x = -2.7, y = 145.5, 
      labels = "Hermitage" ,cex=1)
-lines(c(-2.9,-1.25),c(140,140), col = "grey70")
+lines(c(-2.9,-1.25)+1,c(140,140), col = "grey70")
 
 ### Late lines
 lines(c(-2.9,-1.25),c(135,135), col = "grey70")

### 2020-07-23 R/forest_rows.R

@@ -8,7 +8,10 @@ forest_rows <- function(head_row, ord_var, index,
                sum(ord_var == "Early") + sum(ord_var == "Late") + 
                   sum(ord_var == "Recommended") + sum(ord_var == "Recommended_plus"),
                sum(ord_var == "Early") + sum(ord_var == "Late") + 
-                  sum(ord_var == "Recommended") + sum(ord_var == "Recommended_plus") + sum(ord_var == "Late_plus"))
+                  sum(ord_var == "Recommended") + sum(ord_var == "Recommended_plus") + sum(ord_var == "Late_plus"),
+               sum(ord_var == "Early") + sum(ord_var == "Late") + 
+                  sum(ord_var == "Recommended") + sum(ord_var == "Recommended_plus") + sum(ord_var == "Late_plus") +
+                  sum(ord_var == "control"))
    
    trows_F <- function(x1, head_row, gap){
       if(x1 <= length(ord_var) &&
@@ -32,13 +35,18 @@ forest_rows <- function(head_row, ord_var, index,
          x1 > length(ord_var) - breaks[5]){
          return(x1 + (head_row - length(ord_var)) - (gap * 4))}
       
+      if(x1 <= length(ord_var) - breaks[5] &&
+         x1 > length(ord_var) - breaks[6]){
+         return(x1 + (head_row - length(ord_var)) - (gap * 5))}
+      
    }
    
    stitle_row <- head_row - c(stitle_row_offset,
                               stitle_row_offset + breaks[1] + gap,
                               stitle_row_offset + breaks[2] + (gap*2),
                               stitle_row_offset + breaks[3] + (gap*3),
-                              stitle_row_offset + breaks[4] + (gap*4))
+                              stitle_row_offset + breaks[4] + (gap*4),
+                              stitle_row_offset + breaks[5] + (gap*5))
    
    
    dat2 <- list(stitle_row = stitle_row,
@@ -47,7 +55,8 @@ forest_rows <- function(head_row, ord_var, index,
                                         stitle_row_offset + breaks[2] + gap,
                                         stitle_row_offset + breaks[3] + (gap*2),
                                         stitle_row_offset + breaks[4] + (gap*3),
-                                        stitle_row_offset + breaks[5] + (gap*4)),
+                                        stitle_row_offset + breaks[5] + (gap*4),
+                                        stitle_row_offset + breaks[6] + (gap*5)),
                 
                 trows = unlist(sapply(index,trows_F, head_row = head_row, gap = gap)) + row_offset,
                 

### 2020-07-23 04_MetaAnalysis.Rmd
Make corrections and fix so it knits

@@
 
-   - Grain yield is our response variable and will be converted to kg / ha
+   - Grain yield is our response variable (t / ha)
 
@@
 
-   - We will test spray management (our treatment) as a fixed effect and random slope to trial
+   - We will test spray management (our treatment) as a fixed effect and random interactive term to trial
 
@@
    )
+
 ```
+<!-- I don't like this graph, it is hard to read given that different widths don't translate to anything meaningful -->
 
@@
 There seems like little difference between the treatments, with exception of `Late_plus`.
-Let's do this plot again, but let's look at the proportional mean difference between the treatments and the no spray control for each study, this should reduce variation in yield due between trials.
+Let's do this plot again, but let's look at the proportional mean difference between each treatment and the no spray control for each study, this should reduce variation in yield due between trials.
 
@@
 We know there is a good deal of variability in our studies and between them.
-Mungbean produces variable yields between seasons so we should use a response that highlights the difference in the treatment effects that we are interested in and reduce the variability.
-Let's calculate the standardised mean difference for each treatment to reduce the variability in the meta-analysis.
+Mungbean produces variable yields between seasons so ordinarilly we should use a response that highlights the difference in the treatment effects that we are interested in and reduce the variability.
+However for an arm-based analysis we calculate the differences between control and treatment after the meta-analysis.
+
+### Formating the response variable
+
+Let's inspect the response variance `grain_yield.t.ha` to see if it is normally distributed. 
+In many cases a log transformation of the response variable improves the fit, due to the prevalence of log distributed data in nature.
+
+```{r}
+hist_usq(slimmer_PM_dat$grain_yield.t.ha, main = "Grain yield (t / ha)")
+hist_usq(log(slimmer_PM_dat$grain_yield.t.ha), main = "log(Grain yield (t / ha))")
+hist_usq(sqrt(slimmer_PM_dat$grain_yield.t.ha), main = "sqrt(Grain yield (t / ha))")
+hist_usq(slimmer_PM_dat$yield_gain, main = "Mean difference to control (t / ha)")
+```
+The distribution of data does not seem to be improved by transformation of the data.
+We will retain the continuous variable grain_yield.t.ha as the response.
+Mean differences won't be used as we are following the methodology of a ARM-based model, where mean differences are calculated following the meta-analysis.
 
@@
 
-We have removed the studies that don't report any variance from the analysis.
-
-### Calculate standardised mean differences
-
-Let's calculate standardised mean differences and add them to the data frame.
-
-```{r StandardisedMeanDifference}
-slimmer_PM_dat$pooledSD <- NA
-slimmer_PM_dat$vi_C <- NA
-for (i in slimmer_PM_dat$trial_ref) {
-   # First we need to Calculate the pooled standard deviation
-   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "pooledSD"] <-
-      sqrt(sum((slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "n"] - 1) * slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "yield_error"]) /
-              (sum(slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "n"]) - nrow(slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, ])))
-
-   # Create a column with the value of the mean grain yield of the no spray
-   #  control for comparisons to the treatments means
-   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "yi_C"] <-
-      mean(slimmer_PM_dat[slimmer_PM_dat$trial_ref == i &
-                             slimmer_PM_dat$fungicide_ai == "control",
-                          "grain_yield.t.ha"], na.rm = TRUE)
-
-}
-
-# Calculate standardised mean difference
-slimmer_PM_dat$grain_SMD <-
-   (slimmer_PM_dat$grain_yield.t.ha - slimmer_PM_dat$yi_C) / slimmer_PM_dat$pooledSD
-```
-
-To visualise this formula in mathematical notation:  
-$SMD = \frac{Y_i-\overline{Y_c}}{\sigma_p}$
-
-We can use the same sample variance with the standardised mean difference.
-This is because if you add or subtract from a random variable, the variance does not change.
-
-Let's simplify our data by removing the control data, converting disease pressure (`D_pres`) to a factor and selecting only the columns of data necessary for analysis.
+Now Let's simplify our data by removing the control data, converting disease pressure (`D_pres`) to a factor and selecting only the columns of data necessary for analysis.
 We will also include the mean difference or response ratio `grain_MD`, between the treatment and control as a comparison of responses.
@@
    slimmer_PM_dat %>%
-   filter(fungicide_ai != "control") %>% #remove controls from the data
+   mutate(vi = vi/n) %>% 
    mutate(spray_management =
@@
                       "highD")),
-          grain_MD = grain_yield.t.ha - yi_C) %>%
-   select(
+          id = row_number()) %>%
+   dplyr::select(
       trial,
@@
       grain_yield.t.ha,
-      grain_SMD,
-      grain_MD,
+      yield_gain,
       dose,
       vi,
-      vi2
-      )
+      yield_error,
+      vi2,
+      n,
+      id)
 ```
@@
 
-Let's inspect the data to determine if we need to transform the response variable.
-
-```{r}
-hist_usq(dat1$grain_yield.t.ha)
-hist_usq(log(dat1$grain_yield.t.ha))
-hist_usq(sqrt(dat1$grain_yield.t.ha))
-hist_usq(dat1$grain_MD)
-```
-
-Standardised mean differences have a bit of a long tail however this is not bad and transformations with log or square root will not work on negative values.
-So it looks like no transformation is necessary before we start the meta-analysis.
-
-Let's undertake the meta-analysis using the package `metafor`.
+To do a ARM based model we will use the package `metafor`.
 We are using the `spray_management` variable as a moderator and an interactive term to the `trial` random variable.
-Because we want to know the difference between all treatments and we have no reference treatment, we will remove the intercept.
 
@@
 PM_mv <- rma.mv(
-   yi = grain_MD,
+   yi = grain_yield.t.ha,
    vi,
-   mods = ~ spray_management - 1,
+   mods = ~ spray_management,
    method = "ML",
-   random = ~ spray_management | trial,
+   random = list(~ spray_management | trial, ~1 | id), 
    struct = "UN",
+   control=list(optimizer="optim"),
    data = dat1
 )
+
 summary(PM_mv)
@@
 
-Let's see if we can improve this model by including some other random effects and improving the random effect structure in the model.
-
-```{r rma_noRandomInteractiveTerm}
-PM_mv_St <- rma.mv(
-   yi = grain_MD,
-   vi,
-   mods = ~ spray_management,
-   method = "ML",
-   random = list( ~ 1 | trial),
-   data = dat1
-)
-
-PM_mv_St1 <- rma.mv(
-   yi = grain_MD,
-   vi,
-   mods = ~ spray_management,
-   method = "ML",
-   random = list(
-      ~ 1 |
-         location / year / trial_ref / dose / host_genotype / factor(row_spacing) /
-         spray_management
-   ),
-   data = dat1
-)
-
-AIC(PM_mv) # Printing the AIC of the model helps differentiate the models in the anova output
-anova(PM_mv, PM_mv_St) # PM_mv is the better model
-AIC(PM_mv_St)
-anova(PM_mv_St, PM_mv_St1) # PM_mv_St is the better model
-```
-
-The simpler `PM_mv_St` model explains significantly less variation than the more complicated model `PM_mv`.
-So we will keep the original model `PM_mv`.
-
-I have also tested the structure for testing the random trial and spray_management variables, these show that there is no significant difference to the models `PM_mv_St` and `PM_mv_St1` and that the originally method of specifying the random variables within the `trial` factor provides us with the best model.
-
 The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis.
 This effectively shows the heterogeneity between experiments for these partivular treatments.
+
+The tau^2 also gives us the heterogeneity between trials and indicates `Recommended_plus` showed the highest heterogeneity between experiments followed by `Late_plus`, `Late` then `Recommended`, with `Early` and the no-spray `control` showing the least heterogeneity.
 
@@
 
-The fixed effects, in the last table, show that yields in single early spray treatments are not significantly different from zero, or the no spray control.
+In this result we can see that the `Early` treatment is not significantly different to the intercept, which in this case is the mean of the no spray `control`.
+However the other treatments are significantly different from the no-spray control (intercept).
+The $Q_M$ [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, shows the moderators significantly influence the model ($Q_M =$ `r PM_mv$QM` $, df = $ `r PM_mv$m`, `r reportP(PM_mv$QMp)`) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
+The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = $`r PM_mv$QM` $, df = $`r PM_mv$k - PM_mv$m`, `r reportP(PM_mv$QEp)` ) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
+
+```{r PM_Mv_Contrast}
+source("R/simple_summary.R")
+summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none"))
+contrast_Ssum <- simple_summary(summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none")))
+contrast_Ssum
+```
+
+These contrasts can be viewed in a plot
+```{r plotContrasts}
+par(mar = c(5, 13, 4, 2) + 0.1)
+plot(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), yaxt='n')
+axis(2, at = seq_along(contrast_Ssum$contrast), labels = rev(contrast_Ssum$contrast), las=2, cex.axis = 0.8)
+```
+
+Does disease pressure on the crop affect the optimum spray scenario? 
+Above we can see spraying at the first sign of powdery mildew or with in `r min(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"| slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` - `r max(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"|                   slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` days after first sign is effective at mitigating yield loss.
+Lets test this hypothesis by adding it as a moderator and comparing the new model with the original model above.
+
+```{r DisPressComparison}
+PM_mv2 <- rma.mv(
+   yi = grain_yield.t.ha,
+   vi,
+   mods = ~ spray_management*D_pres,
+   method = "ML",
+   random = list(~ spray_management | trial, ~1 | id), 
+   struct = "UN",
+   control=list(optimizer="optim"),
+   data = dat1
+)
+
+anova(PM_mv, PM_mv2)
+```
+We can see that the lower $QE$ indicates that disease pressure moderator helped explain some of the residual heterogeneity in differences in grain yield between treatments. 
+However according to the Wald-test the models were not significantly different and we should use the original "Reduced" model.
+
+The P value was close to the 0.05 cut-off so we will present the model output for the interest of the readers.
+```{r DissPressMetMod}
+summary(PM_mv2)
+summary(glht(PM_mv2, linfct=cbind(contrMat(rep(7,12), type="Tukey"))), test=adjusted("none"))
+# plot(glht(PM_mv2, linfct=cbind(contrMat(rep(7,12), type="Tukey")))) # I think this plot is too busy to be incorporated
+```
 
@@
 
-*****
-
-### Metafor comparisons
-
-To make it easier to compare each of the treatments we can compute the meta-analysis contrasts.
-
-```{r metafor_contrasts}
-meta_cont <- anova(PM_mv, L = rbind(
-   c(-1, 1, 0, 0, 0),
-   c(-1, 0, 1, 0, 0),
-   c(-1, 0, 0, 1, 0),
-   c(-1, 0, 0, 0, 1),
-   c(0, -1, 1, 0, 0),
-   c(0, -1, 0, 1, 0),
-   c(0, -1, 0, 0, 1),
-   c(0, 0, -1, 1, 0),
-   c(0, 0, -1, 0, 1),
-   c(0, 0, 0, -1, 1)
-))
-
-change_labels <- function(x1) {
-   x1 <- gsub(pattern = "spray_management",
-              replacement = "",
-              x = x1)
-   x1
-}
-
-source("R/p_star.R")
-
-table3 <- data.frame(
-   contrasts = change_labels(meta_cont$hyp[, 1]),
-   estimates = meta_cont$Lb,
-   se = meta_cont$se,
-   z_val = meta_cont$zval,
-   pval = meta_cont$pval,
-   VisP = p_star(meta_cont$pval)
-)
-write.csv(table3, here("cache/Table3_contrasts.csv"), row.names = FALSE)
-```
-
-Results show with the exclusion of the no spray `control` and `Late` treatments, `Early` applications are significantly worse than all other treatments leading to lower yield estimates.
-`Late_plus` is estimated to save the most yield however it is only significantly higher than `Early` and `Late` treatments.
-Let's put these values in a plot to visualise the differences between treatments.
-
-First we will format the results into a data frame.
+Lets present the meta-analysis results for the moderator variables in a forest style plot.
+First lets create a table of the results.
 
@@
 ```{r metafor_plot}
-efficacy %>%
+YieldContrasts <- efficacy %>%
+   filter(Treatment != "control") %>% 
    mutate(Treatment = factor(Treatment, levels = rev(
       c(
+
          "Early",
@@
    coord_flip()
+
+YieldContrasts
 ```
 
-### Disease pressure effect
+### Forest plot of trial treatment effect per trial
+Lets look at the trial variability in this model with a forest plot
+```{r forestP, fig.height= 40, fig.width=17}
+# THIS NEEDS TO BE FIXED
+source(here("R/change_labels.R"))
+source(here("R/forest_rows.R"))
 
-We also want to know if disease pressure exerts an effect on the decision for spray control.
-Above we can see spraying at the first sign of powdery mildew or with in `r min(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"| slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` - `r max(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"|                   slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` days after first sign is effective at mitigating yield loss.
-Does this change between years of low and high disease pressure.
+### Sort and arrange data-frame accordingly and produce a index vector to inform the order of each "Trial" on the plot
+index1 <- dat1 %>%
+   mutate(ID = seq_along(trial_ref)) %>%
+   mutate(spray_management = 
+             factor(spray_management, 
+                    levels = c("Early","Late","Recommended",
+                    "Recommended_plus","Late_plus"))) %>%
+   arrange(desc(spray_management), location, desc(grain_yield.t.ha)) %>%
+   mutate(ID2 = order(ID))%>%
+   pull(ID2)
 
-We will add the intercept back into this model for ease of interpretation. 
-```{r D_pres-Meta}
-PM_mv_Dp <- rma.mv(
-   yi = grain_MD,
-   vi,
-   mods = ~ spray_management * D_pres - 1,
-   method = "ML",
-   random = ~ spray_management | trial,
-   struct = "UN",
-   data = dat1
-)
+### Use forest rows function to return a list of where to place on the plot: sub-titles, each trial row, and summary prediction for each treatment.
+### this list can be used below to reference where to plot each variable
+rows1 <- forest_rows(head_row = 186, 
+                     ord_var = dat1$spray_management, 
+                     index = index1, 
+                     gap = 5, 
+                     row_offset = -2)
 
-summary(PM_mv_Dp)
-```
+### A data-frame of meta-model coefficients used to produce the summary polygons for each treatment
+polys <- data.frame(ref = change_labels(names(coef(PM_mv))),
+                    x = c(coef(PM_mv)[1],coef(PM_mv)[1] + coef(PM_mv)[2:6]),
+                    ci.lb = c(PM_mv$ci.lb[1],PM_mv$ci.lb[1] +PM_mv$ci.lb[2:6]),
+                    ci.ub = c(PM_mv$ci.ub[1],PM_mv$ci.ub[1] +PM_mv$ci.ub[2:6]))[c(2,5,3,4,6,1),]
+polys$rows <- rows1$pred_row - 1.5
 
-These results show that the spray management variable we tested are not significantly better or worse between the two levels of disease pressure.
-It seems that disease preasure does not improve the models ability to assess the most effective fungicide spray management option.
-Let's compare the disease pressure model to the original model to test this assumption.
+forest1  <- metafor::forest(PM_mv, cex = 1.15 , width = 5,
+                #order = "fit",
+                rows = rows1$trows-1.5,
+                ilab = cbind(dat1$year, 
+                             dat1$row_spacing, dat1$host_genotype, dat1$dose),
+                ilab.xpos = c(-2.35,-2.1,-1.8,-1.4)+1,
+                slab = NA, 
+                xlim = c(-2, 4),
+                ylim = c(5,190),
+                xlab = "Grain yield mean difference",
+                addfit = FALSE,
+                efac = c(0.2,0.15,0.2),
+                at = seq(-0.5,3, 0.5))
 
-```{r compareDvNDP}
-AIC(PM_mv_Dp)
-anova(PM_mv_Dp, btt = "D_pres")
-anova(PM_mv, PM_mv_Dp)
-```
-
-A Wald test of `D_pres` shows the moderator is not significant in accounting for heterogeneity (P = 0.4859).
-No significant difference which informs us to use the original model `PM_mv`, which is the simplest.
-
-### Test for bias in indirect comparisons 
-Treatments `Early` and `LatePlus` did not co-occur in any of the trials considered in the meta-analysis.
-Indirect comparisons are ok to interpret in the results of a network meta-analysis, however if there are biases between trials including `Early` or `LatePlus` treatments then the results are likely bias.
-Therefore we wish to do a quick check that the trials which included `Early` treatments did not significantly differ from trials which incorportated `LatePlus`,
-Lets create a data.frame of values for this comparison
-
-```{r}
-Ear <- 
-   dat1 %>%
-   filter(spray_management == "Early")%>%
-   distinct(trial_ref)
-
-LP <- 
-   dat1 %>%
-   filter(spray_management == "Late_plus")%>%
-   distinct(trial_ref)
-
-dat1$indirectC <- NA
-
-dat1 %>%
-   filter(trial_ref == Ear$trial_ref)
-
-dat1[dat1$trial_ref == Ear$trial_ref, "indirectC"] <- "Ear"
-dat1[dat1$trial_ref == LP$trial_ref, "indirectC"] <- "LP"
-
-dat1 %>%
-   filter(!is.na(indirectC))%>%
-   ggplot(aes(x = indirectC, y = grain_MD))+
-   geom_boxplot()
-
-dat1 %>%
-   filter(!is.na(indirectC),
-          spray_management != "Early",
-          spray_management != "Late_plus")%>%
-   ggplot(aes(x = indirectC, y = grain_MD))+
-   geom_boxplot()
-
-dat1[dat1$trial_ref == LP$trial_ref, "indirectC"] <- "LP"
-dat1[dat1$trial_ref == Ear$trial_ref, "indirectC"] <- "Ear"
-
-dat2 <- dat1 %>%
-   filter(!is.na(indirectC),
-          spray_management != "Early",
-          spray_management != "Late_plus")
-
-table(dat2$spray_management, dat2$indirectC)
-
-summary(aov(grain_MD ~ indirectC + spray_management + trial_ref, data = dat2))
+### code which puts lines and annotations on the plot, its a bit long...
+source(here("R/add_annotations.R"))
 
 ```
-
-This anova shows that there is no significant difference between the trials, spray_management or the specific trials with either `Early` or `Late_plus`. 
-Therefore there is low risk that interpreting results from this indirect comparison between `Early` and `Late_plus`.
 
@@
 write.csv(slimmer_PM_dat, file = "data/GYmeta_data.csv")
+save(dat1, efficacy, PM_mv, YieldContrasts, file = here("cache/Meta-analysisData.Rdata"))
 ```
+
+#### Powdery mildewMBM comparison -- Delete
+One aspect we would like to consider is how the results of this meta-analysis compares to how the PowderyMildewMBM estimates the effect of fungicide applications on grain yields.
+Below we create a data frame of the mitigation factors for each spray scenario so we can compare them to the outcomes of the meta-analysis.
+```{r compare2PowderyMildewMDM}
+
+PMBM <- 
+   data.frame(Sprays = c(rep(1,20), rep(2,20)),
+              Disease = rep(c(rep("NotPresent", 5),
+                          rep("LowerCanopy", 5),
+                          rep("MidCanopy", 5),
+                          rep("UpperCanopy", 5)),2),
+              CropMaturity = rep(c("Vegetative", "Budding", "Flowering",
+                                   "EarlyPod", "LatePod"), 8),
+              mitigation = c(0.57, 0.855, 0.95,0.95,0.95,
+                             0.45995, 0.52919,0.5530,0.390,0.1642,
+                             0.291258,0.351051, 0.2454,0.1409,0.4717,
+                             0,0.059597,0.093034,0.0682476,0.0215584,
+                             0.95,0.95,0.95,0.95,0.95,
+                             0.766588,0.6991,0.55042,0.390056,0.1642,
+                             0.485429,0.390,0.2454,0.140904,0.0471684,
+                             0.0791,0.086068,0.093034,0.0682476,0.0215584))
+
+# what is the mean age of the plant in our data when disease first occurs and we apply the first spray?
+source("R/import_data.R")
+PM_MB_dat <- import_data()
+mean(PM_MB_dat$first_sign_disease - PM_MB_dat$planting_date, na.rm =TRUE) # 46.3 days (which is when the plant is flowering)
+
+#What proportion of the yield was saved?
+1 - (coef(PM_mv)[1] /(coef(PM_mv)[1] + coef(PM_mv)[3]))
+1- (coef(PM_mv)[1] /(coef(PM_mv)[1] + coef(PM_mv)[4]))
+
+PMBM %>%
+   filter(CropMaturity == "Flowering")
+
+```
+To to a better comparison I need to know how the mitigation factor is calculated with the estimated yields.

### 2020-07-23 07_Manuscript.Rmd
Edit introductory paragraph and add new references on MB history in Oz

@@
 The bean pod or grain can be consumed raw or added to meals after sprouting.
-The dried grain can also be ground into a protein enriched flour for uses such as noodles, biscuits and cakes [@Chankaew2013].
+The dried grain can also be ground into a protein enriched flour for uses in noodles, biscuits and cakes [@Chankaew2013].
 
-Mungbean was first brought to Australia in the 1930s for use as a forage or green manure crop and it was only as recent as the 1960s until that mungbean was grown commercially [@aboutAMA, @Chauhan2018].
-At the end of the 1980s between 3 - 10 thousand hectares were being harvested for dried beans, of which mungbean is categorised by the FAO statistics data repository [@FAOSTAT].
+Mungbean was first brought to Australia in the 1930s for use as a forage or green manure crop.
+However, it was only somewhat recently, the 1960s that mungbean was grown commercially [@Lawn1978; @Chauhan2018].
+Prior to the 1970s the total area grown in Australia rarely exceeded 1000 hectares [@Lawn1978].
+At the end of the 1980s, between 3,000 to 10,0000 hectares were being harvested for dried beans in Australia, of which mungbean is categorised by the FAO statistics data repository [@FAOSTAT].
 In the decade leading up to 2018 between 35 - 86.4 thousand hectares of dried beans were planted annually.

### 2020-07-23 07_Manuscript.Rmd

@@
 <!-- need to ensure the format of this manuscript adheres to the MDPI Agronomy style guide -->
+<!-- To ensure formatting matches, I suggest that you create a Word template and knit this document using that -->
+
 ## Introduction

### 2020-07-23 04_MetaAnalysis.Rmd
amend T-crit value in 03_prep_data.rmd and re-Knit all subsequently effected files

@@
 However the other treatments are significantly different from the no-spray control (intercept).
-The $Q_M$ [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, shows the moderators significantly influence the model ($Q_M =$ `r PM_mv$QM` $, df = $ `r PM_mv$m`, `r reportP(PM_mv$QMp)`) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
-The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = $`r PM_mv$QM` $, df = $`r PM_mv$k - PM_mv$m`, `r reportP(PM_mv$QEp)` ) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
+The $Q_M$ [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, shows the moderators significantly influence the model ($Q_M =$ `r PM_mv$QM` $,df =$ `r PM_mv$m`, `r reportP(PM_mv$QMp)`) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
+The analysis shows there is still a significant amount of residual heterogeneity ($Q_E =$ `r PM_mv$QM` $,df=$ `r PM_mv$k - PM_mv$m`, `r reportP(PM_mv$QEp)` ) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
 
@@
 
-```{r profile_plots, message=FALSE, results="hide"}
+```{r profile_plots, eval=FALSE, message=FALSE, include=FALSE, results="hide"}
 profile(PM_mv, tau2 = 1)

### 2020-07-23 07_Manuscript.Rmd
Some hard-coding and updated T-crit value

@@
 The sample variance was calculated from the raw data when available or the least squares statistic in trial reports. 
-Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 1.697 and the approach reported in Ngugi et al. [-@Ngugi2011].
-The T-critical value was determined from the 30 degrees of freedom and probability of $a = 0.1$ using a t-distribution table.
-<!-- Checking this reference the T-critical value might need to be adjusted to 2.042 using an alpha of 0.05, or as Ngugi choses df = inf and alpha of 0.05 -->
+Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 2.042 and the approach reported in Ngugi et al. [-@Ngugi2011].
+The T-critical value was determined from the 30 degrees of freedom and probability of $a = 0.05$ using a t-distribution table. 
 The 2012 Gatton and 2015 Emerald trials reported treatment means without accompanying variance and were thus removed from the dataset  prior to the analysis.
@@
 
-Similar to Paul et. al. [-@Paul2007], we fitted a multivariate random effects model
+Similar to Paul *et. al.* [-@Paul2007], we fitted a multivariate random effects model
 $Y_i \sim N(\mu,s_i^2 + \sigma^2)$
@@
 
-The $Q_M$ omnibus test of moderators, shows the moderators significantly influence the model ($Q_M = 26.22, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
-The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 568.31, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators, which might influence grain yield.
+The $Q_M$ omnibus test of moderators, shows the moderators significantly influence the model ($Q_M =$ `r PM_mv$QM` $,df =$ `r PM_mv$m`, `r reportP(PM_mv$QMp)`) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
+The analysis shows there is still a significant amount of residual heterogeneity ($Q_E =$ `r PM_mv$QE` $,df=$ `r PM_mv$k - PM_mv$m`, `r reportP(PM_mv$QEp)`) not captured by the spray management moderator indicating other possible moderators, which might influence grain yield.
 
@@
 While the addition of disease pressure, as an interactive moderator term to `SpraySchedule`, did explain slightly more residual heterogeneity, shown by a lower $Q_E = 409.91,$. 
-The model including disease pressure did not significantly improve the model (P = 0.4859) and did not significantly explain differences in the SpraySchedule term, and therefore disease pressure was not included in the final model.
+The model including disease pressure did not significantly improve the model (P = 0.4859) and did not significantly explain differences in the `SpraySchedule` term, and therefore disease pressure was not included in the final model.
 

### 2020-07-23 04_MetaAnalysis.Rmd
Correct typo

@@
 The $Q_M$ [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, shows the moderators significantly influence the model ($Q_M =$ `r PM_mv$QM` $,df =$ `r PM_mv$m`, `r reportP(PM_mv$QMp)`) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
-The analysis shows there is still a significant amount of residual heterogeneity ($Q_E =$ `r PM_mv$QM` $,df=$ `r PM_mv$k - PM_mv$m`, `r reportP(PM_mv$QEp)` ) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
+The analysis shows there is still a significant amount of residual heterogeneity ($Q_E =$ `r PM_mv$QE` $,df=$ `r PM_mv$k - PM_mv$m`, `r reportP(PM_mv$QEp)` ) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
 

### 2020-07-24 R/reportP.R
Give a as.numeric option for reportP function

@@ -1,7 +1,15 @@
-reportP <- function(p){
-   if(p < 0.0001){
+reportP <- function(p, AsNumeric = FALSE){
+   if(AsNumeric == FALSE){
+      if(p < 0.0001){
       return("P < 0.0001")
    }else{
       return(paste("P =", format(round(p, digits =  4), scientific = FALSE)))
-   }
+   }}
+   
+   if(AsNumeric == TRUE){
+      if(p < 0.0001){
+      return(format(0.0001, scientific = FALSE))
+   }else{
+      return(format(round(p, digits =  4), scientific = FALSE))
+   }}
 }

### 2020-07-24 vignette/Manuscript2Word.Rmd
Create word document of manuscript and styles template

--- 2020-07-23 07_Manuscript.Rmd
@@
+---
+title: "A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean"
+author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
+date: "`r format(Sys.time(), '%d %B, %Y')`"
+output: 
+   word_document:
+      reference_docx: "Manuscript2Word_Template.docx"
+bibliography: "../Mungbean.bib"
+biblio-style: apalike
+link-citations: yes
+---
+
 ```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, here)
+pacman::p_load(tidyverse, knitr, here)
 
@@
 In Australia, quantitative resistance to powdery mildew has also been incorporated into few commercially available varieties.
-Jade-AU <!-- Need PBR emblem here --> has the the best disease resistance to powdery mildew (moderately susceptible), with cv. Green Diamond also containing some notable resistance [@Sparks2017].
+Jade-AU <span class="pbr">(pbr)</span> <!-- Need PBR emblem here --> has the the best disease resistance to powdery mildew (moderately susceptible), with cv.
+Green Diamond also containing some notable resistance [@Sparks2017].
 However commercially available mungbean cultivars in Australia lack sufficient resistance to be used as the primary powdery mildew management strategy. 
@@
 
-```{r Figure2_treatForest}
+<br>
+
+```{r Figure2_treatForest, echo = FALSE}
 YieldContrasts
 ```
+
+<br>
 
@@
    )) %>%
-   kable(caption = "Table 1: Description of Experiments") %>%
-   kable_styling(fixed_thead = TRUE,
-                 full_width = TRUE) %>%
-   scroll_box(width = "900px", height = "500px")
+   kable(caption = "Table 1: Description of Experiments")
 ```
-
+<br>
+<br>
 ```{r Table2_1to9Scale, echo=FALSE}
@@
 ) %>%
-   kable(caption = "Table 2: Powdery Mildew severity scoring scale") %>%
-   kable_styling(fixed_thead = T, full_width = T)
+   kable(caption = "Table 2: Powdery Mildew severity scoring scale") 
 ```
+<br>
 
@@
 
+<br>
+
 ```{r Figure1}
@@
 ```
+
+<br>
 
@@
 ## References
+
+<br>

### 2020-07-24 07_Manuscript.Rmd
small changes due to attempted ccs integration for PBR symbol

@@
+---
+output: 
+html_document:
+
+---
+
 ```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
@@
 pacman::p_load(tidyverse, kableExtra, here)
+
+if (!require("theme.usq"))
+   devtools::install_github("adamhsparks/theme.usq")
+library(theme.usq)
+theme_set(theme_usq())
 
@@
 Early trials showed that for fungicide applications to protect yield, a single fungicide application at first sign of the disease with another follow-up application two weeks later, if necessary, was the most effective [@SueThompson2016; @Sparks2017].
-However due to the variability in the results between seasons and experiments few of these studies produced a clear result based on a statistical analysis. 
+However, due to the variability in the results between seasons and experiments, few of these studies produced a clear result based on a statistical analysis. 
 This variability presents uncertainty for the best practice of fungicide spray schedules to mitigate yield losses from powdery mildew.
 
-<!--Some of the fungicides tested for controlling powdery mildew in mungbean have been registered with the APVMA [@APVMA; @Kelly2017a;  insert all published trials here -->.
+<!--Some of the fungicides tested for controlling powdery mildew in mungbean have been registered with the APVMA [@APVMA; @Kelly2017a;  insert all published trials here -->
 
@@
 
-```{r Figure2_treatForest}
+```{r Figure2_treatForest, echo = FALSE}
 YieldContrasts

### 2020-07-24 vignette/Manuscript2Word.Rmd
Create vignette copy of manuscript from bookdown file, specifically for rendering into word. And the rendered word document plus styles template file

@@
 
+if (!require("theme.usq"))
+   devtools::install_github("adamhsparks/theme.usq")
+library(theme.usq)
+theme_set(theme_usq())
+
 # Data
@@
 
-# Manuscript
+***
+
 <!-- need to ensure the format of this manuscript adheres to the MDPI Agronomy style guide -->
@@
    )) %>%
-   kable(caption = "Table 1: Description of Experiments")
+   kable(caption = "Table 1: Description of Experiments", booktabs = T, align = "c")
 ```
+
 <br>
 <br>
+
 ```{r Table2_1to9Scale, echo=FALSE}
@@
 ) %>%
-   kable(caption = "Table 2: Powdery Mildew severity scoring scale") 
+   kable(caption = "Table 2: Powdery Mildew severity scoring scale",  align = "cl") 
 ```

### 2020-07-27 07_Manuscript.Rmd
Update manuscript to use flextable instead of kable

@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, here)
+pacman::p_load(tidyverse, kableExtra, here, flextable, officer)
 
@@
    )) %>%
-   kable(caption = "Table 1: Description of Experiments") %>%
-   kable_styling(fixed_thead = TRUE,
-                 full_width = TRUE) %>%
-   scroll_box(width = "900px", height = "500px")
+   flextable()%>%
+   set_caption("Table 1: Description of Experiments") %>%
+   set_header_labels(trial_ref = "Unique Trial Reference",
+                     year = "Year",
+                     location = "Trial Location",
+                     planting_date = "Planting Date",
+                     first_sign_disease = "First sign of disease date",
+                     Research_org = "Research organisation")%>%
+   autofit(add_w = 0.5)%>%
+   align(j = c(1,4,5), align = "center", part = "all")%>%
+   fontsize(size = 9)%>%
+   width(j = 1:4, 1)%>%
+   width(j = 5, 1.1)%>%
+   width(j = 6, 1.7)
 ```
@@
 ) %>%
-   kable(caption = "Table 2: Powdery Mildew severity scoring scale") %>%
-   kable_styling(fixed_thead = T, full_width = T)
+   flextable()%>%
+   set_caption("Table 2: Powdery Mildew severity scoring scale") %>%
+   set_header_labels(Scale.Description = "Scale Description")%>%
+   autofit()%>%
+   fontsize(size = 9)%>%
+   align(j = c(1), align = "center", part = "all")%>%
+   width(j = 2, 6.2)
 ```
@@
 
-```{r table3_Contrasts}
+```{r table3_Contrasts, echo = FALSE}
 T3 <- read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
+T3[,2:5] <- round(T3[,2:5], 4)
 T3 %>%
-   kable()
+   mutate(contrasts = gsub("-","",contrasts))%>%
+   mutate(contrasts = gsub(" \\+"," -",contrasts))%>%
+   mutate(contrasts = gsub(" = 0","",contrasts))%>%
+   flextable()%>%
+   set_caption("Table 3: Estimated grain yield contrasts between each spray scheduale") %>%
+   autofit(add_w = 0.2)%>%
+   align(j = c(2,3,4), align = "center", part = "all") %>%
+   set_header_labels(contrasts = "Treatment contrasts",
+                     estimates = "Estimate",
+                     se = "Std Error",
+                     z_val = "Z-Score",
+                     pval = "P-Value",
+                     VisP = " ")%>%
+   fontsize(size = 9)%>%
+   width(j = 5,0.7)%>%
+   width(j = 6, .3)
 ```

### 2020-07-27 vignette/Manuscript2Word.Rmd
Update manuscript to use flextable instead of kable

@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, knitr, here)
+pacman::p_load(tidyverse, knitr, here, kableExtra, flextable, officer)
+options(knitr.table.format = "html")
 
@@
    )) %>%
-   kable(caption = "Table 1: Description of Experiments", booktabs = T, align = "c")
+   flextable()%>%
+   set_caption("Table 1: Description of Experiments") %>%
+   set_header_labels(trial_ref = "Unique Trial Reference",
+                     year = "Year",
+                     location = "Trial Location",
+                     planting_date = "Planting Date",
+                     first_sign_disease = "First sign of disease date",
+                     Research_org = "Research organisation")%>%
+   autofit(add_w = 0.5)%>%
+   align(j = c(1,4,5), align = "center", part = "all")%>%
+   fontsize(size = 9)%>%
+   width(j = 1:4, 1)%>%
+   width(j = 5, 1.1)%>%
+   width(j = 6, 1.7)
 ```
@@
 ) %>%
-   kable(caption = "Table 2: Powdery Mildew severity scoring scale",  align = "cl") 
+   flextable()%>%
+   set_caption("Table 2: Powdery Mildew severity scoring scale") %>%
+   set_header_labels(Scale.Description = "Scale Description")%>%
+   autofit()%>%
+   fontsize(size = 9)%>%
+   align(j = c(1), align = "center", part = "all")%>%
+   width(j = 2, 6.2)
 ```
@@
 T3 <- read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
+T3[,2:5] <- round(T3[,2:5], 4)
 T3 %>%
-   kable()
+   mutate(contrasts = gsub("-","",contrasts))%>%
+   mutate(contrasts = gsub(" \\+"," -",contrasts))%>%
+   mutate(contrasts = gsub(" = 0","",contrasts))%>%
+   flextable()%>%
+   set_caption("Table 3: Estimated grain yield contrasts between each spray scheduale") %>%
+   autofit(add_w = 0.2)%>%
+   align(j = c(2,3,4), align = "center", part = "all") %>%
+   set_header_labels(contrasts = "Treatment contrasts",
+                     estimates = "Estimate",
+                     se = "Std Error",
+                     z_val = "Z-Score",
+                     pval = "P-Value",
+                     VisP = " ")%>%
+   fontsize(size = 9)%>%
+   width(j = 5,0.7)%>%
+   width(j = 6, .3)
+
 ```

### 2020-07-27 04_MetaAnalysis.Rmd
add an extra dataset to the export

@@
 write.csv(slimmer_PM_dat, file = "data/GYmeta_data.csv")
-save(dat1, efficacy, PM_mv, YieldContrasts, file = here("cache/Meta-analysisData.Rdata"))
+save(dat1, efficacy, slimmer_PM_dat PM_mv, YieldContrasts, file = here("cache/Meta-analysisData.Rdata"))
 ```

### 2020-07-27 07_Manuscript.Rmd
More edits and words in the materials and methods

@@
----
-output: 
-html_document:
-
----
-
 ```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
@@
 ## Materials and Methods
-The data for this study were obtained from through personal correspondence with colleagues and collaborating institutions.
-Trials undertaken in the 2013 season were conducted by the Northern Growers Alliance (NGA) [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013].
+The data for this study were obtained through personal correspondence with colleagues and collaborating institutions.
+Trials undertaken in the 2013 season were conducted by the Northern Growers Alliance (NGA) [-@goolhi2013; -@premer2013; -@Millmerran2013; -@Marysmount2013].
 <!-- should check, Sue and Mal moved to USQ in 2015 I think. Therefore the trials probably started with USQ earlier --> 
@@
 Trial data were in different formats with varying levels of information.
-Some trials we obtained the raw data others the reported means of each treatment, with all but one study reporting some form of variance along with the mean. 
+Some trials we obtained the raw data, others the reported means of each treatment, with all but one study reporting some form of variance along with the mean. 
 Twenty six trials in total were collated.
 
-To ensure the correct question was asked of the analysis the data needed to conform to a strict criteria. 
+To ensure the correct question was asked of the analysis, the data needed to conform to a strict criteria. 
 The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the Grains Research and Development (GRDC) northern grains regions of eastern Australia, which grows the majority of Australia's summer crops.
 Trial data had to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; the fungicide active ingredients; fungicide dose; and crop yield.
-The data were subset to only include treatments with the same mode of action; demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole were thus retained in the dataset. 
-Subsequently the 26 trials were reduced to 16 using the same fungicide doses (Table 1). 
-Details of trial data are presented within a research compendium which was prepared to supplement this publication [<!-- DOI to reference to compendium -->].
-With only a small number of trials, and to increase the replication, we made no distinction between the tebuconazole and propiconazole in the analysis. 
-All trials included in this analysis were randomised complete block designs and not previously published in peer-reviewed literature.
+The data were subset to only include fungicide treatments with the same mode of action; demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole were thus retained in the dataset. 
+Subsequently the 26 trials were reduced to 16 trials (Table 1). 
+Details of trial data are presented within a research compendium which was prepared as a supplement to this publication [<!-- DOI to reference to compendium -->].
+Due to the limited number of trials meeting the selection criteria, we made no distinction between the tebuconazole and propiconazole fungicide treatments within the analysis to ensure sufficient replication.
+All trials included in this analysis used a randomised complete block design, and were not previously published in peer-reviewed literature.
+
+From the trials which were included `r sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12)` planted in late December, `r sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 1)` in January and `r sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12)` trials planted in February (Table 1).
 
@@
 These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications and cultivar.
-To account for the variation attributed to some of these variables between trials, and the treatments within trials, a single 'trial' factor was created to describe the main variables; a trial reference code, trial location, trial season, host genotype, row spacing, and fungicide dose.
+To account for the variation attributed to some of these variables between trials, and the treatments within trials, a single $trial$ factor was created.
+The $trial$ variable made distinctions between the following between and within trial variables: unique trial reference code, trial location, trial season, host genotype, row spacing, and fungicide dose.
 Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 -- 9 ordinal scale (Table 2). 
-However, the 2013 NGA trials (Table 1) reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the canopy; lower, middle or upper canopy.
+However, the 2013 NGA trials (Table 1) reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the lower, middle or upper canopy.
 
@@
 The timing of fungicide application treatments, was defined in relation to the recorded date when powdery mildew first occurred in the trial. 
-An 'Early' fungicide application treatment, referred to a fungicide spray schedule that commenced the first spray prior to the disease being observed in the trial. 
-'Recommended' refers to a fungicide spray schedule which commences following the first sign of disease, within three days. 
-'Late' treatments commence between 7 - 13 days after the first sign of disease. 
+An 'Early' fungicide application treatment, referred to a fungicide spray schedule that commenced prior to the disease being observed in the trial. 
+'Recommended' referred to a fungicide spray schedule which commenced 1 -- 3 days following the first sign of disease. 
+'Late' treatments commenced between 7 -- 13 days after the first sign of disease. 
+There were no spray schedule treatments which began between 4 -- 6 days after the first sign of powdery mildew. 
 The number of fungicide applications were binned in to two categories.
 A spray schedule with a single spray, and a spray schedule with two or three spray applications (Plus). 
-The division of the treatments categorised: 13 'Early' treatments; 5 'EarlyPlus', 32 'Recommended'; 46 'RecommendedPlus'; 17 'Late'; and 20 'LatePlus.
+The division of the treatments produced: 13 'Early' treatments; 5 'EarlyPlus', 32 'Recommended'; 46 'RecommendedPlus'; 17 'Late'; and 20 'LatePlus.
 'EarlyPlus' treatments were removed from the subsequent meta-analysis, due to an insufficient sample size.  
-
-<!-- Passage here about trial sowing times and first sign of disease (Figure 1)  PM -->
-
 What remained was the mean yield for total of 173 treatments in the following five spray schedule categories: no spray control, single early spray, single recommended spray, recommended with multiple sprays, single late spray, and late with multiple sprays.
@@
 where $Y_i$ is the response, a vector of the MD grain yield for each treatment in the $i$th trial over total number ($K$) of trials($i$  = 1, ...$K$). 
-$Y_i$ is estimated from a normal distribution with the mean $\mu$, sample variance of $Si_^2$ and a between trial variance of $\sigma^2$.
+$Y_i$ is estimated from a normal distribution with the mean $\mu$, sample variance of $S_i^2$ and a between trial variance of $\sigma^2$.
 
@@
 
+<br>
+
 ```{r Figure2_treatForest, echo = FALSE}
@@
 ```
+<br>
+<br>
+```{r Table1_ExperimentalDetail, echo=FALSE, message=FALSE, warning=FALSE}
+# Add a star to the trials which were not in the final analysis
+PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref, "trial_ref"] <-
+   sapply(PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref,"trial_ref"], paste0, "*")
 
-```{r Table1_ExperimentalDetail, echo=FALSE, message=FALSE, warning=FALSE}
+# Build table 
 PM_Mdat %>%
@@
 ```
-
+<br>
+<br>
 ```{r Table2_1to9Scale, echo=FALSE}
@@
 
-```{r Figure1}
+```{r Figure1, echo=FALSE}
 SeasonPlot
 ```
+
+<br>
+<br>
 

### 2020-07-28 02_Preliminary_analysis.Rmd
Added more commenting to code chunck as per Issue #30

@@
 for (i in unique(PM_MB_means$trial_ref)) {
+   # Loop code over each trial reference
    dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
@@
    if (any(is.na(unique(dat1$row_spacing)))) {
+      # If there is no recorded row.spacing don't calculate proportional yield, skip to the next trial
       warning(
@@
    for (j in unique(dat1$row_spacing)) {
+      # Loop within trial row_spacing
       dat2 <- dat1[dat1$row_spacing == j, ]
       controlY <-
-         mean(dat2[dat2$fungicide_ai == "control", "grain_yield.t.ha."])
+         mean(dat2[dat2$fungicide_ai == "control", "grain_yield.t.ha."]) #Mean taken as some trials had multiple control reps
 
+      # Calculate the yield gain relative to the no spray control (controlY)
       dat2$yield_gain <- dat2$grain_yield.t.ha. - controlY
@@
 
+      # insert NA as yeild_gain and proportional yield gain for the controls
       dat2[dat2$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
@@
 
+      # Reassign values to row_spacing subset
       dat1[dat1$row_spacing == j, ] <- dat2
    }
+   # Reassign values to trial_ref subset
    PM_MB_means[PM_MB_means$trial_ref == i, ] <- dat1
@@
 # calculate yield gain and prop_yield gain for experiments with no row spacing data
-
 dat1 <- PM_MB_means[PM_MB_means$trial_ref == "AM1303", ]

### 2020-07-28 07_Manuscript.Rmd
Added more words and editing

@@
 
-From the trials which were included `r sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12)` planted in late December, `r sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 1)` in January and `r sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12)` trials planted in February (Table 1).
+From the trials which were included `r sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12)` planted in late December, `r sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 1)` in January and `r sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 2)` trials planted in February (Table 1).
 
@@
 'Recommended' referred to a fungicide spray schedule which commenced 1 -- 3 days following the first sign of disease. 
-'Late' treatments commenced between 7 -- 13 days after the first sign of disease. 
-There were no spray schedule treatments which began between 4 -- 6 days after the first sign of powdery mildew. 
+'Late' treatments commenced between 7 and 13 days after the first sign of disease. 
+There were no spray schedule treatments which began between 4 and 6 days after the first sign of powdery mildew. 
 The number of fungicide applications were binned in to two categories.

### 2020-07-28 vignette/Manuscript2Word.Rmd
Added more words and editing

--- 2020-07-24 vignette/Manuscript2Word.Rmd
@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, knitr, here)
+pacman::p_load(tidyverse, kableExtra, here, flextable, officer, english)
 
@@
 
-***
-
+# Manuscript
 <!-- need to ensure the format of this manuscript adheres to the MDPI Agronomy style guide -->
@@
 Trial data were in different formats with varying levels of information.
-Some trials we obtained the raw data others the reported means of each treatment, with all but one study reporting some form of variance along with the mean. 
+Some trials we obtained the raw data, others the reported means of each treatment, with all but one study reporting some form of variance along with the mean. 
 Twenty six trials in total were collated.
 
-To ensure the correct question was asked of the analysis the data needed to conform to a strict criteria. 
+To ensure the correct question was asked of the analysis, the data needed to conform to a strict criteria. 
 The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the Grains Research and Development (GRDC) northern grains regions of eastern Australia, which grows the majority of Australia's summer crops.
 Trial data had to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; the fungicide active ingredients; fungicide dose; and crop yield.
-The data were subset to only include treatments with the same mode of action; demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole were thus retained in the dataset. 
-Subsequently the 26 trials were reduced to 16 using the same fungicide doses (Table 1). 
-Details of trial data are presented within a research compendium which was prepared to supplement this publication [<!-- DOI to reference to compendium -->].
-With only a small number of trials, and to increase the replication, we made no distinction between the tebuconazole and propiconazole in the analysis. 
-All trials included in this analysis were randomised complete block designs and not previously published in peer-reviewed literature.
+The data were subset to only include fungicide treatments with the same mode of action; demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole were thus retained in the dataset. 
+Subsequently the 26 trials were reduced to 16 trials (Table 1). 
+Details of trial data are presented within a research compendium which was prepared as a supplement to this publication [<!-- DOI to reference to compendium -->].
+Due to the limited number of trials meeting the selection criteria, we made no distinction between the tebuconazole and propiconazole fungicide treatments within the analysis to ensure sufficient replication.
+All trials included in this analysis used a randomised complete block design, and were not previously published in peer-reviewed literature.
+
+From the trials which were included `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12))` planted in late December, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 1))` in January and `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 2))` trials planted in February (Table 1).
 
@@
 The timing of fungicide application treatments, was defined in relation to the recorded date when powdery mildew first occurred in the trial. 
-An 'Early' fungicide application treatment, referred to a fungicide spray schedule that commenced the first spray prior to the disease being observed in the trial. 
-'Recommended' refers to a fungicide spray schedule which commences following the first sign of disease, within three days. 
-'Late' treatments commence between 7 - 13 days after the first sign of disease. 
+An 'Early' fungicide application treatment, referred to a fungicide spray schedule that commenced prior to the disease being observed in the trial. 
+'Recommended' referred to a fungicide spray schedule which commenced 1 -- 3 days following the first sign of disease. 
+'Late' treatments commenced between 7 and 13 days after the first sign of disease. 
+There were no spray schedule treatments which began between 4 and 6 days after the first sign of powdery mildew. 
 The number of fungicide applications were binned in to two categories.
 A spray schedule with a single spray, and a spray schedule with two or three spray applications (Plus). 
-The division of the treatments categorised: 13 'Early' treatments; 5 'EarlyPlus', 32 'Recommended'; 46 'RecommendedPlus'; 17 'Late'; and 20 'LatePlus.
+The division of the treatments produced: 13 'Early' treatments; 5 'EarlyPlus', 32 'Recommended'; 46 'RecommendedPlus'; 17 'Late'; and 20 'LatePlus.
 'EarlyPlus' treatments were removed from the subsequent meta-analysis, due to an insufficient sample size.  
-
-<!-- Passage here about trial sowing times and first sign of disease (Figure 1)  PM -->
-
 What remained was the mean yield for total of 173 treatments in the following five spray schedule categories: no spray control, single early spray, single recommended spray, recommended with multiple sprays, single late spray, and late with multiple sprays.
@@
 ```
+<br>
+<br>
+```{r Table1_ExperimentalDetail, echo=FALSE, message=FALSE, warning=FALSE}
+# Add a star to the trials which were not in the final analysis
+PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref, "trial_ref"] <-
+   sapply(PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref,"trial_ref"], paste0, "*")
 
-<br>
-
-```{r Table1_ExperimentalDetail, echo=FALSE, message=FALSE, warning=FALSE}
+# Build table 
 PM_Mdat %>%
@@
    )) %>%
-   kable(caption = "Table 1: Description of Experiments", booktabs = T, align = "c")
+   flextable()%>%
+   set_caption("Table 1: Description of Experiments") %>%
+   set_header_labels(trial_ref = "Unique Trial Reference",
+                     year = "Year",
+                     location = "Trial Location",
+                     planting_date = "Planting Date",
+                     first_sign_disease = "First sign of disease date",
+                     Research_org = "Research organisation")%>%
+   autofit(add_w = 0.5)%>%
+   align(j = c(1,4,5), align = "center", part = "all")%>%
+   fontsize(size = 9)%>%
+   width(j = 1:4, 1)%>%
+   width(j = 5, 1.1)%>%
+   width(j = 6, 1.7)
 ```
-
 <br>
 <br>
-
 ```{r Table2_1to9Scale, echo=FALSE}
@@
 ) %>%
-   kable(caption = "Table 2: Powdery Mildew severity scoring scale",  align = "cl") 
+   flextable()%>%
+   set_caption("Table 2: Powdery Mildew severity scoring scale") %>%
+   set_header_labels(Scale.Description = "Scale Description")%>%
+   autofit()%>%
+   fontsize(size = 9)%>%
+   align(j = c(1), align = "center", part = "all")%>%
+   width(j = 2, 6.2)
 ```
-<br>
 
@@
 
-<br>
-
-```{r Figure1}
+```{r Figure1, echo=FALSE}
 SeasonPlot
@@
 <br>
+<br>
 
-```{r table3_Contrasts}
+```{r table3_Contrasts, echo = FALSE}
 T3 <- read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
+T3[,2:5] <- round(T3[,2:5], 4)
 T3 %>%
-   kable()
+   mutate(contrasts = gsub("-","",contrasts))%>%
+   mutate(contrasts = gsub(" \\+"," -",contrasts))%>%
+   mutate(contrasts = gsub(" = 0","",contrasts))%>%
+   flextable()%>%
+   set_caption("Table 3: Estimated grain yield contrasts between each spray scheduale") %>%
+   autofit(add_w = 0.2)%>%
+   align(j = c(2,3,4), align = "center", part = "all") %>%
+   set_header_labels(contrasts = "Treatment contrasts",
+                     estimates = "Estimate",
+                     se = "Std Error",
+                     z_val = "Z-Score",
+                     pval = "P-Value",
+                     VisP = " ")%>%
+   fontsize(size = 9)%>%
+   width(j = 5,0.7)%>%
+   width(j = 6, .3)
 ```
-
-<br>
 

### 2020-07-28 04_MetaAnalysis.Rmd
Missing comma

--- 2020-07-23 04_MetaAnalysis.Rmd
@@
 write.csv(slimmer_PM_dat, file = "data/GYmeta_data.csv")
-save(dat1, efficacy, PM_mv, YieldContrasts, file = here("cache/Meta-analysisData.Rdata"))
+save(dat1, efficacy, slimmer_PM_dat, PM_mv, YieldContrasts, file = here("cache/Meta-analysisData.Rdata"))
 ```

### 2020-07-28 07_Manuscript.Rmd
Work on the Materials and methods, improve flow and order of ideas. Formatting of treatment variables

@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, here, flextable, officer)
+pacman::p_load(tidyverse, kableExtra, here, flextable, officer, english)
 
@@
 ## Materials and Methods
+**Trial criteria for inclusion and description**
 The data for this study were obtained through personal correspondence with colleagues and collaborating institutions.
@@
 <!-- should check, Sue and Mal moved to USQ in 2015 I think. Therefore the trials probably started with USQ earlier --> 
-The most recent trials starting from 2015 were undertaken by the University of Southern Queensland (USQ) with the assistance of Queensland DAF from 2015 to 2019. 
-Trial data were in different formats with varying levels of information.
+Trial data were obtained in different formats with varying levels of information.
 Some trials we obtained the raw data, others the reported means of each treatment, with all but one study reporting some form of variance along with the mean. 
@@
 The data were subset to only include fungicide treatments with the same mode of action; demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole were thus retained in the dataset. 
-Subsequently the 26 trials were reduced to 16 trials (Table 1). 
+Subsequently the 26 trials were reduced to 17 trials (Table 1). 
+Two more trials were also removed because no form of variance was reported with the fungicide treatment means of grain yield, reducing the number of trials down to 15.
+
+From the trials which were included `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12))` planted in late December, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 1))` in January and `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 2))` trials planted in February (Table 1).
+
+In the meta-analysis, to ensure sufficient replication, we made no distinction between the tebuconazole and propiconazole fungicide treatments within the trials that met the selection criteria. 
+The design of all trials included in this analysis were randomised complete block designs, and were not previously published in peer-reviewed literature. 
 Details of trial data are presented within a research compendium which was prepared as a supplement to this publication [<!-- DOI to reference to compendium -->].
-Due to the limited number of trials meeting the selection criteria, we made no distinction between the tebuconazole and propiconazole fungicide treatments within the analysis to ensure sufficient replication.
-All trials included in this analysis used a randomised complete block design, and were not previously published in peer-reviewed literature.
 
-From the trials which were included `r sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12)` planted in late December, `r sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 1)` in January and `r sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 2)` trials planted in February (Table 1).
-
-While the main aim of all the trials collected for this study were to assess the efficacy of fungicide for control of powdery mildew, some trials tested additional variables in the experimental design.
-These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications and cultivar.
-To account for the variation attributed to some of these variables between trials, and the treatments within trials, a single $trial$ factor was created.
-The $trial$ variable made distinctions between the following between and within trial variables: unique trial reference code, trial location, trial season, host genotype, row spacing, and fungicide dose.
-Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 -- 9 ordinal scale (Table 2). 
-However, the 2013 NGA trials (Table 1) reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the lower, middle or upper canopy.
-
-Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, a conversion to mean plot incidence on the ordinal 1 -- 9 scale was straight-forward.
-
-The timing of fungicide application treatments, was defined in relation to the recorded date when powdery mildew first occurred in the trial. 
-An 'Early' fungicide application treatment, referred to a fungicide spray schedule that commenced prior to the disease being observed in the trial. 
-'Recommended' referred to a fungicide spray schedule which commenced 1 -- 3 days following the first sign of disease. 
-'Late' treatments commenced between 7 and 13 days after the first sign of disease. 
-There were no spray schedule treatments which began between 4 and 6 days after the first sign of powdery mildew. 
-The number of fungicide applications were binned in to two categories.
-A spray schedule with a single spray, and a spray schedule with two or three spray applications (Plus). 
-The division of the treatments produced: 13 'Early' treatments; 5 'EarlyPlus', 32 'Recommended'; 46 'RecommendedPlus'; 17 'Late'; and 20 'LatePlus.
-'EarlyPlus' treatments were removed from the subsequent meta-analysis, due to an insufficient sample size.  
-What remained was the mean yield for total of 173 treatments in the following five spray schedule categories: no spray control, single early spray, single recommended spray, recommended with multiple sprays, single late spray, and late with multiple sprays.
-
-A categorical disease pressure factor was created by binning trials based on the mean AUDPC of the no spray control plot into two levels: 'low disease pressure' or 'high disease pressure'.
-The two levels were separated via the median AUDPC (`r as.double(read.csv(here("cache/median_AUDPC_C.csv")))`) of the no spray control plots.
-
+**Response variable - Grain yield**
+Grain yield (tonne per hectare), was used as the response variable for the meta-analysis. 
 Mean grain yields for each treatment were either obtained directly from trial reports, or calculated from the raw data when available.
@@
 The T-critical value was determined from the 30 degrees of freedom and probability of $a = 0.05$ using a t-distribution table.
-The 2012 Gatton and 2015 Emerald trials reported treatment means without accompanying variance and were thus removed from the dataset  prior to the analysis.
-
-This analysis uses response ratio, or means difference (MD) as the response variable. 
-MD were chosen to reduce the inherent variability between trials due to location and seasonal effects on grain yields by assessing the effect of fungicide spray schedule on the difference between the treatments and no spray control plot.
-$MD = {Y_i-\overline{Y_c}}$ [@HigginsGreen] 
-Where $Y_i$ is the treatment mean, $Y_c$ is the no spray control treatment mean .
 
@@
 $Y_i \sim N(\mu,s_i^2 + \sigma^2)$
-where $Y_i$ is the response, a vector of the MD grain yield for each treatment in the $i$th trial over total number ($K$) of trials($i$  = 1, ...$K$). 
+where $Y_i$ is the response, a vector of the grain yield measurements (tonne per hectare) for each treatment in the $i$th trial over total number ($K$) of trials($i$  = 1, ...$K$). 
 $Y_i$ is estimated from a normal distribution with the mean $\mu$, sample variance of $S_i^2$ and a between trial variance of $\sigma^2$.
 
-**Moderator variables.** The random effects meta-analysis was expanded to evaluate if the residual heterogeneity could be explained by spray schedule ($SPRAY_{Sched}$). 
-`SpraySchedule` was assigned as an inside factor to the outside factor `trial` to provide correlated random effects between the different `SpraySchedule` treatments within `trials`.
+**Trial Variables and moderators**
+While the main aim of all the identified trials were to assess the efficacy of fungicide for control of powdery mildew, some trials tested additional potential covariates in the experimental design.
+These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications and cultivar.
+To account for the variation attributed to some of these variables between trials, and within trials, a single $trial$ factor was created.
+The $trial$ random variable made distinctions between the following variables: unique trial reference code, trial location, trial season, host genotype, row spacing, and fungicide dose.
 
-The intercept was omitted from the model so each treatment would be reported against zero, which represents the control mean. 
+The random effects meta-analysis was expanded to evaluate if the residual heterogeneity could be explained by spray schedule). 
+Spray schedule was assigned as an inside factor to the outside random factor $trial$ to provide correlated random effects between the different spray schedule treatments within $trials$.
+
+The timing of fungicide application treatments, were defined in relation to the recorded date when powdery mildew first occurred in the trial. 
+An $Early$ fungicide application treatment, referred to a fungicide spray schedule that commenced prior to the disease being observed in the trial. 
+$Recommended$ referred to a fungicide spray schedule which commenced 1 -- 3 days following the first sign of disease. 
+$Late$ treatments commenced between 7 and 13 days after the first sign of disease. 
+There were no spray schedule treatments which began between 4 and 6 days after the first sign of powdery mildew. 
+The number of fungicide applications were binned in to two categories.
+A spray schedule with a $single$ spray, and a spray schedule with two or three spray applications $plus$. 
+The division of the treatments produced: 13 $Early_{single}$ treatments; 5 $Early_{plus}$; 32 $Recommended_{single}$; 46 $Recommended_{plus}$'; 17 $Late_{single}$; and 20 $Late_{plus}$.
+$Early_{plus}$ treatments were removed from the subsequent meta-analysis, due to an insufficient sample size.  
+What remained was the mean yield for a total of 173 treatments in the following five spray schedule categories: no spray control, single early spray, single recommended spray, recommended with multiple sprays, single late spray, and late with multiple sprays.
+
+An ordinal 1 -- 9 ordinal scale was used to describe the mean plot powdery mildew severity in most trials (Table 2). 
+However, the 2013 NGA trials (Table 1) reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the lower, middle or upper canopy. 
+Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, a conversion to mean plot severity on the ordinal 1 -- 9 scale was straight-forward. 
+The end of season mean plot severity, and and date of first sign of disease were used to calculate the area under the disease progress curve (AUDPC) for each treatment. 
+Additional powdery mildew mean plot severity observations made in-between these two observations were also included in the AUDPC calculation if they were available. 
+AUDPC was calculated using the `agricolae` package in R [@agricolae2020]. 
+A categorical disease pressure factor was created by binning trials based on the mean AUDPC of the no spray control plot into two levels: 'low disease pressure' or 'high disease pressure'.
+The two levels were separated by the median AUDPC (`r as.double(read.csv(here("cache/median_AUDPC_C.csv")))`) of the no spray control plots.
+
 Linear contrasts were used to compare the mean effect sizes between each spray schedule treatment and their respective standard errors and confidence intervals.

### 2020-07-28 vignette/Manuscript2Word.Rmd
Knit changes to manuscript word document

@@
 The data were subset to only include fungicide treatments with the same mode of action; demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole were thus retained in the dataset. 
-Subsequently the 26 trials were reduced to 16 trials (Table 1). 
-Details of trial data are presented within a research compendium which was prepared as a supplement to this publication [<!-- DOI to reference to compendium -->].
-Due to the limited number of trials meeting the selection criteria, we made no distinction between the tebuconazole and propiconazole fungicide treatments within the analysis to ensure sufficient replication.
-All trials included in this analysis used a randomised complete block design, and were not previously published in peer-reviewed literature.
+Subsequently the 26 trials were reduced to 17 trials (Table 1). 
+Two more trials were also removed because no form of variance was reported with the fungicide treatment means of grain yield, reducing the number of trials down to 15.
 
@@
 
-While the main aim of all the trials collected for this study were to assess the efficacy of fungicide for control of powdery mildew, some trials tested additional variables in the experimental design.
-These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications and cultivar.
-To account for the variation attributed to some of these variables between trials, and the treatments within trials, a single $trial$ factor was created.
-The $trial$ variable made distinctions between the following between and within trial variables: unique trial reference code, trial location, trial season, host genotype, row spacing, and fungicide dose.
-Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 -- 9 ordinal scale (Table 2). 
-However, the 2013 NGA trials (Table 1) reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the lower, middle or upper canopy.
+In the meta-analysis, to ensure sufficient replication, we made no distinction between the tebuconazole and propiconazole fungicide treatments within the trials that met the selection criteria. 
+The design of all trials included in this analysis were randomised complete block designs, and were not previously published in peer-reviewed literature. 
+Details of trial data are presented within a research compendium which was prepared as a supplement to this publication [<!-- DOI to reference to compendium -->].
 
-Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, a conversion to mean plot incidence on the ordinal 1 -- 9 scale was straight-forward.
-
-The timing of fungicide application treatments, was defined in relation to the recorded date when powdery mildew first occurred in the trial. 
-An 'Early' fungicide application treatment, referred to a fungicide spray schedule that commenced prior to the disease being observed in the trial. 
-'Recommended' referred to a fungicide spray schedule which commenced 1 -- 3 days following the first sign of disease. 
-'Late' treatments commenced between 7 and 13 days after the first sign of disease. 
-There were no spray schedule treatments which began between 4 and 6 days after the first sign of powdery mildew. 
-The number of fungicide applications were binned in to two categories.
-A spray schedule with a single spray, and a spray schedule with two or three spray applications (Plus). 
-The division of the treatments produced: 13 'Early' treatments; 5 'EarlyPlus', 32 'Recommended'; 46 'RecommendedPlus'; 17 'Late'; and 20 'LatePlus.
-'EarlyPlus' treatments were removed from the subsequent meta-analysis, due to an insufficient sample size.  
-What remained was the mean yield for total of 173 treatments in the following five spray schedule categories: no spray control, single early spray, single recommended spray, recommended with multiple sprays, single late spray, and late with multiple sprays.
-
-A categorical disease pressure factor was created by binning trials based on the mean AUDPC of the no spray control plot into two levels: 'low disease pressure' or 'high disease pressure'.
-The two levels were separated via the median AUDPC (`r as.double(read.csv(here("cache/median_AUDPC_C.csv")))`) of the no spray control plots.
-
+**Response variable - Grain yield**
+Grain yield (tonne per hectare), was used as the response variable for the meta-analysis. 
 Mean grain yields for each treatment were either obtained directly from trial reports, or calculated from the raw data when available.
@@
 ## References
-
-<br>

### 2020-07-29 07_Manuscript.Rmd
Update the order of headings and add page break style for heading 5 to templates

@@
 
-# Manuscript
-<!-- need to ensure the format of this manuscript adheres to the MDPI Agronomy style guide -->
+<!-- 
+Need to ensure the format of this manuscript adheres to the MDPI Agronomy style guide 
+https://www.agronomy.org/publications/journals/author-resources/aj-instructions#headline-article-requirements 
+-->
 <!-- To ensure formatting matches, I suggest that you create a Word template and knit this document using that -->
+
+## Core ideas
+<!-- up to 85 words per idea -->
+
+## Authors - affiliations and email address
+
+##### PAGE BREAK
+
+## Abstract
+
+## Abrebiations
+
+##### PAGE BREAK
 
@@
 
+## Conclusion
+
+## Supplemental Material
+Supplementary material can be found in the following research compendium.
+<!-- Insert DOI, perhaps we can render the completed bookdown to PDF to add as the supplementary materials (Paul)-->
+
+## Data Availability
+All data and code used in the preparation of this manuscript can be found in the associated research compendium.
+<!-- Should we submit the raw data to a data repository like OSF and Figshare? (Paul) -->
+
+## Conflict of Interest Statement
+The authors of this paper have no conflicting interest in the research presented in this manuscript
+
 ## Acknowledgments

### 2020-07-29 vignette/Manuscript2Word.Rmd
Add Lua author information

@@
 title: "A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean"
-author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
+author:
+  - Paul Melloy:
+      email: Paul.Melloy@usq.edu.au
+      institute: USQ
+      correspondence: true
+  - Emerson Del Ponte:
+      institute: UFV
+  - Adam H. Sparks:
+      institute: USQ
+institute:
+  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland, Australia
+  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
 date: "`r format(Sys.time(), '%d %B, %Y')`"
@@
       reference_docx: "Manuscript2Word_Template.docx"
+      pandoc_args:
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
 bibliography: "../Mungbean.bib"

### 2020-07-29 07_Manuscript.Rmd
attempting to implement lua styles

@@
+---
+title: "A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean"
+author:
+   - Paul Melloy:
+      email: Paul.Melloy@usq.edu.au
+      institute: USQ
+      correspondence: true
+   - Emerson Del Ponte:
+      institute: UFV
+   - Adam H. Sparks:
+      institute: USQ
+institute:
+  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Qld 4350, Australia
+  - UFV: Universidade Federal de Viçosa, Departamento de Fitopatologia, 36570-000 MG, Brazil 
+date: "`r format(Sys.time(), '%d %B, %Y')`"
+output: 
+  bookdown::word_document2:
+    toc: no
+    pandoc_args:
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
+      reference_docx: "Manuscript2Word_Template.docx"
+bibliography: "../Mungbean.bib"
+biblio-style: apalike
+link-citations: yes
+abstract: |
+         Insert abstract here.
+---
+
 ```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}

### 2020-07-29 vignette/Manuscript2Word.Rmd
attempting to implement lua styles

--- 2020-07-29 vignette/Manuscript2Word.Rmd
@@
 ---
-title: "A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean"
-author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
+title: "A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean"
+author:
+   - Paul Melloy:
+      email: Paul.Melloy@usq.edu.au
+      institute: USQ
+      correspondence: true
+   - Emerson Del Ponte:
+      institute: UFV
+   - Adam H. Sparks:
+      institute: USQ
+institute:
+  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Qld 4350, Australia
+  - UFV: Universidade Federal de Viçosa, Departamento de Fitopatologia, 36570-000 MG, Brazil 
 date: "`r format(Sys.time(), '%d %B, %Y')`"
@@
    word_document:
+      toc: no
+      pandoc_args:
+         - '--lua-filter=scholarly-metadata.lua'
+         - '--lua-filter=author-info-blocks.lua'
          reference_docx: "Manuscript2Word_Template.docx"
@@
 link-citations: yes
+abstract: |
+         Insert abstract here.
 ---
+<!-- Should we use the word "fungicide" in the title so it is more searchable for fungicide management? -->
 

### 2020-07-29 vignette/Manuscript2Word.Rmd

@@
 institute:
-  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Qld 4350, Australia
+  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland, Australia
   - UFV: Universidade Federal de Viçosa, Departamento de Fitopatologia, 36570-000 MG, Brazil
@@
    word_document:
-      toc: no
+      reference_docx: "Manuscript2Word_Template.docx"
       pandoc_args:
@@
       - '--lua-filter=author-info-blocks.lua'
-         reference_docx: "Manuscript2Word_Template.docx"
 bibliography: "../Mungbean.bib"

### 2020-07-29 07_Manuscript.Rmd
Add pander library

--- 2020-07-29 07_Manuscript.Rmd
@@
+---
+title: "A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean"
+author:
+   - Paul Melloy:
+      email: Paul.Melloy@usq.edu.au
+      institute: USQ
+      correspondence: true
+   - Emerson Del Ponte:
+      institute: UFV
+   - Adam H. Sparks:
+      institute: USQ
+institute:
+  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Qld 4350, Australia
+  - UFV: Universidade Federal de Viçosa, Departamento de Fitopatologia, 36570-000 MG, Brazil 
+date: "`r format(Sys.time(), '%d %B, %Y')`"
+output: 
+  bookdown::word_document2:
+    toc: no
+    pandoc_args:
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
+      reference_docx: "Manuscript2Word_Template.docx"
+bibliography: "../Mungbean.bib"
+biblio-style: apalike
+link-citations: yes
+abstract: |
+         *Abstract* Insert abstract here.
+---
+
 ```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, here, flextable, officer, english)
+pacman::p_load(tidyverse, kableExtra, here, flextable, officer, english,pander)
 

### 2020-07-29 vignette/Manuscript2Word.Rmd
Spelling
Add custom styles to template

@@
   - UFV: Universidade Federal de Viçosa, Departamento de Fitopatologia, 36570-000 MG, Brazil
-date: "`r format(Sys.time(), '%d %B, %Y')`"
+date: "Last Edit: `r format(Sys.time(), '%d %B, %Y')`"
 output:
@@
       reference_docx: "Manuscript2Word_Template.docx"
+      md_extensions: +styles
       pandoc_args:
@@
 abstract: |
-         Insert abstract here.
+         **Abstract:** Insert abstract here.
 ---
-<!-- Should we use the word "fungicide" in the title so it is more searchable for fungicide management? -->
 
@@
 ```
+::: {custom-style="Art_type"}
+Type of Paper: Article
+:::
+
+::: {custom-style="keywords"}
+**Keywords:** meta-analysis, powdery mildew, mungbean, fungicide                                                      
+:::
+<!-- Is anyone aware of a way to put the "Type of paper" text above the renderd YAML header? ... or ... Specify extra text in the header which is rendered as a different style? 
+I am considering dropping the lua files and just codeing in the different styles to suit the MDPI_Agronomy_Template.docx -->
 
@@
 
-## Core ideas
-<!-- up to 85 words per idea -->
-
-## Authors - affiliations and email address
-
 ##### PAGE BREAK
@@
 
-## Abrebiations
+## Abbreviations
 

### 2020-07-30 vignette/Manuscript2Word.Rmd
Implement MDPI referencing style

--- 2020-07-29 vignette/Manuscript2Word.Rmd
@@
 bibliography: "../Mungbean.bib"
-biblio-style: apalike
+csl: "multidisciplinary-digital-publishing-institute.csl"
 link-citations: yes
 abstract: |
-         Insert abstract here.
+         **Abstract:** Insert abstract here.
 ---
-<!-- Should we use the word "fungicide" in the title so it is more searchable for fungicide management? -->
 
@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, here, flextable, officer, english)
+pacman::p_load(tidyverse, kableExtra, here, flextable, officer, english,pander)
 
@@
 
+::: {custom-style="Art_type"}
+Type of Paper: Article
+:::
+
+::: {custom-style="keywords"}
+**Keywords:** meta-analysis, powdery mildew, mungbean, fungicide `r print("                                                       ")`                                                     
+:::
+<!-- Is anyone aware of a way to put the "Type of paper" text above the renderd YAML header? ... or ... Specify extra text in the header which is rendered as a different style? 
+I am considering dropping the lua files and just codeing in the different styles to suit the MDPI_Agronomy_Template.docx -->
+
 <!-- 
@@
 <!-- To ensure formatting matches, I suggest that you create a Word template and knit this document using that -->
-
-## Core ideas
-<!-- up to 85 words per idea -->
-
-## Authors - affiliations and email address
-
-##### PAGE BREAK
-
-## Abstract
-
-## Abrebiations
-
-##### PAGE BREAK
 

### 2020-07-30 07_Manuscript.Rmd
Corrections movement of figures addition of some hardcoded results

--- 2020-07-29 07_Manuscript.Rmd
@@
 load(file = here("cache/PreliminaryData.Rdata"))
+T3 <- read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
+T3[,2:5] <- round(T3[,2:5], 4)
 source(here("R/reportP.R"))
 ```
+
+::: {custom-style="Art_type"}
+Type of Paper: Article
+:::
+
+::: {custom-style="keywords"}
+**Keywords:** meta-analysis, powdery mildew, mungbean, fungicide `r print("                                                       ")`                                                     
+:::
+<!-- Is anyone aware of a way to put the "Type of paper" text above the renderd YAML header? ... or ... Specify extra text in the header which is rendered as a different style? 
+I am considering dropping the lua files and just codeing in the different styles to suit the MDPI_Agronomy_Template.docx -->
 
@@
 ## Materials and Methods
-**Trial criteria for inclusion and description**
+**Trial criteria for inclusion and description :**
 The data for this study were obtained through personal correspondence with colleagues and collaborating institutions.
@@
 The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the Grains Research and Development (GRDC) northern grains regions of eastern Australia, which grows the majority of Australia's summer crops.
-Trial data had to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; the fungicide active ingredients; fungicide dose; and crop yield.
+Data from trials undertaken in this regionhad to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; the fungicide active ingredients; fungicide dose; and crop yield.
 The data were subset to only include fungicide treatments with the same mode of action; demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole were thus retained in the dataset. 
 Subsequently the 26 trials were reduced to 17 trials (Table 1). 
-Two more trials were also removed because no form of variance was reported with the fungicide treatment means of grain yield, reducing the number of trials down to 15.
+Two more trials were also removed because grain yield variance, which was required for the meta-analysis, was not reported, reducing the number of trials down to 15.
 
-From the trials which were included `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12))` planted in late December, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 1))` in January and `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 2))` trials planted in February (Table 1).
-
-In the meta-analysis, to ensure sufficient replication, we made no distinction between the tebuconazole and propiconazole fungicide treatments within the trials that met the selection criteria. 
-The design of all trials included in this analysis were randomised complete block designs, and were not previously published in peer-reviewed literature. 
-Details of trial data are presented within a research compendium which was prepared as a supplement to this publication [<!-- DOI to reference to compendium -->].
-
-**Response variable - Grain yield**
-Grain yield (tonne per hectare), was used as the response variable for the meta-analysis. 
-Mean grain yields for each treatment were either obtained directly from trial reports, or calculated from the raw data when available.
-The sample variance was calculated from the raw data when available or the least squares statistic in trial reports. 
-Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 2.042 and the approach reported in Ngugi et al. [-@Ngugi2011].
-The T-critical value was determined from the 30 degrees of freedom and probability of $a = 0.05$ using a t-distribution table.
-
-Similar to Paul *et. al.* [-@Paul2007], we fitted a multivariate random effects model
-$Y_i \sim N(\mu,s_i^2 + \sigma^2)$
-where $Y_i$ is the response, a vector of the grain yield measurements (tonne per hectare) for each treatment in the $i$th trial over total number ($K$) of trials($i$  = 1, ...$K$). 
-$Y_i$ is estimated from a normal distribution with the mean $\mu$, sample variance of $S_i^2$ and a between trial variance of $\sigma^2$.
-
-**Trial Variables and moderators**
-While the main aim of all the identified trials were to assess the efficacy of fungicide for control of powdery mildew, some trials tested additional potential covariates in the experimental design.
-These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications and cultivar.
-To account for the variation attributed to some of these variables between trials, and within trials, a single $trial$ factor was created.
-The $trial$ random variable made distinctions between the following variables: unique trial reference code, trial location, trial season, host genotype, row spacing, and fungicide dose.
-
-The random effects meta-analysis was expanded to evaluate if the residual heterogeneity could be explained by spray schedule). 
-Spray schedule was assigned as an inside factor to the outside random factor $trial$ to provide correlated random effects between the different spray schedule treatments within $trials$.
-
-The timing of fungicide application treatments, were defined in relation to the recorded date when powdery mildew first occurred in the trial. 
-An $Early$ fungicide application treatment, referred to a fungicide spray schedule that commenced prior to the disease being observed in the trial. 
-$Recommended$ referred to a fungicide spray schedule which commenced 1 -- 3 days following the first sign of disease. 
-$Late$ treatments commenced between 7 and 13 days after the first sign of disease. 
-There were no spray schedule treatments which began between 4 and 6 days after the first sign of powdery mildew. 
-The number of fungicide applications were binned in to two categories.
-A spray schedule with a $single$ spray, and a spray schedule with two or three spray applications $plus$. 
-The division of the treatments produced: 13 $Early_{single}$ treatments; 5 $Early_{plus}$; 32 $Recommended_{single}$; 46 $Recommended_{plus}$'; 17 $Late_{single}$; and 20 $Late_{plus}$.
-$Early_{plus}$ treatments were removed from the subsequent meta-analysis, due to an insufficient sample size.  
-What remained was the mean yield for a total of 173 treatments in the following five spray schedule categories: no spray control, single early spray, single recommended spray, recommended with multiple sprays, single late spray, and late with multiple sprays.
-
-An ordinal 1 -- 9 ordinal scale was used to describe the mean plot powdery mildew severity in most trials (Table 2). 
-However, the 2013 NGA trials (Table 1) reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the lower, middle or upper canopy. 
-Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, a conversion to mean plot severity on the ordinal 1 -- 9 scale was straight-forward. 
-The end of season mean plot severity, and and date of first sign of disease were used to calculate the area under the disease progress curve (AUDPC) for each treatment. 
-Additional powdery mildew mean plot severity observations made in-between these two observations were also included in the AUDPC calculation if they were available. 
-AUDPC was calculated using the `agricolae` package in R [@agricolae2020]. 
-A categorical disease pressure factor was created by binning trials based on the mean AUDPC of the no spray control plot into two levels: 'low disease pressure' or 'high disease pressure'.
-The two levels were separated by the median AUDPC (`r as.double(read.csv(here("cache/median_AUDPC_C.csv")))`) of the no spray control plots.
-
-Linear contrasts were used to compare the mean effect sizes between each spray schedule treatment and their respective standard errors and confidence intervals.
-
-Additional meta-analysis models tested variables ... for their influence on the SpraySchedule variables ability to mitigate yield loss. 
-For the variable disease pressure a Wald-type test was used to test the impact of this variable on the model as a whole.
-
-The data were analysed in the R statistical software environment, version 4.0.1, [@RCoreTeam2020] using two contributed meta-analysis packages, `metafor`, version 2-4.0, [@Viechtbauer2010] and `netmeta`, version 1.2-1, [@Rucker2020].
-
-<br>
-
-```{r Figure2_treatForest, echo = FALSE}
-YieldContrasts
-```
-<br>
-<br>
 ```{r Table1_ExperimentalDetail, echo=FALSE, message=FALSE, warning=FALSE}
@@
 ```
-<br>
+
+From the trials which were included in the meta-analysis, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12))` were planted in late December, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 1))` in January and `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 2))` were trials planted in February (Table 1).
+
+In the meta-analysis, to ensure sufficient replication, we made no distinction between the tebuconazole and propiconazole fungicide treatments within the trials that met the selection criteria. 
+The design of all trials included in this analysis were randomised complete block designs, and were not previously published in peer-reviewed literature. 
+Details of trial data are presented within a research compendium as a supplement to this publication [<!-- DOI to reference to compendium -->].
+
+**Response variable - Grain yield: **
+Grain yield (tonne per hectare), was used as the response variable for the meta-analysis. 
+Mean grain yields for each treatment were either obtained directly from trial reports, or calculated from the raw data when available.
+The sample variance was calculated from the raw data when available or the least squares statistic in the trial reports. 
+Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 2.042 and the approach reported in Ngugi et al. [-@Ngugi2011].
+The T-critical value was obtained from a t-distribution table using, 30 degrees of freedom and probability of $a = 0.05$.
+
+Similar to Paul *et. al.* [-@Paul2007], we fitted a multivariate random effects model
+$Y_i \sim N(\mu,s_i^2 + \sigma^2)$
+where $Y_i$ is the response, a vector of the grain yield measurements (tonne per hectare) for each treatment in the $i$th trial over total number ($K$) of trials($i$  = 1, ...$K$). 
+$Y_i$ is estimated from a normal distribution with the mean $\mu$, sample variance of $S_i^2$ and a between trial variance of $\sigma^2$.
+
+**Trial Variables and moderators: **
+While the main aim of all the identified trials were to assess the efficacy of fungicide for control of powdery mildew, some trials tested additional potential covariates in the experimental design.
+These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications and cultivar.
+To account for the variation attributed to some of these variables between trials, and within trials, a single $trial$ factor was created.
+The $trial$ random variable made distinctions between the following variables: unique trial reference code, trial location, trial season, host genotype, row spacing, and fungicide dose.
+
+The random effects meta-analysis was expanded to evaluate if the residual heterogeneity could be explained by spray schedule). 
+Spray schedule was assigned as an inside factor to the outside random factor $trial$ to provide correlated random effects between the different spray schedule treatments within $trials$.
+
+The timing of fungicide application treatments, were defined in relation to the recorded date when powdery mildew first occurred in the trial. 
+An $Early$ fungicide application treatment, referred to a fungicide spray schedule that commenced prior to the disease being observed in the trial. 
+$Recommended$ referred to a fungicide spray schedule which commenced 1 -- 3 days following the first sign of disease. 
+$Late$ treatments commenced between 7 and 13 days after the first sign of disease. 
+There were no spray schedule treatments which began between 4 and 6 days after the first sign of powdery mildew. 
+The number of fungicide applications were binned in to two categories.
+A spray schedule with a $single$ spray, and a spray schedule with two or three spray applications $plus$. 
+The division of the treatments produced: 13 $Early_{single}$ treatments; 5 $Early_{plus}$; 32 $Recommended_{single}$; 46 $Recommended_{plus}$'; 17 $Late_{single}$; and 20 $Late_{plus}$.
+$Early_{plus}$ treatments were removed from the subsequent meta-analysis, due to an insufficient sample size.  
+What remained was the mean yield for a total of 173 treatments in the following five spray schedule categories: no spray $control$, $Early_{single}$, $Recommended_{single}$, $Recommended_{plus}$, $Late_{single}$, and $Late_{plus}$.
+
+An ordinal 1 -- 9 scale was used to describe the mean powdery mildew plot severity in most trials (Table 2). 
+However, the 2013 NGA trials (Table 1) reported mean plot severity as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the lower, middle or upper canopy. 
+Given the ordinal scale ranked plots on the percent of foliage showing the disease from the lower canopy to the upper canopy, a conversion from percentage of the diseased canopy, to the 1 -- 9 scale was straight-forward.
+The end of season mean plot severity, and date of first sign of disease were used to calculate the area under the disease progress curve (AUDPC) for each treatment. 
+Additional powdery mildew mean plot severity observations made in-between these two observations were also included in the AUDPC calculation if they were available. 
+AUDPC was calculated using the `agricolae` package in R [@agricolae2020]. 
+A categorical disease pressure factor was created by binning trials into two levels based on the mean AUDPC of the no spray control plot.
+The two levels, 'low disease pressure' and 'high disease pressure', were separated by the median AUDPC (`r as.double(read.csv(here("cache/median_AUDPC_C.csv")))`) of the no spray control plots.  
 <br>
@@
 ```
+<br>
+The mean difference in grain yield was estimated from the difference in model estimates of the non-treated control and each of the spray schedule treatments using fungicide.  
+Disease pressure was tested against the basic model to determine if, when introduced as a moderator variable, it could significantly explain additional heterogeneity between the spray schedule treatments.
+A a Wald-type test was used to test the impact of the disease pressure factor.
+
+Linear contrasts were used to produce the mean difference in effect sizes, and their respective standard errors and 95&nbsp;% confidence intervals, between each spray schedule treatment.
+
+Additional meta-analysis models tested variables ... for their influence on the SpraySchedule variables ability to mitigate yield loss. 
+For the variable disease pressure a Wald-type test was used to test the impact of this variable on the model as a whole.
+
+The data were analysed in the R statistical software environment, version 4.0.1, [@RCoreTeam2020] using two contributed meta-analysis packages, `metafor`, version 2-4.0, [@Viechtbauer2010] and `netmeta`, version 1.2-1, [@Rucker2020].
+
+<br>
+
+```{r Figure2_treatForest, echo = FALSE}
+YieldContrasts
+```
 
@@
 
-<!-- Write about first sign of disease in March -->
-Overall the meta-analysis indicated that, with the exception of `Early` single sprays all the the spray schedules were effective at protecting mungbean yields, relative to the no spray controls (Figure 2).
-Treatments which incorporating multiple fungicide applications, `RecommendedPlus` and `LatePlus` produced the highest mean yield protection estimates at 196.4 (SE = 48.7&nbsp;kg&nbsp;/&nbsp;ha) and 219.9&nbsp;kg&nbsp;/&nbsp;ha (SE = 47.4&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3).
-Both `RecommendedPlus` and `LatePlus` were also significantly higher than single applications starting `Early` (P = 0.008 and P = 0.003 respectively) and `Late`(P = 0.05 and P = 0.03 respectively). 
-However, comparing `LatePlus` and `Early` should done with caution given these treatments did not occur within the same trial for any of the 15 trials included in the meta-analysis. 
+Overall the meta-analysis indicated that, with the exception of the $Early_{single}$ treatment, all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure 2).
+Treatments which incorporating multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3).
+Both $Recommended_{plus}$ and $Late_{plus}$ were also significantly higher than single applications $Early_{single}$ (P = `r T3$pval[2]` and P = `r T3$pval[4]` respectively) and $Late_{single}$(P = `r T3$pval[8]` and P = `r T3$pval[10]` respectively).
+However, comparing $Late_{plus}$ and $Early_{single}$ should done with caution given these treatments did not occur within the same trial for any of the 15 trials included in the meta-analysis. 
 Within the single fungicide application treatments `Recommended` provided the highest yield protection, and was estimated at saving an average of 159.9 kg / ha (SE = 30.5 kg / ha) relative to the no spray control (P < 0.0001).

### 2020-07-30 vignette/Manuscript2Word.Rmd
Corrections movement of figures addition of some hardcoded results

@@
 load(file = here("cache/PreliminaryData.Rdata"))
+T3 <- read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
+T3[,2:5] <- round(T3[,2:5], 4)
 source(here("R/reportP.R"))
@@
 
-<!-- Write about first sign of disease in March -->
-Overall the meta-analysis indicated that, with the exception of `Early` single sprays all the the spray schedules were effective at protecting mungbean yields, relative to the no spray controls (Figure 2).
-Treatments which incorporating multiple fungicide applications, `RecommendedPlus` and `LatePlus` produced the highest mean yield protection estimates at 196.4 (SE = 48.7&nbsp;kg&nbsp;/&nbsp;ha) and 219.9&nbsp;kg&nbsp;/&nbsp;ha (SE = 47.4&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3).
-Both `RecommendedPlus` and `LatePlus` were also significantly higher than single applications starting `Early` (P = 0.008 and P = 0.003 respectively) and `Late`(P = 0.05 and P = 0.03 respectively). 
-However, comparing `LatePlus` and `Early` should done with caution given these treatments did not occur within the same trial for any of the 15 trials included in the meta-analysis. 
+$control$, $Early_{single}$, $Recommended_{single}$, $Recommended_{plus}$, $Late_{single}$, and $Late_{plus}$.  
+Overall the meta-analysis indicated that, with the exception of the $Early_{single}$ treatment, all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure 2).
+Treatments which incorporating multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3).
+Both $Recommended_{plus}$ and $Late_{plus}$ were also significantly higher than single applications $Early_{single}$ (P = `r T3$pval[2]` and P = `r T3$pval[4]` respectively) and $Late_{single}$(P = `r T3$pval[8]` and P = `r T3$pval[10]` respectively).
+However, comparing $Late_{plus}$ and $Early_{single}$ should done with caution given these treatments did not occur within the same trial for any of the 15 trials included in the meta-analysis. 
 Within the single fungicide application treatments `Recommended` provided the highest yield protection, and was estimated at saving an average of 159.9 kg / ha (SE = 30.5 kg / ha) relative to the no spray control (P < 0.0001).

### 2020-07-30 vignette/Manuscript2Word.Rmd
Delete outdated comments

@@
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, here, flextable, officer, english,pander)
+pacman::p_load(tidyverse, kableExtra, here, flextable, officer, english, pander)
 
@@
 load(file = here("cache/PreliminaryData.Rdata"))
-T3 <- read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
-T3[,2:5] <- round(T3[,2:5], 4)
+T3 <-
+   read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
+T3[, 2:5] <- round(T3[, 2:5], 4)
 source(here("R/reportP.R"))
@@
 I am considering dropping the lua files and just codeing in the different styles to suit the MDPI_Agronomy_Template.docx -->
-
-<!-- 
-Need to ensure the format of this manuscript adheres to the MDPI Agronomy style guide 
-https://www.agronomy.org/publications/journals/author-resources/aj-instructions#headline-article-requirements 
--->
-<!-- To ensure formatting matches, I suggest that you create a Word template and knit this document using that -->
 

### 2020-07-31 04_MetaAnalysis.Rmd
Spelling
Add model contrasts to save data

--- 2020-07-23 04_MetaAnalysis.Rmd
@@
 The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis.
-This effectively shows the heterogeneity between experiments for these partivular treatments.
+This effectively shows the heterogeneity between experiments for these particular treatments.
 
@@
 ```{r Save_meta_data, eval=FALSE}
-write.csv(slimmer_PM_dat, file = "data/GYmeta_data.csv")
-save(dat1, efficacy, PM_mv, YieldContrasts, file = here("cache/Meta-analysisData.Rdata"))
+save(dat1, efficacy, slimmer_PM_dat, PM_mv, YieldContrasts,contrast_Ssum,file =
+        here("cache/Meta-analysisData.Rdata"))
 ```

### 2020-07-31 R/simple_summary.R
Update function to include StError and Z values

@@ -19,16 +19,10 @@ simple_summary <-
       
       data.frame(contrast = rename_index(index_name = ind_names, char_name = names1),
                  coefficients = sum_meta[["test"]]$coefficients,
+                 StdErr = sum_meta[["test"]]$sigma,
+                 'Zvalue' = sum_meta[["test"]]$tstat,
                  pvals = sum_meta[["test"]]$pvalues,
                  sig = p_star(sum_meta[["test"]]$pvalues)
                                          )
          
    }
-
-
-
-#### TESTING
-# 
-# summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none"))[["test"]]$pvalues
-# colnames(summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none"))[["test"]]$coefficients)
-simple_summary(summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none")))

### 2020-07-31 R/reportP.R
Add functionallity to function to allow for vectors of pvals

@@ -1,4 +1,6 @@
 reportP <- function(p, AsNumeric = FALSE){
+   if(length(p) == 1){
+   
    if(AsNumeric == FALSE){
       if(p < 0.0001){
       return("P < 0.0001")
@@ -11,5 +13,24 @@ reportP <- function(p, AsNumeric = FALSE){
       return(format(0.0001, scientific = FALSE))
    }else{
       return(format(round(p, digits =  4), scientific = FALSE))
-   }}
+   }}}else{
+      
+      sapply(p,function(p) {
+         if(AsNumeric == FALSE){
+            if(p < 0.0001){
+               return("P < 0.0001")
+            }else{
+               return(paste("P =", format(round(p, digits =  4), scientific = FALSE)))
+            }}
+         
+         if(AsNumeric == TRUE){
+            if(p < 0.0001){
+               return(format(0.0001, scientific = FALSE))
+            }else{
+               return(format(round(p, digits =  4), scientific = FALSE))
+            }}
+      })
+      
+   }
+   
 }

### 2020-07-31 07_Manuscript.Rmd
Update results and hardcoded values. Remove T3 object and use actual summary of contrasts

@@
 :::
-<!-- Is anyone aware of a way to put the "Type of paper" text above the renderd YAML header? ... or ... Specify extra text in the header which is rendered as a different style? 
-I am considering dropping the lua files and just codeing in the different styles to suit the MDPI_Agronomy_Template.docx -->
+<!-- Is anyone aware of a way to put the "Type of paper" text above the rendered YAML header? ... or ... Specify extra text in the header which is rendered as a different style? 
+I am considering dropping the lua files and just coding in the different styles to suit the MDPI_Agronomy_Template.docx -->
 
@@
 Overall the meta-analysis indicated that, with the exception of the $Early_{single}$ treatment, all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure 2).
-Treatments which incorporating multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3).
-Both $Recommended_{plus}$ and $Late_{plus}$ were also significantly higher than single applications $Early_{single}$ (P = `r T3$pval[2]` and P = `r T3$pval[4]` respectively) and $Late_{single}$(P = `r T3$pval[8]` and P = `r T3$pval[10]` respectively).
-However, comparing $Late_{plus}$ and $Early_{single}$ should done with caution given these treatments did not occur within the same trial for any of the 15 trials included in the meta-analysis. 
-Within the single fungicide application treatments `Recommended` provided the highest yield protection, and was estimated at saving an average of 159.9 kg / ha (SE = 30.5 kg / ha) relative to the no spray control (P < 0.0001).
-`Recommended` treatments were was also significantly higher than `Early` treatments by 122.1 kg / ha (SE = 42.1 kg / ha)(P = 0.004). 
-Single `Late` applications were effective at significantly mitigating the effect of powdery mildew on yield by a mean of 122 kg / ha (SE = 39.2 kg / ha)(P = 0.0019). 
-However, this estimate was not significantly different to single `Early` or `Recommended` treatments (P = 0.119; P = 0.278 respectively).
+Treatments which incorporated multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3).
+The treatment that showed the most yield saved compared to the control, $Recommended_{plus}$, was also significantly higher than all other single applications, (
+$Early_{single}$, `r reportP(contrast_Ssum$pvals[grep("Recommended_plus - Early",contrast_Ssum$contrast)])`, 
+$Recommended_{single}$, `r reportP(contrast_Ssum$pvals[grep("Recommended_plus - Recommended",contrast_Ssum$contrast)])` and
+$Late_{single}$, `r reportP(contrast_Ssum$pvals[grep("Late - Recommended_plus",contrast_Ssum$contrast)])`). 
+However the $Late_{plus}$ only showed significantly greater yield saved when compared to the $Early_{single}$ treatment (`r reportP(contrast_Ssum$pvals[grep("Late_plus - Early",contrast_Ssum$contrast)])`)
+Consideration should be given when comparing $Late_{plus}$ and $Early_{single}$ treatments given they did not occur within the same trial for any of the 15 trials included in the meta-analysis. 
+Within the single fungicide application treatments $Late_{single}$ provided the highest yield protection, and was estimated at saving an average of `r round(PM_mv$b[5,1] * 1000, 2)` kg / ha (SE = `r round(PM_mv$se[5] * 1000, 2)` kg / ha) relative to the no spray control (`r reportP(PM_mv$pval[5])`).
+$Early_{single}$ treatments were significantly lower than all other treatments (Table 3) and reported a mean estimate `r abs(round(PM_mv$b[2,1] * 1000, 2))` kg / ha (SE = `r round(PM_mv$se[2] * 1000, 2)` kg / ha) lower than the no spray control (`r reportP(PM_mv$pval[2])`).
 
@@
 
+First sign of powdery mildew was observed as early as the 28th of February in the 2013 trial at .... ; and as late as the 12th of April in the 2018 trial at ...
+
 ```{r Figure1, echo=FALSE}
@@
 ```{r table3_Contrasts, echo = FALSE}
-T3 <- read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
-T3[,2:5] <- round(T3[,2:5], 4)
-T3 %>%
-   mutate(contrasts = gsub("-","",contrasts))%>%
-   mutate(contrasts = gsub(" \\+"," -",contrasts))%>%
-   mutate(contrasts = gsub(" = 0","",contrasts))%>%
+contrast_Ssum[,2:5] <- round(contrast_Ssum[,2:5], 4)
+contrast_Ssum %>%
+   slice(grep("control", contrast, invert = TRUE)) %>%
+   mutate(pvals = reportP(pvals)) %>%
+   mutate(pvals = gsub("P = ","",pvals)) %>%
    flextable()%>%
@@
    autofit(add_w = 0.2)%>%
-   align(j = c(2,3,4), align = "center", part = "all") %>%
+   align(j = c(2:5), align = "center", part = "all") %>%
+   #align(j = c(5), align = "right", part = "all") %>%
    set_header_labels(contrasts = "Treatment contrasts",
-                     estimates = "Estimate",
-                     se = "Std Error",
-                     z_val = "Z-Score",
-                     pval = "P-Value",
-                     VisP = " ")%>%
+                     coefficients = "Estimate",
+                     StdErr = "Std Error",
+                     Zvalue = "Z-Score",
+                     pvals = "P-Value",
+                     sig = " ")%>%
    fontsize(size = 9)%>%
-   width(j = 5,0.7)%>%
+   width(j = 5,0.8)%>%
    width(j = 6, .3)

### 2020-08-03 paper/paper.Rmd
Move paper text into MDPI template format in /paper
* Uses MDPI template
* Updates tables
* Updates table contents with footnotes
* Uses proper cross-references for tables and figures
* Corrects order of figures in which they appear and are referenced
* Spelling corrections
* Grammar corrections
* et. al replaced with et al.

--- 2020-07-30 vignette/Manuscript2Word.Rmd
@@
 ---
-title: "A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean"
+title: A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean
 author:
-  - Paul Melloy:
+  - name: Paul Melloy
+    affil: 1,*
+    orcid: 0000-0003-4253-7167
+  - name: Emerson Del Ponte
+    affil: 2
+    orcid: 0000-0003-4398-409X
+  - name: Adam H. Sparks
+    affil: 3
+    orcid: 0000-0002-0061-8359
+affiliation:
+  - num: 1
+    address: |
+      University of Southern Queensland
+      Centre for Crop Health
+      Toowoomba, Queensland, 4350 Australia
     email: Paul.Melloy@usq.edu.au
-      institute: USQ
-      correspondence: true
-  - Emerson Del Ponte:
-      institute: UFV
-  - Adam H. Sparks:
-      institute: USQ
-institute:
-  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland, Australia
-  - UFV: Universidade Federal de Viçosa, Departamento de Fitopatologia, 36570-000 MG, Brazil
-date: "Last Edit: `r format(Sys.time(), '%d %B, %Y')`"
-output:
-   word_document:
-      reference_docx: "Manuscript2Word_Template.docx"
-      md_extensions: +styles
-      pandoc_args:
-      - '--lua-filter=scholarly-metadata.lua'
-      - '--lua-filter=author-info-blocks.lua'
-bibliography: "../Mungbean.bib"
-csl: "multidisciplinary-digital-publishing-institute.csl"
-link-citations: yes
+  - num: 2
+    address: |
+      Universidade Federal de Viçosa
+      Departamento de Fitopatologia
+      Viçosa, 36570-000 Minas Gearais, Brazil
+    email: delponte@ufv.br
+  - num: 3
+    address: |
+      University of Southern Queensland
+      Centre for Crop Health
+      Toowoomba, Queensland, 4350 Australia
+    email: Adam.Sparks@usq.edu.au
+correspondence: |
+  Paul.Melloy@usq.edu.au; Tel.: +61 7 4631 5527
+journal: agronomy
+type: article
+status: submit
+bibliography: ../Mungbean.bib
+#appendix: appendix.tex
+simplesummary: |
+  A simple summary goes here.
 abstract: |
-         **Abstract:** Insert abstract here.
+  A single paragraph of about 200 words maximum. For research articles, 
+  abstracts should give a pertinent overview of the work. We strongly encourage
+  authors to use the following style of structured abstracts, but without 
+  headings: 1) Background: Place the question addressed in a broad context and
+  highlight the purpose of the study; 2) Methods: Describe briefly the main
+  methods or treatments applied; 3) Results: Summarize the article's main 
+  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
+  The abstract should be an objective representation of the article, it must not 
+  contain results which are not presented and substantiated in the main text and 
+  should not exaggerate the main conclusions.
+keywords: |
+  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
+  to the article, yet reasonably common within the subject discipline.).
+acknowledgement: |
+  All sources of funding of the study should be disclosed. Please clearly 
+  indicate grants that you have received in support of your research work. 
+  Clearly state if you received funds for covering the costs to publish in open 
+  access.
+authorcontributions: |
+  For research articles with several authors, a short paragraph specifying their 
+  individual contributions must be provided. The following statements should be 
+  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
+  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
+  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
+  limited to those who have contributed substantially to the work reported.
+funding: |
+   Please add: ``This research received no external funding'' or ``This research
+   was funded by NAME OF FUNDER grant number XXX.'' and ``The APC was funded by
+   XXX''. Check carefully that the details given are accurate and use the
+   standard spelling of funding agency names at
+   <https://search.crossref.org/funding>, any errors may affect your future
+   funding.
+conflictsofinterest: |
+  Declare conflicts of interest or state 'The authors declare no conflict of 
+  interest.' Authors must identify and declare any personal circumstances or
+  interest that may be perceived as inappropriately influencing the
+  representation or interpretation of reported research results. Any role of the
+  funding sponsors in the design of the study; in the collection, analyses or 
+  interpretation of data in the writing of the manuscript, or in the decision to 
+  publish the results must be declared in this section. If there is no role, 
+  please state 'The founding sponsors had no role in the design of the study; 
+  in the collection, analyses, or interpretation of data; in the writing of the 
+  manuscript, an in the decision to publish the results'.
+sampleavailability: |
+  Samples of the compounds ...... are available from the authors.
+abbreviations:
+  - short: MDPI
+    long: Multidisciplinary Digital Publishing Institute
+  - short: DOAJ
+    long: Directory of open access journals
+  - short: TLA
+    long: Three letter acronym
+  - short: LD 
+    long: linear dichroism
+output: rticles::mdpi_article
 ---
@@
 ```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, here, flextable, officer, english, pander)
+if (!require("pacman"))
+  install.packages("pacman")
+pacman::p_load(tidyverse, kableExtra, here, english, pander)
 
@@
 ```
-
-::: {custom-style="Art_type"}
-Type of Paper: Article
-:::
-
-::: {custom-style="keywords"}
-**Keywords:** meta-analysis, powdery mildew, mungbean, fungicide `r print("                                                       ")`                                                     
-:::
-<!-- Is anyone aware of a way to put the "Type of paper" text above the renderd YAML header? ... or ... Specify extra text in the header which is rendered as a different style? 
-I am considering dropping the lua files and just codeing in the different styles to suit the MDPI_Agronomy_Template.docx -->
-
-## Introduction
 
@@
 While the pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified. 
-The disease lifecycle can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia which disseminate to new infection sites [@Sparks2017].
+The disease lifecycle can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@Sparks2017].
 Weather conditions that favour the rapid development of the disease are cool temperatures between 22&deg; and 26&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
@@
 The collection of experiments mentioned above and other unpublished trials present an excellent opportunity for a meta-analysis.
-Meta-analyses are statistical tools which can analyse a collection of experiments, which have a similar aim, and produces a more accurate estimate of the true effect being measured.
+Meta-analyses are statistical tools, which can analyse a collection of experiments, that have a similar aim, and produces a more accurate estimate of the true effect being measured.
 Using a meta-analysis can be useful in situations like this where several studies exist, that have the same objective but may not provide a clear answer to the question due to variation in the results within the individual studies.
@@
 Multi-variate meta-analyses are particularly useful when there are no direct comparisons between two treatments in any of the included studies. 
-In-direct comparisons can be made between these two treatments if the both had direct comparisons with one or more treatments in common, assuming no significant bias in the studies which investigated each of the treatments which are subject to a indirect comparison [@Jansen2011].
+Indirect comparisons can be made between these two treatments if the both had direct comparisons with one or more treatments in common, assuming no significant bias in the studies that investigated each of the treatments and which are subject to a indirect comparison [@Jansen2011].
 
@@
 
-## Materials and Methods
-**Trial criteria for inclusion and description :**
+# Materials and Methods
+
+## Trial criteria for inclusion and description
+
 The data for this study were obtained through personal correspondence with colleagues and collaborating institutions.
@@
 PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref, "trial_ref"] <-
-   sapply(PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref,"trial_ref"], paste0, "*")
+  sapply(PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref, "trial_ref"], paste0, "*")
 
@@
   mutate(Research_org = c(
-      rep("Queensland DAF", times = 4),
-      rep("Northern Growers Alliance", times = 4),
-      rep("Queensland DAF", times = 4),
-      rep("USQ", times = 5)
+    rep("DAF$^{a}$", times = 4),
+    rep("NGA$^{b}$", times = 4),
+    rep("DAF$^{a}$", times = 4),
+    rep("USQ$^{c}$", times = 5)
   )) %>%
-   flextable()%>%
-   set_caption("Table 1: Description of Experiments") %>%
-   set_header_labels(trial_ref = "Unique Trial Reference",
-                     year = "Year",
-                     location = "Trial Location",
-                     planting_date = "Planting Date",
-                     first_sign_disease = "First sign of disease date",
-                     Research_org = "Research organisation")%>%
-   autofit(add_w = 0.5)%>%
-   align(j = c(1,4,5), align = "center", part = "all")%>%
-   fontsize(size = 9)%>%
-   width(j = 1:4, 1)%>%
-   width(j = 5, 1.1)%>%
-   width(j = 6, 1.7)
+  rename(
+    `Unique Trial Reference` = trial_ref,
+    Year = year,
+    Location = location,
+    `Planting Date` = planting_date,
+    `Date First Sign` = first_sign_disease,
+    `Research Organisation` = Research_org
+  ) %>%
+  kable(format = "latex",
+        booktabs = TRUE,
+        escape = FALSE,
+        caption="Description of fungicide application experiments.") %>%
+  kable_styling() %>%
+  footnote(
+    alphabet = c(
+      "Queensland Department of Agriculture, Fisheries and Forestry",
+      "Northern Growers Alliance",
+      "University of Southern Queensland"
+    )
+  )
 ```
@@
 
-Similar to Paul *et. al.* [-@Paul2007], we fitted a multivariate random effects model
+Similar to Paul *et al..* [-@Paul2007], we fitted a multivariate random effects model
 $Y_i \sim N(\mu,s_i^2 + \sigma^2)$
@@
 The two levels, 'low disease pressure' and 'high disease pressure', were separated by the median AUDPC (`r as.double(read.csv(here("cache/median_AUDPC_C.csv")))`) of the no spray control plots.
-<br>
+
 ```{r Table2_1to9Scale, echo=FALSE}
@@
     "No sign of powdery mildew",
-      "Small colonies in lower 1/3 of canopy, up to 75% of plants affected",
-      "Colonies in lower 1/2 of canopy, > 75 % of plants affected",
-      "Colonies in lower 2/3 of canopy, up to 75 % of plants affected",
-      "Colonies in lower 2/3 of canopy, > 75 % of plants affected",
-      "Colonies in lower 2/3 of canopy, 100 % of plants affected",
-      "Colonies in lower 2/3 of canopy, 100 % of plants, with some plants with colonies in the top 1/3 of canopy",
-      "Colonies to top of the plant with > 75 % of plants affected",
-      "Colonies to top of the plant with > 100 % of plants affected and heavy leaf drop"
+    "Small colonies in lower 1/3 of the canopy, up to 75 % of the plants affected",
+    "Colonies in lower 1/2 of the canopy, > 75 % of the plants affected",
+    "Colonies in lower 2/3 of the canopy, up to 75 % of the plants affected",
+    "Colonies in lower 2/3 of the canopy, > 75 % of the plants affected",
+    "Colonies in lower 2/3 of the canopy, 100 % of the plants affected",
+    "Colonies in lower 2/3 of the canopy, 100 % of plants, with some plants with colonies in the top 1/3 of the canopy",
+    "Colonies to top of the plant with > 75 % of the plants affected",
+    "Colonies to top of the plant with > 100 % of the plants affected and heavy leaf drop"
   )
 ) %>%
-   flextable()%>%
-   set_caption("Table 2: Powdery Mildew severity scoring scale") %>%
-   set_header_labels(Scale.Description = "Scale Description")%>%
-   autofit()%>%
-   fontsize(size = 9)%>%
-   align(j = c(1), align = "center", part = "all")%>%
-   width(j = 2, 6.2)
+kable(format = "latex",
+      booktabs = TRUE,
+      caption="Powdery mildew severity scoring scale.") %>%
+  kable_styling()
 ```
-<br>
+
 The mean difference in grain yield was estimated from the difference in model estimates of the non-treated control and each of the spray schedule treatments using fungicide.  
@@
 
-<br>
-
-```{r Figure2_treatForest, echo = FALSE}
+```{r Figure1, echo = FALSE, caption = "Yield contrasts"}
 YieldContrasts
@@
 
-## Results
+# Results
 
 $control$, $Early_{single}$, $Recommended_{single}$, $Recommended_{plus}$, $Late_{single}$, and $Late_{plus}$.  
-Overall the meta-analysis indicated that, with the exception of the $Early_{single}$ treatment, all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure 2).
+Overall the meta-analysis indicated that, with the exception of the $Early_{single}$ treatment, all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure \@ref(fig:Figure1)).
 Treatments which incorporating multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3).
@@
 
-```{r Figure1, echo=FALSE}
+<!-- What is this `SeasonPlot`? I can't find any docs and no file named `SeasonPlot`. It should just be code here int the doc for easy editing. -->
+
+```{r Figure2, echo=FALSE, caption="Season plot"}
 SeasonPlot
@@
 
-<br>
-<br>
-
 ```{r table3_Contrasts, echo = FALSE}
-T3 <- read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
-T3[,2:5] <- round(T3[,2:5], 4)
+T3 <-
+  read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
+T3[, 2:5] <- round(T3[, 2:5], 4)
 T3 %>%
-   mutate(contrasts = gsub("-","",contrasts))%>%
-   mutate(contrasts = gsub(" \\+"," -",contrasts))%>%
-   mutate(contrasts = gsub(" = 0","",contrasts))%>%
-   flextable()%>%
-   set_caption("Table 3: Estimated grain yield contrasts between each spray scheduale") %>%
-   autofit(add_w = 0.2)%>%
-   align(j = c(2,3,4), align = "center", part = "all") %>%
-   set_header_labels(contrasts = "Treatment contrasts",
-                     estimates = "Estimate",
-                     se = "Std Error",
-                     z_val = "Z-Score",
-                     pval = "P-Value",
-                     VisP = " ")%>%
-   fontsize(size = 9)%>%
-   width(j = 5,0.7)%>%
-   width(j = 6, .3)
+  mutate(contrasts = gsub("-", "", contrasts)) %>%
+  mutate(contrasts = gsub(" \\+", " -", contrasts)) %>%
+  mutate(contrasts = gsub(" = 0", "", contrasts)) %>%
+  rename(
+    `Treatment contrasts` = contrasts,
+    Estimate = estimates,
+    `Standard Error` = se,
+    `Z-score` = z_val,
+    `P-value` = pval,
+    ` ` = VisP
+  ) %>%
+  kable(format = "latex",
+        booktabs = TRUE,
+        caption = "Estimated grain yield contrasts between each spray schedule.") %>%
+  kable_styling() %>%
+  footnote(general = c("** - signficant at 0.005 level",
+                       "* - signficant at 0.05 level"))
 ```
 
-## Discussion
+# Discussion
 The current advice provided to growers for when to commence fungicide applications for control of powdery mildew, is to spray at the first sign of the disease then if necessary a follow-up spray two weeks later [@SueThompson2016; @Sparks2017].
@@
 `r round(PM_mv$ci.lb[4],5)*1000` to `r round(PM_mv$ci.ub[4],5)*1000` kg / ha in the $RecommendedPlus$ treatments (`r reportP(PM_mv$pval[4])`) and
-`r round(PM_mv$ci.lb[6],5)*1000` to `r round(PM_mv$ci.ub[6],5)*1000` kg / ha in the $LatePlus$ treatments (`r reportP(PM_mv$pval[6])`) (Figure 1)
-which again follows the advice given by Thompson et. al [@SueThompson2016].
-This meta-analysis adds certainty to the advice which is currently given to growers, especially around any uncertainty that Early sprays might be effective at suppressing the disease. 
+`r round(PM_mv$ci.lb[6],5)*1000` to `r round(PM_mv$ci.ub[6],5)*1000` kg / ha in the $LatePlus$ treatments (`r reportP(PM_mv$pval[6])`) (Figure \@ref(fig:Figure2))
+which again follows the advice given by Thompson et al. [@SueThompson2016].
+This meta-analysis adds certainty to the advice, which is currently given to growers, especially around any uncertainty that Early sprays might be effective at suppressing the disease. 
 We show here Early fungicide applications, which were made prior to any sign of the disease, were not effective at mitigating yield loss.
 
-This meta-analysis also provides a effective spray window for fungicide applications, given that spray schedules which commenced 'late' were still significantly effective at mitigating yield loss ($Late$ `r reportP(PM_mv$pval[5])`) 7 - 13 days after the first sign of disease.
+This meta-analysis also provides a effective spray window for fungicide applications, given that spray schedules, which commenced 'late' were still significantly effective at mitigating yield loss ($Late$ `r reportP(PM_mv$pval[5])`) 7 - 13 days after the first sign of disease.
 Growers typically do not have the time to inspect their crop regularly for the first sign of powdery mildew and therefore the disease may not be spotted within the first couple of days of it establishing.
@@
 It is important to note, the studies included in this meta-analysis may not reflect a 'normal' mungbean season. 
-All the included experiments were intentionally sown late in the season, from January through to as late as early March, to ensure powdery mildew infection (Figure 1). 
+All the included experiments were intentionally sown late in the season, from January through to as late as early March, to ensure powdery mildew infection (Figure \@ref(fig:Figure2)). 
 While certain circumstances may force growers to sow mungbeans late, many may decide to fallow their fields instead of risking a powdery mildew epidemics and an early frost damaging the crop and yields.
@@
 If the planting guide is adhered to the mungbean would be at a lower risk of powdery mildew, reducing the requirement for fungicide applications. 
-An example of this is if we inspect the six trials which powdery mildew manifested 60 days or greater after planting (Trial references: AM1304, mung1819/01, mung1011/01, AM1303, AM1305 and BB1305). 
+An example of this is if we inspect the six trials in which powdery mildew manifested 60 days or greater after planting (Trial references: AM1304, mung1819/01, mung1011/01, AM1303, AM1305 and BB1305).
 Of these trials, four directly compared single $Recommended$ fungicide applications and $RecommendedPlus$ (AM1303, AM1305, BB1305 and mung1819/01), two of which (AM1305 and mung1819/01) produced at least one treatment $RecommendedPlus$ treatment with a higher grain yield the $Recommended$ treatments.
@@
 Scouting the crop for powdery mildew might not be necessary during the warmer months of the season. 
-Data from the trials included in this experiment show regardless of crop sowing date, powdery mildew establishes on average in the month of March which marks the beginning of Autumn (Figure 1).
+Data from the trials included in this experiment show regardless of crop sowing date, powdery mildew establishes on average in the month of March, which marks the beginning of autumn (Figure \@ref(fig:Figure2)).
 Considering the results of the meta-analysis, weekly inspections would be ideal to ensure timely fungicide applications if necessary. 
@@
 
-According to the Fungicide resistance Action Committee (FRAC) it is important to alternate or mix fungicides with different modes of action to avoid fungicide resistance. 
+According to the Fungicide Resistance Action Committee (FRAC) it is important to alternate or mix fungicides with different modes of action to avoid fungicide resistance. 
 At the time of writing, in Australia one fungicide is registered with the to treat powdery mildew in mungbean, Veritas/Custodia (200 g/L tebuconazole with 120 g/L azoxystrobin).
@@
 While some nitrogen fixing symbiont show a level of tolerance to fungicides, all are detrimentally affected by increasing concentrations of fungicide leading to lower nodulation and biomass accumulation [@Ahemad2011, @Shahid2019].
-Therefore if a grower is relying on rhizobia inoculation to help meet the crops nitrogen requirements, untimely and excessive applications of a systemic fungicide for powdery mildew control may actually reduce yields.
+Therefore if a grower is relying on inoculating with rhizobia to help meet the crops nitrogen requirements, untimely and excessive applications of a systemic fungicide for powdery mildew control may actually reduce yield.
 
-### Future work
+## Future work
 This meta-analysis provides a ballast for the direction of future powdery mildew research in mungbean. 
@@
 The population genetics, epidemiology and alternate hosts are all poorly understood in this host-pathogen relationship.
-The recent discovery of a second powdery mildew species which infects mungbean highlights the paucity of knowledge on this disease.
+The recent discovery of a second powdery mildew species, which infects mungbean highlights the paucity of knowledge on this disease.
 
-## Conclusion
+# Conclusion
 
-## Supplemental Material
+# Supplemental Material
 Supplementary material can be found in the following research compendium.
@@
 
-## Data Availability
+# Data Availability
 All data and code used in the preparation of this manuscript can be found in the associated research compendium.
@@
 
-## Conflict of Interest Statement
+# Conflict of Interest Statement
 The authors of this paper have no conflicting interest in the research presented in this manuscript
 
-## Acknowledgments
+# Acknowledgments
 The authors wish to acknowledge the work done by Professor Malcolm Riley and Dr Sue Thompson whom undertook many of the trials incorporated in this analysis from 2004 - 2015. 
@@
 The Grains Research and Development Corporation who funded this research.
-
-## References

### 2020-08-03 paper/paper.Rmd
knit minus "sample availability" and spell check

@@
   manuscript, an in the decision to publish the results'.
-sampleavailability: |
-  Samples of the compounds ...... are available from the authors.
 abbreviations:
@@
 While the pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified. 
-The disease lifecycle can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@Sparks2017].
+The disease life cycle can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@Sparks2017].
 Weather conditions that favour the rapid development of the disease are cool temperatures between 22&deg; and 26&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
@@
 The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the Grains Research and Development (GRDC) northern grains regions of eastern Australia, which grows the majority of Australia's summer crops.
-Data from trials undertaken in this regionhad to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; the fungicide active ingredients; fungicide dose; and crop yield.
+Data from trials undertaken in this region had to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; the fungicide active ingredients; fungicide dose; and crop yield.
 The data were subset to only include fungicide treatments with the same mode of action; demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole were thus retained in the dataset.
@@
 At the time of writing, in Australia one fungicide is registered with the to treat powdery mildew in mungbean, Veritas/Custodia (200 g/L tebuconazole with 120 g/L azoxystrobin).
-This fungicide provides dual action: tebeconazole disrupts C-14 demethylase, required in sterol biosynthesis for cell membranes; and azoxystrobin, a Quinone outside inhibitor.
+This fungicide provides dual action: tebuconazole disrupts C-14 demethylase, required in sterol biosynthesis for cell membranes; and azoxystrobin, a Quinone outside inhibitor.
 Quinone is required in cell metabolism and active in the mitochondrial complex III.

### 2020-08-03 paper/paper.Rmd
Correct non-functioning cross-references

@@
     long: linear dichroism
-output: rticles::mdpi_article
+output:
+  bookdown::pdf_book:
+    base_format: rticles::mdpi_article
 ---
@@
 The data were subset to only include fungicide treatments with the same mode of action; demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole were thus retained in the dataset.
-Subsequently the 26 trials were reduced to 17 trials (Table 1). 
+Subsequently the 26 trials were reduced to 17 trials (Table \@ref(tab:Table1)).
 Two more trials were also removed because grain yield variance, which was required for the meta-analysis, was not reported, reducing the number of trials down to 15.
 
-```{r Table1_ExperimentalDetail, echo=FALSE, message=FALSE, warning=FALSE}
+```{r Table1, echo=FALSE, message=FALSE, warning=FALSE}
 # Add a star to the trials which were not in the final analysis
@@
 
-From the trials which were included in the meta-analysis, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12))` were planted in late December, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 1))` in January and `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 2))` were trials planted in February (Table 1).
+From the trials which were included in the meta-analysis, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12))` were planted in late December, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 1))` in January and `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 2))` were trials planted in February (Table \@ref(tab:Table1)).
 
@@
 
-An ordinal 1 -- 9 scale was used to describe the mean powdery mildew plot severity in most trials (Table 2).
-However, the 2013 NGA trials (Table 1) reported mean plot severity as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the lower, middle or upper canopy.
+An ordinal 1 -- 9 scale was used to describe the mean powdery mildew plot severity in most trials (Table \@ref(tab:Table2)).
+However, the 2013 NGA trials (Table \@ref(tab:Table1)) reported mean plot severity as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the lower, middle or upper canopy.
 Given the ordinal scale ranked plots on the percent of foliage showing the disease from the lower canopy to the upper canopy, a conversion from percentage of the diseased canopy, to the 1 -- 9 scale was straight-forward.
@@
 
-```{r Table2_1to9Scale, echo=FALSE}
+```{r Table2, echo=FALSE}
 data.frame(
@@
 Overall the meta-analysis indicated that, with the exception of the $Early_{single}$ treatment, all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure \@ref(fig:Figure1)).
-Treatments which incorporating multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3).
+Treatments which incorporating multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table \@ref(tab:Table3)).
 Both $Recommended_{plus}$ and $Late_{plus}$ were also significantly higher than single applications $Early_{single}$ (P = `r T3$pval[2]` and P = `r T3$pval[4]` respectively) and $Late_{single}$(P = `r T3$pval[8]` and P = `r T3$pval[10]` respectively).
@@
 
-```{r table3_Contrasts, echo = FALSE}
-T3 <-
-  read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
+```{r Table3, echo = FALSE}
 T3[, 2:5] <- round(T3[, 2:5], 4)

### 2020-08-03 paper/paper.Rmd
Edits to intro, cross references and abbreviations`
* Copy-edit the introduction
* Fix cross-references for tables and figures
* Clean up abbreviations used, so far I've only found DSS, but there may be others that need to be added to the YAML...

@@
 bibliography: ../Mungbean.bib
-#appendix: appendix.tex
 simplesummary: |
@@
 abbreviations:
-  - short: MDPI
-    long: Multidisciplinary Digital Publishing Institute
-  - short: DOAJ
-    long: Directory of open access journals
-  - short: TLA
-    long: Three letter acronym
-  - short: LD 
-    long: linear dichroism
+  - short: DSS
+    long: Decision support system
 output:
@@
 Mungbean was first brought to Australia in the 1930s for use as a forage or green manure crop.
-However, it was only somewhat recently, the 1960s that mungbean was grown commercially [@Lawn1978; @Chauhan2018].
+However, it was only somewhat recently, during the 1960s that mungbean was grown commercially [@Lawn1978; @Chauhan2018].
 Prior to the 1970s the total area grown in Australia rarely exceeded 1000 hectares [@Lawn1978].
 At the end of the 1980s, between 3,000 to 10,0000 hectares were being harvested for dried beans in Australia, of which mungbean is categorised by the FAO statistics data repository [@FAOSTAT].
-In the decade leading up to 2018 between 35 - 86.4 thousand hectares of dried beans were planted annually.
-This increase is attributed high value export markets and to the improved yields in the new cultivars [@Clarry2016].
+In the decade leading up to 2018, between 35 - 86.4 thousand hectares of dried beans were planted annually.
+This increase is attributed to high value export markets and to the improved yields in the new cultivars [@Clarry2016].
 Currently mungbean is predominantly grown in southern Queensland and northern New South Wales as a short season summer legume crop.
-In 2019, approximately 90&nbsp;% of Australian mungbean was grown for export with lucrative returns of up to \$1300&nbsp;AU a tonne [@QueenslandGovernment2019].
-Mungbean potentially yields up to 3 tonnes per hectare [@ThomasRobert2004], but due to high variability in yields between seasons and locations, the average Australian farm still yields less than 1 tonne per hectare [@Chauhan2018].
+In 2019, approximately 90% of Australian mungbean was grown for export with lucrative returns of up to \$1300&nbsp;AU per tonne [@QueenslandGovernment2019].
+Mungbean potentially yields up to three tonnes per hectare [@ThomasRobert2004], but due to high variability in yields between seasons and locations, the average Australian farm still yields less than one tonne per hectare [@Chauhan2018].
 
-The high variability in yields, in part, can be attributed to a range of diseases that affect the crop [@Kelly2017a].
+The high variability in yields can in part be attributed to a range of diseases that affect the crop [@Kelly2017a].
 Two major foliar diseases, tan spot or common wilt (*Curtobacterium flaccumfaciens* pv.
@@
 
-Powdery mildew is caused by two separate genera of fungi in Australia *Podosphaera xanthii* and an unnamed *Psuedoidium sp.* (Kiss and Kelly Personal Communication).
 While the pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified.
 The disease life cycle can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@Sparks2017].
-Weather conditions that favour the rapid development of the disease are cool temperatures between 22&deg; and 26&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
+Weather conditions that favour the rapid development of the disease are cool temperatures between 22&deg; and 26&nbsp;&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
 
-Due to the requirement for cooler temperatures for infection, planting date is an effective strategy for preventing the development of powdery mildew in mungbean [@AMAplanting].
+Due to the requirement for cool temperatures for infection, planting date is an effective strategy for preventing the development of powdery mildew in mungbean [@AMAplanting].
 In southern Queensland and northern New South Wales, sowing dates between late spring (November) and mid-summer (January) are advised to avoid the conducive cooler autumn temperatures, which normally commence in March.
-Therefore, a delayed sowing date of late January into February increases the possibility powdery mildew will infect earlier in the crop development cycle and cause greater yield losses than in earlier sown mungbean crops.
+Therefore, delayed sowing dates of late January into February increase the possibility powdery mildew will infect earlier in the crop's life cycle and cause greater yield losses than in earlier sown mungbean crops.
 
@@
 Green Diamond also containing some notable resistance [@Sparks2017].
-However commercially available mungbean cultivars in Australia lack sufficient resistance to be used as the primary powdery mildew management strategy. 
-Evidence of this is shown by the 2016 field trials with the moderately susceptible cultivar, Jade-AU, where yield losses of up to 32.7 % were recorded [@SueThompson2016]. 
+However, commercially available mungbean cultivars in Australia lack sufficient resistance to be used as the primary powdery mildew management strategy. 
+Evidence of this is shown by field trials conducted in 2016 with the moderately susceptible cultivar, Jade-AU, where yield losses of up to 32.7% were recorded [@SueThompson2016].
 Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013], however no evidence for how they compare to Australian varietal resistance could be found.
@@
 Meta-analyses are statistical tools, which can analyse a collection of experiments, that have a similar aim, and produces a more accurate estimate of the true effect being measured.
-Using a meta-analysis can be useful in situations like this where several studies exist, that have the same objective but may not provide a clear answer to the question due to variation in the results within the individual studies.
-The outcome of a meta-analysis provides a more accurate estimation of the true treatments effect, because it considers the amount of variance in each study and weights the influence of each studies treatment effects according to it's statistical accuracy.
+Using a meta-analysis can be useful in situations like this where several studies exist that have the same objective but may not provide a clear answer to the question due to variation in the results within the individual studies.
+The outcome of a meta-analysis provides a more accurate estimation of the true treatments effect because it considers the amount of variance in each study and weights the influence of each studies treatment effects according to its statistical accuracy.
 Typically meta-analyses consider the effect of a single treatment against a control group across multiple independent studies [@Madden2011]. 
-However meta-analyses can also consider effect differences between multiple treatments and a control group, these are called multi-variate or network meta-analyses [@MaddenEtAl2016]. 
+However meta-analyses can also consider effect differences between multiple treatments and a control group.
+These are called multi-variate or network meta-analyses [@MaddenEtAl2016]. 
 Multi-variate meta-analyses are particularly useful when there are no direct comparisons between two treatments in any of the included studies. 
@@
 
-Considering the recent launch in 2019 of the decision support system (DSS) PowderyMildewMBM [@Diggle], which provides a cost benefit analysis to assists growers in their decision 'if' and 'when' apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
+Considering the recent launch in November 2019 of the decision support system (DSS) PowderyMildewMBM [@Diggle], which provides a cost benefit analysis to assists growers in their decision 'if' and 'when' apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
 The aim of this meta-analysis was to determine, from a collection of unpublished studies, what spray management scenario provides the greatest yield protection from powdery mildew in Australian mungbean.
@@
 # Add a star to the trials which were not in the final analysis
-PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref, "trial_ref"] <-
-  sapply(PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref, "trial_ref"], paste0, "*")
+PM_Mdat[!PM_Mdat$trial_ref%in% slimmer_PM_dat$trial_ref, "trial_ref"] <-
+  sapply(PM_Mdat[!PM_Mdat$trial_ref%in% slimmer_PM_dat$trial_ref, "trial_ref"], paste0, "*")
 
 # Build table
-PM_Mdat %>%
+PM_Mdat%>%
   filter(fungicide_ai == "tebuconazole" |
-           fungicide_ai == "propiconazole") %>%
-  group_by(trial_ref) %>%
+           fungicide_ai == "propiconazole")%>%
+  group_by(trial_ref)%>%
   summarise(
@@
     first_sign_disease = unique(first_sign_disease)
-  ) %>%
-  arrange(year) %>%
+  )%>%
+  arrange(year)%>%
   mutate(Research_org = c(
@@
     rep("USQ$^{c}$", times = 5)
-  )) %>%
+  ))%>%
   rename(
@@
     `Research Organisation` = Research_org
-  ) %>%
+  )%>%
   kable(format = "latex",
@@
         escape = FALSE,
-        caption="Description of fungicide application experiments.") %>%
-  kable_styling() %>%
+        caption="Description of fungicide application experiments.")%>%
+  kable_styling()%>%
   footnote(
@@
     "No sign of powdery mildew",
-    "Small colonies in lower 1/3 of the canopy, up to 75 % of the plants affected",
-    "Colonies in lower 1/2 of the canopy, > 75 % of the plants affected",
-    "Colonies in lower 2/3 of the canopy, up to 75 % of the plants affected",
-    "Colonies in lower 2/3 of the canopy, > 75 % of the plants affected",
-    "Colonies in lower 2/3 of the canopy, 100 % of the plants affected",
-    "Colonies in lower 2/3 of the canopy, 100 % of plants, with some plants with colonies in the top 1/3 of the canopy",
-    "Colonies to top of the plant with > 75 % of the plants affected",
-    "Colonies to top of the plant with > 100 % of the plants affected and heavy leaf drop"
+    "Small colonies in lower 1/3 of the canopy, up to 75% of the plants affected",
+    "Colonies in lower 1/2 of the canopy, > 75% of the plants affected",
+    "Colonies in lower 2/3 of the canopy, up to 75% of the plants affected",
+    "Colonies in lower 2/3 of the canopy, > 75% of the plants affected",
+    "Colonies in lower 2/3 of the canopy, 100% of the plants affected",
+    "Colonies in lower 2/3 of the canopy, 100% of plants, with some plants with colonies in the top 1/3 of the canopy",
+    "Colonies to top of the plant with > 75% of the plants affected",
+    "Colonies to top of the plant with > 100% of the plants affected and heavy leaf drop"
   )
-) %>%
+)%>%
 kable(format = "latex",
       booktabs = TRUE,
-      caption="Powdery mildew severity scoring scale.") %>%
+      caption="Powdery mildew severity scoring scale.")%>%
   kable_styling()
@@
 
-Linear contrasts were used to produce the mean difference in effect sizes, and their respective standard errors and 95&nbsp;% confidence intervals, between each spray schedule treatment.
+Linear contrasts were used to produce the mean difference in effect sizes, and their respective standard errors and 95% confidence intervals, between each spray schedule treatment.
 
@@
 
-```{r Figure1, echo = FALSE, caption = "Yield contrasts"}
+```{r Figure1, echo = FALSE, fig.cap = "Yield contrasts"}
 YieldContrasts
@@
 
-```{r Figure2, echo=FALSE, caption="Season plot"}
+```{r Figure2, echo=FALSE, fig.cap="Season plot"}
 SeasonPlot
@@
 T3[, 2:5] <- round(T3[, 2:5], 4)
-T3 %>%
-  mutate(contrasts = gsub("-", "", contrasts)) %>%
-  mutate(contrasts = gsub(" \\+", " -", contrasts)) %>%
-  mutate(contrasts = gsub(" = 0", "", contrasts)) %>%
+T3%>%
+  mutate(contrasts = gsub("-", "", contrasts))%>%
+  mutate(contrasts = gsub(" \\+", " -", contrasts))%>%
+  mutate(contrasts = gsub(" = 0", "", contrasts))%>%
   rename(
@@
     ` ` = VisP
-  ) %>%
+  )%>%
   kable(format = "latex",
         booktabs = TRUE,
-        caption = "Estimated grain yield contrasts between each spray schedule.") %>%
-  kable_styling() %>%
+        caption = "Estimated grain yield contrasts between each spray schedule.")%>%
+  kable_styling()%>%
   footnote(general = c("** - signficant at 0.005 level",
@@
 <!-- Should we submit the raw data to a data repository like OSF and Figshare? (Paul) -->
+<!-- AHS - Yes, We should submit the data (as we are allowed to) to something like this, yes.
+See the repository I set up for the chickpea asco study, <https://zenodo.org/search?page=1&size=20&q=conceptrecid:3810826&all_versions&sort=-version> -->
 

### 2020-08-03 paper/paper.Rmd
Fix quotes, degree symbol and unescaped "$"

@@
   individual contributions must be provided. The following statements should be 
-  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
+  used "X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
   experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
-  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
+  reagents/materials/analysis tools; Y.Y. wrote the paper." Authorship must be
   limited to those who have contributed substantially to the work reported.
 funding: |
-   Please add: ``This research received no external funding'' or ``This research
-   was funded by NAME OF FUNDER grant number XXX.'' and ``The APC was funded by
-   XXX''. Check carefully that the details given are accurate and use the
+   Please add: "This research received no external funding" or "This research
+   was funded by NAME OF FUNDER grant number XXX." and "The APC was funded by
+   XXX". Check carefully that the details given are accurate and use the
    standard spelling of funding agency names at
@@
 The disease life cycle can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@Sparks2017].
-Weather conditions that favour the rapid development of the disease are cool temperatures between 22&deg; and 26&nbsp;&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
+Weather conditions that favour the rapid development of the disease are cool temperatures between 22$ˆ{\circ}$ and 26&nbsp;$ˆ{\circ}$C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
 
@@
 
-Considering the recent launch in November 2019 of the decision support system (DSS) PowderyMildewMBM [@Diggle], which provides a cost benefit analysis to assists growers in their decision 'if' and 'when' apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
+Considering the recent launch in November 2019 of the decision support system (DSS) PowderyMildewMBM [@Diggle], which provides a cost benefit analysis to assists growers in their decision "if" and "when" apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
 The aim of this meta-analysis was to determine, from a collection of unpublished studies, what spray management scenario provides the greatest yield protection from powdery mildew in Australian mungbean.
@@
 A spray schedule with a $single$ spray, and a spray schedule with two or three spray applications $plus$.
-The division of the treatments produced: 13 $Early_{single}$ treatments; 5 $Early_{plus}$; 32 $Recommended_{single}$; 46 $Recommended_{plus}$'; 17 $Late_{single}$; and 20 $Late_{plus}$.
+The division of the treatments produced: 13 $Early_{single}$ treatments; 5 $Early_{plus}$; 32 $Recommended_{single}$; 46 $Recommended_{plus}$; 17 $Late_{single}$; and 20 $Late_{plus}$.
 $Early_{plus}$ treatments were removed from the subsequent meta-analysis, due to an insufficient sample size.  
@@
 A categorical disease pressure factor was created by binning trials into two levels based on the mean AUDPC of the no spray control plot.
-The two levels, 'low disease pressure' and 'high disease pressure', were separated by the median AUDPC (`r as.double(read.csv(here("cache/median_AUDPC_C.csv")))`) of the no spray control plots.
+The two levels, "low disease pressure" and "high disease pressure", were separated by the median AUDPC (`r as.double(read.csv(here("cache/median_AUDPC_C.csv")))`) of the no spray control plots.
 
@@
 # Results
+
+<!-- AHS - Seems that there is something missing here in this first line? -->
 
@@
 # Discussion
+
 The current advice provided to growers for when to commence fungicide applications for control of powdery mildew, is to spray at the first sign of the disease then if necessary a follow-up spray two weeks later [@SueThompson2016; @Sparks2017].
 This meta-analysis confirms that advice, by showing that applying the first fungicide application, within three days of first sign will significantly mitigate yield loss from powdery mildew by between `r round(PM_mv$ci.lb[3],5)*1000` to `r round(PM_mv$ci.ub[3],5)*1000` kg / ha ($Recommended$, `r reportP(PM_mv$pval[3])`).
-In addition, spray schedules which commenced 'late', up to 13 days after first sign of the disease were still effective at mitigating yield loss by  `r round(PM_mv$ci.lb[5],5)*1000` to `r round(PM_mv$ci.ub[5],5)*1000` kg / ha ($Late$,`r reportP(PM_mv$pval[5])`).
+Additionally, spray schedules which commenced "late", up to 13 days after first sign of the disease were still effective at mitigating yield loss by `r round(PM_mv$ci.lb[5],5)*1000` to `r round(PM_mv$ci.ub[5],5)*1000` kg / ha ($Late$,`r reportP(PM_mv$pval[5])`).
 Spray schedules which included follow-up fungicide applications were on average more effective at reducing yield loss due to powdery mildew by; 
@@
 
-This meta-analysis also provides a effective spray window for fungicide applications, given that spray schedules, which commenced 'late' were still significantly effective at mitigating yield loss ($Late$ `r reportP(PM_mv$pval[5])`) 7 - 13 days after the first sign of disease.
+This meta-analysis also provides a effective spray window for fungicide applications, given that spray schedules, which commenced "late" were still significantly effective at mitigating yield loss ($Late$ `r reportP(PM_mv$pval[5])`) 7 - 13 days after the first sign of disease.
 Growers typically do not have the time to inspect their crop regularly for the first sign of powdery mildew and therefore the disease may not be spotted within the first couple of days of it establishing.
@@
 Second applications, if they are needed, should be applied at least 10 - 14 days after the first application and not within 21 days of harvest [@APVMAcustodia].
-If time permitted a second spray after the first 'late' application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(T3$estimates[10], 4)*1000` kg / ha, when compared to the $Late$, single spray treatment `r reportP(T3$pval[10])`.
+If time permitted a second spray after the first "late" application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(T3$estimates[10], 4)*1000` kg / ha, when compared to the $Late$, single spray treatment `r reportP(T3$pval[10])`.
 
-It is important to note, the studies included in this meta-analysis may not reflect a 'normal' mungbean season. 
+It is important to note, the studies included in this meta-analysis may not reflect a "normal" mungbean season. 
 All the included experiments were intentionally sown late in the season, from January through to as late as early March, to ensure powdery mildew infection (Figure \@ref(fig:Figure2)). 
@@
 The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability that one or two fungicide sprays would protect yields sufficiently to increase the net profit.
-The scope of the meta-analysis is limited to the timing of fungicide application and therefore we can't validate all the variables available in PowderyMildewMBM. 
+The scope of the meta-analysis is limited to the timing of fungicide application and therefore we can not validate all the variables available in PowderyMildewMBM. 
 However our results validate the decision of the app developers not to recommend prophylactic fungicide applications. 
@@
 Scouting at intervals greater than 12 - 13 days, might risk crop losses if a spray schedule does not commence within aforementioned the spray window.
-More work is needed to understand when 'late' fungicide applications are too late.
+More work is needed to understand when "late" fungicide applications are too late.
 
-We estimate the costs of applying tebuconazole fungicide at \$4.18 AUD / ha, if fungicide is purchased at \$15 / L [@Simfendorfer2011] and applications cost are $2 per hectare [@QueenslandGovernment2019].
+We estimate the costs of applying tebuconazole fungicide at \$4.18 AU / ha, if fungicide is purchased at \$15 / L [@Simfendorfer2011] and applications cost are \$2 per hectare [@QueenslandGovernment2019].
 The meta-analysis estimates average yield savings of between `r coef(PM_mv)[3]*1000` kg / ha ($Recommended$) and `r coef(PM_mv)[4]*1000` kg / ha ($RecommendedPlus$). 
-These average yield savings would save \$`r (coef(PM_mv)[3]*1000)` AUD / ha for a single application at first sign and `r coef(PM_mv)[4]*1000` AUD / ha if a follow-up application is made.
+These average yield savings would save \$`r (coef(PM_mv)[3]*1000)` AU / ha for a single application at first sign and \$`r coef(PM_mv)[4]*1000` AU / ha if a follow-up application is made.
 Lucrative returns such as these may tempt growers into applying fungicide to control diseases such as powdery mildew when they are unnecessary.
 Excessive use of fungicides are highly likely to lead ongoing problems such as fungicide resistance.
-*Podosphaera xanthii* is categorised by the Australian Fungicide resistance Action Committee (FRAC) as a 'High risk' candidate to evolve fungicide resistance [@FRACrisk2019].
+*Podosphaera xanthii* is categorised by the Australian Fungicide resistance Action Committee (FRAC) as a "High risk" candidate to evolve fungicide resistance [@FRACrisk2019].
 Evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with potential fungicide resistance in mind.
@@
 Excessive fungicide sprays by a single active increase the selection pressure on the pathogen to evolve resistance [@Brent2007]. 
-If any strains of the pathogen with resistance to the fungicide are present in a population regular use of the fungicide will increase it's proportion in the population. 
+If any strains of the pathogen with resistance to the fungicide are present in a population regular use of the fungicide will increase its proportion in the population. 
 Therefore, managing the disease with fungicides for the highest economic return is likely not to require eradication of the causal pathogen. 
@@
 However it does not provide enough certainty to when late fungicide applications would be too late to protect yield losses due to the disease. 
-Future experiments should take note of physiological maturity of the crop throughout the season so 'crop age' might be considered as a covariate in future analyses.
+Future experiments should take note of physiological maturity of the crop throughout the season so "crop age" might be considered as a covariate in future analyses.
 In cases where mungbean physiological maturity may not have been recorded the APSIM mungbean module [@RobertsonAPSIMlegume2002].

### 2020-08-03 paper/paper.Rmd
Minor edits to affiliations and fix degree symbols

@@
   - name: Adam H. Sparks
-    affil: 3
+    affil: 1
     orcid: 0000-0002-0061-8359
@@
       Toowoomba, Queensland, 4350 Australia
-    email: Paul.Melloy@usq.edu.au
   - num: 2
@@
       Viçosa, 36570-000 Minas Gearais, Brazil
-    email: delponte@ufv.br
-  - num: 3
-    address: |
-      University of Southern Queensland
-      Centre for Crop Health
-      Toowoomba, Queensland, 4350 Australia
-    email: Adam.Sparks@usq.edu.au
 correspondence: |
@@
 
+<!-- For reference in writing for MDPI, <https://www.mdpi.com/authors/layout> -->
+
 ```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
@@
 The disease life cycle can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@Sparks2017].
-Weather conditions that favour the rapid development of the disease are cool temperatures between 22$ˆ{\circ}$ and 26&nbsp;$ˆ{\circ}$C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
+Weather conditions that favour the rapid development of the disease are cool temperatures between 22&nbsp;&deg; and 26&nbsp;&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
 

### 2020-08-03 paper/paper.Rmd
Capitalise title to follow MDPI guidelines

@@
 ---
-title: A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean
+title: A Meta-analysis of Fungicide Spray Schedules to Minimise Yield Loss From Powdery Mildew in Australian Mungbean
 author:

### 2020-08-03 paper/paper.Rmd
Format numbers in text per MDPI

@@
 Prior to the 1970s the total area grown in Australia rarely exceeded 1000 hectares [@Lawn1978].
-At the end of the 1980s, between 3,000 to 10,0000 hectares were being harvested for dried beans in Australia, of which mungbean is categorised by the FAO statistics data repository [@FAOSTAT].
-In the decade leading up to 2018, between 35 - 86.4 thousand hectares of dried beans were planted annually.
+At the end of the 1980s, between 3,000 to 10,0000 hectares were being harvested for dried beans in Australia, of which mungbean is categorised by the Food and Agriculture Organization of the United Nations' statistics data repository [@FAOSTAT].
+In the decade leading up to 2018, between 35 - 86.4 thousand hectares of dried beans were planted annually in Australia.
 This increase is attributed to high value export markets and to the improved yields in the new cultivars [@Clarry2016].
@@
 In 2019, approximately 90% of Australian mungbean was grown for export with lucrative returns of up to \$1300&nbsp;AU per tonne [@QueenslandGovernment2019].
-Mungbean potentially yields up to three tonnes per hectare [@ThomasRobert2004], but due to high variability in yields between seasons and locations, the average Australian farm still yields less than one tonne per hectare [@Chauhan2018].
+Mungbean potentially yields up to 3 tonnes per hectare [@ThomasRobert2004], but due to high variability in yields between seasons and locations, the average Australian farm still yields less than 1 tonne per hectare [@Chauhan2018].
 
@@
 Some trials we obtained the raw data, others the reported means of each treatment, with all but one study reporting some form of variance along with the mean.
-Twenty six trials in total were collated.
+In total, 26 trials were collated.
 

### 2020-08-04 paper/paper.Rmd
Use same symbol, "*", for italics
Update hard coding and some other corrections updating code for seasonplot

--- 2020-08-03 paper/paper.Rmd
@@
 ---
-title: A Meta-analysis of Fungicide Spray Schedules to Minimise Yield Loss From Powdery Mildew in Australian Mungbean
+title: A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean
 author:
@@
   - name: Adam H. Sparks
-    affil: 1
+    affil: 3
     orcid: 0000-0002-0061-8359
@@
       Toowoomba, Queensland, 4350 Australia
+    email: Paul.Melloy@usq.edu.au
   - num: 2
@@
       Viçosa, 36570-000 Minas Gearais, Brazil
+    email: delponte@ufv.br
+  - num: 3
+    address: |
+      University of Southern Queensland
+      Centre for Crop Health
+      Toowoomba, Queensland, 4350 Australia
+    email: Adam.Sparks@usq.edu.au
 correspondence: |
@@
 bibliography: ../Mungbean.bib
+#appendix: appendix.tex
 simplesummary: |
@@
   individual contributions must be provided. The following statements should be 
-  used "X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
+  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
   experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
-  reagents/materials/analysis tools; Y.Y. wrote the paper." Authorship must be
+  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
   limited to those who have contributed substantially to the work reported.
 funding: |
-   Please add: "This research received no external funding" or "This research
-   was funded by NAME OF FUNDER grant number XXX." and "The APC was funded by
-   XXX". Check carefully that the details given are accurate and use the
+   Please add: ``This research received no external funding'' or ``This research
+   was funded by NAME OF FUNDER grant number XXX.'' and ``The APC was funded by
+   XXX''. Check carefully that the details given are accurate and use the
    standard spelling of funding agency names at
@@
   manuscript, an in the decision to publish the results'.
+sampleavailability: |
+  Samples of the compounds ...... are available from the authors.
 abbreviations:
-  - short: DSS
-    long: Decision support system
-output:
-  bookdown::pdf_book:
-    base_format: rticles::mdpi_article
+  - short: MDPI
+    long: Multidisciplinary Digital Publishing Institute
+  - short: DOAJ
+    long: Directory of open access journals
+  - short: TLA
+    long: Three letter acronym
+  - short: LD 
+    long: linear dichroism
+output: rticles::mdpi_article
 ---
-
-<!-- For reference in writing for MDPI, <https://www.mdpi.com/authors/layout> -->
 
@@
   install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, here, english, pander)
+pacman::p_load(tidyverse, kableExtra, here, english, pander, lubridate)
 
@@
 Mungbean was first brought to Australia in the 1930s for use as a forage or green manure crop.
-However, it was only somewhat recently, during the 1960s that mungbean was grown commercially [@Lawn1978; @Chauhan2018].
+However, it was only somewhat recently, the 1960s that mungbean was grown commercially [@Lawn1978; @Chauhan2018].
 Prior to the 1970s the total area grown in Australia rarely exceeded 1000 hectares [@Lawn1978].
 At the end of the 1980s, between 3,000 to 10,0000 hectares were being harvested for dried beans in Australia, of which mungbean is categorised by the FAO statistics data repository [@FAOSTAT].
-In the decade leading up to 2018, between 35 - 86.4 thousand hectares of dried beans were planted annually.
-This increase is attributed to high value export markets and to the improved yields in the new cultivars [@Clarry2016].
+In the decade leading up to 2018 between 35 - 86.4 thousand hectares of dried beans were planted annually.
+This increase is attributed high value export markets and to the improved yields in the new cultivars [@Clarry2016].
 Currently mungbean is predominantly grown in southern Queensland and northern New South Wales as a short season summer legume crop.
-In 2019, approximately 90% of Australian mungbean was grown for export with lucrative returns of up to \$1300&nbsp;AU per tonne [@QueenslandGovernment2019].
-Mungbean potentially yields up to three tonnes per hectare [@ThomasRobert2004], but due to high variability in yields between seasons and locations, the average Australian farm still yields less than one tonne per hectare [@Chauhan2018].
+In 2019, approximately 90&nbsp;% of Australian mungbean was grown for export with lucrative returns of up to \$1300&nbsp;AU a tonne [@QueenslandGovernment2019].
+Mungbean potentially yields up to 3 tonnes per hectare [@ThomasRobert2004], but due to high variability in yields between seasons and locations, the average Australian farm still yields less than 1 tonne per hectare [@Chauhan2018].
 
-The high variability in yields can in part be attributed to a range of diseases that affect the crop [@Kelly2017a].
+The high variability in yields, in part, can be attributed to a range of diseases that affect the crop [@Kelly2017a].
 Two major foliar diseases, tan spot or common wilt (*Curtobacterium flaccumfaciens* pv.
@@
 
+Powdery mildew is caused by two separate genera of fungi in Australia *Podosphaera xanthii* and an unnamed *Psuedoidium sp.* (Kiss and Kelly Personal Communication).
 While the pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified. 
-The disease life cycle can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@Sparks2017].
-Weather conditions that favour the rapid development of the disease are cool temperatures between 22&nbsp;&deg; and 26&nbsp;&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
+The disease lifecycle can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@Sparks2017].
+Weather conditions that favour the rapid development of the disease are cool temperatures between 22&deg; and 26&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
 
-Due to the requirement for cool temperatures for infection, planting date is an effective strategy for preventing the development of powdery mildew in mungbean [@AMAplanting].
+Due to the requirement for cooler temperatures for infection, planting date is an effective strategy for preventing the development of powdery mildew in mungbean [@AMAplanting].
 In southern Queensland and northern New South Wales, sowing dates between late spring (November) and mid-summer (January) are advised to avoid the conducive cooler autumn temperatures, which normally commence in March.
-Therefore, delayed sowing dates of late January into February increase the possibility powdery mildew will infect earlier in the crop's life cycle and cause greater yield losses than in earlier sown mungbean crops.
+Therefore, a delayed sowing date of late January into February increases the possibility powdery mildew will infect earlier in the crop development cycle and cause greater yield losses than in earlier sown mungbean crops.
 
@@
 Green Diamond also containing some notable resistance [@Sparks2017].
-However, commercially available mungbean cultivars in Australia lack sufficient resistance to be used as the primary powdery mildew management strategy. 
-Evidence of this is shown by field trials conducted in 2016 with the moderately susceptible cultivar, Jade-AU, where yield losses of up to 32.7% were recorded [@SueThompson2016].
+However commercially available mungbean cultivars in Australia lack sufficient resistance to be used as the primary powdery mildew management strategy. 
+Evidence of this is shown by the 2016 field trials with the moderately susceptible cultivar, Jade-AU, where yield losses of up to 32.7 % were recorded [@SueThompson2016]. 
 Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013], however no evidence for how they compare to Australian varietal resistance could be found.
@@
 Meta-analyses are statistical tools, which can analyse a collection of experiments, that have a similar aim, and produces a more accurate estimate of the true effect being measured.
-Using a meta-analysis can be useful in situations like this where several studies exist that have the same objective but may not provide a clear answer to the question due to variation in the results within the individual studies.
-The outcome of a meta-analysis provides a more accurate estimation of the true treatments effect because it considers the amount of variance in each study and weights the influence of each studies treatment effects according to its statistical accuracy.
+Using a meta-analysis can be useful in situations like this where several studies exist, that have the same objective but may not provide a clear answer to the question due to variation in the results within the individual studies.
+The outcome of a meta-analysis provides a more accurate estimation of the true treatments effect, because it considers the amount of variance in each study and weights the influence of each studies treatment effects according to it's statistical accuracy.
 Typically meta-analyses consider the effect of a single treatment against a control group across multiple independent studies [@Madden2011]. 
-However meta-analyses can also consider effect differences between multiple treatments and a control group.
-These are called multi-variate or network meta-analyses [@MaddenEtAl2016]. 
+However meta-analyses can also consider effect differences between multiple treatments and a control group, these are called multi-variate or network meta-analyses [@MaddenEtAl2016]. 
 Multi-variate meta-analyses are particularly useful when there are no direct comparisons between two treatments in any of the included studies. 
@@
 
-Considering the recent launch in November 2019 of the decision support system (DSS) PowderyMildewMBM [@Diggle], which provides a cost benefit analysis to assists growers in their decision "if" and "when" apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
+Considering the recent launch in 2019 of the decision support system (DSS) PowderyMildewMBM [@Diggle], which provides a cost benefit analysis to assists growers in their decision 'if' and 'when' apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
 The aim of this meta-analysis was to determine, from a collection of unpublished studies, what spray management scenario provides the greatest yield protection from powdery mildew in Australian mungbean.
@@
 The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the Grains Research and Development (GRDC) northern grains regions of eastern Australia, which grows the majority of Australia's summer crops.
-Data from trials undertaken in this region had to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; the fungicide active ingredients; fungicide dose; and crop yield.
+Data from trials undertaken in this regionhad to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; the fungicide active ingredients; fungicide dose; and crop yield.
 The data were subset to only include fungicide treatments with the same mode of action; demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole were thus retained in the dataset.
-Subsequently the 26 trials were reduced to 17 trials (Table \@ref(tab:Table1)).
+Subsequently the 26 trials were reduced to 17 trials (Table 1). 
 Two more trials were also removed because grain yield variance, which was required for the meta-analysis, was not reported, reducing the number of trials down to 15.
 
-```{r Table1, echo=FALSE, message=FALSE, warning=FALSE}
+```{r Table1_ExperimentalDetail, echo=FALSE, message=FALSE, warning=FALSE}
 # Add a star to the trials which were not in the final analysis
-PM_Mdat[!PM_Mdat$trial_ref%in% slimmer_PM_dat$trial_ref, "trial_ref"] <-
-  sapply(PM_Mdat[!PM_Mdat$trial_ref%in% slimmer_PM_dat$trial_ref, "trial_ref"], paste0, "*")
+PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref, "trial_ref"] <-
+  sapply(PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref, "trial_ref"], paste0, "*")
 
 # Build table
-PM_Mdat%>%
+PM_Mdat %>%
   filter(fungicide_ai == "tebuconazole" |
-           fungicide_ai == "propiconazole")%>%
-  group_by(trial_ref)%>%
+           fungicide_ai == "propiconazole") %>%
+  group_by(trial_ref) %>%
   summarise(
@@
     first_sign_disease = unique(first_sign_disease)
-  )%>%
-  arrange(year)%>%
+  ) %>%
+  arrange(year) %>%
   mutate(Research_org = c(
@@
     rep("USQ$^{c}$", times = 5)
-  ))%>%
+  )) %>%
   rename(
@@
     `Research Organisation` = Research_org
-  )%>%
+  ) %>%
   kable(format = "latex",
@@
         escape = FALSE,
-        caption="Description of fungicide application experiments.")%>%
-  kable_styling()%>%
+        caption="Description of fungicide application experiments.") %>%
+  kable_styling() %>%
   footnote(
@@
 
-From the trials which were included in the meta-analysis, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12))` were planted in late December, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 1))` in January and `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 2))` were trials planted in February (Table \@ref(tab:Table1)).
+From the trials which were included in the meta-analysis, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12))` were planted in late December, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 1))` in January and `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 2))` were trials planted in February (Table 1).
 
@@
 A spray schedule with a $single$ spray, and a spray schedule with two or three spray applications $plus$.
-The division of the treatments produced: 13 $Early_{single}$ treatments; 5 $Early_{plus}$; 32 $Recommended_{single}$; 46 $Recommended_{plus}$; 17 $Late_{single}$; and 20 $Late_{plus}$.
+The division of the treatments produced: 13 $Early_{single}$ treatments; 5 $Early_{plus}$; 32 $Recommended_{single}$; 46 $Recommended_{plus}$'; 17 $Late_{single}$; and 20 $Late_{plus}$.
 $Early_{plus}$ treatments were removed from the subsequent meta-analysis, due to an insufficient sample size.  
@@
 
-An ordinal 1 -- 9 scale was used to describe the mean powdery mildew plot severity in most trials (Table \@ref(tab:Table2)).
-However, the 2013 NGA trials (Table \@ref(tab:Table1)) reported mean plot severity as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the lower, middle or upper canopy.
+An ordinal 1 -- 9 scale was used to describe the mean powdery mildew plot severity in most trials (Table 2).
+However, the 2013 NGA trials (Table 1) reported mean plot severity as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the lower, middle or upper canopy.
 Given the ordinal scale ranked plots on the percent of foliage showing the disease from the lower canopy to the upper canopy, a conversion from percentage of the diseased canopy, to the 1 -- 9 scale was straight-forward.
@@
 A categorical disease pressure factor was created by binning trials into two levels based on the mean AUDPC of the no spray control plot.
-The two levels, "low disease pressure" and "high disease pressure", were separated by the median AUDPC (`r as.double(read.csv(here("cache/median_AUDPC_C.csv")))`) of the no spray control plots.
+The two levels, 'low disease pressure' and 'high disease pressure', were separated by the median AUDPC (`r as.double(read.csv(here("cache/median_AUDPC_C.csv")))`) of the no spray control plots.
 
-```{r Table2, echo=FALSE}
+```{r Table2_1to9Scale, echo=FALSE}
 data.frame(
@@
     "No sign of powdery mildew",
-    "Small colonies in lower 1/3 of the canopy, up to 75% of the plants affected",
-    "Colonies in lower 1/2 of the canopy, > 75% of the plants affected",
-    "Colonies in lower 2/3 of the canopy, up to 75% of the plants affected",
-    "Colonies in lower 2/3 of the canopy, > 75% of the plants affected",
-    "Colonies in lower 2/3 of the canopy, 100% of the plants affected",
-    "Colonies in lower 2/3 of the canopy, 100% of plants, with some plants with colonies in the top 1/3 of the canopy",
-    "Colonies to top of the plant with > 75% of the plants affected",
-    "Colonies to top of the plant with > 100% of the plants affected and heavy leaf drop"
+    "Small colonies in lower 1/3 of the canopy, up to 75 % of the plants affected",
+    "Colonies in lower 1/2 of the canopy, > 75 % of the plants affected",
+    "Colonies in lower 2/3 of the canopy, up to 75 % of the plants affected",
+    "Colonies in lower 2/3 of the canopy, > 75 % of the plants affected",
+    "Colonies in lower 2/3 of the canopy, 100 % of the plants affected",
+    "Colonies in lower 2/3 of the canopy, 100 % of plants, with some plants with colonies in the top 1/3 of the canopy",
+    "Colonies to top of the plant with > 75 % of the plants affected",
+    "Colonies to top of the plant with > 100 % of the plants affected and heavy leaf drop"
   )
-)%>%
+) %>%
 kable(format = "latex",
       booktabs = TRUE,
-      caption="Powdery mildew severity scoring scale.")%>%
+      caption="Powdery mildew severity scoring scale.") %>%
   kable_styling()
@@
 
-Linear contrasts were used to produce the mean difference in effect sizes, and their respective standard errors and 95% confidence intervals, between each spray schedule treatment.
+Linear contrasts were used to produce the mean difference in effect sizes, and their respective standard errors and 95&nbsp;% confidence intervals, between each spray schedule treatment.
 
@@
 
-```{r Figure1, echo = FALSE, fig.cap = "Yield contrasts"}
+```{r Figure1, echo = FALSE, caption = "Yield contrasts"}
 YieldContrasts
@@
 
-<!-- AHS - Seems that there is something missing here in this first line? -->
-
-$control$, $Early_{single}$, $Recommended_{single}$, $Recommended_{plus}$, $Late_{single}$, and $Late_{plus}$.  
 Overall the meta-analysis indicated that, with the exception of the $Early_{single}$ treatment, all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure \@ref(fig:Figure1)).
-Treatments which incorporating multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table \@ref(tab:Table3)).
-Both $Recommended_{plus}$ and $Late_{plus}$ were also significantly higher than single applications $Early_{single}$ (P = `r T3$pval[2]` and P = `r T3$pval[4]` respectively) and $Late_{single}$(P = `r T3$pval[8]` and P = `r T3$pval[10]` respectively).
-However, comparing $Late_{plus}$ and $Early_{single}$ should done with caution given these treatments did not occur within the same trial for any of the 15 trials included in the meta-analysis. 
-Within the single fungicide application treatments `Recommended` provided the highest yield protection, and was estimated at saving an average of 159.9 kg / ha (SE = 30.5 kg / ha) relative to the no spray control (P < 0.0001).
-`Recommended` treatments were was also significantly higher than `Early` treatments by 122.1 kg / ha (SE = 42.1 kg / ha)(P = 0.004). 
-Single `Late` applications were effective at significantly mitigating the effect of powdery mildew on yield by a mean of 122 kg / ha (SE = 39.2 kg / ha)(P = 0.0019). 
-However, this estimate was not significantly different to single `Early` or `Recommended` treatments (P = 0.119; P = 0.278 respectively).
+Treatments which incorporated multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3).
+The treatment that showed the most yield saved compared to the control, $Recommended_{plus}$, was also significantly higher than all other single applications, (
+$Early_{single}$, `r reportP(contrast_Ssum$pvals[grep("Recommended_plus - Early",contrast_Ssum$contrast)])`, 
+$Recommended_{single}$, `r reportP(contrast_Ssum$pvals[grep("Recommended_plus - Recommended",contrast_Ssum$contrast)])` and
+$Late_{single}$, `r reportP(contrast_Ssum$pvals[grep("Late - Recommended_plus",contrast_Ssum$contrast)])`). 
+However the $Late_{plus}$ only showed significantly greater yield saved when compared to the $Early_{single}$ treatment (`r reportP(contrast_Ssum$pvals[grep("Late_plus - Early",contrast_Ssum$contrast)])`)
+Consideration should be given when comparing $Late_{plus}$ and $Early_{single}$ treatments given they did not occur within the same trial for any of the 15 trials included in the meta-analysis. 
+Within the single fungicide application treatments $Late_{single}$ provided the highest yield protection, and was estimated at saving an average of `r round(PM_mv$b[5,1] * 1000, 2)` kg / ha (SE = `r round(PM_mv$se[5] * 1000, 2)` kg / ha) relative to the no spray control (`r reportP(PM_mv$pval[5])`).
+$Early_{single}$ treatments were significantly lower than all other treatments (Table 3) and reported a mean estimate `r abs(round(PM_mv$b[2,1] * 1000, 2))` kg / ha (SE = `r round(PM_mv$se[2] * 1000, 2)` kg / ha) lower than the no spray control (`r reportP(PM_mv$pval[2])`).
 
@@
 
+First sign of powdery mildew was observed as early as the 28th of February in the 2013 trial at .... ; and as late as the 12th of April in the 2018 trial at ...
+
 <!-- What is this `SeasonPlot`? I can't find any docs and no file named `SeasonPlot`. It should just be code here int the doc for easy editing. -->
 
-```{r Figure2, echo=FALSE, fig.cap="Season plot"}
-SeasonPlot
+```{r Figure2, echo=FALSE, caption="Season plot"}
+# Create the data frame for the plot
+season_dates <- PM_MB_means %>%
+   group_by(trial_ref) %>%
+   summarise(
+      Planting_date = unique(planting_date),
+      Harvest_date = unique(harvest_date),
+      First_sign_PM = unique(first_sign_disease),
+      season_length = as.Date(unique(harvest_date)) - as.Date(unique(planting_date)),
+      cropping_season = "Actual"
+   )
+mean(ymd(PM_Mdat$planting_date), na.rm = TRUE)
+
+PM_Mdat %>%
+  distinct(trial_ref, planting_date, harvest_date,first_sign_disease) %>%
+  mutate(planting_date = ymd(planting_date))%>%
+  mutate(harvest_date = ymd(harvest_date))%>%
+    mutate(cropping_season = case_when(
+    is.na(planting_date) | is.na(harvest_date ) ~ "Estimated",
+    TRUE ~ "Actual"))%>%
+  mutate(season_length = case_when(
+    is.na(planting_date) ~ harvest_date - mean(planting_date,na.rm = TRUE),
+    is.na(harvest_date) ~ mean(harvest_date,na.rm = TRUE) - planting_date,
+    TRUE ~ harvest_date - planting_date
+  ))
+
+# For some trials where planting date and Harvest date is missing let's estimate 
+#     the season length by using the mean of all season lengths
+season_dates[is.na(season_dates$season_length),"cropping_season"] <- "Estimated"
+
+season_dates[is.na(season_dates$Planting_date),"Planting_date"] <- 
+   season_dates[is.na(season_dates$Planting_date),"Harvest_date"] - 
+   as.numeric(mean(season_dates$season_length, na.rm = TRUE))
+
+season_dates[is.na(season_dates$Harvest_date),"Harvest_date"] <- 
+   season_dates[is.na(season_dates$Harvest_date),"Planting_date"] + 
+   as.numeric(mean(season_dates$season_length, na.rm = TRUE))
+
+season_dates[is.na(season_dates$season_length),"season_length"] <- 
+   mean(season_dates$season_length, na.rm = TRUE)
+
+season_dates$Planting_day <- yday(season_dates$Planting_date)
+season_dates$Disease_day <- yday(season_dates$First_sign_PM)
+
+season_dates[c(1:2,6), "Planting_day"] <- 1
+
+season_dates$Harvest_day <-
+   season_dates$Planting_day + season_dates$season_length
+
+first_day_month <- c(0, 31, 60, 91, 121, 152, 182, 212, 244, 274) + 1
+axis_labels_date <-
+   c(
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[1], "%b-%d"),
+      # Jan
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[2], "%b-%d"),
+      # Feb
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[3], "%b-%d"),
+      # March
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[4], "%b-%d"),
+      # April
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[5], "%b-%d"),
+      # May
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[6], "%b-%d"),
+      # June
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[7], "%b-%d"),
+      # July
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[8], "%b-%d"),
+      # August
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[9], "%b-%d"),
+      # Sept
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[10], "%b-%d") # October
+   )
+
+# reorder the factors so they will appear in chronological order
+# I used First sign because all trials have recorded this
+season_dates$trial_ref <-
+   factor(season_dates$trial_ref,
+          levels = levels(season_dates$trial_ref)[rev(order(season_dates$First_sign_PM))])
+
+# Plot
+season_dates %>%
+   ggplot() +
+   geom_pointrange(aes(
+      x = trial_ref,
+      y = Disease_day,
+      ymin = Planting_day,
+      ymax = Harvest_day,
+      colour = cropping_season
+   )) +
+   scale_y_continuous(limits = c(
+      0,
+      max(
+         season_dates$Planting_day +
+            season_dates$season_length,
+         na.rm = TRUE
+      )
+   ),
+   labels = axis_labels_date,
+   breaks = first_day_month) +
+   geom_point(aes(x = trial_ref, y = Disease_day)) +
+   coord_flip() +
+   scale_color_manual(values=c("black","grey70"))+
+   ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
+
 ```
 
-```{r Table3, echo = FALSE}
+```{r table3_Contrasts, echo = FALSE}
+T3 <-
+  read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
 T3[, 2:5] <- round(T3[, 2:5], 4)
-T3%>%
-  mutate(contrasts = gsub("-", "", contrasts))%>%
-  mutate(contrasts = gsub(" \\+", " -", contrasts))%>%
-  mutate(contrasts = gsub(" = 0", "", contrasts))%>%
+T3 %>%
+  mutate(contrasts = gsub("-", "", contrasts)) %>%
+  mutate(contrasts = gsub(" \\+", " -", contrasts)) %>%
+  mutate(contrasts = gsub(" = 0", "", contrasts)) %>%
   rename(
@@
     ` ` = VisP
-  )%>%
+  ) %>%
   kable(format = "latex",
         booktabs = TRUE,
-        caption = "Estimated grain yield contrasts between each spray schedule.")%>%
-  kable_styling()%>%
+        caption = "Estimated grain yield contrasts between each spray schedule.") %>%
+  kable_styling() %>%
   footnote(general = c("** - signficant at 0.005 level",
@@
 # Discussion
-
 The current advice provided to growers for when to commence fungicide applications for control of powdery mildew, is to spray at the first sign of the disease then if necessary a follow-up spray two weeks later [@SueThompson2016; @Sparks2017].
 This meta-analysis confirms that advice, by showing that applying the first fungicide application, within three days of first sign will significantly mitigate yield loss from powdery mildew by between `r round(PM_mv$ci.lb[3],5)*1000` to `r round(PM_mv$ci.ub[3],5)*1000` kg / ha ($Recommended$, `r reportP(PM_mv$pval[3])`).
-Additionally, spray schedules which commenced "late", up to 13 days after first sign of the disease were still effective at mitigating yield loss by `r round(PM_mv$ci.lb[5],5)*1000` to `r round(PM_mv$ci.ub[5],5)*1000` kg / ha ($Late$,`r reportP(PM_mv$pval[5])`).
+In addition, spray schedules which commenced 'late', up to 13 days after first sign of the disease were still effective at mitigating yield loss by  `r round(PM_mv$ci.lb[5],5)*1000` to `r round(PM_mv$ci.ub[5],5)*1000` kg / ha ($Late$,`r reportP(PM_mv$pval[5])`).
 Spray schedules which included follow-up fungicide applications were on average more effective at reducing yield loss due to powdery mildew by; 
@@
 
-This meta-analysis also provides a effective spray window for fungicide applications, given that spray schedules, which commenced "late" were still significantly effective at mitigating yield loss ($Late$ `r reportP(PM_mv$pval[5])`) 7 - 13 days after the first sign of disease.
+This meta-analysis also provides a effective spray window for fungicide applications, given that spray schedules, which commenced 'late' were still significantly effective at mitigating yield loss ($Late$ `r reportP(PM_mv$pval[5])`) 7 - 13 days after the first sign of disease.
 Growers typically do not have the time to inspect their crop regularly for the first sign of powdery mildew and therefore the disease may not be spotted within the first couple of days of it establishing.
@@
 Second applications, if they are needed, should be applied at least 10 - 14 days after the first application and not within 21 days of harvest [@APVMAcustodia].
-If time permitted a second spray after the first "late" application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(T3$estimates[10], 4)*1000` kg / ha, when compared to the $Late$, single spray treatment `r reportP(T3$pval[10])`.
+If time permitted a second spray after the first 'late' application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(T3$estimates[10], 4)*1000` kg / ha, when compared to the $Late$, single spray treatment `r reportP(T3$pval[10])`.
 
-It is important to note, the studies included in this meta-analysis may not reflect a "normal" mungbean season. 
+It is important to note, the studies included in this meta-analysis may not reflect a 'normal' mungbean season. 
 All the included experiments were intentionally sown late in the season, from January through to as late as early March, to ensure powdery mildew infection (Figure \@ref(fig:Figure2)). 
@@
 The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability that one or two fungicide sprays would protect yields sufficiently to increase the net profit.
-The scope of the meta-analysis is limited to the timing of fungicide application and therefore we can not validate all the variables available in PowderyMildewMBM. 
+The scope of the meta-analysis is limited to the timing of fungicide application and therefore we can't validate all the variables available in PowderyMildewMBM. 
 However our results validate the decision of the app developers not to recommend prophylactic fungicide applications. 
@@
 Scouting at intervals greater than 12 - 13 days, might risk crop losses if a spray schedule does not commence within aforementioned the spray window.
-More work is needed to understand when "late" fungicide applications are too late.
+More work is needed to understand when 'late' fungicide applications are too late.
 
-We estimate the costs of applying tebuconazole fungicide at \$4.18 AU / ha, if fungicide is purchased at \$15 / L [@Simfendorfer2011] and applications cost are \$2 per hectare [@QueenslandGovernment2019].
+We estimate the costs of applying tebuconazole fungicide at \$4.18 AUD / ha, if fungicide is purchased at \$15 / L [@Simfendorfer2011] and applications cost are $2 per hectare [@QueenslandGovernment2019].
 The meta-analysis estimates average yield savings of between `r coef(PM_mv)[3]*1000` kg / ha ($Recommended$) and `r coef(PM_mv)[4]*1000` kg / ha ($RecommendedPlus$). 
-These average yield savings would save \$`r (coef(PM_mv)[3]*1000)` AU / ha for a single application at first sign and \$`r coef(PM_mv)[4]*1000` AU / ha if a follow-up application is made.
+These average yield savings would save \$`r (coef(PM_mv)[3]*1000)` AUD / ha for a single application at first sign and `r coef(PM_mv)[4]*1000` AUD / ha if a follow-up application is made.
 Lucrative returns such as these may tempt growers into applying fungicide to control diseases such as powdery mildew when they are unnecessary.
 Excessive use of fungicides are highly likely to lead ongoing problems such as fungicide resistance.
-*Podosphaera xanthii* is categorised by the Australian Fungicide resistance Action Committee (FRAC) as a "High risk" candidate to evolve fungicide resistance [@FRACrisk2019].
+*Podosphaera xanthii* is categorised by the Australian Fungicide resistance Action Committee (FRAC) as a 'High risk' candidate to evolve fungicide resistance [@FRACrisk2019].
 Evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with potential fungicide resistance in mind.
@@
 At the time of writing, in Australia one fungicide is registered with the to treat powdery mildew in mungbean, Veritas/Custodia (200 g/L tebuconazole with 120 g/L azoxystrobin).
-This fungicide provides dual action: tebuconazole disrupts C-14 demethylase, required in sterol biosynthesis for cell membranes; and azoxystrobin, a Quinone outside inhibitor.
+This fungicide provides dual action: tebeconazole disrupts C-14 demethylase, required in sterol biosynthesis for cell membranes; and azoxystrobin, a Quinone outside inhibitor.
 Quinone is required in cell metabolism and active in the mitochondrial complex III.
@@
 Excessive fungicide sprays by a single active increase the selection pressure on the pathogen to evolve resistance [@Brent2007]. 
-If any strains of the pathogen with resistance to the fungicide are present in a population regular use of the fungicide will increase its proportion in the population. 
+If any strains of the pathogen with resistance to the fungicide are present in a population regular use of the fungicide will increase it's proportion in the population. 
 Therefore, managing the disease with fungicides for the highest economic return is likely not to require eradication of the causal pathogen. 
@@
 However it does not provide enough certainty to when late fungicide applications would be too late to protect yield losses due to the disease. 
-Future experiments should take note of physiological maturity of the crop throughout the season so "crop age" might be considered as a covariate in future analyses.
+Future experiments should take note of physiological maturity of the crop throughout the season so 'crop age' might be considered as a covariate in future analyses.
 In cases where mungbean physiological maturity may not have been recorded the APSIM mungbean module [@RobertsonAPSIMlegume2002].
@@
 <!-- Should we submit the raw data to a data repository like OSF and Figshare? (Paul) -->
-<!-- AHS - Yes, We should submit the data (as we are allowed to) to something like this, yes.
-See the repository I set up for the chickpea asco study, <https://zenodo.org/search?page=1&size=20&q=conceptrecid:3810826&all_versions&sort=-version> -->
 

### 2020-08-04 paper/paper.Rmd
add refs to bib and edit intro

--- 2020-08-03 paper/paper.Rmd
@@
 
-The high variability in yields can in part be attributed to a range of diseases that affect the crop [@Kelly2017a].
-Two major foliar diseases, tan spot or common wilt (*Curtobacterium flaccumfaciens* pv.
-_flaccumfaciens_) and halo blight (*Pseudomonas savastanoi* pv.
-*phaseolicola*), are the main focus of the Australian Mungbean Improvement programme's resistance breeding efforts due to lack of effective chemical controls for them.
-While a third disease, powdery mildew, can reduce yields by up to 40% [@Chankaew2013] in susceptible cultivars, the damage can be mitigated through an integrated disease management strategy of fungicide treatments and cultural practices.
+The high variability in yields can in part be attributed to a range of diseases that affect the crop [@Wood1990; @Conde1991; @Fuhlbohm1996; @Fuhlbohm2013; @Wilson2001; @Noble2019].
+Along with these bacterial, fungal and phytoplasma caused diseases, another fungal disease, powdery mildew, can reduce yields by up to 40% [@Chankaew2013] in susceptible cultivars.
+The disease is caused by  The damage can be mitigated through an integrated disease management strategy of fungicide treatments and cultural practices and loci conferring resistance in mungbean have been identified [@Zhang2008].
+However, to date, the focus in Australia has remained on breeding for disease resistance to bacterial diseases rather than powdery mildew due to the wide availability of fungicides for use in controlling powdery mildew.
+<!-- Best to get a quote from Col here so we can say "personal comm".
+I've heard him say this at a mungbean field day, I believe.
+-->
 

### 2020-08-04 04_MetaAnalysis.Rmd

@@
 We know there is a good deal of variability in our studies and between them.
-Mungbean produces variable yields between seasons so ordinarilly we should use a response that highlights the difference in the treatment effects that we are interested in and reduce the variability.
+Mungbean produces variable yields between seasons so ordinarily we should use a response that highlights the difference in the treatment effects that we are interested in and reduce the variability.
 However for an arm-based analysis we calculate the differences between control and treatment after the meta-analysis.

### 2020-08-04 paper/paper.Rmd
Remove "Head" from merge conflicts

@@
 
+First sign of powdery mildew was observed as early as the 28th of February in the 2013 trial at .... ; and as late as the 12th of April in the 2018 trial at ...
+
 <!-- What is this `SeasonPlot`? I can't find any docs and no file named `SeasonPlot`. It should just be code here int the doc for easy editing. -->
 
-```{r Figure2, echo=FALSE, fig.cap="Season plot"}
-SeasonPlot
+```{r Figure2, echo=FALSE, caption="Season plot"}
+# Create the data frame for the plot
+season_dates <- PM_MB_means %>%
+   group_by(trial_ref) %>%
+   summarise(
+      Planting_date = unique(planting_date),
+      Harvest_date = unique(harvest_date),
+      First_sign_PM = unique(first_sign_disease),
+      season_length = as.Date(unique(harvest_date)) - as.Date(unique(planting_date)),
+      cropping_season = "Actual"
+   )
+mean(ymd(PM_Mdat$planting_date), na.rm = TRUE)
+
+PM_Mdat %>%
+  distinct(trial_ref, planting_date, harvest_date,first_sign_disease) %>%
+  mutate(planting_date = ymd(planting_date))%>%
+  mutate(harvest_date = ymd(harvest_date))%>%
+    mutate(cropping_season = case_when(
+    is.na(planting_date) | is.na(harvest_date ) ~ "Estimated",
+    TRUE ~ "Actual"))%>%
+  mutate(season_length = case_when(
+    is.na(planting_date) ~ harvest_date - mean(planting_date,na.rm = TRUE),
+    is.na(harvest_date) ~ mean(harvest_date,na.rm = TRUE) - planting_date,
+    TRUE ~ harvest_date - planting_date
+  ))
+
+# For some trials where planting date and Harvest date is missing let's estimate 
+#     the season length by using the mean of all season lengths
+season_dates[is.na(season_dates$season_length),"cropping_season"] <- "Estimated"
+
+season_dates[is.na(season_dates$Planting_date),"Planting_date"] <- 
+   season_dates[is.na(season_dates$Planting_date),"Harvest_date"] - 
+   as.numeric(mean(season_dates$season_length, na.rm = TRUE))
+
+season_dates[is.na(season_dates$Harvest_date),"Harvest_date"] <- 
+   season_dates[is.na(season_dates$Harvest_date),"Planting_date"] + 
+   as.numeric(mean(season_dates$season_length, na.rm = TRUE))
+
+season_dates[is.na(season_dates$season_length),"season_length"] <- 
+   mean(season_dates$season_length, na.rm = TRUE)
+
+season_dates$Planting_day <- yday(season_dates$Planting_date)
+season_dates$Disease_day <- yday(season_dates$First_sign_PM)
+
+season_dates[c(1:2,6), "Planting_day"] <- 1
+
+season_dates$Harvest_day <-
+   season_dates$Planting_day + season_dates$season_length
+
+first_day_month <- c(0, 31, 60, 91, 121, 152, 182, 212, 244, 274) + 1
+axis_labels_date <-
+   c(
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[1], "%b-%d"),
+      # Jan
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[2], "%b-%d"),
+      # Feb
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[3], "%b-%d"),
+      # March
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[4], "%b-%d"),
+      # April
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[5], "%b-%d"),
+      # May
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[6], "%b-%d"),
+      # June
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[7], "%b-%d"),
+      # July
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[8], "%b-%d"),
+      # August
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[9], "%b-%d"),
+      # Sept
+      format(Sys.Date() - yday(Sys.Date()) + first_day_month[10], "%b-%d") # October
+   )
+
+# reorder the factors so they will appear in chronological order
+# I used First sign because all trials have recorded this
+season_dates$trial_ref <-
+   factor(season_dates$trial_ref,
+          levels = levels(season_dates$trial_ref)[rev(order(season_dates$First_sign_PM))])
+
+# Plot
+season_dates %>%
+   ggplot() +
+   geom_pointrange(aes(
+      x = trial_ref,
+      y = Disease_day,
+      ymin = Planting_day,
+      ymax = Harvest_day,
+      colour = cropping_season
+   )) +
+   scale_y_continuous(limits = c(
+      0,
+      max(
+         season_dates$Planting_day +
+            season_dates$season_length,
+         na.rm = TRUE
+      )
+   ),
+   labels = axis_labels_date,
+   breaks = first_day_month) +
+   geom_point(aes(x = trial_ref, y = Disease_day)) +
+   coord_flip() +
+   scale_color_manual(values=c("black","grey70"))+
+   ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
+
 ```

### 2020-08-04 paper/paper.Rmd
Wordsmithing and references for diseases in Oz mungs

@@
 Along with these bacterial, fungal and phytoplasma caused diseases, another fungal disease, powdery mildew, can reduce yields by up to 40% [@Chankaew2013] in susceptible cultivars.
-The disease is caused by  The damage can be mitigated through an integrated disease management strategy of fungicide treatments and cultural practices and loci conferring resistance in mungbean have been identified [@Zhang2008].
+The disease in Australia currently is thought to be caused by *Podosphaera xanthii*, however, this description has changed over time and a second species has also been cited as causing the disease but not yet officially classified [@Kelly2019].
+Other research refers to the causal agent as *Erysiphe polygoni* outside of Australia [@Thakur1995].
+
+The damage can be mitigated through an integrated disease management strategy of fungicide treatments and cultural practices and loci conferring resistance in mungbean have been identified [@Humphry2003; @Zhang2008].
 However, to date, the focus in Australia has remained on breeding for disease resistance to bacterial diseases rather than powdery mildew due to the wide availability of fungicides for use in controlling powdery mildew.

### 2020-08-04 paper/paper.Rmd
Updated figure 2 to be simplified and show all the code

--- 2020-08-04 paper/paper.Rmd
@@
 ```{r Figure2, echo=FALSE, caption="Season plot"}
-# Create the data frame for the plot
-season_dates <- PM_MB_means %>%
-   group_by(trial_ref) %>%
-   summarise(
-      Planting_date = unique(planting_date),
-      Harvest_date = unique(harvest_date),
-      First_sign_PM = unique(first_sign_disease),
-      season_length = as.Date(unique(harvest_date)) - as.Date(unique(planting_date)),
-      cropping_season = "Actual"
-   )
-mean(ymd(PM_Mdat$planting_date), na.rm = TRUE)
-
 PM_Mdat %>%
@@
   mutate(harvest_date = ymd(harvest_date))%>%
-    mutate(cropping_season = case_when(
+  mutate(first_sign_disease = ymd(first_sign_disease))%>%
+  mutate(cropping_season = case_when( # add categorical value for estimated season period
     is.na(planting_date) | is.na(harvest_date ) ~ "Estimated",
     TRUE ~ "Actual"))%>%
-  mutate(season_length = case_when(
-    is.na(planting_date) ~ harvest_date - mean(planting_date,na.rm = TRUE),
-    is.na(harvest_date) ~ mean(harvest_date,na.rm = TRUE) - planting_date,
-    TRUE ~ harvest_date - planting_date
-  ))
-
-# For some trials where planting date and Harvest date is missing let's estimate 
-#     the season length by using the mean of all season lengths
-season_dates[is.na(season_dates$season_length),"cropping_season"] <- "Estimated"
-
-season_dates[is.na(season_dates$Planting_date),"Planting_date"] <- 
-   season_dates[is.na(season_dates$Planting_date),"Harvest_date"] - 
-   as.numeric(mean(season_dates$season_length, na.rm = TRUE))
-
-season_dates[is.na(season_dates$Harvest_date),"Harvest_date"] <- 
-   season_dates[is.na(season_dates$Harvest_date),"Planting_date"] + 
-   as.numeric(mean(season_dates$season_length, na.rm = TRUE))
-
-season_dates[is.na(season_dates$season_length),"season_length"] <- 
-   mean(season_dates$season_length, na.rm = TRUE)
-
-season_dates$Planting_day <- yday(season_dates$Planting_date)
-season_dates$Disease_day <- yday(season_dates$First_sign_PM)
-
-season_dates[c(1:2,6), "Planting_day"] <- 1
-
-season_dates$Harvest_day <-
-   season_dates$Planting_day + season_dates$season_length
-
-first_day_month <- c(0, 31, 60, 91, 121, 152, 182, 212, 244, 274) + 1
-axis_labels_date <-
-   c(
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[1], "%b-%d"),
-      # Jan
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[2], "%b-%d"),
-      # Feb
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[3], "%b-%d"),
-      # March
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[4], "%b-%d"),
-      # April
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[5], "%b-%d"),
-      # May
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[6], "%b-%d"),
-      # June
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[7], "%b-%d"),
-      # July
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[8], "%b-%d"),
-      # August
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[9], "%b-%d"),
-      # Sept
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[10], "%b-%d") # October
-   )
-
-# reorder the factors so they will appear in chronological order
-# I used First sign because all trials have recorded this
-season_dates$trial_ref <-
-   factor(season_dates$trial_ref,
-          levels = levels(season_dates$trial_ref)[rev(order(season_dates$First_sign_PM))])
-
-# Plot
-season_dates %>%
+  mutate(plant_day = case_when( #for crops planted in late December minus 365 days from yday function
+    yday(planting_date) < 200 ~ yday(planting_date),
+    yday(planting_date) > 200 ~ yday(planting_date) - 365,
+  )) %>%
+  mutate(season_length = case_when(  # when either planting date or harvest date are missing use the overall mean season length as an estimate
+    is.na(planting_date) | is.na(harvest_date) ~
+      mean(yday(harvest_date) - plant_day,na.rm = TRUE),
+    TRUE ~ yday(harvest_date) - plant_day
+  ))%>%
+  mutate(plant_day = case_when( # estimate planting day  from mean season length
+    is.na(plant_day) ~ yday(harvest_date) - season_length,
+    TRUE ~ plant_day
+  ))%>%
+  mutate(harvest_day = case_when( #estimate harvest day from mean season length
+    is.na(harvest_date) ~ plant_day + season_length,
+    TRUE ~ yday(harvest_date)
+  ))%>%
+  mutate(trial_ref = factor(trial_ref, # reorder by the first_sign_of_disease
+                            levels = trial_ref[rev(order(ymd(first_sign_disease)))]))%>%
   ggplot() +
@@
     x = trial_ref,
-      y = Disease_day,
-      ymin = Planting_day,
-      ymax = Harvest_day,
+    y = yday(first_sign_disease),
+    ymin = plant_day,
+    ymax = harvest_day,
     colour = cropping_season
-   )) +
+   ))+
   scale_y_continuous(limits = c(
-      0,
-      max(
-         season_dates$Planting_day +
-            season_dates$season_length,
-         na.rm = TRUE
-      )
-   ),
-   labels = axis_labels_date,
-   breaks = first_day_month) +
-   geom_point(aes(x = trial_ref, y = Disease_day)) +
+    -25,
+    183),
+    labels = paste(month(1:7, label = TRUE, abbr = TRUE), rep(1,7),sep = "-"),
+    breaks = yday(ymd(paste(rep(2018, 7),1:7, rep(1,7),sep = "-")))
+    ) +
+  geom_hline(yintercept = yday(ymd(paste(rep(2018, 7),1:7, rep(1,7),sep = "-"))), 
+             colour = "grey80",
+             linetype = 2)+
+  geom_point(aes(x = trial_ref, y = yday(first_sign_disease))) +
   coord_flip() +
   scale_color_manual(values=c("black","grey70"))+
-   ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
+  ggtitle("Season length and first appearance of powdery mildew \nin each respective trial")+
+  xlab("Trial reference code")+
+  ylab(NULL)
 

### 2020-08-04 paper/paper.Rmd
Update Rmd

--- 2020-08-04 paper/paper.Rmd
@@
     long: Decision support system
+  - short: AUDPC
+    long: Area under the disease progress curve
 output:
@@
 # Data
+source(here("R/import_data.R")) # load `import_data()`
+PM_MB_means <- import_data()
 PM_Mdat <- read.csv(here("cache/PM_MB_updated.csv"))
@@
 
-The damage can be mitigated through an integrated disease management strategy of fungicide treatments and cultural practices and loci conferring resistance in mungbean have been identified [@Humphry2003; @Zhang2008].
-However, to date, the focus in Australia has remained on breeding for disease resistance to bacterial diseases rather than powdery mildew due to the wide availability of fungicides for use in controlling powdery mildew.
-<!-- Best to get a quote from Col here so we can say "personal comm".
-I've heard him say this at a mungbean field day, I believe.
--->
-
 While the pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified.
@@
 Cultivar selection is an additional strategy to mitigate yield damage from powdery mildew.
-In Australia, quantitative resistance to powdery mildew has also been incorporated into few commercially available varieties.
-Jade-AU <span class="pbr">(pbr)</span> <!-- Need PBR emblem here --> has the the best disease resistance to powdery mildew (moderately susceptible), with cv.
-Green Diamond also containing some notable resistance [@Sparks2017].
+While loci conferring resistance in mungbean have been identified [@Humphry2003; @Zhang2008]; to date, the focus in Australia has remained on breeding for disease resistance to bacterial diseases rather than powdery mildew due to the wide availability of fungicides for use in controlling powdery mildew.
+<!-- Best to get a quote from Col here so we can say "personal comm".
+I've heard him say this at a mungbean field day, I believe.
+-->
+Currently, Jade-AU\pbr has the the best disease resistance to powdery mildew (moderately susceptible), with cv. Green Diamond also having some resistance [@Sparks2017].
 However, commercially available mungbean cultivars in Australia lack sufficient resistance to be used as the primary powdery mildew management strategy. 
@@
 However meta-analyses can also consider effect differences between multiple treatments and a control group.
-These are called multi-variate or network meta-analyses [@MaddenEtAl2016]. 
+These are called multi-variate or network meta-analyses [@Madden2016]. 
 Multi-variate meta-analyses are particularly useful when there are no direct comparisons between two treatments in any of the included studies. 
@@
 # Add a star to the trials which were not in the final analysis
-PM_Mdat[!PM_Mdat$trial_ref%in% slimmer_PM_dat$trial_ref, "trial_ref"] <-
-  sapply(PM_Mdat[!PM_Mdat$trial_ref%in% slimmer_PM_dat$trial_ref, "trial_ref"], paste0, "*")
+PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref, "trial_ref"] <-
+  sapply(PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref, "trial_ref"], paste0, "*")
 
 # Build table
-PM_Mdat%>%
+PM_Mdat %>%
   filter(fungicide_ai == "tebuconazole" |
-           fungicide_ai == "propiconazole")%>%
-  group_by(trial_ref)%>%
+           fungicide_ai == "propiconazole") %>%
+  group_by(trial_ref) %>%
   summarise(
@@
     `Research Organisation` = Research_org
-  )%>%
-  kable(format = "latex",
+  ) %>%
+  kable(
+    format = "latex",
     booktabs = TRUE,
     escape = FALSE,
-        caption="Description of fungicide application experiments.")%>%
-  kable_styling()%>%
+    caption = "Description of fungicide application experiments."
+  ) %>%
+  kable_styling() %>%
   footnote(
@@
   )
-)%>%
+) %>%
   kable(format = "latex",
         booktabs = TRUE,
-      caption="Powdery mildew severity scoring scale.")%>%
+        caption = "Powdery mildew severity scoring scale.") %>%
   kable_styling()

### 2020-08-04 paper/paper.Rmd

@@
 ---
-
+<!-- the `rticles` package from <https://github.com/adamhsparks/rticles> is required to compile this PDF.
+The version from CRAN is out of date for MDPI -->
 <!-- For reference in writing for MDPI, <https://www.mdpi.com/authors/layout> -->
@@
 # Data
-source(here("R/import_data.R")) # load `import_data()`
-PM_MB_means <- import_data()
 PM_Mdat <- read.csv(here("cache/PM_MB_updated.csv"))
@@
 
-The high variability in yields can in part be attributed to a range of diseases that affect the crop [@Wood1990; @Conde1991; @Fuhlbohm1996; @Fuhlbohm2013; @Wilson2001; @Noble2019].
-Along with these bacterial, fungal and phytoplasma caused diseases, another fungal disease, powdery mildew, can reduce yields by up to 40% [@Chankaew2013] in susceptible cultivars.
+The high variability in yields can in part be attributed to a range of diseases that affect the crop that include fungi, bacteria and phytoplasmas [@Wood1990; @Conde1991; [@Thakur1995; @Fuhlbohm1996; @Fuhlbohm2013; @Wilson2001; @Noble2019].
+Among the fungal diseases is powdery mildew, which can reduce yields by up to 40% [@Chankaew2013] in susceptible cultivars.
 The disease in Australia currently is thought to be caused by *Podosphaera xanthii*, however, this description has changed over time and a second species has also been cited as causing the disease but not yet officially classified [@Kelly2019].
-Other research refers to the causal agent as *Erysiphe polygoni* outside of Australia [@Thakur1995].
+While other research outside of Australia refers to the causal agent as *Erysiphe polygoni*.
 
-While the pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified.
-The disease life cycle can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@Sparks2017].
+While the powdery mildew pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified in Australia.
+The disease cycle can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@Sparks2017].
 Weather conditions that favour the rapid development of the disease are cool temperatures between 22&nbsp;&deg; and 26&nbsp;&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
+<!-- couldn't we just pull this information on temperatures and RH from our data sets rather than rely on an unofficially-peer reviewed GRDC update paper?
+A simple figure or two could be useful here, based on our data.
+-->
 
@@
 -->
-Currently, Jade-AU\pbr has the the best disease resistance to powdery mildew (moderately susceptible), with cv. Green Diamond also having some resistance [@Sparks2017].
+Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013], however no evidence for how they compare to Australian varietal resistance could be found.
+Currently, Jade-AU has the the best disease resistance to powdery mildew (moderately susceptible), with cv. Green Diamond also having some resistance [@Sparks2017].
 However, commercially available mungbean cultivars in Australia lack sufficient resistance to be used as the primary powdery mildew management strategy.
 Evidence of this is shown by field trials conducted in 2016 with the moderately susceptible cultivar, Jade-AU, where yield losses of up to 32.7% were recorded [@SueThompson2016].
-Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013], however no evidence for how they compare to Australian varietal resistance could be found.
 Additional strategies to cultivar choice, such as fungicide treatments, are necessary to limit yield loss when conditions for the disease are conducive.
@@
 
-The collection of experiments mentioned above and other unpublished trials present an excellent opportunity for a meta-analysis.
+The collection of experiments mentioned above and other unpublished trials conducted in Australia present an excellent opportunity for a meta-analysis.
 Meta-analyses are statistical tools, which can analyse a collection of experiments, that have a similar aim, and produces a more accurate estimate of the true effect being measured.
@@
 
-```{r Figure2, echo=FALSE, caption="Season plot"}
-# Create the data frame for the plot
-season_dates <- PM_MB_means %>%
-  group_by(trial_ref) %>%
-  summarise(
-    Planting_date = unique(planting_date),
-    Harvest_date = unique(harvest_date),
-    First_sign_PM = unique(first_sign_disease),
-    season_length = as.Date(unique(harvest_date)) - as.Date(unique(planting_date)),
-    cropping_season = "Actual"
-  )
-mean(ymd(PM_Mdat$planting_date), na.rm = TRUE)
-
+```{r Figure2, echo=FALSE, fig.cap="Season plot"}
 PM_Mdat %>%

### 2020-08-04 paper/paper.Rmd
Wordsmithing the introduction up to Materials and Methods

@@
 Weather conditions that favour the rapid development of the disease are cool temperatures between 22&nbsp;&deg; and 26&nbsp;&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
-<!-- couldn't we just pull this information on temperatures and RH from our data sets rather than rely on an unofficially-peer reviewed GRDC update paper?
-A simple figure or two could be useful here, based on our data.
--->
 
@@
 
-There is almost a complete lack of peer-reviewed literature summarising fungicide efficacy on powdery mildew in Australian mungbean.
+There is a near complete lack of peer-reviewed literature summarising fungicide efficacy on powdery mildew in mungbean in Australia.
 Much of the experimental work has been published by funding agencies and state government extension departments as extension bulletins or other related type materials.
-Past field trials in eastern Australia have tested a range of fungicide active ingredients while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
-Early trials showed that for fungicide applications to protect yield, a single fungicide application at first sign of the disease with another follow-up application two weeks later, if necessary, was the most effective [@SueThompson2016; @Sparks2017].
+Field trials conducted in eastern Australia over the past ten years have tested a range of fungicide active ingredients while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016].
+The trials showed that for fungicide applications to protect yield, a single fungicide application at first sign of the disease with another follow-up application two weeks later, if necessary, was the most effective [@SueThompson2016; @Sparks2017].
 However, due to the variability in the results between seasons and experiments, few of these studies produced a clear result based on a statistical analysis. 
@@
 
-Considering the recent launch in November 2019 of the decision support system (DSS) PowderyMildewMBM [@Diggle], which provides a cost benefit analysis to assists growers in their decision "if" and "when" apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
+Considering the recent launch in November 2019 of the mobile app decision support system (DSS) PowderyMildewMBM [@Diggle], which provides a cost benefit analysis to assists growers in their decision "if" and "when" apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
 The aim of this meta-analysis was to determine, from a collection of unpublished studies, what spray management scenario provides the greatest yield protection from powdery mildew in Australian mungbean.

### 2020-08-06 paper/paper.Rmd
Correct caps in title
fix a "[" in citations

@@
 ---
-title: A Meta-analysis of Fungicide Spray Schedules to Minimise Yield Loss From Powdery Mildew in Australian Mungbean
+title: A Meta-analysis of Fungicide Spray Schedules to Minimise Yield Loss from Powdery Mildew in Australian Mungbean
 author:
@@
 
-The high variability in yields can in part be attributed to a range of diseases that affect the crop that include fungi, bacteria and phytoplasmas [@Wood1990; @Conde1991; [@Thakur1995; @Fuhlbohm1996; @Fuhlbohm2013; @Wilson2001; @Noble2019].
+The high variability in yields can in part be attributed to a range of diseases that affect the crop that include fungi, bacteria and phytoplasmas [@Wood1990; @Conde1991; @Thakur1995; @Fuhlbohm1996; @Fuhlbohm2013; @Wilson2001; @Noble2019].
 Among the fungal diseases is powdery mildew, which can reduce yields by up to 40% [@Chankaew2013] in susceptible cultivars.

### 2020-08-06 paper/paper.Rmd
Wordsmithing

@@
 
-The collection of experiments mentioned above and other unpublished trials conducted in Australia present an excellent opportunity for a meta-analysis.
-Meta-analyses are statistical tools, which can analyse a collection of experiments, that have a similar aim, and produces a more accurate estimate of the true effect being measured.
+The collection of experiments mentioned above and other unpublished trials conducted in Australia presented an ideal opportunity for a meta-analysis to study fungicide timing to control mungbean powdery mildew.
+Meta-analyses are statistical tools which can analyse a collection of experiments that have a similar aim and produce a more accurate estimate of the true effect being measured.
 Using a meta-analysis can be useful in situations like this where several studies exist that have the same objective but may not provide a clear answer to the question due to variation in the results within the individual studies.
@@
 
-Considering the recent launch in November 2019 of the mobile app decision support system (DSS) PowderyMildewMBM [@Diggle], which provides a cost benefit analysis to assists growers in their decision "if" and "when" apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
+Considering the November 2019 launch of the mobile app decision support system (DSS) PowderyMildewMBM [@Diggle], which provides a cost benefit analysis to assists growers in their decision "if" and "when" apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
 The aim of this meta-analysis was to determine, from a collection of unpublished studies, what spray management scenario provides the greatest yield protection from powdery mildew in Australian mungbean.
@@
 
-## Trial criteria for inclusion and description
+## Trial Criteria for Inclusion and Description
 
-The data for this study were obtained through personal correspondence with colleagues and collaborating institutions.
-Trials undertaken in the 2013 season were conducted by the Northern Growers Alliance (NGA) [-@goolhi2013; -@premer2013; -@Millmerran2013; -@Marysmount2013].
-<!-- should check, Sue and Mal moved to USQ in 2015 I think. Therefore the trials probably started with USQ earlier --> 
+The data for this study were obtained through studies that were conducted by the authors, FAIR (Findable, Accessible, Interoperable, Reusable) data available from GRDC Online Farm Trials <https://www.farmtrials.com.au/>, personal correspondence with colleagues and collaborating institutions.
 Trial data were obtained in different formats with varying levels of information.
-Some trials we obtained the raw data, others the reported means of each treatment, with all but one study reporting some form of variance along with the mean.
+Raw data was obtained for some trials, others reported only the means of each treatment, with all but one trial reporting some form of variance along with the mean.
 In total, 26 trials were collated.
 
-To ensure the correct question was asked of the analysis, the data needed to conform to a strict criteria.
-The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the Grains Research and Development (GRDC) northern grains regions of eastern Australia, which grows the majority of Australia's summer crops.
-Data from trials undertaken in this region had to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; the fungicide active ingredients; fungicide dose; and crop yield.
+To ensure the correct question was asked of the analysis, the data needed to conform to strict criteria for inclusion.
+The criteria for inclusion of trial data in the meta-analysis first required a field trial testing fungicide efficacy for powdery mildew control on mungbean in the Grains Research and Development (GRDC) northern grains region of eastern Australia, which grows the majority of Australia's summer crops.
+Data from trials conducted in this region had to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; the fungicide active ingredients; fungicide dose; and crop yield.
 The data were subset to only include fungicide treatments with the same mode of action; demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole were thus retained in the dataset.
-Subsequently the 26 trials were reduced to 17 trials (Table \@ref(tab:Table1)).
-Two more trials were also removed because grain yield variance, which was required for the meta-analysis, was not reported, reducing the number of trials down to 15.
+Subsequently, the 26 trials were reduced to 17 trials (Table \@ref(tab:Table1)).
+Two more trials were also removed because grain yield variance, which was required for the meta-analysis, was not reported, reducing the total number of trials in the meta-analysis down to 15.
 
 ```{r Table1, echo=FALSE, message=FALSE, warning=FALSE}
-# Add a star to the trials which were not in the final analysis
+# Adds a star to the trials which were not in the final analysis
 PM_Mdat[!PM_Mdat$trial_ref %in% slimmer_PM_dat$trial_ref, "trial_ref"] <-

### 2020-08-06 paper/paper.Rmd
Edit caption to be more descriptive for table 1

@@
     escape = FALSE,
-    caption = "Description of fungicide application experiments."
+    caption = "Description of fungicide application trials included in meta-analysis to determine the most effective fungicide spray schedule to minimise yield loss from powdery mildew in Australian mungbean.
+Trials were all conducted in the Grains Research and Development (GRDC) Northern Grains Region of eastern Australia to test application timing for the best control of powdery mildew of mungbean."
   ) %>%

### 2020-08-06 paper/paper.Rmd
Add more abbreviations
Wordsmithing and edits for clarity

@@
     long: Area under the disease progress curve
+  - short: NGA
+    long: Northern Growers Alliance
+  - short: GRDC
+    long: Grains Research and Development Corporation
+  - short: DMI
+    long: Demethylase inhibitor
 output:
@@
 
-From the trials which were included in the meta-analysis, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12))` were planted in late December, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 1))` in January and `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 2))` were trials planted in February (Table \@ref(tab:Table1)).
+From the trials which were included in the meta-analysis, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 12))` were planted in late December, `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 1))` in January and `r as.english(sum(lubridate::month(distinct(slimmer_PM_dat, trial_ref, planting_date)$planting_date) == 2))` were planted in February (Table \@ref(tab:Table1)).
 
 In the meta-analysis, to ensure sufficient replication, we made no distinction between the tebuconazole and propiconazole fungicide treatments within the trials that met the selection criteria.
-The design of all trials included in this analysis were randomised complete block designs, and were not previously published in peer-reviewed literature. 
+The design of all trials included in this analysis were randomised complete block designs and were not previously published in peer-reviewed literature.
 Details of trial data are presented within a research compendium as a supplement to this publication [<!-- DOI to reference to compendium -->].
 
-**Response variable - Grain yield: **
-Grain yield (tonne per hectare), was used as the response variable for the meta-analysis. 
-Mean grain yields for each treatment were either obtained directly from trial reports, or calculated from the raw data when available.
+## Response Variable - Grain Yield
+
+Grain yield (tonnes per hectare), was used as the response variable for the meta-analysis.
+Mean grain yields for each treatment were either obtained directly from trial reports or calculated from the raw data when available.
 The sample variance was calculated from the raw data when available or the least squares statistic in the trial reports.
-Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 2.042 and the approach reported in Ngugi et al. [-@Ngugi2011].
+Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 2.042 and the approach reported in Ngugi *et al.* [-@Ngugi2011].
 The T-critical value was obtained from a t-distribution table using, 30 degrees of freedom and probability of $a = 0.05$.
@@
 $Y_i \sim N(\mu,s_i^2 + \sigma^2)$
-where $Y_i$ is the response, a vector of the grain yield measurements (tonne per hectare) for each treatment in the $i$th trial over total number ($K$) of trials($i$  = 1, ...$K$). 
+where $Y_i$ is the response, a vector of the grain yield measurements (tonnes per hectare) for each treatment in the $i$th trial over total number ($K$) of trials ($i$  = 1, ...$K$). 
 $Y_i$ is estimated from a normal distribution with the mean $\mu$, sample variance of $S_i^2$ and a between trial variance of $\sigma^2$.
 
-**Trial Variables and moderators: **
-While the main aim of all the identified trials were to assess the efficacy of fungicide for control of powdery mildew, some trials tested additional potential covariates in the experimental design.
+## Trial Variables and Moderators
+
+While the main aim of all the identified trials was to assess the efficacy of fungicide for control of powdery mildew, some trials tested additional potential covariates in the experimental design.
 These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications and cultivar.
@@
 
-The random effects meta-analysis was expanded to evaluate if the residual heterogeneity could be explained by spray schedule). 
+The random effects meta-analysis was expanded to evaluate if the residual heterogeneity could be explained by spray schedule.
 Spray schedule was assigned as an inside factor to the outside random factor $trial$ to provide correlated random effects between the different spray schedule treatments within $trials$.
 
-The timing of fungicide application treatments, were defined in relation to the recorded date when powdery mildew first occurred in the trial.
-An $Early$ fungicide application treatment, referred to a fungicide spray schedule that commenced prior to the disease being observed in the trial.
+The timing of fungicide application treatments was defined in relation to the recorded date when powdery mildew first appeared in the trial.
+An $Early$ fungicide application treatment referred to a fungicide spray schedule that commenced prior to the disease being observed in the trial.
 $Recommended$ referred to a fungicide spray schedule which commenced 1 -- 3 days following the first sign of disease.
@@
 There were no spray schedule treatments which began between 4 and 6 days after the first sign of powdery mildew.
-The number of fungicide applications were binned in to two categories.
+The number of fungicide applications was binned into two categories.
 A spray schedule with a $single$ spray, and a spray schedule with two or three spray applications $plus$.
@@
 $Early_{plus}$ treatments were removed from the subsequent meta-analysis, due to an insufficient sample size.
+
 What remained was the mean yield for a total of 173 treatments in the following five spray schedule categories: no spray $control$, $Early_{single}$, $Recommended_{single}$, $Recommended_{plus}$, $Late_{single}$, and $Late_{plus}$.

### 2020-08-06 paper/paper.Rmd
remove a space
more wordsmithing in the materials and methods

@@
 To ensure the correct question was asked of the analysis, the data needed to conform to strict criteria for inclusion.
-The criteria for inclusion of trial data in the meta-analysis first required a field trial testing fungicide efficacy for powdery mildew control on mungbean in the Grains Research and Development (GRDC) northern grains region of eastern Australia, which grows the majority of Australia's summer crops.
+The criteria for inclusion of data in the meta-analysis first required a field trial testing fungicide efficacy for powdery mildew control on mungbean in the Grains Research and Development (GRDC) northern grains region of eastern Australia, which grows the majority of Australia's summer crops.
 Data from trials conducted in this region had to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; the fungicide active ingredients; fungicide dose; and crop yield.
-The data were subset to only include fungicide treatments with the same mode of action; demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole were thus retained in the dataset.
-Subsequently, the 26 trials were reduced to 17 trials (Table \@ref(tab:Table1)).
-Two more trials were also removed because grain yield variance, which was required for the meta-analysis, was not reported, reducing the total number of trials in the meta-analysis down to 15.
+The data were subset to only include fungicide treatments with the same mode of action; demethylase inhibitor (DMI) fungicides.
+Thus only tebuconazole and propiconazole were retained in the dataset and the 26 trials were reduced to 17 trials.
+Two more trials were removed because grain yield variance, which was required for the meta-analysis, was not reported.
+This reduced the final number of trials included in the meta-analysis to 15 (Table \@ref(tab:Table1)).
 

### 2020-08-07 paper/paper.Rmd
Acknowledge Levente
Updated table 3 to include more detail

@@
   kable_styling() %>%
-  footnote(
+  kableExtra::footnote(
     alphabet = c(
@@
 ```{r Table3, echo = FALSE}
-T3[, 2:5] <- round(T3[, 2:5], 4)
-T3%>%
-  mutate(contrasts = gsub("-", "", contrasts))%>%
-  mutate(contrasts = gsub(" \\+", " -", contrasts))%>%
-  mutate(contrasts = gsub(" = 0", "", contrasts))%>%
-  rename(
-    `Treatment contrasts` = contrasts,
-    Estimate = estimates,
-    `Standard Error` = se,
-    `Z-score` = z_val,
-    `P-value` = pval,
-    ` ` = VisP
-  )%>%
+contrast_Ssum[,2:5] <- round(contrast_Ssum[,2:5], 4)
+contrast_Ssum %>%
+  slice(grep("control", contrast, invert = TRUE)) %>%
+  mutate(pvals = reportP(pvals)) %>%
+  mutate(pvals = gsub("P = ","",pvals)) %>%
   kable(format = "latex",
         booktabs = TRUE,
-        caption = "Estimated grain yield contrasts between each spray schedule.")%>%
+        caption = "Table 3: Estimated grain yield contrasts between each spray schedule.",
+        col.names = c("Treatment contrasts","Estimated difference","Std Error","Z-Score","P-Value"," "))%>%
   kable_styling()%>%
-  footnote(general = c("** - signficant at 0.005 level",
+  kableExtra::footnote(general = c("*** - signficant at 0.001 level",
+                                   "** - signficant at 0.005 level",
                        "* - signficant at 0.05 level"))

### 2020-08-07 paper/paper.Rmd
add lifecycle reference Levente suggested

--- 2020-08-06 paper/paper.Rmd
@@
 Among the fungal diseases is powdery mildew, which can reduce yields by up to 40% [@Chankaew2013] in susceptible cultivars.
-The disease in Australia currently is thought to be caused by *Podosphaera xanthii*, however, this description has changed over time and a second species has also been cited as causing the disease but not yet officially classified [@Kelly2019].
-While other research outside of Australia refers to the causal agent as *Erysiphe polygoni*.
+The disease in Australia currently is thought to be caused by *Podosphaera xanthii*, syn. *Podosphara fusca*.
+However, this description has changed over time and a second species has also been cited as causing the disease but not yet officially classified [@Kelly2019].
+While research outside of Australia refers to the causal agent of mungbean powdery mildew as *Erysiphe polygoni*.
 
-While the powdery mildew pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified in Australia.
-The disease cycle can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@Sparks2017].
+The disease cycle of the pathogen can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@PerezGarcia2009; @Sparks2017].
 Weather conditions that favour the rapid development of the disease are cool temperatures between 22&nbsp;&deg; and 26&nbsp;&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
+To date, the sexual cycle that produces chasomthecia has not been observed in Australian mungbean.
+And while the powdery mildew pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified in Australia.
 
@@
 The Grains Research and Development Corporation who funded this research.
+Thank you to Professor Levente Kiss for his kind assistance in improving this article.

### 2020-08-07 paper/paper.Rmd
Use AMA growing guide for resistance reference
I got the rating from here for my article reference that this one replaces in the text
Update and reorder abbreviations

@@
 abbreviations:
+  - short: AUDPC
+    long: Area under the disease progress curve
+  - short: DAF
+    long: Queensland Department of Agriculture, Fisheries and Forestry
+  - short: DMI
+    long: Demethylase inhibitor
   - short: DSS
     long: Decision support system
-  - short: AUDPC
-    long: Area under the disease progress curve
+  - short: GRDC
+    long: Grains Research and Development Corporation
   - short: NGA
     long: Northern Growers Alliance
-  - short: GRDC
-    long: Grains Research and Development Corporation
-  - short: DMI
-    long: Demethylase inhibitor
+  - short: USQ
+    long: University of Southern Queensland
+
 output:
@@
 Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013], however no evidence for how they compare to Australian varietal resistance could be found.
-Currently, Jade-AU has the the best disease resistance to powdery mildew (moderately susceptible), with cv. Green Diamond also having some resistance [@Sparks2017].
+Currently, Jade-AU has the the best disease resistance to powdery mildew (moderately susceptible), with cv. Green Diamond also having some resistance [@AMAGuide].
 However, commercially available mungbean cultivars in Australia lack sufficient resistance to be used as the primary powdery mildew management strategy.

### 2020-08-07 paper/paper.Rmd
Wordsmithing

@@
 
-Considering the November 2019 launch of the mobile app decision support system (DSS) PowderyMildewMBM [@Diggle], which provides a cost benefit analysis to assists growers in their decision "if" and "when" apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
+With the November 2019 launch of the mobile app decision support system (DSS) PowderyMildewMBM [@Diggle], which provides a cost benefit analysis to assists growers in their decision "if" and "when" apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
 The aim of this meta-analysis was to determine, from a collection of unpublished studies, what spray management scenario provides the greatest yield protection from powdery mildew in Australian mungbean.

### 2020-08-07 paper/paper.Rmd
Edit response variable section
Set up equation to be numbered and edits for clarity

@@
 
-In the meta-analysis, to ensure sufficient replication, we made no distinction between the tebuconazole and propiconazole fungicide treatments within the trials that met the selection criteria.
+In the meta-analysis, to ensure sufficient replication, we made no distinction between the tebuconazole and propiconazole fungicide treatments.
 The design of all trials included in this analysis were randomised complete block designs and were not previously published in peer-reviewed literature.
-Details of trial data are presented within a research compendium as a supplement to this publication [<!-- DOI to reference to compendium -->].
+Details of trial data are presented in a research compendium as a supplement to this publication [<!-- DOI to reference to compendium -->].
 
-## Response Variable - Grain Yield
+## Response Variable
 
-Grain yield (tonnes per hectare), was used as the response variable for the meta-analysis.
+Grain yield measured as tonnes per hectare was used as the response variable for the meta-analysis.
 Mean grain yields for each treatment were either obtained directly from trial reports or calculated from the raw data when available.
@@
 Similar to Paul *et al..* [-@Paul2007], we fitted a multivariate random effects model
-$Y_i \sim N(\mu,s_i^2 + \sigma^2)$
-where $Y_i$ is the response, a vector of the grain yield measurements (tonnes per hectare) for each treatment in the $i$th trial over total number ($K$) of trials ($i$  = 1, ...$K$). 
+\begin{equation}
+Y_i \sim N(\mu,s_i^2 + \sigma^2)
+\end{equation}
+where $Y_i$ is the response, a vector of the grain yield measurements (tonnes per hectare), for each treatment in the $i$th trial over the total number ($K$) of trials ($i = 1, ...K$).
 $Y_i$ is estimated from a normal distribution with the mean $\mu$, sample variance of $S_i^2$ and a between trial variance of $\sigma^2$.
@@
 
-While the main aim of all the identified trials was to assess the efficacy of fungicide for control of powdery mildew, some trials tested additional potential covariates in the experimental design.
+While the main aim of all the included trials was to assess the efficacy of fungicide for control of mungbean powdery mildew, some trials tested additional potential covariates in the experimental design.
 These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications and cultivar.
-To account for the variation attributed to some of these variables between trials, and within trials, a single $trial$ factor was created.
-The $trial$ random variable made distinctions between the following variables: unique trial reference code, trial location, trial season, host genotype, row spacing, and fungicide dose.
+To account for the variation attributed to some of these variables between and within trials, a single $trial$ factor was created.
+The $trial$ factor made distinctions between the following variables: unique trial reference code, trial location, trial season, host cultivar, row spacing, and fungicide dose.
 

### 2020-08-07 paper/paper.Rmd
Wordsmithing

@@
 An $Early$ fungicide application treatment referred to a fungicide spray schedule that commenced prior to the disease being observed in the trial.
-$Recommended$ referred to a fungicide spray schedule which commenced 1 -- 3 days following the first sign of disease.
-$Late$ treatments commenced between 7 and 13 days after the first sign of disease. 
-There were no spray schedule treatments which began between 4 and 6 days after the first sign of powdery mildew.
+$Recommended$ referred to a fungicide spray schedule which commenced one to three days following the first sign of disease.
+$Late$ referred to treatments that were applied between seven and 13 days after the first sign of disease. 
+There were no spray schedule treatments that began between four and six days after the first sign of powdery mildew.
+
 The number of fungicide applications was binned into two categories.
-A spray schedule with a $single$ spray, and a spray schedule with two or three spray applications $plus$.
-The division of the treatments produced: 13 $Early_{single}$ treatments; 5 $Early_{plus}$; 32 $Recommended_{single}$; 46 $Recommended_{plus}$; 17 $Late_{single}$; and 20 $Late_{plus}$.
-$Early_{plus}$ treatments were removed from the subsequent meta-analysis, due to an insufficient sample size.
+A spray schedule with only one application, $single$ and a spray schedule with two or three spray applications, $plus$.
+The division of the treatments produced: 13 $Early_{single}$ treatments; five $Early_{plus}$; 32 $Recommended_{single}$; 46 $Recommended_{plus}$; 17 $Late_{single}$; and 20 $Late_{plus}$.
+$Early_{plus}$ treatments were removed from the meta-analysis due to an insufficient sample size.
 
-What remained was the mean yield for a total of 173 treatments in the following five spray schedule categories: no spray $control$, $Early_{single}$, $Recommended_{single}$, $Recommended_{plus}$, $Late_{single}$, and $Late_{plus}$.
+The remaining data were the mean yields for a total of 173 treatments in the following five spray schedule categories: no spray $control$, $Early_{single}$, $Recommended_{single}$, $Recommended_{plus}$, $Late_{single}$, and $Late_{plus}$.
 
@@
 Given the ordinal scale ranked plots on the percent of foliage showing the disease from the lower canopy to the upper canopy, a conversion from percentage of the diseased canopy, to the 1 -- 9 scale was straight-forward.
-The end of season mean plot severity, and date of first sign of disease were used to calculate the area under the disease progress curve (AUDPC) for each treatment.
+The end of season mean plot severity and date of first sign of disease were used to calculate the area under the disease progress curve (AUDPC) for each treatment.
 Additional powdery mildew mean plot severity observations made in-between these two observations were also included in the AUDPC calculation if they were available.

### 2020-08-07 paper/paper.Rmd
wordsmithing

@@
 
-The mean difference in grain yield was estimated from the difference in model estimates of the non-treated control and each of the spray schedule treatments using fungicide.  
+The mean difference in grain yield was estimated from the difference in model estimates of the non-treated control and each of the fungicide spray schedule treatments.
 Disease pressure was tested against the basic model to determine if, when introduced as a moderator variable, it could significantly explain additional heterogeneity between the spray schedule treatments.
@@
 
-Linear contrasts were used to produce the mean difference in effect sizes, and their respective standard errors and 95% confidence intervals, between each spray schedule treatment.
+Linear contrasts were used to produce the mean difference in effect sizes and their respective standard errors and 95% confidence intervals between each spray schedule treatment.
 
 Additional meta-analysis models tested variables ... for their influence on the SpraySchedule variables ability to mitigate yield loss.
-For the variable disease pressure a Wald-type test was used to test the impact of this variable on the model as a whole.
+For the variable disease pressure a Wald-type test was used to test the effect of this variable on the model as a whole.
 

### 2020-08-07 paper/paper.Rmd
Replace / with -1 per MDPI guidelines

@@
 
-Overall the meta-analysis indicated that, with the exception of the $Early_{single}$ treatment, all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure \@ref(fig:Figure1)).
-Treatments which incorporated multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table 3).
+Overall the meta-analysis indicated that with the exception of the $Early_{single}$ treatment all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure \@ref(fig:Figure1)).
+Treatments which incorporated multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table \@ref(tab:Table3)).
 The treatment that showed the most yield saved compared to the control, $Recommended_{plus}$, was also significantly higher than all other single applications, (
@@
 $Late_{single}$, `r reportP(contrast_Ssum$pvals[grep("Late - Recommended_plus",contrast_Ssum$contrast)])`). 
-However the $Late_{plus}$ only showed significantly greater yield saved when compared to the $Early_{single}$ treatment (`r reportP(contrast_Ssum$pvals[grep("Late_plus - Early",contrast_Ssum$contrast)])`)
+However, the $Late_{plus}$ only showed significantly greater yield saved when compared to the $Early_{single}$ treatment (`r reportP(contrast_Ssum$pvals[grep("Late_plus - Early",contrast_Ssum$contrast)])`)
 Consideration should be given when comparing $Late_{plus}$ and $Early_{single}$ treatments given they did not occur within the same trial for any of the 15 trials included in the meta-analysis.
-Within the single fungicide application treatments $Late_{single}$ provided the highest yield protection, and was estimated at saving an average of `r round(PM_mv$b[5,1] * 1000, 2)` kg / ha (SE = `r round(PM_mv$se[5] * 1000, 2)` kg / ha) relative to the no spray control (`r reportP(PM_mv$pval[5])`).
-$Early_{single}$ treatments were significantly lower than all other treatments (Table 3) and reported a mean estimate `r abs(round(PM_mv$b[2,1] * 1000, 2))` kg / ha (SE = `r round(PM_mv$se[2] * 1000, 2)` kg / ha) lower than the no spray control (`r reportP(PM_mv$pval[2])`).
+Within the single fungicide application treatments $Late_{single}$ provided the highest yield protection and was estimated to save an average of `r round(PM_mv$b[5,1] * 1000, 2)` kg ha^-1^ (SE = `r round(PM_mv$se[5] * 1000, 2)` kg ha^-1^) relative to the no spray control (`r reportP(PM_mv$pval[5])`).
+$Early_{single}$ treatments were significantly lower than all other treatments (Table 3) and reported a mean estimate `r abs(round(PM_mv$b[2,1] * 1000, 2))` kg ha^-1^ (SE = `r round(PM_mv$se[2] * 1000, 2)` kg ha^-1^) lower than the no spray control (`r reportP(PM_mv$pval[2])`).
 
@@
 The current advice provided to growers for when to commence fungicide applications for control of powdery mildew, is to spray at the first sign of the disease then if necessary a follow-up spray two weeks later [@SueThompson2016; @Sparks2017].
-This meta-analysis confirms that advice, by showing that applying the first fungicide application, within three days of first sign will significantly mitigate yield loss from powdery mildew by between `r round(PM_mv$ci.lb[3],5)*1000` to `r round(PM_mv$ci.ub[3],5)*1000` kg / ha ($Recommended$, `r reportP(PM_mv$pval[3])`).
-Additionally, spray schedules which commenced "late", up to 13 days after first sign of the disease were still effective at mitigating yield loss by `r round(PM_mv$ci.lb[5],5)*1000` to `r round(PM_mv$ci.ub[5],5)*1000` kg / ha ($Late$,`r reportP(PM_mv$pval[5])`).
+This meta-analysis confirms that advice, by showing that applying the first fungicide application, within three days of first sign will significantly mitigate yield loss from powdery mildew by between `r round(PM_mv$ci.lb[3],5)*1000` to `r round(PM_mv$ci.ub[3],5)*1000` kg ha^-1^ ($Recommended$, `r reportP(PM_mv$pval[3])`).
+Additionally, spray schedules which commenced "late", up to 13 days after first sign of the disease were still effective at mitigating yield loss by `r round(PM_mv$ci.lb[5],5)*1000` to `r round(PM_mv$ci.ub[5],5)*1000` kg ha^-1^ ($Late$,`r reportP(PM_mv$pval[5])`).
 Spray schedules which included follow-up fungicide applications were on average more effective at reducing yield loss due to powdery mildew by; 
-`r round(PM_mv$ci.lb[4],5)*1000` to `r round(PM_mv$ci.ub[4],5)*1000` kg / ha in the $RecommendedPlus$ treatments (`r reportP(PM_mv$pval[4])`) and
-`r round(PM_mv$ci.lb[6],5)*1000` to `r round(PM_mv$ci.ub[6],5)*1000` kg / ha in the $LatePlus$ treatments (`r reportP(PM_mv$pval[6])`) (Figure \@ref(fig:Figure2))
+`r round(PM_mv$ci.lb[4],5)*1000` to `r round(PM_mv$ci.ub[4],5)*1000` kg ha^-1^ in the $RecommendedPlus$ treatments (`r reportP(PM_mv$pval[4])`) and
+`r round(PM_mv$ci.lb[6],5)*1000` to `r round(PM_mv$ci.ub[6],5)*1000` kg ha^-1^ in the $LatePlus$ treatments (`r reportP(PM_mv$pval[6])`) (Figure \@ref(fig:Figure2))
 which again follows the advice given by Thompson et al. [@SueThompson2016].
@@
 Second applications, if they are needed, should be applied at least 10 - 14 days after the first application and not within 21 days of harvest [@APVMAcustodia].
-If time permitted a second spray after the first "late" application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(T3$estimates[10], 4)*1000` kg / ha, when compared to the $Late$, single spray treatment `r reportP(T3$pval[10])`.
+If time permitted a second spray after the first "late" application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(T3$estimates[10], 4)*1000` kg ha^-1^, when compared to the $Late$, single spray treatment `r reportP(T3$pval[10])`.
 
@@
 
-We estimate the costs of applying tebuconazole fungicide at \$4.18 AU / ha, if fungicide is purchased at \$15 / L [@Simfendorfer2011] and applications cost are \$2 per hectare [@QueenslandGovernment2019].
-The meta-analysis estimates average yield savings of between `r coef(PM_mv)[3]*1000` kg / ha ($Recommended$) and `r coef(PM_mv)[4]*1000` kg / ha ($RecommendedPlus$). 
-These average yield savings would save \$`r (coef(PM_mv)[3]*1000)` AU / ha for a single application at first sign and \$`r coef(PM_mv)[4]*1000` AU / ha if a follow-up application is made.
+We estimate the costs of applying tebuconazole fungicide at \$4.18 AU ha^-1^, if fungicide is purchased at \$15 / L [@Simfendorfer2011] and applications cost are \$2 per hectare [@QueenslandGovernment2019].
+The meta-analysis estimates average yield savings of between `r coef(PM_mv)[3]*1000` kg ha^-1^ ($Recommended$) and `r coef(PM_mv)[4]*1000` kg ha^-1^ ($RecommendedPlus$). 
+These average yield savings would save \$`r (coef(PM_mv)[3]*1000)` AU ha^-1^ for a single application at first sign and \$`r coef(PM_mv)[4]*1000` AU ha^-1^ if a follow-up application is made.
 Lucrative returns such as these may tempt growers into applying fungicide to control diseases such as powdery mildew when they are unnecessary.

### 2020-08-07 paper/paper.Rmd
Insert sentence giving earliest and latest appearance of PM in trials
Wordsmithing  and edits

@@
 
+The first sign of powdery mildew was observed as early as the February 28 in the 2013 Premer trial and as late as the April 12 in the 2019 Hermitage trials.
+
 In the meta-analysis, to ensure sufficient replication, we made no distinction between the tebuconazole and propiconazole fungicide treatments.
@@
 The $Q_M$ omnibus test of moderators, shows the moderators significantly influence the model ($Q_M =$ `r PM_mv$QM` $,df =$ `r PM_mv$m`, `r reportP(PM_mv$QMp)`) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
-The analysis shows there is still a significant amount of residual heterogeneity ($Q_E =$ `r PM_mv$QE` $,df=$ `r PM_mv$k - PM_mv$m`, `r reportP(PM_mv$QEp)`) not captured by the spray management moderator indicating other possible moderators, which might influence grain yield.
+The analysis shows there is still a significant amount of residual heterogeneity ($Q_E =$ `r PM_mv$QE` $,df=$ `r PM_mv$k - PM_mv$m`, `r reportP(PM_mv$QEp)`) not captured by the spray management moderator indicating other possible moderators, which may influence grain yield.
 
-A log-ratio test, based on a chi-squared distribution, indicated that retaining the `SpraySchedule` variable as a random interactive term provided a significantly better model (P = 0.0179). 
-An inspection of log-likelihood profile plots showed the model, for each random interactive term, provided a reasonable estimate of $\tau^2$, with no indication the variables were over-fit.
+A log-ratio test based on a chi-squared distribution indicated that retaining the `SpraySchedule` variable as a random interactive term provided a significantly better model (P = 0.0179).
+An inspection of log-likelihood profile plots showed the model for each random interactive term provided a reasonable estimate of $\tau^2$, with no indication the variables were over-fit.
 
-While the addition of disease pressure, as an interactive moderator term to `SpraySchedule`, did explain slightly more residual heterogeneity, shown by a lower $Q_E = 409.91,$. 
+While the addition of disease pressure as an interactive moderator term to `SpraySchedule`, did explain slightly more residual heterogeneity as shown by a lower $Q_E = 409.91,$.
 The model including disease pressure did not significantly improve the model (P = 0.4859) and did not significantly explain differences in the `SpraySchedule` term, and therefore disease pressure was not included in the final model.
-
-First sign of powdery mildew was observed as early as the 28th of February in the 2013 trial at .... ; and as late as the 12th of April in the 2018 trial at ...
-
-<!-- What is this `SeasonPlot`? I can't find any docs and no file named `SeasonPlot`. It should just be code here int the doc for easy editing. -->
 

### 2020-08-07 paper/paper.Rmd
Fix space in colname of Table 2

@@
         booktabs = TRUE,
-        caption = "Powdery mildew severity scoring scale.") %>%
+        caption = "Powdery mildew severity scoring scale.",
+        col.names = c("Scale",
+                      "Scale Description")) %>%
   kable_styling()

### 2020-08-07 paper/paper.Rmd
Code formatting

@@
 PM_Mdat %>%
-  distinct(trial_ref, planting_date, harvest_date,first_sign_disease) %>%
-  mutate(planting_date = ymd(planting_date))%>%
-  mutate(harvest_date = ymd(harvest_date))%>%
-  mutate(first_sign_disease = ymd(first_sign_disease))%>%
-  mutate(cropping_season = case_when( # add categorical value for estimated season period
-    is.na(planting_date) | is.na(harvest_date ) ~ "Estimated",
-    TRUE ~ "Actual"))%>%
-  mutate(plant_day = case_when( #for crops planted in late December minus 365 days from yday function
+  distinct(trial_ref, planting_date, harvest_date, first_sign_disease) %>%
+  mutate(planting_date = ymd(planting_date)) %>%
+  mutate(harvest_date = ymd(harvest_date)) %>%
+  mutate(first_sign_disease = ymd(first_sign_disease)) %>%
+  mutate(cropping_season = case_when(
+    # add categorical value for estimated season period
+    is.na(planting_date) | is.na(harvest_date) ~ "Estimated",
+    TRUE ~ "Actual"
+  )) %>%
+  mutate(plant_day = case_when(
+    #for crops planted in late December minus 365 days from yday function
     yday(planting_date) < 200 ~ yday(planting_date),
@@
   )) %>%
-  mutate(season_length = case_when(  # when either planting date or harvest date are missing use the overall mean season length as an estimate
+  mutate(season_length = case_when(
+    # when either planting date or harvest date are missing use the overall mean season length as an estimate
     is.na(planting_date) | is.na(harvest_date) ~
-      mean(yday(harvest_date) - plant_day,na.rm = TRUE),
+      mean(yday(harvest_date) - plant_day, na.rm = TRUE),
     TRUE ~ yday(harvest_date) - plant_day
-  ))%>%
-  mutate(plant_day = case_when( # estimate planting day  from mean season length
+  )) %>%
+  mutate(plant_day = case_when(
+    # estimate planting day  from mean season length
     is.na(plant_day) ~ yday(harvest_date) - season_length,
     TRUE ~ plant_day
-  ))%>%
-  mutate(harvest_day = case_when( #estimate harvest day from mean season length
+  )) %>%
+  mutate(harvest_day = case_when(
+    #estimate harvest day from mean season length
     is.na(harvest_date) ~ plant_day + season_length,
     TRUE ~ yday(harvest_date)
-  ))%>%
+  )) %>%
   mutate(trial_ref = factor(trial_ref, # reorder by the first_sign_of_disease
-                            levels = trial_ref[rev(order(ymd(first_sign_disease)))]))%>%
+                            levels = trial_ref[rev(order(ymd(first_sign_disease)))])) %>%
   ggplot() +
-  geom_pointrange(aes(
+  geom_pointrange(
+    aes(
       x = trial_ref,
@@
       colour = cropping_season
-   ))+
-  scale_y_continuous(limits = c(
-    -25,
+    )
+  ) +
+  scale_y_continuous(
+    limits = c(-25,
                183),
-    labels = paste(month(1:7, label = TRUE, abbr = TRUE), rep(1,7),sep = "-"),
-    breaks = yday(ymd(paste(rep(2018, 7),1:7, rep(1,7),sep = "-")))
+    labels = paste(month(1:7, label = TRUE, abbr = TRUE), rep(1, 7), sep = "-"),
+    breaks = yday(ymd(paste(
+      rep(2018, 7), 1:7, rep(1, 7), sep = "-"
+    )))
   ) +
-  geom_hline(yintercept = yday(ymd(paste(rep(2018, 7),1:7, rep(1,7),sep = "-"))), 
+  geom_hline(yintercept = yday(ymd(paste(
+    rep(2018, 7), 1:7, rep(1, 7), sep = "-"
+  ))),
   colour = "grey80",
-             linetype = 2)+
+  linetype = 2) +
   geom_point(aes(x = trial_ref, y = yday(first_sign_disease))) +
   coord_flip() +
-  scale_color_manual(values=c("black","grey70"))+
-  ggtitle("Season length and first appearance of powdery mildew \nin each respective trial")+
-  xlab("Trial reference code")+
+  scale_color_manual(values = c("black", "grey70")) +
+  ggtitle("Season length and first appearance of powdery mildew\nin each respective trial") +
+  xlab("Trial reference code") +
   ylab(NULL)
-
 ```

### 2020-08-07 paper/paper.Rmd
Code formatting and edits to text in discussion

--- 2020-08-07 paper/paper.Rmd
@@
 The sample variance was calculated from the raw data when available or the least squares statistic in the trial reports.
-Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 2.042 and the approach reported in Ngugi *et al.* [-@Ngugi2011].
+Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 2.042 and the approach reported in Ngugi  [-@Ngugi2011].
 The T-critical value was obtained from a t-distribution table using, 30 degrees of freedom and probability of $a = 0.05$.
@@
 T3[, 2:5] <- round(T3[, 2:5], 4)
-T3%>%
-  mutate(contrasts = gsub("-", "", contrasts))%>%
-  mutate(contrasts = gsub(" \\+", " -", contrasts))%>%
-  mutate(contrasts = gsub(" = 0", "", contrasts))%>%
+T3 %>%
+  mutate(contrasts = gsub("-", "", contrasts)) %>%
+  mutate(contrasts = gsub(" \\+", " -", contrasts)) %>%
+  mutate(contrasts = gsub(" = 0", "", contrasts)) %>%
   rename(
@@
 
-The current advice provided to growers for when to commence fungicide applications for control of powdery mildew, is to spray at the first sign of the disease then if necessary a follow-up spray two weeks later [@SueThompson2016; @Sparks2017].
-This meta-analysis confirms that advice, by showing that applying the first fungicide application, within three days of first sign will significantly mitigate yield loss from powdery mildew by between `r round(PM_mv$ci.lb[3],5)*1000` to `r round(PM_mv$ci.ub[3],5)*1000` kg ha^-1^ ($Recommended$, `r reportP(PM_mv$pval[3])`).
+The current advice provided to growers for when to commence fungicide applications for control of powdery mildew is to spray at the first sign of the disease then if necessary a follow-up spray two weeks later [@SueThompson2016; @Sparks2017].
+This meta-analysis confirms that advice, by showing that applying the first fungicide application within three days of first sign will significantly mitigate yield loss from powdery mildew by between `r round(PM_mv$ci.lb[3],5)*1000` to `r round(PM_mv$ci.ub[3],5)*1000` kg ha^-1^ ($Recommended$, `r reportP(PM_mv$pval[3])`).
 Additionally, spray schedules which commenced "late", up to 13 days after first sign of the disease were still effective at mitigating yield loss by `r round(PM_mv$ci.lb[5],5)*1000` to `r round(PM_mv$ci.ub[5],5)*1000` kg ha^-1^ ($Late$,`r reportP(PM_mv$pval[5])`).
@@
 `r round(PM_mv$ci.lb[4],5)*1000` to `r round(PM_mv$ci.ub[4],5)*1000` kg ha^-1^ in the $RecommendedPlus$ treatments (`r reportP(PM_mv$pval[4])`) and
-`r round(PM_mv$ci.lb[6],5)*1000` to `r round(PM_mv$ci.ub[6],5)*1000` kg ha^-1^ in the $LatePlus$ treatments (`r reportP(PM_mv$pval[6])`) (Figure \@ref(fig:Figure2))
-which again follows the advice given by Thompson et al. [@SueThompson2016].
-This meta-analysis adds certainty to the advice, which is currently given to growers, especially around any uncertainty that Early sprays might be effective at suppressing the disease. 
-We show here Early fungicide applications, which were made prior to any sign of the disease, were not effective at mitigating yield loss.
+`r round(PM_mv$ci.lb[6],5)*1000` to `r round(PM_mv$ci.ub[6],5)*1000` kg ha^-1^ in the $LatePlus$ treatments (`r reportP(PM_mv$pval[6])`) (Figure \@ref(fig:Figure2)), which again follows the advice given by Thompson et al.
+and Sparks and Kelly [-@SueThompson2016; -@Sparks2017].
+This meta-analysis supports the advice, which is currently given to growers, especially around any uncertainty that early sprays might be effective at saving yield. 
+We show here early fungicide applications made prior to any sign of the disease were not effective at mitigating yield loss.
 
-This meta-analysis also provides a effective spray window for fungicide applications, given that spray schedules, which commenced "late" were still significantly effective at mitigating yield loss ($Late$ `r reportP(PM_mv$pval[5])`) 7 - 13 days after the first sign of disease.
-Growers typically do not have the time to inspect their crop regularly for the first sign of powdery mildew and therefore the disease may not be spotted within the first couple of days of it establishing.
+This meta-analysis also provides a effective spray window for fungicide applications given that spray schedules which commenced "late" were still significantly effective at mitigating yield loss ($Late$ `r reportP(PM_mv$pval[5])`) 7 -- 13 days after the first sign of disease.
+Growers typically do not have the time to inspect their crop regularly for the first sign of powdery mildew and therefore the disease may not be spotted within the first couple of days of it becoming established.
 Also, weather conditions and logistical issues might prevent growers from getting machinery in the paddock to treat the disease immediately after it is spotted.
-These issues, and perhaps other on farm duties, might delay a timely application, permitting the disease more time to establish. 
-Knowing a delay of up to two weeks may not lead to yield losses, can allow growers to incorporate other integrated pest management options, such as insecticide, with the fungicide spray saving on spray application costs.
-However attention should be made to the label requirements when first planning a spray schedule.
-Second applications, if they are needed, should be applied at least 10 - 14 days after the first application and not within 21 days of harvest [@APVMAcustodia].
-If time permitted a second spray after the first "late" application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(T3$estimates[10], 4)*1000` kg ha^-1^, when compared to the $Late$, single spray treatment `r reportP(T3$pval[10])`.
+These issues, and perhaps other on-farm duties, might delay a timely application permitting the disease more time to become established.
+Knowing a delay of up to two weeks may not lead to yield losses, can allow growers to incorporate other integrated pest management options, such as an insecticide application with the fungicide saving on application costs.
+Second applications, if they are needed, should be applied at least 10 -- 14 days after the first application and not within 21 days of harvest under the currently labelled permit [@APVMAcustodia].
+If time permits a second spray after the first "late" application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(T3$estimates[10], 4)*1000` kg ha^-1^, when compared with the $Late$, single spray treatment `r reportP(T3$pval[10])`.
+In all cases, label requirements should be consulted and strictly adhered to when planning a spray schedule.
 
-It is important to note, the studies included in this meta-analysis may not reflect a "normal" mungbean season. 
-All the included experiments were intentionally sown late in the season, from January through to as late as early March, to ensure powdery mildew infection (Figure \@ref(fig:Figure2)). 
+It is important to note that the studies included in this meta-analysis might not reflect a "normal" mungbean season.
+All the included experiments were intentionally sown late in the mungbean growing season from January through early March to ensure powdery mildew infection (Figure \@ref(fig:Figure2)).
 While certain circumstances may force growers to sow mungbeans late, many may decide to fallow their fields instead of risking a powdery mildew epidemics and an early frost damaging the crop and yields.
@@
 If the planting guide is adhered to the mungbean would be at a lower risk of powdery mildew, reducing the requirement for fungicide applications. 
-An example of this is if we inspect the six trials in which powdery mildew manifested 60 days or greater after planting (Trial references: AM1304, mung1819/01, mung1011/01, AM1303, AM1305 and BB1305).
+An example of this can be shown by inspecting the six trials in which powdery mildew manifested 60 days or greater after planting (Trial references: AM1304, mung1819/01, mung1011/01, AM1303, AM1305 and BB1305).
 Of these trials, four directly compared single $Recommended$ fungicide applications and $RecommendedPlus$ (AM1303, AM1305, BB1305 and mung1819/01), two of which (AM1305 and mung1819/01) produced at least one treatment $RecommendedPlus$ treatment with a higher grain yield the $Recommended$ treatments.
 However, neither AM1305 or mung1819/01 neither contained $Recommended$ or $RecommendedPlus$ treatments with higher mean yields than the no-spray control.
-This indicating there is likely no benefit to applying two fungicide applications when the disease manifests later than 60 days into the growing season. 
-Further the trials undertaken in 2013, such as Premer (AM1303), Goolhi (AM1305) Marys Mount (AM1304) and Millmerran (BB1305) reported a significant difference in powdery mildew severity between the fungicide treatments, however neither trial showed a significant difference in grain yield between treatments [@Millmerran2013, @premer2013, @Marysmount2013, @goolhi2013].
-Therefore, discretion is still required for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.
-The PowderyMildewMBM considers crop growth stage and weather, to assist decision making whether to spray or not to spray [@Diggle].
+This indicated that there is likely no benefit to applying two fungicide applications when the disease manifests later than 60 days into the growing season.
+Furthermore the trials undertaken in 2013, Premer (AM1303), Goolhi (AM1305) Marys Mount (AM1304) and Millmerran (BB1305), reported a significant difference in powdery mildew severity between the fungicide treatments.
+However, none of the trials showed a significant difference in grain yield between treatments [@Millmerran2013, @premer2013, @Marysmount2013, @goolhi2013].
+Therefore, as discretion is still required to determine if fungicide applications are necessary given the crop growth stage and forecast weather conditions, the PowderyMildewMBM considers crop growth stage and weather to assist decision making whether to spray or not to spray [@Diggle].
 

### 2020-08-07 paper/paper.Rmd
Code formatting and edits to discussion

--- 2020-08-07 paper/paper.Rmd
@@
   kable_styling() %>%
-  kableExtra::footnote(
+  footnote(
     alphabet = c(
@@
 ```{r Table3, echo = FALSE}
-contrast_Ssum[,2:5] <- round(contrast_Ssum[,2:5], 4)
-contrast_Ssum %>%
-  slice(grep("control", contrast, invert = TRUE)) %>%
-  mutate(pvals = reportP(pvals)) %>%
-  mutate(pvals = gsub("P = ","",pvals)) %>%
+T3[, 2:5] <- round(T3[, 2:5], 4)
+T3%>%
+  mutate(contrasts = gsub("-", "", contrasts))%>%
+  mutate(contrasts = gsub(" \\+", " -", contrasts))%>%
+  mutate(contrasts = gsub(" = 0", "", contrasts))%>%
+  rename(
+    `Treatment contrasts` = contrasts,
+    Estimate = estimates,
+    `Standard Error` = se,
+    `Z-score` = z_val,
+    `P-value` = pval,
+    ` ` = VisP
+  )%>%
   kable(format = "latex",
         booktabs = TRUE,
-        caption = "Table 3: Estimated grain yield contrasts between each spray schedule.",
-        col.names = c("Treatment contrasts","Estimated difference","Std Error","Z-Score","P-Value"," "))%>%
+        caption = "Estimated grain yield contrasts between each spray schedule.")%>%
   kable_styling()%>%
-  kableExtra::footnote(general = c("*** - signficant at 0.001 level",
-                                   "** - signficant at 0.005 level",
+  footnote(general = c("** - signficant at 0.005 level",
                        "* - signficant at 0.05 level"))

### 2020-08-07 paper/paper.Rmd
Grammar

@@
 This indicating there is likely no benefit to applying two fungicide applications when the disease manifests later than 60 days into the growing season. 
-Further the trials undertaken in 2013, such as Premer (AM1303), Goolhi (AM1305) Marys Mount (AM1304) and Millmerran (BB1305) reported a significant difference in powdery mildew severity between the fungicide treatments, however neither trial showed a significant difference in grain yield between treatments [@Millmerran2013, @premer2013, @Marysmount2013, @goolhi2013].
+Further the trials undertaken in 2013, Premer (AM1303), Goolhi (AM1305) Marys Mount (AM1304) and Millmerran (BB1305), reported a significant difference in powdery mildew severity between the fungicide treatments, however none of the trials showed a significant difference in grain yield between treatments [@Millmerran2013, @premer2013, @Marysmount2013, @goolhi2013].
 Therefore, discretion is still required for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.

### 2020-08-07 paper/paper.Rmd
Standardise formatting of spray variable names

@@
 An example of this is if we inspect the six trials in which powdery mildew manifested 60 days or greater after planting (Trial references: AM1304, mung1819/01, mung1011/01, AM1303, AM1305 and BB1305).
-Of these trials, four directly compared single $Recommended$ fungicide applications and $RecommendedPlus$ (AM1303, AM1305, BB1305 and mung1819/01), two of which (AM1305 and mung1819/01) produced at least one treatment $RecommendedPlus$ treatment with a higher grain yield the $Recommended$ treatments.
-However, neither AM1305 or mung1819/01 neither contained $Recommended$ or $RecommendedPlus$ treatments with higher mean yields than the no-spray control.
+Of these trials, four directly compared single $Recommended$ fungicide applications and $Recommended_{plus}$ (AM1303, AM1305, BB1305 and mung1819/01), two of which (AM1305 and mung1819/01) produced at least one treatment $Recommended_{plus}$ treatment with a higher grain yield the $Recommended$ treatments.
+However, neither AM1305 or mung1819/01 neither contained $Recommended$ or $Recommended_{plus}$ treatments with higher mean yields than the no-spray control.
 This indicating there is likely no benefit to applying two fungicide applications when the disease manifests later than 60 days into the growing season. 
-Further the trials undertaken in 2013, Premer (AM1303), Goolhi (AM1305) Marys Mount (AM1304) and Millmerran (BB1305), reported a significant difference in powdery mildew severity between the fungicide treatments, however none of the trials showed a significant difference in grain yield between treatments [@Millmerran2013, @premer2013, @Marysmount2013, @goolhi2013].
+Furthermore, the 2013 trials, Premer (AM1303), Goolhi (AM1305) Marys Mount (AM1304) and Millmerran (BB1305), reported a significant difference in powdery mildew severity between the fungicide treatments.
+However, none of the trials showed a significant difference in grain yield between treatments [@Millmerran2013, @premer2013, @Marysmount2013, @goolhi2013]. 
 Therefore, discretion is still required for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.
-The PowderyMildewMBM considers crop growth stage and weather, to assist decision making whether to spray or not to spray [@Diggle].
+To aid in making these decisions, DSS tools such as the PowderyMildewMBM consider crop growth stage and weather, to assist decision making whether to spray or not to spray [@Diggle] and can help users make an informed decision.
 
-PowderyMildewMBM also provides a cost-benefit analysis to growers for fungicide spray schedule scenarios.
-The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability that one or two fungicide sprays would protect yields sufficiently to increase the net profit.
 The scope of the meta-analysis is limited to the timing of fungicide application and therefore we can not validate all the variables available in PowderyMildewMBM.

### 2020-08-07 paper/paper.Rmd
Add FRAC abbreviation to list
Edit Discussion for Flow

@@
     long: Decision support system
+  - short: FRAC
+    long: Fungicide Resistance Action Committee
   - short: GRDC
@@
 Therefore, discretion is still required for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.
-To aid in making these decisions, DSS tools such as the PowderyMildewMBM consider crop growth stage and weather, to assist decision making whether to spray or not to spray [@Diggle] and can help users make an informed decision.
-
-The scope of the meta-analysis is limited to the timing of fungicide application and therefore we can not validate all the variables available in PowderyMildewMBM.
-However our results validate the decision of the app developers not to recommend prophylactic fungicide applications.
-If the powdery mildew is not observed in the crop the app advises the user to keep monitoring for disease.
-<!-- Think about how to word this, that we are using this to validate the app: The findings of this meta-analysis confirm the recommendations that PowderyMildewMBM gives in most situations would be correct.
--->
-<!-- I am finding it difficult to say that our findings confirm recommendations of the app, given the app does not advise on early late or recommended spray timing AND we don't investigate the differences in yield mitigations under the variables in the app (growth stage and weather) [Paul]-->
 
 Scouting the crop for powdery mildew might not be necessary during the warmer months of the season.
-Data from the trials included in this experiment show regardless of crop sowing date, powdery mildew establishes on average in the month of March, which marks the beginning of autumn (Figure \@ref(fig:Figure2)).
+Data from the trials included in this experiment show regardless of crop sowing date, powdery mildew establishes on average in the month of March (Figure \@ref(fig:Figure2)), which marks the beginning of autumn in Australia.
 Considering the results of the meta-analysis, weekly inspections would be ideal to ensure timely fungicide applications if necessary.
-Scouting at intervals greater than 12 - 13 days, might risk crop losses if a spray schedule does not commence within aforementioned the spray window.
+Scouting at intervals greater than 12 -- 13 days, might risk crop losses if a spray schedule does not commence within aforementioned the spray window.
 More work is needed to understand when "late" fungicide applications are too late.
@@
 We estimate the costs of applying tebuconazole fungicide at \$4.18 AU ha^-1^, if fungicide is purchased at \$15 / L [@Simfendorfer2011] and applications cost are \$2 per hectare [@QueenslandGovernment2019].
-The meta-analysis estimates average yield savings of between `r coef(PM_mv)[3]*1000` kg ha^-1^ ($Recommended$) and `r coef(PM_mv)[4]*1000` kg ha^-1^ ($RecommendedPlus$). 
+This meta-analysis estimates average yield savings of between `r coef(PM_mv)[3]*1000` kg ha^-1^ ($Recommended$) and `r coef(PM_mv)[4]*1000` kg ha^-1^ ($RecommendedPlus$).
 These average yield savings would save \$`r (coef(PM_mv)[3]*1000)` AU ha^-1^ for a single application at first sign and \$`r coef(PM_mv)[4]*1000` AU ha^-1^ if a follow-up application is made.
@@
 Excessive use of fungicides are highly likely to lead ongoing problems such as fungicide resistance.
-*Podosphaera xanthii* is categorised by the Australian Fungicide resistance Action Committee (FRAC) as a "High risk" candidate to evolve fungicide resistance [@FRACrisk2019].
-Evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with potential fungicide resistance in mind.
+The evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with potential fungicide resistance in mind.
 Powdery mildew is one such group of fungal pathogens with an extensive track record of rapidly developing fungicide resistance.
-In cucurbits, *P.
-xanthii* evolved resistance to benzimidazole within three years of its registration [@Peterson1973] and has evolved resistance to numerous fungicide classes, such as benzimidazoles, demethylation inhibitors, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines since [@Mcgrath2001].
-In cereal crops *Blumeria graminis* showed reduced sensitivity to strobilurins in 1998, two years after the fungicides began being used in Europe [@Chin2001].
+*P. xanthii* is categorised by the Australian Fungicide Resistance Action Committee (FRAC) as a "High Risk" candidate to evolve fungicide resistance [@FRACrisk2019].
+*P.
+xanthii* has evolved resistance to benzimidazole within three years of its registration [@Peterson1973] and has evolved resistance to numerous fungicide classes, such as benzimidazoles, demethylation inhibitors, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines since [@Mcgrath2001] in cucurbits.
+In cereal crops, *Blumeria graminis* showed reduced sensitivity to strobilurins in 1998, two years after the fungicides began being used in Europe [@Chin2001].
 
-According to the Fungicide Resistance Action Committee (FRAC) it is important to alternate or mix fungicides with different modes of action to avoid fungicide resistance. 
-At the time of writing, in Australia one fungicide is registered with the to treat powdery mildew in mungbean, Veritas/Custodia (200 g/L tebuconazole with 120 g/L azoxystrobin).
-This fungicide provides dual action: tebuconazole disrupts C-14 demethylase, required in sterol biosynthesis for cell membranes; and azoxystrobin, a Quinone outside inhibitor.
+According to FRAC it is important to alternate or mix fungicides with different modes of action to avoid fungicide resistance.
+At the time of writing, in Australia, only one fungicide is registered with the to treat powdery mildew in mungbean, Veritas/Custodia (200 g/L tebuconazole with 120 g/L azoxystrobin).
+This fungicide provides dual action: tebuconazole disrupts C-14 demethylase, required in sterol biosynthesis for cell membranes; and azoxystrobin, a quinone outside inhibitor.
 Quinone is required in cell metabolism and active in the mitochondrial complex III.
-However FRAC recommends that applications of QoIs or strobilurins, singularly or as a mixture, should not be applied consecutively and alternated with a fungicide from a different group [@Brent2007]. 
-For mungbean, past experiments have shown some success with sulphur applications to control powdery mildew. 
+However, FRAC recommends that applications of QoIs or strobilurins, singularly or as a mixture, should not be applied consecutively and should be alternated with a fungicide from a different group [@Brent2007].
+For mungbean, past experiments in the Northern Grains Region have shown some success with sulphur applications to control powdery mildew.
 Sulphur is a non-systemic protectant and thus provides an excellent option for rotation to limit the emergence of fungicide resistance.
 
-To extend the time that a fungicide remains effective against the target pathogen, strategic use of the fungicide must be considered.
-Excessive fungicide sprays by a single active increase the selection pressure on the pathogen to evolve resistance [@Brent2007]. 
-If any strains of the pathogen with resistance to the fungicide are present in a population regular use of the fungicide will increase its proportion in the population. 
+To extend the time that a fungicide remains effective against the target pathogen, the strategic use of the fungicide must be considered.
+Excessive fungicide sprays with a single active ingredient increase the selection pressure on the pathogen to evolve resistance [@Brent2007].
+If any strains of the pathogen with resistance to the fungicide are present in a population, regular use of the fungicide will increase its proportion in the population.
 Therefore, managing the disease with fungicides for the highest economic return is likely not to require eradication of the causal pathogen.
@@
 
-Advising use of fungicide for disease control to protect yields should also consider the harm it may do to symbiotic relationships with microbiota. 
-While some nitrogen fixing symbiont show a level of tolerance to fungicides, all are detrimentally affected by increasing concentrations of fungicide leading to lower nodulation and biomass accumulation [@Ahemad2011, @Shahid2019].
-Therefore if a grower is relying on inoculating with rhizobia to help meet the crops nitrogen requirements, untimely and excessive applications of a systemic fungicide for powdery mildew control may actually reduce yield.
+To aid in making these decisions and devising a good strategy, DSS tools such as the PowderyMildewMBM consider crop growth stage and weather, to assist decision making whether to spray or not to spray [@Diggle] and can help users make an informed decision.
+Using these sorts of tools can reduce unnecesary and unprofitable fungicide applications, which may help lead to the development of fungicide resistance.
 
-## Future work
+<!-- I removed the part about inoculating mungbeans.
+This isn't common.
+They're lazy.
+Growers sometimes even look at adding N for them.
+I could be possibly persuaded to reinsert this section but it doesn't really fit the flow here, I don't think.
+If we need more text we might weave it in somehow.
+-->
+
+## Future Work
+
 This meta-analysis provides a ballast for the direction of future powdery mildew research in mungbean. 

### 2020-08-07 paper/paper.Rmd
Add draft of Conclusion section

@@
 
+# Conclusion
+
 To aid in making these decisions and devising a good strategy, DSS tools such as the PowderyMildewMBM consider crop growth stage and weather, to assist decision making whether to spray or not to spray [@Diggle] and can help users make an informed decision.
-Using these sorts of tools can reduce unnecesary and unprofitable fungicide applications, which may help lead to the development of fungicide resistance.
+Using these sorts of tools can reduce unnecessary and unprofitable fungicide applications, which may help lead to the development of fungicide resistance.
 
@@
 
-## Future Work
-
-This meta-analysis provides a ballast for the direction of future powdery mildew research in mungbean. 
-However it does not provide enough certainty to when late fungicide applications would be too late to protect yield losses due to the disease. 
-Future experiments should take note of physiological maturity of the crop throughout the season so "crop age" might be considered as a covariate in future analyses.
-In cases where mungbean physiological maturity may not have been recorded the APSIM mungbean module [@RobertsonAPSIMlegume2002].
+To offer more benefit for future research, experiments should record physiological maturity of the crop throughout the season so "crop age" might be considered as a covariate in future analyses.
+<!-- I've commented this next line out, it seems to be incomplete:
+In cases where mungbean physiological maturity may not have been recorded the APSIM mungbean module [@RobertsonAPSIMlegume2002]. -->
 
 Early detection of powdery mildew is vital for an effective fungicidal control response.
-Data from the collection of 26 studies in the Northern Grain region, indicate powdery mildew is likely to manifest on crops in the first month of autumn. 
+Data from 26 studies in the Northern Grains Region indicate powdery mildew is likely to manifest on crops in the first month of autumn. 
 This data together with additional observations may permit models to predict the likely onset of the disease given weather parameters, providing an early warning system for growers to scout their crop for signs of powdery mildew.
@@
 
-# Conclusion
+Currently, the recommendations that are provided appear to be the best practices for reducing losses due to mungbean powdery mildew.
+Care needs to be taken to adhere to them, especially no prophylactic sprays, to avoid the development of fungicide resistance in the powdery mildew pathogen populations.
+This meta-analysis provides a ballast for the direction of future powdery mildew control research in Australian mungbean.
+However, it does not provide certainty as to when late fungicide applications would be too late to protect yield losses due to the disease.
+Given the high value of mungbean at the farm-gate, further work could be done in this area that would benefit the Australian mungbean industry.
 

### 2020-08-07 paper/paper.Rmd
Spelling correction
Update figure 2 caption to be more descriptive

@@
 Among the fungal diseases is powdery mildew, which can reduce yields by up to 40% [@Chankaew2013] in susceptible cultivars.
-The disease in Australia currently is thought to be caused by *Podosphaera xanthii*, syn. *Podosphara fusca*.
+The disease in Australia currently is thought to be caused by *Podosphaera xanthii*, syn. *Podosphaera fusca*.
 However, this description has changed over time and a second species has also been cited as causing the disease but not yet officially classified [@Kelly2019].
@@
 
-```{r Figure2, echo=FALSE, fig.cap="Season plot"}
+```{r Figure2, echo=FALSE, fig.cap="Season length and first appearance of powdery mildew in each respective trial for fifteen mungbean trials conducted in the Grains Research and Developmet (GRDC) Northern Grains Region of eastern Australia to evaluate the most effective time of fungicide application to save yield from powdery mildew infection.
+Trials were conducted from 2001 to 2019 by Queensland Department of Agriculture, Fisheries and Forestry, Northern Growers Alliance and University of Southern Queensland and coalated for meta-analysis."}
 PM_Mdat %>%

### 2020-08-07 paper/paper.Rmd
Use proper title for figure legend

@@
   coord_flip() +
-  scale_color_manual(values = c("black", "grey70")) +
-  ggtitle("Season length and first appearance of powdery mildew\nin each respective trial") +
+  scale_color_manual(values = c("black", "grey70"), name = "Cropping Season") +
   xlab("Trial reference code") +

### 2020-08-07 paper/paper.Rmd
Edits for flow

@@
 
-The disease cycle of the pathogen can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@PerezGarcia2009; @Sparks2017].
+The disease cycle of the pathogen can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, and which then disseminate to new infection sites [@PerezGarcia2009; @Sparks2017].
 Weather conditions that favour the rapid development of the disease are cool temperatures between 22&nbsp;&deg; and 26&nbsp;&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].

### 2020-08-07 paper/paper.Rmd
Edit caption for table 2

@@
         booktabs = TRUE,
-        caption = "Powdery mildew severity scoring scale.",
+        caption = "1 to 9 scale for rating powdery mildew severity.",
         col.names = c("Scale",

### 2020-08-07 paper/paper.Rmd
Elaboration on the disease biology and edits to introduction

--- 2020-08-07 paper/paper.Rmd
@@
     long: Decision support system
-  - short: FRAC
-    long: Fungicide Resistance Action Committee
   - short: GRDC
@@
 Among the fungal diseases is powdery mildew, which can reduce yields by up to 40% [@Chankaew2013] in susceptible cultivars.
-The disease in Australia currently is thought to be caused by *Podosphaera xanthii*, syn. *Podosphaera fusca*.
+The disease in Australia currently is thought to be caused by *Podosphaera xanthii*, syn. *Podosphara fusca*.
 However, this description has changed over time and a second species has also been cited as causing the disease but not yet officially classified [@Kelly2019].
-While research outside of Australia refers to the causal agent of mungbean powdery mildew as *Erysiphe polygoni*.
+While research outside of Australia refers to the causal agent of mungbean powdery mildew as *Erysiphe polygoni* <!--Ref?-->. Here-after we will refer to the pathogen as *P. xanthii*
 
+*P. xanthii*, is an obligate biotroph, requiring a living plant host to survive and complete it's lifecycle [@PerezGarcia2009]. 
+To date, the sexual cycle that produces chasomthecia has not been observed in Australian mungbean, and the pathogen is suspected to reproduce asexually.
+*P.
+xanthii* has one of the widest host ranges of the powdery mildews, an ability which likely assists this pathogen to survive between mungbean seasons on alternative hosts which have not yet been identified in Australia.
 The disease cycle of the pathogen can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@PerezGarcia2009; @Sparks2017].
+Powdery mildew colonies of crowded conidophores can develop rapidly on leaf surfaces causing a loss in photosynthetic potential leading to reduced yield quantity and quality [@PerezGarcia2009]. 
+In severe cases leaves can become chlorotic and cause premature leaf senescence. 
 Weather conditions that favour the rapid development of the disease are cool temperatures between 22&nbsp;&deg; and 26&nbsp;&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
-To date, the sexual cycle that produces chasomthecia has not been observed in Australian mungbean.
-And while the powdery mildew pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified in Australia.
 
@@
 Currently, Jade-AU has the the best disease resistance to powdery mildew (moderately susceptible), with cv. Green Diamond also having some resistance [@AMAGuide].
-However, commercially available mungbean cultivars in Australia lack sufficient resistance to be used as the primary powdery mildew management strategy.
+However, commercially available m
+ungbean cultivars in Australia lack sufficient resistance to be used as the primary powdery mildew management strategy.
 Evidence of this is shown by field trials conducted in 2016 with the moderately susceptible cultivar, Jade-AU, where yield losses of up to 32.7% were recorded [@SueThompson2016].
@@
 
-The data for this study were obtained through studies that were conducted by the authors, FAIR (Findable, Accessible, Interoperable, Reusable) data available from GRDC Online Farm Trials <https://www.farmtrials.com.au/>, personal correspondence with colleagues and collaborating institutions.
+The data for this study were obtained through studies that were conducted by the authors, FAIR (Findable, Accessible, Interoperable, Reusable) data available from GRDC Online Farm Trials <https://www.farmtrials.com.au/><!--Technically we did not use data from this location we obtained it from Lawrie Price-->, personal correspondence with colleagues and collaborating institutions.
 Trial data were obtained in different formats with varying levels of information.
-Raw data was obtained for some trials, others reported only the means of each treatment, with all but one trial reporting some form of variance along with the mean.
+Raw data was obtained for some trials, others reported only the means of each treatment, with all but two trials reporting some form of variance along with the mean.
 In total, 26 trials were collated.
@@
 The sample variance was calculated from the raw data when available or the least squares statistic in the trial reports.
-Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 2.042 and the approach reported in Ngugi  [-@Ngugi2011].
+Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 2.042 and the approach reported in Ngugi *et al.* [-@Ngugi2011].
 The T-critical value was obtained from a t-distribution table using, 30 degrees of freedom and probability of $a = 0.05$.
@@
 
-```{r Figure2, echo=FALSE, fig.cap="Season length and first appearance of powdery mildew in each respective trial for fifteen mungbean trials conducted in the Grains Research and Developmet (GRDC) Northern Grains Region of eastern Australia to evaluate the most effective time of fungicide application to save yield from powdery mildew infection.
-Trials were conducted from 2001 to 2019 by Queensland Department of Agriculture, Fisheries and Forestry, Northern Growers Alliance and University of Southern Queensland and coalated for meta-analysis."}
+```{r Figure2, echo=FALSE, fig.cap="Season plot"}
 PM_Mdat %>%
@@
   coord_flip() +
-  scale_color_manual(values = c("black", "grey70"), name = "Cropping Season") +
+  scale_color_manual(values = c("black", "grey70")) +
+  ggtitle("Season length and first appearance of powdery mildew\nin each respective trial") +
   xlab("Trial reference code") +
@@
 An example of this is if we inspect the six trials in which powdery mildew manifested 60 days or greater after planting (Trial references: AM1304, mung1819/01, mung1011/01, AM1303, AM1305 and BB1305).
-Of these trials, four directly compared single $Recommended$ fungicide applications and $Recommended_{plus}$ (AM1303, AM1305, BB1305 and mung1819/01), two of which (AM1305 and mung1819/01) produced at least one treatment $Recommended_{plus}$ treatment with a higher grain yield the $Recommended$ treatments.
-However, neither AM1305 or mung1819/01 neither contained $Recommended$ or $Recommended_{plus}$ treatments with higher mean yields than the no-spray control.
+Of these trials, four directly compared single $Recommended$ fungicide applications and $RecommendedPlus$ (AM1303, AM1305, BB1305 and mung1819/01), two of which (AM1305 and mung1819/01) produced at least one treatment $RecommendedPlus$ treatment with a higher grain yield the $Recommended$ treatments.
+However, neither AM1305 or mung1819/01 neither contained $Recommended$ or $RecommendedPlus$ treatments with higher mean yields than the no-spray control.
 This indicating there is likely no benefit to applying two fungicide applications when the disease manifests later than 60 days into the growing season. 
-Furthermore, the 2013 trials, Premer (AM1303), Goolhi (AM1305) Marys Mount (AM1304) and Millmerran (BB1305), reported a significant difference in powdery mildew severity between the fungicide treatments.
-However, none of the trials showed a significant difference in grain yield between treatments [@Millmerran2013, @premer2013, @Marysmount2013, @goolhi2013]. 
+Further the trials undertaken in 2013, such as Premer (AM1303), Goolhi (AM1305) Marys Mount (AM1304) and Millmerran (BB1305) reported a significant difference in powdery mildew severity between the fungicide treatments, however neither trial showed a significant difference in grain yield between treatments [@Millmerran2013, @premer2013, @Marysmount2013, @goolhi2013].
 Therefore, discretion is still required for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.
+The PowderyMildewMBM considers crop growth stage and weather, to assist decision making whether to spray or not to spray [@Diggle].
+
+PowderyMildewMBM also provides a cost-benefit analysis to growers for fungicide spray schedule scenarios.
+The user inputs weather, crop, and economic inputs into the DSS and the application returns the probability that one or two fungicide sprays would protect yields sufficiently to increase the net profit.
+The scope of the meta-analysis is limited to the timing of fungicide application and therefore we can not validate all the variables available in PowderyMildewMBM. 
+However our results validate the decision of the app developers not to recommend prophylactic fungicide applications. 
+If the powdery mildew is not observed in the crop the app advises the user to keep monitoring for disease.  
+<!-- Think about how to word this, that we are using this to validate the app: The findings of this meta-analysis confirm the recommendations that PowderyMildewMBM gives in most situations would be correct.
+-->
+<!-- I am finding it difficult to say that our findings confirm recommendations of the app, given the app does not advise on early late or recommended spray timing AND we don't investigate the differences in yield mitigations under the variables in the app (growth stage and weather) [Paul]-->
 
 Scouting the crop for powdery mildew might not be necessary during the warmer months of the season. 
-Data from the trials included in this experiment show regardless of crop sowing date, powdery mildew establishes on average in the month of March (Figure \@ref(fig:Figure2)), which marks the beginning of autumn in Australia.
+Data from the trials included in this experiment show regardless of crop sowing date, powdery mildew establishes on average in the month of March, which marks the beginning of autumn (Figure \@ref(fig:Figure2)).
 Considering the results of the meta-analysis, weekly inspections would be ideal to ensure timely fungicide applications if necessary. 
-Scouting at intervals greater than 12 -- 13 days, might risk crop losses if a spray schedule does not commence within aforementioned the spray window.
+Scouting at intervals greater than 12 - 13 days, might risk crop losses if a spray schedule does not commence within aforementioned the spray window.
 More work is needed to understand when "late" fungicide applications are too late.
@@
 We estimate the costs of applying tebuconazole fungicide at \$4.18 AU ha^-1^, if fungicide is purchased at \$15 / L [@Simfendorfer2011] and applications cost are \$2 per hectare [@QueenslandGovernment2019].
-This meta-analysis estimates average yield savings of between `r coef(PM_mv)[3]*1000` kg ha^-1^ ($Recommended$) and `r coef(PM_mv)[4]*1000` kg ha^-1^ ($RecommendedPlus$).
+The meta-analysis estimates average yield savings of between `r coef(PM_mv)[3]*1000` kg ha^-1^ ($Recommended$) and `r coef(PM_mv)[4]*1000` kg ha^-1^ ($RecommendedPlus$). 
 These average yield savings would save \$`r (coef(PM_mv)[3]*1000)` AU ha^-1^ for a single application at first sign and \$`r coef(PM_mv)[4]*1000` AU ha^-1^ if a follow-up application is made.
@@
 Excessive use of fungicides are highly likely to lead ongoing problems such as fungicide resistance.
-The evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with potential fungicide resistance in mind.
+*Podosphaera xanthii* is categorised by the Australian Fungicide resistance Action Committee (FRAC) as a "High risk" candidate to evolve fungicide resistance [@FRACrisk2019].
+Evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with potential fungicide resistance in mind.
 Powdery mildew is one such group of fungal pathogens with an extensive track record of rapidly developing fungicide resistance.
-*P. xanthii* is categorised by the Australian Fungicide Resistance Action Committee (FRAC) as a "High Risk" candidate to evolve fungicide resistance [@FRACrisk2019].
-*P.
-xanthii* has evolved resistance to benzimidazole within three years of its registration [@Peterson1973] and has evolved resistance to numerous fungicide classes, such as benzimidazoles, demethylation inhibitors, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines since [@Mcgrath2001] in cucurbits.
-In cereal crops, *Blumeria graminis* showed reduced sensitivity to strobilurins in 1998, two years after the fungicides began being used in Europe [@Chin2001].
+In cucurbits, *P.
+xanthii* evolved resistance to benzimidazole within three years of its registration [@Peterson1973] and has evolved resistance to numerous fungicide classes, such as benzimidazoles, demethylation inhibitors, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines since [@Mcgrath2001].
+In cereal crops *Blumeria graminis* showed reduced sensitivity to strobilurins in 1998, two years after the fungicides began being used in Europe [@Chin2001].
 
-According to FRAC it is important to alternate or mix fungicides with different modes of action to avoid fungicide resistance.
-At the time of writing, in Australia, only one fungicide is registered with the to treat powdery mildew in mungbean, Veritas/Custodia (200 g/L tebuconazole with 120 g/L azoxystrobin).
-This fungicide provides dual action: tebuconazole disrupts C-14 demethylase, required in sterol biosynthesis for cell membranes; and azoxystrobin, a quinone outside inhibitor.
+According to the Fungicide Resistance Action Committee (FRAC) it is important to alternate or mix fungicides with different modes of action to avoid fungicide resistance. 
+At the time of writing, in Australia one fungicide is registered with the to treat powdery mildew in mungbean, Veritas/Custodia (200 g/L tebuconazole with 120 g/L azoxystrobin).
+This fungicide provides dual action: tebuconazole disrupts C-14 demethylase, required in sterol biosynthesis for cell membranes; and azoxystrobin, a Quinone outside inhibitor.
 Quinone is required in cell metabolism and active in the mitochondrial complex III.
-However, FRAC recommends that applications of QoIs or strobilurins, singularly or as a mixture, should not be applied consecutively and should be alternated with a fungicide from a different group [@Brent2007].
-For mungbean, past experiments in the Northern Grains Region have shown some success with sulphur applications to control powdery mildew.
+However FRAC recommends that applications of QoIs or strobilurins, singularly or as a mixture, should not be applied consecutively and alternated with a fungicide from a different group [@Brent2007]. 
+For mungbean, past experiments have shown some success with sulphur applications to control powdery mildew. 
 Sulphur is a non-systemic protectant and thus provides an excellent option for rotation to limit the emergence of fungicide resistance.
 
-To extend the time that a fungicide remains effective against the target pathogen, the strategic use of the fungicide must be considered.
-Excessive fungicide sprays with a single active ingredient increase the selection pressure on the pathogen to evolve resistance [@Brent2007].
-If any strains of the pathogen with resistance to the fungicide are present in a population, regular use of the fungicide will increase its proportion in the population.
+To extend the time that a fungicide remains effective against the target pathogen, strategic use of the fungicide must be considered.
+Excessive fungicide sprays by a single active increase the selection pressure on the pathogen to evolve resistance [@Brent2007]. 
+If any strains of the pathogen with resistance to the fungicide are present in a population regular use of the fungicide will increase its proportion in the population. 
 Therefore, managing the disease with fungicides for the highest economic return is likely not to require eradication of the causal pathogen. 
@@
 
-# Conclusion
+Advising use of fungicide for disease control to protect yields should also consider the harm it may do to symbiotic relationships with microbiota. 
+While some nitrogen fixing symbiont show a level of tolerance to fungicides, all are detrimentally affected by increasing concentrations of fungicide leading to lower nodulation and biomass accumulation [@Ahemad2011, @Shahid2019].
+Therefore if a grower is relying on inoculating with rhizobia to help meet the crops nitrogen requirements, untimely and excessive applications of a systemic fungicide for powdery mildew control may actually reduce yield.
 
-To aid in making these decisions and devising a good strategy, DSS tools such as the PowderyMildewMBM consider crop growth stage and weather, to assist decision making whether to spray or not to spray [@Diggle] and can help users make an informed decision.
-Using these sorts of tools can reduce unnecessary and unprofitable fungicide applications, which may help lead to the development of fungicide resistance.
-
-<!-- I removed the part about inoculating mungbeans.
-This isn't common.
-They're lazy.
-Growers sometimes even look at adding N for them.
-I could be possibly persuaded to reinsert this section but it doesn't really fit the flow here, I don't think.
-If we need more text we might weave it in somehow.
--->
-
-To offer more benefit for future research, experiments should record physiological maturity of the crop throughout the season so "crop age" might be considered as a covariate in future analyses.
-<!-- I've commented this next line out, it seems to be incomplete:
-In cases where mungbean physiological maturity may not have been recorded the APSIM mungbean module [@RobertsonAPSIMlegume2002]. -->
+## Future work
+This meta-analysis provides a ballast for the direction of future powdery mildew research in mungbean. 
+However it does not provide enough certainty to when late fungicide applications would be too late to protect yield losses due to the disease. 
+Future experiments should take note of physiological maturity of the crop throughout the season so "crop age" might be considered as a covariate in future analyses.
+In cases where mungbean physiological maturity may not have been recorded the APSIM mungbean module [@RobertsonAPSIMlegume2002].
 
 Early detection of powdery mildew is vital for an effective fungicidal control response.
-Data from 26 studies in the Northern Grains Region indicate powdery mildew is likely to manifest on crops in the first month of autumn. 
+Data from the collection of 26 studies in the Northern Grain region, indicate powdery mildew is likely to manifest on crops in the first month of autumn. 
 This data together with additional observations may permit models to predict the likely onset of the disease given weather parameters, providing an early warning system for growers to scout their crop for signs of powdery mildew.
@@
 
-Currently, the recommendations that are provided appear to be the best practices for reducing losses due to mungbean powdery mildew.
-Care needs to be taken to adhere to them, especially no prophylactic sprays, to avoid the development of fungicide resistance in the powdery mildew pathogen populations.
-This meta-analysis provides a ballast for the direction of future powdery mildew control research in Australian mungbean.
-However, it does not provide certainty as to when late fungicide applications would be too late to protect yield losses due to the disease.
-Given the high value of mungbean at the farm-gate, further work could be done in this area that would benefit the Australian mungbean industry.
+# Conclusion
 

### 2020-08-07 paper/paper.Rmd
Fix Ngugi reference

--- 2020-08-07 paper/paper.Rmd
@@
 The sample variance was calculated from the raw data when available or the least squares statistic in the trial reports.
-Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 2.042 and the approach reported in Ngugi  [-@Ngugi2011].
+Sample variance for the 2012 Kingaroy study was calculated from the reported least squares statistic using a T-critical value of 2.042 and the approach reported in Ngugi [@Ngugi2011].
 The T-critical value was obtained from a t-distribution table using, 30 degrees of freedom and probability of $a = 0.05$.

### 2020-08-07 paper/paper.Rmd
Add Campbell and Madden AUDPC reference and agricolae

@@
 The end of season mean plot severity and date of first sign of disease were used to calculate the area under the disease progress curve (AUDPC) for each treatment.
-Additional powdery mildew mean plot severity observations made in-between these two observations were also included in the AUDPC calculation if they were available.
-AUDPC was calculated using the `agricolae` package in R [@agricolae2020].
+AUDPC was calculated as described by Campbell and Madden [@Campbell1990] using the `AUDPC()` function from the contributed R package 'agricolae', version 1.3-3 [@agricolae2020].
+
+Additional powdery mildew mean plot severity observations made in-between these two observations were also included in the AUDPC calculation where they were available.
 A categorical disease pressure factor was created by binning trials into two levels based on the mean AUDPC of the no spray control plot.

### 2020-08-07 paper/paper.Rmd
Quotes around packages

@@
 
-The data were analysed in the R statistical software environment, version 4.0.1, [@RCoreTeam2020] using two contributed meta-analysis packages, `metafor`, version 2-4.0, [@Viechtbauer2010] and `netmeta`, version 1.2-1, [@Rucker2020].
+The data were analysed in the R statistical software environment, version 4.0.1, [@RCoreTeam2020] using two contributed meta-analysis packages, 'metafor', version 2-4.0, [@Viechtbauer2010] and 'netmeta', version 1.2-1, [@Rucker2020].
 

### 2020-08-07 paper/paper.Rmd
Wordsmithing

@@
 
-Overall the meta-analysis indicated that with the exception of the $Early_{single}$ treatment all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure \@ref(fig:Figure1)).
+The meta-analysis indicated that with the exception of the $Early_{single}$ treatment all the the spray schedules were effective at protecting mungbean yields relative to the no spray controls (Figure \@ref(fig:Figure1)).
 Treatments which incorporated multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table \@ref(tab:Table3)).

### 2020-08-07 01_Meta-analysis_experiments.Rmd
use here::here() and reknit

@@
 ```{r MEsummary_Libraries, message=FALSE, echo=FALSE}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, leaflet, htmltools,schoolmath)
-source("R/import_data.R")
+if (!require("pacman"))
+   install.packages("pacman")
+pacman::p_load(tidyverse, kableExtra, leaflet, htmltools, schoolmath, here)
+source(here("R/import_data.R")
+)
 ```

### 2020-08-07 03_Prep_data.Rmd
amend T-crit value in 03_prep_data.rmd and re-Knit all subsequently effected files
Edit 03_Prep_data, lets to lets, clean up code chunks, etc.

--- 2020-07-03 03_Prep_data.Rmd
@@
 ```{r import_data}
-PM_MB_means <- read.csv("cache/1911_PM_MB_means&Ygains.csv")
+PM_MB_means <- read.csv(here("cache/1911_PM_MB_means&Ygains.csv"))
 
-source("R/same.R") # matches each element of a vector and does not return NAs
+source(here("R/same.R")) # matches each element of a vector and does not return NAs
 ```
@@
    select(!fungicide_ai) %>%
-   kable(caption = "Number of treatments for each trial and the error type reported", align = "c") %>%
+   kable(caption = "Number of treatments for each trial and the error type reported",
+         align = "c") %>%
    footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
@@
 ```{r LSD_2_Sampling_Variance}
-Tcrit <- 1.697 # 0.05 and DFw = 30
+Tcrit <- 2.042 # 0.05 and DFw = 30
 
@@
 ```
+
+### Mungbeans age and yield saved
+
+The time at which powdery mildew infects in the seasons and the age of the plant might affect the AUDPC and the loss in yield.
+Let's have a look at the age of each trial when each powdery mildew infected it.
+We will use the difference between `planting_date` and `first_sign_disease` as a proxy for crop maturity.
+
+```{r age_andYield}
+dat1 <- slimmer_PM_dat %>%
+   mutate(days2PM = first_sign_disease - planting_date) %>%
+   arrange(desc(days2PM)) %>%
+   select(
+      trial_ref,
+      year,
+      location,
+      spray_management,
+      days2PM,
+      grain_yield.t.ha,
+      yield_gain,
+      prop_yield_gain,
+      AUDPC_m,
+      D_pres,
+      PM_final_severity
+   )
+dat1
+```
+
+From these trials I am most interested in the experiments that directly compare `Recommended` with `Recommended_P_plus` and/or `Late` with `Late_plus`. 
+Therefore I will not inspect, `AM1304` (Marys Mount).
+
+We can see that the crops which were likely the most mature, did not show large yield gains, in particular:
+
+   * Hermitage 2019  
+   * Premer  
+   * Goolhi  
+   * Millmerran
+
+Let's look at this in a quick box plot. 
+We will only look at trials where powdery mildew set in at flowering which is approximately 60 days after planting.
+
+```{r ageBoxPlot}
+dat1 %>%
+   filter(days2PM >= 60) %>%
+   filter(spray_management != "control" &
+             trial_ref != "AM1304") %>%
+   group_by(trial_ref, spray_management) %>%
+   ggplot(aes(x = spray_management, y = yield_gain, colour = trial_ref)) +
+   geom_boxplot() +
+   geom_hline(yintercept = 0)
+```
+
+We can see in these experiments five experiments there is clearly no benefit to applying a second fungicide application.
+
+For completeness let's test this with powdery mildew infection commencing 40 - 60 days after planting, instead of greater than 60.
+
+```{r PM40_2_59_days}
+dat1 %>%
+   filter(days2PM < 60 &
+             days2PM >= 40) %>%
+   filter(spray_management != "control") %>%
+   group_by(trial_ref, spray_management) %>%
+   ggplot(aes(x = spray_management, y = yield_gain, colour = trial_ref)) +
+   geom_boxplot() +
+   geom_hline(yintercept = 0)
+```
+
+We can see here all four experiments benefited, on average, from more than one spray.
+
+Let's estimate the age of the crop based on crop maturity observations, we will use the `PM_MB_means` which include some observations of crop maturity.
+
+```{r whatAreTheAges}
+dat2 <- PM_MB_means %>%
+   mutate(
+      flower = lubridate::ymd(flowering_date) - lubridate::ymd(planting_date),
+      pod = lubridate::ymd(pod_fill_date) - lubridate::ymd(planting_date),
+      late_pod = lubridate::ymd(mid_late_pod_fill) - lubridate::ymd(planting_date)
+   ) %>%
+   select(location, year, flower, pod, late_pod) %>%
+   distinct() %>%
+   arrange(desc(flower))
+
+index1 <-
+   apply(dat2, 1 , function(X)
+      ! all(is.na(X[c("flower", "pod", "late_pod")])))
+
+dat2[index1, ]
+as.double(mean(dat2[index1, "flower"], na.rm = TRUE))
+as.double(mean(dat2[index1, "pod"], na.rm = TRUE))
+as.double(mean(dat2[index1, "late_pod"], na.rm = TRUE))
+```
+
+We can see that flowering and podding can be variable, and depend on the cumulative degree days.
+However, on average flowering starts `r as.double(mean(dat2[index1,"flower"], na.rm = TRUE))` days after sowing, podding starts `r as.double(mean(dat2[index1,"pod"], na.rm = TRUE))`, and late podding `r as.double(mean(dat2[index1,"late_pod"], na.rm = TRUE))`.

### 2020-08-07 paper/paper.Rmd

@@
 However, this description has changed over time and a second species has also been cited as causing the disease but not yet officially classified [@Kelly2019].
-While research outside of Australia refers to the causal agent of mungbean powdery mildew as *Erysiphe polygoni*.
+While research outside of Australia refers to the causal agent of mungbean powdery mildew as *Erysiphe polygoni* <!--Ref?-->. Here-after we will refer to the pathogen as *P. xanthii*
 
-The disease cycle of the pathogen can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, and which then disseminate to new infection sites [@PerezGarcia2009; @Sparks2017].
+*P. xanthii*, is an obligate biotroph, requiring a living plant host to survive and complete it's lifecycle [@PerezGarcia2009]. 
+To date, the sexual cycle that produces chasomthecia has not been observed in Australian mungbean, and the pathogen is suspected to reproduce asexually.
+*P.
+xanthii* has one of the widest host ranges of the powdery mildews, an ability which likely assists this pathogen to survive between mungbean seasons on alternative hosts which have not yet been identified in Australia.
+The disease cycle of the pathogen can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@PerezGarcia2009; @Sparks2017].
+Powdery mildew colonies of crowded conidophores can develop rapidly on leaf surfaces causing a loss in photosynthetic potential leading to reduced yield quantity and quality [@PerezGarcia2009]. 
+In severe cases leaves can become chlorotic and cause premature leaf senescence. 
 Weather conditions that favour the rapid development of the disease are cool temperatures between 22&nbsp;&deg; and 26&nbsp;&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
-To date, the sexual cycle that produces chasomthecia has not been observed in Australian mungbean.
-And while the powdery mildew pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified in Australia.
 

### 2020-08-07 paper/paper.Rmd
Correct missing "Introduction" section in paper
Edit headings and description of data included

--- 2020-08-07 paper/paper.Rmd
@@
 
+# Introduction
+
 Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown in south-east Asia for human consumption as an affordable source of protein [@Lambrides2007].
@@
 
-## Trial Criteria for Inclusion and Description
+## Criteria for Trial Data Inclusion
 
-The data for this study were obtained through studies that were conducted by the authors, FAIR (Findable, Accessible, Interoperable, Reusable) data available from GRDC Online Farm Trials <https://www.farmtrials.com.au/>, personal correspondence with colleagues and collaborating institutions.
+The data for this study were obtained through studies that were conducted by the authors, FAIR (Findable, Accessible, Interoperable, Reusable) data available from GRDC Online Farm Trials <https://www.farmtrials.com.au/>, and through personal correspondence with colleagues and collaborating institutions.
 Trial data were obtained in different formats with varying levels of information.

### 2020-08-07 paper/paper.Rmd
Add FAIR to list of abbreviations

--- 2020-08-07 paper/paper.Rmd
@@
 
-## Trial Criteria for Inclusion and Description
+## Criteria for Trial Data Inclusion
 
-The data for this study were obtained through studies that were conducted by the authors, FAIR (Findable, Accessible, Interoperable, Reusable) data available from GRDC Online Farm Trials <https://www.farmtrials.com.au/><!--Technically we did not use data from this location we obtained it from Lawrie Price-->, personal correspondence with colleagues and collaborating institutions.
+The data for this study were obtained through studies that were conducted by the authors, data that were the intellectual property of the University of Southern Queensland, and through personal correspondence.
 Trial data were obtained in different formats with varying levels of information.

### 2020-08-07 paper/paper.Rmd
NGA is Northern Grower Alliance, correct throughout

@@
   - short: NGA
-    long: Northern Growers Alliance
+    long: Northern Grower Alliance
   - short: USQ
@@
       "Queensland Department of Agriculture, Fisheries and Forestry",
-      "Northern Growers Alliance",
+      "Northern Grower Alliance",
       "University of Southern Queensland"
@@
 ```{r Figure2, echo=FALSE, fig.cap="Season length and first appearance of powdery mildew in each respective trial for fifteen mungbean trials conducted in the Grains Research and Developmet (GRDC) Northern Grains Region of eastern Australia to evaluate the most effective time of fungicide application to save yield from powdery mildew infection.
-Trials were conducted from 2001 to 2019 by Queensland Department of Agriculture, Fisheries and Forestry, Northern Growers Alliance and University of Southern Queensland and coalated for meta-analysis."}
+Trials were conducted from 2001 to 2019 by Queensland Department of Agriculture, Fisheries and Forestry, Northern Grower Alliance and University of Southern Queensland and coalated for meta-analysis."}
 PM_Mdat %>%
@@
 The Queensland Department of Agriculture, Fisheries and Forestry (DAF). 
-The National Growers association and Lawrie Price for contributing data.
+The Northern Grower Alliance and Lawrie Price for contributing data.
 The Grains Research and Development Corporation who funded this research.

### 2020-08-10 vignette/191115_PMMB_DataWrangling_PM.Rmd
Note added about missing trials
remove checks from header

@@
 # Data wrangling
-This file is not complete and there are a number of things that need checking
-   - Mean squares are only calculated for the triazoles and controls
-   - If the years for each trial are input correctly
-   - If the disease and yield errors are calculated and that they are shuffled correctly into the data frame
-   - AUDPC needs to be checked for starting dates and if trials have been omitted
-   - Check that what is generated from this file matches the main file and update
-   - write.csv should have row.names = FALSE
+## Non-wrangled trials
+
+Data from the three follow trials were input manually from either PDF or word files.  
+   - Gatton 2012  
+   - Kingaroy 2012  
+   - Emerald 2016
 

### 2020-08-10 02_Import_and_FormatData.Rmd
rename files and delete unnecessary files/chapters

--- 2020-07-28 02_Preliminary_analysis.Rmd
@@
                lme4,
-               kableExtra)
-source("R/import_data.R")
+               kableExtra,
+               here)
+source(here("R/import_data.R"))
 if (!require("theme.usq"))

### 2020-08-10 04_Prep_data.Rmd
rename files and delete unnecessary files/chapters

--- 2020-02-11 04_Prep_data.Rmd
@@
+# Prepare data for meta-analysis
+
 ## Set environment and import data
 
-```{r load_libraries}
-library(dplyr)
-library(readr)
-library(kableExtra)
-library(ggplot2)
-library(agricolae)
+```{r load_libraries, include=FALSE}
+if (!require("pacman"))
+   install.packages("pacman")
+pacman::p_load(tidyverse, kableExtra, agricolae, lme4, here)
+if (!require("theme.usq"))
+   devtools::install_github("adamhsparks/theme.usq")
+library(theme.usq)
+theme_set(theme_usq()
+)
 ```
@@
 ```{r import_data}
-source("R/import_data.R")
-PM_MB_means <- import_data()
+PM_MB_means <- read.csv(here("cache/1911_PM_MB_means&Ygains.csv"))
 
-# Calculate AUDPC using final severity and first sign of disease - 7 days
-source("R/AUDPC_for_single_obs.R") 
+source(here("R/same.R")) # matches each element of a vector and does not return NAs
 ```
@@
 ## Standardising sample variance  
-Meta-analyses use variance from the data to calculate the effect sizes. The type of variance needs to be the same across all the data incorporated in the meta-analysis.
+Meta-analyses use variance from the data to calculate the effect sizes.
+The type of variance needs to be the same across all the data incorporated in the meta-analysis.
 
-We are narrowing the meta-analysis to only include demethylation inhibitors, tebuconazole and propiconazole. Within studies which have used these fungicides, what type of error was reported?
+We are narrowing the meta-analysis to only include treatments using demethylation inhibitors, tebuconazole and propiconazole.
+Let's look at what type of statistical error was reported for the trials that used these fungicides.
 
@@
    filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole",
-         row_spacing == 0.75) %>%
-   group_by(trial_ref, location, Y_error_type, fungicide_ai) %>%
-   summarise(DMI_trts = length(Y_error_type))%>%
-   arrange(Y_error_type)%>%
-   kable(caption = "Number of treatments for each trial and the error type reported") %>%
-   kable_styling(fixed_thead = T) %>%
+             fungicide_ai == "propiconazole") %>%
+   group_by(trial_ref, location, year , Y_error_type, fungicide_ai) %>%
+   summarise(DMI_treatments = length(Y_error_type)) %>%
+   arrange(Y_error_type) %>%
+   select(!fungicide_ai) %>%
+   kable(caption = "Number of treatments for each trial and the error type reported",
+         align = "c") %>%
    footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
-
 ```
@@
 The experiment summaries report either standard deviation, least square differences or no error term (`NA`). 
-Below we will convert LSD and standard deviation to sample variance.
-In addition, we need to impute variances for the trials which did not report any form of variance (`NA`).
+First we will convert LSD and standard deviation to sample variance.
+Then we will impute variances for the trials, which did not report any form of variance (`NA`).
 
@@
 
+First let's get a list the of trials that reported LSD.
+
 ```{r all_LSD_trials}
 Trials <- PM_MB_means %>%
-   filter(
-          Y_error_type == "lsd (P=0.05)") %>%
+   filter(Y_error_type == "lsd (P=0.05)") %>%
    select(trial_ref) %>%
    distinct()
+Trials
 ```
 
-The following code attempts to convert 'least square differences' (LSD) to sampling variance as per the method in [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
-Ideas for using a T-critical value of 1.697 came from reading a [statisics-how-to website](https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/).
-A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted where 30 degrees of freedom within experiment was used to find the 'T-crit' value of 1.697.
+Let's use this list of trials to subset the data and calculate sampling variances.
+
+We will follow the method of converting 'least square differences' (LSD) to sampling variance reported by [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
+A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted to select the T-crit value in the equation. 
+Our data contained 30 degrees of freedom which equates to a 'T-crit' value of 1.697.
 
@@
 
-```{r LSD_2_Sampling Variance}
+`Tcrit` is the T critical value for which there is significant difference between two groups.
+This value is the same for both trials "mung1112/01" and "mung1112/02".
 
-for (Trial2012 in Trials$trial_ref) {
-   Tcrit <-
-      1.697  # 0.05 and DFw = 30 # T critical value for which there is significant difference between two groups; This value is the same for both trials "mung1112/01" and "mung1112/02"
+```{r LSD_2_Sampling_Variance}
+Tcrit <- 2.042 # 0.05 and DFw = 30
+
+for (i in Trials$trial_ref) {
    DFw <-
-      sum(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates) -
-      length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates) # degrees of freedom within groups
+      sum(PM_MB_means[PM_MB_means$trial_ref == i, ]$replicates) -
+      length(PM_MB_means[PM_MB_means$trial_ref == i, ]$replicates) # degrees of freedom within groups
 
    LSD <-
-      PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error[1]
+      PM_MB_means[PM_MB_means$trial_ref == i, ]$yield_error[1]
 
    V_yield <-
-      (PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[1] * (LSD /
-                                                                            Tcrit) ^ 2) / 2 # method - Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
+      (PM_MB_means[PM_MB_means$trial_ref == i, ]$replicates[1] * 
+          (LSD / Tcrit) ^ 2) / 2 
+   # method - Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
 
-   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates)) {
+   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates)) {
       if (j == 1) {
          Sv <-
-            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates))
+            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates))
       } # reset Sv vector if this is the first loop
 
-      ###############################################3
-      # ___ Adjusting formula to suit our data_______
-      #
-      #  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$replicates[j] *
-      #                   PM_MB_means[PM_MB_means$trial_ref == Trial2012,]$grain_yield.t.ha[j])
-      # Balance equation
-      # Sv[j] = V_yield / 
-      #    (PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j] *
-      #       as.numeric(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$grain_yield.t.ha[j])^2)
-      # #################################################################
-
       Sv[j] = V_yield /
-         PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j]
-
-      # Sv[j] = MSE / 
-      #    (PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$replicates[j] *
-      #       as.numeric(PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$grain_yield.t.ha[j])^2)
-      #
-
-      ### -> This formula should be V = (n * (LSD/1.96)^2) / 2
+         PM_MB_means[PM_MB_means$trial_ref == i,]$replicates[j]
 
@@
 
-   # and replacing the values in the dataset
-
-   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error <-
+   # Replace the values in the dataset
+   PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <-
       Sv
-   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$Y_error_type <-
+   PM_MB_means[PM_MB_means$trial_ref == i,]$Y_error_type <-
       "SamplingVariance"
-
 }
@@
 
-   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error[j]) ^
-      2
+   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error[j]) ^ 2
 }
@@
    "SamplingVariance"
-
 ```
 
-## Yield saving  
-Yield saving and Yield saving proportional to the control.
+### Check variance of data-set
+Our data currently uses sample variance to define the yield error.
+We should expect that when yield increases so does the variance.
+Let's quickly plot this to check.
 
-Data from `r length(PM_MB_means$trial_ref)` trials were collected and the means of each treatment calculated (`R/Cleaning historical data.R`).
-These data were combined into one file `1902 powdery mildew-Mungbean - Collated means.csv`.
+```{r Var_mean_sqaures}
+# redefine sample variance calculated from mean square
+PM_MB_means$vi <-
+   PM_MB_means$Y_Msquare /
+   (PM_MB_means$n)
 
-```{r Calculate_yield-gains}
-PM_MB_means$grain_yield.t.ha. <-
-   as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data
+PM_MB_means %>%
+   ggplot(aes(x = grain_yield.t.ha., y = vi)) +
+   geom_point()
+```
 
-for (i in unique(PM_MB_means$trial_ref)) {
-   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
+We see here that the sample variance generally decreases or has no association with the grain yield.
+This might be due to the unpredictable nature of mungbeans, however going forward we will use mean squares, which defines between trial variation and is the more generic error term.
 
-   if (any(is.na(unique(dat1$row_spacing)))) {
-      warning(
-         paste(
-            unique(dat1$trial_ref),
-            "at",
-            unique(dat1$location),
-            "in year",
-            unique(dat1$year),
-            "has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n"
-         )
-      )
-      next()
-   }
-
-   for (j in unique(dat1$row_spacing)) {
-      dat2 <- dat1[dat1$row_spacing == j, ]
-      controlY <-
-         mean(dat2[dat2$fungicide_ai == "control", "grain_yield.t.ha."])
-
-      dat2$yield_gain <- dat2$grain_yield.t.ha. - controlY
-      dat2$prop_YG <- dat2$yield_gain  /  controlY
-
-      dat2[dat2$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
-         NA
-
-      dat1[dat1$row_spacing == j, ] <- dat2
-   }
-   PM_MB_means[PM_MB_means$trial_ref == i, ] <- dat1
-}
-
-# ____________________________________________
-# calculate yield gain and prop_yield gain for experiments with no row spacing data
-
-dat1 <- PM_MB_means[PM_MB_means$trial_ref == "AM1303", ]
-
-controlY <-
-   mean(dat1[dat1$fungicide_ai == "control", "grain_yield.t.ha."])
-
-dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
-dat1$prop_YG <- dat1$yield_gain / controlY
-dat1[dat1$fungicide_ai == "control", c("yield_gain", "prop_YG")] <- c(NA,NA)
-PM_MB_means[PM_MB_means$trial_ref == "AM1303", ] <- dat1
-
-write.csv(PM_MB_means,
-          "data/1911_PM_MB_means&Ygains.csv")
+```{r Var_MeanSquarePlot}
+PM_MB_means %>%
+   ggplot(aes(x = grain_yield.t.ha., y = Y_Msquare)) +
+   geom_point()
 ```
@@
 ## Reduce data set to required variables
-Lets tidy up the data set into a data frame of only the variables which are required for the analysis.
+
+Let's tidy up the data set into a data frame of only the variables, which are required for the analysis.
 
@@
 Then calculate fungicide application timing variables relative to the first sign of disease.
-Entries with NA in the grain yield or powdery mildew severity are also removed from the data.
+Entries with `NA` in the grain yield or powdery mildew severity are also removed from the data.
 
 ```{r clustered_fungicide_applications}
-source("R/slimming_PM_dat.R") # see R script for the code which reduces the data.
+source("R/slimming_PM_dat.R") # see R script for the code, which reduces the data.
 
@@
 These categorical variables are named:
+
    - **Early**: First fungicide application was prior to first sign of disease.
+
    - **Recommended**: First fungicide application was applied on the day powdery mildew was observed, or within three days of first sign.
+
    - **Late**: First fungicide application was four or more days after first sign of disease being observed. 
-
-Follow up fungicide applications (cluster_2 and cluster_3) were also categorised as either, early, recommended or late.
+Follow up fungicide applications (cluster_2 and cluster_3) were also categorised as either early, recommended or late.
 
 ```{r cluster}
-
 slim_PM_dat %<>%
@@
    )
-
 ```
 
-Lets look at these clusters to see where we have the most degrees of freedom.
+Let's look at these clusters to see where we have the most degrees of freedom.
 
 ```{r cluster_clusters}
+clusters <-
+   unique(slim_PM_dat[c("cluster_1", "cluster_2", "cluster_3")])
 
-clusters <- unique(slim_PM_dat[c("cluster_1","cluster_2","cluster_3")])
+for (i in 1:nrow(clusters)) {
+   if (i == 1) {
+      clusters$n <- NA
+      clusters$n_x_trial <- NA
+   }
 
-for(i in 1:nrow(clusters)){
-   if(i == 1){clusters$n <- NA
-   clusters$n_x_trial <- NA}
+   clusters[i, "n"] <-
+      nrow(slim_PM_dat[same(slim_PM_dat$cluster_1, clusters[i, "cluster_1"]) &
+                          same(slim_PM_dat$cluster_2, clusters[i, "cluster_2"]) &
+                          same(slim_PM_dat$cluster_3, clusters[i, "cluster_3"]),])
 
-   clusters[i,"n"] <- nrow(slim_PM_dat[slim_PM_dat$cluster_1 == clusters[i,"cluster_1"] &
-                                          slim_PM_dat$cluster_2 == clusters[i,"cluster_2"] &
-                                          slim_PM_dat$cluster_3 == clusters[i,"cluster_3"],
-                                       ])
-
-   clusters[i,"n_x_trial"] <- length(unique(slim_PM_dat[slim_PM_dat$cluster_1 == clusters[i,"cluster_1"] &
-                                          slim_PM_dat$cluster_2 == clusters[i,"cluster_2"] &
-                                          slim_PM_dat$cluster_3 == clusters[i,"cluster_3"],
+   clusters[i, "n_x_trial"] <-
+      length(unique(slim_PM_dat[same(slim_PM_dat$cluster_1, clusters[i, "cluster_1"]) &
+                                   same(slim_PM_dat$cluster_2, clusters[i, "cluster_2"]) &
+                                   same(slim_PM_dat$cluster_3, clusters[i, "cluster_3"]),
                                 "trial_ref"]))
@@
 knitr::kable(clusters)
-
 ```
 
-From this we can see that there are 16 different cluster combinations, which would make the analysis too difficult. I will reduce this to 6 levels within one variable.
+From this we can see that there are 16 different cluster combinations, which would make the analysis too difficult. We will reduce this to 6 levels within one variable.
 
-Single sprays either early, recommended timing or late.
+Single sprays of either:
 
-Two sprays or more where the first spray was either early, recommended timing, or late.
+   a) early,
+
+   b) recommended timing,
+
+   c) late.
+
+Two or more sprays where the first spray was either:
+
+   d) early,
+
+   e) recommended timing,
+
+   f) late.
 
 ```{r simple_clusters}
-
 slim_PM_dat <- slim_PM_dat %>%
@@
             !is.na(fungicide_application_2) ~ "Recommended_plus",
-      fungicide_timing_1 >= 4 ~ "Late_plus",
+         fungicide_timing_1 >= 4 &
+            !is.na(fungicide_application_2) ~ "Late_plus",
          TRUE ~ "Other"
@@
 slim_PM_dat[slim_PM_dat$fungicide_ai == "control",
-            c("fungicide_timing_1", "fungicide_timing_2", "fungicide_timing_3",
+            c(
+               "fungicide_timing_1",
+               "fungicide_timing_2",
+               "fungicide_timing_3",
                "spray_management"
             )] <- "control"
-
-table(slim_PM_dat$spray_management)
-
-table(slim_PM_dat$spray_management,slim_PM_dat$fungicide_timing_1)
-
-```
-There are few 'Early_plus' and 'late' treatments, these treatments therefore will have too few comparisons with other treatments in the meta-analysis to be provide accurate results.
-Therefore we will remove 'Early_plus' and 'Late' from the analysis.
-
-```{r simpler_clusters_REMOVE}
-
-slimmer_PM_dat <- slim_PM_dat[slim_PM_dat$spray_management != "Late" & 
-               slim_PM_dat$spray_management != "Early_plus",]
-
-write.csv(slimmer_PM_dat, file = "data/slimmer_PM_clusterdat.csv", row.names = FALSE)
 ```
 
-Our data currently uses sample variance to define the yield error. We should expect that when yield increases so does the variance. Lets quickly plot this to check.
+Now to view the number break-down of the `spray_management` treatments
 
-```{r Var_mean_sqaures}
-# redefine sample variance calculated from mean square
-slimmer_PM_dat$vi <- 
-   slimmer_PM_dat$Y_Msquare / 
-   (slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha ^ 2)
-
-slimmer_PM_dat %>%
-   ggplot(aes(x= grain_yield.t.ha, y = vi))+
-   geom_point()
+```{r tableSprayManagement}
+table(slim_PM_dat$spray_management)
 ```
 
-We see here that the sample variance generally decreases or has no association with the grain yield.
-This might be due to the unpredictable nature of mungbeans, however going forward we will use mean squares which defines between trial variation and is a the more generic error term.
+There are few 'Early_plus' treatments, these treatments therefore will have too few comparisons with other treatments in the meta-analysis to provide accurate results.
+Therefore we will remove 'Early_plus' from the analysis.
 
-```{r Var_MeanSquarePlot}
-slimmer_PM_dat %>%
-   ggplot(aes(x= grain_yield.t.ha, y = Y_Msquare))+
-   geom_point()
-
+```{r simpler_clusters_remove}
+slimmer_PM_dat <-
+   slim_PM_dat[slim_PM_dat$spray_management != "Early_plus", ]
 ```
 
-```{r Yield_vs_AUDPC}
+****
 
-slimmer_PM_dat %>%
-   filter(AUDPC_m <=280)%>%
-#   filter(fungicide_ai == "control")%>%
-   ggplot(aes(x = grain_yield.t.ha, y = AUDPC_m))+
-   geom_point()
+## Test dose effect
 
-summary(lm(grain_yield.t.ha ~ AUDPC_m, data = subset(slimmer_PM_dat, AUDPC_m <= 280)))
+Earlier we noted there were different doses of propiconazole, which might influence our analysis.
+Let's check this by comparing a linear mixed effect model including and excluding dose.
+We already have a factor breaking down the dose in the `trial` variable.
+Let's make a new one without dose.
 
-plot(grain_yield.t.ha. ~ AUDPC_m,data = subset(PM_MB_means, AUDPC_m <= 280) )
-abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = subset(PM_MB_means, AUDPC_m <= 280)))
+```{r dose_test}
+slimmer_PM_dat$trial_noDose <- paste(slimmer_PM_dat$trial_ref, slimmer_PM_dat$year,
+                 slimmer_PM_dat$location,slimmer_PM_dat$host_genotype,
+                 slimmer_PM_dat$row_spacing,sep = "_")
 
-sm2lg <- PM_MB_means%>%
-   group_by(trial_ref)%>%
-   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE))%>%
-   arrange(TY)
+cbind(Dose = head(slimmer_PM_dat$trial),
+      NoDose = head(slimmer_PM_dat$trial_noDose)) %>%
+   kable()
+```
 
-for(i in sm2lg$trial_ref){
-   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
-   if(any(is.na(dat1$grain_yield.t.ha.))){next}
-   if(any(is.na(dat1$AUDPC_m))){next}
+Let's test the dose effect in a basic linear mixed effect model.
 
-plot(grain_yield.t.ha. ~ AUDPC_m, 
-     data = dat1, main = paste(dat1$location[1],(dat1$year[1])),
-     ylim = c(0,max(PM_MB_means$grain_yield.t.ha., na.rm = TRUE)), 
-     xlim = c(0,max(PM_MB_means$AUDPC_m, na.rm = TRUE)))
-abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = dat1))
-points(grain_yield.t.ha. ~ AUDPC_m, data = dat1[dat1$fungicide_ai == "control",], col = "red")
+```{r dose_lmer}
+m1 <-
+   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
+           (1 | trial),
+        data = slimmer_PM_dat)
 
+m2 <-
+   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
+           (1 | trial_noDose),
+        data = slimmer_PM_dat)
+
+anova(m1, m2)
+```
+
+Using the model without dose produces a lower AIC, however we should accept the data with dose as there is a significant difference between the models and we should accept the more complicated model `m1`.
+We will retain dose as a variable inside the `trial` factor.
+
+```{r saveDat}
+slimmer_PM_dat <-
+   slimmer_PM_dat[, colnames(slimmer_PM_dat) != "trial_noDose"] #remove second trial column
+```
+
+## Disease pressure factor
+
+We may wish to investigate the impact of spray management in mitigating the yield loss through the effect on the disease pressure.
+We will set a categorical variable to indicate the amount of disease pressure in the trial, which will be evaluated on the control plot.
+We will create two categories, `lowD` and `highD`.
+We will use the median `AUDPC` to separate the trials into these two groups.
+
+```{r DiseasePressure}
+slimmer_PM_dat$D_pres <- NA_character_
+
+Trial_Dpress <- slimmer_PM_dat %>%
+   group_by(trial_ref) %>%
+   filter(fungicide_ai == "control") %>%
+   summarise(AUDPC_C = mean(AUDPC_m, na.rm = TRUE))
+
+median_AUDPC <-
+   median(as.vector(Trial_Dpress$AUDPC_C), na.rm = TRUE)
+median_AUDPC
+
+write.csv(median_AUDPC, here("cache/median_AUDPC_C.csv"), row.names = FALSE)
+
+sort(Trial_Dpress$AUDPC_C)
+
+for (i in unique(slimmer_PM_dat$trial_ref)) {
+   if (is.na(Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"])) {
+      next()
    }
 
+   if (Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"] < median_AUDPC)
+   {
+      slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <- "lowD"
+   } else{
+      if (Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"] >= median_AUDPC) {
+         slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <- "highD"
+      } else{
+         slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <-
+            NA_character_
+      }
+   }
+}
 ```
 
-This sequence of graphs show that AUDPC and disease incidence does not impact on yields if the season is a low yielding, ie lower than 1 tonne per hectare.  
-The higher the yield the greater greater the influence on the disease on the yield especially if the crop is high yielding and a large AUDPC.
+Let's have a quick look to examine whether trials with high disease pressure sustain a greater yield loss.
 
-```{r delete_this_chunk}
-PM_MB_means$infected_days <- as.numeric(PM_MB_means$harvest_date - PM_MB_means$first_sign_disease)
+```{r plot_disease_pressure}
+slimmer_PM_dat %>%
+   ggplot(aes(x = D_pres, y = grain_yield.t.ha))+
+   geom_boxplot() +
+   xlab("Disease pressure") +
+   ylab("Grain yield (t/ha)")
+```
 
-plot(AUDPC_m ~ infected_days, data = PM_MB_means)
-plot(grain_yield.t.ha. ~ infected_days, data = PM_MB_means)
+From this plot we see that in the trials with high disease pressure tended to produce lower yields. 
+There are `r length(unique(slimmer_PM_dat[is.na(slimmer_PM_dat$D_pres),"trial_ref"]))` trials that contained no data for AUDPC and thus produced `NA` values.
 
-PM_MB_means$harvest_date - PM_MB_means$first_sign_disease
-PM_MB_means[0 > as.Date(PM_MB_means$harvest_date, format = "%Y-%m-%d")-
-as.Date(PM_MB_means$first_sign_disease, format = "%Y-%m-%d"),]
+## Row spacing
 
-# correct dates (this has been done in wrangle file but not updated yet in the data-set)
-PM_MB_means[PM_MB_means$trial_ref == "mung1516/01", "harvest_date"] <- as.Date("2016-05-06", format = "%Y-%m-%d")
-PM_MB_means[PM_MB_means$trial_ref == "mung1516/01", "final_assessment"] <- final_assessment = as.Date("2016-04-15", format = "%Y-%m-%d")
+We may want to consider row spacing in the trials.
+However one of the locations has `NA` as the row spacing.
+For now let's assign the most used row spacing of 0.33 m as an approximation so the model can analyse this as a continuous variable. 
+If we decide to use the row_spacing column as a factor in the final model we will need to remove this approximation.
 
-#curiouspw10-
+```{r assign_row_spacing_missing}
+slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),]
+slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),"row_spacing"] <- 0.33
+
+write.csv(slimmer_PM_dat, file = here("cache/slimmer_PM_clusterdat.csv"), row.names = FALSE)
 ```
+
+### Mungbeans age and yield saved
+
+The time at which powdery mildew infects in the seasons and the age of the plant might affect the AUDPC and the loss in yield.
+Let's have a look at the age of each trial when each powdery mildew infected it.
+We will use the difference between `planting_date` and `first_sign_disease` as a proxy for crop maturity.
+
+```{r age_andYield}
+dat1 <- slimmer_PM_dat %>%
+   mutate(days2PM = first_sign_disease - planting_date) %>%
+   arrange(desc(days2PM)) %>%
+   select(
+      trial_ref,
+      year,
+      location,
+      spray_management,
+      days2PM,
+      grain_yield.t.ha,
+      yield_gain,
+      prop_yield_gain,
+      AUDPC_m,
+      D_pres,
+      PM_final_severity
+   )
+dat1
+```
+
+From these trials I am most interested in the experiments that directly compare `Recommended` with `Recommended_P_plus` and/or `Late` with `Late_plus`. 
+Therefore I will not inspect, `AM1304` (Marys Mount).
+
+We can see that the crops which were likely the most mature, did not show large yield gains, in particular:
+
+   * Hermitage 2019  
+   * Premer  
+   * Goolhi  
+   * Millmerran
+
+Let's look at this in a quick box plot. 
+We will only look at trials where powdery mildew set in at flowering which is approximately 60 days after planting.
+
+```{r ageBoxPlot}
+dat1 %>%
+   filter(days2PM >= 60) %>%
+   filter(spray_management != "control" &
+             trial_ref != "AM1304") %>%
+   group_by(trial_ref, spray_management) %>%
+   ggplot(aes(x = spray_management, y = yield_gain, fill = trial_ref)) +
+   geom_boxplot() +
+   scale_fill_usq() +
+   geom_hline(yintercept = 0)
+```
+
+We can see in these experiments five experiments there is clearly no benefit to applying a second fungicide application.
+
+For completeness let's test this with powdery mildew infection commencing 40 - 60 days after planting, instead of greater than 60.
+
+```{r PM40_2_59_days}
+dat1 %>%
+   filter(days2PM < 60 &
+             days2PM >= 40) %>%
+   filter(spray_management != "control") %>%
+   group_by(trial_ref, spray_management) %>%
+   ggplot(aes(x = spray_management, y = yield_gain, fill = trial_ref)) +
+   geom_boxplot() +
+   scale_fill_usq() +
+   geom_hline(yintercept = 0)
+```
+
+We can see here all four experiments benefited, on average, from more than one spray.
+
+Let's estimate the age of the crop based on crop maturity observations, we will use the `PM_MB_means` which include some observations of crop maturity.
+
+```{r whatAreTheAges}
+dat2 <- PM_MB_means %>%
+   mutate(
+      flower = lubridate::ymd(flowering_date) - lubridate::ymd(planting_date),
+      pod = lubridate::ymd(pod_fill_date) - lubridate::ymd(planting_date),
+      late_pod = lubridate::ymd(mid_late_pod_fill) - lubridate::ymd(planting_date)
+   ) %>%
+   select(location, year, flower, pod, late_pod) %>%
+   distinct() %>%
+   arrange(desc(flower))
+
+index1 <-
+   apply(dat2, 1 , function(X)
+      ! all(is.na(X[c("flower", "pod", "late_pod")])))
+
+dat2[index1,]
+as.double(mean(dat2[index1, "flower"], na.rm = TRUE))
+as.double(mean(dat2[index1, "pod"], na.rm = TRUE))
+as.double(mean(dat2[index1, "late_pod"], na.rm = TRUE))
+```
+
+We can see that flowering and podding can be variable, and depend on the cumulative degree days.
+However, on average flowering starts `r as.double(mean(dat2[index1,"flower"], na.rm = TRUE))` days after sowing, podding starts `r as.double(mean(dat2[index1,"pod"], na.rm = TRUE))`, and late podding `r as.double(mean(dat2[index1,"late_pod"], na.rm = TRUE))`.

### 2020-08-10 05_MetaAnalysis.Rmd
rename files and delete unnecessary files/chapters

--- 2020-02-17 05_MetaAnalysis.Rmd
@@
-```{r MEsummary_Libraries2, message=FALSE}
-# install.packages("tidyverse")
-# install.packages("devtools")
-# devtools::install_github("https://github.com/PaulMelloy/bomrang")
-# devtools::install_github("https://github.com/adamhsparks/theme.usq", dependencies = TRUE)
-# install.packages("lme4")
+---
+output: html_document
+editor_options: 
+  chunk_output_type: inline
+---
 
-library(RColorBrewer)
-library(tidyverse)
+```{r MEsummary_Libraries2, message=FALSE, include=FALSE}
+if (!require("pacman"))
+   install.packages("pacman")
+pacman::p_load(tidyverse,
+               kableExtra,
+               bomrang,
+               lme4,
+               RColorBrewer,
+               metafor,
+               here,
+               netmeta,
+               multcomp)
+
+if (!require("theme.usq"))
+   devtools::install_github("adamhsparks/theme.usq")
 library(theme.usq)
-library(bomrang)
-library(lme4)
-library(kableExtra)
+theme_set(theme_usq())
+source(here("R/reportP.R"))
 
 # Data
-slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
+slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv"
+)
 ```
 
-# Meta-analysis
-## Grain yield meta-analysis
+# Grain yield meta-analysis
 
-```{r LME_slimmer_cluster_disease_mod}
+Let's get started with the analysis by first finding the best model fit that answers our research question.
 
-m8 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) +
-              (factor(spray_management) | trial_ref), 
-           data = slimmer_PM_dat)
+> Which spray management scenario provides the greatest yield protection from powdery mildew.
 
-m9 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + 
-              (factor(spray_management) | trial_ref), 
-           data = slimmer_PM_dat)
+To do this, in our model:
 
-m10 <- lmer(log(grain_yield.t.ha*1000) ~ 
-               (factor(spray_management) | trial_ref), 
-           data = slimmer_PM_dat)
+   - Grain yield is our response variable (t / ha)
 
-m11 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + 
-              (1 | trial_ref), 
-           data = slimmer_PM_dat)
+   - Trial, which resolves combinations of categorical variables: year, location, row spacing, fungicide dose and cultivar; is set as a random intercept
 
-anova(m8,m9) # m9 is significantly better model
-anova(m9,m10) # m9 is significantly better model
-anova(m9,m11) # m11 is a simpler model which is no different to m9
+   - We will test spray management (our treatment) as a fixed effect and random interactive term to trial
 
-summary(m9)
+First, how well does the data compare across the trial years and trials?
+
+```{r table_of_nTreatments}
+# class spray_management as a factor and reorder them for the plot
+slimmer_PM_dat$spray_management <-
+   factor(slimmer_PM_dat$spray_management, rev(
+      c(
+         "control",
+         "Early",
+         "Recommended",
+         "Recommended_plus",
+         "Late",
+         "Late_plus"
+      )
+   ))
+
+ggplot(slimmer_PM_dat, aes(x = as.factor(year), fill = spray_management)) +
+   geom_bar(position = "dodge2") +
+   scale_fill_usq(name = "Spray Management") +
+   xlab("Year")
+
+kable(
+   table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year),
+   align = rep('c', 8),
+   caption = "Which treatments and how many treatments are represented in each year"
+) %>%
+   kable_styling(
+      "striped",
+      fixed_thead = TRUE,
+      full_width = FALSE,
+      position = "center"
+   )
+
+```
+<!-- I don't like this graph, it is hard to read given that different widths don't translate to anything meaningful -->
+
+Treatments `Late_plus` and `Early` don't have very good comparison to other treatments.
+
+Let's visualise the spread of data in each treatments with box-plots.
+
+```{r treatment_means_plot}
+slimmer_PM_dat %>%
+   ggplot(
+      aes(
+         y = grain_yield.t.ha,
+         x = spray_management,
+         fill = spray_management,
+         colour = spray_management
+      )
+   ) +
+   geom_boxplot(alpha = 0.25) +
+   geom_jitter(width = 0.1, alpha = 0.5) +
+   labs(x = "Spray management variable",
+        y = "Grain yield (t/Ha)",
+        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
+   theme(plot.title = element_text(hjust = 0.5)) +
+   geom_hline(yintercept = 0, linetype = 2) +
+   scale_fill_usq() +
+   scale_colour_usq() +
+   coord_flip() +
+   guides(fill = FALSE, color = FALSE)
+```
+
+There seems like little difference between the treatments, with exception of `Late_plus`.
+Let's do this plot again, but let's look at the proportional mean difference between each treatment and the no spray control for each study, this should reduce variation in yield due between trials.
+
+```{r plot_yieldProportion}
+slimmer_PM_dat %>%
+   filter(spray_management != "control") %>% 
+   ggplot(
+      aes(
+         y = prop_yield_gain,
+         x = spray_management,
+         fill = spray_management,
+         colour = spray_management
+      )
+   ) +
+   geom_boxplot(alpha = 0.25) +
+   geom_jitter(width = 0.1, alpha = 0.5) +
+   labs(x = "Spray management variable",
+        y = "Grain yield (t/Ha)",
+        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
+   theme(plot.title = element_text(hjust = 0.5)) +
+   geom_hline(yintercept = 0, linetype = 2) +
+   scale_fill_usq() +
+   scale_colour_usq() +
+   coord_flip() +
+   guides(fill = FALSE, color = FALSE)
+```
+
+Using the mean difference in the treatment effect seems to show the effect of each treatment better than just raw yield and reduces the variability in the treatments.
+We know there is a good deal of variability in our studies and between them.
+Mungbean produces variable yields between seasons so ordinarily we should use a response that highlights the difference in the treatment effects that we are interested in and reduce the variability.
+However for an arm-based analysis we calculate the differences between control and treatment after the meta-analysis.
+
+### Formating the response variable
+
+Let's inspect the response variance `grain_yield.t.ha` to see if it is normally distributed. 
+In many cases a log transformation of the response variable improves the fit, due to the prevalence of log distributed data in nature.
+
+```{r}
+hist_usq(slimmer_PM_dat$grain_yield.t.ha, main = "Grain yield (t / ha)")
+hist_usq(log(slimmer_PM_dat$grain_yield.t.ha), main = "log(Grain yield (t / ha))")
+hist_usq(sqrt(slimmer_PM_dat$grain_yield.t.ha), main = "sqrt(Grain yield (t / ha))")
+hist_usq(slimmer_PM_dat$yield_gain, main = "Mean difference to control (t / ha)")
+```
+The distribution of data does not seem to be improved by transformation of the data.
+We will retain the continuous variable grain_yield.t.ha as the response.
+Mean differences won't be used as we are following the methodology of a ARM-based model, where mean differences are calculated following the meta-analysis.
+
+### Formatting Variance
+
+First let's remove any entries missing variance.
+
+```{r remove_studies}
+any(is.na(slimmer_PM_dat$yield_error))
+
+slimmer_PM_dat <-
+   slimmer_PM_dat[!is.na(slimmer_PM_dat$yield_error), ]
+
+slimmer_PM_dat$vi <- slimmer_PM_dat$yield_error
+```
+
+#### Calculate sample variance from mean square errors
+
+Currently our data frame has the sample variance calculated earlier, however we can approximate it using the mean squared error.
+Let's show the rational for our calculation and then add a secondary variance column (`vi2`).
+
+$MSE = Var + bias$
+
+However if our MSE was calculated from an unbiased sample we can assume $bias = 0$ and therefore:
+
+$MSE = Var$
+
+To calculate the sample variance (for each treatment in the trial) from the mean square error (Trial variance) all we need to do is divide by the number of samples in each treatment.
+We can show this because:
+$MSE = \frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n - 1}$
+Where the sum of squares for the fungicide treatment estimator ($y$) is divided by the number of fungicide treatments ($n$).
+
+The sample variance is a similar formula except we use $x$ instead of $y$.
+$S_{Var} = \frac{\sum_{x_1}^{x_n}(x_i - \overline{x})^2}{n - 1}$  
+$x$ being each observation within the experiment and $n$ being the number of samples in the whole trial.
+Therefore: 
+$S_{Var}\approx\frac{1}{n_{x}}\frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n_y - 1}$  
+Where $n_x$ is the number of samples within each treatment.
+
+```{r MSE_2_SVar}
+#calculation when using log of response
+# slimmer_PM_dat$vi <-
+#    slimmer_PM_dat$Y_Msquare / (slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha ^
+#                                   2)
+
+slimmer_PM_dat$vi2 <- 
+   slimmer_PM_dat$Y_Msquare / 
+   slimmer_PM_dat$n
+```
+
+Now Let's simplify our data by removing the control data, converting disease pressure (`D_pres`) to a factor and selecting only the columns of data necessary for analysis.
+We will also include the mean difference or response ratio `grain_MD`, between the treatment and control as a comparison of responses.
+
+```{r metafor_organisation}
+dat1 <-
+   slimmer_PM_dat %>%
+   mutate(vi = vi/n) %>% 
+   mutate(spray_management =
+             factor(
+                spray_management,
+                c(
+                   "control",
+                   "Early",
+                   "Recommended",
+                   "Recommended_plus",
+                   "Late",
+                   "Late_plus"
+                )
+             ),
+          D_pres = 
+             factor(D_pres,
+                    c("lowD",
+                      "highD")),
+          id = row_number()) %>%
+   dplyr::select(
+      trial,
+      trial_ref,
+      location,
+      year,
+      row_spacing,
+      host_genotype,
+      spray_management,
+      fungicide_ai,
+      D_pres,
+      grain_yield.t.ha,
+      yield_gain,
+      dose,
+      vi,
+      yield_error,
+      vi2,
+      n,
+      id)
+```
+
+## metafor analysis
+
+For the first grain yield meta-analysis, we'll use the `metafor` package [@Viechtbauer2010].
+
+To do a ARM based model we will use the package `metafor`.
+We are using the `spray_management` variable as a moderator and an interactive term to the `trial` random variable.
+
+```{r Metafor-analysis}
+PM_mv <- rma.mv(
+   yi = grain_yield.t.ha,
+   vi,
+   mods = ~ spray_management,
+   method = "ML",
+   random = list(~ spray_management | trial, ~1 | id), 
+   struct = "UN",
+   control=list(optimizer="optim"),
+   data = dat1
+)
+
+summary(PM_mv)
+```
+
+The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis.
+This effectively shows the heterogeneity between experiments for these particular treatments.
+
+The tau^2 also gives us the heterogeneity between trials and indicates `Recommended_plus` showed the highest heterogeneity between experiments followed by `Late_plus`, `Late` then `Recommended`, with `Early` and the no-spray `control` showing the least heterogeneity.
+
+The second table is in two parts (left and right). 
+The left part, rho, is the correlation of variation between the specified treatments.
+All comparisons were acceptable except for a comparison between `Early` and `Late_plus`, `0.000` rho.
+`Early` and `Late_plus` treatments never occurred within the same trial, which is indicated by the right side of the table (hence the warning).
+
+In this result we can see that the `Early` treatment is not significantly different to the intercept, which in this case is the mean of the no spray `control`.
+However the other treatments are significantly different from the no-spray control (intercept).
+The $Q_M$ [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, shows the moderators significantly influence the model ($Q_M =$ `r PM_mv$QM` $,df =$ `r PM_mv$m`, `r reportP(PM_mv$QMp)`) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
+The analysis shows there is still a significant amount of residual heterogeneity ($Q_E =$ `r PM_mv$QE` $,df=$ `r PM_mv$k - PM_mv$m`, `r reportP(PM_mv$QEp)` ) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
+
+```{r PM_Mv_Contrast}
+source("R/simple_summary.R")
+summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none"))
+contrast_Ssum <- simple_summary(summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none")))
+contrast_Ssum
+```
+
+These contrasts can be viewed in a plot
+```{r plotContrasts}
+par(mar = c(5, 13, 4, 2) + 0.1)
+plot(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), yaxt='n')
+axis(2, at = seq_along(contrast_Ssum$contrast), labels = rev(contrast_Ssum$contrast), las=2, cex.axis = 0.8)
+```
+
+Does disease pressure on the crop affect the optimum spray scenario? 
+Above we can see spraying at the first sign of powdery mildew or with in `r min(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"| slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` - `r max(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"|                   slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` days after first sign is effective at mitigating yield loss.
+Lets test this hypothesis by adding it as a moderator and comparing the new model with the original model above.
+
+```{r DisPressComparison}
+PM_mv2 <- rma.mv(
+   yi = grain_yield.t.ha,
+   vi,
+   mods = ~ spray_management*D_pres,
+   method = "ML",
+   random = list(~ spray_management | trial, ~1 | id), 
+   struct = "UN",
+   control=list(optimizer="optim"),
+   data = dat1
+)
+
+anova(PM_mv, PM_mv2)
+```
+We can see that the lower $QE$ indicates that disease pressure moderator helped explain some of the residual heterogeneity in differences in grain yield between treatments. 
+However according to the Wald-test the models were not significantly different and we should use the original "Reduced" model.
+
+The P value was close to the 0.05 cut-off so we will present the model output for the interest of the readers.
+```{r DissPressMetMod}
+summary(PM_mv2)
+summary(glht(PM_mv2, linfct=cbind(contrMat(rep(7,12), type="Tukey"))), test=adjusted("none"))
+# plot(glht(PM_mv2, linfct=cbind(contrMat(rep(7,12), type="Tukey")))) # I think this plot is too busy to be incorporated
+```
+
+### Profile plots
+
+Let's inspect the profile plots to ensure the model is not over-fitted.
+We expect to see the estimate align with the peak of the curve.
+Also that the shape of the line is a curve.
+Caution! this will take some time to run.
+
+```{r profile_plots, eval=FALSE, message=FALSE, include=FALSE, results="hide"}
+profile(PM_mv, tau2 = 1)
+profile(PM_mv, tau2 = 2)
+profile(PM_mv, tau2 = 3)
+profile(PM_mv, tau2 = 4)
+profile(PM_mv, tau2 = 5)
+```
+
+Lets present the meta-analysis results for the moderator variables in a forest style plot.
+First lets create a table of the results.
+
+```{r metafor_results}
+results_AI <- data.frame(cbind(PM_mv$b,
+                               PM_mv$ci.lb,
+                               PM_mv$ci.ub))
+
+efficacy <- as_tibble(results_AI)
+efficacy$Treatment <-
+   factor(c(
+
+       "control",
+      "Early",
+      "Recommended",
+      "Recommended_plus",
+      "Late",
+      "Late_plus"
+   ))
+
+efficacy$se <- PM_mv$se
+colnames(efficacy) <-
+   c("Mean", "CIs_lower", "CI_upper", "Treatment", "SE")
+efficacy
+```
+
+Let's view these comparisons in a plot.
+
+```{r metafor_plot}
+YieldContrasts <- efficacy %>%
+   filter(Treatment != "control") %>% 
+   mutate(Treatment = factor(Treatment, levels = rev(
+      c(
+
+         "Early",
+         "Recommended",
+         "Recommended_plus",
+         "Late",
+         "Late_plus"
+      )
+   ))) %>%
+   ggplot(aes(Treatment, Mean)) +
+   geom_hline(
+      yintercept = seq(-0.05, 0.3, by = 0.05),
+      color = usq_cols("usq charcoal"),
+      linetype = 3
+   ) +
+   geom_hline(yintercept = 0) +
+   geom_point(aes(size = 1 / SE), shape = 15) +
+   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper)) +
+   coord_flip()
+
+YieldContrasts
+```
+
+### Forest plot of trial treatment effect per trial
+Lets look at the trial variability in this model with a forest plot
+```{r forestP, fig.height= 40, fig.width=17}
+# THIS NEEDS TO BE FIXED
+source(here("R/change_labels.R"))
+source(here("R/forest_rows.R"))
+
+### Sort and arrange data-frame accordingly and produce a index vector to inform the order of each "Trial" on the plot
+index1 <- dat1 %>%
+   mutate(ID = seq_along(trial_ref)) %>%
+   mutate(spray_management = 
+             factor(spray_management, 
+                    levels = c("Early","Late","Recommended",
+                    "Recommended_plus","Late_plus"))) %>%
+   arrange(desc(spray_management), location, desc(grain_yield.t.ha)) %>%
+   mutate(ID2 = order(ID))%>%
+   pull(ID2)
+
+### Use forest rows function to return a list of where to place on the plot: sub-titles, each trial row, and summary prediction for each treatment.
+### this list can be used below to reference where to plot each variable
+rows1 <- forest_rows(head_row = 186, 
+                     ord_var = dat1$spray_management, 
+                     index = index1, 
+                     gap = 5, 
+                     row_offset = -2)
+
+### A data-frame of meta-model coefficients used to produce the summary polygons for each treatment
+polys <- data.frame(ref = change_labels(names(coef(PM_mv))),
+                    x = c(coef(PM_mv)[1],coef(PM_mv)[1] + coef(PM_mv)[2:6]),
+                    ci.lb = c(PM_mv$ci.lb[1],PM_mv$ci.lb[1] +PM_mv$ci.lb[2:6]),
+                    ci.ub = c(PM_mv$ci.ub[1],PM_mv$ci.ub[1] +PM_mv$ci.ub[2:6]))[c(2,5,3,4,6,1),]
+polys$rows <- rows1$pred_row - 1.5
+
+forest1  <- metafor::forest(PM_mv, cex = 1.15 , width = 5,
+                #order = "fit",
+                rows = rows1$trows-1.5,
+                ilab = cbind(dat1$year, 
+                             dat1$row_spacing, dat1$host_genotype, dat1$dose),
+                ilab.xpos = c(-2.35,-2.1,-1.8,-1.4)+1,
+                slab = NA, 
+                xlim = c(-2, 4),
+                ylim = c(5,190),
+                xlab = "Grain yield mean difference",
+                addfit = FALSE,
+                efac = c(0.2,0.15,0.2),
+                at = seq(-0.5,3, 0.5))
+
+### code which puts lines and annotations on the plot, its a bit long...
+source(here("R/add_annotations.R"))
 
@@
 
-This linear mixed effect model shows indicates:  
-   - A single early spray before first sign of powdery mildew is not likely to increase yields.  
-   - A single or single spray with one or more follow sprays starting  at the `recommended` first spray , within 3 days of powdery mildew first sign are likely to produce significantly higher grain yields compared to the no spray control.
-   - The `recommended_plus` spray which has one or more follow-up sprays after first sign are likley to increase the mean grain yield.  
-   - `Late_plus` spray treatments showed the highest mean grain yield, and was significantly higher than the no spray control. However showed no difference to either of the `recommended` treatments.
+****
 
-### Imputing sample variances
+## netmeta analysis
 
-We need to impute the variances which are missing for a few of the trials.
-These trials `r unique(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),c("location","year", "trial_ref")])$trial_ref` were analysed and reported that there was no significant difference between the treatments in each trial.
-So therefore we need the imputed variances not to show a significant difference.
+We can use the `netmeta` package to give a graphical representation of the pairwise comparisons.
 
-There are `r sum(is.na(slimmer_PM_dat$yield_error))` treatments without yield error in our data, and `r sum(!is.na(slimmer_PM_dat$yield_error))` where yield error was recorded.
-
-Plotting a histogram of the variances show that the yield is not normally distributed.
-A log transformation, however, shows a normal disrtubution.
-We can use the mean and standard deviation of the log(V) to sample variances for the treatments where V is missing.
-
-```{r variance_histograms}
-hist(slimmer_PM_dat$yield_error) # yield error is not normally distributed
-hist(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is normally distributed 
-```
-
-We will evaluate wheather the imputed variances confer a significant difference to the recorded means.
-I created a distance matrix of two standard errors above the mean against two standard errors below the mean.
-If any errors don't overlap, infering signicifant difference, the imputed variances are discarded and resampled until all treatment variances show no significant differences.
-
-```{r imputing_variances}
-
-# generate yield error values
-for(i in 0:500){
-
-   # Imputing missing log variances
-   log_Yerror <- rnorm(n = sum(is.na(slimmer_PM_dat$yield_error)),
-               mean = mean(log(slimmer_PM_dat$yield_error), na.rm = TRUE),
-               sd = sd(log(slimmer_PM_dat$yield_error), na.rm = TRUE))
-
-   # First lets convert Variance to standard error for all the variables that have variance recorded
-   slimmer_PM_dat$yield_SE <- 
-      sqrt(slimmer_PM_dat$yield_error)/sqrt(slimmer_PM_dat$n)
-
-   # Second; adding the imputed standard errors
-   slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"] <-
-      sqrt(exp(log_Yerror))/sqrt(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"n"])
-
-# all errorbars should overlap so they are consistant with the meta-data describing no significant difference bettween treatments
-# lets test to make sure
-if(
-   max(outer(X = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] -
-               (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
-             Y = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] +
-               (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
-             FUN = "-")
-       ) > 0){
-
-   message(paste("\nWarning!!: Imputed yield errors show significant differences when they should not, imputation will automatically rerun - iteration", "i =",i))
-   next()
-   }else{
-      message(paste(i,"iterations: ", "imputed variances now show no significant distances :)\n Now adding variances to data "))
-
-      # Plot the imputed errors for each trial
-      Vplot <- slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),] %>%
-         ggplot(aes(y = grain_yield.t.ha, trial))+
-         #geom_point()+
-         geom_pointrange(ymin = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] -
-                            (1.95*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
-                         ymax = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] +
-                            (1.95*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
-                         position = "jitter"
-                         )+
-         ylim(0.2,1.5)
-
-      slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_error"] <- exp(log_Yerror)
-      print(Vplot)
-      break()}
-}
-
-```
-
-The imputed variances calculated above don't show the expected positive correlation between grain yield and variance.
-This is unexpected and reflects the inherent variability of the data.
-Therefore we will calculate the trial mean squares and use this to calculate the variance for each sample.
-
-#### Imputing sample variances from Mean squares
-```{r imputing_MSE_dataSpread}
-slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
-hist(unique(slimmer_PM_dat$Y_Msquare))
-hist(log(unique(slimmer_PM_dat$Y_Msquare))) # log mean square has a more normal distribution
-
-```
-
-Imputing using a log transformation of the data is required. Which trials need variance imputation?
-
-```{r imputing_MSE}
-TrialMSQ <- slimmer_PM_dat %>%
-   group_by(trial_ref)%>%
-   summarise(unique(Y_Msquare))
-
-TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), "trial_ref"]
-```
-
-```{r imputation_MSE}
-
-for(i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`),]$trial_ref){
-   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i,"Y_Msquare"] <- 
-      exp(
-         rnorm(n = 1,
-               mean = mean(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE),
-               sd(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE)
-         )
-      )
-   }
-
-```
-
-Before analysis lets have a look at the trimmed down modified data.
-
-```{r treatment_means_plot}
-slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management, levels(slimmer_PM_dat$spray_management)[rev(c(1,2,4,5,3))])
-
-slimmer_PM_dat %>%
-   ggplot(aes(y = grain_yield.t.ha, x = spray_management))+
-   geom_boxplot()+
-   #geom_point(position = "jitter", alpha = 1/5)+
-   geom_jitter(width = 0.1, alpha = 1/5)+
-   theme_usq()+
-   labs(x = "Spray management variable", 
-        y = "Grain yield (t/Ha)",
-        title = "Mean grain yield from each treatment \n categorised by spray management scenario")+
-   theme(plot.title = element_text(hjust = 0.5))+
-   geom_hline(yintercept = 0, linetype = 2)+
-   coord_flip()
-```
-
-There seems like no difference between the treatments, with exception to Late_plus.
-Lets do this plot again, but use the proportion of yield increase compared to the no spray control as the response variable.
-
-It is also important to visualise how well the data is compared across the trial years and trials.
-
-```{r table_of_nTreatments}
-kableExtra::kable(table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year), align=rep('c', 8))%>%  #commented as was redering empty, needs a look in
-   kable_styling("striped", fixed_thead = TRUE, full_width = FALSE, position = "center")
-
-```
-Treatments Late_plus and early don't have very good comparison to other treatments.
-
-```{r plot_yieldProportion}
-slimmer_PM_dat$spray_management <-
-   factor(slimmer_PM_dat$spray_management,rev(c("control", "Early", "Recommended", "Recommended_plus","Late_plus")))
-
-slimmer_PM_dat %>%
-   ggplot(aes(y = prop_yield_gain, x = spray_management))+
-   geom_boxplot()+
-   #geom_point(position = "jitter", alpha = 1/5)+
-   geom_jitter(width = 0.1, alpha = 1/5)+
-   theme_usq()+
-   labs(x = "Spray management variable", 
-        y = "Grain yield (t/Ha)",
-        title = "Mean grain yield from each treatment \n categorised by spray management scenario")+
-   theme(plot.title = element_text(hjust = 0.5))+
-   geom_hline(yintercept = 0, linetype = 2)+
-   coord_flip()
-```
-
-## Meta-analysis  
-### metafor package  
-Let's load the metafor package we are using to analyse the data, then rearrange the factors we want to examine by placing the control treatment first.
-This way all treatments will be compared to the no spray controls.
-Next we are log transforming the grain yield and calculating the variance from the trial mean squares.  
-Finally we will assign factor classes to the main variables in the meta-analysis. Note that variable trial is a combination of:  
-   - Trial identifier  
-   - Trial year  
-   - Trial location  
-   - Host genotype  
-   - Trial row spacing
-
-```{r metafor_organisation}
-library(metafor)
-slimmer_PM_dat$spray_management <-
-   factor(slimmer_PM_dat$spray_management,c("control", "Early", "Recommended", "Recommended_plus","Late_plus"))
-
-slimmer_PM_dat$yi <- log(slimmer_PM_dat$grain_yield.t.ha)
-slimmer_PM_dat$vi <- slimmer_PM_dat$Y_Msquare/(slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha^2)
-
-slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management)
-slimmer_PM_dat$trial_ref <- factor(slimmer_PM_dat$trial_ref)
-slimmer_PM_dat$trial <- factor(slimmer_PM_dat$trial)
-```
-
-```{r Metafor-analysis}
-
-PM_mv_AI <- rma.mv(yi,vi,
-                   mods = ~ spray_management,
-                   method = "ML",
-                   random = list(~ spray_management | trial),
-                   struct = "UN",
-                   data = slimmer_PM_dat)
-
-summary(PM_mv_AI)
-
-```
-
-Results show that yields in single early spray treatments are not significantly different to the no spray control.
-Commencing spray manangement schedules at first sign of disease (Recommended), or between 7 - 19 days after first sign (late) produced significantly higher yields compared to the no spray control.
-On average a spray scheduale with two or more applications stating late (7-19 days after first sign of powdery mildew) produced the highest yields.
-
-When we compare these results to those of the linear mixed effect model there is little difference in the outcome.
-The most noteable difference is the linear mixed-effect model is somewhat less certain about the `Late_plus` treatment, and the mean yield lower than the `recommended_plus` treatment.
-
-```{r compare_meta&lmer}
-lme_PM <- lmer(yi ~ spray_management + (spray_management | trial), data = slimmer_PM_dat)
-
-summary(lme_PM)
-
-```
-
-To make it easier to compare each of the treatments we can compute the meta-analysis contrasts.
-```{r metafor_contrasts}
-anova(PM_mv_AI, L=rbind(c(0,1,-1,0,0),  # early vs Recomended
-                        c(0,1,0,-1,0),  # early vs recommended plus
-                        c(0,1,0,0,-1),  # early vs Late plus
-                        c(0,0,-1,1,0),  # Recommended vs recommended_plus
-                        c(0,0,-1,0,1),  # Recommended vs Late_Plus
-                        c(0,0,0,-1,1))) # recommended_plus vs Late_plus
-```
-Results show with the exclusion of the no spray control, none of the treatments are significantly different, however, early applications treatments on average produced lower yields.
-Lets view this on a plot.
-
-```{r metafor_results}
-results_AI <- data.frame(cbind(exp(PM_mv_AI$b), 
-                              exp((PM_mv_AI$ci.lb)),
-                              exp(PM_mv_AI$ci.ub)))
-
-# results_AI <- data.frame(cbind(PM_mv_AI$b, 
-#                               (PM_mv_AI$ci.lb),
-#                               PM_mv_AI$ci.ub))
-
-treat <- c("control", "Early", "Recommended", "Recommended_plus","Late_plus")
-efficacy <- tbl_df(results_AI)
-efficacy$treat <- treat
-efficacy$se <- PM_mv_AI$se
-colnames(efficacy) <- c("Mean", "CIs_lower", "CI_upper", "Treatment", "SE")
-efficacy
-```
-
-```{r metafor_plot}
-efficacy$Treatment <-
-   factor(efficacy$Treatment,c("control", "Early", "Recommended", "Recommended_plus","Late_plus"))
-
-efficacy %>% 
-   ggplot(aes(Treatment, Mean))+
-   geom_hline(yintercept = c(0.8,1,1.2,1.4), color = "grey80", linetype = 3)+
-   geom_point(aes(size=1/SE), shape=15)+
-   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper))+
-   coord_flip()+
-   theme_usq()
-
-```
-
-What is interesting here is that the variance in the control has increased while the treatments have decreased.
-This is despite the control being the best represented across all experiments.
-However it could also be because it also has a low number of pooled reps per trial.
-Lets look at how well each of the treatments compare to each other.
-We can use the netmeta package to give a graphical representation of this.
-
-### netmeta package  
-Lets analyse the data again using a different statistical approach to see if our outcome with the `metafor` package was robust.
-The `netmeta` package uses a frequentist approach to the analysis, and focuses on the pairwise comparisons between treatments.
+Let's analyse the data again using a different statistical approach to see if our outcome with the `metafor` package was robust.
+The `netmeta` package uses a frequentist approach to the analysis and focuses on the pairwise comparisons between treatments.
 
 ```{r netmeta-analysis}
-library(netmeta)
-
 datPM3 <- slimmer_PM_dat %>%
    group_by(trial, spray_management, n) %>%
-      summarize(yi_mean = mean(yi), 
-             vi_mean = mean(vi)) %>% 
+   summarize(yi_mean = mean(grain_yield.t.ha),
+             vi_mean = mean(yield_error)) %>%
    ungroup()
 
-PM_con <- pairwise(treat = spray_management,
+PM_con <- pairwise(
+   treat = spray_management,
    n = n,
@@
    sd = sqrt(vi_mean),
-                  studlab= trial,
+   studlab = trial,
    data = datPM3,
-                  sm="MD")
+   sm = "MD"
+)
 
@@
                    studlab,
-                data=PM_con, 
-                sm="MD")
+                   data = PM_con,
+                   sm = "MD")
 
 summary(net_con)
+```
+
+Now let's visualise this as a forest plot.
+
+```{r netmeta-forest}
+forest(
+   net_con,
+   reference.group = 1,
+   rightcols = c("effect", "ci", "Pscore"),
+   rightlabs = "P-Score",
+   small.values = "bad"
+)
+```
+
+The `netmeta` analysis suggests the spray schedule commencing early are no different to any other treatment including the no spray `control`.
+It estimates the mean is very similar to the recommended treatments.
+The `Recommended_plus` and `Late_plus` treatments show higher mean estimates, however are not significantly different from the `Early` estimate.
+
+```{r netgraphGW}
+netgraph(
+   net_con,
+   plastic = FALSE,
+   col = usq_cols("support orange"),
+   thickness =  "number.of.studies",
+   points = FALSE,
+   col.points = usq_cols("usq charcoal"),
+   cex.points = 1,
+   number.of.studies = TRUE,
+   cex.number.of.studies = 1,
+   col.number.of.studies = "black",
+   bg.number.of.studies = usq_cols("support orange"),
+   multiarm = FALSE,
+   col.multiarm = usq_cols("support turquiose"),
+   pos.number.of.studies = 0.5
+)
+```
+
+```{r}
+netleague(net_con)
+
+decomp.design(net_con)
+
+netsplit(net_con)
+
+nm1 <- netmeasures(net_con)
+
+plot(
+   nm1$meanpath,
+   nm1$minpar,
+   pch = "",
+   xlab = "Mean path length",
+   ylab = "Minimal parallelism"
+)
+text(nm1$meanpath, nm1$minpar, names(nm1$meanpath), cex = 0.8)
+```
+
+```{r Save_meta_data, eval=FALSE}
+save(dat1, efficacy, slimmer_PM_dat, PM_mv, YieldContrasts, contrast_Ssum, 
+     file = here("cache/Meta-analysisData.Rdata"))
+```
+
+#### Powdery mildewMBM comparison -- Delete
+One aspect we would like to consider is how the results of this meta-analysis compares to how the PowderyMildewMBM estimates the effect of fungicide applications on grain yields.
+Below we create a data frame of the mitigation factors for each spray scenario so we can compare them to the outcomes of the meta-analysis.
+```{r compare2PowderyMildewMDM}
+
+PMBM <- 
+   data.frame(Sprays = c(rep(1,20), rep(2,20)),
+              Disease = rep(c(rep("NotPresent", 5),
+                          rep("LowerCanopy", 5),
+                          rep("MidCanopy", 5),
+                          rep("UpperCanopy", 5)),2),
+              CropMaturity = rep(c("Vegetative", "Budding", "Flowering",
+                                   "EarlyPod", "LatePod"), 8),
+              mitigation = c(0.57, 0.855, 0.95,0.95,0.95,
+                             0.45995, 0.52919,0.5530,0.390,0.1642,
+                             0.291258,0.351051, 0.2454,0.1409,0.4717,
+                             0,0.059597,0.093034,0.0682476,0.0215584,
+                             0.95,0.95,0.95,0.95,0.95,
+                             0.766588,0.6991,0.55042,0.390056,0.1642,
+                             0.485429,0.390,0.2454,0.140904,0.0471684,
+                             0.0791,0.086068,0.093034,0.0682476,0.0215584))
+
+# what is the mean age of the plant in our data when disease first occurs and we apply the first spray?
+source("R/import_data.R")
+PM_MB_dat <- import_data()
+mean(PM_MB_dat$first_sign_disease - PM_MB_dat$planting_date, na.rm =TRUE) # 46.3 days (which is when the plant is flowering)
+
+#What proportion of the yield was saved?
+1 - (coef(PM_mv)[1] /(coef(PM_mv)[1] + coef(PM_mv)[3]))
+1- (coef(PM_mv)[1] /(coef(PM_mv)[1] + coef(PM_mv)[4]))
+
+PMBM %>%
+   filter(CropMaturity == "Flowering")
 
 ```
-Now lets visualise this as a forest plot
-
-```{r netmeta-forest}
-forest(net_con, reference.group = 4,
-       rightcols=c("effect", "ci", "Pscore"),
-       rightlabs="P-Score", small.values = "bad")
-
-```
-
-The `netmeta` analysis suggests the spray scheduale commencing early are no different to any other treatment including the no spray control.
-It estimates the mean is very similar to the recommended treatments.
-The recommended plus and late_plus treatments show higher mean estimates, however not significantly different from the early estimate.
-
-```{r Save_meta_data}
-write.csv(slimmer_PM_dat, file = "data/GYmeta_data.csv")
-
-```
+To to a better comparison I need to know how the mitigation factor is calculated with the estimated yields.

### 2020-08-10 02_Import_and_FormatData.Rmd
Re-save data-wrangling vignette to chapter 2

--- 2020-07-21 02_Preliminary_analysis.Rmd
@@
-# Preliminary Analysis
-
-```{r PA_Libraries, include=FALSE, message=FALSE}
-if (!require("pacman"))
-   install.packages("pacman")
-pacman::p_load(tidyverse,
-               lubridate,
-               bomrang,
-               openxlsx,
-               devtools,
-               reshape2,
-               lme4,
-               kableExtra)
-source("R/import_data.R")
-if (!require("theme.usq"))
-   devtools::install_github("adamhsparks/theme.usq")
-library(theme.usq)
-theme_set(theme_usq()
-)
-```
-
-## Explore and Visualise Data
-First let's import the data.
-Each row provides the mean yield for each experimental treatment.
-
-```{r echo=TRUE, message=FALSE, warning=FALSE}
+# Import and Format Data
+## Non-wrangled trials
+
+Data from the three follow trials were input manually from either PDF or word files.  
+   - Gatton 2012  
+   - Kingaroy 2012  
+   - Emerald 2016
+
+## Import Libraries
+```{r message=FALSE, warning=FALSE}
+library(openxlsx)
+library(readxl)
+library(tidyr)
+library(dplyr)
+library(data.table)
+library(agricolae)
+library(here)
+
+source(here("R/import_data.R"))
 PM_MB_means <- import_data()
@@
 
-The data explored in the `PM_MB_means` data frame is a list of mean values from each treatment in each respective experiment.
-These preliminary analyses will focus on the change in mungbean yields, which is attributable to the fungicide treatment. 
-Later in this document we will also consider the impact of fungicide treatments on disease incidence/severity.
-Mean powdery mildew incidence was recorded at the end of each growing season.
-Some experiments recorded disease incidence throughout the season and these were summarised with AUDPC.
-AUDPC for trials which only provided final powdery mildew incidence was calculated using the record of 'first sign of disease' and final assessment.
-More details on how the `PM_MB_means` data was compiled can be found in the ['Data wrangle vingette'](./vignette/191115_PMMB_DataWrangling_PM.html)
-
-Various factors have been studied in the previous experiments which may influence the subsequent meta-analysis.
-On this page, unless stated, the following plots and analyses were made disregarding other effects.
-The following factors are postulated to influence mungbean grain yield and/or powdery mildew mean plot severity.
-
-   1 Fungicide type
-
-   2 Fungicide dose (varies only slightly within some fungicide types)
-
-   3 Number of fungicide sprays
-
-   4 Timing of fungicide spray/s relative to first sign of disease
-
-   5 Host cultivar (probably is a co-variate with season due to changing cultivars over time)
-
-   6 Experiment location
-
-   7 Row spacing
-
-   8 In-crop rainfall
-
-   9 Irrigated versus non-irrigated trials
-
-   10 Mean daily temperature in the weeks following spray application
-
-   11 Final disease rating
-
-   12 Two pathogen species cause PM (new discovery in 2018)
-
-The data plotted below are from `r length(unique(PM_MB_means$trial_ref))` field trials between (`r first(levels(PM_MB_means$year))` - `r last(levels(PM_MB_means$year))`) of which the details are described in the [studies considered in meta-analysis section](#studies-considered-in-meta-analysis).
-
-### Fungicides
-
-#### Fungicide type
-
-First let's standardise the sulphur treatments.
-Some early experiments tested different formulations.
-There was no difference in the sulphur formulations so we will refer to all of them as "sulphur".
-
-```{r sulphur_simplify}
-# Remove the variation in different sulphur formulations
-unique(PM_MB_means[grep("sulphur", PM_MB_means$fungicide_ai),
-                   "fungicide_ai"])
-PM_MB_means[grep("sulphur", PM_MB_means$fungicide_ai), "fungicide_ai"] <-
-   "sulphur"
-```
-
-Let's explore how many different types of fungicide were used and at what frequency.
-
-```{r Fungicides}
-PM_MB_means %>%
-   group_by(fungicide_ai, trial_ref) %>%
-   summarise() %>%
-   count(sort = TRUE) %>%
-   rename(Trials = n) %>%
-   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
-   xlab("Fungicide active ingredient") +
-   ylab("N Trials") +
-   geom_col() +
-   scale_fill_usq() +
-   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
-   scale_colour_usq() +
-   coord_flip()
-```
-
-The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in the highest frequencies, along with sulphur.
-The DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.
-
-Amistar Xtra and Custodia both contain strobilurin and triazole, however, because they contain differing dose ratios (inverted) pooling may not be appropriate.
-
-Perhaps best way forward is to focus the meta-analysis on only the DMIs.
-This can then be compared to an additional meta-analysis including azoxystrobin as a comparison.
-
-*****
-
-Before we exclude non-DMI fungicides let's have a look at the efficacy of the other fungicides in comparison to the DMIs.
-For this comparison we will focus on the proportional yield saved, relative to the no spray control.
-The primary focus of this research is the effect of fungicide on mitigating yield loss due to disease.
-We are using proportional yield, relative to the no spray control, to reduce the effect of location and seasonal influences.
-
-Let's investigate the difference in the effect of the type of fungicide on proportion of yield saved, but first we need to calculate yield saved relative to the no spray control.
-
-```{r Calculate_yield-savings}
-PM_MB_means$grain_yield.t.ha. <-
-   as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data
-
-for (i in unique(PM_MB_means$trial_ref)) {
-   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
-
-   if (any(is.na(unique(dat1$row_spacing)))) {
-      warning(
-         unique(dat1$trial_ref),
-         "at",
-         unique(dat1$location),
-         "in year",
-         unique(dat1$year),
-         "has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n"
-      )
-      next()
-   }
-
-   for (j in unique(dat1$row_spacing)) {
-      dat2 <- dat1[dat1$row_spacing == j, ]
-      controlY <-
-         mean(dat2[dat2$fungicide_ai == "control", "grain_yield.t.ha."])
-
-      dat2$yield_gain <- dat2$grain_yield.t.ha. - controlY
-      dat2$prop_YG <- dat2$yield_gain  /  controlY
-
-      dat2[dat2$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
-         NA
-
-      dat1[dat1$row_spacing == j, ] <- dat2
-   }
-   PM_MB_means[PM_MB_means$trial_ref == i, ] <- dat1
-}
-
-# ____________________________________________
-# calculate yield gain and prop_yield gain for experiments with no row spacing data
-
-dat1 <- PM_MB_means[PM_MB_means$trial_ref == "AM1303", ]
-
-controlY <-
-   mean(dat1[dat1$fungicide_ai == "control", "grain_yield.t.ha."])
-
-dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
-dat1$prop_YG <- dat1$yield_gain / controlY
-dat1[dat1$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
-   c(NA, NA)
-PM_MB_means[PM_MB_means$trial_ref == "AM1303", ] <- dat1
-
-write.csv(PM_MB_means,
-          "cache/1911_PM_MB_means&Ygains.csv")
-```
-
-Now we have calculated proportional yield savings we can inspect the difference between the fungicide active ingredients
-
-```{r Fungicide_x_nSprays_tble2, message=FALSE}
-PM_MB_means %>%
-   group_by(fungicide_ai, total_fungicide) %>%
-   summarise(
-      n = length(prop_YG),
-      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
-      median = median(prop_YG, na.rm = T),
-      mean = mean(prop_YG, na.rm = T),
-      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
+## Functions
+```{r functions}
+fold_data <- function(new_DataFrame, template_DataFrame) {
+   # This function formats a dataframe to have the same column order as a template data.frame
+   # If columns are missing from the new_DataFrame that are in the template_DataFrame, it creates them 
+   # with NA values. 
+   # Columns in the new_DataFrame, which are not in the template_DataFrame are appended to the right-hand-side
+   # of the new_DataFrame
+   # Using this function assists in joining the two data.frames together so columns are in the same order
+
+   for (i in colnames(new_DataFrame)) {
+      if (i == colnames(new_DataFrame)[1]) {
+         x1 <- vector()
+      }
+
+      cnames1 <- as.character(colnames(new_DataFrame))
+      cnames2 <- as.character(colnames(template_DataFrame))
+
+      x1 <-
+         c(x1, match(i, cnames2, nomatch = NA)) # MAke a index vector for the location of new_DataFrame col names in template_DataFrame
+   }
+
+   new_DataFrame <- as.data.frame(new_DataFrame)
+
+   new_DataFrame[,cnames2[!(cnames2 %in% cnames1)]] <-
+      NA # adding column names to new_DataFrame which are in the template_DataFrame
+   new_DataFrame <-
+      new_DataFrame[, c(cnames2, cnames1[is.na(x1)])]  # adding columns to new_DataFrame not in template_DataFrame  # arranges column names to new_DataFrame not in template_DataFrame
+
+   return(new_DataFrame)
+}
+source(here("R/copy_class.R"))
+source(here("R/replace_data.R"))
+```
+
+## Data wrangling for each trial
+### Hermitage 2010
+
+```{r Hermitage_2010}
+Herm_10 <-
+   as.data.frame(read_xls(here(
+      "data/2010 PMmung hermitage RAW field book.xls"
+   ),
+   sheet = "For analysis"),
+   stringsAsFactors == FALSE)
+
+Herm_10 <- Herm_10 %>%
+   mutate(
+      trade_name = case_when(
+         `Schedule!` == "U/S" ~ NA_character_,
+         `Schedule!` == "FirstsignC" ~ " ",
+         TRUE ~ "Kendon"
+      )
    ) %>%
-   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
-   arrange(desc(median)) %>%
-   kable(
-      caption = "Fungicide effect on proportion of yield gain.",
-      col.names = c(
-         "Fungicide active ingredient",
-         "Total fungicide applications",
-         "n Treatments",
-         "2.5% quartile",
-         "Median proportional grain yield",
-         "Mean proportional grain yield",
-         "97.5 % quartile"
+   mutate(
+      fungicide = case_when(
+         `Schedule!` == "U/S" ~ "control",
+         `Schedule!` == "FirstsignC" ~ "carbendazim",
+         TRUE ~ "sulphur"
+      )
+   ) %>%
+   mutate(dose_ai.ha = case_when(
+      `Schedule!` == "U/S" ~ 0,
+      `Schedule!` == "FirstsignC" ~ 250,
+      TRUE ~ 2400
+   )) %>%
+   mutate(
+      fungicide_application_1 = case_when(
+         `Schedule!` == "Full Sp" ~ as.Date("2010-02-19", format = "%Y-%m-%d"),
+         `Schedule!` == "Early Sp" ~ as.Date("2010-02-19", format = "%Y-%m-%d"),
+         `Schedule!` == "FirstsignC" ~ as.Date("2010-03-18", format = "%Y-%m-%d"),
+         `Schedule!` == "FirstsignS" ~ as.Date("2010-03-18", format = "%Y-%m-%d"),
+         `Schedule!` == "U/S" ~ as.Date(NA),
+         TRUE ~ as.Date(NA)
+      )
+   ) %>%
+   mutate(
+      fungicide_application_2 = case_when(
+         `Schedule!` == "Full Sp" ~ as.Date("2010-02-26", format = "%Y-%m-%d"),
+         `Schedule!` == "Early Sp" ~ as.Date("2010-02-26", format = "%Y-%m-%d"),
+         TRUE ~ as.Date(NA)
+      )
+   ) %>%
+   mutate(fungicide_application_3 = case_when(
+      `Schedule!` == "Full Sp" ~ as.Date("2010-03-05", format = "%Y-%m-%d"),
+      TRUE ~ as.Date(NA)
+   )) %>%
+   mutate(fungicide_application_4 = case_when(
+      `Schedule!` == "Full Sp" ~ as.Date("2010-03-11", format = "%Y-%m-%d"),
+      TRUE ~ as.Date(NA)
+   )) %>%
+   mutate(fungicide_application_5 = case_when(
+      `Schedule!` == "Full Sp" ~ as.Date("2010-03-18", format = "%Y-%m-%d"),
+      TRUE ~ as.Date(NA)
+   )) %>%
+   mutate(fungicide_application_6 = case_when(
+      `Schedule!` == "Full Sp" ~ as.Date("2010-03-25", format = "%Y-%m-%d"),
+      TRUE ~ as.Date(NA)
+   )) %>%
+   mutate(fungicide_application_7 = case_when(
+      `Schedule!` == "Full Sp" ~ as.Date("2010-03-07", format = "%Y-%m-%d"),
+      TRUE ~ as.Date(NA)
+   )) %>%
+   mutate(
+      total_fungicide = case_when(
+         `Schedule!` == "Full Sp" ~ 7,
+         `Schedule!` == "Early Sp" ~ 2,
+         `Schedule!` == "FirstsignC" ~ 1,
+         `Schedule!` == "FirstsignS" ~ 1,
+         `Schedule!` == "U/S" ~ 0,
+         TRUE ~ 9999
+      )
+   )
+
+```
+
+```{r Herm10_dataInput}
+Herm_10_dat <-
+   data.frame(
+      trial_ref = "mung0910/01",
+      year = "2010",
+      location = "Hermitage",
+      host_genotype = Herm_10$`Cultivar!`,
+      trial_design = "RB",
+      plot_length = Herm_10$`Length (m)`,
+      plot_width = 4,
+      plant_density = NA,
+      row_spacing = 0.25,
+      replicate = Herm_10$`Rep!`,
+      planting_date = as.Date("2010-01-22"),
+      emergence_date = NA,
+      flowering_date = NA,
+      pod_fill_date = NA,
+      mid_late_pod_fill = NA,
+      first_sign_disease = as.Date("2010-03-18"),
+      trade_name = Herm_10$trade_name,
+      fungicide_ai = Herm_10$fungicide,
+      dose_ai.ha = Herm_10$dose_ai.ha,
+      n_treatment = Herm_10$`Treat!`,
+      fungicide_application_1 = Herm_10$fungicide_application_1,
+      fungicide_application_2 = Herm_10$fungicide_application_2,
+      fungicide_application_3 = Herm_10$fungicide_application_3,
+      fungicide_application_4 = Herm_10$fungicide_application_4,
+      fungicide_application_5 = Herm_10$fungicide_application_5,
+      fungicide_application_6 = Herm_10$fungicide_application_6,
+      fungicide_application_7 = Herm_10$fungicide_application_7,
+      total_fungicide = Herm_10$total_fungicide,
+      harvest_date = as.Date("2010-05-14"),
+      final_assessment = as.Date("2010-04-20"),
+      PM_final_severity = Herm_10$P.M.13wap,
+      rating_scale = "1-9",
+      grain_yield.t.ha. = Herm_10$`Kg/ha` / 1000,
+      stringsAsFactors = FALSE
+   )
+
+```
+
+#### AUDPC curve
+```{r Herm10_audpc}
+library(ggplot2)
+
+Herm_10_dat <- cbind(
+   Herm_10_dat,
+   AUDPC = apply(
+      data.frame(zero = 0,
+                 Herm_10[, c("P.M.9wap", "P.M.11wap", "P.M.13wap")] -
+                    1),
+      1,
+      FUN = audpc,
+      dates = c((Herm_10_dat$first_sign_disease[1] -
+                    7) -
+                   Herm_10_dat$planting_date[1],
+                9 * 7,
+                11 * 7,
+                13 * 7
+      )
    ),
-      align = "c"
-   ) %>%
-   kable_styling(fixed_thead = T, full_width = T) %>%
-   column_spec(c(2, 3), width = "1cm") %>%
-   footnote(general = "Fungicides with less than five observations were omitted from this table")
-```
-
-**  **  *
-
-Let's visualise this in a plot for one and two sprays only.
-
-```{r Fungicide_x_nSprays_tble1, message=FALSE, warning=FALSE}
-PM_MB_means %>%
-   mutate(fungicide_ai = as.factor(PM_MB_means$fungicide_ai)) %>%
-   filter(total_fungicide == 1 | total_fungicide == 2) %>%
-   filter(
-      fungicide_ai != "pyrazophos" &
-         fungicide_ai != "control" &
-         fungicide_ai != "benomyl" &
-         fungicide_ai != "Acibenzolar-S-methyl"
-   ) %>%
-   mutate(fungicide_ai = factor(
-      fungicide_ai,
-      levels = c(
-         "carbendazim",
-         "pyraclostrobin",
-         "sulphur",
-         "200 g/L azoxystrobin + 80 g/L cyproconazole",
-         "tebuconazole",
-         "propiconazole",
-         "200 g/L tebuconazole + 120 g/L azoxystrobin"
-      )
-   )) %>%
-   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
-   facet_grid(rows = vars(total_fungicide)) +
-   geom_boxplot(aes(fill = fungicide_ai)) +
-   geom_hline(aes(yintercept = 0), size = 0.5) +
-   labs(y = "Proportion of grain yield saved",
-        title = "Grain yield proportion saved\ngrouped by fungicide type") +
-   theme(legend.position = "none") +
-   scale_fill_usq() +
-   coord_flip()
-```
-
-There is a small yield effect among the strobilurin fungicide mixes and the DMI fungicides. 
-While there is some differences in the variation between tebuconazole and propiconazole, the medians are very similar. 
-I think it is safe to combine these fungicides, with the same mode of action in the meta-analysis.
-The follow-up spray seems to show an increase in yield protection.
-Interestingly sulphur sprays show good protection when sprayed twice.
-
-*****
-
-#### Fungicide Doses  
-From this point on we will investigate only the DMI fungicides, tebuconazole and propiconazole, and disregard all other fungicide modes-of-action.
-
-We should check that all fungicide doses that were used were roughly the same, if we are to compare between trials where dose might be different.
-
-```{r tebuAndPropi_dose}
-PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole") %>%
-   select(
-      trial_ref,
-      year,
-      location,
-      first_sign_disease,
-      fungicide_ai,
-      dose_ai.ha,
-      total_fungicide
-   ) %>%
-   ggplot(aes(x = as.factor(dose_ai.ha), fill = fungicide_ai)) +
-   xlab("Dose (g ai/ha)") +
-   ggtitle(label = "Total number of treatments for each respective tebuconazole dose") +
-   geom_bar() +
-   scale_fill_usq() +
-   scale_colour_usq()
-```
-
-All trials that used tebuconazole used approximately the same dose.
-Dose of the active ingredient ranged from 62.35&nbsp;g per hectare to 60&nbsp;g per hectare.
-
-Doses for propiconazole range from 62.5 to 125, a large variation.
-Let's inspect the difference in yields for each dose.
-
-```{r PropiDoseEffect}
-PM_MB_means %>%
-   filter(fungicide_ai == "propiconazole") %>%
-   ggplot(aes(x = relevel(as.factor(dose_ai.ha), "62.5"), y = prop_YG)) +
-   xlab("Dose (g ai/ha)") +
-   ggtitle(label = "Yield for each respective propiconazole dose,\nfaceted by number of applications") +
-   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
-   facet_grid(cols = vars(total_fungicide))
-```
-
-This dose effect should be acknowledged in the meta-analysis.
-How many treatments of each dose have been investigated per trial?
-
-```{r table_PropiDoses}
-table(as.character(PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole",]$trial_ref),
-      PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole",]$dose_ai.ha)
-```
-
-Two trials show both doses were applied in the same trial, mung1112/01 and mung1112/02.
-Let's look at the difference in proportion of yield saved in these trials.
-
-```{r PropiDoses_TrialCompare}
-PM_MB_means[(PM_MB_means$trial_ref == "mung1112/01" |
-                PM_MB_means$trial_ref == "mung1112/02") &
-                PM_MB_means$fungicide_ai == "propiconazole",] %>%
-   mutate(dose_ai.ha = as.factor(dose_ai.ha)) %>%
-               ggplot(aes(y = prop_YG, x = dose_ai.ha))+
-   geom_boxplot()+
-   facet_grid(cols = vars(total_fungicide)) +
-   xlab("Dose (g ai/ha)") +
-   ggtitle(label = "Yield for each respective propiconazole dose, faceted by number of applications") +
-   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5)
-```
-
-This plot is similar to the previous plot, indicating dose needs to be considered in the analysis. Especially as there is a interaction between dose and number of sprays.
-
-*****
-
-#### Number of fungicide sprays
-
-Let's look at the frequency of sprays per fungicide.  
-```{r Fungicide_x_nSprays}
-table(PM_MB_means$fungicide_ai, PM_MB_means$total_fungicide)
-```
-
-This table shows that the majority of treatments inspected one and two spray management practices.
-
-*****
-
-#### Timing of fungicide sprays  
-The timing of fungicide application can be crucial for maximum disease control and yield loss mitigation. 
-The experiments all relied on natural infection and thus infection at a standardised crop maturity stage was not possible. 
-To best estimate the effect of fungicide application timing we will use the day when the disease was first found in the field as a reference.
-The first sign of disease is a useful reference as it can be assessed with little training for the assessor.
-
-First let's make a plot to visualise when one or more spray management regimes were made in relation to the first sign of disease regardless of fungicide active. 
-The plot is faceted by number of spray applications.
-
-```{r spray_relative2FS}
-PM_MB_means %>%
+   AUDPS = apply(
+      data.frame(zero = 0,
+                 Herm_10[, c("P.M.9wap", "P.M.11wap", "P.M.13wap")] -
+                    1),
+      1,
+      FUN = audps,
+      dates = c((Herm_10_dat$first_sign_disease[1] -
+                    7) -
+                   Herm_10_dat$planting_date[1],
+                9 * 7,
+                11 * 7,
+                13 * 7
+      )
+   )
+)
+
+Herm_10$PM_zero <- 1
+Herm_plot <-
+   melt(
+      Herm_10,
+      id.vars = c(
+         "Description!",
+         "Treat!",
+         "Rep!",
+         "Cultivar!",
+         "fungicide",
+         "total_fungicide"
+      ),
+      measure.vars = c("PM_zero", "P.M.9wap", "P.M.11wap", "P.M.13wap")
+   )
+
+Herm_plot <- Herm_plot %>%
    mutate(
-      s1_DfromFS = fungicide_application_1 - first_sign_disease,
-      s2_DfromFS = fungicide_application_2 - first_sign_disease,
-      s3_DfromFS = fungicide_application_3 - first_sign_disease,
-      s4_DfromFS = fungicide_application_4 - first_sign_disease,
-      s5_DfromFS = fungicide_application_5 - first_sign_disease
-   ) %>%
-   gather(
-      key = spray,
-      value = n_days,
-      s1_DfromFS,
-      s2_DfromFS,
-      s3_DfromFS,
-      s4_DfromFS,
-      s5_DfromFS
-   ) %>%
-   drop_na(n_days) %>%
-   ggplot(aes(x = spray, y = as.numeric(n_days))) +
-   geom_violin() +
-   scale_x_discrete(labels = c(
-      "First spray",
-      "Second spray",
-      "Third spray",
-      "Fourth spray",
-      "Fifth spray"
+      T_var = case_when(
+         variable == "PM_zero" ~
+            as.numeric((Herm_10_dat$first_sign_disease[1] -
+                           7) - Herm_10_dat$planting_date[1]
+            ),
+         variable == "P.M.9wap" ~ 9 * 7,
+         variable == "P.M.11wap" ~ 11 * 7,
+         variable == "P.M.13wap" ~ 13 * 7
+      )
+   )
+Herm_plot$`Treat!` <- as.factor(Herm_plot$`Treat!`)
+Herm_plot %>%
+   ggplot(aes(
+      x = T_var,
+      y = value,
+      color = `Treat!`,
+      shape = `Treat!`
    )) +
-   ylab("Days to First Sign of Disease") +
-   facet_grid(cols = vars(total_fungicide)) +
-   coord_flip()
-```
-
-The plot shows single fungicide applications are mostly made at zero, first sign of disease in the crop.
-Experiments that tested two spray treatments also tend to make the first application at first sign of disease, and the second spray between 10 and 25 days later.
-Three spray treatments seemed to be mostly used in experiments where preventative sprays as the first fungicide application were made.
-
-*****
-
-### Mungbean cultivars
-
-Australian mungbean varieties have the following resistance to powdery mildew.
-
-   - Berken: Highly susceptible
-
-   - Crystal: Susceptible
-
-   - Jade: Moderately susceptible
-
-Let's view a stacked bar plot of the number of sprays for both demethylation inhibitors, tebuconazole and propiconazole against each cultivar.
-
-```{r Host_genotype}
-PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole") %>%
-   group_by(host_genotype, fungicide_ai, trial_ref) %>%
-   summarise() %>%
-   count() %>%
-   rename(Treatments = n) %>%
-   ggplot(aes(x = host_genotype, y = Treatments, fill = fungicide_ai)) +
-   xlab("Cultivar") +
-   ylab("N Trials") +
-   ggtitle(label = "Cultivars used in either tebuconazole or propiconazole trials") +
-   geom_col() +
-   scale_fill_usq(name = "Fungicide AI")
-```
-
-#### Genotype yield variability
-
-Does host cultivar significantly impact the yield?
-Let's look at the volatility in yields to see if any cultivar yields better or has greater tolerance to powdery mildew.
-Below we plot distributions of mean trial yields for each cultivar.
-The following plots use data that includes all fungicide types.
-
-First let's look at overall yields for each cultivar, where trial is not a factor, for all treatments (spray and no spray).
-
-```{r yield_vol}
-# Outputs the table and graph
-source("R/yield_volatility.r") # function to investigate the volatility in yields
-# Volatility is the range between the upper and lower 97.5 and 2.5 % quartiles
-YV1 <-
-   yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
-YV1[[2]] + 
-   scale_fill_usq()
-YV1[[3]]
-```
-
-This plot shows a large amount of yield volatility in all cultivars except Green Diamond.
-Green Diamond shows little volatility probably because this cultivar was only used in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trial.
-
-Now let's look at overall yields for each cultivar, where trial is not a factor, in only the no spray control treatments.
-
-```{r yieldVol_control}
-YV2 <-
-   yield_volatility(genotype_by_trial = FALSE, control_only = TRUE)
-YV2[[2]] +
-   scale_fill_usq()
-YV2[[3]]
-```
-
-Volatility of the cultivars are less, albeit fairly similar, in control plots when trial is not considered as a factor.
-
-*****
-
-Let's examine the same plots as above but only for the most commonly used trial site, Hermitage.
-
-```{r yieldVol_Herm}
-YV1_herm <-
-   yield_volatility(
-      genotype_by_trial = FALSE,
-      control_only = FALSE,
-      location = "Hermitage"
-   )
-YV1_herm[[2]] +
-   scale_fill_usq()
-
-YV1_herm[[3]]
-```
-
-Jade shows a large amount of volatility, excluding Green Diamond, Crystal shows the next least volatility.
-
-*****
-
-Let's take a closer look at Crystal with spray management treatments and without.
-
-```{r YieldVol_Crystal}
-YV1_crystal <-
-   yield_volatility(genotype = "Crystal", control_only = FALSE)
-YV1_crystal[[2]] +
-   scale_fill_usq()
-
-YV1_crystal[[3]]
-
-YV2_crystal <-
-   yield_volatility(genotype = "Crystal", control_only = TRUE)
-YV2_crystal[[2]] +
-   scale_fill_usq()
-
-YV2_crystal[[3]]
-```
-
-There is a lot of variation between field trials for Crystal, but little variation within field trials. This indicates that trial should be fit as a random effect when we fit a model to this data.
-
-Let's look at Jade, to see if it differs.
-
-```{r YieldVol_Jade}
-YV1_jade <- yield_volatility("Jade",control_only = FALSE)
-YV1_jade[[2]] +
-   scale_fill_usq()
-
-YV1_jade[[3]]
-```
-
-For Jade there is high variation between trials and with-in.
-Perhaps indicating lower tolerance. 
-Let's look at the same plot with data only from no spray controls to see if the variation is the same.
-
-```{r YieldVol_JadeControl}
-YV2_jade <- yield_volatility("Jade", control_only = TRUE)
-YV2_jade[[2]] +
-   scale_fill_usq()
-
-YV2_jade[[3]]
-```
-
-There still remains a higher volatility in Jade and perhaps a greater shift in the probability curve including fungicide treatments versus probability curves including only no spray controls.
-Indicating that there might be a difference in powdery mildew tolerance between Jade and Crystal.
-
-Overall there seems to be an influence of cultivar.
-However this variation is not as distinct as the variation between trials.
-
-*****
-
-### Row spacing
-
-Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease as well as fungicide timing and efficacy.
-The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows in most cases increased yield significantly.
-This finding has also been shown by several other researchers' work in Queensland and New South Wales as well.
-Eight trials used a row spacing of 0.75&nbsp;meters and tebuconazole as an active ingredient (AI).
-
-```{r row_spacing.m}
-PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole") %>%
-   group_by(fungicide_ai, row_spacing, trial_ref) %>%
-   summarise() %>%
-   count() %>%
-   rename(Trials = n) %>%
-   ggplot(aes(x = as.factor(row_spacing), y = Trials)) +
-   xlab("Row Spacing (m)") +
-   ylab("N Trials") +
-   ggtitle(label = "Trial row spacing using tebuconazole") +
-   geom_col(aes(fill = fungicide_ai),
-            position = "dodge") +
-   scale_fill_usq(name = "Fungicide AI")
-```
-
-Let's plot the row spacing treatments for the response variables yield and disease severity.
-The main questions are:
-
-   * Were there any statistical differences for mungbean yield or powdery mildew severity between row spacing treatments?
-
-   * If not, can we pool certain row spacing that have no significant difference?
-
-```{r RS_severity}
-# Which row spacing leads to the higher disease severity
-PM_MB_means %>%
-   filter(year == 2017 |
-             year == 2018) %>%
-   filter(fungicide_ai == "control") %>%
-   ggplot(aes(y = PM_final_severity, x = factor(row_spacing))) +
-   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
-   ylab("Final severity rating") +
-   xlab("Row spacing (m)") +
-   ggtitle("Powdery mildew variation between different row spacing")
-```
-
-```{r RS_severity_x_trial}
-# Which row spacing leads to the higher disease severity
-PM_MB_means %>%
-   filter(year == 2017 |
-             year == 2018) %>%
-   filter(fungicide_ai == "control") %>%
-   ggplot(aes(y = PM_final_severity, x = factor(row_spacing))) +
-   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
-   facet_grid(cols = vars(location)) +
-   ggtitle("Powdery mildew variation between different row spacing") +
-   ylab("Final severity rating") +
-   xlab("Row spacing (m)")
-```
-
-In the Wellcamp site, wider row spacing reduces PM severity, the other sites it seems there was not enough variation to make a distinction between row spacing treatments.
-
-```{r RS_yield}
-# Which row spacing leads to the higher yield potential
-PM_MB_means %>%
-   filter(year == 2017 |
-             year == 2018) %>%
-   ggplot(aes(
-      y = as.numeric(grain_yield.t.ha.),
-      x = as.factor(row_spacing),
-      colour = location
-   )) +
-   geom_jitter(width = 0.1) +
-   ggtitle("Grain yield results for different row spacing at three locations") +
-   xlab("Row spacing (m)") +
-   ylab("Grain yield (t/ha)") +
-   scale_colour_usq()
-```
-
-The plots seem to imply when yield is limited, presumably by other abiotic factors, there is no effect of row spacing on yield, like in the Hermitage trial.
-However, if the average yield is more than approximately 1 t/ha then smaller row spacing has the potential to provide greater yield per hectare.
-
-Overall row spacing may influence both powdery mildew severity and yield.
-However, in the studies that were conducted, no interaction was found between row spacing, powdery mildew severity and yield.
-That is, the row spacing appeared to increase yield even if the amount of powdery mildew increased and no relationship could be detected between an interaction of the three.
-
-*****
-
-### Yield vs in-season rain
-
-In0-crop rain could be a significant factor which contributes to the end of season grain yield.
-To investigate this effect I will use a linear model (GY ~ SR) where seasonal rainfall represents a specific time frame with respect to planting time.
-Multiple time frames were tested from 20 days prior to planting, to 100 days after planting.
-
-The multiple time frames were tested by a loop over the dates at the start of the season (to 90 days after planting) to find which date fits the best linear model for grain weight and in-crop rainfall.
-The code for this process was moved to be contained within it's own script and can be run as a job as it can take a long time.
-To speed up the computation I split the script into four, ran the jobs and bound the data into one frame.
-The output of the script is saved with the prefix `lmInSeasonRainfall` followed by the time windows the model is run.
-For example `lmInSeasonRainfall_20.40_50.80.csv` holds the model results for start days between 20 and 40 days after planting to end window dates between 50 and 80 days after planting.
-
-This tests when rainfall during the cropping season could be best associated with yield
-
-```{r rainfall_sum_Sstart}
-# The four data files were created from four scripts run as four jobs in RStudio
-# when the four jobs are finished they can be imported and combined into one data.frame
-# source(Rainfall_x_cropYield_s-10.09_e30.65.R)
-# source(Rainfall_x_cropYield_s-10.09_e65.100.R)
-# source(Rainfall_x_cropYield_s10.30_e30.65.R)
-# source(Rainfall_x_cropYield_s10.30_e65.10.R)
-
-lm_rain1 <-
-   read.csv("cache/lmInSeasonRainfall_-10.09_30.64.csv",
+   geom_jitter(width = 1) +
+   geom_smooth()
+
+```
+
+#### Treatment means  
+```{r Herm10_means}
+
+Herm_10_m <- Herm_10_dat %>%
+   group_by(trial_ref, year, location, host_genotype, trial_design, trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
+   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
+              plot_width.m. = mean(plot_width, na.rm = TRUE),
+              plant_density = unique(plant_density),
+              row_spacing = unique(row_spacing),
+              replicates = length(replicate),
+              planting_date = unique(planting_date),
+              emergence_date = NA,
+              flowering_date = NA,
+              pod_fill_date = NA,
+              mid_late_pod_fill = NA,
+              first_sign_disease = unique(first_sign_disease),
+              fungicide_application_1 = unique(fungicide_application_1),
+              fungicide_application_2 = unique(fungicide_application_2),
+              fungicide_application_3 = unique(fungicide_application_3),
+              fungicide_application_4 = unique(fungicide_application_4),
+              fungicide_application_5 = unique(fungicide_application_5),
+             fungicide_application_6 = unique(fungicide_application_6),
+             fungicide_application_6 = unique(fungicide_application_7),
+              total_fungicide = unique(total_fungicide),
+              harvest_date = unique(harvest_date),
+              final_assessment = unique(final_assessment),
+              rating_scale = unique(rating_scale),
+              disease_error = sd(PM_final_severity, na.rm = TRUE),
+              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+              D_error_type = "stdev",
+              raw_graded = NA,
+              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+              Y_error_type = "stdev",
+              AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ host_genotype + factor(n_treatment), data = Herm_10_dat))[2,3],
+             Y_Msquare = anova(lm(grain_yield.t.ha. ~ host_genotype + factor(n_treatment), data = Herm_10_dat))[2,3]
+
+   )
+
+Herm_tentmp <- Herm_10_dat %>% 
+   group_by(host_genotype,n_treatment)%>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE))
+
+Herm_10_m[order(Herm_10_m$n_treatment),"disease_error"] <- Herm_tentmp[order(Herm_tentmp$n_treatment),"disease_error"]
+Herm_10_m[order(Herm_10_m$n_treatment),"yield_error"] <- Herm_tentmp[order(Herm_tentmp$n_treatment),"yield_error"]
+
+Herm_10_m <- fold_data(Herm_10_m, PM_MB_means)
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Herm_10_m, 
+                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
+                            #ignore_columns = c(6,17,30:ncol(Herm_10_m))
+
+write.csv(
+   as.data.frame(Herm_10_m),
+   here("cache/2010 PMmung Hermitage means.csv"), row.names = FALSE
+)
+
+```
+
+### Hermitage 2011
+#### Define treatments
+```{r Herm_2011}
+
+Herm_11 <-
+   as.data.frame(read_xls(
+      here("data/pmhermratings2011.xls"),
+      sheet = "Analyses factor"
+   ), stringsAsFactors = FALSE)
+
+Herm_11 <- Herm_11 %>%
+   mutate(trade_name = 
+             case_when(`Treatment!` == "1 spray AMI-X" ~ "Amistar Xtra",
+                       `Treatment!` == "3 spray AMI-X" ~ "Amistar Xtra",
+                       `Treatment!` == "1 spray SULPHUR" ~ "Kendon",
+                       `Treatment!` == "3 spray SULPHUR" ~ "Kendon",
+                       `Treatment!` == "1 spray FOLICUR" ~ "Folicur",
+                       TRUE ~ "control"))%>%
+   mutate(fungicide_ai = 
+             case_when(`Treatment!` == "1 spray AMI-X" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       `Treatment!` == "3 spray AMI-X" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       `Treatment!` == "1 spray SULPHUR" ~ "sulphur",
+                       `Treatment!` == "3 spray SULPHUR" ~ "sulphur",
+                       `Treatment!` == "1 spray FOLICUR" ~ "tebuconazole",
+                       TRUE ~ "control"))%>%
+   mutate(dose_ai.ha = 
+             case_when(`Treatment!` == "1 spray AMI-X" ~ 120,
+                       `Treatment!` == "3 spray AMI-X" ~ 120,
+                       `Treatment!` == "1 spray SULPHUR" ~ 3000,
+                       `Treatment!` == "3 spray SULPHUR" ~ 3000,
+                       `Treatment!` == "1 spray FOLICUR" ~ 62.35,
+                       TRUE ~ 0))%>%
+   mutate(fungicide_application_1 = 
+             case_when(`Treatment!` == "1 spray AMI-X" ~ as.Date("2011-03-28", format = "%Y-%m-%d"),
+                       `Treatment!` == "3 spray AMI-X" ~ as.Date("2011-02-28", format = "%Y-%m-%d"),
+                       `Treatment!` == "1 spray SULPHUR" ~ as.Date("2011-03-28", format = "%Y-%m-%d"),
+                       `Treatment!` == "3 spray SULPHUR" ~ as.Date("2011-02-28", format = "%Y-%m-%d"),
+                       `Treatment!` == "1 spray FOLICUR" ~ as.Date("2011-03-28", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(`Treatment!` == "3 spray AMI-X" ~ as.Date("2011-03-14", format = "%Y-%m-%d"),
+                       `Treatment!` == "3 spray SULPHUR" ~ as.Date("2011-03-14", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_3 = 
+             case_when(`Treatment!` == "3 spray AMI-X" ~ as.Date("2011-03-14", format = "%Y-%m-%d"),
+                       `Treatment!` == "3 spray SULPHUR" ~ as.Date("2011-03-14", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(total_fungicide = 
+             case_when(`Treatment!` == "1 spray AMI-X" ~ 1,
+                       `Treatment!` == "3 spray AMI-X" ~ 3,
+                       `Treatment!` == "1 spray SULPHUR" ~ 1,
+                       `Treatment!` == "3 spray SULPHUR" ~ 3,
+                       `Treatment!` == "1 spray FOLICUR" ~ 1,
+                       TRUE ~ 0))
+
+```
+
+#### Input trial data  
+```{r Herm11_dataInput}
+Herm_11_dat <- 
+   data.frame(trial_ref = "mung1011/01",
+              year = "2011",
+              location = "Hermitage",
+              host_genotype = Herm_11$`Cultivar!`,
+              trial_design = "RCB",
+              plot_length = 11,
+              plot_width = 4,
+              plant_density = NA,
+              row_spacing = 0.75,
+              replicate = Herm_11$`Rep!`,
+              planting_date = as.Date("2011-01-24", format = "%Y-%m-%d"),
+              emergence_date = NA,
+              flowering_date = as.Date("2011-03-22", format = "%Y-%m-%d"),
+              pod_fill_date = NA,
+              mid_late_pod_fill = NA,
+              first_sign_disease = as.Date("2011-03-28", format = "%Y-%m-%d"),
+              trade_name = as.factor(Herm_11$trade_name),
+              fungicide_ai = Herm_11$fungicide_ai,
+              dose_ai.ha = Herm_11$dose_ai.ha,
+              n_treatment = Herm_11$Tr,
+              fungicide_application_1 = Herm_11$fungicide_application_1,
+              fungicide_application_2 = Herm_11$fungicide_application_2,
+              fungicide_application_3 = Herm_11$fungicide_application_3,
+              total_fungicide = Herm_11$total_fungicide,
+              harvest_date = as.Date("2011-04-25", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2011-04-11", format = "%Y-%m-%d"),
+              PM_final_severity = Herm_11$`P.M. 11  w.a.p.`,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = Herm_11$`Yld Kg/ha`,
               stringsAsFactors = FALSE)
-lm_rain2 <-
-   read.csv("cache/lmInSeasonRainfall_-10.09_65.100.csv",
+
+```
+
+#### AUDPC curve
+```{r Herm_audpc, warning=FALSE}
+
+Herm_11_dat <- cbind(Herm_11_dat,
+                     AUDPC = apply(data.frame(zero = rep(0,42),
+                                       wap11 = Herm_11[,c("P.M. 11  w.a.p.")]-1),1, 
+                            FUN = audpc, dates = c((as.Date("2011-03-28", format = "%Y-%m-%d")-7)- 
+                                                      as.Date("2011-01-24", format = "%Y-%m-%d"),
+                                                   77)
+                     ),
+                     AUDPS = apply(data.frame(zero = rep(0,42),
+                                       wap11 = Herm_11[,c("P.M. 11  w.a.p.")]-1),
+                                        1, 
+                                   FUN = audps, 
+                                        dates = c((as.Date("2011-03-28", format = "%Y-%m-%d")-7)- 
+                                                      as.Date("2011-01-24", format = "%Y-%m-%d"),
+                                                  77)
+                                        )
+                          )
+
+Herm_11$PM_zero <- 1
+Herm11_plot <- melt(Herm_11, id.vars = c("Treatment!", "Cultivar!","Tr","Rep!","fungicide_ai","total_fungicide"),
+                  measure.vars = c("PM_zero","P.M. 11  w.a.p."))
+
+Herm11_plot <- Herm11_plot %>%
+   mutate(T_var = case_when(variable == "PM_zero" ~ 
+                               as.numeric((Herm_11_dat$first_sign_disease[1]-7) - Herm_11_dat$planting_date[1]),
+                            variable == "P.M. 11  w.a.p." ~ 11*7))
+
+Herm11_plot$`Treatment!` <- as.factor(Herm11_plot$`Treatment!`)
+Herm11_plot %>%
+   ggplot(aes(x = T_var, y = value, color = `Treatment!`, shape = `Treatment!`))+
+   geom_jitter(width = .5, height = 0.05)+
+   geom_smooth(method = "lm")
+
+```
+
+#### Treatment means
+```{r Herm11_means}
+Herm_11_dat[Herm_11_dat$n_treatment == 5, "n_treatment"] <- 1
+Herm_11_dat[Herm_11_dat$n_treatment == 12, "n_treatment"] <- 8
+
+Herm_11_m <- Herm_11_dat %>%
+   group_by(trial_ref, year, location, host_genotype, trial_design, trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
+   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
+              plot_width.m. = mean(plot_width, na.rm = TRUE),
+              plant_density = unique(plant_density),
+              row_spacing = unique(row_spacing),
+              replicates = length(replicate),
+              planting_date = unique(planting_date),
+              emergence_date = NA,
+              flowering_date = unique(flowering_date),
+              pod_fill_date = NA,
+              mid_late_pod_fill = NA,
+              first_sign_disease = unique(first_sign_disease),
+              fungicide_application_1 = unique(fungicide_application_1),
+              fungicide_application_2 = unique(fungicide_application_2),
+              fungicide_application_3 = unique(fungicide_application_3),
+              total_fungicide = unique(total_fungicide),
+              harvest_date = unique(harvest_date),
+              final_assessment = unique(final_assessment),
+              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+              rating_scale = unique(rating_scale),
+              disease_error = sd(PM_final_severity, na.rm = TRUE),
+              D_error_type = "stdev",
+              grain_yield.t.ha. = mean(grain_yield.t.ha./1000, na.rm = TRUE),
+              raw_graded = NA,
+              yield_error = sd(grain_yield.t.ha./1000, na.rm = TRUE),
+              Y_error_type = "stdev",
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ host_genotype + factor(n_treatment), 
+                               data = Herm_11_dat[Herm_11_dat$fungicide_ai == "tebuconazole" | 
+                                                        Herm_11_dat$fungicide_ai == "control" ,]))[2,3],
+              Y_Msquare = anova(lm(grain_yield.t.ha./1000 ~ factor(n_treatment) + host_genotype, 
+                                data = Herm_11_dat[Herm_11_dat$fungicide_ai == "tebuconazole" | 
+                                                        Herm_11_dat$fungicide_ai == "control" ,]))[1,3]
+   )
+
+Herm_tmp <- Herm_11_dat %>% 
+   group_by(host_genotype,n_treatment)%>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha./1000, na.rm = TRUE))
+
+Herm_11_m[order(Herm_11_m$n_treatment),"disease_error"] <- Herm_tmp[order(Herm_tmp$n_treatment),"disease_error"]
+Herm_11_m[order(Herm_11_m$n_treatment),"yield_error"] <- Herm_tmp[order(Herm_tmp$n_treatment),"yield_error"]
+
+Herm_11_m <- fold_data(Herm_11_m, PM_MB_means)
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Herm_11_m, 
+                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
+
+write.csv(
+   as.data.frame(Herm_11_m),
+   here("cache/2011 PMmung Herm means.csv"), row.names = FALSE
+)
+
+```
+
+### Kingaroy 2011
+```{r King_11}
+King_11 <-
+   as.data.frame(read_xls(
+      here("data/pmKing ratings2011.xls"),
+      sheet = "analyses"
+   ), stringsAsFactors = FALSE)
+
+tmp1 <- do.call(rbind.data.frame, strsplit(King_11$`Treatment!`, " "))
+colnames(tmp1) <- c("cultivar" , "spray_n", "spray", "fungicide")
+King_11 <- cbind(tmp1, King_11)
+King_11$spray_n <- as.numeric(as.character(King_11$spray_n))
+```
+
+#### Define treatment data
+```{r King_11_define}
+King_11 <- King_11 %>%
+   mutate(trade_name = 
+             case_when(fungicide == "AMIS-X" ~ "Amistar Xtra",
+                       fungicide == "SULPHUR" ~ "Kendon",
+                       fungicide == "FOLICUR" ~ "Folicur",
+                       TRUE ~ "control"))%>%
+   mutate(fungicide_ai = 
+             case_when(fungicide == "AMIS-X" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       fungicide == "SULPHUR" ~ "sulphur",
+                       fungicide == "FOLICUR" ~ "tebuconazole",
+                       TRUE ~ "control"))%>%
+   mutate(dose_ai.ha = 
+             case_when(fungicide == "AMIS-X" ~ 120,
+                       fungicide == "SULPHUR" ~ 3000,
+                       fungicide == "FOLICUR" ~ 62.35,
+                       TRUE ~ 0))%>%
+   mutate(fungicide_application_1 = 
+             case_when(spray_n == 1 ~ as.Date("2011-03-23", format = "%Y-%m-%d"),
+                       spray_n == 2 ~ as.Date("2011-03-23", format = "%Y-%m-%d"),
+                       spray_n == 3 ~ as.Date("2011-03-09", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+
+   mutate(fungicide_application_2 = 
+             case_when(spray_n == 2 ~ as.Date("2011-04-13", format = "%Y-%m-%d"),
+                       spray_n == 3 ~ as.Date("2011-03-30", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_3 = 
+             case_when(spray_n == 3 ~ as.Date("2011-04-12", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))
+
+```
+
+#### Input trial data
+```{r King_11_input}
+King_11_dat <- 
+   data.frame(trial_ref = "mung1011/02",
+              year = "2011",
+              location = "Kingaroy",
+              host_genotype = King_11$cultivar,
+              trial_design = "RCB",
+              plot_length = 11,
+              plot_width = 4,
+              plant_density = NA,
+              row_spacing = 0.75,
+              replicate = King_11$`rep!`,
+              planting_date = as.Date("2011-02-02", format = "%Y-%m-%d"),
+              emergence_date = NA,
+              flowering_date = NA,
+              pod_fill_date = NA,
+              mid_late_pod_fill = NA,
+              first_sign_disease = as.Date("2011-03-22", format = "%Y-%m-%d"),
+              trade_name = as.factor(King_11$trade_name),
+              fungicide_ai = King_11$fungicide_ai,
+              dose_ai.ha = King_11$dose_ai.ha,
+              n_treatment = King_11$`trt!`,
+              fungicide_application_1 = King_11$fungicide_application_1,
+              fungicide_application_2 = King_11$fungicide_application_2,
+              fungicide_application_3 = King_11$fungicide_application_3,
+              total_fungicide = King_11$spray_n,
+              harvest_date = as.Date(NA),
+              final_assessment = as.Date("2011-05-11", format = "%Y-%m-%d"),
+              PM_final_severity = King_11$`14 w.a.p.`,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(King_11$`Yld kg ha`),
               stringsAsFactors = FALSE)
-lm_rain3 <-
-   read.csv("cache/lmInSeasonRainfall_10.30_30.64.csv",
+```
+
+#### AUDPC curve
+```{r King11_AUDPC, warning=FALSE}
+library(ggplot2)
+
+King_11_dat <- cbind(King_11_dat,
+                     AUDPC = apply(data.frame(zero = 0,
+                                              King_11[,c("9 w.a.p.","11 w.a.p.","12 w.a.p.","14 w.a.p.")]-1),
+                                   1, 
+                                   FUN = audpc,
+                                   dates = c((King_11_dat$first_sign_disease[1]-7)-
+                                                King_11_dat$planting_date[1],
+                                             9*7,11*7,12*7,14*7)
+                                   ),
+                     AUDPS = apply(data.frame(zero = 0,
+                                                   King_11[,c("9 w.a.p.","11 w.a.p.","12 w.a.p.","14 w.a.p.")]-1),
+                                        1, 
+                                        FUN = audps, 
+                                        dates = c((King_11_dat$first_sign_disease[1]-7)-
+                                                     King_11_dat$planting_date[1],
+                                                  9*7,11*7,12*7,14*7)
+                                        )
+                          )
+
+King_11$PM_zero <- 1
+King11_plot <- reshape2::melt(King_11, id.vars = c("Treatment!","cultivar","rep!","spray_n","fungicide"),
+                  measure.vars = c("PM_zero","9 w.a.p.","11 w.a.p.","12 w.a.p.","14 w.a.p."))
+
+King11_plot <- King11_plot %>%
+   mutate(T_var = case_when(variable == "PM_zero" ~ 
+                               as.numeric((King_11_dat$first_sign_disease[1]-7) - King_11_dat$planting_date[1]),
+                            variable == "9 w.a.p." ~ 9*7,
+                            variable == "11 w.a.p." ~ 11*7,
+                            variable == "12 w.a.p." ~ 12*7,
+                            variable == "14 w.a.p." ~ 14 *7)
+   )
+
+King11_plot$Treat <- paste0(King11_plot$fungicide,King11_plot$spray_n)
+
+King11_plot %>%
+   ggplot(aes(x = T_var, y = value, color = Treat, shape = Treat))+
+   geom_jitter(width = 0.7, height = 0.07)+
+   geom_smooth()
+
+```
+
+#### Treatment means  
+```{r King_11_means}
+King_11_m <- King_11_dat %>%
+   group_by(host_genotype, fungicide_ai,n_treatment) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             trade_name = unique(trade_name),
+             location = unique(location),
+             trial_design = unique(trial_design),
+             dose_ai.ha = unique(dose_ai.ha),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
+              plot_width.m. = mean(plot_width, na.rm = TRUE),
+              plant_density = unique(plant_density),
+              row_spacing = unique(row_spacing),
+              replicates = length(replicate),
+              planting_date = unique(planting_date),
+              emergence_date = NA,
+              flowering_date = unique(flowering_date),
+              pod_fill_date = NA,
+              mid_late_pod_fill = NA,
+              first_sign_disease = unique(first_sign_disease),
+              fungicide_application_1 = unique(fungicide_application_1),
+              fungicide_application_2 = unique(fungicide_application_2),
+              fungicide_application_3 = unique(fungicide_application_3),
+              total_fungicide = unique(total_fungicide),
+              harvest_date = unique(harvest_date),
+              final_assessment = unique(final_assessment),
+              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+              rating_scale = unique(rating_scale),
+              #disease_error = sd(PM_final_severity, na.rm = TRUE),  # this is commented because it never worked for some reason. 
+              D_error_type = "stdev",
+              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE)/1000,
+              raw_graded = NA,
+              #yield_error = sd(grain_yield.t.ha./1000, na.rm = TRUE),  # this is commented because it never worked for some reason. 
+              Y_error_type = "stdev",
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ host_genotype + factor(n_treatment), 
+                               data = King_11_dat[King_11_dat$fungicide_ai == "tebuconazole" | 
+                                                        King_11_dat$fungicide_ai == "control" ,]))[2,3],
+              Y_Msquare = anova(lm(grain_yield.t.ha./1000 ~ factor(n_treatment) + host_genotype, 
+                                data = King_11_dat[King_11_dat$fungicide_ai == "tebuconazole" | 
+                                                        King_11_dat$fungicide_ai == "control" ,]))[1,3])
+
+# For some wierd reason standard deviations are comming back NA in the code above
+# Because of n_treatment being converted to a factor I need to wrangle carefully here
+King_tmp <- King_11_dat %>%
+   group_by(host_genotype, fungicide_ai,n_treatment) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha./1000, na.rm = TRUE))
+
+King_11_m <- left_join(King_11_m,King_tmp)
+King_11_m <- fold_data(King_11_m, PM_MB_means)
+King_11_m <- copy_class(PM_MB_means,King_11_m)
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = King_11_m, 
+                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
+
+write.csv(
+   King_11_m,
+   here("cache/2011 PMmung Kingaroy means.csv"),row.names = FALSE
+)
+
+```
+
+### Goolhi 2013
+#### Convert disease scores
+```{r Goolhi_2013}
+
+for(D_assessment in c("16 DAT1", "33DAT1")){
+
+# Import final disease survey
+Goolhi.13 <-
+   as.data.frame(
+      read_xlsx(
+         path = here("data/AM1305 Fungicides for powdery mildew in mungbean - Goolhi.xlsx"),
+         sheet = D_assessment,
+         range = "A15:AG75",
+         col_names = TRUE
+      )
+   )
+
+Goolhi.13 <- Goolhi.13[order(Goolhi.13[,1],Goolhi.13[,2],Goolhi.13[,3],Goolhi.13[,4]),]
+
+# Replace empty cells / NAs with zeros
+for (i in 7:33) {
+   Goolhi.13[is.na(Goolhi.13[, i]), i] <- 0
+}
+
+# This table gives the column references for each respective 
+# location in the canopy
+# Calculate incidence
+#     Sites      1     2     3
+# low canopy  c(7:9, 16:18, 25:27)
+# mid canopy c(10:12, 19:21, 28:30)
+# upp canopy c(13:15, 22:24, 31:33)
+
+incidence1 <-
+   vector(mode = "numeric", length = length(Goolhi.13[, 1]))
+
+# Convert disease survey data to 1-9 Incidence rating scale
+for (i in seq_along(incidence1)) {
+   # when incidence = 1
+   if (all(Goolhi.13[i, 7:33] == 0)) {
+      incidence1[i] <- 1
+      next()
+   }
+
+   # when incidence = 2
+   if (all(Goolhi.13[i, c(10:15, 19:24, 28, 33)] == 0) &&
+       (sum(Goolhi.13[i, c(7:9, 16:18, 25:27)] > 0) /
+        length(Goolhi.13[i, c(7:9, 16:18, 25:27)])) <= 0.75) {
+      incidence1[i] <- 2
+      next()
+   }
+
+   # when incidence = 3
+   if (all(Goolhi.13[i, c(13:15, 22:24, 31:33)] == 0) &&
+       sum(Goolhi.13[i, c(10:12, 19:21, 28:30)] != 0) <= 3 &&
+       (sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] > 0) /
+        length(Goolhi.13[i, c(7:12, 16:21, 25:30)])) > 0.75) {
+      incidence1[i] <- 3
+   } else{
+      # if it is in the lower half of the canopy and in less than 75% of plants then incidence = 2.5
+      if (all(Goolhi.13[i, c(13:15, 22:24, 31:33)] == 0) &&
+          sum(Goolhi.13[i, c(10:12, 19:21, 28:30)] != 0) <= 3 &&
+          (sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] > 0) /
+           length(Goolhi.13[i, c(7:12, 16:21, 25:30)])) <= 0.75) {
+         incidence1[i] <- 2.5
+         next()
+      }
+   }
+
+   # when incidence = 4
+   if (all(Goolhi.13[i, c(13:15, 22:24, 31:33)] == 0) &&
+       sum(Goolhi.13[i, c(10:12, 19:21, 28:30)] != 0) > 3 &&
+       (sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] > 0) /
+        length(Goolhi.13[i, c(7:12, 16:21, 25:30)])) <= 0.75) {
+      incidence1[i] <- 4
+      next()
+   }
+
+   # when incidence = 5
+   if (all(Goolhi.13[i, c(13:15, 22:24, 31:33)] == 0) &&
+       sum(Goolhi.13[i, c(10:12, 19:21, 28:30)] != 0) > 3 &&
+       (sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] > 0) /
+        length(Goolhi.13[i, c(7:12, 16:21, 25:30)])) > 0.75 &&
+       any(Goolhi.13[i, c(7:12, 16:21, 25:30)] == 0)) {
+      incidence1[i] <- 5
+      next()
+   }
+
+   # when incidence = 6
+   if (all(Goolhi.13[i, c(13:15, 22:24, 31:33)] == 0) &&
+       all(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0)) {
+      incidence1[i] <- 6
+      next()
+   }
+
+   # when incidence = 7
+   if (sum(Goolhi.13[i, c(13:15, 22:24, 31:33)] != 0) <= 3 &&
+       all(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0)) {
+      incidence1[i] <- 7
+      next()
+   }
+
+   # when incidence = 8
+   if ((sum(Goolhi.13[i, c(13:15, 22:24, 31:33)] != 0) > 3 |
+        sum(Goolhi.13[i, c(13:15, 22:24, 31:33)]) <= 200) &&
+       all(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0) &&
+       (sum(Goolhi.13[i, 7:33] > 0) /
+        length(Goolhi.13[i, 7:33]) > 0.75) &&
+       sum(Goolhi.13[i, 7:33]) <= 2000) {
+      incidence1[i] <- 8
+      next()
+   }
+
+   # when incidence = 9
+   if (sum(Goolhi.13[i, c(13:15, 22:24, 31:33)] != 0) > 3 &&
+       all(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0) &&
+       (sum(Goolhi.13[i, 7:33] > 0) /
+        length(Goolhi.13[i, 7:33]) > 0.75) &&
+       sum(Goolhi.13[i, 7:33]) > 2000) {
+      incidence1[i] <- 9
+      next()
+   }
+
+   # if not in the lower canopy but small colonies in mid and upper canopy
+   if (all(Goolhi.13[i, c(7:9, 16:18, 25:27)] == 0) &&
+       (sum(Goolhi.13[i, c(10:15, 19:24, 28, 33)] > 0) /
+        length(Goolhi.13[i, 7:33]) <= 0.5)) {
+      incidence1[i] <- 2.5
+      next()
+   }
+
+   # incidence = 7.5
+   if (sum(Goolhi.13[i, c(13:15, 22:24, 31:33)] != 0) > 3 &&
+       sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0) > 10 &&
+       any(Goolhi.13[i, c(7:12, 16:21, 25:30)] == 0) &&
+       (sum(Goolhi.13[i, 7:33] > 0) /
+        length(Goolhi.13[i, 7:33]) > 0.7) &&
+       sum(Goolhi.13[i, 7:33]) <= 2000) {
+      incidence1[i] <- 7.5
+      next()
+   }
+
+   # incidence = 6.5
+   if (sum(Goolhi.13[i, c(13:15, 22:24, 31:33)] != 0) > 3 &&
+       sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0) <= 12 &&
+       sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0) >= 10 &&
+       (sum(Goolhi.13[i, 7:33] > 0) /
+        length(Goolhi.13[i, 7:33]) <= 0.75) &&
+       sum(Goolhi.13[i, 7:33]) <= 2000) {
+      incidence1[i] <- 6.5
+      next()
+   }
+
+   # incidence = 4.5
+   if (sum(Goolhi.13[i, c(13:15, 22:24, 31:33)] != 0) > 3 &&
+       sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0) < 10 &&
+       sum(Goolhi.13[i, c(7:12, 16:21, 25:30)] != 0) > 5 &&
+       (sum(Goolhi.13[i, 7:33] > 0) /
+        length(Goolhi.13[i, 7:33]) <= 0.75) &&
+       sum(Goolhi.13[i, 7:33]) <= 2000) {
+      incidence1[i] <- 4.5
+      next()
+   } else{
+      # If none of the conditions are met give the incidence zero
+      incidence1[i] <- 0
+   }
+
+}
+
+# check data to make sure there are no zeros
+incidence1
+length(Goolhi.13[incidence1 == 0, 1])
+Goolhi.13[incidence1 == 0, ]
+hist(incidence1)
+
+# Re-format data-frame
+if(D_assessment == "16 DAT1"){
+Goolhi.13D <- Goolhi.13[,c("Treat", "Rep", "Run", "Plot")]
+Goolhi.13D$Inc_16D <-  incidence1
+
+}
+
+if(D_assessment == "33DAT1"){
+Goolhi.13D$Inc_33D <-  incidence1
+}
+}
+
+#_____________________
+# Read in Harvest data
+Goolhi.13Y <-
+   as.data.frame(
+      read_xlsx(
+         path = here("data/AM1305 Fungicides for powdery mildew in mungbean - Goolhi.xlsx"),
+         sheet = "Yield",
+         range = "A15:F75",
+         col_names = TRUE
+      )
+   )
+Goolhi.13Y <- Goolhi.13Y[order(Goolhi.13Y[,1],Goolhi.13Y[,2],Goolhi.13Y[,3],Goolhi.13Y[,4]),]
+
+# Join disease and Yield data
+Goolhi_13 <- left_join(Goolhi.13D, Goolhi.13Y)
+
+```
+
+#### Define treatment data
+```{r GoolhiDefine}
+
+Goolhi_13 <- Goolhi_13 %>%
+   mutate(trade_name = 
+             case_when(Treat == "1" ~ "control",
+                       Treat == "2" ~ "Spin-flo",
+                       Treat == "3" ~ "Tilt",
+                       Treat == "4" ~ "Amistar Xtra",
+                       Treat == "5" ~ "Amistar Xtra + adj",
+                       Treat == "6" ~ "Cabrio",
+                       Treat == "7" ~ "Spin-flo",
+                       Treat == "8" ~ "Tilt",
+                       Treat == "9" ~ "Amistar Xtra + adj",
+                       Treat == "10" ~ "Cabrio",
+                       Treat == "11" ~ "Tilt",
+                       TRUE ~ "other"))%>%
+   mutate(fungicide_ai = 
+             case_when(Treat == "1" ~ "control",
+                       Treat == "2" ~ "carbendazim",
+                       Treat == "3" ~ "propiconazole",
+                       Treat == "4" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "5" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "6" ~ "pyraclostrobin",
+                       Treat == "7" ~ "carbendazim",
+                       Treat == "8" ~ "propiconazole",
+                       Treat == "9" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "10" ~ "pyraclostrobin",
+                       Treat == "11" ~ "propiconazole",
+                       TRUE ~ "other"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Treat == "1" ~ 0,
+                       Treat == "2" ~ 250,
+                       Treat == "3" ~ 62.5,
+                       Treat == "4" ~ 40,
+                       Treat == "5" ~ 40,
+                       Treat == "6" ~ 125,
+                       Treat == "7" ~ 250,
+                       Treat == "8" ~ 62.5,
+                       Treat == "9" ~ 40,
+                       Treat == "10" ~ 125,
+                       Treat == "11" ~ 62.5,
+                       TRUE ~ 0))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Treat == "1" ~ as.Date(NA),
+                       Treat == "2" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "3" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "4" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "5" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "6" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "7" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Treat == "7" ~ as.Date("2013-04-13", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-04-13", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-04-13", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-04-13", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-04-13", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_3 = 
+             case_when(Treat == "11" ~ as.Date("2013-04-27", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Treat == "1" ~ 0,
+                       Treat == "7" ~ 2,
+                       Treat == "8" ~ 2,
+                       Treat == "9" ~ 2,
+                       Treat == "10" ~ 2,
+                       Treat == "11" ~ 3,
+                       TRUE ~ 1))
+
+```
+
+#### Input trial data
+```{r Goolhis_TrialData}
+
+Goolhi_13_dat <- 
+   data.frame(trial_ref = "AM1305",
+              year = "2013",
+              location = "Goolhi",
+              host_genotype = "Crystal",
+              trial_design = "RB",
+              plot_length = 12,
+              plot_width = 4,
+              plant_density = NA,
+              row_spacing = 0.33,
+              replicate = Goolhi_13$Rep,
+              planting_date = as.Date("2013-01-23", format = "%Y-%m-%d"),
+              emergence_date = NA,
+              flowering_date = as.Date("2013-04-04", format = "%Y-%m-%d"),
+              pod_fill_date = as.Date("2013-04-18", format = "%Y-%m-%d"),
+              mid_late_pod_fill = NA,
+              first_sign_disease = as.Date("2013-03-25", format = "%Y-%m-%d"),
+              trade_name = as.factor(Goolhi_13$trade_name),
+              fungicide_ai = Goolhi_13$fungicide_ai,
+              dose_ai.ha = Goolhi_13$dose_ai.ha,
+              n_treatment = Goolhi_13$Treat,
+              fungicide_application_1 = Goolhi_13$fungicide_application_1,
+              fungicide_application_2 = Goolhi_13$fungicide_application_2,
+              fungicide_application_3 = Goolhi_13$fungicide_application_3,
+              total_fungicide = Goolhi_13$spray_n,
+              harvest_date = as.Date("2013-06-20", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2013-04-30", format = "%Y-%m-%d"),
+              PM_final_severity = Goolhi_13$Inc_33D,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(Goolhi_13$`Yield Kg/ha`)/1000
+              )
+
+```
+
+#### AUDPC curve
+```{r Goolhi13_AUDPC}
+Goolhi_13_dat <- cbind(Goolhi_13_dat,
+                          AUDPC = apply(data.frame(zero = 0,
+                                                   Goolhi_13[,c("Inc_16D","Inc_33D")]-1),
+                                        1, 
+                                        FUN = audpc, 
+                                        dates = c(1,16,33)
+                                        ),
+                     AUDPS = apply(data.frame(zero = 0,
+                                                   Goolhi_13[,c("Inc_16D","Inc_33D")]-1),
+                                        1, 
+                                        FUN = audps, 
+                                        dates = c(1,16,33)
+                                        )
+                          )
+
+```
+
+#### Calculating the treatment means
+```{r Goolhis_means}
+
+Goolhi_13_m <- Goolhi_13_dat %>%
+   group_by(trial_ref, year, location, host_genotype, trial_design, 
+            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
+   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
+              plot_width.m. = mean(plot_width, na.rm = TRUE),
+              plant_density = unique(plant_density),
+              row_spacing = unique(row_spacing),
+              replicates = length(replicate),
+              planting_date = unique(planting_date),
+              emergence_date = NA,
+              flowering_date = unique(flowering_date),
+              pod_fill_date = unique(pod_fill_date),
+              mid_late_pod_fill = unique(mid_late_pod_fill),
+              first_sign_disease = unique(first_sign_disease),
+              fungicide_application_1 = unique(fungicide_application_1),
+              fungicide_application_2 = unique(fungicide_application_2),
+              fungicide_application_3 = unique(fungicide_application_3),
+              total_fungicide = unique(total_fungicide),
+              harvest_date = unique(harvest_date),
+              final_assessment = unique(final_assessment),
+              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+              rating_scale = unique(rating_scale),
+              #disease_error = sd(PM_final_severity, na.rm = TRUE), # Commented because were not being calculated and included in the summary function
+              D_error_type = "stdev",
+              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+              raw_graded = NA,
+              #yield_error = sd(grain_yield.t.ha., na.rm = TRUE), # Commented because were not being calculated and included in the summary function
+              Y_error_type = "stdev",
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ factor(n_treatment), 
+                               data = Goolhi_13_dat[Goolhi_13_dat$fungicide_ai == "propiconazole" | 
+                                                        Goolhi_13_dat$fungicide_ai == "control" ,]))[1,3],
+              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), 
+                                data = Goolhi_13_dat[Goolhi_13_dat$fungicide_ai == "propiconazole" | 
+                                                        Goolhi_13_dat$fungicide_ai == "control" ,]))[1,3]
+   )
+
+# For some wierd reason standard deviations are comming back NA in the code above
+# Because of n_treatment being converted to a factor I need to wrangle carefully here
+Goolhi_tmp <- Goolhi_13_dat %>%
+   group_by(n_treatment) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE))
+
+Goolhi_13_m <- left_join(Goolhi_13_m, Goolhi_tmp)
+
+Goolhi_13_m <- fold_data(Goolhi_13_m, PM_MB_means)
+Goolhi_13_m <- Goolhi_13_m[Goolhi_13_m$trade_name != "other",]
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Goolhi_13_m, 
+                            new_data_column = c("planting_date","AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
+
+write.csv(
+   Goolhi_13_m,
+   here("cache/AM1305_Goolhi_means.csv"),row.names = FALSE
+)
+
+```
+
+### Mary's Mount 2013
+#### Convert disease scores
+```{r MarysM_13_Convertdisease}
+
+for(D_assess in c("18 DAT1 18-3-2013","19 DAT1 19-3-2013")){
+
+# Import  disease survey
+MarysM.13D <-
+   as.data.frame(
+      read_xlsx(
+         path = here("data/AM1304 Fungicides for powdery mildew in mungbean - Marys Mount.xlsx"),
+         sheet = D_assess,
+         range = "A14:DC72",
+         col_names = TRUE
+      )
+   )
+
+colnames(MarysM.13D)[1:4] <- c("Treat", "Rep", "Run", "Plot")
+MarysM.13D <- MarysM.13D[order(MarysM.13D[,1],MarysM.13D[,2],MarysM.13D[,3],MarysM.13D[,4]),]
+
+if(D_assess == "18 DAT1 18-3-2013"){
+   col_ref <- 33:57
+   col_ref2 <- 7:31
+}
+if(D_assess == "19 DAT1 19-3-2013"){
+   col_ref <- 58:107
+   col_ref2 <- 7:56
+}
+
+# Replace empty cells / NAs with zeros
+for (i in c(col_ref2,col_ref)) {
+   MarysM.13D[is.na(MarysM.13D[, i]), i] <- 0
+}
+
+incidence2 <-
+   vector(mode = "numeric", length = length(MarysM.13D[, 1]))
+
+# Convert disease survey data to 1-9 Incidence rating scale
+for (i in seq_along(incidence2)) {
+   # incidence = 1
+   if (all(MarysM.13D[i, col_ref] == 0)) {
+      incidence2[i] <- 1
+      next()
+   }
+
+   # incidence = 2
+   if (sum(MarysM.13D[i, col_ref] == 2) == 0 &&
+       sum(MarysM.13D[i, col_ref] == 1) == 0 &&
+       (sum(MarysM.13D[i, col_ref] == 3) /
+        length(MarysM.13D[i, col_ref])) <= 0.75) {
+      incidence2[i] <- 2
+      next()
+   }
+
+   # incidence = 3
+   if (sum(MarysM.13D[i, col_ref] == 1) == 0 &&
+       sum(MarysM.13D[i, col_ref] == 2) <= 8 &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref])) > 0.75) {
+      incidence2[i] <- 3
+   } else{
+      # if it is in the lower half of the canopy and in less than 75% of plants then incidence = 2.5
+      if (sum(MarysM.13D[i, col_ref] == 1) == 0 &&
+          sum(MarysM.13D[i, col_ref] == 2) <= 8 &&
+          sum(MarysM.13D[i, col_ref] == 3) > 0 &&
+          (sum(MarysM.13D[i, col_ref] > 0) /
+           length(MarysM.13D[i, col_ref])) <= 0.75) {
+         incidence2[i] <- 2.5
+         next()
+      }
+   }
+
+   # incidence = 4
+   if (sum(MarysM.13D[i, col_ref] == 1) == 0 &&
+       sum(MarysM.13D[i, col_ref] == 2) > 0 &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref])) <= 0.75) {
+      incidence2[i] <- 4
+      next()
+   }
+
+   # incidence = 5
+   if (sum(MarysM.13D[i, col_ref] == 1) == 0 &&
+       sum(MarysM.13D[i, col_ref] == 2) > 0 &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref])) > 0.75) {
+      incidence2[i] <- 5
+      next()
+   }
+
+   # incidence = 6
+   if (sum(MarysM.13D[i, col_ref] == 1) == 0 &&
+       sum(MarysM.13D[i, col_ref] >= 2) > 0 &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref])) > 0.95) {
+      incidence2[i] <- 6
+      next()
+   }
+
+   # incidence = 7
+   if (sum(MarysM.13D[i, col_ref] == 1) <= 8 &&
+       sum(MarysM.13D[i, col_ref] >= 2) > 0 &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref])) > 0.95) {
+      incidence2[i] <- 7
+      next()
+   }
+
+   # incidence = 8
+   if (sum(MarysM.13D[i, col_ref] >= 1) > 0 &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref])) > 0.75) {
+      incidence2[i] <- 8
+      next()
+   }
+
+   # incidence = 9
+   if (sum(MarysM.13D[i, col_ref] >= 1) > 0 &&
+       sum(MarysM.13D[i, col_ref2] >= (10 * 5 * 100 * 0.75)) &&
+       # ten leaves from 5 sample sites with a maximum % leaf area infected with PM of 100% * 0.75 as a threshold for leaf drop
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref])) > 0.75) {
+      incidence2[i] <- 9
+      next()
+   }
+
+   # if there are few (< 10%) leaves with very small infections in all parts of the canopy OR
+   # if there is a stray colony on a upper leaf in addition to all lower
+   if (sum(MarysM.13D[i, col_ref] == 3) >= 1 &&
+       sum(MarysM.13D[i, col_ref] == 1) <= 2 &&
+       sum(MarysM.13D[i, col_ref] == 2) <= 2 &&
+       sum(MarysM.13D[i, col_ref2]) <= 150) {
+      incidence2[i] <- 2.5
+      next()
+   }
+
+   # incidence = 7.5  In the upper canopy with less than 75% plants infected
+   if (sum(MarysM.13D[i, col_ref] == 3) > 0 &&
+       sum(MarysM.13D[i, col_ref] == 2) > 0 &&
+       sum(MarysM.13D[i, col_ref] == 1) > 0 &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref]) <= 0.75) &&
+       sum(MarysM.13D[i, col_ref2]) >= 2000) {
+      incidence2[i] <- 7.5
+      next()
+   }
+   #
+   # incidence = 6.5
+   if (sum(MarysM.13D[i, col_ref] == 1) > 3 &&
+       sum(MarysM.13D[i, col_ref] >= 2) > 0 &&
+       sum(MarysM.13D[i, col_ref2] <= 500)  &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref]) >= 0.65)) {
+      incidence2[i] <- 6.5
+      next()
+   }
+   #
+   #
+   # incidence = 4.5 If PM is in the the lower and mid-canopy in less than 75% of plants and one or two in the upper canopy
+   if (sum(MarysM.13D[i, col_ref] == 1) <= 3 &&
+       sum(MarysM.13D[i, col_ref] >= 2) > 0 &&
+       (sum(MarysM.13D[i, col_ref] > 0) /
+        length(MarysM.13D[i, col_ref])) <= 0.75) {
+      incidence2[i] <- 4.5
+      next()
+   } else{
+      # If none of the conditions are met give the incidence zero
+      incidence2[i] <- 0
+   }
+
+}# End of incidence2 loop
+
+if(any(incidence2 == 0)){
+   warning("Code caluculated incidence on '0' which is off the incidence scale")
+}
+
+# Re-format data-frame
+if(D_assess == "18 DAT1 18-3-2013"){
+MarysM.13D.1 <- MarysM.13D[,c("Treat", "Rep", "Run", "Plot")]
+MarysM.13D.1$Inc_18D <-  incidence2
+}
+
+if(D_assess == "19 DAT1 19-3-2013"){
+   MarysM.13D.1$Inc_19D <-  incidence2
+}
+
+} #end of loop on disease observations
+
+write.csv(
+   MarysM.13D.1,
+   here("cache/AM1304-MaryMount-Disease_means.csv"),
+   row.names = FALSE
+)
+
+# read in yield and format
+MarysM.13Y <-
+   as.data.frame(
+      read_xlsx(
+         path = here("data/AM1304 Fungicides for powdery mildew in mungbean - Marys Mount.xlsx"),
+         sheet = "42 DAT1 Yield",
+         range = "A14:F58",
+         col_names = TRUE
+      )
+   )
+
+MarysM.13Y$Treat <- as.character(MarysM.13Y$Treat)
+MarysM.13Y$Rep <- as.character(MarysM.13Y$Rep)
+
+MarysM.13Y <- MarysM.13Y[order(MarysM.13Y[,1],MarysM.13Y[,2],MarysM.13Y[,3],MarysM.13Y[,4]),]
+
+MarysM_13 <- left_join(MarysM.13D.1,MarysM.13Y)
+```
+
+#### Define treatment data
+```{r MarysDefine}
+MarysM_13 <- MarysM_13 %>%
+   mutate(trade_name = 
+             case_when(Treat == "1" ~ "control",
+                       Treat == "2" ~ "Spin-flo",
+                       Treat == "3" ~ "Tilt",
+                       Treat == "4" ~ "Amistar Xtra",
+                       Treat == "5" ~ "Amistar Xtra + adj",
+                       Treat == "6" ~ "Cabrio",
+                       Treat == "7" ~ "Spin-flo",
+                       Treat == "8" ~ "Tilt",
+                       Treat == "9" ~ "Amistar Xtra + adj",
+                       Treat == "10" ~ "Cabrio",
+                       Treat == "11" ~ "Tilt",
+                       TRUE ~ "other"))%>%
+   mutate(fungicide_ai = 
+             case_when(Treat == "1" ~ "control",
+                       Treat == "2" ~ "carbendazim",
+                       Treat == "3" ~ "propiconazole",
+                       Treat == "4" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "5" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "6" ~ "pyraclostrobin",
+                       Treat == "7" ~ "carbendazim",
+                       Treat == "8" ~ "propiconazole",
+                       Treat == "9" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "10" ~ "pyraclostrobin",
+                       Treat == "11" ~ "propiconazole",
+                       TRUE ~ "other"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Treat == "1" ~ 0,
+                       Treat == "2" ~ 250,
+                       Treat == "3" ~ 62.5,
+                       Treat == "4" ~ 40,
+                       Treat == "5" ~ 40,
+                       Treat == "6" ~ 125,
+                       Treat == "7" ~ 250,
+                       Treat == "8" ~ 62.5,
+                       Treat == "9" ~ 40,
+                       Treat == "10" ~ 125,
+                       Treat == "11" ~ 62.5,
+                       TRUE ~ 0))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Treat == "1" ~ as.Date(NA),
+                       Treat == "2" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "3" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "4" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "5" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "6" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "7" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Treat == "7" ~ as.Date("2013-03-18", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-03-18", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-03-18", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-03-18", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-03-18", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_3 = 
+             case_when(Treat == "11" ~ as.Date("2013-04-02", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Treat == "1" ~ 0,
+                       Treat == "2" ~ 1,
+                       Treat == "3" ~ 1,
+                       Treat == "4" ~ 1,
+                       Treat == "5" ~ 1,
+                       Treat == "6" ~ 1,
+                       Treat == "7" ~ 2,
+                       Treat == "8" ~ 2,
+                       Treat == "9" ~ 2,
+                       Treat == "10" ~ 2,
+                       Treat == "11" ~ 2, # third spray not applied ?
+                       TRUE ~ 0))
+```
+
+#### Input trial data
+```{r Marys_TrialData}
+MarysM_13_dat <- 
+   data.frame(trial_ref = "AM1304",
+              year = "2013",
+              location = "Marys Mount",
+              host_genotype = "Crystal",
+              trial_design = "RCB",
+              plot_length = 12,
+              plot_width = 4,
+              plant_density = NA,
+              row_spacing = 1,
+              replicate = MarysM_13$Rep,
+              planting_date = as.Date("2012-12-24", format = "%Y-%m-%d"),
+              emergence_date = NA,
+              flowering_date = NA,
+              pod_fill_date = as.Date("2013-02-28", format = "%Y-%m-%d"),
+              mid_late_pod_fill = NA,
+              first_sign_disease = as.Date("2013-03-16", format = "%Y-%m-%d"),
+              trade_name = as.factor(MarysM_13$trade_name),
+              fungicide_ai = MarysM_13$fungicide_ai,
+              dose_ai.ha = MarysM_13$dose_ai.ha,
+              n_treatment = MarysM_13$Treat,
+              fungicide_application_1 = MarysM_13$fungicide_application_1,
+              fungicide_application_2 = MarysM_13$fungicide_application_2,
+              fungicide_application_3 = MarysM_13$fungicide_application_3,
+              total_fungicide = MarysM_13$spray_n,
+              harvest_date = as.Date("2013-04-11", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2013-03-26", format = "%Y-%m-%d"),
+              PM_final_severity = MarysM_13$Inc_19D,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(MarysM_13$`Yield Kg/ha`)/1000
+              )
+
+```
+
+#### AUDPC curve
+```{r Mary13_AUDPC}
+MarysM_13_dat <- cbind(MarysM_13_dat,
+                          AUDPC = apply(data.frame(zero = 0,
+                                                   MarysM_13[,c("Inc_18D","Inc_19D")]-1),
+                                        1, 
+                                        FUN = audpc, 
+                                        dates = c(1,12,12+19)
+                                        ),
+                     AUDPS = apply(data.frame(zero = 0,
+                                                   MarysM_13[,c("Inc_18D","Inc_19D")]-1),
+                                        1, 
+                                        FUN = audps, 
+                                        dates = c(1,12,12+19)
+                                        )
+                          )
+
+```
+
+#### Calculating the treatment means
+```{r Marys_means}
+MarysM_13_m <- MarysM_13_dat %>%
+   group_by(n_treatment) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             location = unique(location),
+             host_genotype = unique(host_genotype),
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             fungicide_ai = unique(fungicide_ai),
+             dose_ai.ha = unique(dose_ai.ha),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
+              plot_width.m. = mean(plot_width, na.rm = TRUE),
+              plant_density = unique(plant_density),
+              row_spacing = unique(row_spacing),
+              replicates = length(as.numeric(replicate)),
+              planting_date = unique(planting_date),
+              emergence_date = NA,
+              flowering_date = unique(flowering_date),
+              pod_fill_date = unique(pod_fill_date),
+              mid_late_pod_fill = unique(mid_late_pod_fill),
+              first_sign_disease = unique(first_sign_disease),
+              fungicide_application_1 = unique(fungicide_application_1),
+              fungicide_application_2 = unique(fungicide_application_2),
+              fungicide_application_3 = unique(fungicide_application_3),
+              total_fungicide = unique(total_fungicide),
+              harvest_date = unique(harvest_date),
+              final_assessment = unique(final_assessment),
+              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+              rating_scale = unique(rating_scale),
+              disease_error = sd(PM_final_severity, na.rm = TRUE), # this not calculating sd and returning NAs?
+              D_error_type = "stdev",
+              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+              raw_graded = NA,
+              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+              Y_error_type = "stdev",
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ factor(n_treatment), 
+                               data = MarysM_13_dat[MarysM_13_dat$fungicide_ai == "propiconazole" | 
+                                                        MarysM_13_dat$fungicide_ai == "control" ,]))[1,3],
+              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), 
+                                data = MarysM_13_dat[MarysM_13_dat$fungicide_ai == "propiconazole" | 
+                                                        MarysM_13_dat$fungicide_ai == "control" ,]))[1,3]
+             )
+
+# For some wierd reason standard deviations are comming back NA in the code above
+# Because of n_treatment being converted to a factor I need to wrangle carefully here
+Mary_tmp <- MarysM_13_dat %>%
+   group_by(n_treatment) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE))
+
+# Remive the existing yield_error columns and replace with new ones
+MarysM_13_m <- left_join(MarysM_13_m[,colnames(MarysM_13_m)[c(-29,-33)]], Mary_tmp)
+
+# Remove other plots not in experiment
+MarysM_13_m <- MarysM_13_m[MarysM_13_m$trade_name != "other",]
+
+MarysM_13_m$n_treatment <- as.numeric(as.character(MarysM_13_m$n_treatment))
+MarysM_13_m <- fold_data(MarysM_13_m, PM_MB_means)
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = MarysM_13_m, 
+                            new_data_column = c("planting_date","AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
+
+write.csv(
+   MarysM_13_m[order(as.numeric(MarysM_13_m$n_treatment)),],
+   here("cache/AM1304-MarysMount_means.csv"),
+   row.names = FALSE
+)
+
+```
+
+### Premer 2013
+#### Convert disease scores
+```{r Premer_13_convert_scores}
+
+for(D_assess in c("19 DAT1 19-3-2013","31 DAT1 31-3-2013")){
+
+# Import final disease survey
+Premer.13D <-
+   as.data.frame(
+      read_xlsx(
+         path = here("data/AM1303 Fungicides for powdery mildew in mungbean - Premer.xlsx"),
+         sheet = D_assess,
+         range = "A14:DC64",
+         col_names = TRUE
+      )
+   )
+
+colnames(Premer.13D)[1:4] <- c("Treat", "Rep", "Run", "Plot")
+Premer.13D <- Premer.13D[order(Premer.13D[,1],Premer.13D[,2],Premer.13D[,3],Premer.13D[,4]),]
+
+# remove Plots not surveyed
+for (i in seq_along(Premer.13D[, 1])) {
+   if (i == 1) {
+      plotsRecorded <- vector(length = length(Premer.13D[, 1]))
+   }
+
+   plotsRecorded[i] <- all(is.na(Premer.13D[i, 7:56]))
+
+}
+# remove Plots not surveyed
+Premer.13D <- Premer.13D[!plotsRecorded, ]
+
+incidence3 <-
+   vector(mode = "numeric", length = length(Premer.13D[, 1]))
+
+# Convert disease survey data to 1-9 Incidence rating scale
+for (i in seq_along(incidence3)) {
+
+   # incidence = 1
+   if (all(Premer.13D[i, 58:107] == 0)) {
+      incidence3[i] <- 1
+      next()
+   }
+
+   # incidence = 2
+   if (sum(Premer.13D[i, 58:107] == 2, na.rm = TRUE) == 0 &&
+       sum(Premer.13D[i, 58:107] == 1, na.rm = TRUE) == 0 &&
+       (sum(Premer.13D[i, 58:107] == 3, na.rm = TRUE) /
+        length(Premer.13D[i, 58:107])) <= 0.75) {
+      incidence3[i] <- 2
+      next()
+   }
+
+   # incidence = 3
+   if (sum(Premer.13D[i, 58:107] == 1, na.rm = TRUE) == 0 &&
+       sum(Premer.13D[i, 58:107] == 2, na.rm = TRUE) <= 8 &&
+       (sum(Premer.13D[i, 58:107] > 0, na.rm = TRUE) /
+        length(Premer.13D[i, 58:107])) > 0.75) {
+      incidence3[i] <- 3
+   } else{
+      # if it is in the lower half of the canopy and in less than 75% of plants then incidence = 2.5
+      if (sum(Premer.13D[i, 58:107] == 1, na.rm = TRUE) == 0 &&
+          sum(Premer.13D[i, 58:107] == 2, na.rm = TRUE) <= 8 &&
+          sum(Premer.13D[i, 58:107] == 3, na.rm = TRUE) > 0 &&
+          (sum(Premer.13D[i, 58:107] > 0, na.rm = TRUE) /
+           length(Premer.13D[i, 58:107])) <= 0.75) {
+         incidence3[i] <- 2.5
+         next()
+      }
+   }
+
+   # incidence = 4
+   if (sum(Premer.13D[i, 58:107] == 1, na.rm = TRUE) == 0 &&
+       sum(Premer.13D[i, 58:107] == 2, na.rm = TRUE) > 0 &&
+       (sum(Premer.13D[i, 58:107] > 0, na.rm = TRUE) /
+        length(Premer.13D[i, 58:107])) <= 0.75) {
+      incidence3[i] <- 4
+      next()
+   }
+
+   # incidence = 5
+   if (sum(Premer.13D[i, 58:107] == 1, na.rm = TRUE) == 0 &&
+       sum(Premer.13D[i, 58:107] == 2, na.rm = TRUE) > 0 &&
+       (sum(Premer.13D[i, 58:107] > 0, na.rm = TRUE) /
+        length(Premer.13D[i, 58:107])) > 0.75) {
+      incidence3[i] <- 5
+      next()
+   }
+
+   # incidence = 6
+   if (sum(Premer.13D[i, 58:107] == 1, na.rm = TRUE) == 0 &&
+       sum(Premer.13D[i, 58:107] >= 2, na.rm = TRUE) > 0 &&
+       (sum(Premer.13D[i, 58:107] > 0, na.rm = TRUE) /
+        length(Premer.13D[i, 58:107])) > 0.95) {
+      incidence3[i] <- 6
+      next()
+   }
+
+   # incidence = 7
+   if (sum(Premer.13D[i, 58:107] == 1, na.rm = TRUE) <= 8 &&
+       sum(Premer.13D[i, 58:107] >= 2, na.rm = TRUE) > 0 &&
+       (sum(Premer.13D[i, 58:107] > 0, na.rm = TRUE) /
+        length(Premer.13D[i, 58:107])) > 0.95) {
+      incidence3[i] <- 7
+      next()
+   }
+
+   # incidence = 8
+   if (sum(Premer.13D[i, 58:107] >= 1, na.rm = TRUE) > 0 &&
+       (sum(Premer.13D[i, 58:107] > 0, na.rm = TRUE) /
+        length(Premer.13D[i, 58:107])) > 0.75) {
+      incidence3[i] <- 8
+      next()
+   }
+
+   # incidence = 9
+   if (sum(Premer.13D[i, 58:107] >= 1) > 0 &&
+       sum(Premer.13D[i, 7:56] >= (10 * 5 * 100 * 0.75)) &&
+       # ten leaves from 5 sample sites with a maximum % leaf area infected with PM of 100% * 0.75 as a threshold for leaf drop
+       (sum(Premer.13D[i, 58:107] > 0) /
+        length(Premer.13D[i, 58:107])) > 0.75) {
+      incidence3[i] <- 9
+      next()
+   }
+
+   # if there are few (< 10%) leaves with very small infections in all parts of the canopy OR
+   # if there is a stray colony on a upper leaf in addition to all lower
+   if (sum(Premer.13D[i, 58:107] == 3) >= 1 &&
+       sum(Premer.13D[i, 58:107] == 1) <= 2 &&
+       sum(Premer.13D[i, 58:107] == 2) <= 2 &&
+       sum(Premer.13D[i, 7:56]) <= 150) {
+      incidence3[i] <- 2.5
+      next()
+   }
+
+   # incidence = 7.5  In the upper canopy with less than 75% plants infected
+   if (sum(Premer.13D[i, 58:107] == 3) >= 0 &&
+       sum(Premer.13D[i, 58:107] == 2) > 0 &&
+       sum(Premer.13D[i, 58:107] == 1) > 0 &&
+       (sum(Premer.13D[i, 58:107] > 0) /
+        length(Premer.13D[i, 58:107]) <= 0.75) &&
+       sum(Premer.13D[i, 7:56]) >= 150) {
+      incidence3[i] <- 7.5
+      next()
+   }
+   #
+   # incidence = 6.5
+   if (sum(Premer.13D[i, 58:107] == 1) > 3 &&
+       sum(Premer.13D[i, 58:107] >= 2) > 0 &&
+       sum(Premer.13D[i, 7:56] <= 500)  &&
+       (sum(Premer.13D[i, 58:107] > 0) /
+        length(Premer.13D[i, 58:107]) >= 0.65)) {
+      incidence3[i] <- 6.5
+      next()
+   }
+   #
+   #
+   # incidence = 4.5 If PM is in the the lower and mid-canopy in less than 75% of plants and one or two in the upper canopy
+   if (sum(Premer.13D[i, 58:107] == 1) <= 3 &&
+       sum(Premer.13D[i, 58:107] >= 2) > 0 &&
+       (sum(Premer.13D[i, 58:107] > 0) /
+        length(Premer.13D[i, 58:107])) <= 0.75) {
+      incidence3[i] <- 4.5
+      next()
+   } else{
+      # If none of the conditions are met give the incidence zero
+      incidence3[i] <- 0
+   }
+
+}# end incidence loop
+
+if(any(incidence3 == 0)){
+   warning("Code caluculated incidence on '0' which is off the incidence scale")}
+
+# Re-format data-frame
+if(D_assess == "19 DAT1 19-3-2013"){
+   Premer.13D.1 <- Premer.13D[,c("Treat", "Rep", "Run", "Plot")]
+   Premer.13D.1$Inc_19D <-  incidence3}
+
+if(D_assess == "31 DAT1 31-3-2013"){
+   Premer.13D.2 <- Premer.13D[,c("Treat", "Rep", "Run", "Plot")]
+   Premer.13D.2$Inc_31D <-  incidence3}
+
+}# end disease assessment loop
+
+# The 19 Days after T1 only assessed the first 6 treatments
+# Therefore it will be dropped
+Premer.13D <- Premer.13D.2
+
+# read in yield and format
+Premer.13Y <-
+   as.data.frame(
+      read_xlsx(
+         path = here("data/AM1303 Fungicides for powdery mildew in mungbean - Premer.xlsx"),
+         sheet = "Yield 18-4-2013",
+         range = "A14:F58",
+         col_names = TRUE
+      )
+   )
+Premer.13Y$Treat <- as.character(Premer.13Y$Treat)
+
+Premer_13 <- left_join(Premer.13D,Premer.13Y)
+
+```
+
+#### Define treatment data
+```{r Premer13_define_treat}
+
+Premer_13 <- Premer_13 %>%
+   mutate(trade_name = 
+             case_when(Treat == "1" ~ "control",
+                       Treat == "2" ~ "Spin-flo",
+                       Treat == "3" ~ "Tilt",
+                       Treat == "4" ~ "Amistar Xtra",
+                       Treat == "5" ~ "Amistar Xtra + adj",
+                       Treat == "6" ~ "Cabrio",
+                       Treat == "7" ~ "Spin-flo",
+                       Treat == "8" ~ "Tilt",
+                       Treat == "9" ~ "Amistar Xtra + adj",
+                       Treat == "10" ~ "Cabrio",
+                       Treat == "11" ~ "Tilt",
+                       TRUE ~ "other"))%>%
+   mutate(fungicide_ai = 
+             case_when(Treat == "1" ~ "control",
+                       Treat == "2" ~ "carbendazim",
+                       Treat == "3" ~ "propiconazole",
+                       Treat == "4" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "5" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "6" ~ "pyraclostrobin",
+                       Treat == "7" ~ "carbendazim",
+                       Treat == "8" ~ "propiconazole",
+                       Treat == "9" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "10" ~ "pyraclostrobin",
+                       Treat == "11" ~ "propiconazole",
+                       TRUE ~ "other"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Treat == "1" ~ 0,
+                       Treat == "2" ~ 250,
+                       Treat == "3" ~ 62.5,
+                       Treat == "4" ~ 40,
+                       Treat == "5" ~ 40,
+                       Treat == "6" ~ 125,
+                       Treat == "7" ~ 250,
+                       Treat == "8" ~ 62.5,
+                       Treat == "9" ~ 40,
+                       Treat == "10" ~ 125,
+                       Treat == "11" ~ 62.5,
+                       TRUE ~ 0))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Treat == "1" ~ as.Date(NA),
+                       Treat == "2" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "3" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "4" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "5" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "6" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "7" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-02-28", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Treat == "7" ~ as.Date("2013-03-19", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-03-19", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-03-19", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-03-19", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-03-19", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_3 = 
+             case_when(Treat == "11" ~ as.Date("2013-03-31", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Treat == "1" ~ 0,
+                       Treat == "2" ~ 1,
+                       Treat == "3" ~ 1,
+                       Treat == "4" ~ 1,
+                       Treat == "5" ~ 1,
+                       Treat == "6" ~ 1,
+                       Treat == "7" ~ 2,
+                       Treat == "8" ~ 2,
+                       Treat == "9" ~ 2,
+                       Treat == "10" ~ 2,
+                       Treat == "11" ~ 3, 
+                       TRUE ~ 0))
+```
+
+#### Input trial data
+```{r Prem13_Trialdat}
+
+Premer_13_dat <- 
+   data.frame(trial_ref = "AM1303",
+              year = "2013",
+              location = "Premer",
+              host_genotype = "Crystal",
+              trial_design = "RCB",
+              plot_length = 12,
+              plot_width = 4,
+              plant_density = as.Date(NA),
+              row_spacing = as.Date(NA),
+              replicate = Premer_13$Rep,
+              planting_date = as.Date("2012-12-28", format = "%Y-%m-%d"),
+              emergence_date = as.Date(NA),
+              flowering_date = as.Date("2013-02-28", format = "%Y-%m-%d"),
+              pod_fill_date = as.Date(NA),
+              mid_late_pod_fill = as.Date(NA),
+              first_sign_disease = as.Date("2013-02-28", format = "%Y-%m-%d"),
+              trade_name = as.factor(Premer_13$trade_name),
+              fungicide_ai = Premer_13$fungicide_ai,
+              dose_ai.ha = Premer_13$dose_ai.ha,
+              n_treatment = Premer_13$Treat,
+              fungicide_application_1 = Premer_13$fungicide_application_1,
+              fungicide_application_2 = Premer_13$fungicide_application_2,
+              fungicide_application_3 = Premer_13$fungicide_application_3,
+              total_fungicide = Premer_13$spray_n,
+              harvest_date = as.Date("2013-04-18", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2013-03-31", format = "%Y-%m-%d"),
+              PM_final_severity = Premer_13$Inc_31D,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(Premer_13$`Yield kg/ha`)/1000
+              )
+
+```
+
+#### AUDPC curve
+```{r Prem13_AUDPC}
+Premer_13_dat <- cbind(Premer_13_dat,
+                          AUDPC = apply(data.frame(zero = 0,
+                                                           Premer_13[,c("Inc_31D")]-1),# -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
+                                        1, 
+                                        FUN = audpc, 
+                                        dates = c((Premer_13_dat$first_sign_disease[1]-7)-
+                                                     as.Date("2013-01-28", format = "%Y-%m-%d"),
+                                                  12+19)
+                                        ),
+                     AUDPS = apply(data.frame(zero = 0,
+                                                           Premer_13[,c("Inc_31D")]-1),
+                                        1, 
+                                        FUN = audps, 
+                                        dates = c((Premer_13_dat$first_sign_disease[1]-7)-
+                                                     as.Date("2013-01-28", format = "%Y-%m-%d"),
+                                                  12+19)
+                                        )
+                          )
+
+```
+
+#### Calculating the treatment means
+```{r Prem13_TreatmentMeans}
+Premer_13_m <- Premer_13_dat %>%
+   group_by(n_treatment) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             location = unique(location),
+             host_genotype = unique(host_genotype),
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             fungicide_ai = unique(fungicide_ai),
+             dose_ai.ha = unique(dose_ai.ha),
+            plot_length.m. = mean(plot_length, na.rm = TRUE),
+              plot_width.m. = mean(plot_width, na.rm = TRUE),
+              plant_density = unique(plant_density),
+              row_spacing = unique(row_spacing),
+              replicates = length(as.numeric(replicate)),
+              planting_date = unique(planting_date),
+              emergence_date = NA,
+              flowering_date = unique(flowering_date),
+              pod_fill_date = unique(pod_fill_date),
+              mid_late_pod_fill = unique(mid_late_pod_fill),
+              first_sign_disease = unique(first_sign_disease),
+              fungicide_application_1 = unique(fungicide_application_1),
+              fungicide_application_2 = unique(fungicide_application_2),
+              fungicide_application_3 = unique(fungicide_application_3),
+              total_fungicide = unique(total_fungicide),
+              harvest_date = unique(harvest_date),
+              final_assessment = unique(final_assessment),
+              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+              rating_scale = unique(rating_scale),
+              disease_error = sd(PM_final_severity, na.rm = TRUE), # Produces NAs and needs to be reproduced again below
+              D_error_type = "stdev",
+              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+              raw_graded = NA,
+              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+              Y_error_type = "stdev",
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+            AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ factor(n_treatment), 
+                               data = Premer_13_dat[Premer_13_dat$fungicide_ai == "propiconazole" | 
+                                                        Premer_13_dat$fungicide_ai == "control" ,]))[1,3],
+              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), 
+                                data = Premer_13_dat[Premer_13_dat$fungicide_ai == "propiconazole" | 
+                                                        Premer_13_dat$fungicide_ai == "control" ,]))[1,3]
+   )
+
+# For some wierd reason standard deviations are comming back NA in the code above
+# Because of n_treatment being converted to a factor I need to wrangle carefully here
+Prem_tmp <- Premer_13_dat %>%
+   group_by(n_treatment) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE))
+
+# Remive the existing yield_error columns and replace with new ones
+Premer_13_m <- left_join(Premer_13_m[,colnames(Premer_13_m)[c(-29,-33)]], Prem_tmp)
+
+# Remove other plots not in experiment
+Premer_13_m <- Premer_13_m[Premer_13_m$trade_name != "other",]
+
+Premer_13_m$n_treatment <- as.numeric(as.character(Premer_13_m$n_treatment))
+Premer_13_m <- fold_data(Premer_13_m, PM_MB_means)
+
+##########################
+# For some wierd reason standard deviations are comming back NA in the code above
+Premer_13_m[,c("disease_error","yield_error")] <- 
+   Premer_13_dat %>%
+   group_by(n_treatment) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("disease_error","yield_error"))
+
+Premer_13_m <- fold_data(Premer_13_m, PM_MB_means)
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Premer_13_m, 
+                            new_data_column = c("planting_date","AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
+
+write.csv(
+   Premer_13_m,
+   here("cache/AM1303-Premer-Disease_means.csv"),row.names = FALSE
+)
+
+```
+
+### Millmerran 2013
+#### Convert disease scores
+```{r Millm_13_convert_scores}
+
+for(D_assess in c("Assessment Sheet 5.4.2013","Assessment Sheet 24.4.2013")){
+
+# Import final disease survey
+Millm_13D <-
+   as.data.frame(
+      read_xlsx(
+         path = here("data/BB1305 Fungicides for powdery mildew in mungbean - Millmerran.xlsx"),
+         sheet = D_assess,
+         range = "A12:AH56",
+         col_names = TRUE
+      )
+   )
+
+colnames(Millm_13D)[1:4] <- c("Run", "Plot", "Treat", "Rep")
+Millm_13D <- Millm_13D[order(Millm_13D[,1],Millm_13D[,2],Millm_13D[,3],Millm_13D[,4]),]
+
+sum(is.na(Millm_13D[, 5:34]))
+# replace NAs with zero Plots not surveyed
+for (i in 5:34) {
+   for (j in seq_along(Millm_13D[, i])) {
+      if (is.na(Millm_13D[j, i])) {
+         Millm_13D[j, i] <- 0
+      }
+   }
+}
+
+incidence4 <-
+   vector(mode = "numeric", length = length(Millm_13D[, 1]))
+
+# column index table for incidence ratings
+# Calculate incidence
+#     Sites
+# low canopy  c(5:13)
+# mid canopy c(15:23)
+# upp canopy c(25:33)
+
+# Convert disease survey data to 1-9 Incidence rating scale
+for (i in seq_along(incidence4)) {
+
+   # incidence = 1
+   if (all(Millm_13D[i, c(5:13, 15:23, 25:33)] == 0)) {
+      incidence4[i] <- 1
+      next()
+   }
+
+   # incidence = 2
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       all(Millm_13D[i, 15:23] == 0) &&
+       all(Millm_13D[i, 25:33] == 0) &&
+       (sum(Millm_13D[i, c(5:13)] > 0) /
+        length(Millm_13D[i, c(5:13)])) <= 0.75) {
+      incidence4[i] <- 2
+      next()
+   }
+
+   # incidence = 3
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       sum(Millm_13D[i, 15:23] != 0) <= 3 &&
+       sum(Millm_13D[i, 25:33] == 0) == 0 &&
+       (sum(Millm_13D[i, c(5:13, 15:23)] > 0) /
+        length(Millm_13D[i, c(5:13, 15:23)])) >= 0.75) {
+      incidence4[i] <- 3
+   } else{
+      # if it is in the lower half of the canopy and in less than 75% of plants then incidence = 2.5
+      if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+          sum(Millm_13D[i, 15:23] != 0) <= 3 &&
+          sum(Millm_13D[i, 25:33] == 0) == 0 &&
+          (sum(Millm_13D[i, c(5:13, 15:23)] > 0) /
+           length(Millm_13D[i, c(5:13, 15:23)])) <= 0.75) {
+         incidence4[i] <- 2.5
+         next()
+      }
+   }
+
+   # incidence = 4
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       sum(Millm_13D[i, 15:23] != 0) >= 1 &&
+       all(Millm_13D[i, 25:33] == 0) &&
+       (sum(Millm_13D[i, c(5:13, 15:23)] > 0) /
+        length(Millm_13D[i, c(5:13, 15:23)])) <= 0.75) {
+      incidence4[i] <- 4
+      next()
+   }
+
+   # incidence = 5
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       sum(Millm_13D[i, 15:23] != 0) >= 1 &&
+       all(Millm_13D[i, 25:33] == 0) &&
+       (sum(Millm_13D[i, c(5:13, 15:23)] > 0) /
+        length(Millm_13D[i, c(5:13, 15:23)])) >= 0.75) {
+      incidence4[i] <- 5
+      next()
+   }
+
+   # incidence = 6
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       sum(Millm_13D[i, 15:23] != 0) >= 1 &&
+       all(Millm_13D[i, 25:33] == 0) &&
+       (sum(Millm_13D[i, c(5:13, 15:23)] > 0) /
+        length(Millm_13D[i, c(5:13, 15:23)])) >= 0.90) {
+      incidence4[i] <- 6
+      next()
+   }
+
+   # incidence = 7
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       sum(Millm_13D[i, 15:23] != 0) >= 1 &&
+       sum(Millm_13D[i, 25:33] != 0) <= 3 &&
+       (sum(Millm_13D[i, c(5:13, 15:23)] > 0) /
+        length(Millm_13D[i, c(5:13, 15:23)])) >= 0.90) {
+      incidence4[i] <- 7
+      next()
+   }
+
+   # incidence = 8
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       sum(Millm_13D[i, 15:23] != 0) >= 1 &&
+       sum(Millm_13D[i, 25:33] != 0) >= 1 &&
+       (sum(Millm_13D[i, c(5:13, 15:23, 25:33)] > 0) /
+        length(Millm_13D[i, c(5:13, 15:23, 25:33)])) >= 0.75) {
+      incidence4[i] <- 8
+      next()
+   }
+
+   # incidence = 9
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       sum(Millm_13D[i, 15:23] != 0) >= 1 &&
+       sum(Millm_13D[i, 25:33] != 0) >= 1 &&
+       (sum(Millm_13D[i, c(5:13, 15:23, 25:33)] > 0) /
+        length(Millm_13D[i, c(5:13, 15:23, 25:33)])) >= 0.75 &&
+       sum(Millm_13D[i, c(5:13, 15:23, 25:33)]) > (9 * 3 * 100) * 0.75) {
+      incidence4[i] <- 9
+      next()
+   }
+
+   # if there are few (< 10%) leaves with very small infections in all parts of the canopy OR
+   # if there is a stray colony on a upper leaf in addition to all lower
+
+   if (sum(Millm_13D[i, 15:23] != 0) <= 3 &&
+       sum(Millm_13D[i, 25:33] != 0) <= 3 &&
+       (sum(Millm_13D[i, c(5:13, 15:23, 25:33)]) /
+        length(Millm_13D[i, c(5:13, 15:23, 25:33)]) / 100) <= 0.1) {
+      incidence4[i] <- 2.5
+      next()
+   }
+
+   # incidence = 7.5  In the upper canopy with less than 75% plants infected
+   if (sum(Millm_13D[i, 5:13] != 0) >= 1 &&
+       sum(Millm_13D[i, 15:23] != 0) >= 1 &&
+       sum(Millm_13D[i, 25:33] != 0) >= 3 &&
+       (sum(Millm_13D[i, c(5:13, 15:23, 25:33)] > 0) /
+        length(Millm_13D[i, c(5:13, 15:23, 25:33)])) <= 0.75) {
+      incidence4[i] <- 7.5
+      next()
+   }
+
+   # if there are few more colonies(< 10%) leaves with very small infections in all parts of the canopy OR
+   # if there is a stray colony on a upper leaf in addition to all lower
+
+   if (sum(Millm_13D[i, 15:23] != 0) <= 6 &&
+       sum(Millm_13D[i, 25:33] != 0) <= 3 &&
+       (sum(Millm_13D[i, c(5:13, 15:23, 25:33)]) /
+        length(Millm_13D[i, c(5:13, 15:23, 25:33)]) / 100) <= 0.1) {
+      incidence4[i] <- 3.5
+      next()
+   }
+
+   if (sum(Millm_13D[i, 15:23] != 0) >= 1 &&
+       sum(Millm_13D[i, 25:33] != 0) <= 3 &&
+       (sum(Millm_13D[i, c(5:13, 15:23, 25:33)]) /
+        length(Millm_13D[i, c(5:13, 15:23, 25:33)]) / 100) <= 0.5) {
+      incidence4[i] <- 6.5
+      next()
+   }
+   else{
+      # If none of the conditions are met give the incidence zero
+      incidence4[i] <- 0
+   }
+}
+# end incidence loop
+
+if(any(incidence4 == 0)){
+   warning("Code caluculated incidence on '0' which is off the incidence scale")}
+
+# Re-format data-frame
+if(D_assess == "Assessment Sheet 5.4.2013"){
+   Millm_13D.1 <- Millm_13D[,c("Treat", "Rep", "Run", "Plot")]
+   Millm_13D.1$Inc_23D <-  incidence4}
+
+if(D_assess == "Assessment Sheet 24.4.2013"){
+   Millm_13D.2 <- Millm_13D[,c("Treat", "Rep", "Run", "Plot")]
+   Millm_13D.2$Inc_42D <-  incidence4}
+
+}# end disease assessment loop
+
+# The 19 Days after T1 only assessed the first 6 treatments
+# Therefore it will be dropped
+Millm_13D <- left_join(Millm_13D.1, Millm_13D.2)
+
+# read in yield and format
+Millm.13Y <-
+   as.data.frame(
+      read_xlsx(
+         path = here("data/BB1305 Fungicides for powdery mildew in mungbean - Millmerran.xlsx"),
+         sheet = "Harvest Sheet 6.5.2013",
+         range = "A11:F55",
+         col_names = TRUE
+      )
+   )
+Millm.13Y$Treatment <- as.character(Millm.13Y$Treatment)
+Millm.13Y$Treat <- as.double(Millm.13Y$Treat)
+colnames(Millm.13Y)[1:4] <- c("Run", "Plot","TreatY", "Rep")
+
+Millm_13 <- left_join(Millm_13D, Millm.13Y, by = c("Run", "Plot","Treat", "Rep"))
+
+```
+
+#### Define treatment data
+```{r Millm_13_define_treat}
+
+Millm_13 <- Millm_13 %>%
+   mutate(trade_name = 
+             case_when(Treat == "1" ~ "control",
+                       Treat == "2" ~ "Spin-flo",
+                       Treat == "3" ~ "Tilt",
+                       Treat == "4" ~ "Amistar Xtra",
+                       Treat == "5" ~ "Amistar Xtra + adj",
+                       Treat == "6" ~ "Cabrio",
+                       Treat == "7" ~ "Spin-flo",
+                       Treat == "8" ~ "Tilt",
+                       Treat == "9" ~ "Amistar Xtra + adj",
+                       Treat == "10" ~ "Cabrio",
+                       Treat == "11" ~ "Tilt",
+                       TRUE ~ "other"))%>%
+   mutate(fungicide_ai = 
+             case_when(Treat == "1" ~ "control",
+                       Treat == "2" ~ "carbendazim",
+                       Treat == "3" ~ "propiconazole",
+                       Treat == "4" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "5" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "6" ~ "pyraclostrobin",
+                       Treat == "7" ~ "carbendazim",
+                       Treat == "8" ~ "propiconazole",
+                       Treat == "9" ~ "200 g/L azoxystrobin + 80 g/L cyproconazole",
+                       Treat == "10" ~ "pyraclostrobin",
+                       Treat == "11" ~ "propiconazole",
+                       TRUE ~ "other"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Treat == "1" ~ 0,
+                       Treat == "2" ~ 250,
+                       Treat == "3" ~ 62.5,
+                       Treat == "4" ~ 40,
+                       Treat == "5" ~ 40,
+                       Treat == "6" ~ 125,
+                       Treat == "7" ~ 250,
+                       Treat == "8" ~ 62.5,
+                       Treat == "9" ~ 40,
+                       Treat == "10" ~ 125,
+                       Treat == "11" ~ 62.5,
+                       TRUE ~ 0))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Treat == "1" ~ as.Date(NA),
+                       Treat == "2" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "3" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "4" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "5" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "6" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "7" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-03-13", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Treat == "7" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
+                       Treat == "8" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
+                       Treat == "9" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
+                       Treat == "10" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
+                       Treat == "11" ~ as.Date("2013-03-21", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_3 = 
+             case_when(Treat == "11" ~ as.Date("2013-03-28", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Treat == "1" ~ 0,
+                       Treat == "2" ~ 1,
+                       Treat == "3" ~ 1,
+                       Treat == "4" ~ 1,
+                       Treat == "5" ~ 1,
+                       Treat == "6" ~ 1,
+                       Treat == "7" ~ 2,
+                       Treat == "8" ~ 2,
+                       Treat == "9" ~ 2,
+                       Treat == "10" ~ 2,
+                       Treat == "11" ~ 3, 
+                       TRUE ~ 0))
+```
+
+#### Input trial data
+```{r Millm13_Trialdat}
+
+Millm_13_dat <- 
+   data.frame(trial_ref = "BB1305",
+              year = "2013",
+              location = "Millmerran",
+              host_genotype = "Crystal",
+              trial_design = "RCB",
+              plot_length = 12,
+              plot_width = 4,
+              plant_density = as.Date(NA),
+              row_spacing = 1/3,
+              replicate = Millm_13$Rep,
+              planting_date = as.Date("2013-01-12", format = "%Y-%m-%d"), # Lawrie prices guess for planting date
+              emergence_date = as.Date(NA),
+              flowering_date = as.Date(NA),
+              pod_fill_date = as.Date("2013-03-21", format = "%Y-%m-%d"),
+              mid_late_pod_fill = as.Date("2013-03-28", format = "%Y-%m-%d"),
+              first_sign_disease = as.Date("2013-03-13", format = "%Y-%m-%d"),
+              trade_name = as.factor(Millm_13$trade_name),
+              fungicide_ai = Millm_13$fungicide_ai,
+              dose_ai.ha = Millm_13$dose_ai.ha,
+              n_treatment = Millm_13$Treat,
+              fungicide_application_1 = Millm_13$fungicide_application_1,
+              fungicide_application_2 = Millm_13$fungicide_application_2,
+              fungicide_application_3 = Millm_13$fungicide_application_3,
+              total_fungicide = Millm_13$spray_n,
+              harvest_date = as.Date("2013-05-06", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2013-04-24", format = "%Y-%m-%d"),
+              PM_final_severity = Millm_13$Inc_42D,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(Millm_13$`kg/Ha`)/1000,
               stringsAsFactors = FALSE)
-lm_rain4 <-
-   read.csv("cache/lmInSeasonRainfall_10.30_65.100.csv",
+
+```
+
+#### AUDPC curve
+```{r Mill13_AUDPC}
+Millm_13_dat <- cbind(Millm_13_dat,
+                          AUDPC = apply(data.frame(zero = 0,
+                                                           Millm_13[,c("Inc_23D","Inc_42D")]-1),
+                                        1, 
+                                        FUN = audpc, 
+                                        dates = c(1,23,42)
+                                        ),
+                     AUDPS = apply(data.frame(zero = 0,
+                                                           Millm_13[,c("Inc_23D","Inc_42D")]-1),
+                                        1, 
+                                        FUN = audps, 
+                                        dates = c(1,23,42)
+                                        )
+                          )
+
+```
+
+#### Calculating the treatment means
+```{r Millm13_TreatmentMeans}
+Millm_13_m <- Millm_13_dat %>%
+   group_by(trial_ref, year, location, host_genotype, trial_design, 
+            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
+   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
+             plot_width.m. = mean(plot_width, na.rm = TRUE),
+             plant_density = unique(plant_density),
+             row_spacing = unique(row_spacing),
+             replicates = length(as.numeric(replicate)),
+             planting_date = unique(planting_date),
+             emergence_date = NA,
+             flowering_date = unique(flowering_date),
+             pod_fill_date = unique(pod_fill_date),
+             mid_late_pod_fill = unique(mid_late_pod_fill),
+             first_sign_disease = unique(first_sign_disease),
+             fungicide_application_1 = unique(fungicide_application_1),
+             fungicide_application_2 = unique(fungicide_application_2),
+             fungicide_application_3 = unique(fungicide_application_3),
+             total_fungicide = unique(total_fungicide),
+             harvest_date = unique(harvest_date),
+             final_assessment = unique(final_assessment),
+             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+             rating_scale = unique(rating_scale),
+             disease_error = sd(PM_final_severity, na.rm = TRUE), # Createds NAs and need repeating below
+             D_error_type = "stdev",
+             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+             raw_graded = NA,
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+             Y_error_type = "stdev",
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ factor(n_treatment), 
+                               data = Millm_13_dat[Millm_13_dat$fungicide_ai == "propiconazole" | 
+                                                        Millm_13_dat$fungicide_ai == "control" ,]))[1,3],
+              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), 
+                                data = Millm_13_dat[Millm_13_dat$fungicide_ai == "propiconazole" | 
+                                                        Millm_13_dat$fungicide_ai == "control" ,]))[1,3]
+             )
+
+# For some wierd reason standard deviations are comming back NA in the code above
+# Because of n_treatment being converted to a factor I need to wrangle carefully here
+Millm_tmp <- Millm_13_dat %>%
+   group_by(n_treatment) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE))
+
+# Remive the existing yield_error columns and replace with new ones
+Millm_13_m <- left_join(Millm_13_m[,colnames(Millm_13_m)[c(-29,-33)]], Millm_tmp)
+
+# Remove other plots not in experiment
+Millm_13_m <- Millm_13_m[Millm_13_m$trade_name != "other",]
+
+Millm_13_m$n_treatment <- as.numeric(as.character(Millm_13_m$n_treatment))
+Millm_13_m <- fold_data(Millm_13_m, PM_MB_means)
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Millm_13_m, 
+                            new_data_column = c("planting_date","AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
+
+write.csv(
+   Millm_13_m[order(as.numeric(Millm_13_m$n_treatment)),],
+   here("cache/BB1305_Millmerran_means.csv"), row.names = FALSE
+)
+
+```
+
+### Hermitage 2015
+```{r Herm_15}
+
+Herm_15 <-
+   read.xlsx(
+      here("data/Mugbean powdery mildew 2014-15 inc results v2.xlsx"),
+      sheet = "HRS yield data",
+      startRow = 4,
+      colNames = TRUE,
+      detectDates = TRUE
+   )[1:30, 1:9]
+
+Herm_15$Year <- 2015
+Herm_15$location <- "Hermitage"
+
+# Disease incidence assessments through the 2016 season
+Herm_15.DR  <-
+   read.xlsx(
+      here("data/Mugbean powdery mildew 2014-15 inc results v2.xlsx"),
+      sheet = "HRS ratings & graphs",
+      startRow = 5,
+      colNames = TRUE
+   )[1:30, 1:8]
+
+Herm_15$Plot.Length <- as.numeric(Herm_15$Plot.Length)
+Herm_15$Plot.Weight <- as.numeric(Herm_15$Plot.Weight)
+Herm_15$Plot.weight <- as.numeric(Herm_15$Plot.weight)
+Herm_15$`Plot.Yield.(kg/ha)` <-
+   as.numeric(Herm_15$`Plot.Yield.(kg/ha)`)
+Herm_15$`Plot.Yield.(t/ha)` <-
+   as.numeric(Herm_15$`Plot.Yield.(t/ha)`)
+
+# Rename the plot column and remove lines without data
+colnames(Herm_15)[3] <- "Plot"
+Herm_15.DR <- Herm_15.DR[!is.na(Herm_15.DR$Treatment),]
+
+# rename the disease assesment columns
+# For comparing between trials I am forcing the assumption 
+#   that the disease did not exist prior to it being spotted in the trial. 
+#   Therefore day0 observes zero disease and day1 is first sign
+colnames(Herm_15.DR)[4:8] <- c("day0", "day1", "day8", "day15","day22") 
+Herm_15.DR$day0 <- as.numeric(Herm_15.DR$day0)
+Herm_15.DR$day1 <- as.numeric(Herm_15.DR$day1)
+Herm_15.DR$day8 <- as.numeric(Herm_15.DR$day8)
+Herm_15.DR$day15 <- as.numeric(Herm_15.DR$day15)
+Herm_15.DR$day22 <- as.numeric(Herm_15.DR$day22)
+
+# Merge yield and disease data
+Herm_15 <- left_join(Herm_15.DR, Herm_15)
+
+```
+
+#### Define treatment data
+```{r Herm_15_Treats}
+
+Herm_15_dat <- Herm_15 %>%
+   mutate(n_treatment = 
+             case_when(Treatment == "1st sign +1" ~ 4,
+                       Treatment == "control" ~ 1,
+                       Treatment == "1st sign" ~ 3,
+                       Treatment == "1/3C + 1" ~ 6,
+                       Treatment == "5wks+2" ~ 2,
+                       Treatment == "1/3C" ~ 5,
+                       TRUE ~ 9998))%>%
+   mutate(trade_name = 
+             case_when(Treatment == "control" ~ "control",
+                       TRUE ~ "Folicur"))%>%
+   mutate(fungicide_ai = 
+             case_when(Treatment == "control" ~ "control",
+                       TRUE ~ "tebuconazole"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Treatment == "control" ~ 0,
+                       TRUE ~ 62.35))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Treatment == "1st sign +1" ~ as.Date("2015-03-17", format = "%Y-%m-%d"),
+                       Treatment == "control" ~ as.Date(NA),
+                       Treatment == "1st sign" ~ as.Date("2015-03-17", format = "%Y-%m-%d"),
+                       Treatment == "1/3C + 1" ~ as.Date("2015-03-23", format = "%Y-%m-%d"),
+                       Treatment == "5wks+2" ~ as.Date("2015-03-02", format = "%Y-%m-%d"),
+                       Treatment == "1/3C" ~ as.Date("2015-03-24", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Treatment == "1st sign +1" ~ as.Date("2015-03-31", format = "%Y-%m-%d"),
+                       Treatment == "control" ~ as.Date(NA),
+                       Treatment == "1/3C + 1" ~ as.Date("2015-04-07", format = "%Y-%m-%d"),
+                       Treatment == "5wks+2" ~ as.Date("2015-03-17", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_3 = 
+             case_when(Treatment == "5wks+2" ~ as.Date("2015-03-31", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Treatment == "1st sign +1" ~ 2,
+                       Treatment == "control" ~ 0,
+                       Treatment == "1st sign" ~ 1,
+                       Treatment == "1/3C + 1" ~ 2,
+                       Treatment == "5wks+2" ~ 3,
+                       Treatment == "1/3C" ~ 1,
+                       TRUE ~ 9999))
+
+```
+
+#### Input trial data
+```{r Herm15_Trialdat}
+
+Herm_15_dat <- 
+   data.frame(trial_ref = "mung1415/01",
+              year = "2015",
+              location = "Hermitage",
+              host_genotype = "Jade",
+              trial_design = "RCB",
+              plot_length = 12,
+              plot_width = 4,
+              plant_density = NA,
+              row_spacing = 0.75,
+              replicate = Herm_15_dat$Rep,
+              planting_date = as.Date("2015-01-19", format = "%Y-%m-%d"),
+              emergence_date = as.Date("2015-01-24", format = "%Y-%m-%d"),
+              flowering_date = as.Date(NA),
+              pod_fill_date = as.Date(NA),
+              mid_late_pod_fill = as.Date(NA),
+              first_sign_disease = as.Date("2015-03-16", format = "%Y-%m-%d"),
+              trade_name = as.factor(Herm_15_dat$trade_name),
+              fungicide_ai = Herm_15_dat$fungicide_ai,
+              dose_ai.ha = Herm_15_dat$dose_ai.ha,
+              n_treatment = as.numeric(Herm_15_dat$n_treatment),
+              fungicide_application_1 = Herm_15_dat$fungicide_application_1,
+              fungicide_application_2 = Herm_15_dat$fungicide_application_2,
+              fungicide_application_3 = Herm_15_dat$fungicide_application_3,
+              total_fungicide = Herm_15_dat$spray_n,
+              harvest_date = as.Date("2015-04-20", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2015-04-06", format = "%Y-%m-%d"),
+              PM_final_severity = Herm_15_dat$day22,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(Herm_15_dat$`Plot.Yield.(t/ha)`),
+              AUDPC = apply(Herm_15_dat[,c("day0", "day1", "day8", "day15","day22")]-1,1, 
+                            FUN = audpc, 
+                            dates = c(0,1,8,15,22)),
+              # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
+              AUDPS = apply(Herm_15_dat[,c("day0", "day1", "day8", "day15","day22")]-1,1, 
+                            FUN = audps, 
+                            dates = c(0,1,8,15,22)),
               stringsAsFactors = FALSE)
 
-lm_rain <- rbind(lm_rain1, lm_rain2, lm_rain3, lm_rain4)
-```
-
-Now we have read in the data from the previously computed models let's find the linear model which has:  
-   - The lowest P value  
-   - the highest adjusted r squared value
-
-```{r WhichLModel}
-lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)), ]
-lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)), ]
-lm_rain[which(lm_rain$lm_adj_rsquared == max(lm_rain$lm_adj_rsquared)), ]
-```
-
-To visualise the model fits we will use a heat map to describe how the models faired in relation to the rainfall windows.
-log of the p value was used to improve the resolution of small very small p values.
-
-```{r rainLMpvalue}
-ggplot(lm_rain, aes(x = start_day, y = end_day, z = log(lm_pval))) +
-   geom_raster(aes(fill = log(lm_pval)), interpolate = TRUE) +
-   geom_contour(bins = 15, colour = "white") +
-   geom_point(data = lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)), ],
-              aes(x = start_day, y = end_day),
-              colour = " red") +
-   scale_fill_distiller(palette = "RdBu", direction = -1) 
-```
-
-```{r rainLMadjrsquared}
-ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_adj_rsquared)) +
-   geom_raster(aes(fill = lm_adj_rsquared), interpolate = TRUE) +
-   geom_contour(bins = 15, colour = "white") +
-   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)), ],
-              aes(x = start_day, y = end_day),
-              colour = " red") +
-   scale_fill_distiller(palette = "RdBu") 
-```
-
-The approximate period when in-crop rainfall affects the most on the mean harvest is between 14 - 67 days after planting.
-
-*****
-
-### Season range and first incidence
-
-Mungbean is a summer crop and powdery mildew requires cool conditions to establish.
-Therefore the disease can be avoided by planting early in summer or spring, avoiding cooler temperatures at the end of some seasons.
-Can we visualise when PM is most likely to establish over the calendar year?
-
-I'll build a plot of horizontal lines indicating the season length and use a dot on the line to indicating the day of the year first sign was observed for that trial.
-
-```{r first_incidence}
-# Create the data frame for the plot
-season_dates <- PM_MB_means %>%
-   group_by(trial_ref) %>%
-   summarise(
-      Planting_date = unique(planting_date),
-      Harvest_date = unique(harvest_date),
-      First_sign_PM = unique(first_sign_disease),
-      season_length = as.Date(unique(harvest_date)) - as.Date(unique(planting_date)),
-      cropping_season = "Actual"
-   )
-
-# For some trials where planting date and Harvest date is missing let's estimate 
-#     the season length by using the mean of all season lengths
-season_dates[is.na(season_dates$season_length),"cropping_season"] <- "Estimated"
-
-season_dates[is.na(season_dates$Planting_date),"Planting_date"] <- 
-   season_dates[is.na(season_dates$Planting_date),"Harvest_date"] - 
-   as.numeric(mean(season_dates$season_length, na.rm = TRUE))
-
-season_dates[is.na(season_dates$Harvest_date),"Harvest_date"] <- 
-   season_dates[is.na(season_dates$Harvest_date),"Planting_date"] + 
-   as.numeric(mean(season_dates$season_length, na.rm = TRUE))
-
-season_dates[is.na(season_dates$season_length),"season_length"] <- 
-   mean(season_dates$season_length, na.rm = TRUE)
-
-season_dates$Planting_day <- yday(season_dates$Planting_date)
-season_dates$Disease_day <- yday(season_dates$First_sign_PM)
-
-season_dates[c(1:2,6), "Planting_day"] <- 1
-
-season_dates$Harvest_day <-
-   season_dates$Planting_day + season_dates$season_length
-
-first_day_month <- c(0, 31, 60, 91, 121, 152, 182, 212, 244, 274) + 1
-axis_labels_date <-
-   c(
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[1], "%b-%d"),
-      # Jan
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[2], "%b-%d"),
-      # Feb
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[3], "%b-%d"),
-      # March
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[4], "%b-%d"),
-      # April
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[5], "%b-%d"),
-      # May
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[6], "%b-%d"),
-      # June
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[7], "%b-%d"),
-      # July
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[8], "%b-%d"),
-      # August
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[9], "%b-%d"),
-      # Sept
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[10], "%b-%d") # October
-   )
-
-# reorder the factors so they will appear in chronological order
-# I used First sign because all trials have recorded this
-season_dates$trial_ref <-
-   factor(season_dates$trial_ref,
-          levels = levels(season_dates$trial_ref)[rev(order(season_dates$First_sign_PM))])
-
-# Plot
-SeasonPlot <- season_dates %>%
-   ggplot() +
-   geom_pointrange(aes(
-      x = trial_ref,
-      y = Disease_day,
-      ymin = Planting_day,
-      ymax = Harvest_day,
-      colour = cropping_season
-   )) +
-   scale_y_continuous(limits = c(
-      0,
-      max(
-         season_dates$Planting_day +
-            season_dates$season_length,
-         na.rm = TRUE
-      )
+```
+
+#### Calculating treatment means
+```{r Herm15_means}
+Herm_15_m <- Herm_15_dat %>%
+   group_by(host_genotype, n_treatment) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             location = unique(location),
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             fungicide_ai = unique(fungicide_ai),
+             dose_ai.ha = unique(dose_ai.ha),
+             trial_ref = unique(trial_ref),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
+             plot_width.m. = mean(plot_width, na.rm = TRUE),
+             plant_density = unique(plant_density),
+             row_spacing = unique(row_spacing),
+             replicates = length(as.numeric(replicate)),
+             planting_date = unique(planting_date),
+             emergence_date = unique(emergence_date),
+             flowering_date = unique(flowering_date),
+             pod_fill_date = unique(pod_fill_date),
+             mid_late_pod_fill = unique(mid_late_pod_fill),
+             first_sign_disease = unique(first_sign_disease),
+             fungicide_application_1 = unique(fungicide_application_1),
+             fungicide_application_2 = unique(fungicide_application_2),
+             fungicide_application_3 = unique(fungicide_application_3),
+             total_fungicide = unique(total_fungicide),
+             harvest_date = unique(harvest_date),
+             final_assessment = unique(final_assessment),
+             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+             rating_scale = unique(rating_scale),
+             disease_error = sd(PM_final_severity, na.rm = TRUE), # generates NAs and needs repeating below
+             D_error_type = "stdev",
+             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+             raw_graded = NA,
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+             Y_error_type = "stdev",
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ factor(n_treatment), 
+                               data = Herm_15_dat))[1,3],
+              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), 
+                                data = Herm_15_dat))[1,3]
+   )
+
+# For some wierd reason standard deviations are comming back NA in the code above
+Herm_15_m[,c("disease_error","yield_error")] <- 
+   Herm_15_dat %>%
+   group_by(n_treatment) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("disease_error","yield_error"))
+
+Herm_15_m <- fold_data(Herm_15_m, PM_MB_means)
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Herm_15_m, 
+                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
+
+write.csv(
+   Herm_15_m,
+   here("cache/Herm_15_means.csv"),row.names = FALSE
+)
+
+```
+
+### Hermitage 2016  
+Disease data for Hermitage 2016 only exists as a mean of treatments within the `2016 Mungbean PM trials summary.xlsx` file.  
+```{r Herm16_dataimport}
+# Yield data from 2016 Hermitage trial with final disease severity
+Herm_16 <-
+   read.xlsx(
+      here("data/Yeild Data 2016 Kingaroy Hermitage (PaulM adjusted).xlsx"),
+      sheet = "Hermitage",
+      startRow = 1,
+      colNames = TRUE
+   )[1:28, 1:9]
+
+Herm_16$Year <- 2016
+Herm_16$location <- "Hermitage"
+
+Herm_16$Plot <- as.numeric(unlist(strsplit(
+   Herm_16$Plot, "P"))[
+      seq(from = 2, to = 56, by = 2)])
+
+```
+
+#### Define treatment data
+```{r Herm16_treatmentDefine}
+Herm_16_dat <- Herm_16 %>%
+   mutate(trade_name = 
+             case_when(Treatment == "1" ~ "control",
+                       TRUE ~ "Folicur"))%>%
+   mutate(fungicide_ai = 
+             case_when(Treatment == "1" ~ "control",
+                       TRUE ~ "tebuconazole"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Treatment == "1" ~ 0,
+                       TRUE ~ 62.35))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Treatment == "1" ~ as.Date(NA),
+                       Treatment == "2" ~ as.Date("2016-03-17", format = "%Y-%m-%d"),
+                       Treatment == "3" ~ as.Date("2016-03-17", format = "%Y-%m-%d"),
+                       Treatment == "4" ~ as.Date("2016-03-17", format = "%Y-%m-%d"),
+                       Treatment == "5" ~ as.Date("2016-03-8", format = "%Y-%m-%d"),
+                       Treatment == "6" ~ as.Date("2016-03-8", format = "%Y-%m-%d"),
+                       Treatment == "7" ~ as.Date("2016-03-17", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Treatment == "1" ~ as.Date(NA),
+                       Treatment == "3" ~ as.Date("2016-03-30", format = "%Y-%m-%d"),
+                       Treatment == "4" ~ as.Date("2016-03-30", format = "%Y-%m-%d"),
+                       Treatment == "6" ~ as.Date("2016-03-22", format = "%Y-%m-%d"),
+                       Treatment == "7" ~ as.Date("2016-03-30", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_3 = 
+             case_when(Treatment == "4" ~ as.Date("2016-04-13", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Treatment == "1" ~ 0,
+                       Treatment == "2" ~ 1,
+                       Treatment == "3" ~ 2,
+                       Treatment == "4" ~ 3,
+                       Treatment == "5" ~ 1,
+                       Treatment == "6" ~ 2,
+                       Treatment == "7" ~ 2,
+                       TRUE ~ 9999))
+
+```
+
+#### Input trial data
+```{r Herm16_Trialdat}
+
+Herm_16_dat <- 
+   data.frame(trial_ref = "mung1516/01",
+              year = "2016",
+              location = "Hermitage",
+              host_genotype = "Jade",
+              trial_design = "RCB",
+              plot_length = 12,
+              plot_width = 4,
+              plant_density = NA,
+              row_spacing = 0.75,
+              replicate = Herm_16_dat$rep,
+              planting_date = as.Date("2016-02-03", format = "%Y-%m-%d"),
+              emergence_date = as.Date("2016-02-12", format = "%Y-%m-%d"),
+              flowering_date = as.Date(NA),
+              pod_fill_date = as.Date(NA),
+              mid_late_pod_fill = as.Date("2016-04-15", format = "%Y-%m-%d"),
+              first_sign_disease = as.Date("2016-03-08", format = "%Y-%m-%d"),
+              trade_name = as.factor(Herm_16_dat$trade_name),
+              fungicide_ai = Herm_16_dat$fungicide_ai,
+              dose_ai.ha = Herm_16_dat$dose_ai.ha,
+              n_treatment = as.numeric(Herm_16_dat$Treatment),
+              fungicide_application_1 = Herm_16_dat$fungicide_application_1,
+              fungicide_application_2 = Herm_16_dat$fungicide_application_2,
+              fungicide_application_3 = Herm_16_dat$fungicide_application_3,
+              total_fungicide = Herm_16_dat$spray_n,
+              harvest_date = as.Date("2016-05-06", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2016-04-15", format = "%Y-%m-%d"),
+              PM_final_severity = NA,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(Herm_16_dat$`Raw.Adjusted.Yeild./.ha`),
+              stringsAsFactors = FALSE)
+```
+
+#### Calculating treatment means
+```{r Herm16_means}
+Herm_16_m <- Herm_16_dat %>%
+   group_by(host_genotype, n_treatment) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             location = unique(location),
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             fungicide_ai = unique(fungicide_ai),
+             dose_ai.ha = unique(dose_ai.ha),
+             trial_ref = unique(trial_ref),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
+             plot_width.m. = mean(plot_width, na.rm = TRUE),
+             plant_density = unique(plant_density),
+             row_spacing = unique(row_spacing),
+             replicates = length(as.numeric(replicate)),
+             planting_date = unique(planting_date),
+             emergence_date = unique(emergence_date),
+             flowering_date = unique(flowering_date),
+             pod_fill_date = unique(pod_fill_date),
+             mid_late_pod_fill = unique(mid_late_pod_fill),
+             first_sign_disease = unique(first_sign_disease),
+             fungicide_application_1 = unique(fungicide_application_1),
+             fungicide_application_2 = unique(fungicide_application_2),
+             fungicide_application_3 = unique(fungicide_application_3),
+             total_fungicide = unique(total_fungicide),
+             harvest_date = unique(harvest_date),
+             final_assessment = unique(final_assessment),
+             rating_scale = unique(rating_scale),
+             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+             raw_graded = "Yes",
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+             Y_error_type = "stdev",
+             Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = Herm_16_dat))[1,3]
+   )
+
+# For some wierd reason standard deviations are comming back NA in the code above
+Herm_16_m[,"yield_error"] <- 
+   Herm_16_dat %>%
+   group_by(n_treatment) %>%
+   summarise(yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("yield_error"))
+
+```
+
+#### Mean disease incidence data
+```{r}
+Herm_16.DR  <-
+   read.xlsx(
+      here("data/2016 Mungbean PM trials summary.xlsx"),
+      sheet = "Hermitage_2016",
+      startRow = 5,
+      colNames = TRUE
+   )
+names(Herm_16.DR)[1:6] <- c("Treatment", "dae24","dae38","dae48","dae63","Final_Yield_tHa")
+
+Herm_16.DR <- Herm_16.DR %>%
+   mutate(n_treatment = 
+             case_when(Treatment == "5wk + 2s (3s)" ~ 4,
+                       Treatment == "5wk+1 (2s)" ~ 3,
+                       Treatment == "1/3+1 (2s)" ~ 7,
+                       Treatment == "1st sign (1s)" ~ 5,
+                       Treatment == "5wk (1s)" ~ 2,
+                       Treatment == "1st sign+1 (2s)" ~ 6,
+                       Treatment == "Unsprayed" ~ 1,
+                       TRUE ~ 9999))
+
+Herm_16_m <- left_join(Herm_16_m,Herm_16.DR)
+
+# dae24 recorded no incidence
+Herm_16_m$AUDPC_m <- apply(Herm_16_m[,c("dae24", "dae38", "dae48", "dae63")]-1,1, 
+                            FUN = audpc, 
+                           dates = c(9,13,23,38))
+
+Herm_16_m$AUDPS_m <- apply(Herm_16_m[,c("dae24", "dae38", "dae48", "dae63")]-1,1, 
+                            FUN = audps, 
+                           dates = c(9,13,23,38))
+
+Herm_16_m$AUDPC_sd <- NA
+Herm_16_m$AUDPS_sd <- NA
+Herm_16_m$PM_final_severity <- Herm_16_m$dae63
+Herm_16_m$Inc_Ms <- anova(lm(AUDPC_m ~ factor(n_treatment), data = Herm_16_m))[1,3] #ANOVA F-tests on an essentially perfect fit are unreliable
+
+```
+
+#### Tidy and save data
+```{r Herm16_tidyAndSaveData}
+Herm_16_m <- fold_data(Herm_16_m, PM_MB_means)
+Herm_16_m <- Herm_16_m[,!colnames(Herm_16_m) %in%
+                          c('Treatment',"dae24","dae38","dae48","dae63","Final_Yield_tHa")]
+
+#final Yields from disease data different to yield data set
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Herm_16_m, 
+                             new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
+
+write.csv(
+   Herm_16_m,
+   here("cache/Herm_16_means.csv"),row.names = FALSE
+)
+
+```
+
+### Kingaroy 2016  
+Disease data for Kingaroy 2016 only exists as a mean of treatments within the `2016 Mungbean PM trials summary.xlsx` file.  
+```{r King16_dataimport}
+# Yield data from 2016 Hermitage trial with final disease severity
+King_16 <-
+   read.xlsx(
+      here("data/Yeild Data 2016 Kingaroy Hermitage (PaulM adjusted).xlsx"),
+      sheet = "Kingaroy",
+      startRow = 1,
+      colNames = TRUE
+   )[1:28, 1:9]
+
+# Create Year and location variables
+King_16$Year <- 2016
+King_16$location <- "Kingaroy"
+
+# Convert plot values to numeric and remove "P" prefix
+King_16$Plot <- as.numeric(unlist(strsplit(
+   King_16$Plot, "P"))[
+      seq(from = 2, to = 56, by = 2)])
+
+```
+
+#### Define treatment data
+```{r King16_treatmentDefine}
+King_16_dat <- King_16 %>%
+   mutate(trade_name = 
+             case_when(Treatment == "1" ~ "control",
+                       TRUE ~ "Folicur"))%>%
+   mutate(fungicide_ai = 
+             case_when(Treatment == "1" ~ "control",
+                       TRUE ~ "tebuconazole"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Treatment == "1" ~ 0,
+                       TRUE ~ 62.35))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Treatment == "1" ~ as.Date(NA),
+                       Treatment == "2" ~ as.Date("2016-03-22", format = "%Y-%m-%d"),
+                       Treatment == "3" ~ as.Date("2016-03-22", format = "%Y-%m-%d"),
+                       Treatment == "4" ~ as.Date("2016-03-22", format = "%Y-%m-%d"),
+                       Treatment == "5" ~ as.Date("2016-03-09", format = "%Y-%m-%d"),
+                       Treatment == "6" ~ as.Date("2016-03-09", format = "%Y-%m-%d"),
+                       Treatment == "7" ~ as.Date("2016-03-22", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Treatment == "1" ~ as.Date(NA),
+                       Treatment == "3" ~ as.Date("2016-04-05", format = "%Y-%m-%d"),
+                       Treatment == "4" ~ as.Date("2016-04-05", format = "%Y-%m-%d"),
+                       Treatment == "6" ~ as.Date("2016-03-22", format = "%Y-%m-%d"),
+                       Treatment == "7" ~ as.Date("2016-04-05", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_3 = 
+             case_when(Treatment == "4" ~ as.Date("2016-04-19", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Treatment == "1" ~ 0,
+                       Treatment == "2" ~ 1,
+                       Treatment == "3" ~ 2,
+                       Treatment == "4" ~ 3,
+                       Treatment == "5" ~ 1,
+                       Treatment == "6" ~ 2,
+                       Treatment == "7" ~ 2,
+                       TRUE ~ 9999))
+
+```
+
+#### Input trial data
+```{r King16_Trialdat}
+
+King_16_dat <- 
+   data.frame(trial_ref = "mung1516/02",
+              year = "2016",
+              location = "Kingaroy",
+              host_genotype = "Jade",
+              trial_design = "RCB",
+              plot_length = 12,
+              plot_width = 4,
+              plant_density = NA,
+              row_spacing = 0.75,
+              replicate = King_16_dat$rep,
+              planting_date = as.Date("2016-02-11", format = "%Y-%m-%d"),
+              emergence_date = as.Date("2016-02-19", format = "%Y-%m-%d"),
+              flowering_date = as.Date(NA),
+              pod_fill_date = as.Date("2016-04-05", format = "%Y-%m-%d"),
+              mid_late_pod_fill = as.Date(NA),
+              first_sign_disease = as.Date("2016-03-09", format = "%Y-%m-%d"),
+              trade_name = as.factor(King_16_dat$trade_name),
+              fungicide_ai = King_16_dat$fungicide_ai,
+              dose_ai.ha = King_16_dat$dose_ai.ha,
+              n_treatment = as.numeric(King_16_dat$Treatment),
+              fungicide_application_1 = King_16_dat$fungicide_application_1,
+              fungicide_application_2 = King_16_dat$fungicide_application_2,
+              fungicide_application_3 = King_16_dat$fungicide_application_3,
+              total_fungicide = King_16_dat$spray_n,
+              harvest_date = as.Date("2016-05-10", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2016-04-19", format = "%Y-%m-%d"),
+              PM_final_severity = NA,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(King_16_dat$`Raw.Adjusted.Yeild./.ha`),
+              stringsAsFactors = FALSE)
+```
+
+#### Calculating treatment means
+```{r King16_means}
+King_16_m <- King_16_dat %>%
+   group_by(host_genotype, n_treatment) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             location = unique(location),
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             fungicide_ai = unique(fungicide_ai),
+             dose_ai.ha = unique(dose_ai.ha),
+             trial_ref = unique(trial_ref),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
+             plot_width.m. = mean(plot_width, na.rm = TRUE),
+             plant_density = unique(plant_density),
+             row_spacing = unique(row_spacing),
+             replicates = length(as.numeric(replicate)),
+             planting_date = unique(planting_date),
+             emergence_date = unique(emergence_date),
+             flowering_date = unique(flowering_date),
+             pod_fill_date = unique(pod_fill_date),
+             mid_late_pod_fill = unique(mid_late_pod_fill),
+             first_sign_disease = unique(first_sign_disease),
+             fungicide_application_1 = unique(fungicide_application_1),
+             fungicide_application_2 = unique(fungicide_application_2),
+             fungicide_application_3 = unique(fungicide_application_3),
+             total_fungicide = unique(total_fungicide),
+             harvest_date = unique(harvest_date),
+             final_assessment = unique(final_assessment),
+             rating_scale = unique(rating_scale),
+             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+             raw_graded = "Yes",
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE), # Calculation returned as NA, repeated below
+             Y_error_type = "stdev",
+             Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment), data = King_16_dat))[1,3]
+   )
+
+# For some wierd reason standard deviations are comming back NA in the code above
+King_16_m[,"yield_error"] <- 
+   King_16_dat %>%
+   group_by(n_treatment) %>%
+   summarise(yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("yield_error"))
+
+```
+
+#### Mean Disease incidence assessments through the 2016 season
+```{r King16_disease}
+King_16.DR  <-
+   read.xlsx(
+      here("data/2016 Mungbean PM trials summary.xlsx"),
+      sheet = "Kingaroy_2016",
+      startRow = 5,
+      colNames = TRUE
+   )
+
+# Rename columns
+colnames(King_16.DR)[1:6] <- c("Treatment", "dae20","dae34","dae46","PM_final_severity","Final_Yield_tHa")
+
+# Define Treatments
+King_16.DR <- King_16.DR %>%
+   mutate(n_treatment = 
+             case_when(Treatment == "4wk+2 (3s)" ~ 4,
+                       Treatment == "4wk+1 (2s)" ~ 3,
+                       Treatment == "1/3+1 (2s)" ~ 7,
+                       Treatment == "1st sign (1s)" ~ 5,
+                       Treatment == "4wk (1s)" ~ 2,
+                       Treatment == "1st sign+1 (2s)" ~ 6,
+                       Treatment == "Unsprayed" ~ 1,
+                       TRUE ~ 9999))
+
+# Join disease assesment data with grain yield data
+King_16_m <- left_join(King_16_m,King_16.DR)
+
+# Calculate AUDPC
+King_16_m$AUDPC_m <- apply(King_16_m[,c("dae20", "dae34", "dae46", "PM_final_severity")]-1,1, 
+                            FUN = audps, dates = c(20,34,46,60))
+King_16_m$AUDPS_m <- apply(King_16_m[,c("dae20", "dae34", "dae46", "PM_final_severity")]-1,1, 
+                            FUN = audps, dates = c(20,34,46,60))
+
+# Create AUDPC/S standard deviation columns
+#  defined as NA because we only had treatment mean data
+#  for this experiment
+King_16_m$AUDPS_sd <- NA
+King_16_m$AUDPC_sd <- NA
+
+# Calculate disease mean squares
+King_16_m$Inc_Ms <- anova(lm(AUDPC_m ~ factor(n_treatment), 
+                             data = King_16_m))[1,3] #ANOVA F-tests on an essentially perfect fit are unreliable
+```
+
+#### Tidy and save data
+```{r tidyKing16}
+King_16_m <- fold_data(King_16_m, PM_MB_means)
+King_16_m <- King_16_m[,!colnames(King_16_m) %in% c('Treatment',"dae20","dae34","dae46","Final_Yield_tHa")]
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = King_16_m, 
+                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
+
+write.csv(
+   King_16_m,
+   here("cache/King_16_means.csv"),
+   row.names = FALSE
+)
+
+```
+
+### Missen Flats 2017
+```{r fog2017}
+# ____________________________________________________________
+# _____________   Missen Flats (Fogarty's) 2017     ____________
+Fogerty_17 <-
+   read.xlsx(
+      here("data/Fogerty Work File 2017 (Autosaved).xlsx"),
+      sheet = "Data",
+      startRow = 3,
+      colNames = TRUE,
+      detectDates = TRUE
+   )[, 1:43]
+
+# Columns to keep
+Fogerty_17 <- Fogerty_17[, c('Plot', 'Rep', 'Row', 'Column', 'Chem.Trt',
+                           'Chemical', 'Row.Spacing.(m)', 'Treatment.No',
+                           'Treatment', 'Population.plsnts/ha',
+                           '2017-03-07', '2017-03-19', '2017-03-24',
+                           '2017-04-02', '2017-04-10', '2017-04-18',
+                           'Yield.t/ha', 'Grain.Moisture.%', 'Temp.moisture.Taken',
+                           '100.grain.wt.Grams')]
+
+# could also use gsub to remove Ts in the treatment variable
+Fogerty_17$Treatment.No <- as.numeric(unlist(strsplit(
+   Fogerty_17$Treatment.No, "T"))[
+      seq(from = 2, to = 324, by = 2)])
+
+```
+
+#### Define treatment data
+```{r Fog17_treatmentDefine}
+Fogerty_17_dat <- Fogerty_17 %>%
+   mutate(trade_name = 
+             case_when(Chem.Trt == 1 ~ "Folicur",
+                       Chem.Trt == 2 ~ "Throttle",
+                       Chem.Trt == 3 ~ "Custodia",
+                       TRUE ~ "other"))%>%
+   mutate(fungicide_ai = 
+             as.character(case_when(Chem.Trt == 1 ~ "tebuconazole",
+                                    Chem.Trt == 2 ~ "propiconazole",
+                                    Chem.Trt == 3 ~ "200 g/L tebuconazole + 120 g/L azoxystrobin",
+                                    TRUE ~ "other")))%>%
+   mutate(dose_ai.ha = 
+             case_when(Chem.Trt == 1 ~ 62,
+                       Chem.Trt == 2 ~ 125,
+                       Chem.Trt == 3 ~ 60,
+                       TRUE ~ NA_real_))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Treatment.No == 1 ~ as.Date(NA),
+                       Treatment.No == 2 ~ as.Date("2017-02-22", format = "%Y-%m-%d"),
+                       Treatment.No == 3 ~ as.Date("2017-03-08", format = "%Y-%m-%d"),
+                       Treatment.No == 4 ~ as.Date("2017-03-08", format = "%Y-%m-%d"),
+                       Treatment.No == 5 ~ as.Date("2017-03-19", format = "%Y-%m-%d"),
+                       Treatment.No == 6 ~ as.Date("2017-03-08", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Treatment.No == 4 ~ as.Date("2017-03-24", format = "%Y-%m-%d"),
+                       Treatment.No == 6 ~ as.Date("2017-04-02", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Treatment.No == 1 ~ 0,
+                       Treatment.No == 4 ~ 2,
+                       Treatment.No == 6 ~ 2,
+                       TRUE ~ 1))
+
+```
+
+#### Input trial data
+```{r Fog17_Trialdat}
+# Remove zeros because of recording errors (some people recorded zero for no incidence when it should be 1)
+Fogerty_17_dat[Fogerty_17_dat$`2017-03-07` == 0 ,c("2017-03-07")] <- 1
+
+Fogerty_17_dat <- 
+   data.frame(trial_ref = "mung1617/02",
+              year = "2017",
+              location = "Missen Flats",
+              host_genotype = "Jade",
+              trial_design = "RCB",
+              plot_length = 10,
+              plot_width = 2,
+              plant_density = Fogerty_17_dat$`Population.plsnts/ha`,
+              row_spacing = Fogerty_17_dat$`Row.Spacing.(m)`,
+              replicate = Fogerty_17_dat$Rep,
+              planting_date = as.Date("2017-01-27", format = "%Y-%m-%d"),
+              emergence_date = as.Date("2017-02-01", format = "%Y-%m-%d"),
+              flowering_date = as.Date(NA),
+              pod_fill_date = as.Date(NA),
+              mid_late_pod_fill = as.Date(NA),
+              first_sign_disease = as.Date("2017-03-07", format = "%Y-%m-%d"),
+              trade_name = as.character(Fogerty_17_dat$trade_name),
+              fungicide_ai = as.character(Fogerty_17_dat$fungicide_ai),
+              dose_ai.ha = Fogerty_17_dat$dose_ai.ha,
+              n_treatment = as.numeric(Fogerty_17_dat$Treatment.No),
+              fungicide_application_1 = Fogerty_17_dat$fungicide_application_1,
+              fungicide_application_2 = Fogerty_17_dat$fungicide_application_2,
+              total_fungicide = Fogerty_17_dat$spray_n,
+              harvest_date = as.Date("2017-05-11", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2017-04-18", format = "%Y-%m-%d"),
+              PM_final_severity = Fogerty_17_dat$`2017-04-18`,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(Fogerty_17_dat$`Yield.t/ha`),
+              AUDPC = apply(Fogerty_17_dat[,c("2017-03-07", "2017-03-19", "2017-03-24",
+                                              "2017-04-02","2017-04-10","2017-04-18")]-1,1, 
+                            FUN = audpc, dates = c(1,12,17,26,34,42)), # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
+              AUDPS = apply(Fogerty_17_dat[,c("2017-03-07", "2017-03-19", "2017-03-24",
+                                              "2017-04-02","2017-04-10","2017-04-18")]-1,1, 
+                            FUN = audps, dates = c(1,12,17,26,34,42)),
+              stringsAsFactors = FALSE)
+```
+
+#### Calculating treatment means
+```{r Fog17_means}
+
+Fogerty_17_m <- Fogerty_17_dat %>%
+   group_by(n_treatment, row_spacing, fungicide_ai) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             location = unique(location),
+             host_genotype = unique(host_genotype),
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             dose_ai.ha = unique(dose_ai.ha),
+             trial_ref = unique(trial_ref),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
+             plot_width.m. = mean(plot_width, na.rm = TRUE),
+             plant_density = mean(plant_density, na.rm = TRUE),
+             replicates = length(as.numeric(replicate)),
+             planting_date = unique(planting_date),
+             emergence_date = unique(emergence_date),
+             flowering_date = unique(flowering_date),
+             pod_fill_date = unique(pod_fill_date),
+             mid_late_pod_fill = unique(mid_late_pod_fill),
+             first_sign_disease = unique(first_sign_disease),
+             fungicide_application_1 = unique(fungicide_application_1),
+             fungicide_application_2 = unique(fungicide_application_2),
+             total_fungicide = unique(total_fungicide),
+             harvest_date = unique(harvest_date),
+             final_assessment = unique(final_assessment),
+             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+             rating_scale = unique(rating_scale),
+             disease_error = sd(PM_final_severity, na.rm = TRUE), # Generating NAs so it will be repeated below
+             D_error_type = "stdev",
+             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+             raw_graded = NA,
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+             Y_error_type = "stdev",
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ factor(n_treatment) + fungicide_ai + row_spacing, 
+                                  data = subset(Fogerty_17_dat, trade_name != "Custodia")))[1,3], # of only triazoles
+             Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(n_treatment) + fungicide_ai + row_spacing, 
+                                  data = subset(Fogerty_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
+   )
+
+# For some weird reason standard deviations are comming back NA in the code above
+Fogerty_17_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <-
+   Fogerty_17_dat %>%
+   group_by(n_treatment, row_spacing, fungicide_ai) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("n_treatment","row_spacing","disease_error","yield_error"))
+
+# Define control treatments
+Fogerty_17_m[Fogerty_17_m$n_treatment == 1, "fungicide_ai"] <- "control"
+Fogerty_17_m[Fogerty_17_m$n_treatment == 1,"dose_ai.ha"] <- 0
+Fogerty_17_m[Fogerty_17_m$n_treatment == 1, "trade_name"] <- "control"
+
+# Format and organise the dataframe
+Fogerty_17_m <- fold_data(Fogerty_17_m, PM_MB_means)
+Fogerty_17_m <- copy_class(PM_MB_means, Fogerty_17_m)
+
+# I have comment out this code because it does not replace the control plots properly as there is nothing to separate them from each other
+# insert new calculations into data
+#PM_MB_means <-   
+   # replace_data(template_data = PM_MB_means,
+   #                          new_data = Fogerty_17_m,
+   #                          new_data_column = "AUDPC_m",
+   #                          ignore_columns = c(5:8,10:16,29:46),
+   #                          subset_factor = "mung1617/02")
+
+if(all(dim(Fogerty_17_m) == dim(PM_MB_means[PM_MB_means$trial_ref == "mung1617/02",]))){
+PM_MB_means[PM_MB_means$trial_ref == "mung1617/02",] <- 
+   Fogerty_17_m
+}else{warning("Dimensions don't match check data")}
+
+write.csv(
+   Fogerty_17_m,
+   here("cache/Fogerty_17_mean.csv"),
+   row.names = FALSE
+)
+
+```
+
+### Hermitage 2017
+```{r Herm_17}
+
+# _____________   Hermitage  2017     ____________
+Herm_17 <-
+   read.xlsx(
+      here("data/Hermitage working file 2017 .xlsx"),
+      sheet = "Hermitage Trial",
+      rows = 3:165,
+      cols = 1:38,
+      colNames = TRUE,
+      detectDates = TRUE
+   )
+
+# Adjust the Yield to 12% moisture
+Herm_17$`Yield.T/Ha` <-
+   (Herm_17$`Yield.T/Ha` / Herm_17$`Moisture%`) * 12
+
+```
+
+#### Define treatment data
+```{r Herm_17_treatmentDefine}
+Herm_17_dat <- Herm_17 %>%
+   mutate(trade_name = 
+             case_when(Chemical.Trt == 1 ~ "Folicur",
+                       Chemical.Trt == 2 ~ "Throttle",
+                       Chemical.Trt == 3 ~ "Custodia",
+                       TRUE ~ "other"))%>%
+   mutate(fungicide_ai = 
+             case_when(Chemical.Trt == 1 ~ "tebuconazole",
+                       Chemical.Trt == 2 ~ "propiconazole",
+                       Chemical.Trt == 3 ~ "200 g/L tebuconazole + 120 g/L azoxystrobin",
+                       TRUE ~ "other"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Chemical.Trt == 1 ~ 62,
+                       Chemical.Trt == 2 ~ 125,
+                       Chemical.Trt == 3 ~ 60,
+                       TRUE ~ 9999))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Manage.Trt == "1" ~ as.Date(NA),
+                       Manage.Trt == "T2" ~ as.Date("2017-03-13", format = "%Y-%m-%d"),
+                       Manage.Trt == "T3" ~ as.Date("2017-03-24", format = "%Y-%m-%d"),
+                       Manage.Trt == "T4" ~ as.Date("2017-03-27", format = "%Y-%m-%d"),
+                       Manage.Trt == "T5" ~ as.Date("2017-03-27", format = "%Y-%m-%d"),
+                       Manage.Trt == "T6" ~ as.Date("2017-04-05", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Manage.Trt == "T3" ~ as.Date("2017-04-07", format = "%Y-%m-%d"),
+                       Manage.Trt == "T5" ~ as.Date("2017-04-11", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Manage.Trt == "1" ~ 0,
+                       Manage.Trt == "T3" ~ 2,
+                       Manage.Trt == "T5" ~ 2,
+                       TRUE ~ 1))
+
+```
+
+#### Input trial data
+```{r Herm17_Trialdat}
+Herm_17_dat <- 
+   data.frame(trial_ref = "mung1617/01",
+              year = "2017",
+              location = "Hermitage",
+              host_genotype = "Jade",
+              trial_design = "RCB",
+              plot_length = Herm_17_dat$Plot.Length,
+              plot_width = 2,
+              plant_density = NA,
+              row_spacing = Herm_17_dat$`Row.Spacing.(m)`,
+              replicate = Herm_17_dat$Rep,
+              planting_date = as.Date("2017-02-13", format = "%Y-%m-%d"),
+              emergence_date = as.Date("2017-02-20", format = "%Y-%m-%d"),
+              flowering_date = as.Date(NA),
+              pod_fill_date = as.Date(NA),
+              mid_late_pod_fill = as.Date(NA),
+              first_sign_disease = as.Date("2017-03-24", format = "%Y-%m-%d"),
+              trade_name = as.character(Herm_17_dat$trade_name),
+              fungicide_ai = Herm_17_dat$fungicide_ai,
+              dose_ai.ha = Herm_17_dat$dose_ai.ha,
+              n_treatment = as.numeric(unlist(strsplit(Herm_17_dat$Manage.Trt, "T")
+                                              )[unlist(strsplit(Herm_17_dat$Manage.Trt, "T")) != ""]),
+              fungicide_application_1 = Herm_17_dat$fungicide_application_1,
+              fungicide_application_2 = Herm_17_dat$fungicide_application_2,
+              total_fungicide = Herm_17_dat$spray_n,
+              harvest_date = as.Date("2017-06-26", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2017-05-11", format = "%Y-%m-%d"),
+              PM_final_severity = Herm_17_dat$`I_11/05/2017`,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(Herm_17_dat$`Yield.T/Ha`),
+              stringsAsFactors = FALSE)
+
+Herm_17_dat <- cbind(Herm_17_dat,data.frame(
+   AUDPC = apply(data.frame(zero = 0,
+                            Herm_17[,c("2017-03-24","I_2/04/2017", "I_11/04/2017", 
+                                       "I_18/04/2017", "I_24/04/2017","I_3/05/2017","I_11/05/2017")]-1),1, 
+                 FUN = audpc, 
+                 dates = c((Herm_17_dat$first_sign_disease[1]-7)-
+                              Herm_17_dat$planting_date[1],
+                           39,48,57,64,70,79,87)
                  ),
-   labels = axis_labels_date,
-   breaks = first_day_month) +
-   geom_point(aes(x = trial_ref, y = Disease_day)) +
-   coord_flip() +
-   scale_color_manual(values=c("black","grey70"))+
-   ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
-
-SeasonPlot
-```
-
-In most years, regardless of the age of the crop, powdery mildew establishes in March, which is to be expected.
-The disease is driven by weather conditions and the plant is vulnerable at any growth stage.
-
-### AUDPC visualise raw data
-
-First let's check we have all the AUDPC observations.
-
-```{r AUDPC_check}
-PM_MB_means %>%
-   filter(is.na(AUDPC_m)) %>%
-   distinct(trial_ref, location, year,AUDPC_m, first_sign_disease, final_assessment)%>%
-   kable(align = "c")
-```
-
-The trials `r unique(PM_MB_means[is.na(PM_MB_means$AUDPC_m),"trial_ref"]) ` don't have an estimate of AUDPC and need to be filled in. 
-The following script estimates AUDPC from the final disease severity rating and the first sign of disease information.
-
-```{r SingleObsAUDPC}
-source(here("R/AUDPC_for_single_obs.R"))
-write.csv(PM_MB_means,
-          "cache/1911_PM_MB_means&Ygains.csv", row.names = FALSE)
-```
-
-      _How well does 'area under the disease progress curve' (AUDPC) predict grain yield?_
-
-   and
-
-      _Does spray_management scenario mitigate yield loss through reducing AUDPC?_
-
-We would expect to see grain yield decline with increasing AUDPC.
-Let's just plot yield vs AUDPC.
-
-```{r Yield_vs_AUDPC}
-
-plot(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means)
-abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means))
-
-```
-
-There appears to be a weak positive relationship between the two continuous variables.
-Does a linear model confirm this?
-
-```{r AUDPClm}
-summary(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means))
-```
-
-This is not what we would expect and the low R squared value of `r round(summary(lm(grain_yield.t.ha.
-~ AUDPC_m, data = PM_MB_means))$adj.r.squared,3)` perhaps there are additional factors influencing this relationship.
-
-Let's tease out variation due to trial location, season, row spacing, and other seasonal variables are preventing us from seeing the expected relationship.
-Let's do the plot again for each trial where there are no missing values.
-Note: The plots are ordered by mean yield of the trial.
-
-```{r AUDPCxTrial}
-sm2lg <- PM_MB_means %>%
-   group_by(trial_ref) %>%
-   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
-   arrange(TY)
-
-for (i in sm2lg$trial_ref) {
-   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
-   if (any(is.na(dat1$grain_yield.t.ha.))) {
-      next
-   }
-   if (any(is.na(dat1$AUDPC_m))) {
-      next
-   }
-
-   plot(
-      grain_yield.t.ha. ~ AUDPC_m,
-      data = dat1,
-      main = paste(dat1$location[1], (dat1$year[1])),
-      ylim = c(0, max(PM_MB_means$grain_yield.t.ha., na.rm = TRUE)),
-      xlim = c(0, max(PM_MB_means$AUDPC_m, na.rm = TRUE))
-   )
-   abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = dat1))
-   points(grain_yield.t.ha. ~ AUDPC_m,
-          data = dat1[dat1$fungicide_ai == "control",],
-          col = "red")
-
-}
-```
-
-Based on a GRDC report by Sue Thompson [-@SueThompson2016] we want to know what the yield loss was in on cultivar Jade in the 2016 Trials.
-```{r}
-dat3 <- PM_MB_means %>%
-   filter(year == "2016",
-          host_genotype == "Jade",
-          fungicide_ai == "control")%>%
-   group_by(location)%>%
-   summarise(C_Yield = mean(grain_yield.t.ha., na.rm = TRUE))
-
-dat3$F_Yield <- PM_MB_means %>%
-   filter(year == "2016",
-          host_genotype == "Jade",
-          fungicide_ai != "control")%>%
-   group_by(location)%>%
-   summarise(F_Yield = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
-   pull(F_Yield)
-
-dat3 %>% 
-   mutate(diff = F_Yield - C_Yield) %>%
-   mutate(percent = (diff/F_Yield)*100)
-
-```
-
-This sequence of graphs show that AUDPC and disease incidence tends not affect yields if the season is a low yielding season, _i.e._ lower than 1 tonne per hectare.
-The higher the yield, the greater greater the influence on the disease on the yield especially if the crop is high yielding with AUDPC also being large enough to reduce yield.
-
-Let's have a look again at the same sequence of graphs and analyses for area under the disease progress _stairs_.
-
-```{r Yield_vs_AUDPS}
-plot(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means)
-abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means))
-
-summary(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means))
-
-sm2lg <- PM_MB_means %>%
-   group_by(trial_ref) %>%
-   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
-   arrange(TY)
-
-for (i in sm2lg$trial_ref) {
-   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
-   if (any(is.na(dat1$grain_yield.t.ha.))) {
-      next
-   }
-   if (any(is.na(dat1$AUDPS_m))) {
-      next
-   }
-
-   plot(
-      grain_yield.t.ha. ~ AUDPS_m,
-      data = dat1,
-      main = paste(dat1$location[1], (dat1$year[1])),
-      ylim = c(0, max(
-         PM_MB_means$grain_yield.t.ha., na.rm = TRUE
-      )),
-      xlim = c(0, max(PM_MB_means$AUDPS_m, na.rm = TRUE))
-   )
-   abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = dat1))
-   points(grain_yield.t.ha. ~ AUDPS_m,
-          data = dat1[dat1$fungicide_ai == "control",],
-          col = "red")
-
-}
-```
-
-The plots from the AUPDS is similar to the AUDPC, however according to the linear model the AUDPC is a better, significant fit.
-
-A mixed effect model would be more suitable to investigate the interactive effects of location, season, and trial. 
-The mixed effect model will help us decide on the best approach and structure for our meta-analysis model.
-
-```{r}
-beans <- read.csv(here("data/FAOSTAT_data_7-6-2020.csv"))
-
-glimpse(beans)
-
-beans %>%
-   filter(Item == "Beans, dry",
-          Element == "Area harvested")%>%
-   select(Year,Value)%>%
-   ggplot(aes(y = Value, x = Year))+
-   geom_point()+
-   geom_smooth()
-
-beans %>%
-   filter(Item == "Beans, dry",
-          Element == "Yield")%>%
-   ggplot(aes(y = Value *0.1, x = Year))+
-   geom_point()+
-   geom_smooth()
-
-beans %>%
-   filter(Item == "Beans, dry",
-          Element == "Production")%>%
-   ggplot(aes(y = Value, x = Year))+
-   geom_point()+
-   geom_smooth(method = "lm")
-
-```
-
-```{r}
-save(SeasonPlot, file = here("cache/PreliminaryData.Rdata"))
-```
+   AUDPS = apply(data.frame(zero = 0,
+                            Herm_17[,c("2017-03-24","I_2/04/2017", "I_11/04/2017", 
+                                       "I_18/04/2017", "I_24/04/2017","I_3/05/2017","I_11/05/2017")]-1),1, 
+                 FUN = audps, 
+                 dates = c((Herm_17_dat$first_sign_disease[1]-7)-
+                              Herm_17_dat$planting_date[1],
+                           39,48,57,64,70,79,87))
+   ))
+
+```
+
+#### Calculating treatment means
+```{r Herm17_means}
+Herm_17_m <- Herm_17_dat %>%
+   group_by(n_treatment, fungicide_ai,row_spacing) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             location = unique(location),
+             host_genotype = unique(host_genotype),
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             dose_ai.ha = unique(dose_ai.ha),
+             trial_ref = unique(trial_ref),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
+             plot_width.m. = mean(plot_width, na.rm = TRUE),
+             plant_density = mean(plant_density, na.rm = TRUE),
+             replicates = length(as.numeric(replicate)),
+             planting_date = unique(planting_date),
+             emergence_date = unique(emergence_date),
+             flowering_date = unique(flowering_date),
+             pod_fill_date = unique(pod_fill_date),
+             mid_late_pod_fill = unique(mid_late_pod_fill),
+             first_sign_disease = unique(first_sign_disease),
+             fungicide_application_1 = unique(fungicide_application_1),
+             fungicide_application_2 = unique(fungicide_application_2),
+             total_fungicide = unique(total_fungicide),
+             harvest_date = unique(harvest_date),
+             final_assessment = unique(final_assessment),
+             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+             rating_scale = unique(rating_scale),
+             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
+             D_error_type = "stdev",
+             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+             raw_graded = NA,
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+             Y_error_type = "stdev",
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ 
+                                  factor(n_treatment) + fungicide_ai + row_spacing, 
+                               data = subset(Herm_17_dat, trade_name != "Custodia")))[1,3], # of only triazoles
+             Y_Msquare = anova(lm(grain_yield.t.ha. ~ 
+                                  factor(n_treatment) + fungicide_ai + row_spacing, 
+                               data = subset(Herm_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
+   )
+
+# For some weird reason standard deviations are comming back NA in the code above
+Herm_17_m[,c("n_treatment","fungicide_ai","row_spacing", "disease_error","yield_error")] <-
+   Herm_17_dat %>%
+   group_by(n_treatment, fungicide_ai,row_spacing) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("n_treatment","fungicide_ai","row_spacing","disease_error","yield_error"))
+
+# Add control treatment detail
+Herm_17_m <- data.frame(Herm_17_m)
+Herm_17_m[Herm_17_m$n_treatment == 1, "fungicide_ai"] <- "control"
+Herm_17_m[Herm_17_m$n_treatment == 1,"dose_ai.ha"] <- 0
+Herm_17_m[Herm_17_m$n_treatment == 1, "trade_name"] <- "control"
+
+Herm_17_m <- fold_data(Herm_17_m, PM_MB_means)
+Herm_17_m <- copy_class(PM_MB_means,Herm_17_m)
+
+if(all(dim(Herm_17_m) == dim(PM_MB_means[PM_MB_means$trial_ref == "mung1617/01",]))){
+PM_MB_means[PM_MB_means$trial_ref == "mung1617/01",] <- 
+   Herm_17_m
+}else{warning("Dimensions don't match check data")}
+
+write.csv(
+   Herm_17_m,
+   here("cache/Hermitage_17_mean.csv"),
+   row.names = FALSE
+)
+
+```
+
+### Wellcamp 2018
+```{r Wellcamp2018}
+Well_18 <-
+   read.xlsx(
+      here("data/Wellcamp Fungicide x Row Spacing x Plant Population - Experimental Design Fogarty 2018.xlsx"),
+      sheet = "Data",
+      startRow = 1,
+      colNames = TRUE
+   )
+
+colnames(Well_18)[13:14] <- c("Row.Spacing_ID", "Fungicide_ID")
+
+```
+
+#### Define treatment data
+```{r Well_18_treatmentDefine}
+Well_18_dat <- Well_18 %>%
+   mutate(trade_name = 
+             case_when(Fung.Trt == 1 ~ "Folicur",
+                       Fung.Trt == 3 ~ "Throttle",
+                       Fung.Trt == 2 ~ "Custodia",
+                       Fung.Trt == 4 ~ "control",
+                       TRUE ~ "other"))%>%
+   mutate(fungicide_ai = 
+             case_when(Fung.Trt == 1 ~ "tebuconazole",
+                       Fung.Trt == 3 ~ "propiconazole",
+                       Fung.Trt == 2 ~ "200 g/L tebuconazole + 120 g/L azoxystrobin",
+                       Fung.Trt == 4 ~ "control",
+                       TRUE ~ "other"))%>%
+   mutate(dose_ai.ha = 
+             case_when(Fung.Trt == 1 ~ 60,
+                       Fung.Trt == 2 ~ 62,
+                       Fung.Trt == 3 ~ 125,
+                       Fung.Trt == 4 ~ 0,
+                       TRUE ~ 9999))%>%
+   mutate(Row.Spacing = 
+             case_when(Row.Sp.Trt == 1 ~ 0.25,
+                       Row.Sp.Trt == 2 ~ 0.5,
+                       Row.Sp.Trt == 3 ~ 1,
+                       TRUE ~ 9999))%>%
+   mutate(fungicide_application_2 = 
+             case_when(Fung.Trt <= 3 ~ as.Date("2018-04-16", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_1 = 
+             case_when(Fung.Trt == 4 ~ as.Date(NA),
+                       Fung.Trt == 1 ~ as.Date("2018-03-28", format = "%Y-%m-%d"),
+                       Fung.Trt == 2 ~ as.Date("2018-03-28", format = "%Y-%m-%d"),
+                       Fung.Trt == 3 ~ as.Date("2018-03-28", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(Fung.Trt <= 3 ~ 2,
+                       Fung.Trt == 4 ~ 0,
+                       TRUE ~ NA_real_))
+
+```
+
+#### Input trial data
+```{r Well18_Trialdat}
+
+Well_18_dat <- 
+   data.frame(trial_ref = "mung1718/01",
+              year = "2018",
+              location = "Wellcamp",
+              host_genotype = "Jade",
+              trial_design = "RCB",
+              plot_length = Well_18_dat$Row.Length,
+              plot_width = 2,
+              plant_density = Well_18_dat$Plant.Pop,
+              row_spacing = Well_18_dat$Row.Spacing,
+              replicate = Well_18_dat$Rep,
+              planting_date = as.Date("2018-02-13", format = "%Y-%m-%d"),
+              emergence_date = as.Date(NA),
+              flowering_date = as.Date(NA),
+              pod_fill_date = as.Date(NA),
+              mid_late_pod_fill = as.Date(NA),
+              first_sign_disease = as.Date("2018-03-21", format = "%Y-%m-%d"),
+              trade_name = as.factor(Well_18_dat$trade_name),
+              fungicide_ai = Well_18_dat$fungicide_ai,
+              dose_ai.ha = Well_18_dat$dose_ai.ha,
+              n_treatment = Well_18_dat$Treatment,
+              fungicide_application_1 = Well_18_dat$fungicide_application_1,
+              fungicide_application_2 = Well_18_dat$fungicide_application_2,
+              total_fungicide = Well_18_dat$spray_n,
+              harvest_date = as.Date("2018-05-31", format = "%Y-%m-%d"),
+              final_assessment = as.Date("2018-05-02", format = "%Y-%m-%d"),
+              PM_final_severity = Well_18_dat$`IR.2-5-18`,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(Well_18_dat$`Yield./.ha`)
+              )
+
+# Calculate AUDPC
+Well_18_dat <- cbind(Well_18_dat,
+                          AUDPC = apply(data.frame(zero = 0,
+                                                   Well_18[,c("IR.23-3-18","IR.5-4-18", "IR.11-4-18", "IR.18-4-18","IR.26-4-18","IR.2-5-18")]-1),
+                                        1, 
+                                        FUN = audpc, 
+                                        dates = c((Well_18_dat$first_sign_disease[1]-7)-
+                                                     Well_18_dat$planting_date[1],
+                                                  38,51 ,57,64,72,78)
+                                        ),
+                     AUDPS = apply(data.frame(zero = 0,
+                                                   Well_18[,c("IR.23-3-18","IR.5-4-18", "IR.11-4-18", "IR.18-4-18","IR.26-4-18","IR.2-5-18")]-1),
+                                        1, 
+                                        FUN = audps, 
+                                        dates = c((Well_18_dat$first_sign_disease[1]-7)-
+                                                     Well_18_dat$planting_date[1],
+                                                  38,51 ,57,64,72,78)
+                                        )
+                          )
+
+```
+
+#### Calculating treatment means
+```{r Well17_means}
+
+Well_18_m <- Well_18_dat %>%
+   group_by(host_genotype, n_treatment, row_spacing, fungicide_ai) %>%
+   summarise(trial_ref = unique(trial_ref),
+             year = unique(year),
+             location = unique(location),
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             dose_ai.ha = unique(dose_ai.ha),
+             trial_ref = unique(trial_ref),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
+             plot_width.m. = mean(plot_width, na.rm = TRUE),
+             plant_density = mean(plant_density, na.rm = TRUE),
+             replicates = length(as.numeric(replicate)),
+             planting_date = unique(planting_date),
+             emergence_date = unique(emergence_date),
+             flowering_date = unique(flowering_date),
+             pod_fill_date = unique(pod_fill_date),
+             mid_late_pod_fill = unique(mid_late_pod_fill),
+             first_sign_disease = unique(first_sign_disease),
+             fungicide_application_1 = unique(fungicide_application_1),
+             fungicide_application_2 = unique(fungicide_application_2),
+             total_fungicide = unique(total_fungicide),
+             harvest_date = unique(harvest_date),
+             final_assessment = unique(final_assessment),
+             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+             rating_scale = unique(rating_scale),
+             disease_error = sd(PM_final_severity, na.rm = TRUE), # Generates NAs repeated below
+             D_error_type = "stdev",
+             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+             raw_graded = NA,
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+             Y_error_type = "stdev",
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Inc_Ms = anova(lm(AUDPC ~ 
+                                  factor(n_treatment) + fungicide_ai + row_spacing, 
+                               data = subset(Well_18_dat, trade_name != "Custodia")))[1,3], # of only triazoles
+             Y_Msquare = anova(lm(grain_yield.t.ha. ~ 
+                                  factor(n_treatment) + fungicide_ai + row_spacing, 
+                               data = subset(Well_18_dat, trade_name != "Custodia")))[1,3] # of only triazoles
+   )
+
+# For some weird reason standard deviations are coming back NA in the code above
+Well_18_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
+   Well_18_dat %>%
+   group_by(n_treatment, row_spacing, fungicide_ai) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("disease_error","yield_error"))
+
+Well_18_m <- fold_data(Well_18_m, PM_MB_means)
+Well_18_m <- copy_class(PM_MB_means,Well_18_m)
+
+# insert new calculations into data
+PM_MB_means <- 
+   replace_data(template_data = PM_MB_means, 
+                            new_data = Well_18_m, 
+                            new_data_column = c("total_fungicide","AUDPC_m", "AUDPC_sd"),
+                            filter_cols = c("trial_ref","year","location","n_treatment"))
+
+write.csv(
+   Well_18_m,
+   here("cache/Wellcamp_18_mean.csv"),
+   row.names = FALSE
+)
+
+```
+
+### Hermitage 2019
+```{r Herm19}
+PM_MB_19 <-
+   read.xlsx(
+      here("data/1901 Mungbean powdery mildew disease and yeild data.xlsx"),
+      startRow = 2,
+      cols = c(1:21)
+   )
+
+# Remove these plots as the results can't be trusted
+PM_MB_19 <- subset(PM_MB_19, Harvest.Plot.Number != 5)
+PM_MB_19 <- subset(PM_MB_19, Harvest.Plot.Number != 6)
+
+# Calculate area under the disease progress curve
+PM_MB_19$AUDPC <- apply(data.frame(zero = 0,PM_MB_19[,c("15-4-19.Incedence", "23-4-19.Incedence", "1-5-19.Incedence")]-1),1,FUN = audpc, dates = c(60, 70,78,86))
+PM_MB_19$AUDPS <- apply(data.frame(zero = 0,PM_MB_19[,c("15-4-19.Incedence", "23-4-19.Incedence", "1-5-19.Incedence")]-1),1,FUN = audps, dates = c(60, 70,78,86))
+
+# Calculate area under the disease progress curve for plots which were not assessed at on 2019-05-01
+PM_MB_19[is.na(PM_MB_19$`1-5-19.Incedence`),"AUDPC"] <- 
+   apply(data.frame(zero = 0,PM_MB_19[is.na(PM_MB_19$`1-5-19.Incedence`),
+                                      c("15-4-19.Incedence", "23-4-19.Incedence")]-1),
+         1,FUN = audpc,
+         dates = c(60, 70,78))
+PM_MB_19[is.na(PM_MB_19$`1-5-19.Incedence`),"AUDPS"] <- 
+   apply(data.frame(zero = 0,PM_MB_19[is.na(PM_MB_19$`1-5-19.Incedence`),
+                                      c("15-4-19.Incedence", "23-4-19.Incedence")]-1),
+         1,FUN = audps, 
+         dates = c(60, 70,78))
+```
+
+#### Define treatment data
+```{r Herm_19_treatmentDefine}
+Herm_19_dat <- PM_MB_19 %>%
+   mutate(fungicide_application_1 = 
+             case_when(`T/ment.NUM` == 1 ~ as.Date("2018-04-15", format = "%Y-%m-%d"),
+                       `T/ment.NUM` == 2 ~ as.Date("2018-04-15", format = "%Y-%m-%d"),
+                       `T/ment.NUM` == 3 ~ as.Date("2018-04-23", format = "%Y-%m-%d"),
+                       `T/ment.NUM` == 4 ~ as.Date(NA),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(fungicide_application_2 = 
+             case_when(`T/ment.NUM` == 2 ~ as.Date("2018-04-29", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(spray_n = 
+             case_when(`T/ment.NUM` == 2 ~ 2,
+                       `T/ment.NUM` == 1 ~ 1,
+                       `T/ment.NUM` == 3 ~ 1,
+                       TRUE ~ 0))%>%
+   mutate(trial_ref = 
+             case_when(TOS.NUM == 1 ~ "mung1819/01",
+                       TOS.NUM == 2 ~ "mung1819/02",
+                       TRUE ~ NA_character_))%>%
+   mutate(planting_date = 
+             case_when(TOS.NUM == 1 ~ as.Date("2018-02-04", format = "%Y-%m-%d"),
+                       TOS.NUM == 2 ~ as.Date("2018-02-18", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(emergence_date = 
+             case_when(TOS.NUM == 1 ~ as.Date("2018-02-11", format = "%Y-%m-%d"),
+                       TOS.NUM == 2 ~ as.Date("2018-02-25", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(final_assessment = 
+             case_when(TOS.NUM == 1 ~ as.Date("2018-04-24", format = "%Y-%m-%d"),
+                       TOS.NUM == 2 ~ as.Date("2018-05-01", format = "%Y-%m-%d"),
+                       TRUE ~ as.Date(NA)))%>%
+   mutate(PM_final_severity = 
+             case_when(is.na(`1-5-19.Incedence`) ~ `23-4-19.Incedence`,
+                       TRUE ~ `1-5-19.Incedence`))%>%
+   mutate(trade_name = 
+             case_when(`T/ment.NUM` == 4 ~ "control",
+                       TRUE ~ "Folicur"))%>%
+   mutate(fungicide_ai = 
+             case_when(`T/ment.NUM` == 4 ~ "control",
+                       TRUE ~ "tebuconazole"))%>%
+
+   mutate(dose_ai.ha = 
+             case_when(`T/ment.NUM` == 4 ~ 0,
+                       TRUE ~ 62))%>%
+   mutate(Y_Msquare = 
+             case_when(TOS.NUM == 1 ~ anova(lm(Yeild/1000 ~ 
+                                  factor(`T/ment.NUM`) , 
+                               data = PM_MB_19[PM_MB_19$TOS.NUM == 1,]))[1,3],
+                       TOS.NUM == 2 ~ anova(lm(Yeild/1000 ~ 
+                                  factor(`T/ment.NUM`) , 
+                               data = PM_MB_19[PM_MB_19$TOS.NUM == 2,]))[1,3],
+                       TRUE ~ NA_real_))%>%
+   mutate(Inc_Ms = 
+             case_when(TOS.NUM == 1 ~ anova(lm(AUDPC ~ 
+                                  factor(`T/ment.NUM`) , 
+                               data = PM_MB_19[PM_MB_19$TOS.NUM == 1,]))[1,3],
+                       TOS.NUM == 2 ~ anova(lm(AUDPC ~ 
+                                  factor(`T/ment.NUM`) , 
+                               data = PM_MB_19[PM_MB_19$TOS.NUM == 2,]))[1,3],
+                       TRUE ~ NA_real_))
+
+```
+
+#### Input trial data
+```{r Herm_19_Trialdat}
+
+Herm_19_dat <- 
+   data.frame(trial_ref = Herm_19_dat$trial_ref,
+              year = "2019",
+              location = "Hermitage",
+              host_genotype = "Jade",
+              trial_design = "RCB",
+              plot_length = Herm_19_dat$Plot.Lengths,
+              plot_width = 2,
+              plant_density = NA_character_,
+              row_spacing = 0.25,
+              replicate = Herm_19_dat$Rep.Num,
+              planting_date = Herm_19_dat$planting_date,
+              emergence_date = Herm_19_dat$emergence_date,
+              flowering_date = as.Date(NA),
+              pod_fill_date = as.Date(NA),
+              mid_late_pod_fill = as.Date(NA),
+              first_sign_disease = as.Date("2018-04-12", format = "%Y-%m-%d"),
+              trade_name = as.factor(Herm_19_dat$trade_name),
+              fungicide_ai = Herm_19_dat$fungicide_ai,
+              dose_ai.ha = Herm_19_dat$dose_ai.ha,
+              n_treatment = Herm_19_dat$`T/ment.NUM`,
+              fungicide_application_1 = Herm_19_dat$fungicide_application_1,
+              fungicide_application_2 = Herm_19_dat$fungicide_application_2,
+              total_fungicide = Herm_19_dat$spray_n,
+              harvest_date = as.Date("2018-05-22", format = "%Y-%m-%d"),
+              final_assessment = Herm_19_dat$final_assessment,
+              PM_final_severity = Herm_19_dat$PM_final_severity,
+              rating_scale = "1-9",
+              grain_yield.t.ha. = as.numeric(Herm_19_dat$Yeild)/1000,
+              Y_Msquare = Herm_19_dat$Y_Msquare,
+              Inc_Ms = Herm_19_dat$Inc_Ms,
+              AUDPC = Herm_19_dat$AUDPC,
+              AUDPS = Herm_19_dat$AUDPS
+              )
+
+```
+
+```{r Herm19_means}
+
+Herm_19_m <- Herm_19_dat %>%
+   group_by(trial_ref, n_treatment) %>%
+   summarise(year = unique(year),
+             location = unique(location),
+             host_genotype = "Jade",
+             trial_design = unique(trial_design),
+             trade_name = unique(trade_name),
+             dose_ai.ha = unique(dose_ai.ha),
+             plot_length.m. = mean(plot_length, na.rm = TRUE),
+             plot_width.m. = mean(plot_width, na.rm = TRUE),
+             plant_density = "40k",
+             row_spacing = unique(row_spacing),
+             replicates = length(as.numeric(replicate)),
+             planting_date = unique(planting_date),
+             emergence_date = unique(emergence_date),
+             flowering_date = unique(flowering_date),
+             pod_fill_date = unique(pod_fill_date),
+             mid_late_pod_fill = unique(mid_late_pod_fill),
+             first_sign_disease = unique(first_sign_disease),
+             fungicide_application_1 = unique(fungicide_application_1),
+             fungicide_application_2 = unique(fungicide_application_2),
+             total_fungicide = unique(total_fungicide),
+             fungicide_ai = unique(fungicide_ai),
+             harvest_date = unique(harvest_date),
+             final_assessment = unique(final_assessment),
+             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
+             rating_scale = unique(rating_scale),
+             disease_error = sd(PM_final_severity, na.rm = TRUE), # Producing NAs so code is repeated below
+             D_error_type = "stdev",
+             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
+             raw_graded = NA,
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
+             Y_error_type = "stdev",
+             AUDPC_m = mean(AUDPC),
+             AUDPC_sd = sd(AUDPC),
+             AUDPS_m = mean(AUDPS),
+             AUDPS_sd = sd(AUDPS),
+             Y_Msquare = unique(Y_Msquare),
+             Inc_Ms = unique(Inc_Ms)
+   )
+
+# For some weird reason standard deviations are comming back NA in the code above
+Herm_19_m[,c("trial_ref","disease_error","yield_error")] <-
+   Herm_19_dat %>%
+   group_by(trial_ref, n_treatment) %>%
+   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
+             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
+   select(c("disease_error","yield_error"))
+
+Herm_19_m <- fold_data(Herm_19_m, PM_MB_means)
+
+# insert new calculations into data
+PM_MB_means <- replace_data(template_data = PM_MB_means, 
+                            new_data = Herm_19_m, 
+                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
+                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
+                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
+
+write.csv(
+   Herm_19_m,
+   here("cache/Hermitage_19_mean.csv"),
+   row.names = FALSE
+)
+
+```
+
+```{r Save_PM_MB_means, echo=TRUE}
+
+write.csv(PM_MB_means, file = here("cache/PM_MB_updated.csv"), row.names = FALSE)
+
+```

### 2020-08-10 paper/paper.Rmd
Update Figure 2 to incorporate leapyears and remove use of T3 in document

@@
 load(file = here("cache/PreliminaryData.Rdata"))
-T3 <-
-  read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
-T3[, 2:5] <- round(T3[, 2:5], 4)
 source(here("R/reportP.R"))
@@
   )) %>%
+  mutate(season_length = case_when(
+    # add a day for leap years
+    leap_year(year(first_sign_disease)) &
+      (is.na(planting_date) | is.na(harvest_date)) ~
+      season_length + 1,
+    TRUE ~ season_length
+  ))%>%
+  mutate(season_length = round(season_length, digits = 0))%>%
   mutate(plant_day = case_when(
@@
   ylab(NULL)
+
+cbind(x1,x2)
 ```
@@
 Second applications, if they are needed, should be applied at least 10 - 14 days after the first application and not within 21 days of harvest [@APVMAcustodia].
-If time permitted a second spray after the first "late" application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(T3$estimates[10], 4)*1000` kg ha^-1^, when compared to the $Late$, single spray treatment `r reportP(T3$pval[10])`.
+If time permitted a second spray after the first "late" application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(contrast_Ssum$coefficients[15], 4)*1000` kg ha^-1^, when compared to the $Late$, single spray treatment `r reportP(contrast_Ssum$pvals[15])` <!--This needs checking and correcting, T3 says late and latePlus were significantly different however the contrasts.Rdata says it is not-->.
 

### 2020-08-10 paper/paper.Rmd
Word smithing some edits and comments to followup

@@
 Disease pressure was tested against the basic model to determine if, when introduced as a moderator variable, it could significantly explain additional heterogeneity between the spray schedule treatments.
-A a Wald-type test was used to test the impact of the disease pressure factor.
 
@@
 
-Additional meta-analysis models tested variables ... for their influence on the SpraySchedule variables ability to mitigate yield loss.
-For the variable disease pressure a Wald-type test was used to test the effect of this variable on the model as a whole.
+A Wald-type test was used to determine if the moderator variable 'disease pressure' significantly influenced spray intervention treatments.
 
@@
 
-```{r Figure1, echo = FALSE, fig.cap = "Yield contrasts"}
+```{r Figure1, echo = FALSE, fig.cap = "Estimated mean effect sizes of fungicide spray schedules and accompanying 95% confidence intervals"}
 YieldContrasts
@@
 Treatments which incorporated multiple fungicide applications, $Recommended_{plus}$ and $Late_{plus}$, produced the highest mean yield protection estimates at `r round(PM_mv$b[4,1] * 1000, 2)` (SE = `r round(PM_mv$se[4] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) and `r round(PM_mv$b[6,1] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha (SE = `r round(PM_mv$se[6] * 1000, 2)`&nbsp;kg&nbsp;/&nbsp;ha) respectively (Table \@ref(tab:Table3)).
-The treatment that showed the most yield saved compared to the control, $Recommended_{plus}$, was also significantly higher than all other single applications, (
+$Recommended_{plus}$ was estimated to best protect yield, and was also significantly higher than all other single applications, (
 $Early_{single}$, `r reportP(contrast_Ssum$pvals[grep("Recommended_plus - Early",contrast_Ssum$contrast)])`, 
@@
 $Late_{single}$, `r reportP(contrast_Ssum$pvals[grep("Late - Recommended_plus",contrast_Ssum$contrast)])`). 
-However, the $Late_{plus}$ only showed significantly greater yield saved when compared to the $Early_{single}$ treatment (`r reportP(contrast_Ssum$pvals[grep("Late_plus - Early",contrast_Ssum$contrast)])`)
-Consideration should be given when comparing $Late_{plus}$ and $Early_{single}$ treatments given they did not occur within the same trial for any of the 15 trials included in the meta-analysis.
+The $Late_{plus}$, however, only showed significantly greater yield saved when compared to the $Early_{single}$ treatment (`r reportP(contrast_Ssum$pvals[grep("Late_plus - Early",contrast_Ssum$contrast)])`).
 Within the single fungicide application treatments $Late_{single}$ provided the highest yield protection and was estimated to save an average of `r round(PM_mv$b[5,1] * 1000, 2)` kg ha^-1^ (SE = `r round(PM_mv$se[5] * 1000, 2)` kg ha^-1^) relative to the no spray control (`r reportP(PM_mv$pval[5])`).
@@
 
-The $Q_M$ omnibus test of moderators, shows the moderators significantly influence the model ($Q_M =$ `r PM_mv$QM` $,df =$ `r PM_mv$m`, `r reportP(PM_mv$QMp)`) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
+The $Q_M$ omnibus test of moderators, shows the moderators significantly influence the model ($Q_M =$ `r PM_mv$QM` $,df =$ `r PM_mv$m`, `r reportP(PM_mv$QMp)`) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 =\beta_5 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
 The analysis shows there is still a significant amount of residual heterogeneity ($Q_E =$ `r PM_mv$QE` $,df=$ `r PM_mv$k - PM_mv$m`, `r reportP(PM_mv$QEp)`) not captured by the spray management moderator indicating other possible moderators, which may influence grain yield.
 
-A log-ratio test based on a chi-squared distribution indicated that retaining the `SpraySchedule` variable as a random interactive term provided a significantly better model (P = 0.0179).
 An inspection of log-likelihood profile plots showed the model for each random interactive term provided a reasonable estimate of $\tau^2$, with no indication the variables were over-fit.
@@
 While the addition of disease pressure as an interactive moderator term to `SpraySchedule`, did explain slightly more residual heterogeneity as shown by a lower $Q_E = 409.91,$.
-The model including disease pressure did not significantly improve the model (P = 0.4859) and did not significantly explain differences in the `SpraySchedule` term, and therefore disease pressure was not included in the final model.
+The Wald-test of moderators indicated disease pressure did not significantly improve the model (P = 0.0762) and did not significantly explain differences in the `SpraySchedule` term, and therefore disease pressure was not included in the final model.
 
-```{r Figure2, echo=FALSE, fig.cap="Season length and first appearance of powdery mildew in each respective trial for fifteen mungbean trials conducted in the Grains Research and Developmet (GRDC) Northern Grains Region of eastern Australia to evaluate the most effective time of fungicide application to save yield from powdery mildew infection.
-Trials were conducted from 2001 to 2019 by Queensland Department of Agriculture, Fisheries and Forestry, Northern Grower Alliance and University of Southern Queensland and coalated for meta-analysis."}
+```{r Figure2, echo=FALSE, fig.cap="Season length and first appearance of powdery mildew in each respective trial for fifteen mungbean trials conducted in the Grains Research and Developmet (GRDC) Northern Grains Region of eastern Australia by Queensland Department of Agriculture, Fisheries and Forestry, Northern Grower Alliance and University of Southern Queensland.
+Trials were conducted between 2001 to 2019 to evaluate the most effective fungicide application schedule to protect yield-loss caused by powdery mildew infection."}
 PM_Mdat %>%
@@
   ylab(NULL)
-
-cbind(x1,x2)
 ```
 
-```{r Table3, echo = FALSE}
+```{r Table3, echo = FALSE, fig.cap= "Table 3: Estimated grain yield contrasts between each spray schedule."}
 contrast_Ssum[,2:5] <- round(contrast_Ssum[,2:5], 4)
@@
         booktabs = TRUE,
-        caption = "Table 3: Estimated grain yield contrasts between each spray schedule.",
         col.names = c("Treatment contrasts","Estimated difference","Std Error","Z-Score","P-Value"," "))%>%
@@
 
-The current advice provided to growers for when to commence fungicide applications for control of powdery mildew, is to spray at the first sign of the disease then if necessary a follow-up spray two weeks later [@SueThompson2016; @Sparks2017].
+The current advice provided to growers for when to commence fungicide applications for control of powdery mildew is to spray at the first sign of the disease, then if necessary a follow-up spray two weeks later [@SueThompson2016; @Sparks2017].
 This meta-analysis confirms that advice, by showing that applying the first fungicide application, within three days of first sign will significantly mitigate yield loss from powdery mildew by between `r round(PM_mv$ci.lb[3],5)*1000` to `r round(PM_mv$ci.ub[3],5)*1000` kg ha^-1^ ($Recommended$, `r reportP(PM_mv$pval[3])`).
@@
 Second applications, if they are needed, should be applied at least 10 - 14 days after the first application and not within 21 days of harvest [@APVMAcustodia].
-If time permitted a second spray after the first "late" application, on average the meta-analysis shows this would be optimal, as the $LatePlus$ treatment significantly limited yield loss by `r round(contrast_Ssum$coefficients[15], 4)*1000` kg ha^-1^, when compared to the $Late$, single spray treatment `r reportP(contrast_Ssum$pvals[15])` <!--This needs checking and correcting, T3 says late and latePlus were significantly different however the contrasts.Rdata says it is not-->.
+If time permitted a second spray after the first "late" application, on average the meta-analysis shows this might be optimal, as the $LatePlus$ treatment limited yield loss by `r round(contrast_Ssum$coefficients[15], 4)*1000` kg ha^-1^, when compared to the $Late$, single spray treatment `r reportP(contrast_Ssum$pvals[15])`.
 
-It is important to note, the studies included in this meta-analysis may not reflect a "normal" mungbean season. 
+It is important to note, the studies included in this meta-analysis may not reflect a "normal" commercial mungbean season. 
 All the included experiments were intentionally sown late in the season, from January through to as late as early March, to ensure powdery mildew infection (Figure \@ref(fig:Figure2)). 
@@
 If the planting guide is adhered to the mungbean would be at a lower risk of powdery mildew, reducing the requirement for fungicide applications. 
-An example of this is if we inspect the six trials in which powdery mildew manifested 60 days or greater after planting (Trial references: AM1304, mung1819/01, mung1011/01, AM1303, AM1305 and BB1305).
-Of these trials, four directly compared single $Recommended$ fungicide applications and $Recommended_{plus}$ (AM1303, AM1305, BB1305 and mung1819/01), two of which (AM1305 and mung1819/01) produced at least one treatment $Recommended_{plus}$ treatment with a higher grain yield the $Recommended$ treatments.
-However, neither AM1305 or mung1819/01 neither contained $Recommended$ or $Recommended_{plus}$ treatments with higher mean yields than the no-spray control.
+An example of this is if we inspect the six trials in which powdery mildew manifested late in the season, 60 days or greater after planting (Trial references: AM1304, mung1819/01, mung1011/01, AM1303, AM1305 and BB1305).
+Of these trials, four directly compared single $Recommended$ fungicide applications and $Recommended_{plus}$ (AM1303, AM1305, BB1305 and mung1819/01), two of which (AM1305 and mung1819/01) produced only one $Recommended_{plus}$ treatment with a higher grain yield than the $Recommended$ treatments.
+<!--need to check this and rewrite to add clarity (Paul)-->
+However, neither mung1819/01 or AM1305 contained $Recommended$ or $Recommended_{plus}$ treatments with higher mean yields than the no-spray control.
 This indicating there is likely no benefit to applying two fungicide applications when the disease manifests later than 60 days into the growing season. 
-Furthermore, the 2013 trials, Premer (AM1303), Goolhi (AM1305) Marys Mount (AM1304) and Millmerran (BB1305), reported a significant difference in powdery mildew severity between the fungicide treatments.
-However, none of the trials showed a significant difference in grain yield between treatments [@Millmerran2013, @premer2013, @Marysmount2013, @goolhi2013]. 
-Therefore, discretion is still required for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.
+Furthermore, while the 2013 trials, Premer (AM1303), Goolhi (AM1305) Marys Mount (AM1304) and Millmerran (BB1305), reported a significant difference in powdery mildew severity between the fungicide treatments.
+None of the trials showed a significant difference in grain yield between treatments [@Millmerran2013, @premer2013, @Marysmount2013, @goolhi2013]. 
+Therefore, discretion is still required for if fungicide applications are necessary, and consideration given to the crop growth stage and forecast weather conditions at the first sign of powdery mildew.
 
@@
 Data from the trials included in this experiment show regardless of crop sowing date, powdery mildew establishes on average in the month of March (Figure \@ref(fig:Figure2)), which marks the beginning of autumn in Australia.
-Considering the results of the meta-analysis, weekly inspections would be ideal to ensure timely fungicide applications if necessary.
+Considering the results of the meta-analysis, weekly inspections commencing in March would be ideal to ensure timely fungicide applications if necessary.
 Scouting at intervals greater than 12 -- 13 days, might risk crop losses if a spray schedule does not commence within aforementioned the spray window.
@@
 *P.
-xanthii* has evolved resistance to benzimidazole within three years of its registration [@Peterson1973] and has evolved resistance to numerous fungicide classes, such as benzimidazoles, demethylation inhibitors, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines since [@Mcgrath2001] in cucurbits.
+xanthii* has evolved resistance to benzimidazole within three years of its registration [@Peterson1973] and has evolved resistance to numerous fungicide classes, such as benzimidazoles, demethylation inhibitors, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines since ???
+<!--missing year; since ...
+-->  [@Mcgrath2001] in cucurbits.
 In cereal crops, *Blumeria graminis* showed reduced sensitivity to strobilurins in 1998, two years after the fungicides began being used in Europe [@Chin2001].
@@
 The population genetics, epidemiology and alternate hosts are all poorly understood in this host-pathogen relationship.
-The recent discovery of a second powdery mildew species, which infects mungbean highlights the paucity of knowledge on this disease.
+The recent discovery, in 2019, of a second powdery mildew species, which infects mungbean highlights the paucity of knowledge on this disease.
 

### 2020-08-10 paper/paper_WordVersion.Rmd
Create word version for Emerson to edit

--- 2020-08-10 paper/paper.Rmd
@@
 ---
-title: A Meta-analysis of Fungicide Spray Schedules to Minimise Yield Loss from Powdery Mildew in Australian Mungbean
+title: "A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean"
 author:
-  - name: Paul Melloy
-    affil: 1,*
-    orcid: 0000-0003-4253-7167
-  - name: Emerson Del Ponte
-    affil: 2
-    orcid: 0000-0003-4398-409X
-  - name: Adam H. Sparks
-    affil: 1
-    orcid: 0000-0002-0061-8359
-affiliation:
-  - num: 1
-    address: |
-      University of Southern Queensland
-      Centre for Crop Health
-      Toowoomba, Queensland, 4350 Australia
-  - num: 2
-    address: |
-      Universidade Federal de Viçosa
-      Departamento de Fitopatologia
-      Viçosa, 36570-000 Minas Gearais, Brazil
-correspondence: |
-  Paul.Melloy@usq.edu.au; Tel.: +61 7 4631 5527
-journal: agronomy
-type: article
-status: submit
-bibliography: ../Mungbean.bib
-simplesummary: |
-  A simple summary goes here.
+  - Paul Melloy:
+      email: Paul.Melloy@usq.edu.au
+      institute: USQ
+      correspondence: true
+  - Emerson Del Ponte:
+      institute: UFV
+  - Adam H. Sparks:
+      institute: USQ
+institute:
+  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland, Australia
+  - UFV: Universidade Federal de Viçosa, Departamento de Fitopatologia, 36570-000 MG, Brazil
+date: "Last Edit: `r format(Sys.time(), '%d %B, %Y')`"
+output:
+   word_document:
+      reference_docx: "Manuscript2Word_Template.docx"
+      md_extensions: +styles
+bibliography: "../Mungbean.bib"
+csl: "multidisciplinary-digital-publishing-institute.csl"
+link-citations: yes
 abstract: |
-  A single paragraph of about 200 words maximum. For research articles, 
-  abstracts should give a pertinent overview of the work. We strongly encourage
-  authors to use the following style of structured abstracts, but without 
-  headings: 1) Background: Place the question addressed in a broad context and
-  highlight the purpose of the study; 2) Methods: Describe briefly the main
-  methods or treatments applied; 3) Results: Summarize the article's main 
-  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
-  The abstract should be an objective representation of the article, it must not 
-  contain results which are not presented and substantiated in the main text and 
-  should not exaggerate the main conclusions.
-keywords: |
-  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
-  to the article, yet reasonably common within the subject discipline.).
-acknowledgement: |
-  All sources of funding of the study should be disclosed. Please clearly 
-  indicate grants that you have received in support of your research work. 
-  Clearly state if you received funds for covering the costs to publish in open 
-  access.
-authorcontributions: |
-  For research articles with several authors, a short paragraph specifying their 
-  individual contributions must be provided. The following statements should be 
-  used "X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
-  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
-  reagents/materials/analysis tools; Y.Y. wrote the paper." Authorship must be
-  limited to those who have contributed substantially to the work reported.
-funding: |
-   Please add: "This research received no external funding" or "This research
-   was funded by NAME OF FUNDER grant number XXX." and "The APC was funded by
-   XXX". Check carefully that the details given are accurate and use the
-   standard spelling of funding agency names at
-   <https://search.crossref.org/funding>, any errors may affect your future
-   funding.
-conflictsofinterest: |
-  Declare conflicts of interest or state 'The authors declare no conflict of 
-  interest.' Authors must identify and declare any personal circumstances or
-  interest that may be perceived as inappropriately influencing the
-  representation or interpretation of reported research results. Any role of the
-  funding sponsors in the design of the study; in the collection, analyses or 
-  interpretation of data in the writing of the manuscript, or in the decision to 
-  publish the results must be declared in this section. If there is no role, 
-  please state 'The founding sponsors had no role in the design of the study; 
-  in the collection, analyses, or interpretation of data; in the writing of the 
-  manuscript, an in the decision to publish the results'.
-abbreviations:
-  - short: AUDPC
-    long: Area under the disease progress curve
-  - short: DAF
-    long: Queensland Department of Agriculture, Fisheries and Forestry
-  - short: DMI
-    long: Demethylase inhibitor
-  - short: DSS
-    long: Decision support system
-  - short: FRAC
-    long: Fungicide Resistance Action Committee
-  - short: GRDC
-    long: Grains Research and Development Corporation
-  - short: NGA
-    long: Northern Grower Alliance
-  - short: USQ
-    long: University of Southern Queensland
+         **Abstract:** Insert abstract here.
+---
 
-output:
-  bookdown::pdf_book:
-    base_format: rticles::mdpi_article
----
-<!-- the `rticles` package from <https://github.com/adamhsparks/rticles> is required to compile this PDF.
-The version from CRAN is out of date for MDPI -->
-<!-- For reference in writing for MDPI, <https://www.mdpi.com/authors/layout> -->
+::: {custom-style="Art_type"}
+Type of Paper: Article
+:::
+
+::: {custom-style="keywords"}
+**Keywords:** meta-analysis, powdery mildew, mungbean, fungicide `r print("                                                       ")` 
+:::
 
@@
   install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, here, english, pander, lubridate)
+pacman::p_load(tidyverse, here, english, pander, flextable, lubridate)
 
@@
   ) %>%
-  kable(
-    format = "latex",
-    booktabs = TRUE,
-    escape = FALSE,
-    caption = "Description of fungicide application trials included in meta-analysis to determine the most effective fungicide spray schedule to minimise yield loss from powdery mildew in Australian mungbean.
-Trials were all conducted in the Grains Research and Development (GRDC) Northern Grains Region of eastern Australia to test application timing for the best control of powdery mildew of mungbean."
-  ) %>%
-  kable_styling() %>%
-  kableExtra::footnote(
-    alphabet = c(
-      "Queensland Department of Agriculture, Fisheries and Forestry",
-      "Northern Grower Alliance",
-      "University of Southern Queensland"
-    )
-  )
+   flextable()%>%
+   set_caption("Table 1: Description of Experiments") %>%
+   set_header_labels(trial_ref = "Unique Trial Reference",
+                     year = "Year",
+                     location = "Trial Location",
+                     planting_date = "Planting Date",
+                     first_sign_disease = "First sign of disease date",
+                     Research_org = "Research organisation")%>%
+   autofit(add_w = 0.5)%>%
+   align(j = c(1,4,5), align = "center", part = "all")%>%
+   fontsize(size = 9)%>%
+   width(j = 1:4, 1)%>%
+   width(j = 5, 1.1)%>%
+   width(j = 6, 1.7)
 ```
@@
 ) %>%
-  kable(format = "latex",
-        booktabs = TRUE,
-        caption = "1 to 9 scale for rating powdery mildew severity.",
-        col.names = c("Scale",
-                      "Scale Description")) %>%
-  kable_styling()
+   flextable()%>%
+   set_caption("Table 2: Powdery Mildew severity scoring scale") %>%
+   set_header_labels(Scale.Description = "Scale Description")%>%
+   autofit()%>%
+   fontsize(size = 9)%>%
+   align(j = c(1), align = "center", part = "all")%>%
+   width(j = 2, 6.2)
 ```
@@
   mutate(pvals = gsub("P = ","",pvals)) %>%
-  kable(format = "latex",
-        booktabs = TRUE,
-        col.names = c("Treatment contrasts","Estimated difference","Std Error","Z-Score","P-Value"," "))%>%
-  kable_styling()%>%
-  kableExtra::footnote(general = c("*** - signficant at 0.001 level",
-                                   "** - signficant at 0.005 level",
-                       "* - signficant at 0.05 level"))
+  flextable()%>%
+   set_caption("Table 3: Estimated grain yield contrasts between each spray scheduale") %>%
+   align(j = c(2,3,4), align = "center", part = "all") 
 ```

### 2020-08-11 paper/Word_Version/paper_WordVersion.Rmd
Move word document to it's own folder edit the template for formatting, change tables back to flextable for knitting to word. Rename knitted document for sharing, editting and reviewing. Initialise MDPI document template

--- 2020-08-10 paper/paper_WordVersion.Rmd
@@
       md_extensions: +styles
-bibliography: "../Mungbean.bib"
+bibliography: "../../Mungbean.bib"
 csl: "multidisciplinary-digital-publishing-institute.csl"
@@
 ::: {custom-style="keywords"}
-**Keywords:** meta-analysis, powdery mildew, mungbean, fungicide `r print("                                                       ")` 
+**Keywords:** meta-analysis, powdery mildew, mungbean, fungicide `r print("                                                       .")` 
 :::
@@
    set_caption("Table 3: Estimated grain yield contrasts between each spray scheduale") %>%
-   align(j = c(2,3,4), align = "center", part = "all") 
+   autofit(add_w = 0.2)%>%
+   align(j = c(2:5), align = "center", part = "all") %>%
+   set_header_labels(contrast = "Treatment contrasts",
+                     coefficients = "Estimate",
+                     StdErr = "Std Error",
+                     Zvalue = "Z-Score",
+                     pvals = "P-Value",
+                     sig = " ")%>%
+   fontsize(size = 9)%>%
+   width(j = 5,0.8)%>%
+   width(j = 6, .3)
 ```

### 2020-08-11 04_Prep_data.Rmd
clarify inspection of crop maturity when powdery mildew first manifested and yield loss statements. Change color scheme of plots

@@
 The time at which powdery mildew infects in the seasons and the age of the plant might affect the AUDPC and the loss in yield.
-Let's have a look at the age of each trial when each powdery mildew infected it.
-We will use the difference between `planting_date` and `first_sign_disease` as a proxy for crop maturity.
+Let's have a look at the age of each trial when powdery mildew infected it.
+We will use the difference between `planting_date` and `first_sign_disease` as a proxy for crop maturity when it became infected.
 
@@
 From these trials I am most interested in the experiments that directly compare `Recommended` with `Recommended_P_plus` and/or `Late` with `Late_plus`. 
-Therefore I will not inspect, `AM1304` (Marys Mount).
+Therefore I will not inspect, `AM1304` (Marys Mount), which only trialled an early, prophylactic spray.
 
@@
 Let's look at this in a quick box plot. 
-We will only look at trials where powdery mildew set in at flowering which is approximately 60 days after planting.
+We will only look at trials where powdery mildew set in 60 days after planting, when the physiological maturity was likely flowering.
 
@@
    group_by(trial_ref, spray_management) %>%
-   ggplot(aes(x = spray_management, y = yield_gain, fill = trial_ref)) +
+   ggplot(aes(x = spray_management, y = yield_gain, colour = trial_ref)) +
    geom_boxplot() +
@@
 
-We can see in these experiments five experiments there is clearly no benefit to applying a second fungicide application.
+We can see in these experiments five experiments there is clearly no benefit to applying a second fungicide application given the values of the recommended _plus treatment were predominantly lower than zero.
 

### 2020-08-11 03_Preliminary_analysis.Rmd
Small changes to clean-up compendium. Larger changes to come

@@
 ```{r PA_Libraries, include=FALSE, message=FALSE}
-library(tidyverse)
-library(lubridate)
-library(bomrang)
-library(openxlsx)
-library(kableExtra)
-library(ggplot2)
-library(devtools)
-library(reshape2)
-library(lme4)
+if (!require("pacman"))
+   install.packages("pacman")
+pacman::p_load(tidyverse,
+               lubridate,
+               bomrang,
+               openxlsx,
+               devtools,
+               reshape2,
+               lme4,
+               kableExtra,
+               here)
+source(here("R/import_data.R"))
+if (!require("theme.usq"))
+   devtools::install_github("adamhsparks/theme.usq")
 library(theme.usq)
-source("R/import_data.R")
-#source("./getPPD2.R")
-theme_set(theme_usq())
+theme_set(theme_usq()
+)
 ```
@@
 ## Explore and Visualise Data
+First let's import the data.
+Each row provides the mean yield for each experimental treatment.
 
-```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
-# Import data
-PM_MB_means <- import_data() # link expires 2021-12-01
-
-#remove the variation in different sulphur formulations
-unique(PM_MB_means[
-   grep("sulphur",PM_MB_means$fungicide_ai),
-   "fungicide_ai"])
-PM_MB_means[grep("sulphur",PM_MB_means$fungicide_ai),"fungicide_ai"] <- "sulphur"
-
+```{r echo=TRUE, message=FALSE, warning=FALSE}
+PM_MB_means <- import_data() 
 ```
 
-Various factors have been studied in the previous experiments which may influence the following results.
-However unless stated the following plots and analyses were made disregarding effects from other factors not mentioned.
+The data explored in the `PM_MB_means` data frame is a list of mean values from each treatment in each respective experiment.
+These preliminary analyses will focus on the change in mungbean yields, which is attributable to the fungicide treatment. 
+Later in this document we will also consider the impact of fungicide treatments on disease incidence/severity.
+Mean powdery mildew incidence was recorded at the end of each growing season.
+Some experiments recorded disease incidence throughout the season and these were summarised with AUDPC.
+AUDPC for trials which only provided final powdery mildew incidence was calculated using the record of 'first sign of disease' and final assessment.
+More details on how the `PM_MB_means` data was compiled can be found in the ['Data wrangle vingette'](./vignette/191115_PMMB_DataWrangling_PM.html)
 
-   1) Fungicide type
+Various factors have been studied in the previous experiments which may influence the subsequent meta-analysis.
+On this page, unless stated, the following plots and analyses were made disregarding other effects.
+The following factors are postulated to influence mungbean grain yield and/or powdery mildew mean plot severity.
 
-   2) Fungicide dose (varies only slightly within some fungicide types)
+   1 Fungicide type
 
-   3) Number of fungicide sprays
+   2 Fungicide dose (varies only slightly within some fungicide types)
 
-   4) Timing of fungicide spray/s relative to first sign of disease (_i.e_. when pathogen is present)
+   3 Number of fungicide sprays
 
-   5) Host cultivars (probably is a co-variate with season due to changing cultivars over time)
+   4 Timing of fungicide spray/s relative to first sign of disease
 
-   6) Experiment location
+   5 Host cultivar (probably is a co-variate with season due to changing cultivars over time)
 
-   7) Row spacing
+   6 Experiment location
 
-   8) In-crop rainfall
+   7 Row spacing
 
-   9) Irrigated vs non-irrigated trials
+   8 In-crop rainfall
 
-   10) Mean daily temperature in the weeks following spray application
+   9 Irrigated versus non-irrigated trials
 
-   11) Final disease rating
+   10 Mean daily temperature in the weeks following spray application
 
-   12) Two pathogen species cause PM (new discovery in 2018)
+   11 Final disease rating
 
-The data plotted below are from `r length(unique(PM_MB_means$trial_ref))` field trials between (`r first(levels(PM_MB_means$year))` - `r last(levels(PM_MB_means$year))`) of which the details are described in [Studies considered in meta-analysis section](#studies-considered-in-meta-analysis).
-All data explored below are a list of mean values from each treatment applied in each experiment.
-Some experiments have in-season observations of disease incidence and severity, however here we have summarised the data to show only the end of season observations.
+   12 Two pathogen species cause PM (new discovery in 2018)
+
+The data plotted below are from `r length(unique(PM_MB_means$trial_ref))` field trials between (`r first(levels(PM_MB_means$year))` - `r last(levels(PM_MB_means$year))`) of which the details are described in the [studies considered in meta-analysis section](#studies-considered-in-meta-analysis).
 
 ### Fungicides
+
 #### Fungicide type
+
+First let's standardise the sulphur treatments.
+Some early experiments tested different formulations.
+There was no difference in the sulphur formulations so we will refer to all of them as "sulphur".
+
+```{r sulphur_simplify}
+# Remove the variation in different sulphur formulations
+unique(PM_MB_means[grep("sulphur", PM_MB_means$fungicide_ai),
+                   "fungicide_ai"])
+PM_MB_means[grep("sulphur", PM_MB_means$fungicide_ai), "fungicide_ai"] <-
+   "sulphur"
+```
+
 Let's explore how many different types of fungicide were used and at what frequency.
@@
 
-   - Tebuconazole and propiconazole could be pooled as a triazole or demethylation inhibitors (DMI) fungicide treatment.
+The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in the highest frequencies, along with sulphur.
+The DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.
 
-   - Amistar Xtra and Custodia are both contain strobilurin and triazole, however, because they contain differing dose ratios (inverted) pooling may not be appropriate.
+Amistar Xtra and Custodia both contain strobilurin and triazole, however, because they contain differing dose ratios (inverted) pooling may not be appropriate.
 
-   - Perhaps best way forward is to do an analysis of only the triazoles/DMIs.
-   Then do another including azoxystrobin as a comparison.
+Perhaps best way forward is to focus the meta-analysis on only the DMIs.
+This can then be compared to an additional meta-analysis including azoxystrobin as a comparison.
 
@@
 
-The primary focus of this research is the effect of fungicide on mitigating yield loss to disease.
-To reduce the effect of location and seasonal influences we will investigate the proportion of grain yield saved relative to the no spray control.
+Before we exclude non-DMI fungicides let's have a look at the efficacy of the other fungicides in comparison to the DMIs.
+For this comparison we will focus on the proportional yield saved, relative to the no spray control.
+The primary focus of this research is the effect of fungicide on mitigating yield loss due to disease.
+We are using proportional yield, relative to the no spray control, to reduce the effect of location and seasonal influences.
 
-First, let's investigate the difference in the effect of the type of fungicide on proportion of yield saved. Proportion of yield saved is used in attempt to reduce variation between trials.
+Let's investigate the difference in the effect of the type of fungicide on proportion of yield saved, but first we need to calculate yield saved relative to the no spray control.
+
+```{r Calculate_yield-savings}
+PM_MB_means$grain_yield.t.ha. <-
+   as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data
+
+for (i in unique(PM_MB_means$trial_ref)) {
+   # Loop code over each trial reference
+   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
+
+   if (any(is.na(unique(dat1$row_spacing)))) {
+      # If there is no recorded row.spacing don't calculate proportional yield, skip to the next trial
+      warning(
+         unique(dat1$trial_ref),
+         "at",
+         unique(dat1$location),
+         "in year",
+         unique(dat1$year),
+         "has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n"
+      )
+      next()
+   }
+
+   for (j in unique(dat1$row_spacing)) {
+      # Loop within trial row_spacing
+      dat2 <- dat1[dat1$row_spacing == j, ]
+      controlY <-
+         mean(dat2[dat2$fungicide_ai == "control", "grain_yield.t.ha."]) #Mean taken as some trials had multiple control reps
+
+      # Calculate the yield gain relative to the no spray control (controlY)
+      dat2$yield_gain <- dat2$grain_yield.t.ha. - controlY
+      dat2$prop_YG <- dat2$yield_gain  /  controlY
+
+      # insert NA as yeild_gain and proportional yield gain for the controls
+      dat2[dat2$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
+         NA
+
+      # Reassign values to row_spacing subset
+      dat1[dat1$row_spacing == j, ] <- dat2
+   }
+   # Reassign values to trial_ref subset
+   PM_MB_means[PM_MB_means$trial_ref == i, ] <- dat1
+}
+
+# ____________________________________________
+# calculate yield gain and prop_yield gain for experiments with no row spacing data
+dat1 <- PM_MB_means[PM_MB_means$trial_ref == "AM1303", ]
+
+controlY <-
+   mean(dat1[dat1$fungicide_ai == "control", "grain_yield.t.ha."])
+
+dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
+dat1$prop_YG <- dat1$yield_gain / controlY
+dat1[dat1$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
+   c(NA, NA)
+PM_MB_means[PM_MB_means$trial_ref == "AM1303", ] <- dat1
+
+write.csv(PM_MB_means,
+          "cache/1911_PM_MB_means&Ygains.csv")
+```
+
+Now we have calculated proportional yield savings we can inspect the difference between the fungicide active ingredients
 
@@
    arrange(desc(median)) %>%
-   kable(caption = "Fungicide effect on proportion of yield gain.") %>%
+   kable(
+      caption = "Fungicide effect on proportion of yield gain.",
+      col.names = c(
+         "Fungicide active ingredient",
+         "Total fungicide applications",
+         "n Treatments",
+         "2.5% quartile",
+         "Median proportional grain yield",
+         "Mean proportional grain yield",
+         "97.5 % quartile"
+      ),
+      align = "c"
+   ) %>%
    kable_styling(fixed_thead = T, full_width = T) %>%
+   column_spec(c(2, 3), width = "1cm") %>%
    footnote(general = "Fungicides with less than five observations were omitted from this table")
-
 ```
 
-*****
+**  **  *
 
@@
 
-```{r Fungicide_x_nSprays_tble1, message=FALSE}
-
+```{r Fungicide_x_nSprays_tble1, message=FALSE, warning=FALSE}
 PM_MB_means %>%
@@
 
-There is a small yield effect when applying fungicide and it is unclear how much a second spray improves yield saved. Interestingly sulphur sprays might be worth investigating when sprayed twice.
+There is a small yield effect among the strobilurin fungicide mixes and the DMI fungicides. 
+While there is some differences in the variation between tebuconazole and propiconazole, the medians are very similar. 
+I think it is safe to combine these fungicides, with the same mode of action in the meta-analysis.
+The follow-up spray seems to show an increase in yield protection.
+Interestingly sulphur sprays show good protection when sprayed twice.
 
@@
 #### Fungicide Doses  
-We should check that all fungicide doses that were used were roughly the same if we are to compare between trials were dose might be different.
+From this point on we will investigate only the DMI fungicides, tebuconazole and propiconazole, and disregard all other fungicide modes-of-action.
+
+We should check that all fungicide doses that were used were roughly the same, if we are to compare between trials where dose might be different.
 
@@
    scale_fill_usq() +
-   scale_colour_usq() +
-   theme_usq()
+   scale_colour_usq()
 ```
 
-All trials that used tebuconazole used approximately the same dose. Dose of the active ingredient ranged from 62.35&nbsp;g per hectare to 60&nbsp;g per hectare.
+All trials that used tebuconazole used approximately the same dose.
+Dose of the active ingredient ranged from 62.35&nbsp;g per hectare to 60&nbsp;g per hectare.
 
-There is a large amount of variation in the propiconazole dose, let's inspect the difference in yields for each dose.
+Doses for propiconazole range from 62.5 to 125, a large variation.
+Let's inspect the difference in yields for each dose.
 
@@
    xlab("Dose (g ai/ha)") +
-   ggtitle(label = "Yield for each respective propiconazole dose") +
-   geom_boxplot() +
-   scale_fill_usq() +
-   scale_colour_usq() +
-   theme_usq()
+   ggtitle(label = "Yield for each respective propiconazole dose,\nfaceted by number of applications") +
+   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
+   facet_grid(cols = vars(total_fungicide))
 ```
 
-This dose effect should be acknowledged in the meta-analysis. How many treatments of each dose have been investigated per trial?
+This dose effect should be acknowledged in the meta-analysis.
+How many treatments of each dose have been investigated per trial?
 
 ```{r table_PropiDoses}
-table(as.character(PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole", ]$trial_ref),
-      PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole", ]$dose_ai.ha)
+table(as.character(PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole",]$trial_ref),
+      PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole",]$dose_ai.ha)
 ```
 
-Two trials show both doses were applied in the same trial, mung1112/01 and mung1112/02. Let look at the difference in proportion of yield saved in these trials.
+Two trials show both doses were applied in the same trial, mung1112/01 and mung1112/02.
+Let's look at the difference in proportion of yield saved in these trials.
 
-```{r PropiDoses_TrialCompar}
-boxplot_usq(prop_YG ~ dose_ai.ha,
-            data = PM_MB_means[(PM_MB_means$trial_ref == "mung1112/01" |
+```{r PropiDoses_TrialCompare}
+PM_MB_means[(PM_MB_means$trial_ref == "mung1112/01" |
                 PM_MB_means$trial_ref == "mung1112/02") &
-                                  PM_MB_means$fungicide_ai == "propiconazole",])
+                PM_MB_means$fungicide_ai == "propiconazole",] %>%
+   mutate(dose_ai.ha = as.factor(dose_ai.ha)) %>%
+               ggplot(aes(y = prop_YG, x = dose_ai.ha))+
+   geom_boxplot()+
+   facet_grid(cols = vars(total_fungicide)) +
+   xlab("Dose (g ai/ha)") +
+   ggtitle(label = "Yield for each respective propiconazole dose, faceted by number of applications") +
+   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5)
 ```
 
-This plot plot, however, indicated the previous plot might be skewed by high yielding trials.
+This plot is similar to the previous plot, indicating dose needs to be considered in the analysis. Especially as there is a interaction between dose and number of sprays.
 
@@
 
+This table shows that the majority of treatments inspected one and two spray management practices.
+
 *****
@@
 #### Timing of fungicide sprays  
-When are fungicides sprayed in relation to first sign.
+The timing of fungicide application can be crucial for maximum disease control and yield loss mitigation. 
+The experiments all relied on natural infection and thus infection at a standardised crop maturity stage was not possible. 
+To best estimate the effect of fungicide application timing we will use the day when the disease was first found in the field as a reference.
+The first sign of disease is a useful reference as it can be assessed with little training for the assessor.
+
+First let's make a plot to visualise when one or more spray management regimes were made in relation to the first sign of disease regardless of fungicide active. 
+The plot is faceted by number of spray applications.
 
@@
    geom_violin() +
-   scale_x_discrete(
-      labels = c(
-         "First\nspray",
-         "Second\nspray",
-         "Third\nspray",
-         "Fourth\nspray",
-         "Fifth\nspray"
-      )
-   ) +
-   theme_usq()
+   scale_x_discrete(labels = c(
+      "First spray",
+      "Second spray",
+      "Third spray",
+      "Fourth spray",
+      "Fifth spray"
+   )) +
+   ylab("Days to First Sign of Disease") +
+   facet_grid(cols = vars(total_fungicide)) +
+   coord_flip()
 ```
+
+The plot shows single fungicide applications are mostly made at zero, first sign of disease in the crop.
+Experiments that tested two spray treatments also tend to make the first application at first sign of disease, and the second spray between 10 and 25 days later.
+Three spray treatments seemed to be mostly used in experiments where preventative sprays as the first fungicide application were made.
 
@@
 ### Mungbean cultivars
-In general, the mungbean varieties have the following resistance to powdery mildew.
+
+Australian mungbean varieties have the following resistance to powdery mildew.
 
@@
    geom_col() +
-   scale_fill_usq() +
-   scale_colour_usq() +
-   theme_usq()
+   scale_fill_usq(name = "Fungicide AI")
 ```
-
-&nbsp;
 
@@
 Below we plot distributions of mean trial yields for each cultivar.
+The following plots use data that includes all fungicide types.
 
-First lets look at overall yields for each cultivar, where trial is not a factor, for all treatments (spray and no spray).  
+First let's look at overall yields for each cultivar, where trial is not a factor, for all treatments (spray and no spray).
+
 ```{r yield_vol}
-# this could be converted into a shiny app as a chunk. Make each input for the function a shiny option
 # Outputs the table and graph
-source("R/yield_volatility.r") #function to investigate the volatility in yields
-# Volitility is the range between the upper and lower 97.5 and 2.5 % quartiles
-
+source("R/yield_volatility.r") # function to investigate the volatility in yields
+# Volatility is the range between the upper and lower 97.5 and 2.5 % quartiles
 YV1 <-
    yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
-YV1[[2]]
+YV1[[2]] + 
+   scale_fill_usq()
 YV1[[3]]
 ```
-Now lets look at overall yields for each cultivar, where trial is not a factor, in only the no spray treatments.
+
+This plot shows a large amount of yield volatility in all cultivars except Green Diamond.
+Green Diamond shows little volatility probably because this cultivar was only used in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trial.
+
+Now let's look at overall yields for each cultivar, where trial is not a factor, in only the no spray control treatments.
+
 ```{r yieldVol_control}
-
 YV2 <-
    yield_volatility(genotype_by_trial = FALSE, control_only = TRUE)
-YV2[[2]]
+YV2[[2]] +
+   scale_fill_usq()
 YV2[[3]]
@@
 
-Volatility of the cultivars are fairly similar when trial is not considered as a factor (when we inspect plots of all treatments and only spray treatments).
-Green Diamond shows little volatility however this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trials.
+Volatility of the cultivars are less, albeit fairly similar, in control plots when trial is not considered as a factor.
 
@@
 
-Lets examine the same plots as above but only for the most commonly used trial site, Hermitage.  
+Let's examine the same plots as above but only for the most commonly used trial site, Hermitage.
+
 ```{r yieldVol_Herm}
@@
    )
-YV1_herm[[2]]
+YV1_herm[[2]] +
+   scale_fill_usq()
+
+YV1_herm[[3]]
 ```
@@
 
-Lets take a closer look at Crystal with spray management treatments and without.  
+*****
+
+Let's take a closer look at Crystal with spray management treatments and without.
+
 ```{r YieldVol_Crystal}
@@
    yield_volatility(genotype = "Crystal", control_only = FALSE)
-YV1_crystal[[2]]
-YV1_crystal <-
+YV1_crystal[[2]] +
+   scale_fill_usq()
+
+YV1_crystal[[3]]
+
+YV2_crystal <-
    yield_volatility(genotype = "Crystal", control_only = TRUE)
-YV1_crystal[[2]]
+YV2_crystal[[2]] +
+   scale_fill_usq()
+
+YV2_crystal[[3]]
 ```
 
-There is a lot of variation between field trials for Crystal, but little variation within field trials.
+There is a lot of variation between field trials for Crystal, but little variation within field trials. This indicates that trial should be fit as a random effect when we fit a model to this data.
 
-Lets look at Jade, to see if it differs.
+Let's look at Jade, to see if it differs.
+
 ```{r YieldVol_Jade}
-YV2_crystal <- yield_volatility("Jade",control_only = FALSE)
-YV2_crystal[[2]]
+YV1_jade <- yield_volatility("Jade",control_only = FALSE)
+YV1_jade[[2]] +
+   scale_fill_usq()
+
+YV1_jade[[3]]
 ```
 
-For Jade there is high variation between trials and with in. Perhaps indicating lower tolerance. Lets look at the same plot with data only from no spray controls to see if the variation is the same.
+For Jade there is high variation between trials and with-in.
+Perhaps indicating lower tolerance. 
+Let's look at the same plot with data only from no spray controls to see if the variation is the same.
 
 ```{r YieldVol_JadeControl}
-YV3_crystal <- yield_volatility("Jade", control_only = TRUE)
-YV3_crystal[[2]]
+YV2_jade <- yield_volatility("Jade", control_only = TRUE)
+YV2_jade[[2]] +
+   scale_fill_usq()
+
+YV2_jade[[3]]
 ```
 
-There seems to be a noticeable shift in the probability curves between the two plots.
-Indicating that the tolerance in Jade may not as good as Crystal.
-A comparison between the fungicide efficacy for reducing powdery mildew severity and fungicide efficacy at mitigating yield loss.
+There still remains a higher volatility in Jade and perhaps a greater shift in the probability curve including fungicide treatments versus probability curves including only no spray controls.
+Indicating that there might be a difference in powdery mildew tolerance between Jade and Crystal.
 
-Overall there seems to be an influence of cultivar however this variation is not as distinct as the variation between trials.
+Overall there seems to be an influence of cultivar.
+However this variation is not as distinct as the variation between trials.
 
@@
 
-Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease.
+Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease as well as fungicide timing and efficacy.
 The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows in most cases increased yield significantly.
-This finding has also been shown by Kerry McKenzie's work as well.
+This finding has also been shown by several other researchers' work in Queensland and New South Wales as well.
 Eight trials used a row spacing of 0.75&nbsp;meters and tebuconazole as an active ingredient (AI).
@@
             position = "dodge") +
-   scale_fill_usq(name = "Fungicide AI") +
-   theme_usq()
-
-PM_MB_means %>%
-   filter(fungicide_ai == "tebuconazole",
-          row_spacing == 0.75) %>%
-   glimpse()
+   scale_fill_usq(name = "Fungicide AI")
 ```
 
-Lets plot the row spacing treatments for the response variables yield and disease severity. The main questions are:  
-   - Were there any statistical differences for mungbean yield or powdery mildew severity between row spacing treatments?  
-   - Can we pool certain row spacing that have no significant difference?
+Let's plot the row spacing treatments for the response variables yield and disease severity.
+The main questions are:
+
+   * Were there any statistical differences for mungbean yield or powdery mildew severity between row spacing treatments?
+
+   * If not, can we pool certain row spacing that have no significant difference?
 
@@
    ggplot(aes(y = PM_final_severity, x = factor(row_spacing))) +
-   geom_boxplot() +
+   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
+   ylab("Final severity rating") +
+   xlab("Row spacing (m)") +
    ggtitle("Powdery mildew variation between different row spacing")
@@
              year == 2018) %>%
-   #   filter(Fungicide == "control") %>%
    ggplot(aes(
       y = as.numeric(grain_yield.t.ha.),
-      x = row_spacing,
+      x = as.factor(row_spacing),
       colour = location
    )) +
-   geom_smooth(method = "gam") +
-   geom_jitter(width = 0.01) +
+   geom_jitter(width = 0.1) +
    ggtitle("Grain yield results for different row spacing at three locations") +
    xlab("Row spacing (m)") +
-   ylab("Grain yield - tonnes per hectare")
+   ylab("Grain yield (t/ha)") +
+   scale_colour_usq()
 ```
@@
 
+This tests when rainfall during the cropping season could be best associated with yield
+
 ```{r rainfall_sum_Sstart}
-# The four data files were created from four scripts run as four jobs in Rstudio
+# The four data files were created from four scripts run as four jobs in RStudio
 # when the four jobs are finished they can be imported and combined into one data.frame
@@
    scale_fill_distiller(palette = "RdBu", direction = -1) 
-```
-
-```{r rainLMrsquared}
-ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_rsquared)) +
-   geom_raster(aes(fill = lm_rsquared), interpolate = TRUE) +
-   geom_contour(bins = 15, colour = "white") +
-   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)), ],
-              aes(x = start_day, y = end_day),
-              colour = " red") +
-   scale_fill_distiller(palette = "RdBu") 
 ```
@@
 ### Season range and first incidence
+
 Mungbean is a summer crop and powdery mildew requires cool conditions to establish.
 Therefore the disease can be avoided by planting early in summer or spring, avoiding cooler temperatures at the end of some seasons.
-Can we visualise when PM is most likely to establish over the calender year?
+Can we visualise when PM is most likely to establish over the calendar year?
 
 I'll build a plot of horizontal lines indicating the season length and use a dot on the line to indicating the day of the year first sign was observed for that trial.
+
 ```{r first_incidence}
@@
       First_sign_PM = unique(first_sign_disease),
-      season_length = as.integer(as.Date(unique(harvest_date)) - as.Date(unique(planting_date)))
+      season_length = as.Date(unique(harvest_date)) - as.Date(unique(planting_date)),
+      cropping_season = "Actual"
    )
+
+# For some trials where planting date and Harvest date is missing let's estimate 
+#     the season length by using the mean of all season lengths
+season_dates[is.na(season_dates$season_length),"cropping_season"] <- "Estimated"
+
+season_dates[is.na(season_dates$Planting_date),"Planting_date"] <- 
+   season_dates[is.na(season_dates$Planting_date),"Harvest_date"] - 
+   as.numeric(mean(season_dates$season_length, na.rm = TRUE))
+
+season_dates[is.na(season_dates$Harvest_date),"Harvest_date"] <- 
+   season_dates[is.na(season_dates$Harvest_date),"Planting_date"] + 
+   as.numeric(mean(season_dates$season_length, na.rm = TRUE))
+
+season_dates[is.na(season_dates$season_length),"season_length"] <- 
+   mean(season_dates$season_length, na.rm = TRUE)
 
@@
 season_dates$Disease_day <- yday(season_dates$First_sign_PM)
+
+season_dates[c(1:2,6), "Planting_day"] <- 1
+
 season_dates$Harvest_day <-
@@
 
-season_dates[1, "Planting_day"] <-
-   yday(as.Date("2012-02-28") - 7) # planted in december and emerged in February, Assuming due to lack of rain or recording error. Using 7 days prior to emergence day as planting day
-
-first_day_month <- c(0, 31, 59, 90, 120, 151, 181, 211, 243, 273)
+first_day_month <- c(0, 31, 60, 91, 121, 152, 182, 212, 244, 274) + 1
 axis_labels_date <-
@@
    breaks = first_day_month) +
-   geom_point(aes(x = trial_ref, y = Disease_day)) +
+   geom_point(aes(x = trial_ref, y = Disease_day), size =2.5) +
    coord_flip() +
+   scale_color_manual(values=c("black","grey70"))+
    ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
+
+SeasonPlot
 ```
 
-In most years, regardless of the age of the crop, PM establishes in March.
+In most years, regardless of the age of the crop, powdery mildew establishes in March, which is to be expected.
+The disease is driven by weather conditions and the plant is vulnerable at any growth stage.
 
-*****
+### AUDPC visualise raw data
 
-#### Effect of Fungicide
+First let's check we have all the AUDPC observations.
 
-**Fungicide effect on proportional yield gain with respect to time of application**  
-First lets look at the quantiles for each fungicide irrespective of other factors.
-We will focus on proportional yield gain, compared to no treatment control, as this should partially correct for some spatial and seasonal effects.  
-```{r fungicide_proportion_yield}
+```{r AUDPC_check}
 PM_MB_means %>%
-   group_by(fungicide_ai) %>%
-   summarise(
-      n = length(prop_YG),
-      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
-      median = median(prop_YG, na.rm = T),
-      mean = mean(prop_YG, na.rm = T),
-      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
-   ) %>%
-   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
-   arrange(desc(median)) %>%
-   kable(caption = "Fungicide effect on proportion of yield gain") %>%
-   kable_styling(fixed_thead = T, full_width = T)
-
-# plot table as a box plot
-PM_MB_means %>%
-   filter(
-      fungicide_ai == c(
-         "200 g/L tebuconazole +\n120 g/L azoxystrobin" ,
-         "200 g/L azoxystrobin +\n80 g/L cyproconazole",
-         "tebuconazole",
-         "propiconazole",
-         "sulphur"
-      )
-   ) %>%
-   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
-   geom_boxplot() +
-   geom_hline(aes(yintercept = 0), size = 0.5) +
-   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
-   labs(x = "Proportion of grain yield saved",
-        title = "Grain yield proportion saved grouped by\nfungicide type") +
-   theme(
-      panel.grid.major = element_line(colour = "grey80"),
-      panel.grid.minor = element_line(colour = "grey50"),
-      panel.background = element_rect(fill = NA)
-   ) +
-   guides(fill = guide_legend(title = "Fungicide")) +
-   coord_flip()
+   filter(is.na(AUDPC_m)) %>%
+   distinct(trial_ref, location, year,AUDPC_m, first_sign_disease, final_assessment)%>%
+   kable(align = "c")
 ```
 
-There was some hope groups of fungicide could be combined, _i.e._ propiconazole and tebuconazole, however it seems that they have different efficacies.
-Let us look to see if there is anything skewing the above.
+The trials `r unique(PM_MB_means[is.na(PM_MB_means$AUDPC_m),"trial_ref"]) ` don't have an estimate of AUDPC and need to be filled in. 
+The following script estimates AUDPC from the final disease severity rating and the first sign of disease information.
 
-We need to also define the relationship between yield loss and disease severity. When exploring this data we should look primarily at the no spray control plots
-
-```{r yield_x_PMseverity}
-PM_MB_means %>%
-   filter(fungicide_ai == "control") %>%
-   ggplot(aes(x = PM_final_severity, y = grain_yield.t.ha.)) +
-   geom_point() +
-   geom_smooth(method = "lm")
+```{r SingleObsAUDPC}
+source(here("R/AUDPC_for_single_obs.R"))
+write.csv(PM_MB_means,
+          "cache/1911_PM_MB_means&Ygains.csv", row.names = FALSE)
 ```
 
-From the data that we have, it is difficult to determine if there is an association between powdery mildew severity and grain yield.
+      _How well does 'area under the disease progress curve' (AUDPC) predict grain yield?_
+
+   and
+
+      _Does spray_management scenario mitigate yield loss through reducing AUDPC?_
+
+We would expect to see grain yield decline with increasing AUDPC.
+Let's just plot yield vs AUDPC.
+
+```{r Yield_vs_AUDPC}
+
+plot(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means)
+abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means))
+
+```
+
+There appears to be a weak positive relationship between the two continuous variables.
+Does a linear model confirm this?
+
+```{r AUDPClm}
+summary(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means))
+```
+
+This is not what we would expect and the low R squared value of `r round(summary(lm(grain_yield.t.ha.
+~ AUDPC_m, data = PM_MB_means))$adj.r.squared,3)` perhaps there are additional factors influencing this relationship.
+
+Let's tease out variation due to trial location, season, row spacing, and other seasonal variables are preventing us from seeing the expected relationship.
+Let's do the plot again for each trial where there are no missing values.
+Note: The plots are ordered by mean yield of the trial.
+
+```{r AUDPCxTrial}
+sm2lg <- PM_MB_means %>%
+   group_by(trial_ref) %>%
+   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
+   arrange(TY)
+
+for (i in sm2lg$trial_ref) {
+   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
+   if (any(is.na(dat1$grain_yield.t.ha.))) {
+      next
+   }
+   if (any(is.na(dat1$AUDPC_m))) {
+      next
+   }
+
+   plot(
+      grain_yield.t.ha. ~ AUDPC_m,
+      data = dat1,
+      main = paste(dat1$location[1], (dat1$year[1])),
+      ylim = c(0, max(PM_MB_means$grain_yield.t.ha., na.rm = TRUE)),
+      xlim = c(0, max(PM_MB_means$AUDPC_m, na.rm = TRUE))
+   )
+   abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = dat1))
+   points(grain_yield.t.ha. ~ AUDPC_m,
+          data = dat1[dat1$fungicide_ai == "control",],
+          col = "red")
+
+}
+```
+
+Based on a GRDC report by Sue Thompson [-@SueThompson2016] we want to know what the yield loss was in on cultivar Jade in the 2016 Trials.
+```{r}
+dat3 <- PM_MB_means %>%
+   filter(year == "2016",
+          host_genotype == "Jade",
+          fungicide_ai == "control")%>%
+   group_by(location)%>%
+   summarise(C_Yield = mean(grain_yield.t.ha., na.rm = TRUE))
+
+dat3$F_Yield <- PM_MB_means %>%
+   filter(year == "2016",
+          host_genotype == "Jade",
+          fungicide_ai != "control")%>%
+   group_by(location)%>%
+   summarise(F_Yield = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
+   pull(F_Yield)
+
+dat3 %>% 
+   mutate(diff = F_Yield - C_Yield) %>%
+   mutate(percent = (diff/F_Yield)*100)
+
+```
+
+This sequence of graphs show that AUDPC and disease incidence tends not affect yields if the season is a low yielding season, _i.e._ lower than 1 tonne per hectare.
+The higher the yield, the greater greater the influence on the disease on the yield especially if the crop is high yielding with AUDPC also being large enough to reduce yield.
+
+Let's have a look again at the same sequence of graphs and analyses for area under the disease progress _stairs_.
+
+```{r Yield_vs_AUDPS}
+plot(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means)
+abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means))
+
+summary(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means))
+
+sm2lg <- PM_MB_means %>%
+   group_by(trial_ref) %>%
+   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
+   arrange(TY)
+
+for (i in sm2lg$trial_ref) {
+   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
+   if (any(is.na(dat1$grain_yield.t.ha.))) {
+      next
+   }
+   if (any(is.na(dat1$AUDPS_m))) {
+      next
+   }
+
+   plot(
+      grain_yield.t.ha. ~ AUDPS_m,
+      data = dat1,
+      main = paste(dat1$location[1], (dat1$year[1])),
+      ylim = c(0, max(
+         PM_MB_means$grain_yield.t.ha., na.rm = TRUE
+      )),
+      xlim = c(0, max(PM_MB_means$AUDPS_m, na.rm = TRUE))
+   )
+   abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = dat1))
+   points(grain_yield.t.ha. ~ AUDPS_m,
+          data = dat1[dat1$fungicide_ai == "control",],
+          col = "red")
+
+}
+```
+
+The plots from the AUPDS is similar to the AUDPC, however according to the linear model the AUDPC is a better, significant fit.
+
+A mixed effect model would be more suitable to investigate the interactive effects of location, season, and trial. 
+The mixed effect model will help us decide on the best approach and structure for our meta-analysis model.
+
+### FAO mungbean data
+
+An important consideration for why to carry out work on mungbean diseases is the value the crop provides. 
+Lets pull in data from the FAOSTAT website for the area of mungbean crops harvested.
+
+```{r FAO_data_inquiry}
+beans <- read.csv(here("data/FAOSTAT_data_7-6-2020.csv"))
+
+glimpse(beans)
+
+beans %>%
+   filter(Item == "Beans, dry",
+          Element == "Area harvested")%>%
+   select(Year,Value)%>%
+   ggplot(aes(y = Value, x = Year))+
+   geom_point()+
+   geom_smooth()
+
+```
+
+```{r}
+save(SeasonPlot, file = here("cache/PreliminaryData.Rdata"))
+```

### 2020-08-12 01_Meta-analysis_experiments.Rmd
Edit first chapter to follow the structure of the paper. Add the selection criteria and begin to implement it on the dataset

--- 2020-06-22 01_Meta-analysis_experiments.Rmd
@@
 ```{r MEsummary_Libraries, message=FALSE, echo=FALSE}
-if (!require("pacman")) install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, leaflet, htmltools,schoolmath)
-source("R/import_data.R")
+if (!require("pacman"))
+   install.packages("pacman")
+pacman::p_load(tidyverse, kableExtra, leaflet, htmltools, schoolmath, here)
+source(here("R/import_data.R")
+)
 ```
+Trials testing fungicide efficacy on powdery mildew in mungbean in the Grains Research and Development Corporation (GRDC) northern grains region were sourced for a meta-analysis.
 
-This meta-analysis uses data collected by a number of researchers from the Department of Agriculture and Primary Industries and the University of Southern Queensland.
-It is worth noting in particular Professor Malcolm Riley's and Dr. Sue Thompson's effort in establishing and coordinating early field trials between 2010 and 2016.
+Data was collected from a number of researchers from the Department of Agriculture and Primary Industries and the University of Southern Queensland and the National Growers Association.
+We would like to acknowledge in particular Professor Malcolm Riley's and Dr. Sue Thompson's effort in establishing and coordinating early field trials between 2010 and 2014.
 
-Studies were conducted in the following locations and years and were considered for inclusion in this analysis.
+Studies were collated from the following locations and years and were considered for inclusion in this analysis.
 
@@
 
-## Summary of trials
-
-```{r data_summary, echo=FALSE, message=FALSE, warning=FALSE}
-PM.dat <- import_data()
-
-kable(
-   PM.dat %>%
-      group_by(trial_ref, ) %>%
-      summarise(
-         Year = unique(year),
-         Location = unique(location),
-         `Replicates per treatment` = if(is.whole(mean(replicates))){
-            as.character(mean(replicates))}else{
-               as.character(paste(min(replicates),"-",max(replicates)))},
-         `Planting date` = unique(planting_date),
-         `First sign of disease` = unique(first_sign_disease),
-         `Fungicide treatments` = length(n_treatment),
-      ) %>%
-      arrange(Year)%>%
-      select(-trial_ref),
-   caption = "Description of Experiments",
-   align = "c",
-   col.names = c("Year", "Location", "Replicates\nper treatments",
-                 "Planting date", "First sign\nof disease", "Fungicide\n treatments")
-)  %>%
-   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
-   column_spec(c(3,5:6), width = "3cm") %>% 
-   scroll_box(height = "500px")
-
-```
-
-## Powdery mildew rating scales
-
-**2001 - 2004 trials**
-
-Trial data were obtained from a non-published manuscript.
-
-### 1 - 5 powdery mildew rating scale
-
-Ratings for powdery mildew were on a 1 - 5 rating scale where
-
-   1 - No sign of disease
-
-   2 - 1 - 30&nbsp;% diseased leaf area
-
-   3 - 31 - 65&nbsp;% diseased leaf area
-
-   4 - 66 - 99&nbsp;% diseased leaf area and
-
-   5 - Complete defoliation
-
-Comparing these trials which have not used the 1 - 9 rating scale will be converted using a percentage change.
-
-**2013 Field trials**
-
-Trials from 2013 were all conducted by the [Northern Growers Alliance (NGA)](https://www.nga.org.au/).
-The raw data were obtained from Lawrie Price.
-NGA data were formatted to be compliant with the 1 - 9 rating scale used in all other experiments.
-Detailed code for the conversion can be found in the following vignette [191115_PMMB_DataWrangling_PM.Rmd](./vignette/191115_PMMB_DataWrangling_PM.html).
-
-### 1 - 9 powdery mildew rating scale
-
-   1 - No powdery mildew colonies observed on any plant
-
-   2 - Small colonies in lower 1/3 of canopy, up to 75&nbsp;% of plants affected
-
-   3 - Colonies in lower 1/2 of canopy, >75&nbsp;% of plants affected
-
-   4 - Colonies in lower 2/3 of canopy, up to 7&nbsp;5% of plants affected
-
-   5 - Colonies in lower 2/3 of canopy, >75&nbsp;% of plants affected
-
-   6 - Colonies in lower 2/3 of canopy, 100&nbsp;% of plants affected
-
-   7 - Colonies in lower 2/3 of canopy of 10&nbsp;0% of plants, some plants with colonies also in top 1/3 of canopy
-
-   8 - Colonies to top of plant with >75&nbsp;% of plants affected
-
-   9 - Colonies to top of plant with 100&nbsp;% of plants affected and heavy leaf drop
-
 ## Experiment locations
 
-The following map displays experiment locations which were considered for inclusion in this meta-analysis.
+The following map displays experiment locations in the GRDC northern grain growing region which were considered for inclusion in this meta-analysis.
 
@@
 ```
+
+## Criteria for inclusion in meta-analysis
+
+   1. A field trial testing the efficacy of fungicide on powdery mildew afflicted mungbean plants.  
+   2. Trial data needed to include:  
+      i) fungicide active ingredients.  
+      ii) A Demethylase inhibitor (DMI) fungicide.  
+      iii) The data at which powdery mildew first appeared in the trial.  
+      iv) Disease severity at the end of the growing seasons.  
+      v) Fungicide application dates.  
+      vi) fungicide dose.  
+      vii) Crop yield.  
+      viii) Treatment means and accompanying variance
+
+## Import data and apply selection criteria
+
+### Import data from trials we have the raw data  
+```{r import_dataRAW}
+PM_MB_raw <- 
+   rbind(
+      read.csv(here("cache/2010 PMmung Hermitage means.csv"), stringsAsFactors = FALSE),
+      read.csv(here("cache/2011 PMmung Herm means.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/2011 PMmung Kingaroy means.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/AM1305_Goolhi_means.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/AM1304-MarysMount_means.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/AM1303-Premer-Disease_means.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/BB1305_Millmerran_means.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/Herm_16_means.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/King_16_means.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/Fogerty_17_mean.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/Hermitage_17_mean.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/Wellcamp_18_mean.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/Hermitage_19_mean.csv"),stringsAsFactors = FALSE)
+      )
+write.csv(PM_MB_raw, file = here("cache/PM_Mungbean_SummaryOfTrialsWithRawData"), row.names = FALSE)
+```
+### Import dataset of manual entries  
+Import dataset which were manually entered from trial reports
+```{r import_dataMan}
+source(here("R/import_ManData.R"))
+PM_MB_man <- import_ManData()
+```
+
+Bind datasets, data set compiled from raw trial data and data manually compiled from trial reports.
+```{r bind_data}
+PM_MB_dat <- 
+   rbind(
+      PM_MB_raw,
+      PM_MB_man
+      )
+```
+
+## Summary of all trials  
+```{r data_summary, echo=FALSE, message=FALSE, warning=FALSE}
+PM_MB_dat %>%
+   arrange(year, location) %>%
+   group_by(trial_ref) %>%
+   summarise(
+         Year = unique(year),
+         Location = unique(location),
+         `Replicates per treatment` = if(all(replicates[1] == replicates)){
+            as.character(replicates[1])}else{
+               as.character(paste(min(replicates),"-",max(replicates)))},
+         `Planting date` = unique(planting_date),
+         `First sign of disease` = unique(first_sign_disease),
+         `Fungicide treatments` = length(n_treatment),
+      ) %>%
+      arrange(Year)%>%
+   kable(caption = "Description of Experiments",
+         align = "c",
+         col.names = c("Unique Trial\nReference","Year", "Location", "Replicates\nper treatments",
+                       "Planting date", "First sign\nof disease", "Fungicide\n treatments")
+         )  %>%
+   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
+   column_spec(c(3,5:6), width = "3cm") %>% 
+   scroll_box(height = "500px")
+
+```
+
+## Powdery mildew rating scales
+
+**2001 - 2004 trials**
+
+Trial data were obtained from a non-published manuscript.
+
+### 1 - 5 powdery mildew rating scale
+
+Ratings for powdery mildew were on a 1 - 5 rating scale where
+
+   1 - No sign of disease
+
+   2 - 1 - 30&nbsp;% diseased leaf area
+
+   3 - 31 - 65&nbsp;% diseased leaf area
+
+   4 - 66 - 99&nbsp;% diseased leaf area and
+
+   5 - Complete defoliation
+
+Comparing these trials which have not used the 1 - 9 rating scale will be converted using a percentage change.
+
+**2013 Field trials**
+
+Trials from 2013 were all conducted by the [Northern Growers Alliance (NGA)](https://www.nga.org.au/).
+The raw data were obtained from Lawrie Price.
+NGA data were formatted to be compliant with the 1 - 9 rating scale used in all other experiments.
+Detailed code for the conversion can be found in the following vignette [191115_PMMB_DataWrangling_PM.Rmd](./vignette/191115_PMMB_DataWrangling_PM.html).
+
+### 1 - 9 powdery mildew rating scale
+
+   1 - No powdery mildew colonies observed on any plant
+
+   2 - Small colonies in lower 1/3 of canopy, up to 75&nbsp;% of plants affected
+
+   3 - Colonies in lower 1/2 of canopy, >75&nbsp;% of plants affected
+
+   4 - Colonies in lower 2/3 of canopy, up to 7&nbsp;5% of plants affected
+
+   5 - Colonies in lower 2/3 of canopy, >75&nbsp;% of plants affected
+
+   6 - Colonies in lower 2/3 of canopy, 100&nbsp;% of plants affected
+
+   7 - Colonies in lower 2/3 of canopy of 10&nbsp;0% of plants, some plants with colonies also in top 1/3 of canopy
+
+   8 - Colonies to top of plant with >75&nbsp;% of plants affected
+
+   9 - Colonies to top of plant with 100&nbsp;% of plants affected and heavy leaf drop

### 2020-08-12 R/import_ManData.R
Create two data sets reflecting what data was manually created from trial reports and what was generated from raw trial data

@@ -1,0 +1,21 @@
+
+#' Import mungbean powdery mildew data
+#'
+#' Imports mungbean powdery mildew data and formats columns correctly.
+#'
+#' @return a Tibble of mungbean powdery mildew trial data
+#'
+#' @examples
+#'
+#' PM_MB_means <- import_data()
+#'
+
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(here)
+
+import_ManData <- function() {
+   x <- read.csv(file = here::here("cache/PM_MB_updated.csv"), stringsAsFactors = FALSE)
+   y <- read.csv(file = here::here("cache/PM_Mungbean_SummaryOfTrialsWithRawData"), stringsAsFactors = FALSE)
+   x <- x[!(x$trial_ref %in% unique(y$trial_ref)),] # note ! negate, therefore %notin%
+   return(x)
+}

### 2020-08-12 01_Meta-analysis_experiments.Rmd
Apply selection criteria to dataset and save variable to Rdata file

@@
    install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, leaflet, htmltools, schoolmath, here)
-source(here("R/import_data.R")
-)
+pacman::p_load(tidyverse, kableExtra, leaflet, htmltools, lubridate, here)
+
+if (!require("theme.usq"))
+   devtools::install_github("adamhsparks/theme.usq")
+library(theme.usq)
+theme_set(theme_usq())
 ```
@@
       ii) A Demethylase inhibitor (DMI) fungicide.  
-      iii) The data at which powdery mildew first appeared in the trial.  
+      iii) The date at which powdery mildew first appeared in the trial.  
       iv) Disease severity at the end of the growing seasons.  
@@
 ```
+
 ### Import dataset of manual entries  
@@
 ```{r import_dataMan}
-source(here("R/import_ManData.R"))
-PM_MB_man <- import_ManData()
+PM_MB_man <- read.csv(here("cache/PM_Mungbean_DataManuallyEntered.csv"), stringsAsFactors = FALSE)
 ```
@@
 
-## Summary of all trials  
+### Summary of all trials  
 ```{r data_summary, echo=FALSE, message=FALSE, warning=FALSE}
@@
 
-## Powdery mildew rating scales
+Lets apply the selection criteria our dataset.  
+All trials identified for this meta-analysis reported: fungicide active ingredient, dose, first sign of disease. 
+Therefore no trials need to be removed to satisfy this criteria.
 
-**2001 - 2004 trials**
+Three trials omitted due to not reporting yields  
+```{r TrialWithoutYield}
+PM_MB_dat %>%
+   filter(is.na(grain_yield.t.ha.)) %>%
+   distinct(trial_ref, year, location)
 
-Trial data were obtained from a non-published manuscript.
+PM_MB_dat <- PM_MB_dat %>%
+   filter(!is.na(grain_yield.t.ha.))
+```
+One more trial removed as it did not report disease severity.  
+```{r TrialsWithotDisease}
+PM_MB_dat %>%
+   filter(is.na(PM_final_severity)) %>%
+   distinct(trial_ref, year, location)
 
-### 1 - 5 powdery mildew rating scale
+PM_MB_dat <- PM_MB_dat %>%
+   filter(!is.na(PM_final_severity))
+```
 
-Ratings for powdery mildew were on a 1 - 5 rating scale where
+No trials from our subset need to be removed for not reporting fungicide application dates.  
+```{r FungicideApplicationDates}
+PM_MB_dat %>%
+   group_by(trial_ref) %>%
+   summarise(No_Record_Of_Fungicide_Application_Dates = all(is.na(fungicide_application_1)),
+             .groups = 'drop')%>%
+   filter(No_Record_Of_Fungicide_Application_Dates)
+```
+No trials from our subset need to be removed for not reporting fungicide dose.  
+```{r FungicideDoseTrials}
+PM_MB_dat %>%
+   group_by(trial_ref) %>%
+   summarise(No_Record_Of_Fungicide_Dose = all(is.na(dose_ai.ha)),
+             .groups = 'drop')%>%
+   filter(No_Record_Of_Fungicide_Dose)
+```
 
-   1 - No sign of disease
+Four trials from our subset need to be removed for not reporting yield variance.  
+```{r TrialsWithVariance}
+NoVar <- PM_MB_dat %>%
+   group_by(trial_ref) %>%
+   summarise(location = location,
+             year = year,
+             No_Var = all(is.na(yield_error)),
+             .groups = 'drop')%>%
+   filter(No_Var)%>%
+   distinct(trial_ref, year, location)
+NoVar
 
-   2 - 1 - 30&nbsp;% diseased leaf area
+PM_MB_dat <- PM_MB_dat %>%
+   filter(!(trial_ref %in% NoVar$trial_ref))
+```
 
-   3 - 31 - 65&nbsp;% diseased leaf area
+We need to focus the meta-analysis on fungicides with the same mode of action.
+Let's look at all the fungicides and retain the best represented fungicide group in the data.
+```{r Fungicides}
+PM_MB_dat %>%
+   group_by(fungicide_ai, trial_ref) %>%
+   summarise(groups = 'drop') %>%
+   count(sort = TRUE) %>%
+   rename(Trials = n) %>%
+   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
+   xlab("Fungicide active ingredient") +
+   ylab("N Trials") +
+   geom_col() +
+   scale_fill_usq() +
+   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
+   scale_colour_usq() +
+   coord_flip()
+```
 
-   4 - 66 - 99&nbsp;% diseased leaf area and
+Tebuconazole and propiconazole are both classed as demethylase inhibitors. 
+We will retain the trials trials which only contain DMI fungicides.  
+```{r}
+PM_MB_dat %>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")%>%
+   distinct(trial_ref, location, year)%>%
+   arrange(year)
+```
+We will retain all fungicides for now and remove them before the analysis.
 
-   5 - Complete defoliation
+Finally we are going to define the class of each variable in the data, retaining only the variables relevant to the analysis.
+```{r classifyData}
+PM_MB_dat <- 
+   PM_MB_dat %>%
+   mutate(trial_ref = as.character(trial_ref)) %>%
+   mutate(year = as.character(year)) %>%
+   mutate(location = as.character(location)) %>%
+   mutate(host_genotype = as.character(host_genotype)) %>%
+   mutate(row_spacing = as.double(round(row_spacing, digits = 2))) %>%
+   mutate(replicates = as.integer(replicates)) %>%
+   mutate(planting_date = ymd(planting_date)) %>%
+   mutate(flowering_date = ymd(flowering_date)) %>%
+   mutate(pod_fill_date = ymd(pod_fill_date)) %>%
+   mutate(mid_late_pod_fill = ymd(mid_late_pod_fill)) %>%
+   mutate(first_sign_disease = ymd(first_sign_disease)) %>%
+   mutate(fungicide_ai = as.character(fungicide_ai))%>%
+   mutate(dose_ai.ha = round(as.double(dose_ai.ha), digits = 2))%>%
+   mutate(fungicide_application_1 = ymd(fungicide_application_1)) %>%
+   mutate(fungicide_application_2 = ymd(fungicide_application_2)) %>%
+   mutate(fungicide_application_3 = ymd(fungicide_application_3)) %>%
+   mutate(fungicide_application_4 = ymd(fungicide_application_4)) %>%
+   mutate(fungicide_application_5 = ymd(fungicide_application_5)) %>%
+   mutate(fungicide_application_6 = ymd(fungicide_application_6)) %>%
+   mutate(total_fungicide = as.integer(total_fungicide)) %>%
+   mutate(harvest_date = ymd(harvest_date)) %>%
+   mutate(final_assessment = ymd(final_assessment)) %>%
+   mutate(PM_final_severity = round(as.double(PM_final_severity), digits = 4))%>%
+   mutate(disease_error = round(as.double(disease_error), digits = 6))%>%
+   mutate(D_error_type = as.character(D_error_type))%>%
+   mutate(grain_yield.t.ha. = round(as.double(grain_yield.t.ha.), digits = 4))%>%
+   mutate(yield_error = round(as.double(yield_error), digits = 6))%>%
+   mutate(Y_error_type = as.character(Y_error_type))%>%
+   mutate(Y_Msquare = round(as.double(Y_Msquare), digits = 6))%>%
+   mutate(yield_gain = round(as.double(yield_gain), digits = 4))%>%
+   mutate(prop_YG = round(as.double(prop_YG), digits = 4))%>%
+   select(-c(trial_design, # remove the following columns
+             plot_length.m.,
+             plot_width.m.,
+             plant_density,
+             trade_name,
+             n_treatment,
+             emergence_date,
+             rating_scale,
+             raw_graded,
+             raw_data_avail,
+             comments,
+             days_harvest.planting,
+             AUDPS_m,
+             AUDPC_sd,
+             Inc_Ms))
+```
 
-Comparing these trials which have not used the 1 - 9 rating scale will be converted using a percentage change.
-
-**2013 Field trials**
-
-Trials from 2013 were all conducted by the [Northern Growers Alliance (NGA)](https://www.nga.org.au/).
-The raw data were obtained from Lawrie Price.
-NGA data were formatted to be compliant with the 1 - 9 rating scale used in all other experiments.
-Detailed code for the conversion can be found in the following vignette [191115_PMMB_DataWrangling_PM.Rmd](./vignette/191115_PMMB_DataWrangling_PM.html).
-
-### 1 - 9 powdery mildew rating scale
-
-   1 - No powdery mildew colonies observed on any plant
-
-   2 - Small colonies in lower 1/3 of canopy, up to 75&nbsp;% of plants affected
-
-   3 - Colonies in lower 1/2 of canopy, >75&nbsp;% of plants affected
-
-   4 - Colonies in lower 2/3 of canopy, up to 7&nbsp;5% of plants affected
-
-   5 - Colonies in lower 2/3 of canopy, >75&nbsp;% of plants affected
-
-   6 - Colonies in lower 2/3 of canopy, 100&nbsp;% of plants affected
-
-   7 - Colonies in lower 2/3 of canopy of 10&nbsp;0% of plants, some plants with colonies also in top 1/3 of canopy
-
-   8 - Colonies to top of plant with >75&nbsp;% of plants affected
-
-   9 - Colonies to top of plant with 100&nbsp;% of plants affected and heavy leaf drop
+```{r saveData01}
+save(PM_MB_dat, file = here("cache/ImportDataAndSelectTrials01.Rdata"))
+```

### 2020-08-12 01_Meta-analysis_experiments.Rmd
move text to first chapter

@@
-# Studies considered in meta-analysis
+# Trials considered for inclusion in meta-analysis
 
@@
 ```
+The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in the highest frequencies.
+The DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.
 
-Tebuconazole and propiconazole are both classed as demethylase inhibitors. 
+Amistar Xtra and Custodia both contain strobilurin and triazole, however, because they contain differing dose ratios (inverted) pooling may not be appropriate.
+
+Perhaps best way forward is to focus the meta-analysis on only the DMIs.
+This can then be compared to an additional meta-analysis including azoxystrobin as a comparison.
+
 We will retain the trials trials which only contain DMI fungicides.  

### 2020-08-12 03_Preliminary_analysis.Rmd
Update preliminart analysis page

@@
                here)
-source(here("R/import_data.R"))
+
 if (!require("theme.usq"))
@@
 )
+load("cache/ImportDataAndSelectTrials01.Rdata")
 ```
@@
 ## Explore and Visualise Data
-First let's import the data.
 Each row provides the mean yield for each experimental treatment.
 
-```{r echo=TRUE, message=FALSE, warning=FALSE}
-PM_MB_means <- import_data() 
-```
-
-The data explored in the `PM_MB_means` data frame is a list of mean values from each treatment in each respective experiment.
+The data explored in the `PM_MB_dat` data frame is a list of mean values from each treatment in each respective experiment.
 These preliminary analyses will focus on the change in mungbean yields, which is attributable to the fungicide treatment. 
@@
 AUDPC for trials which only provided final powdery mildew incidence was calculated using the record of 'first sign of disease' and final assessment.
-More details on how the `PM_MB_means` data was compiled can be found in the ['Data wrangle vingette'](./vignette/191115_PMMB_DataWrangling_PM.html)
 
@@
 
-   8 In-crop rainfall
+   8 Final disease rating
 
-   9 Irrigated versus non-irrigated trials
-
-   10 Mean daily temperature in the weeks following spray application
-
-   11 Final disease rating
-
-   12 Two pathogen species cause PM (new discovery in 2018)
-
-The data plotted below are from `r length(unique(PM_MB_means$trial_ref))` field trials between (`r first(levels(PM_MB_means$year))` - `r last(levels(PM_MB_means$year))`) of which the details are described in the [studies considered in meta-analysis section](#studies-considered-in-meta-analysis).
+The data plotted below are from `r length(unique(PM_MB_dat$trial_ref))` field trials between (`r first(levels(PM_MB_dat$year))` - `r last(levels(PM_MB_dat$year))`) of which the details are described in the [Trials considered for inclusion in meta-analysis section](#Trials-considered-for-inclusion-in-meta-analysis).
 
@@
 #### Fungicide type
-
-First let's standardise the sulphur treatments.
-Some early experiments tested different formulations.
-There was no difference in the sulphur formulations so we will refer to all of them as "sulphur".
-
-```{r sulphur_simplify}
-# Remove the variation in different sulphur formulations
-unique(PM_MB_means[grep("sulphur", PM_MB_means$fungicide_ai),
-                   "fungicide_ai"])
-PM_MB_means[grep("sulphur", PM_MB_means$fungicide_ai), "fungicide_ai"] <-
-   "sulphur"
-```
-
-Let's explore how many different types of fungicide were used and at what frequency.
-
-```{r Fungicides}
-PM_MB_means %>%
-   group_by(fungicide_ai, trial_ref) %>%
-   summarise() %>%
-   count(sort = TRUE) %>%
-   rename(Trials = n) %>%
-   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
-   xlab("Fungicide active ingredient") +
-   ylab("N Trials") +
-   geom_col() +
-   scale_fill_usq() +
-   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
-   scale_colour_usq() +
-   coord_flip()
-```
-
-The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in the highest frequencies, along with sulphur.
-The DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.
-
-Amistar Xtra and Custodia both contain strobilurin and triazole, however, because they contain differing dose ratios (inverted) pooling may not be appropriate.
-
-Perhaps best way forward is to focus the meta-analysis on only the DMIs.
-This can then be compared to an additional meta-analysis including azoxystrobin as a comparison.
-
-*****
 
@@
 ```{r Calculate_yield-savings}
-PM_MB_means$grain_yield.t.ha. <-
-   as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data
-
-for (i in unique(PM_MB_means$trial_ref)) {
+for (i in unique(PM_MB_dat$trial_ref)) {
    # Loop code over each trial reference
-   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
+   dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == i, ]
 
@@
    # Reassign values to trial_ref subset
-   PM_MB_means[PM_MB_means$trial_ref == i, ] <- dat1
+   PM_MB_dat[PM_MB_dat$trial_ref == i, ] <- dat1
 }
@@
 # calculate yield gain and prop_yield gain for experiments with no row spacing data
-dat1 <- PM_MB_means[PM_MB_means$trial_ref == "AM1303", ]
+dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == "AM1303", ]
 
@@
    c(NA, NA)
-PM_MB_means[PM_MB_means$trial_ref == "AM1303", ] <- dat1
 
-write.csv(PM_MB_means,
-          "cache/1911_PM_MB_means&Ygains.csv")
+PM_MB_dat[PM_MB_dat$trial_ref == "AM1303", ] <- dat1
 ```
@@
 ```{r Fungicide_x_nSprays_tble2, message=FALSE}
-PM_MB_means %>%
+PM_MB_dat %>%
    group_by(fungicide_ai, total_fungicide) %>%
@@
 
-**  **  *
+*****
 
@@
 ```{r Fungicide_x_nSprays_tble1, message=FALSE, warning=FALSE}
-PM_MB_means %>%
-   mutate(fungicide_ai = as.factor(PM_MB_means$fungicide_ai)) %>%
+PM_MB_dat %>%
+   mutate(fungicide_ai = as.factor(PM_MB_dat$fungicide_ai)) %>%
    filter(total_fungicide == 1 | total_fungicide == 2) %>%
@@
    labs(y = "Proportion of grain yield saved",
-        title = "Grain yield proportion saved\ngrouped by fungicide type") +
+        title = "Grain yield proportion saved\nfaceted by number of sprays") +
    theme(legend.position = "none") +
@@
 The follow-up spray seems to show an increase in yield protection.
-Interestingly sulphur sprays show good protection when sprayed twice.
 
@@
 ```{r tebuAndPropi_dose}
-PM_MB_means %>%
+PM_MB_dat %>%
    filter(fungicide_ai == "tebuconazole" |
@@
    xlab("Dose (g ai/ha)") +
-   ggtitle(label = "Total number of treatments for each respective tebuconazole dose") +
+   ggtitle(label = "Total number of treatments for each respective tebuconazole\nor propiconazole dose") +
    geom_bar() +
@@
 ```{r PropiDoseEffect}
-PM_MB_means %>%
+PM_MB_dat %>%
    filter(fungicide_ai == "propiconazole") %>%
@@
    geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
+   ylab("Yield gain proportially\nto the no spray control") +
    facet_grid(cols = vars(total_fungicide))
@@
 ```{r table_PropiDoses}
-table(as.character(PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole",]$trial_ref),
-      PM_MB_means[PM_MB_means$fungicide_ai == "propiconazole",]$dose_ai.ha)
+table(as.character(PM_MB_dat[PM_MB_dat$fungicide_ai == "propiconazole",]$trial_ref),
+      PM_MB_dat[PM_MB_dat$fungicide_ai == "propiconazole",]$dose_ai.ha)
 ```
 
-Two trials show both doses were applied in the same trial, mung1112/01 and mung1112/02.
-Let's look at the difference in proportion of yield saved in these trials.
-
-```{r PropiDoses_TrialCompare}
-PM_MB_means[(PM_MB_means$trial_ref == "mung1112/01" |
-                PM_MB_means$trial_ref == "mung1112/02") &
-                PM_MB_means$fungicide_ai == "propiconazole",] %>%
-   mutate(dose_ai.ha = as.factor(dose_ai.ha)) %>%
-               ggplot(aes(y = prop_YG, x = dose_ai.ha))+
-   geom_boxplot()+
-   facet_grid(cols = vars(total_fungicide)) +
-   xlab("Dose (g ai/ha)") +
-   ggtitle(label = "Yield for each respective propiconazole dose, faceted by number of applications") +
-   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5)
-```
-
-This plot is similar to the previous plot, indicating dose needs to be considered in the analysis. Especially as there is a interaction between dose and number of sprays.
+One trial show both doses were applied in the same trial, and mung1112/02.
 
@@
 ```{r Fungicide_x_nSprays}
-table(PM_MB_means$fungicide_ai, PM_MB_means$total_fungicide)
+table(PM_MB_dat$fungicide_ai, PM_MB_dat$total_fungicide)
 ```
@@
 ```{r spray_relative2FS}
-PM_MB_means %>%
+PM_MB_dat %>%
    mutate(
@@
    )) +
-   ylab("Days to First Sign of Disease") +
+   ylab("Fungicide application timing relative to First Sign of Disease") +
    facet_grid(cols = vars(total_fungicide)) +
@@
 
-The plot shows single fungicide applications are mostly made at zero, first sign of disease in the crop.
+The plot shows single fungicide applications are mostly made at zero, first sign of disease in the crop. Some were made earlier and some around 10 days later.  
 Experiments that tested two spray treatments also tend to make the first application at first sign of disease, and the second spray between 10 and 25 days later.
@@
 ```{r Host_genotype}
-PM_MB_means %>%
+PM_MB_dat %>%
    filter(fungicide_ai == "tebuconazole" |
@@
 This plot shows a large amount of yield volatility in all cultivars except Green Diamond.
-Green Diamond shows little volatility probably because this cultivar was only used in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trial.
+Green Diamond shows little volatility probably because this cultivar was only used in `r length(unique(PM_MB_dat[PM_MB_dat$host_genotype == "Green Diamond","trial_ref"]))` trial.
 
@@
 ```{r row_spacing.m}
-PM_MB_means %>%
+PM_MB_dat %>%
    filter(fungicide_ai == "tebuconazole" |
@@
 # Which row spacing leads to the higher disease severity
-PM_MB_means %>%
+PM_MB_dat %>%
    filter(year == 2017 |
@@
 # Which row spacing leads to the higher yield potential
-PM_MB_means %>%
+PM_MB_dat %>%
    filter(year == 2017 |
@@
 # Create the data frame for the plot
-season_dates <- PM_MB_means %>%
+season_dates <- PM_MB_dat %>%
    group_by(trial_ref) %>%
@@
 ```{r AUDPC_check}
-PM_MB_means %>%
+PM_MB_dat %>%
    filter(is.na(AUDPC_m)) %>%
@@
 
-The trials `r unique(PM_MB_means[is.na(PM_MB_means$AUDPC_m),"trial_ref"]) ` don't have an estimate of AUDPC and need to be filled in. 
+The trials `r unique(PM_MB_dat[is.na(PM_MB_dat$AUDPC_m),"trial_ref"]) ` don't have an estimate of AUDPC and need to be filled in. 
 The following script estimates AUDPC from the final disease severity rating and the first sign of disease information.
@@
 source(here("R/AUDPC_for_single_obs.R"))
-write.csv(PM_MB_means,
-          "cache/1911_PM_MB_means&Ygains.csv", row.names = FALSE)
+write.csv(PM_MB_dat,
+          "cache/1911_PM_MB_dat&Ygains.csv", row.names = FALSE)
 ```
@@
 
-plot(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means)
-abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means))
+plot(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_dat)
+abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_dat))
 
@@
 ```{r AUDPClm}
-summary(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means))
+summary(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_dat))
 ```
@@
 This is not what we would expect and the low R squared value of `r round(summary(lm(grain_yield.t.ha.
-~ AUDPC_m, data = PM_MB_means))$adj.r.squared,3)` perhaps there are additional factors influencing this relationship.
+~ AUDPC_m, data = PM_MB_dat))$adj.r.squared,3)` perhaps there are additional factors influencing this relationship.
 
@@
 ```{r AUDPCxTrial}
-sm2lg <- PM_MB_means %>%
+sm2lg <- PM_MB_dat %>%
    group_by(trial_ref) %>%
@@
 for (i in sm2lg$trial_ref) {
-   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
+   dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == i, ]
    if (any(is.na(dat1$grain_yield.t.ha.))) {
@@
       main = paste(dat1$location[1], (dat1$year[1])),
-      ylim = c(0, max(PM_MB_means$grain_yield.t.ha., na.rm = TRUE)),
-      xlim = c(0, max(PM_MB_means$AUDPC_m, na.rm = TRUE))
+      ylim = c(0, max(PM_MB_dat$grain_yield.t.ha., na.rm = TRUE)),
+      xlim = c(0, max(PM_MB_dat$AUDPC_m, na.rm = TRUE))
    )
@@
 ```{r}
-dat3 <- PM_MB_means %>%
+dat3 <- PM_MB_dat %>%
    filter(year == "2016",
@@
 
-dat3$F_Yield <- PM_MB_means %>%
+dat3$F_Yield <- PM_MB_dat %>%
    filter(year == "2016",
@@
 ```{r Yield_vs_AUDPS}
-plot(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means)
-abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means))
+plot(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_dat)
+abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_dat))
 
-summary(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means))
+summary(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_dat))
 
-sm2lg <- PM_MB_means %>%
+sm2lg <- PM_MB_dat %>%
    group_by(trial_ref) %>%
@@
       ylim = c(0, max(
-         PM_MB_means$grain_yield.t.ha., na.rm = TRUE
+         PM_MB_dat$grain_yield.t.ha., na.rm = TRUE
       )),
-      xlim = c(0, max(PM_MB_means$AUDPS_m, na.rm = TRUE))
+      xlim = c(0, max(PM_MB_dat$AUDPS_m, na.rm = TRUE))
    )

### 2020-08-17 01_TrialsForInclusionInAnalysis.Rmd
Editing and formating

--- 2020-08-12 01_Meta-analysis_experiments.Rmd
@@
 
-Studies were collated from the following locations and years and were considered for inclusion in this analysis.
+<br>
+<br>
+<br>
 
-* 2001  
-   + Bongeen #1  
-   + Bongeen #2
+## Criteria for inclusion in meta-analysis
 
-* 2002  
-   + Hermitage #1  
-   + Hermitage #2  
-   + Kingaroy
+   1. A field trial testing the efficacy of fungicide on powdery mildew afflicted mungbean plants.  
+   2. Trial data needed to include:  
+      i) fungicide active ingredients.  
+      ii) A Demethylase inhibitor (DMI) fungicide.  
+      iii) The date at which powdery mildew first appeared in the trial.  
+      iv) Disease severity at the end of the growing seasons.  
+      v) Fungicide application dates.  
+      vi) fungicide dose.  
+      vii) Crop yield.  
+      viii) Treatment means and accompanying variance
 
-* 2004  
-   + Redvale
+<br>
+<br>
+<br>
 
-* 2010  
-   + Hermitage  
-   + Kingaroy
+## Import data and apply selection criteria  
+### Import data from trials we have the raw data  
+```{r import_dataRAW}
+PM_MB_raw <- 
+   rbind(
+      read.csv(here("cache/2010 PMmung Hermitage means.csv"), stringsAsFactors = FALSE),
+      read.csv(here("cache/2011 PMmung Herm means.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/2011 PMmung Kingaroy means.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/AM1305_Goolhi_means.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/AM1304-MarysMount_means.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/AM1303-Premer-Disease_means.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/BB1305_Millmerran_means.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/Herm_16_means.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/King_16_means.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/Fogerty_17_mean.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/Hermitage_17_mean.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/Wellcamp_18_mean.csv"),stringsAsFactors = FALSE),
+      read.csv(here("cache/Hermitage_19_mean.csv"),stringsAsFactors = FALSE)
+      )
+write.csv(PM_MB_raw, file = here("cache/PM_Mungbean_SummaryOfTrialsWithRawData"), row.names = FALSE)
+```
 
-* 2011  
-   + Hermitage  
-   + Kingaroy
+<br>
+<br>
+<br>
 
-* 2012  
-   + Gatton  
-   + Kingaroy
+### Import dataset of manual entries  
+Import dataset which were manually entered from trial reports  
+```{r import_dataMan}
+PM_MB_man <- read.csv(here("cache/PM_Mungbean_DataManuallyEntered.csv"), stringsAsFactors = FALSE)
+```
 
-* 2013  
-   + Premer  
-   + Millmerran   
-   + Marys Mount  
-   + Goolhi
+Bind datasets, data set compiled from raw trial data and data manually compiled from trial reports.  
+```{r bind_data}
+PM_MB_dat <- 
+   rbind(
+      PM_MB_raw,
+      PM_MB_man
+      )
+```
 
-* 2015  
-   + Hermitage  
-   + Dalby - Site abandoned due to insufficient/late disease infection  
-   + Emerald
+<br>
+<br>
+<br>
 
-* 2016  
-   + Hermitage  
-   + Kingaroy  
-   + Emerald
+### Summary of all trials  
+```{r data_summary, echo=FALSE, message=FALSE, warning=FALSE}
+PM_MB_dat %>%
+   arrange(year, location) %>%
+   group_by(trial_ref) %>%
+   summarise(
+         Year = unique(year),
+         Location = unique(location),
+         `Replicates per treatment` = if(all(replicates[1] == replicates)){
+            as.character(replicates[1])}else{
+               as.character(paste(min(replicates),"-",max(replicates)))},
+         `Planting date` = unique(planting_date),
+         `First sign of disease` = unique(first_sign_disease),
+         `Fungicide treatments` = length(n_treatment),
+      ) %>%
+      arrange(Year)%>%
+   kable(caption = "Description of Experiments",
+         align = "c",
+         col.names = c("Unique Trial\nReference","Year", "Location", "Replicates\nper treatments",
+                       "Planting date", "First sign\nof disease", "Fungicide\n treatments")
+         )  %>%
+   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
+   column_spec(c(3,5:6), width = "3cm") %>% 
+   scroll_box(height = "500px")
 
-* 2017  
-   + Missen Flats (Fogerty's farm)  
-   + Hermitage
+```
 
-* 2018  
-   + Wellcamp
+<br>
 
-* 2019  
-   + Hermitage
-
-## Experiment locations
+### Experiment locations
 
@@
 
-## Criteria for inclusion in meta-analysis
+<br>
+<br>
+<br>
 
-   1. A field trial testing the efficacy of fungicide on powdery mildew afflicted mungbean plants.  
-   2. Trial data needed to include:  
-      i) fungicide active ingredients.  
-      ii) A Demethylase inhibitor (DMI) fungicide.  
-      iii) The date at which powdery mildew first appeared in the trial.  
-      iv) Disease severity at the end of the growing seasons.  
-      v) Fungicide application dates.  
-      vi) fungicide dose.  
-      vii) Crop yield.  
-      viii) Treatment means and accompanying variance
-
-## Import data and apply selection criteria
-
-### Import data from trials we have the raw data  
-```{r import_dataRAW}
-PM_MB_raw <- 
-   rbind(
-      read.csv(here("cache/2010 PMmung Hermitage means.csv"), stringsAsFactors = FALSE),
-      read.csv(here("cache/2011 PMmung Herm means.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/2011 PMmung Kingaroy means.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/AM1305_Goolhi_means.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/AM1304-MarysMount_means.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/AM1303-Premer-Disease_means.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/BB1305_Millmerran_means.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/Herm_16_means.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/King_16_means.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/Fogerty_17_mean.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/Hermitage_17_mean.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/Wellcamp_18_mean.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/Hermitage_19_mean.csv"),stringsAsFactors = FALSE)
-      )
-write.csv(PM_MB_raw, file = here("cache/PM_Mungbean_SummaryOfTrialsWithRawData"), row.names = FALSE)
-```
-
-### Import dataset of manual entries  
-Import dataset which were manually entered from trial reports  
-```{r import_dataMan}
-PM_MB_man <- read.csv(here("cache/PM_Mungbean_DataManuallyEntered.csv"), stringsAsFactors = FALSE)
-```
-
-Bind datasets, data set compiled from raw trial data and data manually compiled from trial reports.  
-```{r bind_data}
-PM_MB_dat <- 
-   rbind(
-      PM_MB_raw,
-      PM_MB_man
-      )
-```
-
-### Summary of all trials  
-```{r data_summary, echo=FALSE, message=FALSE, warning=FALSE}
-PM_MB_dat %>%
-   arrange(year, location) %>%
-   group_by(trial_ref) %>%
-   summarise(
-         Year = unique(year),
-         Location = unique(location),
-         `Replicates per treatment` = if(all(replicates[1] == replicates)){
-            as.character(replicates[1])}else{
-               as.character(paste(min(replicates),"-",max(replicates)))},
-         `Planting date` = unique(planting_date),
-         `First sign of disease` = unique(first_sign_disease),
-         `Fungicide treatments` = length(n_treatment),
-      ) %>%
-      arrange(Year)%>%
-   kable(caption = "Description of Experiments",
-         align = "c",
-         col.names = c("Unique Trial\nReference","Year", "Location", "Replicates\nper treatments",
-                       "Planting date", "First sign\nof disease", "Fungicide\n treatments")
-         )  %>%
-   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
-   column_spec(c(3,5:6), width = "3cm") %>% 
-   scroll_box(height = "500px")
-
-```
+## Subset data to selection criteria
 
@@
 ```
+
+<br>
+<br>
+<br>
+
 One more trial removed as it did not report disease severity.  
@@
 
+<br>
+<br>
+<br>
+
 No trials from our subset need to be removed for not reporting fungicide application dates.  
@@
 ```
+
+<br>
+<br>
+<br>
+
 No trials from our subset need to be removed for not reporting fungicide dose.  
@@
 ```
+
+<br>
+<br>
+<br>
 
@@
 
-Tebuconazole and propiconazole are both classed as demethylase inhibitors. 
-We will retain the trials trials which only contain DMI fungicides.  
+The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in the highest frequencies.
+Thee DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.
+
+Amistar Xtra and Custodia both contain strobilurin and triazole, however, because they contain differing dose ratios (inverted) pooling may not be appropriate.
+
+Perhaps best way forward is to focus the meta-analysis on only the DMIs.
+This can then be compared to an additional meta-analysis including azoxystrobin as a comparison.
+
+<br>
+<br>
+<br>
+
+We will retain the follow trials which only contain DMI fungicides. 
+However we won't remove non-DMI fungicides just yet, we will do this before the analysis. 
 ```{r}
@@
 ```
-We will retain all fungicides for now and remove them before the analysis.
+
+<br>
+<br>
+<br>
+<br>
+
+### Classify dataset variables
 

### 2020-08-17 03_Preliminary_analysis.Rmd
Wordsmithing and editing Fixing titles Removing irrelevant sections like irrigation, yield volatility Simplifying code. More use of tidyverse code

@@
 Later in this document we will also consider the impact of fungicide treatments on disease incidence/severity.
-Mean powdery mildew incidence was recorded at the end of each growing season.
-Some experiments recorded disease incidence throughout the season and these were summarised with AUDPC.
-AUDPC for trials which only provided final powdery mildew incidence was calculated using the record of 'first sign of disease' and final assessment.
+Mean powdery mildew severity was recorded at the end of each growing season.
+Some experiments recorded disease severity throughout the season and these were summarised with AUDPC.
+AUDPC for trials which only provided final powdery mildew severity were calculated using the record of 'first sign of disease' and final assessment.
 
@@
 
-   8 Final disease rating
+   8 Final disease rating / disease pressure
 
@@
          unique(dat1$trial_ref),
-         "at",
+         " at ",
          unique(dat1$location),
-         "in year",
+         " in year ",
          unique(dat1$year),
-         "has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n"
+         " has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n"
       )
@@
 
+<br>
+<br>
+<br>
+
 Now we have calculated proportional yield savings we can inspect the difference between the fungicide active ingredients
@@
 
-*****
+<br>
+<br>
+<br>
 
@@
    )) +
-   ylab("Fungicide application timing relative to First Sign of Disease") +
+   ylab("Number of days after or before first sign of powdery mildew") +
+   ggtitle("Fungicide application timing relative to First Sign of Disease.\n - Faceted by number of applications")+
    facet_grid(cols = vars(total_fungicide)) +
@@
 
-#### Genotype yield variability
-
-Does host cultivar significantly impact the yield?
-Let's look at the volatility in yields to see if any cultivar yields better or has greater tolerance to powdery mildew.
-Below we plot distributions of mean trial yields for each cultivar.
-The following plots use data that includes all fungicide types.
-
-First let's look at overall yields for each cultivar, where trial is not a factor, for all treatments (spray and no spray).
-
-```{r yield_vol}
-# Outputs the table and graph
-source("R/yield_volatility.r") # function to investigate the volatility in yields
-# Volatility is the range between the upper and lower 97.5 and 2.5 % quartiles
-YV1 <-
-   yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
-YV1[[2]] + 
-   scale_fill_usq()
-YV1[[3]]
-```
-
-This plot shows a large amount of yield volatility in all cultivars except Green Diamond.
-Green Diamond shows little volatility probably because this cultivar was only used in `r length(unique(PM_MB_dat[PM_MB_dat$host_genotype == "Green Diamond","trial_ref"]))` trial.
-
-Now let's look at overall yields for each cultivar, where trial is not a factor, in only the no spray control treatments.
-
-```{r yieldVol_control}
-YV2 <-
-   yield_volatility(genotype_by_trial = FALSE, control_only = TRUE)
-YV2[[2]] +
-   scale_fill_usq()
-YV2[[3]]
-```
-
-Volatility of the cultivars are less, albeit fairly similar, in control plots when trial is not considered as a factor.
-
-*****
-
-Let's examine the same plots as above but only for the most commonly used trial site, Hermitage.
-
-```{r yieldVol_Herm}
-YV1_herm <-
-   yield_volatility(
-      genotype_by_trial = FALSE,
-      control_only = FALSE,
-      location = "Hermitage"
-   )
-YV1_herm[[2]] +
-   scale_fill_usq()
-
-YV1_herm[[3]]
-```
-
-Jade shows a large amount of volatility, excluding Green Diamond, Crystal shows the next least volatility.
-
-*****
-
-Let's take a closer look at Crystal with spray management treatments and without.
-
-```{r YieldVol_Crystal}
-YV1_crystal <-
-   yield_volatility(genotype = "Crystal", control_only = FALSE)
-YV1_crystal[[2]] +
-   scale_fill_usq()
-
-YV1_crystal[[3]]
-
-YV2_crystal <-
-   yield_volatility(genotype = "Crystal", control_only = TRUE)
-YV2_crystal[[2]] +
-   scale_fill_usq()
-
-YV2_crystal[[3]]
-```
-
-There is a lot of variation between field trials for Crystal, but little variation within field trials. This indicates that trial should be fit as a random effect when we fit a model to this data.
-
-Let's look at Jade, to see if it differs.
-
-```{r YieldVol_Jade}
-YV1_jade <- yield_volatility("Jade",control_only = FALSE)
-YV1_jade[[2]] +
-   scale_fill_usq()
-
-YV1_jade[[3]]
-```
-
-For Jade there is high variation between trials and with-in.
-Perhaps indicating lower tolerance. 
-Let's look at the same plot with data only from no spray controls to see if the variation is the same.
-
-```{r YieldVol_JadeControl}
-YV2_jade <- yield_volatility("Jade", control_only = TRUE)
-YV2_jade[[2]] +
-   scale_fill_usq()
-
-YV2_jade[[3]]
-```
-
-There still remains a higher volatility in Jade and perhaps a greater shift in the probability curve including fungicide treatments versus probability curves including only no spray controls.
-Indicating that there might be a difference in powdery mildew tolerance between Jade and Crystal.
-
-Overall there seems to be an influence of cultivar.
-However this variation is not as distinct as the variation between trials.
-
-*****
-
 ### Row spacing
@@
 
+Lets plot disease severity in boxplots grouped by row spacing treatment.
+We are asking here, which row spacing leads to the higher disease severity?
+
 ```{r RS_severity}
@@
 ```
+
+There is little difference here between the row spacing treatments, lets look if there is a trial location effect as disease pressure lead to varying results.
 
@@
 
-*****
-
-### Yield vs in-season rain
-
-In0-crop rain could be a significant factor which contributes to the end of season grain yield.
-To investigate this effect I will use a linear model (GY ~ SR) where seasonal rainfall represents a specific time frame with respect to planting time.
-Multiple time frames were tested from 20 days prior to planting, to 100 days after planting.
-
-The multiple time frames were tested by a loop over the dates at the start of the season (to 90 days after planting) to find which date fits the best linear model for grain weight and in-crop rainfall.
-The code for this process was moved to be contained within it's own script and can be run as a job as it can take a long time.
-To speed up the computation I split the script into four, ran the jobs and bound the data into one frame.
-The output of the script is saved with the prefix `lmInSeasonRainfall` followed by the time windows the model is run.
-For example `lmInSeasonRainfall_20.40_50.80.csv` holds the model results for start days between 20 and 40 days after planting to end window dates between 50 and 80 days after planting.
-
-This tests when rainfall during the cropping season could be best associated with yield
-
-```{r rainfall_sum_Sstart}
-# The four data files were created from four scripts run as four jobs in RStudio
-# when the four jobs are finished they can be imported and combined into one data.frame
-# source(Rainfall_x_cropYield_s-10.09_e30.65.R)
-# source(Rainfall_x_cropYield_s-10.09_e65.100.R)
-# source(Rainfall_x_cropYield_s10.30_e30.65.R)
-# source(Rainfall_x_cropYield_s10.30_e65.10.R)
-
-lm_rain1 <-
-   read.csv("cache/lmInSeasonRainfall_-10.09_30.64.csv",
-            stringsAsFactors = FALSE)
-lm_rain2 <-
-   read.csv("cache/lmInSeasonRainfall_-10.09_65.100.csv",
-            stringsAsFactors = FALSE)
-lm_rain3 <-
-   read.csv("cache/lmInSeasonRainfall_10.30_30.64.csv",
-            stringsAsFactors = FALSE)
-lm_rain4 <-
-   read.csv("cache/lmInSeasonRainfall_10.30_65.100.csv",
-            stringsAsFactors = FALSE)
-
-lm_rain <- rbind(lm_rain1, lm_rain2, lm_rain3, lm_rain4)
-```
-
-Now we have read in the data from the previously computed models let's find the linear model which has:  
-   - The lowest P value  
-   - the highest adjusted r squared value
-
-```{r WhichLModel}
-lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)), ]
-lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)), ]
-lm_rain[which(lm_rain$lm_adj_rsquared == max(lm_rain$lm_adj_rsquared)), ]
-```
-
-To visualise the model fits we will use a heat map to describe how the models faired in relation to the rainfall windows.
-log of the p value was used to improve the resolution of small very small p values.
-
-```{r rainLMpvalue}
-ggplot(lm_rain, aes(x = start_day, y = end_day, z = log(lm_pval))) +
-   geom_raster(aes(fill = log(lm_pval)), interpolate = TRUE) +
-   geom_contour(bins = 15, colour = "white") +
-   geom_point(data = lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)), ],
-              aes(x = start_day, y = end_day),
-              colour = " red") +
-   scale_fill_distiller(palette = "RdBu", direction = -1) 
-```
-
-```{r rainLMadjrsquared}
-ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_adj_rsquared)) +
-   geom_raster(aes(fill = lm_adj_rsquared), interpolate = TRUE) +
-   geom_contour(bins = 15, colour = "white") +
-   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)), ],
-              aes(x = start_day, y = end_day),
-              colour = " red") +
-   scale_fill_distiller(palette = "RdBu") 
-```
-
-The approximate period when in-crop rainfall affects the most on the mean harvest is between 14 - 67 days after planting.
-
-*****
-
-### Season range and first incidence
-
-Mungbean is a summer crop and powdery mildew requires cool conditions to establish.
-Therefore the disease can be avoided by planting early in summer or spring, avoiding cooler temperatures at the end of some seasons.
-Can we visualise when PM is most likely to establish over the calendar year?
-
-I'll build a plot of horizontal lines indicating the season length and use a dot on the line to indicating the day of the year first sign was observed for that trial.
-
-```{r first_incidence}
-# Create the data frame for the plot
-season_dates <- PM_MB_dat %>%
-   group_by(trial_ref) %>%
-   summarise(
-      Planting_date = unique(planting_date),
-      Harvest_date = unique(harvest_date),
-      First_sign_PM = unique(first_sign_disease),
-      season_length = as.Date(unique(harvest_date)) - as.Date(unique(planting_date)),
-      cropping_season = "Actual"
-   )
-
-# For some trials where planting date and Harvest date is missing let's estimate 
-#     the season length by using the mean of all season lengths
-season_dates[is.na(season_dates$season_length),"cropping_season"] <- "Estimated"
-
-season_dates[is.na(season_dates$Planting_date),"Planting_date"] <- 
-   season_dates[is.na(season_dates$Planting_date),"Harvest_date"] - 
-   as.numeric(mean(season_dates$season_length, na.rm = TRUE))
-
-season_dates[is.na(season_dates$Harvest_date),"Harvest_date"] <- 
-   season_dates[is.na(season_dates$Harvest_date),"Planting_date"] + 
-   as.numeric(mean(season_dates$season_length, na.rm = TRUE))
-
-season_dates[is.na(season_dates$season_length),"season_length"] <- 
-   mean(season_dates$season_length, na.rm = TRUE)
-
-season_dates$Planting_day <- yday(season_dates$Planting_date)
-season_dates$Disease_day <- yday(season_dates$First_sign_PM)
-
-season_dates[c(1:2,6), "Planting_day"] <- 1
-
-season_dates$Harvest_day <-
-   season_dates$Planting_day + season_dates$season_length
-
-first_day_month <- c(0, 31, 60, 91, 121, 152, 182, 212, 244, 274) + 1
-axis_labels_date <-
-   c(
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[1], "%b-%d"),
-      # Jan
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[2], "%b-%d"),
-      # Feb
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[3], "%b-%d"),
-      # March
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[4], "%b-%d"),
-      # April
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[5], "%b-%d"),
-      # May
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[6], "%b-%d"),
-      # June
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[7], "%b-%d"),
-      # July
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[8], "%b-%d"),
-      # August
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[9], "%b-%d"),
-      # Sept
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[10], "%b-%d") # October
-   )
-
-# reorder the factors so they will appear in chronological order
-# I used First sign because all trials have recorded this
-season_dates$trial_ref <-
-   factor(season_dates$trial_ref,
-          levels = levels(season_dates$trial_ref)[rev(order(season_dates$First_sign_PM))])
-
-# Plot
-SeasonPlot <- season_dates %>%
-   ggplot() +
-   geom_pointrange(aes(
-      x = trial_ref,
-      y = Disease_day,
-      ymin = Planting_day,
-      ymax = Harvest_day,
-      colour = cropping_season
-   )) +
-   scale_y_continuous(limits = c(
-      0,
-      max(
-         season_dates$Planting_day +
-            season_dates$season_length,
-         na.rm = TRUE
-      )
-   ),
-   labels = axis_labels_date,
-   breaks = first_day_month) +
-   geom_point(aes(x = trial_ref, y = Disease_day), size =2.5) +
-   coord_flip() +
-   scale_color_manual(values=c("black","grey70"))+
-   ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
-
-SeasonPlot
-```
-
-In most years, regardless of the age of the crop, powdery mildew establishes in March, which is to be expected.
-The disease is driven by weather conditions and the plant is vulnerable at any growth stage.
+<br>
+<br>
+<br>
+<br>
 
@@
 
-First let's check we have all the AUDPC observations.
+First let's check if we have all the AUDPC observations by searching for trials with mission AUDPC.
 
@@
 source(here("R/AUDPC_for_single_obs.R"))
-write.csv(PM_MB_dat,
-          "cache/1911_PM_MB_dat&Ygains.csv", row.names = FALSE)
 ```
@@
 
-```{r AUDPCxTrial}
-sm2lg <- PM_MB_dat %>%
+```{r AUDPCxTrial, fig.height= 10, fig.width=10}
+mTrialYield <- PM_MB_dat %>%
    group_by(trial_ref) %>%
-   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
-   arrange(TY)
+   mutate(TY = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
+   pull(TY)
 
-for (i in sm2lg$trial_ref) {
-   dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == i, ]
-   if (any(is.na(dat1$grain_yield.t.ha.))) {
-      next
-   }
-   if (any(is.na(dat1$AUDPC_m))) {
-      next
-   }
+PM_MB_dat$trial_ref <- reorder(PM_MB_dat$trial_ref, mTrialYield)
 
-   plot(
-      grain_yield.t.ha. ~ AUDPC_m,
-      data = dat1,
-      main = paste(dat1$location[1], (dat1$year[1])),
-      ylim = c(0, max(PM_MB_dat$grain_yield.t.ha., na.rm = TRUE)),
-      xlim = c(0, max(PM_MB_dat$AUDPC_m, na.rm = TRUE))
-   )
-   abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = dat1))
-   points(grain_yield.t.ha. ~ AUDPC_m,
-          data = dat1[dat1$fungicide_ai == "control",],
-          col = "red")
+PM_MB_dat %>%
+   filter(!is.na(grain_yield.t.ha.)) %>%
+   mutate(Treatment = case_when(
+      fungicide_ai == "control" ~ "control",
+      TRUE ~ "FungicideTreated"))%>%
+   ggplot(aes(y = grain_yield.t.ha., x = AUDPC_m))+
+   geom_point(aes(color = Treatment))+
+   facet_wrap(vars(trial_ref))+
+   scale_y_continuous(limits = c(0,3))+
+   geom_smooth(method = "lm", se = FALSE, linetype = 1, colour = "grey", size =1)+
+   scale_colour_usq()
 
-}
 ```
 
+### Yield loss in cultivar Jade
+
+Mungbean Jade shows the best quantitative resistance to powdery mildew.
 Based on a GRDC report by Sue Thompson [-@SueThompson2016] we want to know what the yield loss was in on cultivar Jade in the 2016 Trials.
-```{r}
-dat3 <- PM_MB_dat %>%
+```{r JadeYieldLoss}
+PM_MB_dat %>%
    filter(year == "2016",
-          host_genotype == "Jade",
-          fungicide_ai == "control")%>%
-   group_by(location)%>%
-   summarise(C_Yield = mean(grain_yield.t.ha., na.rm = TRUE))
-
-dat3$F_Yield <- PM_MB_dat %>%
-   filter(year == "2016",
-          host_genotype == "Jade",
-          fungicide_ai != "control")%>%
-   group_by(location)%>%
-   summarise(F_Yield = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
-   pull(F_Yield)
-
-dat3 %>% 
-   mutate(diff = F_Yield - C_Yield) %>%
-   mutate(percent = (diff/F_Yield)*100)
+          host_genotype == "Jade")%>%
+   mutate(Treatment = case_when(
+      fungicide_ai == "control" ~ "control",
+      TRUE ~ "FungicideTreated"))%>%
+   group_by(location, Treatment)%>%
+   summarise(trial_ref = trial_ref,
+             location = location, 
+             year = year,
+             Yield = mean(grain_yield.t.ha., na.rm = TRUE),
+             .groups = "drop")%>%
+   distinct()%>%
+   pivot_wider(names_from = Treatment, values_from = Yield)%>%
+   mutate(Diff = FungicideTreated - control) %>%
+   mutate(percent = (Diff/FungicideTreated)*100)%>%
+   select(trial_ref, location, year, control, FungicideTreated,percent, Diff)
 
@@
 The higher the yield, the greater greater the influence on the disease on the yield especially if the crop is high yielding with AUDPC also being large enough to reduce yield.
-
-Let's have a look again at the same sequence of graphs and analyses for area under the disease progress _stairs_.
-
-```{r Yield_vs_AUDPS}
-plot(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_dat)
-abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_dat))
-
-summary(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_dat))
-
-sm2lg <- PM_MB_dat %>%
-   group_by(trial_ref) %>%
-   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
-   arrange(TY)
-
-for (i in sm2lg$trial_ref) {
-   dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == i, ]
-   if (any(is.na(dat1$grain_yield.t.ha.))) {
-      next
-   }
-   if (any(is.na(dat1$AUDPS_m))) {
-      next
-   }
-
-   plot(
-      grain_yield.t.ha. ~ AUDPS_m,
-      data = dat1,
-      main = paste(dat1$location[1], (dat1$year[1])),
-      ylim = c(0, max(
-         PM_MB_dat$grain_yield.t.ha., na.rm = TRUE
-      )),
-      xlim = c(0, max(PM_MB_dat$AUDPS_m, na.rm = TRUE))
-   )
-   abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = dat1))
-   points(grain_yield.t.ha. ~ AUDPS_m,
-          data = dat1[dat1$fungicide_ai == "control",],
-          col = "red")
-
-}
-```
-
-The plots from the AUPDS is similar to the AUDPC, however according to the linear model the AUDPC is a better, significant fit.
-
-A mixed effect model would be more suitable to investigate the interactive effects of location, season, and trial. 
-The mixed effect model will help us decide on the best approach and structure for our meta-analysis model.
 
@@
 ```{r}
-save(SeasonPlot, file = here("cache/PreliminaryData.Rdata"))
+save(PM_MB_dat, file = here("cache/PreliminaryData.Rdata"))
 ```

### 2020-08-17 R/AUDPC_for_single_obs.R
remove AUDPS

@@ -2,8 +2,9 @@
 
 library(agricolae)
 
-estAUDPC <- PM_MB_means[is.na(PM_MB_means$AUDPC_m) &
-                           !is.na(PM_MB_means$PM_final_severity),]
+
+estAUDPC <- PM_MB_dat[is.na(PM_MB_dat$AUDPC_m) &
+                           !is.na(PM_MB_dat$PM_final_severity),]
 
 # are there any entries which don't state the first sign of disease?
 any(is.na(estAUDPC$first_sign_disease)) # No
@@ -25,35 +26,6 @@ for(i in unique(estAUDPC$trial_ref)){
    estAUDPC[estAUDPC$trial_ref == i,"AUDPC_m"] <- x1
 }
 
-PM_MB_means[is.na(PM_MB_means$AUDPC_m) &
-               !is.na(PM_MB_means$PM_final_severity),"AUDPC_m"] <- estAUDPC$AUDPC_m
-
-#____________________________AUDPStairs________________________________________________
-# estimating_AUDPStairs_for_trials with no raw data
-
-estAUDPS <- PM_MB_means[is.na(PM_MB_means$AUDPS_m) &
-                           !is.na(PM_MB_means$PM_final_severity),]
-
-# are there any entries which don't state the first sign of disease?
-any(is.na(estAUDPS$first_sign_disease)) # No
-
-
-# are there any entries which don't state when they were assessed for disease at the end of the trial
-any(is.na(estAUDPS$final_assessment)) # No
-
-#Good! Lets begin 
-
-estAUDPS$tInf <- as.Date(estAUDPS$final_assessment, format = "%Y-%m-%d") - 
-   as.Date(estAUDPS$first_sign_disease, format = "%Y-%m-%d")
-
-for(i in unique(estAUDPS$trial_ref)){
-   x1 <- apply(data.frame(zero = rep(0, times = length(estAUDPS[estAUDPS$trial_ref == i,"final_assessment"])),
-                          FSev = estAUDPS[estAUDPS$trial_ref == i,"PM_final_severity"]-1),1,
-               FUN = audps, dates = c(0, unique(estAUDPS[estAUDPS$trial_ref == i,"tInf"])+7)
-   )
-   estAUDPS[estAUDPS$trial_ref == i,"AUDPS_m"] <- x1
-}
-
[…]

### 2020-08-18 01_TrialsForInclusionInAnalysis.Rmd
copy edits

@@
       i) fungicide active ingredients.  
-      ii) A Demethylase inhibitor (DMI) fungicide.  
+      ii) A demethylase inhibitor (DMI) fungicide.  
       iii) The date at which powdery mildew first appeared in the trial.  
@@
 
-We will retain the follow trials which only contain DMI fungicides. 
-However we won't remove non-DMI fungicides just yet, we will do this before the analysis. 
+We will retain the following trials, which only contain DMI fungicides. 
+However, we won't remove non-DMI fungicides just yet, we will do this before the analysis.
+
 ```{r}
@@
 Finally we are going to define the class of each variable in the data, retaining only the variables relevant to the analysis.
+
 ```{r classifyData}

### 2020-08-24 01_TrialsForInclusionInAnalysis.Rmd
name a chunck

@@
 
-```{r}
+```{r FinalTrialsForInclusion}
 PM_MB_dat %>%

### 2020-08-24 03_Preliminary_analysis.Rmd
Add descriptive statistics for average mungbean yield

@@
 The data explored in the `PM_MB_dat` data frame is a list of mean values from each treatment in each respective experiment.
-These preliminary analyses will focus on the change in mungbean yields, which is attributable to the fungicide treatment. 
+These preliminary analyses will describe the data and then investigate any change in mungbean yields which is attributable to the fungicide treatment. 
+### Descriptive statistics
+#### Spatio-temporal variation
+
+Lets look at how many trials were undertaken each season
+
+```{r FinalTrialsForInclusion}
+tmp1 <- PM_MB_dat %>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")%>%
+   distinct(trial_ref, location, year)%>%
+   arrange(year)
+   table(tmp1$year)
+```
+
+Also the location of the trials
+
+```{r FinalTrialsForInclusion}
+tmp2 <- PM_MB_dat %>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")%>%
+   distinct(trial_ref, location, year)%>%
+   arrange(year)
+   table(tmp1$location)
+```
+
+#### Mean yield
+
+What is the variation in yield over all the trials (including non-DMI fungicide trials) in the no spray control and fungicide treated plots.  
+```{r ControlYield_AllTrials}
+PM_MB_dat %>%
+   filter(fungicide_ai == "control")%>%
+   summarise(mean_yield = mean(grain_yield.t.ha.),
+             minimum_yield = min(grain_yield.t.ha.),
+             maximum_yield = max(grain_yield.t.ha.),
+             yield_stdev = sd(grain_yield.t.ha.))
+
+```
+
+What is the yield variation in no spray control trials yield over only the DMI fungicide trials.  
+```{r ControlYield_DMITrials}
+DMITrials <- PM_MB_dat %>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")%>%
+   distinct(trial_ref)%>%
+   pull()
+
+PM_MB_dat %>%
+   filter(trial_ref %in% DMITrials)%>%
+   filter(fungicide_ai == "control" )%>%
+   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
+             minimum_yield = min(grain_yield.t.ha.*1000),
+             maximum_yield = max(grain_yield.t.ha.*1000),
+             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))
+
+```
+
+Mean yields in DMI fungicide treated plots
+```{r Yield_DMITrials}
+PM_MB_dat %>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")%>%
+   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
+             minimum_yield = min(grain_yield.t.ha.*1000),
+             maximum_yield = max(grain_yield.t.ha.*1000),
+             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))
+
+```
+
+Lets look at the yield gains in each trial compared to the no spray control, we will also calculate the proportional grain yield gains.
+
+```{r Calculate_yield-savings}
+for (i in unique(PM_MB_dat$trial_ref)) {
+   # Loop code over each trial reference
+   dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == i, ]
+
+   if (any(is.na(unique(dat1$row_spacing)))) {
+      # If there is no recorded row.spacing don't calculate proportional yield, skip to the next trial
+      warning(
+         unique(dat1$trial_ref),
+         " at ",
+         unique(dat1$location),
+         " in year ",
+         unique(dat1$year),
+         " has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n"
+      )
+      next()
+   }
+
+   for (j in unique(dat1$row_spacing)) {
+      # Loop within trial row_spacing
+      dat2 <- dat1[dat1$row_spacing == j, ]
+      controlY <-
+         mean(dat2[dat2$fungicide_ai == "control", "grain_yield.t.ha."]) #Mean taken as some trials had multiple control reps
+
+      # Calculate the yield gain relative to the no spray control (controlY)
+      dat2$yield_gain <- dat2$grain_yield.t.ha. - controlY
+      dat2$prop_YG <- dat2$yield_gain  /  controlY
+
+      # insert NA as yeild_gain and proportional yield gain for the controls
+      dat2[dat2$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
+         NA
+
+      # Reassign values to row_spacing subset
+      dat1[dat1$row_spacing == j, ] <- dat2
+   }
+   # Reassign values to trial_ref subset
+   PM_MB_dat[PM_MB_dat$trial_ref == i, ] <- dat1
+}
+
+# ____________________________________________
+# calculate yield gain and prop_yield gain for experiments with no row spacing data
+dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == "AM1303", ]
+
+controlY <-
+   mean(dat1[dat1$fungicide_ai == "control", "grain_yield.t.ha."])
+
+dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
+dat1$prop_YG <- dat1$yield_gain / controlY
+dat1[dat1$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
+   c(NA, NA)
+
+PM_MB_dat[PM_MB_dat$trial_ref == "AM1303", ] <- dat1
+```
+
+Lets show the yield gains in each trial as a table and plot
+```{r YieldGain_table}
+PM_MB_dat %>%
+   filter(trial_ref %in% DMITrials)%>%  # selects only the trials with DMI fungicide treatments
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")%>%
+   group_by(trial_ref, location, year)%>%
+   summarise(yield_gain_m = mean(yield_gain),
+             yield_gain_se = sd(yield_gain, na.rm = T)/sqrt(n()),
+             yg_n = n(),
+             .groups = "drop")%>%
+   arrange(yield_gain_m)
+```
+
+```{r YieldGain_plot}
+PM_MB_dat %>%
+   filter(trial_ref %in% DMITrials)%>%  
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")%>%
+   group_by(trial_ref, location, year)%>%
+   summarise(yield_gain_m = mean(yield_gain),
+             yield_gain_se = sd(yield_gain, na.rm = T)/sqrt(n()),
+             .groups = "drop")%>%
+   mutate(trial = paste(location,year,sep = "\n"))%>%
+   ggplot(aes(reorder(trial, yield_gain_m), yield_gain_m))+
+   geom_bar(stat = "identity")+
+   geom_errorbar(width = 0.3 ,aes(ymax = yield_gain_m + yield_gain_se, 
+                     ymin = yield_gain_m - yield_gain_se))+
+   theme(axis.text.x = element_text(angle = 90, hjust = 1))
+
+```
+
+```{r}
+mpg %>%
+   group_by(manufacturer,drv,cyl)%>%
+   filter(n() >= 2)%>%
+   summarise(mean_Sp = mean(cty),
+             stdev_h = sd(cty),
+             n_group = n())
+
+data()
+
+mpg
+
+```
+
 Later in this document we will also consider the impact of fungicide treatments on disease incidence/severity.

### 2020-08-24 04_Prep_data.Rmd
Change PM_MB_dat to the new for and load it in from rdata

@@
 ```{r import_data}
-PM_MB_means <- read.csv(here("cache/1911_PM_MB_means&Ygains.csv"))
-
+load("cache/PreliminaryData.Rdata")
 source(here("R/same.R")) # matches each element of a vector and does not return NAs
@@
 ```{r variance_types}
-PM_MB_means %>%
+PM_MB_dat %>%
    filter(fungicide_ai == "tebuconazole" |
              fungicide_ai == "propiconazole") %>%
-   group_by(trial_ref, location, year , Y_error_type, fungicide_ai) %>%
-   summarise(DMI_treatments = length(Y_error_type)) %>%
+   group_by(trial_ref, location, year , Y_error_type) %>%
+   summarise(DMI_treatments = length(Y_error_type), .groups = 'drop') %>%
    arrange(Y_error_type) %>%
-   select(!fungicide_ai) %>%
    kable(caption = "Number of treatments for each trial and the error type reported",
@@
 ```{r all_LSD_trials}
-Trials <- PM_MB_means %>%
+Trials <- PM_MB_dat %>%
    filter(Y_error_type == "lsd (P=0.05)") %>%
@@
    DFw <-
-      sum(PM_MB_means[PM_MB_means$trial_ref == i, ]$replicates) -
-      length(PM_MB_means[PM_MB_means$trial_ref == i, ]$replicates) # degrees of freedom within groups
+      sum(PM_MB_dat[PM_MB_dat$trial_ref == i, ]$replicates) -
+      length(PM_MB_dat[PM_MB_dat$trial_ref == i, ]$replicates) # degrees of freedom within groups
 
    LSD <-
-      PM_MB_means[PM_MB_means$trial_ref == i, ]$yield_error[1]
+      PM_MB_dat[PM_MB_dat$trial_ref == i, ]$yield_error[1]
 
    V_yield <-
-      (PM_MB_means[PM_MB_means$trial_ref == i, ]$replicates[1] * 
+      (PM_MB_dat[PM_MB_dat$trial_ref == i, ]$replicates[1] * 
           (LSD / Tcrit) ^ 2) / 2 
@@
 
-   for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates)) {
+   for (j in seq_along(PM_MB_dat[PM_MB_dat$trial_ref == i,]$replicates)) {
       if (j == 1) {
          Sv <-
-            vector(length = length(PM_MB_means[PM_MB_means$trial_ref == i,]$replicates))
+            vector(length = length(PM_MB_dat[PM_MB_dat$trial_ref == i,]$replicates))
       } # reset Sv vector if this is the first loop
@@
       Sv[j] = V_yield /
-         PM_MB_means[PM_MB_means$trial_ref == i,]$replicates[j]
+         PM_MB_dat[PM_MB_dat$trial_ref == i,]$replicates[j]
 
@@
    # Replace the values in the dataset
-   PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <-
+   PM_MB_dat[PM_MB_dat$trial_ref == i,]$yield_error <-
       Sv
-   PM_MB_means[PM_MB_means$trial_ref == i,]$Y_error_type <-
+   PM_MB_dat[PM_MB_dat$trial_ref == i,]$Y_error_type <-
       "SamplingVariance"
@@
 # subset data by those which describe the Yield error with standard deviation
-Trials <- PM_MB_means %>%
+Trials <- PM_MB_dat %>%
    filter(Y_error_type == "stdev") %>%
@@
 
-for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error)) {
+for (j in seq_along(PM_MB_dat[PM_MB_dat$trial_ref %in% Trials$trial_ref,]$yield_error)) {
    if (j == 1) {
       Sv <-
-         vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error))
+         vector(length = length(PM_MB_dat[PM_MB_dat$trial_ref %in% Trials$trial_ref,]$yield_error))
    }# create empty vector at first iteration with length of j
 
-   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error[j]) ^ 2
+   Sv[j] = (PM_MB_dat[PM_MB_dat$trial_ref %in% Trials$trial_ref,]$yield_error[j]) ^ 2
 }
@@
 # and replacing the values in the dataset
-PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error <-
+PM_MB_dat[PM_MB_dat$trial_ref %in% Trials$trial_ref,]$yield_error <-
    Sv
-PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$Y_error_type <-
+PM_MB_dat[PM_MB_dat$trial_ref %in% Trials$trial_ref,]$Y_error_type <-
    "SamplingVariance"
@@
 # redefine sample variance calculated from mean square
-PM_MB_means$vi <-
-   PM_MB_means$Y_Msquare /
-   (PM_MB_means$n)
+PM_MB_dat$vi <-
+   PM_MB_dat$Y_Msquare /
+   (PM_MB_dat$replicates)
 
-PM_MB_means %>%
+PM_MB_dat %>%
    ggplot(aes(x = grain_yield.t.ha., y = vi)) +
@@
 ```{r Var_MeanSquarePlot}
-PM_MB_means %>%
+PM_MB_dat %>%
    ggplot(aes(x = grain_yield.t.ha., y = Y_Msquare)) +
@@
 Follow up fungicide applications (cluster_2 and cluster_3) were also categorised as either early, recommended or late.
+
+```{r}
+data.frame(SprayTimingName = c("Early", "Recommended", "Late"),
+           DaysRelativeToFirstSign = c("Prior to first sign of PM",
+                                       "1 - 3 days after first sign of PM",
+                                       "7 - 8 days after first sign of PM"))%>%
+   kable()
+```
 
@@
 
-Let's estimate the age of the crop based on crop maturity observations, we will use the `PM_MB_means` which include some observations of crop maturity.
+Let's estimate the age of the crop based on crop maturity observations, we will use the `PM_MB_dat` which include some observations of crop maturity.
 
 ```{r whatAreTheAges}
-dat2 <- PM_MB_means %>%
+dat2 <- PM_MB_dat %>%
    mutate(

### 2020-08-24 R/dpc.R
beta function to test the linearity of a disease progress curve

@@ -1,0 +1,203 @@
+# this is a function to test a disease progress curve for it's ability
+# To fit a linear or polynomial functions.
+# The function expects a dataframe where each column variable is a column of disease severity ratings for a specific day
+# The function also requires a vector of days the same length as the number of columns and
+# corresponding to the days separating each disease observation 
+# There is a beta function which can handle multiple treatments
+
+
+library(lme4)
+library(dplyr)
+library(agricolae)
+library(ggplot2)
+dpc <- function(dat, days, treat_var = NULL,treat_subset = NULL){
+
+dat$dis_zero <- 1
+dat <- select(dat, dis_zero, everything())
+disease_var <- sapply(dat,class) %in% "numeric"
+colNames_Disease <- colnames(dat)[disease_var]
+if(!is.null(treat_var)){
+colNames_Disease <- colNames_Disease[colNames_Disease != (treat_var)]}
+
+if(length(days) != length(colNames_Disease)){
+   warning("Number of column variables for disease observations does not match the length of the number of days")
+}
+
+# Change dataset from wide to long
+dat_long <- as.data.frame(dat %>%
+   pivot_longer(
+      #-treat_var,
+         cols = colNames_Disease,
+         names_to = "disease_obs",
+         values_to = "dis_score")
+)
+
+# add a column which will reference the day number of disease observation
+# this will be used in agricolae
+dat_long$days <- 0   
+
+# assign the number of days to align with the disease observation columns
+# This assumes the columns were arranged left to right from earliers to latest observation
+   for(i in colNames_Disease){
+      dat_long[dat_long$disease_obs == i,"days"] <- days[colNames_Disease == i]
+   }
+   
+# Order the factor to ensure they will be understood from earliest to latest observation
+   dat_long$disease_obs <- reorder(factor(dat_long$disease_obs), dat_long$days)
+   
+   
+# undertake linear model Plotting and AUDPC for when treatment_var is not specified
+      if(is.null(treat_var)){
+         
+         lm_1 <- lm(dat_long[,"dis_score"] ~ 
+                       dat_long[,"days"]
+         )
+         
+         lm_sqrt <- lm(sqrt(dat_long[,"dis_score"]) ~ 
+                          dat_long[,"days"]
+         )
[…]

### 2020-08-28 03_Preliminary_analysis.Rmd
Clean up preliminary analysis, more concise code

@@
 ## Explore and Visualise Data
-Each row provides the mean yield for each experimental treatment.
 
@@
 These preliminary analyses will describe the data and then investigate any change in mungbean yields which is attributable to the fungicide treatment.
+
 ### Descriptive statistics  
@@
 ```{r FinalTrialsForInclusion}
-tmp2 <- PM_MB_dat %>%
-   filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole")%>%
-   distinct(trial_ref, location, year)%>%
-   arrange(year)
    table(tmp1$location)
@@
 What is the variation in yield over all the trials (including non-DMI fungicide trials) in the no spray control and fungicide treated plots.
+
 ```{r ControlYield_AllTrials}
@@
              maximum_yield = max(grain_yield.t.ha.),
-             yield_stdev = sd(grain_yield.t.ha.))
+             yield_stdev = sd(grain_yield.t.ha.)) %>%
+   kable(align = 'c',
+   caption = "Average yield statistics for no spray contol plots"
+)
 
@@
              maximum_yield = max(grain_yield.t.ha.*1000),
-             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))
+             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
+   kable(align = 'c',
+   caption = "Average yield statistics for control plots in trials which used a DMI fungicide")
 
@@
              maximum_yield = max(grain_yield.t.ha.*1000),
-             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))
+             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
+   kable(align = 'c',
+   caption = "Average yield statistics for DMI fungicide treated plots")
 
@@
 
-```{r}
-mpg %>%
-   group_by(manufacturer,drv,cyl)%>%
-   filter(n() >= 2)%>%
-   summarise(mean_Sp = mean(cty),
-             stdev_h = sd(cty),
-             n_group = n())
-
-data()
-
-mpg
-
-```
-
-Later in this document we will also consider the impact of fungicide treatments on disease incidence/severity.
-Mean powdery mildew severity was recorded at the end of each growing season.
-Some experiments recorded disease severity throughout the season and these were summarised with AUDPC.
-AUDPC for trials which only provided final powdery mildew severity were calculated using the record of 'first sign of disease' and final assessment.
-
 Various factors have been studied in the previous experiments which may influence the subsequent meta-analysis.
@@
 
+<br>
+<br>
+<br>
+
 ### Fungicides
@@
 We are using proportional yield, relative to the no spray control, to reduce the effect of location and seasonal influences.
-
-Let's investigate the difference in the effect of the type of fungicide on proportion of yield saved, but first we need to calculate yield saved relative to the no spray control.
-
-```{r Calculate_yield-savings}
-for (i in unique(PM_MB_dat$trial_ref)) {
-   # Loop code over each trial reference
-   dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == i, ]
-
-   if (any(is.na(unique(dat1$row_spacing)))) {
-      # If there is no recorded row.spacing don't calculate proportional yield, skip to the next trial
-      warning(
-         unique(dat1$trial_ref),
-         " at ",
-         unique(dat1$location),
-         " in year ",
-         unique(dat1$year),
-         " has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n"
-      )
-      next()
-   }
-
-   for (j in unique(dat1$row_spacing)) {
-      # Loop within trial row_spacing
-      dat2 <- dat1[dat1$row_spacing == j, ]
-      controlY <-
-         mean(dat2[dat2$fungicide_ai == "control", "grain_yield.t.ha."]) #Mean taken as some trials had multiple control reps
-
-      # Calculate the yield gain relative to the no spray control (controlY)
-      dat2$yield_gain <- dat2$grain_yield.t.ha. - controlY
-      dat2$prop_YG <- dat2$yield_gain  /  controlY
-
-      # insert NA as yeild_gain and proportional yield gain for the controls
-      dat2[dat2$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
-         NA
-
-      # Reassign values to row_spacing subset
-      dat1[dat1$row_spacing == j, ] <- dat2
-   }
-   # Reassign values to trial_ref subset
-   PM_MB_dat[PM_MB_dat$trial_ref == i, ] <- dat1
-}
-
-# ____________________________________________
-# calculate yield gain and prop_yield gain for experiments with no row spacing data
-dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == "AM1303", ]
-
-controlY <-
-   mean(dat1[dat1$fungicide_ai == "control", "grain_yield.t.ha."])
-
-dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
-dat1$prop_YG <- dat1$yield_gain / controlY
-dat1[dat1$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
-   c(NA, NA)
-
-PM_MB_dat[PM_MB_dat$trial_ref == "AM1303", ] <- dat1
-```
-
-<br>
-<br>
-<br>
-
-Now we have calculated proportional yield savings we can inspect the difference between the fungicide active ingredients
 
@@
    xlab("Row spacing (m)") +
-   ggtitle("Powdery mildew variation between different row spacing")
+   ggtitle("Powdery mildew severity between different row spacing across all trials")
 ```
@@
    )) +
-   geom_jitter(width = 0.1) +
+   geom_jitter(width = 0.05) +
    ggtitle("Grain yield results for different row spacing at three locations") +
@@
 <br>
-
-### AUDPC visualise raw data
-
-First let's check if we have all the AUDPC observations by searching for trials with mission AUDPC.
-
-```{r AUDPC_check}
-PM_MB_dat %>%
-   filter(is.na(AUDPC_m)) %>%
-   distinct(trial_ref, location, year,AUDPC_m, first_sign_disease, final_assessment)%>%
-   kable(align = "c")
-```
-
-The trials `r unique(PM_MB_dat[is.na(PM_MB_dat$AUDPC_m),"trial_ref"]) ` don't have an estimate of AUDPC and need to be filled in. 
-The following script estimates AUDPC from the final disease severity rating and the first sign of disease information.
-
-```{r SingleObsAUDPC}
-source(here("R/AUDPC_for_single_obs.R"))
-```
-
-      _How well does 'area under the disease progress curve' (AUDPC) predict grain yield?_
-
-   and
-
-      _Does spray_management scenario mitigate yield loss through reducing AUDPC?_
-
-We would expect to see grain yield decline with increasing AUDPC.
-Let's just plot yield vs AUDPC.
-
-```{r Yield_vs_AUDPC}
-
-plot(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_dat)
-abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_dat))
-
-```
-
-There appears to be a weak positive relationship between the two continuous variables.
-Does a linear model confirm this?
-
-```{r AUDPClm}
-summary(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_dat))
-```
-
-This is not what we would expect and the low R squared value of `r round(summary(lm(grain_yield.t.ha.
-~ AUDPC_m, data = PM_MB_dat))$adj.r.squared,3)` perhaps there are additional factors influencing this relationship.
-
-Let's tease out variation due to trial location, season, row spacing, and other seasonal variables are preventing us from seeing the expected relationship.
-Let's do the plot again for each trial where there are no missing values.
-Note: The plots are ordered by mean yield of the trial.
-
-```{r AUDPCxTrial, fig.height= 10, fig.width=10}
-mTrialYield <- PM_MB_dat %>%
-   group_by(trial_ref) %>%
-   mutate(TY = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
-   pull(TY)
-
-PM_MB_dat$trial_ref <- reorder(PM_MB_dat$trial_ref, mTrialYield)
-
-PM_MB_dat %>%
-   filter(!is.na(grain_yield.t.ha.)) %>%
-   mutate(Treatment = case_when(
-      fungicide_ai == "control" ~ "control",
-      TRUE ~ "FungicideTreated"))%>%
-   ggplot(aes(y = grain_yield.t.ha., x = AUDPC_m))+
-   geom_point(aes(color = Treatment))+
-   facet_wrap(vars(trial_ref))+
-   scale_y_continuous(limits = c(0,3))+
-   geom_smooth(method = "lm", se = FALSE, linetype = 1, colour = "grey", size =1)+
-   scale_colour_usq()
-
-```
 
@@
 
-glimpse(beans)
+str(beans)
 

### 2020-08-28 04_Prep_data.Rmd
Simplify prep data. Remove disease severity assessments

@@
 source(here("R/same.R")) # matches each element of a vector and does not return NAs
+```
+
+## Subset to Trials containing DMI fungicides
+
+```{r filterDMI_trials}
+DMI_Trials <- 
+   PM_MB_dat %>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")%>%
+   distinct(trial_ref) %>%
+   pull()
+
+PM_MB_dat <- 
+   PM_MB_dat[PM_MB_dat$trial_ref %in% DMI_Trials,]
 ```
@@
    select(trial_ref) %>%
-   distinct()
+   pull()
 
-# calculate the Sampling variance from the standard deviation
-# standard error of the mean equals the standard deviation divided by the square
-#  root of the number of samples
-# Sv <- sem^2 <- stdev/sqrt(n)
-# Sampling variance equals the square of the standard error.
-# Sv <- (stdev/sqrt(n))^2
+PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,"yield_error"] <- 
+   PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,"yield_error"]^2
 
-# Therefore
+PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,]$Y_error_type <-
+   "SamplingVariance"
 
-for (j in seq_along(PM_MB_dat[PM_MB_dat$trial_ref %in% Trials$trial_ref,]$yield_error)) {
-   if (j == 1) {
-      Sv <-
-         vector(length = length(PM_MB_dat[PM_MB_dat$trial_ref %in% Trials$trial_ref,]$yield_error))
-   }# create empty vector at first iteration with length of j
-
-   Sv[j] = (PM_MB_dat[PM_MB_dat$trial_ref %in% Trials$trial_ref,]$yield_error[j]) ^ 2
-}
-
-# and replacing the values in the dataset
-PM_MB_dat[PM_MB_dat$trial_ref %in% Trials$trial_ref,]$yield_error <-
-   Sv
-PM_MB_dat[PM_MB_dat$trial_ref %in% Trials$trial_ref,]$Y_error_type <-
-   "SamplingVariance"
 ```
@@
 ```{r Var_mean_sqaures}
-# redefine sample variance calculated from mean square
-PM_MB_dat$vi <-
-   PM_MB_dat$Y_Msquare /
-   (PM_MB_dat$replicates)
-
 PM_MB_dat %>%
-   ggplot(aes(x = grain_yield.t.ha., y = vi)) +
+   ggplot(aes(x = grain_yield.t.ha., y = yield_error)) +
    geom_point()
 ```
+No association between yield and sample variance, this might be due to the unpredictable nature of mungbeans.
 
-We see here that the sample variance generally decreases or has no association with the grain yield.
-This might be due to the unpredictable nature of mungbeans, however going forward we will use mean squares, which defines between trial variation and is the more generic error term.
+Lets look at the association between mean squares and yield to see if there is a more typical association between yield and variance.
 
@@
 PM_MB_dat %>%
-   ggplot(aes(x = grain_yield.t.ha., y = Y_Msquare)) +
+   ggplot(aes(x = grain_yield.t.ha., y = Y_Msquare/replicates)) +
    geom_point()
+PM_MB_dat[is.na(PM_MB_dat$Y_Msquare),]
+
 ```

### 2020-08-31 03_Prep_data.Rmd
Rename files for order in bookdown Rename importData file. maybe delete later

--- 2020-07-03 03_Prep_data.Rmd
@@
 ```{r import_data}
-PM_MB_means <- read.csv("cache/1911_PM_MB_means&Ygains.csv")
+load("cache/PreliminaryData.Rdata")
+source(here("R/same.R")) # matches each element of a vector and does not return NAs
+```
 
-source("R/same.R") # matches each element of a vector and does not return NAs
+## Subset to Trials containing DMI fungicides
+
+```{r filterDMI_trials}
+DMI_Trials <- 
+   PM_MB_dat %>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")%>%
+   distinct(trial_ref) %>%
+   pull()
+
+PM_MB_dat <- 
+   PM_MB_dat[PM_MB_dat$trial_ref %in% DMI_Trials,]
+```
+
+Now remove any non-DMI treatments or controls
+```{r}
+PM_MB_dat <- 
+   PM_MB_dat %>%
+   filter(fungicide_ai == "control" |
+             fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")
 ```
@@
 ```{r variance_types}
-PM_MB_means %>%
+PM_MB_dat %>%
    filter(fungicide_ai == "tebuconazole" |
              fungicide_ai == "propiconazole") %>%
-   group_by(trial_ref, location, year , Y_error_type, fungicide_ai) %>%
-   summarise(DMI_treatments = length(Y_error_type)) %>%
+   group_by(trial_ref, location, year , Y_error_type) %>%
+   summarise(DMI_treatments = length(Y_error_type), .groups = 'drop') %>%
    arrange(Y_error_type) %>%
-   select(!fungicide_ai) %>%
-   kable(caption = "Number of treatments for each trial and the error type reported", align = "c") %>%
+   kable(caption = "Number of treatments for each trial and the error type reported",
+         align = "c") %>%
    footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
@@
 
-The experiment summaries report either standard deviation, least square differences or no error term (`NA`). 
+The experiment summaries report either standard deviation, least square differences. 
 First we will convert LSD and standard deviation to sample variance.
-Then we will impute variances for the trials, which did not report any form of variance (`NA`).
 
@@
 We will follow the method of converting 'least square differences' (LSD) to sampling variance reported by [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
-A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted to select the T-crit value in the equation. 
-Our data contained 30 degrees of freedom which equates to a 'T-crit' value of 1.697.
-
-![Calculating sampling variance from mean squared error Paul et al. (2008)](Paul_etal_2008.PNG)
-
-`Tcrit` is the T critical value for which there is significant difference between two groups.
-This value is the same for both trials "mung1112/01" and "mung1112/02".
 
 ```{r LSD_2_Sampling_Variance}
-Tcrit <- 1.697 # 0.05 and DFw = 30
+Tcrit <- 2.042
 
@@
 # subset data by those which describe the Yield error with standard deviation
-Trials <- PM_MB_means %>%
+Trials <- PM_MB_dat %>%
    filter(Y_error_type == "stdev") %>%
    select(trial_ref) %>%
-   distinct()
+   pull()
 
-# calculate the Sampling variance from the standard deviation
-# standard error of the mean equals the standard deviation divided by the square
-#  root of the number of samples
-# Sv <- sem^2 <- stdev/sqrt(n)
-# Sampling variance equals the square of the standard error.
-# Sv <- (stdev/sqrt(n))^2
+PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,"yield_error"] <- 
+   PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,"yield_error"]^2
 
-# Therefore
+PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,]$Y_error_type <-
+   "SamplingVariance"
 
-for (j in seq_along(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error)) {
-   if (j == 1) {
-      Sv <-
-         vector(length = length(PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error))
-   }# create empty vector at first iteration with length of j
-
-   Sv[j] = (PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error[j]) ^ 2
-}
-
-# and replacing the values in the dataset
-PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error <-
-   Sv
-PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$Y_error_type <-
-   "SamplingVariance"
 ```
@@
 ```{r Var_mean_sqaures}
-# redefine sample variance calculated from mean square
-PM_MB_means$vi <-
-   PM_MB_means$Y_Msquare /
-   (PM_MB_means$n)
-
-PM_MB_means %>%
-   ggplot(aes(x = grain_yield.t.ha., y = vi)) +
+PM_MB_dat %>%
+   ggplot(aes(x = grain_yield.t.ha., y = yield_error)) +
    geom_point()
 ```
+No association between yield and sample variance, this might be due to the unpredictable nature of mungbeans.
 
-We see here that the sample variance generally decreases or has no association with the grain yield.
-This might be due to the unpredictable nature of mungbeans, however going forward we will use mean squares, which defines between trial variation and is the more generic error term.
+Lets look at the association between mean squares and yield to see if there is a more typical association between yield and variance.
 
 ```{r Var_MeanSquarePlot}
-PM_MB_means %>%
-   ggplot(aes(x = grain_yield.t.ha., y = Y_Msquare)) +
+PM_MB_dat %>%
+   ggplot(aes(x = grain_yield.t.ha., y = Y_Msquare/replicates)) +
    geom_point()
+PM_MB_dat[is.na(PM_MB_dat$Y_Msquare),]
+
 ```
 
-## Reduce data set to required variables
+## Classifying fungicide treatment
 
-Let's tidy up the data set into a data frame of only the variables, which are required for the analysis.
-
-First remove the irrelevant columns/variables.
-Then calculate fungicide application timing variables relative to the first sign of disease.
-Entries with `NA` in the grain yield or powdery mildew severity are also removed from the data.
+First we need to calculate the time between the first sign of disease and the fungicide treatments.
 
 ```{r clustered_fungicide_applications}
-source("R/slimming_PM_dat.R") # see R script for the code, which reduces the data.
-
-slim_PM_dat %<>%
+PM_MB_dat %<>%
    mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
    mutate(fungicide_timing_2 = fungicide_application_2 - fungicide_application_1) %>%
-   mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2) %>%
-   filter(!is.na(grain_yield.t.ha)) %>%
-   filter(!is.na(PM_final_severity))
+   mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2)
+
 ```
 
-### Cluster fungicide applications
-
-We are going to define 'fungicide application timing' as a categorical variable, relative to the first sign of powdery mildew.
+To ensure sufficient number of replicates, we will bin the continuous variable into three categorical variables relating to when the first fungicide application was made.
 
@@
    - **Late**: First fungicide application was four or more days after first sign of disease being observed.
-Follow up fungicide applications (cluster_2 and cluster_3) were also categorised as either early, recommended or late.
 
-```{r cluster}
-slim_PM_dat %<>%
-   mutate(
-      cluster_1 = case_when(
-         fungicide_timing_1 < 0 ~ "Early",
-         fungicide_timing_1 >= 0 &
-            fungicide_timing_1 < 4 ~ "Recommended",
-         TRUE ~ "Late"
-      )
-   ) %>%
-   mutate(
-      cluster_2 = case_when(
-         is.na(fungicide_timing_2) ~ NA_character_,
-         fungicide_timing_2 < 13 ~ "Early",
-         fungicide_timing_2 >= 13 &
-            fungicide_timing_2 < 17 ~ "Recommended",
-         TRUE ~ "Late"
-      )
-   ) %>%
-   mutate(
-      cluster_3 = case_when(
-         fungicide_timing_3 < 14 ~ "Early",
-         is.na(fungicide_timing_3) ~ NA_character_,
-         TRUE ~ "Recommended"
-      )
-   )
+The number of sprays need also be defined.
+
+```{r}
+data.frame(TreatmentName = c("Early", "Recommended", "Late", "EarlyPlus", "RecommendedPlus", "LatePlus"),
+           n_sprays = rep(c("Single", "Two - Three"), each = 3),
+           DaysRelativeToFirstSign = c("Prior to first sign of Powdery Mildew",
+                                       "1 - 3 days after first sign of Powdery Mildew",
+                                       "7 - 8 days after first sign of Powdery Mildew"))%>%
+   kable()
 ```
 
-Let's look at these clusters to see where we have the most degrees of freedom.
-
-```{r cluster_clusters}
-clusters <-
-   unique(slim_PM_dat[c("cluster_1", "cluster_2", "cluster_3")])
-
-for (i in 1:nrow(clusters)) {
-   if (i == 1) {
-      clusters$n <- NA
-      clusters$n_x_trial <- NA
-   }
-
-   clusters[i, "n"] <-
-      nrow(slim_PM_dat[same(slim_PM_dat$cluster_1, clusters[i, "cluster_1"]) &
-                          same(slim_PM_dat$cluster_2, clusters[i, "cluster_2"]) &
-                          same(slim_PM_dat$cluster_3, clusters[i, "cluster_3"]),])
-
-   clusters[i, "n_x_trial"] <-
-      length(unique(slim_PM_dat[same(slim_PM_dat$cluster_1, clusters[i, "cluster_1"]) &
-                                   same(slim_PM_dat$cluster_2, clusters[i, "cluster_2"]) &
-                                   same(slim_PM_dat$cluster_3, clusters[i, "cluster_3"]),
-                                "trial_ref"]))
-
-}
-
-knitr::kable(clusters)
-```
-
-From this we can see that there are 16 different cluster combinations, which would make the analysis too difficult. We will reduce this to 6 levels within one variable.
-
-Single sprays of either:
-
-   a) early,
-
-   b) recommended timing,
-
-   c) late.
-
-Two or more sprays where the first spray was either:
-
-   d) early,
-
-   e) recommended timing,
-
-   f) late.
-
 ```{r simple_clusters}
-slim_PM_dat <- slim_PM_dat %>%
+PM_MB_dat <- PM_MB_dat %>%
    mutate(
@@
 
-slim_PM_dat[slim_PM_dat$fungicide_ai == "control",
+PM_MB_dat[PM_MB_dat$fungicide_ai == "control",
             c(
@@
 ```{r tableSprayManagement}
-table(slim_PM_dat$spray_management)
+table(PM_MB_dat$spray_management)
 ```
@@
 ```{r simpler_clusters_remove}
-slimmer_PM_dat <-
-   slim_PM_dat[slim_PM_dat$spray_management != "Early_plus", ]
+PM_MB_dat <-
+   PM_MB_dat %>%
+   filter(spray_management != "Early_plus")
 ```
@@
 
+## Trial factor
+We have a number of variable which could introduce variation in our analysis. 
+We will combine these variables into a single variable called `trial` which will help us define the between trial variation.
+
+```{r define_trial}
+PM_MB_dat <-
+   PM_MB_dat %>%
+   mutate(trial = paste(trial_ref, year, location, host_genotype,
+                        row_spacing, sep = "_")) %>%
+   select(trial_ref, trial, everything())
+```
+
 ## Test dose effect
@@
 Earlier we noted there were different doses of propiconazole, which might influence our analysis.
-Let's check this by comparing a linear mixed effect model including and excluding dose.
+Let's add the dose variable to the `trial` variable then compare linear mixed effect models including and excluding dose in the trial variable.
 We already have a factor breaking down the dose in the `trial` variable.
@@
 
+```{r define_Dose}
+table(PM_MB_dat$dose_ai.ha)
+
+PM_MB_dat <- 
+   PM_MB_dat %>%
+   mutate(dose = case_when(
+      dose_ai.ha == 0 ~ "control",
+      dose_ai.ha <= 70 ~ "lowDose",
+      dose_ai.ha > 70 ~ "highDose",
+      TRUE ~ NA_character_
+   ))
+
+```
+
 ```{r dose_test}
-slimmer_PM_dat$trial_noDose <- paste(slimmer_PM_dat$trial_ref, slimmer_PM_dat$year,
-                 slimmer_PM_dat$location,slimmer_PM_dat$host_genotype,
-                 slimmer_PM_dat$row_spacing,sep = "_")
+PM_MB_dat <-
+   PM_MB_dat %>%
+    mutate(trial_dose = paste(trial_ref, year, location, host_genotype,
+                        row_spacing,dose , sep = "_"))
 
-cbind(Dose = head(slimmer_PM_dat$trial),
-      NoDose = head(slimmer_PM_dat$trial_noDose)) %>%
+cbind(NoDose = head(PM_MB_dat$trial),
+      Dose = head(PM_MB_dat$trial_dose)) %>%
    kable()
@@
 ```{r dose_lmer}
-m1 <-
-   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
+m_noDose <-
+   lmer(log(grain_yield.t.ha. * 1000) ~ factor(spray_management) +
            (1 | trial),
-        data = slimmer_PM_dat)
+        data = PM_MB_dat)
 
-m2 <-
-   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
-           (1 | trial_noDose),
-        data = slimmer_PM_dat)
+m_dose <-
+   lmer(log(grain_yield.t.ha. * 1000) ~ factor(spray_management) +
+           (1 | trial_dose),
+        data = PM_MB_dat)
 
-anova(m1, m2)
+anova(m_noDose, m_dose)
 ```
 
-Using the model without dose produces a lower AIC, however we should accept the data with dose as there is a significant difference between the models and we should accept the more complicated model `m1`.
-We will retain dose as a variable inside the `trial` factor.
+Using the model without dose produces a lower AIC and we find no significant difference between models.
+We will not use dose as a defining variable in `trial`.
 
+Remove columns which are not needed
 ```{r saveDat}
-slimmer_PM_dat <-
-   slimmer_PM_dat[, colnames(slimmer_PM_dat) != "trial_noDose"] #remove second trial column
+PM_MB_dat <-
+   PM_MB_dat %>%
+   select(-c(trial_dose,fungicide_timing_1,fungicide_timing_2, fungicide_timing_3, 
+             dose, fungicide_application_4, fungicide_application_5, fungicide_application_6,
+             fungicide_application_7)) 
 ```
-
-## Disease pressure factor
-
-We may wish to investigate the impact of spray management in mitigating the yield loss through the effect on the disease pressure.
-We will set a categorical variable to indicate the amount of disease pressure in the trial, which will be evaluated on the control plot.
-We will create two categories, `lowD` and `highD`.
-We will use the median `AUDPC` to separate the trials into these two groups.
-
-```{r DiseasePressure}
-slimmer_PM_dat$D_pres <- NA_character_
-
-Trial_Dpress <- slimmer_PM_dat %>%
-   group_by(trial_ref) %>%
-   filter(fungicide_ai == "control") %>%
-   summarise(AUDPC_C = mean(AUDPC_m, na.rm = TRUE))
-
-median_AUDPC <-
-   median(as.vector(Trial_Dpress$AUDPC_C), na.rm = TRUE)
-median_AUDPC
-
-sort(Trial_Dpress$AUDPC_C)
-
-for (i in unique(slimmer_PM_dat$trial_ref)) {
-   if (is.na(Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"])) {
-      next()
-   }
-
-   if (Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"] < median_AUDPC)
-   {
-      slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <- "lowD"
-   } else{
-      if (Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"] >= median_AUDPC) {
-         slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <- "highD"
-      } else{
-         slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <-
-            NA_character_
-      }
-   }
-}
-```
-
-Let's have a quick look to examine whether trials with high disease pressure sustain a greater yield loss.
-
-```{r plot_disease_pressure}
-slimmer_PM_dat %>%
-   ggplot(aes(x = D_pres, y = grain_yield.t.ha))+
-   geom_boxplot() +
-   xlab("Disease pressure") +
-   ylab("Grain yield (t/ha)")
-```
-
-From this plot we see that in the trials with high disease pressure tended to produce lower yields. 
-There are `r length(unique(slimmer_PM_dat[is.na(slimmer_PM_dat$D_pres),"trial_ref"]))` trials that contained no data for AUDPC and thus produced `NA` values.
 
@@
 However one of the locations has `NA` as the row spacing.
+```{r}
+PM_MB_dat%>%
+   filter(is.na(row_spacing))%>%
+   select(trial_ref,year, location, row_spacing,spray_management,host_genotype, fungicide_ai)
+```
+
 For now let's assign the most used row spacing of 0.33 m as an approximation so the model can analyse this as a continuous variable. 
@@
 ```{r assign_row_spacing_missing}
-slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),]
-slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),"row_spacing"] <- 0.33
+PM_MB_dat[is.na(PM_MB_dat$row_spacing),"row_spacing"] <- 0.33
+```
 
-write.csv(slimmer_PM_dat, file = here("cache/slimmer_PM_clusterdat.csv"), row.names = FALSE)
+# Perhaps move below to post analysis, analysis
+
+### Mungbeans age and yield saved
+
+The time at which powdery mildew infects in the seasons and the age of the plant might affect the AUDPC and the loss in yield.
+Let's have a look at the age of each trial when powdery mildew infected it.
+We will use the difference between `planting_date` and `first_sign_disease` as a proxy for crop maturity when it became infected.
+
+```{r age_andYield}
+dat1 <- PM_MB_dat %>%
+   mutate(days2PM = first_sign_disease - planting_date) %>%
+   arrange(desc(days2PM)) %>%
+   select(
+      trial_ref,
+      year,
+      location,
+      spray_management,
+      days2PM,
+      grain_yield.t.ha,
+      yield_gain,
+      prop_yield_gain,
+      AUDPC_m,
+      D_pres,
+      PM_final_severity
+   )
+dat1
 ```
+
+From these trials I am most interested in the experiments that directly compare `Recommended` with `Recommended_P_plus` and/or `Late` with `Late_plus`. 
+Therefore I will not inspect, `AM1304` (Marys Mount), which only trialled an early, prophylactic spray.
+
+We can see that the crops which were likely the most mature, did not show large yield gains, in particular:
+
+   * Hermitage 2019  
+   * Premer  
+   * Goolhi  
+   * Millmerran
+
+Let's look at this in a quick box plot. 
+We will only look at trials where powdery mildew set in 60 days after planting, when the physiological maturity was likely flowering.
+
+```{r ageBoxPlot}
+dat1 %>%
+   filter(days2PM >= 60) %>%
+   filter(spray_management != "control" &
+             trial_ref != "AM1304") %>%
+   group_by(trial_ref, spray_management) %>%
+   ggplot(aes(x = spray_management, y = yield_gain, colour = trial_ref)) +
+   geom_boxplot() +
+   scale_fill_usq() +
+   geom_hline(yintercept = 0)
+```
+
+We can see in these experiments five experiments there is clearly no benefit to applying a second fungicide application given the values of the recommended _plus treatment were predominantly lower than zero.
+
+For completeness let's test this with powdery mildew infection commencing 40 - 60 days after planting, instead of greater than 60.
+
+```{r PM40_2_59_days}
+dat1 %>%
+   filter(days2PM < 60 &
+             days2PM >= 40) %>%
+   filter(spray_management != "control") %>%
+   group_by(trial_ref, spray_management) %>%
+   ggplot(aes(x = spray_management, y = yield_gain, colour = trial_ref)) +
+   geom_boxplot() +
+   scale_fill_usq() +
+   geom_hline(yintercept = 0)
+```
+
+We can see here all four experiments benefited, on average, from more than one spray.
+
+Let's estimate the age of the crop based on crop maturity observations, we will use the `PM_MB_dat` which include some observations of crop maturity.
+
+```{r whatAreTheAges}
+dat2 <- PM_MB_dat %>%
+   mutate(
+      flower = lubridate::ymd(flowering_date) - lubridate::ymd(planting_date),
+      pod = lubridate::ymd(pod_fill_date) - lubridate::ymd(planting_date),
+      late_pod = lubridate::ymd(mid_late_pod_fill) - lubridate::ymd(planting_date)
+   ) %>%
+   select(location, year, flower, pod, late_pod) %>%
+   distinct() %>%
+   arrange(desc(flower))
+
+index1 <-
+   apply(dat2, 1 , function(X)
+      ! all(is.na(X[c("flower", "pod", "late_pod")])))
+
+dat2[index1,]
+as.double(mean(dat2[index1, "flower"], na.rm = TRUE))
+as.double(mean(dat2[index1, "pod"], na.rm = TRUE))
+as.double(mean(dat2[index1, "late_pod"], na.rm = TRUE))
+```
+
+We can see that flowering and podding can be variable, and depend on the cumulative degree days.
+However, on average flowering starts `r as.double(mean(dat2[index1,"flower"], na.rm = TRUE))` days after sowing, podding starts `r as.double(mean(dat2[index1,"pod"], na.rm = TRUE))`, and late podding `r as.double(mean(dat2[index1,"late_pod"], na.rm = TRUE))`.

### 2020-08-31 04_MetaAnalysis.Rmd
Rename files for order in bookdown Rename importData file. maybe delete later

@@
 ggplot(slimmer_PM_dat, aes(x = as.factor(year), fill = spray_management)) +
-   geom_bar(position = "dodge2") +
+   geom_bar(position = position_dodge2(width = 0.9, preserve = "single")) +
    scale_fill_usq(name = "Spray Management") +
@@
 ```
-<!-- I don't like this graph, it is hard to read given that different widths don't translate to anything meaningful -->
 
@@
    col.multiarm = usq_cols("support turquiose"),
-   pos.number.of.studies = 0.5
+   pos.number.of.studies = 0.4
 )
@@
 ```{r Save_meta_data, eval=FALSE}
-save(dat1, efficacy, slimmer_PM_dat, PM_mv, YieldContrasts,contrast_Ssum,file =
-        here("cache/Meta-analysisData.Rdata"))
+save(dat1, efficacy, slimmer_PM_dat, PM_mv, YieldContrasts, contrast_Ssum, 
+     file = here("cache/Meta-analysisData.Rdata"))
 ```
-
-#### Powdery mildewMBM comparison -- Delete
-One aspect we would like to consider is how the results of this meta-analysis compares to how the PowderyMildewMBM estimates the effect of fungicide applications on grain yields.
-Below we create a data frame of the mitigation factors for each spray scenario so we can compare them to the outcomes of the meta-analysis.
-```{r compare2PowderyMildewMDM}
-
-PMBM <- 
-   data.frame(Sprays = c(rep(1,20), rep(2,20)),
-              Disease = rep(c(rep("NotPresent", 5),
-                          rep("LowerCanopy", 5),
-                          rep("MidCanopy", 5),
-                          rep("UpperCanopy", 5)),2),
-              CropMaturity = rep(c("Vegetative", "Budding", "Flowering",
-                                   "EarlyPod", "LatePod"), 8),
-              mitigation = c(0.57, 0.855, 0.95,0.95,0.95,
-                             0.45995, 0.52919,0.5530,0.390,0.1642,
-                             0.291258,0.351051, 0.2454,0.1409,0.4717,
-                             0,0.059597,0.093034,0.0682476,0.0215584,
-                             0.95,0.95,0.95,0.95,0.95,
-                             0.766588,0.6991,0.55042,0.390056,0.1642,
-                             0.485429,0.390,0.2454,0.140904,0.0471684,
-                             0.0791,0.086068,0.093034,0.0682476,0.0215584))
-
-# what is the mean age of the plant in our data when disease first occurs and we apply the first spray?
-source("R/import_data.R")
-PM_MB_dat <- import_data()
-mean(PM_MB_dat$first_sign_disease - PM_MB_dat$planting_date, na.rm =TRUE) # 46.3 days (which is when the plant is flowering)
-
-#What proportion of the yield was saved?
-1 - (coef(PM_mv)[1] /(coef(PM_mv)[1] + coef(PM_mv)[3]))
-1- (coef(PM_mv)[1] /(coef(PM_mv)[1] + coef(PM_mv)[4]))
-
-PMBM %>%
-   filter(CropMaturity == "Flowering")
-
-```
-To to a better comparison I need to know how the mitigation factor is calculated with the estimated yields.

### 2020-08-31 05_Post-hoc_analysis_Investigation.Rmd
Rename files for order in bookdown Rename importData file. maybe delete later

--- 2020-08-31 03_Prep_data.Rmd
@@
-# Prepare data for meta-analysis
+# Post-hoc analysis and ploting
 
-## Set environment and import data
-
-```{r load_libraries, include=FALSE}
+```{r PHA_Libraries, include=FALSE, message=FALSE}
 if (!require("pacman"))
    install.packages("pacman")
-pacman::p_load(tidyverse, kableExtra, agricolae, lme4, here)
+pacman::p_load(tidyverse,
+               kableExtra,
+               here)
+
 if (!require("theme.usq"))
@@
 )
+load("cache/PrepData.Rdata")
 ```
-
-```{r import_data}
-load("cache/PreliminaryData.Rdata")
-source(here("R/same.R")) # matches each element of a vector and does not return NAs
-```
-
-## Subset to Trials containing DMI fungicides
-
-```{r filterDMI_trials}
-DMI_Trials <- 
-   PM_MB_dat %>%
-   filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole")%>%
-   distinct(trial_ref) %>%
-   pull()
-
-PM_MB_dat <- 
-   PM_MB_dat[PM_MB_dat$trial_ref %in% DMI_Trials,]
-```
-
-Now remove any non-DMI treatments or controls
-```{r}
-PM_MB_dat <- 
-   PM_MB_dat %>%
-   filter(fungicide_ai == "control" |
-             fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole")
-```
-
-## Standardising sample variance  
-Meta-analyses use variance from the data to calculate the effect sizes.
-The type of variance needs to be the same across all the data incorporated in the meta-analysis.
-
-We are narrowing the meta-analysis to only include treatments using demethylation inhibitors, tebuconazole and propiconazole.
-Let's look at what type of statistical error was reported for the trials that used these fungicides.
-
-```{r variance_types}
-PM_MB_dat %>%
-   filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole") %>%
-   group_by(trial_ref, location, year , Y_error_type) %>%
-   summarise(DMI_treatments = length(Y_error_type), .groups = 'drop') %>%
-   arrange(Y_error_type) %>%
-   kable(caption = "Number of treatments for each trial and the error type reported",
-         align = "c") %>%
-   footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
-```
-
-The experiment summaries report either standard deviation, least square differences. 
-First we will convert LSD and standard deviation to sample variance.
-
-### Converting least-squares to sample variance
-
-First let's get a list the of trials that reported LSD.
-
-```{r all_LSD_trials}
-Trials <- PM_MB_dat %>%
-   filter(Y_error_type == "lsd (P=0.05)") %>%
-   select(trial_ref) %>%
-   distinct()
-Trials
-```
-
-Let's use this list of trials to subset the data and calculate sampling variances.
-
-We will follow the method of converting 'least square differences' (LSD) to sampling variance reported by [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
-
-```{r LSD_2_Sampling_Variance}
-Tcrit <- 2.042
-
-for (i in Trials$trial_ref) {
-   DFw <-
-      sum(PM_MB_dat[PM_MB_dat$trial_ref == i, ]$replicates) -
-      length(PM_MB_dat[PM_MB_dat$trial_ref == i, ]$replicates) # degrees of freedom within groups
-
-   LSD <-
-      PM_MB_dat[PM_MB_dat$trial_ref == i, ]$yield_error[1]
-
-   V_yield <-
-      (PM_MB_dat[PM_MB_dat$trial_ref == i, ]$replicates[1] * 
-          (LSD / Tcrit) ^ 2) / 2 
-   # method - Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
-
-   for (j in seq_along(PM_MB_dat[PM_MB_dat$trial_ref == i,]$replicates)) {
-      if (j == 1) {
-         Sv <-
-            vector(length = length(PM_MB_dat[PM_MB_dat$trial_ref == i,]$replicates))
-      } # reset Sv vector if this is the first loop
-
-      Sv[j] = V_yield /
-         PM_MB_dat[PM_MB_dat$trial_ref == i,]$replicates[j]
-
-   }
-
-   # Replace the values in the dataset
-   PM_MB_dat[PM_MB_dat$trial_ref == i,]$yield_error <-
-      Sv
-   PM_MB_dat[PM_MB_dat$trial_ref == i,]$Y_error_type <-
-      "SamplingVariance"
-}
-```
-
-### Converting standard deviation to sample variance
-
-Now to estimate the variance from the standard deviation.
-
-```{r stdev2SampVariance}
-# subset data by those which describe the Yield error with standard deviation
-Trials <- PM_MB_dat %>%
-   filter(Y_error_type == "stdev") %>%
-   select(trial_ref) %>%
-   pull()
-
-PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,"yield_error"] <- 
-   PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,"yield_error"]^2
-
-PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,]$Y_error_type <-
-   "SamplingVariance"
-
-```
-
-### Check variance of data-set
-Our data currently uses sample variance to define the yield error.
-We should expect that when yield increases so does the variance.
-Let's quickly plot this to check.
-
-```{r Var_mean_sqaures}
-PM_MB_dat %>%
-   ggplot(aes(x = grain_yield.t.ha., y = yield_error)) +
-   geom_point()
-```
-No association between yield and sample variance, this might be due to the unpredictable nature of mungbeans.
-
-Lets look at the association between mean squares and yield to see if there is a more typical association between yield and variance.
-
-```{r Var_MeanSquarePlot}
-PM_MB_dat %>%
-   ggplot(aes(x = grain_yield.t.ha., y = Y_Msquare/replicates)) +
-   geom_point()
-PM_MB_dat[is.na(PM_MB_dat$Y_Msquare),]
-
-```
-
-## Classifying fungicide treatment
-
-First we need to calculate the time between the first sign of disease and the fungicide treatments.
-
-```{r clustered_fungicide_applications}
-PM_MB_dat %<>%
-   mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
-   mutate(fungicide_timing_2 = fungicide_application_2 - fungicide_application_1) %>%
-   mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2)
-
-```
-
-To ensure sufficient number of replicates, we will bin the continuous variable into three categorical variables relating to when the first fungicide application was made.
-
-These categorical variables are named:
-
-   - **Early**: First fungicide application was prior to first sign of disease.
-
-   - **Recommended**: First fungicide application was applied on the day powdery mildew was observed, or within three days of first sign.
-
-   - **Late**: First fungicide application was four or more days after first sign of disease being observed.
-
-The number of sprays need also be defined.
-
-```{r}
-data.frame(TreatmentName = c("Early", "Recommended", "Late", "EarlyPlus", "RecommendedPlus", "LatePlus"),
-           n_sprays = rep(c("Single", "Two - Three"), each = 3),
-           DaysRelativeToFirstSign = c("Prior to first sign of Powdery Mildew",
-                                       "1 - 3 days after first sign of Powdery Mildew",
-                                       "7 - 8 days after first sign of Powdery Mildew"))%>%
-   kable()
-```
-
-```{r simple_clusters}
-PM_MB_dat <- PM_MB_dat %>%
-   mutate(
-      spray_management = case_when(
-         fungicide_timing_1 < 0 &
-            is.na(fungicide_application_2) &
-            is.na(fungicide_application_3) ~ "Early",
-         fungicide_timing_1 >= 0 &
-            fungicide_timing_1 < 4 &
-            is.na(fungicide_application_2) &
-            is.na(fungicide_application_3) ~ "Recommended",
-         fungicide_timing_1 >= 4 &
-            is.na(fungicide_application_2) &
-            is.na(fungicide_application_3) ~ "Late",
-         fungicide_timing_1 < 0 &
-            !is.na(fungicide_application_2) ~ "Early_plus",
-         fungicide_timing_1 >= 0 &
-            fungicide_timing_1 < 4 &
-            !is.na(fungicide_application_2) ~ "Recommended_plus",
-         fungicide_timing_1 >= 4 &
-            !is.na(fungicide_application_2) ~ "Late_plus",
-         TRUE ~ "Other"
-      )
-   )
-
-PM_MB_dat[PM_MB_dat$fungicide_ai == "control",
-            c(
-               "fungicide_timing_1",
-               "fungicide_timing_2",
-               "fungicide_timing_3",
-               "spray_management"
-            )] <- "control"
-```
-
-Now to view the number break-down of the `spray_management` treatments
-
-```{r tableSprayManagement}
-table(PM_MB_dat$spray_management)
-```
-
-There are few 'Early_plus' treatments, these treatments therefore will have too few comparisons with other treatments in the meta-analysis to provide accurate results.
-Therefore we will remove 'Early_plus' from the analysis.
-
-```{r simpler_clusters_remove}
-PM_MB_dat <-
-   PM_MB_dat %>%
-   filter(spray_management != "Early_plus")
-```
-
-****
-
-## Trial factor
-We have a number of variable which could introduce variation in our analysis. 
-We will combine these variables into a single variable called `trial` which will help us define the between trial variation.
-
-```{r define_trial}
-PM_MB_dat <-
-   PM_MB_dat %>%
-   mutate(trial = paste(trial_ref, year, location, host_genotype,
-                        row_spacing, sep = "_")) %>%
-   select(trial_ref, trial, everything())
-```
-
-## Test dose effect
-
-Earlier we noted there were different doses of propiconazole, which might influence our analysis.
-Let's add the dose variable to the `trial` variable then compare linear mixed effect models including and excluding dose in the trial variable.
-We already have a factor breaking down the dose in the `trial` variable.
-Let's make a new one without dose.
-
-```{r define_Dose}
-table(PM_MB_dat$dose_ai.ha)
-
-PM_MB_dat <- 
-   PM_MB_dat %>%
-   mutate(dose = case_when(
-      dose_ai.ha == 0 ~ "control",
-      dose_ai.ha <= 70 ~ "lowDose",
-      dose_ai.ha > 70 ~ "highDose",
-      TRUE ~ NA_character_
-   ))
-
-```
-
-```{r dose_test}
-PM_MB_dat <-
-   PM_MB_dat %>%
-    mutate(trial_dose = paste(trial_ref, year, location, host_genotype,
-                        row_spacing,dose , sep = "_"))
-
-cbind(NoDose = head(PM_MB_dat$trial),
-      Dose = head(PM_MB_dat$trial_dose)) %>%
-   kable()
-```
-
-Let's test the dose effect in a basic linear mixed effect model.
-
-```{r dose_lmer}
-m_noDose <-
-   lmer(log(grain_yield.t.ha. * 1000) ~ factor(spray_management) +
-           (1 | trial),
-        data = PM_MB_dat)
-
-m_dose <-
-   lmer(log(grain_yield.t.ha. * 1000) ~ factor(spray_management) +
-           (1 | trial_dose),
-        data = PM_MB_dat)
-
-anova(m_noDose, m_dose)
-```
-
-Using the model without dose produces a lower AIC and we find no significant difference between models.
-We will not use dose as a defining variable in `trial`.
-
-Remove columns which are not needed
-```{r saveDat}
-PM_MB_dat <-
-   PM_MB_dat %>%
-   select(-c(trial_dose,fungicide_timing_1,fungicide_timing_2, fungicide_timing_3, 
-             dose, fungicide_application_4, fungicide_application_5, fungicide_application_6,
-             fungicide_application_7)) 
-```
-
-## Row spacing
-
-We may want to consider row spacing in the trials.
-However one of the locations has `NA` as the row spacing.
-```{r}
-PM_MB_dat%>%
-   filter(is.na(row_spacing))%>%
-   select(trial_ref,year, location, row_spacing,spray_management,host_genotype, fungicide_ai)
-```
-
-For now let's assign the most used row spacing of 0.33 m as an approximation so the model can analyse this as a continuous variable. 
-If we decide to use the row_spacing column as a factor in the final model we will need to remove this approximation.
-
-```{r assign_row_spacing_missing}
-PM_MB_dat[is.na(PM_MB_dat$row_spacing),"row_spacing"] <- 0.33
-```
-
-# Perhaps move below to post analysis, analysis
 

### 2020-08-31 04_Prep_data.Rmd
Simplify prep data, focus on defining variables for meta-analysis Remove disease variables

@@
 
+Now remove any non-DMI treatments or controls
+```{r}
+PM_MB_dat <- 
+   PM_MB_dat %>%
+   filter(fungicide_ai == "control" |
+             fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")
+```
+
 ## Standardising sample variance  
@@
 We will follow the method of converting 'least square differences' (LSD) to sampling variance reported by [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
-A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted to select the T-crit value in the equation. 
-Our data contained 30 degrees of freedom which equates to a 'T-crit' value of 1.697.
-
-![Calculating sampling variance from mean squared error Paul et al. (2008)](Paul_etal_2008.PNG)
-
-`Tcrit` is the T critical value for which there is significant difference between two groups.
-This value is the same for both trials "mung1112/01" and "mung1112/02".
 
 ```{r LSD_2_Sampling_Variance}
-Tcrit <- 2.042 # 0.05 and DFw = 30
+Tcrit <- 2.042
 
@@
 
-## Reduce data set to required variables
+## Classifying fungicide treatment
 
-Let's tidy up the data set into a data frame of only the variables, which are required for the analysis.
-
-First remove the irrelevant columns/variables.
-Then calculate fungicide application timing variables relative to the first sign of disease.
-Entries with `NA` in the grain yield or powdery mildew severity are also removed from the data.
+First we need to calculate the time between the first sign of disease and the fungicide treatments.
 
 ```{r clustered_fungicide_applications}
-source("R/slimming_PM_dat.R") # see R script for the code, which reduces the data.
-
-slim_PM_dat %<>%
+PM_MB_dat %<>%
    mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
    mutate(fungicide_timing_2 = fungicide_application_2 - fungicide_application_1) %>%
-   mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2) %>%
-   filter(!is.na(grain_yield.t.ha)) %>%
-   filter(!is.na(PM_final_severity))
+   mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2)
+
 ```
 
-### Cluster fungicide applications
-
-We are going to define 'fungicide application timing' as a categorical variable, relative to the first sign of powdery mildew.
+To ensure sufficient number of replicates, we will bin the continuous variable into three categorical variables relating to when the first fungicide application was made.
 
@@
    - **Late**: First fungicide application was four or more days after first sign of disease being observed.
-Follow up fungicide applications (cluster_2 and cluster_3) were also categorised as either early, recommended or late.
+
+The number of sprays need also be defined.
 
 ```{r}
-data.frame(SprayTimingName = c("Early", "Recommended", "Late"),
-           DaysRelativeToFirstSign = c("Prior to first sign of PM",
-                                       "1 - 3 days after first sign of PM",
-                                       "7 - 8 days after first sign of PM"))%>%
+data.frame(TreatmentName = c("Early", "Recommended", "Late", "EarlyPlus", "RecommendedPlus", "LatePlus"),
+           n_sprays = rep(c("Single", "Two - Three"), each = 3),
+           DaysRelativeToFirstSign = c("Prior to first sign of Powdery Mildew",
+                                       "1 - 3 days after first sign of Powdery Mildew",
+                                       "7 - 8 days after first sign of Powdery Mildew"))%>%
    kable()
@@
 
-```{r cluster}
-slim_PM_dat %<>%
-   mutate(
-      cluster_1 = case_when(
-         fungicide_timing_1 < 0 ~ "Early",
-         fungicide_timing_1 >= 0 &
-            fungicide_timing_1 < 4 ~ "Recommended",
-         TRUE ~ "Late"
-      )
-   ) %>%
-   mutate(
-      cluster_2 = case_when(
-         is.na(fungicide_timing_2) ~ NA_character_,
-         fungicide_timing_2 < 13 ~ "Early",
-         fungicide_timing_2 >= 13 &
-            fungicide_timing_2 < 17 ~ "Recommended",
-         TRUE ~ "Late"
-      )
-   ) %>%
-   mutate(
-      cluster_3 = case_when(
-         fungicide_timing_3 < 14 ~ "Early",
-         is.na(fungicide_timing_3) ~ NA_character_,
-         TRUE ~ "Recommended"
-      )
-   )
-```
-
-Let's look at these clusters to see where we have the most degrees of freedom.
-
-```{r cluster_clusters}
-clusters <-
-   unique(slim_PM_dat[c("cluster_1", "cluster_2", "cluster_3")])
-
-for (i in 1:nrow(clusters)) {
-   if (i == 1) {
-      clusters$n <- NA
-      clusters$n_x_trial <- NA
-   }
-
-   clusters[i, "n"] <-
-      nrow(slim_PM_dat[same(slim_PM_dat$cluster_1, clusters[i, "cluster_1"]) &
-                          same(slim_PM_dat$cluster_2, clusters[i, "cluster_2"]) &
-                          same(slim_PM_dat$cluster_3, clusters[i, "cluster_3"]),])
-
-   clusters[i, "n_x_trial"] <-
-      length(unique(slim_PM_dat[same(slim_PM_dat$cluster_1, clusters[i, "cluster_1"]) &
-                                   same(slim_PM_dat$cluster_2, clusters[i, "cluster_2"]) &
-                                   same(slim_PM_dat$cluster_3, clusters[i, "cluster_3"]),
-                                "trial_ref"]))
-
-}
-
-knitr::kable(clusters)
-```
-
-From this we can see that there are 16 different cluster combinations, which would make the analysis too difficult. We will reduce this to 6 levels within one variable.
-
-Single sprays of either:
-
-   a) early,
-
-   b) recommended timing,
-
-   c) late.
-
-Two or more sprays where the first spray was either:
-
-   d) early,
-
-   e) recommended timing,
-
-   f) late.
-
 ```{r simple_clusters}
-slim_PM_dat <- slim_PM_dat %>%
+PM_MB_dat <- PM_MB_dat %>%
    mutate(
@@
 ```{r dose_lmer}
-m1 <-
-   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
+m_noDose <-
+   lmer(log(grain_yield.t.ha. * 1000) ~ factor(spray_management) +
            (1 | trial),
-        data = slimmer_PM_dat)
+        data = PM_MB_dat)
 
-m2 <-
-   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
-           (1 | trial_noDose),
-        data = slimmer_PM_dat)
+m_dose <-
+   lmer(log(grain_yield.t.ha. * 1000) ~ factor(spray_management) +
+           (1 | trial_dose),
+        data = PM_MB_dat)
 
-anova(m1, m2)
+anova(m_noDose, m_dose)
 ```
 
-Using the model without dose produces a lower AIC, however we should accept the data with dose as there is a significant difference between the models and we should accept the more complicated model `m1`.
-We will retain dose as a variable inside the `trial` factor.
+Using the model without dose produces a lower AIC and we find no significant difference between models.
+We will not use dose as a defining variable in `trial`.
 
+Remove columns which are not needed
 ```{r saveDat}
-slimmer_PM_dat <-
-   slimmer_PM_dat[, colnames(slimmer_PM_dat) != "trial_noDose"] #remove second trial column
+PM_MB_dat <-
+   PM_MB_dat %>%
+   select(-c(trial_dose,fungicide_timing_1,fungicide_timing_2, fungicide_timing_3, 
+             dose, fungicide_application_4, fungicide_application_5, fungicide_application_6,
+             fungicide_application_7)) 
 ```
-
-## Disease pressure factor
-
-We may wish to investigate the impact of spray management in mitigating the yield loss through the effect on the disease pressure.
-We will set a categorical variable to indicate the amount of disease pressure in the trial, which will be evaluated on the control plot.
-We will create two categories, `lowD` and `highD`.
-We will use the median `AUDPC` to separate the trials into these two groups.
-
-```{r DiseasePressure}
-slimmer_PM_dat$D_pres <- NA_character_
-
-Trial_Dpress <- slimmer_PM_dat %>%
-   group_by(trial_ref) %>%
-   filter(fungicide_ai == "control") %>%
-   summarise(AUDPC_C = mean(AUDPC_m, na.rm = TRUE))
-
-median_AUDPC <-
-   median(as.vector(Trial_Dpress$AUDPC_C), na.rm = TRUE)
-median_AUDPC
-
-write.csv(median_AUDPC, here("cache/median_AUDPC_C.csv"), row.names = FALSE)
-
-sort(Trial_Dpress$AUDPC_C)
-
-for (i in unique(slimmer_PM_dat$trial_ref)) {
-   if (is.na(Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"])) {
-      next()
-   }
-
-   if (Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"] < median_AUDPC)
-   {
-      slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <- "lowD"
-   } else{
-      if (Trial_Dpress[Trial_Dpress$trial_ref == i, "AUDPC_C"] >= median_AUDPC) {
-         slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <- "highD"
-      } else{
-         slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "D_pres"] <-
-            NA_character_
-      }
-   }
-}
-```
-
-Let's have a quick look to examine whether trials with high disease pressure sustain a greater yield loss.
-
-```{r plot_disease_pressure}
-slimmer_PM_dat %>%
-   ggplot(aes(x = D_pres, y = grain_yield.t.ha))+
-   geom_boxplot() +
-   xlab("Disease pressure") +
-   ylab("Grain yield (t/ha)")
-```
-
-From this plot we see that in the trials with high disease pressure tended to produce lower yields. 
-There are `r length(unique(slimmer_PM_dat[is.na(slimmer_PM_dat$D_pres),"trial_ref"]))` trials that contained no data for AUDPC and thus produced `NA` values.
 
@@
 ```{r assign_row_spacing_missing}
-slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),]
-slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),"row_spacing"] <- 0.33
-
-write.csv(slimmer_PM_dat, file = here("cache/slimmer_PM_clusterdat.csv"), row.names = FALSE)
+PM_MB_dat[is.na(PM_MB_dat$row_spacing),"row_spacing"] <- 0.33
 ```
 
-### Mungbeans age and yield saved
-
-The time at which powdery mildew infects in the seasons and the age of the plant might affect the AUDPC and the loss in yield.
-Let's have a look at the age of each trial when powdery mildew infected it.
-We will use the difference between `planting_date` and `first_sign_disease` as a proxy for crop maturity when it became infected.
-
-```{r age_andYield}
-dat1 <- slimmer_PM_dat %>%
-   mutate(days2PM = first_sign_disease - planting_date) %>%
-   arrange(desc(days2PM)) %>%
-   select(
-      trial_ref,
-      year,
-      location,
-      spray_management,
-      days2PM,
-      grain_yield.t.ha,
-      yield_gain,
-      prop_yield_gain,
-      AUDPC_m,
-      D_pres,
-      PM_final_severity
-   )
-dat1
+```{r saveData_PrepD}
+save(PM_MB_dat, file = here("cache/PrepData.Rdata"))
 ```
 
-From these trials I am most interested in the experiments that directly compare `Recommended` with `Recommended_P_plus` and/or `Late` with `Late_plus`. 
-Therefore I will not inspect, `AM1304` (Marys Mount), which only trialled an early, prophylactic spray.
-
-We can see that the crops which were likely the most mature, did not show large yield gains, in particular:
-
-   * Hermitage 2019  
-   * Premer  
-   * Goolhi  
-   * Millmerran
-
-Let's look at this in a quick box plot. 
-We will only look at trials where powdery mildew set in 60 days after planting, when the physiological maturity was likely flowering.
-
-```{r ageBoxPlot}
-dat1 %>%
-   filter(days2PM >= 60) %>%
-   filter(spray_management != "control" &
-             trial_ref != "AM1304") %>%
-   group_by(trial_ref, spray_management) %>%
-   ggplot(aes(x = spray_management, y = yield_gain, colour = trial_ref)) +
-   geom_boxplot() +
-   scale_fill_usq() +
-   geom_hline(yintercept = 0)
-```
-
-We can see in these experiments five experiments there is clearly no benefit to applying a second fungicide application given the values of the recommended _plus treatment were predominantly lower than zero.
-
-For completeness let's test this with powdery mildew infection commencing 40 - 60 days after planting, instead of greater than 60.
-
-```{r PM40_2_59_days}
-dat1 %>%
-   filter(days2PM < 60 &
-             days2PM >= 40) %>%
-   filter(spray_management != "control") %>%
-   group_by(trial_ref, spray_management) %>%
-   ggplot(aes(x = spray_management, y = yield_gain, colour = trial_ref)) +
-   geom_boxplot() +
-   scale_fill_usq() +
-   geom_hline(yintercept = 0)
-```
-
-We can see here all four experiments benefited, on average, from more than one spray.
-
-Let's estimate the age of the crop based on crop maturity observations, we will use the `PM_MB_dat` which include some observations of crop maturity.
-
-```{r whatAreTheAges}
-dat2 <- PM_MB_dat %>%
-   mutate(
-      flower = lubridate::ymd(flowering_date) - lubridate::ymd(planting_date),
-      pod = lubridate::ymd(pod_fill_date) - lubridate::ymd(planting_date),
-      late_pod = lubridate::ymd(mid_late_pod_fill) - lubridate::ymd(planting_date)
-   ) %>%
-   select(location, year, flower, pod, late_pod) %>%
-   distinct() %>%
-   arrange(desc(flower))
-
-index1 <-
-   apply(dat2, 1 , function(X)
-      ! all(is.na(X[c("flower", "pod", "late_pod")])))
-
-dat2[index1,]
-as.double(mean(dat2[index1, "flower"], na.rm = TRUE))
-as.double(mean(dat2[index1, "pod"], na.rm = TRUE))
-as.double(mean(dat2[index1, "late_pod"], na.rm = TRUE))
-```
-
-We can see that flowering and podding can be variable, and depend on the cumulative degree days.
-However, on average flowering starts `r as.double(mean(dat2[index1,"flower"], na.rm = TRUE))` days after sowing, podding starts `r as.double(mean(dat2[index1,"pod"], na.rm = TRUE))`, and late podding `r as.double(mean(dat2[index1,"late_pod"], na.rm = TRUE))`.
+# Perhaps move below to post analysis, analysis

### 2020-08-31 03_Prep_data.Rmd
Rename file

@@
 
-## Subset to Trials containing DMI fungicides
+## Subset to trials containing DMI fungicides
 
@@
 ```
+
+*****
 
@@
 ```
+
 No association between yield and sample variance, this might be due to the unpredictable nature of mungbeans.
@@
    geom_point()
-PM_MB_dat[is.na(PM_MB_dat$Y_Msquare),]
 
@@
 
+There is a somewhat better trend here, if sampling variance from standard deviation proves unsuitable for the analysis we may compare models using variance from stdev and mean square for the best fit.
+
+*******
+
 ## Classifying fungicide treatment
 
-First we need to calculate the time between the first sign of disease and the fungicide treatments.
+First are going to calculate the time between the first sign of disease and the fungicide applications.
 
@@
 
-To ensure sufficient number of replicates, we will bin the continuous variable into three categorical variables relating to when the first fungicide application was made.
+To ensure sufficient number of replicates, we will bin the continuous variable into three categorical variables relating to when the first fungicide application was made, relative to the first sign of disease.
 
@@
    - **Early**: First fungicide application was prior to first sign of disease. 
-
    - **Recommended**: First fungicide application was applied on the day powdery mildew was observed, or within three days of first sign. 
-
    - **Late**: First fungicide application was four or more days after first sign of disease being observed.
@@
 
-```{r}
+```{r TreatmentTable}
 data.frame(TreatmentName = c("Early", "Recommended", "Late", "EarlyPlus", "RecommendedPlus", "LatePlus"),
@@
 
+*****
+
 ## Test dose effect
@@
 
+******
+
 ## Row spacing
@@
 
-# Perhaps move below to post analysis, analysis
-
-### Mungbeans age and yield saved
-
-The time at which powdery mildew infects in the seasons and the age of the plant might affect the AUDPC and the loss in yield.
-Let's have a look at the age of each trial when powdery mildew infected it.
-We will use the difference between `planting_date` and `first_sign_disease` as a proxy for crop maturity when it became infected.
-
-```{r age_andYield}
-dat1 <- PM_MB_dat %>%
-   mutate(days2PM = first_sign_disease - planting_date) %>%
-   arrange(desc(days2PM)) %>%
-   select(
-      trial_ref,
-      year,
-      location,
-      spray_management,
-      days2PM,
-      grain_yield.t.ha,
-      yield_gain,
-      prop_yield_gain,
-      AUDPC_m,
-      D_pres,
-      PM_final_severity
-   )
-dat1
+```{r saveData_PrepD}
+save(PM_MB_dat, file = here("cache/PrepData.Rdata"))
 ```
-
-From these trials I am most interested in the experiments that directly compare `Recommended` with `Recommended_P_plus` and/or `Late` with `Late_plus`. 
-Therefore I will not inspect, `AM1304` (Marys Mount), which only trialled an early, prophylactic spray.
-
-We can see that the crops which were likely the most mature, did not show large yield gains, in particular:
-
-   * Hermitage 2019  
-   * Premer  
-   * Goolhi  
-   * Millmerran
-
-Let's look at this in a quick box plot. 
-We will only look at trials where powdery mildew set in 60 days after planting, when the physiological maturity was likely flowering.
-
-```{r ageBoxPlot}
-dat1 %>%
-   filter(days2PM >= 60) %>%
-   filter(spray_management != "control" &
-             trial_ref != "AM1304") %>%
-   group_by(trial_ref, spray_management) %>%
-   ggplot(aes(x = spray_management, y = yield_gain, colour = trial_ref)) +
-   geom_boxplot() +
-   scale_fill_usq() +
-   geom_hline(yintercept = 0)
-```
-
-We can see in these experiments five experiments there is clearly no benefit to applying a second fungicide application given the values of the recommended _plus treatment were predominantly lower than zero.
-
-For completeness let's test this with powdery mildew infection commencing 40 - 60 days after planting, instead of greater than 60.
-
-```{r PM40_2_59_days}
-dat1 %>%
-   filter(days2PM < 60 &
-             days2PM >= 40) %>%
-   filter(spray_management != "control") %>%
-   group_by(trial_ref, spray_management) %>%
-   ggplot(aes(x = spray_management, y = yield_gain, colour = trial_ref)) +
-   geom_boxplot() +
-   scale_fill_usq() +
-   geom_hline(yintercept = 0)
-```
-
-We can see here all four experiments benefited, on average, from more than one spray.
-
-Let's estimate the age of the crop based on crop maturity observations, we will use the `PM_MB_dat` which include some observations of crop maturity.
-
-```{r whatAreTheAges}
-dat2 <- PM_MB_dat %>%
-   mutate(
-      flower = lubridate::ymd(flowering_date) - lubridate::ymd(planting_date),
-      pod = lubridate::ymd(pod_fill_date) - lubridate::ymd(planting_date),
-      late_pod = lubridate::ymd(mid_late_pod_fill) - lubridate::ymd(planting_date)
-   ) %>%
-   select(location, year, flower, pod, late_pod) %>%
-   distinct() %>%
-   arrange(desc(flower))
-
-index1 <-
-   apply(dat2, 1 , function(X)
-      ! all(is.na(X[c("flower", "pod", "late_pod")])))
-
-dat2[index1,]
-as.double(mean(dat2[index1, "flower"], na.rm = TRUE))
-as.double(mean(dat2[index1, "pod"], na.rm = TRUE))
-as.double(mean(dat2[index1, "late_pod"], na.rm = TRUE))
-```
-
-We can see that flowering and podding can be variable, and depend on the cumulative degree days.
-However, on average flowering starts `r as.double(mean(dat2[index1,"flower"], na.rm = TRUE))` days after sowing, podding starts `r as.double(mean(dat2[index1,"pod"], na.rm = TRUE))`, and late podding `r as.double(mean(dat2[index1,"late_pod"], na.rm = TRUE))`.

### 2020-08-31 03_Prep_data.Rmd
relocate code from meta analysis.rmd to Prep data. More wordsmithing and corrections

@@
 
-The experiment summaries report either standard deviation, least square differences. 
-First we will convert LSD and standard deviation to sample variance.
+The experiment summaries report either standard deviation or least square differences. 
+First we will convert LSD and standard deviation, then square the stdev to get sample variance.
 
@@
 
-No association between yield and sample variance, this might be due to the unpredictable nature of mungbeans.
+There seems to be no association between yield and sample variance, this might be due to the variability of mungbeans yields.
 
@@
 There is a somewhat better trend here, if sampling variance from standard deviation proves unsuitable for the analysis we may compare models using variance from stdev and mean square for the best fit.
+However, seven treatments are missing Mean square error.
+
+### Inspect variance and response for analysis
+
+Let's inspect the response variance `grain_yield.t.ha` to see if it is normally distributed. 
+In many cases a log transformation of the response variable improves the fit, due to the prevalence of log distributed data in nature.
+
+```{r}
+hist_usq(PM_MB_dat$grain_yield.t.ha, main = "Grain yield (t / ha)")
+hist_usq(log(PM_MB_dat$grain_yield.t.ha), main = "log(Grain yield (t / ha))")
+hist_usq(sqrt(PM_MB_dat$grain_yield.t.ha), main = "sqrt(Grain yield (t / ha))")
+hist_usq(PM_MB_dat$yield_gain, main = "Mean difference to control (t / ha)")
+```
+The distribution of data does not seem to be improved by transformation of the data.
+We will retain the continuous variable grain_yield.t.ha as the response.
+Mean differences won't be used as we are following the methodology of a ARM-based model, where mean differences are calculated following the meta-analysis.
+
+### Formatting Variance
+
+First let's check for any entries missing variance and remove them.
+
+```{r remove_studies}
+any(is.na(PM_MB_dat$yield_error))
+
+PM_MB_dat <-
+   PM_MB_dat[!is.na(PM_MB_dat$yield_error), ]
+
+PM_MB_dat$vi <- PM_MB_dat$yield_error
+```
+
+#### Calculate sample variance from mean square errors
+
+Currently our data frame has the sample variance calculated earlier, however we can approximate it using the mean squared error.
+Let's show the rational for our calculation and then add a secondary variance column (`vi2`).
+
+$MSE = Var + bias$
+
+However if our MSE was calculated from an unbiased sample we can assume $bias = 0$ and therefore:
+
+$MSE = Var$
+
+To calculate the sample variance (for each treatment in the trial) from the mean square error (Trial variance) all we need to do is divide by the number of samples in each treatment.
+We can show this because:
+$MSE = \frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n - 1}$
+Where the sum of squares for the fungicide treatment estimator ($y$) is divided by the number of fungicide treatments ($n$).
+
+The sample variance is a similar formula except we use $x$ instead of $y$.
+$S_{Var} = \frac{\sum_{x_1}^{x_n}(x_i - \overline{x})^2}{n - 1}$  
+$x$ being each observation within the experiment and $n$ being the number of samples in the whole trial.
+Therefore: 
+$S_{Var}\approx\frac{1}{n_{x}}\frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n_y - 1}$  
+Where $n_x$ is the number of samples within each treatment.
+
+As mentioned before there are a few treatments with no MSE (NAs), we can calculate it from the sample variance using this logic above.
+
+```{r EstMSE}
+PM_MB_dat[is.na(PM_MB_dat$Y_Msquare),"Y_Msquare"] <- 
+   PM_MB_dat %>%
+   filter(is.na(Y_Msquare))%>%
+   mutate(Y_Msquare = yield_error * replicates)%>%
+   pull(Y_Msquare)
+```
+
+Now to calculate the sample variance from MSE for all treatments.
+
+```{r MSE_2_SVar}
+#calculation when using log of response
+# PM_MB_dat$vi <-
+#    PM_MB_dat$Y_Msquare / (PM_MB_dat$n * PM_MB_dat$grain_yield.t.ha ^
+#                                   2)
+
+PM_MB_dat$vi2 <- 
+   PM_MB_dat$Y_Msquare / 
+   PM_MB_dat$replicates
+```
 
@@
 
+Now we have defined our treatments lets inspect plots to visualise how well the data compares across the trial years and locations?
+
+```{r table_of_nTreatments}
+# class spray_management as a factor and reorder them for the plot
+PM_MB_dat$spray_management <-
+   factor(PM_MB_dat$spray_management, rev(
+      c(
+         "control",
+         "Early",
+         "Recommended",
+         "Recommended_plus",
+         "Late",
+         "Late_plus"
+      )
+   ))
+
+ggplot(PM_MB_dat, aes(x = as.factor(year), fill = spray_management)) +
+   geom_bar(position = position_dodge2(width = 0.9, preserve = "single")) +
+   scale_fill_usq(name = "Spray Management") +
+   xlab("Year")
+
+kable(
+   table(PM_MB_dat$spray_management, PM_MB_dat$year),
+   align = rep('c', 8),
+   caption = "Which treatments and how many treatments are represented in each year"
+) %>%
+   kable_styling(
+      "striped",
+      fixed_thead = TRUE,
+      full_width = FALSE,
+      position = "center"
+   )
+
+```
+
+Treatments `Late_plus` and `Early` don't have very good comparison to other treatments.
+
+Let's visualise the spread of data in each treatments with box-plots.
+
+```{r treatment_means_plot}
+PM_MB_dat %>%
+   ggplot(
+      aes(
+         y = grain_yield.t.ha.,
+         x = spray_management,
+         fill = spray_management,
+         colour = spray_management
+      )
+   ) +
+   geom_boxplot(alpha = 0.25) +
+   geom_jitter(width = 0.1, alpha = 0.5) +
+   labs(x = "Spray management variable",
+        y = "Grain yield (t/Ha)",
+        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
+   theme(plot.title = element_text(hjust = 0.5)) +
+   geom_hline(yintercept = 0, linetype = 2) +
+   scale_fill_usq() +
+   scale_colour_usq() +
+   coord_flip() +
+   guides(fill = FALSE, color = FALSE)
+```
+
+There seems like little difference between the treatments, with exception of `Late_plus`.
+Let's do this plot again, but let's look at the proportional mean difference between each treatment and the no spray control for each study, this should reduce variation in yield due between trials.
+
+```{r plot_yieldProportion}
+PM_MB_dat %>%
+   filter(spray_management != "control") %>% 
+   ggplot(
+      aes(
+         y = prop_YG,
+         x = spray_management,
+         fill = spray_management,
+         colour = spray_management
+      )
+   ) +
+   geom_boxplot(alpha = 0.25) +
+   geom_jitter(width = 0.1, alpha = 0.5) +
+   labs(x = "Spray management variable",
+        y = "Grain yield (t/Ha)",
+        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
+   theme(plot.title = element_text(hjust = 0.5)) +
+   geom_hline(yintercept = 0, linetype = 2) +
+   scale_fill_usq() +
+   scale_colour_usq() +
+   coord_flip() +
+   guides(fill = FALSE, color = FALSE)
+```
+
+Using the mean difference in the treatment effect seems to show the effect of each treatment better than just raw yield and reduces the variability in the treatments.
+We know there is a good deal of variability in our studies and between them.
+Mungbean produces variable yields between seasons so ordinarily we should use a response that highlights the difference in the treatment effects that we are interested in and reduce the variability.
+However for an arm-based analysis, which we intend to do, we calculate the differences between control and treatment after the meta-analysis.
+
 ****
@@
    PM_MB_dat %>%
-   mutate(trial = paste(trial_ref, year, location, host_genotype,
-                        row_spacing, sep = "_")) %>%
+   mutate(trial = paste(
+      trial_ref, 
+      year, 
+      location, 
+      host_genotype,
+      row_spacing, 
+      sep = "_")) %>%
    select(trial_ref, trial, everything())
@@
 
-Let's test the dose effect in a basic linear mixed effect model.
+Let's test the dose effect in a linear mixed effect model.
 
@@
 We will not use dose as a defining variable in `trial`.
-
-Remove columns which are not needed
-```{r saveDat}
-PM_MB_dat <-
-   PM_MB_dat %>%
-   select(-c(trial_dose,fungicide_timing_1,fungicide_timing_2, fungicide_timing_3, 
-             dose, fungicide_application_4, fungicide_application_5, fungicide_application_6,
-             fungicide_application_7)) 
-```
 
@@
 
+********
+## Remove unnecersary variables
+
+```{r saveDat}
+PM_MB_dat <-
+   PM_MB_dat %>%
+   select(-c(trial_dose,fungicide_timing_1,fungicide_timing_2, fungicide_timing_3, 
+             dose, fungicide_application_4, fungicide_application_5, fungicide_application_6,
+             fungicide_application_7)) 
+```
+
+```{r simplifyData}
+PM_MB_dat <- 
+   PM_MB_dat %>%
+   mutate(spray_management =
+             factor(
+                spray_management,
+                c(
+                   "control",
+                   "Early",
+                   "Recommended",
+                   "Recommended_plus",
+                   "Late",
+                   "Late_plus"
+                )
+             ),
+          id = row_number(),
+          vi = yield_error,
+          n = replicates) %>%
+   select(
+      trial,
+      trial_ref,
+      location,
+      year,
+      row_spacing,
+      host_genotype,
+      spray_management,
+      fungicide_ai,
+      grain_yield.t.ha.,
+      yield_gain,
+      vi,
+      vi2,
+      n,
+      id)
+```
+
 ```{r saveData_PrepD}

### 2020-08-31 03_Prep_data.Rmd
Small edits Move final check plots for better flow Add some more headings

@@
 There is a somewhat better trend here, if sampling variance from standard deviation proves unsuitable for the analysis we may compare models using variance from stdev and mean square for the best fit.
-However, seven treatments are missing Mean square error.
+However, seven treatments are missing mean square error.
 
@@
 ```{r}
-hist_usq(PM_MB_dat$grain_yield.t.ha, main = "Grain yield (t / ha)")
-hist_usq(log(PM_MB_dat$grain_yield.t.ha), main = "log(Grain yield (t / ha))")
-hist_usq(sqrt(PM_MB_dat$grain_yield.t.ha), main = "sqrt(Grain yield (t / ha))")
+hist_usq(PM_MB_dat$grain_yield.t.ha., main = "Grain yield (t / ha)")
+hist_usq(log(PM_MB_dat$grain_yield.t.ha.), main = "log(Grain yield (t / ha))")
+hist_usq(sqrt(PM_MB_dat$grain_yield.t.ha.), main = "sqrt(Grain yield (t / ha))")
 hist_usq(PM_MB_dat$yield_gain, main = "Mean difference to control (t / ha)")
 ```
+
 The distribution of data does not seem to be improved by transformation of the data.
@@
 # PM_MB_dat$vi <-
-#    PM_MB_dat$Y_Msquare / (PM_MB_dat$n * PM_MB_dat$grain_yield.t.ha ^
+#    PM_MB_dat$Y_Msquare / (PM_MB_dat$n * PM_MB_dat$grain_yield.t.ha. ^
 #                                   2)
@@
 These categorical variables are named:
-
    - **Early**: First fungicide application was prior to first sign of disease. 
@@
 
-There are few 'Early_plus' treatments, these treatments therefore will have too few comparisons with other treatments in the meta-analysis to provide accurate results.
+'Early_plus' treatments are few in number, these treatments will have too few comparisons with other treatments in the meta-analysis to provide accurate results.
 Therefore we will remove 'Early_plus' from the analysis.
@@
 ```
-
-Now we have defined our treatments lets inspect plots to visualise how well the data compares across the trial years and locations?
-
-```{r table_of_nTreatments}
-# class spray_management as a factor and reorder them for the plot
-PM_MB_dat$spray_management <-
-   factor(PM_MB_dat$spray_management, rev(
-      c(
-         "control",
-         "Early",
-         "Recommended",
-         "Recommended_plus",
-         "Late",
-         "Late_plus"
-      )
-   ))
-
-ggplot(PM_MB_dat, aes(x = as.factor(year), fill = spray_management)) +
-   geom_bar(position = position_dodge2(width = 0.9, preserve = "single")) +
-   scale_fill_usq(name = "Spray Management") +
-   xlab("Year")
-
-kable(
-   table(PM_MB_dat$spray_management, PM_MB_dat$year),
-   align = rep('c', 8),
-   caption = "Which treatments and how many treatments are represented in each year"
-) %>%
-   kable_styling(
-      "striped",
-      fixed_thead = TRUE,
-      full_width = FALSE,
-      position = "center"
-   )
-
-```
-
-Treatments `Late_plus` and `Early` don't have very good comparison to other treatments.
-
-Let's visualise the spread of data in each treatments with box-plots.
-
-```{r treatment_means_plot}
-PM_MB_dat %>%
-   ggplot(
-      aes(
-         y = grain_yield.t.ha.,
-         x = spray_management,
-         fill = spray_management,
-         colour = spray_management
-      )
-   ) +
-   geom_boxplot(alpha = 0.25) +
-   geom_jitter(width = 0.1, alpha = 0.5) +
-   labs(x = "Spray management variable",
-        y = "Grain yield (t/Ha)",
-        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
-   theme(plot.title = element_text(hjust = 0.5)) +
-   geom_hline(yintercept = 0, linetype = 2) +
-   scale_fill_usq() +
-   scale_colour_usq() +
-   coord_flip() +
-   guides(fill = FALSE, color = FALSE)
-```
-
-There seems like little difference between the treatments, with exception of `Late_plus`.
-Let's do this plot again, but let's look at the proportional mean difference between each treatment and the no spray control for each study, this should reduce variation in yield due between trials.
-
-```{r plot_yieldProportion}
-PM_MB_dat %>%
-   filter(spray_management != "control") %>% 
-   ggplot(
-      aes(
-         y = prop_YG,
-         x = spray_management,
-         fill = spray_management,
-         colour = spray_management
-      )
-   ) +
-   geom_boxplot(alpha = 0.25) +
-   geom_jitter(width = 0.1, alpha = 0.5) +
-   labs(x = "Spray management variable",
-        y = "Grain yield (t/Ha)",
-        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
-   theme(plot.title = element_text(hjust = 0.5)) +
-   geom_hline(yintercept = 0, linetype = 2) +
-   scale_fill_usq() +
-   scale_colour_usq() +
-   coord_flip() +
-   guides(fill = FALSE, color = FALSE)
-```
-
-Using the mean difference in the treatment effect seems to show the effect of each treatment better than just raw yield and reduces the variability in the treatments.
-We know there is a good deal of variability in our studies and between them.
-Mungbean produces variable yields between seasons so ordinarily we should use a response that highlights the difference in the treatment effects that we are interested in and reduce the variability.
-However for an arm-based analysis, which we intend to do, we calculate the differences between control and treatment after the meta-analysis.
-
-****
+*****
 
@@
 
+## Final data check  
+Now we have defined our treatments lets inspect plots to visualise how well the data compares across the trial years and locations?
+
+```{r table_of_nTreatments}
+# class spray_management as a factor and reorder them for the plot
+PM_MB_dat$spray_management <-
+   factor(PM_MB_dat$spray_management, rev(
+      c(
+         "control",
+         "Early",
+         "Recommended",
+         "Recommended_plus",
+         "Late",
+         "Late_plus"
+      )
+   ))
+
+ggplot(PM_MB_dat, aes(x = as.factor(year), fill = spray_management)) +
+   geom_bar(position = position_dodge2(width = 0.9, preserve = "single")) +
+   scale_fill_usq(name = "Spray Management") +
+   xlab("Year")
+
+kable(
+   table(PM_MB_dat$spray_management, PM_MB_dat$year),
+   align = rep('c', 8),
+   caption = "Which treatments and how many treatments are represented in each year"
+) %>%
+   kable_styling(
+      "striped",
+      fixed_thead = TRUE,
+      full_width = FALSE,
+      position = "center"
+   )
+
+```
+
+Treatments `Late_plus` and `Early` don't have very good comparison to other treatments.
+
+Let's visualise the spread of data in each treatments with box-plots.
+
+```{r treatment_means_plot}
+PM_MB_dat %>%
+   ggplot(
+      aes(
+         y = grain_yield.t.ha.,
+         x = spray_management,
+         fill = spray_management,
+         colour = spray_management
+      )
+   ) +
+   geom_boxplot(alpha = 0.25) +
+   geom_jitter(width = 0.1, alpha = 0.5) +
+   labs(x = "Spray management variable",
+        y = "Grain yield (t/Ha)",
+        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
+   theme(plot.title = element_text(hjust = 0.5)) +
+   geom_hline(yintercept = 0, linetype = 2) +
+   scale_fill_usq() +
+   scale_colour_usq() +
+   coord_flip() +
+   guides(fill = FALSE, color = FALSE)
+```
+
+There seems like little difference between the treatments, with exception of `Late_plus`.
+Let's do this plot again, but let's look at the proportional mean difference between each treatment and the no spray control for each study, this should reduce variation in yield due between trials.
+
+```{r plot_yieldProportion}
+PM_MB_dat %>%
+   filter(spray_management != "control") %>% 
+   ggplot(
+      aes(
+         y = prop_YG,
+         x = spray_management,
+         fill = spray_management,
+         colour = spray_management
+      )
+   ) +
+   geom_boxplot(alpha = 0.25) +
+   geom_jitter(width = 0.1, alpha = 0.5) +
+   labs(x = "Spray management variable",
+        y = "Grain yield (t/Ha)",
+        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
+   theme(plot.title = element_text(hjust = 0.5)) +
+   geom_hline(yintercept = 0, linetype = 2) +
+   scale_fill_usq() +
+   scale_colour_usq() +
+   coord_flip() +
+   guides(fill = FALSE, color = FALSE)
+```
+
+Using the mean difference in the treatment effect seems to show the effect of each treatment better than just raw yield and reduces the variability in the treatments.
+We know there is a good deal of variability in our studies and between them.
+Mungbean produces variable yields between seasons so ordinarily we should use a response that highlights the difference in the treatment effects that we are interested in and reduce the variability.
+However for an arm-based analysis, which we intend to do, we calculate the differences between control and treatment after the meta-analysis.
+
+### Simplify and save data
+
 ```{r simplifyData}

### 2020-08-31 04_MetaAnalysis.Rmd
relocate code from meta analysis.rmd to Prep data. More wordsmithing and corrections
Move chunks to Prep_data.rmd

@@
 # Data
-slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv"
-)
+load("cache/PrepData.Rdata")
 ```
@@
 
-First, how well does the data compare across the trial years and trials?
-
-```{r table_of_nTreatments}
-# class spray_management as a factor and reorder them for the plot
-slimmer_PM_dat$spray_management <-
-   factor(slimmer_PM_dat$spray_management, rev(
-      c(
-         "control",
-         "Early",
-         "Recommended",
-         "Recommended_plus",
-         "Late",
-         "Late_plus"
-      )
-   ))
-
-ggplot(slimmer_PM_dat, aes(x = as.factor(year), fill = spray_management)) +
-   geom_bar(position = position_dodge2(width = 0.9, preserve = "single")) +
-   scale_fill_usq(name = "Spray Management") +
-   xlab("Year")
-
-kable(
-   table(slimmer_PM_dat$spray_management, slimmer_PM_dat$year),
-   align = rep('c', 8),
-   caption = "Which treatments and how many treatments are represented in each year"
-) %>%
-   kable_styling(
-      "striped",
-      fixed_thead = TRUE,
-      full_width = FALSE,
-      position = "center"
-   )
-
-```
-
-Treatments `Late_plus` and `Early` don't have very good comparison to other treatments.
-
-Let's visualise the spread of data in each treatments with box-plots.
-
-```{r treatment_means_plot}
-slimmer_PM_dat %>%
-   ggplot(
-      aes(
-         y = grain_yield.t.ha,
-         x = spray_management,
-         fill = spray_management,
-         colour = spray_management
-      )
-   ) +
-   geom_boxplot(alpha = 0.25) +
-   geom_jitter(width = 0.1, alpha = 0.5) +
-   labs(x = "Spray management variable",
-        y = "Grain yield (t/Ha)",
-        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
-   theme(plot.title = element_text(hjust = 0.5)) +
-   geom_hline(yintercept = 0, linetype = 2) +
-   scale_fill_usq() +
-   scale_colour_usq() +
-   coord_flip() +
-   guides(fill = FALSE, color = FALSE)
-```
-
-There seems like little difference between the treatments, with exception of `Late_plus`.
-Let's do this plot again, but let's look at the proportional mean difference between each treatment and the no spray control for each study, this should reduce variation in yield due between trials.
-
-```{r plot_yieldProportion}
-slimmer_PM_dat %>%
-   filter(spray_management != "control") %>% 
-   ggplot(
-      aes(
-         y = prop_yield_gain,
-         x = spray_management,
-         fill = spray_management,
-         colour = spray_management
-      )
-   ) +
-   geom_boxplot(alpha = 0.25) +
-   geom_jitter(width = 0.1, alpha = 0.5) +
-   labs(x = "Spray management variable",
-        y = "Grain yield (t/Ha)",
-        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
-   theme(plot.title = element_text(hjust = 0.5)) +
-   geom_hline(yintercept = 0, linetype = 2) +
-   scale_fill_usq() +
-   scale_colour_usq() +
-   coord_flip() +
-   guides(fill = FALSE, color = FALSE)
-```
-
-Using the mean difference in the treatment effect seems to show the effect of each treatment better than just raw yield and reduces the variability in the treatments.
-We know there is a good deal of variability in our studies and between them.
-Mungbean produces variable yields between seasons so ordinarily we should use a response that highlights the difference in the treatment effects that we are interested in and reduce the variability.
-However for an arm-based analysis we calculate the differences between control and treatment after the meta-analysis.
-
-### Formating the response variable
-
-Let's inspect the response variance `grain_yield.t.ha` to see if it is normally distributed. 
-In many cases a log transformation of the response variable improves the fit, due to the prevalence of log distributed data in nature.
-
-```{r}
-hist_usq(slimmer_PM_dat$grain_yield.t.ha, main = "Grain yield (t / ha)")
-hist_usq(log(slimmer_PM_dat$grain_yield.t.ha), main = "log(Grain yield (t / ha))")
-hist_usq(sqrt(slimmer_PM_dat$grain_yield.t.ha), main = "sqrt(Grain yield (t / ha))")
-hist_usq(slimmer_PM_dat$yield_gain, main = "Mean difference to control (t / ha)")
-```
-The distribution of data does not seem to be improved by transformation of the data.
-We will retain the continuous variable grain_yield.t.ha as the response.
-Mean differences won't be used as we are following the methodology of a ARM-based model, where mean differences are calculated following the meta-analysis.
-
-### Formatting Variance
-
-First let's remove any entries missing variance.
-
-```{r remove_studies}
-any(is.na(slimmer_PM_dat$yield_error))
-
-slimmer_PM_dat <-
-   slimmer_PM_dat[!is.na(slimmer_PM_dat$yield_error), ]
-
-slimmer_PM_dat$vi <- slimmer_PM_dat$yield_error
-```
-
-#### Calculate sample variance from mean square errors
-
-Currently our data frame has the sample variance calculated earlier, however we can approximate it using the mean squared error.
-Let's show the rational for our calculation and then add a secondary variance column (`vi2`).
-
-$MSE = Var + bias$
-
-However if our MSE was calculated from an unbiased sample we can assume $bias = 0$ and therefore:
-
-$MSE = Var$
-
-To calculate the sample variance (for each treatment in the trial) from the mean square error (Trial variance) all we need to do is divide by the number of samples in each treatment.
-We can show this because:
-$MSE = \frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n - 1}$
-Where the sum of squares for the fungicide treatment estimator ($y$) is divided by the number of fungicide treatments ($n$).
-
-The sample variance is a similar formula except we use $x$ instead of $y$.
-$S_{Var} = \frac{\sum_{x_1}^{x_n}(x_i - \overline{x})^2}{n - 1}$  
-$x$ being each observation within the experiment and $n$ being the number of samples in the whole trial.
-Therefore: 
-$S_{Var}\approx\frac{1}{n_{x}}\frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n_y - 1}$  
-Where $n_x$ is the number of samples within each treatment.
-
-```{r MSE_2_SVar}
-#calculation when using log of response
-# slimmer_PM_dat$vi <-
-#    slimmer_PM_dat$Y_Msquare / (slimmer_PM_dat$n * slimmer_PM_dat$grain_yield.t.ha ^
-#                                   2)
-
-slimmer_PM_dat$vi2 <- 
-   slimmer_PM_dat$Y_Msquare / 
-   slimmer_PM_dat$n
-```
-
-Now Let's simplify our data by removing the control data, converting disease pressure (`D_pres`) to a factor and selecting only the columns of data necessary for analysis.
-We will also include the mean difference or response ratio `grain_MD`, between the treatment and control as a comparison of responses.
-
 ```{r metafor_organisation}
 dat1 <-
-   slimmer_PM_dat %>%
+   PM_MB_dat %>%
    mutate(vi = vi/n) %>% 
@@
 Does disease pressure on the crop affect the optimum spray scenario? 
-Above we can see spraying at the first sign of powdery mildew or with in `r min(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"| slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` - `r max(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"|                   slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` days after first sign is effective at mitigating yield loss.
+Above we can see spraying at the first sign of powdery mildew or with in `r min(as.numeric(PM_MB_dat[PM_MB_dat$spray_management == "Late"| PM_MB_dat$spray_management == "Late_plus","fungicide_timing_1"]))` - `r max(as.numeric(PM_MB_dat[PM_MB_dat$spray_management == "Late"|                   PM_MB_dat$spray_management == "Late_plus","fungicide_timing_1"]))` days after first sign is effective at mitigating yield loss.
 Lets test this hypothesis by adding it as a moderator and comparing the new model with the original model above.
@@
 ```{r netmeta-analysis}
-datPM3 <- slimmer_PM_dat %>%
+datPM3 <- PM_MB_dat %>%
    group_by(trial, spray_management, n) %>%
@@
 ```{r Save_meta_data, eval=FALSE}
-save(dat1, efficacy, slimmer_PM_dat, PM_mv, YieldContrasts, contrast_Ssum, 
+save(dat1, efficacy, PM_MB_dat, PM_mv, YieldContrasts, contrast_Ssum, 
      file = here("cache/Meta-analysisData.Rdata"))

### 2020-08-31 04_MetaAnalysis.Rmd
Updated objects to remove run errors

@@
 
-   - We will test spray management (our treatment) as a fixed effect and random interactive term to trial
-
-```{r metafor_organisation}
-dat1 <-
-   PM_MB_dat %>%
-   mutate(vi = vi/n) %>% 
-   mutate(spray_management =
-             factor(
-                spray_management,
-                c(
-                   "control",
-                   "Early",
-                   "Recommended",
-                   "Recommended_plus",
-                   "Late",
-                   "Late_plus"
-                )
-             ),
-          D_pres = 
-             factor(D_pres,
-                    c("lowD",
-                      "highD")),
-          id = row_number()) %>%
-   dplyr::select(
-      trial,
-      trial_ref,
-      location,
-      year,
-      row_spacing,
-      host_genotype,
-      spray_management,
-      fungicide_ai,
-      D_pres,
-      grain_yield.t.ha,
-      yield_gain,
-      dose,
-      vi,
-      yield_error,
-      vi2,
-      n,
-      id)
-```
+   - We will test spray management (our treatment)
 
@@
 PM_mv <- rma.mv(
-   yi = grain_yield.t.ha,
+   yi = grain_yield.t.ha.,
    vi,
@@
    control=list(optimizer="optim"),
-   data = dat1
+   data = PM_MB_dat
 )
@@
 axis(2, at = seq_along(contrast_Ssum$contrast), labels = rev(contrast_Ssum$contrast), las=2, cex.axis = 0.8)
-```
-
-Does disease pressure on the crop affect the optimum spray scenario? 
-Above we can see spraying at the first sign of powdery mildew or with in `r min(as.numeric(PM_MB_dat[PM_MB_dat$spray_management == "Late"| PM_MB_dat$spray_management == "Late_plus","fungicide_timing_1"]))` - `r max(as.numeric(PM_MB_dat[PM_MB_dat$spray_management == "Late"|                   PM_MB_dat$spray_management == "Late_plus","fungicide_timing_1"]))` days after first sign is effective at mitigating yield loss.
-Lets test this hypothesis by adding it as a moderator and comparing the new model with the original model above.
-
-```{r DisPressComparison}
-PM_mv2 <- rma.mv(
-   yi = grain_yield.t.ha,
-   vi,
-   mods = ~ spray_management*D_pres,
-   method = "ML",
-   random = list(~ spray_management | trial, ~1 | id), 
-   struct = "UN",
-   control=list(optimizer="optim"),
-   data = dat1
-)
-
-anova(PM_mv, PM_mv2)
-```
-We can see that the lower $QE$ indicates that disease pressure moderator helped explain some of the residual heterogeneity in differences in grain yield between treatments. 
-However according to the Wald-test the models were not significantly different and we should use the original "Reduced" model.
-
-The P value was close to the 0.05 cut-off so we will present the model output for the interest of the readers.
-```{r DissPressMetMod}
-summary(PM_mv2)
-summary(glht(PM_mv2, linfct=cbind(contrMat(rep(7,12), type="Tukey"))), test=adjusted("none"))
-# plot(glht(PM_mv2, linfct=cbind(contrMat(rep(7,12), type="Tukey")))) # I think this plot is too busy to be incorporated
 ```
@@
 Lets look at the trial variability in this model with a forest plot
-```{r forestP, fig.height= 40, fig.width=17}
+```{r forestP, eval=FALSE, fig.height=40, fig.width=17, include=FALSE}
 # THIS NEEDS TO BE FIXED
@@
 ### Sort and arrange data-frame accordingly and produce a index vector to inform the order of each "Trial" on the plot
-index1 <- dat1 %>%
+index1 <- PM_MB_dat %>%
    mutate(ID = seq_along(trial_ref)) %>%
@@
                     "Recommended_plus","Late_plus"))) %>%
-   arrange(desc(spray_management), location, desc(grain_yield.t.ha)) %>%
+   arrange(desc(spray_management), location, desc(grain_yield.t.ha.)) %>%
    mutate(ID2 = order(ID))%>%
@@
 rows1 <- forest_rows(head_row = 186, 
-                     ord_var = dat1$spray_management, 
+                     ord_var = PM_MB_dat$spray_management, 
                      index = index1, 
@@
                 rows = rows1$trows-1.5,
-                ilab = cbind(dat1$year, 
-                             dat1$row_spacing, dat1$host_genotype, dat1$dose),
+                ilab = cbind(PM_MB_dat$year, 
+                             PM_MB_dat$row_spacing, PM_MB_dat$host_genotype, PM_MB_dat$dose),
                 ilab.xpos = c(-2.35,-2.1,-1.8,-1.4)+1,
@@
    group_by(trial, spray_management, n) %>%
-   summarize(yi_mean = mean(grain_yield.t.ha),
-             vi_mean = mean(yield_error)) %>%
+   summarize(yi_mean = mean(grain_yield.t.ha.),
+             vi_mean = mean(vi)) %>%
    ungroup()
@@
 ```{r Save_meta_data, eval=FALSE}
-save(dat1, efficacy, PM_MB_dat, PM_mv, YieldContrasts, contrast_Ssum, 
+save(efficacy, PM_MB_dat, PM_mv, YieldContrasts, contrast_Ssum, 
      file = here("cache/Meta-analysisData.Rdata"))

### 2020-09-01 02_Preliminary_analysis.Rmd
Label changes

@@
                lme4,
-               kableExtra)
-source("R/import_data.R")
+               kableExtra,
+               here)
+
 if (!require("theme.usq"))
@@
 ## Explore and Visualise Data
-First let's import the data.
-Each row provides the mean yield for each experimental treatment.
 
-```{r echo=TRUE, message=FALSE, warning=FALSE}
-PM_MB_means <- import_data() 
+The data explored in the `PM_MB_dat` data frame is a list of mean values from each treatment in each respective experiment.
+These preliminary analyses will describe the data and then investigate any change in mungbean yields which is attributable to the fungicide treatment.
+
+### Descriptive statistics  
+#### Spatio-temporal variation
+
+Lets look at how many trials were undertaken each season
+
+```{r FinalTrialsForInclusion1}
+tmp1 <- PM_MB_dat %>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")%>%
+   distinct(trial_ref, location, year)%>%
+   arrange(year)
+   table(tmp1$year)
 ```
 
-The data explored in the `PM_MB_means` data frame is a list of mean values from each treatment in each respective experiment.
-These preliminary analyses will focus on the change in mungbean yields, which is attributable to the fungicide treatment. 
-Later in this document we will also consider the impact of fungicide treatments on disease incidence/severity.
-Mean powdery mildew incidence was recorded at the end of each growing season.
-Some experiments recorded disease incidence throughout the season and these were summarised with AUDPC.
-AUDPC for trials which only provided final powdery mildew incidence was calculated using the record of 'first sign of disease' and final assessment.
-More details on how the `PM_MB_means` data was compiled can be found in the ['Data wrangle vingette'](./vignette/191115_PMMB_DataWrangling_PM.html)
+Also the location of the trials
 
-Various factors have been studied in the previous experiments which may influence the subsequent meta-analysis.
-On this page, unless stated, the following plots and analyses were made disregarding other effects.
-The following factors are postulated to influence mungbean grain yield and/or powdery mildew mean plot severity.
-
-   1 Fungicide type
-
-   2 Fungicide dose (varies only slightly within some fungicide types)
-
-   3 Number of fungicide sprays
-
-   4 Timing of fungicide spray/s relative to first sign of disease
-
-   5 Host cultivar (probably is a co-variate with season due to changing cultivars over time)
-
-   6 Experiment location
-
-   7 Row spacing
-
-   8 In-crop rainfall
-
-   9 Irrigated versus non-irrigated trials
-
-   10 Mean daily temperature in the weeks following spray application
-
-   11 Final disease rating
-
-   12 Two pathogen species cause PM (new discovery in 2018)
-
-The data plotted below are from `r length(unique(PM_MB_means$trial_ref))` field trials between (`r first(levels(PM_MB_means$year))` - `r last(levels(PM_MB_means$year))`) of which the details are described in the [studies considered in meta-analysis section](#studies-considered-in-meta-analysis).
-
-### Fungicides
-
-#### Fungicide type
-
-First let's standardise the sulphur treatments.
-Some early experiments tested different formulations.
-There was no difference in the sulphur formulations so we will refer to all of them as "sulphur".
-
-```{r sulphur_simplify}
-# Remove the variation in different sulphur formulations
-unique(PM_MB_means[grep("sulphur", PM_MB_means$fungicide_ai),
-                   "fungicide_ai"])
-PM_MB_means[grep("sulphur", PM_MB_means$fungicide_ai), "fungicide_ai"] <-
-   "sulphur"
+```{r FinalTrialsForInclusion}
+   table(tmp1$location)
 ```
 
-Let's explore how many different types of fungicide were used and at what frequency.
+#### Mean yield
 
-```{r Fungicides}
-PM_MB_means %>%
-   group_by(fungicide_ai, trial_ref) %>%
-   summarise() %>%
-   count(sort = TRUE) %>%
-   rename(Trials = n) %>%
-   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
-   xlab("Fungicide active ingredient") +
-   ylab("N Trials") +
-   geom_col() +
-   scale_fill_usq() +
-   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
-   scale_colour_usq() +
-   coord_flip()
+What is the variation in yield over all the trials (including non-DMI fungicide trials) in the no spray control and fungicide treated plots.
+
+```{r ControlYield_AllTrials}
+PM_MB_dat %>%
+   filter(fungicide_ai == "control")%>%
+   summarise(mean_yield = mean(grain_yield.t.ha.),
+             minimum_yield = min(grain_yield.t.ha.),
+             maximum_yield = max(grain_yield.t.ha.),
+             yield_stdev = sd(grain_yield.t.ha.)) %>%
+   kable(align = 'c',
+   caption = "Average yield statistics for no spray contol plots"
+)
+
 ```
 
-The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in the highest frequencies, along with sulphur.
-The DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.
+What is the yield variation in no spray control trials yield over only the DMI fungicide trials.  
+```{r ControlYield_DMITrials}
+DMITrials <- PM_MB_dat %>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")%>%
+   distinct(trial_ref)%>%
+   pull()
 
-Amistar Xtra and Custodia both contain strobilurin and triazole, however, because they contain differing dose ratios (inverted) pooling may not be appropriate.
+PM_MB_dat %>%
+   filter(trial_ref %in% DMITrials)%>%
+   filter(fungicide_ai == "control" )%>%
+   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
+             minimum_yield = min(grain_yield.t.ha.*1000),
+             maximum_yield = max(grain_yield.t.ha.*1000),
+             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
+   kable(align = 'c',
+   caption = "Average yield statistics for control plots in trials which used a DMI fungicide")
 
-Perhaps best way forward is to focus the meta-analysis on only the DMIs.
-This can then be compared to an additional meta-analysis including azoxystrobin as a comparison.
+```
 
-*****
+Mean yields in DMI fungicide treated plots
+```{r Yield_DMITrials}
+PM_MB_dat %>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")%>%
+   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
+             minimum_yield = min(grain_yield.t.ha.*1000),
+             maximum_yield = max(grain_yield.t.ha.*1000),
+             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
+   kable(align = 'c',
+   caption = "Average yield statistics for DMI fungicide treated plots")
 
-Before we exclude non-DMI fungicides let's have a look at the efficacy of the other fungicides in comparison to the DMIs.
-For this comparison we will focus on the proportional yield saved, relative to the no spray control.
-The primary focus of this research is the effect of fungicide on mitigating yield loss due to disease.
-We are using proportional yield, relative to the no spray control, to reduce the effect of location and seasonal influences.
+```
 
-Let's investigate the difference in the effect of the type of fungicide on proportion of yield saved, but first we need to calculate yield saved relative to the no spray control.
+Lets look at the yield gains in each trial compared to the no spray control, we will also calculate the proportional grain yield gains.
 
 ```{r Calculate_yield-savings}
-PM_MB_means$grain_yield.t.ha. <-
-   as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data
-
-for (i in unique(PM_MB_means$trial_ref)) {
+for (i in unique(PM_MB_dat$trial_ref)) {
    # Loop code over each trial reference
-   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
+   dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == i, ]
 
@@
    c(NA, NA)
-PM_MB_means[PM_MB_means$trial_ref == "AM1303", ] <- dat1
 
-write.csv(PM_MB_means,
-          "cache/1911_PM_MB_means&Ygains.csv")
+PM_MB_dat[PM_MB_dat$trial_ref == "AM1303", ] <- dat1
 ```
 
-Now we have calculated proportional yield savings we can inspect the difference between the fungicide active ingredients
+Lets show the yield gains in each trial as a table and plot
+```{r YieldGain_table}
+PM_MB_dat %>%
+   filter(trial_ref %in% DMITrials)%>%  # selects only the trials with DMI fungicide treatments
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")%>%
+   group_by(trial_ref, location, year)%>%
+   summarise(yield_gain_m = mean(yield_gain),
+             yield_gain_se = sd(yield_gain, na.rm = T)/sqrt(n()),
+             yg_n = n(),
+             .groups = "drop")%>%
+   arrange(yield_gain_m)
+```
+
+```{r YieldGain_plot}
+PM_MB_dat %>%
+   filter(trial_ref %in% DMITrials)%>%  
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")%>%
+   group_by(trial_ref, location, year)%>%
+   summarise(yield_gain_m = mean(yield_gain),
+             yield_gain_se = sd(yield_gain, na.rm = T)/sqrt(n()),
+             .groups = "drop")%>%
+   mutate(trial = paste(location,year,sep = "\n"))%>%
+   ggplot(aes(reorder(trial, yield_gain_m), yield_gain_m))+
+   geom_bar(stat = "identity")+
+   geom_errorbar(width = 0.3 ,aes(ymax = yield_gain_m + yield_gain_se, 
+                     ymin = yield_gain_m - yield_gain_se))+
+   theme(axis.text.x = element_text(angle = 90, hjust = 1))
+
+```
+
+Various factors have been studied in the previous experiments which may influence the subsequent meta-analysis.
+On this page, unless stated, the following plots and analyses were made disregarding other effects.
+The following factors are postulated to influence mungbean grain yield and/or powdery mildew mean plot severity.
+
+   1 Fungicide type
+
+   2 Fungicide dose (varies only slightly within some fungicide types)
+
+   3 Number of fungicide sprays
+
+   4 Timing of fungicide spray/s relative to first sign of disease
+
+   5 Host cultivar (probably is a co-variate with season due to changing cultivars over time)
+
+   6 Experiment location
+
+   7 Row spacing
+
+   8 Final disease rating / disease pressure
+
+The data plotted below are from `r length(unique(PM_MB_dat$trial_ref))` field trials between (`r first(levels(PM_MB_dat$year))` - `r last(levels(PM_MB_dat$year))`) of which the details are described in the [Trials considered for inclusion in meta-analysis section](#Trials-considered-for-inclusion-in-meta-analysis).
+
+<br>
+<br>
+<br>
+
+### Fungicides
+
+#### Fungicide type
+
+Before we exclude non-DMI fungicides let's have a look at the efficacy of the other fungicides in comparison to the DMIs.
+For this comparison we will focus on the proportional yield saved, relative to the no spray control.
+The primary focus of this research is the effect of fungicide on mitigating yield loss due to disease.
+We are using proportional yield, relative to the no spray control, to reduce the effect of location and seasonal influences.
 
 ```{r Fungicide_x_nSprays_tble2, message=FALSE}
-PM_MB_means %>%
+PM_MB_dat %>%
    group_by(fungicide_ai, total_fungicide) %>%
@@
 
-**  **  *
+<br>
+<br>
+<br>
 
@@
 
-#### Fungicide Doses  
+#### Fungicide Doses{#fungicide-doses}  
 From this point on we will investigate only the DMI fungicides, tebuconazole and propiconazole, and disregard all other fungicide modes-of-action.
@@
    )) +
-   ylab("Days to First Sign of Disease") +
+   ylab("Number of days after or before first sign of powdery mildew") +
+   ggtitle("Fungicide application timing relative to First Sign of Disease.\n - Faceted by number of applications")+
    facet_grid(cols = vars(total_fungicide)) +
@@
 
-#### Genotype yield variability
-
-Does host cultivar significantly impact the yield?
-Let's look at the volatility in yields to see if any cultivar yields better or has greater tolerance to powdery mildew.
-Below we plot distributions of mean trial yields for each cultivar.
-The following plots use data that includes all fungicide types.
-
-First let's look at overall yields for each cultivar, where trial is not a factor, for all treatments (spray and no spray).
-
-```{r yield_vol}
-# Outputs the table and graph
-source("R/yield_volatility.r") # function to investigate the volatility in yields
-# Volatility is the range between the upper and lower 97.5 and 2.5 % quartiles
-YV1 <-
-   yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
-YV1[[2]] + 
-   scale_fill_usq()
-YV1[[3]]
-```
-
-This plot shows a large amount of yield volatility in all cultivars except Green Diamond.
-Green Diamond shows little volatility probably because this cultivar was only used in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trial.
-
-Now let's look at overall yields for each cultivar, where trial is not a factor, in only the no spray control treatments.
-
-```{r yieldVol_control}
-YV2 <-
-   yield_volatility(genotype_by_trial = FALSE, control_only = TRUE)
-YV2[[2]] +
-   scale_fill_usq()
-YV2[[3]]
-```
-
-Volatility of the cultivars are less, albeit fairly similar, in control plots when trial is not considered as a factor.
-
-*****
-
-Let's examine the same plots as above but only for the most commonly used trial site, Hermitage.
-
-```{r yieldVol_Herm}
-YV1_herm <-
-   yield_volatility(
-      genotype_by_trial = FALSE,
-      control_only = FALSE,
-      location = "Hermitage"
-   )
-YV1_herm[[2]] +
-   scale_fill_usq()
-
-YV1_herm[[3]]
-```
-
-Jade shows a large amount of volatility, excluding Green Diamond, Crystal shows the next least volatility.
-
-*****
-
-Let's take a closer look at Crystal with spray management treatments and without.
-
-```{r YieldVol_Crystal}
-YV1_crystal <-
-   yield_volatility(genotype = "Crystal", control_only = FALSE)
-YV1_crystal[[2]] +
-   scale_fill_usq()
-
-YV1_crystal[[3]]
-
-YV2_crystal <-
-   yield_volatility(genotype = "Crystal", control_only = TRUE)
-YV2_crystal[[2]] +
-   scale_fill_usq()
-
-YV2_crystal[[3]]
-```
-
-There is a lot of variation between field trials for Crystal, but little variation within field trials. This indicates that trial should be fit as a random effect when we fit a model to this data.
-
-Let's look at Jade, to see if it differs.
-
-```{r YieldVol_Jade}
-YV1_jade <- yield_volatility("Jade",control_only = FALSE)
-YV1_jade[[2]] +
-   scale_fill_usq()
-
-YV1_jade[[3]]
-```
-
-For Jade there is high variation between trials and with-in.
-Perhaps indicating lower tolerance. 
-Let's look at the same plot with data only from no spray controls to see if the variation is the same.
-
-```{r YieldVol_JadeControl}
-YV2_jade <- yield_volatility("Jade", control_only = TRUE)
-YV2_jade[[2]] +
-   scale_fill_usq()
-
-YV2_jade[[3]]
-```
-
-There still remains a higher volatility in Jade and perhaps a greater shift in the probability curve including fungicide treatments versus probability curves including only no spray controls.
-Indicating that there might be a difference in powdery mildew tolerance between Jade and Crystal.
-
-Overall there seems to be an influence of cultivar.
-However this variation is not as distinct as the variation between trials.
-
-*****
-
 ### Row spacing
@@
 
+Lets plot disease severity in boxplots grouped by row spacing treatment.
+We are asking here, which row spacing leads to the higher disease severity?
+
 ```{r RS_severity}
 # Which row spacing leads to the higher disease severity
-PM_MB_means %>%
+PM_MB_dat %>%
    filter(year == 2017 |
@@
    xlab("Row spacing (m)") +
-   ggtitle("Powdery mildew variation between different row spacing")
+   ggtitle("Powdery mildew severity between different row spacing across all trials")
 ```
+
+There is little difference here between the row spacing treatments, lets look if there is a trial location effect as disease pressure lead to varying results.
 
@@
 
-*****
+<br>
+<br>
+<br>
+<br>
 
-### Yield vs in-season rain
+### Yield loss in cultivar Jade
 
-In0-crop rain could be a significant factor which contributes to the end of season grain yield.
-To investigate this effect I will use a linear model (GY ~ SR) where seasonal rainfall represents a specific time frame with respect to planting time.
-Multiple time frames were tested from 20 days prior to planting, to 100 days after planting.
-
-The multiple time frames were tested by a loop over the dates at the start of the season (to 90 days after planting) to find which date fits the best linear model for grain weight and in-crop rainfall.
-The code for this process was moved to be contained within it's own script and can be run as a job as it can take a long time.
-To speed up the computation I split the script into four, ran the jobs and bound the data into one frame.
-The output of the script is saved with the prefix `lmInSeasonRainfall` followed by the time windows the model is run.
-For example `lmInSeasonRainfall_20.40_50.80.csv` holds the model results for start days between 20 and 40 days after planting to end window dates between 50 and 80 days after planting.
-
-This tests when rainfall during the cropping season could be best associated with yield
-
-```{r rainfall_sum_Sstart}
-# The four data files were created from four scripts run as four jobs in RStudio
-# when the four jobs are finished they can be imported and combined into one data.frame
-# source(Rainfall_x_cropYield_s-10.09_e30.65.R)
-# source(Rainfall_x_cropYield_s-10.09_e65.100.R)
-# source(Rainfall_x_cropYield_s10.30_e30.65.R)
-# source(Rainfall_x_cropYield_s10.30_e65.10.R)
-
-lm_rain1 <-
-   read.csv("cache/lmInSeasonRainfall_-10.09_30.64.csv",
-            stringsAsFactors = FALSE)
-lm_rain2 <-
-   read.csv("cache/lmInSeasonRainfall_-10.09_65.100.csv",
-            stringsAsFactors = FALSE)
-lm_rain3 <-
-   read.csv("cache/lmInSeasonRainfall_10.30_30.64.csv",
-            stringsAsFactors = FALSE)
-lm_rain4 <-
-   read.csv("cache/lmInSeasonRainfall_10.30_65.100.csv",
-            stringsAsFactors = FALSE)
-
-lm_rain <- rbind(lm_rain1, lm_rain2, lm_rain3, lm_rain4)
-```
-
-Now we have read in the data from the previously computed models let's find the linear model which has:  
-   - The lowest P value  
-   - the highest adjusted r squared value
-
-```{r WhichLModel}
-lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)), ]
-lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)), ]
-lm_rain[which(lm_rain$lm_adj_rsquared == max(lm_rain$lm_adj_rsquared)), ]
-```
-
-To visualise the model fits we will use a heat map to describe how the models faired in relation to the rainfall windows.
-log of the p value was used to improve the resolution of small very small p values.
-
-```{r rainLMpvalue}
-ggplot(lm_rain, aes(x = start_day, y = end_day, z = log(lm_pval))) +
-   geom_raster(aes(fill = log(lm_pval)), interpolate = TRUE) +
-   geom_contour(bins = 15, colour = "white") +
-   geom_point(data = lm_rain[which(lm_rain$lm_pval == min(lm_rain$lm_pval)), ],
-              aes(x = start_day, y = end_day),
-              colour = " red") +
-   scale_fill_distiller(palette = "RdBu", direction = -1) 
-```
-
-```{r rainLMadjrsquared}
-ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_adj_rsquared)) +
-   geom_raster(aes(fill = lm_adj_rsquared), interpolate = TRUE) +
-   geom_contour(bins = 15, colour = "white") +
-   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)), ],
-              aes(x = start_day, y = end_day),
-              colour = " red") +
-   scale_fill_distiller(palette = "RdBu") 
-```
-
-The approximate period when in-crop rainfall affects the most on the mean harvest is between 14 - 67 days after planting.
-
-*****
-
-### Season range and first incidence
-
-Mungbean is a summer crop and powdery mildew requires cool conditions to establish.
-Therefore the disease can be avoided by planting early in summer or spring, avoiding cooler temperatures at the end of some seasons.
-Can we visualise when PM is most likely to establish over the calendar year?
-
-I'll build a plot of horizontal lines indicating the season length and use a dot on the line to indicating the day of the year first sign was observed for that trial.
-
-```{r first_incidence}
-# Create the data frame for the plot
-season_dates <- PM_MB_means %>%
-   group_by(trial_ref) %>%
-   summarise(
-      Planting_date = unique(planting_date),
-      Harvest_date = unique(harvest_date),
-      First_sign_PM = unique(first_sign_disease),
-      season_length = as.Date(unique(harvest_date)) - as.Date(unique(planting_date)),
-      cropping_season = "Actual"
-   )
-
-# For some trials where planting date and Harvest date is missing let's estimate 
-#     the season length by using the mean of all season lengths
-season_dates[is.na(season_dates$season_length),"cropping_season"] <- "Estimated"
-
-season_dates[is.na(season_dates$Planting_date),"Planting_date"] <- 
-   season_dates[is.na(season_dates$Planting_date),"Harvest_date"] - 
-   as.numeric(mean(season_dates$season_length, na.rm = TRUE))
-
-season_dates[is.na(season_dates$Harvest_date),"Harvest_date"] <- 
-   season_dates[is.na(season_dates$Harvest_date),"Planting_date"] + 
-   as.numeric(mean(season_dates$season_length, na.rm = TRUE))
-
-season_dates[is.na(season_dates$season_length),"season_length"] <- 
-   mean(season_dates$season_length, na.rm = TRUE)
-
-season_dates$Planting_day <- yday(season_dates$Planting_date)
-season_dates$Disease_day <- yday(season_dates$First_sign_PM)
-
-season_dates[c(1:2,6), "Planting_day"] <- 1
-
-season_dates$Harvest_day <-
-   season_dates$Planting_day + season_dates$season_length
-
-first_day_month <- c(0, 31, 60, 91, 121, 152, 182, 212, 244, 274) + 1
-axis_labels_date <-
-   c(
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[1], "%b-%d"),
-      # Jan
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[2], "%b-%d"),
-      # Feb
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[3], "%b-%d"),
-      # March
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[4], "%b-%d"),
-      # April
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[5], "%b-%d"),
-      # May
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[6], "%b-%d"),
-      # June
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[7], "%b-%d"),
-      # July
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[8], "%b-%d"),
-      # August
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[9], "%b-%d"),
-      # Sept
-      format(Sys.Date() - yday(Sys.Date()) + first_day_month[10], "%b-%d") # October
-   )
-
-# reorder the factors so they will appear in chronological order
-# I used First sign because all trials have recorded this
-season_dates$trial_ref <-
-   factor(season_dates$trial_ref,
-          levels = levels(season_dates$trial_ref)[rev(order(season_dates$First_sign_PM))])
-
-# Plot
-SeasonPlot <- season_dates %>%
-   ggplot() +
-   geom_pointrange(aes(
-      x = trial_ref,
-      y = Disease_day,
-      ymin = Planting_day,
-      ymax = Harvest_day,
-      colour = cropping_season
-   )) +
-   scale_y_continuous(limits = c(
-      0,
-      max(
-         season_dates$Planting_day +
-            season_dates$season_length,
-         na.rm = TRUE
-      )
-   ),
-   labels = axis_labels_date,
-   breaks = first_day_month) +
-   geom_point(aes(x = trial_ref, y = Disease_day)) +
-   coord_flip() +
-   scale_color_manual(values=c("black","grey70"))+
-   ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
-
-SeasonPlot
-```
-
-In most years, regardless of the age of the crop, powdery mildew establishes in March, which is to be expected.
-The disease is driven by weather conditions and the plant is vulnerable at any growth stage.
-
-### AUDPC visualise raw data
-
-First let's check we have all the AUDPC observations.
-
-```{r AUDPC_check}
-PM_MB_means %>%
-   filter(is.na(AUDPC_m)) %>%
-   distinct(trial_ref, location, year,AUDPC_m, first_sign_disease, final_assessment)%>%
-   kable(align = "c")
-```
-
-The trials `r unique(PM_MB_means[is.na(PM_MB_means$AUDPC_m),"trial_ref"]) ` don't have an estimate of AUDPC and need to be filled in. 
-The following script estimates AUDPC from the final disease severity rating and the first sign of disease information.
-
-```{r SingleObsAUDPC}
-source(here("R/AUDPC_for_single_obs.R"))
-write.csv(PM_MB_means,
-          "cache/1911_PM_MB_means&Ygains.csv", row.names = FALSE)
-```
-
-      _How well does 'area under the disease progress curve' (AUDPC) predict grain yield?_
-
-   and
-
-      _Does spray_management scenario mitigate yield loss through reducing AUDPC?_
-
-We would expect to see grain yield decline with increasing AUDPC.
-Let's just plot yield vs AUDPC.
-
-```{r Yield_vs_AUDPC}
-
-plot(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means)
-abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means))
-
-```
-
-There appears to be a weak positive relationship between the two continuous variables.
-Does a linear model confirm this?
-
-```{r AUDPClm}
-summary(lm(grain_yield.t.ha. ~ AUDPC_m, data = PM_MB_means))
-```
-
-This is not what we would expect and the low R squared value of `r round(summary(lm(grain_yield.t.ha.
-~ AUDPC_m, data = PM_MB_means))$adj.r.squared,3)` perhaps there are additional factors influencing this relationship.
-
-Let's tease out variation due to trial location, season, row spacing, and other seasonal variables are preventing us from seeing the expected relationship.
-Let's do the plot again for each trial where there are no missing values.
-Note: The plots are ordered by mean yield of the trial.
-
-```{r AUDPCxTrial}
-sm2lg <- PM_MB_means %>%
-   group_by(trial_ref) %>%
-   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
-   arrange(TY)
-
-for (i in sm2lg$trial_ref) {
-   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
-   if (any(is.na(dat1$grain_yield.t.ha.))) {
-      next
-   }
-   if (any(is.na(dat1$AUDPC_m))) {
-      next
-   }
-
-   plot(
-      grain_yield.t.ha. ~ AUDPC_m,
-      data = dat1,
-      main = paste(dat1$location[1], (dat1$year[1])),
-      ylim = c(0, max(PM_MB_means$grain_yield.t.ha., na.rm = TRUE)),
-      xlim = c(0, max(PM_MB_means$AUDPC_m, na.rm = TRUE))
-   )
-   abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = dat1))
-   points(grain_yield.t.ha. ~ AUDPC_m,
-          data = dat1[dat1$fungicide_ai == "control",],
-          col = "red")
-
-}
-```
-
+Mungbean Jade shows the best quantitative resistance to powdery mildew.
 Based on a GRDC report by Sue Thompson [-@SueThompson2016] we want to know what the yield loss was in on cultivar Jade in the 2016 Trials.
-```{r}
-dat3 <- PM_MB_means %>%
+```{r JadeYieldLoss}
+PM_MB_dat %>%
    filter(year == "2016",
-          host_genotype == "Jade",
-          fungicide_ai == "control")%>%
-   group_by(location)%>%
-   summarise(C_Yield = mean(grain_yield.t.ha., na.rm = TRUE))
-
-dat3$F_Yield <- PM_MB_means %>%
-   filter(year == "2016",
-          host_genotype == "Jade",
-          fungicide_ai != "control")%>%
-   group_by(location)%>%
-   summarise(F_Yield = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
-   pull(F_Yield)
-
-dat3 %>% 
-   mutate(diff = F_Yield - C_Yield) %>%
-   mutate(percent = (diff/F_Yield)*100)
+          host_genotype == "Jade")%>%
+   mutate(Treatment = case_when(
+      fungicide_ai == "control" ~ "control",
+      TRUE ~ "FungicideTreated"))%>%
+   group_by(location, Treatment)%>%
+   summarise(trial_ref = trial_ref,
+             location = location, 
+             year = year,
+             Yield = mean(grain_yield.t.ha., na.rm = TRUE),
+             .groups = "drop")%>%
+   distinct()%>%
+   pivot_wider(names_from = Treatment, values_from = Yield)%>%
+   mutate(Diff = FungicideTreated - control) %>%
+   mutate(percent = (Diff/FungicideTreated)*100)%>%
+   select(trial_ref, location, year, control, FungicideTreated,percent, Diff)
 
@@
 
-Let's have a look again at the same sequence of graphs and analyses for area under the disease progress _stairs_.
+### FAO mungbean data
 
-```{r Yield_vs_AUDPS}
-plot(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means)
-abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means))
+An important consideration for why to carry out work on mungbean diseases is the value the crop provides. 
+Lets pull in data from the FAOSTAT website for the area of mungbean crops harvested.
 
-summary(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means))
-
-sm2lg <- PM_MB_means %>%
-   group_by(trial_ref) %>%
-   summarise(TY = mean(grain_yield.t.ha., na.rm = TRUE)) %>%
-   arrange(TY)
-
-for (i in sm2lg$trial_ref) {
-   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
-   if (any(is.na(dat1$grain_yield.t.ha.))) {
-      next
-   }
-   if (any(is.na(dat1$AUDPS_m))) {
-      next
-   }
-
-   plot(
-      grain_yield.t.ha. ~ AUDPS_m,
-      data = dat1,
-      main = paste(dat1$location[1], (dat1$year[1])),
-      ylim = c(0, max(
-         PM_MB_means$grain_yield.t.ha., na.rm = TRUE
-      )),
-      xlim = c(0, max(PM_MB_means$AUDPS_m, na.rm = TRUE))
-   )
-   abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = dat1))
-   points(grain_yield.t.ha. ~ AUDPS_m,
-          data = dat1[dat1$fungicide_ai == "control",],
-          col = "red")
-
-}
-```
-
-The plots from the AUPDS is similar to the AUDPC, however according to the linear model the AUDPC is a better, significant fit.
-
-A mixed effect model would be more suitable to investigate the interactive effects of location, season, and trial. 
-The mixed effect model will help us decide on the best approach and structure for our meta-analysis model.
-
-```{r}
+```{r FAO_data_inquiry}
 beans <- read.csv(here("data/FAOSTAT_data_7-6-2020.csv"))
 
-glimpse(beans)
+str(beans)
 
@@
 
-beans %>%
-   filter(Item == "Beans, dry",
-          Element == "Yield")%>%
-   ggplot(aes(y = Value *0.1, x = Year))+
-   geom_point()+
-   geom_smooth()
-
-beans %>%
-   filter(Item == "Beans, dry",
-          Element == "Production")%>%
-   ggplot(aes(y = Value, x = Year))+
-   geom_point()+
-   geom_smooth(method = "lm")
-
 ```

### 2020-09-01 03_Prep_data.Rmd
Dose elaboration

@@
 
-Earlier we noted there were different doses of propiconazole, which might influence our analysis.
+Earlier, in section [Fungicide Doses](#fungicide-doses) we noted there were different doses of propiconazole, which might influence our analysis. 
+The current label for custodia [PER82104](http://permits.apvma.gov.au/PER82104.PDF), Containing: 120 g/L azoxystrobin and 200 g/L tebuconazole, recommends between 300 ml - 600 ml of the tebuconazole fraction per hectare, equivalent to 60 - 120 grams per hectare.
+These label rates are assumed to be the same for propiconazole infering these concentrations might be within the recommended rates. 
+It is also worth noting the APVMA permit [PER13979](http://permits.apvma.gov.au/PER13979.PDF) which allows the use of Tebuconazole between 62.35 g / ha and 83 g / ha depending on the product formulation.
+
 Let's add the dose variable to the `trial` variable then compare linear mixed effect models including and excluding dose in the trial variable.
@@
    PM_MB_dat %>%
-   select(-c(trial_dose,fungicide_timing_1,fungicide_timing_2, fungicide_timing_3, 
-             dose, fungicide_application_4, fungicide_application_5, fungicide_application_6,
-             fungicide_application_7)) 
+   select(-c(trial_dose,
+             fungicide_timing_1,fungicide_timing_2, fungicide_timing_3, 
+             dose, fungicide_application_4, fungicide_application_5,
+             fungicide_application_6, fungicide_application_7)) 
 ```

### 2020-09-02 04_MetaAnalysis.Rmd
Edits and treatment effects table for publication

@@
                bomrang,
-               lme4,
                RColorBrewer,
@@
 
-> Which spray management scenario provides the greatest yield protection from powdery mildew.
+> When, in relation to PM establishes in the crop, should farmers begin spraying mungbean to mitigate yield loss: before PM establishing,  immediately after first sign of PM establishing, or after PM has become established in the crop.
+
+A secondary question to this aim is: given the time at which the first spray occurred is a second spray provide worthwhile yield protection.
 
@@
 
-   - We will test spray management (our treatment)
+   - We will investigate the effect size of our treatment - spray management,
 
@@
 
-For the first grain yield meta-analysis, we'll use the `metafor` package [@Viechtbauer2010].
+For the first grain yield meta-analysis will be an ARM based model using the `metafor` package [@Viechtbauer2010].
 
-To do a ARM based model we will use the package `metafor`.
 We are using the `spray_management` variable as a moderator and an interactive term to the `trial` random variable.
@@
 
+Lets present the meta-analysis results for the moderator variables in a forest style plot.
+First lets create a table of the results.
+
+```{r metafor_results}
+
+k5 <- as.data.frame(table(PM_MB_dat$trial, PM_MB_dat$spray_management)) %>%
+   filter(Freq !=0)%>%
+   group_by(Var2)%>%
+   summarise(n())%>%
+   pull()
+
+results_mv <- data.frame(N = PM_mv$g.levels.k,
+                         k = k5,
+                         Effect = round(PM_mv$b,4),
+                         se = round(PM_mv$se,4),
+                         CI_lower = round(PM_mv$ci.lb,4),
+                         CI_upper = round(PM_mv$ci.ub,4),
+                         z_val = round(PM_mv$zval,4),
+                         p_val = reportP(PM_mv$pval,AsNumeric = TRUE),
+                         row.names = c("Intercept",
+                                       "$Early_{single}$",
+                                       "$Recommended_{single}$",
+                                       "$Recommended_{plus}$",
+                                       "$Late_{single}$",
+                                       "$Late_{plus}$"))
+
+colnames(results_mv)[c(1:4,6:9)] <- c("Treatment","$N$", "$k$","$\\mu$","$CI_{L}$","$CI_{U}$", "$Z$","$P$")
+
+kable(results_mv[,2:9],
+      align = "lcccccccc",
+      booktabs = TRUE,
+      caption = "Table ##: Mean effect size of five spray schedule treatments on mitigating yield losses to powdery mildew in mungbean crops grown in eastern Australia.
+Effect sizes were estimated from the network meta-analysis of data obtained from grey literature reports.
+Intercept indicates the mean of the no spray control and the treatments show the mean difference to the intercept")
+
+```
+
+Let's view these comparisons in a plot.
+
+```{r metafor_plot}
+results_mv %>%
+   filter(Treatment != "control") %>% 
+   mutate(Treatment = factor(Treatment, levels = rev(
+      c(
+
+         "Early",
+         "Recommended",
+         "Recommended_plus",
+         "Late",
+         "Late_plus"
+      )
+   ))) %>%
+   ggplot(aes(Treatment, `$\\mu$`)) +
+   geom_hline(
+      yintercept = seq(-0.05, 0.3, by = 0.05),
+      color = usq_cols("usq charcoal"),
+      linetype = 3
+   ) +
+   geom_hline(yintercept = 0) +
+   geom_point(aes(size = 1 / se), shape = 15) +
+   geom_linerange(aes(ymin = `$CI_{L}$`, ymax = `$CI_{U}$`)) +
+   coord_flip()+
+   ggtitle("Mean spray schedule effect sizes\nand 95% confidence intervals")
+
+```
+
+Lets investigate the treatment contrasts
+
 ```{r PM_Mv_Contrast}
-source("R/simple_summary.R")
+source("R/simple_summary.R") #function to provide a table that includes the treatment names in the contrasts
 summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none"))
@@
 profile(PM_mv, tau2 = 5)
-```
-
-Lets present the meta-analysis results for the moderator variables in a forest style plot.
-First lets create a table of the results.
-
-```{r metafor_results}
-results_AI <- data.frame(cbind(PM_mv$b,
-                               PM_mv$ci.lb,
-                               PM_mv$ci.ub))
-
-efficacy <- as_tibble(results_AI)
-efficacy$Treatment <-
-   factor(c(
-
-       "control",
-      "Early",
-      "Recommended",
-      "Recommended_plus",
-      "Late",
-      "Late_plus"
-   ))
-
-efficacy$se <- PM_mv$se
-colnames(efficacy) <-
-   c("Mean", "CIs_lower", "CI_upper", "Treatment", "SE")
-efficacy
-```
-
-Let's view these comparisons in a plot.
-
-```{r metafor_plot}
-YieldContrasts <- efficacy %>%
-   filter(Treatment != "control") %>% 
-   mutate(Treatment = factor(Treatment, levels = rev(
-      c(
-
-         "Early",
-         "Recommended",
-         "Recommended_plus",
-         "Late",
-         "Late_plus"
-      )
-   ))) %>%
-   ggplot(aes(Treatment, Mean)) +
-   geom_hline(
-      yintercept = seq(-0.05, 0.3, by = 0.05),
-      color = usq_cols("usq charcoal"),
-      linetype = 3
-   ) +
-   geom_hline(yintercept = 0) +
-   geom_point(aes(size = 1 / SE), shape = 15) +
-   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper)) +
-   coord_flip()
-
-YieldContrasts
 ```
@@
 ```{r Save_meta_data, eval=FALSE}
-save(efficacy, PM_MB_dat, PM_mv, YieldContrasts, contrast_Ssum, 
+save(efficacy, PM_MB_dat, PM_mv, contrast_Ssum, 
      file = here("cache/Meta-analysisData.Rdata"))

### 2020-12-16 02_Preliminary_analysis.Rmd
Add standard error to table

@@
              maximum_yield = max(grain_yield.t.ha.),
-             yield_stdev = sd(grain_yield.t.ha.)) %>%
+             yield_stdev = sd(grain_yield.t.ha.),
+             yield_SE = sd(grain_yield.t.ha.)/
+                              sqrt(n())) %>%
    kable(align = 'c',

### 2020-12-20 02_Preliminary_analysis.Rmd
Examine the output of a stacked bar graph

@@
    filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole")%>%
-   group_by(trial_ref, location, year)%>%
-   summarise(yield_gain_m = mean(yield_gain),
+             fungicide_ai == "propiconazole"|
+             fungicide_ai == "control")%>%
+   mutate(spray_NoSpray = factor(ifelse(fungicide_ai == "control","control","Fungicide treated"))) %>%
+   mutate(control_yield = ifelse(fungicide_ai == "control",grain_yield.t.ha.,NA))%>%
+   group_by(trial_ref, location, year,spray_NoSpray)%>%
+   summarise(yield_c = mean(control_yield),
+             yield_gain_m = mean(yield_gain, na.rm = TRUE),
              yield_gain_se = sd(yield_gain, na.rm = T)/sqrt(n()),
@@
    mutate(trial = paste(location,year,sep = "\n"))%>%
-   ggplot(aes(reorder(trial, yield_gain_m), yield_gain_m))+
-   geom_bar(stat = "identity")+
-   geom_errorbar(width = 0.3 ,aes(ymax = yield_gain_m + yield_gain_se, 
-                     ymin = yield_gain_m - yield_gain_se))+
-   theme(axis.text.x = element_text(angle = 90, hjust = 1))
+   mutate(yield = ifelse(spray_NoSpray == "control", yield_c, yield_gain_m))%>%
+   ggplot(aes(reorder(trial_ref, yield), yield, fill = (spray_NoSpray)))+
+   geom_col()+
+   # geom_errorbar(width = 0.3 ,aes(ymax = yield_gain_m + yield_gain_se, 
+   #                   ymin = yield_gain_m - yield_gain_se))+
+   theme(axis.text.x = element_text(angle = 90, hjust = 1))+
+   scale_fill_usq() +
+   scale_colour_usq()
 
@@
              fungicide_ai == "propiconazole") %>%
-   select(
-      trial_ref,
-      year,
-      location,
-      first_sign_disease,
-      fungicide_ai,
-      dose_ai.ha,
-      total_fungicide
-   ) %>%
    ggplot(aes(x = as.factor(dose_ai.ha), fill = fungicide_ai)) +

### 2020-12-21 02_Preliminary_analysis.Rmd
graph mean yield per trial grouped by treatmented non-treated

@@
    filter(fungicide_ai == "control")%>%
-   summarise(mean_yield = mean(grain_yield.t.ha.),
-             minimum_yield = min(grain_yield.t.ha.),
-             maximum_yield = max(grain_yield.t.ha.),
-             yield_stdev = sd(grain_yield.t.ha.),
-             yield_SE = sd(grain_yield.t.ha.)/
+   summarise(mean_yield = mean(grain_yield.t.ha. * 1000),
+             minimum_yield = min(grain_yield.t.ha. * 1000),
+             maximum_yield = max(grain_yield.t.ha. * 1000),
+             yield_stdev = sd(grain_yield.t.ha. * 1000),
+             yield_SE = sd(grain_yield.t.ha. * 1000)/
                               sqrt(n())) %>%
@@
              yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
+   kable(align = 'c',
+   caption = "Average yield statistics for DMI fungicide treated plots")
+
+```
+
+Trial mean yields in DMI fungicide treated plots
+```{r Yield_DMITrials}
+PM_MB_dat %>%
+   group_by(trial_ref, location, year)%>%
+   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
+             minimum_yield = min(grain_yield.t.ha.*1000),
+             maximum_yield = max(grain_yield.t.ha.*1000),
+             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
+   arrange(yield_sterr) %>%
    kable(align = 'c',
@@
 
-```{r YieldGain_plot}
+```{r Yield_plot}
+
+bw_labels <- 
    PM_MB_dat %>%
    filter(trial_ref %in% DMITrials)%>% 
-   filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole"|
-             fungicide_ai == "control")%>%
-   mutate(spray_NoSpray = factor(ifelse(fungicide_ai == "control","control","Fungicide treated"))) %>%
-   mutate(control_yield = ifelse(fungicide_ai == "control",grain_yield.t.ha.,NA))%>%
-   group_by(trial_ref, location, year,spray_NoSpray)%>%
-   summarise(yield_c = mean(control_yield),
-             yield_gain_m = mean(yield_gain, na.rm = TRUE),
-             yield_gain_se = sd(yield_gain, na.rm = T)/sqrt(n()),
-             .groups = "drop")%>%
-   mutate(trial = paste(location,year,sep = "\n"))%>%
-   mutate(yield = ifelse(spray_NoSpray == "control", yield_c, yield_gain_m))%>%
-   ggplot(aes(reorder(trial_ref, yield), yield, fill = (spray_NoSpray)))+
-   geom_col()+
-   # geom_errorbar(width = 0.3 ,aes(ymax = yield_gain_m + yield_gain_se, 
-   #                   ymin = yield_gain_m - yield_gain_se))+
-   theme(axis.text.x = element_text(angle = 90, hjust = 1))+
-   scale_fill_usq() +
-   scale_colour_usq()
+   group_by(trial_ref, location, year)%>%
+   summarise(m_gy = mean(grain_yield.t.ha.)) %>%
+   mutate(trial = paste(location,year,sep = "\n")) %>%
+   arrange(m_gy) %>%
+   pull(trial)
+
+bw_labels[1] <- paste0(bw_labels[1],"(b)")
+bw_labels[3] <- paste0(bw_labels[3],"(a)")
+
+fungicide_spray_plot <- 
+   PM_MB_dat %>%
+   filter(trial_ref %in% DMITrials)%>%  
+   mutate(spray_treat = ifelse(fungicide_ai == "control","control", "DMI spray"))%>%
+   group_by(trial_ref, location, year)%>%
+   ggplot(aes(reorder(trial_ref, grain_yield.t.ha.), grain_yield.t.ha., colour = spray_treat))+
+   geom_boxplot()+
+   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
+   xlab("Trial location and year")+
+   ylab(bquote('Mungbean yeild  '*t~ha^-1*''))+
+   scale_x_discrete(labels = bw_labels)+
+   ylim(0,2.5)+
+   scale_colour_usq()+
+   labs(colour = "Fungicide treatment")
 

### 2021-01-05 04_MetaAnalysis.Rmd
test compound symetry VCV matrix and update means difference figure

@@
 
-The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis.
+Lets try the model with an implied simpler variance-covariance matrix "compound symetry" ("CS") to examine if unstructured matrix is suitable.
+```{r}
+PM_mv_cs <- rma.mv(
+   yi = grain_yield.t.ha.,
+   vi,
+   mods = ~ spray_management,
+   method = "ML",
+   random = list(~ spray_management | trial, ~1 | id), 
+   struct = "CS",
+   control=list(optimizer="optim"),
+   data = PM_MB_dat
+)
+
+anova(PM_mv, PM_mv_cs)
+```
+
+The test shows that the 'Full', more complicated model `PM_mv`, is a better fit and therefore we should keep the unstructured variance-covariance matrix.
+
+The first table in the `PM_mv` output shows tau^2 (between trial variance) of each moderator random effects and the number of occurrences for each treatment in the analysis.
 This effectively shows the heterogeneity between experiments for these particular treatments.
@@
       c(
-
          "Early",
@@
    geom_linerange(aes(ymin = `$CI_{L}$`, ymax = `$CI_{U}$`)) +
-   coord_flip()+
-   ggtitle("Mean spray schedule effect sizes\nand 95% confidence intervals")
-
+   coord_flip() +
+   #ggtitle("Mean spray schedule effect sizes\nand 95% confidence intervals")+
+   ylab(expression(paste("Mean yield difference to control (t ha" ^ -1,")",sep = ""))) +
+   scale_x_discrete(
+      "Moderator variable",
+      labels = c(
+         expression("Late"["plus"]),
+         expression("Late"["single"]),
+         expression("Recommended"["plus"]),
+         expression("Recommended"["single"]),
+         expression("Early"["single"])
+      )
+   )
+ggsave("paper/figures/Fig2_means_difference.png")
 ```
@@
 profile(PM_mv, tau2 = 5)
+profile(PM_mv, tau2 = 6)
 ```

### 2021-01-18 02_Preliminary_analysis.Rmd
Update yield box and whisker plot and create Full trial summary table

@@
    filter(trial_ref %in% DMITrials)%>%  
-   mutate(spray_treat = ifelse(fungicide_ai == "control","control", "DMI spray"))%>%
+   mutate(spray_treat = ifelse(fungicide_ai == "control","control", "Fungicide treated"))%>%
    group_by(trial_ref, location, year)%>%
-   ggplot(aes(reorder(trial_ref, grain_yield.t.ha.), grain_yield.t.ha., colour = spray_treat))+
+   ggplot(aes(reorder(trial_ref, grain_yield.t.ha.), grain_yield.t.ha., fill = spray_treat))+
    geom_boxplot()+
@@
    xlab("Trial location and year")+
-   ylab(bquote('Mungbean yeild  '*t~ha^-1*''))+
+   ylab(bquote('Mungbean yield  '*t~ha^-1*''))+
    scale_x_discrete(labels = bw_labels)+
    ylim(0,2.5)+
-   scale_colour_usq()+
-   labs(colour = "Fungicide treatment")
+   scale_fill_grey(start = 1, end = 0.7)+
+   labs(colour = "Fungicide treatment")+
+   guides(fill = guide_legend(title = "Treatment"))
 
+fungicide_spray_plot
+#ggsave("paper/figures/Fig1_trial_yield_bw.png")
 ```
@@
 <br>
+
+#### Full trial summary
+
+```{r Full_Trial_Summary_table}
+PM_MB_dat %>%
+   filter(
+      fungicide_ai == "control" |
+         fungicide_ai == "tebuconazole" |
+         fungicide_ai == "propiconazole"
+   ) %>%
+   mutate(PM_sev_control = case_when(fungicide_ai == "control" ~ PM_final_severity,
+                                     TRUE ~ NA_real_)) %>%
+   mutate(PM_sev_treat = case_when(fungicide_ai != "control" ~ PM_final_severity,
+                                     TRUE ~ NA_real_)) %>%
+   mutate(PM_y_control = case_when(fungicide_ai == "control" ~ grain_yield.t.ha.,
+                                     TRUE ~ NA_real_)) %>%
+   mutate(PM_y_treat = case_when(fungicide_ai != "control" ~ grain_yield.t.ha.,
+                                     TRUE ~ NA_real_)) %>%
+
+   # filter(location == "Bongeen_1")%>%
+   # select(PM_sev_treat,
+   #        trial_ref,
+   #          location,
+   #          year,
+   #          planting_date,
+   #          first_sign_disease)
+
+   group_by(trial_ref,
+            location,
+            year,
+            planting_date,
+            first_sign_disease) %>%
+   summarise(n = n(),
+             m_PM_sev_control = mean(PM_sev_control, na.rm = TRUE),
+             min_PM_sev = min(PM_sev_treat, na.rm = TRUE),
+             max_PM_sev = max(PM_sev_treat, na.rm = TRUE),
+             m_PM_yeild_control = mean(PM_y_control, na.rm = TRUE),
+             min_PM_yeild = min(PM_y_treat, na.rm = TRUE),
+             max_PM_yeild = max(PM_y_treat, na.rm = TRUE)
+             )%>%
+   filter(min_PM_sev < 10) # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf
+
+```
 

### 2021-01-18 02_Preliminary_analysis.Rmd
remove commented lines and add flextable library to load

@@
                kableExtra,
+               flextable,
                here)
@@
                                      TRUE ~ NA_real_)) %>%
-
-   # filter(location == "Bongeen_1")%>%
-   # select(PM_sev_treat,
-   #        trial_ref,
-   #          location,
-   #          year,
-   #          planting_date,
-   #          first_sign_disease)
-
    group_by(trial_ref,
@@
              min_PM_yeild = min(PM_y_treat, na.rm = TRUE),
-             max_PM_yeild = max(PM_y_treat, na.rm = TRUE)
+             max_PM_yeild = max(PM_y_treat, na.rm = TRUE),
              )%>%

### 2021-01-18 02_Preliminary_analysis.Rmd
Parse into a flextable with named headings

@@
 
-```{r Full_Trial_Summary_table}
+```{r Full_Trial_Summary_table, warning= FALSE}
 PM_MB_dat %>%
@@
              )%>%
-   filter(min_PM_sev < 10) # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf
-
+   filter(min_PM_sev < 10) %>% # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf
+   flextable() %>%
+   set_header_labels(trial_ref = "Trial code",
+                     location = "Location",
+                     year = "Year",
+                     planting_date = "Sowing date",
+                     first_sign_disease = "PM onset date",
+                     n = "n treatments",
+                     m_PM_sev_control = "Control mean PM severity",
+                     min_PM_sev = "Minimum PM severity*",
+                     max_PM_sev = "Maximum PM severity*",
+                     m_PM_yeild_control = "Control mean yeild",
+                     min_PM_yeild = "Minimum yeild*",
+                     max_PM_yeild = "Maximum yeild*"
+                     )
 ```

### 2021-01-19 02_Preliminary_analysis.Rmd
Correct spelling, combine max min columns to a range

--- 2021-01-18 02_Preliminary_analysis.Rmd
@@
 
-      # insert NA as yeild_gain and proportional yield gain for the controls
+      # insert NA as yield_gain and proportional yield gain for the controls
       dat2[dat2$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
@@
 
-```{r Full_Trial_Summary_table}
+```{r Full_Trial_Summary_table, warning= FALSE}
+Sev_yield_table <-
 PM_MB_dat %>%
@@
    summarise(n = n(),
-             m_PM_sev_control = mean(PM_sev_control, na.rm = TRUE),
-             min_PM_sev = min(PM_sev_treat, na.rm = TRUE),
-             max_PM_sev = max(PM_sev_treat, na.rm = TRUE),
-             m_PM_yeild_control = mean(PM_y_control, na.rm = TRUE),
-             min_PM_yeild = min(PM_y_treat, na.rm = TRUE),
-             max_PM_yeild = max(PM_y_treat, na.rm = TRUE),
+             m_PM_sev_control = round(mean(PM_sev_control, na.rm = TRUE),digits = 2),
+             min_PM_sev = round(min(PM_sev_treat, na.rm = TRUE),digits = 2),
+             max_PM_sev = round(max(PM_sev_treat, na.rm = TRUE),digits = 2),
+             m_PM_yield_control = round(mean(PM_y_control, na.rm = TRUE),digits = 3),
+             min_PM_yield = round(min(PM_y_treat, na.rm = TRUE),digits = 3),
+             max_PM_yield = round(max(PM_y_treat, na.rm = TRUE),digits = 3),
              )%>%
-   filter(min_PM_sev < 10) # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf
+   filter(min_PM_sev < 10) %>% # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf
+   arrange(year)%>%
+   mutate(PM_sev_range = paste(min_PM_sev, max_PM_sev, sep = " - "))%>%
+   mutate(yield_range = paste(min_PM_yield, max_PM_yield, sep = " - "))%>%
+   select(-c(min_PM_sev,max_PM_sev,min_PM_yield,max_PM_yield)) %>%
+   flextable() %>%
+   set_header_labels(trial_ref = "Trial code",
+                     location = "Location",
+                     year = "Year",
+                     planting_date = "Sowing date",
+                     first_sign_disease = "PM onset date",
+                     n = "n",
+                     m_PM_sev_control = "Control mean\nPM severity",
+                     PM_sev_range = "PM severity\nrange*",
+                     m_PM_yield_control = "Control\nmean yield",
+                     yield_range = "Yield range\n(t / ha)*"
+                     ) %>%
+   fontsize(size = 8,part = "body")%>%
+   fontsize(size = 10, part = "header")%>%
+   align(j = 3:10, align = "center", part = "all") %>%
+   padding(j = 4:5, padding.left = 2) %>%
+   autofit() %>%
+   set_caption("Table1: Mean values of the trials included in the meta-analysis.
+Powdery mildew (PM) onset, number of treatments per trial (n), PM mean plot severity of the non-fungicide treated plots and the severity range in fungicide treatments; Mean yield in non-fungicide treated control and the range of yields in the fungicide treatments in tonnes per hectare")
+Sev_yield_table
+
+doc <- officer::read_docx()
+doc <- body_add_flextable(doc, value = Sev_yield_table)
+print(doc, target = "paper/figures/Table1_severity&yield.docx")
 

### 2021-01-19 02_Preliminary_analysis.Rmd
A few edits to the Summary table

--- 2021-01-18 02_Preliminary_analysis.Rmd
@@
    summarise(n = n(),
-             m_PM_sev_control = mean(PM_sev_control, na.rm = TRUE),
-             min_PM_sev = min(PM_sev_treat, na.rm = TRUE),
-             max_PM_sev = max(PM_sev_treat, na.rm = TRUE),
-             m_PM_yeild_control = mean(PM_y_control, na.rm = TRUE),
-             min_PM_yeild = min(PM_y_treat, na.rm = TRUE),
-             max_PM_yeild = max(PM_y_treat, na.rm = TRUE),
-             )%>%
-   filter(min_PM_sev < 10) # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf
+             m_PM_sev_control = round(mean(PM_sev_control, na.rm = TRUE),digits = 2),
+             min_PM_sev = round(min(PM_sev_treat, na.rm = TRUE),digits = 2),
+             max_PM_sev = round(max(PM_sev_treat, na.rm = TRUE),digits = 2),
+             m_PM_yield_control = round(mean(PM_y_control, na.rm = TRUE),digits = 3),
+             min_PM_yield = round(min(PM_y_treat, na.rm = TRUE),digits = 3),
+             max_PM_yield = round(max(PM_y_treat, na.rm = TRUE),digits = 3),
+             .groups = "drop")%>%
+   filter(min_PM_sev < 10) %>% # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf
+   arrange(year)%>%
+   mutate(PM_sev_range = paste(min_PM_sev, max_PM_sev, sep = " - "))%>%
+   mutate(yield_range = paste(min_PM_yield, max_PM_yield, sep = " - "))%>%
+   select(-c(min_PM_sev,max_PM_sev,min_PM_yield,max_PM_yield)) %>%
+   flextable() %>%
+   set_header_labels(trial_ref = "Trial code",
+                     location = "Location",
+                     year = "Year",
+                     planting_date = "Sowing date",
+                     first_sign_disease = "PM onset",
+                     n = "n",
+                     m_PM_sev_control = "Control mean\nPM severity",
+                     PM_sev_range = "PM severity\nrange*",
+                     m_PM_yield_control = "Control\nmean yield",
+                     yield_range = "Yield range\n(t / ha)*"
+                     ) %>%
+   fontsize(size = 8,part = "body")%>%
+   fontsize(size = 10, part = "header")%>%
+   align(j = 3:10, align = "center", part = "all") %>%
+   autofit() %>%
+   width(j = 7:10, width = 0.9)%>%
+   width(j = 3, width = 0.5)%>%
+   set_caption("Table 1: Mean yield and severity for trials included in the meta-analysis.
+Powdery mildew (PM) onset, number of treatments per trial (n), PM mean plot severity of the non-fungicide treated plots and the severity range in fungicide treatments; Mean yield in non-fungicide treated control and the range of yields in the fungicide treatments in tonnes per hectare")
+Sev_yield_table
+
+doc <- officer::read_docx()
+doc <- body_add_flextable(doc, value = Sev_yield_table)
+doc <- officer::body_end_section_landscape(doc)
+print(doc, target = "paper/figures/Table1_severity&yield.docx")
 

### 2021-01-20 01_TrialsForInclusionInAnalysis.Rmd
removed unnecessary group code in summarise() function

@@
 PM_MB_dat %>%
-   group_by(fungicide_ai, trial_ref) %>%
-   summarise(groups = 'drop') %>%
+   group_by(fungicide_ai,trial_ref) %>%
+   summarise() %>%
    count(sort = TRUE) %>%

### 2021-01-20 02_Preliminary_analysis.Rmd
Add clarity on what the dataset contains DMI or all fungicides, and shift code order

@@
 
+All fungicide ai treatments are still contained in the `PM_MB_dat` data, so filtering the data might be necessary to only inspect DMI treatments.
+
 ### Descriptive statistics  
@@
 
-Lets look at how many trials were undertaken each season
+Lets look at how many trials were undertaken each season in trials including DMI fungicides.
 
@@
 
-Also the location of the trials
+Also the location of the trials including DMI fungicides.
 
@@
 
-Various factors have been studied in the previous experiments which may influence the subsequent meta-analysis.
-On this page, unless stated, the following plots and analyses were made disregarding other effects.
-The following factors are postulated to influence mungbean grain yield and/or powdery mildew mean plot severity.
+#### Full trial summary
 
-   1 Fungicide type
-
-   2 Fungicide dose (varies only slightly within some fungicide types)
-
-   3 Number of fungicide sprays
-
-   4 Timing of fungicide spray/s relative to first sign of disease
-
-   5 Host cultivar (probably is a co-variate with season due to changing cultivars over time)
-
-   6 Experiment location
-
-   7 Row spacing
-
-   8 Final disease rating / disease pressure
-
-The data plotted below are from `r length(unique(PM_MB_dat$trial_ref))` field trials between (`r first(levels(PM_MB_dat$year))` - `r last(levels(PM_MB_dat$year))`) of which the details are described in the [Trials considered for inclusion in meta-analysis section](#Trials-considered-for-inclusion-in-meta-analysis).
-
-<br>
-<br>
-<br>
-
-#### Full trial summary
+Lets inspect a summary of both powdery mildew severity and grain yield for trials including DMI funcgicides.
 
@@
 ```
+
+Various factors have been studied in the previous experiments which may influence the subsequent meta-analysis.
+On this page, unless stated, the following plots and analyses were made disregarding other effects.
+The following factors are postulated to influence mungbean grain yield and/or powdery mildew mean plot severity.
+
+   1 Fungicide type
+
+   2 Fungicide dose (varies only slightly within some fungicide types)
+
+   3 Number of fungicide sprays
+
+   4 Timing of fungicide spray/s relative to first sign of disease
+
+   5 Host cultivar (probably is a co-variate with season due to changing cultivars over time)
+
+   6 Experiment location
+
+   7 Row spacing
+
+   8 Final disease rating / disease pressure
+
+The data plotted below are from `r length(unique(PM_MB_dat$trial_ref))` field trials between (`r first(levels(PM_MB_dat$year))` - `r last(levels(PM_MB_dat$year))`) of which the details are described in the [Trials considered for inclusion in meta-analysis section](#Trials-considered-for-inclusion-in-meta-analysis).
+
+<br>
+<br>
+<br>
 

### 2021-01-20 02_Preliminary_analysis.Rmd
move save table to docx to it's own chunk

@@
 Sev_yield_table
+```
 
+```{r eval=FALSE, include=FALSE}
+# Save table as a word document
 doc <- officer::read_docx()

### 2021-01-20 02_Preliminary_analysis.Rmd
correct table footnote syntax

@@
    column_spec(c(2, 3), width = "1cm") %>%
-   footnote(general = "Fungicides with less than five observations were omitted from this table")
+   kableExtra::add_footnote(label = "Fungicides with less than five observations were omitted from this table")
 ```

### 2021-01-20 03_Prep_data.Rmd
Remove code removing trials not reporting variance, already done;
correct KableExtra::add_footnote syntax

@@
          align = "c") %>%
-   footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
+   kableExtra::add_footnote(label = "DMI - demethylation inhibitors (tebuconazole and propiconazole).", notation = "none")
 ```
@@
 Mean differences won't be used as we are following the methodology of a ARM-based model, where mean differences are calculated following the meta-analysis.
-
-### Formatting Variance
-
-First let's check for any entries missing variance and remove them.
-
-```{r remove_studies}
-any(is.na(PM_MB_dat$yield_error))
-
-PM_MB_dat <-
-   PM_MB_dat[!is.na(PM_MB_dat$yield_error), ]
-
-PM_MB_dat$vi <- PM_MB_dat$yield_error
-```
 

### 2021-01-20 04_MetaAnalysis.Rmd
Edit estimates table; and apply stylr

@@
 # Data
-load("cache/PrepData.Rdata")
+load("cache/PrepData.Rdata"
+)
 ```
@@
    method = "ML",
-   random = list(~ spray_management | trial, ~1 | id), 
+   random = list( ~ spray_management | trial, ~ 1 | id),
    struct = "UN",
-   control=list(optimizer="optim"),
+   control = list(optimizer = "optim"),
    data = PM_MB_dat
@@
    method = "ML",
-   random = list(~ spray_management | trial, ~1 | id), 
+   random = list( ~ spray_management | trial, ~ 1 | id),
    struct = "CS",
-   control=list(optimizer="optim"),
+   control = list(optimizer = "optim"),
    data = PM_MB_dat
@@
 ```{r metafor_results}
-
-k5 <- as.data.frame(table(PM_MB_dat$trial, PM_MB_dat$spray_management)) %>%
-   filter(Freq !=0)%>%
-   group_by(Var2)%>%
-   summarise(n())%>%
+# obtain number of treatments included in each moderator variable
+k5 <-
+   as.data.frame(table(PM_MB_dat$trial, PM_MB_dat$spray_management)) %>%
+   filter(Freq != 0) %>%
+   group_by(Var2) %>%
+   summarise(n()) %>%
    pull()
 
-results_mv <- data.frame(N = PM_mv$g.levels.k,
+# create data.frame
+results_mv <- data.frame(
+   N = PM_mv$g.levels.k,
    k = k5,
-                         Effect = round(PM_mv$b,4),
-                         se = round(PM_mv$se,4),
-                         CI_lower = round(PM_mv$ci.lb,4),
-                         CI_upper = round(PM_mv$ci.ub,4),
-                         z_val = round(PM_mv$zval,4),
-                         p_val = reportP(PM_mv$pval,AsNumeric = TRUE),
-                         row.names = c("Intercept",
+   Effect = round(PM_mv$b, 4),
+   se = round(PM_mv$se, 4),
+   CI_lower = round(PM_mv$ci.lb, 4),
+   CI_upper = round(PM_mv$ci.ub, 4),
+   z_val = round(PM_mv$zval, 4),
+   p_val = reportP(PM_mv$pval, AsNumeric = TRUE)
+)
+
+# adjust estimates to show absolute means
+results_mv <-
+   results_mv[2:6, ] %>%
+   mutate(Effect = Effect + results_mv$Effect[1]) %>%
+   mutate(CI_lower = CI_lower + results_mv$CI_lower[1]) %>%
+   mutate(CI_upper = CI_upper + results_mv$CI_upper[1]) %>%
+   bind_rows(results_mv[1, ]) %>%
+   mutate(index = c(2:6, 1)) %>%
+   arrange(index)
+
+# rename colnames to give table headings
+colnames(results_mv)[c(1:4, 6:9)] <-
+   c("Treatment",
+     "$N$",
+     "$k$",
+     "$\\mu$",
+     "$CI_{L}$",
+     "$CI_{U}$",
+     "$Z$",
+     "$P$")
+
+# provide rownames for each moderator variable
+row.names(results_mv) <- c(
+   "Intercept / No Spray control",
    "$Early_{single}$",
@@
    "$Late_{single}$",
-                                       "$Late_{plus}$"))
+   "$Late_{plus}$"
+)
 
-colnames(results_mv)[c(1:4,6:9)] <- c("Treatment","$N$", "$k$","$\\mu$","$CI_{L}$","$CI_{U}$", "$Z$","$P$")
-
-kable(results_mv[,2:9],
+kable(results_mv[, 2:9],
       align = "lcccccccc",
       booktabs = TRUE,
-      caption = "Table ##: Mean effect size of five spray schedule treatments on mitigating yield losses to powdery mildew in mungbean crops grown in eastern Australia.
-Effect sizes were estimated from the network meta-analysis of data obtained from grey literature reports.
-Intercept indicates the mean of the no spray control and the treatments show the mean difference to the intercept")
+      caption = "Table ##: Estimated mean mungbean yields for each spray schedule treatment used for mitigating yield losses to powdery mildew in mungbean crops grown in eastern Australia.
+Yield estimates were calculated from the network meta-analysis of data obtained from grey literature reports.
+Z and P values indicate statistical significance in comparison to the intercept.")
 
@@
    #ggtitle("Mean spray schedule effect sizes\nand 95% confidence intervals")+
-   ylab(expression(paste("Mean yield difference to control (t ha" ^ -1,")",sep = ""))) +
+   ylab(expression(paste(
+      "Mean yield difference to control (t ha" ^ -1, ")", sep = ""
+   ))) +
    scale_x_discrete(
@@
    )
-ggsave("paper/figures/Fig2_means_difference.png")
+ggsave("paper/figures/Fig2_means_difference.png",
+       height = 3,
+       dpi = 500)
 ```
@@
 source("R/simple_summary.R") #function to provide a table that includes the treatment names in the contrasts
-summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none"))
-contrast_Ssum <- simple_summary(summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none")))
+summary(glht(PM_mv, linfct = cbind(contrMat(rep(
+   1, 6
+), type = "Tukey"))), test = adjusted("none"))
+contrast_Ssum <-
+   simple_summary(summary(glht(PM_mv, linfct = cbind(
+      contrMat(rep(1, 6), type = "Tukey")
+   )), test = adjusted("none")))
 contrast_Ssum
@@
 par(mar = c(5, 13, 4, 2) + 0.1)
-plot(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), yaxt='n')
-axis(2, at = seq_along(contrast_Ssum$contrast), labels = rev(contrast_Ssum$contrast), las=2, cex.axis = 0.8)
+plot(glht(PM_mv, linfct = cbind(contrMat(rep(
+   1, 6
+), type = "Tukey"))), yaxt = 'n')
+axis(
+   2,
+   at = seq_along(contrast_Ssum$contrast),
+   labels = rev(contrast_Ssum$contrast),
+   las = 2,
+   cex.axis = 0.8
+)
 ```
@@
    mutate(spray_management =
-             factor(spray_management, 
-                    levels = c("Early","Late","Recommended",
-                    "Recommended_plus","Late_plus"))) %>%
+             factor(
+                spray_management,
+                levels = c(
+                   "Early",
+                   "Late",
+                   "Recommended",
+                   "Recommended_plus",
+                   "Late_plus"
+                )
+             )) %>%
    arrange(desc(spray_management), location, desc(grain_yield.t.ha.)) %>%
-   mutate(ID2 = order(ID))%>%
+   mutate(ID2 = order(ID)) %>%
    pull(ID2)
@@
 ### this list can be used below to reference where to plot each variable
-rows1 <- forest_rows(head_row = 186, 
+rows1 <- forest_rows(
+   head_row = 186,
    ord_var = PM_MB_dat$spray_management,
@@
    gap = 5,
-                     row_offset = -2)
+   row_offset = -2
+)
 
 ### A data-frame of meta-model coefficients used to produce the summary polygons for each treatment
-polys <- data.frame(ref = change_labels(names(coef(PM_mv))),
-                    x = c(coef(PM_mv)[1],coef(PM_mv)[1] + coef(PM_mv)[2:6]),
-                    ci.lb = c(PM_mv$ci.lb[1],PM_mv$ci.lb[1] +PM_mv$ci.lb[2:6]),
-                    ci.ub = c(PM_mv$ci.ub[1],PM_mv$ci.ub[1] +PM_mv$ci.ub[2:6]))[c(2,5,3,4,6,1),]
+polys <- data.frame(
+   ref = change_labels(names(coef(PM_mv))),
+   x = c(coef(PM_mv)[1], coef(PM_mv)[1] + coef(PM_mv)[2:6]),
+   ci.lb = c(PM_mv$ci.lb[1], PM_mv$ci.lb[1] + PM_mv$ci.lb[2:6]),
+   ci.ub = c(PM_mv$ci.ub[1], PM_mv$ci.ub[1] + PM_mv$ci.ub[2:6])
+)[c(2, 5, 3, 4, 6, 1), ]
 polys$rows <- rows1$pred_row - 1.5
 
-forest1  <- metafor::forest(PM_mv, cex = 1.15 , width = 5,
+forest1  <- metafor::forest(
+   PM_mv,
+   cex = 1.15 ,
+   width = 5,
    #order = "fit",
-                rows = rows1$trows-1.5,
-                ilab = cbind(PM_MB_dat$year, 
-                             PM_MB_dat$row_spacing, PM_MB_dat$host_genotype, PM_MB_dat$dose),
-                ilab.xpos = c(-2.35,-2.1,-1.8,-1.4)+1,
+   rows = rows1$trows - 1.5,
+   ilab = cbind(
+      PM_MB_dat$year,
+      PM_MB_dat$row_spacing,
+      PM_MB_dat$host_genotype,
+      PM_MB_dat$dose
+   ),
+   ilab.xpos = c(-2.35, -2.1, -1.8, -1.4) + 1,
    slab = NA,
    xlim = c(-2, 4),
-                ylim = c(5,190),
+   ylim = c(5, 190),
    xlab = "Grain yield mean difference",
    addfit = FALSE,
-                efac = c(0.2,0.15,0.2),
-                at = seq(-0.5,3, 0.5))
+   efac = c(0.2, 0.15, 0.2),
+   at = seq(-0.5, 3, 0.5)
+)
 
@@
 ```{r Save_meta_data, eval=FALSE}
-save(efficacy, PM_MB_dat, PM_mv, contrast_Ssum, 
+save(efficacy,
+     PM_MB_dat,
+     PM_mv,
+     contrast_Ssum,
      file = here("cache/Meta-analysisData.Rdata"))

### 2021-01-20 01_TrialsForInclusionInAnalysis.Rmd
Add note that we hav e yet to exclude non-DMI fungicides from the dataset
edit chunk name

@@
 
-```{r FinalTrialsForInclusion}
+```{r Final_Trials_For_Inclusion}
 PM_MB_dat %>%
@@
 Finally we are going to define the class of each variable in the data, retaining only the variables relevant to the analysis. 
+It should be noted that the data-set below has still retained all fungicide active ingredients. 
+Before dropping the non-DMI fungicides from the final meta-analysis we will inspect their influence on grain yield.
 

### 2021-01-20 02_Preliminary_analysis.Rmd
Edit duplicate chunk names

@@
 
-Trial mean yields in DMI fungicide treated plots
-```{r Yield_DMITrials}
+Trial mean yields in all fungicide treated plots
+```{r Yield_AllTrials}
 PM_MB_dat %>%

### 2021-01-20 03_Prep_data.Rmd
Save full dataset to object before slimming

@@
 ```{r simplifyData}
+PM_MB_dat_full <- PM_MB_dat
+
 PM_MB_dat <- 
@@
 ```{r saveData_PrepD}
-save(PM_MB_dat, file = here("cache/PrepData.Rdata"))
+save(PM_MB_dat, PM_MB_dat_full, file = here("cache/PrepData.Rdata"))
 ```

### 2021-01-20 05_Post-hoc_analysis_Investigation.Rmd
edit data variable names

@@
 ```{r age_andYield}
-dat1 <- PM_MB_dat %>%
+dat1 <- PM_MB_dat_full %>%
    mutate(days2PM = first_sign_disease - planting_date) %>%
@@
       days2PM,
-      grain_yield.t.ha,
+      grain_yield.t.ha.,
       yield_gain,
-      prop_yield_gain,
       AUDPC_m,
-      D_pres,
       PM_final_severity

### 2021-01-20 05_Post-hoc_analysis_Investigation.Rmd
correct object names

@@
 
-Let's estimate the age of the crop based on crop maturity observations, we will use the `PM_MB_dat` which include some observations of crop maturity.
+Let's estimate the age of the crop based on crop maturity observations, we will use the `PM_MB_dat_full` which include some observations of crop maturity.
 
 ```{r whatAreTheAges}
-dat2 <- PM_MB_dat %>%
+dat2 <- PM_MB_dat_full %>%
    mutate(

### 2021-01-22 02_Preliminary_analysis.Rmd
change mean to median on summary table

@@
    summarise(n = n(),
-             m_PM_sev_control = round(mean(PM_sev_control, na.rm = TRUE),digits = 2),
+             m_PM_sev_control = round(median(PM_sev_control, na.rm = TRUE),digits = 2),
              min_PM_sev = round(min(PM_sev_treat, na.rm = TRUE),digits = 2),
@@
                      n = "n",
-                     m_PM_sev_control = "Control mean\nPM severity",
+                     m_PM_sev_control = "Control median\nPM severity",
                      PM_sev_range = "PM severity\nrange*",

### 2021-01-22 02_Preliminary_analysis.Rmd
Add number of controls and remove "mung" string in summary table1

--- 2021-01-20 02_Preliminary_analysis.Rmd
@@
                                      TRUE ~ NA_real_)) %>%
+   mutate(trial_ref = str_remove(trial_ref, "mung"))%>%  # remove "mung" prefix from trial_ref
    group_by(trial_ref,
@@
    summarise(n = n(),
-             m_PM_sev_control = round(mean(PM_sev_control, na.rm = TRUE),digits = 2),
+             m_PM_sev_control = round(median(PM_sev_control, na.rm = TRUE),digits = 2),
+             n_controls = sum(is.na(PM_sev_control) == FALSE),
              min_PM_sev = round(min(PM_sev_treat, na.rm = TRUE),digits = 2),
@@
    arrange(year)%>%
-   mutate(PM_sev_range = paste(min_PM_sev, max_PM_sev, sep = " - "))%>%
-   mutate(yield_range = paste(min_PM_yield, max_PM_yield, sep = " - "))%>%
-   select(-c(min_PM_sev,max_PM_sev,min_PM_yield,max_PM_yield)) %>%
+   mutate(PM_sev_range = paste(min_PM_sev, max_PM_sev, sep = " - ")) %>%
+   mutate(yield_range = paste(min_PM_yield, max_PM_yield, sep = " - ")) %>%
+   mutate(m_PM_sev_control = paste(m_PM_sev_control, " (", n_controls, ")", sep = "")) %>%
+   select(-c(min_PM_sev, max_PM_sev, min_PM_yield, max_PM_yield)) %>%
    flextable() %>%
@@
                      n = "n",
-                     m_PM_sev_control = "Control mean\nPM severity",
+                     m_PM_sev_control = "Control median\nPM severity",
+                     n_controls = "n controls",
                      PM_sev_range = "PM severity\nrange*",

### 2021-01-22 02_Preliminary_analysis.Rmd
remove n_controls column and reorder columns

@@
    mutate(m_PM_sev_control = paste(m_PM_sev_control, " (", n_controls, ")", sep = "")) %>%
-   select(-c(min_PM_sev, max_PM_sev, min_PM_yield, max_PM_yield)) %>%
+   select(-c(min_PM_sev, max_PM_sev, min_PM_yield, max_PM_yield, n_controls)) %>%
+   select(c(1:7, 9, 8, 10)) %>% # order columns
    flextable() %>%
@@
                      m_PM_sev_control = "Control median\nPM severity",
-                     n_controls = "n controls",
                      PM_sev_range = "PM severity\nrange*",
@@
    autofit() %>%
-   width(j = 7:10, width = 0.9)%>%
+   width(j = 7:10, width = 1)%>%
    width(j = 3, width = 0.5)%>%

### 2021-01-22 02_Preliminary_analysis.Rmd
annotate note for bracketed numbers

--- 2021-01-22 02_Preliminary_analysis.Rmd
@@
                      m_PM_sev_control = "Control median\nPM severity",
-                     n_controls = "n controls",
                      PM_sev_range = "PM severity\nrange*",
-                     m_PM_yield_control = "Control\nmean yield",
-                     yield_range = "Yield range\n(t / ha)*"
+                     m_PM_yield_control = "Control\nmean yield*",
+                     yield_range = "Yield range\n(t / ha)"
                      ) %>%
@@
    autofit() %>%
-   width(j = 7:10, width = 0.9)%>%
+   width(j = 7:10, width = 1)%>%
    width(j = 3, width = 0.5)%>%
    set_caption("Table 1: Mean yield and severity for trials included in the meta-analysis.
-Powdery mildew (PM) onset, number of treatments per trial (n), PM mean plot severity of the non-fungicide treated plots and the severity range in fungicide treatments; Mean yield in non-fungicide treated control and the range of yields in the fungicide treatments in tonnes per hectare")
+Powdery mildew (PM) onset, number of treatments per trial (n), PM median plot severity of the non-fungicide treated plots and the severity range in fungicide treatments, * bracketed numbers refer to the number of pooled control treatments summarised; Mean yield in non-fungicide treated control and the range of yields in the fungicide treatments in tonnes per hectare")
 Sev_yield_table

### 2021-01-29 05_severity_metaAnalysis.Rmd
Initialise meta-analysis on final season severity

---
output: html_document
editor_options: 
  chunk_output_type: inline
---

# Meta-analysis of powdery mildew severity

```{r MEsummary_Libraries2, message=FALSE, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               kableExtra,
               bomrang,
               RColorBrewer,
               metafor,
               here,
               netmeta,
               multcomp,
               dplyr)

if (!require("theme.usq"))
   devtools::install_github("adamhsparks/theme.usq")
library(theme.usq)
theme_set(theme_usq())
#source(here("R/reportP.R"))

# Data
load("cache/PrepData.Rdata")
```

Which trials don't have all the required variance information?
```{r noDiseaseError}
unique(PM_MB_dat_full[is.na(PM_MB_dat_full$disease_error),
                      c("trial_ref", "location", "year")])
```

Eliminate trials with out disease severity variance.
```{r rm_SevDiseaseError}
PM_sev <- 
   PM_MB_dat_full %>%
   filter(is.na(disease_error) == FALSE)
```
Are all the reported disease variance the same type?
```{r sev_var_type}
unique(PM_sev[,"D_error_type"])
```

Now we have eliminated 2 trials do all spray management categories have sufficient replications
```{r treatment_n}
table(PM_sev$spray_management)
```

Convert variance to the same measure
```{r calc_sampleVar}
PM_sev <- 
   PM_sev %>%
   mutate(
      d_vi = 
         case_when(
            D_error_type == "stdev" ~ disease_error ^2,
            D_error_type == "lsd (P=0.05)" ~ 
               (replicates * ((disease_error / 1.96) ^2) /2)/replicates
         ),
      id = row_number(),
      spray_management = fct_relevel(spray_management,sort)
   )

```

Inspect for a normal distribution of disease severity
```{r sev_hist}
hist(PM_sev$PM_final_severity)
```

Let's get started with the analysis by first finding the best model fit that answers our research question.

> When, in relation to PM establishes in the crop, should farmers begin spraying mungbean to obtain the highest fungicide efficacy for lowering disease severity: before PM establishing,  immediately after first sign of PM establishing, or after PM has become established in the crop.

A secondary question to this aim is: does a second spray increase the efficacy?

To do this, in our model:

   - Powdery mildew severity 1-9 scale

   - Trial, which resolves combinations of categorical variables: year, location, row spacing, fungicide dose and cultivar; is set as a random intercept

   - We will investigate the effect size of our treatment - spray management,

```{r Metafor-Sev-analysis}
PMsev_mv <- rma.mv(
   yi = PM_final_severity,
   d_vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_sev
)

summary(PMsev_mv)
```

All spray schedules were effective at lowering the disease severity at the end of the season

```{r sevContrasts}
source("R/simple_summary.R") #function to provide a table that includes the treatment names in the contrasts

contrast_Ssum <-
   simple_summary(summary(glht(PMsev_mv, linfct = cbind(
      contrMat(rep(1, 6), type = "Tukey")
   )), test = adjusted("none")))

contrast_Ssum
```

```{r plotsevContrasts}
par(mar = c(5, 13, 4, 2) + 0.1)
plot(glht(PMsev_mv, linfct = cbind(contrMat(rep(
   1, 6
), type = "Tukey"))), yaxt = 'n')
axis(
   2,
   at = seq_along(contrast_Ssum$contrast),
   labels = rev(contrast_Ssum$contrast),
   las = 2,
   cex.axis = 0.8
)
```

### 2021-01-29 01_TrialsForInclusionInAnalysis.Rmd
Edits mainly spelling and grammar

@@
    2. Trial data needed to include:  
-      i) fungicide active ingredients.  
+      i) Fungicide active ingredients.  
       ii) A demethylase inhibitor (DMI) fungicide.  
@@
       v) Fungicide application dates.  
-      vi) fungicide dose.  
+      vi) Fungicide dose.  
       vii) Crop yield.  
-      viii) Treatment means and accompanying variance
+      viii) Treatment means and accompanying variance.
 
@@
    rbind(
-      read.csv(here("cache/2010 PMmung Hermitage means.csv"), stringsAsFactors = FALSE),
-      read.csv(here("cache/2011 PMmung Herm means.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/2011 PMmung Kingaroy means.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/AM1305_Goolhi_means.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/AM1304-MarysMount_means.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/AM1303-Premer-Disease_means.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/BB1305_Millmerran_means.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/Herm_16_means.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/King_16_means.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/Fogerty_17_mean.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/Hermitage_17_mean.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/Wellcamp_18_mean.csv"),stringsAsFactors = FALSE),
-      read.csv(here("cache/Hermitage_19_mean.csv"),stringsAsFactors = FALSE)
+      read.csv(
+         here("cache/2010 PMmung Hermitage means.csv"),
+         stringsAsFactors = FALSE
+      ),
+      read.csv(here("cache/2011 PMmung Herm means.csv"), stringsAsFactors = FALSE),
+      read.csv(
+         here("cache/2011 PMmung Kingaroy means.csv"),
+         stringsAsFactors = FALSE
+      ),
+      read.csv(here("cache/AM1305_Goolhi_means.csv"), stringsAsFactors = FALSE),
+      read.csv(
+         here("cache/AM1304-MarysMount_means.csv"),
+         stringsAsFactors = FALSE
+      ),
+      read.csv(
+         here("cache/AM1303-Premer-Disease_means.csv"),
+         stringsAsFactors = FALSE
+      ),
+      read.csv(
+         here("cache/BB1305_Millmerran_means.csv"),
+         stringsAsFactors = FALSE
+      ),
+      read.csv(here("cache/Herm_16_means.csv"), stringsAsFactors = FALSE),
+      read.csv(here("cache/King_16_means.csv"), stringsAsFactors = FALSE),
+      read.csv(here("cache/Fogerty_17_mean.csv"), stringsAsFactors = FALSE),
+      read.csv(here("cache/Hermitage_17_mean.csv"), stringsAsFactors = FALSE),
+      read.csv(here("cache/Wellcamp_18_mean.csv"), stringsAsFactors = FALSE),
+      read.csv(here("cache/Hermitage_19_mean.csv"), stringsAsFactors = FALSE)
    )
-write.csv(PM_MB_raw, file = here("cache/PM_Mungbean_SummaryOfTrialsWithRawData"), row.names = FALSE)
+write.csv(
+   PM_MB_raw,
+   file = here("cache/PM_Mungbean_SummaryOfTrialsWithRawData"),
+   row.names = FALSE
+)
 ```
@@
 ```{r import_dataMan}
-PM_MB_man <- read.csv(here("cache/PM_Mungbean_DataManuallyEntered.csv"), stringsAsFactors = FALSE)
+PM_MB_man <-
+   read.csv(here("cache/PM_Mungbean_DataManuallyEntered.csv"),
+            stringsAsFactors = FALSE)
 ```
@@
 PM_MB_dat <-
-   rbind(
-      PM_MB_raw,
-      PM_MB_man
-      )
+   rbind(PM_MB_raw,
+         PM_MB_man)
 ```
@@
       Location = unique(location),
-         `Replicates per treatment` = if(all(replicates[1] == replicates)){
-            as.character(replicates[1])}else{
-               as.character(paste(min(replicates),"-",max(replicates)))},
+      `Replicates per treatment` = if (all(replicates[1] == replicates)) {
+         as.character(replicates[1])
+      } else{
+         as.character(paste(min(replicates), "-", max(replicates)))
+      },
       `Planting date` = unique(planting_date),
@@
    ) %>%
-      arrange(Year)%>%
-   kable(caption = "Description of Experiments",
+   arrange(Year) %>%
+   kable(
+      caption = "Description of Experiments",
       align = "c",
-         col.names = c("Unique Trial\nReference","Year", "Location", "Replicates\nper treatments",
-                       "Planting date", "First sign\nof disease", "Fungicide\n treatments")
+      col.names = c(
+         "Unique Trial\nReference",
+         "Year",
+         "Location",
+         "Replicates\nper treatments",
+         "Planting date",
+         "First sign\nof disease",
+         "Fungicide\n treatments"
+      )
    )  %>%
    kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
-   column_spec(c(3,5:6), width = "3cm") %>% 
+   column_spec(c(3, 5:6), width = "3cm") %>%
    scroll_box(height = "500px") 
-
 ```
@@
 
-The following map displays experiment locations in the GRDC northern grain growing region which were considered for inclusion in this meta-analysis.
+The following map displays experiment locations in the GRDC Northern Grains Region, which were considered for inclusion in this meta-analysis.
 
@@
 
-Lets apply the selection criteria our dataset.  
-All trials identified for this meta-analysis reported: fungicide active ingredient, dose, first sign of disease. 
-Therefore no trials need to be removed to satisfy this criteria.
+Let's apply the selection criteria our dataset.  
+All trials identified for this meta-analysis reported:
+
+* fungicide active ingredient,
+* dose,
+* first sign of disease.
+
+Therefore no trials need to be removed to satisfy these criteria.
 
@@
 
-One more trial removed as it did not report disease severity.  
+One more was trial removed as it did not report disease severity.  
 ```{r TrialsWithotDisease}
@@
    summarise(No_Record_Of_Fungicide_Application_Dates = all(is.na(fungicide_application_1)),
-             .groups = 'drop')%>%
+             .groups = 'drop') %>%
    filter(No_Record_Of_Fungicide_Application_Dates)
@@
    summarise(No_Record_Of_Fungicide_Dose = all(is.na(dose_ai.ha)),
-             .groups = 'drop')%>%
+             .groups = 'drop') %>%
    filter(No_Record_Of_Fungicide_Dose)
@@
    group_by(trial_ref) %>%
-   summarise(location = location,
+   summarise(
+      location = location,
       year = year,
       No_Var = all(is.na(yield_error)),
-             .groups = 'drop')%>%
-   filter(No_Var)%>%
+      .groups = 'drop'
+   ) %>%
+   filter(No_Var) %>%
    distinct(trial_ref, year, location)
@@
 PM_MB_dat %>%
-   group_by(fungicide_ai,trial_ref) %>%
+   group_by(fungicide_ai, trial_ref) %>%
    summarise() %>%
@@
 The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in the highest frequencies.
-Thee DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.
+The DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.
 
@@
    filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole")%>%
-   distinct(trial_ref, location, year)%>%
+             fungicide_ai == "propiconazole") %>%
+   distinct(trial_ref, location, year) %>%
    arrange(year) 
@@
 
-Finally we are going to define the class of each variable in the data, retaining only the variables relevant to the analysis. 
+Finally, we are going to define the class of each variable in the data, retaining only the variables relevant to the analysis. 
 It should be noted that the data-set below has still retained all fungicide active ingredients. 
@@
    mutate(first_sign_disease = ymd(first_sign_disease)) %>%
-   mutate(fungicide_ai = as.character(fungicide_ai))%>%
-   mutate(dose_ai.ha = round(as.double(dose_ai.ha), digits = 2))%>%
+   mutate(fungicide_ai = as.character(fungicide_ai)) %>%
+   mutate(dose_ai.ha = round(as.double(dose_ai.ha), digits = 2)) %>%
    mutate(fungicide_application_1 = ymd(fungicide_application_1)) %>%
@@
    mutate(final_assessment = ymd(final_assessment)) %>%
-   mutate(PM_final_severity = round(as.double(PM_final_severity), digits = 4))%>%
-   mutate(disease_error = round(as.double(disease_error), digits = 6))%>%
-   mutate(D_error_type = as.character(D_error_type))%>%
-   mutate(grain_yield.t.ha. = round(as.double(grain_yield.t.ha.), digits = 4))%>%
-   mutate(yield_error = round(as.double(yield_error), digits = 6))%>%
-   mutate(Y_error_type = as.character(Y_error_type))%>%
-   mutate(Y_Msquare = round(as.double(Y_Msquare), digits = 6))%>%
-   mutate(yield_gain = round(as.double(yield_gain), digits = 4))%>%
-   mutate(prop_YG = round(as.double(prop_YG), digits = 4))%>%
-   select(-c(trial_design, # remove the following columns
+   mutate(PM_final_severity = round(as.double(PM_final_severity), digits = 4)) %>%
+   mutate(disease_error = round(as.double(disease_error), digits = 6)) %>%
+   mutate(D_error_type = as.character(D_error_type)) %>%
+   mutate(grain_yield.t.ha. = round(as.double(grain_yield.t.ha.), digits = 4)) %>%
+   mutate(yield_error = round(as.double(yield_error), digits = 6)) %>%
+   mutate(Y_error_type = as.character(Y_error_type)) %>%
+   mutate(Y_Msquare = round(as.double(Y_Msquare), digits = 6)) %>%
+   mutate(yield_gain = round(as.double(yield_gain), digits = 4)) %>%
+   mutate(prop_YG = round(as.double(prop_YG), digits = 4)) %>%
+   select(
+      -c(
+         trial_design,
+         # remove the following columns
          plot_length.m.,
@@
          AUDPC_sd,
-             Inc_Ms))
+         Inc_Ms
+      )
+   )
 ```

### 2021-01-29 02_Preliminary_analysis.Rmd
Edits mainly spelling and grammar

--- 2021-01-22 02_Preliminary_analysis.Rmd
@@
 
-All fungicide ai treatments are still contained in the `PM_MB_dat` data, so filtering the data might be necessary to only inspect DMI treatments.
+All fungicide AI treatments are still contained in the `PM_MB_dat` data, so filtering the data might be necessary to only inspect DMI treatments.
 
@@
 
-Lets look at how many trials were undertaken each season in trials including DMI fungicides.
+Let's look at how many trials were undertaken each season in trials including DMI fungicides.
 
@@
    filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole")%>%
-   distinct(trial_ref, location, year)%>%
+             fungicide_ai == "propiconazole") %>%
+   distinct(trial_ref, location, year) %>%
    arrange(year)
@@
 PM_MB_dat %>%
-   filter(fungicide_ai == "control")%>%
-   summarise(mean_yield = mean(grain_yield.t.ha. * 1000),
+   filter(fungicide_ai == "control") %>%
+   summarise(
+      mean_yield = mean(grain_yield.t.ha. * 1000),
       minimum_yield = min(grain_yield.t.ha. * 1000),
@@
       yield_stdev = sd(grain_yield.t.ha. * 1000),
-             yield_SE = sd(grain_yield.t.ha. * 1000)/
-                              sqrt(n())) %>%
+      yield_SE = sd(grain_yield.t.ha. * 1000) /
+         sqrt(n())
+   ) %>%
    kable(align = 'c',
-   caption = "Average yield statistics for no spray contol plots"
-)
-
+         caption = "Average yield statistics for no spray control plots")
 ```
@@
    filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole")%>%
-   distinct(trial_ref)%>%
+             fungicide_ai == "propiconazole") %>%
+   distinct(trial_ref) %>%
    pull()
@@
 PM_MB_dat %>%
-   filter(trial_ref %in% DMITrials)%>%
-   filter(fungicide_ai == "control" )%>%
-   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
-             minimum_yield = min(grain_yield.t.ha.*1000),
-             maximum_yield = max(grain_yield.t.ha.*1000),
-             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
+   filter(trial_ref %in% DMITrials) %>%
+   filter(fungicide_ai == "control") %>%
+   summarise(
+      mean_yield = mean(grain_yield.t.ha. * 1000),
+      minimum_yield = min(grain_yield.t.ha. * 1000),
+      maximum_yield = max(grain_yield.t.ha. * 1000),
+      yield_stdev = sd(grain_yield.t.ha. * 1000),
+      yield_sterr = sd(grain_yield.t.ha. * 1000) / (sqrt(length(grain_yield.t.ha.)))
+   ) %>%
    kable(align = 'c',
          caption = "Average yield statistics for control plots in trials which used a DMI fungicide")
-
 ```
@@
              maximum_yield = max(grain_yield.t.ha.*1000),
+             yield_stdev = sd(grain_yield.t.ha. * 1000),
              yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
@@
 
-Lets look at the yield gains in each trial compared to the no spray control, we will also calculate the proportional grain yield gains.
+Let's look at the yield gains in each trial compared to the no spray control, we will also calculate the proportional grain yield gains.
 
@@
    # Loop code over each trial reference
-   dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == i, ]
+   dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == i,]
 
@@
       # Loop within trial row_spacing
-      dat2 <- dat1[dat1$row_spacing == j, ]
+      dat2 <- dat1[dat1$row_spacing == j,]
       controlY <-
@@
       # Reassign values to row_spacing subset
-      dat1[dat1$row_spacing == j, ] <- dat2
+      dat1[dat1$row_spacing == j,] <- dat2
    }
    # Reassign values to trial_ref subset
-   PM_MB_dat[PM_MB_dat$trial_ref == i, ] <- dat1
+   PM_MB_dat[PM_MB_dat$trial_ref == i,] <- dat1
 }
@@
 # calculate yield gain and prop_yield gain for experiments with no row spacing data
-dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == "AM1303", ]
+dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == "AM1303",]
 
@@
 
-PM_MB_dat[PM_MB_dat$trial_ref == "AM1303", ] <- dat1
+PM_MB_dat[PM_MB_dat$trial_ref == "AM1303",] <- dat1
 ```
 
-Lets show the yield gains in each trial as a table and plot
+Let's show the yield gains in each trial as a table and plot
 ```{r YieldGain_table}
@@
 ```{r Yield_plot}
-
 bw_labels <-
    PM_MB_dat %>%
-   filter(trial_ref %in% DMITrials)%>% 
-   group_by(trial_ref, location, year)%>%
+   filter(trial_ref %in% DMITrials) %>%
+   group_by(trial_ref, location, year) %>%
    summarise(m_gy = mean(grain_yield.t.ha.)) %>%
-   mutate(trial = paste(location,year,sep = "\n")) %>%
+   mutate(trial = paste(location, year, sep = "\n")) %>%
    arrange(m_gy) %>%
@@
 
-bw_labels[1] <- paste0(bw_labels[1],"(b)")
-bw_labels[3] <- paste0(bw_labels[3],"(a)")
+bw_labels[1] <- paste0(bw_labels[1], "(b)")
+bw_labels[3] <- paste0(bw_labels[3], "(a)")
 
@@
    PM_MB_dat %>%
-   filter(trial_ref %in% DMITrials)%>%  
-   mutate(spray_treat = ifelse(fungicide_ai == "control","control", "Fungicide treated"))%>%
-   group_by(trial_ref, location, year)%>%
-   ggplot(aes(reorder(trial_ref, grain_yield.t.ha.), grain_yield.t.ha., fill = spray_treat))+
-   geom_boxplot()+
-   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
-   xlab("Trial location and year")+
-   ylab(bquote('Mungbean yield  '*t~ha^-1*''))+
-   scale_x_discrete(labels = bw_labels)+
-   ylim(0,2.5)+
-   scale_fill_grey(start = 1, end = 0.7)+
-   labs(colour = "Fungicide treatment")+
+   filter(trial_ref %in% DMITrials) %>%
+   mutate(spray_treat = ifelse(fungicide_ai == "control", "control", "Fungicide treated")) %>%
+   group_by(trial_ref, location, year) %>%
+   ggplot(aes(
+      reorder(trial_ref, grain_yield.t.ha.),
+      grain_yield.t.ha.,
+      fill = spray_treat
+   )) +
+   geom_boxplot() +
+   theme(axis.text.x = element_text(
+      angle = 90,
+      hjust = 1,
+      vjust = 0.3
+   )) +
+   xlab("Trial location and year") +
+   ylab(bquote('Mungbean yield  ' * t ~ ha ^ -1 * '')) +
+   scale_x_discrete(labels = bw_labels) +
+   ylim(0, 2.5) +
+   scale_fill_grey(start = 1, end = 0.7) +
+   labs(colour = "Fungicide treatment") +
    guides(fill = guide_legend(title = "Treatment"))
@@
 
-Lets inspect a summary of both powdery mildew severity and grain yield for trials including DMI funcgicides.
+Let's inspect a summary of both powdery mildew severity and grain yield for trials including DMI fungicides.
 
@@
                                  TRUE ~ NA_real_)) %>%
-   mutate(trial_ref = str_remove(trial_ref, "mung"))%>%  # remove "mung" prefix from trial_ref
+   mutate(trial_ref = str_remove(trial_ref, "mung")) %>%  # remove "mung" prefix from trial_ref
    group_by(trial_ref,
@@
             first_sign_disease) %>%
-   summarise(n = n(),
-             m_PM_sev_control = round(median(PM_sev_control, na.rm = TRUE),digits = 2),
+   summarise(
+      n = n(),
+      m_PM_sev_control = round(median(PM_sev_control, na.rm = TRUE), digits = 2),
       n_controls = sum(is.na(PM_sev_control) == FALSE),
-             min_PM_sev = round(min(PM_sev_treat, na.rm = TRUE),digits = 2),
-             max_PM_sev = round(max(PM_sev_treat, na.rm = TRUE),digits = 2),
-             m_PM_yield_control = round(mean(PM_y_control, na.rm = TRUE),digits = 3),
-             min_PM_yield = round(min(PM_y_treat, na.rm = TRUE),digits = 3),
-             max_PM_yield = round(max(PM_y_treat, na.rm = TRUE),digits = 3),
-             .groups = "drop")%>%
+      min_PM_sev = round(min(PM_sev_treat, na.rm = TRUE), digits = 2),
+      max_PM_sev = round(max(PM_sev_treat, na.rm = TRUE), digits = 2),
+      m_PM_yield_control = round(mean(PM_y_control, na.rm = TRUE), digits = 3),
+      min_PM_yield = round(min(PM_y_treat, na.rm = TRUE), digits = 3),
+      max_PM_yield = round(max(PM_y_treat, na.rm = TRUE), digits = 3),
+      .groups = "drop"
+   ) %>%
    filter(min_PM_sev < 10) %>% # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf
-   arrange(year)%>%
+   arrange(year) %>%
    mutate(PM_sev_range = paste(min_PM_sev, max_PM_sev, sep = " - ")) %>%
@@
    mutate(m_PM_sev_control = paste(m_PM_sev_control, " (", n_controls, ")", sep = "")) %>%
-   select(-c(min_PM_sev, max_PM_sev, min_PM_yield, max_PM_yield)) %>%
+   select(-c(min_PM_sev, max_PM_sev, min_PM_yield, max_PM_yield, n_controls)) %>%
+   select(c(1:7, 9, 8, 10)) %>% # order columns
    flextable() %>%
-   set_header_labels(trial_ref = "Trial code",
+   set_header_labels(
+      trial_ref = "Trial code",
       location = "Location",
@@
       m_PM_sev_control = "Control median\nPM severity",
-                     n_controls = "n controls",
       PM_sev_range = "PM severity\nrange*",
-                     m_PM_yield_control = "Control\nmean yield",
-                     yield_range = "Yield range\n(t / ha)*"
+      m_PM_yield_control = "Control\nmean yield*",
+      yield_range = "Yield range\n(t / ha)"
    ) %>%
-   fontsize(size = 8,part = "body")%>%
-   fontsize(size = 10, part = "header")%>%
+   fontsize(size = 8, part = "body") %>%
+   fontsize(size = 10, part = "header") %>%
    align(j = 3:10, align = "center", part = "all") %>%
    autofit() %>%
-   width(j = 7:10, width = 0.9)%>%
-   width(j = 3, width = 0.5)%>%
-   set_caption("Table 1: Mean yield and severity for trials included in the meta-analysis.
-Powdery mildew (PM) onset, number of treatments per trial (n), PM mean plot severity of the non-fungicide treated plots and the severity range in fungicide treatments; Mean yield in non-fungicide treated control and the range of yields in the fungicide treatments in tonnes per hectare")
+   width(j = 7:10, width = 1) %>%
+   width(j = 3, width = 0.5) %>%
+   set_caption(
+      "Table 1: Mean yield and severity for trials included in the meta-analysis.
+Powdery mildew (PM) onset, number of treatments per trial (n), PM median plot severity of the non-fungicide treated plots and the severity range in fungicide treatments, * bracketed numbers refer to the number of pooled control treatments summarised; Mean yield in non-fungicide treated control and the range of yields in the fungicide treatments in tonnes per hectare"
+   )
 Sev_yield_table
@@
 print(doc, target = "paper/figures/Table1_severity&yield.docx")
-
 ```
@@
    labs(y = "Proportion of grain yield saved",
-        title = "Grain yield proportion saved\nfaceted by number of sprays") +
+        title = "Grain yield proportion saved",
+        caption = "Facets indicate number of sprays") +
    theme(legend.position = "none") +
@@
    xlab("Dose (g ai/ha)") +
-   ggtitle(label = "Yield for each respective propiconazole dose,\nfaceted by number of applications") +
+   labs(label = "Yield for each respective propiconazole dose",
+        caption = "Facets indicate the number of applications") +
    geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
@@
    ylab("Number of days after or before first sign of powdery mildew") +
-   ggtitle("Fungicide application timing relative to First Sign of Disease.\n - Faceted by number of applications")+
+   labs(title = "Fungicide application timing relative to First Sign of Disease",
+        caption = "Facets indicate the number of applications") +
    facet_grid(cols = vars(total_fungicide)) +
@@
 
-Lets plot disease severity in boxplots grouped by row spacing treatment.
+Let's plot disease severity in boxplots grouped by row spacing treatment.
 We are asking here, which row spacing leads to the higher disease severity?
@@
 
-There is little difference here between the row spacing treatments, lets look if there is a trial location effect as disease pressure lead to varying results.
+There is little difference here between the row spacing treatments, Let's look if there is a trial location effect as disease pressure lead to varying results.
 
@@
 Based on a GRDC report by Sue Thompson [-@SueThompson2016] we want to know what the yield loss was in on cultivar Jade in the 2016 Trials.
+
 ```{r JadeYieldLoss}
@@
    filter(year == "2016",
-          host_genotype == "Jade")%>%
-   mutate(Treatment = case_when(
-      fungicide_ai == "control" ~ "control",
-      TRUE ~ "FungicideTreated"))%>%
-   group_by(location, Treatment)%>%
-   summarise(trial_ref = trial_ref,
+          host_genotype == "Jade") %>%
+   mutate(Treatment = case_when(fungicide_ai == "control" ~ "control",
+                                TRUE ~ "FungicideTreated")) %>%
+   group_by(location, Treatment) %>%
+   summarise(
+      trial_ref = trial_ref,
       location = location,
@@
       Yield = mean(grain_yield.t.ha., na.rm = TRUE),
-             .groups = "drop")%>%
-   distinct()%>%
-   pivot_wider(names_from = Treatment, values_from = Yield)%>%
+      .groups = "drop"
+   ) %>%
+   distinct() %>%
+   pivot_wider(names_from = Treatment, values_from = Yield) %>%
    mutate(Diff = FungicideTreated - control) %>%
-   mutate(percent = (Diff/FungicideTreated)*100)%>%
-   select(trial_ref, location, year, control, FungicideTreated,percent, Diff)
+   mutate(percent = (Diff / FungicideTreated) * 100) %>%
+   select(trial_ref,
+          location,
+          year,
+          control,
+          FungicideTreated,
+          percent,
+          Diff)
+```
 
-```
+## Summary of disease incidence effect on yields
 
@@
 An important consideration for why to carry out work on mungbean diseases is the value the crop provides. 
-Lets pull in data from the FAOSTAT website for the area of mungbean crops harvested.
+Let's pull in data from the FAOSTAT website for the area of mungbean crops harvested.
 
@@
    filter(Item == "Beans, dry",
-          Element == "Area harvested")%>%
-   select(Year,Value)%>%
-   ggplot(aes(y = Value, x = Year))+
-   geom_point()+
+          Element == "Area harvested") %>%
+   select(Year, Value) %>%
+   ggplot(aes(y = Value, x = Year)) +
+   geom_point() +
    geom_smooth()
-
 ```

### 2021-01-29 03_Prep_data.Rmd
Edits mainly spelling and grammar

@@
    filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole")%>%
+             fungicide_ai == "propiconazole") %>%
    distinct(trial_ref) %>%
@@
 PM_MB_dat <-
-   PM_MB_dat[PM_MB_dat$trial_ref %in% DMI_Trials,]
+   PM_MB_dat[PM_MB_dat$trial_ref %in% DMI_Trials, ]
 ```
@@
    PM_MB_dat %>%
-   filter(fungicide_ai == "control" |
+   filter(
+      fungicide_ai == "control" |
          fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole")
+         fungicide_ai == "propiconazole"
+   )
 ```
@@
 
-We will follow the method of converting 'least square differences' (LSD) to sampling variance reported by [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
+We will follow the method of converting 'least square differences' (LSD) to sampling variance reported by [Ngugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
 
@@
           (LSD / Tcrit) ^ 2) / 2 
-   # method - Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
+   # method - Ngugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
 
@@
 
-PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,"yield_error"] <- 
-   PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,"yield_error"]^2
+PM_MB_dat[PM_MB_dat$trial_ref %in% Trials, "yield_error"] <-
+   PM_MB_dat[PM_MB_dat$trial_ref %in% Trials, "yield_error"] ^ 2
 
-PM_MB_dat[PM_MB_dat$trial_ref %in% Trials,]$Y_error_type <-
+PM_MB_dat[PM_MB_dat$trial_ref %in% Trials, ]$Y_error_type <-
    "SamplingVariance"
-
 ```
@@
 
-Lets look at the association between mean squares and yield to see if there is a more typical association between yield and variance.
+Let's look at the association between mean squares and yield to see if there is a more typical association between yield and variance.
 
@@
 These categorical variables are named:
+
    - **Early**: First fungicide application was prior to first sign of disease. 
@@
    PM_MB_dat %>%
-   mutate(trial = paste(
-      trial_ref, 
+   mutate(trial = paste(trial_ref,
                         year,
@@
 Earlier, in section [Fungicide Doses](#fungicide-doses) we noted there were different doses of propiconazole, which might influence our analysis. 
-The current label for custodia [PER82104](http://permits.apvma.gov.au/PER82104.PDF), Containing: 120 g/L azoxystrobin and 200 g/L tebuconazole, recommends between 300 ml - 600 ml of the tebuconazole fraction per hectare, equivalent to 60 - 120 grams per hectare.
-These label rates are assumed to be the same for propiconazole infering these concentrations might be within the recommended rates. 
-It is also worth noting the APVMA permit [PER13979](http://permits.apvma.gov.au/PER13979.PDF) which allows the use of Tebuconazole between 62.35 g / ha and 83 g / ha depending on the product formulation.
+The current label for Custodia [PER82104](http://permits.apvma.gov.au/PER82104.PDF), containing: 120 g/L azoxystrobin and 200 g/L tebuconazole, recommends between 300 ml - 600 ml of the tebuconazole fraction per hectare, equivalent to 60 - 120 grams per hectare.
+These label rates are assumed to be the same for propiconazole inferring these concentrations might be within the recommended rates. 
+It is also worth noting the APVMA permit [PER13979](http://permits.apvma.gov.au/PER13979.PDF) which allows the use of tebuconazole between 62.35 g / ha and 83 g / ha depending on the product formulation.
 
@@
 ********
-## Remove unnecersary variables
+
+## Remove unnecessary variables
 
@@
    PM_MB_dat %>%
-   select(-c(trial_dose,
-             fungicide_timing_1,fungicide_timing_2, fungicide_timing_3, 
-             dose, fungicide_application_4, fungicide_application_5,
-             fungicide_application_6, fungicide_application_7)) 
+   select(
+      -c(
+         trial_dose,
+         fungicide_timing_1,
+         fungicide_timing_2,
+         fungicide_timing_3,
+         dose,
+         fungicide_application_4,
+         fungicide_application_5,
+         fungicide_application_6,
+         fungicide_application_7
+      )
+   ) 
 ```
@@
 ## Final data check  
-Now we have defined our treatments lets inspect plots to visualise how well the data compares across the trial years and locations?
+Now we have defined our treatments. Let's inspect plots to visualise how well the data compares across the trial years and locations.
 
@@
    PM_MB_dat %>%
-   mutate(spray_management =
+   mutate(
+      spray_management =
          factor(
@@
       vi = yield_error,
-          n = replicates) %>%
+      n = replicates
+   ) %>%
    select(
@@
       n,
-      id)
+      id
+   )
 ```

### 2021-01-29 04_MetaAnalysis.Rmd
Edits mainly spelling and grammar

@@
 
-A secondary question to this aim is: given the time at which the first spray occurred is a second spray provide worthwhile yield protection.
+A secondary question to this aim is: given the time at which the first spray occurred does a second spray provide worthwhile yield protection.
 
@@
    method = "ML",
-   random = list( ~ spray_management | trial, ~ 1 | id),
+   random = list(~ spray_management | trial, ~ 1 | id),
    struct = "UN",
@@
 
-Lets try the model with an implied simpler variance-covariance matrix "compound symetry" ("CS") to examine if unstructured matrix is suitable.
+Let's try the model with an implied simpler variance-covariance matrix "compound symmetry" ("CS") to examine if unstructured matrix is suitable.
 ```{r}
@@
    method = "ML",
-   random = list( ~ spray_management | trial, ~ 1 | id),
+   random = list(~ spray_management | trial, ~ 1 | id),
    struct = "CS",
@@
 
-Lets present the meta-analysis results for the moderator variables in a forest style plot.
-First lets create a table of the results.
+Let's present the meta-analysis results for the moderator variables in a forest style plot.
+First Let's create a table of the results.
 
@@
 results_mv <-
-   results_mv[2:6, ] %>%
+   results_mv[2:6,] %>%
    mutate(Effect = Effect + results_mv$Effect[1]) %>%
@@
    mutate(CI_upper = CI_upper + results_mv$CI_upper[1]) %>%
-   bind_rows(results_mv[1, ]) %>%
+   bind_rows(results_mv[1,]) %>%
    mutate(index = c(2:6, 1)) %>%
@@
 Z and P values indicate statistical significance in comparison to the intercept.")
-
 ```
@@
 
-Lets investigate the treatment contrasts
+Let's investigate the treatment contrasts
 
@@
 ### Forest plot of trial treatment effect per trial
-Lets look at the trial variability in this model with a forest plot
+Let's look at the trial variability in this model with a forest plot
 ```{r forestP, eval=FALSE, fig.height=40, fig.width=17, include=FALSE}
@@
 
-### Sort and arrange data-frame accordingly and produce a index vector to inform the order of each "Trial" on the plot
+# Sort and arrange data-frame accordingly and produce a index vector to inform
+# the order of each "Trial" on the plot
 index1 <- PM_MB_dat %>%
@@
 
-### Use forest rows function to return a list of where to place on the plot: sub-titles, each trial row, and summary prediction for each treatment.
-### this list can be used below to reference where to plot each variable
+# Use forest rows function to return a list of where to place on the plot:
+# sub-titles, each trial row, and summary prediction for each treatment.
+# this list can be used below to reference where to plot each variable
 rows1 <- forest_rows(
@@
 
-### A data-frame of meta-model coefficients used to produce the summary polygons for each treatment
+# A data-frame of meta-model coefficients used to produce the summary polygons
+# for each treatment
 polys <- data.frame(

### 2021-02-01 01_TrialsForInclusionInAnalysis.Rmd
Move spray schedule designation, and variance standardisation to ch1

--- 2021-01-20 01_TrialsForInclusionInAnalysis.Rmd
@@
              AUDPC_sd,
-             Inc_Ms))
+             Inc_Ms,
+             pod_fill_date,
+             mid_late_pod_fill))
+```
+
+## Subset to trials containing DMI fungicides
+
+```{r filterDMI_trials}
+DMI_Trials <- 
+   PM_MB_dat %>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")%>%
+   distinct(trial_ref) %>%
+   pull()
+
+PM_MB_dat <- 
+   PM_MB_dat[PM_MB_dat$trial_ref %in% DMI_Trials,]
+```
+
+Now remove any non-DMI treatments or controls
+```{r}
+PM_MB_dat <- 
+   PM_MB_dat %>%
+   filter(fungicide_ai == "control" |
+             fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole")
+```
+
+## Classifying spray schedule
+
+First are going to calculate the time between the first sign of disease and the fungicide applications.
+
+```{r clustered_fungicide_applications}
+PM_MB_dat %<>%
+   mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
+   mutate(fungicide_timing_2 = fungicide_application_2 - fungicide_application_1) %>%
+   mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2)
+
+```
+
+To ensure sufficient number of replicates, we will bin the continuous variable into three categorical variables relating to when the first fungicide application was made, relative to the first sign of disease.
+
+These categorical variables are named:
+   - **Early**: First fungicide application was prior to first sign of disease. 
+   - **Recommended**: First fungicide application was applied on the day powdery mildew was observed, or within three days of first sign. 
+   - **Late**: First fungicide application was four or more days after first sign of disease being observed.
+
+The number of sprays need also be defined.
+
+```{r TreatmentTable}
+data.frame(TreatmentName = c("Early", "Recommended", "Late", "EarlyPlus", "RecommendedPlus", "LatePlus"),
+           n_sprays = rep(c("Single", "Two - Three"), each = 3),
+           DaysRelativeToFirstSign = c("Prior to first sign of Powdery Mildew",
+                                       "1 - 3 days after first sign of Powdery Mildew",
+                                       "7 - 8 days after first sign of Powdery Mildew"))%>%
+   kable()
+```
+
+```{r simple_clusters}
+PM_MB_dat <- PM_MB_dat %>%
+   mutate(
+      spray_management = case_when(
+         fungicide_timing_1 < 0 &
+            is.na(fungicide_application_2) &
+            is.na(fungicide_application_3) ~ "Early",
+         fungicide_timing_1 >= 0 &
+            fungicide_timing_1 < 4 &
+            is.na(fungicide_application_2) &
+            is.na(fungicide_application_3) ~ "Recommended",
+         fungicide_timing_1 >= 4 &
+            is.na(fungicide_application_2) &
+            is.na(fungicide_application_3) ~ "Late",
+         fungicide_timing_1 < 0 &
+            !is.na(fungicide_application_2) ~ "Early_plus",
+         fungicide_timing_1 >= 0 &
+            fungicide_timing_1 < 4 &
+            !is.na(fungicide_application_2) ~ "Recommended_plus",
+         fungicide_timing_1 >= 4 &
+            !is.na(fungicide_application_2) ~ "Late_plus",
+         TRUE ~ "Other"
+      )
+   )
+
+PM_MB_dat[PM_MB_dat$fungicide_ai == "control",
+            c(
+               "fungicide_timing_1",
+               "fungicide_timing_2",
+               "fungicide_timing_3",
+               "spray_management"
+            )] <- "control"
+```
+
+Now to view the number break-down of the `spray_management` treatments
+
+```{r tableSprayManagement}
+table(PM_MB_dat$spray_management)
+```
+
+'Early_plus' treatments are few in number, these treatments will have too few comparisons with other treatments in the meta-analysis to provide accurate results.
+Therefore we will remove 'Early_plus' from the analysis.
+
+```{r simpler_clusters_remove}
+PM_MB_dat <-
+   PM_MB_dat %>%
+   filter(spray_management != "Early_plus")
+```
+
+## Standardise Variance
+
+All the variance types need to be converted to sample variance. 
+First we will start by standardising yield variance according to the method reported by [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
+
+### Yield variance
+```{r}
+PM_MB_dat <- 
+   PM_MB_dat %>%
+   mutate(
+      d_vi = 
+         case_when(
+            D_error_type == "stdev" ~ disease_error ^2,
+            D_error_type == "lsd (P=0.05)" ~ 
+               (replicates * ((disease_error / 1.96) ^2) /2)/replicates
+         ),
+      id = row_number(),
+      spray_management = fct_relevel(spray_management,sort)
+   )
+
+```
+
+```{r}
+PM_sev <- 
+   PM_sev %>%
+   mutate(
+      d_vi = 
+         case_when(
+            D_error_type == "stdev" ~ disease_error ^2,
+            D_error_type == "lsd (P=0.05)" ~ 
+               (replicates * ((disease_error / 1.96) ^2) /2)/replicates
+         ),
+      id = row_number(),
+      spray_management = fct_relevel(spray_management,sort)
+   )
+
 ```
@@
 ```{r saveData01}
+write.csv(PM_MB_dat, file = "cache/PM_MB_clean_data.csv",row.names = FALSE)
 save(PM_MB_dat, file = here("cache/ImportDataAndSelectTrials01.Rdata"))

### 2021-02-01 01_TrialsForInclusionInAnalysis.Rmd
Remove unused columns, and standadise yield variance

@@
              pod_fill_date,
-             mid_late_pod_fill))
+             mid_late_pod_fill,
+             yield_gain,
+             Y_Msquare,
+             prop_YG))
 ```
@@
    PM_MB_dat %>%
-   filter(spray_management != "Early_plus")
+   filter(spray_management != "Early_plus") %>%
+   select(-c(fungicide_timing_1, # remove the following columns which no longer have use
+             fungicide_timing_2,
+             fungicide_timing_3))
 ```
@@
 
-### Yield variance
+### Yield variance standardisation
 ```{r}
@@
    mutate(
-      d_vi = 
+      vi = 
          case_when(
-            D_error_type == "stdev" ~ disease_error ^2,
-            D_error_type == "lsd (P=0.05)" ~ 
+            Y_error_type == "stdev" ~ disease_error ^2,
+            Y_error_type == "lsd (P=0.05)" ~ 
                (replicates * ((disease_error / 1.96) ^2) /2)/replicates
          ),
-      id = row_number(),
       spray_management = fct_relevel(spray_management,sort)
@@
 
+### Disease severity variance standardisation
 ```{r}
-PM_sev <- 
-   PM_sev %>%
+PM_MB_dat <- 
+   PM_MB_dat %>%
    mutate(

### 2021-02-01 01_TrialsForInclusionInAnalysis.Rmd
rename chunks

@@
 Now remove any non-DMI treatments or controls
-```{r}
+```{r KeepOnlyDMI}
 PM_MB_dat <- 
@@
 ### Yield variance standardisation
-```{r}
+```{r StandardiseYieldVariance}
 PM_MB_dat <- 
@@
 ### Disease severity variance standardisation
-```{r}
+```{r StandardiseSeverityVariance}
 PM_MB_dat <- 

### 2021-02-01 01_TrialsForInclusionInAnalysis.Rmd
remove more columns for tidier df

@@
              Y_Msquare,
-             prop_YG))
+             prop_YG,
+             AUDPC_m,
+             AUDPC_sd))
 ```
@@
              fungicide_timing_2,
-             fungicide_timing_3))
+             fungicide_timing_3,
+             fungicide_application_1,
+             fungicide_application_2,
+             fungicide_application_3,
+             fungicide_application_4,
+             fungicide_application_5,
+             fungicide_application_6,
+             fungicide_application_7,
+             ))
 ```
@@
       spray_management = fct_relevel(spray_management,sort)
-   )
+   ) %>%
+   select(-c(yield_error,
+             Y_error_type))
 
@@
       spray_management = fct_relevel(spray_management,sort)
-   )
+   ) %>%
+   select(-c(disease_error,
+             D_error_type))
 

### 2021-02-01 01_TrialsForInclusionInAnalysis.Rmd
code stylr

@@
          AUDPC_m,
-             AUDPC_sd))
+         AUDPC_sd
+      )
+   )
 ```
@@
 ```{r TreatmentTable}
-data.frame(TreatmentName = c("Early", "Recommended", "Late", "EarlyPlus", "RecommendedPlus", "LatePlus"),
+data.frame(
+   TreatmentName = c(
+      "Early",
+      "Recommended",
+      "Late",
+      "EarlyPlus",
+      "RecommendedPlus",
+      "LatePlus"
+   ),
    n_sprays = rep(c("Single", "Two - Three"), each = 3),
-           DaysRelativeToFirstSign = c("Prior to first sign of Powdery Mildew",
+   DaysRelativeToFirstSign = c(
+      "Prior to first sign of Powdery Mildew",
       "1 - 3 days after first sign of Powdery Mildew",
-                                       "7 - 8 days after first sign of Powdery Mildew"))%>%
+      "7 - 8 days after first sign of Powdery Mildew"
+   )
+) %>%
    kable()
@@
          case_when(
-            Y_error_type == "stdev" ~ disease_error ^2,
+            Y_error_type == "stdev" ~ disease_error ^ 2,
             Y_error_type == "lsd (P=0.05)" ~
-               (replicates * ((disease_error / 1.96) ^2) /2)/replicates
+               (replicates * ((disease_error / 1.96) ^ 2) / 2) / replicates
          ),
-      spray_management = fct_relevel(spray_management,sort)
+      spray_management = fct_relevel(spray_management, sort)
    ) %>%
@@
          case_when(
-            D_error_type == "stdev" ~ disease_error ^2,
+            D_error_type == "stdev" ~ disease_error ^ 2,
             D_error_type == "lsd (P=0.05)" ~
-               (replicates * ((disease_error / 1.96) ^2) /2)/replicates
+               (replicates * ((disease_error / 1.96) ^ 2) / 2) / replicates
          ),
       id = row_number(),
-      spray_management = fct_relevel(spray_management,sort)
+      spray_management = fct_relevel(spray_management, sort)
    ) %>%
@@
 ```{r saveData01}
-write.csv(PM_MB_dat, file = "cache/PM_MB_clean_data.csv",row.names = FALSE)
+write.csv(PM_MB_dat, file = "cache/PM_MB_clean_data.csv", row.names = FALSE)
 save(PM_MB_dat, file = here("cache/ImportDataAndSelectTrials01.Rdata"))

### 2021-02-01 01_TrialsForInclusionInAnalysis.Rmd
remove more columns

@@
          mid_late_pod_fill,
+         flowering_date,
          yield_gain,
@@
          AUDPC_m,
-         AUDPC_sd
+         AUDPC_sd,
+         AUDPS_sd
       )

### 2021-02-01 02_Preliminary_analysis.Rmd
Remove duplicated tables

@@
 tmp1 <- PM_MB_dat %>%
-   filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole") %>%
    distinct(trial_ref, location, year) %>%
@@
 
-What is the variation in yield over all the trials (including non-DMI fungicide trials) in the no spray control and fungicide treated plots.
+What is the variation in yield over all the trials in the no spray control.
 
@@
       mean_yield = mean(grain_yield.t.ha. * 1000),
+      median_yield = median(grain_yield.t.ha. * 1000),
       minimum_yield = min(grain_yield.t.ha. * 1000),
@@
 
-What is the yield variation in no spray control trials yield over only the DMI fungicide trials.  
-```{r ControlYield_DMITrials}
-DMITrials <- PM_MB_dat %>%
-   filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole") %>%
-   distinct(trial_ref) %>%
-   pull()
-
-PM_MB_dat %>%
-   filter(trial_ref %in% DMITrials) %>%
-   filter(fungicide_ai == "control") %>%
-   summarise(
-      mean_yield = mean(grain_yield.t.ha. * 1000),
-      minimum_yield = min(grain_yield.t.ha. * 1000),
-      maximum_yield = max(grain_yield.t.ha. * 1000),
-      yield_stdev = sd(grain_yield.t.ha. * 1000),
-      yield_sterr = sd(grain_yield.t.ha. * 1000) / (sqrt(length(grain_yield.t.ha.)))
-   ) %>%
-   kable(align = 'c',
-         caption = "Average yield statistics for control plots in trials which used a DMI fungicide")
-```
-
 Mean yields in DMI fungicide treated plots
@@
    summarise(mean_yield = mean(grain_yield.t.ha.*1000),
+             median_yield = median(grain_yield.t.ha. * 1000),
              minimum_yield = min(grain_yield.t.ha.*1000),

### 2021-02-01 02_Preliminary_analysis.Rmd
remove yield gain calculation and non DMI Fungicide inspection

@@
 
-```
-
-Let's look at the yield gains in each trial compared to the no spray control, we will also calculate the proportional grain yield gains.
-
-```{r Calculate_yield-savings}
-for (i in unique(PM_MB_dat$trial_ref)) {
-   # Loop code over each trial reference
-   dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == i,]
-
-   if (any(is.na(unique(dat1$row_spacing)))) {
-      # If there is no recorded row.spacing don't calculate proportional yield, skip to the next trial
-      warning(
-         unique(dat1$trial_ref),
-         " at ",
-         unique(dat1$location),
-         " in year ",
-         unique(dat1$year),
-         " has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n"
-      )
-      next()
-   }
-
-   for (j in unique(dat1$row_spacing)) {
-      # Loop within trial row_spacing
-      dat2 <- dat1[dat1$row_spacing == j,]
-      controlY <-
-         mean(dat2[dat2$fungicide_ai == "control", "grain_yield.t.ha."]) #Mean taken as some trials had multiple control reps
-
-      # Calculate the yield gain relative to the no spray control (controlY)
-      dat2$yield_gain <- dat2$grain_yield.t.ha. - controlY
-      dat2$prop_YG <- dat2$yield_gain  /  controlY
-
-      # insert NA as yield_gain and proportional yield gain for the controls
-      dat2[dat2$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
-         NA
-
-      # Reassign values to row_spacing subset
-      dat1[dat1$row_spacing == j,] <- dat2
-   }
-   # Reassign values to trial_ref subset
-   PM_MB_dat[PM_MB_dat$trial_ref == i,] <- dat1
-}
-
-# ____________________________________________
-# calculate yield gain and prop_yield gain for experiments with no row spacing data
-dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == "AM1303",]
-
-controlY <-
-   mean(dat1[dat1$fungicide_ai == "control", "grain_yield.t.ha."])
-
-dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
-dat1$prop_YG <- dat1$yield_gain / controlY
-dat1[dat1$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
-   c(NA, NA)
-
-PM_MB_dat[PM_MB_dat$trial_ref == "AM1303",] <- dat1
-```
-
-Let's show the yield gains in each trial as a table and plot
-```{r YieldGain_table}
-PM_MB_dat %>%
-   filter(trial_ref %in% DMITrials)%>%  # selects only the trials with DMI fungicide treatments
-   filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole")%>%
-   group_by(trial_ref, location, year)%>%
-   summarise(yield_gain_m = mean(yield_gain),
-             yield_gain_se = sd(yield_gain, na.rm = T)/sqrt(n()),
-             yg_n = n(),
-             .groups = "drop")%>%
-   arrange(yield_gain_m)
-```
-
-```{r Yield_plot}
-bw_labels <-
-   PM_MB_dat %>%
-   filter(trial_ref %in% DMITrials) %>%
-   group_by(trial_ref, location, year) %>%
-   summarise(m_gy = mean(grain_yield.t.ha.)) %>%
-   mutate(trial = paste(location, year, sep = "\n")) %>%
-   arrange(m_gy) %>%
-   pull(trial)
-
-bw_labels[1] <- paste0(bw_labels[1], "(b)")
-bw_labels[3] <- paste0(bw_labels[3], "(a)")
-
-fungicide_spray_plot <-
-   PM_MB_dat %>%
-   filter(trial_ref %in% DMITrials) %>%
-   mutate(spray_treat = ifelse(fungicide_ai == "control", "control", "Fungicide treated")) %>%
-   group_by(trial_ref, location, year) %>%
-   ggplot(aes(
-      reorder(trial_ref, grain_yield.t.ha.),
-      grain_yield.t.ha.,
-      fill = spray_treat
-   )) +
-   geom_boxplot() +
-   theme(axis.text.x = element_text(
-      angle = 90,
-      hjust = 1,
-      vjust = 0.3
-   )) +
-   xlab("Trial location and year") +
-   ylab(bquote('Mungbean yield  ' * t ~ ha ^ -1 * '')) +
-   scale_x_discrete(labels = bw_labels) +
-   ylim(0, 2.5) +
-   scale_fill_grey(start = 1, end = 0.7) +
-   labs(colour = "Fungicide treatment") +
-   guides(fill = guide_legend(title = "Treatment"))
-
-fungicide_spray_plot
-#ggsave("paper/figures/Fig1_trial_yield_bw.png")
 ```

### 2021-02-01 02_Preliminary_analysis.Rmd
Remove fungicide application timing plot

@@
 
-### Fungicides
-
-#### Fungicide type
-
-Before we exclude non-DMI fungicides let's have a look at the efficacy of the other fungicides in comparison to the DMIs.
-For this comparison we will focus on the proportional yield saved, relative to the no spray control.
-The primary focus of this research is the effect of fungicide on mitigating yield loss due to disease.
-We are using proportional yield, relative to the no spray control, to reduce the effect of location and seasonal influences.
-
-```{r Fungicide_x_nSprays_tble2, message=FALSE}
-PM_MB_dat %>%
-   group_by(fungicide_ai, total_fungicide) %>%
-   summarise(
-      n = length(prop_YG),
-      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
-      median = median(prop_YG, na.rm = T),
-      mean = mean(prop_YG, na.rm = T),
-      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
-   ) %>%
-   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
-   arrange(desc(median)) %>%
-   kable(
-      caption = "Fungicide effect on proportion of yield gain.",
-      col.names = c(
-         "Fungicide active ingredient",
-         "Total fungicide applications",
-         "n Treatments",
-         "2.5% quartile",
-         "Median proportional grain yield",
-         "Mean proportional grain yield",
-         "97.5 % quartile"
-      ),
-      align = "c"
-   ) %>%
-   kable_styling(fixed_thead = T, full_width = T) %>%
-   column_spec(c(2, 3), width = "1cm") %>%
-   kableExtra::add_footnote(label = "Fungicides with less than five observations were omitted from this table")
-```
-
-<br>
-<br>
-<br>
-
-Let's visualise this in a plot for one and two sprays only.
-
-```{r Fungicide_x_nSprays_tble1, message=FALSE, warning=FALSE}
-PM_MB_dat %>%
-   mutate(fungicide_ai = as.factor(PM_MB_dat$fungicide_ai)) %>%
-   filter(total_fungicide == 1 | total_fungicide == 2) %>%
-   filter(
-      fungicide_ai != "pyrazophos" &
-         fungicide_ai != "control" &
-         fungicide_ai != "benomyl" &
-         fungicide_ai != "Acibenzolar-S-methyl"
-   ) %>%
-   mutate(fungicide_ai = factor(
-      fungicide_ai,
-      levels = c(
-         "carbendazim",
-         "pyraclostrobin",
-         "sulphur",
-         "200 g/L azoxystrobin + 80 g/L cyproconazole",
-         "tebuconazole",
-         "propiconazole",
-         "200 g/L tebuconazole + 120 g/L azoxystrobin"
-      )
-   )) %>%
-   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
-   facet_grid(rows = vars(total_fungicide)) +
-   geom_boxplot(aes(fill = fungicide_ai)) +
-   geom_hline(aes(yintercept = 0), size = 0.5) +
-   labs(y = "Proportion of grain yield saved",
-        title = "Grain yield proportion saved",
-        caption = "Facets indicate number of sprays") +
-   theme(legend.position = "none") +
-   scale_fill_usq() +
-   coord_flip()
-```
-
-There is a small yield effect among the strobilurin fungicide mixes and the DMI fungicides. 
-While there is some differences in the variation between tebuconazole and propiconazole, the medians are very similar. 
-I think it is safe to combine these fungicides, with the same mode of action in the meta-analysis.
-The follow-up spray seems to show an increase in yield protection.
-
-*****
-
-#### Fungicide Doses{#fungicide-doses}  
+### Fungicide Doses{#fungicide-doses}  
 From this point on we will investigate only the DMI fungicides, tebuconazole and propiconazole, and disregard all other fungicide modes-of-action.
@@
 This table shows that the majority of treatments inspected one and two spray management practices.
-
-*****
-
-#### Timing of fungicide sprays  
-The timing of fungicide application can be crucial for maximum disease control and yield loss mitigation. 
-The experiments all relied on natural infection and thus infection at a standardised crop maturity stage was not possible. 
-To best estimate the effect of fungicide application timing we will use the day when the disease was first found in the field as a reference.
-The first sign of disease is a useful reference as it can be assessed with little training for the assessor.
-
-First let's make a plot to visualise when one or more spray management regimes were made in relation to the first sign of disease regardless of fungicide active. 
-The plot is faceted by number of spray applications.
-
-```{r spray_relative2FS}
-PM_MB_dat %>%
-   mutate(
-      s1_DfromFS = fungicide_application_1 - first_sign_disease,
-      s2_DfromFS = fungicide_application_2 - first_sign_disease,
-      s3_DfromFS = fungicide_application_3 - first_sign_disease,
-      s4_DfromFS = fungicide_application_4 - first_sign_disease,
-      s5_DfromFS = fungicide_application_5 - first_sign_disease
-   ) %>%
-   gather(
-      key = spray,
-      value = n_days,
-      s1_DfromFS,
-      s2_DfromFS,
-      s3_DfromFS,
-      s4_DfromFS,
-      s5_DfromFS
-   ) %>%
-   drop_na(n_days) %>%
-   ggplot(aes(x = spray, y = as.numeric(n_days))) +
-   geom_violin() +
-   scale_x_discrete(labels = c(
-      "First spray",
-      "Second spray",
-      "Third spray",
-      "Fourth spray",
-      "Fifth spray"
-   )) +
-   ylab("Number of days after or before first sign of powdery mildew") +
-   labs(title = "Fungicide application timing relative to First Sign of Disease",
-        caption = "Facets indicate the number of applications") +
-   facet_grid(cols = vars(total_fungicide)) +
-   coord_flip()
-```
-
-The plot shows single fungicide applications are mostly made at zero, first sign of disease in the crop. Some were made earlier and some around 10 days later.  
-Experiments that tested two spray treatments also tend to make the first application at first sign of disease, and the second spray between 10 and 25 days later.
-Three spray treatments seemed to be mostly used in experiments where preventative sprays as the first fungicide application were made.
 

### 2021-02-01 02_Preliminary_analysis.Rmd
remove proportionl grain yield inspection and small edits

@@
    filter(fungicide_ai == "propiconazole") %>%
-   ggplot(aes(x = relevel(as.factor(dose_ai.ha), "62.5"), y = prop_YG)) +
+   ggplot(aes(x = relevel(as.factor(dose_ai.ha), "62.5"), y = grain_yield.t.ha.)) +
    xlab("Dose (g ai/ha)") +
@@
    geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
-   ylab("Yield gain proportially\nto the no spray control") +
+   ylab("Grain yield t / ha") +
    facet_grid(cols = vars(total_fungicide))
@@
           host_genotype == "Jade") %>%
-   mutate(Treatment = case_when(fungicide_ai == "control" ~ "control",
-                                TRUE ~ "FungicideTreated")) %>%
+   mutate(Treatment = case_when(fungicide_ai == "control" ~ "control_yield",
+                                TRUE ~ "FungicideTreated_yield")) %>%
    group_by(location, Treatment) %>%
@@
    pivot_wider(names_from = Treatment, values_from = Yield) %>%
-   mutate(Diff = FungicideTreated - control) %>%
-   mutate(percent = (Diff / FungicideTreated) * 100) %>%
+   mutate(Diff = FungicideTreated_yield - control_yield) %>%
+   mutate(percent = (Diff / FungicideTreated_yield) * 100) %>%
    select(trial_ref,
@@
           year,
-          control,
-          FungicideTreated,
+          control_yield,
+          FungicideTreated_yield,
           percent,
@@
 ```
-
-## Summary of disease incidence effect on yields
-
-This sequence of graphs show that AUDPC and disease incidence tends not affect yields if the season is a low yielding season, _i.e._ lower than 1 tonne per hectare.
-The higher the yield, the greater greater the influence on the disease on the yield especially if the crop is high yielding with AUDPC also being large enough to reduce yield.
 

### 2021-02-01 03_Prep_data.Rmd
comment code to delete after second inspection

@@
 
-## Subset to trials containing DMI fungicides
+<!-- ## Subset to trials containing DMI fungicides -->
 
-```{r filterDMI_trials}
-DMI_Trials <-
-   PM_MB_dat %>%
-   filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole") %>%
-   distinct(trial_ref) %>%
-   pull()
+<!-- ```{r filterDMI_trials} -->
+<!-- DMI_Trials <- -->
+<!--    PM_MB_dat %>% -->
+<!--    filter(fungicide_ai == "tebuconazole" | -->
+<!--              fungicide_ai == "propiconazole") %>% -->
+<!--    distinct(trial_ref) %>% -->
+<!--    pull() -->
 
-PM_MB_dat <-
-   PM_MB_dat[PM_MB_dat$trial_ref %in% DMI_Trials, ]
-```
+<!-- PM_MB_dat <- -->
+<!--    PM_MB_dat[PM_MB_dat$trial_ref %in% DMI_Trials, ] -->
+<!-- ``` -->
 
-Now remove any non-DMI treatments or controls
-```{r}
-PM_MB_dat <-
-   PM_MB_dat %>%
-   filter(
-      fungicide_ai == "control" |
-         fungicide_ai == "tebuconazole" |
-         fungicide_ai == "propiconazole"
-   )
-```
+<!-- Now remove any non-DMI treatments or controls -->
+<!-- ```{r} -->
+<!-- PM_MB_dat <- -->
+<!--    PM_MB_dat %>% -->
+<!--    filter( -->
+<!--       fungicide_ai == "control" | -->
+<!--          fungicide_ai == "tebuconazole" | -->
+<!--          fungicide_ai == "propiconazole" -->
+<!--    ) -->
+<!-- ``` -->
 
-*****
+<!-- ***** -->
 
-## Standardising sample variance  
-Meta-analyses use variance from the data to calculate the effect sizes.
-The type of variance needs to be the same across all the data incorporated in the meta-analysis.
+<!-- ## Standardising sample variance   -->
+<!-- Meta-analyses use variance from the data to calculate the effect sizes. -->
+<!-- The type of variance needs to be the same across all the data incorporated in the meta-analysis. -->
 
-We are narrowing the meta-analysis to only include treatments using demethylation inhibitors, tebuconazole and propiconazole.
-Let's look at what type of statistical error was reported for the trials that used these fungicides.
+<!-- We are narrowing the meta-analysis to only include treatments using demethylation inhibitors, tebuconazole and propiconazole. -->
+<!-- Let's look at what type of statistical error was reported for the trials that used these fungicides. -->
 
-```{r variance_types}
-PM_MB_dat %>%
-   filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole") %>%
-   group_by(trial_ref, location, year , Y_error_type) %>%
-   summarise(DMI_treatments = length(Y_error_type), .groups = 'drop') %>%
-   arrange(Y_error_type) %>%
-   kable(caption = "Number of treatments for each trial and the error type reported",
-         align = "c") %>%
-   kableExtra::add_footnote(label = "DMI - demethylation inhibitors (tebuconazole and propiconazole).", notation = "none")
-```
+<!-- ```{r variance_types} -->
+<!-- PM_MB_dat %>% -->
+<!--    filter(fungicide_ai == "tebuconazole" | -->
+<!--              fungicide_ai == "propiconazole") %>% -->
+<!--    group_by(trial_ref, location, year , Y_error_type) %>% -->
+<!--    summarise(DMI_treatments = length(Y_error_type), .groups = 'drop') %>% -->
+<!--    arrange(Y_error_type) %>% -->
+<!--    kable(caption = "Number of treatments for each trial and the error type reported", -->
+<!--          align = "c") %>% -->
+<!--    kableExtra::add_footnote(label = "DMI - demethylation inhibitors (tebuconazole and propiconazole).", notation = "none") -->
+<!-- ``` -->
 
-The experiment summaries report either standard deviation or least square differences. 
-First we will convert LSD and standard deviation, then square the stdev to get sample variance.
+<!-- The experiment summaries report either standard deviation or least square differences.  -->
+<!-- First we will convert LSD and standard deviation, then square the stdev to get sample variance.   -->
 
-### Converting least-squares to sample variance
+<!-- ### Converting least-squares to sample variance   -->
 
-First let's get a list the of trials that reported LSD.
+<!-- First let's get a list the of trials that reported LSD.   -->
 
-```{r all_LSD_trials}
-Trials <- PM_MB_dat %>%
-   filter(Y_error_type == "lsd (P=0.05)") %>%
-   select(trial_ref) %>%
-   distinct()
-Trials
-```
+<!-- ```{r all_LSD_trials} -->
+<!-- Trials <- PM_MB_dat %>% -->
+<!--    filter(Y_error_type == "lsd (P=0.05)") %>% -->
+<!--    select(trial_ref) %>% -->
+<!--    distinct() -->
+<!-- Trials -->
+<!-- ``` -->
 
-Let's use this list of trials to subset the data and calculate sampling variances.
+<!-- Let's use this list of trials to subset the data and calculate sampling variances.   -->
 
-We will follow the method of converting 'least square differences' (LSD) to sampling variance reported by [Ngugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
+<!-- We will follow the method of converting 'least square differences' (LSD) to sampling variance reported by [Ngugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).   -->
 
-```{r LSD_2_Sampling_Variance}
-Tcrit <- 2.042
+<!-- ```{r LSD_2_Sampling_Variance} -->
+<!-- Tcrit <- 2.042  -->
 
-for (i in Trials$trial_ref) {
-   DFw <-
-      sum(PM_MB_dat[PM_MB_dat$trial_ref == i, ]$replicates) -
-      length(PM_MB_dat[PM_MB_dat$trial_ref == i, ]$replicates) # degrees of freedom within groups
+<!-- for (i in Trials$trial_ref) { -->
+<!--    DFw <- -->
+<!--       sum(PM_MB_dat[PM_MB_dat$trial_ref == i, ]$replicates) - -->
+<!--       length(PM_MB_dat[PM_MB_dat$trial_ref == i, ]$replicates) # degrees of freedom within groups -->
 
-   LSD <-
-      PM_MB_dat[PM_MB_dat$trial_ref == i, ]$yield_error[1]
+<!--    LSD <- -->
+<!--       PM_MB_dat[PM_MB_dat$trial_ref == i, ]$yield_error[1] -->
 
-   V_yield <-
-      (PM_MB_dat[PM_MB_dat$trial_ref == i, ]$replicates[1] * 
-          (LSD / Tcrit) ^ 2) / 2 
-   # method - Ngugi et.al (2011) DOI: 10.1094/phyto-08-10-0221
+<!--    V_yield <- -->
+<!--       (PM_MB_dat[PM_MB_dat$trial_ref == i, ]$replicates[1] *  -->
+<!--           (LSD / Tcrit) ^ 2) / 2  -->
+<!--    # method - Ngugi et.al (2011) DOI: 10.1094/phyto-08-10-0221 -->
 
-   for (j in seq_along(PM_MB_dat[PM_MB_dat$trial_ref == i,]$replicates)) {
-      if (j == 1) {
-         Sv <-
-            vector(length = length(PM_MB_dat[PM_MB_dat$trial_ref == i,]$replicates))
-      } # reset Sv vector if this is the first loop
+<!--    for (j in seq_along(PM_MB_dat[PM_MB_dat$trial_ref == i,]$replicates)) { -->
+<!--       if (j == 1) { -->
+<!--          Sv <- -->
+<!--             vector(length = length(PM_MB_dat[PM_MB_dat$trial_ref == i,]$replicates)) -->
+<!--       } # reset Sv vector if this is the first loop -->
 
-      Sv[j] = V_yield /
-         PM_MB_dat[PM_MB_dat$trial_ref == i,]$replicates[j]
+<!--       Sv[j] = V_yield / -->
+<!--          PM_MB_dat[PM_MB_dat$trial_ref == i,]$replicates[j] -->
 
-   }
+<!--    } -->
 
-   # Replace the values in the dataset
-   PM_MB_dat[PM_MB_dat$trial_ref == i,]$yield_error <-
-      Sv
-   PM_MB_dat[PM_MB_dat$trial_ref == i,]$Y_error_type <-
-      "SamplingVariance"
-}
-```
+<!--    # Replace the values in the dataset -->
+<!--    PM_MB_dat[PM_MB_dat$trial_ref == i,]$yield_error <- -->
+<!--       Sv -->
+<!--    PM_MB_dat[PM_MB_dat$trial_ref == i,]$Y_error_type <- -->
+<!--       "SamplingVariance" -->
+<!-- } -->
+<!-- ``` -->
 
-### Converting standard deviation to sample variance
+<!-- ### Converting standard deviation to sample variance -->
 
-Now to estimate the variance from the standard deviation.
+<!-- Now to estimate the variance from the standard deviation. -->
 
-```{r stdev2SampVariance}
-# subset data by those which describe the Yield error with standard deviation
-Trials <- PM_MB_dat %>%
-   filter(Y_error_type == "stdev") %>%
-   select(trial_ref) %>%
-   pull()
+<!-- ```{r stdev2SampVariance} -->
+<!-- # subset data by those which describe the Yield error with standard deviation -->
+<!-- Trials <- PM_MB_dat %>% -->
+<!--    filter(Y_error_type == "stdev") %>% -->
+<!--    select(trial_ref) %>% -->
+<!--    pull() -->
 
-PM_MB_dat[PM_MB_dat$trial_ref %in% Trials, "yield_error"] <-
-   PM_MB_dat[PM_MB_dat$trial_ref %in% Trials, "yield_error"] ^ 2
+<!-- PM_MB_dat[PM_MB_dat$trial_ref %in% Trials, "yield_error"] <- -->
+<!--    PM_MB_dat[PM_MB_dat$trial_ref %in% Trials, "yield_error"] ^ 2 -->
 
-PM_MB_dat[PM_MB_dat$trial_ref %in% Trials, ]$Y_error_type <-
-   "SamplingVariance"
-```
+<!-- PM_MB_dat[PM_MB_dat$trial_ref %in% Trials, ]$Y_error_type <- -->
+<!--    "SamplingVariance" -->
+<!-- ``` -->
 
-### Check variance of data-set
-Our data currently uses sample variance to define the yield error.
-We should expect that when yield increases so does the variance.
-Let's quickly plot this to check.
+<!-- ### Check variance of data-set -->
+<!-- Our data currently uses sample variance to define the yield error. -->
+<!-- We should expect that when yield increases so does the variance. -->
+<!-- Let's quickly plot this to check. -->
 
-```{r Var_mean_sqaures}
-PM_MB_dat %>%
-   ggplot(aes(x = grain_yield.t.ha., y = yield_error)) +
-   geom_point()
-```
+<!-- ```{r Var_mean_sqaures} -->
+<!-- PM_MB_dat %>% -->
+<!--    ggplot(aes(x = grain_yield.t.ha., y = yield_error)) + -->
+<!--    geom_point() -->
+<!-- ``` -->
 
-There seems to be no association between yield and sample variance, this might be due to the variability of mungbeans yields.
+<!-- There seems to be no association between yield and sample variance, this might be due to the variability of mungbeans yields. -->
 
-Let's look at the association between mean squares and yield to see if there is a more typical association between yield and variance.
+<!-- Let's look at the association between mean squares and yield to see if there is a more typical association between yield and variance. -->
 
-```{r Var_MeanSquarePlot}
-PM_MB_dat %>%
-   ggplot(aes(x = grain_yield.t.ha., y = Y_Msquare/replicates)) +
-   geom_point()
+<!-- ```{r Var_MeanSquarePlot} -->
+<!-- PM_MB_dat %>% -->
+<!--    ggplot(aes(x = grain_yield.t.ha., y = Y_Msquare/replicates)) + -->
+<!--    geom_point() -->
 
-```
+<!-- ``` -->
 
-There is a somewhat better trend here, if sampling variance from standard deviation proves unsuitable for the analysis we may compare models using variance from stdev and mean square for the best fit.
-However, seven treatments are missing mean square error.
+<!-- There is a somewhat better trend here, if sampling variance from standard deviation proves unsuitable for the analysis we may compare models using variance from stdev and mean square for the best fit.
+-->
+<!-- However, seven treatments are missing mean square error.   -->
 
-### Inspect variance and response for analysis
+<!-- ### Inspect variance and response for analysis   -->
 
-Let's inspect the response variance `grain_yield.t.ha` to see if it is normally distributed. 
-In many cases a log transformation of the response variable improves the fit, due to the prevalence of log distributed data in nature.
+<!-- Let's inspect the response variance `grain_yield.t.ha` to see if it is normally distributed.  -->
+<!-- In many cases a log transformation of the response variable improves the fit, due to the prevalence of log distributed data in nature.  -->
 
-```{r}
-hist_usq(PM_MB_dat$grain_yield.t.ha., main = "Grain yield (t / ha)")
-hist_usq(log(PM_MB_dat$grain_yield.t.ha.), main = "log(Grain yield (t / ha))")
-hist_usq(sqrt(PM_MB_dat$grain_yield.t.ha.), main = "sqrt(Grain yield (t / ha))")
-hist_usq(PM_MB_dat$yield_gain, main = "Mean difference to control (t / ha)")
-```
+<!-- ```{r} -->
+<!-- hist_usq(PM_MB_dat$grain_yield.t.ha., main = "Grain yield (t / ha)") -->
+<!-- hist_usq(log(PM_MB_dat$grain_yield.t.ha.), main = "log(Grain yield (t / ha))") -->
+<!-- hist_usq(sqrt(PM_MB_dat$grain_yield.t.ha.), main = "sqrt(Grain yield (t / ha))") -->
+<!-- hist_usq(PM_MB_dat$yield_gain, main = "Mean difference to control (t / ha)") -->
+<!-- ``` -->
 
-The distribution of data does not seem to be improved by transformation of the data.
-We will retain the continuous variable grain_yield.t.ha as the response.
-Mean differences won't be used as we are following the methodology of a ARM-based model, where mean differences are calculated following the meta-analysis.
+<!-- The distribution of data does not seem to be improved by transformation of the data. -->
+<!-- We will retain the continuous variable grain_yield.t.ha as the response. -->
+<!-- Mean differences won't be used as we are following the methodology of a ARM-based model, where mean differences are calculated following the meta-analysis. -->
 
-#### Calculate sample variance from mean square errors
+<!-- #### Calculate sample variance from mean square errors -->
 
-Currently our data frame has the sample variance calculated earlier, however we can approximate it using the mean squared error.
-Let's show the rational for our calculation and then add a secondary variance column (`vi2`).
+<!-- Currently our data frame has the sample variance calculated earlier, however we can approximate it using the mean squared error. -->
+<!-- Let's show the rational for our calculation and then add a secondary variance column (`vi2`). -->
 
-$MSE = Var + bias$
+<!-- $MSE = Var + bias$ -->
 
-However if our MSE was calculated from an unbiased sample we can assume $bias = 0$ and therefore:
+<!-- However if our MSE was calculated from an unbiased sample we can assume $bias = 0$ and therefore: -->
 
-$MSE = Var$
+<!-- $MSE = Var$ -->
 
-To calculate the sample variance (for each treatment in the trial) from the mean square error (Trial variance) all we need to do is divide by the number of samples in each treatment.
-We can show this because:
-$MSE = \frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n - 1}$
-Where the sum of squares for the fungicide treatment estimator ($y$) is divided by the number of fungicide treatments ($n$).
+<!-- To calculate the sample variance (for each treatment in the trial) from the mean square error (Trial variance) all we need to do is divide by the number of samples in each treatment. -->
+<!-- We can show this because: -->
+<!-- $MSE = \frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n - 1}$ -->
+<!-- Where the sum of squares for the fungicide treatment estimator ($y$) is divided by the number of fungicide treatments ($n$). -->
 
-The sample variance is a similar formula except we use $x$ instead of $y$.
-$S_{Var} = \frac{\sum_{x_1}^{x_n}(x_i - \overline{x})^2}{n - 1}$  
-$x$ being each observation within the experiment and $n$ being the number of samples in the whole trial.
-Therefore: 
-$S_{Var}\approx\frac{1}{n_{x}}\frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n_y - 1}$  
-Where $n_x$ is the number of samples within each treatment.
+<!-- The sample variance is a similar formula except we use $x$ instead of $y$. -->
+<!-- $S_{Var} = \frac{\sum_{x_1}^{x_n}(x_i - \overline{x})^2}{n - 1}$   -->
+<!-- $x$ being each observation within the experiment and $n$ being the number of samples in the whole trial. -->
+<!-- Therefore:  -->
+<!-- $S_{Var}\approx\frac{1}{n_{x}}\frac{\sum_{y_1}^{y_n}(y_i - \overline{y})^2}{n_y - 1}$   -->
+<!-- Where $n_x$ is the number of samples within each treatment. -->
 
-As mentioned before there are a few treatments with no MSE (NAs), we can calculate it from the sample variance using this logic above.
+<!-- As mentioned before there are a few treatments with no MSE (NAs), we can calculate it from the sample variance using this logic above.  -->
 
-```{r EstMSE}
-PM_MB_dat[is.na(PM_MB_dat$Y_Msquare),"Y_Msquare"] <- 
-   PM_MB_dat %>%
-   filter(is.na(Y_Msquare))%>%
-   mutate(Y_Msquare = yield_error * replicates)%>%
-   pull(Y_Msquare)
-```
+<!-- ```{r EstMSE} -->
+<!-- PM_MB_dat[is.na(PM_MB_dat$Y_Msquare),"Y_Msquare"] <-  -->
+<!--    PM_MB_dat %>% -->
+<!--    filter(is.na(Y_Msquare))%>% -->
+<!--    mutate(Y_Msquare = yield_error * replicates)%>% -->
+<!--    pull(Y_Msquare) -->
+<!-- ``` -->
 
-Now to calculate the sample variance from MSE for all treatments.
+<!-- Now to calculate the sample variance from MSE for all treatments. -->
 
-```{r MSE_2_SVar}
-#calculation when using log of response
-# PM_MB_dat$vi <-
-#    PM_MB_dat$Y_Msquare / (PM_MB_dat$n * PM_MB_dat$grain_yield.t.ha. ^
-#                                   2)
+<!-- ```{r MSE_2_SVar} -->
+<!-- #calculation when using log of response -->
+<!-- # PM_MB_dat$vi <- -->
+<!-- #    PM_MB_dat$Y_Msquare / (PM_MB_dat$n * PM_MB_dat$grain_yield.t.ha. ^ -->
+<!-- #                                   2) -->
 
-PM_MB_dat$vi2 <- 
-   PM_MB_dat$Y_Msquare / 
-   PM_MB_dat$replicates
-```
+<!-- PM_MB_dat$vi2 <-  -->
+<!--    PM_MB_dat$Y_Msquare /  -->
+<!--    PM_MB_dat$replicates -->
+<!-- ``` -->
 
-*******
+<!-- ******* -->
 
-## Classifying fungicide treatment
+<!-- ## Classifying fungicide treatment   -->
 
-First are going to calculate the time between the first sign of disease and the fungicide applications.
+<!-- First are going to calculate the time between the first sign of disease and the fungicide applications.   -->
 
-```{r clustered_fungicide_applications}
-PM_MB_dat %<>%
-   mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
-   mutate(fungicide_timing_2 = fungicide_application_2 - fungicide_application_1) %>%
-   mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2)
+<!-- ```{r clustered_fungicide_applications} -->
+<!-- PM_MB_dat %<>% -->
+<!--    mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>% -->
+<!--    mutate(fungicide_timing_2 = fungicide_application_2 - fungicide_application_1) %>% -->
+<!--    mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2) -->
 
-```
+<!-- ``` -->
 
-To ensure sufficient number of replicates, we will bin the continuous variable into three categorical variables relating to when the first fungicide application was made, relative to the first sign of disease.
+<!-- To ensure sufficient number of replicates, we will bin the continuous variable into three categorical variables relating to when the first fungicide application was made, relative to the first sign of disease.
+-->
 
-These categorical variables are named:
+<!-- These categorical variables are named: -->
 
-   - **Early**: First fungicide application was prior to first sign of disease. 
-   - **Recommended**: First fungicide application was applied on the day powdery mildew was observed, or within three days of first sign. 
-   - **Late**: First fungicide application was four or more days after first sign of disease being observed.
+<!--    - **Early**: First fungicide application was prior to first sign of disease.  -->
+<!--    - **Recommended**: First fungicide application was applied on the day powdery mildew was observed, or within three days of first sign.  -->
+<!--    - **Late**: First fungicide application was four or more days after first sign of disease being observed.  -->
 
-The number of sprays need also be defined.
+<!-- The number of sprays need also be defined. -->
 
-```{r TreatmentTable}
-data.frame(TreatmentName = c("Early", "Recommended", "Late", "EarlyPlus", "RecommendedPlus", "LatePlus"),
-           n_sprays = rep(c("Single", "Two - Three"), each = 3),
-           DaysRelativeToFirstSign = c("Prior to first sign of Powdery Mildew",
-                                       "1 - 3 days after first sign of Powdery Mildew",
-                                       "7 - 8 days after first sign of Powdery Mildew"))%>%
-   kable()
-```
+<!-- ```{r TreatmentTable} -->
+<!-- data.frame(TreatmentName = c("Early", "Recommended", "Late", "EarlyPlus", "RecommendedPlus", "LatePlus"), -->
+<!--            n_sprays = rep(c("Single", "Two - Three"), each = 3), -->
+<!--            DaysRelativeToFirstSign = c("Prior to first sign of Powdery Mildew", -->
+<!--                                        "1 - 3 days after first sign of Powdery Mildew", -->
+<!--                                        "7 - 8 days after first sign of Powdery Mildew"))%>% -->
+<!--    kable() -->
+<!-- ``` -->
 
-```{r simple_clusters}
-PM_MB_dat <- PM_MB_dat %>%
-   mutate(
-      spray_management = case_when(
-         fungicide_timing_1 < 0 &
-            is.na(fungicide_application_2) &
-            is.na(fungicide_application_3) ~ "Early",
-         fungicide_timing_1 >= 0 &
-            fungicide_timing_1 < 4 &
-            is.na(fungicide_application_2) &
-            is.na(fungicide_application_3) ~ "Recommended",
-         fungicide_timing_1 >= 4 &
-            is.na(fungicide_application_2) &
-            is.na(fungicide_application_3) ~ "Late",
-         fungicide_timing_1 < 0 &
-            !is.na(fungicide_application_2) ~ "Early_plus",
-         fungicide_timing_1 >= 0 &
-            fungicide_timing_1 < 4 &
-            !is.na(fungicide_application_2) ~ "Recommended_plus",
-         fungicide_timing_1 >= 4 &
-            !is.na(fungicide_application_2) ~ "Late_plus",
-         TRUE ~ "Other"
-      )
-   )
+<!-- ```{r simple_clusters} -->
+<!-- PM_MB_dat <- PM_MB_dat %>% -->
+<!--    mutate( -->
+<!--       spray_management = case_when( -->
+<!--          fungicide_timing_1 < 0 & -->
+<!--             is.na(fungicide_application_2) & -->
+<!--             is.na(fungicide_application_3) ~ "Early", -->
+<!--          fungicide_timing_1 >= 0 & -->
+<!--             fungicide_timing_1 < 4 & -->
+<!--             is.na(fungicide_application_2) & -->
+<!--             is.na(fungicide_application_3) ~ "Recommended", -->
+<!--          fungicide_timing_1 >= 4 & -->
+<!--             is.na(fungicide_application_2) & -->
+<!--             is.na(fungicide_application_3) ~ "Late", -->
+<!--          fungicide_timing_1 < 0 & -->
+<!--             !is.na(fungicide_application_2) ~ "Early_plus", -->
+<!--          fungicide_timing_1 >= 0 & -->
+<!--             fungicide_timing_1 < 4 & -->
+<!--             !is.na(fungicide_application_2) ~ "Recommended_plus", -->
+<!--          fungicide_timing_1 >= 4 & -->
+<!--             !is.na(fungicide_application_2) ~ "Late_plus", -->
+<!--          TRUE ~ "Other" -->
+<!--       ) -->
+<!--    ) -->
 
-PM_MB_dat[PM_MB_dat$fungicide_ai == "control",
-            c(
-               "fungicide_timing_1",
-               "fungicide_timing_2",
-               "fungicide_timing_3",
-               "spray_management"
-            )] <- "control"
-```
+<!-- PM_MB_dat[PM_MB_dat$fungicide_ai == "control", -->
+<!--             c( -->
+<!--                "fungicide_timing_1", -->
+<!--                "fungicide_timing_2", -->
+<!--                "fungicide_timing_3", -->
+<!--                "spray_management" -->
+<!--             )] <- "control" -->
+<!-- ``` -->
 
-Now to view the number break-down of the `spray_management` treatments
+<!-- Now to view the number break-down of the `spray_management` treatments -->
 
-```{r tableSprayManagement}
-table(PM_MB_dat$spray_management)
-```
+<!-- ```{r tableSprayManagement} -->
+<!-- table(PM_MB_dat$spray_management) -->
+<!-- ``` -->
 
-'Early_plus' treatments are few in number, these treatments will have too few comparisons with other treatments in the meta-analysis to provide accurate results.
+<!-- 'Early_plus' treatments are few in number, these treatments will have too few comparisons with other treatments in the meta-analysis to provide accurate results.
 Therefore we will remove 'Early_plus' from the analysis.
+-->
 
-```{r simpler_clusters_remove}
-PM_MB_dat <-
-   PM_MB_dat %>%
-   filter(spray_management != "Early_plus")
-```
-*****
+<!-- ```{r simpler_clusters_remove} -->
+<!-- PM_MB_dat <- -->
+<!--    PM_MB_dat %>% -->
+<!--    filter(spray_management != "Early_plus") -->
+<!-- ``` -->
+<!-- ***** -->
 
-## Trial factor
-We have a number of variable which could introduce variation in our analysis. 
-We will combine these variables into a single variable called `trial` which will help us define the between trial variation.
+<!-- ## Trial factor -->
+<!-- We have a number of variable which could introduce variation in our analysis.  -->
+<!-- We will combine these variables into a single variable called `trial` which will help us define the between trial variation.   -->
 
-```{r define_trial}
-PM_MB_dat <-
-   PM_MB_dat %>%
-   mutate(trial = paste(trial_ref,
-                        year,
-                        location,
-                        host_genotype,
-                        row_spacing,
-                        sep = "_")) %>%
-   select(trial_ref, trial, everything())
-```
+<!-- ```{r define_trial} -->
+<!-- PM_MB_dat <- -->
+<!--    PM_MB_dat %>% -->
+<!--    mutate(trial = paste(trial_ref, -->
+<!--                         year, -->
+<!--                         location, -->
+<!--                         host_genotype, -->
+<!--                         row_spacing, -->
+<!--                         sep = "_")) %>% -->
+<!--    select(trial_ref, trial, everything()) -->
+<!-- ``` -->
 
-*****
+<!-- ***** -->
 
-## Test dose effect
+<!-- ## Test dose effect -->
 
-Earlier, in section [Fungicide Doses](#fungicide-doses) we noted there were different doses of propiconazole, which might influence our analysis. 
-The current label for Custodia [PER82104](http://permits.apvma.gov.au/PER82104.PDF), containing: 120 g/L azoxystrobin and 200 g/L tebuconazole, recommends between 300 ml - 600 ml of the tebuconazole fraction per hectare, equivalent to 60 - 120 grams per hectare.
-These label rates are assumed to be the same for propiconazole inferring these concentrations might be within the recommended rates. 
-It is also worth noting the APVMA permit [PER13979](http://permits.apvma.gov.au/PER13979.PDF) which allows the use of tebuconazole between 62.35 g / ha and 83 g / ha depending on the product formulation.
+<!-- Earlier, in section [Fungicide Doses](#fungicide-doses) we noted there were different doses of propiconazole, which might influence our analysis.  -->
+<!-- The current label for Custodia [PER82104](http://permits.apvma.gov.au/PER82104.PDF), containing: 120 g/L azoxystrobin and 200 g/L tebuconazole, recommends between 300 ml - 600 ml of the tebuconazole fraction per hectare, equivalent to 60 - 120 grams per hectare.
+-->
+<!-- These label rates are assumed to be the same for propiconazole inferring these concentrations might be within the recommended rates.  -->
+<!-- It is also worth noting the APVMA permit [PER13979](http://permits.apvma.gov.au/PER13979.PDF) which allows the use of tebuconazole between 62.35 g / ha and 83 g / ha depending on the product formulation.
+-->
 
-Let's add the dose variable to the `trial` variable then compare linear mixed effect models including and excluding dose in the trial variable.
-We already have a factor breaking down the dose in the `trial` variable.
-Let's make a new one without dose.
+<!-- Let's add the dose variable to the `trial` variable then compare linear mixed effect models including and excluding dose in the trial variable. -->
+<!-- We already have a factor breaking down the dose in the `trial` variable. -->
+<!-- Let's make a new one without dose. -->
 
-```{r define_Dose}
-table(PM_MB_dat$dose_ai.ha)
+<!-- ```{r define_Dose} -->
+<!-- table(PM_MB_dat$dose_ai.ha) -->
 
-PM_MB_dat <- 
-   PM_MB_dat %>%
-   mutate(dose = case_when(
-      dose_ai.ha == 0 ~ "control",
-      dose_ai.ha <= 70 ~ "lowDose",
-      dose_ai.ha > 70 ~ "highDose",
-      TRUE ~ NA_character_
-   ))
+<!-- PM_MB_dat <-  -->
+<!--    PM_MB_dat %>% -->
+<!--    mutate(dose = case_when( -->
+<!--       dose_ai.ha == 0 ~ "control", -->
+<!--       dose_ai.ha <= 70 ~ "lowDose", -->
+<!--       dose_ai.ha > 70 ~ "highDose", -->
+<!--       TRUE ~ NA_character_ -->
+<!--    )) -->
 
-```
+<!-- ``` -->
 
-```{r dose_test}
-PM_MB_dat <-
-   PM_MB_dat %>%
-    mutate(trial_dose = paste(trial_ref, year, location, host_genotype,
-                        row_spacing,dose , sep = "_"))
+<!-- ```{r dose_test} -->
+<!-- PM_MB_dat <- -->
+<!--    PM_MB_dat %>% -->
+<!--     mutate(trial_dose = paste(trial_ref, year, location, host_genotype, -->
+<!--                         row_spacing,dose , sep = "_")) -->
 
-cbind(NoDose = head(PM_MB_dat$trial),
-      Dose = head(PM_MB_dat$trial_dose)) %>%
-   kable()
-```
+<!-- cbind(NoDose = head(PM_MB_dat$trial), -->
+<!--       Dose = head(PM_MB_dat$trial_dose)) %>% -->
+<!--    kable() -->
+<!-- ``` -->
 
-Let's test the dose effect in a linear mixed effect model.
+<!-- Let's test the dose effect in a linear mixed effect model. -->
 
-```{r dose_lmer}
-m_noDose <-
-   lmer(log(grain_yield.t.ha. * 1000) ~ factor(spray_management) +
-           (1 | trial),
-        data = PM_MB_dat)
+<!-- ```{r dose_lmer} -->
+<!-- m_noDose <- -->
+<!--    lmer(log(grain_yield.t.ha. * 1000) ~ factor(spray_management) + -->
+<!--            (1 | trial), -->
+<!--         data = PM_MB_dat) -->
 
-m_dose <-
-   lmer(log(grain_yield.t.ha. * 1000) ~ factor(spray_management) +
-           (1 | trial_dose),
-        data = PM_MB_dat)
+<!-- m_dose <- -->
+<!--    lmer(log(grain_yield.t.ha. * 1000) ~ factor(spray_management) + -->
+<!--            (1 | trial_dose), -->
+<!--         data = PM_MB_dat) -->
 
-anova(m_noDose, m_dose)
-```
+<!-- anova(m_noDose, m_dose) -->
+<!-- ``` -->
 
-Using the model without dose produces a lower AIC and we find no significant difference between models.
-We will not use dose as a defining variable in `trial`.
+<!-- Using the model without dose produces a lower AIC and we find no significant difference between models. -->
+<!-- We will not use dose as a defining variable in `trial`.   -->
 
-******
+<!-- ****** -->
 
-## Row spacing
+<!-- ## Row spacing -->
 
-We may want to consider row spacing in the trials.
-However one of the locations has `NA` as the row spacing.
-```{r}
-PM_MB_dat%>%
-   filter(is.na(row_spacing))%>%
-   select(trial_ref,year, location, row_spacing,spray_management,host_genotype, fungicide_ai)
-```
+<!-- We may want to consider row spacing in the trials. -->
+<!-- However one of the locations has `NA` as the row spacing. -->
+<!-- ```{r} -->
+<!-- PM_MB_dat%>% -->
+<!--    filter(is.na(row_spacing))%>% -->
+<!--    select(trial_ref,year, location, row_spacing,spray_management,host_genotype, fungicide_ai) -->
+<!-- ``` -->
 
-For now let's assign the most used row spacing of 0.33 m as an approximation so the model can analyse this as a continuous variable. 
-If we decide to use the row_spacing column as a factor in the final model we will need to remove this approximation.
+<!-- For now let's assign the most used row spacing of 0.33 m as an approximation so the model can analyse this as a continuous variable.  -->
+<!-- If we decide to use the row_spacing column as a factor in the final model we will need to remove this approximation.   -->
 
-```{r assign_row_spacing_missing}
-PM_MB_dat[is.na(PM_MB_dat$row_spacing),"row_spacing"] <- 0.33
-```
+<!-- ```{r assign_row_spacing_missing} -->
+<!-- PM_MB_dat[is.na(PM_MB_dat$row_spacing),"row_spacing"] <- 0.33 -->
+<!-- ``` -->
 
-********
+<!-- ******** -->
 
-## Remove unnecessary variables
+<!-- ## Remove unnecessary variables -->
 
-```{r saveDat}
-PM_MB_dat <-
-   PM_MB_dat %>%
-   select(
-      -c(
-         trial_dose,
-         fungicide_timing_1,
-         fungicide_timing_2,
-         fungicide_timing_3,
-         dose,
-         fungicide_application_4,
-         fungicide_application_5,
-         fungicide_application_6,
-         fungicide_application_7
-      )
-   ) 
-```
+<!-- ```{r saveDat} -->
+<!-- PM_MB_dat <- -->
+<!--    PM_MB_dat %>% -->
+<!--    select( -->
+<!--       -c( -->
+<!--          trial_dose, -->
+<!--          fungicide_timing_1, -->
+<!--          fungicide_timing_2, -->
+<!--          fungicide_timing_3, -->
+<!--          dose, -->
+<!--          fungicide_application_4, -->
+<!--          fungicide_application_5, -->
+<!--          fungicide_application_6, -->
+<!--          fungicide_application_7 -->
+<!--       ) -->
+<!--    )  -->
+<!-- ``` -->
 

### 2021-02-01 03_Prep_data.Rmd
remove code chunk simplifying data

@@
 
-### Simplify and save data
-
-```{r simplifyData}
-PM_MB_dat_full <- PM_MB_dat
-
-PM_MB_dat <-
-   PM_MB_dat %>%
-   mutate(
-      spray_management =
-         factor(
-            spray_management,
-            c(
-               "control",
-               "Early",
-               "Recommended",
-               "Recommended_plus",
-               "Late",
-               "Late_plus"
-            )
-         ),
-      id = row_number(),
-      vi = yield_error,
-      n = replicates
-   ) %>%
-   select(
-      trial,
-      trial_ref,
-      location,
-      year,
-      row_spacing,
-      host_genotype,
-      spray_management,
-      fungicide_ai,
-      grain_yield.t.ha.,
-      yield_gain,
-      vi,
-      vi2,
-      n,
-      id
-   )
-```
-
 ```{r saveData_PrepD}

### 2021-02-01 01_TrialsForInclusionInAnalysis.Rmd
correct yield variance calculation

@@
          case_when(
-            Y_error_type == "stdev" ~ disease_error ^ 2,
+            Y_error_type == "stdev" ~ yield_error ^ 2,
             Y_error_type == "lsd (P=0.05)" ~
-               (replicates * ((disease_error / 1.96) ^ 2) / 2) / replicates
+               (replicates * ((yield_error / 1.96) ^ 2) / 2) / replicates
          ),

### 2021-02-01 02_Preliminary_analysis.Rmd
Simplify and correct introduction, clearer headings, remove dupplicate tables

@@
 
-The data explored in the `PM_MB_dat` data frame is a list of mean values from each treatment in each respective experiment.
-These preliminary analyses will describe the data and then investigate any change in mungbean yields which is attributable to the fungicide treatment.
+The data explored in the `PM_MB_dat` data frame is a clean data frame focusing on trials which met the selection criteria and the treatments testing DMi fungicides (tebuconazole / propiconazole) or no spray controls.
 
-All fungicide AI treatments are still contained in the `PM_MB_dat` data, so filtering the data might be necessary to only inspect DMI treatments.
-
-### Descriptive statistics  
-#### Spatio-temporal variation
-
+### Spatio-temporal variation  
+#### Trial seasons
 Let's look at how many trials were undertaken each season in trials including DMI fungicides.
@@
 ```
-
-Also the location of the trials including DMI fungicides.
+#### Trial locations
+The location of the trials including DMI fungicides.
 
@@
 
-#### Mean yield
-
-What is the variation in yield over all the trials in the no spray control.
-
-```{r ControlYield_AllTrials}
-PM_MB_dat %>%
-   filter(fungicide_ai == "control") %>%
-   summarise(
-      mean_yield = mean(grain_yield.t.ha. * 1000),
-      median_yield = median(grain_yield.t.ha. * 1000),
-      minimum_yield = min(grain_yield.t.ha. * 1000),
-      maximum_yield = max(grain_yield.t.ha. * 1000),
-      yield_stdev = sd(grain_yield.t.ha. * 1000),
-      yield_SE = sd(grain_yield.t.ha. * 1000) /
-         sqrt(n())
-   ) %>%
-   kable(align = 'c',
-         caption = "Average yield statistics for no spray control plots")
-```
-
-Mean yields in DMI fungicide treated plots
-```{r Yield_DMITrials}
-PM_MB_dat %>%
-   filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole")%>%
-   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
-             median_yield = median(grain_yield.t.ha. * 1000),
-             minimum_yield = min(grain_yield.t.ha.*1000),
-             maximum_yield = max(grain_yield.t.ha.*1000),
-             yield_stdev = sd(grain_yield.t.ha. * 1000),
-             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
-   kable(align = 'c',
-   caption = "Average yield statistics for DMI fungicide treated plots")
-
-```
-
-Trial mean yields in all fungicide treated plots
-```{r Yield_AllTrials}
-PM_MB_dat %>%
-   group_by(trial_ref, location, year)%>%
-   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
-             median_yield = median(grain_yield.t.ha. * 1000),
-             minimum_yield = min(grain_yield.t.ha.*1000),
-             maximum_yield = max(grain_yield.t.ha.*1000),
-             yield_stdev = sd(grain_yield.t.ha. * 1000),
-             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
-   arrange(yield_sterr) %>%
-   kable(align = 'c',
-   caption = "Average yield statistics for DMI fungicide treated plots")
-
-```
-
 #### Full trial summary
-
 Let's inspect a summary of both powdery mildew severity and grain yield for trials including DMI fungicides.

### 2021-02-02 02_Preliminary_analysis.Rmd
Code improvements to full summary table

@@
    PM_MB_dat %>%
-   filter(
-      fungicide_ai == "control" |
-         fungicide_ai == "tebuconazole" |
-         fungicide_ai == "propiconazole"
-   ) %>%
    mutate(PM_sev_control = case_when(fungicide_ai == "control" ~ PM_final_severity,
@@
    ) %>%
-   filter(min_PM_sev < 10) %>% # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf
    arrange(year) %>%

### 2021-02-02 02_Preliminary_analysis.Rmd
Edit headings and inspect fungicide effect on severity

@@
 
-## Explore and Visualise Data
+## Trial focused summaries
 
@@
 
-#### Full trial summary
+### Full trial summary
 Let's inspect a summary of both powdery mildew severity and grain yield for trials including DMI fungicides.
@@
 
+Save table to a word document to use in manuscript
 ```{r eval=FALSE, include=FALSE}
@@
 ```
+
+## Treatment focuses summaries
 
@@
 
-<br>
-<br>
-<br>
+### Fungicide type
+#### Powdery mildew severity
+```{r TebuVPropi_sev}
+n_C <- sum(PM_MB_dat$fungicide_ai == "control")
+n_P <- sum(PM_MB_dat$fungicide_ai == "propiconazole")
+n_T <- sum(PM_MB_dat$fungicide_ai == "tebuconazole")
+
+PM_MB_dat %>%
+   ggplot(aes(y = PM_final_severity, x = as.factor(fungicide_ai))) +
+   xlab("Fungicide treatment") +
+   ggtitle(label = "Powdery mildew severity for each fungicide active ingredient") +
+   labs(caption = paste("Control n:", n_C,
+                        "; Propiconazole n:", n_P,
+                        "; Tebuconazole n:", n_T, sep = "")) +
+   geom_boxplot() +
+   scale_fill_usq() +
+   scale_colour_usq()
+```
+#### Yield effect
+```{r TebuVPropi_Yi}
+PM_MB_dat %>%
+   ggplot(aes(y = grain_yield.t.ha., x = as.factor(fungicide_ai))) +
+   xlab("Fungicide treatment") +
+   ggtitle(label = "Grain yield for each fungicide active ingredient") +
+   labs(caption = paste("Control n:", n_C,
+                        "; Propiconazole n:", n_P,
+                        "; Tebuconazole n:", n_T, sep = "")) +
+   geom_boxplot() +
+   scale_colour_usq()
+```
 
 ### Fungicide Doses{#fungicide-doses}  
-From this point on we will investigate only the DMI fungicides, tebuconazole and propiconazole, and disregard all other fungicide modes-of-action.
+This analysis focuses only the DMI fungicides, tebuconazole and propiconazole, which were trialed the most often.
 

### 2021-02-02 02_Preliminary_analysis.Rmd
spelling

@@
 ### Fungicide Doses{#fungicide-doses}  
-This analysis focuses only the DMI fungicides, tebuconazole and propiconazole, which were trialed the most often.
+This analysis focuses only the DMI fungicides, tebuconazole and propiconazole, which were trialled the most often.
 

### 2021-02-03 02_Preliminary_analysis.Rmd
remove code chunk that saves Rdata file
Add inspection of crop rainfall

@@
 
-```{r}
-save(PM_MB_dat, file = here("cache/PreliminaryData.Rdata"))
+### In-crop rainfall
+First an inspection of all rainfall within the season
+```{r season_rainfall}
+source("R/add_lat_longs.R") # code adds the latitude- and longitude to PM_MB_dat
+source("R/crop_rain.R")
+
+# Obtain rainfall from bomrang
+PM_MB_dat$sum_rain <-
+   apply(PM_MB_dat, 1, function(x) {
+      crop_rain(
+         latitude = x["lat"],
+         longitude = x["lon"],
+         start = x["planting_date"],
+         end = x["harvest_date"]
+      )
+   })
+
+# plot yield vs rainfall
+PM_MB_dat %>%
+   ggplot(aes(y = grain_yield.t.ha., x = sum_rain)) + 
+   geom_point()
 ```
+
+```{r lm_total}
+summary(lm(grain_yield.t.ha. ~ sum_rain, data = PM_MB_dat))
+```
+
+```{r early_season_rain}
+PM_MB_dat$early_rain <-
+   apply(PM_MB_dat, 1, function(x) {
+      crop_rain(
+         latitude = x["lat"],
+         longitude = x["lon"],
+         start = x["planting_date"],
+         end = x["first_sign_disease"]
+      )
+   })
+
+PM_MB_dat %>%
+   ggplot(aes(y = grain_yield.t.ha., x = early_rain)) + 
+   geom_point()
+```
+
+```{r lm_early_rain}
+summary(lm(grain_yield.t.ha. ~ early_rain, data = PM_MB_dat))
+```
+
+```{r late_rain}
+PM_MB_dat$late_rain <-
+   apply(PM_MB_dat, 1, function(x) {
+      crop_rain(
+         latitude = x["lat"],
+         longitude = x["lon"],
+         start = x["first_sign_disease"],
+         end = x["harvest_date"]
+      )
+   })
+
+PM_MB_dat %>%
+   ggplot(aes(y = grain_yield.t.ha., x = late_rain)) + 
+   geom_point()
+```
+
+```{r lm_late_rain}
+summary(lm(grain_yield.t.ha. ~ late_rain, data = PM_MB_dat))
+```
+
+```{r mid_rain}
+PM_MB_dat$mid_rain <-
+   apply(PM_MB_dat, 1, function(x) {
+      crop_rain(
+         latitude = x["lat"],
+         longitude = x["lon"],
+         start = ymd(x["first_sign_disease"]) + days(30),
+         end = ymd(x["first_sign_disease"]) + days(70)
+      )
+   })
+
+PM_MB_dat %>%
+   ggplot(aes(y = grain_yield.t.ha., x = mid_rain)) + 
+   geom_point()
+```
+
+```{r lm_late_rain}
+summary(lm(grain_yield.t.ha. ~ late_rain, data = PM_MB_dat))
+```

### 2021-02-03 04_MetaAnalysis.Rmd
load data from clean_data.csv or preliminary analysis.rmd
import Rdata from chap1
comment -load Rdata
add moderator to test the effect of early onset PM vs late onset PM

@@
 # Data
-load("cache/PrepData.Rdata"
-)
+# load("cache/ImportDataAndSelectTrials01.Rdata")
+
+PM_MB_dat <-
+   read.csv("cache/PM_MB_clean_data.csv", stringsAsFactors = FALSE)
 ```
@@
    - Trial, which resolves combinations of categorical variables: year, location, row spacing, fungicide dose and cultivar; is set as a random intercept
+
+### Define Trial
+```{r define_trial}
+PM_MB_dat <-
+   PM_MB_dat %>%
+   mutate(trial = paste(trial_ref,
+                        year,
+                        location,
+                        host_genotype,
+                        row_spacing,
+                        sep = "_")) 
+```
 
@@
 summary(PM_mv)
+```
+
+### Influence of disease onset
+
+To determine if when in the season the disease occurs influences the efficacy at which fungicide applications protect yield we will create a categorical variable defining `early` or `late` disease onset.
+
+`early` and `late` will be divided by the median days after sowing when signs of the disease were first observed.
+```{r median onset}
+PM_MB_dat %>%
+   mutate(first_sign_days = lubridate::ymd(first_sign_disease) -
+             lubridate::ymd(planting_date)) %>%
+   pull(first_sign_days)%>%
+   median()
+```
+Now lets define these two new variables, `first_sign_days` and `onset` in the data.
+
+```{r define_onset}
+PM_MB_dat <- PM_MB_dat %>%
+   mutate(first_sign_days = lubridate::ymd(first_sign_disease) -
+             lubridate::ymd(planting_date)) %>%
+   mutate(onset = case_when(first_sign_days <= 39 ~ "early_onset",
+                            first_sign_days > 39 ~ "late_onset"))
+```
+
+Inspect a histogram of when first sign occured in the crop
+```{r hist_onset}
+PM_MB_dat %>%
+   ggplot(aes(x = first_sign_days)) +
+   geom_histogram() +
+   geom_vline(xintercept = 39)
+```
+
+To put this onset number into context for plant maturity, 40 days is approximately when flowering begins in the plant.
+
+#### metafor onset analysis
+
+We are adding the `onset` variable as a moderator to test and interaction with the `spray_management` variable as a moderator and an interactive term to the `trial` random variable.
+
+```{r osset_Metafor-analysis}
+PM_mv_onset <- rma.mv(
+   yi = grain_yield.t.ha.,
+   vi,
+   mods = ~ spray_management * onset,
+   method = "ML",
+   random = list(~ spray_management | trial, ~ 1 | id),
+   struct = "UN",
+   control = list(optimizer = "optim"),
+   data = PM_MB_dat
+)
+
+```
+
+```{r}
+anova(PM_mv, PM_mv_onset)
+```
+This comparison tells us the meta-analysis including `onset` explained more residual heterogeneity, as shown by the lower QE value.
+However the higher AIC indicates that the model omitting `onset` is a slightly better fit.
+Also the chi-squared test uncertain that the `onset` model is significantly better as indicated by the `pval` 0.3258.
+The higher log likelihood on the `onset` model does intricate there is some merit to this model and that perhaps with more trials to increase statistical power might provide a useful model.
+
+```{r}
+summary(PM_mv_onset)
 ```

### 2021-02-04 04_MetaAnalysis.Rmd
Add moderator test of disease pressure, and other small corrections

@@
 
+### Influence of disease pressure
+
+To determine if the seasonal disease pressure influences the efficacy at which fungicide applications protect yield we will create a categorical variable defining `high_pressure` or `low_pressure`.
+
+`high_pressure` and `low_pressure` will be divided by the median disease severity in the no spray control treatments at the end of the season.
+```{r median_pressure}
+PM_MB_dat %>%
+   filter(fungicide_ai == "control") %>%
+   pull(PM_final_severity)%>%
+   median()
+```
+Now lets define these two new variables, `first_sign_days` and `onset` in the data.
+
+```{r define_disease_pressure}
+PM_MB_dat <- PM_MB_dat %>%
+   mutate(d_pressure = case_when(PM_final_severity < 8 ~ "low_pressure",
+                            PM_final_severity >= 8 ~ "high_pressure"))
+```
+
+Inspect a histogram of when first sign occured in the crop
+```{r hist_pressure}
+PM_MB_dat %>%
+   ggplot(aes(x = PM_final_severity)) +
+   geom_histogram() +
+   geom_vline(xintercept = 8)
+```
+
+#### metafor onset analysis
+
+We are adding the `onset` variable as a moderator to test and interaction with the `spray_management` variable as a moderator and an interactive term to the `trial` random variable.
+
+```{r osset_Metafor-analysis}
+PM_mv_dp <- rma.mv(
+   yi = grain_yield.t.ha.,
+   vi,
+   mods = ~ spray_management * d_pressure,
+   method = "ML",
+   random = list(~ spray_management | trial, ~ 1 | id),
+   struct = "UN",
+   control = list(optimizer = "optim"),
+   data = PM_MB_dat
+)
+
+```
+
+```{r}
+anova(PM_mv, PM_mv_dp)
+```
+This comparison tells us the meta-analysis including `d_pressure` explained more residual heterogeneity, as shown by the lower QE value.
+However the higher AIC indicates that the model omitting `d_pressure` is a slightly better fit.
+Also the chi-squared test uncertain that the `d_pressure` model is significantly better as indicated by the `pval` 0.1336.
+The higher log likelihood on the `d_pressure` model does intricate there is some merit to this model and that perhaps with more trials to increase statistical power might provide a useful model.
+
+```{r}
+summary(PM_mv_dp)
+```
+
+### Test variance-covavriance matrix structure
 Let's try the model with an implied simpler variance-covariance matrix "compound symmetry" ("CS") to examine if unstructured matrix is suitable.
@@
 
-The test shows that the 'Full', more complicated model `PM_mv`, is a better fit and therefore we should keep the unstructured variance-covariance matrix.
+Again `PM_mv` (Full) prevails as the better model (p = 0.0014; AIC = -45.4359) and therefore we should keep the unstructured variance-covariance matrix.
+
+ > Therfore the model `PM_mv`, is a best fit.
+
+## Summarise PM_mv model
 
@@
 
-Let's present the meta-analysis results for the moderator variables in a forest style plot.
-First Let's create a table of the results.
+### Meta-analysis moderator estimates table
+Let's present the meta-analysis results for the moderator variables in a table of estimates.
 
@@
 # adjust estimates to show absolute means
-results_mv <-
-   results_mv[2:6,] %>%
-   mutate(Effect = Effect + results_mv$Effect[1]) %>%
-   mutate(CI_lower = CI_lower + results_mv$CI_lower[1]) %>%
-   mutate(CI_upper = CI_upper + results_mv$CI_upper[1]) %>%
-   bind_rows(results_mv[1,]) %>%
-   mutate(index = c(2:6, 1)) %>%
-   arrange(index)
+# results_mv <-
+#    results_mv[2:6,] %>%
+#    mutate(Effect = Effect + results_mv$Effect[1]) %>%
+#    mutate(CI_lower = CI_lower + results_mv$CI_lower[1]) %>%
+#    mutate(CI_upper = CI_upper + results_mv$CI_upper[1]) %>%
+#    bind_rows(results_mv[1,]) %>%
+#    mutate(index = c(2:6, 1)) %>%
+#    arrange(index)
 
@@
    mutate(Treatment = factor(Treatment, levels = rev(
-      c(
-         "Early",
+      c( "Early",
          "Recommended",
@@
    ) +
-   geom_hline(yintercept = 0) +
    geom_point(aes(size = 1 / se), shape = 15) +
@@
 source("R/simple_summary.R") #function to provide a table that includes the treatment names in the contrasts
-summary(glht(PM_mv, linfct = cbind(contrMat(rep(
+summary(glht(PM_mv_, linfct = cbind(contrMat(rep(
    1, 6
@@
 contrast_Ssum <-
-   simple_summary(summary(glht(PM_mv, linfct = cbind(
+   simple_summary(summary(glht(PM_mv_, linfct = cbind(
       contrMat(rep(1, 6), type = "Tukey")
@@
 contrast_Ssum
+
 ```

### 2021-02-04 02_Preliminary_analysis.Rmd
small corrections to rain inspection

@@
          longitude = x["lon"],
-         start = ymd(x["first_sign_disease"]) + days(30),
-         end = ymd(x["first_sign_disease"]) + days(70)
+         start = ymd(x["planting_date"]) + days(0),
+         end = ymd(x["planting_date"]) + days(63)
       )
@@
 
-```{r lm_late_rain}
-summary(lm(grain_yield.t.ha. ~ late_rain, data = PM_MB_dat))
+```{r lm_mid_rain}
+summary(lm(grain_yield.t.ha. ~ mid_rain, data = PM_MB_dat))
 ```

### 2021-02-10 04_MetaAnalysis.Rmd
Remove forest plot code

@@
 
-### Forest plot of trial treatment effect per trial
-Let's look at the trial variability in this model with a forest plot
-```{r forestP, eval=FALSE, fig.height=40, fig.width=17, include=FALSE}
-# THIS NEEDS TO BE FIXED
-source(here("R/change_labels.R"))
-source(here("R/forest_rows.R"))
-
-# Sort and arrange data-frame accordingly and produce a index vector to inform
-# the order of each "Trial" on the plot
-index1 <- PM_MB_dat %>%
-   mutate(ID = seq_along(trial_ref)) %>%
-   mutate(spray_management =
-             factor(
-                spray_management,
-                levels = c(
-                   "Early",
-                   "Late",
-                   "Recommended",
-                   "Recommended_plus",
-                   "Late_plus"
-                )
-             )) %>%
-   arrange(desc(spray_management), location, desc(grain_yield.t.ha.)) %>%
-   mutate(ID2 = order(ID)) %>%
-   pull(ID2)
-
-# Use forest rows function to return a list of where to place on the plot:
-# sub-titles, each trial row, and summary prediction for each treatment.
-# this list can be used below to reference where to plot each variable
-rows1 <- forest_rows(
-   head_row = 186,
-   ord_var = PM_MB_dat$spray_management,
-   index = index1,
-   gap = 5,
-   row_offset = -2
-)
-
-# A data-frame of meta-model coefficients used to produce the summary polygons
-# for each treatment
-polys <- data.frame(
-   ref = change_labels(names(coef(PM_mv))),
-   x = c(coef(PM_mv)[1], coef(PM_mv)[1] + coef(PM_mv)[2:6]),
-   ci.lb = c(PM_mv$ci.lb[1], PM_mv$ci.lb[1] + PM_mv$ci.lb[2:6]),
-   ci.ub = c(PM_mv$ci.ub[1], PM_mv$ci.ub[1] + PM_mv$ci.ub[2:6])
-)[c(2, 5, 3, 4, 6, 1), ]
-polys$rows <- rows1$pred_row - 1.5
-
-forest1  <- metafor::forest(
-   PM_mv,
-   cex = 1.15 ,
-   width = 5,
-   #order = "fit",
-   rows = rows1$trows - 1.5,
-   ilab = cbind(
-      PM_MB_dat$year,
-      PM_MB_dat$row_spacing,
-      PM_MB_dat$host_genotype,
-      PM_MB_dat$dose
-   ),
-   ilab.xpos = c(-2.35, -2.1, -1.8, -1.4) + 1,
-   slab = NA,
-   xlim = c(-2, 4),
-   ylim = c(5, 190),
-   xlab = "Grain yield mean difference",
-   addfit = FALSE,
-   efac = c(0.2, 0.15, 0.2),
-   at = seq(-0.5, 3, 0.5)
-)
-
-### code which puts lines and annotations on the plot, its a bit long...
-source(here("R/add_annotations.R"))
-
-```
-
 ****

### 2021-02-10 04_MetaAnalysis.Rmd
Remove code calculating estimate means instead of means dif

@@
 
-# adjust estimates to show absolute means
-# results_mv <-
-#    results_mv[2:6,] %>%
-#    mutate(Effect = Effect + results_mv$Effect[1]) %>%
-#    mutate(CI_lower = CI_lower + results_mv$CI_lower[1]) %>%
-#    mutate(CI_upper = CI_upper + results_mv$CI_upper[1]) %>%
-#    bind_rows(results_mv[1,]) %>%
-#    mutate(index = c(2:6, 1)) %>%
-#    arrange(index)
-
 # rename colnames to give table headings
@@
 source("R/simple_summary.R") #function to provide a table that includes the treatment names in the contrasts
-summary(glht(PM_mv_, linfct = cbind(contrMat(rep(
+summary(glht(PM_mv, linfct = cbind(contrMat(rep(
    1, 6
@@
 contrast_Ssum <-
-   simple_summary(summary(glht(PM_mv_, linfct = cbind(
+   simple_summary(summary(glht(PM_mv, linfct = cbind(
       contrMat(rep(1, 6), type = "Tukey")

### 2021-02-10 04_MetaAnalysis.Rmd
Update estimate table, removing the intercept

@@
 
-kable(results_mv[, 2:9],
+kable(results_mv[2:6, 2:9],
       align = "lcccccccc",
       booktabs = TRUE,
-      caption = "Table ##: Estimated mean mungbean yields for each spray schedule treatment used for mitigating yield losses to powdery mildew in mungbean crops grown in eastern Australia.
-Yield estimates were calculated from the network meta-analysis of data obtained from grey literature reports.
+      caption = "Table ##: Estimated  mungbean yields mean difference to the no spray control for each spray schedule treatment.
+Estimates were calculated from the network meta-analysis of data obtained from grey literature reports of field trials undertaken in Eastern Australia.
 Z and P values indicate statistical significance in comparison to the intercept.")

### 2021-02-10 04_MetaAnalysis.Rmd
update table title

@@
       booktabs = TRUE,
-      caption = "Table ##: Estimated  mungbean yields mean difference to the no spray control for each spray schedule treatment.
-Estimates were calculated from the network meta-analysis of data obtained from grey literature reports of field trials undertaken in Eastern Australia.
+      caption = "Table 2: Estimated mungbean yield mean difference to the no spray control (intercept) for each spray schedule treatment.
+Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of field trials undertaken in Eastern Australia.
 Z and P values indicate statistical significance in comparison to the intercept.")

### 2021-02-10 01_TrialsForInclusionInAnalysis.Rmd
Rearrange trial inclusion and data selection for disease MA and Yield MA

@@
 
-Four trials from our subset need to be removed for not reporting yield variance.  
-```{r TrialsWithVariance}
-NoVar <- PM_MB_dat %>%
-   group_by(trial_ref) %>%
-   summarise(
-      location = location,
-      year = year,
-      No_Var = all(is.na(yield_error)),
-      .groups = 'drop'
-   ) %>%
-   filter(No_Var) %>%
-   distinct(trial_ref, year, location)
-NoVar
-
-PM_MB_dat <- PM_MB_dat %>%
-   filter(!(trial_ref %in% NoVar$trial_ref))
-```
-
-<br>
-<br>
-<br>
-
 We need to focus the meta-analysis on fungicides with the same mode of action.
@@
 
-We will retain the following trials, which only contain DMI fungicides. 
-However, we won't remove non-DMI fungicides just yet, we will do this before the analysis.
-
-```{r Final_Trials_For_Inclusion}
-PM_MB_dat %>%
-   filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole") %>%
-   distinct(trial_ref, location, year) %>%
-   arrange(year) 
-```
-
-<br>
-<br>
-<br>
-<br>
-
-### Classify dataset variables
-
-Finally, we are going to define the class of each variable in the data, retaining only the variables relevant to the analysis. 
-It should be noted that the data-set below has still retained all fungicide active ingredients. 
-Before dropping the non-DMI fungicides from the final meta-analysis we will inspect their influence on grain yield.
-
-```{r classifyData}
-PM_MB_dat <-
-   PM_MB_dat %>%
-   mutate(trial_ref = as.character(trial_ref)) %>%
-   mutate(year = as.character(year)) %>%
-   mutate(location = as.character(location)) %>%
-   mutate(host_genotype = as.character(host_genotype)) %>%
-   mutate(row_spacing = as.double(round(row_spacing, digits = 2))) %>%
-   mutate(replicates = as.integer(replicates)) %>%
-   mutate(planting_date = ymd(planting_date)) %>%
-   mutate(flowering_date = ymd(flowering_date)) %>%
-   mutate(pod_fill_date = ymd(pod_fill_date)) %>%
-   mutate(mid_late_pod_fill = ymd(mid_late_pod_fill)) %>%
-   mutate(first_sign_disease = ymd(first_sign_disease)) %>%
-   mutate(fungicide_ai = as.character(fungicide_ai)) %>%
-   mutate(dose_ai.ha = round(as.double(dose_ai.ha), digits = 2)) %>%
-   mutate(fungicide_application_1 = ymd(fungicide_application_1)) %>%
-   mutate(fungicide_application_2 = ymd(fungicide_application_2)) %>%
-   mutate(fungicide_application_3 = ymd(fungicide_application_3)) %>%
-   mutate(fungicide_application_4 = ymd(fungicide_application_4)) %>%
-   mutate(fungicide_application_5 = ymd(fungicide_application_5)) %>%
-   mutate(fungicide_application_6 = ymd(fungicide_application_6)) %>%
-   mutate(total_fungicide = as.integer(total_fungicide)) %>%
-   mutate(harvest_date = ymd(harvest_date)) %>%
-   mutate(final_assessment = ymd(final_assessment)) %>%
-   mutate(PM_final_severity = round(as.double(PM_final_severity), digits = 4)) %>%
-   mutate(disease_error = round(as.double(disease_error), digits = 6)) %>%
-   mutate(D_error_type = as.character(D_error_type)) %>%
-   mutate(grain_yield.t.ha. = round(as.double(grain_yield.t.ha.), digits = 4)) %>%
-   mutate(yield_error = round(as.double(yield_error), digits = 6)) %>%
-   mutate(Y_error_type = as.character(Y_error_type)) %>%
-   mutate(Y_Msquare = round(as.double(Y_Msquare), digits = 6)) %>%
-   mutate(yield_gain = round(as.double(yield_gain), digits = 4)) %>%
-   mutate(prop_YG = round(as.double(prop_YG), digits = 4)) %>%
-   select(
-      -c(
-         trial_design,
-         # remove the following columns
-         plot_length.m.,
-         plot_width.m.,
-         plant_density,
-         trade_name,
-         n_treatment,
-         emergence_date,
-         rating_scale,
-         raw_graded,
-         raw_data_avail,
-         comments,
-         days_harvest.planting,
-         AUDPS_m,
-         AUDPC_sd,
-         Inc_Ms,
-         pod_fill_date,
-         mid_late_pod_fill,
-         flowering_date,
-         yield_gain,
-         Y_Msquare,
-         prop_YG,
-         AUDPC_m,
-         AUDPC_sd,
-         AUDPS_sd
-      )
-   )
-```
-
 ## Subset to trials containing DMI fungicides
@@
 
+## Excluding variance
+Following an inspection of the yield and disease variance we determined imputation was not suitable and therefore we must exlude trials that did not report variance.
+For each analysis, yield and disease severity a separate data-set will be created, including only trials that report variance for the respective response variable
+
+Four trials will be removed for our yield data set `PM_dat_Y` for not reporting yield variance.  
+```{r TrialsWithVariance}
+NoVar <- PM_MB_dat %>%
+   group_by(trial_ref) %>%
+   summarise(
+      location = location,
+      year = year,
+      No_Var = all(is.na(yield_error)),
+      .groups = 'drop'
+   ) %>%
+   distinct(trial_ref, year, location)
+NoVar
+
+PM_dat_Y <- PM_MB_dat %>%
+   filter(!(trial_ref %in% NoVar$trial_ref))
+```
+
+Four trials will be removed for our disease severity data set `PM_dat_S` for not reporting yield variance.  
+```{r TrialsWithVariance}
+NoVar <- PM_MB_dat %>%
+   group_by(trial_ref) %>%
+   summarise(
+      location = location,
+      year = year,
+      No_Var = all(is.na(disease_error)),
+      .groups = 'drop'
+   ) %>%
+   distinct(trial_ref, year, location)
+NoVar
+
+PM_dat_D <- PM_MB_dat %>%
+   filter(!(trial_ref %in% NoVar$trial_ref))
+```
+
+We will retain the following trials, which only contain DMI fungicides. 
+However, we won't remove non-DMI fungicides just yet, we will do this before the analysis.
+
+```{r Final_Trials_For_Inclusion}
+PM_MB_dat %>%
+   filter(fungicide_ai == "tebuconazole" |
+             fungicide_ai == "propiconazole") %>%
+   mutate(MA_analysis = case_when(
+      is.na(yield_error & disease_error) == FALSE ~ "Yield and Disease",
+      is.na(yield_error) == FALSE & 
+         is.na(disease_error) ~ "Yield",
+      is.na(disease_error) == FALSE & 
+         is.na(yield_error) ~ "Disease",
+      TRUE ~ "Nil"
+   )) %>%
+   distinct(trial_ref, location, year, MA_analysis) %>%
+   arrange(year) 
+```
+
+<br>
+<br>
+<br>
+<br>
+
+### Classify dataset variables
+
+Finally, we are going to define the class of each variable in the data, retaining only the variables relevant to the analysis.
+
+```{r classifyData}
+source("R/classify_PM_data.R")
+
+# classify yield data
+PM_dat_Y <- 
+   classify_PM_data(PM_dat_Y)
+
+#classify disease data
+PM_dat_D <- 
+   classify_PM_data(PM_dat_D)
+```
+
 ## Classifying spray schedule
@@
 ```{r clustered_fungicide_applications}
-PM_MB_dat %<>%
+# Yield data
+PM_dat_Y %<>%
+   mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
+   mutate(fungicide_timing_2 = fungicide_application_2 - fungicide_application_1) %>%
+   mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2)
+
+# Disease data
+PM_dat_D %<>%
    mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
@@
 
-```{r simple_clusters}
-PM_MB_dat <- PM_MB_dat %>%
+Simplify the clusters for the yield data-set
+```{r simple_Y_clusters}
+PM_dat_Y <- PM_dat_Y %>%
+   mutate(
+      spray_management = case_when(
+         fungicide_timing_1 < 0 &
+            is.na(fungicide_application_2) &
+            is.na(fungicide_application_3) ~ "Early",
+         fungicide_timing_1 >= 0 &
+            fungicide_timing_1 < 4 &
+            is.na(fungicide_application_2) &
+            is.na(fungicide_application_3) ~ "Recommended",
+         fungicide_timing_1 >= 4 &
+            is.na(fungicide_application_2) &
+            is.na(fungicide_application_3) ~ "Late",
+         fungicide_timing_1 < 0 &
+            !is.na(fungicide_application_2) ~ "Early_plus",
+         fungicide_timing_1 >= 0 &
+            fungicide_timing_1 < 4 &
+            !is.na(fungicide_application_2) ~ "Recommended_plus",
+         fungicide_timing_1 >= 4 &
+            !is.na(fungicide_application_2) ~ "Late_plus",
+         TRUE ~ "Other"
+      )
+   )
+
+PM_dat_Y[PM_dat_Y$fungicide_ai == "control",
+          c(
+             "fungicide_timing_1",
+             "fungicide_timing_2",
+             "fungicide_timing_3",
+             "spray_management"
+          )] <- "control"
+```
+
+Simplify the clusters
+```{r simple_D_clusters}
+PM_dat_D <- PM_dat_D %>%
    mutate(
@@
 
-Now to view the number break-down of the `spray_management` treatments
+Now to view the number break-down of the `spray_management` treatments in the yield and disease severity data-sets
 
-```{r tableSprayManagement}
-table(PM_MB_dat$spray_management)
+```{r tableSprayManagement_Y}
+table(PM_dat_Y$spray_management)
+```
+
+```{r tableSprayManagement_Y}
+table(PM_dat_D$spray_management)
 ```
@@
 ```{r StandardiseYieldVariance}
-PM_MB_dat <-
-   PM_MB_dat %>%
+PM_dat_Y <-
+   PM_dat_Y %>%
    mutate(
@@
 ```{r StandardiseSeverityVariance}
-PM_MB_dat <-
-   PM_MB_dat %>%
+PM_dat_D <-
+   PM_dat_D %>%
    mutate(

### 2021-02-10 01_TrialsForInclusionInAnalysis.Rmd
Update data selection to create a dataset for severity and yield MA;

@@
 NoVar <- PM_MB_dat %>%
-   group_by(trial_ref) %>%
-   summarise(
-      location = location,
-      year = year,
-      No_Var = all(is.na(yield_error)),
-      .groups = 'drop'
-   ) %>%
+   mutate(No_Var = is.na(yield_error)) %>%
+   filter(No_Var == TRUE) %>%
    distinct(trial_ref, year, location)
@@
 Four trials will be removed for our disease severity data set `PM_dat_S` for not reporting yield variance.  
-```{r TrialsWithVariance}
+```{r TrialsWithVariance_D}
 NoVar <- PM_MB_dat %>%
-   group_by(trial_ref) %>%
-   summarise(
-      location = location,
-      year = year,
-      No_Var = all(is.na(disease_error)),
-      .groups = 'drop'
-   ) %>%
+   mutate(No_Var = is.na(disease_error)) %>%
+   filter(No_Var == TRUE) %>%
    distinct(trial_ref, year, location)
@@
 
-PM_MB_dat[PM_MB_dat$fungicide_ai == "control",
+PM_dat_D[PM_dat_D$fungicide_ai == "control",
           c(
@@
 ```{r simpler_clusters_remove}
-PM_MB_dat <-
-   PM_MB_dat %>%
+PM_dat_Y <-
+   PM_dat_Y %>%
+   filter(spray_management != "Early_plus") %>%
+   select(-c(fungicide_timing_1, # remove the following columns which no longer have use
+             fungicide_timing_2,
+             fungicide_timing_3,
+             fungicide_application_1,
+             fungicide_application_2,
+             fungicide_application_3,
+             fungicide_application_4,
+             fungicide_application_5,
+             fungicide_application_6,
+             fungicide_application_7,
+             ))
+
+PM_dat_D <-
+   PM_dat_D %>%
    filter(spray_management != "Early_plus") %>%
@@
    mutate(
-      d_vi =
+      vi =
          case_when(
@@
 ```{r saveData01}
-write.csv(PM_MB_dat, file = "cache/PM_MB_clean_data.csv", row.names = FALSE)
-save(PM_MB_dat, file = here("cache/ImportDataAndSelectTrials01.Rdata"))
+write.csv(PM_dat_Y, file = "cache/PM_yield_clean_data.csv", row.names = FALSE)
+write.csv(PM_dat_D, file = "cache/PM_disease_clean_data.csv", row.names = FALSE)
+save(PM_MB_dat, PM_dat_D, PM_dat_Y, file = here("cache/ImportDataAndSelectTrials01.Rdata"))
 ```

### 2021-02-10 04_MetaAnalysis.Rmd
Change yield data object to reflect data set appropriate for yield only

@@
 
-PM_MB_dat <-
-   read.csv("cache/PM_MB_clean_data.csv", stringsAsFactors = FALSE)
+PM_dat_Y <-
+   read.csv("cache/PM_yield_clean_data.csv", stringsAsFactors = FALSE)
 ```
@@
 ```{r define_trial}
-PM_MB_dat <-
-   PM_MB_dat %>%
+PM_dat_Y <-
+   PM_dat_Y %>%
    mutate(trial = paste(trial_ref,
@@
    control = list(optimizer = "optim"),
-   data = PM_MB_dat
+   data = PM_dat_Y
 )
@@
 ```{r median onset}
-PM_MB_dat %>%
+PM_dat_Y %>%
    mutate(first_sign_days = lubridate::ymd(first_sign_disease) -
@@
 ```{r define_onset}
-PM_MB_dat <- PM_MB_dat %>%
+PM_dat_Y <- PM_dat_Y %>%
    mutate(first_sign_days = lubridate::ymd(first_sign_disease) -
@@
 ```{r hist_onset}
-PM_MB_dat %>%
+PM_dat_Y %>%
    ggplot(aes(x = first_sign_days)) +
@@
 ```{r median_pressure}
-PM_MB_dat %>%
+PM_dat_Y %>%
    filter(fungicide_ai == "control") %>%
@@
 ```{r define_disease_pressure}
-PM_MB_dat <- PM_MB_dat %>%
+PM_dat_Y <- PM_dat_Y %>%
    mutate(d_pressure = case_when(PM_final_severity < 8 ~ "low_pressure",
@@
 ```{r hist_pressure}
-PM_MB_dat %>%
+PM_dat_Y %>%
    ggplot(aes(x = PM_final_severity)) +
@@
 k5 <-
-   as.data.frame(table(PM_MB_dat$trial, PM_MB_dat$spray_management)) %>%
+   as.data.frame(table(PM_dat_Y$trial, PM_dat_Y$spray_management)) %>%
    filter(Freq != 0) %>%
@@
 ```{r netmeta-analysis}
-datPM3 <- PM_MB_dat %>%
+datPM3 <- PM_dat_Y %>%
    group_by(trial, spray_management, n) %>%
@@
 save(efficacy,
-     PM_MB_dat,
+     PM_dat_Y,
      PM_mv,

### 2021-02-10 05_severity_metaAnalysis.Rmd
add boxplot
Update MA to use disease severity data set including all trials with V

@@
 # Data
-load("cache/PrepData.Rdata")
+PM_dat_D <-
+   read.csv("cache/PM_disease_clean_data.csv", stringsAsFactors = FALSE)
 ```
@@
 ```{r noDiseaseError}
-unique(PM_MB_dat_full[is.na(PM_MB_dat_full$disease_error),
+unique(PM_dat_D[is.na(PM_dat_D$d_vi),
                       c("trial_ref", "location", "year")])
@@
 PM_sev <- 
-   PM_MB_dat_full %>%
-   filter(is.na(disease_error) == FALSE)
+   PM_dat_D %>%
+   filter(is.na(d_vi) == FALSE)
 ```
@@
 
+```
+
+Inspect raw disease severity scores
+
+```{r PMsev_bwplot}
+PM_sev %>%
+   ggplot(aes(x = spray_management, y = PM_final_severity)) +
+   geom_boxplot()
 ```

### 2021-02-10 05_severity_metaAnalysis.Rmd
replace `d_vi` with `vi`

@@
 ```{r noDiseaseError}
-unique(PM_dat_D[is.na(PM_dat_D$d_vi),
+unique(PM_dat_D[is.na(PM_dat_D$vi),
                       c("trial_ref", "location", "year")])
@@
    PM_dat_D %>%
-   filter(is.na(d_vi) == FALSE)
+   filter(is.na(vi) == FALSE)
 ```
@@
    mutate(
-      d_vi = 
+      vi = 
          case_when(
@@
    yi = PM_final_severity,
-   d_vi,
+   vi,
    mods = ~ spray_management,

### 2021-02-10 05_severity_metaAnalysis.Rmd
Delete code which now resides in 01TrialsForInclusionInAnalysis

@@
    read.csv("cache/PM_disease_clean_data.csv", stringsAsFactors = FALSE)
-```
-
-Which trials don't have all the required variance information?
-```{r noDiseaseError}
-unique(PM_dat_D[is.na(PM_dat_D$vi),
-                      c("trial_ref", "location", "year")])
-```
-
-Eliminate trials with out disease severity variance.
-```{r rm_SevDiseaseError}
-PM_sev <- 
-   PM_dat_D %>%
-   filter(is.na(vi) == FALSE)
-```
-Are all the reported disease variance the same type?
-```{r sev_var_type}
-unique(PM_sev[,"D_error_type"])
-```
-
-Now we have eliminated 2 trials do all spray management categories have sufficient replications
-```{r treatment_n}
-table(PM_sev$spray_management)
-```
-
-Convert variance to the same measure
-```{r calc_sampleVar}
-PM_sev <- 
-   PM_sev %>%
-   mutate(
-      vi = 
-         case_when(
-            D_error_type == "stdev" ~ disease_error ^2,
-            D_error_type == "lsd (P=0.05)" ~ 
-               (replicates * ((disease_error / 1.96) ^2) /2)/replicates
-         ),
-      id = row_number(),
-      spray_management = fct_relevel(spray_management,sort)
-   )
-
-```
-
-Inspect raw disease severity scores
-
-```{r PMsev_bwplot}
-PM_sev %>%
-   ggplot(aes(x = spray_management, y = PM_final_severity)) +
-   geom_boxplot()
 ```

### 2021-02-10 05_severity_metaAnalysis.Rmd
Add trial variable to PM_dat_D

@@
 ```{r sev_hist}
-hist(PM_sev$PM_final_severity)
+hist(PM_dat_D$PM_final_severity)
 ```
@@
 
+### Define Trial
+```{r define_trial}
+PM_dat_D <-
+   PM_dat_D %>%
+   mutate(trial = paste(trial_ref,
+                        year,
+                        location,
+                        host_genotype,
+                        row_spacing,
+                        sep = "_")) 
+```
+
    - We will investigate the effect size of our treatment - spray management,
@@
    control = list(optimizer = "optim"),
-   data = PM_sev
+   data = PM_dat_D
 )

### 2021-02-10 05_severity_metaAnalysis.Rmd
Update object names and input MA estimates table

@@
 theme_set(theme_usq())
-#source(here("R/reportP.R"))
+source(here("R/reportP.R"))
 
@@
 ```
+
+```{r metafor_results}
+# obtain number of treatments included in each moderator variable
+k5 <-
+   as.data.frame(table(PM_dat_D$trial, PM_dat_D$spray_management)) %>%
+   filter(Freq != 0) %>%
+   group_by(Var2) %>%
+   summarise(n()) %>%
+   pull()
+
+# create data.frame
+results_mv <- data.frame(
+   N = PMsev_mv$g.levels.k,
+   k = k5,
+   Effect = round(PMsev_mv$b, 4),
+   se = round(PMsev_mv$se, 4),
+   CI_lower = round(PMsev_mv$ci.lb, 4),
+   CI_upper = round(PMsev_mv$ci.ub, 4),
+   z_val = round(PMsev_mv$zval, 4),
+   p_val = reportP(PMsev_mv$pval, AsNumeric = TRUE)
+)
+
+# rename colnames to give table headings
+colnames(results_mv)[c(1:4, 6:9)] <-
+   c("Treatment",
+     "$N$",
+     "$k$",
+     "$\\mu$",
+     "$CI_{L}$",
+     "$CI_{U}$",
+     "$Z$",
+     "$P$")
+
+# provide rownames for each moderator variable
+row.names(results_mv) <- c(
+   "Intercept / No Spray control",
+   "$Early_{single}$",
+   "$Recommended_{single}$",
+   "$Recommended_{plus}$",
+   "$Late_{single}$",
+   "$Late_{plus}$"
+)
+
+kable(results_mv[2:6, 2:9],
+      align = "lcccccccc",
+      booktabs = TRUE,
+      caption = "Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment.
+Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of field trials undertaken in Eastern Australia.
+Z and P values indicate statistical significance in comparison to the intercept.")
+```

### 2021-02-10 01_TrialsForInclusionInAnalysis.Rmd
add id number for Yield data set

@@
          ),
+      id = row_number(),
       spray_management = fct_relevel(spray_management, sort)

### 2021-02-11 01_TrialsForInclusionInAnalysis.Rmd
Rearrange code chunks to be more streamline and eliminate repetition

@@
 
-## Excluding variance
-Following an inspection of the yield and disease variance we determined imputation was not suitable and therefore we must exlude trials that did not report variance.
-For each analysis, yield and disease severity a separate data-set will be created, including only trials that report variance for the respective response variable
-
-Four trials will be removed for our yield data set `PM_dat_Y` for not reporting yield variance.  
-```{r TrialsWithVariance}
-NoVar <- PM_MB_dat %>%
-   mutate(No_Var = is.na(yield_error)) %>%
-   filter(No_Var == TRUE) %>%
-   distinct(trial_ref, year, location)
-NoVar
-
-PM_dat_Y <- PM_MB_dat %>%
-   filter(!(trial_ref %in% NoVar$trial_ref))
-```
-
-Four trials will be removed for our disease severity data set `PM_dat_S` for not reporting yield variance.  
-```{r TrialsWithVariance_D}
-NoVar <- PM_MB_dat %>%
-   mutate(No_Var = is.na(disease_error)) %>%
-   filter(No_Var == TRUE) %>%
-   distinct(trial_ref, year, location)
-NoVar
-
-PM_dat_D <- PM_MB_dat %>%
-   filter(!(trial_ref %in% NoVar$trial_ref))
-```
-
-We will retain the following trials, which only contain DMI fungicides. 
-However, we won't remove non-DMI fungicides just yet, we will do this before the analysis.
-
-```{r Final_Trials_For_Inclusion}
-PM_MB_dat %>%
-   filter(fungicide_ai == "tebuconazole" |
-             fungicide_ai == "propiconazole") %>%
-   mutate(MA_analysis = case_when(
-      is.na(yield_error & disease_error) == FALSE ~ "Yield and Disease",
-      is.na(yield_error) == FALSE & 
-         is.na(disease_error) ~ "Yield",
-      is.na(disease_error) == FALSE & 
-         is.na(yield_error) ~ "Disease",
-      TRUE ~ "Nil"
-   )) %>%
-   distinct(trial_ref, location, year, MA_analysis) %>%
-   arrange(year) 
-```
-
-<br>
 <br>
@@
 
-# classify yield data
-PM_dat_Y <- 
-   classify_PM_data(PM_dat_Y)
+# classify dataset with Trials in both 
+PM_MB_dat <-
+   classify_PM_data(PM_MB_dat)
 
-#classify disease data
-PM_dat_D <- 
-   classify_PM_data(PM_dat_D)
 ```
@@
 ```{r clustered_fungicide_applications}
-# Yield data
-PM_dat_Y %<>%
-   mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
-   mutate(fungicide_timing_2 = fungicide_application_2 - fungicide_application_1) %>%
-   mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2)
-
-# Disease data
-PM_dat_D %<>%
+# collective data
+PM_MB_dat %<>%
    mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
@@
 
-Simplify the clusters for the yield data-set
+Simplify the clusters for the data-set
 ```{r simple_Y_clusters}
-PM_dat_Y <- PM_dat_Y %>%
+PM_MB_dat <- PM_MB_dat %>%
    mutate(
@@
 
-PM_dat_Y[PM_dat_Y$fungicide_ai == "control",
-          c(
-             "fungicide_timing_1",
-             "fungicide_timing_2",
-             "fungicide_timing_3",
-             "spray_management"
-          )] <- "control"
-```
-
-Simplify the clusters
-```{r simple_D_clusters}
-PM_dat_D <- PM_dat_D %>%
-   mutate(
-      spray_management = case_when(
-         fungicide_timing_1 < 0 &
-            is.na(fungicide_application_2) &
-            is.na(fungicide_application_3) ~ "Early",
-         fungicide_timing_1 >= 0 &
-            fungicide_timing_1 < 4 &
-            is.na(fungicide_application_2) &
-            is.na(fungicide_application_3) ~ "Recommended",
-         fungicide_timing_1 >= 4 &
-            is.na(fungicide_application_2) &
-            is.na(fungicide_application_3) ~ "Late",
-         fungicide_timing_1 < 0 &
-            !is.na(fungicide_application_2) ~ "Early_plus",
-         fungicide_timing_1 >= 0 &
-            fungicide_timing_1 < 4 &
-            !is.na(fungicide_application_2) ~ "Recommended_plus",
-         fungicide_timing_1 >= 4 &
-            !is.na(fungicide_application_2) ~ "Late_plus",
-         TRUE ~ "Other"
-      )
-   )
-
-PM_dat_D[PM_dat_D$fungicide_ai == "control",
+PM_MB_dat[PM_MB_dat$fungicide_ai == "control",
           c(
@@
 ```{r tableSprayManagement_Y}
-table(PM_dat_Y$spray_management)
-```
-
-```{r tableSprayManagement_Y}
-table(PM_dat_D$spray_management)
+table(PM_MB_dat$spray_management)
 ```
@@
 ```{r simpler_clusters_remove}
-PM_dat_Y <-
-   PM_dat_Y %>%
+PM_MB_dat <-
+   PM_MB_dat %>%
    filter(spray_management != "Early_plus") %>%
@@
 
+```
+
+## Trial variance
+We need variance for each treatment for the data to be useful in a meta-analysis.
+Lets look at which of the included trials contain variance for both response variables of interest, yield and disease severity.
+
+```{r Trials_For_Inclusion}
+PM_MB_dat %>%
+   mutate(MA_analysis = case_when(
+      is.na(yield_error & disease_error) == FALSE ~ "Yield and Disease",
+      is.na(yield_error) == FALSE & 
+         is.na(disease_error) ~ "Yield",
+      is.na(disease_error) == FALSE & 
+         is.na(yield_error) ~ "Disease",
+      TRUE ~ "Nil"
+   )) %>%
+   distinct(trial_ref, location, year, MA_analysis) %>%
+   arrange(year)
+
+# Remove trials without variance for both Disease and yield for data_set `PM_MB_dat
+PM_MB_dat <- 
+   PM_MB_dat %>%
+   mutate(contains_var = case_when(
+      is.na(yield_error) &
+         is.na(disease_error) ~ NA_character_,
+      TRUE ~ trial_ref)) %>%
+   filter(trial_ref %in% contains_var) %>%
+   select(-contains_var)
+```
+
+## Excluding variance
+Following an inspection of the yield and disease variance we determined imputation was not suitable and therefore we must exclude trials that did not report variance.
+For each analysis, yield and disease severity a separate data-set will be created, including only trials that report variance for the respective response variable
+
+Four trials will be removed for our yield data set `PM_dat_Y` for not reporting yield variance.  
+```{r TrialsWithVariance}
+PM_MB_dat %>%
+   mutate(No_Var = is.na(yield_error)) %>%
+   filter(No_Var == TRUE) %>%
+   distinct(trial_ref, year, location)
+
+PM_dat_Y <- 
+   PM_MB_dat %>%
+   mutate(contains_var = case_when(
+      is.na(yield_error) ~ NA_character_,
+      TRUE ~ trial_ref)) %>%
+   filter(trial_ref %in% contains_var) %>%
+   select(-contains_var)
+```
+
+Four trials will be removed for our disease severity data set `PM_dat_D` for not reporting yield variance.  
+```{r TrialsWithVariance_D}
+PM_MB_dat %>%
+   mutate(No_Var = is.na(disease_error)) %>%
+   filter(No_Var == TRUE) %>%
+   distinct(trial_ref, year, location)
+
 PM_dat_D <- 
-   PM_dat_D %>%
-   filter(spray_management != "Early_plus") %>%
-   select(-c(fungicide_timing_1, # remove the following columns which no longer have use
-             fungicide_timing_2,
-             fungicide_timing_3,
-             fungicide_application_1,
-             fungicide_application_2,
-             fungicide_application_3,
-             fungicide_application_4,
-             fungicide_application_5,
-             fungicide_application_6,
-             fungicide_application_7,
-             ))
+   PM_MB_dat %>%
+   mutate(contains_var = case_when(
+      is.na(disease_error) ~ NA_character_,
+      TRUE ~ trial_ref)) %>%
+   filter(trial_ref %in% contains_var) %>%
+   select(-contains_var)
 ```

### 2021-02-11 01_TrialsForInclusionInAnalysis.Rmd
Save PM_MB_dat as a csv

@@
 write.csv(PM_dat_D, file = "cache/PM_disease_clean_data.csv", row.names = FALSE)
+write.csv(PM_MB_dat, file = "cache/PM_MB_clean_data.csv", row.names = FALSE)
 save(PM_MB_dat, PM_dat_D, PM_dat_Y, file = here("cache/ImportDataAndSelectTrials01.Rdata"))

### 2021-02-11 04_MetaAnalysis.Rmd
change estimates table to flextable and save it to word doc

@@
                netmeta,
-               multcomp)
+               multcomp,
+               flextable)
 
@@
 results_mv <- data.frame(
+   moderator = c(
+   "Intercept / No Spray control",
+   "Early",
+   "Recommended",
+   "Recommended+",
+   "Late",
+   "Late+"
+   ),
    N = PM_mv$g.levels.k,
@@
    z_val = round(PM_mv$zval, 4),
-   p_val = reportP(PM_mv$pval, AsNumeric = TRUE)
+   p_val = reportP(PM_mv$pval, AsNumeric = FALSE, P_prefix = FALSE)
 )
@@
 # rename colnames to give table headings
-colnames(results_mv)[c(1:4, 6:9)] <-
+colnames(results_mv)[c(2:5, 7:10)] <-
    c("Treatment",
-     "$N$",
-     "$k$",
-     "$\\mu$",
-     "$CI_{L}$",
-     "$CI_{U}$",
-     "$Z$",
-     "$P$")
+     "N",
+     "k",
+     "mu",
+     "CI_{L}",
+     "CI_{U}",
+     "Z",
+     "P")
 
-# provide rownames for each moderator variable
-row.names(results_mv) <- c(
-   "Intercept / No Spray control",
-   "$Early_{single}$",
-   "$Recommended_{single}$",
-   "$Recommended_{plus}$",
-   "$Late_{single}$",
-   "$Late_{plus}$"
-)
+yield_estimates_table <- 
+   flextable(results_mv[c(2:6), c(1,3:8,10)]) %>%
+   align(j = 3:8, align = "center", part = "all") %>%
+   fontsize(size = 8, part = "body") %>%
+   fontsize(size = 10, part = "header") %>%
+   italic(italic = TRUE, part = "header") %>%
+   set_caption("Table 2: Estimated mungbean yield mean difference to the no spray control (intercept) for each spray schedule treatment.
+Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of 'k' field trials undertaken in Eastern Australia.
+P values indicate statistical significance in comparison to the intercept.") %>%
+   autofit()
 
-kable(results_mv[2:6, 2:9],
-      align = "lcccccccc",
-      booktabs = TRUE,
-      caption = "Table 2: Estimated mungbean yield mean difference to the no spray control (intercept) for each spray schedule treatment.
-Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of field trials undertaken in Eastern Australia.
-Z and P values indicate statistical significance in comparison to the intercept.")
+yield_estimates_table
+```
+
+Save table to a word document to use in manuscript
+```{r eval=FALSE, include=FALSE}
+# Save table as a word document
+doc <- officer::read_docx()
+doc <- body_add_flextable(doc, value = yield_estimates_table)
+print(doc, target = "paper/figures/Table2_yield_estimates.docx")
 ```

### 2021-02-11 04_MetaAnalysis.Rmd
Update variable names in results_mv

@@
    ))) %>%
-   ggplot(aes(Treatment, `$\\mu$`)) +
+   ggplot(aes(Treatment, mu)) +
    geom_hline(
@@
    geom_point(aes(size = 1 / se), shape = 15) +
-   geom_linerange(aes(ymin = `$CI_{L}$`, ymax = `$CI_{U}$`)) +
+   geom_linerange(aes(ymin = `CI_{L}`, ymax = `CI_{U}`)) +
    coord_flip() +

### 2021-02-11 05_severity_metaAnalysis.Rmd
Update table to flextable and export to word doc

--- 2021-02-10 05_severity_metaAnalysis.Rmd
@@
                multcomp,
-               dplyr)
+               dplyr,
+               flextable)
 
@@
 ```
+
+```{r metafor_results}
+# obtain number of treatments included in each moderator variable
+k5 <-
+   as.data.frame(table(PM_dat_D$trial, PM_dat_D$spray_management)) %>%
+   filter(Freq != 0) %>%
+   group_by(Var2) %>%
+   summarise(n()) %>%
+   pull()
+
+# create data.frame
+results_mv <- data.frame(
+   moderator = c(
+   "Intercept / No Spray control",
+   "Early",
+   "Recommended",
+   "Recommended+",
+   "Late",
+   "Late+"
+   ),
+   N = PMsev_mv$g.levels.k,
+   k = k5,
+   Effect = round(PMsev_mv$b, 4),
+   se = round(PMsev_mv$se, 4),
+   CI_lower = round(PMsev_mv$ci.lb, 4),
+   CI_upper = round(PMsev_mv$ci.ub, 4),
+   z_val = round(PMsev_mv$zval, 4),
+   p_val = reportP(PMsev_mv$pval, AsNumeric = FALSE, P_prefix = FALSE)
+)
+
+# rename colnames to give table headings
+colnames(results_mv)[c(2:5, 7:10)] <-
+   c("Treatment",
+     "N",
+     "k",
+     "mu",
+     "CI_{L}",
+     "CI_{U}",
+     "Z",
+     "P")
+
+disease_estimates_table <- 
+   flextable(results_mv[c(2:6), c(1,3:8,10)]) %>%
+   align(j = 3:8, align = "center", part = "all") %>%
+   fontsize(size = 8, part = "body") %>%
+   fontsize(size = 10, part = "header") %>%
+   italic(italic = TRUE, part = "header") %>%
+   set_caption("Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment.
+Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of field trials undertaken in Eastern Australia.
+Z and P values indicate statistical significance in comparison to the intercept.") %>%
+   autofit()
+
+disease_estimates_table
+```
+
+Save table to a word document to use in manuscript
+```{r eval=FALSE, include=FALSE}
+# Save table as a word document
+doc <- officer::read_docx()
+doc <- body_add_flextable(doc, value = disease_estimates_table)
+print(doc, target = "paper/figures/Table3_severity_esimates.docx")
+```

### 2021-02-12 02_Preliminary_analysis.Rmd
Add four (severity and yield) plots combined into figure 1

@@
                flextable,
-               here)
+               here,
+               gridExtra)
 
@@
 print(doc, target = "paper/figures/Table1_severity&yield.docx")
+```
+
+## Disease and Yield in a box blot
+
+```{r bwplot}
+sev_control_plot <- 
+   PM_MB_dat %>%
+   filter(fungicide_ai == "control") %>%
+   ggplot(aes(x = year, y = PM_final_severity)) +
+   geom_boxplot(outlier.alpha = 0) +
+   geom_jitter(size = 2, colour = "cadetblue",alpha = 0.4,width = 0.15) +
+   scale_y_continuous(breaks = c(1,3,5,7,9), limits = c(0.9,9.1)) +
+   ylab("PM severity (1 -9)")+
+   # xlab("Crop season")+
+   theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+   ggtitle("A")
+
+sev_control_plot      
+```
+
+```{r bwplot}
+sev_schedule_plot <-
+   PM_MB_dat %>%
+   ggplot(aes(x = spray_management, y = PM_final_severity)) +
+   geom_boxplot(outlier.alpha = 0) +
+   geom_jitter(
+      size = 2,
+      colour = "cadetblue",
+      alpha = 0.4,
+      width = 0.15
+   ) +
+   scale_y_continuous(breaks = c(1, 3, 5, 7, 9), limits = c(0.9, 9.1)) +
+   scale_x_discrete(labels = c(
+      "control",
+      "early",
+      "late",
+      "late+",
+      "recommended",
+      "recomended+"
+   )) +
+   ylab("PM severity (1 -9)") +
+   #xlab("Spray Schedule")+
+   theme(
+      axis.title.x = element_blank(),
+      axis.text.x = element_blank(),
+      axis.title.y = element_blank(),
+      #axis.ticks.x = element_blank()
+   )+
+   ggtitle("B")
+
+sev_schedule_plot
+```
+
+```{r}
+Y_control_plot <-
+   PM_MB_dat %>%
+   filter(fungicide_ai == "control") %>%
+   ggplot(aes(x = year, y = grain_yield.t.ha.)) +
+   geom_boxplot() +
+   geom_jitter(
+      size = 2,
+      colour = "coral",
+      alpha = 0.4,
+      width = 0.15
+   ) +
+   scale_y_continuous(breaks = seq(0, 2.5, by = 0.5), limits = c(0, 2.6)) +
+   ylab(bquote('Mungbean grain yield ' *  ~  ~ t ~ ha ^ -1 * "")) +
+   xlab("Crop season") +
+   theme(axis.text.x = element_text(angle = 20, hjust = 0.75),
+         plot.margin = margin(0.2, 0, 0.71, 0, "cm"),
+         axis.title.x = element_text(vjust = -5))
+
+Y_control_plot
+```
+
+```{r bwplot}
+Y_schedule_plot <- 
+   PM_MB_dat %>%
+   ggplot(aes(x = spray_management, y = grain_yield.t.ha.)) +
+   geom_boxplot(outlier.alpha = 0) +
+   geom_jitter(
+      size = 2,
+      colour = "coral",
+      alpha = 0.4,
+      width = 0.15
+   ) +
+   scale_y_continuous(breaks = seq(0, 2.5, by = 0.5), limits = c(0, 2.6)) +
+   scale_x_discrete(labels = c(
+      "control",
+      "early",
+      "late",
+      "late+",
+      "recommended",
+      "recomended+"
+   )) +
+   #ylab(bquote('Mungbean grain yield ' *  ~  ~ t ~ ha ^ -1 * "")) +
+   xlab("Spray Schedule")+
+    theme(
+      axis.title.y = element_blank(),
+      axis.text.x = element_text(angle = 20, hjust = 0.75))
+
+Y_schedule_plot
+```
+
+```{r}
+#library(gridExtra)
+
+p4 <- arrangeGrob(sev_control_plot,
+                  sev_schedule_plot,
+                  Y_control_plot,
+                  Y_schedule_plot)
+
+ggsave(
+   filename = "paper/figures/Fig1_boxplots_yield&sev.png",
+   plot = p4,
+   height = 6,
+   width = 8,
+   dpi = 1000
+)
 ```

### 2021-02-12 05_severity_metaAnalysis.Rmd
render figure 1 plot

@@
    set_caption("Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment.
-Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of field trials undertaken in Eastern Australia.
-Z and P values indicate statistical significance in comparison to the intercept.") %>%
+Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia.
+P values indicate statistical significance in comparison to the intercept.") %>%
    autofit()

### 2021-02-12 R/reportP.R
add parameter to suppress "P" in character formatting

@@ -1,34 +1,71 @@
-reportP <- function(p, AsNumeric = FALSE){
-   if(length(p) == 1){
+reportP <- function(p,
+                    AsNumeric = FALSE,
+                    P_prefix = TRUE) {
+   if (AsNumeric == TRUE &
+       P_prefix == TRUE) {
+      warning("'AsNumeric' and 'P_prefix' can't both be 'TRUE'.\n
+           Forcing `P_prefix = FALSE`")
+      P_prefix <- FALSE
+      # normally I would make this a stop()
+      # but I want to make the lastest version of this function backwards compatible
+   }
    
-   if(AsNumeric == FALSE){
-      if(p < 0.0001){
-      return("P < 0.0001")
-   }else{
-      return(paste("P =", format(round(p, digits =  4), scientific = FALSE)))
-   }}
-   
-   if(AsNumeric == TRUE){
-      if(p < 0.0001){
-      return(format(0.0001, scientific = FALSE))
-   }else{
-      return(format(round(p, digits =  4), scientific = FALSE))
-   }}}else{
+   if (length(p) == 1) {
+      if (AsNumeric == FALSE &
+          P_prefix == TRUE) {
+         if (p < 0.0001) {
+            return("P < 0.0001")
+         } else{
+            return(paste("P =", format(
+               round(p, digits =  4), scientific = FALSE
+            )))
+         }
+      }
+      if (AsNumeric == FALSE &
+          P_prefix == FALSE) {
+         if (p < 0.0001) {
+            return("< 0.0001")
+         } else{
+            return(format(round(p, digits =  4), scientific = FALSE))
+         }
+      }
       
-      sapply(p,function(p) {
-         if(AsNumeric == FALSE){
-            if(p < 0.0001){
+      if (AsNumeric == TRUE) {
+         if (p < 0.0001) {
+            return(format(0.0001, scientific = FALSE))
+         } else{
+            return(format(round(p, digits =  4), scientific = FALSE))
+         }
+      }
+   } else{
+      sapply(p, function(p) {
+         if (AsNumeric == FALSE &
+             P_prefix == TRUE) {
+            if (p < 0.0001) {
                return("P < 0.0001")
-            }else{
-               return(paste("P =", format(round(p, digits =  4), scientific = FALSE)))
-            }}
+            } else{
+               return(paste("P =", format(
+                  round(p, digits =  4), scientific = FALSE
+               )))
+            }
+         }
          
-         if(AsNumeric == TRUE){
-            if(p < 0.0001){
[…]

### 2021-02-14 04_MetaAnalysis.Rmd
Add footnotes and correct row labels

@@
 results_mv <- data.frame(
-   moderator = c(
+   Moderator = c(
    "Intercept / No Spray control",
    "Early",
+   "Late",
+   "Late+",
    "Recommended",
    "Recommended+",
-   "Late",
-   "Late+"
    ),
@@
 yield_estimates_table <- 
-   flextable(results_mv[c(2:6), c(1,3:8,10)]) %>%
+   flextable(results_mv[c(2,5,6,3,4), c(1,3:8,10)]) %>%
    align(j = 3:8, align = "center", part = "all") %>%
@@
    set_caption("Table 2: Estimated mungbean yield mean difference to the no spray control (intercept) for each spray schedule treatment.
-Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of 'k' field trials undertaken in Eastern Australia.
+Yield estimates (u) were calculated from a network meta-analysis of data obtained from grey literature reports of 'k' field trials undertaken in Eastern Australia.
 P values indicate statistical significance in comparison to the intercept.") %>%
-   autofit()
+   autofit() %>%
+   footnote(i = 1,
+            j = c(2:4,6:8),
+            value = as_paragraph(c(
+               "number of treatment means categorised to each spray schedule",
+               "number of trials with the respective spray schedule",
+               "estimated mean yield determined by the meta-analysis",
+               "Lower range of the 95% confidence interval",
+               "Upper range of the 95% confidence interval",
+               "indicates the significance between each respective spray schedule and the no spray control (intercept)"
+                                   )),
+            ref_symbols = letters[1:6],
+            part = "header", inline = TRUE
+            )
 

### 2021-02-14 05_severity_metaAnalysis.Rmd
Add footnotes and correct row labels

@@
 results_mv <- data.frame(
-   moderator = c(
+   Moderator = c(
    "Intercept / No Spray control",
    "Early",
+   "Late",
+   "Late+",
    "Recommended",
-   "Recommended+",
-   "Late",
-   "Late+"
+   "Recommended+"
    ),
@@
 disease_estimates_table <-
-   flextable(results_mv[c(2:6), c(1,3:8,10)]) %>%
+   flextable(results_mv[c(2,5,6,3,4), c(1, 3:8, 10)]) %>%
    align(j = 3:8, align = "center", part = "all") %>%
@@
    italic(italic = TRUE, part = "header") %>%
-   set_caption("Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment.
+   set_caption(
+      "Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment.
 Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia.
-P values indicate statistical significance in comparison to the intercept.") %>%
-   autofit()
+P values indicate statistical significance in comparison to the intercept."
+   ) %>%
+   autofit() %>%
+   footnote(
+      i = 1,
+      j = c(2:4, 6:8),
+      value = as_paragraph(
+         c(
+            "number of treatment means categorised to each spray schedule",
+            "number of trials with the respective spray schedule",
+            "estimated mean yield determined by the meta-analysis",
+            "Lower range of the 95% confidence interval",
+            "Upper range of the 95% confidence interval",
+            "indicates the significance between each respective spray schedule and the no spray control (intercept)"
+         )
+      ),
+      ref_symbols = letters[1:6],
+      part = "header",
+      inline = TRUE
+   )
 

### 2021-02-14 04_MetaAnalysis.Rmd
remove dangling comma

@@
    "Recommended",
-   "Recommended+",
+   "Recommended+"
    ),

### 2021-02-24 01_TrialsForInclusionInAnalysis.Rmd
amend variance calculations

@@
 Four trials will be removed for our disease severity data set `PM_dat_D` for not reporting yield variance.
+Leaving 
 ```{r TrialsWithVariance_D}
@@
             Y_error_type == "lsd (P=0.05)" ~
-               (replicates * ((yield_error / 1.96) ^ 2) / 2) / replicates
+               (replicates * ((yield_error / 1.96) ^ 2) / 2)
          ),
@@
             D_error_type == "lsd (P=0.05)" ~
-               (replicates * ((disease_error / 1.96) ^ 2) / 2) / replicates
+               (replicates * ((disease_error / 1.96) ^ 2) / 2)
          ),

### 2021-02-24 04_MetaAnalysis.Rmd
summarise the division of spray shedules under each disease pressure

@@
 However the higher AIC indicates that the model omitting `d_pressure` is a slightly better fit.
-Also the chi-squared test uncertain that the `d_pressure` model is significantly better as indicated by the `pval` 0.1336.
-The higher log likelihood on the `d_pressure` model does intricate there is some merit to this model and that perhaps with more trials to increase statistical power might provide a useful model.
+Also the chi-squared test marginally significant that the `d_pressure` model is better as indicated by the `pval` 0.0468.
+The higher log likelihood on the `d_pressure` model does indicate there is some merit to this model.  
+It is worth noting that there were no Late plus schedules that experienced low disease pressure. 
+Even though the disease pressure interaction on the moderators was marginally significant (P =0.0468), the division of schedules due to disease pressure (reducing k) makes drawing conclusions risky.
+More data is needed to explore this possible effect.
+
+```{r}
+PM_dat_Y %>%
+   group_by(spray_management, d_pressure)%>%
+   summarise(n())
+```
 

### 2021-02-24 05_severity_metaAnalysis.Rmd
Ammend table

--- 2021-02-12 05_severity_metaAnalysis.Rmd
@@
 k5 <-
-   as.data.frame(table(PM_dat_D$trial, PM_dat_D$spray_management)) %>%
+   as.data.frame(table(PM_dat_D$spray_management)) %>%
    filter(Freq != 0) %>%
@@
 
+k6 <-
+   as.data.frame(table(PM_dat_D$trial_ref, PM_dat_D$spray_management)) %>%
+   filter(Freq != 0) %>%
+   group_by(Var2) %>%
+   summarise(n()) %>%
+   pull()
+
+intercept <- round(PMsev_mv$b, 4)[1,1]
+
 # create data.frame
 results_mv <- data.frame(
-   moderator = c(
+   Moderator = c(
    "Intercept / No Spray control",
    "Early",
+   "Late",
+   "Late+",
    "Recommended",
-   "Recommended+",
-   "Late",
-   "Late+"
+   "Recommended+"
    ),
-   N = PMsev_mv$g.levels.k,
-   k = k5,
+   N = k5,
+   k = k6,
    Effect = round(PMsev_mv$b, 4),
@@
    z_val = round(PMsev_mv$zval, 4),
-   p_val = reportP(PMsev_mv$pval, AsNumeric = FALSE, P_prefix = FALSE)
+   p_val = reportP(PMsev_mv$pval, AsNumeric = FALSE, P_prefix = FALSE),
+   eff_bar = round(1 -(intercept + PMsev_mv$b)/intercept,4)*100,
+   eff_CI_low = round(1 -(intercept + PMsev_mv$ci.lb)/intercept,4)*100,
+   eff_CI_high = round(1 -(intercept + PMsev_mv$ci.ub)/intercept,4)*100
 )
@@
 # rename colnames to give table headings
-colnames(results_mv)[c(2:5, 7:10)] <-
-   c("Treatment",
+colnames(results_mv)[c(1:4,6:12 )] <-
+   c("Moderator",
      "N",
@@
      "Z",
-     "P")
+     "P",
+     "Efficacy",
+     "Eff CI upper",
+     "Eff CI_lower")
 
 disease_estimates_table <-
-   flextable(results_mv[c(2:6), c(1,3:8,10)]) %>%
-   align(j = 3:8, align = "center", part = "all") %>%
+   flextable(results_mv[c(2,5,6,3,4), c(1:4,6:7, 9:12)]) %>%
+   align(j = 2:10, align = "center", part = "all") %>%
    fontsize(size = 8, part = "body") %>%
@@
    italic(italic = TRUE, part = "header") %>%
-   set_caption("Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment.
+   set_caption(
+      "Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment.
 Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia.
-P values indicate statistical significance in comparison to the intercept.") %>%
-   autofit()
+P values indicate statistical significance in comparison to the intercept."
+   ) %>%
+   autofit() %>%
+   footnote(
+      i = 1,
+      j = c(2:10),
+      value = as_paragraph(
+         c(
+            "number of treatment means categorised to each spray schedule",
+            "number of trials with the respective spray schedule",
+            "estimated mean yield determined by the meta-analysis",
+            "Lower range of the 95% confidence interval",
+            "Upper range of the 95% confidence interval",
+            "indicates the significance between each respective spray schedule and the no spray control (intercept)",
+            "Fungicide spray schedule efficacy",
+            "Lower range of the 95% confidence interval",
+            "Upper range of the 95% confidence interval"
+         )
+      ),
+      ref_symbols = letters[c(1:7,4,5)],
+      part = "header",
+      inline = TRUE
+   )%>%
+   add_header(Moderator = "",
+              N = "",
+              k = "",
+              mu = "Effect Size",
+              `CI_{L}` = "Effect Size",
+              `CI_{U}` = "Effect Size",
+              P  = "Effect Size",
+              Efficacy = "PM control",
+              `Eff CI_lower` = "PM control",
+              `Eff CI upper` = "PM control") %>%
+   merge_h( part = "header")%>%
+   hline_top(part="all", border = officer::fp_border(color = "black", width = 2) )
 

### 2021-02-27 01_TrialsForInclusionInAnalysis.Rmd
Edit draft

@@
 Data was collected from a number of researchers from the Department of Agriculture and Primary Industries and the University of Southern Queensland and the National Growers Association.
-We would like to acknowledge in particular Professor Malcolm Riley's and Dr. Sue Thompson's effort in establishing and coordinating early field trials between 2010 and 2014.
+We would like to acknowledge in particular Professor Malcolm Riley's and Dr.
+Sue Thompson's effort in establishing and coordinating early field trials between 2010 and 2014 and GRDC for funding many of the trials featured in this meta-analysis.
 
-<br>
-<br>
 <br>
@@
 
-   1. A field trial testing the efficacy of fungicide on powdery mildew afflicted mungbean plants.  
+   1. A field trial testing the efficacy of fungicide on powdery mildew afflicted mungbean plants in eastern Australia.  
    2. Trial data needed to include:  
@@
 <br>
-<br>
-<br>
 
-## Import data and apply selection criteria  
-### Import data from trials we have the raw data  
+## Import data  
+**Import data from trials where we obtained the raw data**  
 ```{r import_dataRAW}
@@
 
-### Import dataset of manual entries  
-Import dataset which were manually entered from trial reports  
+Import dataset of manual entries  
+**Import dataset which were manually entered from trial reports**  
 ```{r import_dataMan}
@@
 
-Bind datasets, data set compiled from raw trial data and data manually compiled from trial reports.  
+Bind raw and transcribed datasets.  
 ```{r bind_data}
@@
 
-### Summary of all trials  
+## Summary of all trials  
 ```{r data_summary, echo=FALSE, message=FALSE, warning=FALSE}
@@
       },
+      `Trial design` = unique(trial_design),
       `Planting date` = unique(planting_date),
@@
          "Replicates\nper treatments",
+         "Trial design",
          "Planting date",
@@
 
-The following map displays experiment locations in the GRDC Northern Grains Region, which were considered for inclusion in this meta-analysis.
+Trial locations occurring in the GRDC Northern Grains Region.
 
@@
 
+<br>
+
+**Retain trials including: Yield**
 Three trials omitted due to not reporting yields  
@@
 <br>
-<br>
-<br>
 
+**Retain trials including: Disease severity**
 One more was trial removed as it did not report disease severity.  
@@
 
+**Retain trials including: fungicide application dates**
 No trials from our subset need to be removed for not reporting fungicide application dates.  
@@
 
+**Retain trials including: fungicide dose**
 No trials from our subset need to be removed for not reporting fungicide dose.  
@@
 
+**Exclude fungicides tested in too few trials**
 We need to focus the meta-analysis on fungicides with the same mode of action.
@@
 
-## Subset to trials containing DMI fungicides
-
+**Retain only fungicides with DMI action**
 ```{r filterDMI_trials}
@@
 
-## Classifying spray schedule
+## Defining spray schedule variable
 
@@
 
-The number of sprays need also be defined.
+The number of follow-up sprays need also be defined.
 
@@
 
-Now to view the number break-down of the `spray_management` treatments in the yield and disease severity data-sets
+Now to view the number break-down of the `spray_management` treatments in the *yield* and *disease severity* data-sets
 
@@
 
-## Trial variance
-We need variance for each treatment for the data to be useful in a meta-analysis.
-Lets look at which of the included trials contain variance for both response variables of interest, yield and disease severity.
+## Identify variance
+We need variance accompanying the mean observations for each treatment to successfully undertake a meta-analysis.
+Lets investigate which of the included trials included variance for both response variables of interest, yield and disease severity.
 
@@
    distinct(trial_ref, location, year, MA_analysis) %>%
-   arrange(year)
+   arrange(year) %>%
+   kable()
+```
 
+Remove one trial in Emerald which did not report disease variance or yield variance.
+```{r remove_nil_var}
 # Remove trials without variance for both Disease and yield for data_set `PM_MB_dat
@@
 
-## Excluding variance
 Following an inspection of the yield and disease variance we determined imputation was not suitable and therefore we must exclude trials that did not report variance.
@@
 
-Four trials will be removed for our yield data set `PM_dat_Y` for not reporting yield variance.  
+One more trial will be removed for our yield data set `PM_dat_Y` for not reporting yield variance.  
 ```{r TrialsWithVariance}
@@
 
-Four trials will be removed for our disease severity data set `PM_dat_D` for not reporting yield variance.
-Leaving 
+Two more trials will be removed for our disease severity data set `PM_dat_D` for not reporting yield variance.
 ```{r TrialsWithVariance_D}
@@
 All the variance types need to be converted to sample variance. 
-First we will start by standardising yield variance according to the method reported by [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
+First we will start by standardising yield variance according to the method reported by [Ngugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
 
@@
 
+#### Save the cleaned data
 ```{r saveData01}

### 2021-02-27 index.Rmd
Rework title for clarity
update headings

@@
 ---
-title: "Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis."
+title: "A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean"
 author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
@@
 
-   1. [Details of the experiments, which were included in the analysis][Studies considered in meta-analysis]  
+   1. [Details of the experiments, and application of inclusion criteria in the analysis][Trials considered for inclusion in meta-analysis]  
+      a. [Inclusion criteria][Criteria for inclusion in meta-analysis]
+      b. [Import data][Import data]
+      c. [Trial summary][Summary of all trials]
+      d. [Locations of considered trials][Experiment locations]
+      e. [Apply selection criteria][Subset data to selection criteria]
+      f. [Classifing moderator variable - spray schedule][Classifying spray schedule]
+      g. [Identifing treatment variance][Identify variance]
    2. [Preliminary data exploration which investigates possible variables that could influence the meta-analysis][Preliminary Analysis]  

### 2021-02-27 02_Preliminary_analysis.Rmd
Save figure1 as a tiff for publication
Save figure format for phytopath guidelines
update chunk names

--- 2021-02-04 02_Preliminary_analysis.Rmd
@@
 print(doc, target = "paper/figures/Table1_severity&yield.docx")
+```
+
+## Disease and Yield in a box blot
+
+```{r bwplot_sev}
+sev_control_plot <- 
+   PM_MB_dat %>%
+   filter(fungicide_ai == "control") %>%
+   ggplot(aes(x = year, y = PM_final_severity)) +
+   geom_boxplot(outlier.alpha = 0) +
+   geom_jitter(size = 2, colour = "cadetblue",alpha = 0.4,width = 0.15) +
+   scale_y_continuous(breaks = c(1,3,5,7,9), limits = c(0.9,9.1)) +
+   ylab("PM severity (1 -9)")+
+   # xlab("Crop season")+
+   theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+   ggtitle("A")
+
+sev_control_plot      
+```
+
+```{r bwplot_yield}
+sev_schedule_plot <-
+   PM_MB_dat %>%
+   ggplot(aes(x = spray_management, y = PM_final_severity)) +
+   geom_boxplot(outlier.alpha = 0) +
+   geom_jitter(
+      size = 2,
+      colour = "cadetblue",
+      alpha = 0.4,
+      width = 0.15
+   ) +
+   scale_y_continuous(breaks = c(1, 3, 5, 7, 9), limits = c(0.9, 9.1)) +
+   scale_x_discrete(labels = c(
+      "control",
+      "early",
+      "late",
+      "late+",
+      "recommended",
+      "recomended+"
+   )) +
+   ylab("PM severity (1 -9)") +
+   #xlab("Spray Schedule")+
+   theme(
+      axis.title.x = element_blank(),
+      axis.text.x = element_blank(),
+      axis.title.y = element_blank(),
+      #axis.ticks.x = element_blank()
+   )+
+   ggtitle("B")
+
+sev_schedule_plot
+```
+
+```{r bwplot_yield_year}
+Y_control_plot <-
+   PM_MB_dat %>%
+   filter(fungicide_ai == "control") %>%
+   ggplot(aes(x = year, y = grain_yield.t.ha.)) +
+   geom_boxplot() +
+   geom_jitter(
+      size = 2,
+      colour = "coral",
+      alpha = 0.4,
+      width = 0.15
+   ) +
+   scale_y_continuous(breaks = seq(0, 2.5, by = 0.5), limits = c(0, 2.6)) +
+   ylab(bquote('Mungbean grain yield ' *  ~  ~ t ~ ha ^ -1 * "")) +
+   xlab("Crop season") +
+   theme(axis.text.x = element_text(angle = 20, hjust = 0.75),
+         plot.margin = margin(0.2, 0, 0.71, 0, "cm"),
+         axis.title.x = element_text(vjust = -5))
+
+Y_control_plot
+```
+
+```{r bwplot_yield_sched}
+Y_schedule_plot <- 
+   PM_MB_dat %>%
+   ggplot(aes(x = spray_management, y = grain_yield.t.ha.)) +
+   geom_boxplot(outlier.alpha = 0) +
+   geom_jitter(
+      size = 2,
+      colour = "coral",
+      alpha = 0.4,
+      width = 0.15
+   ) +
+   scale_y_continuous(breaks = seq(0, 2.5, by = 0.5), limits = c(0, 2.6)) +
+   scale_x_discrete(labels = c(
+      "control",
+      "early",
+      "late",
+      "late+",
+      "recommended",
+      "recomended+"
+   )) +
+   #ylab(bquote('Mungbean grain yield ' *  ~  ~ t ~ ha ^ -1 * "")) +
+   xlab("Spray Schedule")+
+    theme(
+      axis.title.y = element_blank(),
+      axis.text.x = element_text(angle = 20, hjust = 0.75))
+
+Y_schedule_plot
+```
+
+```{r}
+#library(gridExtra)
+
+p4 <- arrangeGrob(sev_control_plot,
+                  sev_schedule_plot,
+                  Y_control_plot,
+                  Y_schedule_plot)
+
+ggsave(
+   filename = "paper/figures/Fig1_boxplots_yield&sev.tiff",
+   plot = p4,
+   device = "tiff",
+   height = 6,
+   width = 7,
+   dpi = 300,
+   units = "in"
+
+)
 ```

### 2021-02-27 R/y_save.R
re-render chap 1 + 2

@@ -1,0 +1,14 @@
+y_save <- function(est,
+                   se,
+                   g_price_ha = 1.2,
+                   fun_price_ha = 4.18,
+                   applications = 1,
+                   application_cost = 2) {
+   net_return <- c((est - (se * 2)) * g_price_ha,
+                   (est + (se * 2)) * g_price_ha)
+   gross_return <-
+      net_return - (fun_price_ha * (applications + application_cost))
+   
+   return(gross_return)
+   
+}

### 2021-03-01 02_Preliminary_analysis.Rmd
line breaks, word smithing and add disease pressure plot

@@
 
-## Trial focused summaries
+Now we have the clean data let's summarise the main variables.
 
-The data explored in the `PM_MB_dat` data frame is a clean data frame focusing on trials which met the selection criteria and the treatments testing DMi fungicides (tebuconazole / propiconazole) or no spray controls.
+## Trial summaries statistics
 
-### Spatio-temporal variation  
-#### Trial seasons
-Let's look at how many trials were undertaken each season in trials including DMI fungicides.
+The data explored in the `PM_MB_dat` data frame is a clean data frame focusing on trials which met the selection criteria testing DMI fungicides (tebuconazole / propiconazole) or no spray controls.
+
+### Trial seasons
+How many trials were undertaken each season.
 
 ```{r FinalTrialsForInclusion1}
-tmp1 <- PM_MB_dat %>%
+PM_MB_dat %>%
    distinct(trial_ref, location, year) %>%
-   arrange(year)
-table(tmp1$year)
+   arrange(year) %>%
+   group_by(year) %>%
+   summarise(n = n())%>%
+   flextable()
+
 ```
-#### Trial locations
+### Trial locations
 The location of the trials including DMI fungicides.
@@
 ```{r FinalTrialsForInclusion}
-   table(tmp1$location)
+PM_MB_dat %>%
+   distinct(trial_ref, location, year) %>%
+   group_by(location) %>%
+   summarise(n = n())%>%
+   flextable()
 ```
+<br>
 
-### Full trial summary
-Let's inspect a summary of both powdery mildew severity and grain yield for trials including DMI fungicides.
+### Powdery mildew severity and mungbean grain yield summary per trial  
+Show a summary of both `powdery mildew severity` and mungbean `grain yield` means and ranges for all trials including DMI fungicides.
 
@@
       m_PM_sev_control = "Control median\nPM severity",
-      PM_sev_range = "PM severity\nrange*",
-      m_PM_yield_control = "Control\nmean yield*",
+      PM_sev_range = "PM severity\nrange",
+      m_PM_yield_control = "Control\nmean yield",
       yield_range = "Yield range\n(t / ha)"
@@
       "Table 1: Mean yield and severity for trials included in the meta-analysis.
-Powdery mildew (PM) onset, number of treatments per trial (n), PM median plot severity of the non-fungicide treated plots and the severity range in fungicide treatments, * bracketed numbers refer to the number of pooled control treatments summarised; Mean yield in non-fungicide treated control and the range of yields in the fungicide treatments in tonnes per hectare"
+Powdery mildew (PM) onset date, number of treatments per trial (n), PM median plot severity of the non-fungicide treated plots and the severity range in fungicide treatments, bracketed numbers refer to the number of pooled control treatments summarised; Mean yield in non-fungicide treated control and the range of yields in the fungicide treatments in tonnes per hectare"
    )
@@
 
-Save table to a word document to use in manuscript
 ```{r eval=FALSE, include=FALSE}
@@
 ```
+<br>
+<br>
 
-## Disease and Yield in a box blot
+### Summary plots
+#### Seasonal disease pressure
 
@@
    # xlab("Crop season")+
-   theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+
+   # theme(axis.title.x=element_blank(),
+   #      axis.text.x=element_blank(),
+   #      axis.ticks.x=element_blank())+
    ggtitle("A")
@@
 ```
+<br>
+<br>
+
+#### Disease severity range for each spray schedule
 
@@
    ylab("PM severity (1 -9)") +
-   #xlab("Spray Schedule")+
-   theme(
-      axis.title.x = element_blank(),
-      axis.text.x = element_blank(),
-      axis.title.y = element_blank(),
-      #axis.ticks.x = element_blank()
-   )+
+   # xlab("Spray Schedule")+
    ggtitle("B")
@@
 ```
+
+<br>  
+<br>
+
+#### Seasonal grain yield
 
@@
 ```
+
+<br>
+<br>
+
+#### Mungbean yield for each spray schedule
 
@@
 #library(gridExtra)
+# save plots into a 4 x 4 grid for publication
 
-p4 <- arrangeGrob(sev_control_plot,
-                  sev_schedule_plot,
+p4 <- arrangeGrob(
+   sev_control_plot + theme(
+      axis.title.x = element_blank(),
+      axis.text.x = element_blank(),
+      axis.title.y = element_blank()
+   ),
+   sev_schedule_plot + theme(
+      axis.title.x = element_blank(),
+      axis.text.x = element_blank(),
+      axis.title.y = element_blank()
+   ),
    Y_control_plot,
-                  Y_schedule_plot)
+   Y_schedule_plot
+)
 
@@
 
-## Treatment focuses summaries
+![Box plots of the unsprayed control treatments means for both PM severity (top) and crop yield (bottom), indicating within-season variation (A), and trial treatment means for each spray schedule (B).](paper/figures/Fig1_boxplots_yield&sev.png)
 
-Various factors have been studied in the previous experiments which may influence the subsequent meta-analysis.
-On this page, unless stated, the following plots and analyses were made disregarding other effects.
-The following factors are postulated to influence mungbean grain yield and/or powdery mildew mean plot severity.
+<br>  
+<br>  
+<br>  
+<br>
 
-   1 Fungicide type
+*****
 
-   2 Fungicide dose (varies only slightly within some fungicide types)
+## Treatment focused summaries
 
-   3 Number of fungicide sprays
+Various factors have been studied in the collated trials which may influence the subsequent meta-analysis.
+A quick inspection of the following factors were done to examine the possible influence these variables may have on on mungbean grain yield and/or powdery mildew mean plot severity.
 
-   4 Timing of fungicide spray/s relative to first sign of disease
+   1. [Fungicide type] (propiconazole and tebuconazole)  
+   2. [Fungicide Doses]
+   3. [Number of fungicide sprays]  
+   4. [Host cultivar][Mungbean cultivars] (probably is a co-variate with season due to changing cultivars over time)  
+   5. [Row spacing]  
+   6. [Final disease rating / disease pressure][Disease pressure]
+   7. [Moisture availability for the crop][In-crop rainfall]
 
-   5 Host cultivar (probably is a co-variate with season due to changing cultivars over time)
-
-   6 Experiment location
-
-   7 Row spacing
-
-   8 Final disease rating / disease pressure
-
-The data plotted below are from `r length(unique(PM_MB_dat$trial_ref))` field trials between (`r first(levels(PM_MB_dat$year))` - `r last(levels(PM_MB_dat$year))`) of which the details are described in the [Trials considered for inclusion in meta-analysis section](#Trials-considered-for-inclusion-in-meta-analysis).
+The data plotted below are from `r length(unique(PM_MB_dat$trial_ref))` field trials between (`r min(PM_MB_dat$year)` - `r max(PM_MB_dat$year)`) of which the details are described in the [Trials considered for inclusion in meta-analysis].
+<br>
 
@@
 ```
+
+<br>  
+<br>
+
+*****
+
 #### Yield effect
@@
 ```
+<br>  
+<br>
+
+*****
 
@@
 This dose effect should be acknowledged in the meta-analysis.
+
 How many treatments of each dose have been investigated per trial?
+
+<br>
 
@@
 ```
-
-One trial show both doses were applied in the same trial, and mung1112/02.
+<br>  
+<br>
 
@@
 
-#### Number of fungicide sprays
+### Number of fungicide sprays
 
-Let's look at the frequency of sprays per fungicide.  
+Inspect the frequency of sprays per fungicide.  
 ```{r Fungicide_x_nSprays}
@@
 ```
+Very few treatments were sprayed more than three times and only in `r unique(PM_MB_dat[PM_MB_dat$total_fungicide == 3,"trial_ref"])`
 
-This table shows that the majority of treatments inspected one and two spray management practices.
+<br>  
+<br>
 
 *****
-
 ### Mungbean cultivars
@@
 
-```{r Host_genotype}
+```{r Host_genotype, message=FALSE}
 PM_MB_dat %>%
@@
 ```
+
+#### Yield loss in cultivar Jade
+
+Mungbean Jade shows the best quantitative resistance to powdery mildew.  
+Based on a GRDC report by Sue Thompson [-@SueThompson2016] we want to know what the yield loss was in on cultivar Jade in the 2016 Trials.
+
+```{r JadeYieldLoss}
+PM_MB_dat %>%
+   filter(year == "2016",
+          host_genotype == "Jade") %>%
+   mutate(Treatment = case_when(fungicide_ai == "control" ~ "control_yield",
+                                TRUE ~ "FungicideTreated_yield")) %>%
+   group_by(location, Treatment) %>%
+   summarise(
+      trial_ref = trial_ref,
+      location = location,
+      year = year,
+      Yield = mean(grain_yield.t.ha., na.rm = TRUE),
+      .groups = "drop"
+   ) %>%
+   distinct() %>%
+   pivot_wider(names_from = Treatment, values_from = Yield) %>%
+   mutate(Diff = FungicideTreated_yield - control_yield) %>%
+   mutate(percent = (Diff / FungicideTreated_yield) * 100) %>%
+   select(trial_ref,
+          location,
+          year,
+          control_yield,
+          FungicideTreated_yield,
+          percent,
+          Diff) %>%
+   flextable()
+```
+
+<br>  
+<br>
+
+*****
 
@@
 
-Let's plot the row spacing treatments for the response variables yield and disease severity.  
+Let's plot the row spacing treatments for the response variables, *yield* and *disease severity*.  
 The main questions are:
@@
 <br>
+
+*****
+
+### Disease pressure  
+The amount of disease pressure between seasons is another variable which could impact mungbean yield meta-analysis effect size. 
+```{r D_pres}
+# Assess the effect of yield pressure on the spray schedule efficacy
+PM_MB_dat[,"trial_ref"]
+
+mean_control <- function(trial) {
+   mean(PM_MB_dat[PM_MB_dat$trial_ref == trial &
+               PM_MB_dat$fungicide_ai == "control", "grain_yield.t.ha."], na.rm = TRUE)
+}
+
+PM_MB_dat$Y_control <- sapply(PM_MB_dat$trial_ref, mean_control)
+
+# Quantile to separate disease pressure
+DP33 <- 
+   PM_MB_dat %>%
+   filter(fungicide_ai == "control") %>%
+   pull(PM_final_severity) %>%
+   quantile(0.3333)
+
+DP66 <- 
+   PM_MB_dat %>%
+   filter(fungicide_ai == "control") %>%
+   pull(PM_final_severity) %>%
+   quantile(0.6666)
+
+PM_MB_dat %>%
+   mutate(yc = case_when(fungicide_ai == "control" ~ grain_yield.t.ha.,
+                         TRUE ~ NA_real_))%>%
+   group_by(trial_ref)%>%
+   mutate(yc = mean(yc, na.rm=TRUE)) %>%
+   mutate(yield_saved = case_when(fungicide_ai != "control" ~ grain_yield.t.ha. - yc,
+                    fungicide_ai == "control" ~ NA_real_)) %>%
+   mutate(dc = case_when(fungicide_ai == "control" ~ PM_final_severity,
+                         TRUE ~ NA_real_))%>%
+   mutate(dc = mean(dc, na.rm = TRUE))%>%
+   ungroup() %>%
+   mutate(disease_pressure = case_when(dc <= DP33 ~ "low",
+                                 dc <= DP66 &
+                                 dc > DP33 ~ "medium",
+                                 dc > DP66 ~ "high",
+                                 TRUE ~ NA_character_))%>%
+   filter(spray_management != "control") %>%
+   ggplot(aes(disease_pressure, yield_saved))+
+   geom_boxplot()+ 
+   facet_grid(. ~ spray_management)
+
+```
+
+From these plots it is difficult to determine if there is an interaction between disease pressure and the yield saved, or if no interaction exists and fungicide efficacy in general has greater potential to save yield when disease pressure is higher.
+It is worth noting there was not sufficient variation in the control plot disease severity to produce a `medium` disease severity category.
+
+<br>  
+<br> 
 <br>  
@@
 
-### Yield loss in cultivar Jade
-
-Mungbean Jade shows the best quantitative resistance to powdery mildew.
-Based on a GRDC report by Sue Thompson [-@SueThompson2016] we want to know what the yield loss was in on cultivar Jade in the 2016 Trials.
-
-```{r JadeYieldLoss}
-PM_MB_dat %>%
-   filter(year == "2016",
-          host_genotype == "Jade") %>%
-   mutate(Treatment = case_when(fungicide_ai == "control" ~ "control_yield",
-                                TRUE ~ "FungicideTreated_yield")) %>%
-   group_by(location, Treatment) %>%
-   summarise(
-      trial_ref = trial_ref,
-      location = location,
-      year = year,
-      Yield = mean(grain_yield.t.ha., na.rm = TRUE),
-      .groups = "drop"
-   ) %>%
-   distinct() %>%
-   pivot_wider(names_from = Treatment, values_from = Yield) %>%
-   mutate(Diff = FungicideTreated_yield - control_yield) %>%
-   mutate(percent = (Diff / FungicideTreated_yield) * 100) %>%
-   select(trial_ref,
-          location,
-          year,
-          control_yield,
-          FungicideTreated_yield,
-          percent,
-          Diff)
-```
-
-### FAO mungbean data
-
-An important consideration for why to carry out work on mungbean diseases is the value the crop provides. 
-Let's pull in data from the FAOSTAT website for the area of mungbean crops harvested.
-
-```{r FAO_data_inquiry}
-beans <- read.csv(here("data/FAOSTAT_data_7-6-2020.csv"))
-
-str(beans)
-
-beans %>%
-   filter(Item == "Beans, dry",
-          Element == "Area harvested") %>%
-   select(Year, Value) %>%
-   ggplot(aes(y = Value, x = Year)) +
-   geom_point() +
-   geom_smooth()
-```
+*****
 
 ### In-crop rainfall  
+#### Whole season
+
 First an inspection of all rainfall within the season
@@
 
+<br>  
+<br>
+
+#### Early-season rainfall
+Here we only look at the effect of rainfall between the _planting date_ and _first sign of disease_. 
+We are choosing first sign of disease as a mid point in the crop maturity.
+
 ```{r early_season_rain}
@@
 ```
+
+There is a significant negative association here, indicating rain fall early in the crop development negativley affects mungbean yields.
+However the very low R-squared value indicates it is no a strong one.
+
+<br>  
+<br>
+
+#### Late-season rainfall  
+Here we only look at the effect of rainfall between the _first sign of disease_ and _crop harvest_.
 
@@
 
+There is a significant positive association here, indicating rainfall after disease commences is likely to lead to increased yield.
+However the very low R-squared value indicates it is no a strong one.
+
+<br>  
+<br>
+
+#### Mid-season rainfall  
+Here we only look at the effect of rainfall between the 20 days after planting and 80 days after planting.
 ```{r mid_rain}
@@
          longitude = x["lon"],
-         start = ymd(x["planting_date"]) + days(0),
-         end = ymd(x["planting_date"]) + days(63)
+         start = ymd(x["planting_date"]) + days(20),
+         end = ymd(x["planting_date"]) + days(80)
       )
@@
 ```
+There is no association with mid season rain and crop yields.
+
+<br>  
+<br> 
+<br> 
+******
+
+### FAO mungbean data
+
+An important consideration for why to carry out work on mungbean diseases is the value the crop provides. 
+Let's pull in data from the FAOSTAT website for the area of mungbean crops harvested.
+
+```{r FAO_data_inquiry}
+beans <- read.csv(here("data/FAOSTAT_data_7-6-2020.csv"))
+
+str(beans)
+
+beans %>%
+   filter(Item == "Beans, dry",
+          Element == "Area harvested") %>%
+   select(Year, Value) %>%
+   ggplot(aes(y = Value, x = Year)) +
+   geom_point() +
+   geom_smooth()
+```

### 2021-03-01 05_severity_metaAnalysis.Rmd
rearrange table headings

@@
    filter(Freq != 0) %>%
-   group_by(Var2) %>%
-   summarise(n()) %>%
-   pull()
+   pull(Freq)
 
@@
    eff_bar = round(1 -(intercept + PMsev_mv$b)/intercept,4)*100,
-   eff_CI_low = round(1 -(intercept + PMsev_mv$ci.lb)/intercept,4)*100,
-   eff_CI_high = round(1 -(intercept + PMsev_mv$ci.ub)/intercept,4)*100
+   eff_CI_high = round(1 -(intercept + PMsev_mv$ci.ub)/intercept,4)*100,
+   eff_CI_low = round(1 -(intercept + PMsev_mv$ci.lb)/intercept,4)*100
+
 )
@@
      "Efficacy",
-     "Eff CI upper",
-     "Eff CI_lower")
+     "Eff CI_lower",
+     "Eff CI upper")
 

### 2021-03-01 03_Yield_MetaAnalysis.Rmd
Rename chunks and filename

--- 2021-02-24 04_MetaAnalysis.Rmd
@@
 
-```{r MEsummary_Libraries2, message=FALSE, include=FALSE}
+```{r Yield_ME_libraries, message=FALSE, include=FALSE}
 if (!require("pacman"))
@@
 ### Define Trial
-```{r define_trial}
+```{r Yield_define_trial}
 PM_dat_Y <-
@@
 
-```{r Metafor-analysis}
+```{r Yield_Metafor-analysis}
 PM_mv <- rma.mv(
@@
 
-```{r osset_Metafor-analysis}
+```{r onset_Metafor-analysis}
 PM_mv_onset <- rma.mv(
@@
 
-```{r metafor_results}
+```{r metafor_results_table_yield}
 # obtain number of treatments included in each moderator variable
@@
 
-```{r metafor_plot}
+```{r metafor_plot_yied}
 results_mv %>%
@@
 
-```{r PM_Mv_Contrast}
+```{r PM_Mv_Contrast_yield}
 source("R/simple_summary.R") #function to provide a table that includes the treatment names in the contrasts
@@
 These contrasts can be viewed in a plot
-```{r plotContrasts}
+```{r plotContrasts_yield}
 par(mar = c(5, 13, 4, 2) + 0.1)
@@
 datPM3 <- PM_dat_Y %>%
-   group_by(trial, spray_management, n) %>%
+   group_by(trial, spray_management, replicates) %>%
    summarize(yi_mean = mean(grain_yield.t.ha.),
@@
    treat = spray_management,
-   n = n,
+   n = replicates,
    mean = yi_mean,
@@
 ```{r Save_meta_data, eval=FALSE}
-save(efficacy,
-     PM_dat_Y,
+save(PM_dat_Y,
      PM_mv,

### 2021-03-01 02_Preliminary_analysis.Rmd
Delete unused function

@@
 # Assess the effect of yield pressure on the spray schedule efficacy
-PM_MB_dat[,"trial_ref"]
-
-mean_control <- function(trial) {
-   mean(PM_MB_dat[PM_MB_dat$trial_ref == trial &
-               PM_MB_dat$fungicide_ai == "control", "grain_yield.t.ha."], na.rm = TRUE)
-}
-
-PM_MB_dat$Y_control <- sapply(PM_MB_dat$trial_ref, mean_control)
-
-# Quantile to separate disease pressure
+# Quantile to separate disease pressure into High, Medium and low disease pressure categories
 DP33 <- 

### 2021-03-02 03_Yield_MetaAnalysis.Rmd
Edit headings

@@
 
-## metafor analysis
+<br>  
+<br>  
+<br>
+
+## Spray schedule meta-analysis  
+### Spray schedule moderator
 
@@
 
-### Influence of disease onset
+<br>  
+<br>  
+<br>  
+******
+
+### Disease onset interaction with spray schedule
 
@@
 
+<br>  
+<br>  
+<br>  
+******
+
 #### metafor onset analysis
@@
 
-### Influence of disease pressure
+<br>  
+<br>  
+<br>  
+******
+
+### Disease pressure interaction with spray schedule
 
@@
 
-#### metafor onset analysis
+<br>  
+<br>  
+<br>  
+******
+
+#### metafor disease pressure interaction
 
@@
 
-```{r osset_Metafor-analysis}
+```{r Dpressure_Metafor-analysis}
 PM_mv_dp <- rma.mv(
@@
 ```
+
+<br>  
+<br>  
+<br>  
+******
 
@@
 
-### Meta-analysis moderator estimates table
+<br>
+<br>
+<br>
+******
+
+## Meta-analysis results summary
+### Moderator estimates table
 Let's present the meta-analysis results for the moderator variables in a table of estimates.
@@
 
+<br>  
+<br>
+
 Let's view these comparisons in a plot.
+
+### Moderator estimates plot
 
@@
 
+<br>  
+<br>
+
+### Moderator contrasts
 Let's investigate the treatment contrasts
@@
 
-****
+<br>  
+<br>  
+<br>  
+******
 
@@
 
+<br>  
+<br>
+
+### netmeta estimates plot
 Now let's visualise this as a forest plot.
@@
 ```
+<br>  
+<br>  
+<br>  
+******
+
+### Moderator netgraph
 

### 2021-03-02 04_Severity_MetaAnalysis.Rmd
Edit headings

--- 2021-03-01 05_severity_metaAnalysis.Rmd
@@
 
-# Meta-analysis of powdery mildew severity
+# Powdery mildew severity Meta-analysis
 
@@
 
+<br>  
+<br>  
+<br>  
+******
+
+## Disease severity spray schedule meta-analysis
+
 ```{r Metafor-Sev-analysis}
@@
 
+<br>  
+<br>  
+<br>
+
+### Disease severity moderator contrasts
+
 ```{r sevContrasts}
@@
 ```
+
+<br>  
+<br>  
+<br>
 
@@
 
+<br>  
+<br>  
+<br>
+
+### Meta-analysis summary table
 ```{r metafor_results}

### 2021-03-02 index.Rmd
Edit headings

@@
 ## Contents
-This compendium is broken down into seven sections:
+This compendium is broken down into four sections:
 
@@
       e. [Apply selection criteria][Subset data to selection criteria]
-      f. [Classifing moderator variable - spray schedule][Classifying spray schedule]
+      f. [Classifing moderator variable - spray schedule][Defining spray schedule variable]
       g. [Identifing treatment variance][Identify variance]
-   2. [Preliminary data exploration which investigates possible variables that could influence the meta-analysis][Preliminary Analysis]  
+   2. [Preliminary data exploration][Preliminary Analysis]  
+      a. [Trial summary statistics]  
+         i) [Seasons][Trial seasons]  
+         ii) [Location][Trial locations]  
+         iii) [Severity and Yield summary table][Powdery mildew severity and mungbean grain yield summary per trial]  
+         iv) [Severity and Yield summary plots][Summary plots]  
+      b. [Treatment focused summaries]  
+         i) [Fungicide type]  
+         ii) [Fungicide doses]  
+         iii) [Number of fungicide sprays]  
+         iv) [Mungbean cultivars]  
+         v) [Row spacing]  
+         vi) [Disease pressure]  
+         vii) [In-crop rainfall]  
+   3. [Grain yield meta-analysis]  
+      a. [Spray schedule meta-analysis and moderator interactions][Spray schedule meta-analysis]  
+         i. [Spray schedule moderator]  
+         ii. [Disease onset interaction with spray schedule]
+         iii. [Disease pressure interaction with spray schedule]  
+         iv. [Compare variance-covavriance matrix structure][Test variance-covavriance matrix structure]  
+      b. [Meta-analysis results summary]  
+         i. [Moderator estimates table]  
+         ii. [Moderator estimates plot]  
+         iii. [Moderator contrasts]  
+         iv. [Profile plots]
+      c. [netmeta analysis]  
+         i. [netmeta estimates plot]
+         ii. [Moderator netgraph]
+   4. [Powdery mildew severity Meta-analysis]  
+      a. [Disease severity spray schedule meta-analysis]
+
       a. [Fungicides][Fungicides]  

### 2021-03-02 01_TrialsForInclusionInAnalysis.Rmd
change devtools:: to remotes::

@@
 if (!require("theme.usq"))
-   devtools::install_github("adamhsparks/theme.usq")
+   remotes::install_github("adamhsparks/theme.usq")
 library(theme.usq)

### 2021-03-02 02_Preliminary_analysis.Rmd
Edit headings
change devtools:: to remotes::

@@
 
-## Trial summaries statistics
+## Trial summary statistics
 

### 2021-03-03 index.Rmd
reduce title page

--- 2020-06-22 index.Rmd
@@
 ## Contents
-This compendium is broken down into seven sections:
+This compendium is broken down into four sections:
 
-   1. [Details of the experiments, which were included in the analysis][Studies considered in meta-analysis]  
-   2. [Preliminary data exploration which investigates possible variables that could influence the meta-analysis][Preliminary Analysis]  
-      a. [Fungicides][Fungicides]  
-      b. [Mungbean cultivar][Mungbean cultivars]  
-      c. [Row spacing][Row spacing]  
-      d. [Rainfall][Yield vs in-season rain]  
-      e. [When conditions become suitable for powdery mildew infection][Season range and first incidence]  
-   3. [Preparation of data for the meta-analysis][Prepare data for meta-analysis]  
-   4. [Meta-analysis of the effect of fungicide spray schedule on yield loss][Meta-analysis]  
-   5. [Meta-analysis of the effect of fungicide spray schedule on disease severity and yield loss][AUPDC meta-analysis]
-   6. [Manuscript Wireframe][Manuscript wire frame]
-   7. [Manuscript: A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew.][Manuscript]
+   1. [Details of the experiments, and application of inclusion criteria in the analysis][Trials considered for inclusion in meta-analysis]  
+   2. [Preliminary data exploration][Preliminary Analysis]  
+   *including a summary of the cleaned trial data and the treatments*
+   3. [Grain yield meta-analysis]  
+   4. [Powdery mildew severity Meta-analysis]
 
-## Other research questions, which are not the focus of this study
+These sections detail the methods and process we undertook during this meta-analysis.
 
-+ How has the first sign of powdery mildew changed between the seasons and experimental sites?
+The manuscript publishing the results presented in this compendium can be found at ....
 
-+ Is there an ideal planting time, or fungicide management strategy, which could make use of powdery mildew defoliation during pod maturation resulting in an increased yield?
-
-+ Do infections that occur before flowering increase the probable yield loss?
-
-## Possible sources of variation in this analysis.
-
-+ Variability among host genotypes.
-
-   + The probable influence of season might be influenced by host genotype.
-   This is because newer varieties were adopted into experimental trials as they were released.
-
-   + Between 2001 and 2015 mungbean genotype changed from Green Diamond, Berken, Crystal to Jade.
-   Jade was the only cultivar used between 2015 and 2019.
-
-   + Estimations of plant maturity stages over each growing season.
-    These estimations might able to be computed using APSIM.
+Preprint at .........

### 2021-03-03 index.Rmd
Update index title page with background

@@
 ---
-# Home
+# About
+## Background  
+A common practice for managing powdery mildew in mungbean is to couple fungicide with an insecticide spray early in the development of the crop, usually before the disease is detected.
+This is despite the current recommendations that the best yield protection is achieved when the fungicide is first applied at the first sign of the disease.
+These recommendations were based on individual studies, many of which lacked sufficient power to draw significant conclusions.
+We undertook a meta-analysis to determine, when should the first fungicide spray be applied on mungbean to maximise yield protection.
 
-This research compendium details the statistical analysis and methods of a meta-analysis of fungicide efficacy trials for controlling powdery mildew in mungbean.
+## Compendium contents
+This research compendium details importing and summarising the raw data, application of the selection criteria, defining moderator variables for fungicide spray timing, and the statistical analysis methods for this meta-analysis of fungicide efficacy trials for controlling powdery mildew in mungbean.
 The meta-analysis's main aim is to determine:
@@
 
-## Contents
+For completeness We also evaluated the efficacy of spray schedules on disease severity in the field.
+
+## Main chapters
 This compendium is broken down into four sections:
@@
 
+## Links to manuscript
 The manuscript publishing the results presented in this compendium can be found at ....

### 2021-03-08 01_TrialsForInclusionInAnalysis.Rmd
Word smithing and document spacing

@@
 
-```{r MEsummary_Libraries, message=FALSE, echo=FALSE}
+Trials testing fungicide efficacy on powdery mildew in mungbean in the Grains Research and Development Corporation (GRDC) northern grains region were sourced for a meta-analysis.
+
+Data were collected from a number of researchers from the Department of Agriculture and Fisheries (DAF), the University of Southern Queensland (USQ) and the National Growers Association (NGA).
+We would like to acknowledge in particular Professor Malcolm Riley's and Dr.
+Sue Thompson's effort in establishing and coordinating early field trials between 2010 and 2014 and GRDC for funding many of the trials which were included in this meta-analysis.
+
+<br>
+
+### Load required r packages
+
+```{r MEsummary_Libraries, echo=TRUE, results='hide'}
 if (!require("pacman"))
    install.packages("pacman")
+
 pacman::p_load(tidyverse, kableExtra, leaflet, htmltools, lubridate, here)
@@
    remotes::install_github("adamhsparks/theme.usq")
+
 library(theme.usq)
-theme_set(theme_usq()
-)
+theme_set(theme_usq())
 ```
-Trials testing fungicide efficacy on powdery mildew in mungbean in the Grains Research and Development Corporation (GRDC) northern grains region were sourced for a meta-analysis.
 
-Data was collected from a number of researchers from the Department of Agriculture and Primary Industries and the University of Southern Queensland and the National Growers Association.
-We would like to acknowledge in particular Professor Malcolm Riley's and Dr.
-Sue Thompson's effort in establishing and coordinating early field trials between 2010 and 2014 and GRDC for funding many of the trials featured in this meta-analysis.
-
+<br>  
 <br>
@@
 <br>  
+<br>
 
 ## Import data  
-**Import data from trials where we obtained the raw data**  
+**Import data from trials which the raw data was available**  
 ```{r import_dataRAW}
@@
 <br>
-<br>
-<br>
 
@@
 <br>
-<br>
 
 ## Summary of all trials
-```{r data_summary, echo=FALSE, message=FALSE, warning=FALSE}
+
+```{r data_summary}
 PM_MB_dat %>%
@@
 **Exclude fungicides tested in too few trials**  
-We need to focus the meta-analysis on fungicides with the same mode of action.
-Let's look at all the fungicides and retain the best represented fungicide group in the data.
+The meta-analysis should be focused on fungicides with the same mode of action.
+Fungicides from the best represented group will be retained.
 ```{r Fungicides}
@@
 
-Amistar Xtra and Custodia both contain strobilurin and triazole, however, because they contain differing dose ratios (inverted) pooling may not be appropriate.
-
-Perhaps best way forward is to focus the meta-analysis on only the DMIs.
-This can then be compared to an additional meta-analysis including azoxystrobin as a comparison.
+Amistar Xtra and Custodia both contain strobilurin and triazole, however, because they contain differing dose ratios (inverted) pooling may not be appropriate therefore they will be removed.
 
@@
 
-Finally, we are going to define the class of each variable in the data, retaining only the variables relevant to the analysis.
+Importantly, the class of each variable in the data should be defined, retaining only the variables relevant to the analysis.
 
 ```{r classifyData}
-source("R/classify_PM_data.R")
+source("R/classify_PM_data.R") # use a custom code
 
@@
 ```
+
+<br>  
+<br>
 
@@
 
-To ensure sufficient number of replicates, we will bin the continuous variable into three categorical variables relating to when the first fungicide application was made, relative to the first sign of disease.
+To ensure sufficient number of replicates, treatments were binned by the first fungicide application date into three categorical variables relating to when the first fungicide application was made, relative to the first sign of disease.
+
+<br>
 
@@
    - **Late**: First fungicide application was four or more days after first sign of disease being observed.
+
+<br>
 
@@
 
+<br>  
+<br>  
+<br>
+
 ## Identify variance
@@
 
+<br>
+
 Remove one trial in Emerald which did not report disease variance or yield variance.
@@
 
+<br>
+
 Following an inspection of the yield and disease variance we determined imputation was not suitable and therefore we must exclude trials that did not report variance.
@@
 
-One more trial will be removed for our yield data set `PM_dat_Y` for not reporting yield variance.  
+One trial will be removed from the yield data set `PM_dat_Y` for not reporting yield variance.  
 ```{r TrialsWithVariance}
@@
 
+<br>
+
 #### Save the cleaned data

### 2021-03-09 02_Preliminary_analysis.Rmd
Wordsmithing and appearance

@@
 
-```{r PA_Libraries, include=FALSE, message=FALSE}
+```{r PA_Libraries, echo=TRUE, results='hide'}
 if (!require("pacman"))
@@
 
-Now we have the clean data let's summarise the main variables.
+<br>  
+<br>
 
@@
 The data explored in the `PM_MB_dat` data frame is a clean data frame focusing on trials which met the selection criteria testing DMI fungicides (tebuconazole / propiconazole) or no spray controls.
+
+<br>
 
@@
 ```
+
+<br>  
+<br>
+
 ### Trial locations
@@
 ```
+
+<br>  
 <br>
@@
 ### Summary plots
-#### Seasonal disease pressure
+#### Seasonal disease pressure in the control
 
@@
 
-#### Seasonal grain yield
+#### Seasonal grain yield in the control
 
@@
 
-```{r}
+```{r include = FALSE}
 #library(gridExtra)
@@
 The data plotted below are from `r length(unique(PM_MB_dat$trial_ref))` field trials between (`r min(PM_MB_dat$year)` - `r max(PM_MB_dat$year)`) of which the details are described in the [Trials considered for inclusion in meta-analysis].
+
 <br>
@@
 
-*****
-
 #### Yield effect
@@
 ```
+
 <br>  
 <br>  
-
-*****
+<br>
 
@@
 
-Doses for propiconazole range from 62.5 to 125, a large variation.  
+Doses for propiconazole range from 62.5&nbsp;g to 125&nbsp;g, a large variation.  
 Let's inspect the difference in yields for each dose.
@@
 
-This dose effect should be acknowledged in the meta-analysis.
+This dose effect should be investigated in the meta-analysis.
+
+<br>  
+<br>
 
 How many treatments of each dose have been investigated per trial?
-
-<br>
 
@@
 <br>
-
-*****
 
@@
 
-*****
 ### Mungbean cultivars
@@
 
-Mungbean Jade shows the best quantitative resistance to powdery mildew.  
-Based on a GRDC report by Sue Thompson [-@SueThompson2016] we want to know what the yield loss was in on cultivar Jade in the 2016 Trials.
+Cultivar Jade shows the best quantitative resistance to powdery mildew.  
+Based on the 2016 GRDC report by Sue Thompson [-@SueThompson2016] we want to know what is the possible yield loss for this moderately susceptible cultivar.
 
@@
 
-*****
-
 ### Row spacing
@@
 This finding has also been shown by several other researchers' work in Queensland and New South Wales as well.
-Eight trials used a row spacing of 0.75&nbsp;meters and tebuconazole as an active ingredient (AI).
 
@@
 
-Let's plot the row spacing treatments for the response variables, *yield* and *disease severity*.  
+<br>  
+<br>
+
+Will plotting row spacing treatments show differences for the response variables, *yield* and *disease severity*.  
 The main questions are:
 
-   * Were there any statistical differences for mungbean yield or powdery mildew severity between row spacing treatments?
+   * Were there any statistical differences for mungbean *yield* or *powdery mildew severity* between row spacing treatments?
 
    * If not, can we pool certain row spacing that have no significant difference?
-
-Let's plot disease severity in boxplots grouped by row spacing treatment.
-We are asking here, which row spacing leads to the higher disease severity?
 
@@
 ```{r RS_severity_x_trial}
-# Which row spacing leads to the higher disease severity
+# Does trial year and location interact between row spacing amd disease severity
 PM_MB_dat %>%
@@
 Overall row spacing may influence both powdery mildew severity and yield.
-However, in the studies that were conducted, no interaction was found between row spacing, powdery mildew severity and yield.
-That is, the row spacing appeared to increase yield even if the amount of powdery mildew increased and no relationship could be detected between an interaction of the three.
+However, in the trial reports, no significant interaction was found between row spacing, powdery mildew severity and yield.
+That is, with narrower row spacing appeared to increase yield even if the amount of powdery mildew increased and no relationship could be detected between an interaction of the three.
 
@@
 # Assess the effect of yield pressure on the spray schedule efficacy
-# Quantile to separate disease pressure into High, Medium and low disease pressure categories
+# Use quantiles to separate disease pressure into High, Medium and low disease pressure categories
 DP33 <- 
@@
 
-*****
-
 ### In-crop rainfall  
@@
 source("R/crop_rain.R")
+
+unique(PM_MB_dat[,c("location","lat","lon")])
+PM_MB_dat[is.na(PM_MB_dat$lat),]
+
+trials <- unique(PM_MB_dat, c("location","lat","lon"))
+apply(trials,1, function(LL) {
+
+   stat_sweep <- bomrang::sweep_for_stations(as.numeric(c(LL["lat"],LL["lon"])))
+
+   # Remove banned stations
+   banned_stations <- c("055286") # stations don't report rain
+   stat_sweep <- stat_sweep[stat_sweep$site != banned_stations,]
+
+   statID <- paste(stat_sweep[1,"name"],stat_sweep[1,"site"], sep = "_")
+
+   return(statID)
+
+})
+bomrang::sweep_for_stations(unlist(PM_MB_dat[1,c("lat","lon")]))
+
+bomrang::get
 

### 2021-03-09 R/add_lat_longs.R
add gatton and Wellcamp

@@ -31,8 +31,10 @@ PM_MB_dat <-
             experiment_sites[experiment_sites$location == "NGA - Millmerran", "lat"],
          location == "Missen Flats" ~
             experiment_sites[experiment_sites$location == "Missen Flats", "lat"],
-         location == "Wellcamp " ~
-            experiment_sites[experiment_sites$location == "Wellcamp", "lat"]
+         location == "Wellcamp" ~
+            experiment_sites[experiment_sites$location == "Wellcamp", "lat"],
+         location == "Gatton" ~
+            experiment_sites[experiment_sites$location == "Gatton", "lat"]
       ),
       lon = case_when(
          location == "Hermitage" ~
@@ -49,8 +51,10 @@ PM_MB_dat <-
             experiment_sites[experiment_sites$location == "NGA - Millmerran", "lon"],
          location == "Missen Flats" ~
             experiment_sites[experiment_sites$location == "Missen Flats", "lon"],
-         location == "Wellcamp " ~
-            experiment_sites[experiment_sites$location == "Wellcamp", "lon"]
+         location == "Wellcamp" ~
+            experiment_sites[experiment_sites$location == "Wellcamp", "lon"],
+         location == "Gatton" ~
+            experiment_sites[experiment_sites$location == "Gatton", "lon"]
       )
    )
 

### 2021-03-09 R/crop_rain.R
edit function so does not use apply download on every row

@@ -1,50 +1,140 @@
 library("dplyr")
 library("lubridate")
 # Function to run over each line for sum rainfall
-crop_rain <- function(latitude, longitude, start, end) {
-   # locations <- unique(data.frame(lat = latitude,
-   #                                lon = longitude))
-   
-   LL <- format(round(as.numeric(c(latitude, longitude)),4), nsmall = 4)
-   
-      if (file.exists(paste("weather/", str_remove(paste(LL, collapse = ""),"-"), ".csv", sep = ""))) {
-      station_site <-
-         read.csv(paste("weather/", str_remove(paste(LL, collapse = ""),"-"), ".csv", sep = ""),
-                  stringsAsFactors = FALSE)
-      #message("imported: ",paste(LL,collapse = " "))
-      site_num <- unique(station_site$site_num)
+crop_rain <-
+   function(location_name,
+            latitude,
+            longitude,
+            start,
+            end) {
+      # # locations <- unique(data.frame(lat = latitude,
+      # #                                lon = longitude))
+      #
+      # LL <- format(round(as.numeric(c(latitude, longitude)),4), nsmall = 4)
+      #
+      #    if (file.exists(paste("weather/", str_remove(paste(LL, collapse = ""),"-"), ".csv", sep = ""))) {
+      #    station_site <-
+      #       read.csv(paste("weather/", str_remove(paste(LL, collapse = ""),"-"), ".csv", sep = ""),
+      #                stringsAsFactors = FALSE)
+      #    #message("imported: ",paste(LL,collapse = " "))
+      #    site_num <- unique(station_site$site_num)
+      #
+      # } else{
+      #    stat_sweep <- sweep_for_stations(latlon = as.numeric(LL))
+      #
+      #    site_num <- stat_sweep[1, site]
+      #    banned_stations <- c("055286") # stations don't report rain
+      #
+      #    if (banned_stations %in% site_num) {
+      #       site_num <- stat_sweep[2, site]
+      #    }
+      #    message("Downloading weather data from BOM servers,\nplease make a cup of coffee this will take some time.")
+      #    station_site <-
+      #       bomrang::get_historical(stationid = site_num, type = "rain")
+      #    station_site$site_num <- as.character(site_num)
+      #
+      #    write.csv(
+      #       station_site,
+      #       file = paste("weather/", str_remove(paste(LL, collapse = ""),"-"), ".csv", sep = ""),
+      #       row.names = FALSE
+      #    )
[…]

### 2021-03-09 R/crop_rain.R
correct sum_rain output and name conflicts

@@ -5,8 +5,8 @@ crop_rain <-
    function(location_name,
             latitude,
             longitude,
-            start,
-            end) {
+            first_day,
+            last_day) {
       # # locations <- unique(data.frame(lat = latitude,
       # #                                lon = longitude))
       #
@@ -105,15 +105,24 @@ crop_rain <-
                                             trials[i, "stat_file"],
                                          TRUE ~ stat_file
                                             ),
-                   s1 = ymd(start),
-                   e1 = ymd(end))%>%
-            mutate(season = interval(start = s1, end = e1))
+                   start = first_day,
+                   end = last_day)
       }
       
       
-      # apply(input_data, 1, function(x1){
-      #   
-      #})
+      input_data$sum_rain <-
+         apply(input_data, 1, function(x1) {
+            weather <-
+               read.csv(file = x1["stat_file"], stringsAsFactors = FALSE)
+            
+            int1 <- interval(start = ymd(x1["start"]), end = ymd(x1["end"]))
+      
+            weather %>%
+               mutate(log_date = ymd(paste(year, month, day, sep = "-"))) %>%
+               filter(log_date %within% int1) %>%
+               summarise(total_rain = sum(rainfall, na.rm = TRUE)) %>%
+               pull()
+         })
       
          
       # cbind(input_data, start, end)
@@ -133,8 +142,12 @@ crop_rain <-
          # return(sum_rain)
          
       
-      
+      input_data <-
+         input_data %>%
+         mutate(sum_rain = case_when(is.na(start) |
+                             is.na(end) ~ NA_real_,
+                TRUE ~ sum_rain))
 
       
-      return(input_data)
+      return(input_data$sum_rain)
    }

### 2021-03-09 02_Preliminary_analysis.Rmd
update code from crop_rain()

@@
 
-unique(PM_MB_dat[,c("location","lat","lon")])
-PM_MB_dat[is.na(PM_MB_dat$lat),]
+# Obtain rainfall from bomrang
 
-trials <- unique(PM_MB_dat, c("location","lat","lon"))
-apply(trials,1, function(LL) {
+crop_rain(location_name = PM_MB_dat$location,
+          latitude = PM_MB_dat$lat,
+          longitude = PM_MB_dat$lon,
+          first_day = PM_MB_dat$planting_date,
+          last_day = PM_MB_dat$harvest_date)
 
-   stat_sweep <- bomrang::sweep_for_stations(as.numeric(c(LL["lat"],LL["lon"])))
-
-   # Remove banned stations
-   banned_stations <- c("055286") # stations don't report rain
-   stat_sweep <- stat_sweep[stat_sweep$site != banned_stations,]
-
-   statID <- paste(stat_sweep[1,"name"],stat_sweep[1,"site"], sep = "_")
-
-   return(statID)
-
-})
-bomrang::sweep_for_stations(unlist(PM_MB_dat[1,c("lat","lon")]))
-
-bomrang::get
-
-# Obtain rainfall from bomrang
 PM_MB_dat$sum_rain <-
-   apply(PM_MB_dat, 1, function(x) {
-      crop_rain(
-         latitude = x["lat"],
-         longitude = x["lon"],
-         start = x["planting_date"],
-         end = x["harvest_date"]
-      )
-   })
+   crop_rain(location_name = PM_MB_dat$location,
+          latitude = PM_MB_dat$lat,
+          longitude = PM_MB_dat$lon,
+          first_day = PM_MB_dat$planting_date,
+          last_day = PM_MB_dat$harvest_date)
 
@@
 PM_MB_dat$early_rain <-
-   apply(PM_MB_dat, 1, function(x) {
-      crop_rain(
-         latitude = x["lat"],
-         longitude = x["lon"],
-         start = x["planting_date"],
-         end = x["first_sign_disease"]
-      )
-   })
+   crop_rain(location_name = PM_MB_dat$location,
+          latitude = PM_MB_dat$lat,
+          longitude = PM_MB_dat$lon,
+          first_day = PM_MB_dat$planting_date,
+          last_day = PM_MB_dat$first_sign_disease)
 
@@
 PM_MB_dat$late_rain <-
-   apply(PM_MB_dat, 1, function(x) {
-      crop_rain(
-         latitude = x["lat"],
-         longitude = x["lon"],
-         start = x["first_sign_disease"],
-         end = x["harvest_date"]
-      )
-   })
+   crop_rain(location_name = PM_MB_dat$location,
+          latitude = PM_MB_dat$lat,
+          longitude = PM_MB_dat$lon,
+          first_day = PM_MB_dat$first_sign_disease,
+          last_day = PM_MB_dat$harvest_date)
 
@@
 PM_MB_dat$mid_rain <-
-   apply(PM_MB_dat, 1, function(x) {
-      crop_rain(
-         latitude = x["lat"],
-         longitude = x["lon"],
-         start = ymd(x["planting_date"]) + days(20),
-         end = ymd(x["planting_date"]) + days(80)
+   crop_rain(location_name = PM_MB_dat$location,
+          latitude = PM_MB_dat$lat,
+          longitude = PM_MB_dat$lon,
+          first_day = ymd(PM_MB_dat$planting_date) + days(20),
+          last_day = ymd(PM_MB_dat$planting_date) + days(80)
    )
-   })
 

### 2021-03-09 02_Preliminary_analysis.Rmd
remove test code

@@
 # Obtain rainfall from bomrang
-
-crop_rain(location_name = PM_MB_dat$location,
-          latitude = PM_MB_dat$lat,
-          longitude = PM_MB_dat$lon,
-          first_day = PM_MB_dat$planting_date,
-          last_day = PM_MB_dat$harvest_date)
-
 PM_MB_dat$sum_rain <-

### 2021-03-09 02_Preliminary_analysis.Rmd
small edits

@@
 
+In season rainfall is known to contribute significantly to crop yields, however the timing of rainfall is likely important.
+
 First an inspection of all rainfall within the season
@@
           longitude = PM_MB_dat$lon,
-          first_day = ymd(PM_MB_dat$planting_date) + days(20),
-          last_day = ymd(PM_MB_dat$planting_date) + days(80)
+          first_day = ymd(PM_MB_dat$planting_date) + days(45),
+          last_day = ymd(PM_MB_dat$planting_date) + days(75)
    )
@@
 There is no association with mid season rain and crop yields.
+
+From the plots shown here we can draw the conclusion that we lack sufficient information. 
+Most likely available soil water between trials along with other unobserved variables influence of rainfall on mungbean crops and therefore we will not investigate any further.
 

### 2021-03-10 02_Preliminary_analysis.Rmd
Spelling corrections

@@
 ```{r RS_severity_x_trial}
-# Does trial year and location interact between row spacing amd disease severity
+# Does trial year and location interact between row spacing and disease severity
 PM_MB_dat %>%
@@
 
-There is a significant negative association here, indicating rain fall early in the crop development negativley affects mungbean yields.
+There is a significant negative association here, indicating rain fall early in the crop development negatively affects mungbean yields.
 However the very low R-squared value indicates it is no a strong one.

### 2021-03-10 03_Yield_MetaAnalysis.Rmd
change devtools:: to remotes::
Wordsmithing, editing for flow

@@
 ---
+# Grain yield meta-analysis
 
-```{r Yield_ME_libraries, message=FALSE, include=FALSE}
+Let's get started with the analysis by first finding the best model fit that answers our research question.
+
+> When, in relation to PM establishes in the crop, should farmers begin spraying mungbean to mitigate yield loss: before PM establishing, immediately after first sign of PM establishing, or after PM has become established in the crop.
+
+A secondary question to this aim is: given the time at which the first spray occurred does a second spray provide worthwhile yield protection.
+
+To do this, the model will use the main variables:
+
+   - *Grain yield* is our response variable (t / ha)
+
+   - *Trial*, which resolves combinations of categorical random variables: 
+      i) year  
+      ii) location  
+      iii) row spacing  
+      iv) fungicide dose
+      v) cultivar
+
+   - *spray_management* a moderator to evaluate the difference in effect size attributed to fungicide application timing.
+
+   - *id* random variable indicating each treatment is independent
+
+```{r Yield_ME_libraries, echo=TRUE,results='hide'}
 if (!require("pacman"))
@@
 # Data
-# load("cache/ImportDataAndSelectTrials01.Rdata")
-
 PM_dat_Y <-
@@
 ```
-
-# Grain yield meta-analysis
-
-Let's get started with the analysis by first finding the best model fit that answers our research question.
-
-> When, in relation to PM establishes in the crop, should farmers begin spraying mungbean to mitigate yield loss: before PM establishing, immediately after first sign of PM establishing, or after PM has become established in the crop.
-
-A secondary question to this aim is: given the time at which the first spray occurred does a second spray provide worthwhile yield protection.
-
-To do this, in our model:
-
-   - Grain yield is our response variable (t / ha)
-
-   - Trial, which resolves combinations of categorical variables: year, location, row spacing, fungicide dose and cultivar; is set as a random intercept
 
@@
 
-   - We will investigate the effect size of our treatment - spray management,
-
 <br>  
@@
 
-For the first grain yield meta-analysis will be an ARM based model using the `metafor` package [@Viechtbauer2010].
+For the first grain yield meta-analysis will be an ARM based model or multi-variate meta-analysis, using the `metafor` package function `rma.mv()` [@Viechtbauer2010].
 
@@
 
-To determine if when in the season the disease occurs influences the efficacy at which fungicide applications protect yield we will create a categorical variable defining `early` or `late` disease onset.
+To determine if the time at which disease occurs in the cropping season influences the efficacy at which fungicide applications protect yield we will create a categorical variable defining `early` or `late` disease onset.
 
-`early` and `late` will be divided by the median days after sowing when signs of the disease were first observed.
+`early` and `late` will be divided by a number close to the median days after sowing when signs of the disease were first observed.
+A number close to the median should ensure roughly even numbers in each category.
 ```{r median onset}
@@
 ```
+We will choose 42 days as this is the average days to flowering in mungbean. 
+In addition Kelly et. al. [@-Kelly2017a] noted that yield losses are higher in cultivar Berken when disease establishes before flowering.
+
 Now lets define these two new variables, `first_sign_days` and `onset` in the data.
@@
              lubridate::ymd(planting_date)) %>%
-   mutate(onset = case_when(first_sign_days <= 39 ~ "early_onset",
-                            first_sign_days > 39 ~ "late_onset"))
+   mutate(onset = case_when(first_sign_days <= 42 ~ "early_onset",
+                            first_sign_days > 42 ~ "late_onset"))
 ```
@@
 PM_dat_Y %>%
-   ggplot(aes(x = first_sign_days)) +
-   geom_histogram() +
-   geom_vline(xintercept = 39)
+   ggplot(aes(x = as.integer(first_sign_days))) +
+   geom_histogram(binwidth = 1) +
+   geom_vline(xintercept = 42)
 ```
@@
 ```{r}
-anova(PM_mv, PM_mv_onset)
+anova(PM_mv, PM_mv_onset)$pval
 ```
@@
 However the higher AIC indicates that the model omitting `onset` is a slightly better fit.
-Also the chi-squared test uncertain that the `onset` model is significantly better as indicated by the `pval` 0.3258.
+Also the chi-squared test uncertain that the `onset` model is significantly better as indicated by the `pval` `r round(anova(PM_mv, PM_mv_onset)$pval,3)`.
 The higher log likelihood on the `onset` model does intricate there is some merit to this model and that perhaps with more trials to increase statistical power might provide a useful model.
@@
    ggplot(aes(x = PM_final_severity)) +
-   geom_histogram() +
+   geom_histogram(binwidth = 1) +
    geom_vline(xintercept = 8)

### 2021-03-10 R/crop_rain.R
edit stat_file object name and use full_join

@@ -13,7 +13,7 @@ crop_rain <-
       
       
       # Download trial data
-      trials$stat_file <-
+      trials$station_file <-
          apply(trials, 1, function(LL) {
             stat_sweep <-
                bomrang::sweep_for_stations(as.numeric(c(LL["latitude"], LL["longitude"])))
@@ -29,7 +29,7 @@ crop_rain <-
             stat_file <-
                paste("cache/weather/", statID, ".csv",sep = "", collapse = " ")
             
-            if (file.exists(stat_file)) {
+            if (stat_file %in% paste0("cache/weather/", list.files(here::here("cache/weather/")))) {
                #weather <- read.csv(stat_file, stringsAsFactors = FALSE)
                return(stat_file)
             } else{
@@ -41,27 +41,17 @@ crop_rain <-
          })
 
 
+      input_data <- full_join(input_data,trials, by = c("location_name", "latitude", "longitude"))
       
-      # add a column with the weather station file name 
-      for (i in 1:nrow(trials)) {
-         input_data <- 
-            input_data%>%
-            mutate(stat_file = case_when(location_name == trials[i, "location_name"] &
-                                            latitude == trials[i, "latitude"] &                     
-                                            longitude == trials[i, "longitude"] ~ 
-                                            trials[i, "stat_file"],
-                                         TRUE ~ stat_file
-                                            ),
-                   start = first_day,
-                   end = last_day)
-      }
-      
+      input_data$start <- first_day
+      input_data$end <- last_day
+
       
       # calculate the sum rainfall for the specified time interval
       input_data$sum_rain <-
          apply(input_data, 1, function(x1) {
             weather <-
-               read.csv(file = x1["stat_file"], stringsAsFactors = FALSE)
+               read.csv(file = x1["station_file"], stringsAsFactors = FALSE)
             
             int1 <- interval(start = ymd(x1["start"]), end = ymd(x1["end"]))
       

### 2021-03-10 03_Yield_MetaAnalysis.Rmd
More spellchecking

@@
 
-Inspect a histogram of when first sign occured in the crop
+Inspect a histogram of when first sign occurred in the crop
 ```{r hist_onset}
@@
 
-Inspect a histogram of when first sign occured in the crop
+Inspect a histogram of when first sign occurred in the crop
 ```{r hist_pressure}

### 2021-03-10 03_Yield_MetaAnalysis.Rmd
Correct some grammar

@@
 
-> When, in relation to PM establishes in the crop, should farmers begin spraying mungbean to mitigate yield loss: before PM establishing, immediately after first sign of PM establishing, or after PM has become established in the crop.
+> When, in relation to PM establishment in the crop, should farmers begin spraying mungbean to mitigate yield loss: before PM establishing, immediately after first sign of PM establishing, or after PM has become established in the crop.
 

### 2021-03-10 04_Severity_MetaAnalysis.Rmd
change devtools:: to remotes::
Correct some grammar

@@
 
-> When, in relation to PM establishes in the crop, should farmers begin spraying mungbean to obtain the highest fungicide efficacy for lowering disease severity: before PM establishing,  immediately after first sign of PM establishing, or after PM has become established in the crop.
+> When, in relation to PM establishment in the crop, should farmers begin spraying mungbean to obtain the highest fungicide efficacy for lowering disease severity: before PM establishing,  immediately after first sign of PM establishing, or after PM has become established in the crop.
 

### 2021-03-10 02_Preliminary_analysis.Rmd
remove unused colour codes

@@
                         "; Tebuconazole n:", n_T, sep = "")) +
-   geom_boxplot() +
-   scale_fill_usq() +
-   scale_colour_usq()
+   geom_boxplot()
 ```
@@
                         "; Tebuconazole n:", n_T, sep = "")) +
-   geom_boxplot() +
-   scale_colour_usq()
+   geom_boxplot()
 ```

### 2021-03-10 03_Yield_MetaAnalysis.Rmd
Clarification and cleaning in analysis

@@
    install.packages("pacman")
-pacman::p_load(tidyverse,
+pacman::p_load(
+   tidyverse,
    kableExtra,
@@
    multcomp,
-               flextable)
+   flextable
+)
 
@@
 PM_dat_Y <-
-   read.csv("cache/PM_yield_clean_data.csv", stringsAsFactors = FALSE)
+   read.csv("cache/PM_yield_clean_data.csv", stringsAsFactors = FALSE
+   )
 ```
@@
 ## Spray schedule meta-analysis
+
 ### Spray schedule moderator
@@
    yi = grain_yield.t.ha.,
-   vi,
+   V = vi,
    mods = ~ spray_management,
    method = "ML",
-   random = list(~ spray_management | trial, ~ 1 | id),
+   random = list( ~ spray_management | trial, ~ 1 | id),
    struct = "UN",
@@
 <br>
-<br>  
+
 ******
@@
 A number close to the median should ensure roughly even numbers in each category.
+
 ```{r median onset}
@@
              lubridate::ymd(planting_date)) %>%
-   pull(first_sign_days)%>%
+   pull(first_sign_days) %>%
    median()
 ```
+
 We will choose 42 days as this is the average days to flowering in mungbean. 
-In addition Kelly et. al. [@-Kelly2017a] noted that yield losses are higher in cultivar Berken when disease establishes before flowering.
+In addition, Kelly et. al. [-@Kelly2017a] noted that yield losses are higher in cultivar Berken when disease establishes before flowering.
 
-Now lets define these two new variables, `first_sign_days` and `onset` in the data.
+Now let's define these two new variables, `first_sign_days` and `onset` in the data.
 
@@
              lubridate::ymd(planting_date)) %>%
-   mutate(onset = case_when(first_sign_days <= 42 ~ "early_onset",
-                            first_sign_days > 42 ~ "late_onset"))
+   mutate(onset = case_when(
+      first_sign_days <= 42 ~ "early_onset",
+      first_sign_days > 42 ~ "late_onset"
+   ))
 ```
 
-Inspect a histogram of when first sign occurred in the crop
+Inspect a histogram of when first sign occurred in the crop.
+
 ```{r hist_onset}
@@
    yi = grain_yield.t.ha.,
-   vi,
+   V = vi,
    mods = ~ spray_management * onset,
    method = "ML",
-   random = list(~ spray_management | trial, ~ 1 | id),
+   random = list( ~ spray_management | trial, ~ 1 | id),
    struct = "UN",
@@
 ```{r}
-anova(PM_mv, PM_mv_onset)$pval
+anova(PM_mv, PM_mv_onset)
 ```
-This comparison tells us the meta-analysis including `onset` explained more residual heterogeneity, as shown by the lower QE value.
-However the higher AIC indicates that the model omitting `onset` is a slightly better fit.
-Also the chi-squared test uncertain that the `onset` model is significantly better as indicated by the `pval` `r round(anova(PM_mv, PM_mv_onset)$pval,3)`.
-The higher log likelihood on the `onset` model does intricate there is some merit to this model and that perhaps with more trials to increase statistical power might provide a useful model.
 
@@
 
+This comparison tells us the meta-analysis including `onset` explained more residual heterogeneity, as shown by the lower QE value.
+However the higher AIC indicates that the model omitting `onset` is a slightly better fit.
+Also the chi-squared test is uncertain that the `onset` model is significantly better as indicated by the ANOVA `pval` `r round(anova(PM_mv, PM_mv_onset)$pval,3)`.
+The higher log likelihood on the `onset` model does indicate that there is some merit to this model and that perhaps with more trials to increase statistical power it might be a useful model.  
 <br>  
@@
 <br>
+
 ******
@@
 `high_pressure` and `low_pressure` will be divided by the median disease severity in the no spray control treatments at the end of the season.
+
 ```{r median_pressure}
@@
    filter(fungicide_ai == "control") %>%
-   pull(PM_final_severity)%>%
+   pull(PM_final_severity) %>%
    median()
 ```
-Now lets define these two new variables, `first_sign_days` and `onset` in the data.
+
+Now let's define these two new variables, `low_pressure` and `high_pressure` in the data.
 
@@
 PM_dat_Y <- PM_dat_Y %>%
-   mutate(d_pressure = case_when(PM_final_severity < 8 ~ "low_pressure",
-                            PM_final_severity >= 8 ~ "high_pressure"))
+   mutate(
+      d_pressure = case_when(
+         PM_final_severity < 8 ~ "low_pressure",
+         PM_final_severity >= 8 ~ "high_pressure"
+      )
+   )
 ```
 
-Inspect a histogram of when first sign occurred in the crop
+Inspect a histogram of the final severity values in the crop.
+
 ```{r hist_pressure}
@@
 
-We are adding the `onset` variable as a moderator to test and interaction with the `spray_management` variable as a moderator and an interactive term to the `trial` random variable.
+We are adding the `d_pressure` variable as a moderator to test and interaction with the `spray_management` variable as a moderator and an interactive term to the `trial` random variable.
 
@@
    yi = grain_yield.t.ha.,
-   vi,
+   V = vi,
    mods = ~ spray_management * d_pressure,
    method = "ML",
-   random = list(~ spray_management | trial, ~ 1 | id),
+   random = list( ~ spray_management | trial, ~ 1 | id),
    struct = "UN",
@@
 PM_dat_Y %>%
-   group_by(spray_management, d_pressure)%>%
+   group_by(spray_management, d_pressure) %>%
    summarise(n())
@@
 ### Test variance-covavriance matrix structure
-Let's try the model with an implied simpler variance-covariance matrix "compound symmetry" ("CS") to examine if unstructured matrix is suitable.
+
+Let's try the model with an implied simpler variance-covariance matrix, "compound symmetry" (CS), to examine if unstructured matrix is suitable.
+
 ```{r}
@@
    yi = grain_yield.t.ha.,
-   vi,
+   V = vi,
    mods = ~ spray_management,
    method = "ML",
-   random = list(~ spray_management | trial, ~ 1 | id),
+   random = list( ~ spray_management | trial, ~ 1 | id),
    struct = "CS",
@@
 
- > Therfore the model `PM_mv`, is a best fit.
+ > Therefore the model `PM_mv`, is a best fit.
 
@@
 ## Meta-analysis results summary
+
 ### Moderator estimates table
+
 Let's present the meta-analysis results for the moderator variables in a table of estimates.
@@
 yield_estimates_table <-
-   flextable(results_mv[c(2,5,6,3,4), c(1,3:8,10)]) %>%
+   flextable(results_mv[c(2, 5, 6, 3, 4), c(1, 3:8, 10)]) %>%
    align(j = 3:8, align = "center", part = "all") %>%
@@
    italic(italic = TRUE, part = "header") %>%
-   set_caption("Table 2: Estimated mungbean yield mean difference to the no spray control (intercept) for each spray schedule treatment.
+   set_caption(
+      "Table 2: Estimated mungbean yield mean difference to the no spray control (intercept) for each spray schedule treatment.
 Yield estimates (u) were calculated from a network meta-analysis of data obtained from grey literature reports of 'k' field trials undertaken in Eastern Australia.
-P values indicate statistical significance in comparison to the intercept.") %>%
+P values indicate statistical significance in comparison to the intercept."
+   ) %>%
    autofit() %>%
-   footnote(i = 1,
-            j = c(2:4,6:8),
-            value = as_paragraph(c(
+   footnote(
+      i = 1,
+      j = c(2:4, 6:8),
+      value = as_paragraph(
+         c(
             "number of treatment means categorised to each spray schedule",
@@
             "indicates the significance between each respective spray schedule and the no spray control (intercept)"
-                                   )),
+         )
+      ),
       ref_symbols = letters[1:6],
-            part = "header", inline = TRUE
+      part = "header",
+      inline = TRUE
    )
@@
 
-Save table to a word document to use in manuscript
+Save table to a word document to use in manuscript.
+
 ```{r eval=FALSE, include=FALSE}
@@
    mutate(Treatment = factor(Treatment, levels = rev(
-      c( "Early",
+      c(
+         "Early",
          "Recommended",
@@
 ### Moderator contrasts
+
 Let's investigate the treatment contrasts
@@
 
-These contrasts can be viewed in a plot
+These contrasts can be viewed in a plot.
+
 ```{r plotContrasts_yield}

### 2021-03-10 03_Yield_MetaAnalysis.Rmd
Auto stash before merge of "master" and "origin/master"

@@
 
-Let's get started with the analysis by first finding the best model fit that answers our research question.
+Let's get started with the analysis by first finding the best fitting model which answers our research question.
 
@@
 ```{r Yield_ME_libraries, echo=TRUE,results='hide'}
+# load R packages
 if (!require("pacman"))
@@
 
+The `spray_management` moderator will be evaluated in the first model. 
+Then this model will be tested against other models incorporating, time of disease onset, disease pressure and other variance-covariance matrix structures.
+
 ### Spray schedule moderator
 
-For the first grain yield meta-analysis will be an ARM based model or multi-variate meta-analysis, using the `metafor` package function `rma.mv()` [@Viechtbauer2010].
+This *grain yield* meta-analysis is a multi-variate meta-analysis, using the `metafor` package function `rma.mv()` [@Viechtbauer2010].
 
-We are using the `spray_management` variable as a moderator and an interactive term to the `trial` random variable.
+We are using the `spray_management` variable as a moderator and an interactive random term with the `trial` random variable.
+The variance-covariance matrix is specified as unstructured (UN) to allow correlations between and within trials.
 
@@
 <br>  
+<br>
 
-******
+*****
 
@@
 
-`early` and `late` will be divided by a number close to the median days after sowing when signs of the disease were first observed.
-A number close to the median should ensure roughly even numbers in each category.
-
+`early` and `late` categories should be divided by a number close to the median days after sowing when signs of the disease were first observed to ensure roughly even numbers in each category.
 ```{r median onset}

### 2021-03-11 03_Yield_MetaAnalysis.Rmd
Edits and wordsmithing

@@
       iii) row spacing  
-      iv) fungicide dose
-      v) cultivar
+      iv) cultivar
 
@@
 )
-
-summary(PM_mv)
 ```
@@
 
-Now let's define these two new variables, `first_sign_days` and `onset` in the data.
+Now let's define a continuous variable`first_sign_days` and a categorical variable `onset`.
 
@@
 
-To put this onset number into context for plant maturity, 40 days is approximately when flowering begins in the plant.
+`early_onset` contains `r nrow(PM_dat_Y[PM_dat_Y$onset == "early_onset",])` treatments and,  
+`late_onset` contains `r nrow(PM_dat_Y[PM_dat_Y$onset == "late_onset",])` treatments.
 
@@
 
-```{r}
-summary(PM_mv_onset)
-```
+This comparison tells us the meta-analysis including `onset` explained more residual heterogeneity, as shown by the lower QE value, and has a better fit, indicated by the higher log-likelihood with the additional `onset` parameters.
+However the higher AIC indicates in the model with the additional `onset` parameters does not sufficiently improve the model fit to warrant including these parameters and therefore the 'reduced' model is a better option.
+This inference is also reflected by the the chi-squared test, which is uncertain that the `onset` model is significantly better as indicated by the ANOVA `pval` `r round(anova(PM_mv, PM_mv_onset)$pval,3)`.
 
-This comparison tells us the meta-analysis including `onset` explained more residual heterogeneity, as shown by the lower QE value.
-However the higher AIC indicates that the model omitting `onset` is a slightly better fit.
-Also the chi-squared test is uncertain that the `onset` model is significantly better as indicated by the ANOVA `pval` `r round(anova(PM_mv, PM_mv_onset)$pval,3)`.
-The higher log likelihood on the `onset` model does indicate that there is some merit to this model and that perhaps with more trials to increase statistical power it might be a useful model.  
 <br>  
@@
 
-To determine if the seasonal disease pressure influences the efficacy at which fungicide applications protect yield we will create a categorical variable defining `high_pressure` or `low_pressure`.
+To determine if the seasonal disease pressure influences the efficacy at which fungicide applications protect yield a categorical variable defining `high_pressure` or `low_pressure` can be defined.
 
@@
 
-Now let's define these two new variables, `low_pressure` and `high_pressure` in the data.
+Now to define these two new variables, `low_pressure` and `high_pressure` in the data.
 
@@
 
-We are adding the `d_pressure` variable as a moderator to test and interaction with the `spray_management` variable as a moderator and an interactive term to the `trial` random variable.
+Test `d_pressure` variable addition as a moderator to evaluate it's interaction with the `spray_management` to influence the grain yield effect size.
 
@@
 ```
-This comparison tells us the meta-analysis including `d_pressure` explained more residual heterogeneity, as shown by the lower QE value.
-However the higher AIC indicates that the model omitting `d_pressure` is a slightly better fit.
-Also the chi-squared test marginally significant that the `d_pressure` model is better as indicated by the `pval` 0.0468.
-The higher log likelihood on the `d_pressure` model does indicate there is some merit to this model.  
-It is worth noting that there were no Late plus schedules that experienced low disease pressure. 
-Even though the disease pressure interaction on the moderators was marginally significant (P =0.0468), the division of schedules due to disease pressure (reducing k) makes drawing conclusions risky.
+This comparison tells us the meta-analysis including `d_pressure` explained more residual heterogeneity, as shown by the lower QE value, and has a better fit, indicated by the higher log-likelihood with the additional `d_pressure` parameter.
+However the lower AIC in the 'Full' model indicates that retaining the model including the additional `d_pressure` variables could be a reasonable decision.
+In addition the chi-squared test indicates that the `d_pressure` model is better as indicated by the `pval` 0.0468.
+
+However it is worth noting that there were no Late plus schedules that experienced low disease pressure. 
+Even though the disease pressure interaction on the moderators could be deemed significant (P = 0.0468), the division of schedules due to disease pressure (reducing k) makes drawing conclusions risky.
 More data is needed to explore this possible effect.
@@
 ```{r}
+# show the division of spray schedules by the d_pressure moderator
 PM_dat_Y %>%
@@
 
-Let's try the model with an implied simpler variance-covariance matrix, "compound symmetry" (CS), to examine if unstructured matrix is suitable.
+Test a model with an implied simpler variance-covariance matrix, "compound symmetry" (CS), to examine if unstructured matrix is suitable.
 
@@
 
- > Therefore the model `PM_mv`, is a best fit.
+ > Therefore the model `PM_mv`, is the preffered model with this data.
 
@@
 
-The first table in the `PM_mv` output shows tau^2 (between trial variance) of each moderator random effects and the number of occurrences for each treatment in the analysis.
-This effectively shows the heterogeneity between experiments for these particular treatments.
+```{r PM_mv_summary}
+summary(PM_mv)
+```
 
-The tau^2 also gives us the heterogeneity between trials and indicates `Recommended_plus` showed the highest heterogeneity between experiments followed by `Late_plus`, `Late` then `Recommended`, with `Early` and the no-spray `control` showing the least heterogeneity.
+The first table in the `PM_mv` output shows the tau^2 (between trial variance) for each random effect intercept (spray_management) to trial and the number of occurrences for each treatment in the analysis.
+This effectively shows the heterogeneity between trials for these particular treatments.
+
+This table shows `Recommended_plus` showed the highest heterogeneity between trials followed by `Late_plus`, `Late` then `Recommended`, with `Early` and the no-spray `control` showing the least heterogeneity.
 
@@
 The left part, rho, is the correlation of variation between the specified treatments.
-All comparisons were acceptable except for a comparison between `Early` and `Late_plus`, `0.000` rho.
-`Early` and `Late_plus` treatments never occurred within the same trial, which is indicated by the right side of the table (hence the warning).
+All comparisons were acceptable except for a comparison between `Early` and `Late_plus`, indicating `0.000` rho.
+`Early` and `Late_plus` treatments never occurred within the same trial, which is indicated by the right side of the table (hence earlier warnings). 
+This is not a concern for this type of network meta-analysis because the differences between these treatments can be inferred by their differences with other treatments [@Madden2016].
 
@@
 
-Save table to a word document to use in manuscript.
-
 ```{r eval=FALSE, include=FALSE}
@@
 
-Let's view these comparisons in a plot.
+### Moderator estimates plot
 
-### Moderator estimates plot
+View the moderator comparisons in a plot.
 
@@
    coord_flip() +
-   #ggtitle("Mean spray schedule effect sizes\nand 95% confidence intervals")+
+   labs(caption = "Bars indicate 95% confidence intervals")+
    ylab(expression(paste(
@@
 
-Let's investigate the treatment contrasts
+Calculate treatment contrasts
 
@@
 
-Let's inspect the profile plots to ensure the model is not over-fitted.
+An inspection of the profile plots to ensure the model is not over-fitted can be undertaken.
 We expect to see the estimate align with the peak of the curve.
 Also that the shape of the line is a curve.
-Caution! this will take some time to run.
+As these plots take a long time to generate they will not be evaluated.
 
-```{r profile_plots, eval=FALSE, message=FALSE, include=FALSE, results="hide"}
+```{r profile_plots, eval=FALSE, echo=TRUE, results="hide"}
 profile(PM_mv, tau2 = 1)
@@
 
-We can use the `netmeta` package to give a graphical representation of the pairwise comparisons.
+The `netmeta` package can provide a graphical representation of the pairwise comparisons.
 
-Let's analyse the data again using a different statistical approach to see if our outcome with the `metafor` package was robust.
-The `netmeta` package uses a frequentist approach to the analysis and focuses on the pairwise comparisons between treatments.
+The `netmeta` package uses a frequentist approach focusing on the pairwise comparisons between treatments. 
+These results can be used to evaluate if our outcome with the `metafor` package was robust.
 
@@
 ### netmeta estimates plot
-Now let's visualise this as a forest plot.
+Visualise netmeta results as a forest plot.
 

### 2021-03-11 03_Yield_MetaAnalysis.Rmd
output contrasts results to a flextable

@@
 
-   - *Grain yield* is our response variable (t / ha)
+   - *Grain yield* the response variable (t / ha)
 
@@
    group_by(spray_management, d_pressure) %>%
-   summarise(n())
+   summarise(n()) %>%
+   flextable()
 ```
@@
    )), test = adjusted("none")))
-contrast_Ssum
+contrast_Ssum %>%
+   flextable()
 

### 2021-03-11 04_Severity_MetaAnalysis.Rmd
Wordsmithing and output contrasts to a flextable

@@
 
-```{r MEsummary_Libraries2, message=FALSE, include=FALSE}
+An additional question to our main aim: does spray schedule have a similar effect on disease severity?
+
+This model will be similar to the grain yield meta-analysis and use the main variables:
+
+   - *Powdery mildew severity* the response variable (1-9 scale)
+
+   - *Trial*, which resolves combinations of categorical random variables: 
+      i) year  
+      ii) location  
+      iii) row spacing  
+      iv) cultivar
+
+   - *spray_management* a moderator to evaluate the difference in effect size attributed to fungicide application timing.
+
+   - *id* random variable indicating each treatment is independent
+
+<br>
+
+Load libraries and data  
+```{r MEsummary_Libraries2, echo=TRUE,results='hide'}
 if (!require("pacman"))
@@
 
-Inspect for a normal distribution of disease severity
-```{r sev_hist}
-hist(PM_dat_D$PM_final_severity)
-```
-
-Let's get started with the analysis by first finding the best model fit that answers our research question.
-
-> When, in relation to PM establishment in the crop, should farmers begin spraying mungbean to obtain the highest fungicide efficacy for lowering disease severity: before PM establishing,  immediately after first sign of PM establishing, or after PM has become established in the crop.
-
-A secondary question to this aim is: does a second spray increase the efficacy?
-
-To do this, in our model:
-
-   - Powdery mildew severity 1-9 scale
-
-   - Trial, which resolves combinations of categorical variables: year, location, row spacing, fungicide dose and cultivar; is set as a random intercept
+<br>  
+<br>
 
@@
 
-   - We will investigate the effect size of our treatment - spray management,
+Inspect disease severity for a normality.
+```{r sev_hist}
+hist(PM_dat_D$PM_final_severity)
+```
 
@@
 <br>
-******
+
+*****
 
@@
 
-All spray schedules were effective at lowering the disease severity at the end of the season
+All spray schedules were effective at lowering the disease severity at the end of the season.
+`Recommended_plus` reduced powdery mildew incidence the most.
 
@@
 ### Disease severity moderator contrasts
+
+Calculate the treatment contrasts
 
@@
 
-contrast_Ssum
+contrast_Ssum %>%
+   flextable()
 ```
@@
 ```
+
+`Recommended_plus` limited disease severity significantly better than any other spray treatment. 
+`Late_plus` limited disease severity significantly better than a single `Late` application. 
+This indicates that two spray treatments were significantly better than a single application, but the timing of the fungicide application was more critical.
 

### 2021-03-11 R/simple_summary.R
round the output of data.frame contents

@@ -2,6 +2,7 @@
 # it requires the summary of a glht test on a model object
 
 source(here::here("R/p_star.R"))
+source(here::here("R/reportP.R"))
 
 simple_summary <-
    function(sum_meta){
@@ -17,12 +18,13 @@ simple_summary <-
          return(new_name)
       }
       
-      data.frame(contrast = rename_index(index_name = ind_names, char_name = names1),
-                 coefficients = sum_meta[["test"]]$coefficients,
-                 StdErr = sum_meta[["test"]]$sigma,
-                 'Zvalue' = sum_meta[["test"]]$tstat,
-                 pvals = sum_meta[["test"]]$pvalues,
-                 sig = p_star(sum_meta[["test"]]$pvalues)
-                                         )
+      data.frame(
+         contrast = rename_index(index_name = ind_names, char_name = names1),
+         coefficients = round(sum_meta[["test"]]$coefficients, 4),
+         StdErr = round(sum_meta[["test"]]$sigma,4),
+         'Zvalue' = round(sum_meta[["test"]]$tstat,4),
+         pvals = reportP(sum_meta[["test"]]$pvalues, AsNumeric = TRUE, P_prefix = FALSE),
+         sig = p_star(sum_meta[["test"]]$pvalues)
+      )
          
    }

### 2021-03-11 03_Yield_MetaAnalysis.Rmd
Autofit flextables

@@
 contrast_Ssum %>%
-   flextable()
+   flextable()%>%
+   autofit()
 

### 2021-03-12 index.Rmd
Fix incomplete final line
change book style

@@
 site: bookdown::bookdown_site
-output: bookdown::gitbook
 documentclass: book

### 2021-03-14 01_TrialsForInclusionInAnalysis.Rmd
r -> R
remove usq.theme

@@
 
-### Load required r packages
+### Load required R packages
 
@@
 
-if (!require("theme.usq"))
-   remotes::install_github("adamhsparks/theme.usq")
-
-library(theme.usq)
-theme_set(theme_usq())
 ```
@@
    geom_col() +
-   scale_fill_usq() +
    ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
-   scale_colour_usq() +
    coord_flip()

### 2021-03-14 02_Preliminary_analysis.Rmd
remove usq.theme

@@
 
-if (!require("theme.usq"))
-   remotes::install_github("adamhsparks/theme.usq")
-library(theme.usq)
-theme_set(theme_usq()
-)
 load("cache/ImportDataAndSelectTrials01.Rdata")
@@
    ggtitle(label = "Total number of treatments for each respective tebuconazole\nor propiconazole dose") +
-   geom_bar() +
-   scale_fill_usq() +
-   scale_colour_usq()
+   geom_bar() 
 ```
@@
         caption = "Facets indicate the number of applications") +
-   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
+   geom_boxplot(fill = "grey", alpha = 0.5) +
    ylab("Grain yield t / ha") +
@@
    geom_col() +
-   scale_fill_usq(name = "Fungicide AI")
+   scale_fill_discrete(name = "Fungicide AI")
 ```
@@
             position = "dodge") +
-   scale_fill_usq(name = "Fungicide AI")
+   scale_fill_discrete(name = "Fungicide AI")
 ```
@@
    ggplot(aes(y = PM_final_severity, x = factor(row_spacing))) +
-   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
+   geom_boxplot(alpha = 0.5) +
    ylab("Final severity rating") +
@@
    ggplot(aes(y = PM_final_severity, x = factor(row_spacing))) +
-   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
+   geom_boxplot(alpha = 0.5) +
    facet_grid(cols = vars(location)) +
@@
    xlab("Row spacing (m)") +
-   ylab("Grain yield (t/ha)") +
-   scale_colour_usq()
+   ylab("Grain yield (t/ha)")+
+   theme_minimal()
 ```

### 2021-03-14 03_Yield_MetaAnalysis.Rmd
remove usq.theme

@@
 
-if (!require("theme.usq"))
-   remotes::install_github("adamhsparks/theme.usq")
-library(theme.usq)
-theme_set(theme_usq())
 source(here("R/reportP.R"))
@@
 
-```{r Yield_Metafor-analysis}
+```{r Yield_Metafor-analysis, cache=TRUE}
 PM_mv <- rma.mv(
@@
 
-```{r define_onset}
+```{r define_onset, cache=TRUE}
 PM_dat_Y <- PM_dat_Y %>%
@@
 
-```{r onset_Metafor-analysis}
+```{r onset_Metafor-analysis, cache=TRUE}
 PM_mv_onset <- rma.mv(
@@
 
-```{r Dpressure_Metafor-analysis}
+```{r Dpressure_Metafor-analysis, cache=TRUE}
 PM_mv_dp <- rma.mv(
@@
       yintercept = seq(-0.05, 0.3, by = 0.05),
-      color = usq_cols("usq charcoal"),
       linetype = 3
@@
    plastic = FALSE,
-   col = usq_cols("support orange"),
    thickness =  "number.of.studies",
    points = FALSE,
-   col.points = usq_cols("usq charcoal"),
    cex.points = 1,
@@
    col.number.of.studies = "black",
-   bg.number.of.studies = usq_cols("support orange"),
    multiarm = FALSE,
-   col.multiarm = usq_cols("support turquiose"),
    pos.number.of.studies = 0.4

### 2021-03-14 04_Severity_MetaAnalysis.Rmd
Autofit flextables
remove usq.theme

@@
 
-```{r Metafor-Sev-analysis}
+```{r Metafor-Sev-analysis, cache=TRUE}
 PMsev_mv <- rma.mv(
@@
 contrast_Ssum %>%
-   flextable()
+   flextable()%>%
+   autofit()
 ```

### 2021-03-15 docs/vignette/191115_PMMB_DataWrangling_PM.Rmd
rerender

--- 2020-08-10 02_Import_and_FormatData.Rmd
@@
-# Import and Format Data
-## Non-wrangled trials
-
-Data from the three follow trials were input manually from either PDF or word files.  
-   - Gatton 2012  
-   - Kingaroy 2012  
-   - Emerald 2016
+# Data wrangling
+This file is not complete and there are a number of things that need checking
+   - Mean squares are only calculated for the triazoles and controls
+   - If the years for each trial are input correctly
+   - If the disease and yield errors are calculated and that they are shuffled correctly into the data frame
+   - AUDPC needs to be checked for starting dates and if trials have been omitted
+   - Check that what is generated from this file matches the main file and update
+   - write.csv should have row.names = FALSE
 
@@
    # This function formats a dataframe to have the same column order as a template data.frame
-   # If columns are missing from the new_DataFrame that are in the template_DataFrame, it creates them 
+   # If colums are missing from the new_DataFrame that are in the template_DataFrame, it creates them 
    # with NA values. 
@@
    # of the new_DataFrame
-   # Using this function assists in joining the two data.frames together so columns are in the same order
+   # Using this function assists in joining the two data.frames together so colums are in the same order
 
@@
    new_DataFrame <-
-      new_DataFrame[, c(cnames2, cnames1[is.na(x1)])]  # adding columns to new_DataFrame not in template_DataFrame  # arranges column names to new_DataFrame not in template_DataFrame
+      new_DataFrame[, c(cnames2, cnames1[is.na(x1)])]  # adding columns to new_DataFrame not in template_DataFrame  # aranges column names to new_DataFrame not in template_DataFrame
 
@@
 source(here("R/copy_class.R"))
-source(here("R/replace_data.R"))
+source(here("R/data_mesh.R"))
 ```
@@
 #### AUDPC curve
-```{r Herm_audpc, warning=FALSE}
+```{r Herm_audpc}
 
@@
 #### AUDPC curve
-```{r King11_AUDPC, warning=FALSE}
+```{r King11_AUDPC}
 library(ggplot2)
@@
 Disease data for Kingaroy 2016 only exists as a mean of treatments within the `2016 Mungbean PM trials summary.xlsx` file.  
-```{r King16_dataimport}
+```{r Herm16_dataimport}
 # Yield data from 2016 Hermitage trial with final disease severity
@@
    )[, 1:43]
+
+#dim(Fogerty_17)   # 162 rows , 43 Columns
 
@@
 
-# I have comment out this code because it does not replace the control plots properly as there is nothing to separate them from each other
+# I have comment out this code because it does not replace the control plots properly
 # insert new calculations into data
-#PM_MB_means <-   
-   # replace_data(template_data = PM_MB_means,
+# PM_MB_means <-   replace_data(template_data = PM_MB_means, 
 #                             new_data = Fogerty_17_m, 
 #                             new_data_column = "AUDPC_m", 
-   #                          ignore_columns = c(5:8,10:16,29:46),
-   #                          subset_factor = "mung1617/02")
+#                             ignore_columns = c(5:8,10:16,29:46))
+#
 
@@
              case_when(Fung.Trt <= 3 ~ 2,
-                       Fung.Trt == 4 ~ 0,
                        TRUE ~ NA_real_))
@@
 
-# For some weird reason standard deviations are coming back NA in the code above
+# For some weird reason standard deviations are comming back NA in the code above
 Well_18_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
@@
                             new_data = Well_18_m, 
-                            new_data_column = c("total_fungicide","AUDPC_m", "AUDPC_sd"),
+                            new_data_column = c("AUDPC_m", "AUDPC_sd"),
                             filter_cols = c("trial_ref","year","location","n_treatment"))
+
+# check the same dimensions
+dim(Well_18_m) ==
+dim(PM_MB_means[PM_MB_means$trial_ref == "mung1718/01",])
+
+   # Not sure why replace_data will not replcae the following columns
+   PM_MB_means[c(324: 347),
+               c("AUDPS_m", "AUDPS_sd","Inc_Ms")] #<-
+      Well_18_m[,c("AUDPS_m", "AUDPS_sd","Inc_Ms")]
 
@@
 
-```{r Save_PM_MB_means, echo=TRUE}
+```{r Save_PM_MB_means, eval=FALSE, include=FALSE}
 

### 2021-03-16 01_TrialsForInclusionInAnalysis.Rmd
correct NGA name

@@
 
-Data were collected from a number of researchers from the Department of Agriculture and Fisheries (DAF), the University of Southern Queensland (USQ) and the National Growers Association (NGA).
+Data were collected from a number of researchers from the Department of Agriculture and Fisheries (DAF), the University of Southern Queensland (USQ) and the Northern Growers Alliance (NGA).
 We would like to acknowledge in particular Professor Malcolm Riley's and Dr.

### 2021-03-16 index.Rmd
Reknit with new theme
Add acknowledgments

@@
 
-For completeness We also evaluated the efficacy of spray schedules on disease severity in the field.
+For completeness, we also evaluated the efficacy of spray schedules on disease severity in the field.
 
@@
 Preprint at .........
+
+## Acknowledgments  
+This meta-analysis was carried out with the funding assistance of the Grains Research and Development Corporation in Australia.
+Raw data for this work were contributed by the University of Southern Queensland, Queensland Department of Agriculture, Fisheries and Forestry (DAF), the Northern Grower Alliance.
+Additional thanks to Malcolm Riley, Sue Thompson and Lawrie Price.

### 2021-03-16 index.Rmd
update title
rebuild book

@@
 ---
-title: "A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean"
+title: "A meta-analysis of fungicide effects on mungbean powdery mildew"
 author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
@@
 This meta-analysis was carried out with the funding assistance of the Grains Research and Development Corporation in Australia.
-Raw data for this work were contributed by the University of Southern Queensland, Queensland Department of Agriculture, Fisheries and Forestry (DAF), the Northern Grower Alliance.
+Raw data for this work were contributed by the University of Southern Queensland, Queensland Department of Agriculture, Fisheries and Forestry (DAF), and the Northern Grower Alliance.
 Additional thanks to Malcolm Riley, Sue Thompson and Lawrie Price.

### 2021-03-16 livro.Rmd
rebuild book

---
title: "A meta-analysis of fungicide effects on mungbean powdery mildew"
author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
date: "`r format(Sys.time(), '%d %B, %Y')`"
site: bookdown::bookdown_site
documentclass: book
bibliography: "Mungbean.bib"
biblio-style: apalike
link-citations: yes
github-repo: OpenPlantPathology/Mungbean_PM
description: "A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew."
---
# About
## Background  
A common practice for managing powdery mildew in mungbean is to couple fungicide with an insecticide spray early in the development of the crop, usually before the disease is detected. This is despite the current recommendations that the best yield protection is achieved when the fungicide is first applied at the first sign of the disease. These recommendations were based on individual studies, many of which lacked sufficient power to draw significant conclusions. We undertook a meta-analysis to determine, when should the first fungicide spray be applied on mungbean to maximise yield protection.

## Compendium contents
This research compendium details importing and summarising the raw data, application of the selection criteria, defining moderator variables for fungicide spray timing, and the statistical analysis methods for this meta-analysis of fungicide efficacy trials for controlling powdery mildew in mungbean.
The meta-analysis's main aim is to determine:

> When is the optimum time to spray fungicide to limit the effect of powdery mildew on mungbean yields?

For completeness, we also evaluated the efficacy of spray schedules on disease severity in the field.

## Main chapters
This compendium is broken down into four sections:

   1. [Details of the experiments, and application of inclusion criteria in the analysis][Trials considered for inclusion in meta-analysis]  
   2. [Preliminary data exploration][Preliminary Analysis]  
   *including a summary of the cleaned trial data and the treatments*
   3. [Grain yield meta-analysis]  
   4. [Powdery mildew severity Meta-analysis]

These sections detail the methods and process we undertook during this meta-analysis.

## Links to manuscript
The manuscript publishing the results presented in this compendium can be found at ....

Preprint at .........

## Acknowledgments  
This meta-analysis was carried out with the funding assistance of the Grains Research and Development Corporation in Australia. Raw data for this work were contributed by the University of Southern Queensland, Queensland Department of Agriculture, Fisheries and Forestry (DAF), and the Northern Grower Alliance. Additional thanks to Malcolm Riley, Sue Thompson and Lawrie Price.

<!--chapter:end:index.Rmd-->

# Trials considered for inclusion in meta-analysis

Trials testing fungicide efficacy on powdery mildew in mungbean in the Grains Research and Development Corporation (GRDC) northern grains region were sourced for a meta-analysis.

Data were collected from a number of researchers from the Department of Agriculture and Fisheries (DAF), the University of Southern Queensland (USQ) and the Northern Growers Alliance (NGA).
We would like to acknowledge in particular Professor Malcolm Riley's and Dr. Sue Thompson's effort in establishing and coordinating early field trials between 2010 and 2014 and GRDC for funding many of the trials which were included in this meta-analysis.

<br>

### Load required R packages

```{r MEsummary_Libraries, echo=TRUE, results='hide'}
if (!require("pacman"))
   install.packages("pacman")

pacman::p_load(tidyverse, kableExtra, leaflet, htmltools, lubridate, here)

```

<br>  
<br>

## Criteria for inclusion in meta-analysis

   1. A field trial testing the efficacy of fungicide on powdery mildew afflicted mungbean plants in eastern Australia.  
   2. Trial data needed to include:  
      i) Fungicide active ingredients.  
      ii) A demethylase inhibitor (DMI) fungicide.  
      iii) The date at which powdery mildew first appeared in the trial.  
      iv) Disease severity at the end of the growing seasons.  
      v) Fungicide application dates.  
      vi) Fungicide dose.  
      vii) Crop yield.  
      viii) Treatment means and accompanying variance.

<br>  
<br>

## Import data  
**Import data from trials which the raw data was available**  
```{r import_dataRAW}
PM_MB_raw <-
   rbind(
      read.csv(
         here("cache/2010 PMmung Hermitage means.csv"),
         stringsAsFactors = FALSE
      ),
      read.csv(here("cache/2011 PMmung Herm means.csv"), stringsAsFactors = FALSE),
      read.csv(
         here("cache/2011 PMmung Kingaroy means.csv"),
         stringsAsFactors = FALSE
      ),
      read.csv(here("cache/AM1305_Goolhi_means.csv"), stringsAsFactors = FALSE),
      read.csv(
         here("cache/AM1304-MarysMount_means.csv"),
         stringsAsFactors = FALSE
      ),
      read.csv(
         here("cache/AM1303-Premer-Disease_means.csv"),
         stringsAsFactors = FALSE
      ),
      read.csv(
         here("cache/BB1305_Millmerran_means.csv"),
         stringsAsFactors = FALSE
      ),
      read.csv(here("cache/Herm_16_means.csv"), stringsAsFactors = FALSE),
      read.csv(here("cache/King_16_means.csv"), stringsAsFactors = FALSE),
      read.csv(here("cache/Fogerty_17_mean.csv"), stringsAsFactors = FALSE),
      read.csv(here("cache/Hermitage_17_mean.csv"), stringsAsFactors = FALSE),
      read.csv(here("cache/Wellcamp_18_mean.csv"), stringsAsFactors = FALSE),
      read.csv(here("cache/Hermitage_19_mean.csv"), stringsAsFactors = FALSE)
   )
write.csv(
   PM_MB_raw,
   file = here("cache/PM_Mungbean_SummaryOfTrialsWithRawData"),
   row.names = FALSE
)
```

<br>

Import dataset of manual entries  
**Import dataset which were manually entered from trial reports**  
```{r import_dataMan}
PM_MB_man <-
   read.csv(here("cache/PM_Mungbean_DataManuallyEntered.csv"),
            stringsAsFactors = FALSE)
```

Bind raw and transcribed datasets.  
```{r bind_data}
PM_MB_dat <-
   rbind(PM_MB_raw,
         PM_MB_man)
```

<br>  
<br>

## Summary of all trials

```{r data_summary}
PM_MB_dat %>%
   arrange(year, location) %>%
   group_by(trial_ref) %>%
   summarise(
      Year = unique(year),
      Location = unique(location),
      `Replicates per treatment` = if (all(replicates[1] == replicates)) {
         as.character(replicates[1])
      } else{
         as.character(paste(min(replicates), "-", max(replicates)))
      },
      `Trial design` = unique(trial_design),
      `Planting date` = unique(planting_date),
      `First sign of disease` = unique(first_sign_disease),
      `Fungicide treatments` = length(n_treatment),
   ) %>%
   arrange(Year) %>%
   kable(
      caption = "Description of Experiments",
      align = "c",
      col.names = c(
         "Unique Trial\nReference",
         "Year",
         "Location",
         "Replicates\nper treatments",
         "Trial design",
         "Planting date",
         "First sign\nof disease",
         "Fungicide\n treatments"
      )
   )  %>%
   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
   column_spec(c(3, 5:6), width = "3cm") %>%
   scroll_box(height = "500px") 
```

<br>

### Experiment locations

Trial locations occurring in the GRDC Northern Grains Region.

```{r Experiment_locations, echo=FALSE}
experiment_sites <- data.frame(
   location = c(
      "Hermitage Research Station",
      "Red Vale & Kingaroy Research Station",
      "Gatton",
      "Emerald Agricultural College",
      "Bongeen 1 & 2",
      "NGA - Premer",
      "NGA - Millmerran",
      "NGA - Marys Mount",
      "NGA - Goolhi",
      "Missen Flats",
      "Wellcamp"
   ),
   lat = c(
      -28.215 ,
      -26.58,
      -27.56,
      -23.54,
      -27.51666,
      -31.43449,
      -27.923674,
      -31.0142,
      -31.00246,
      -27.905313,
      -27.564277
   ),
   lon = c(
      152.1003,
      151.83,
      152.32,
      148.19,
      151.450,
      150.0052,
      151.242706,
      150.05018,
      149.82507,
      151.9772,
      151.867879
   )
)

write.csv(experiment_sites,
          "cache/Mungbean_experiment_sites.csv",
          row.names = FALSE)

leaflet(experiment_sites) %>%
   addProviderTiles("Esri.WorldTopoMap") %>%
   setView(lat = -27.31,
           lng = 150.456,
           zoom = 5) %>%
   addMarkers(
      lng = ~ lon,
      lat = ~ lat,
      popup = ~ htmlEscape(location)
   )
```

<br>
<br>
<br>

## Subset data to selection criteria

Let's apply the selection criteria our dataset.  
All trials identified for this meta-analysis reported:

* fungicide active ingredient,
* dose,
* first sign of disease.

Therefore no trials need to be removed to satisfy these criteria.

<br>

**Retain trials including: Yield**  
Three trials omitted due to not reporting yields  
```{r TrialWithoutYield}
PM_MB_dat %>%
   filter(is.na(grain_yield.t.ha.)) %>%
   distinct(trial_ref, year, location)

PM_MB_dat <- PM_MB_dat %>%
   filter(!is.na(grain_yield.t.ha.))
```

<br>

**Retain trials including: Disease severity**  
One more was trial removed as it did not report disease severity.  
```{r TrialsWithotDisease}
PM_MB_dat %>%
   filter(is.na(PM_final_severity)) %>%
   distinct(trial_ref, year, location)

PM_MB_dat <- PM_MB_dat %>%
   filter(!is.na(PM_final_severity))
```

<br>
<br>
<br>

**Retain trials including: fungicide application dates**  
No trials from our subset need to be removed for not reporting fungicide application dates.  
```{r FungicideApplicationDates}
PM_MB_dat %>%
   group_by(trial_ref) %>%
   summarise(No_Record_Of_Fungicide_Application_Dates = all(is.na(fungicide_application_1)),
             .groups = 'drop') %>%
   filter(No_Record_Of_Fungicide_Application_Dates)
```

<br>
<br>
<br>

**Retain trials including: fungicide dose**  
No trials from our subset need to be removed for not reporting fungicide dose.  
```{r FungicideDoseTrials}
PM_MB_dat %>%
   group_by(trial_ref) %>%
   summarise(No_Record_Of_Fungicide_Dose = all(is.na(dose_ai.ha)),
             .groups = 'drop') %>%
   filter(No_Record_Of_Fungicide_Dose)
```

<br>
<br>
<br>

**Exclude fungicides tested in too few trials**  
The meta-analysis should be focused on fungicides with the same mode of action.
Fungicides from the best represented group will be retained.
```{r Fungicides}
PM_MB_dat %>%
   group_by(fungicide_ai, trial_ref) %>%
   summarise() %>%
   count(sort = TRUE) %>%
   rename(Trials = n) %>%
   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
   xlab("Fungicide active ingredient") +
   ylab("N Trials") +
   geom_col() +
   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
   coord_flip()
```

The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in the highest frequencies.
The DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.

Amistar Xtra and Custodia both contain strobilurin and triazole, however, because they contain differing dose ratios (inverted) pooling may not be appropriate therefore they will be removed.

<br>
<br>
<br>

**Retain only fungicides with DMI action**
```{r filterDMI_trials}
DMI_Trials <-
   PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   distinct(trial_ref) %>%
   pull()

PM_MB_dat <-
   PM_MB_dat[PM_MB_dat$trial_ref %in% DMI_Trials, ]
```

Now remove any non-DMI treatments or controls  
```{r KeepOnlyDMI}
PM_MB_dat <-
   PM_MB_dat %>%
   filter(
      fungicide_ai == "control" |
         fungicide_ai == "tebuconazole" |
         fungicide_ai == "propiconazole"
   )
```

<br>
<br>
<br>

### Classify dataset variables

Importantly, the class of each variable in the data should be defined, retaining only the variables relevant to the analysis.

```{r classifyData}
source("R/classify_PM_data.R") # use a custom code

# classify dataset with Trials in both 
PM_MB_dat <-
   classify_PM_data(PM_MB_dat)

```

<br>  
<br>

## Defining spray schedule variable

First are going to calculate the time between the first sign of disease and the fungicide applications.

```{r clustered_fungicide_applications}
# collective data
PM_MB_dat %<>%
   mutate(fungicide_timing_1 = fungicide_application_1 - first_sign_disease) %>%
   mutate(fungicide_timing_2 = fungicide_application_2 - fungicide_application_1) %>%
   mutate(fungicide_timing_3 = fungicide_application_3 - fungicide_application_2)

```

To ensure sufficient number of replicates, treatments were binned by the first fungicide application date into three categorical variables relating to when the first fungicide application was made, relative to the first sign of disease.

<br>

These categorical variables are named:  
   - **Early**: First fungicide application was prior to first sign of disease.  
   - **Recommended**: First fungicide application was applied on the day powdery mildew was observed, or within three days of first sign.  
   - **Late**: First fungicide application was four or more days after first sign of disease being observed.

<br>

The number of follow-up sprays need also be defined.

```{r TreatmentTable}
data.frame(
   TreatmentName = c(
      "Early",
      "Recommended",
      "Late",
      "EarlyPlus",
      "RecommendedPlus",
      "LatePlus"
   ),
   n_sprays = rep(c("Single", "Two - Three"), each = 3),
   DaysRelativeToFirstSign = c(
      "Prior to first sign of Powdery Mildew",
      "1 - 3 days after first sign of Powdery Mildew",
      "7 - 8 days after first sign of Powdery Mildew"
   )
) %>%
   kable()
```

Simplify the clusters for the data-set
```{r simple_Y_clusters}
PM_MB_dat <- PM_MB_dat %>%
   mutate(
      spray_management = case_when(
         fungicide_timing_1 < 0 &
            is.na(fungicide_application_2) &
            is.na(fungicide_application_3) ~ "Early",
         fungicide_timing_1 >= 0 &
            fungicide_timing_1 < 4 &
            is.na(fungicide_application_2) &
            is.na(fungicide_application_3) ~ "Recommended",
         fungicide_timing_1 >= 4 &
            is.na(fungicide_application_2) &
            is.na(fungicide_application_3) ~ "Late",
         fungicide_timing_1 < 0 &
            !is.na(fungicide_application_2) ~ "Early_plus",
         fungicide_timing_1 >= 0 &
            fungicide_timing_1 < 4 &
            !is.na(fungicide_application_2) ~ "Recommended_plus",
         fungicide_timing_1 >= 4 &
            !is.na(fungicide_application_2) ~ "Late_plus",
         TRUE ~ "Other"
      )
   )

PM_MB_dat[PM_MB_dat$fungicide_ai == "control",
          c(
             "fungicide_timing_1",
             "fungicide_timing_2",
             "fungicide_timing_3",
             "spray_management"
          )] <- "control"
```

Now to view the number break-down of the `spray_management` treatments in the *yield* and *disease severity* data-sets

```{r tableSprayManagement_Y}
table(PM_MB_dat$spray_management)
```

'Early_plus' treatments are few in number, these treatments will have too few comparisons with other treatments in the meta-analysis to provide accurate results. Therefore we will remove 'Early_plus' from the analysis.

```{r simpler_clusters_remove}
PM_MB_dat <-
   PM_MB_dat %>%
   filter(spray_management != "Early_plus") %>%
   select(-c(fungicide_timing_1, # remove the following columns which no longer have use
             fungicide_timing_2,
             fungicide_timing_3,
             fungicide_application_1,
             fungicide_application_2,
             fungicide_application_3,
             fungicide_application_4,
             fungicide_application_5,
             fungicide_application_6,
             fungicide_application_7,
             ))

```

<br>  
<br>  
<br>

## Identify variance
We need variance accompanying the mean observations for each treatment to successfully undertake a meta-analysis.
Lets investigate which of the included trials included variance for both response variables of interest, yield and disease severity.

```{r Trials_For_Inclusion}
PM_MB_dat %>%
   mutate(MA_analysis = case_when(
      is.na(yield_error & disease_error) == FALSE ~ "Yield and Disease",
      is.na(yield_error) == FALSE & 
         is.na(disease_error) ~ "Yield",
      is.na(disease_error) == FALSE & 
         is.na(yield_error) ~ "Disease",
      TRUE ~ "Nil"
   )) %>%
   distinct(trial_ref, location, year, MA_analysis) %>%
   arrange(year) %>%
   kable()
```

<br>

Remove one trial in Emerald which did not report disease variance or yield variance.
```{r remove_nil_var}
# Remove trials without variance for both Disease and yield for data_set `PM_MB_dat
PM_MB_dat <- 
   PM_MB_dat %>%
   mutate(contains_var = case_when(
      is.na(yield_error) &
         is.na(disease_error) ~ NA_character_,
      TRUE ~ trial_ref)) %>%
   filter(trial_ref %in% contains_var) %>%
   select(-contains_var) 
```

<br>

Following an inspection of the yield and disease variance we determined imputation was not suitable and therefore we must exclude trials that did not report variance.
For each analysis, yield and disease severity a separate data-set will be created, including only trials that report variance for the respective response variable

One trial will be removed from the yield data set `PM_dat_Y` for not reporting yield variance.  
```{r TrialsWithVariance}
PM_MB_dat %>%
   mutate(No_Var = is.na(yield_error)) %>%
   filter(No_Var == TRUE) %>%
   distinct(trial_ref, year, location)

PM_dat_Y <- 
   PM_MB_dat %>%
   mutate(contains_var = case_when(
      is.na(yield_error) ~ NA_character_,
      TRUE ~ trial_ref)) %>%
   filter(trial_ref %in% contains_var) %>%
   select(-contains_var)
```

<br>

Two more trials will be removed for our disease severity data set `PM_dat_D` for not reporting yield variance.
```{r TrialsWithVariance_D}
PM_MB_dat %>%
   mutate(No_Var = is.na(disease_error)) %>%
   filter(No_Var == TRUE) %>%
   distinct(trial_ref, year, location)

PM_dat_D <- 
   PM_MB_dat %>%
   mutate(contains_var = case_when(
      is.na(disease_error) ~ NA_character_,
      TRUE ~ trial_ref)) %>%
   filter(trial_ref %in% contains_var) %>%
   select(-contains_var)
```

<br>  
<br>  
<br>

## Standardise Variance

All the variance types need to be converted to sample variance. 
First we will start by standardising yield variance according to the method reported by [Ngugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).

### Yield variance standardisation
```{r StandardiseYieldVariance}
PM_dat_Y <-
   PM_dat_Y %>%
   mutate(
      vi =
         case_when(
            Y_error_type == "stdev" ~ yield_error ^ 2,
            Y_error_type == "lsd (P=0.05)" ~
               (replicates * ((yield_error / 1.96) ^ 2) / 2)
         ),
      id = row_number(),
      spray_management = fct_relevel(spray_management, sort)
   ) %>%
   select(-c(yield_error,
             Y_error_type))

```

### Disease severity variance standardisation
```{r StandardiseSeverityVariance}
PM_dat_D <-
   PM_dat_D %>%
   mutate(
      vi =
         case_when(
            D_error_type == "stdev" ~ disease_error ^ 2,
            D_error_type == "lsd (P=0.05)" ~
               (replicates * ((disease_error / 1.96) ^ 2) / 2)
         ),
      id = row_number(),
      spray_management = fct_relevel(spray_management, sort)
   ) %>%
   select(-c(disease_error,
             D_error_type))

```

<br>

#### Save the cleaned data
```{r saveData01}
write.csv(PM_dat_Y, file = "cache/PM_yield_clean_data.csv", row.names = FALSE)
write.csv(PM_dat_D, file = "cache/PM_disease_clean_data.csv", row.names = FALSE)
write.csv(PM_MB_dat, file = "cache/PM_MB_clean_data.csv", row.names = FALSE)
save(PM_MB_dat, PM_dat_D, PM_dat_Y, file = here("cache/ImportDataAndSelectTrials01.Rdata"))
```

<!--chapter:end:01_TrialsForInclusionInAnalysis.Rmd-->

# Preliminary Analysis

```{r PA_Libraries, echo=TRUE, results='hide'}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               lubridate,
               bomrang,
               openxlsx,
               devtools,
               reshape2,
               lme4,
               kableExtra,
               flextable,
               here,
               gridExtra)

load("cache/ImportDataAndSelectTrials01.Rdata")
```

<br>  
<br>

## Trial summary statistics

The data explored in the `PM_MB_dat` data frame is a clean data frame focusing on trials which met the selection criteria testing DMI fungicides (tebuconazole / propiconazole) or no spray controls.

<br>

### Trial seasons
How many trials were undertaken each season.

```{r FinalTrialsForInclusion1}
PM_MB_dat %>%
   distinct(trial_ref, location, year) %>%
   arrange(year) %>%
   group_by(year) %>%
   summarise(n = n())%>%
   flextable()

```

<br>  
<br>

### Trial locations
The location of the trials including DMI fungicides.

```{r FinalTrialsForInclusion}
PM_MB_dat %>%
   distinct(trial_ref, location, year) %>%
   group_by(location) %>%
   summarise(n = n())%>%
   flextable()
```

<br>  
<br>

### Powdery mildew severity and mungbean grain yield summary per trial  
Show a summary of both `powdery mildew severity` and mungbean `grain yield` means and ranges for all trials including DMI fungicides.

```{r Full_Trial_Summary_table, warning= FALSE}
Sev_yield_table <-
   PM_MB_dat %>%
   mutate(PM_sev_control = case_when(fungicide_ai == "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_sev_treat = case_when(fungicide_ai != "control" ~ PM_final_severity,
                                   TRUE ~ NA_real_)) %>%
   mutate(PM_y_control = case_when(fungicide_ai == "control" ~ grain_yield.t.ha.,
                                   TRUE ~ NA_real_)) %>%
   mutate(PM_y_treat = case_when(fungicide_ai != "control" ~ grain_yield.t.ha.,
                                 TRUE ~ NA_real_)) %>%
   mutate(trial_ref = str_remove(trial_ref, "mung")) %>%  # remove "mung" prefix from trial_ref
   group_by(trial_ref,
            location,
            year,
            planting_date,
            first_sign_disease) %>%
   summarise(
      n = n(),
      m_PM_sev_control = round(median(PM_sev_control, na.rm = TRUE), digits = 2),
      n_controls = sum(is.na(PM_sev_control) == FALSE),
      min_PM_sev = round(min(PM_sev_treat, na.rm = TRUE), digits = 2),
      max_PM_sev = round(max(PM_sev_treat, na.rm = TRUE), digits = 2),
      m_PM_yield_control = round(mean(PM_y_control, na.rm = TRUE), digits = 3),
      min_PM_yield = round(min(PM_y_treat, na.rm = TRUE), digits = 3),
      max_PM_yield = round(max(PM_y_treat, na.rm = TRUE), digits = 3),
      .groups = "drop"
   ) %>%
   arrange(year) %>%
   mutate(PM_sev_range = paste(min_PM_sev, max_PM_sev, sep = " - ")) %>%
   mutate(yield_range = paste(min_PM_yield, max_PM_yield, sep = " - ")) %>%
   mutate(m_PM_sev_control = paste(m_PM_sev_control, " (", n_controls, ")", sep = "")) %>%
   select(-c(min_PM_sev, max_PM_sev, min_PM_yield, max_PM_yield, n_controls)) %>%
   select(c(1:7, 9, 8, 10)) %>% # order columns
   flextable() %>%
   set_header_labels(
      trial_ref = "Trial code",
      location = "Location",
      year = "Year",
      planting_date = "Sowing date",
      first_sign_disease = "PM onset",
      n = "n",
      m_PM_sev_control = "Control median\nPM severity",
      PM_sev_range = "PM severity\nrange",
      m_PM_yield_control = "Control\nmean yield",
      yield_range = "Yield range\n(t / ha)"
   ) %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   align(j = 3:10, align = "center", part = "all") %>%
   autofit() %>%
   width(j = 7:10, width = 1) %>%
   width(j = 3, width = 0.5) %>%
   set_caption(
      "Table 1: Mean yield and severity for trials included in the meta-analysis. Powdery mildew (PM) onset date, number of treatments per trial (n), PM median plot severity of the non-fungicide treated plots and the severity range in fungicide treatments, bracketed numbers refer to the number of pooled control treatments summarised; Mean yield in non-fungicide treated control and the range of yields in the fungicide treatments in tonnes per hectare"
   )
Sev_yield_table
```

```{r eval=FALSE, include=FALSE}
# Save table as a word document
doc <- officer::read_docx()
doc <- body_add_flextable(doc, value = Sev_yield_table)
doc <- officer::body_end_section_landscape(doc)
print(doc, target = "paper/figures/Table1_severity&yield.docx")
```
<br>  
<br>

### Summary plots
#### Seasonal disease pressure in the control

```{r bwplot_sev}
sev_control_plot <- 
   PM_MB_dat %>%
   filter(fungicide_ai == "control") %>%
   ggplot(aes(x = year, y = PM_final_severity)) +
   geom_boxplot(outlier.alpha = 0) +
   geom_jitter(size = 2, colour = "cadetblue",alpha = 0.4,width = 0.15) +
   scale_y_continuous(breaks = c(1,3,5,7,9), limits = c(0.9,9.1)) +
   ylab("PM severity (1 -9)")+
   # xlab("Crop season")+
   # theme(axis.title.x=element_blank(),
   #      axis.text.x=element_blank(),
   #      axis.ticks.x=element_blank())+
   ggtitle("A")

sev_control_plot      
```
<br>  
<br>

#### Disease severity range for each spray schedule

```{r bwplot_yield}
sev_schedule_plot <-
   PM_MB_dat %>%
   ggplot(aes(x = spray_management, y = PM_final_severity)) +
   geom_boxplot(outlier.alpha = 0) +
   geom_jitter(
      size = 2,
      colour = "cadetblue",
      alpha = 0.4,
      width = 0.15
   ) +
   scale_y_continuous(breaks = c(1, 3, 5, 7, 9), limits = c(0.9, 9.1)) +
   scale_x_discrete(labels = c(
      "control",
      "early",
      "late",
      "late+",
      "recommended",
      "recomended+"
   )) +
   ylab("PM severity (1 -9)") +
   # xlab("Spray Schedule")+
   ggtitle("B")

sev_schedule_plot
```

<br>  
<br>

#### Seasonal grain yield in the control

```{r bwplot_yield_year}
Y_control_plot <-
   PM_MB_dat %>%
   filter(fungicide_ai == "control") %>%
   ggplot(aes(x = year, y = grain_yield.t.ha.)) +
   geom_boxplot() +
   geom_jitter(
      size = 2,
      colour = "coral",
      alpha = 0.4,
      width = 0.15
   ) +
   scale_y_continuous(breaks = seq(0, 2.5, by = 0.5), limits = c(0, 2.6)) +
   ylab(bquote('Mungbean grain yield ' *  ~  ~ t ~ ha ^ -1 * "")) +
   xlab("Crop season") +
   theme(axis.text.x = element_text(angle = 20, hjust = 0.75),
         plot.margin = margin(0.2, 0, 0.71, 0, "cm"),
         axis.title.x = element_text(vjust = -5))

Y_control_plot
```

<br>  
<br>

#### Mungbean yield for each spray schedule

```{r bwplot_yield_sched}
Y_schedule_plot <- 
   PM_MB_dat %>%
   ggplot(aes(x = spray_management, y = grain_yield.t.ha.)) +
   geom_boxplot(outlier.alpha = 0) +
   geom_jitter(
      size = 2,
      colour = "coral",
      alpha = 0.4,
      width = 0.15
   ) +
   scale_y_continuous(breaks = seq(0, 2.5, by = 0.5), limits = c(0, 2.6)) +
   scale_x_discrete(labels = c(
      "control",
      "early",
      "late",
      "late+",
      "recommended",
      "recomended+"
   )) +
   #ylab(bquote('Mungbean grain yield ' *  ~  ~ t ~ ha ^ -1 * "")) +
   xlab("Spray Schedule")+
    theme(
      axis.title.y = element_blank(),
      axis.text.x = element_text(angle = 20, hjust = 0.75))

Y_schedule_plot
```

```{r include = FALSE}
#library(gridExtra)
# save plots into a 4 x 4 grid for publication

p4 <- arrangeGrob(
   sev_control_plot + theme(
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      axis.title.y = element_blank()
   ),
   sev_schedule_plot + theme(
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      axis.title.y = element_blank()
   ),
   Y_control_plot,
   Y_schedule_plot
)

ggsave(
   filename = "paper/figures/Fig1_boxplots_yield&sev.tiff",
   plot = p4,
   device = "tiff",
   height = 6,
   width = 7,
   dpi = 300,
   units = "in"

)
```

![Box plots of the unsprayed control treatments means for both PM severity (top) and crop yield (bottom), indicating within-season variation (A), and trial treatment means for each spray schedule (B).](paper/figures/Fig1_boxplots_yield&sev.png)

<br>  
<br>  
<br>  
<br>

*****

## Treatment focused summaries

Various factors have been studied in the collated trials which may influence the subsequent meta-analysis.
A quick inspection of the following factors were done to examine the possible influence these variables may have on on mungbean grain yield and/or powdery mildew mean plot severity.

   1. [Fungicide type] (propiconazole and tebuconazole)  
   2. [Fungicide Doses]
   3. [Number of fungicide sprays]  
   4. [Host cultivar][Mungbean cultivars] (probably is a co-variate with season due to changing cultivars over time)  
   5. [Row spacing]  
   6. [Final disease rating / disease pressure][Disease pressure]
   7. [Moisture availability for the crop][In-crop rainfall]

The data plotted below are from `r length(unique(PM_MB_dat$trial_ref))` field trials between (`r min(PM_MB_dat$year)` - `r max(PM_MB_dat$year)`) of which the details are described in the [Trials considered for inclusion in meta-analysis].

<br>

### Fungicide type
#### Powdery mildew severity
```{r TebuVPropi_sev}
n_C <- sum(PM_MB_dat$fungicide_ai == "control")
n_P <- sum(PM_MB_dat$fungicide_ai == "propiconazole")
n_T <- sum(PM_MB_dat$fungicide_ai == "tebuconazole")

PM_MB_dat %>%
   ggplot(aes(y = PM_final_severity, x = as.factor(fungicide_ai))) +
   xlab("Fungicide treatment") +
   ggtitle(label = "Powdery mildew severity for each fungicide active ingredient") +
   labs(caption = paste("Control n:", n_C,
                        "; Propiconazole n:", n_P,
                        "; Tebuconazole n:", n_T, sep = "")) +
   geom_boxplot()
```

<br>  
<br>

#### Yield effect
```{r TebuVPropi_Yi}
PM_MB_dat %>%
   ggplot(aes(y = grain_yield.t.ha., x = as.factor(fungicide_ai))) +
   xlab("Fungicide treatment") +
   ggtitle(label = "Grain yield for each fungicide active ingredient") +
   labs(caption = paste("Control n:", n_C,
                        "; Propiconazole n:", n_P,
                        "; Tebuconazole n:", n_T, sep = "")) +
   geom_boxplot()
```

<br>  
<br>  
<br>

### Fungicide Doses{#fungicide-doses}  
This analysis focuses only the DMI fungicides, tebuconazole and propiconazole, which were trialled the most often.

We should check that all fungicide doses that were used were roughly the same, if we are to compare between trials where dose might be different.

```{r tebuAndPropi_dose}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   ggplot(aes(x = as.factor(dose_ai.ha), fill = fungicide_ai)) +
   xlab("Dose (g ai/ha)") +
   ggtitle(label = "Total number of treatments for each respective tebuconazole\nor propiconazole dose") +
   geom_bar() 
```

All trials that used tebuconazole used approximately the same dose.
Dose of the active ingredient ranged from 62.35&nbsp;g per hectare to 60&nbsp;g per hectare.

Doses for propiconazole range from 62.5&nbsp;g to 125&nbsp;g, a large variation.  
Let's inspect the difference in yields for each dose.

```{r PropiDoseEffect}
PM_MB_dat %>%
   filter(fungicide_ai == "propiconazole") %>%
   ggplot(aes(x = relevel(as.factor(dose_ai.ha), "62.5"), y = grain_yield.t.ha.)) +
   xlab("Dose (g ai/ha)") +
   labs(label = "Yield for each respective propiconazole dose",
        caption = "Facets indicate the number of applications") +
   geom_boxplot(fill = "grey", alpha = 0.5) +
   ylab("Grain yield t / ha") +
   facet_grid(cols = vars(total_fungicide))
```

This dose effect should be investigated in the meta-analysis.

<br>  
<br>

How many treatments of each dose have been investigated per trial?

```{r table_PropiDoses}
table(as.character(PM_MB_dat[PM_MB_dat$fungicide_ai == "propiconazole",]$trial_ref),
      PM_MB_dat[PM_MB_dat$fungicide_ai == "propiconazole",]$dose_ai.ha)
```
<br>  
<br>

### Number of fungicide sprays

Inspect the frequency of sprays per fungicide.  
```{r Fungicide_x_nSprays}
table(PM_MB_dat$fungicide_ai, PM_MB_dat$total_fungicide)
```
Very few treatments were sprayed more than three times and only in `r unique(PM_MB_dat[PM_MB_dat$total_fungicide == 3,"trial_ref"])`

<br>  
<br>

### Mungbean cultivars

Australian mungbean varieties have the following resistance to powdery mildew.

   - Berken: Highly susceptible

   - Crystal: Susceptible

   - Jade: Moderately susceptible

Let's view a stacked bar plot of the number of sprays for both demethylation inhibitors, tebuconazole and propiconazole against each cultivar.

```{r Host_genotype, message=FALSE}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(host_genotype, fungicide_ai, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Treatments = n) %>%
   ggplot(aes(x = host_genotype, y = Treatments, fill = fungicide_ai)) +
   xlab("Cultivar") +
   ylab("N Trials") +
   ggtitle(label = "Cultivars used in either tebuconazole or propiconazole trials") +
   geom_col() +
   scale_fill_discrete(name = "Fungicide AI")
```

#### Yield loss in cultivar Jade

Cultivar Jade shows the best quantitative resistance to powdery mildew.  
Based on the 2016 GRDC report by Sue Thompson [-@SueThompson2016] we want to know what is the possible yield loss for this moderately susceptible cultivar.

```{r JadeYieldLoss}
PM_MB_dat %>%
   filter(year == "2016",
          host_genotype == "Jade") %>%
   mutate(Treatment = case_when(fungicide_ai == "control" ~ "control_yield",
                                TRUE ~ "FungicideTreated_yield")) %>%
   group_by(location, Treatment) %>%
   summarise(
      trial_ref = trial_ref,
      location = location,
      year = year,
      Yield = mean(grain_yield.t.ha., na.rm = TRUE),
      .groups = "drop"
   ) %>%
   distinct() %>%
   pivot_wider(names_from = Treatment, values_from = Yield) %>%
   mutate(Diff = FungicideTreated_yield - control_yield) %>%
   mutate(percent = (Diff / FungicideTreated_yield) * 100) %>%
   select(trial_ref,
          location,
          year,
          control_yield,
          FungicideTreated_yield,
          percent,
          Diff) %>%
   flextable()
```

<br>  
<br>

### Row spacing

Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease as well as fungicide timing and efficacy.
The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows in most cases increased yield significantly.
This finding has also been shown by several other researchers' work in Queensland and New South Wales as well.

```{r row_spacing.m}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(fungicide_ai, row_spacing, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Trials = n) %>%
   ggplot(aes(x = as.factor(row_spacing), y = Trials)) +
   xlab("Row Spacing (m)") +
   ylab("N Trials") +
   ggtitle(label = "Trial row spacing using tebuconazole") +
   geom_col(aes(fill = fungicide_ai),
            position = "dodge") +
   scale_fill_discrete(name = "Fungicide AI")
```

<br>  
<br>

Will plotting row spacing treatments show differences for the response variables, *yield* and *disease severity*.  
The main questions are:

   * Were there any statistical differences for mungbean *yield* or *powdery mildew severity* between row spacing treatments?

   * If not, can we pool certain row spacing that have no significant difference?

```{r RS_severity}
# Which row spacing leads to the higher disease severity
PM_MB_dat %>%
   filter(year == 2017 |
             year == 2018) %>%
   filter(fungicide_ai == "control") %>%
   ggplot(aes(y = PM_final_severity, x = factor(row_spacing))) +
   geom_boxplot(alpha = 0.5) +
   ylab("Final severity rating") +
   xlab("Row spacing (m)") +
   ggtitle("Powdery mildew severity between different row spacing across all trials")
```

There is little difference here between the row spacing treatments, Let's look if there is a trial location effect as disease pressure lead to varying results.

```{r RS_severity_x_trial}
# Does trial year and location interact between row spacing and disease severity
PM_MB_dat %>%
   filter(year == 2017 |
             year == 2018) %>%
   filter(fungicide_ai == "control") %>%
   ggplot(aes(y = PM_final_severity, x = factor(row_spacing))) +
   geom_boxplot(alpha = 0.5) +
   facet_grid(cols = vars(location)) +
   ggtitle("Powdery mildew variation between different row spacing") +
   ylab("Final severity rating") +
   xlab("Row spacing (m)")
```

<br>

In the Wellcamp site, wider row spacing reduces PM severity, the other sites it seems there was not enough variation to make a distinction between row spacing treatments.

```{r RS_yield}
# Which row spacing leads to the higher yield potential
PM_MB_dat %>%
   filter(year == 2017 |
             year == 2018) %>%
   ggplot(aes(
      y = as.numeric(grain_yield.t.ha.),
      x = as.factor(row_spacing),
      colour = location
   )) +
   geom_jitter(width = 0.05) +
   ggtitle("Grain yield results for different row spacing at three locations") +
   xlab("Row spacing (m)") +
   ylab("Grain yield (t/ha)")+
   theme_minimal()
```

The plots seem to imply when yield is limited, presumably by other abiotic factors, there is no effect of row spacing on yield, like in the Hermitage trial.
However, if the average yield is more than approximately 1 t/ha then smaller row spacing has the potential to provide greater yield per hectare.

Overall row spacing may influence both powdery mildew severity and yield.
However, in the trial reports, no significant interaction was found between row spacing, powdery mildew severity and yield.
That is, with narrower row spacing appeared to increase yield even if the amount of powdery mildew increased and no relationship could be detected between an interaction of the three.

<br>  
<br>

### Disease pressure  
The amount of disease pressure between seasons is another variable which could impact mungbean yield meta-analysis effect size. 
```{r D_pres}
# Assess the effect of yield pressure on the spray schedule efficacy
# Use quantiles to separate disease pressure into High, Medium and low disease pressure categories
DP33 <- 
   PM_MB_dat %>%
   filter(fungicide_ai == "control") %>%
   pull(PM_final_severity) %>%
   quantile(0.3333)

DP66 <- 
   PM_MB_dat %>%
   filter(fungicide_ai == "control") %>%
   pull(PM_final_severity) %>%
   quantile(0.6666)

PM_MB_dat %>%
   mutate(yc = case_when(fungicide_ai == "control" ~ grain_yield.t.ha.,
                         TRUE ~ NA_real_))%>%
   group_by(trial_ref)%>%
   mutate(yc = mean(yc, na.rm=TRUE)) %>%
   mutate(yield_saved = case_when(fungicide_ai != "control" ~ grain_yield.t.ha. - yc,
                    fungicide_ai == "control" ~ NA_real_)) %>%
   mutate(dc = case_when(fungicide_ai == "control" ~ PM_final_severity,
                         TRUE ~ NA_real_))%>%
   mutate(dc = mean(dc, na.rm = TRUE))%>%
   ungroup() %>%
   mutate(disease_pressure = case_when(dc <= DP33 ~ "low",
                                 dc <= DP66 &
                                 dc > DP33 ~ "medium",
                                 dc > DP66 ~ "high",
                                 TRUE ~ NA_character_))%>%
   filter(spray_management != "control") %>%
   ggplot(aes(disease_pressure, yield_saved))+
   geom_boxplot()+ 
   facet_grid(. ~ spray_management)

```

From these plots it is difficult to determine if there is an interaction between disease pressure and the yield saved, or if no interaction exists and fungicide efficacy in general has greater potential to save yield when disease pressure is higher.
It is worth noting there was not sufficient variation in the control plot disease severity to produce a `medium` disease severity category.

<br>  
<br> 
<br>  
<br>

### In-crop rainfall  
#### Whole season

In season rainfall is known to contribute significantly to crop yields, however the timing of rainfall is likely important.

First an inspection of all rainfall within the season
```{r season_rainfall}
source("R/add_lat_longs.R") # code adds the latitude- and longitude to PM_MB_dat
source("R/crop_rain.R")

# Obtain rainfall from bomrang
PM_MB_dat$sum_rain <-
   crop_rain(location_name = PM_MB_dat$location,
          latitude = PM_MB_dat$lat,
          longitude = PM_MB_dat$lon,
          first_day = PM_MB_dat$planting_date,
          last_day = PM_MB_dat$harvest_date)

# plot yield vs rainfall
PM_MB_dat %>%
   ggplot(aes(y = grain_yield.t.ha., x = sum_rain)) + 
   geom_point()
```

```{r lm_total}
summary(lm(grain_yield.t.ha. ~ sum_rain, data = PM_MB_dat))
```

<br>  
<br>

#### Early-season rainfall
Here we only look at the effect of rainfall between the _planting date_ and _first sign of disease_. 
We are choosing first sign of disease as a mid point in the crop maturity.

```{r early_season_rain}
PM_MB_dat$early_rain <-
   crop_rain(location_name = PM_MB_dat$location,
          latitude = PM_MB_dat$lat,
          longitude = PM_MB_dat$lon,
          first_day = PM_MB_dat$planting_date,
          last_day = PM_MB_dat$first_sign_disease)

PM_MB_dat %>%
   ggplot(aes(y = grain_yield.t.ha., x = early_rain)) + 
   geom_point()
```

```{r lm_early_rain}
summary(lm(grain_yield.t.ha. ~ early_rain, data = PM_MB_dat))
```

There is a significant negative association here, indicating rain fall early in the crop development negatively affects mungbean yields. However the very low R-squared value indicates it is no a strong one.

<br>  
<br>

#### Late-season rainfall  
Here we only look at the effect of rainfall between the _first sign of disease_ and _crop harvest_.

```{r late_rain}
PM_MB_dat$late_rain <-
   crop_rain(location_name = PM_MB_dat$location,
          latitude = PM_MB_dat$lat,
          longitude = PM_MB_dat$lon,
          first_day = PM_MB_dat$first_sign_disease,
          last_day = PM_MB_dat$harvest_date)

PM_MB_dat %>%
   ggplot(aes(y = grain_yield.t.ha., x = late_rain)) + 
   geom_point()
```

```{r lm_late_rain}
summary(lm(grain_yield.t.ha. ~ late_rain, data = PM_MB_dat))
```

There is a significant positive association here, indicating rainfall after disease commences is likely to lead to increased yield. However the very low R-squared value indicates it is no a strong one.

<br>  
<br>

#### Mid-season rainfall  
Here we only look at the effect of rainfall between the 20 days after planting and 80 days after planting.
```{r mid_rain}
PM_MB_dat$mid_rain <-
   crop_rain(location_name = PM_MB_dat$location,
          latitude = PM_MB_dat$lat,
          longitude = PM_MB_dat$lon,
          first_day = ymd(PM_MB_dat$planting_date) + days(45),
          last_day = ymd(PM_MB_dat$planting_date) + days(75)
   )

PM_MB_dat %>%
   ggplot(aes(y = grain_yield.t.ha., x = mid_rain)) + 
   geom_point()
```

```{r lm_mid_rain}
summary(lm(grain_yield.t.ha. ~ mid_rain, data = PM_MB_dat))
```
There is no association with mid season rain and crop yields.

From the plots shown here we can draw the conclusion that we lack sufficient information. 
Most likely available soil water between trials along with other unobserved variables influence of rainfall on mungbean crops and therefore we will not investigate any further.

<br>  
<br> 
<br> 
******

### FAO mungbean data

An important consideration for why to carry out work on mungbean diseases is the value the crop provides. 
Let's pull in data from the FAOSTAT website for the area of mungbean crops harvested.

```{r FAO_data_inquiry}
beans <- read.csv(here("data/FAOSTAT_data_7-6-2020.csv"))

str(beans)

beans %>%
   filter(Item == "Beans, dry",
          Element == "Area harvested") %>%
   select(Year, Value) %>%
   ggplot(aes(y = Value, x = Year)) +
   geom_point() +
   geom_smooth()
```

<!--chapter:end:02_Preliminary_analysis.Rmd-->

---
output: html_document
editor_options: 
  chunk_output_type: inline
---
# Grain yield meta-analysis

Let's get started with the analysis by first finding the best fitting model which answers our research question.

> When, in relation to PM establishment in the crop, should farmers begin spraying mungbean to mitigate yield loss: before PM establishing, immediately after first sign of PM establishing, or after PM has become established in the crop.

A secondary question to this aim is: given the time at which the first spray occurred does a second spray provide worthwhile yield protection.

To do this, the model will use the main variables:

   - *Grain yield* the response variable (t / ha)

   - *Trial*, which resolves combinations of categorical random variables: 
      i) year  
      ii) location  
      iii) row spacing  
      iv) cultivar

   - *spray_management* a moderator to evaluate the difference in effect size attributed to fungicide application timing.

   - *id* random variable indicating each treatment is independent

```{r Yield_ME_libraries, echo=TRUE,results='hide'}
# load R packages
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(
   tidyverse,
   kableExtra,
   bomrang,
   RColorBrewer,
   metafor,
   here,
   netmeta,
   multcomp,
   flextable
)

source(here("R/reportP.R"))

# Data
PM_dat_Y <-
   read.csv("cache/PM_yield_clean_data.csv", stringsAsFactors = FALSE
   )
```

### Define Trial
```{r Yield_define_trial}
PM_dat_Y <-
   PM_dat_Y %>%
   mutate(trial = paste(trial_ref,
                        year,
                        location,
                        host_genotype,
                        row_spacing,
                        sep = "_")) 
```

<br>  
<br>  
<br>

## Spray schedule meta-analysis

The `spray_management` moderator will be evaluated in the first model. 
Then this model will be tested against other models incorporating, time of disease onset, disease pressure and other variance-covariance matrix structures.

### Spray schedule moderator

This *grain yield* meta-analysis is a multi-variate meta-analysis, using the `metafor` package function `rma.mv()` [@Viechtbauer2010].

We are using the `spray_management` variable as a moderator and an interactive random term with the `trial` random variable. The variance-covariance matrix is specified as unstructured (UN) to allow correlations between and within trials.

```{r Yield_Metafor-analysis, cache=TRUE}
PM_mv <- rma.mv(
   yi = grain_yield.t.ha.,
   V = vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_Y
)
```

<br>  
<br>  
<br>

*****

### Disease onset interaction with spray schedule

To determine if the time at which disease occurs in the cropping season influences the efficacy at which fungicide applications protect yield we will create a categorical variable defining `early` or `late` disease onset.

`early` and `late` categories should be divided by a number close to the median days after sowing when signs of the disease were first observed to ensure roughly even numbers in each category.
```{r median onset}
PM_dat_Y %>%
   mutate(first_sign_days = lubridate::ymd(first_sign_disease) -
             lubridate::ymd(planting_date)) %>%
   pull(first_sign_days) %>%
   median()
```

We will choose 42 days as this is the average days to flowering in mungbean. 
In addition, Kelly et. al. [-@Kelly2017a] noted that yield losses are higher in cultivar Berken when disease establishes before flowering.

Now let's define a continuous variable`first_sign_days` and a categorical variable `onset`.

```{r define_onset, cache=TRUE}
PM_dat_Y <- PM_dat_Y %>%
   mutate(first_sign_days = lubridate::ymd(first_sign_disease) -
             lubridate::ymd(planting_date)) %>%
   mutate(onset = case_when(
      first_sign_days <= 42 ~ "early_onset",
      first_sign_days > 42 ~ "late_onset"
   ))
```

Inspect a histogram of when first sign occurred in the crop.

```{r hist_onset}
PM_dat_Y %>%
   ggplot(aes(x = as.integer(first_sign_days))) +
   geom_histogram(binwidth = 1) +
   geom_vline(xintercept = 42)
```

`early_onset` contains `r nrow(PM_dat_Y[PM_dat_Y$onset == "early_onset",])` treatments and,  
`late_onset` contains `r nrow(PM_dat_Y[PM_dat_Y$onset == "late_onset",])` treatments.

<br>  
<br>

******

#### metafor onset analysis

We are adding the `onset` variable as a moderator to test and interaction with the `spray_management` variable as a moderator and an interactive term to the `trial` random variable.

```{r onset_Metafor-analysis, cache=TRUE}
PM_mv_onset <- rma.mv(
   yi = grain_yield.t.ha.,
   V = vi,
   mods = ~ spray_management * onset,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_Y
)
```

```{r}
anova(PM_mv, PM_mv_onset)
```

This comparison tells us the meta-analysis including `onset` explained more residual heterogeneity, as shown by the lower QE value, and has a better fit, indicated by the higher log-likelihood with the additional `onset` parameters.
However the higher AIC indicates in the model with the additional `onset` parameters does not sufficiently improve the model fit to warrant including these parameters and therefore the 'reduced' model is a better option.
This inference is also reflected by the the chi-squared test, which is uncertain that the `onset` model is significantly better as indicated by the ANOVA `pval` `r round(anova(PM_mv, PM_mv_onset)$pval,3)`.

<br>  
<br>  
<br>

******

### Disease pressure interaction with spray schedule

To determine if the seasonal disease pressure influences the efficacy at which fungicide applications protect yield a categorical variable defining `high_pressure` or `low_pressure` can be defined.

`high_pressure` and `low_pressure` will be divided by the median disease severity in the no spray control treatments at the end of the season.

```{r median_pressure}
PM_dat_Y %>%
   filter(fungicide_ai == "control") %>%
   pull(PM_final_severity) %>%
   median()
```

Now to define these two new variables, `low_pressure` and `high_pressure` in the data.

```{r define_disease_pressure}
PM_dat_Y <- PM_dat_Y %>%
   mutate(
      d_pressure = case_when(
         PM_final_severity < 8 ~ "low_pressure",
         PM_final_severity >= 8 ~ "high_pressure"
      )
   )
```

Inspect a histogram of the final severity values in the crop.

```{r hist_pressure}
PM_dat_Y %>%
   ggplot(aes(x = PM_final_severity)) +
   geom_histogram(binwidth = 1) +
   geom_vline(xintercept = 8)
```

<br>  
<br>  
<br>

******

#### metafor disease pressure interaction

Test `d_pressure` variable addition as a moderator to evaluate it's interaction with the `spray_management` to influence the grain yield effect size.

```{r Dpressure_Metafor-analysis, cache=TRUE}
PM_mv_dp <- rma.mv(
   yi = grain_yield.t.ha.,
   V = vi,
   mods = ~ spray_management * d_pressure,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_Y
)
```

```{r}
anova(PM_mv, PM_mv_dp)
```
This comparison tells us the meta-analysis including `d_pressure` explained more residual heterogeneity, as shown by the lower QE value, and has a better fit, indicated by the higher log-likelihood with the additional `d_pressure` parameter.
However the lower AIC in the 'Full' model indicates that retaining the model including the additional `d_pressure` variables could be a reasonable decision.
In addition the chi-squared test indicates that the `d_pressure` model is better as indicated by the `pval` 0.0468.

However it is worth noting that there were no Late plus schedules that experienced low disease pressure. 
Even though the disease pressure interaction on the moderators could be deemed significant (P = 0.0468), the division of schedules due to disease pressure (reducing k) makes drawing conclusions risky. More data is needed to explore this possible effect.

```{r}
# show the division of spray schedules by the d_pressure moderator
PM_dat_Y %>%
   group_by(spray_management, d_pressure) %>%
   summarise(n()) %>%
   flextable()
```

```{r}
summary(PM_mv_dp)
```

<br>  
<br>  
<br>

******

### Test variance-covavriance matrix structure

Test a model with an implied simpler variance-covariance matrix, "compound symmetry" (CS), to examine if unstructured matrix is suitable.

```{r}
PM_mv_cs <- rma.mv(
   yi = grain_yield.t.ha.,
   V = vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "CS",
   control = list(optimizer = "optim"),
   data = PM_dat_Y
)

anova(PM_mv, PM_mv_cs)
```

Again `PM_mv` (Full) prevails as the better model (p = 0.0014; AIC = -45.4359) and therefore we should keep the unstructured variance-covariance matrix.

 > Therefore the model `PM_mv`, is the preffered model with this data.

## Summarise PM_mv model

```{r PM_mv_summary}
summary(PM_mv)
```

The first table in the `PM_mv` output shows the tau^2 (between trial variance) for each random effect intercept (spray_management) to trial and the number of occurrences for each treatment in the analysis.
This effectively shows the heterogeneity between trials for these particular treatments.

This table shows `Recommended_plus` showed the highest heterogeneity between trials followed by `Late_plus`, `Late` then `Recommended`, with `Early` and the no-spray `control` showing the least heterogeneity.

The second table is in two parts (left and right). 
The left part, rho, is the correlation of variation between the specified treatments.
All comparisons were acceptable except for a comparison between `Early` and `Late_plus`, indicating `0.000` rho.
`Early` and `Late_plus` treatments never occurred within the same trial, which is indicated by the right side of the table (hence earlier warnings). 
This is not a concern for this type of network meta-analysis because the differences between these treatments can be inferred by their differences with other treatments [@Madden2016].

In this result we can see that the `Early` treatment is not significantly different to the intercept, which in this case is the mean of the no spray `control`.
However the other treatments are significantly different from the no-spray control (intercept).
The $Q_M$ [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, shows the moderators significantly influence the model ($Q_M =$ `r PM_mv$QM` $,df =$ `r PM_mv$m`, `r reportP(PM_mv$QMp)`) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
The analysis shows there is still a significant amount of residual heterogeneity ($Q_E =$ `r PM_mv$QE` $,df=$ `r PM_mv$k - PM_mv$m`, `r reportP(PM_mv$QEp)` ) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.

<br>
<br>
<br>

******

## Meta-analysis results summary

### Moderator estimates table

Let's present the meta-analysis results for the moderator variables in a table of estimates.

```{r metafor_results_table_yield}
# obtain number of treatments included in each moderator variable
k5 <-
   as.data.frame(table(PM_dat_Y$trial, PM_dat_Y$spray_management)) %>%
   filter(Freq != 0) %>%
   group_by(Var2) %>%
   summarise(n()) %>%
   pull()

# create data.frame
results_mv <- data.frame(
   Moderator = c(
      "Intercept / No Spray control",
      "Early",
      "Late",
      "Late+",
      "Recommended",
      "Recommended+"
   ),
   N = PM_mv$g.levels.k,
   k = k5,
   Effect = round(PM_mv$b, 4),
   se = round(PM_mv$se, 4),
   CI_lower = round(PM_mv$ci.lb, 4),
   CI_upper = round(PM_mv$ci.ub, 4),
   z_val = round(PM_mv$zval, 4),
   p_val = reportP(PM_mv$pval, AsNumeric = FALSE, P_prefix = FALSE)
)

# rename colnames to give table headings
colnames(results_mv)[c(2:5, 7:10)] <-
   c("Treatment",
     "N",
     "k",
     "mu",
     "CI_{L}",
     "CI_{U}",
     "Z",
     "P")

yield_estimates_table <-
   flextable(results_mv[c(2, 5, 6, 3, 4), c(1, 3:8, 10)]) %>%
   align(j = 3:8, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption(
      "Table 2: Estimated mungbean yield mean difference to the no spray control (intercept) for each spray schedule treatment. Yield estimates (u) were calculated from a network meta-analysis of data obtained from grey literature reports of 'k' field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept."
   ) %>%
   autofit() %>%
   footnote(
      i = 1,
      j = c(2:4, 6:8),
      value = as_paragraph(
         c(
            "number of treatment means categorised to each spray schedule",
            "number of trials with the respective spray schedule",
            "estimated mean yield determined by the meta-analysis",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval",
            "indicates the significance between each respective spray schedule and the no spray control (intercept)"
         )
      ),
      ref_symbols = letters[1:6],
      part = "header",
      inline = TRUE
   )

yield_estimates_table
```

```{r eval=FALSE, include=FALSE}
# Save table as a word document
doc <- officer::read_docx()
doc <- body_add_flextable(doc, value = yield_estimates_table)
print(doc, target = "paper/figures/Table2_yield_estimates.docx")
```

<br>  
<br>

### Moderator estimates plot

View the moderator comparisons in a plot.

```{r metafor_plot_yied}
results_mv %>%
   filter(Treatment != "control") %>%
   mutate(Treatment = factor(Treatment, levels = rev(
      c(
         "Early",
         "Recommended",
         "Recommended_plus",
         "Late",
         "Late_plus"
      )
   ))) %>%
   ggplot(aes(Treatment, mu)) +
   geom_hline(
      yintercept = seq(-0.05, 0.3, by = 0.05),
      linetype = 3
   ) +
   geom_point(aes(size = 1 / se), shape = 15) +
   geom_linerange(aes(ymin = `CI_{L}`, ymax = `CI_{U}`)) +
   coord_flip() +
   labs(caption = "Bars indicate 95% confidence intervals")+
   ylab(expression(paste(
      "Mean yield difference to control (t ha" ^ -1, ")", sep = ""
   ))) +
   scale_x_discrete(
      "Moderator variable",
      labels = c(
         expression("Late"["plus"]),
         expression("Late"["single"]),
         expression("Recommended"["plus"]),
         expression("Recommended"["single"]),
         expression("Early"["single"])
      )
   )
ggsave("paper/figures/Fig2_means_difference.png",
       height = 3,
       dpi = 500)
```

<br>  
<br>

### Moderator contrasts

Calculate treatment contrasts

```{r PM_Mv_Contrast_yield}
source("R/simple_summary.R") #function to provide a table that includes the treatment names in the contrasts
summary(glht(PM_mv, linfct = cbind(contrMat(rep(
   1, 6
), type = "Tukey"))), test = adjusted("none"))
contrast_Ssum <-
   simple_summary(summary(glht(PM_mv, linfct = cbind(
      contrMat(rep(1, 6), type = "Tukey")
   )), test = adjusted("none")))
contrast_Ssum %>%
   flextable()%>%
   autofit()

```

These contrasts can be viewed in a plot.

```{r plotContrasts_yield}
par(mar = c(5, 13, 4, 2) + 0.1)
plot(glht(PM_mv, linfct = cbind(contrMat(rep(
   1, 6
), type = "Tukey"))), yaxt = 'n')
axis(
   2,
   at = seq_along(contrast_Ssum$contrast),
   labels = rev(contrast_Ssum$contrast),
   las = 2,
   cex.axis = 0.8
)
```

### Profile plots

An inspection of the profile plots to ensure the model is not over-fitted can be undertaken.
We expect to see the estimate align with the peak of the curve.
Also that the shape of the line is a curve.
As these plots take a long time to generate they will not be evaluated.

```{r profile_plots, eval=FALSE, echo=TRUE, results="hide"}
profile(PM_mv, tau2 = 1)
profile(PM_mv, tau2 = 2)
profile(PM_mv, tau2 = 3)
profile(PM_mv, tau2 = 4)
profile(PM_mv, tau2 = 5)
profile(PM_mv, tau2 = 6)
```

<br>  
<br>  
<br>

******

## netmeta analysis

The `netmeta` package can provide a graphical representation of the pairwise comparisons.

The `netmeta` package uses a frequentist approach focusing on the pairwise comparisons between treatments. 
These results can be used to evaluate if our outcome with the `metafor` package was robust.

```{r netmeta-analysis}
datPM3 <- PM_dat_Y %>%
   group_by(trial, spray_management, replicates) %>%
   summarize(yi_mean = mean(grain_yield.t.ha.),
             vi_mean = mean(vi)) %>%
   ungroup()

PM_con <- pairwise(
   treat = spray_management,
   n = replicates,
   mean = yi_mean,
   sd = sqrt(vi_mean),
   studlab = trial,
   data = datPM3,
   sm = "MD"
)

net_con <- netmeta(TE,
                   seTE,
                   treat1,
                   treat2,
                   studlab,
                   data = PM_con,
                   sm = "MD")

summary(net_con)
```

<br>  
<br>

### netmeta estimates plot
Visualise netmeta results as a forest plot.

```{r netmeta-forest}
forest(
   net_con,
   reference.group = 1,
   rightcols = c("effect", "ci", "Pscore"),
   rightlabs = "P-Score",
   small.values = "bad"
)
```
<br>  
<br>  
<br>

******

### Moderator netgraph

The `netmeta` analysis suggests the spray schedule commencing early are no different to any other treatment including the no spray `control`.
It estimates the mean is very similar to the recommended treatments.
The `Recommended_plus` and `Late_plus` treatments show higher mean estimates, however are not significantly different from the `Early` estimate.

```{r netgraphGW}
netgraph(
   net_con,
   plastic = FALSE,
   thickness =  "number.of.studies",
   points = FALSE,
   cex.points = 1,
   number.of.studies = TRUE,
   cex.number.of.studies = 1,
   col.number.of.studies = "black",
   multiarm = FALSE,
   pos.number.of.studies = 0.4
)
```

<br>  
<br>  
<br>

******

```{r}
netleague(net_con)

decomp.design(net_con)

netsplit(net_con)

nm1 <- netmeasures(net_con)

plot(
   nm1$meanpath,
   nm1$minpar,
   pch = "",
   xlab = "Mean path length",
   ylab = "Minimal parallelism"
)
text(nm1$meanpath, nm1$minpar, names(nm1$meanpath), cex = 0.8)
```

```{r Save_meta_data, eval=FALSE}
save(PM_dat_Y,
     PM_mv,
     contrast_Ssum,
     file = here("cache/Meta-analysisData.Rdata"))
```

<!--chapter:end:03_Yield_MetaAnalysis.Rmd-->

---
output: html_document
editor_options: 
  chunk_output_type: inline
---

# Powdery mildew severity Meta-analysis

An additional question to our main aim: does spray schedule have a similar effect on disease severity?

This model will be similar to the grain yield meta-analysis and use the main variables:

   - *Powdery mildew severity* the response variable (1-9 scale)

   - *Trial*, which resolves combinations of categorical random variables: 
      i) year  
      ii) location  
      iii) row spacing  
      iv) cultivar

   - *spray_management* a moderator to evaluate the difference in effect size attributed to fungicide application timing.

   - *id* random variable indicating each treatment is independent

<br>

Load libraries and data  
```{r MEsummary_Libraries2, echo=TRUE,results='hide'}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               kableExtra,
               bomrang,
               RColorBrewer,
               metafor,
               here,
               netmeta,
               multcomp,
               dplyr,
               flextable)

source(here("R/reportP.R"))

# Data
PM_dat_D <-
   read.csv("cache/PM_disease_clean_data.csv", stringsAsFactors = FALSE)
```

<br>  
<br>

### Define Trial
```{r define_trial}
PM_dat_D <-
   PM_dat_D %>%
   mutate(trial = paste(trial_ref,
                        year,
                        location,
                        host_genotype,
                        row_spacing,
                        sep = "_")) 
```

Inspect disease severity for a normality.
```{r sev_hist}
hist(PM_dat_D$PM_final_severity)
```

<br>  
<br>  
<br>

*****

## Disease severity spray schedule meta-analysis

```{r Metafor-Sev-analysis, cache=TRUE}
PMsev_mv <- rma.mv(
   yi = PM_final_severity,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)

summary(PMsev_mv)
```

All spray schedules were effective at lowering the disease severity at the end of the season.
`Recommended_plus` reduced powdery mildew incidence the most.

<br>  
<br>  
<br>

### Disease severity moderator contrasts

Calculate the treatment contrasts

```{r sevContrasts}
source("R/simple_summary.R") #function to provide a table that includes the treatment names in the contrasts

contrast_Ssum <-
   simple_summary(summary(glht(PMsev_mv, linfct = cbind(
      contrMat(rep(1, 6), type = "Tukey")
   )), test = adjusted("none")))

contrast_Ssum %>%
   flextable()%>%
   autofit()
```

<br>  
<br>  
<br>

```{r plotsevContrasts}
par(mar = c(5, 13, 4, 2) + 0.1)
plot(glht(PMsev_mv, linfct = cbind(contrMat(rep(
   1, 6
), type = "Tukey"))), yaxt = 'n')
axis(
   2,
   at = seq_along(contrast_Ssum$contrast),
   labels = rev(contrast_Ssum$contrast),
   las = 2,
   cex.axis = 0.8
)
```

`Recommended_plus` limited disease severity significantly better than any other spray treatment. 
`Late_plus` limited disease severity significantly better than a single `Late` application. 
This indicates that two spray treatments were significantly better than a single application, but the timing of the fungicide application was more critical.

<br>  
<br>  
<br>

### Meta-analysis summary table
```{r metafor_results}
# obtain number of treatments included in each moderator variable
k5 <-
   as.data.frame(table(PM_dat_D$spray_management)) %>%
   filter(Freq != 0) %>%
   pull(Freq)

k6 <-
   as.data.frame(table(PM_dat_D$trial_ref, PM_dat_D$spray_management)) %>%
   filter(Freq != 0) %>%
   group_by(Var2) %>%
   summarise(n()) %>%
   pull()

intercept <- round(PMsev_mv$b, 4)[1,1]

# create data.frame
results_mv <- data.frame(
   Moderator = c(
   "Intercept / No Spray control",
   "Early",
   "Late",
   "Late+",
   "Recommended",
   "Recommended+"
   ),
   N = k5,
   k = k6,
   Effect = round(PMsev_mv$b, 4),
   se = round(PMsev_mv$se, 4),
   CI_lower = round(PMsev_mv$ci.lb, 4),
   CI_upper = round(PMsev_mv$ci.ub, 4),
   z_val = round(PMsev_mv$zval, 4),
   p_val = reportP(PMsev_mv$pval, AsNumeric = FALSE, P_prefix = FALSE),
   eff_bar = round(1 -(intercept + PMsev_mv$b)/intercept,4)*100,
   eff_CI_high = round(1 -(intercept + PMsev_mv$ci.ub)/intercept,4)*100,
   eff_CI_low = round(1 -(intercept + PMsev_mv$ci.lb)/intercept,4)*100

)

# rename colnames to give table headings
colnames(results_mv)[c(1:4,6:12 )] <-
   c("Moderator",
     "N",
     "k",
     "mu",
     "CI_{L}",
     "CI_{U}",
     "Z",
     "P",
     "Efficacy",
     "Eff CI_lower",
     "Eff CI upper")

disease_estimates_table <-
   flextable(results_mv[c(2,5,6,3,4), c(1:4,6:7, 9:12)]) %>%
   align(j = 2:10, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption(
      "Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment. Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept."
   ) %>%
   autofit() %>%
   footnote(
      i = 1,
      j = c(2:10),
      value = as_paragraph(
         c(
            "number of treatment means categorised to each spray schedule",
            "number of trials with the respective spray schedule",
            "estimated mean yield determined by the meta-analysis",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval",
            "indicates the significance between each respective spray schedule and the no spray control (intercept)",
            "Fungicide spray schedule efficacy",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval"
         )
      ),
      ref_symbols = letters[c(1:7,4,5)],
      part = "header",
      inline = TRUE
   )%>%
   add_header(Moderator = "",
              N = "",
              k = "",
              mu = "Effect Size",
              `CI_{L}` = "Effect Size",
              `CI_{U}` = "Effect Size",
              P  = "Effect Size",
              Efficacy = "PM control",
              `Eff CI_lower` = "PM control",
              `Eff CI upper` = "PM control") %>%
   merge_h( part = "header")%>%
   hline_top(part="all", border = officer::fp_border(color = "black", width = 2) )

disease_estimates_table
```

```{r eval=FALSE, include=FALSE}
# Save table as a word document
doc <- officer::read_docx()
doc <- body_add_flextable(doc, value = disease_estimates_table)
print(doc, target = "paper/figures/Table3_severity_esimates.docx")
```

<!--chapter:end:04_Severity_MetaAnalysis.Rmd-->

### 2021-03-26 01_TrialsForInclusionInAnalysis.Rmd
make gps locations generic

@@
       -27.51666,
-      -31.43449,
-      -27.923674,
-      -31.0142,
-      -31.00246,
+      -31.4514,
+      -27.87653,
+      -31.0245,
+      -31,
       -27.905313,
@@
       151.450,
-      150.0052,
-      151.242706,
-      150.05018,
-      149.82507,
+      149.9,
+      151.2567,
+      150.0618,
+      149.755,
       151.9772,

### 2021-03-26 02_Preliminary_analysis.Rmd
use minimal theme and lowercase labels

@@
    #      axis.ticks.x=element_blank())+
-   ggtitle("A")
+   ggtitle("A") +
+   theme_minimal()
 
@@
    # xlab("Spray Schedule")+
-   ggtitle("B")
+   ggtitle("B")+
+   theme_minimal()
 
@@
    #ylab(bquote('Mungbean grain yield ' *  ~  ~ t ~ ha ^ -1 * "")) +
-   xlab("Spray Schedule")+
-    theme(
-      axis.title.y = element_blank(),
+   xlab("Spray schedule")+
+   theme_minimal()+
+   theme(axis.title.y = element_blank(),
          axis.text.x = element_text(angle = 20, hjust = 0.75))

### 2021-03-27 index.Rmd
Reknit index with link to preprint
Add WAAA to acknowledgments for funding

@@
 ## Links to manuscript
-The manuscript publishing the results presented in this compendium can be found at ....
 
-Preprint at .........
+The preprint is available from agriRxiv: <https://doi.org/10.31220/agriRxiv.2021.00042>.
 
 ## Acknowledgments  
-This meta-analysis was carried out with the funding assistance of the Grains Research and Development Corporation in Australia.
+This meta-analysis was carried out with the funding assistance of the Grains Research and Development Corporation in Australia and the Western Australia Agriculture Authority.
 Raw data for this work were contributed by the University of Southern Queensland, Queensland Department of Agriculture, Fisheries and Forestry (DAF), and the Northern Grower Alliance.

### 2021-05-12 04_Severity_MetaAnalysis.Rmd
square transform severity and back transform estimates

@@
 hist(PM_dat_D$PM_final_severity)
+summary(PM_dat_D$PM_final_severity)
+```
+This meta-analysis assumes the effect size to be normally distributed, however, we can see here that it is skewed towards the top of the scale, eight and nine in this case.
+
+Traditionally disease severity is log transformed due to it being more likely to be skewed to the lower disease severity scores.
+In this case if we `log()` transformed the response it would increase the skew towards higher disease severity.
+
+We can improve the normality by transforming the effect size, disease severity, by squaring. As variance is proportional to the mean we square the variance aswell
+```{r}
+hist(PM_dat_D$PM_final_severity^2)
+summary(PM_dat_D$PM_final_severity^2)
 ```
 
+```{r}
+# dat1 <- escalc(measure = "MN", yi = PM_final_severity., vi = vi, ni = replicates, data = PM_dat_D, slab = paste0(trial, spray_management))
+
+PM_dat_D$yi_square <- PM_dat_D$PM_final_severity ^2
+PM_dat_D$vi_square <- (PM_dat_D$vi +1)^2
+```
+Note: Here I added 1 to the variance before it was squared.
+This is because squaring numbers below one makes the number smaller or remain zero.
+This does not change the meta-analysis estimates but does increase tao
 <br>  
@@
 ```{r Metafor-Sev-analysis, cache=TRUE}
+PMsev_mvSQ <- rma.mv(
+   yi = yi_square,
+   V = vi_square,
+   mods = ~ spray_management,
+   method = "ML",
+   random = list( ~ spray_management | trial, ~ 1 | id),
+   struct = "UN",
+   control = list(optimizer = "optim"),
+   data = PM_dat_D
+)
+
+summary(PMsev_mvSQ)
+```
+
+```{r Metafor-Sev-analysis, cache=TRUE}
+
 PMsev_mv <- rma.mv(
@@
 )
-
 summary(PMsev_mv)
@@
 
-contrast_Ssum %>%
+contrast_Ssum[6:15,] %>%
+   mutate(coefficients = -sqrt(abs(coefficients)),
+          StdErr = sqrt(StdErr))%>%
    flextable()%>%
@@
 par(mar = c(5, 13, 4, 2) + 0.1)
-plot(glht(PMsev_mv, linfct = cbind(contrMat(rep(
+plot(glht(PMsev_mvSQ, linfct = cbind(contrMat(rep(
    1, 6
@@
 
-intercept <- round(PMsev_mv$b, 4)[1,1]
+intercept <- round(PMsev_mvSQ$b, 4)[1,1]
 
@@
    k = k6,
-   Effect = round(PMsev_mv$b, 4),
-   se = round(PMsev_mv$se, 4),
-   CI_lower = round(PMsev_mv$ci.lb, 4),
-   CI_upper = round(PMsev_mv$ci.ub, 4),
-   z_val = round(PMsev_mv$zval, 4),
-   p_val = reportP(PMsev_mv$pval, AsNumeric = FALSE, P_prefix = FALSE),
-   eff_bar = round(1 -(intercept + PMsev_mv$b)/intercept,4)*100,
-   eff_CI_high = round(1 -(intercept + PMsev_mv$ci.ub)/intercept,4)*100,
-   eff_CI_low = round(1 -(intercept + PMsev_mv$ci.lb)/intercept,4)*100
+   Effect = round(sqrt(abs(PMsev_mvSQ$b)), 4),
+   se = round(sqrt(abs(PMsev_mvSQ$se)), 4),
+   CI_lower = round(sqrt(abs(PMsev_mvSQ$ci.lb)), 4),
+   CI_upper = round(sqrt(abs(PMsev_mvSQ$ci.ub)), 4),
+   z_val = round(sqrt(abs(PMsev_mvSQ$zval)), 4),
+   p_val = reportP(PMsev_mvSQ$pval, AsNumeric = FALSE, P_prefix = FALSE),
+   eff_bar = round(sqrt(abs(1 -(intercept + PMsev_mvSQ$b)/intercept)),4)*100,
+   eff_CI_high = round(sqrt(abs(1 -(intercept + PMsev_mvSQ$ci.ub)/intercept)),4)*100,
+   eff_CI_low = round(sqrt(abs(1 -(intercept + PMsev_mvSQ$ci.lb)/intercept)),4)*100
 
 )
+
+# restore negative numbers
+results_mv[2:6, c(4,6:8,10:12)] <- -results_mv[2:6, c(4,6:8,10:12)]
 

### 2021-05-13 04_Severity_MetaAnalysis.Rmd
correction in back-transformations of effect, se, and CI

@@
 
-intercept <- round(PMsev_mvSQ$b, 4)[1,1]
+intercept <- PMsev_mvSQ$b[1,1]
 
@@
    k = k6,
-   Effect = round(sqrt(abs(PMsev_mvSQ$b)), 4),
-   se = round(sqrt(abs(PMsev_mvSQ$se)), 4),
-   CI_lower = round(sqrt(abs(PMsev_mvSQ$ci.lb)), 4),
-   CI_upper = round(sqrt(abs(PMsev_mvSQ$ci.ub)), 4),
-   z_val = round(sqrt(abs(PMsev_mvSQ$zval)), 4),
+   Effect = ifelse(PMsev_mvSQ$b == intercept, sqrt(intercept),
+                   round(
+                      sqrt(PMsev_mvSQ$b + intercept) - sqrt(intercept), 4
+                   )),
+   se = round(
+      sqrt(
+         ifelse(PMsev_mvSQ$b == intercept, intercept,
+                PMsev_mvSQ$b + intercept) + PMsev_mvSQ$se) -
+         sqrt(
+            ifelse(PMsev_mvSQ$b == intercept, intercept,
+                   PMsev_mvSQ$b + intercept)),
+      4),
+   CI_lower = round(sqrt(PMsev_mvSQ$ci.lb + intercept) - sqrt(intercept), 4),
+   CI_upper = round(sqrt(PMsev_mvSQ$ci.ub + intercept) - sqrt(intercept), 4),
+   z_val = round(PMsev_mvSQ$zval, 4),
    p_val = reportP(PMsev_mvSQ$pval, AsNumeric = FALSE, P_prefix = FALSE),
-   eff_bar = round(sqrt(abs(1 -(intercept + PMsev_mvSQ$b)/intercept)),4)*100,
-   eff_CI_high = round(sqrt(abs(1 -(intercept + PMsev_mvSQ$ci.ub)/intercept)),4)*100,
-   eff_CI_low = round(sqrt(abs(1 -(intercept + PMsev_mvSQ$ci.lb)/intercept)),4)*100
+   eff_bar = round(sqrt(1 - (
+      intercept + PMsev_mvSQ$b
+   ) / intercept), 4) * 100,
+   eff_CI_high = round(sqrt(
+      1 - (intercept + PMsev_mvSQ$ci.ub) / intercept
+   ), 4) * 100,
+   eff_CI_low = round(sqrt(
+      1 - (intercept + PMsev_mvSQ$ci.lb) / intercept
+   ), 4) * 100
 

### 2021-05-13 04_Severity_MetaAnalysis.Rmd
can remove restoration of negative numbers now ifelse has been used and the new backtransformation
correct fungicide efficacy calculations

--- 2021-05-12 04_Severity_MetaAnalysis.Rmd
@@
    k = k6,
-   Effect = round(sqrt(abs(PMsev_mvSQ$b)), 4),
-   se = round(sqrt(abs(PMsev_mvSQ$se)), 4),
-   CI_lower = round(sqrt(abs(PMsev_mvSQ$ci.lb)), 4),
-   CI_upper = round(sqrt(abs(PMsev_mvSQ$ci.ub)), 4),
-   z_val = round(sqrt(abs(PMsev_mvSQ$zval)), 4),
-   p_val = reportP(PMsev_mvSQ$pval, AsNumeric = FALSE, P_prefix = FALSE),
-   eff_bar = round(sqrt(abs(1 -(intercept + PMsev_mvSQ$b)/intercept)),4)*100,
-   eff_CI_high = round(sqrt(abs(1 -(intercept + PMsev_mvSQ$ci.ub)/intercept)),4)*100,
-   eff_CI_low = round(sqrt(abs(1 -(intercept + PMsev_mvSQ$ci.lb)/intercept)),4)*100
+   Effect = ifelse(PMsev_mvSQ$b == intercept, sqrt(intercept),
+                   round(
+                      sqrt(PMsev_mvSQ$b + intercept) - sqrt(intercept), 4
+                   )),
+   se = round(
+      sqrt(
+         ifelse(PMsev_mvSQ$b == intercept, intercept,
+                PMsev_mvSQ$b + intercept) + PMsev_mvSQ$se) -
+         sqrt(
+            ifelse(PMsev_mvSQ$b == intercept, intercept,
+                   PMsev_mvSQ$b + intercept)),
+      4),
+   CI_lower = round(sqrt(PMsev_mvSQ$ci.lb + intercept) - sqrt(intercept), 4),
+   CI_upper = round(sqrt(PMsev_mvSQ$ci.ub + intercept) - sqrt(intercept), 4),
+   z_val = round(PMsev_mvSQ$zval, 4),
+   p_val = reportP(PMsev_mvSQ$pval, AsNumeric = FALSE, P_prefix = FALSE))
+
+results_mv <- 
+   results_mv %>%
+   mutate(
+   eff_bar = round(
+      1 - (sqrt(intercept) + Effect) /
+              sqrt(intercept), 
+      4) * 100,
+   eff_CI_high = round(
+      1 - (sqrt(intercept) + CI_upper) / sqrt(intercept)
+   , 4) * 100,
+   eff_CI_low = round(
+      1 - (sqrt(intercept) + CI_lower) / sqrt(intercept)
+   , 4) * 100
 
@@
 
-# restore negative numbers
-results_mv[2:6, c(4,6:8,10:12)] <- -results_mv[2:6, c(4,6:8,10:12)]
+# remove efficacy in control
+results_mv[1,10:12] <- NA
 
@@
 disease_estimates_table <-
-   flextable(results_mv[c(2,5,6,3,4), c(1:4,6:7, 9:12)]) %>%
+   flextable(results_mv[c(2,5,6,3,4), c(1:7, 9:12)]) %>%
    align(j = 2:10, align = "center", part = "all") %>%
@@
       i = 1,
-      j = c(2:10),
+      j = c(2:4,6:11),
       value = as_paragraph(
@@
             "estimated mean yield determined by the meta-analysis",
+
             "Lower range of the 95% confidence interval",
@@
               mu = "Effect Size",
+              se = "Effect Size",
               `CI_{L}` = "Effect Size",

### 2021-05-13 04_Severity_MetaAnalysis.Rmd
Wordsmithing and explainations, attempt analysis on percent severity

@@
 
-Inspect disease severity for a normality.
+### Inspect PM severity for normality
+Given the meta-analysis assumes powdery mildew severity observations to be a univariate normal distubution $Y_i = N(\mu , \sigma)$, with a mean $\mu$ and standard deviation $\sigma$.
+We need to inspect severity for a normality.
 ```{r sev_hist}
@@
 ```
-This meta-analysis assumes the effect size to be normally distributed, however, we can see here that it is skewed towards the top of the scale, eight and nine in this case.
+We can see here that powdery mildew severity observations are skewed towards the top of the scale, eight and nine in this case.
 
-Traditionally disease severity is log transformed due to it being more likely to be skewed to the lower disease severity scores.
+Traditionally disease severity is `log` transformed due to it being more likely to be skewed to the lower disease severity scores.
 In this case if we `log()` transformed the response it would increase the skew towards higher disease severity.
 
-We can improve the normality by transforming the effect size, disease severity, by squaring. As variance is proportional to the mean we square the variance aswell
+We can improve the normality by transforming the effect size, disease severity, by squaring.
 ```{r}
@@
 
-```{r}
-# dat1 <- escalc(measure = "MN", yi = PM_final_severity., vi = vi, ni = replicates, data = PM_dat_D, slab = paste0(trial, spray_management))
-
+### Transform severity response
+As variance is proportional to the mean we square the variance as well.
+```{r square_severity}
 PM_dat_D$yi_square <- PM_dat_D$PM_final_severity ^2
@@
 ```
-Note: Here I added 1 to the variance before it was squared.
+_Note: Here I added 1 to the variance before it was squared.
 This is because squaring numbers below one makes the number smaller or remain zero.
-This does not change the meta-analysis estimates but does increase tao
+This does not change the meta-analysis mean estimates but does increase heterogeneity and tao._
+
+Let us also transform the severity onto a percentage scale so we can compare the results of meta-analyses with no transformation, squared severity, and percent severity.
+
+```{r}
+PM_dat_D$yi_percent <- ((PM_dat_D$PM_final_severity - 1)/8) * 100
+PM_dat_D$vi_percent <- ((PM_dat_D$vi)/8)* 100
+```
+
 <br>  
@@
 ## Disease severity spray schedule meta-analysis  
+First lets look at the results of the meta-analysis without transformation
+```{r Metafor-Sev-analysis, cache=TRUE}
+PMsev_mv <- rma.mv(
+   yi = PM_final_severity,
+   vi,
+   mods = ~ spray_management,
+   method = "ML",
+   random = list( ~ spray_management | trial, ~ 1 | id),
+   struct = "UN",
+   control = list(optimizer = "optim"),
+   data = PM_dat_D
+)
+summary(PMsev_mv)
+```
 
+All spray schedules were effective at lowering the disease severity at the end of the season.
+`Recommended_plus` reduced powdery mildew incidence the most, however `Early` sprays are estimated as more effective than single `late` sprays and not significantly different to single `recommended` sprays at reducing powdery mildew severity assessed the end of the season.
+This does not reflect the results of the yield analysis.
+
+Next lets assess the square transformed severity
 ```{r Metafor-Sev-analysis, cache=TRUE}
@@
 ```
+This meta-analysis is more in-line with estimates from the yield meta-analysis.
+`Early` sprays are not effective at reducing powdery mildew severity and two or more sprays had higher efficacy than single sprays.
+Recommended sprays were the most effective spray timing at reducing disease severity.
 
+Finally lets assess the percent severity
 ```{r Metafor-Sev-analysis, cache=TRUE}
-
-PMsev_mv <- rma.mv(
-   yi = PM_final_severity,
-   vi,
+PMsev_mvSQ <- rma.mv(
+   yi = yi_percent,
+   V = vi_percent,
    mods = ~ spray_management,
@@
 )
-summary(PMsev_mv)
+
+summary(PMsev_mvSQ)
 ```
-
-All spray schedules were effective at lowering the disease severity at the end of the season.
-`Recommended_plus` reduced powdery mildew incidence the most.
-
 <br>  

### 2021-05-13 04_Severity_MetaAnalysis.Rmd
Correct namings and back transformations for contrasts

@@
 ```{r}
-PM_dat_D$yi_percent <- ((PM_dat_D$PM_final_severity - 1)/8) * 100
+PM_dat_D$yi_percent <- log(((PM_dat_D$PM_final_severity - 1)/8) * 100 +1)
 PM_dat_D$vi_percent <- ((PM_dat_D$vi)/8)* 100
+hist(PM_dat_D$yi_percent)
+summary(PM_dat_D$yi_percent)
 ```
@@
 ```{r Metafor-Sev-analysis, cache=TRUE}
-PMsev_mvSQ <- rma.mv(
+PMsev_mvPer <- rma.mv(
    yi = yi_percent,
@@
 
-summary(PMsev_mvSQ)
+summary(PMsev_mvPer)
 ```
+Model does not converge we will proceed with the square transformed severity
+
 <br>  
@@
 
+intercept <-PMsev_mvSQ$b[1,1]
+z <- PMsev_mvSQ$zval[1]
+
 contrast_Ssum <-
-   simple_summary(summary(glht(PMsev_mv, linfct = cbind(
+   simple_summary(summary(glht(PMsev_mvSQ, linfct = cbind(
       contrMat(rep(1, 6), type = "Tukey")
@@
 contrast_Ssum[6:15,] %>%
-   mutate(coefficients = -sqrt(abs(coefficients)),
-          StdErr = sqrt(StdErr))%>%
+   mutate(coefficients = sqrt(coefficients + intercept) - sqrt(intercept),
+          StdErr = sqrt(StdErr + intercept) - sqrt(intercept),
+          Zvalue = sqrt(Zvalue + z) - sqrt(z))%>%
    flextable()%>%
@@
 `Recommended_plus` limited disease severity significantly better than any other spray treatment. 
-`Late_plus` limited disease severity significantly better than a single `Late` application. 
-This indicates that two spray treatments were significantly better than a single application, but the timing of the fungicide application was more critical.
+Early sprays were not effective in decreasing disease severity.
+Two spray treatments were significantly better than a single application, but the timing of the fungicide application was more critical.
 

### 2021-05-13 04_Severity_MetaAnalysis.Rmd
update percent severity as a function of the median

@@
 ```{r}
-PM_dat_D$yi_percent <- log(((PM_dat_D$PM_final_severity - 1)/8) * 100 +1)
-PM_dat_D$vi_percent <- ((PM_dat_D$vi)/8)* 100
+PM_dat_D$yi_percent <- ((PM_dat_D$PM_final_severity)/median(PM_dat_D$PM_final_severity) * 100)
+PM_dat_D$vi_percent <- PM_dat_D$vi/median(PM_dat_D$PM_final_severity)
 hist(PM_dat_D$yi_percent)
@@
    yi = yi_percent,
-   V = vi_percent,
+   V = vi,
    mods = ~ spray_management,
@@
 summary(PMsev_mvPer)
+# Intecep <- coef(PMsev_mvPer)[1]
+# ((coef(PMsev_mvPer)[2:6]+ Intecep)/100)* median(PM_dat_D$PM_final_severity) - (Intecep/100*median(PM_dat_D$PM_final_severity))
 ```
@@
       "Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment.
-Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia.
+Estimates were back transformed using a square-root from the network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia.
 P values indicate statistical significance in comparison to the intercept."

### 2021-05-17 04_Severity_MetaAnalysis.Rmd
Gam predicted conversion for percent disease severity

@@
 ```{r}
-PM_dat_D$yi_percent <- ((PM_dat_D$PM_final_severity)/median(PM_dat_D$PM_final_severity) * 100)
-PM_dat_D$vi_percent <- PM_dat_D$vi/median(PM_dat_D$PM_final_severity)
-hist(PM_dat_D$yi_percent)
-summary(PM_dat_D$yi_percent)
+# Disease response ratio
+# create column giving the respective disease severity in the control 
+PM_dat_D$yi_C <- unlist(apply(PM_dat_D, 1, function(x1){
+
+   mean(PM_dat_D[PM_dat_D$trial == x1[["trial"]] &
+               PM_dat_D$spray_management == "control", "PM_final_severity"])
+}))
+
+# Calculate response ratio
+PM_dat_D$yi_RR <- PM_dat_D$PM_final_severity/PM_dat_D$yi_C
+hist(PM_dat_D[PM_dat_D$spray_management != "control", "yi_RR"])
+
+# Log response ratio 
+PM_dat_D$yi_LR <- log(PM_dat_D$yi_RR)
+hist(PM_dat_D[PM_dat_D$spray_management != "control", "yi_LR"])
+
+# Percent severity conversion
+# define ordinal conversion from scale to proportion
+s1 <- 0
+s2 <- 0.33*0.5
+s3 <- 0.5*0.87
+s4 <- 0.66*0.75
+s5 <- 0.66*0.87
+s6 <- 0.66*1
+s7 <- 0.75*1
+s8 <- 1*0.87
+s9 <- 1*1
+x <- c(s1, s2, s3, s4, s5, s6, s7, s8, s9)
+y <- c(1:9)
+a = data.frame(x,y)
+plot(a)
+
+# fit a curve using a gam with spline value 0.2
+g1 <- gam(x ~ s(y,spar = 0.1))
+
+# View plot of gam
+plot(x = predict(g1, data.frame(y= seq(1,9, by =0.1))), y= seq(1,9, by =0.1))
+points(x,y,col = "red", pch = 16)
+
+# predict values for dataset
+new_sev <- predict(object =  g1, 
+                   newdata = data.frame(y = PM_dat_D[,"PM_final_severity"])
+                   )
+# inspect distribution
+hist(new_sev)
+PM_dat_D$yi_percent <- new_sev
+
+# Conversion of variance
+# Here I add the variance and mean severity and predict the conversion value
+# then subtract the mean severity to obtain the difference as the sample variance
+PM_dat_D$vi_percent  <- predict(object =  g1, 
+                   newdata = data.frame(y = PM_dat_D[,"vi"] + PM_dat_D[,"PM_final_severity"])
+                   ) - PM_dat_D$yi_percent
+
+# campare untransformed variance to transformed variance
+summary(PM_dat_D$vi)
+summary(PM_dat_D$vi_percent)
+PM_dat_D[10:12,]
 ```

### 2021-05-17 04_Severity_MetaAnalysis.Rmd
add library(gam)

@@
                dplyr,
-               flextable)
+               flextable,
+               gam)
 

### 2021-05-17 04_Severity_MetaAnalysis.Rmd
attempt with log transformation

@@
 
-# campare untransformed variance to transformed variance
+# compare untransformed variance to transformed variance
 summary(PM_dat_D$vi)
 summary(PM_dat_D$vi_percent)
-PM_dat_D[10:12,]
+
+# scale to 100% 
+PM_dat_D$yi_percent  <- PM_dat_D$yi_percent * 100
+PM_dat_D$vi_percent  <- PM_dat_D$vi_percent * 100
+
+# scale to 100% 
+PM_dat_D$L_yi_p  <- log(PM_dat_D$yi_percent + 1 )
+PM_dat_D$L_vi_p  <- log(PM_dat_D$vi_percent +1 )
 ```
@@
 PMsev_mvPer <- rma.mv(
-   yi = yi_percent,
-   V = vi,
+   yi = L_yi_p,
+   V = L_vi_p,
    mods = ~ spray_management,

### 2021-05-17 04_Severity_MetaAnalysis.Rmd
try meta-analysis of the log response ratio

@@
 # scale to 100% 
-PM_dat_D$L_yi_p  <- log(PM_dat_D$yi_percent + 1 )
-PM_dat_D$L_vi_p  <- log(PM_dat_D$vi_percent +1 )
+# create column giving the respective disease severity in the control 
+PM_dat_D$yi_Cp <- unlist(apply(PM_dat_D, 1, function(x1){
+
+   mean(PM_dat_D[PM_dat_D$trial == x1[["trial"]] &
+               PM_dat_D$spray_management == "control", "yi_percent"])
+}))
+
+# calculate response ratio
+PM_dat_D$L_yi_p  <- log((PM_dat_D$yi_percent / PM_dat_D$yi_Cp) + 1)
+
+# transform variance as per Paul et. al 2007
+PM_dat_D <- 
+   PM_dat_D %>%
+   mutate(L_RR_v = vi *(1/replicates * (yi_percent ^ 2) + 1/replicates * (yi_Cp^2)))
 ```
@@
 ```{r Metafor-Sev-analysis, cache=TRUE}
+# remove controls for response ratio meta-analysis
+dat_RR <- PM_dat_D[PM_dat_D$spray_management != "control",]
+
 PMsev_mvPer <- rma.mv(
    yi = L_yi_p,
-   V = L_vi_p,
+   V = L_RR_v,
    mods = ~ spray_management,
@@
    control = list(optimizer = "optim"),
-   data = PM_dat_D
+   data = dat_RR
 )

### 2021-05-18 04_Severity_MetaAnalysis.Rmd
Logit transformed severity attempt

@@
                    )
+# one value is a negative, this should be a zero
+new_sev[12] <- 0
+
 # inspect distribution
@@
 # scale to 100% 
-PM_dat_D$yi_percent  <- PM_dat_D$yi_percent * 100
-PM_dat_D$vi_percent  <- PM_dat_D$vi_percent * 100
-
-# scale to 100% 
 # create column giving the respective disease severity in the control 
@@
    mutate(L_RR_v = vi *(1/replicates * (yi_percent ^ 2) + 1/replicates * (yi_Cp^2)))
+
+#logit transformed
+PM_dat_D$yi_logit <- log(
+   (PM_dat_D$yi_percent) / 
+      (1 - (PM_dat_D$yi_percent))
+   )
+hist(PM_dat_D$yi_logit)
+PM_dat_D$vi_logit <-
+   (PM_dat_D$vi_percent) /
+   (PM_dat_D$yi_percent * (1 - PM_dat_D$yi_percent)) ^ 2
+
+# Correct -Inf to zeros
+PM_dat_D[PM_dat_D$yi_logit == -Inf,"yi_logit"] <- 0.001
+PM_dat_D[PM_dat_D$vi_logit == -Inf,"vi_logit"] <- 0.001
 ```
@@
    struct = "UN",
-   control = list(optimizer = "optim"),
+   #control = list(optimizer = "optim"),
    data = PM_dat_D
@@
 # remove controls for response ratio meta-analysis
-dat_RR <- PM_dat_D[PM_dat_D$spray_management != "control",]
-
 PMsev_mvPer <- rma.mv(
-   yi = L_yi_p,
-   V = L_RR_v,
+   yi = yi_logit,
+   V = yi_logit,
    mods = ~ spray_management,
@@
    control = list(optimizer = "optim"),
-   data = dat_RR
+   data = PM_dat_D
 )
@@
 summary(PMsev_mvPer)
+
+#summary(PMsev_mvPer)
 # Intecep <- coef(PMsev_mvPer)[1]
@@
 Model does not converge we will proceed with the square transformed severity
+```{r}
+#logit transformed
+PM_dat_D$yi_logit <- log(
+   (PM_dat_D$yi_percent) / 
+      (1 - (PM_dat_D$yi_percent))
+   )
+
+1- LaplacesDemon::invlogit(PMsev_mvPer$b)
+mean(PM_dat_D[PM_dat_D$spray_management == "control","PM_final_severity"])
+mean(PM_dat_D[PM_dat_D$spray_management == "Recommended_plus","PM_final_severity"])
+
+```
 

### 2021-05-19 04_Severity_MetaAnalysis.Rmd
add log of pecent severity meta-analysis, and plots of the residuals

@@
 
-# scale to 100% 
+# create log transformed values
+PM_dat_D$yi_log <- log(PM_dat_D$yi_percent)
+PM_dat_D$vi_log <- (PM_dat_D$vi_percent) / (PM_dat_D$replicates * PM_dat_D$yi_percent^2)
+
+PM_dat_D[PM_dat_D$yi_log == -Inf,"yi_log"] <- 0
+PM_dat_D[PM_dat_D$vi_log == -Inf,"vi_log"] <- 0.001
+
 # create column giving the respective disease severity in the control 
@@
 
-#logit transformed
+#logit transformed percentages
 PM_dat_D$yi_logit <- log(
@@
 summary(PMsev_mv)
+plot(rstandard(PMsev_mv)$z, ylim=c(-3,3), pch=19)
 ```
@@
 summary(PMsev_mvSQ)
+plot(rstandard(PMsev_mvSQ)$z, ylim=c(-3,3), pch=19)
 ```
@@
 
-Finally lets assess the percent severity
-```{r Metafor-Sev-analysis, cache=TRUE}
+Finally lets assess the logit transformed percent severity
+```{r Metafor-Sev-analysis_log, cache=TRUE}
+# remove controls for response ratio meta-analysis
+PMsev_mv_log <- rma.mv(
+   yi = yi_log,
+   V = yi_log,
+   mods = ~ spray_management,
+   method = "ML",
+   random = list( ~ spray_management | trial, ~ 1 | id),
+   struct = "US",
+   control = list(optimizer = "optim"),
+   data = PM_dat_D
+)
+
+summary(PMsev_mv_log)
+plot(rstandard(PMsev_mv_log)$z, ylim=c(-3,3), pch=19)
+data.frame(cbind((1-exp(PMsev_mv_log$b)),
+                              (1-exp(PMsev_mv_log$ci.lb)),
+                              (1-exp(PMsev_mv_log$ci.ub))))
+```
+
+Finally lets assess the logit transformed percent severity
+```{r Metafor-Sev-analysis_logitP, cache=TRUE}
 # remove controls for response ratio meta-analysis
@@
 
-#summary(PMsev_mvPer)
-# Intecep <- coef(PMsev_mvPer)[1]
-# ((coef(PMsev_mvPer)[2:6]+ Intecep)/100)* median(PM_dat_D$PM_final_severity) - (Intecep/100*median(PM_dat_D$PM_final_severity))
+1- LaplacesDemon::invlogit(PMsev_mvPer$b)
+mean(PM_dat_D[PM_dat_D$spray_management == "control","PM_final_severity"])
+mean(PM_dat_D[PM_dat_D$spray_management == "Recommended_plus","PM_final_severity"])
 ```
-Model does not converge we will proceed with the square transformed severity
+This produces estimates which are too high and likely incorrect
+
+```{r Metafor-Sev-analysis_logit, cache=TRUE}
+#logit transformed 1- 9 values
+PM_dat_D$yi_logit <- log(
+   ((PM_dat_D$PM_final_severity-1)/8) / 
+      (1 - ((PM_dat_D$PM_final_severity-1)/8))
+   )
+
+PM_dat_D$vi_logit <-
+   (PM_dat_D$vi) /
+   (((PM_dat_D$PM_final_severity-1)/8) * (1 -((PM_dat_D$PM_final_severity-1)/8))) ^ 2
+
+# Correct -Inf to zeros
+PM_dat_D[PM_dat_D$yi_logit == -Inf |
+            PM_dat_D$yi_logit == Inf ,"yi_logit"] <- 0
+PM_dat_D[is.na(PM_dat_D$vi_logit == Inf),"vi_logit"] <- 0
+
+PM_dat_D[PM_dat_D$vi_logit <= 0,"vi_logit"] <- 0.001
+# remove controls for response ratio meta-analysis
+PMsev_mvPer <- rma.mv(
+   yi = yi_logit,
+   V = yi_logit,
+   mods = ~ spray_management,
+   method = "ML",
+   random = list( ~ spray_management | trial, ~ 1 | id),
+   struct = "UN",
+   control = list(optimizer = "optim"),
+   data = PM_dat_D
+)
+
+summary(PMsev_mvPer)
+```
+
 ```{r}

### 2021-05-19 04_Severity_MetaAnalysis.Rmd
add residual plots and intercept correction on back calculation

@@
 summary(PMsev_mvPer)
+plot(rstandard(PMsev_mvPer)$z, ylim=c(-3,3), pch=19)
 
-1- LaplacesDemon::invlogit(PMsev_mvPer$b)
+1- LaplacesDemon::invlogit(PMsev_mvPer$b + PMsev_mvPer$b[1])
 mean(PM_dat_D[PM_dat_D$spray_management == "control","PM_final_severity"])

### 2021-05-19 04_Severity_MetaAnalysis.Rmd
define logit functions and simplify explainations towards using logit transformation

--- 2021-05-19 04_Severity_MetaAnalysis.Rmd
@@
    read.csv("cache/PM_disease_clean_data.csv", stringsAsFactors = FALSE)
+
+# functions
+logit <- function(x){
+   log((x)/(1 - x))
+}
+
+inv_logit <- function(x){
+   exp(x)/(1 + exp(x))
+}
+
 ```
@@
 #logit transformed percentages
-PM_dat_D$yi_logit <- log(
-   (PM_dat_D$yi_percent) / 
-      (1 - (PM_dat_D$yi_percent))
-   )
+PM_dat_D$yi_logit <- logit(PM_dat_D$yi_percent)
+
 hist(PM_dat_D$yi_logit)
@@
 
-Finally lets assess the logit transformed percent severity
+However square severity is not common when evaluating a response that was obtained on a scale.
+Log transformed is a more common method of evaluating non-normal disease severity.
+
+Lets assess the log transformed percent severity
 ```{r Metafor-Sev-analysis_log, cache=TRUE}
@@
 summary(PMsev_mv_log)
-plot(rstandard(PMsev_mv_log)$z, ylim=c(-3,3), pch=19)
-data.frame(cbind((1-exp(PMsev_mv_log$b)),
-                              (1-exp(PMsev_mv_log$ci.lb)),
-                              (1-exp(PMsev_mv_log$ci.ub))))
+plot(rstandard(PMsev_mv_log)$z, ylim=c(-3.2,3), pch=19)
+data.frame(Estimates = (1-exp(PMsev_mv_log$b)),
+           lowerCI = (1-exp(PMsev_mv_log$ci.lb)),
+           upperCI = (1-exp(PMsev_mv_log$ci.ub)))
 ```
+The plot of the residuals show the model is not normally distributed.
+In addition the estimates don't reflect what can be [observed in the raw data][Disease severity range for each spray schedule].
+Log transformed percent severity is therefore no a suitable transformation
 
@@
 
-1- LaplacesDemon::invlogit(PMsev_mvPer$b)
-mean(PM_dat_D[PM_dat_D$spray_management == "control","PM_final_severity"])
-mean(PM_dat_D[PM_dat_D$spray_management == "Recommended_plus","PM_final_severity"])
-```
-This produces estimates which are too high and likely incorrect
+# plot the model residuals
+plot(rstandard(PMsev_mvPer)$z, ylim=c(-3,3), pch=19)
 
-```{r Metafor-Sev-analysis_logit, cache=TRUE}
-#logit transformed 1- 9 values
-PM_dat_D$yi_logit <- log(
-   ((PM_dat_D$PM_final_severity-1)/8) / 
-      (1 - ((PM_dat_D$PM_final_severity-1)/8))
-   )
-
-PM_dat_D$vi_logit <-
-   (PM_dat_D$vi) /
-   (((PM_dat_D$PM_final_severity-1)/8) * (1 -((PM_dat_D$PM_final_severity-1)/8))) ^ 2
-
-# Correct -Inf to zeros
-PM_dat_D[PM_dat_D$yi_logit == -Inf |
-            PM_dat_D$yi_logit == Inf ,"yi_logit"] <- 0
-PM_dat_D[is.na(PM_dat_D$vi_logit == Inf),"vi_logit"] <- 0
-
-PM_dat_D[PM_dat_D$vi_logit <= 0,"vi_logit"] <- 0.001
-# remove controls for response ratio meta-analysis
-PMsev_mvPer <- rma.mv(
-   yi = yi_logit,
-   V = yi_logit,
-   mods = ~ spray_management,
-   method = "ML",
-   random = list( ~ spray_management | trial, ~ 1 | id),
-   struct = "UN",
-   control = list(optimizer = "optim"),
-   data = PM_dat_D
-)
-
-summary(PMsev_mvPer)
-```
-
-```{r}
-#logit transformed
-PM_dat_D$yi_logit <- log(
-   (PM_dat_D$yi_percent) / 
-      (1 - (PM_dat_D$yi_percent))
-   )
-
-1- LaplacesDemon::invlogit(PMsev_mvPer$b)
-mean(PM_dat_D[PM_dat_D$spray_management == "control","PM_final_severity"])
-mean(PM_dat_D[PM_dat_D$spray_management == "Recommended_plus","PM_final_severity"])
-
+1 - exp(PMsev_mvPer$b + PMsev_mvPer$b[1])/(1+exp(PMsev_mvPer$b + PMsev_mvPer$b[1]))
+logit_estimates <- ifelse(PMsev_mvPer$b == PMsev_mvPer$b[1], PMsev_mvPer$b, PMsev_mvPer$b + PMsev_mvPer$b[1])
+1 - inv_logit(logit_estimates)
 ```

### 2021-05-19 04_Severity_MetaAnalysis.Rmd
add function to backtransform model estimates

@@
 plot(rstandard(PMsev_mvPer)$z, ylim=c(-3,3), pch=19)
+```
 
+```{r logit_estimates}
 1 - exp(PMsev_mvPer$b + PMsev_mvPer$b[1])/(1+exp(PMsev_mvPer$b + PMsev_mvPer$b[1]))
@@
 1 - inv_logit(logit_estimates)
+
+backtransform <- function(m, input_only = FALSE, intercept) {
+   if (input_only == FALSE) {
+      intercept <- m$b[1]
+
+      dat <- data.frame(
+         estimates = 1 - inv_logit(c(intercept, m$b[-1] + intercept)),
+         StdErr = inv_logit(m$se + intercept) - inv_logit(intercept),
+         Zval = c(inv_logit(m$z[1]),
+                  inv_logit(m$z[-1] + m$z[1]) - inv_logit(m$z[1])),
+         Pval = reportP(m$pval, P_prefix = FALSE),
+         CI_lb = 1 - c(inv_logit(m$ci.lb[1]), 
+                       inv_logit(m$ci.lb[-1] + intercept)),
+         CI_ub = 1 - c(inv_logit(m$ci.ub[1]), 
+                       inv_logit(m$ci.ub[-1] + intercept)) 
+      )
+   }
+   if (input_only == TRUE) {
+      if (missing(intercept))
+         stop("'intercept' argument is empty")
+     return( inv_logit(m + intercept) - inv_logit(intercept))
+   }
+   return(dat)
+}
+backtransform(PMsev_mvPer)
 ```
@@
 contrast_Ssum <-
-   simple_summary(summary(glht(PMsev_mvSQ, linfct = cbind(
+   simple_summary(summary(glht(PMsev_mvPer, linfct = cbind(
       contrMat(rep(1, 6), type = "Tukey")
@@
 par(mar = c(5, 13, 4, 2) + 0.1)
-plot(glht(PMsev_mvSQ, linfct = cbind(contrMat(rep(
+plot(glht(PMsev_mvPer, linfct = cbind(contrMat(rep(
    1, 6

### 2021-05-19 04_Severity_MetaAnalysis.Rmd
tidy up estimates chunk

@@
 ```{r logit_estimates}
-1 - exp(PMsev_mvPer$b + PMsev_mvPer$b[1])/(1+exp(PMsev_mvPer$b + PMsev_mvPer$b[1]))
-logit_estimates <- ifelse(PMsev_mvPer$b == PMsev_mvPer$b[1], PMsev_mvPer$b, PMsev_mvPer$b + PMsev_mvPer$b[1])
-1 - inv_logit(logit_estimates)
-
 backtransform <- function(m, input_only = FALSE, intercept) {
@@
          CI_ub = 1 - c(inv_logit(m$ci.ub[1]), 
-                       inv_logit(m$ci.ub[-1] + intercept)) 
+                       inv_logit(m$ci.ub[-1] + intercept)), 
+         row.names = colnames(m$G)
       )
@@
 }
+
 backtransform(PMsev_mvPer)

### 2021-05-20 04_Severity_MetaAnalysis.Rmd
Remove irrelavant calculations and add some words

@@
 ### Inspect PM severity for normality
-Given the meta-analysis assumes powdery mildew severity observations to be a univariate normal distubution $Y_i = N(\mu , \sigma)$, with a mean $\mu$ and standard deviation $\sigma$.
+Given the meta-analysis assumes powdery mildew severity observations to be a univariate normal distribution $Y_i = N(\mu , \sigma)$, with a mean $\mu$ and standard deviation $\sigma$.
 We need to inspect severity for a normality.
@@
 
-Traditionally disease severity is `log` transformed due to it being more likely to be skewed to the lower disease severity scores.
-In this case if we `log()` transformed the response it would increase the skew towards higher disease severity.
-
 We can improve the normality by transforming the effect size, disease severity, by squaring.
 ```{r}
-hist(PM_dat_D$PM_final_severity^2)
-summary(PM_dat_D$PM_final_severity^2)
+PM_dat_D$yi_square <- PM_dat_D$PM_final_severity ^2
+PM_dat_D$vi_square <- (PM_dat_D$vi +1)^2
+# Note: Here I added 1 to the variance before it was squared.
+This is because squaring numbers below one makes the number smaller or remain zero.
+This does not change the meta-analysis mean estimates but does increase heterogeneity and tao._
+
+hist(PM_dat_D$yi_square)
+summary(PM_dat_D$yi_square)
 ```
 
+Another transformation which might be more suitable for a discrete response is either a `log()` or `logit()` transformation. 
+However first we should convert the scale from 1 - 9 to between 0 and 1.
+
 ### Transform severity response
-As variance is proportional to the mean we square the variance as well.
-```{r square_severity}
-PM_dat_D$yi_square <- PM_dat_D$PM_final_severity ^2
-PM_dat_D$vi_square <- (PM_dat_D$vi +1)^2
-```
-_Note: Here I added 1 to the variance before it was squared.
-This is because squaring numbers below one makes the number smaller or remain zero.
-This does not change the meta-analysis mean estimates but does increase heterogeneity and tao._
 
@@
 ```{r}
-# Disease response ratio
-# create column giving the respective disease severity in the control 
-PM_dat_D$yi_C <- unlist(apply(PM_dat_D, 1, function(x1){
-
-   mean(PM_dat_D[PM_dat_D$trial == x1[["trial"]] &
-               PM_dat_D$spray_management == "control", "PM_final_severity"])
-}))
-
-# Calculate response ratio
-PM_dat_D$yi_RR <- PM_dat_D$PM_final_severity/PM_dat_D$yi_C
-hist(PM_dat_D[PM_dat_D$spray_management != "control", "yi_RR"])
-
-# Log response ratio 
-PM_dat_D$yi_LR <- log(PM_dat_D$yi_RR)
-hist(PM_dat_D[PM_dat_D$spray_management != "control", "yi_LR"])
-
 # Percent severity conversion
@@
 plot(a)
+```
 
+We can fit a gam curve between the 1 - 9 scale and the new scale between 0 and 1
+```{r}
 # fit a curve using a gam with spline value 0.2
@@
                    )
+# Check fit
+plot(x = new_sev, y = PM_dat_D[,"PM_final_severity"])
+points(x,y,col = "red", pch = 16)
+```
+
+```{r}
 # one value is a negative, this should be a zero
-new_sev[12] <- 0
+# new_sev[12] <- 0
 
-# inspect distribution
-hist(new_sev)
+# Allocate new variable percent severity
 PM_dat_D$yi_percent <- new_sev
@@
 
-# compare untransformed variance to transformed variance
-summary(PM_dat_D$vi)
-summary(PM_dat_D$vi_percent)
-
 # create log transformed values
@@
 
+# Correct Inf to 0
 PM_dat_D[PM_dat_D$yi_log == -Inf,"yi_log"] <- 0
 PM_dat_D[PM_dat_D$vi_log == -Inf,"vi_log"] <- 0.001
-
-# create column giving the respective disease severity in the control 
-PM_dat_D$yi_Cp <- unlist(apply(PM_dat_D, 1, function(x1){
-
-   mean(PM_dat_D[PM_dat_D$trial == x1[["trial"]] &
-               PM_dat_D$spray_management == "control", "yi_percent"])
-}))
-
-# calculate response ratio
-PM_dat_D$L_yi_p  <- log((PM_dat_D$yi_percent / PM_dat_D$yi_Cp) + 1)
-
-# transform variance as per Paul et. al 2007
-PM_dat_D <- 
-   PM_dat_D %>%
-   mutate(L_RR_v = vi *(1/replicates * (yi_percent ^ 2) + 1/replicates * (yi_Cp^2)))
 

### 2021-05-20 04_Severity_MetaAnalysis.Rmd
simplify correction of neg values to once

@@
 # Correct Inf to 0
-PM_dat_D[PM_dat_D$yi_log == -Inf,"yi_log"] <- 0
+PM_dat_D[is.na(PM_dat_D$yi_log),"yi_log"] <- 0
 PM_dat_D[PM_dat_D$vi_log == -Inf,"vi_log"] <- 0.001
@@
 
-hist(PM_dat_D$yi_logit)
+# logit transformed variance
 PM_dat_D$vi_logit <-
@@
 # Correct -Inf to zeros
-PM_dat_D[PM_dat_D$yi_logit == -Inf,"yi_logit"] <- 0.001
-PM_dat_D[PM_dat_D$vi_logit == -Inf,"vi_logit"] <- 0.001
+PM_dat_D[is.na(PM_dat_D$yi_logit),"yi_logit"] <- 0.000
+
 ```

### 2021-05-21 04_Severity_MetaAnalysis.Rmd
Update wording and backtransformation to show severity estimates

@@
 # Correct -Inf to zeros
-PM_dat_D[is.na(PM_dat_D$yi_logit),"yi_logit"] <- 0.000
+PM_dat_D[is.na(PM_dat_D$yi_logit),"yi_logit"] <- 0
 
@@
 
-All spray schedules were effective at lowering the disease severity at the end of the season.
-`Recommended_plus` reduced powdery mildew incidence the most, however `Early` sprays are estimated as more effective than single `late` sprays and not significantly different to single `recommended` sprays at reducing powdery mildew severity assessed the end of the season.
-This does not reflect the results of the yield analysis.
+This analysis shows the residual are slightly unbalanced and perhaps an effect of time. 
+Does squaring the response improve the residuals?
 
-Next lets assess the square transformed severity
 ```{r Metafor-Sev-analysis, cache=TRUE}
@@
    random = list( ~ spray_management | trial, ~ 1 | id),
-   struct = "US",
+   struct = "UN",
    control = list(optimizer = "optim"),
@@
 plot(rstandard(PMsev_mv_log)$z, ylim=c(-3.2,3), pch=19)
-data.frame(Estimates = (1-exp(PMsev_mv_log$b)),
-           lowerCI = (1-exp(PMsev_mv_log$ci.lb)),
-           upperCI = (1-exp(PMsev_mv_log$ci.ub)))
 ```
@@
 
+The estimates and significance from this model better reflect the distribution of raw values. 
+In addition the residuals from this model are more evenly distributed.
+Let's back transform the estimates.
+
 ```{r logit_estimates}
@@
       dat <- data.frame(
-         estimates = 1 - inv_logit(c(intercept, m$b[-1] + intercept)),
+         estimates = inv_logit(c(intercept, m$b[-1] + intercept)),
          StdErr = inv_logit(m$se + intercept) - inv_logit(intercept),
@@
          Pval = reportP(m$pval, P_prefix = FALSE),
-         CI_lb = 1 - c(inv_logit(m$ci.lb[1]), 
+         CI_lb = c(inv_logit(m$ci.lb[1]), 
                        inv_logit(m$ci.lb[-1] + intercept)),
-         CI_ub = 1 - c(inv_logit(m$ci.ub[1]), 
+         CI_ub = c(inv_logit(m$ci.ub[1]), 
                        inv_logit(m$ci.ub[-1] + intercept)), 
@@
 
-Calculate the treatment contrasts
+Calculate the treatment contrasts without back-transformation.
 
@@
 
-intercept <-PMsev_mvSQ$b[1,1]
-z <- PMsev_mvSQ$zval[1]
+intercept <-PMsev_mvPer$b[1,1]
+z <- PMsev_mvPer$zval[1]
 
@@
 contrast_Ssum[6:15,] %>%
-   mutate(coefficients = sqrt(coefficients + intercept) - sqrt(intercept),
-          StdErr = sqrt(StdErr + intercept) - sqrt(intercept),
-          Zvalue = sqrt(Zvalue + z) - sqrt(z))%>%
    flextable()%>%

### 2021-05-21 04_Severity_MetaAnalysis.Rmd
Update model estimates table with results from logit model

@@
 
-intercept <- PMsev_mvSQ$b[1,1]
-
-# create data.frame
-results_mv <- data.frame(
+# create data.frame of percent disease severity estimates
+results_mv <- cbind(
+   data.frame(
       Moderator = c(
@@
       N = k5,
-   k = k6,
-   Effect = ifelse(PMsev_mvSQ$b == intercept, sqrt(intercept),
-                   round(
-                      sqrt(PMsev_mvSQ$b + intercept) - sqrt(intercept), 4
-                   )),
-   se = round(
-      sqrt(
-         ifelse(PMsev_mvSQ$b == intercept, intercept,
-                PMsev_mvSQ$b + intercept) + PMsev_mvSQ$se) -
-         sqrt(
-            ifelse(PMsev_mvSQ$b == intercept, intercept,
-                   PMsev_mvSQ$b + intercept)),
-      4),
-   CI_lower = round(sqrt(PMsev_mvSQ$ci.lb + intercept) - sqrt(intercept), 4),
-   CI_upper = round(sqrt(PMsev_mvSQ$ci.ub + intercept) - sqrt(intercept), 4),
-   z_val = round(PMsev_mvSQ$zval, 4),
-   p_val = reportP(PMsev_mvSQ$pval, AsNumeric = FALSE, P_prefix = FALSE))
+      k = k6
+   ),
+   backtransform(PMsev_mvPer))
+
+# round the numbers
+results_mv[,c(4:6,8:9)] <- round(results_mv[,c(4:6,8:9)], 4)
 
@@
    eff_bar = round(
-      1 - (sqrt(intercept) + Effect) /
-              sqrt(intercept), 
+      1 - estimates, 
       4) * 100,
    eff_CI_high = round(
-      1 - (sqrt(intercept) + CI_upper) / sqrt(intercept)
+      1 - CI_lb
    , 4) * 100,
    eff_CI_low = round(
-      1 - (sqrt(intercept) + CI_lower) / sqrt(intercept)
+      1 - CI_ub
    , 4) * 100
@@
 # rename colnames to give table headings
-colnames(results_mv)[c(1:4,6:12 )] <-
+colnames(results_mv)[c(1:12 )] <-
    c("Moderator",
@@
      "mu",
+     "se",
+     "Z",
+     "P",
      "CI_{L}",
      "CI_{U}",
-     "Z",
-     "P",
      "Efficacy",
@@
 disease_estimates_table <-
-   flextable(results_mv[c(2,5,6,3,4), c(1:7, 9:12)]) %>%
+   flextable(results_mv[c(2,5,6,3,4), ]) %>%
    align(j = 2:10, align = "center", part = "all") %>%
@@
    set_caption(
-      "Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment.
-Estimates were back transformed using a square-root from the network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia.
+      "Table 3: Estimated powdery mildew severity for each spray schedule treatment.
+Estimates were back transformed using a inverse logit from the network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia.
 P values indicate statistical significance in comparison to the intercept."
@@
       i = 1,
-      j = c(2:4,6:11),
+      j = c(2:4,7:12),
       value = as_paragraph(
@@
             "number of trials with the respective spray schedule",
-            "estimated mean yield determined by the meta-analysis",
-
+            "estimated mean disease severity",
+            "indicates the significance between each respective spray schedule and the no spray control (intercept)",
             "Lower range of the 95% confidence interval",
             "Upper range of the 95% confidence interval",
-            "indicates the significance between each respective spray schedule and the no spray control (intercept)",
-            "Fungicide spray schedule efficacy",
+            "Fungicide spray schedule percent efficacy",
             "Lower range of the 95% confidence interval",
@@
               se = "Effect Size",
+              Z = "Effect Size",
               `CI_{L}` = "Effect Size",

### 2021-05-25 04_Severity_MetaAnalysis.Rmd
add clubsandwich library

@@
                flextable,
-               gam)
+               gam,
+               clubSandwich)
 
@@
 plot(rstandard(PMsev_mvPer)$z, ylim=c(-3,3), pch=19)
+
 ```

### 2021-05-25 02_Preliminary_analysis.Rmd
add severity rating table to compendium, and save for paper

@@
 <br>  
+## Define powdery mildew severity
+Powdery mildew severity was assessed on a 1 - 9 scale.
+```{r disease_scale}
+d_rating_table <-
+   data.frame(
+      Severity_rating = 1:9,
+      Description = c(
+         "No sign of powdery mildew",
+         "Small colonies in the lower 1/3 of canopy with up to 75% of plants infected",
+         "Colonies in lower half of canopy with more than 75% of plants infected",
+         "Colonies in lower 2/3 of canopy with up to 75% of plants infected",
+         "Colonies in lower 2/3 of canopy with more than 75% of plants infected",
+         "Colonies in lower 2/3 of canopy with 100% of plants infected",
+         "Colonies in lower 2/3 of canopy with 100% of plants infected, some plants with colonies in the top 1/3 of the canopy",
+         "Colonies all the way to the top of the plant with more than 75% of plants affected",
+         "Colonies all the way to the top of the plant with severe leaf drop"
+      )
+   ) %>%
+   flextable() %>%
+   autofit() %>%
+   set_header_labels(Severity_rating = "Severity rating") %>%
+   align(j = 1, align = "center")
+d_rating_table
+```
+```{r eval=FALSE, include=FALSE}
+# Save table as a word document
+doc <- officer::read_docx()
+doc <- body_add_flextable(doc, value = d_rating_table)
+print(doc, target = "paper/figures/SeverityTable.docx")
+```
 

### 2021-05-27 04_Severity_MetaAnalysis.Rmd
Capitalise sentances

@@
          c(
-            "number of treatment means categorised to each spray schedule",
-            "number of trials with the respective spray schedule",
-            "estimated mean disease severity",
-            "indicates the significance between each respective spray schedule and the no spray control (intercept)",
+            "Number of treatment means categorised to each spray schedule",
+            "Number of trials with the respective spray schedule",
+            "Estimated mean disease severity",
+            "Indicates the significance between each respective spray schedule and the no spray control (intercept)",
             "Lower range of the 95% confidence interval",

### 2021-05-27 04_Severity_MetaAnalysis.Rmd
Remove percent efficacy from estimates table

@@
 
+# Calculate mean differences
+Intcpt <- results_mv$estimates[1]
+results_mv <- 
+   results_mv %>%
+   mutate(estimates = estimates - Intcpt,
+          CI_lb = CI_lb - Intcpt,
+          CI_ub = CI_lb - Intcpt)
+
 # round the numbers
@@
 
-results_mv <- 
-   results_mv %>%
-   mutate(
-   eff_bar = round(
-      1 - estimates, 
-      4) * 100,
-   eff_CI_high = round(
-      1 - CI_lb
-   , 4) * 100,
-   eff_CI_low = round(
-      1 - CI_ub
-   , 4) * 100
-
-)
+# results_mv <- 
+#    results_mv %>%
+#    mutate(
+#    eff_bar = round(
+#       1 - estimates, 
+#       4) * 100,
+#    eff_CI_high = round(
+#       1 - CI_lb
+#    , 4) * 100,
+#    eff_CI_low = round(
+#       1 - CI_ub
+#    , 4) * 100
+#    
+# )
 
 # remove efficacy in control
-results_mv[1,10:12] <- NA
+#results_mv[1,10:12] <- NA
 
@@
      "CI_{L}",
-     "CI_{U}",
-     "Efficacy",
-     "Eff CI_lower",
-     "Eff CI upper")
+     "CI_{U}")
 
 disease_estimates_table <-
-   flextable(results_mv[c(2,5,6,3,4), ]) %>%
-   align(j = 2:10, align = "center", part = "all") %>%
+   results_mv[c(2,5,6,3,4), -6] %>%
+   flextable() %>%
+   align(j = 2:8, align = "center", part = "all") %>%
    fontsize(size = 8, part = "body") %>%
@@
    set_caption(
-      "Table 3: Estimated powdery mildew severity for each spray schedule treatment.
+      "Table 3: Estimated powdery mildew severity mean difference for each spray schedule treatment.
 Estimates were back transformed using a inverse logit from the network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia.
@@
    ) %>%
-   autofit() %>%
    footnote(
       i = 1,
-      j = c(2:4,7:12),
+      j = c(2:4,6:8),
       value = as_paragraph(
@@
             "Indicates the significance between each respective spray schedule and the no spray control (intercept)",
-            "Lower range of the 95% confidence interval",
-            "Upper range of the 95% confidence interval",
-            "Fungicide spray schedule percent efficacy",
             "Lower range of the 95% confidence interval",
@@
               se = "Effect Size",
-              Z = "Effect Size",
               `CI_{L}` = "Effect Size",
               `CI_{U}` = "Effect Size",
-              P  = "Effect Size",
-              Efficacy = "PM control",
-              `Eff CI_lower` = "PM control",
-              `Eff CI upper` = "PM control") %>%
+              P  = "Effect Size") %>%
    merge_h( part = "header")%>%
-   hline_top(part="all", border = officer::fp_border(color = "black", width = 2) )
+   hline_top(part="all", border = officer::fp_border(color = "black", width = 2))%>%
+   width(j = 1, width = 1) %>%
+   width(j = 2, width = 0.3) %>%
+   width(j = 3, width = 0.3) %>%
+   width(j = 4:8, width = 0.6)
 

### 2021-05-27 04_Severity_MetaAnalysis.Rmd
remove header

@@
 # rename colnames to give table headings
-colnames(results_mv)[c(1:12 )] <-
+colnames(results_mv)[c(1:9 )] <-
    c("Moderator",
@@
       ),
-      ref_symbols = letters[c(1:7,4,5)],
+      ref_symbols = letters[c(1:6)],
       part = "header",
@@
     )%>%
-   add_header(Moderator = "",
-              N = "",
-              k = "",
-              mu = "Effect Size",
-              se = "Effect Size",
-              `CI_{L}` = "Effect Size",
-              `CI_{U}` = "Effect Size",
-              P  = "Effect Size") %>%
-   merge_h( part = "header")%>%
+   # add_header(Moderator = "",
+   #            N = "",
+   #            k = "",
+   #            mu = "Effect Size",
+   #            se = "Effect Size",
+   #            `CI_{L}` = "Effect Size",
+   #            `CI_{U}` = "Effect Size",
+   #            P  = "Effect Size") %>%
+   # merge_h( part = "header")%>%
    hline_top(part="all", border = officer::fp_border(color = "black", width = 2))%>%

### 2021-05-27 04_Severity_MetaAnalysis.Rmd
Remove headers and update table title

@@
    set_caption(
-      "Table 3: Estimated powdery mildew severity mean difference for each spray schedule treatment.
-Estimates were back transformed using a inverse logit from the network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia.
+      "Table 3: Estimated powdery mildew severity mean difference for each spray schedule treatment to the unsprayed control treatments.
+Meta-analysis estimates were back transformed using an inverse logit.
+Data were obtained from the grey literature reports of (k) field trials undertaken in Eastern Australia.
 P values indicate statistical significance in comparison to the intercept."
@@
     )%>%
-   # add_header(Moderator = "",
-   #            N = "",
-   #            k = "",
-   #            mu = "Effect Size",
-   #            se = "Effect Size",
-   #            `CI_{L}` = "Effect Size",
-   #            `CI_{U}` = "Effect Size",
-   #            P  = "Effect Size") %>%
-   # merge_h( part = "header")%>%
    hline_top(part="all", border = officer::fp_border(color = "black", width = 2))%>%

### 2021-05-27 02_Preliminary_analysis.Rmd
Add severity percentages and edit table widths

--- 2021-03-26 02_Preliminary_analysis.Rmd
@@
 <br>  
+## Define powdery mildew severity
+Powdery mildew severity was assessed on a 1 - 9 scale.
+```{r disease_scale}
+d_rating_table <-
+   data.frame(
+      Severity_rating = 1:9,
+      Description = c(
+         "No sign of powdery mildew",
+         "Small colonies in the lower 1/3 of canopy with up to 75% of plants infected",
+         "Colonies in lower half of canopy with more than 75% of plants infected",
+         "Colonies in lower 2/3 of canopy with up to 75% of plants infected",
+         "Colonies in lower 2/3 of canopy with more than 75% of plants infected",
+         "Colonies in lower 2/3 of canopy with 100% of plants infected",
+         "Colonies in lower 2/3 of canopy with 100% of plants infected, some plants with colonies in the top 1/3 of the canopy",
+         "Colonies all the way to the top of the plant with more than 75% of plants affected",
+         "Colonies all the way to the top of the plant with severe leaf drop"
+      ),
+      percent = c(0,0.33 * 0.5, 0.5 * 0.87, 0.66*0.75, 0.66 * 0.87,
+                  0.66, 0.75, 0.87, 1) *100
+   ) %>%
+   flextable() %>%
+   fontsize(size = 8, part = "body") %>%
+   fontsize(size = 10, part = "header") %>%
+   autofit() %>%
+   set_header_labels(Severity_rating = "Severity rating",
+                     percent = "Equivalent percent severity") %>%
+   width(j = 1, width = 0.8) %>%
+   width(j = 2, width = 4) %>%
+   width(j = 3, width = 1.2) %>%
+   align(j = 1, align = "center") %>%
+   set_caption("Table 2: Powdery mildew severity rating scale and calculated percent severity for each ordinal rating")
+d_rating_table
+```
+```{r eval=FALSE, include=FALSE}
+# Save table as a word document
+doc <- officer::read_docx()
+doc <- body_add_flextable(doc, value = d_rating_table)
+print(doc, target = "paper/figures/SeverityRatingTable.docx")
+```
 
@@
       max_PM_sev = round(max(PM_sev_treat, na.rm = TRUE), digits = 2),
-      m_PM_yield_control = round(mean(PM_y_control, na.rm = TRUE), digits = 3),
+      m_PM_yield_control = round(median(PM_y_control, na.rm = TRUE), digits = 3),
       min_PM_yield = round(min(PM_y_treat, na.rm = TRUE), digits = 3),
@@
       PM_sev_range = "PM severity\nrange",
-      m_PM_yield_control = "Control\nmean yield",
+      m_PM_yield_control = "Control\nmedian yield",
       yield_range = "Yield range\n(t / ha)"
@@
    align(j = 3:10, align = "center", part = "all") %>%
-   autofit() %>%
-   width(j = 7:10, width = 1) %>%
+   #autofit() %>%
+   width(j = 1, width = 0.6) %>%
+   width(j = 2, width = 0.8) %>%
    width(j = 3, width = 0.5) %>%
+   width(j = 4:5, width = 0.8) %>%
+   width(j = 6, width = 0.3) %>%
+   width(j = 7, width = 0.9) %>%
+   width(j = 8, width = 0.7) %>%
+   width(j = 9, width = 0.6) %>%
+   width(j = 10, width = 1) %>%
    set_caption(
@@
 Powdery mildew (PM) onset date, number of treatments per trial (n), PM median plot severity of the non-fungicide treated plots and the severity range in fungicide treatments, bracketed numbers refer to the number of pooled control treatments summarised; Mean yield in non-fungicide treated control and the range of yields in the fungicide treatments in tonnes per hectare"
-   )
+   ) %>%
+   footnote(
+      i = 4,
+      j = 1,
+      value = as_paragraph(
+         c("Trials which reported PM severity variance and not yield variance and therefore excluded in the yield protection meta-analysis;")),
+      ref_symbols = "a") %>%
+   footnote(
+      i = c(11,12),
+      j = 1,
+      value = as_paragraph(
+         c("Trials which did not report powdery mildew (PM) severity variance and therefore excluded in the PM severity meta-analysis")),
+      ref_symbols = "b")
+
 Sev_yield_table
@@
 doc <- body_add_flextable(doc, value = Sev_yield_table)
-doc <- officer::body_end_section_landscape(doc)
-print(doc, target = "paper/figures/Table1_severity&yield.docx")
+#doc <- officer::body_end_section_landscape(doc)
+print(doc, target = "paper/figures/Severity&yield_SummaryTable.docx")
 ```

### 2021-06-02 03_Yield_MetaAnalysis.Rmd
add stability analysis

@@
 
+## Meta-analysis stability test
+
+To check the stability in the network analysis we will rerun the chosen model 15 times. 
+Each run, one of the 15 trials will be excluded from the analysis to detect if any estimates varied significantly indicating an unstable network meta-analysis.
+```{r stability}
+stab_PM_mv <- 
+   lapply(unique(PM_dat_Y$trial_ref), function(Trial){
+
+      #subset to remove a trial
+      dat <- filter(PM_dat_Y, trial_ref != Trial)
+
+      PM_mv <- rma.mv(
+         yi = grain_yield.t.ha.,
+         V = vi,
+         mods = ~ spray_management,
+         method = "ML",
+         random = list(~ spray_management | trial, ~ 1 | id),
+         struct = "UN",
+         control = list(optimizer = "optim"),
+         data = dat
+      )
+   })
+
+length(stab_PM_mv)
+est <- lapply(stab_PM_mv, function(e1){
+   data.frame(treat = rownames(e1$b),
+              estimates = e1$b,
+              p = as.numeric(reportP(e1$pval, P_prefix = FALSE,AsNumeric = TRUE)))
+   })
+
+stab_df <- data.table::rbindlist(est)
+stab_df$Tnum <- rep(1:15, each = 6)
+
+stab_df %>%
+   ggplot(aes(Tnum, estimates, colour = treat))+
+   geom_line()
+
+stab_df %>%
+   ggplot(aes(Tnum, p, colour = treat))+
+   geom_line()+
+   scale_y_log10()
+
+stab_df %>%
+   group_by(treat) %>%
+   summarise(minEst = min(estimates),
+             medEst = median(estimates),
+             maxEst = max(estimates),
+             minP = min(p),
+             medP = median(p),
+             maxP= max(p))
+```
+
+Trial 9 at missen flats changes the estimates the most when excluded due to the high number of reps
+```{r}
+unique(PM_dat_Y$trial_ref)[9]
+```
+
+### Between study heterogeneity
+Calculation of I^2
+```{r}
+W <- diag(1/(PM_dat_Y$vi))
+X <- model.matrix(PM_mv)
+P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+100 * sum(PM_mv$sigma2) / (sum(PM_mv$sigma2) + (PM_mv$k-PM_mv$p)/sum(diag(P)))
+
+100 * PM_mv$sigma2 / (sum(PM_mv$sigma2) + (PM_mv$k-PM_mv$p)/sum(diag(P)))
+```
+This indicates that approximate amount of total variance attributed to trials/ clusters is 99%, which is very high. 
+However given that many of the means included in the model contained an accompanying sample variance of zero, this might have been expected.
+
 ## Meta-analysis results summary

### 2021-06-02 04_Severity_MetaAnalysis.Rmd
add sensittivity analysis and I^2 heterogenety test

@@
 
+```{r Sensitivity_logitP, cache=TRUE}
+s_analysis <- 
+   lapply(unique(PM_dat_D$trial_ref), function(Trial) {
+
+      dat <- filter(PM_dat_D, trial_ref != Trial)
+      # remove controls for response ratio meta-analysis
+      rma.mv(
+         yi = yi_logit,
+         V = yi_logit,
+         mods = ~ spray_management,
+         method = "ML",
+         random = list(~ spray_management | trial, ~ 1 | id),
+         struct = "UN",
+         control = list(optimizer = "optim"),
+         data = dat
+      )
+
+   })
+
+length(s_analysis)
+est <- lapply(s_analysis, function(e1){
+   data.frame(treat = rownames(e1$b),
+              estimates = e1$b,
+              p = as.numeric(reportP(e1$pval, P_prefix = FALSE,AsNumeric = TRUE)))
+   })
+
+sensitiviy_df <- data.table::rbindlist(est)
+sensitiviy_df$Tnum <- rep(1:14, each = 6)
+
+sensitiviy_df %>%
+   ggplot(aes(Tnum, estimates, colour = treat))+
+   geom_line()
+
+sensitiviy_df %>%
+   ggplot(aes(Tnum, p, colour = treat))+
+   geom_line()
+
+unique(PM_dat_D$trial_ref)[7]
+sensitiviy_df %>%
+   group_by(treat) %>%
+   summarise(minEst = min(estimates),
+             medEst = median(estimates),
+             maxEst = max(estimates),
+             minP = min(p),
+             medP = median(p),
+             maxP= max(p))
+```
+While estimates and P values remained the mostly same when each trial was dropped from the analysis.
+Estimates changed the most when Trial 1617/02 at Missen Flats in 2017 was ommited from the analysis.
+
+Calculation of I^2
+```{r}
+W <- diag(1/(PM_dat_D$vi_logit+0.0001))
+X <- model.matrix(PMsev_mvPer)
+P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
+100 * sum(PMsev_mvPer$sigma2) / (sum(PMsev_mvPer$sigma2) + (PMsev_mvPer$k-PMsev_mvPer$p)/sum(diag(P)))
+
+100 * PMsev_mvPer$sigma2 / (sum(PMsev_mvPer$sigma2) + (PMsev_mvPer$k-PMsev_mvPer$p)/sum(diag(P)))
+```
+This indicates that approximate amount of total variance attributed to trials/ clusters is 99%, which is very high. 
+However given that many of the means included in the model contained an accompanying sample variance of zero, this might have been expected.
+
 The estimates and significance from this model better reflect the distribution of raw values. 

### 2021-06-02 03_Yield_MetaAnalysis.Rmd
cache stability chunk and change plot line thickness

@@
 Each run, one of the 15 trials will be excluded from the analysis to detect if any estimates varied significantly indicating an unstable network meta-analysis.
-```{r stability}
+```{r stability, cache=TRUE}
 stab_PM_mv <- 
@@
    ggplot(aes(Tnum, estimates, colour = treat))+
-   geom_line()
+   geom_line(size = 1)
 
@@
    ggplot(aes(Tnum, p, colour = treat))+
-   geom_line()+
+   geom_line(size = 1)+
    scale_y_log10()
@@
              maxP= max(p))
+stab_df[Tnum == 9]
 ```

### 2021-06-07 04_Severity_MetaAnalysis.Rmd
edit sensitivity plot line thickness and scale

@@
    ggplot(aes(Tnum, p, colour = treat))+
-   geom_line()
+   geom_line(size = 1)+
+   scale_y_log10()
 

### 2021-09-12 04_Severity_MetaAnalysis.Rmd
Revise header to match other chapter title capitalisation

@@
 
-```{r Metafor-Sev-analysis, cache=TRUE}
+```{r Metafor-Sev-analysisSQ, cache=TRUE}
 PMsev_mvSQ <- rma.mv(

### 2021-09-12 02_Preliminary_analysis.Rmd
remove bomrang from packages - not required

@@
                lubridate,
-               bomrang,
                openxlsx,

### 2021-09-12 03_Yield_MetaAnalysis.Rmd
remove bomrang from packages - not required

@@
    kableExtra,
-   bomrang,
    RColorBrewer,

### 2021-09-12 04_Severity_MetaAnalysis.Rmd
remove bomrang from packages - not required

@@
 
-# Powdery mildew severity Meta-analysis
+# Powdery mildew severity meta-analysis
 
@@
                kableExtra,
-               bomrang,
                RColorBrewer,

### 2021-09-12 02_Preliminary_analysis.Rmd
install bomrang package from github repo

@@
                devtools,
+               remotes,
                reshape2,

### 2021-09-12 R/crop_rain.R

@@ -1,5 +1,6 @@
 library("dplyr")
 library("lubridate")
+remotes::install_github("ropensci/bomrang")
 # Function to run over each line for sum rainfall
 crop_rain <-
    function(location_name,

### 2021-09-13 R/crop_rain.R
read station metadata from cached values bypassing need for bomrang

@@ -1,6 +1,6 @@
 library("dplyr")
 library("lubridate")
-remotes::install_github("ropensci/bomrang")
+
 # Function to run over each line for sum rainfall
 crop_rain <-
    function(location_name,
@@ -12,37 +12,40 @@ crop_rain <-
       input_data <- data.frame(location_name, latitude, longitude)
       trials <- unique(input_data)
       
+# Commented due to problems with bomrang package, see github page for more details
+# https://github.com/ropensci/bomrang
+      # # Download trial data
+      # trials$station_file <-
+      #    apply(trials, 1, function(LL) {
+      #       stat_sweep <-
+      #          bomrang::sweep_for_stations(as.numeric(c(LL["latitude"], LL["longitude"])))
+      #       
+      #       # Remove banned stations
+      #       banned_stations <-
+      #          c("055286") # stations don't report rain
+      #       stat_sweep <-
+      #          stat_sweep[site != banned_stations, ]
+      #       
+      #       statID <-
+      #          paste(stat_sweep[1, "name"], stat_sweep[1, "site"], sep = "_")
+      #       stat_file <-
+      #          paste("cache/weather/", statID, ".csv",sep = "", collapse = " ")
+      #       
+      #       if (stat_file %in% paste0("cache/weather/", list.files(here::here("cache/weather/")))) {
+      #          #weather <- read.csv(stat_file, stringsAsFactors = FALSE)
+      #          return(stat_file)
+      #       } else{
+      #          weather <-
+      #             bomrang::get_historical(stationid = stat_sweep[1, "site"], type = "rain")
+      #          write.csv(weather, file = stat_file, row.names = FALSE)
+      #          return(stat_file)
+      #       }
+      #    })
+      # 
+      # 
+      # input_data <- full_join(input_data,trials, by = c("location_name", "latitude", "longitude"))
       
-      # Download trial data
-      trials$station_file <-
-         apply(trials, 1, function(LL) {
-            stat_sweep <-
-               bomrang::sweep_for_stations(as.numeric(c(LL["latitude"], LL["longitude"])))
-            
-            # Remove banned stations
-            banned_stations <-
-               c("055286") # stations don't report rain
-            stat_sweep <-
-               stat_sweep[site != banned_stations, ]
-            
-            statID <-
-               paste(stat_sweep[1, "name"], stat_sweep[1, "site"], sep = "_")
-            stat_file <-
-               paste("cache/weather/", statID, ".csv",sep = "", collapse = " ")
[…]

### 2021-09-14 04_Severity_MetaAnalysis.Rmd
Grammar

@@
 Another transformation which might be more suitable for a discrete response is either a `log()` or `logit()` transformation. 
-However first we should convert the scale from 1 - 9 to between 0 and 1.
+However, first we should convert the scale from 1 - 9 to between 0 and 1.
 
@@
 Let us also transform the severity onto a percentage scale so we can compare the results of meta-analyses with no transformation, squared severity, and percent severity.
+
+This conversion from ordinal scale to a severity rating is described in Table 2 of the paper.
 
@@
 ## Disease severity spray schedule meta-analysis  
-First lets look at the results of the meta-analysis without transformation
+First let's look at the results of the meta-analysis without transformation
 ```{r Metafor-Sev-analysis, cache=TRUE}
@@
 
-Lets assess the log transformed percent severity
+Let's assess the log transformed percent severity
 ```{r Metafor-Sev-analysis_log, cache=TRUE}
@@
 
-Finally lets assess the logit transformed percent severity
+Finally let's assess the logit transformed percent severity
 ```{r Metafor-Sev-analysis_logitP, cache=TRUE}

### 2021-09-14 04_Severity_MetaAnalysis.Rmd
Add comment on analysis of ordinal scales

@@
 ```
+
+<!--- I would remove from this line, 77 to line 96 as we shouldn't be promoting the idea of analysing an ordinal scale directly, just go straight to the severity conversion step and describe it and why it's done (i.e., you can't analyse an ordinal scale like this, though I found a cool presentation on how to analyse an ordinal scale using metanalysis for future reference, https://methods.cochrane.org/sites/methods.cochrane.org.statistics/files/public/uploads/SMG_training_course_cardiff/2010_SMG_training_cardiff_day1_session2_lewis.pdf) -->
 

### 2021-09-14 04_Severity_MetaAnalysis.Rmd
Remove commented code
Format code. Be more specific in GAM model structure

@@
 
-We can fit a gam curve between the 1 - 9 scale and the new scale between 0 and 1
+We can fit a GAM curve between the 1 - 9 scale and the new scale between 0 and 1.
+
 ```{r}
-# fit a curve using a gam with spline value 0.2
-g1 <- gam(x ~ s(y,spar = 0.1))
+# fit a curve using a gam with spline value 0.01
+g1 <- gam(x ~ s(y, spar = 0.1), family = gaussian)
 
 # View plot of gam
-plot(x = predict(g1, data.frame(y= seq(1,9, by =0.1))), y= seq(1,9, by =0.1))
-points(x,y,col = "red", pch = 16)
+plot(x = predict(g1,
+                 data.frame(y = seq(1, 9, by = 0.1))), y = seq(1, 9, by = 0.1))
+points(x, y, col = "red", pch = 16)
 
@@
 ```{r}
-# one value is a negative, this should be a zero
-# new_sev[12] <- 0
-
 # Allocate new variable percent severity

### 2021-09-14 03_Yield_MetaAnalysis.Rmd
yied > yield

@@
 
-```{r metafor_plot_yied}
+```{r metafor_plot_yield}
 results_mv %>%

### 2021-09-14 04_Severity_MetaAnalysis.Rmd
Grammar

@@
 
-   - *Powdery mildew severity* the response variable (1-9 scale)
+   - *Powdery mildew severity*, the response variable (1-9 scale)
 
@@
 
-   - *spray_management* a moderator to evaluate the difference in effect size attributed to fungicide application timing.
+   - *spray_management*, a moderator to evaluate the difference in effect size attributed to fungicide application timing.
 
-   - *id* random variable indicating each treatment is independent
+   - *id*, random variable indicating each treatment is independent
 
-<br>
+Load libraries and data.
 
-Load libraries and data  
 ```{r MEsummary_Libraries2, echo=TRUE,results='hide'}

### 2021-12-28 01_TrialsForInclusionInAnalysis.Rmd
Lets > Let's
Fix any issues that prevented book from building locally

@@
 
-<br>
-<br>
-<br>
-
 ### Classify dataset variables
@@
    filter(spray_management != "Early_plus") %>%
-   select(-c(fungicide_timing_1, # remove the following columns which no longer have use
+   dplyr::select(
+      -c(
+         fungicide_timing_1,
+         # remove the following columns which no longer have use
          fungicide_timing_2,
@@
          fungicide_application_7,
-             ))
-
+      )
+   )
 ```
-
-<br>  
-<br>  
-<br>
 
@@
 We need variance accompanying the mean observations for each treatment to successfully undertake a meta-analysis.
-Lets investigate which of the included trials included variance for both response variables of interest, yield and disease severity.
+Let's investigate which of the included trials included variance for both response variables of interest, yield and disease severity.
 
@@
 
-<br>
-
 Remove one trial in Emerald which did not report disease variance or yield variance.
@@
    filter(trial_ref %in% contains_var) %>%
-   select(-contains_var) 
+   dplyr::select(-contains_var) 
 ```
-
-<br>
 
@@
    filter(trial_ref %in% contains_var) %>%
-   select(-contains_var)
+   dplyr::select(-contains_var)
 ```
-
-<br>
 
@@
    filter(trial_ref %in% contains_var) %>%
-   select(-contains_var)
+   dplyr::select(-contains_var)
 ```
-
-<br>  
-<br>  
-<br>
 
@@
    ) %>%
-   select(-c(yield_error,
+   dplyr::select(-c(yield_error,
                     Y_error_type))
@@
    ) %>%
-   select(-c(disease_error,
+   dplyr::select(-c(disease_error,
                     D_error_type))
@@
 
-<br>
+#### Save the cleaned data
 
-#### Save the cleaned data
 ```{r saveData01}

### 2021-12-28 02_Preliminary_analysis.Rmd
read station metadata from cached values bypassing need for bomrang
Fix any issues that prevented book from building locally

@@
    mutate(m_PM_sev_control = paste(m_PM_sev_control, " (", n_controls, ")", sep = "")) %>%
-   select(-c(min_PM_sev, max_PM_sev, min_PM_yield, max_PM_yield, n_controls)) %>%
-   select(c(1:7, 9, 8, 10)) %>% # order columns
+   dplyr::select(-c(min_PM_sev, max_PM_sev, min_PM_yield, max_PM_yield, n_controls)) %>%
+   dplyr::select(c(1:7, 9, 8, 10)) %>% # order columns
    flextable() %>%
@@
    align(j = 3:10, align = "center", part = "all") %>%
-   #autofit() %>%
    width(j = 1, width = 0.6) %>%
@@
       value = as_paragraph(
-         c("Trials which reported PM severity variance and not yield variance and therefore excluded in the yield protection meta-analysis;")),
-      ref_symbols = "a") %>%
+         c(
+            "Trials which reported PM severity variance and not yield variance and therefore excluded in the yield protection meta-analysis;"
+         )
+      ),
+      ref_symbols = "a"
+   ) %>%
    footnote(
-      i = c(11,12),
+      i = c(11, 12),
       j = 1,
       value = as_paragraph(
-         c("Trials which did not report powdery mildew (PM) severity variance and therefore excluded in the PM severity meta-analysis")),
-      ref_symbols = "b")
+         c(
+            "Trials which did not report powdery mildew (PM) severity variance and therefore excluded in the PM severity meta-analysis"
+         )
+      ),
+      ref_symbols = "b"
+   )
 
@@
    geom_boxplot(outlier.alpha = 0) +
-   geom_jitter(size = 2, colour = "cadetblue",alpha = 0.4,width = 0.15) +
-   scale_y_continuous(breaks = c(1,3,5,7,9), limits = c(0.9,9.1)) +
-   ylab("PM severity (1 -9)")+
-   # xlab("Crop season")+
-   # theme(axis.title.x=element_blank(),
-   #      axis.text.x=element_blank(),
-   #      axis.ticks.x=element_blank())+
+   geom_jitter(
+      size = 2,
+      colour = "cadetblue",
+      alpha = 0.4,
+      width = 0.15
+   ) +
+   scale_y_continuous(breaks = c(1, 3, 5, 7, 9),
+                      limits = c(0.9, 9.1)) +
+   ylab("PM severity (1 -9)") +
    ggtitle("A") +
@@
 ```
-<br>  
-<br>
 
@@
    ) +
-   scale_y_continuous(breaks = c(1, 3, 5, 7, 9), limits = c(0.9, 9.1)) +
+   scale_y_continuous(breaks = c(1, 3, 5, 7, 9),
+                      limits = c(0.9, 9.1)) +
    scale_x_discrete(labels = c(
@@
    # xlab("Spray Schedule")+
-   ggtitle("B")+
+   ggtitle("B") +
    theme_minimal()
@@
           host_genotype == "Jade") %>%
-   mutate(Treatment = case_when(fungicide_ai == "control" ~ "control_yield",
-                                TRUE ~ "FungicideTreated_yield")) %>%
+   mutate(
+      Treatment = case_when(
+         fungicide_ai == "control" ~ "control_yield",
+         TRUE ~ "FungicideTreated_yield"
+      )
+   ) %>%
    group_by(location, Treatment) %>%
@@
    mutate(percent = (Diff / FungicideTreated_yield) * 100) %>%
-   select(trial_ref,
+   dplyr::select(trial_ref,
                  location,
@@
 ```
-
-<br>  
-<br>
 
@@
 
+# Due to the Bureau of Meteorology in Australia blocking requests using the 
+#  R package `bomrang` this code has been changed to import the cached values
+
 # plot yield vs rainfall
@@
           Element == "Area harvested") %>%
-   select(Year, Value) %>%
+   dplyr::select(Year, Value) %>%
    ggplot(aes(y = Value, x = Year)) +

### 2021-12-28 03_Yield_MetaAnalysis.Rmd
Fix any issues that prevented book from building locally

@@
 
-<br>  
-<br>  
-<br>
-
 ## Spray schedule meta-analysis
@@
 ```
-
-<br>  
-<br>  
-<br>
 
@@
 
-<br>  
-<br>
-
 ******
@@
 This inference is also reflected by the the chi-squared test, which is uncertain that the `onset` model is significantly better as indicated by the ANOVA `pval` `r round(anova(PM_mv, PM_mv_onset)$pval,3)`.
-
-<br>  
-<br>  
-<br>
 
@@
 
-<br>  
-<br>  
-<br>
-
 ******
@@
 This comparison tells us the meta-analysis including `d_pressure` explained more residual heterogeneity, as shown by the lower QE value, and has a better fit, indicated by the higher log-likelihood with the additional `d_pressure` parameter.
-However the lower AIC in the 'Full' model indicates that retaining the model including the additional `d_pressure` variables could be a reasonable decision.
+However, the lower AIC in the 'Full' model indicates that retaining the model including the additional `d_pressure` variables could be a reasonable decision.
 In addition the chi-squared test indicates that the `d_pressure` model is better as indicated by the `pval` 0.0468.

### 2021-12-28 index.Rmd
Fix any issues that prevented book from building locally

@@
 # About
+
 ## Background
+
 A common practice for managing powdery mildew in mungbean is to couple fungicide with an insecticide spray early in the development of the crop, usually before the disease is detected.
@@
 ## Compendium contents
+
 This research compendium details importing and summarising the raw data, application of the selection criteria, defining moderator variables for fungicide spray timing, and the statistical analysis methods for this meta-analysis of fungicide efficacy trials for controlling powdery mildew in mungbean.
@@
 Raw data for this work were contributed by the University of Southern Queensland, Queensland Department of Agriculture, Fisheries and Forestry (DAF), and the Northern Grower Alliance.
-Additional thanks to Malcolm Riley, Sue Thompson and Lawrie Price.
+Additional thanks to Prof.
+Malcolm Riley, Dr.
+Sue Thompson and Lawrie Price.

### 2021-12-28 R/Rainfall_x_cropYield.R

@@ -3,7 +3,6 @@
 #  Code chunk rainfall_sum_Sstart
 
 library(tidyverse)
-library(theme.usq)
 library(bomrang)
 library(parallel)
 source("R/import_data.R")

### 2021-12-28 R/Rainfall_x_cropYield_s-10.09_e65.100.R

@@ -17,7 +17,6 @@ end2 <- 100
 
 
 library(tidyverse)
-library(theme.usq)
 library(bomrang)
 library(parallel)
 source("R/import_data.R")

### 2021-12-28 R/classify_PM_data.R

@@ -1,65 +1,65 @@
 classify_PM_data <- function(dat) {
    dat <-
       dat %>%
-      mutate(trial_ref = as.character(trial_ref)) %>%
-      mutate(year = as.character(year)) %>%
-      mutate(location = as.character(location)) %>%
-      mutate(host_genotype = as.character(host_genotype)) %>%
-      mutate(row_spacing = as.double(round(row_spacing, digits = 2))) %>%
-      mutate(replicates = as.integer(replicates)) %>%
-      mutate(planting_date = ymd(planting_date)) %>%
-      mutate(flowering_date = ymd(flowering_date)) %>%
-      mutate(pod_fill_date = ymd(pod_fill_date)) %>%
-      mutate(mid_late_pod_fill = ymd(mid_late_pod_fill)) %>%
-      mutate(first_sign_disease = ymd(first_sign_disease)) %>%
-      mutate(fungicide_ai = as.character(fungicide_ai)) %>%
-      mutate(dose_ai.ha = round(as.double(dose_ai.ha), digits = 2)) %>%
-      mutate(fungicide_application_1 = ymd(fungicide_application_1)) %>%
-      mutate(fungicide_application_2 = ymd(fungicide_application_2)) %>%
-      mutate(fungicide_application_3 = ymd(fungicide_application_3)) %>%
-      mutate(fungicide_application_4 = ymd(fungicide_application_4)) %>%
-      mutate(fungicide_application_5 = ymd(fungicide_application_5)) %>%
-      mutate(fungicide_application_6 = ymd(fungicide_application_6)) %>%
-      mutate(total_fungicide = as.integer(total_fungicide)) %>%
-      mutate(harvest_date = ymd(harvest_date)) %>%
-      mutate(final_assessment = ymd(final_assessment)) %>%
-      mutate(PM_final_severity = round(as.double(PM_final_severity), digits = 4)) %>%
-      mutate(disease_error = round(as.double(disease_error), digits = 6)) %>%
-      mutate(D_error_type = as.character(D_error_type)) %>%
-      mutate(grain_yield.t.ha. = round(as.double(grain_yield.t.ha.), digits = 4)) %>%
-      mutate(yield_error = round(as.double(yield_error), digits = 6)) %>%
-      mutate(Y_error_type = as.character(Y_error_type)) %>%
-      mutate(Y_Msquare = round(as.double(Y_Msquare), digits = 6)) %>%
[…]

### 2021-12-28 01_TrialsForInclusionInAnalysis.Rmd
Clean linebreaks, <br>, reformat code, etc.

@@
 pacman::p_load(tidyverse, kableExtra, leaflet, htmltools, lubridate, here)
-
 ```
-
-<br>  
-<br>
 
@@
 ## Import data
+
 **Import data from trials which the raw data was available**
+
 ```{r import_dataRAW}
@@
       ),
-      read.csv(here("cache/2011 PMmung Herm means.csv"), stringsAsFactors = FALSE),
+      read.csv(here("cache/2011 PMmung Herm means.csv"),
+               stringsAsFactors = FALSE),
       read.csv(
@@
       ),
-      read.csv(here("cache/AM1305_Goolhi_means.csv"), stringsAsFactors = FALSE),
+      read.csv(here("cache/AM1305_Goolhi_means.csv"),
+               stringsAsFactors = FALSE),
       read.csv(
@@
       ),
-      read.csv(here("cache/Herm_16_means.csv"), stringsAsFactors = FALSE),
-      read.csv(here("cache/King_16_means.csv"), stringsAsFactors = FALSE),
-      read.csv(here("cache/Fogerty_17_mean.csv"), stringsAsFactors = FALSE),
-      read.csv(here("cache/Hermitage_17_mean.csv"), stringsAsFactors = FALSE),
-      read.csv(here("cache/Wellcamp_18_mean.csv"), stringsAsFactors = FALSE),
-      read.csv(here("cache/Hermitage_19_mean.csv"), stringsAsFactors = FALSE)
+      read.csv(here("cache/Herm_16_means.csv"),
+               stringsAsFactors = FALSE),
+      read.csv(here("cache/King_16_means.csv"),
+               stringsAsFactors = FALSE),
+      read.csv(here("cache/Fogerty_17_mean.csv"),
+               stringsAsFactors = FALSE),
+      read.csv(here("cache/Hermitage_17_mean.csv"),
+               stringsAsFactors = FALSE),
+      read.csv(here("cache/Wellcamp_18_mean.csv"),
+               stringsAsFactors = FALSE),
+      read.csv(here("cache/Hermitage_19_mean.csv"),
+               stringsAsFactors = FALSE)
    )
@@
 ```
-
-<br>
 
@@
 
-<br>
-<br>
-<br>
-
 ## Subset data to selection criteria
@@
 
-<br>
+### Retain trials including: Yield
 
-**Retain trials including: Yield**  
 Three trials omitted due to not reporting yields
+
 ```{r TrialWithoutYield}
@@
 
-<br>
+###Retain trials including: Disease severity
 
-**Retain trials including: Disease severity**  
 One more was trial removed as it did not report disease severity.
+
 ```{r TrialsWithotDisease}
@@
 ```
+### Retain trials including: fungicide application dates
 
-<br>
-<br>
-<br>
+No trials from our subset need to be removed for not reporting fungicide application dates.
 
-**Retain trials including: fungicide application dates**  
-No trials from our subset need to be removed for not reporting fungicide application dates.  
 ```{r FungicideApplicationDates}
@@
 
-<br>
-<br>
-<br>
+### Retain trials including: fungicide dose
 
-**Retain trials including: fungicide dose**  
 No trials from our subset need to be removed for not reporting fungicide dose.
+
 ```{r FungicideDoseTrials}
@@
 
-<br>
-<br>
-<br>
+### Exclude fungicides tested in too few trials
 
-**Exclude fungicides tested in too few trials**  
 The meta-analysis should be focused on fungicides with the same mode of action.
 Fungicides from the best represented group will be retained.
+
 ```{r Fungicides}
@@
    ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
-   coord_flip()
+   coord_flip() +
+   theme_classic()
 ```
@@
 
-<br>
-<br>
-<br>
+### Retain only fungicides with DMI action
 
-**Retain only fungicides with DMI action**
 ```{r filterDMI_trials}
@@
 
-Now remove any non-DMI treatments or controls  
+Now remove any non-DMI treatments or controls.
+
 ```{r KeepOnlyDMI}
@@
 
-<br>  
-<br>
-
 ## Defining spray schedule variable
@@
 
-<br>
-
 These categorical variables are named:  
@@
    - **Late**: First fungicide application was four or more days after first sign of disease being observed.
-
-<br>
 
@@
 ## Identify variance
+
 We need variance accompanying the mean observations for each treatment to successfully undertake a meta-analysis.
@@
 Remove one trial in Emerald which did not report disease variance or yield variance.
+
 ```{r remove_nil_var}
@@
 One trial will be removed from the yield data set `PM_dat_Y` for not reporting yield variance.
+
 ```{r TrialsWithVariance}
@@
 Two more trials will be removed for our disease severity data set `PM_dat_D` for not reporting yield variance.
+
 ```{r TrialsWithVariance_D}
@@
 
-### Yield variance standardisation
+## Yield variance standardisation
+
 ```{r StandardiseYieldVariance}
@@
 
-### Disease severity variance standardisation
+## Disease severity variance standardisation
+
 ```{r StandardiseSeverityVariance}
@@
 
-#### Save the cleaned data
+## Save the cleaned data
 
@@
 write.csv(PM_MB_dat, file = "cache/PM_MB_clean_data.csv", row.names = FALSE)
-save(PM_MB_dat, PM_dat_D, PM_dat_Y, file = here("cache/ImportDataAndSelectTrials01.Rdata"))
+save(PM_MB_dat,
+     PM_dat_D,
+     PM_dat_Y,
+     file = here("cache/ImportDataAndSelectTrials01.Rdata"))
 ```

### 2021-12-28 02_Preliminary_analysis.Rmd
Clean linebreaks, <br>, reformat code, etc.

@@
 
-<br>
+### Trial seasons
 
-### Trial seasons
 How many trials were undertaken each season.
@@
 
-<br>  
-<br>
+### Trial locations
 
-### Trial locations
 The location of the trials including DMI fungicides.
@@
 
-<br>  
-<br>
+### Powdery mildew severity and mungbean grain yield summary per trial
 
-### Powdery mildew severity and mungbean grain yield summary per trial  
 Show a summary of both `powdery mildew severity` and mungbean `grain yield` means and ranges for all trials including DMI fungicides.
@@
 ```
-<br>  
-<br>
 
 ### Summary plots
+
 #### Seasonal disease pressure in the control
@@
    ggtitle("A") +
-   theme_minimal()
+   theme_classic()
 
@@
    ggtitle("B") +
-   theme_minimal()
+   theme_classic()
 
@@
 
-<br>  
-<br>
-
 #### Mungbean yield for each spray schedule
@@
    xlab("Spray schedule")+
-   theme_minimal()+
+   theme_classic()+
    theme(axis.title.y = element_blank(),
@@
 
-<br>  
-<br>  
-<br>  
-<br>
-
 *****
@@
 
-<br>
+### Fungicide type
 
-### Fungicide type
 #### Powdery mildew severity
+
 ```{r TebuVPropi_sev}
@@
 
-<br>  
-<br>
+#### Yield effect
 
-#### Yield effect
 ```{r TebuVPropi_Yi}
@@
 
-<br>  
-<br>  
-<br>
+### Fungicide Doses{#fungicide-doses}
 
-### Fungicide Doses{#fungicide-doses}  
 This analysis focuses only the DMI fungicides, tebuconazole and propiconazole, which were trialled the most often.
@@
 
-<br>  
-<br>
-
 How many treatments of each dose have been investigated per trial?
@@
 Very few treatments were sprayed more than three times and only in `r unique(PM_MB_dat[PM_MB_dat$total_fungicide == 3,"trial_ref"])`
-
-<br>  
-<br>
 
@@
 
-<br>  
-<br>
-
 Will plotting row spacing treatments show differences for the response variables, *yield* and *disease severity*.
 The main questions are:
-
    * Were there any statistical differences for mungbean *yield* or *powdery mildew severity* between row spacing treatments?
-
    * If not, can we pool certain row spacing that have no significant difference?
@@
 
-<br>
-
 In the Wellcamp site, wider row spacing reduces PM severity, the other sites it seems there was not enough variation to make a distinction between row spacing treatments.
@@
    ylab("Grain yield (t/ha)")+
-   theme_minimal()
+   theme_classic()
 ```
@@
 
-<br>  
-<br>
+### Disease pressure
 
-### Disease pressure  
 The amount of disease pressure between seasons is another variable which could impact mungbean yield meta-analysis effect size.
+
 ```{r D_pres}
@@
 
-<br>  
-<br> 
-<br>  
-<br>
+### In-crop rainfall
 
-### In-crop rainfall  
 #### Whole season
@@
 First an inspection of all rainfall within the season
+
 ```{r season_rainfall}
@@
 
-<br>  
-<br>
+#### Early-season rainfall
 
-#### Early-season rainfall
 Here we only look at the effect of rainfall between the _planting date_ and _first sign of disease_. 
@@
 
-<br>  
-<br>
+#### Late-season rainfall
 
-#### Late-season rainfall  
 Here we only look at the effect of rainfall between the _first sign of disease_ and _crop harvest_.
@@
 
-<br>  
-<br>
+#### Mid-season rainfall
 
-#### Mid-season rainfall  
 Here we only look at the effect of rainfall between the 20 days after planting and 80 days after planting.
+
 ```{r mid_rain}
@@
 
-<br>  
-<br> 
-<br> 
 ******

### 2021-12-28 03_Yield_MetaAnalysis.Rmd
Clean linebreaks, <br>, reformat code, etc.

@@
 ---
+
 # Grain yield meta-analysis
@@
 ### Define Trial
+
 ```{r Yield_define_trial}
@@
 `early` and `late` categories should be divided by a number close to the median days after sowing when signs of the disease were first observed to ensure roughly even numbers in each category.
+
 ```{r median onset}
@@
 We will choose 42 days as this is the average days to flowering in mungbean. 
-In addition, Kelly et. al. [-@Kelly2017a] noted that yield losses are higher in cultivar Berken when disease establishes before flowering.
+In addition, Kelly et al. [-@Kelly2017a] noted that yield losses are higher in cultivar Berken when disease establishes before flowering.
 
@@
 ```{r}
-anova(PM_mv, PM_mv_dp)
+mod <- anova(PM_mv, PM_mv_dp)
+mod
 ```
+
 This comparison tells us the meta-analysis including `d_pressure` explained more residual heterogeneity, as shown by the lower QE value, and has a better fit, indicated by the higher log-likelihood with the additional `d_pressure` parameter.
 However, the lower AIC in the 'Full' model indicates that retaining the model including the additional `d_pressure` variables could be a reasonable decision.
-In addition the chi-squared test indicates that the `d_pressure` model is better as indicated by the `pval` 0.0468.
+In addition the chi-squared test indicates that the `d_pressure` model is better as indicated by the `pval` $`r mod$pval`$.
 
@@
 
-<br>
-<br>
-<br>
-
 ******
@@
 Each run, one of the 15 trials will be excluded from the analysis to detect if any estimates varied significantly indicating an unstable network meta-analysis.
+
 ```{r stability, cache=TRUE}
 stab_PM_mv <-
-   lapply(unique(PM_dat_Y$trial_ref), function(Trial){
-
+   lapply(unique(PM_dat_Y$trial_ref), function(Trial) {
       #subset to remove a trial
@@
          method = "ML",
-         random = list(~ spray_management | trial, ~ 1 | id),
+         random = list( ~ spray_management | trial, ~ 1 | id),
          struct = "UN",
@@
 length(stab_PM_mv)
-est <- lapply(stab_PM_mv, function(e1){
-   data.frame(treat = rownames(e1$b),
+est <- lapply(stab_PM_mv, function(e1) {
+   data.frame(
+      treat = rownames(e1$b),
       estimates = e1$b,
-              p = as.numeric(reportP(e1$pval, P_prefix = FALSE,AsNumeric = TRUE)))
+      p = as.numeric(reportP(
+         e1$pval, P_prefix = FALSE, AsNumeric = TRUE
+      ))
+   )
 })
@@
 stab_df %>%
-   ggplot(aes(Tnum, estimates, colour = treat))+
+   ggplot(aes(Tnum, estimates, colour = treat)) +
    geom_line(size = 1)
@@
 stab_df %>%
-   ggplot(aes(Tnum, p, colour = treat))+
-   geom_line(size = 1)+
+   ggplot(aes(Tnum, p, colour = treat)) +
+   geom_line(size = 1) +
    scale_y_log10()
@@
    group_by(treat) %>%
-   summarise(minEst = min(estimates),
+   summarise(
+      minEst = min(estimates),
       medEst = median(estimates),
@@
       medP = median(p),
-             maxP= max(p))
+      maxP = max(p)
+   )
 stab_df[Tnum == 9]
@@
 Trial 9 at missen flats changes the estimates the most when excluded due to the high number of reps
+
 ```{r}
@@
 ### Between study heterogeneity
+
 Calculation of I^2
+
 ```{r}
@@
 ```
+
 This indicates that approximate amount of total variance attributed to trials/ clusters is 99%, which is very high. 
@@
 
-<br>  
-<br>
-
 ### Moderator estimates plot
@@
    ggplot(aes(Treatment, mu)) +
-   geom_hline(
-      yintercept = seq(-0.05, 0.3, by = 0.05),
-      linetype = 3
-   ) +
+   geom_hline(yintercept = seq(-0.05, 0.3, by = 0.05),
+              linetype = 3) +
    geom_point(aes(size = 1 / se), shape = 15) +
@@
    coord_flip() +
-   labs(caption = "Bars indicate 95% confidence intervals")+
+   labs(caption = "Bars indicate 95% confidence intervals") +
    ylab(expression(paste(
@@
 
-<br>  
-<br>
-
 ### Moderator contrasts
@@
 contrast_Ssum %>%
-   flextable()%>%
+   flextable() %>%
    autofit()
-
 ```
@@
 ```
-<br>  
-<br>  
-<br>
 

### 2021-12-28 04_Severity_MetaAnalysis.Rmd
Clean linebreaks, <br>, reformat code, etc.

@@
 This model will be similar to the grain yield meta-analysis and use the main variables:
-
    - *Powdery mildew severity*, the response variable (1-9 scale)
-
    - *Trial*, which resolves combinations of categorical random variables: 
@@
       iv) cultivar
-
    - *spray_management*, a moderator to evaluate the difference in effect size attributed to fungicide application timing.  
-
    - *id*, random variable indicating each treatment is independent
@@
 
-<br>  
-<br>
+### Define Trial
 
-### Define Trial
 ```{r define_trial}
@@
 
-<!--- I would remove from this line, 77 to line 96 as we shouldn't be promoting the idea of analysing an ordinal scale directly, just go straight to the severity conversion step and describe it and why it's done (i.e., you can't analyse an ordinal scale like this, though I found a cool presentation on how to analyse an ordinal scale using metanalysis for future reference, https://methods.cochrane.org/sites/methods.cochrane.org.statistics/files/public/uploads/SMG_training_course_cardiff/2010_SMG_training_cardiff_day1_session2_lewis.pdf) -->
-
-### Inspect PM severity for normality
-Given the meta-analysis assumes powdery mildew severity observations to be a univariate normal distribution $Y_i = N(\mu , \sigma)$, with a mean $\mu$ and standard deviation $\sigma$.
-We need to inspect severity for a normality.
-```{r sev_hist}
-hist(PM_dat_D$PM_final_severity)
-summary(PM_dat_D$PM_final_severity)
-```
-We can see here that powdery mildew severity observations are skewed towards the top of the scale, eight and nine in this case.
-
-We can improve the normality by transforming the effect size, disease severity, by squaring.
-```{r}
-PM_dat_D$yi_square <- PM_dat_D$PM_final_severity ^2
-PM_dat_D$vi_square <- (PM_dat_D$vi +1)^2
-# Note: Here I added 1 to the variance before it was squared.
-This is because squaring numbers below one makes the number smaller or remain zero.
-This does not change the meta-analysis mean estimates but does increase heterogeneity and tao._
-
-hist(PM_dat_D$yi_square)
-summary(PM_dat_D$yi_square)
-```
-
-Another transformation which might be more suitable for a discrete response is either a `log()` or `logit()` transformation. 
-However, first we should convert the scale from 1 - 9 to between 0 and 1.
-
 ### Transform severity response
 
-Let us also transform the severity onto a percentage scale so we can compare the results of meta-analyses with no transformation, squared severity, and percent severity.
+Because the data were taken on an ordinal scale, we need to transform this to a numeric value to perform the analysis, _i.e._
+
+> For ordinal measurements (e.g., disease rating on a 0 to 3 scale designating the ordinal degree of symptoms), nonparametric methods based on ranks should generally be used for hypothesis testing.
+See Shah and Madden (2004) for recommendations on the treatment of ordinal data.
+As an alternative, parametric proportional-odds models may be used for ordinal data, if there are sufficiently large numbers of observations for each experimental unit.
+If ordinal rating scores are used for ranges of disease severity (e.g., Horsfall-Barratt [where, for instance, a “2” corresponds to a severity range from 3 to 6%, and a “3” corresponds to a range of 6 to 12%]), each score should be converted to the midpoint of the corresponding disease severity range prior to use of a parametric analytical technique.
+
+- From <https://apsjournals.apsnet.org/page/authorinformation>
 
@@
 
-```{r}
+```{r ord-to-perc}
 # Percent severity conversion
@@
 s1 <- 0
-s2 <- 0.33*0.5
-s3 <- 0.5*0.87
-s4 <- 0.66*0.75
-s5 <- 0.66*0.87
-s6 <- 0.66*1
-s7 <- 0.75*1
-s8 <- 1*0.87
-s9 <- 1*1
+s2 <- 0.33 * 0.5
+s3 <- 0.5 * 0.87
+s4 <- 0.66 * 0.75
+s5 <- 0.66 * 0.87
+s6 <- 0.66 * 1
+s7 <- 0.75 * 1
+s8 <- 1 * 0.87
+s9 <- 1
 x <- c(s1, s2, s3, s4, s5, s6, s7, s8, s9)
 y <- c(1:9)
-a = data.frame(x,y)
+a = data.frame(x, y)
 plot(a)
@@
 
-```{r}
+```{r fit-gam}
 # fit a curve using a gam with spline value 0.01
@@
 
-# View plot of gam
+# View plot of the GAM
 plot(x = predict(g1,
-                 data.frame(y = seq(1, 9, by = 0.1))), y = seq(1, 9, by = 0.1))
+                 data.frame(y = seq(1, 9, by = 0.1))),
+     y = seq(1, 9, by = 0.1))
 points(x, y, col = "red", pch = 16)
@@
 new_sev <- predict(object =  g1,
-                   newdata = data.frame(y = PM_dat_D[,"PM_final_severity"])
-                   )
+                   newdata = data.frame(y = PM_dat_D[, "PM_final_severity"]))
 # Check fit
-plot(x = new_sev, y = PM_dat_D[,"PM_final_severity"])
-points(x,y,col = "red", pch = 16)
+plot(x = new_sev, y = PM_dat_D[, "PM_final_severity"])
+points(x, y, col = "red", pch = 16)
 ```
@@
 PM_dat_D$vi_percent  <- predict(object =  g1,
-                   newdata = data.frame(y = PM_dat_D[,"vi"] + PM_dat_D[,"PM_final_severity"])
-                   ) - PM_dat_D$yi_percent
+                                newdata = data.frame(y = PM_dat_D[, "vi"] + PM_dat_D[, "PM_final_severity"])) - PM_dat_D$yi_percent
 
@@
 PM_dat_D$yi_log <- log(PM_dat_D$yi_percent)
-PM_dat_D$vi_log <- (PM_dat_D$vi_percent) / (PM_dat_D$replicates * PM_dat_D$yi_percent^2)
+PM_dat_D$vi_log <-
+   (PM_dat_D$vi_percent) / (PM_dat_D$replicates * PM_dat_D$yi_percent ^ 2)
 
 # Correct Inf to 0
-PM_dat_D[is.na(PM_dat_D$yi_log),"yi_log"] <- 0
-PM_dat_D[PM_dat_D$vi_log == -Inf,"vi_log"] <- 0.001
+PM_dat_D[is.na(PM_dat_D$yi_log), "yi_log"] <- 0
+PM_dat_D[PM_dat_D$vi_log == -Inf, "vi_log"] <- 0.001
 
@@
 # Correct -Inf to zeros
-PM_dat_D[is.na(PM_dat_D$yi_logit),"yi_logit"] <- 0
+PM_dat_D[is.na(PM_dat_D$yi_logit), "yi_logit"] <- 0
 
 ```
-
-<br>  
-<br>  
-<br>
 
@@
 ## Disease severity spray schedule meta-analysis
+
 First let's look at the results of the meta-analysis without transformation
-```{r Metafor-Sev-analysis, cache=TRUE}
+
+```{r Metafor-Sev-analysis, cache=FALSE}
 PMsev_mv <- rma.mv(
@@
 summary(PMsev_mv)
-plot(rstandard(PMsev_mv)$z, ylim=c(-3,3), pch=19)
+plot(rstandard(PMsev_mv)$z, ylim = c(-3, 3), pch = 19)
 ```
@@
 
-```{r Metafor-Sev-analysisSQ, cache=TRUE}
+```{r Metafor-Sev-analysisSQ, cache=FALSE}
+# create transformations
+PM_dat_D$yi_square <- PM_dat_D$PM_final_severity ^ 2
+PM_dat_D$vi_square <- (PM_dat_D$vi + 1) ^ 2
+
 PMsev_mvSQ <- rma.mv(
@@
 summary(PMsev_mvSQ)
-plot(rstandard(PMsev_mvSQ)$z, ylim=c(-3,3), pch=19)
+plot(rstandard(PMsev_mvSQ)$z,
+     ylim = c(-3, 3),
+     pch = 19)
 ```
+
 This meta-analysis is more in-line with estimates from the yield meta-analysis.
@@
 
-Let's assess the log transformed percent severity
-```{r Metafor-Sev-analysis_log, cache=TRUE}
+Let's assess the log transformed percent severity.
+
+```{r Metafor-Sev-analysis_log, cache=FALSE}
 # remove controls for response ratio meta-analysis
@@
 summary(PMsev_mv_log)
-plot(rstandard(PMsev_mv_log)$z, ylim=c(-3.2,3), pch=19)
+plot(rstandard(PMsev_mv_log)$z,
+     ylim = c(-3.2, 3),
+     pch = 19)
 ```
+
 The plot of the residuals show the model is not normally distributed.
 In addition the estimates don't reflect what can be [observed in the raw data][Disease severity range for each spray schedule].
-Log transformed percent severity is therefore no a suitable transformation
+Log transformed percent severity is therefore no a suitable transformation.
 
-Finally let's assess the logit transformed percent severity
-```{r Metafor-Sev-analysis_logitP, cache=TRUE}
+Finally let's assess the logit transformed percent severity.
+
+```{r Metafor-Sev-analysis_logitP, cache=FALSE}
 # remove controls for response ratio meta-analysis
@@
 # plot the model residuals
-plot(rstandard(PMsev_mvPer)$z, ylim=c(-3,3), pch=19)
-
+plot(rstandard(PMsev_mvPer)$z,
+     ylim = c(-3, 3),
+     pch = 19)
 ```
 
-```{r Sensitivity_logitP, cache=TRUE}
+```{r Sensitivity_logitP, cache=FALSE}
 s_analysis <-
    lapply(unique(PM_dat_D$trial_ref), function(Trial) {
-
       dat <- filter(PM_dat_D, trial_ref != Trial)
@@
 length(s_analysis)
-est <- lapply(s_analysis, function(e1){
-   data.frame(treat = rownames(e1$b),
+est <- lapply(s_analysis, function(e1) {
+   data.frame(
+      treat = rownames(e1$b),
       estimates = e1$b,
-              p = as.numeric(reportP(e1$pval, P_prefix = FALSE,AsNumeric = TRUE)))
+      p = as.numeric(reportP(
+         e1$pval, P_prefix = FALSE, AsNumeric = TRUE
+      ))
+   )
 })
@@
 sensitiviy_df %>%
-   ggplot(aes(Tnum, estimates, colour = treat))+
+   ggplot(aes(Tnum, estimates, colour = treat)) +
    geom_line(size = 1)
@@
 sensitiviy_df %>%
-   ggplot(aes(Tnum, p, colour = treat))+
-   geom_line(size = 1)+
+   ggplot(aes(Tnum, p, colour = treat)) +
+   geom_line(size = 1) +
    scale_y_log10()
@@
       medP = median(p),
-             maxP= max(p))
+      maxP = max(p)
+   )
 ```
+
 While estimates and P values remained the mostly same when each trial was dropped from the analysis.
@@
 
-Calculation of I^2
+Calculation of I^2.
+
 ```{r}
@@
          stop("'intercept' argument is empty")
-     return( inv_logit(m + intercept) - inv_logit(intercept))
+      return(inv_logit(m + intercept) - inv_logit(intercept))
    }
@@
 
-intercept <-PMsev_mvPer$b[1,1]
+intercept <- PMsev_mvPer$b[1, 1]
 z <- PMsev_mvPer$zval[1]
@@
 
-contrast_Ssum[6:15,] %>%
-   flextable()%>%
+contrast_Ssum[6:15, ] %>%
+   flextable() %>%
    autofit()
 ```
-
-<br>  
-<br>  
-<br>
 
@@
 
-<br>  
-<br>  
-<br>
+### Meta-analysis summary table
 
-### Meta-analysis summary table
 ```{r metafor_results}
@@
 # create data.frame of percent disease severity estimates
-results_mv <- cbind(
-   data.frame(
+results_mv <- cbind(data.frame(
    Moderator = c(
@@
    results_mv %>%
-   mutate(estimates = estimates - Intcpt,
+   mutate(
+      estimates = estimates - Intcpt,
       CI_lb = CI_lb - Intcpt,
-          CI_ub = CI_lb - Intcpt)
+      CI_ub = CI_lb - Intcpt
+   )
 
 # round the numbers
-results_mv[,c(4:6,8:9)] <- round(results_mv[,c(4:6,8:9)], 4)
-
-# results_mv <- 
-#    results_mv %>%
-#    mutate(
-#    eff_bar = round(
-#       1 - estimates, 
-#       4) * 100,
-#    eff_CI_high = round(
-#       1 - CI_lb
-#    , 4) * 100,
-#    eff_CI_low = round(
-#       1 - CI_ub
-#    , 4) * 100
-#    
-# )
-
-# remove efficacy in control
-#results_mv[1,10:12] <- NA
+results_mv[, c(4:6, 8:9)] <- round(results_mv[, c(4:6, 8:9)], 4)
 
 # rename colnames to give table headings
-colnames(results_mv)[c(1:9 )] <-
+colnames(results_mv)[c(1:9)] <-
    c("Moderator",
@@
 disease_estimates_table <-
-   results_mv[c(2,5,6,3,4), -6] %>%
+   results_mv[c(2, 5, 6, 3, 4), -6] %>%
    flextable() %>%
@@
       i = 1,
-      j = c(2:4,6:8),
+      j = c(2:4, 6:8),
       value = as_paragraph(
@@
       inline = TRUE
-    )%>%
-   hline_top(part="all", border = officer::fp_border(color = "black", width = 2))%>%
+   ) %>%
+   hline_top(part = "all",
+             border = officer::fp_border(color = "black", width = 2)) %>%
    width(j = 1, width = 1) %>%

### 2021-12-28 04_Severity_MetaAnalysis.Rmd
Revert major changes to analysis, leave incorrect analysis in place

@@
 This model will be similar to the grain yield meta-analysis and use the main variables:
+
    - *Powdery mildew severity*, the response variable (1-9 scale)
+
    - *Trial*, which resolves combinations of categorical random variables: 
@@
       iv) cultivar
+
    - *spray_management*, a moderator to evaluate the difference in effect size attributed to fungicide application timing.
+
    - *id*, random variable indicating each treatment is independent
@@
 
+<br>  
+<br>
+
 ### Define Trial
-
 ```{r define_trial}
@@
 
+<!--- I would remove from this line, 77 to line 96 as we shouldn't be promoting the idea of analysing an ordinal scale directly, just go straight to the severity conversion step and describe it and why it's done (i.e., you can't analyse an ordinal scale like this, though I found a cool presentation on how to analyse an ordinal scale using metanalysis for future reference, https://methods.cochrane.org/sites/methods.cochrane.org.statistics/files/public/uploads/SMG_training_course_cardiff/2010_SMG_training_cardiff_day1_session2_lewis.pdf) -->
+
+### Inspect PM severity for normality
+Given the meta-analysis assumes powdery mildew severity observations to be a univariate normal distribution $Y_i = N(\mu , \sigma)$, with a mean $\mu$ and standard deviation $\sigma$.
+We need to inspect severity for a normality.
+```{r sev_hist}
+hist(PM_dat_D$PM_final_severity)
+summary(PM_dat_D$PM_final_severity)
+```
+We can see here that powdery mildew severity observations are skewed towards the top of the scale, eight and nine in this case.
+
+We can improve the normality by transforming the effect size, disease severity, by squaring.
+```{r}
+PM_dat_D$yi_square <- PM_dat_D$PM_final_severity ^2
+PM_dat_D$vi_square <- (PM_dat_D$vi +1)^2
+# Note: Here I added 1 to the variance before it was squared.
+This is because squaring numbers below one makes the number smaller or remain zero.
+This does not change the meta-analysis mean estimates but does increase heterogeneity and tao._
+
+hist(PM_dat_D$yi_square)
+summary(PM_dat_D$yi_square)
+```
+
+Another transformation which might be more suitable for a discrete response is either a `log()` or `logit()` transformation. 
+However, first we should convert the scale from 1 - 9 to between 0 and 1.
+
 ### Transform severity response
 
-Because the data were taken on an ordinal scale, we need to transform this to a numeric value to perform the analysis, _i.e._
-
-> For ordinal measurements (e.g., disease rating on a 0 to 3 scale designating the ordinal degree of symptoms), nonparametric methods based on ranks should generally be used for hypothesis testing.
-See Shah and Madden (2004) for recommendations on the treatment of ordinal data.
-As an alternative, parametric proportional-odds models may be used for ordinal data, if there are sufficiently large numbers of observations for each experimental unit.
-If ordinal rating scores are used for ranges of disease severity (e.g., Horsfall-Barratt [where, for instance, a “2” corresponds to a severity range from 3 to 6%, and a “3” corresponds to a range of 6 to 12%]), each score should be converted to the midpoint of the corresponding disease severity range prior to use of a parametric analytical technique.
-
-- From <https://apsjournals.apsnet.org/page/authorinformation>
+Let us also transform the severity onto a percentage scale so we can compare the results of meta-analyses with no transformation, squared severity, and percent severity.
 
@@
 
-```{r ord-to-perc}
+```{r}
 # Percent severity conversion
@@
 
-```{r fit-gam}
+```{r}
 # fit a curve using a gam with spline value 0.01
@@
 
-# View plot of the GAM
+# View plot of gam
 plot(x = predict(g1,
-                 data.frame(y = seq(1, 9, by = 0.1))),
-     y = seq(1, 9, by = 0.1))
+                 data.frame(y = seq(1, 9, by = 0.1))), y = seq(1, 9, by = 0.1))
 points(x, y, col = "red", pch = 16)
@@
 ## Disease severity spray schedule meta-analysis  
-
 First let's look at the results of the meta-analysis without transformation
-
-```{r Metafor-Sev-analysis, cache=FALSE}
+```{r Metafor-Sev-analysis, cache=TRUE}
 PMsev_mv <- rma.mv(
@@
 
-```{r Metafor-Sev-analysisSQ, cache=FALSE}
-# create transformations
-PM_dat_D$yi_square <- PM_dat_D$PM_final_severity ^ 2
-PM_dat_D$vi_square <- (PM_dat_D$vi + 1) ^ 2
-
+```{r Metafor-Sev-analysisSQ, cache=TRUE}
 PMsev_mvSQ <- rma.mv(
@@
 ```
-
 This meta-analysis is more in-line with estimates from the yield meta-analysis.
@@
 
-```{r Metafor-Sev-analysis_log, cache=FALSE}
+```{r Metafor-Sev-analysis_log, cache=TRUE}
 # remove controls for response ratio meta-analysis
@@
 
-```{r Metafor-Sev-analysis_logitP, cache=FALSE}
+```{r Metafor-Sev-analysis_logitP, cache=TRUE}
 # remove controls for response ratio meta-analysis
@@
 
-```{r Sensitivity_logitP, cache=FALSE}
+```{r Sensitivity_logitP, cache=TRUE}
 s_analysis <-
@@
 ```{r}
-W <- diag(1/(PM_dat_D$vi_logit+0.0001))
+W <- diag(1 / (PM_dat_D$vi_logit + 0.0001))
 X <- model.matrix(PMsev_mvPer)
 P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
-100 * sum(PMsev_mvPer$sigma2) / (sum(PMsev_mvPer$sigma2) + (PMsev_mvPer$k-PMsev_mvPer$p)/sum(diag(P)))
+100 * sum(PMsev_mvPer$sigma2) / (sum(PMsev_mvPer$sigma2) + (PMsev_mvPer$k -
+                                                               PMsev_mvPer$p) / sum(diag(P)))
 
-100 * PMsev_mvPer$sigma2 / (sum(PMsev_mvPer$sigma2) + (PMsev_mvPer$k-PMsev_mvPer$p)/sum(diag(P)))
+100 * PMsev_mvPer$sigma2 / (sum(PMsev_mvPer$sigma2) + (PMsev_mvPer$k - PMsev_mvPer$p) /
+                               sum(diag(P)))
 ```
